### 2021-06-09 summaries/22-06/22-06.tex
Summary 22-06

 %\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib, floatfix]{revtex4}
\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib,floatfix]{revtex4-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx}      % tools for importing graphics
%\usepackage{lgrind}        % convert program code listings to a form 
                            % includable in a LaTeX document
%\usepackage{xcolor}        % produces boxes or entire pages with 
                            % colored backgrounds
%\usepackage{longtable}     % helps with long table options
%\usepackage{epsf}          % old package handles encapsulated postscript issues
\usepackage{bm}            % special bold-math package. usge: \bm{mathsymbol}
\usepackage{subcaption}
%\usepackage{asymptote}     % For typesetting of mathematical illustrations
%\usepackage{thumbpdf}
\usepackage[colorlinks=true]{hyperref}  % this package should be added after 
                                        % all others.
                                        % usage: \url{http://web.mit.edu/8.13}
\usepackage{wasysym}

\begin{document}
\title{June 2022 Summary of Project to Determine Asteroid Shape and Density from Flybys}
\author{Jack Dinsmore, Julien de Wit}
\email{jtdinsmo@mit.edu}
\date{\today}
\affiliation{MIT Department of Physics}

\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\comment}[1]{\textcolor{red}{\emph{ #1 }}}

\begin{abstract}
    Tidal torque induces changes in the angular velocity of asteroids on close flyby to a planet, and the nature of this change is strongly dependent on asteroid shape and density. We propose two models for the shape of the (convex) asteroid in question: a polyhedral model and an expansion of the surface in terms of the real spherical harmonics. The asteroid is divided into regions of similar volume, which are allowed to vary in density from each other. For many types of simulated asteroid flybys, a light curve is generated and the two asteroid models are fitted \comment{Results and Conclusion}.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\subsection{Tidal torque}
The torque $d\bm{\tau}$ imposed on a section of mass $dm$ inside an asteroid by tidal forces is
\begin{equation}
    \frac{d\bm{\tau}}{dm} =\frac{3\mu}{D^3} (\bm{\hat x} yz - \bm{\hat y} xz) = \frac{3\mu}{D^3} \bm{t}(\bm{r})
    \label{eqn:diff-torque}
\end{equation}
where $D$ is the distance between the asteroid and $x$, $y$, and $z$ are of course all new utensils. Here, we have chosen $+\$hat z$ to e

\section{Model}
\subsection{Asteroid model requirements}
\label{sec:requirements}
Any asteroid model with floating paramters designed to describe an asteroid with nonuniform density on flyby with a planet must be well-equipped to perform the following operations

\begin{enumerate}
    \item Rotate the asteroid along its axis of spin
    \item Extract the tidal torque on the asteroid at an instant
    \item Extract the moment of inertia tensor as a function of the parameters of the model
    \item Extract the center of mass of the asteroid as a function of the parameters of the model
\end{enumerate}
Fortunately, the first task requires no extra work; Euler's equations dictate the manner of rotation of a three dimensional body:
\begin{equation}
    I\dot{\bm{\omega}} + \bm \omega \times (I \bm \omega) = \bm \tau
    \label{eqn:euler}
\end{equation}
where $\bm \tau$ is the external torque on the asteroid: tidal torque in this case.

The second task requires us to integrate equation \ref{eqn:diff-torque} over the volume of the asteroid model as follows:
\begin{equation}
    \bm{\tau} =  \frac{3\mu}{D^3}\int_{V} d^3 r \bm{t}(\bm{r}) \rho(\bm r) 
    \label{eqn:total-torque}
\end{equation}
with the definition of $\bm{t}$ given in equation \ref{eqn:diff-torque}. Here, $V$ represents the volume of the asteroid, which will rotate and move over time.

Next, we calculate the moment of inertia in the co-rotating frame of the asteroid, which we call the ``local frame'' $\mathcal{L}$. The values we calculate will remain constant throughout the course of the asteroid's trajectory. We can convert vectors in the local frame to the global frame by the rotation matrix $R$. The moment of inertia tensor is then defined entirely by the following integrals
\begin{equation}
\begin{aligned}
    I_{xx} &= \int_{V_\mathcal{L}} d^3 r  \rho(\bm r) (y^2 + z^2) \\
    I_{yy} &= \int_{V_\mathcal{L}} d^3 r  \rho(\bm r) (x^2 + z^2) \\
    I_{zz} &= \int_{V_\mathcal{L}} d^3 r  \rho(\bm r) (x^2 + y^2) \\
    I_{xy}=I_{yx} &= -\int_{V_\mathcal{L}} d^3r \rho(\bm r) xy \\
    I_{yz}=I_{yx} &= -\int_{V_\mathcal{L}} d^3r \rho(\bm r) yz\\
    I_{xz}=I_{zx} &= -\int_{V_\mathcal{L}} d^3r \rho(\bm r) xz
    \label{eqn:moi-local}
\end{aligned}
\end{equation}
where $I_{ij}$ are the components of the inertia tensor $I_\mathcal{L}$ in the local frame, and
\begin{equation}
    I_\mathcal{G} = R I_\mathcal{L} R^{-1}
    \label{eqn:moi-global}
\end{equation}
is the inertia tensor in the global frame.

The final task is to extract the center of mass of the asteroid in the local frame, which is defined as 
\begin{equation}
    \bm C_\mathcal{L} = \brackets{\int_{V_\mathcal{L}} d^3 r \rho(\bm r)\bm r}\brackets{\int_{V_\mathcal{L}} d^3 r \rho(\bm r)}^{-1}.
    \label{eqn:com}
\end{equation}

For this paper, we will model the density distribution of the asteroid by partitioning the asteroid into $N$ chunks $V_i$ of uniform density $\rho_i$. We then compute the integrals in equations \ref{eqn:total-torque} and \ref{eqn:moi-local} by summing over the same integrals computed on each $V_i$. Performing the volume integrals directly is difficult, so we making use of the identity $\int_{V_i} d^3 r \nabla \times \bm A = \oint_{\partial V_i} d^2 \bm r \times \bm A$
and achieve
\begin{equation}
    \bm \tau = \frac{3\mu}{D^3} \sum_{i=1}^N \rho_i\oint_{\partial V_i} (d^2 \bm r) \times \bm T(\bm r)
    \label{eqn:surface-torque}
\end{equation}
where 
\begin{equation}
    \bm T(\bm r) = \frac{r_z}{2}\parens{r_x^2 + r_y^2}\hat{\bm z}
    \label{eqn:torque-generator}
\end{equation}
was chosen such that $\nabla \times \bm T = \bm t$. By the divergence theorem,
\begin{equation}
    I_{ij} = \sum_{i=1}^N \rho_i\oint_{\partial V_i} d^2 \bm r \cdot \bm I_{ij}(\bm r)
    \label{eqn:surface-moi}
\end{equation}
for 
\begin{equation}
\begin{aligned}
    \bm I_{ii}(\bm r)& = \hat{\bm j} \frac{r_j^3}{3} + \hat{\bm k} \frac{r_k^3}{3} \\
    \bm I_{ij}(\bm r)& = \hat{\bm k} r_i r_j r_k \hspace{1.5 cm} i \neq j
    \label{eqn:moi-generator}.
\end{aligned}
\end{equation}
Similarly, we calculate the center of mass:
\begin{equation}
    \bm C_\mathcal{L} = \brackets{\sum_{i=1}^N \rho_i \oint_{\partial V_i}d^2 \bm r \frac{r^2}{2}}\brackets{\sum_{i=1}^N \rho_i \oint_{\partial V_i}d^2 \bm r \cdot \frac{\bm r}{3}}^{-1}
    \label{eqn:com-surf}
\end{equation}
where we implicitly used the identity $\int_V \nabla \psi d^3 r = \int_{\partial V} d^2 \bm r \psi$.

\subsection{Parameterization of asteroid surface}
We seek a model of asteroid surface that covers many asteroid shapes, is well behaved for all fit parameters, and admits an adjustable number of parameters. In this paper we model the asteroid surface as a sum of the real spherical harmonics:
\begin{equation}
    r(\theta, \phi) = \sum_{l=0}^L\sum_{m=-l}^l C_{lm} Y_{lm}(\theta, \phi)
    \label{eqn:sph-surface}
\end{equation}
where $r(\theta, \phi)$ is the distance from the origin to the surface of the pulsar in direction $(\theta, \phi)$, and $C_{lm}$ are the fit parameters. Here we define the real spherical harmonics as 
\begin{equation}
    \begin{aligned}
        Y_{lm} = &(-1)^m\sqrt{\frac{2l + 1}{2\pi}\frac{(l-|m|)!}{(l+|m|)!}}\\
        &\times P_l^{|m|}(\cos\theta)\begin{cases}
            \sin(|m|\phi)& m < 0\\
            1/\sqrt{2}& m = 0\\
            \cos(|m|\phi)& m > 0\\
        \end{cases}.
        \label{eqn:spherical-harmonics}
    \end{aligned}
\end{equation}
The number of parameters may be changed by adjusting $L$. Note that there are $(L+1)^2$ parameters.

Once the $C_{lm}$ parameters have been set, the asteroid surface is approximated as a polyhedron. The radial positions of each vertex are determined by equation \ref{eqn:sph-surface}. The angular positions are assigned as followed. A cube is considered, with each side tessellated into an $n\times n$ grid. The grids are projected onto the unit sphere and their angular positions are used for the angular coordinates of the polyhedron vertices.

In general, the $l$th order spherical harmonic encodes fluctuation with wavelength $2\pi / l$ radians. Similarly, each face of the polyhedron has angular width $2\pi / (4n)$. It is therefore sensible to set $n \gg L/4$, so that the high-order spherical harmonics are included in the model. The upper bound on $n$ is determined by computation speed.

The angular positions of the vertices need not be the projection of a cube onto the unit sphere; projections of a tetrahedron, octahedron, or icosahedron are also possible, since the symmetry properties of these platonic solids guarantee that the vertices will be placed evenly around the sphere. The icosahedron provides the most even distribution of points, but its 20 faces produce a large number of vertices which might not be desired depending on the computation speed available.

Since the angular positions of the polyhedron vertices are spread evenly along the surface and do not depend on the parameters $C_{lm}$, they will behave well even for extreme fit parameters $C_{lm}$.

The radial positions of the vertices are not guaranteed to be well behaved, so we outlaw all choices of $C_{lm}$ that result in vertices too close to or too far from the origin. For example, we could require that the range of $r(\theta, \phi)$ over the asteroid be less than or equal to its mean value.

\subsection{Parameterization of asteroid interior}
As discussed in section \ref{sec:requirements}, we will model the density distribution of the asteroid interior by breaking the interior into $N$ chunks of uniform density. It will be advantageous for the chunks to be of roughly equal volume, so that the model does not induce any unphysical structure in the interior of the asteroid.

To guarantee this property, we subdivide the asteroid interior by foliating it into $m$ thick shells, with the $s$th shell containing the radii from $\frac{s-1}{n}r(\theta, \phi)$ to $\frac{s}{n}r(\theta, \phi)$. Each shell is further subdivided as the surface was divided, by projecting the tessellated faces of a cube onto the unit sphere. However, we tessellate the faces less for the inner shells, using a grid with $ns / m$ squares in each row for shell $s$. The integers $n$ and $m$ should be chosen such that $n/m$ is itself an integer.

The volume of the $s$th shell is roughly proportional to $s^2$. With the above subdivision method, the $s$th shell is divided into $6(ns / m)^2$ chunks, so that the volume of each chunk is independent of $s$. There will be some variation in volume caused by different radii at different points of the asteroid, the thickness of the shells, and warping of the cube's faces caused by the projection, but for this paper we will accept these variations.

There are $\sum_{s=1}^m 6(ns/m)^2$ chunks all together, each with their one parameter for their density. Adding the parameters of the spherical harmonics, we achieve a total number of parameters:
\begin{equation}
    P = (L+1)^2 + \frac{n^2(m+1)(2m+1)}{m}
    \label{eqn:num-parameters}
\end{equation}

\subsection{Calculating moment of inertia and torque}
Once the shape of the asteroid has been fixed for parameters $C_{lm}$ and the densities $\rho_i$ have been assigned to each chunk, the center of mass must next be calculated via equation \ref{eqn:com-surf}. Each volume $V_i$ is a hexahedron, with the exception of those touching the origin which are pentahedra. So we break the faces into 10 or 12 triangles and compute both surface integral on each. The first surface integral is
\begin{equation}
    \oint_{\partial V_i} d^2 \bm r \frac{r^2}{2} =
    \frac{1}{2}\sum_{j=1}^{10, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\int_0^1 d\alpha \int_0^{1-\alpha} d\beta r^2
    \label{eqn:com-triangle-1}
\end{equation}
while the second, which also determines the mass of the asteroid, is 
\begin{equation}
    \oint_{\partial V_i} d^2 \bm r \frac{\bm r}{3} =
    \frac{1}{3}\sum_{j=1}^{10, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\cdot \int_0^1 d\alpha \int_0^{1-\alpha} d\beta \bm r.
    \label{eqn:com-triangle-2}
\end{equation}
Here, $\bm \ell_{ij1}$ and $\bm \ell_{ij2}$ are two edges of the $j$th triangular face of $V_i$, ordered such that $\bm \ell_{ij1} \times \bm \ell_{ij2}$ points out of $V_i$. These vectors can be computed once the fit parameters are known, and then simply rotated by $R$ as the asteroid rotates.

The above two integrals have analytical solutions to be found in the appendix.

Once the center of mass $\bm C_{\mathcal L}$ is calculated, the asteroid model should be manually translated by $\bm -C_{\mathcal L}$ so that the origin represents the center of mass. Then we may perform the torque integral (equation \ref{eqn:surface-torque}) and the moment of inertia integrals (equation \ref{eqn:surface-moi}) in a similar method to equations \ref{eqn:com-triangle-1} and \ref{eqn:com-triangle-2}. Again, the solutions are analytical and can be found in the appendix.

\subsection{Limitations of the model}
The depth of this model is easily scalable by changing $L$, $m$, or $n$. Higher $L$ results in a more precise shape, and higher $m$ and $n$ result in better knowledge of the radial and angular density distribution respectively. The model is robust under allowed values of the parameters $C_{lm}$, and the asteroid's torque, moment of inertia, and center of mass are all analytically calculable, which speeds up the rate of fitting.

However, the model contains two major limitations. First, it can only represent ``star shaped'' asteroids---that is, asteroids where there is a point such that a line segment from that point to any point on the surface does not exit the asteroid. By restricting the values of $C_{lm}$, we also rule out some extreme shapes that are star-shaped. Most known asteroid shapes can be represented with this model, so we conclude that this limitation does not pose too serious a threat to accuracy. \comment{Prove this!}

A radial density profile is also built into this asteroid model. Although the chunks of constant density $V_i$ do not shrink in volume towards the center, their sides all point towards the center, which may give a slight bias towards radial density profiles. \comment{I can check whether this exists}.

\newpage

\section{Old spherical harmonic model}
For the spherical harmonic model, we describe the shape of the model with the first $L$ orders of the real spherical harmonics:
\begin{equation}
    r(\theta, \phi) = \sum_{l=0}^L\sum_{m=-l}^l C_{lm} Y_{lm}(\theta, \phi)
    \label{eqn:sph-surface}
\end{equation}
where $C_{lm}$ are parameters, and 
\begin{equation}
\begin{aligned}
    Y_{lm} = &(-1)^m\sqrt{\frac{2l + 1}{2\pi}\frac{(l-|m|)!}{(l+|m|)!}}\\
    &\times P_l^{|m|}(\cos\theta)\begin{cases}
        \sin(|m|\phi)& m < 0\\
        1/\sqrt{2}& m = 0\\
        \cos(|m|\phi)& m > 0\\
    \end{cases}.
    \label{eqn:spherical-harmonics}
\end{aligned}
\end{equation}
Note that there are $(L+1)^2$ parameters.

Like for the polyhedral model, we will need to break this shape into $M$ chunks. We would like for these chunks to be of roughly equal size so that the model is ambivalent as possible about the density distribution of the asteroid. To do so, we will first foliate the asteroid into $n$ thick shells by multiplying $r(\theta, \phi)$ by integer multiples of $1/n$. In the next step, we break up the shells further.

Consider a cube, where each face is subdivided into an $i\times i$ array of smaller squares. The vertices of these squares can be projected onto a sphere, yielding $6i^2$ patches of roughly equal area on the sphere, with vertices given in spherical coordinates by the projection. The $i$th shell can be broken up into $6i^2$ chunks using these projected vertices.

The volume of each of these chunks is roughly proportional to the volume of each shell divided by $6i^2$. The shell volume in turn is proportional to $4\pi i^2$, so that we expect the volume of each chunk to be roughly equal.

% Ensure origin is center of mass for both models
% Use mathematica to do the integrals

% Talk about rotations.

We parameterize each chunk with spherical coordinates: ($\alpha$, $\theta$, $\phi$), where the radial coordinate is $\alpha r(\theta, \phi)$. The Jacobian turns out to be $\alpha^2 \sin\theta r^3(\theta, \phi)$, which is the same as spherical coordinates. Thus, the torque integral reduces to 
\begin{equation}
    \begin{aligned}
    \int_{V_i} d^3 r \bm t(\bm r) = \frac{2}{5}\sqrt{\frac{\pi}{15}}\frac{(i+1)^5-i^5}{n^5}\\
    \times\int_{\Omega_i} d\Omega \brackets{\sum_{l=0}^\infty\sum_{m=-l}^l C_{lm} Y_{lm}}^5\brackets{\hat{\bm x} Y_{2, -1} - \hat{\bm y} Y_{2, 1}}
    \end{aligned}
\end{equation}
where $\Omega_i$ is the solid angle occupied by chunk $i$.

\section{Update}
Instead of doing what I've outlined above, I'd like to use the spherical harmonic technique to segment the asteroid and define its shape. Then break it into polyhedrons, and use the polyhedral integral outlined above.

\bibliography{../asteroids-flybys.bib}
\end{document}

### 2021-06-09 summaries/22-06/22-06.tex
Added analytical equations to summary

@@
 \end{equation}
-where $I_{ij}$ are the components of the inertia tensor $I_\mathcal{L}$ in the local frame, and
+where $I_{ab}$ are the components of the inertia tensor $I_\mathcal{L}$ in the local frame, and
 \begin{equation}
@@
 \begin{equation}
-    I_{ij} = \sum_{i=1}^N \rho_i\oint_{\partial V_i} d^2 \bm r \cdot \bm I_{ij}(\bm r)
+    I_{ab} = \sum_{i=1}^N \rho_i\oint_{\partial V_i} d^2 \bm r \cdot \bm I_{ab}(\bm r)
     \label{eqn:surface-moi}
@@
 \begin{aligned}
-    \bm I_{ii}(\bm r)& = \hat{\bm j} \frac{r_j^3}{3} + \hat{\bm k} \frac{r_k^3}{3} \\
-    \bm I_{ij}(\bm r)& = \hat{\bm k} r_i r_j r_k \hspace{1.5 cm} i \neq j
+    \bm I_{aa}(\bm r)& = \hat{\bm b} \frac{r_b^3}{3} + \hat{\bm c} \frac{r_c^3}{3} \\
+    \bm I_{ab}(\bm r)& = -\hat{\bm c} r_a r_b r_c \hspace{1.5 cm} a \neq b
     \label{eqn:moi-generator}.
@@
 \subsection{Calculating moment of inertia and torque}
+\label{sec:equations}
 Once the shape of the asteroid has been fixed for parameters $C_{lm}$ and the densities $\rho_i$ have been assigned to each chunk, the center of mass must next be calculated via equation \ref{eqn:com-surf}.
@@
 Here, $\bm \ell_{ij1}$ and $\bm \ell_{ij2}$ are two edges of the $j$th triangular face of $V_i$, ordered such that $\bm \ell_{ij1} \times \bm \ell_{ij2}$ points out of $V_i$.
+The vector $v_i$ points to the intersection of $\bm \ell_{ij1}$ and $\bm \ell_{ij2}$.
 These vectors can be computed once the fit parameters are known, and then simply rotated by $R$ as the asteroid rotates.
@@
 
-\section{Update}
-Instead of doing what I've outlined above, I'd like to use the spherical harmonic technique to segment the asteroid and define its shape.
-Then break it into polyhedrons, and use the polyhedral integral outlined above.
+\appendix
+\section{Analytical equations for torque, center of mass, and moment of inertia}
+In section \ref{sec:equations}, we outlined integrals for calculating the torque on the asteroid, the moment of inertia, and the center of mass.
+We stated that the integrals were analytical, but did not give the analytical values.
+They are given here.
+
+The mass of the asteroid is given by equation \ref{eqn:analytical-mass}.
+It can be used to calculate the center of mass of the asteroid with equation \ref{eqn:analytical-com}.
+Once the center of mass is subtracted so that the origin is the new center, the moment of inertia components in the local frame can be computed with equations \ref{eqn:analytical-moi-same} and  \ref{eqn:analytical-moi-diff}.
+Then the torque can be computed with equation \ref{eqn:analytical-torque} with the model positions rotated by $R$ to account for asteroid rotation.
+
+\begin{table*} 
+    \begin{equation}
+        M = \frac{1}{6}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \cdot (\bm \ell_{ij1} + \bm \ell_{ij2} + 2\bm v)
+        \label{eqn:analytical-mass}
+    \end{equation}
+    \begin{equation}
+        C_\mathcal{L} = \frac{1}{12M}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \{2(\bm \ell_{ij1} - \bm \ell_{ij2})^2 + \bm \ell_{ij1}\cdot  \bm \ell_{ij2} + 6(\bm \ell_{ij1}+ \bm v)\cdot (\bm \ell_{ij2} + \bm v)\}
+        \label{eqn:analytical-com}
+    \end{equation}
+    \caption*{\textit{Top}: mass of the asteroid model, and \textit{bottom}: center of mass of the asteroid model. }
+\end{table*}
+
+\begin{table*} 
+    \begin{equation}
+        \begin{aligned}
+            I_{aa} = \frac{1}{60}\sum_{i=1}^N \rho_i \sum_{j=1}^{10, 12} \parens{\ell_{ij1}\times \ell_{ij2}}\cdot \{&\hat{\bm b}[\ell_{1b}^3 + \ell_{1b}^2 \ell_{2b} + \ell_{1b} \ell_{2b}^2 + \ell_{2b}^3 +
+            5 v_b (\ell_{1b}^2 + \ell_{1b} l2b + \ell_{2b}^2) + 
+            10 v_b^2 (\ell_{1b} + \ell_{2b}) + 10 v_b^3]\\
+             + & \hat {\bm c}[\ell_{1c}^3 + \ell_{1c}^2 \ell_{2c} + \ell_{1c} \ell_{2c}^2 + \ell_{2c}^3 + 5 v_c (\ell_{1c}^2 + \ell_{1c} \ell_{2c} + \ell_{2c}^2) + 10 v_c^2(\ell_{1c} + \ell_{2c}) + 10 v_c^3]\}
+        \end{aligned}
+    \label{eqn:analytical-moi-same}
+    \end{equation}
+    \begin{equation}
+        \begin{aligned}
+            I_{ab} = -\frac{1}{120}\sum_{i=1}^N \rho_i \sum_{j=1}^{10, 12} \parens{\ell_{ij1}\times \ell_{ij2}}\cdot \hat{\bm c}\{
+                &\ell_{1c} [6 \ell_{1a} \ell_{1b} + 2 \ell_{2a} \ell_{2b} + 2 \ell_{1b} (\ell_{2a} + 5 v_a) + 2 \ell_{1a} (\ell_{2b} + 5 v_b) +  5 \ell_{2a} v_b + 5 \ell_{2b} v_a + 20 v_a v_b] \\
+                + &\ell_{2c}[2 \ell_{1a} \ell_{1b} + 6 \ell_{2a} \ell_{2b}
+                + 2 \ell_{2b}(\ell_{1a}  + 5 v_a) + 2 \ell_{2a}(\ell_{1b} + 5 v_b)
+                + 5 \ell_{1a} v_b + 5 \ell_{1b}v_a + 20 v_a v_b] \\
+                + &5v_c[ \ell_{1a} (2\ell_{1b} + \ell_{2b}) + \ell_{2a}(2\ell_{2b} + \ell_{1b}) + 4 v_a(\ell_{2b} + \ell_{1b}) + 4v_b(\ell_{1a} + \ell_{2a})  + 12 v_a v_b]\}
+        \end{aligned}
+    \label{eqn:analytical-moi-diff}
+    \end{equation}
+    \caption*{Diagonal (\textit{top}) and off-diagonal (\textit{bottom}) components of the moment of inertia tensor on an asteroid model.
+The $b$th component of $\bm \ell_{ij1}$ has been written as $\ell_{1b}$ for brevity, and likewise for other components.}
+\end{table*}
+
+\begin{table*} 
+    \begin{equation}
+        \begin{aligned}
+        \tau = \frac{\mu}{40D^3}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \times \hat {\bm z} \{
+        &\ell_{1z} [(\ell_{2x} + 5v_x)(\ell_{2x} + 2\ell_{1x}) + (\ell_{2y} + 5 v_y)(\ell_{2y}+2\ell_{1y}) + 3 (\ell_{1x}^2 + \ell_{1y}^2) + 10(v_x^2 + v_y^2)]\\
+        + &\ell_{2z} [ (\ell_{1x}+5v_x)(\ell_{1x}+2\ell_{2x}) + (\ell_{1y}+5v_y)(\ell_{1y}+2\ell_{2y}) + 3 (\ell_{2x}^2 + \ell_{2y}^2) + 10(v_x^2 + v_y^2)]\\
+        + &5v_z [(\ell_{1x}^2 + \ell_{1y}^2 + \ell_{2x}^2 + \ell_{2y}^2 + \ell_{1x} \ell_{2x} + \ell_{1y} \ell_{2y}) \\
+        & + 2v_x(2\ell_{1x} + 2\ell_{2x} + 3 v_x) + 2v_y(2\ell_{1y} + 2\ell_{2y} + 3 v_y)]\}
+        \end{aligned}
+    \label{eqn:analytical-torque}
+    \end{equation}
+    \caption*{Torque on an asteroid model.
+The $z$th component of $\bm \ell_{ij1}$ has been written as $\ell_{1z}$ for brevity, and likewise for other components.
+The $\bm \ell$ vectors used to do this integral should be in the global frame of reference, rotated by $R$.}
+\end{table*}
 

### 2021-06-11 summaries/22-06/22-06.tex
Updated summary

@@
 \end{equation}
-where $D$ is the distance between the asteroid and $x$, $y$, and $z$ are of course all new utensils. Here, we have chosen $+\$hat z$ to e
+where $D$ is the distance between the asteroid, $\mu$ is the gravitational parameter of the planet being orbited.
+We have oriented our axes such that $\hat {\bm z}$ points towards the planet and $\hat {\bm y}$ points forward in the plane of orbit of the asteroid.
 
@@
 where $\bm \tau$ is the external torque on the asteroid: tidal torque in this case.
+
+Equation \ref{eqn:diff-torque} is written in the frame where $\hat {\bm z}$ points towards the planet.
+Assuming the torque $\bm \tau$ in equation \ref{eqn:euler} is also written in this frame, there will be an additional rotation caused by the orbital motion of the asteroid of $\bm \Omega = \bm v \times \hat{\bm z} / D$, where $\bm v$ is the orbital velocity of the asteroid.
+Note that $\bm \Omega$ is parallel to $\hat x$.
+From conservation of angular momentum, it follows that $\dot{\bm \Omega} = -2(\bm v \cdot \hat{\bm z})\bm \Omega / D$.
+The final angular acceleration is then
+\begin{equation}
+    \dot{\bm \omega} = -\dot{\bm \Omega} + I^{-1}\brackets{\bm \tau - (\bm \omega + \bm \Omega) \times I(\bm \omega + \bm \Omega)}
+    \label{eqn:angular-acc}
+\end{equation}
 
@@
     \begin{equation}
-        C_\mathcal{L} = \frac{1}{12M}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \{2(\bm \ell_{ij1} - \bm \ell_{ij2})^2 + \bm \ell_{ij1}\cdot  \bm \ell_{ij2} + 6(\bm \ell_{ij1}+ \bm v)\cdot (\bm \ell_{ij2} + \bm v)\}
+        \bm C_\mathcal{L} = \frac{1}{12M}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \{2(\bm \ell_{ij1} - \bm \ell_{ij2})^2 + \bm \ell_{ij1}\cdot  \bm \ell_{ij2} + 6(\bm \ell_{ij1}+ \bm v)\cdot (\bm \ell_{ij2} + \bm v)\}
         \label{eqn:analytical-com}
@@
         \begin{aligned}
-        \tau = \frac{\mu}{40D^3}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \times \hat {\bm z} \{
+        \bm \tau = \frac{\mu}{40D^3}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \times \hat {\bm z} \{
         &\ell_{1z} [(\ell_{2x} + 5v_x)(\ell_{2x} + 2\ell_{1x}) + (\ell_{2y} + 5 v_y)(\ell_{2y}+2\ell_{1y}) + 3 (\ell_{1x}^2 + \ell_{1y}^2) + 10(v_x^2 + v_y^2)]\\

### 2021-06-14 summaries/22-06/22-06.tex
Fixed typo in integrals (corrected in summaries as well)

@@
 
+\newcommand{\abs}[1]{\left| #1 \right|}
 \newcommand{\parens}[1]{\left( #1 \right)}
@@
 Each volume $V_i$ is a hexahedron, with the exception of those touching the origin which are pentahedra.
-So we break the faces into 10 or 12 triangles and compute both surface integral on each.
+So we break the faces into 6 (pentahedra) or 12 (hexahedra) triangles and compute both surface integral on each.
 The first surface integral is
@@
     \oint_{\partial V_i} d^2 \bm r \frac{r^2}{2} =
-    \frac{1}{2}\sum_{j=1}^{10, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\int_0^1 d\alpha \int_0^{1-\alpha} d\beta r^2
+    \frac{1}{2}\sum_{j=1}^{6, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\int_0^1 d\alpha \int_0^{1-\alpha} d\beta r^2
     \label{eqn:com-triangle-1}
@@
     \oint_{\partial V_i} d^2 \bm r \frac{\bm r}{3} =
-    \frac{1}{3}\sum_{j=1}^{10, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\cdot \int_0^1 d\alpha \int_0^{1-\alpha} d\beta \bm r.
+    \frac{1}{3}\sum_{j=1}^{6, 12} \parens{\bm \ell_{ij1}\times\bm \ell_{ij2}}\cdot \int_0^1 d\alpha \int_0^{1-\alpha} d\beta \bm r.
     \label{eqn:com-triangle-2}
@@
     \begin{equation}
-        M = \frac{1}{6}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \cdot (\bm \ell_{ij1} + \bm \ell_{ij2} + 2\bm v)
+        M = \frac{1}{18}\sum_{i=1}^N\rho_i \sum_{j=1}^{6, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \cdot (\bm \ell_{ij1} + \bm \ell_{ij2} + 3\bm v)
         \label{eqn:analytical-mass}
@@
     \begin{equation}
-        \bm C_\mathcal{L} = \frac{1}{12M}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \{2(\bm \ell_{ij1} - \bm \ell_{ij2})^2 + \bm \ell_{ij1}\cdot  \bm \ell_{ij2} + 6(\bm \ell_{ij1}+ \bm v)\cdot (\bm \ell_{ij2} + \bm v)\}
+        \bm C_\mathcal{L} = \frac{1}{24M}\sum_{i=1}^N\rho_i \sum_{j=1}^{6, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \parens{\abs{\bm\ell_{ij1}}^2  + \abs{\bm\ell_{ij2}}^2 + 6\abs{\bm v}^2 + \bm\ell_{ij1} \cdot \bm\ell_{ij2} + 4(\bm \ell_{ij1} + \bm \ell_{ij2})\cdot \bm v}
         \label{eqn:analytical-com}
@@
         \begin{aligned}
-            I_{aa} = \frac{1}{60}\sum_{i=1}^N \rho_i \sum_{j=1}^{10, 12} \parens{\ell_{ij1}\times \ell_{ij2}}\cdot \{&\hat{\bm b}[\ell_{1b}^3 + \ell_{1b}^2 \ell_{2b} + \ell_{1b} \ell_{2b}^2 + \ell_{2b}^3 +
-            5 v_b (\ell_{1b}^2 + \ell_{1b} l2b + \ell_{2b}^2) + 
+            I_{aa} = \frac{1}{60}\sum_{i=1}^N \rho_i \sum_{j=1}^{6, 12} \parens{\bm \ell_{ij1}\times \bm \ell_{ij2}}\cdot \{&\hat{\bm b}[\ell_{1b}^3 + \ell_{1b}^2 \ell_{2b} + \ell_{1b} \ell_{2b}^2 + \ell_{2b}^3 +
+            5 v_b (\ell_{1b}^2 + \ell_{1b} \ell_{2b} + \ell_{2b}^2) + 
             10 v_b^2 (\ell_{1b} + \ell_{2b}) + 10 v_b^3]\\
@@
         \begin{aligned}
-            I_{ab} = -\frac{1}{120}\sum_{i=1}^N \rho_i \sum_{j=1}^{10, 12} \parens{\ell_{ij1}\times \ell_{ij2}}\cdot \hat{\bm c}\{
+            I_{ab} = -\frac{1}{120}\sum_{i=1}^N \rho_i \sum_{j=1}^{6, 12} \parens{\bm \ell_{ij1}\times \bm \ell_{ij2}}\cdot \hat{\bm c}\{
                 &\ell_{1c} [6 \ell_{1a} \ell_{1b} + 2 \ell_{2a} \ell_{2b} + 2 \ell_{1b} (\ell_{2a} + 5 v_a) + 2 \ell_{1a} (\ell_{2b} + 5 v_b) +  5 \ell_{2a} v_b + 5 \ell_{2b} v_a + 20 v_a v_b] \\
@@
         \begin{aligned}
-        \bm \tau = \frac{\mu}{40D^3}\sum_{i=1}^N\rho_i \sum_{j=1}^{10, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \times \hat {\bm z} \{
+        \bm \tau = \frac{\mu}{40D^3}\sum_{i=1}^N\rho_i \sum_{j=1}^{6, 12} \parens{\bm\ell_{ij1} \times \bm\ell_{ij2}} \times \hat {\bm z} \{
         &\ell_{1z} [(\ell_{2x} + 5v_x)(\ell_{2x} + 2\ell_{1x}) + (\ell_{2y} + 5 v_y)(\ell_{2y}+2\ell_{1y}) + 3 (\ell_{1x}^2 + \ell_{1y}^2) + 10(v_x^2 + v_y^2)]\\
@@
 
-\bibliography{../asteroids-flybys.bib}
+\bibliography{../asteroid-flybys.bib}
 \end{document}

### 2021-07-06 summaries/22-07/22-07.tex
New summary

 %\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib, floatfix]{revtex4}
\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib,floatfix]{revtex4-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx}      % tools for importing graphics
%\usepackage{lgrind}        % convert program code listings to a form
                            % includable in a LaTeX document
%\usepackage{xcolor}        % produces boxes or entire pages with
                            % colored backgrounds
%\usepackage{longtable}     % helps with long table options
%\usepackage{epsf}          % old package handles encapsulated postscript issues
\usepackage{bm}            % special bold-math package. usge: \bm{mathsymbol}
\usepackage{subcaption}
%\usepackage{asymptote}     % For typesetting of mathematical illustrations
%\usepackage{thumbpdf}
\usepackage[colorlinks=true]{hyperref}  % this package should be added after
                                        % all others.
                                        % usage: \url{http://web.mit.edu/8.13}
\usepackage{wasysym}

\begin{document}
\title{July 2022 Summary of Project to Determine Asteroid Shape and Density from Flybys}
\author{Jack Dinsmore, Julien de Wit}
\email{jtdinsmo@mit.edu}
\date{\today}
\affiliation{MIT Department of Physics}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\comment}[1]{\textcolor{red}{\emph{ #1 }}}
\newcommand{\x}{\bm{\hat x}}
\newcommand{\y}{\bm{\hat y}}
\newcommand{\z}{\bm{\hat z}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\R}{\mathcal{R}}

\begin{abstract}
    The purpose of this summary is to derive the math governing the way an asteroid reacts to a non-point source. It was motivated by the discovery that, under the assumption of a gravitating point source and a small asteroid, the tidal torque can be written in terms of components of the moment of inertia, which means inference is limited to the six components of the inertia matrix. By violating these assumptions and considering other effects (oblateness, etc.), we can break the degeneracy.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Definitions}
Please see \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.56.5257&rep=rep1&type=pdf}{info on spherical harmonics}
$$P_{lm}=\frac{1}{2l!}(1-t^2)^{m/2} \frac{d^{l+1}}{dl^{l+m}}(t^2-1)^l$$
$$Y_{lm}(\theta, \phi) = P_{lm}(\cos\theta)e^{im\phi}$$
$$\bar Y_{lm}(\theta, \phi) = (-1)^m \sqrt{\frac{2l+1}{4\pi}\frac{(l-m)!}{(l+m)!}} Y_{lm}(\theta, \phi)$$
$$R_{lm}(\bm r) = (-1)^m \frac{r^l}{(l+m)!}Y_{lm}(\bm r)$$
$$S_{lm}(\bm r) = (-1)^m \frac{(l-m)!}{r^{l+1}}Y_{lm}(\bm r)$$
We write $Y(\bm r)=Y(\hat{\bm r})$.

These definitions lead to several key facts. For $r' < r$,
$$\frac{1}{|\bm r - \bm r'|}=\sum_{lm}R_{lm}(\bm r')S^*_{lm}(\bm r).$$
We also have a translation rule:
$$S_{lm}=\sum_{l'm'}R^*_{l'm'}(\bm r')S_{l+l',m+m'}(\bm r)$$
which I have used to show, via Mathematica, for $D > r$,
$$S_{lm}^*(\bm r - \bm D)=(-1)^l (-1)^m \sum_{l'=|m|}^\infty R_{l'm}^*(\bm r) \frac{(l+l')!}{D^{l+l'+1}}.$$
Similarly, we have some gradient formulas that result in
$$\bm r \times \nabla R_{lm}^*=\frac{1}{2}[(\x + i\y)(l-m+1)R^*_{l,m-1}$$
$$+(-\x+i\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}]$$
All of these functions obey the symmetry relations $F_{l,-m}=(-1)^mF_{lm}^*$
\comment{WRONG! Y DOES NOT! FIX THIS!!!}.

\section{Derivation}
Consider an asteroid at distance $D$ from a gravitating body. Place the origin near the asteroid (it will be convenient later for the origin to be at the center of mass of the asteroid, but not necessary), and orient the $\z$ axis to point towards the gravitating body. For brevity, we will call the gravitating body a planet, but it could be a star or another asteroid. No assumptions are made about the nature of the body except that its distance to the asteroid can be placed inside a sphere which does not contain the asteroid.

Consider the gravitational field $V$ of the body, defined by
$$V = -G\int_M d^3 r' \rho_M(\bm r')\frac{1}{|\bm r' - \bm r|}.$$
The force dealt on an object of mass $m$ by such a potential is $\bm F = -m\nabla V$. This potential can be expanded into spherical harmonics by one of the defintions:
$$V = -G\sum_{lm}S^*_{lm}(\bm r)\int_M d^3 r' \rho_M(\bm r')R_{lm}(\bm r').$$
For convenience, we define
$$\J_{lm} = \int_M d^3 r' \rho_M(\bm r')R_{lm}(\bm r')$$
so that the potential and force experience by small amount of mass $dm$, is
$$V = -G\sum_{lm}S^*_{lm}(\bm r)\J_{lm},\indent \frac{d\bm F}{dm}=G\sum_{lm}\J_{lm} \nabla_{\bm r} S^*_{lm}(\bm r).$$
Consequentially, the torque on an entire asteroid is
$$\bm \tau = G\sum_{lm}\J_{lm} \int d^3 r\rho(\bm r)\bm r \times \nabla_{\bm R} S^*_{lm}(\bm R)$$
where the integral is carried out over the smaller body, and $\bm R$ represents the vector pointing from the center of the planet to the point of integration, which is $\bm R = \bm r - \bm D$ if $\bm D$ points to the center of the asteroid.

The word ``center'' here is loosely defined because the center of the planet need only be the point around which $\J_{lm}$ is calculated, and the center of the asteroid need only be the origin of $\bm r$. They do not need to be the center of mass, although it may be computationally easier. The centers do need to be close to their respective bodies in some sense, or else the assumptions about $D > r$ will be violated.

We will start by translating $S^*_{lm}(\bm R)$. Via an equation in the definition,
\begin{equation*}
\begin{aligned}
\bm \tau = &G\sum_{lm}\J_{lm} \int d^3 r\rho(\bm r)\bm r \times \nabla_{\bm R}\\
&\brackets{(-1)^l (-1)^m \sum_{l'=|m|}^\infty R_{l'm}^*(\bm r) \frac{(l+l')!}{D^{l+l'+1}}}.
\end{aligned}
\end{equation*}
Since $\nabla_{\bm R}=\nabla_{\bm r}$, the equation is separable into an integral which is computed locally:
\begin{equation*}
\begin{aligned}
\bm \tau = &(-1)^l (-1)^m G\sum_{lm}  \frac{\J_{lm}}{D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\\
& \int d^3 r\rho(\bm r)\bm r\times \nabla_{\bm r}R_{l'm}^*(\bm r).
\end{aligned}
\end{equation*}

Note for ease of unit analysis that the integral is unitless.

Now we will compute the gradient of the equation by one of the equations in the preamble:
\begin{equation*}
\begin{aligned}
\bm \tau = &(-1)^l (-1)^m G\sum_{lm}  \frac{\J_{lm}}{2D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\\
& \int d^3 r\rho(\bm r)[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)]
\end{aligned}
\end{equation*}
and we had better hope that this is real. To proove that it is real, we combine $m$ and $-m$ terms in the first sum, restricting ourselves to the off-diagonal ($m \neq 0$) terms. We will do the diagonal terms later.
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
& \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
&+ (-1)^{-m} \J_{l,-m}\\
&\int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'+m+1)R^*_{l',-m-1}(\bm r)\\
&+(-\x+i\y)(l'-m+1)R^*_{l',-m+1}(\bm r)-2im\z R^*_{l',-m}(\bm r)\Big]\Bigg\}
\end{aligned}
\end{equation*}
We make use of the relation that $(-1)^m R_{l,-m}=R^*_{lm}$ to get
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
& \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
&+ (-1)^{-m} \J_{l,-m}\\
&\int d^3 r\rho(\bm r)\Big[-(\x + i\y)(l'+m+1)R_{l',m+1}(\bm r)\\
&-(-\x+i\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
\end{aligned}
\end{equation*}

Now let us compute the relationship between $\J_{lm}$ and $\J_{-lm}$. From the definition of $\J_{lm}$,
$$\J_{l,-m} = \int_M d^3 r' \rho_M(\bm r')R_{l,-m}(\bm r')$$
$$\J_{l,-m} = (-1)^m\int_M d^3 r' \rho_M(\bm r')R^*_{l,m}(\bm r')$$
$$\J_{l,-m} = (-1)^m\J_{lm}^*$$
so it obeys the same relation. Thus,
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
&\Bigg\{\J_{lm} \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
&+ \J_{l,m}^* \int d^3 r\rho(\bm r)\Big[-(\x + i\y)(l'+m+1)R_{l',m+1}(\bm r)\\
&-(-\x+i\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
\end{aligned}
\end{equation*}
which is, in turn
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
&\Bigg\{\int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)\J_{lm} R^*_{l',m-1}(\bm r)\\
&+(-\x+i\y)(l'+m+1)\J_{lm} R^*_{l',m+1}(\bm r)+2im\z \J_{lm} R^*_{l'm}(\bm r) \\
&-(\x + i\y)(l'+m+1)\J_{l,m}^* R_{l',m+1}(\bm r)\\
&-(-\x+i\y)(l'-m+1)\J_{l,m}^* R_{l',m-1}(\bm r)-2im\z \J_{l,m}^* R_{l',m}(\bm r)\Big]\Bigg\}
\end{aligned}
\end{equation*}
and finally
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
&\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
&(l'-m+1)\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\\
&-(-\x+i\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
&+(l'+m+1)\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
&- (\x + i\y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
&+2im\z\Big[\J_{lm} R^*_{l'm}(\bm r)-\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
\end{aligned}
\end{equation*}
Just changing some signs for convenience,
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
&\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
&(l'-m+1)\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\\
&+(\x-i\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
&+(l'+m+1)\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
&+(-\x - i\y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
&+2im\z\Big[\J_{lm} R^*_{l'm}(\bm r)-\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
\end{aligned}
\end{equation*}

Since $2\Re z = z + z^*$ and $2\Im z = i(z^* - z)$, we may write
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
&\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
&(l'-m+1)\Re\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\Big]\\
&+(l'+m+1)\Re\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\Big]\\
&+2m\z\Im\Big[\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
\end{aligned}
\end{equation*}
Now we have proved that the off diagonal terms of torque are real. To make it even more agnostic of imaginary numbers, another way to put the above equation is that
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
&\x\bigg((l'-m+1)\Re\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
&-(l'+m+1)\Re\Big[\J^*_{lm} R_{l',m+1}(\bm r)\Big]\bigg)\\
&+\y\bigg((l'-m+1)\Im\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
&+(l'+m+1)\Im\Big[\J^*_{lm} R_{l',m+1}(\bm r)\Big]\bigg)\\
&+2m\z\Im\Big[\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
\end{aligned}
\end{equation*}

The on-diagonal ($m=0$) terms of torque are as follows:
\begin{equation*}
\begin{aligned}
\bm \tau_d = &(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{2D^{l+1}}\sum_{l'=0}^\infty \frac{(l+l')!}{D^{l'}}\\
& \int d^3 r\rho(\bm r)[(\x + i\y)(l'+1)R^*_{l',-1}(\bm r)\\
&+(-\x+i\y)(l'+1)R^*_{l',1}(\bm r)].
\end{aligned}
\end{equation*}
Already we see that the $l'=0$ term cannot come into play, so we skip it. Then, making use of the complex conjugate identity,
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{2D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
& \int d^3 r\rho(\bm r)[(\x + i\y)R_{l',1}(\bm r)+(\x-i\y)R^*_{l',1}(\bm r)].
\end{aligned}
\end{equation*}
The result is simple enough:
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
& \int d^3 r\rho(\bm r)\Re[(\x + i\y)R_{l',1}(\bm r)]
\end{aligned}
\end{equation*}
or
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-G\sum_{l=0}^\infty  \frac{(-1)^l \J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
& \int d^3 r\rho(\bm r)\parens{\x\Re [R_{l',1}(\bm r)] - \y\Im [R_{l',1}(\bm r)]}.
\end{aligned}
\end{equation*}
This is also manifestly real since $\J_{l0}$ is always real.

Suppose we have the following precomputed matrix:
$$\M_{lm} = \int d^3 r \rho(\bm r) R_{lm} \bm (r),$$
which is an identical definition to $\J$, except for the asteroid rather than for the planet. Then we have
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
&\x\bigg((l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&-(l'+m+1)\Re\Big[\J^*_{lm} \M_{l',m+1}\Big]\bigg)\\
&+\y\bigg((l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&+(l'+m+1)\Im\Big[\J^*_{lm} \M_{l',m+1}\Big]\bigg)\\
&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &G\sum_{l=0}^\infty  \frac{(-1)^l \J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
& \parens{-\x\Re [\M_{l',1}] + \y\Im [\M_{l',1}]}.
\end{aligned}
\end{equation*}
Finally,
$$\bm \tau = \bm\tau_d + \bm\tau_o.$$
Note that
$$\Re[\J_{l,-m}^* M_{l',-m-1}]=-\Re[\J_{lm} M^*_{l',m+1}]=-\Re[\J^*_{lm} M_{l',m+1}]$$
and
$$\Im[\J_{l,-m}^* M_{l',-m-1}]=-\Im[\J_{lm} M^*_{l',m+1}]=\Im[\J^*_{lm} M_{l',m+1}].$$
Therefore, we may write
\begin{equation*}
\begin{aligned}
\bm \tau_o = &G\sum_{l=1}^\infty \sum_{|m|\neq 0}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
&\x(l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&+\y(l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
\end{aligned}
\end{equation*}
Note that $\bm \tau_d$ is actually the $m=0$ case of this sum, Thus,
\begin{equation*}
\begin{aligned}
\bm \tau = &G\sum_{l=0}^\infty \sum_{m=-l}^l \frac{(-1)^l(-1)^{m}}{D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
&\x(l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&+\y(l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
\end{aligned}
\end{equation*}

\section{Rotation}
The constants $\M$ rotate over the course of the asteroid's orbit due to the asteroid's own rotation. Let the constants $\M$ be calculated at some time $t_0$ in the orbit, and define the rotation $\R(t)$ such for any vector $\bm r$ pointing to some point in the asteroid at time $t_0$, $\bm r' = \R(t) \bm r$ points to the same point at time $t$. Let $\M'$ be the constants calculated at time $t$. Then
$$\M'_{lm} = \int' d^3 r' \rho'(\bm r') R_{lm}(\bm r'),$$
$$\M'_{lm} = \int d^3 r \rho(\bm r) R_{lm}(\R(t)\bm r).$$
Now we use the following fact:
$$\overline{Y_{lm}} = \sum_{m'=-l}^l\parens{D^l_{mm'}(\R(t))}^*\overline{Y_{lm'}}(\bm r),$$
where $D^l_{mm'}$ are the components of the \href{https://en.wikipedia.org/wiki/Wigner_D-matrix#Relation_to_spherical_harmonics_and_Legendre_polynomials}{Wigner-$D$ matrix}, and $\overline{Y_{lm}}$ are the normalized spherical harmonics. For our purposes, this amounts to
$$Y_{lm}(\bm r') = \sum_{m'=-l}^l\sqrt{\frac{(l+m)!}{(l-m)!}\frac{(l-m')!}{(l+m')!}}\parens{D^l_{mm'}(\R(t))}^*Y_{lm'}(\bm r),$$
or
\begin{equation*}
\begin{aligned}
R_{lm}(\bm r') = &\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\\
&\parens{D^l_{mm'}(t)}^*R_{lm'}(\bm r)(-1)^{m+m'},
\end{aligned}
\end{equation*}
where we have written $D^l_{mm'}(t)=D^l_{mm'}(\R(t))$. Finally,
\begin{equation*}
\begin{aligned}
\M'_{lm} =& \int d^3 r \rho(\bm r) \\
&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\\
&\parens{D^l_{mm'}(t)}^*R_{lm'}(\bm r)(-1)^{m+m'}\\
=&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}(-1)^{m+m'}\\
&\parens{D^l_{mm'}(t)}^*\M_{lm'}.
\end{aligned}
\end{equation*}

The problem of computing the tidal torque on an asteroid over an orbit is then reduced to computing the constants $M_{lm}$ at some point in the orbit, then computing the components of $D^l_{mm'}$ at all other points in the orbit.

\section{Asteroid model that is friendly to tidal torque computation}
Assume

We want to design an asteroid model with adjustable density profile and shape, which is also easily able to calculate $\M_{lm}$. One such asteroid is as follows:
Define the density at point $\bm r$ to be
$$\rho(\bm r) = \sum_{l=0}^L \sum_{m=-l}^l \sum_{s=0}^\infty C_{lms}Y^*_{lm}(\hat{\bm r})r^s$$
with parameters $C_{lms} \in \mathbb{C}$. The constants $\M_{lm}$ are as follows:
\begin{equation*}
\begin{aligned}\M_{lm} = &\sum_{l'=0}^\infty \sum_{m'=-l'}^{l'} \sum_{s=0}^\infty\int d^3 r  C_{l'm's}Y^*_{l'm'}(\hat{\bm r})\\
&r^s (-1)^m \frac{r^l}{(l+m)!}Y_{lm}(\bm r).
\end{aligned}
\end{equation*}
\comment{Actually, this radial distribution is a terrible idea. It diverges for $s=0$ and isn't natural. Maybe just fit $\M_{lm}$?}
This can be broken into spherical coordinates and integrated, taking advantage of the fact that
$$\int d\Omega Y_{lm}Y^*_{l'm'}=\delta_{ll'}\delta_{mm'}\frac{4\pi}{2l+1}\frac{(l+m)!}{(l-m)!},$$
so
\begin{equation*}
\begin{aligned}\M_{lm} = &\sum_{l'=0}^\infty \sum_{m'=-l'}^{l'} \sum_{s=0}^\infty\int_0^R r^2 dr  C_{l'm's}\\
&r^s \frac{r^l}{(l-m)!}\delta_{ll'}\delta_{mm'}\frac{4\pi}{2l+1}(-1)^m.
\end{aligned}
\end{equation*}
This, in turn, becomes
$$\M_{lm} = \frac{4\pi (-1)^m}{(2l+1)(l-m)!}\sum_{s=0}^\infty C_{lms} \frac{R^{l+s+3}}{l+s+3}.$$
We want to require that the density be real, which we do by combining the $m$ and $-m$ terms:
$$\rho(\bm r) =  \sum_{s=0}^\infty r^s\sum_{l=0}^L C_{l0s}Y_{l0} + \sum_{m=1}^l \parens{C_{lms}Y_{lm} + C_{l,-m,s}Y_{l,-m}}$$

$$\rho(\bm r) =  \sum_{s=0}^\infty r^s\sum_{l=0}^L C_{l0s}Y_{l0} + \sum_{m=1}^l \parens{C_{lms}Y_{lm} + (-1)^m C_{l,-m,s}Y^*_{lm}},$$
and therefore if $C_{lms} = (-1)^m C_{l,-m,s}^*$, our density is real.

The reader may think it useful to use a different radial function instead of $r^s$, and indeed other functions might provide better fits. One choice that seems most preferable would be radial functions $B_{n}(r)$ that are orthonormal to $r^n$, so that each $\M_{lm}$ can be written with no sum. Unfortunately such functions do not exist. One can get close with
$$B_n(x)=\sum_{k=n}^K 2^k \binom{n}{k} \binom{\frac{n+k-1}{2}}{n}P_k(x)\frac{2n + 1}{2}$$
where $P_k(x)$ are the Legendre polynomials, and with $K \in \mathbb{N}$. Here, $\int_{-1}^1 B_n r^m dx = \delta_{nm}$ for all $n, m < K$, but this sum diverges for large $K$. An alternative, derived via Taylor series, is to define $B_n = \sum_k a_{kn}x^k$, where $a_{kn}$ are the components of the matrix $A=C^{-1}$, and the components of matrix $C$ are $c_{mk}=\frac{1}{m+k+1}$. This sum also diverges.

\section{Moment of inertia}
The moment of inertia matrix of an object is written as
$$I_{xx}=\int d^3 r \rho(\bm r) (y^2 + z^2), \indent \dots$$
$$I_{xy}=-\int d^3 r \rho(\bm r) xy, \indent \dots.$$
Note that
$$x^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)+2Y_{2,-2}+\frac{1}{12}Y_{22}}$$
$$y^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)-2Y_{2,-2}-\frac{1}{12}Y_{22}}$$
$$z^2=r^2\brackets{\frac{2}{3}Y_{20}+\frac{1}{3}}$$
$$xz=r^2\brackets{\frac{Y_{21}}{6}-Y_{2,-1}}$$
$$yz=r^2\brackets{\frac{Y_{21}}{6i}+\frac{Y_{2,-1}}{i}}$$
$$xy=r^2\brackets{\frac{Y_{22}}{12i}-2\frac{Y_{2,-2}}{i}}.$$
Then we can write the above in terms of $R_{2m}$:
$$I_{xx}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)+2R_{2,-2}+2R_{22}$$
$$I_{yy}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)-2R_{2,-2}-2R_{22}$$
$$I_{zz}=\int d^3r \rho(\bm r)\frac{4}{3}R_{20}+\frac{1}{3}$$
$$I_{xz}=-\int d^3r \rho(\bm r)R_{21}-R_{2,-1}$$
$$I_{yz}=-\int d^3r \rho(\bm r)\frac{R_{21}+R_{2,-1}}{i}$$
$$I_{xy}=-\int d^3r \rho(\bm r)2\frac{R_{22}-R_{2,-2}}{i}$$
and therefore
$$I_{xx}=-\frac{1}{3}(2\M_{20}-1)+2\M_{2,-2}+2\M_{22}$$
$$I_{yy}=-\frac{1}{3}(2\M_{20}-1)-2\M_{2,-2}-2\M_{22}$$
$$I_{zz}=\frac{4}{3}\M_{20}+\frac{1}{3}$$
$$I_{xz}=-\M_{21}+\M_{2,-1}$$
$$I_{yz}=-\frac{\M_{21}+\M_{2,-1}}{i}$$
$$I_{xy}=-2\frac{\M_{22}-\M_{2,-2}}{i}.$$

Thus, the moment of inertia is determined entirely by $\M_{lm}$ and therefore by $C_{lms}$. The equation of motion of the asteroid,
$$\dot{\bm \omega} = I^{-1}(\bm \tau - \bm\omega \times (I \bm\omega)),$$
is now entirely known as a function of orientation.

\section{Degeneracy}
We are interested in looking at the degeneracy of the $C_{lms}$ parameters with respect to their effect on the equation of motion. First of all, note that $l'=0$ gives no torque. The $\M_{00}$, or spherically symmetric term, will then never come into play. Also, if we take the origin of $\M$ to be the asteroid's center of mass, all of the first order moments $\M_{1,m}$ will vanish as well, meaning that the dynamics of the asteroid depend only on $C_{lms}$, $l\geq 2$. This incidentally requires that the torque term that is lowest order in $1/D$ is $(l,l',m)=(0,2,0)$, and is proportional to $1/D^3.$ It evaluates to
$$\tau \approx \frac{3G\J_{00}}{D^3}(\x I_{xz}-\y I_{yz}).$$
\comment{This indicates a mistake!}. Since $Y_{00}=1$, we know $\J_{00}$ is equal to the mass of the planet. So this agrees with the result achieved from a Taylor series expansion of tidal force, assuming a point mass for the Earth.

This relationship between first-order torque and the inertia tensor indicates that $\M_{lm}$ may be orthogonal in some sense; identifying one does not affect the rest. We may therefore hope to fit $C_{l'm's}$ independently of $C_{lms}$. We also expect $\J_{00}\gg \J_{lm}$, where $l\neq 0$, and we expect $D$ to be large. Consequentially, $C_{lms}$ will be damped by a factor of $\frac{l-2}{D}$ compared to the first order coefficients $C_{2ms}$, which determine $\M_{2m}$ and therefore the moment of inertia matrix. This is good news; it means that our $\M_{lm}$ parameterization is well-aligned with the system.

Unfortunately, the $s$ component of the $C_{lms}$ parameterization is not well-aligned. It is not obvious which terms will dominate, and as a result they may have a great deal of uncertainty, which could negatively affect the uncertainty of the entire fit. I think it's best to just fit $\M_{lm}$ instead.

\clearpage

\section{Matrix representation}
We can rearrange the sum, since
$$\sum_{l=1}^\infty \sum_{m=-l}^l\sum_{l'=|m|}^\infty = \sum_{l=1}^\infty \sum_{l'=0}^\infty \sum_{m=-\text{min}(l,l')}^{\text{min}(l,l')}.$$

Let us define $\tau = \x \Re\tau_{\parallel} + \y \Im \tau_{\parallel} + \hat z \Im\tau_\perp$. We wish to determine $\tau_\parallel$ and $\tau_\perp$ by matrix multiplication.

Suppose we define $\mathcal{P}_{l'm} = (-1)^{-m}(l' - m + 1) \M_{l',m-1}$ and
$\mathcal{L}_{l'm}=(-1)^{-m}m\M_{l'p}$. Then
$$\tau_\perp =G\sum \sum \sum \frac{(-1)^l}{D^{l+1}} \frac{(l+l')!}{D^{l'}}\J_{lm}^*\mathcal{P}_{l'm}$$
$$\tau_\parallel =G\sum \sum \sum \frac{(-1)^l}{D^{l+1}} \frac{(l+l')!}{D^{l'}}\J_{lm}^*\mathcal{L}_{l'm}.$$
We can write the above as a matrix multiplication by defining the infinite-dimensional matrix
$$\J_{ab} = \begin{cases}
    \J_{l=a,m=b-a} & b \leq 2a+1 \\
    0 & \text{else}
\end{cases}$$
and similarly for $\mathcal{P}$ and $\mathcal{L}$.

\bibliography{../asteroid-flybys.bib}
\end{document}

### 2021-07-07 summaries/22-07/22-07.tex
Correct math

@@
 Please see \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.56.5257&rep=rep1&type=pdf}{info on spherical harmonics}
-$$P_{lm}=\frac{1}{2l!}(1-t^2)^{m/2} \frac{d^{l+1}}{dl^{l+m}}(t^2-1)^l$$
+$$P_{lm}=\frac{1}{2^ll!}(1-t^2)^{m/2} \frac{d^{l+m}}{dl^{l+m}}(t^2-1)^l$$
 $$Y_{lm}(\theta, \phi) = P_{lm}(\cos\theta)e^{im\phi}$$
@@
 $$+(-\x+i\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}]$$
+\comment{This last one is wrong; the way I have it in writing is correct. But for some reason, the mistake cancels, and the final answer is correct anyway.}
 All of these functions obey the symmetry relations $F_{l,-m}=(-1)^mF_{lm}^*$

### 2021-07-08 summaries/21-07/21-07.tex
Checked formulas

--- 2021-07-07 summaries/22-07/22-07.tex
@@
- %\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib, floatfix]{revtex4}
 \documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib,floatfix]{revtex4-1}
@@
 Similarly, we have some gradient formulas that result in
-$$\bm r \times \nabla R_{lm}^*=\frac{1}{2}[(\x + i\y)(l-m+1)R^*_{l,m-1}$$
-$$+(-\x+i\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}]$$
+$$\bm r \times \nabla R_{lm}^*=-\frac{1}{2}[(i\x + \y)(l-m+1)R^*_{l,m-1}$$
+$$+(i\x-\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}]$$
 \comment{This last one is wrong; the way I have it in writing is correct. But for some reason, the mistake cancels, and the final answer is correct anyway.}
@@
 \begin{aligned}
-\bm \tau = &(-1)^l (-1)^m G\sum_{lm}  \frac{\J_{lm}}{2D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\\
-& \int d^3 r\rho(\bm r)[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
-&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)]
+\bm \tau = &-(-1)^l (-1)^m G\sum_{lm}  \frac{\J_{lm}}{2D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\\
+& \int d^3 r\rho(\bm r)[(i\x + \y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
+&+(i\x-\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)]
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
-& \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
-&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
+& \int d^3 r\rho(\bm r)\Big[(i\x + \y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
+&+(i\x-\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
 &+ (-1)^{-m} \J_{l,-m}\\
-&\int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'+m+1)R^*_{l',-m-1}(\bm r)\\
-&+(-\x+i\y)(l'-m+1)R^*_{l',-m+1}(\bm r)-2im\z R^*_{l',-m}(\bm r)\Big]\Bigg\}
+&\int d^3 r\rho(\bm r)\Big[(i\x + \y)(l'+m+1)R^*_{l',-m-1}(\bm r)\\
+&+(i\x-\y)(l'-m+1)R^*_{l',-m+1}(\bm r)-2im\z R^*_{l',-m}(\bm r)\Big]\Bigg\}
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
-& \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
-&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{(-1)^m \J_{lm}\\
+& \int d^3 r\rho(\bm r)\Big[(i\x + \y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
+&+(i\x-\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
 &+ (-1)^{-m} \J_{l,-m}\\
-&\int d^3 r\rho(\bm r)\Big[-(\x + i\y)(l'+m+1)R_{l',m+1}(\bm r)\\
-&-(-\x+i\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
+&\int d^3 r\rho(\bm r)\Big[-(i\x + \y)(l'+m+1)R_{l',m+1}(\bm r)\\
+&-(i\x-\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
-&\Bigg\{\J_{lm} \int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
-&+(-\x+i\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
-&+ \J_{l,m}^* \int d^3 r\rho(\bm r)\Big[-(\x + i\y)(l'+m+1)R_{l',m+1}(\bm r)\\
-&-(-\x+i\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
+&\Bigg\{\J_{lm} \int d^3 r\rho(\bm r)\Big[(i\x + \y)(l'-m+1)R^*_{l',m-1}(\bm r)\\
+&+(i\x-\y)(l'+m+1)R^*_{l',m+1}(\bm r)+2im\z R^*_{l'm}(\bm r)\Big] \\
+&+ \J_{l,m}^* \int d^3 r\rho(\bm r)\Big[-(i\x + \y)(l'+m+1)R_{l',m+1}(\bm r)\\
+&-(i\x-\y)(l'-m+1)R_{l',m-1}(\bm r)-2im\z R_{l',m}(\bm r)\Big]\Bigg\}
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
-&\Bigg\{\int d^3 r\rho(\bm r)\Big[(\x + i\y)(l'-m+1)\J_{lm} R^*_{l',m-1}(\bm r)\\
-&+(-\x+i\y)(l'+m+1)\J_{lm} R^*_{l',m+1}(\bm r)+2im\z \J_{lm} R^*_{l'm}(\bm r) \\
-&-(\x + i\y)(l'+m+1)\J_{l,m}^* R_{l',m+1}(\bm r)\\
-&-(-\x+i\y)(l'-m+1)\J_{l,m}^* R_{l',m-1}(\bm r)-2im\z \J_{l,m}^* R_{l',m}(\bm r)\Big]\Bigg\}
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
+&\Bigg\{\int d^3 r\rho(\bm r)\Big[(i\x + \y)(l'-m+1)\J_{lm} R^*_{l',m-1}(\bm r)\\
+&+(i\x-\y)(l'+m+1)\J_{lm} R^*_{l',m+1}(\bm r)+2im\z \J_{lm} R^*_{l'm}(\bm r) \\
+&-(i\x + \y)(l'+m+1)\J_{l,m}^* R_{l',m+1}(\bm r)\\
+&-(i\x-\y)(l'-m+1)\J_{l,m}^* R_{l',m-1}(\bm r)-2im\z \J_{l,m}^* R_{l',m}(\bm r)\Big]\Bigg\}
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
 &\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
-&(l'-m+1)\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\\
-&-(-\x+i\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
-&+(l'+m+1)\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
-&- (\x + i\y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
+&(l'-m+1)\Big[(i\x + \y)\J_{lm} R^*_{l',m-1}(\bm r)\\
+&-(i\x-\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
+&+(l'+m+1)\Big[(i\x-\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
+&- (i\x + \y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
 &+2im\z\Big[\J_{lm} R^*_{l'm}(\bm r)-\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{2D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
 &\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
-&(l'-m+1)\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\\
-&+(\x-i\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
-&+(l'+m+1)\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
-&+(-\x - i\y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
+&(l'-m+1)\Big[(i\x + \y)\J_{lm} R^*_{l',m-1}(\bm r)\\
+&+(-i\x+\y)\J_{l,m}^* R_{l',m-1}(\bm r)\Big]\\
+&+(l'+m+1)\Big[(i\x-\y)\J_{lm} R^*_{l',m+1}(\bm r)\\
+&+(-i\x - \y)\J_{l,m}^* R_{l',m+1}(\bm r)\Big]\\
 &+2im\z\Big[\J_{lm} R^*_{l'm}(\bm r)-\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
@@
 \begin{aligned}
-\bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
+\bm \tau_o = &-G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\\
 &\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
-&(l'-m+1)\Re\Big[(\x + i\y)\J_{lm} R^*_{l',m-1}(\bm r)\Big]\\
-&+(l'+m+1)\Re\Big[(-\x+i\y)\J_{lm} R^*_{l',m+1}(\bm r)\Big]\\
+&(l'-m+1)\Re\Big[(i\x+\y)\J_{lm} R^*_{l',m-1}(\bm r)\Big]\\
+&+(l'+m+1)\Re\Big[(i\x-\y)\J_{lm} R^*_{l',m+1}(\bm r)\Big]\\
 &+2m\z\Im\Big[\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
@@
 \bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\int d^3 r\rho(\bm r)\Big[\\
-&\x\bigg((l'-m+1)\Re\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
+&\y\bigg((l'-m+1)\Re\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
 &-(l'+m+1)\Re\Big[\J^*_{lm} R_{l',m+1}(\bm r)\Big]\bigg)\\
-&+\y\bigg((l'-m+1)\Im\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
-&+(l'+m+1)\Im\Big[\J^*_{lm} R_{l',m+1}(\bm r)\Big]\bigg)\\
+&-\x\bigg((l'-m+1)\Im\Big[\J^*_{lm} R_{l',m-1}(\bm r)\Big]\\
+&-(l'+m+1)\Im\Big[\J^*_{lm} R_{l',m+1}(\bm r)\Big]\bigg)\\
 &+2m\z\Im\Big[\J_{l,m}^* R_{l',m}(\bm r)\Big]\Big]\Bigg\}.
@@
 \begin{aligned}
-\bm \tau_d = &(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{2D^{l+1}}\sum_{l'=0}^\infty \frac{(l+l')!}{D^{l'}}\\
-& \int d^3 r\rho(\bm r)[(\x + i\y)(l'+1)R^*_{l',-1}(\bm r)\\
-&+(-\x+i\y)(l'+1)R^*_{l',1}(\bm r)].
+\bm \tau_d = &-(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{2D^{l+1}}\sum_{l'=0}^\infty \frac{(l+l')!}{D^{l'}}\\
+& \int d^3 r\rho(\bm r)[(i\x + \y)(l'+1)R^*_{l',-1}(\bm r)\\
+&+(i\x-\y)(l'+1)R^*_{l',1}(\bm r)].
 \end{aligned}
@@
 \bm \tau_d = &-(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{2D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
-& \int d^3 r\rho(\bm r)[(\x + i\y)R_{l',1}(\bm r)+(\x-i\y)R^*_{l',1}(\bm r)].
+& \int d^3 r\rho(\bm r)[(-i\x - \y)R_{l',1}(\bm r)+(i\x-\y)R^*_{l',1}(\bm r)].
 \end{aligned}
@@
 \begin{aligned}
-\bm \tau_d = &-(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
-& \int d^3 r\rho(\bm r)\Re[(\x + i\y)R_{l',1}(\bm r)]
+\bm \tau_d = &(-1)^l G\sum_{l=0}^\infty  \frac{\J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
+& \int d^3 r\rho(\bm r)\Re[(i\x + \y)R_{l',1}(\bm r)]
 \end{aligned}
@@
 \bm \tau_d = &-G\sum_{l=0}^\infty  \frac{(-1)^l \J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
-& \int d^3 r\rho(\bm r)\parens{\x\Re [R_{l',1}(\bm r)] - \y\Im [R_{l',1}(\bm r)]}.
+& \int d^3 r\rho(\bm r)\parens{\y\Re [R_{l',1}(\bm r)] - \x\Im [R_{l',1}(\bm r)]}.
 \end{aligned}
@@
 \bm \tau_o = &G\sum_{l=1}^\infty \sum_{m=1}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=m}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
-&\x\bigg((l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
-&-(l'+m+1)\Re\Big[\J^*_{lm} \M_{l',m+1}\Big]\bigg)\\
-&+\y\bigg((l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
+&\x\bigg((l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
 &+(l'+m+1)\Im\Big[\J^*_{lm} \M_{l',m+1}\Big]\bigg)\\
-&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}
+&+\y\bigg(-(l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
+&+(l'+m+1)\Re\Big[\J^*_{lm} \M_{l',m+1}\Big]\bigg)\\
+&-2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}
 \end{aligned}
@@
 \bm \tau_d = &G\sum_{l=0}^\infty  \frac{(-1)^l \J_{l0}}{D^{l+1}}\sum_{l'=1}^\infty \frac{(l+l')!(l'+1)}{D^{l'}}\\
-& \parens{-\x\Re [\M_{l',1}] + \y\Im [\M_{l',1}]}.
+& \parens{\x\Im [\M_{l',1}] - \y\Re [\M_{l',1}]}.
 \end{aligned}
@@
 \bm \tau_o = &G\sum_{l=1}^\infty \sum_{|m|\neq 0}^l \frac{(-1)^l(-1)^{-m}}{D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
-&\x(l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
-&+\y(l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
-&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
+&\x(l'+m+1)\Im\Big[\J_{lm}^* \M_{l',m+1}\Big]\\
+&+\y(l'+m+1)\Re\Big[\J_{lm}^* \M_{l',m+1}\Big]\\
+&-m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
 \end{aligned}
 \end{equation*}
-Note that $\bm \tau_d$ is actually the $m=0$ case of this sum, Thus,
+Note that $\bm \tau_d$ is actually the $m=0$ case of this sum, \comment{Nope} Thus,
 \begin{equation*}
@@
 \bm \tau = &G\sum_{l=0}^\infty \sum_{m=-l}^l \frac{(-1)^l(-1)^{m}}{D^{l+1}}\sum_{l'=|m|}^\infty \frac{(l+l')!}{D^{l'}}\Bigg\{\\
-&\x(l'-m+1)\Re\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
-&+\y(l'-m+1)\Im\Big[\J^*_{lm} \M_{l',m-1}\Big]\\
-&+2m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
+&\x(l'+m+1)\Im\Big[\J^*_{lm} \M_{l',m+1}\Big]\\
+&-\y(l'+m+1)\Re\Big[\J^*_{lm} \M_{l',m+1}\Big]\\
+&-m\z\Im\Big[\J_{l,m}^* \M_{l',m}\Big]\Bigg\}.
 \end{aligned}
@@
 \section{Rotation}
-The constants $\M$ rotate over the course of the asteroid's orbit due to the asteroid's own rotation.
-Let the constants $\M$ be calculated at some time $t_0$ in the orbit, and define the rotation $\R(t)$ such for any vector $\bm r$ pointing to some point in the asteroid at time $t_0$, $\bm r' = \R(t) \bm r$ points to the same point at time $t$.
-Let $\M'$ be the constants calculated at time $t$.
+The constants $\M_{lm}$ rotate over the course of the asteroid's orbit due to the asteroid's own rotation.
+Let the constants $\M_{lm}$ be calculated at some time $t_0$ in the orbit, and define the rotation $\R(t)$ such for any vector $\bm r$ pointing to some point in the asteroid at time $t_0$, $\R(t) \bm r$ points to the same point at time $t$.
+Let $\M'_{lm}$ be the constants calculated at time $t$.
 Then
-$$\M'_{lm} = \int' d^3 r' \rho'(\bm r') R_{lm}(\bm r'),$$
-$$\M'_{lm} = \int d^3 r \rho(\bm r) R_{lm}(\R(t)\bm r).$$
+$$\M'_{lm} = \int d^3 r \rho'(\bm r) R_{lm}(\bm r),$$
+$$\M'_{lm} = \int d^3 r \rho(\R(t)^{-1}\bm r) R_{lm}(\bm r),$$
+$$\M'_{lm} = \int' d^3 r \rho(\bm r) R_{lm}(\R(t) \bm r)$$
+where the prime over the last integral indicates that the bounds have been rotated by $\R(t)$.
+However, we can take the region of integration as spherical; specifically, we integrate over a ball which encloses the entire asteroid and set $\rho(\bm r)=0$ for every piece of volume we have added.
+Introducing this change does not change the value of any of these integrals, but it allows us to ignore the prime over the last integral.
+
 Now we use the following fact:
@@
 R_{lm}(\bm r') = &\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\\
-&\parens{D^l_{mm'}(t)}^*R_{lm'}(\bm r)(-1)^{m+m'},
+&\parens{D^l_{mm'}(t)}^*R_{lm'}(\bm r),
 \end{aligned}
@@
 &\parens{D^l_{mm'}(t)}^*R_{lm'}(\bm r)(-1)^{m+m'}\\
-=&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}(-1)^{m+m'}\\
+=&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\\
 &\parens{D^l_{mm'}(t)}^*\M_{lm'}.

### 2021-07-22 summaries/new-math/new-math.tex
I just realized a fundamental flaw in my math. I have to go back and fix a bunch of stuff. Redeveloping the math in summaries/new-math.

\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib,floatfix]{revtex4-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx}      % tools for importing graphics
%\usepackage{lgrind}        % convert program code listings to a form
                            % includable in a LaTeX document
%\usepackage{xcolor}        % produces boxes or entire pages with
                            % colored backgrounds
%\usepackage{longtable}     % helps with long table options
%\usepackage{epsf}          % old package handles encapsulated postscript issues
\usepackage{bm}            % special bold-math package. usge: \bm{mathsymbol}
\usepackage{subcaption}
%\usepackage{asymptote}     % For typesetting of mathematical illustrations
%\usepackage{thumbpdf}
\usepackage[colorlinks=true]{hyperref}  % this package should be added after
                                        % all others.
                                        % usage: \url{http://web.mit.edu/8.13}
\usepackage{wasysym}

\begin{document}
\title{New math derivation}
\author{Jack Dinsmore, Julien de Wit}
\email{jtdinsmo@mit.edu}
\date{\today}
\affiliation{MIT Department of Physics}

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\comment}[1]{\textcolor{red}{\emph{ #1 }}}
\newcommand{\x}{\bm{\hat x}}
\newcommand{\y}{\bm{\hat y}}
\newcommand{\z}{\bm{\hat z}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\R}{\mathcal{R}}

\begin{abstract}
    The purpose of this summary is to derive the math governing the way an asteroid reacts to a non-point source. It was motivated by the discovery that, under the assumption of a gravitating point source and a small asteroid, the tidal torque can be written in terms of components of the moment of inertia, which means inference is limited to the six components of the inertia matrix. By violating these assumptions and considering other effects (oblateness, etc.), we can break the degeneracy.
\end{abstract}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Definitions}
Please see \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.56.5257&rep=rep1&type=pdf}{info on spherical harmonics}
$$P_{lm}=\frac{1}{2^ll!}(1-t^2)^{m/2} \frac{d^{l+m}}{dl^{l+m}}(t^2-1)^l$$
$$Y_{lm}(\theta, \phi) = P_{lm}(\cos\theta)e^{im\phi}$$
$$\bar Y_{lm}(\theta, \phi) = (-1)^m \sqrt{\frac{2l+1}{4\pi}\frac{(l-m)!}{(l+m)!}} Y_{lm}(\theta, \phi)$$
$$R_{lm}(\bm r) = (-1)^m \frac{r^l}{(l+m)!}Y_{lm}(\bm r)$$
$$S_{lm}(\bm r) = (-1)^m \frac{(l-m)!}{r^{l+1}}Y_{lm}(\bm r)$$
We write $Y(\bm r)=Y(\hat{\bm r})$.

These definitions lead to several key facts. For $r' < r$,
\begin{equation}
\frac{1}{|\bm r - \bm r'|}=\sum_{lm}R_{lm}(\bm r')S^*_{lm}(\bm r).
\label{eqn:expansion}
\end{equation}
We also have a translation rule:
\begin{equation}
S_{lm}(\bm r' - \bm r)=(-1)^l\sum_{l'm'}R^*_{l'm'}(\bm r')S_{l+l',m+m'}(\bm r)
\label{eqn:trans}.
\end{equation}
Similarly, we have some gradient formulas that result in
\begin{equation}
\begin{aligned}
\bm r \times \nabla R_{lm}^*=&-\frac{1}{2}[(i\x + \y)(l-m+1)R^*_{l,m-1}\\
&+(i\x-\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}].
\end{aligned}
\label{eqn:grad}
\end{equation}
Finally, we have the symmetry relations $R_{l,-m}=(-1)^mR_{lm}^*$, $S_{l,-m}=(-1)^mS_{lm}^*$.

\section{Linear law of motion}
We use Newton's law of gravity for the linear law of motion:
\begin{equation}
\ddot{\bm D} = \hat {\bm D} \frac{\mu}{D^2}
\label{eqn:linear-eom}
\end{equation}
where $\bm D$ points from the asteroid to the planet, and $\mu$ is the reduced mass of the system. We assume that the asteroid mass is so much smaller than the planet's mass that the difference between $\mu$ and the mass of the planet cannot be detected. The initial conditions for $\bm D$ should have large magnitude of $D$ and $\dot D$ greater than the escape velocity of the system.

\section{Angular law of motion}
Recall that angular momentum satisfies $ \dot{\bm L} = \bm \tau = \frac{d}{dt}(I \bm \omega)$,
where $I$ is the moment of inertia matrix. This equation is not easily simplified in general, but in a coordinate system fixed to the rotating body, we make use of the fact that $\dot I = 0$. Also,
$$\dot{\bm L} = \dot{\bm L}_\text{rot} + L_x \dot{\x} + L_y \dot{\y} + L_z \dot{\z},$$
where $\dot{\bm L}_\text{rot} = \dot L_x \x + \dot L_y \y + \dot L_z \z$. By considering $\bm\omega \parallel \z$, we see that
$$L_x \dot{\x} + L_y \dot{\y} + L_z \dot{\z} = \bm\omega \times \bm L,$$
and since this pattern is replicated for all axes, it must be generally true. Furthermore, $\dot{\bm L}_\text{rot} = \dot I_\text{rot} \bm \omega + I \dot{\bm \omega}_\text{rot}$, and since $\dot I_\text{rot} = 0$, we have
$$\bm \tau = I \dot{\bm \omega} + \bm\omega \times \bm L.$$
Here we have removed the rot subscript on $\dot{\bm \omega}$ because $\dot{\bm \omega} = \dot{\bm \omega}_\text{rot} + \omega \times \omega =  \dot{\bm \omega}_\text{rot}.$ Reversing to solve for $\dot{\bm \omega}$, we have
\begin{equation}
\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times (I \bm \omega)}.
\label{eqn:euler}
\end{equation}
Once again, this is valid only in a frame fixed to the body. The torque $\bm \tau$ will be calculated in the next section.

The initial conditions are that $\omega$ is initially parallel to the eigenvector of $I$ with the largest eigenvalue, to minimize energy. The norm and direction of $\omega$ is observed.

It will turn out that our equation for $\tau$ will invoke the use of $\bm D$ in the rotating frame. To track $\bm D$ in that frame, we need $\dot{\bm D}_\text{rot}$. To find it,
$$\dot{\bm D} = \dot{\bm D}_\text{rot} + \bm \omega \times \bm D$$
or
\begin{equation}
\dot{\bm D}_\text{rot} = \bm D \times \bm \omega + \hat{\bm D}.
\label{eqn:d-eom}
\end{equation}
where $\dot D$ is given by the evolution of equation \ref{eqn:linear-eom}

\section{Torque}
By definition, the differential torque on a small unit of mass $dm$ within an asteroid is $d\bm \tau = \bm r \times d\bm F$, where $\bm r$ points to $dm$ from the center of mass of the asteroid. In the regime where $d\bm F$ is constant, there is no tidal torque. But if $d\bm F$ is allowed to vary across the asteroid, we will get tidal torque as shown.

The differential force is $d\bm F = -dm \nabla_{\bm R} V(\bm R)$, where
$$V(\bm R) = -\int d^3 r' \frac{\rho_M(\bm r')}{|\bm r' - \bm R|}$$
is the gravitational potential field of the planet, and $\bm R = \bm r - \bm D$ points from $dm$ to the center of mass of the planet. Also, we have $\rho_M$ as the mass distribution of the planet. Expanding this potential field using equation \ref{eqn:expansion}, we get
$$V(\bm R) = -\sum_{lm}S^*_{lm}(\bm R)\int d^3 r' \rho_M(\bm r') R_{lm}(\bm r').$$
We introduce the useful symbol
\begin{equation}
\J_{lm} = \int d^3 r \rho_M(\bm r) R_{lm} (\bm r)
\label{eqn:jlm-def}
\end{equation}
and we have
\begin{equation}
V(\bm R) = -\sum_{lm} S^*_{lm} (\bm R) \J_{lm}.
\label{eqn:potential}
\end{equation}
Incidentally, since $R_{00} = 1$, we have that $\J_{00}$ is the total mass of the asteroid and $\mu = G \J_{00}$, which can be used to simplify equation \ref{eqn:linear-eom}.

The total torque on the asteroid can therefore be written as
\begin{equation}
\bm \tau = \int d^3 r \rho(\bm r) \bm r \times \nabla_{\bm R} \sum_{lm} S^*_{lm}(\bm R) \J_{lm}.
\label{eqn:first-torque}
\end{equation}
Here, $\rho(\bm r)$ is now the mass density of the asteroid. Since $\nabla_{\bm R} = \nabla_{\bm r}$, we will drop the subscript henceforth.

Note that the bounds of integration of equations \ref{eqn:jlm-def} and \ref{eqn:first-torque} can be chosen to be the surfaces of the bodies in question, or any surface encompassing the bodies. It will be useful in the future to imagine these bounds as spherically symmetrical.

We expand equation \ref{eqn:first-torque} using equation \ref{eqn:trans}:
\begin{equation*}
\begin{aligned}
\bm \tau = &\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
&\int d^3 r \rho(\bm r) \bm r \times \nabla R^*_{l'm'}(\bm r).
\end{aligned}
\end{equation*}
Now we can move straight on to substitution equation \ref{eqn:grad}:
\begin{equation*}
\begin{aligned}
\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)].
\end{aligned}
\end{equation*}
This equation had better be real. To prove it, let us combine the $\pm m'$ terms, leaving out the $m'=0$ term and using the subscript o (off-diagonal) to indicate its absence:
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'_+}\Bigg\{S_{l+l',m+m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
&S_{l+l',m-m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'+m'+1)R^*_{l',-m'-1}(\bm r)\\
&+(i\x-\y)(l'-m'+1)R^*_{l',-m'+1}(\bm r)-2im'\z R^*_{l',-m'}(\bm r)]\Bigg\}.
\end{aligned}
\end{equation*}
Using the symmetry rules for complex conjugates,
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'_+}\Bigg\{S_{l+l',m+m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
&S_{l+l',m-m'}(\bm D) \\
&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg\}.
\end{aligned}
\end{equation*}
Now we expand for $\pm m$ too:
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}(-1)^l \Bigg\{\J_{lm}\sum_{l'm'_+} \Bigg[S_{l+l',m+m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
&+S_{l+l',m-m'}(\bm D) \\
&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg]\\
&+ \J_{l,-m}\sum_{l'm'_+} \Bigg[S_{l+l',-m+m'}(\bm D) \\
&+\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
&+S_{l+l',-m-m'}(\bm D) \\
&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg]\Bigg\}.
\end{aligned}
\end{equation*}
Let us introduce a new notation:
\begin{equation}
\K_{lm} = \int d^3 r \rho(\bm r) R_{lm} (\bm r)
\label{eqn:klm-def}
\end{equation}
which are the expansion coefficients of the potential of the asteroid. Then the above becomes
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}(-1)^l \Bigg\{\J_{lm}\sum_{l'm'_+} \Bigg[S_{l+l',m+m'}(\bm D) \\
&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
&+S_{l+l',m-m'}(\bm D) \\
&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
&+ (-1)^m (-1)^{m+m'}\J_{l,m}^*\sum_{l'm'_+} \Bigg[S^*_{l+l',m-m'}(\bm D) \\
&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
&+S^*_{l+l',m+m'}(\bm D) \\
&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\Bigg\}.
\end{aligned}
\end{equation*}
which can be simplified as
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l \Bigg\{\J_{lm} \Bigg[S_{l+l',m+m'}(\bm D) \\
&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
&+S_{l+l',m-m'}(\bm D) \\
&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
&+\J_{lm}^*\Bigg[S^*_{l+l',m+m'}(\bm D) \\
&\bigg[-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)\\
&-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
&+(-1)^{m'}S^*_{l+l',m-m'}(\bm D) \\
&\bigg[(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}(\bm r)\\
&+(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\Bigg\}
\end{aligned}
\end{equation*}
or
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&(l'-m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}\\
&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'-1}(i\x-\y)\\
&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\bigg)\\
&+(l'+m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}\\
&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'+1}(i\x + \y)\\
&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\bigg)\\
&+2im'\z\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}\\
&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l'm'}\\
&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)\K^*_{l'm'}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}
This can be written as follows
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&(l'-m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\\
&+\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'-1}(-i\x+\y)\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}\\
&-(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(-i\x - \y)\K^*_{l',m'-1}\bigg)\\
&+(l'+m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\\
&+\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'+1}(-i\x - \y)\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}\\
&-(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(-i\x+\y)\K^*_{l',m'+1}\bigg)\\
&+2im'\z\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}\\
&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l'm'}\\
&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}\\
&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)\K^*_{l'm'}\bigg)\Bigg\},
\end{aligned}
\end{equation*}
or
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&+(l'-m'+1)\bigg(\Re\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)(-i\x+\y)\K^*_{l',m'-1}}\\
&-(-1)^{m'}\Re\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}}\bigg)\\
&+(l'+m'+1)\bigg(\Re\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}}\\
&-(-1)^{m'}\Re\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}}\bigg)\\
&-2m'\z\bigg(\Im\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}}\\
&-(-1)^{m'}\Im\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}
Define
$$\J_{lml'm'}^\pm = \J_{lm} S_{l+l',m\pm m'}(\bm D)(\pm 1)^{m'+1}.$$
Then
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&+(l'-m'+1)\bigg(\Re\brackets{\J_{lml'm'}^+(-i\x+\y)\K^*_{l',m'-1}}\\
&+\Re\brackets{\J_{lml'm'}^-(i\x-\y)\K_{l',m'-1}}\bigg)\\
&+(l'+m'+1)\bigg(\Re\brackets{\J_{lml'm'}^+(i\x-\y)\K^*_{l',m'+1}}\\
&+\Re\brackets{\J_{lml'm'}^-(i\x + \y)\K_{l',m'+1}}\bigg)\\
&-2m'\z\bigg(\Im\brackets{\J_{lml'm'}^+\K^*_{l'm'}}+\Im\brackets{\J_{lml'm'}^-\K_{l'm'}}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}
Further defining
\begin{equation}
\begin{aligned}
\chi_{lml'm'}^{\pm,s}& = \J_{lml'm'}^\pm \K^*_{l',m'+s}\\
&= (\pm 1)^{m'+1}S_{l+l',m\pm m'}(\bm D)\J_{lm} \K^*_{l',m'+s},
\end{aligned}
\label{eqn:chi}
\end{equation}
we get
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&+(l'-m'+1)\bigg(\Re\brackets{\chi_{lml'm'}^{+-}(i\x+\y)}\\
&+\Re\brackets{\chi_{lml'm'}^{--}(i\x-\y)}\bigg)\\
&+(l'+m'+1)\bigg(\Re\brackets{\chi_{lml'm'}^{++}(i\x-\y)}\\
&+\Re\brackets{\chi_{lml'm'}^{-+}(i\x + \y)}\bigg)\\
&-2m'\z\bigg(\Im\brackets{\chi_{lml'm'}^{+0}}+\Im\brackets{\chi_{lml'm'}^{-0}}\bigg)\Bigg\}
\end{aligned}
\end{equation*}
\comment{(Here I realized I made a mistake earlier; I took the complex conjugate of the top line and forgot to conjugate the vector term, so I do it here)}, or
\begin{equation*}
\begin{aligned}
\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&+(l'-m'+1)\bigg(\Re\chi_{lml'm'}^{+-}\y - \Im\chi_{lml'm'}^{+-}\x\\
&-\Re\chi_{lml'm'}^{--}\y - \Im\chi_{lml'm'}^{--}\x \bigg)\\
&+(l'+m'+1)\bigg(-\Re\chi_{lml'm'}^{++}\y - \Im\chi_{lml'm'}^{++}\x\\
&+\Re\chi_{lml'm'}^{-+}\y - \Im\chi_{lml'm'}^{-+}\x\bigg)\\
&-2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}
We can write this as
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&+(l'-m'+1)\bigg(\Im\chi_{lml'm'}^{+-}\x - \Re\chi_{lml'm'}^{+-}\y\\
&+\Re\chi_{lml'm'}^{--}\y + \Im\chi_{lml'm'}^{--}\x \bigg)\\
&+(l'+m'+1)\bigg(\Re\chi_{lml'm'}^{++}\y + \Im\chi_{lml'm'}^{++}\x\\
&\Im\chi_{lml'm'}^{-+}\x - \Re\chi_{lml'm'}^{-+}\y\bigg)\\
&+2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\},
\end{aligned}
\end{equation*}
or, joining vectors,
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&\x \bigg((l'-m'+1)\Im\chi_{lml'm'}^{+-} + (l'-m'+1)\Im\chi_{lml'm'}^{--}\\
&+(l'+m'+1)\Im\chi_{lml'm'}^{++} + (l'+m'+1)\Im\chi_{lml'm'}^{-+}\bigg)\\
&+\y \bigg(-(l'-m'+1)\Re\chi_{lml'm'}^{+-} + (l'-m'+1)\Re\chi_{lml'm'}^{--}\\
&+(l'+m'+1)\Re\chi_{lml'm'}^{++} - (l'+m'+1)\Re\chi_{lml'm'}^{-+}\bigg)\\
&+2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}
Finally,
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++}+ (l'-m'+1)\chi_{lml'm'}^{--}\\
&+ (l'-m'+1)\chi_{lml'm'}^{+-} + (l'+m'+1)\chi_{lml'm'}^{-+}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--} \\
&- (l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{-+}\bigg)\\
&+2m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
\end{aligned}
\end{equation*}

Note that
\begin{equation}
\begin{aligned}
\chi_{l,-m,l',m'}^{\pm,s} = &(\pm 1)^{m'+1}S_{l+l',-m\pm m'}(\bm D)\J_{l,-m} \K^*_{l',m'+s}\\
=&(-1)^s(\pm 1)^{m'+1}S^*_{l+l',m\mp m'}(\bm D)\J^*_{lm} \K_{l',-m'-s}\\
=&(-1)^s{\chi_{l,m,l',-m'}^{\pm,-s}}^*.
\end{aligned}
\label{eqn:chi}
\end{equation}
and
\begin{equation}
\begin{aligned}
\chi_{l,-m,l',-m'}^{\pm,s} = &(\pm 1)^{-m'+1}S_{l+l',-m\mp m'}(\bm D)\J_{l,-m} \K^*_{l',-m'+s}\\
=&(-1)^s(\pm 1)^{m'+1}S^*_{l+l',m\pm m'}(\bm D)\J^*_{lm} \K_{l',m'-s}\\
=&(-1)^s{\chi_{lml'm'}^{\pm,-s}}^*
\end{aligned}
\label{eqn:chi}
\end{equation}
so
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\\
&+ (l'-m'+1)\chi_{l,-m,l',-m'}^{++} + (l'+m'+1)\chi_{l,-m,l',-m'}^{--}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--} \\
&+ (l'-m'+1)\chi_{l,-m,l',-m'}^{++} + (l'+m'+1)\chi_{l,-m,l',-m'}^{--}\bigg)\\
&+2m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}\\
&+\sum_{lm_-}\sum_{l'm'_-}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\parens{\sum_{lm_+}\sum_{l'm'_+}+\sum_{lm_-}\sum_{l'm'_-}}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
\end{aligned}
\end{equation*}

\clearpage

Then consider
\begin{equation*}
\begin{aligned}
&\sum_{l,m\neq0}\sum_{l',m'\neq 0'}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
=&\sum_{l,m_+}\sum_{l',m'\neq 0'}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
&\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
=&\sum_{l,m_+}\sum_{l',m'_+}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
&+\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
&+\x \Im\bigg((l'-m'+1)\chi_{l,m,l',-m'}^{++} - (l'+m'+1)\chi_{l,m,l',-m'}^{+-}\bigg)\\
&+\x \Im\bigg((l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{++}\bigg)
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
=&\sum_{l,m_+}\sum_{l',m'_+}(-1)^l\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
&+\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
&+\x \Im\bigg((l'-m'+1)\chi_{l,m,l',-m'}^{++} - (l'+m'+1)\chi_{l,m,l',-m'}^{+-}\bigg)\\
&+\x \Im\bigg((l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{++}\bigg)
\end{aligned}
\end{equation*}

Now we want to compute the on-diagonal component of torque, which is where $m'=0$, and $m\in \mathbb{Z}.$ That's
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'}(l'+1)S_{l+l',m}(\bm D) \\
&[(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}].
\end{aligned}
\end{equation*}
Now we combine $\pm m$,
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{lm_+}(-1)^l\Bigg\{\J_{lm}\sum_{l'}(l'+1)S_{l+l',m}(\bm D) \\
&[(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}]\\
& + \J_{l,-m}\sum_{l'}(l'+1)S_{l+l',-m}(\bm D) \\
& [(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}]\Big\}\\
& - \frac{1}{2}\sum_{l}(-1)^l \J_{l0} \sum_{l'}(l'+1)S_{l+l',0}(\bm D)\\
& [(i\x + \y)\K^*_{l',-1} + (i\x - \y \K^*_{l',1})].
\end{aligned}
\end{equation*}
Note that
$$\chi_{lml'0}^{\pm,s} = \pm S_{l+l',m}(\bm D)\J_{lm} \K^*_{l',s},$$
so
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{ \\
&[(-i\x - \y)\chi_{lml'0}^{--}+(i\x-\y)\chi_{lml'0}^{++}]\\
& + [(-i\x - \y){\chi_{lml'0}^{++}}^*+(i\x-\y){\chi_{lml'0}^{--}}^*]\Big\}\\
& - \frac{1}{2}\sum_{l}(-1)^l \sum_{l'}(l'+1)\\
& [(-i\x - \y)\chi_{l0l'0}^{--} + (i\x - \y)\chi_{l0l'0}^{++}].
\end{aligned}
\end{equation*}
Since $\chi_{l0l'0}^{--}={\chi_{l0l'0}^{++}}^*$, this simplifies as follows:
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Big( \\
&\Re[(-i\x - \y)\chi_{lml'0}^{--}]+\Re[(i\x-\y)\chi_{lml'0}^{++}]\Big)\\
& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \Re[(i\x - \y)\chi_{l0l'0}^{++}]
\end{aligned}
\end{equation*}
or
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
&\parens{-\y\Re\chi_{lml'0}^{--} + \x\Im\chi_{lml'0}^{--}}\\
&+\parens{-\y\Re\chi_{lml'0}^{++}-\x\Im\chi_{lml'0}^{++}}\Bigg\}\\
& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}]}
\end{aligned}
\end{equation*}
which is
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
&\x\Im\parens{\chi_{lml'0}^{--}-\chi_{lml'0}^{++}} -\y\Re\parens{\chi_{lml'0}^{++}+\chi_{lml'0}^{--}} \Bigg\}\\
& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}}.
\end{aligned}
\end{equation*}
We can also write this as
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
&\x\Im\parens{\chi_{lml'0}^{--}+\chi_{lml'0}^{-+}} - \y\Re\parens{\chi_{lml'0}^{++} - \chi_{lml'0}^{+-}} \Bigg\}\\
& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}}
\end{aligned}
\end{equation*}
which is
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
&\x\Im\parens{\chi_{lml'0}^{--}+\chi_{l,-m,l',0}^{--}} - \y\Re\parens{\chi_{lml'0}^{++} + \chi_{l,-m,l',0}^{++}} \Bigg\}\\
& + \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{\y\Re\chi_{l0l'0}^{++} + \x\Im\chi_{l0l'0}^{++}}
\end{aligned}
\end{equation*}
or
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm}(-1)^l\sum_{l'}(l'+1)\Bigg\{\x\Im\chi_{lml'0}^{--} - \y\Re\chi_{lml'0}^{++}\Bigg\}.
\end{aligned}
\end{equation*}
Note that the sum now extends over all $m$.

I forgot to add the case where $m=0$, $m'\neq 0$. So add this part:
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'\neq 0}S_{l+l',m'}(\bm D) \\
&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
&\bigg[(i\x + \y)(l'-m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'-1}\\
&+(i\x-\y)(l'+m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'+1}\\
&+2im'\z S_{l+l',m'}(\bm D)\K^*_{l'm'}\bigg]\\
&+\bigg[(i\x + \y)(l'+m'+1)S_{l+l',-m'}(\bm D)\K^*_{l',-m'-1}\\
&+(i\x-\y)(l'-m'+1)S_{l+l',-m'}(\bm D)\K^*_{l',-m'+1}\\
&-2im'\z S_{l+l',-m'}(\bm D)\K^*_{l'-m'}\bigg]\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
&\bigg[(i\x + \y)(l'-m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'-1}\\
&+(i\x-\y)(l'+m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'+1}\\
&+2im'\z S_{l+l',m'}(\bm D)\K^*_{l'm'}\bigg]\\
&+\bigg[-(i\x + \y)(l'+m'+1)S^*_{l+l',m'}(\bm D)\K_{l',m'+1}\\
&-(i\x-\y)(l'-m'+1)S^*_{l+l',m'}(\bm D)\K_{l',m'-1}\\
&-2im'\z S^*_{l+l',m'}(\bm D)\K_{l'm'}\bigg]\Bigg\}
\end{aligned}
\end{equation*}

\begin{equation}
\begin{aligned}
\chi_{l0l'm'}^{\pm,s}&= (\pm 1)^{m'+1}S_{l+l',\pm m'}(\bm D)\J_{l0} \K^*_{l',m'+s},\\
\end{aligned}
\label{eqn:chi}
\end{equation}

\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
&\bigg[(i\x + \y)(l'-m'+1)\chi_{l0l'm'}^{+-}\\
&+(i\x-\y)(l'+m'+1)\chi_{l0l'm'}^{++} +2im'\z \chi_{l0l'm'}^{+0}\bigg]\\
&+\bigg[(-i\x - \y)(l'+m'+1){\chi_{l0l'm'}^{++}}^*\\
&+(-i\x+\y)(l'-m'+1){\chi_{l0l'm'}^{+-}}^* -2im'\z {\chi_{l0l'm'}^{+0}}^*\bigg]\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
&\Re[(i\x + \y)(l'-m'+1)\chi_{l0l'm'}^{+-}]\\
&+\Re[(i\x-\y)(l'+m'+1)\chi_{l0l'm'}^{++}]\\
&-2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
&\y\Re\chi_{l0l'm'}^{+-}(l'-m'+1) - \x\Im\chi_{l0l'm'}^{+-}(l'-m'+1)\\
&-\y\Re\chi_{l0l'm'}^{++}(l'+m'+1) - \x\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
&-2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
&\x\Im\parens{\chi_{l0l'm'}^{+-}(l'-m'+1) +\chi_{l0l'm'}^{++}(l'+m'+1)}\\
&+\y\Re\parens{\chi_{l0l'm'}^{++}(l'+m'+1)-\chi_{l0l'm'}^{+-}(l'-m'+1)}\\
&+2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
&\x\Im\parens{\chi_{l,0,l',-m'}^{++}(l'-m'+1) +\chi_{l0l'm'}^{++}(l'+m'+1)}\\
&+\y\Re\parens{\chi_{l0l'm'}^{++}(l'+m'+1)+\chi_{l,0,l',-m'}^{++}(l'-m'+1)}\\
&+m'\z \Im\chi_{l0l'm'}^{+0}-m'\z \Im\chi_{l,0,l',-m'}^{+0}\bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_d = &\sum_{l}(-1)^l\sum_{l',m'\neq 0}\bigg\{ \\
&\x\Im\chi_{l0l'm'}^{++}(l'+m'+1)+\y\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
&+m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
\end{aligned}
\end{equation*}
So in all,
\begin{equation*}
\begin{aligned}
\bm \tau_d = &-\sum_{lm}(-1)^l\sum_{l'}(l'+1)\Bigg\{\x\Im\chi_{lml'0}^{--} - \y\Re\chi_{lml'0}^{++}\Bigg\}+\\
 &\sum_{l}(-1)^l\sum_{l',m'\neq 0}\bigg\{ \\
&\x\Im\chi_{l0l'm'}^{++}(l'+m'+1)+\y\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
&+m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}.
\end{aligned}
\end{equation*}
When the limits are extended to $m_-,m'_- \cup m\geq 0, m' \geq 0$, the off diagonal formula reduces to
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{l'}\sum_{l,m\geq0}(-1)^l(l'+1)\Bigg\{\\
&\x \Im\bigg(\chi_{lml'0}^{++} + \chi_{lml'0}^{--}\bigg)+\y \Re\bigg(\chi_{lml'0}^{++} + \chi_{lml'0}^{--}\bigg)\Bigg\}\\
&+\sum_{l}(-1)^l\sum_{l',m'>0}\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'-m'+1)\chi_{l0l'm'}^{--}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'-m'+1)\chi_{l0l'm'}^{--}\bigg)\\
&+m'\z\Im\bigg(\chi_{l0l'm'}^{+0}+\chi_{l0l'm'}^{-0}\bigg)\Bigg\}
\end{aligned}
\end{equation*}
\begin{equation*}
\begin{aligned}
\bm \tau_o = &\sum_{l'}\sum_{l,m\geq0}(-1)^l(l'+1)\Bigg\{\\
&\x \Im\bigg(-\chi_{l,-m,l',0}^{--} + \chi_{lml'0}^{--}\bigg)+\y \Re\bigg(\chi_{lml'0}^{++} + \chi_{l,-m,l',0}^{++}\bigg)\Bigg\}\\
&+\sum_{l}(-1)^l\sum_{l',m'>0}\Bigg\{\\
&\x \Im\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'+m'+1)\chi_{l,0,l',-m'}^{-+}\bigg)\\
&+\y \Re\bigg((l'+m'+1)\chi_{l0l'm'}^{++} - (l'+m'+1)\chi_{l,0,l',-m'}^{-+}\bigg)\\
&+m'\z\Im\bigg(\chi_{l0l'm'}^{+0}+\chi_{l0l'm'}^{-0}\bigg)\Bigg\}
\end{aligned}
\end{equation*}
So it doesn't really work out. I'll have to do this later.

\clearpage

\bibliography{../asteroid-flybys.bib}
\end{document}

### 2021-07-22 summaries/new-math/new-math.tex
More math

@@
 \end{equation*}
+By defining the new varialble
+\begin{equation}
+\K_{lm} = \int d^3 r \rho(\bm r) R_{lm} (\bm r),
+\label{eqn:klm-def}
+\end{equation}
+we can simplify this to
+\begin{equation*}
+\begin{aligned}
+\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
+&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
+&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
+\label{eqn:complex-torque}
+\end{aligned}
+\end{equation*}
+
+\section{Proof of real-ness}
 This equation had better be real. To prove it, let us combine the $\pm m'$ terms, leaving out the $m'=0$ term and using the subscript o (off-diagonal) to indicate its absence:
@@
 \end{equation*}
-So it doesn't really work out. I'll have to do this later.
+\comment{So it doesn't really work out. I'll have to do this later.}
 
@@
 
+\section{Moment of inertia}
+The moment of inertia matrix of an object is written as
+$$I_{xx}=\int d^3 r \rho(\bm r) (y^2 + z^2), \indent \dots$$
+$$I_{xy}=-\int d^3 r \rho(\bm r) xy, \indent \dots.$$
+Note that
+$$x^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)+2Y_{2,-2}+\frac{1}{12}Y_{22}}$$
+$$y^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)-2Y_{2,-2}-\frac{1}{12}Y_{22}}$$
+$$z^2=r^2\brackets{\frac{2}{3}Y_{20}+\frac{1}{3}}$$
+$$xz=r^2\brackets{\frac{Y_{21}}{6}-Y_{2,-1}}$$
+$$yz=r^2\brackets{\frac{Y_{21}}{6i}+\frac{Y_{2,-1}}{i}}$$
+$$xy=r^2\brackets{\frac{Y_{22}}{12i}-2\frac{Y_{2,-2}}{i}}.$$
+Then we can write the above in terms of $R_{2m}$:
+$$I_{xx}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)+2R_{2,-2}+2R_{22}$$
+$$I_{yy}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)-2R_{2,-2}-2R_{22}$$
+$$I_{zz}=\int d^3r \rho(\bm r)\frac{4}{3}R_{20}+\frac{1}{3}$$
+$$I_{xz}=-\int d^3r \rho(\bm r)R_{21}-R_{2,-1}$$
+$$I_{yz}=-\int d^3r \rho(\bm r)\frac{R_{21}+R_{2,-1}}{i}$$
+$$I_{xy}=-\int d^3r \rho(\bm r)2\frac{R_{22}-R_{2,-2}}{i}$$
+and therefore
+$$I_{xx}=\frac{2}{3}\K_{20}-2\K_{2,-2}-2\K_{22}+\frac{2}{5}\K_{00}$$
+$$I_{yy}=\frac{2}{3}\K_{20}+2\K_{2,-2}+2\K_{22}+\frac{2}{5}\K_{00}$$
+$$I_{zz}=-\frac{4}{3}\K_{20} + \frac{2}{5}\K_{00}$$
+$$I_{xz}=\K_{21}-\K_{2,-1}$$
+$$I_{yz}=\frac{\K_{21}+\K_{2,-1}}{i}$$
+$$I_{xy}=-2\frac{\K_{22}-\K_{2,-2}}{i}.$$
+
+Thus, the moment of inertia is determined entirely by $\K_{lm}$ and therefore by $C_{lms}$.
+The reader will notice that the moment of inertia depends counter-intuitively on the asteroid mass $\K_{00}$.
+However, we may write the moment of inertia as $I_\perp+\mathbb{I}\frac{2}{5}\K_{00}$, where $\mathbb{I}$ is the identity matrix, and $I_\perp$ depends only on $K_{2m}$.
+Then equation $$\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times \parens{I_\perp+\mathbb{I}\frac{2}{5}\K_{00}} \bm \omega}$$
+$$\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times I_\perp\bm \omega}$$
+because the identity matrix does not change the direction of a vector multiplied by it.
+However, due to the first term, the mass of the asteroid must indeed be known to integrate the equation of motion.
+
+\section{Computing torque}
+Since the proof that our torque in equation \ref{eqn:complex-torque} is real is generally difficult and does not seem very enlightening, we will move on for now.
+
+Note that the $S$ present in equation \ref{eqn:complex-torque} forces $l$ and $l'$ to be low in the dominant terms.
+However, $l'=0$ contributes nothing to torque, nor does $l'=1$ due to the fact that $\K_{1m}=0$, which is caused by $\K_{lm}$ being centered on the center of mass of the asteroid.
+Therefore, $l'=2$ is the minimum value, and the dominant torque term is proportional to $D^{-3}$.
+
+Note that $\K_{lm}$ are constants, since we are using coordinates fixed to the body.
+Our derivation requires that we use the same coordinates for $\J_{lm}$, which are therefore not constant.
+We can find their values at any point in the orbit using the \href{https://en.wikipedia.org/wiki/Wigner_D-matrix#Relation_to_spherical_harmonics_and_Legendre_polynomials}{Wigner-$D$ matrices}, which rotate spherical harmonics according to
+$$Y_{lm}(\bm r') = \sum_{m'=-l}^l\sqrt{\frac{(l+m)!}{(l-m)!}\frac{(l-m')!}{(l+m')!}}\parens{D^l_{mm'}(\R}^*Y_{lm'}(\bm r),$$
+where $\R$ indicates a rotation, and $\bm r' = \R \bm r$. Generally, $\R$ is represented by Euler angles.
+
+Let $\R$ rotate from the body-fixed axes to some inertial coordinate system. Then we must rotate both the $S$ in equation \ref{eqn:complex-torque} and the $\J_{lm}$, the latter of which rotate by
+\begin{equation*}
+\begin{aligned}
+\J^\text{rot}_{lm} =&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\parens{D^l_{mm'}(t)}^*\J_{lm'}.
+\end{aligned}
+\end{equation*}
+We also have
+$$S_{lm}(\bm r') = \sum_{m'=-l}^l \sqrt{\frac{(l+m)!}{(l-m')!} \frac{(l-m)!}{(l+m')!}} \parens{D^l_{mm'}(\R}^*S_{lm'}(\bm r)$$
+Thus, equation \ref{eqn:complex-torque} becomes
+\begin{equation*}
+\begin{aligned}
+\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\\
+&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
+&\bigg[\sum_{m''=-l-l'}^{l+l'} \sqrt{\frac{(l+l'+m+m')!}{(l+l'-m'')!}\frac{(l+l'-m-m')!}{(l+l'+m'')!}}\\
+&\parens{D^{l+l'}_{m+m',m''}(\R)}^*S_{l+l',m''}(\bm D^0)\bigg]\\
+&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
+&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
+\end{aligned}
+\end{equation*}
+where $\J_{lm}^0$ and $\bm D^0$ are the values of $\J_{lm}$ and $\bm D$ with respect to the inertial reference frame.
+There is some subtlety with $\bm D^0$; the length changes over the course of the orbit, so $\bm D^0$ must have length equal to the length of $\bm D$ at the moment of calculation, but its direction is constant.
+
+ We have some freedom in our choice of inertial coordinate system, so let us choose $\z$ to point towards the planet; $\bm D^0 \propto \z$. Then
+$$S_{l+l',m+m'}(\bm D^0) = (-1)^{m} \frac{(l-m)!}{D^{1+l}} P_{lm}(1)e^{im\phi}.$$
+The requirement that $\phi \in \mathbb{R}$ all give the same answer means $m=0$ is necessary, and since $P_{l0}(1)=1$,
+$$S_{l+l',m+m'}(\bm D^0) = \frac{l!}{D^{1+l}}\delta_{m0}.$$
+Thus,
+\begin{equation*}
+\begin{aligned}
+\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\\
+&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
+&\bigg[\sqrt{\frac{(l+l'+m+m')!}{(l+l')!}\frac{(l+l'-m-m')!}{(l+l')!}}\\
+&\parens{D^{l+l'}_{m+m',0}(\R)}^*\frac{(l+l')!}{D^{1+l+l'}}\bigg]\\
+&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
+&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].\\
+= &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\frac{\sqrt{(l+l'+m+m')!(l+l'-m-m')!}}{D^{1+l+l'}}\\
+&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
+&\parens{D^{l+l'}_{m+m',0}(\R)}^*\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
+&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
+\end{aligned}
+\end{equation*}
+We have a little more freedom in our inertial coordinate system; we have not specified which direction $\bm D^0$ points to.
+We may do this by demanding that $\bm D^0=\hat z$ at the beginning of the simulation; in other words, the body-fixed and inertial coordinates coincide there.
+We have then determined $\R(t)$, which has initial condition $\R(t)=\mathbb{I}]$ and evolves according to $\dot \R = \omega$ in some sense.
+
+However, we have still not fully specified the problem, because the body-fixed coordinate system has not been identified.
+We will allow the end user to specify this coordinate system evaluating $\J_{lm}$ with respect to these axes.
+Therefore, the choice of $\J_{lm}$ determines the body-fixed coordinate system which controls $\K_{lm}$, and the angular and linear equations of motion (eqs.~\ref{eqn:linear-eom} and \ref{eqn:euler}) combined with initial conditions $\bm D(0)=D\z$ and $\bm v$ set to its observed value, and angular initial conditions of $\R(0)=\mathbb{I}$ and $\omega$ set to a known value or an estimate.
+
+\section{Evolution of Euler Angles}
+The Wigner-$D$ matrices are commonly expressed in terms of the Euler angles, so we will use these to track the evolution of the body.
+Let us use $z-y-z$ Euler angles, or $\bm E = (\alpha, \beta, \gamma)$, with
+\begin{equation}
+\R = R_z(\alpha) R_y(\beta) R_z(\gamma)
+\label{eqn:euler-angle-rotation}
+\end{equation}
+where $R_z$ and $R_y$ represent right-handed rotations around the $\z$ and $\y$ axes respectively.
+These angles control the orientation of the asteroid, so we need an equation of motion to describe them.
+
+By definition of angular velocity, we know $\frac{d}{dt}(\R \bm v) = \bm \omega \times \bm v,$ where $\bm v$ is any constant vector, and therefore $\dot \R \bm v = \bm \omega \times \bm v,$.
+Let $\omega_{\times}$ be the skew-symmetric matrix for $\omega$, such that $\omega_{\times} \bm v = \bm\omega \times \bm v$.
+Then $\dot \R \bm v = \omega_\times \bm v$.
+Since this is true for all $\bm v$, we see that $\dot \R = \omega_\times$, or
+$$\frac{d}{dt}\parens{R_z(\alpha)R_y(\beta)R_z(\gamma)} = \parens{\begin{matrix}
+0 & -\omega_z & \omega_y \\
+\omega_z & 0 & -\omega_x \\
+-\omega_y & \omega_x & 0
+ \end{matrix}}.$$
+ This is
+ $$\dot \alpha \dot R_z(\alpha)R_y(\beta)R_z(\gamma) + \dot \beta R_z(\alpha)\dot R_y(\beta)R_z(\gamma) + \dot \gamma R_z(\alpha)R_y(\beta)\dot R_z(\gamma) = \parens{\begin{matrix}
+ 0 & -\omega_z & \omega_y \\
+ \omega_z & 0 & -\omega_x \\
+ -\omega_y & \omega_x & 0
+  \end{matrix}}.$$
+
 \bibliography{../asteroid-flybys.bib}

### 2021-07-23 summaries/new-math/new-math.tex
New rotation model

@@
 
-Let $\R$ rotate from the body-fixed axes to some inertial coordinate system. Then we must rotate both the $S$ in equation \ref{eqn:complex-torque} and the $\J_{lm}$, the latter of which rotate by
+Let $\R$ rotate from the body-fixed axes to some inertial coordinate system.
+We choose this coordinate system so that the orbit of the asteroid lies in the $xz$-plane, but the exact orientation of the axes is left to the reader.
+The constants $\J_{lm}$ are then fixed in this frame at $\J_{lm}^0$.
+Then we must rotate both the $\J_{lm}$ in equation \ref{eqn:complex-torque} according to
 \begin{equation*}
@@
 \end{equation*}
-We also have
-$$S_{lm}(\bm r') = \sum_{m'=-l}^l \sqrt{\frac{(l+m)!}{(l-m')!} \frac{(l-m)!}{(l+m')!}} \parens{D^l_{mm'}(\R}^*S_{lm'}(\bm r)$$
 Thus, equation \ref{eqn:complex-torque} becomes
@@
 \begin{aligned}
-\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\\
+\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}S_{l+l',m+m'}(\bm D)\\
 &\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
-&\bigg[\sum_{m''=-l-l'}^{l+l'} \sqrt{\frac{(l+l'+m+m')!}{(l+l'-m'')!}\frac{(l+l'-m-m')!}{(l+l'+m'')!}}\\
-&\parens{D^{l+l'}_{m+m',m''}(\R)}^*S_{l+l',m''}(\bm D^0)\bigg]\\
 &\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
 &+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
+\label{eqn:torque-final}
 \end{aligned}
 \end{equation*}
-where $\J_{lm}^0$ and $\bm D^0$ are the values of $\J_{lm}$ and $\bm D$ with respect to the inertial reference frame.
-There is some subtlety with $\bm D^0$; the length changes over the course of the orbit, so $\bm D^0$ must have length equal to the length of $\bm D$ at the moment of calculation, but its direction is constant.
+The only value left unfixed is the body-fixed coordinate system.
+We fix it to the principal axes of the asteroid, so that $\z$ aligns with the axis with maximal inertia.
+Then $\bm\omega = \omega \z$ initially in the body-fixed system.
+Now everything is determined; the choice of $\J_{lm}$ determines position and velocity $\bm D$ and $\bm v$ which evolve via the linear equation of motion, equation \ref{eqn:linear-eom}.
+The body's initial orientation--unknown when the spin axis has not been resolved and known up to a roll parameter when the spin axis is resolved---fixes the initial orientation, represented by $\R$.
+The orientation and angular velocity $\omega$ then evolve according to equation \ref{eqn:euler}, which references the torque displayed in equation \ref{eqn:torque-final}.
 
- We have some freedom in our choice of inertial coordinate system, so let us choose $\z$ to point towards the planet; $\bm D^0 \propto \z$. Then
-$$S_{l+l',m+m'}(\bm D^0) = (-1)^{m} \frac{(l-m)!}{D^{1+l}} P_{lm}(1)e^{im\phi}.$$
-The requirement that $\phi \in \mathbb{R}$ all give the same answer means $m=0$ is necessary, and since $P_{l0}(1)=1$,
-$$S_{l+l',m+m'}(\bm D^0) = \frac{l!}{D^{1+l}}\delta_{m0}.$$
-Thus,
-\begin{equation*}
+In practice, we represent the orientation as a quaternion $\bm q$ and evolve it according to the quaternion equation of motion
+$$\dot {\bm q} = \frac{1}{2}\bm \omega \bm q$$
+and we extract Euler angles from it to get $\R$, and a matrix from it to convert $\bm D$. from the inertial axes to the body-fixed system.
+
+A benefit to requiring that the body-fixed system be aligned with principal axes is that, in this regime, equation \ref{eqn:euler} simplifies to
+\begin{equation}
 \begin{aligned}
-\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\\
-&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
-&\bigg[\sqrt{\frac{(l+l'+m+m')!}{(l+l')!}\frac{(l+l'-m-m')!}{(l+l')!}}\\
-&\parens{D^{l+l'}_{m+m',0}(\R)}^*\frac{(l+l')!}{D^{1+l+l'}}\bigg]\\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].\\
-= &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}\frac{\sqrt{(l+l'+m+m')!(l+l'-m-m')!}}{D^{1+l+l'}}\\
-&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
-&\parens{D^{l+l'}_{m+m',0}(\R)}^*\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
+\dot \omega_x = I_x^{-1}\parens{\tau_x + (I_y - I_z)\omega_y \omega_z}\\
+\dot \omega_y = I_y^{-1}\parens{\tau_y + (I_z - I_x)\omega_z \omega_x}\\
+\dot \omega_z = I_z^{-1}\parens{\tau_z + (I_x - I_y)\omega_x \omega_y}\\
 \end{aligned}
-\end{equation*}
-We have a little more freedom in our inertial coordinate system; we have not specified which direction $\bm D^0$ points to.
-We may do this by demanding that $\bm D^0=\hat z$ at the beginning of the simulation; in other words, the body-fixed and inertial coordinates coincide there.
-We have then determined $\R(t)$, which has initial condition $\R(t)=\mathbb{I}]$ and evolves according to $\dot \R = \omega$ in some sense.
-
-However, we have still not fully specified the problem, because the body-fixed coordinate system has not been identified.
-We will allow the end user to specify this coordinate system evaluating $\J_{lm}$ with respect to these axes.
-Therefore, the choice of $\J_{lm}$ determines the body-fixed coordinate system which controls $\K_{lm}$, and the angular and linear equations of motion (eqs.~\ref{eqn:linear-eom} and \ref{eqn:euler}) combined with initial conditions $\bm D(0)=D\z$ and $\bm v$ set to its observed value, and angular initial conditions of $\R(0)=\mathbb{I}$ and $\omega$ set to a known value or an estimate.
+\end{equation}
+and the inertial matrix is diagonal, meaning that
+$$\K_{21} = \K_{2,-1}=\Im K_{22} = \Im K_{2,-2}= 0.$$
+The only free parameters with $l\leq 2$ are $\K_{00}$, $\K_{20}$, and $\Re \K_{22}$, which is three total.
 
@@
   \end{matrix}}.$$
+  This looks hard, so instead, I suggest using the old Quaternion strategy.
 

### 2021-07-23 code/sim/triangle.cpp

@@ -1,217 +1,0 @@
-#include "triangle.hpp"
-
-double real_spherical_harmonic(uint l, int m, double theta, double phi) {
-    if (m < 0) {
-        return sqrt(2) * pow(-1, m) *
-        boost::math::spherical_harmonic(l, -m, theta, phi).imag();
-    }
-    if (m == 0) {
-        return boost::math::spherical_harmonic(l, 0, theta, phi).real();
-    }
-    else {
-        return sqrt(2) * pow(-1, m) *
-        boost::math::spherical_harmonic(l, m, theta, phi).real();
-    }
-}
-
-Triangle::Triangle(Chunk& parent, Vector3 v1, Vector3 v2, Vector3 v3) :
-    v(v1), l1(v2-v1), l2(v3-v1), norm(Vector3::cross(l1, l2)), parent(parent) {}
-std::array<Vector3, 3> Triangle::get_corners() const {
-    return {v, v + l1, v + l2};
-}
-void Triangle::operator*=(Matrix3 const& m) {
-    v = m * v;
-    l1 = m * l1;
-    l2 = m * l2;
-    norm = m * norm;// Assume this is a rotation matrix
-}
-double Triangle::get_density() const{
-    return parent.density;
-}
-bool Triangle::is_edge() const {
-    return abs(parent.ab - 1.0) < EPSILON;
-}
-
-double Triangle::get_mass() const {
-    return 1/18.0 * parent.density * Vector3::dot(norm, l1 + l2 + 3 * v);
-}
-Vector3 Triangle::get_lever_arm() const {
-    return 1/24.0 * parent.density * norm * (
-        l1.mag2() + l2.mag2() + 6 * v.mag2() + Vector3::dot(l1, l2) +
-        4 * Vector3::dot(l1 + l2, v)
-    );
-}
-double Triangle::get_Isame(int a) const {
-    Vector3 b, c;
-    switch(a){
-    case 0:
-        b = Vector3::y() * get_Isame_component(l1[1], l2[1], v[1]);
-        c = Vector3::z() * get_Isame_component(l1[2], l2[2], v[2]);
-        break;
-    case 1:
-        b = Vector3::x() * get_Isame_component(l1[0], l2[0], v[0]);
-        c = Vector3::z() * get_Isame_component(l1[2], l2[2], v[2]);
-        break;
-    case 2:
[…]

### 2021-07-23 code/sim/triangle.hpp

@@ -1,77 +1,0 @@
-#pragma once
-
-#include <vector>
-#include <boost/math/special_functions/spherical_harmonic.hpp>
-
-#include "algebra.hpp"
-
-class Chunk;
-
-class ThetaPhi {
-public:
-    ThetaPhi() {}
-    ThetaPhi(Vector3 cart) {
-        theta = acos(cart[2] / cart.mag());
-        phi = atan2(cart[1], cart[0]);
-    }
-
-    Vector3 to_vector(double r) const {
-        return r * Vector3({ sin(theta) * cos(phi),
-                             sin(theta) * sin(phi),
-                             cos(theta) });
-    }
-    double theta;
-    double phi;
-};
-
-class Triangle {
-public:
-    Triangle(Chunk& parent, Vector3 v1, Vector3 v2, Vector3 v3);
-
-    void recenter(Vector3 const& l) {
-        v += l;
-    }
-
-    void operator*=(Matrix3 const& m);
-
-    Vector3 get_lever_arm() const; // Used for com
-    double get_mass() const; // Used for com
-    Vector3 get_torque() const; // Used tor torque
-    double get_Isame(int a) const; // Used for MOI
-    double get_Idiff(int a, int b) const; // Used for MOI
-    std::array<Vector3, 3> get_corners() const;
-    double get_density() const;
-    bool is_edge() const;
-    bool is_nan() const;
-
-private:
-    double get_Isame_component(double l1b, double l2b, double vb) const;
-    double get_Idiff_component(double l1a, double l1b,
-        double l2a, double l2b, double va, double vb) const;
-    double get_torque_component(Vector3 const& l1_, Vector3 const& l2_) const;
-
-    Vector3 v;
-    Vector3 l1;
-    Vector3 l2;
-    Vector3 norm;
-    Vector3 premul;
-    Chunk& parent;
-};
-
-class Chunk {
-    friend class Triangle;
-public:
-    Chunk(double alpha_above, double alpha_below,
-        int n_here, int face, int a, int b);
-
-    void shape(double density_, uint L, std::vector<double> const& clms,
-    std::vector<Triangle>& tris);
-
-protected:
-    double density;
-    double ab;// alpha_above
-
-private:
-    ThetaPhi ul, ur, ll, lr;
-    double be;// alpha_below
-};

### 2021-07-29 summaries/new-math/new-math.tex
Updated math for shape model

@@
 
+\section{Shape model}
+When asteroid density is allowed to vary, there is not a direct connection between asteroid shape and $\K_{lm}$, because $\K_{lm}$ has two dimensions whereas shape parameters should have three: one for $\theta$, one for $\phi$, and one for $r$.
+This argument is far from rigorous and probably incorrect, but it poses a difficult problem to overcome.
+
+We could establish shape coordinates $C_{lmn}$ and allow $\K_{lm}$ to define a combination of $C_{lmn}$.
+This is made difficult, however, since there is no basis of functions orthogonal to $r^n$ for all $n \in \mathbb{N}$ over $\mathbb{R}$.
+The basis exists for $n < N$ for some $N$, and can be written in terms of the Legendre polynomials.
+But as $N\rightarrow\infty$, the basis functions get very squigally and they diverge in the limit.
+So, the combination would be more complicated than some kind of orthonormal basis.
+
+\subsection{Unfitted density}
+Suppose we don't want to deal with density distribution, as a start. Then there is a good shape model available to us. Let
+\begin{equation}
+    \rho(\bm r) = \sum_{lm} Y_{lm}^* \rho_{lm} \begin{cases}
+        1 & r < \R_{lm}\\
+        0 & \text{else}
+    \end{cases}.
+\end{equation}
+with $\rho_{lm} \in \mathbb{C}$, $\R_{lm} \in \mathbb{R}$. Then equation \ref{eqn:klm-def} becomes
+\begin{equation*}
+    \K_{lm} = \int r^2 dr \int d\Omega \sum_{l'm'} Y_{l'm'}^* R_{lm}(\bm r) \begin{cases}
+        \rho_{lm} & r < \R_{lm}\\
+        0 & \text{else}
+    \end{cases}.
+\end{equation*}
+Recall that $R_{lm}(\bm r) \propto Y_{lm}(\bm r)$, and
+$$\int d\Omega Y_{lm}Y^*_{l'm'} = \delta_{ll'}\delta_{mm'} \frac{4\pi (l+m)!}{(2l+1)(l-m)!}$$
+so
+\begin{equation*}
+    \K_{lm} = \frac{4\pi (-1)^m }{(2l+1)(l-m)!} \int r^{2+l} dr \begin{cases}
+        \rho_{lm} & r < \R_{lm}\\
+        0 & \text{else}
+    \end{cases}.
+\end{equation*}
+This in turn is
+\begin{equation*}
+    \K_{lm} = \parens{\frac{4\pi (-1)^m \rho_{lm}}{(2l+1)(l-m)!}} \parens{\frac{\R_{lm}^{3+l}}{3+l}}
+\end{equation*}
+Thus, there are three parameters $\rho_{lm}$ and $\R_{lm}$ to match with two parameters $\K_{lm}$ (counting complex numbers as two parameters), and the problem is nearly determined.
+Setting $\rho_{lm}$ independentently will cause it to be entirely determined.
+
+It is not at all clear that this setup will give us a good asteroid model, however.
+If all $\rho_{lm}$ were positive in some sense (they are complex after all), then the center would be denser than the edges.
+It would be better to have some holistic model without these sharp edges, but those will not integrate as well.
+
+\comment{I thought about a way of subdividing the sphere. Do that?}
+
 \bibliography{../asteroid-flybys.bib}

### 2021-09-02 summaries/21-06/21-06.tex
Summaries added back

--- 2021-06-14 summaries/22-06/22-06.tex
@@
 \section{Introduction}
+\subsection{Coordinate frames}
+We will make use of three coordinate frames in this project.
+First is the ``local frame,'' which rotates with the asteroid.
+We will describe the shape of the asteroid only in the local frame, where it is constant.
+Next is the ``global frame,'' in which $\hat {\bm z}$ points towards the Earth at all times, $\hat {\bm y}$ points forward in the plane of the orbit, and $\hat {\bm x}$ points perpendicular to the plane of the orbit.
+
+It is important to note that neither of the above two frames are inertial, so we will define a third frame, which is the ``inertial frame.'' We will not discuss the inertial frame much, except as a comparison to derive the phantom forces imposed on the global frame.
+The inertial frame is defined with $\hat {\bm x}$ pointing perpendicular to the plane of the orbit in the same direction as the $\hat {\bm x}$ of the global frame, so that the inertial frame is just a rotation of the global frame around their common $\hat {\bm x}$
+
 \subsection{Tidal torque}
@@
 where $D$ is the distance between the asteroid, $\mu$ is the gravitational parameter of the planet being orbited.
-We have oriented our axes such that $\hat {\bm z}$ points towards the planet and $\hat {\bm y}$ points forward in the plane of orbit of the asteroid.
+This equation is true in the global frame, where $\hat{\bm z}$ points towards the planet.
 
@@
 \label{sec:requirements}
-Any asteroid model with floating paramters designed to describe an asteroid with nonuniform density on flyby with a planet must be well-equipped to perform the following operations
+Any asteroid model with floating parameters designed to describe an asteroid with nonuniform density on flyby with a planet must be well-equipped to perform the following operations
 
@@
 \begin{equation}
-    I\dot{\bm{\omega}} + \bm \omega \times (I \bm \omega) = \bm \tau
-    \label{eqn:euler}
+    I_\mathcal{I}\dot{\bm{\omega}}_\mathcal{I} + \bm \omega_\mathcal{I} \times (I_\mathcal{I}\bm \omega_\mathcal{I}) = \bm \tau_\mathcal{I}
+    \label{eqn:euler-inertial}
 \end{equation}
-where $\bm \tau$ is the external torque on the asteroid: tidal torque in this case.
+where $\bm \tau_\mathcal{I}$ is the external torque on the asteroid---tidal torque in this case---and the subscript $\mathcal I$ indicates that a quantity is written in the inertial frame.
+It will be more useful to us to express this equation in the global frame, so we define a rotation matrix $R_x$, which rotates vectors in the global frame to the inertial frame.
+We also define $\bm \Omega = \bm r \times \bm v/ r^2$ to be the rotation rate of the global frame around the planet, where $\bm r$ is the position and $\bm v$ is the velocity of the asteroid.
+Since $\bm \Omega$ points along $\hat{\bm x}$, the common axis between the inertial and global frames, we know $R_x \bm\Omega = \bm\Omega$, so that $\bm \omega_\mathcal{I} = R_x(\bm \omega_\mathcal{G} + \Omega)$ where the subscript $\mathcal G$ indicates global coordinates.
+Similarly, $I_\mathcal{I} = R_x I_\mathcal{G}R_x^T$.
+Finally, the external torque $\tau$ is simply rotated: $\bm \tau_\mathcal{I} = R_x \bm \tau_\mathcal{G}$.
 
-Equation \ref{eqn:diff-torque} is written in the frame where $\hat {\bm z}$ points towards the planet.
-Assuming the torque $\bm \tau$ in equation \ref{eqn:euler} is also written in this frame, there will be an additional rotation caused by the orbital motion of the asteroid of $\bm \Omega = \bm v \times \hat{\bm z} / D$, where $\bm v$ is the orbital velocity of the asteroid.
-Note that $\bm \Omega$ is parallel to $\hat x$.
-From conservation of angular momentum, it follows that $\dot{\bm \Omega} = -2(\bm v \cdot \hat{\bm z})\bm \Omega / D$.
-The final angular acceleration is then
+To simplify equation \ref{eqn:euler-inertial}, we will also need the facts $\dot R_x\bm\omega_\mathcal{G}=R_x(\bm\Omega\times\bm\omega_\mathcal{G})$ and $\dot \Omega = -2(\bm r \cdot \bm v / r^2)\bm \Omega$.
+Taking this into account, we have
 \begin{equation}
-    \dot{\bm \omega} = -\dot{\bm \Omega} + I^{-1}\brackets{\bm \tau - (\bm \omega + \bm \Omega) \times I(\bm \omega + \bm \Omega)}
-    \label{eqn:angular-acc}
+    \dot{\bm{\omega}} = I^{-1}\brackets{\bm \tau - (\bm \omega + \bm \Omega) \times I (\bm \omega + \bm \Omega)} + 2 \bm \Omega \frac{\bm r \cdot \bm v}{r^2} - \bm \Omega \times \bm \omega
 \end{equation}
+where all the quantities are now in global coordinates.
 

### 2021-09-02 code/fit_resolved/optimizer/minimizer.py

@@ -1,22 +1,26 @@
-from scipy.optimize import minimize
-import time, sys, os, inspect
+import numpy as np
+import matplotlib.pyplot as plt
+import sys, os, inspect
 currentdir = os.path.dirname(os.path.abspath(inspect.getfile(inspect.currentframe())))
 parentdir = os.path.dirname(currentdir)
 sys.path.insert(0, parentdir)
-import numpy as np
-import matplotlib.pyplot as plt
-import asteroids
+
+import asteroids, time
+from multiprocessing import Pool
 from random_vector import *
+from scipy import optimize, linalg
 
 
 ASTEROIDS_MAX_K = 2 # Remember to change the counterpart in backend.hpp
 ASTEROIDS_MAX_J = 0 # Remember to change the counterpart in backend.hpp
 EARTH_RADIUS = 6370000
+NUM_MINIMIZE_POINTS = 8
+EPSILON = 1e-8
 
 if len(sys.argv) not in [2, 3]:
     raise Exception("Please pass a file to describe the fit")
 output_name = sys.argv[1]
-f = open("../../staged/" + output_name+".dat", 'r')
+f = open("../../../staged/" + output_name+".dat", 'r')
 cadence = int(f.readline())
 impact_parameter = EARTH_RADIUS * int(f.readline())
 radius = float(f.readline())
@@ -24,8 +28,6 @@ speed = float(f.readline())
 spin = [float(x) for x in f.readline().split(',')]
 jlms = [float(x) for x in f.readline().split(',')]
 theta_true = [float(x) for x in f.readline().split(',')]
-theta_start = [float(x) for x in f.readline().split(',')]
-theta_spread = [float(x) for x in f.readline().split(',')]
 theta_high = np.asarray([float(x) for x in f.readline().split(',')])
 theta_low = np.asarray([float(x) for x in f.readline().split(',')])
 
@@ -33,53 +35,165 @@ sigma = float(f.readline()) * np.sqrt(spin[0]**2 + spin[1]**2 + spin[2]**2)
 while output_name[-1] == '\n':
     output_name = output_name[:-1]
 f.close()
-assert(len(theta_true) == len(theta_start) == len(theta_spread) == len(theta_high) == len(theta_low))
+assert(len(theta_true) == len(theta_high) == len(theta_low))
 assert(len(theta_true) == (ASTEROIDS_MAX_K + 1)**2 - 6)
[…]

### 2021-10-31 summaries/21-11/21-11.tex
Updated sensitivity model

--- 2021-07-29 summaries/new-math/new-math.tex
@@
 \begin{document}
-\title{New math derivation}
-\author{Jack Dinsmore, Julien de Wit}
+\title{Summary for August, 2021}
+\author{Jack Dinsmore}
 \email{jtdinsmo@mit.edu}
@@
 By violating these assumptions and considering other effects (oblateness, etc.), we can break the degeneracy.
+This month I correct some old mistakes.
 \end{abstract}
@@
 \begin{equation}
-\J_{lm} = \int d^3 r \rho_M(\bm r) R_{lm} (\bm r)
+\J_{lm} = \frac{1}{M_M}\int d^3 r \rho_M(\bm r) a_M^{-l} R_{lm} (\bm r)
 \label{eqn:jlm-def}
 \end{equation}
-and we have
+where $M_M$ is the mass of the Earth and $a_M$ is its radius. Then we have
 \begin{equation}
-V(\bm R) = -\sum_{lm} S^*_{lm} (\bm R) \J_{lm}.
+V(\bm R) = -M_M\sum_{lm} a_M^{l} S^*_{lm} (\bm R) \J_{lm}.
 \label{eqn:potential}
 \end{equation}
-Incidentally, since $R_{00} = 1$, we have that $\J_{00}$ is the total mass of the asteroid and $\mu = G \J_{00}$, which can be used to simplify equation \ref{eqn:linear-eom}.
+Incidentally, since $R_{00} = 1$, we have that $\J_{00}=1$. Choosing coordinates in which the Earth's center of mass is at the origin, we have $\J_{1m}=0$ as well.
 
@@
 \begin{equation}
-\bm \tau = \int d^3 r \rho(\bm r) \bm r \times \nabla_{\bm R} \sum_{lm} S^*_{lm}(\bm R) \J_{lm}.
+\bm \tau = GM_M \int d^3 r \rho(\bm r) \bm r \times \nabla_{\bm R} \sum_{lm} a_M^l S^*_{lm}(\bm R) \J_{lm}.
 \label{eqn:first-torque}
@@
 \begin{aligned}
-\bm \tau = &\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
+\bm \tau = &GM_M \sum_{lm}(-1)^l a_M^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
 &\int d^3 r \rho(\bm r) \bm r \times \nabla R^*_{l'm'}(\bm r).
@@
 \begin{aligned}
-\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
+\bm \tau = &-\frac{GM_M}{2}\sum_{lm}(-1)^l a_M^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
 &\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
@@
 \end{equation*}
-By defining the new varialble
+We define the new varialble
 \begin{equation}
-\K_{lm} = \int d^3 r \rho(\bm r) R_{lm} (\bm r),
+\K_{lm} = m\int d^3 a_m^{-l}r \rho(\bm r) R_{lm} (\bm r),
 \label{eqn:klm-def}
 \end{equation}
-we can simplify this to
-\begin{equation*}
+where $M_m$ is the mass of the asteroid and $a_m$ is a constant with units of length which we define later. Think of it as something like the radius of the asteroid. Note the convenient fact that
+\begin{equation}
 \begin{aligned}
-\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
+\K_{lm}^* = &M_m\int d^3 a_m^{-l}r \rho(\bm r) R_{lm}^* (\bm r) \\
+= &(-1)^mM_m\int d^3 a_m^{-l}r \rho(\bm r) R_{l,-m} (\bm r) = (-1)^mK_{l,-m}.\\
+\label{eqn:klm-def}
+\end{aligned}
+\end{equation}
+
+We can simplify the torque to
+\begin{equation}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2}\sum_{lm}(-1)^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) a_M^l a_m^{l'}\\
 &\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
@@
 \end{aligned}
-\end{equation*}
-
-\section{Proof of real-ness}
-This equation had better be real. To prove it, let us combine the $\pm m'$ terms, leaving out the $m'=0$ term and using the subscript o (off-diagonal) to indicate its absence:
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'_+}\Bigg\{S_{l+l',m+m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
-&S_{l+l',m-m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'+m'+1)R^*_{l',-m'-1}(\bm r)\\
-&+(i\x-\y)(l'-m'+1)R^*_{l',-m'+1}(\bm r)-2im'\z R^*_{l',-m'}(\bm r)]\Bigg\}.
-\end{aligned}
-\end{equation*}
-Using the symmetry rules for complex conjugates,
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'm'_+}\Bigg\{S_{l+l',m+m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
-&S_{l+l',m-m'}(\bm D) \\
-&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg\}.
-\end{aligned}
-\end{equation*}
-Now we expand for $\pm m$ too:
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}(-1)^l \Bigg\{\J_{lm}\sum_{l'm'_+} \Bigg[S_{l+l',m+m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
-&+S_{l+l',m-m'}(\bm D) \\
-&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg]\\
-&+ \J_{l,-m}\sum_{l'm'_+} \Bigg[S_{l+l',-m+m'}(\bm D) \\
-&+\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]\\
-&+S_{l+l',-m-m'}(\bm D) \\
-&(-1)^{m'}\int d^3 r \rho(\bm r) [-(i\x + \y)(l'+m'+1)R_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)R_{l',m'-1}(\bm r)-2im'\z R_{l',m'}(\bm r)]\Bigg]\Bigg\}.
-\end{aligned}
-\end{equation*}
-Let us introduce a new notation:
-\begin{equation}
-\K_{lm} = \int d^3 r \rho(\bm r) R_{lm} (\bm r)
-\label{eqn:klm-def}
 \end{equation}
-which are the expansion coefficients of the potential of the asteroid. Then the above becomes
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}(-1)^l \Bigg\{\J_{lm}\sum_{l'm'_+} \Bigg[S_{l+l',m+m'}(\bm D) \\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
-&+S_{l+l',m-m'}(\bm D) \\
-&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
-&+ (-1)^m (-1)^{m+m'}\J_{l,m}^*\sum_{l'm'_+} \Bigg[S^*_{l+l',m-m'}(\bm D) \\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
-&+S^*_{l+l',m+m'}(\bm D) \\
-&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\Bigg\}.
-\end{aligned}
-\end{equation*}
-which can be simplified as
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l \Bigg\{\J_{lm} \Bigg[S_{l+l',m+m'}(\bm D) \\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)K^*_{l',m'+1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\\
-&+S_{l+l',m-m'}(\bm D) \\
-&(-1)^{m'}\bigg[-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)\\
-&-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
-&+\J_{lm}^*\Bigg[S^*_{l+l',m+m'}(\bm D) \\
-&\bigg[-(i\x-\y)(l'-m'+1)\K_{l',m'-1}(\bm r)\\
-&-(i\x + \y)(l'+m'+1)\K_{l',m'+1}(\bm r)-2im'\z \K_{l',m'}(\bm r)\bigg]\Bigg]\\
-&+(-1)^{m'}S^*_{l+l',m-m'}(\bm D) \\
-&\bigg[(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}(\bm r)\\
-&+(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}(\bm r)+2im'\z \K^*_{l'm'}(\bm r)\bigg]\Bigg\}
-\end{aligned}
-\end{equation*}
-or
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&(l'-m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}\\
-&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'-1}(i\x-\y)\\
-&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\bigg)\\
-&+(l'+m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}\\
-&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'+1}(i\x + \y)\\
-&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\bigg)\\
-&+2im'\z\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}\\
-&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l'm'}\\
-&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)\K^*_{l'm'}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-This can be written as follows
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\frac{1}{2}\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&(l'-m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x + \y)\K^*_{l',m'-1}\\
-&+\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'-1}(-i\x+\y)\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}\\
-&-(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(-i\x - \y)\K^*_{l',m'-1}\bigg)\\
-&+(l'+m'+1)\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}\\
-&+\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l',m'+1}(-i\x - \y)\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}\\
-&-(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)(-i\x+\y)\K^*_{l',m'+1}\bigg)\\
-&+2im'\z\bigg(\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}\\
-&-\J_{lm}^*S^*_{l+l',m+m'}(\bm D)\K_{l'm'}\\
-&-(-1)^{m'}\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}\\
-&+(-1)^{m'}\J_{lm}^*S^*_{l+l',m-m'}(\bm D)\K^*_{l'm'}\bigg)\Bigg\},
-\end{aligned}
-\end{equation*}
-or
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&+(l'-m'+1)\bigg(\Re\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)(-i\x+\y)\K^*_{l',m'-1}}\\
-&-(-1)^{m'}\Re\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)(i\x-\y)\K_{l',m'-1}}\bigg)\\
-&+(l'+m'+1)\bigg(\Re\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)(i\x-\y)\K^*_{l',m'+1}}\\
-&-(-1)^{m'}\Re\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)(i\x + \y)\K_{l',m'+1}}\bigg)\\
-&-2m'\z\bigg(\Im\brackets{\J_{lm}S_{l+l',m+m'}(\bm D)\K^*_{l'm'}}\\
-&-(-1)^{m'}\Im\brackets{\J_{lm}S_{l+l',m-m'}(\bm D)\K_{l'm'}}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-Define
-$$\J_{lml'm'}^\pm = \J_{lm} S_{l+l',m\pm m'}(\bm D)(\pm 1)^{m'+1}.$$
-Then
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&+(l'-m'+1)\bigg(\Re\brackets{\J_{lml'm'}^+(-i\x+\y)\K^*_{l',m'-1}}\\
-&+\Re\brackets{\J_{lml'm'}^-(i\x-\y)\K_{l',m'-1}}\bigg)\\
-&+(l'+m'+1)\bigg(\Re\brackets{\J_{lml'm'}^+(i\x-\y)\K^*_{l',m'+1}}\\
-&+\Re\brackets{\J_{lml'm'}^-(i\x + \y)\K_{l',m'+1}}\bigg)\\
-&-2m'\z\bigg(\Im\brackets{\J_{lml'm'}^+\K^*_{l'm'}}+\Im\brackets{\J_{lml'm'}^-\K_{l'm'}}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-Further defining
-\begin{equation}
-\begin{aligned}
-\chi_{lml'm'}^{\pm,s}& = \J_{lml'm'}^\pm \K^*_{l',m'+s}\\
-&= (\pm 1)^{m'+1}S_{l+l',m\pm m'}(\bm D)\J_{lm} \K^*_{l',m'+s},
-\end{aligned}
-\label{eqn:chi}
-\end{equation}
-we get
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&+(l'-m'+1)\bigg(\Re\brackets{\chi_{lml'm'}^{+-}(i\x+\y)}\\
-&+\Re\brackets{\chi_{lml'm'}^{--}(i\x-\y)}\bigg)\\
-&+(l'+m'+1)\bigg(\Re\brackets{\chi_{lml'm'}^{++}(i\x-\y)}\\
-&+\Re\brackets{\chi_{lml'm'}^{-+}(i\x + \y)}\bigg)\\
-&-2m'\z\bigg(\Im\brackets{\chi_{lml'm'}^{+0}}+\Im\brackets{\chi_{lml'm'}^{-0}}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-\comment{(Here I realized I made a mistake earlier; I took the complex conjugate of the top line and forgot to conjugate the vector term, so I do it here)}, or
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &-\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&+(l'-m'+1)\bigg(\Re\chi_{lml'm'}^{+-}\y - \Im\chi_{lml'm'}^{+-}\x\\
-&-\Re\chi_{lml'm'}^{--}\y - \Im\chi_{lml'm'}^{--}\x \bigg)\\
-&+(l'+m'+1)\bigg(-\Re\chi_{lml'm'}^{++}\y - \Im\chi_{lml'm'}^{++}\x\\
-&+\Re\chi_{lml'm'}^{-+}\y - \Im\chi_{lml'm'}^{-+}\x\bigg)\\
-&-2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-We can write this as
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&+(l'-m'+1)\bigg(\Im\chi_{lml'm'}^{+-}\x - \Re\chi_{lml'm'}^{+-}\y\\
-&+\Re\chi_{lml'm'}^{--}\y + \Im\chi_{lml'm'}^{--}\x \bigg)\\
-&+(l'+m'+1)\bigg(\Re\chi_{lml'm'}^{++}\y + \Im\chi_{lml'm'}^{++}\x\\
-&\Im\chi_{lml'm'}^{-+}\x - \Re\chi_{lml'm'}^{-+}\y\bigg)\\
-&+2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\},
-\end{aligned}
-\end{equation*}
-or, joining vectors,
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&\x \bigg((l'-m'+1)\Im\chi_{lml'm'}^{+-} + (l'-m'+1)\Im\chi_{lml'm'}^{--}\\
-&+(l'+m'+1)\Im\chi_{lml'm'}^{++} + (l'+m'+1)\Im\chi_{lml'm'}^{-+}\bigg)\\
-&+\y \bigg(-(l'-m'+1)\Re\chi_{lml'm'}^{+-} + (l'-m'+1)\Re\chi_{lml'm'}^{--}\\
-&+(l'+m'+1)\Re\chi_{lml'm'}^{++} - (l'+m'+1)\Re\chi_{lml'm'}^{-+}\bigg)\\
-&+2m'\z\bigg(\Im\chi_{lml'm'}^{+0}+\Im\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-Finally,
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++}+ (l'-m'+1)\chi_{lml'm'}^{--}\\
-&+ (l'-m'+1)\chi_{lml'm'}^{+-} + (l'+m'+1)\chi_{lml'm'}^{-+}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--} \\
-&- (l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{-+}\bigg)\\
-&+2m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}.
-\end{aligned}
-\end{equation*}
-
-Note that
-\begin{equation}
-\begin{aligned}
-\chi_{l,-m,l',m'}^{\pm,s} = &(\pm 1)^{m'+1}S_{l+l',-m\pm m'}(\bm D)\J_{l,-m} \K^*_{l',m'+s}\\
-=&(-1)^s(\pm 1)^{m'+1}S^*_{l+l',m\mp m'}(\bm D)\J^*_{lm} \K_{l',-m'-s}\\
-=&(-1)^s{\chi_{l,m,l',-m'}^{\pm,-s}}^*.
-\end{aligned}
-\label{eqn:chi}
-\end{equation}
-and
-\begin{equation}
-\begin{aligned}
-\chi_{l,-m,l',-m'}^{\pm,s} = &(\pm 1)^{-m'+1}S_{l+l',-m\mp m'}(\bm D)\J_{l,-m} \K^*_{l',-m'+s}\\
-=&(-1)^s(\pm 1)^{m'+1}S^*_{l+l',m\pm m'}(\bm D)\J^*_{lm} \K_{l',m'-s}\\
-=&(-1)^s{\chi_{lml'm'}^{\pm,-s}}^*
-\end{aligned}
-\label{eqn:chi}
-\end{equation}
-so
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\\
-&+ (l'-m'+1)\chi_{l,-m,l',-m'}^{++} + (l'+m'+1)\chi_{l,-m,l',-m'}^{--}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--} \\
-&+ (l'-m'+1)\chi_{l,-m,l',-m'}^{++} + (l'+m'+1)\chi_{l,-m,l',-m'}^{--}\bigg)\\
-&+2m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{lm_+}\sum_{l'm'_+}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}\\
-&+\sum_{lm_-}\sum_{l'm'_-}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\parens{\sum_{lm_+}\sum_{l'm'_+}+\sum_{lm_-}\sum_{l'm'_-}}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{lml'm'}^{++} + (l'-m'+1)\chi_{lml'm'}^{--}\bigg)\\
-&+m'\z\Im\bigg(\chi_{lml'm'}^{+0}+\chi_{lml'm'}^{-0}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-
-\clearpage
-
-Then consider
-\begin{equation*}
-\begin{aligned}
-&\sum_{l,m\neq0}\sum_{l',m'\neq 0'}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-=&\sum_{l,m_+}\sum_{l',m'\neq 0'}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
-&\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-=&\sum_{l,m_+}\sum_{l',m'_+}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
-&+\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
-&+\x \Im\bigg((l'-m'+1)\chi_{l,m,l',-m'}^{++} - (l'+m'+1)\chi_{l,m,l',-m'}^{+-}\bigg)\\
-&+\x \Im\bigg((l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{++}\bigg)
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-=&\sum_{l,m_+}\sum_{l',m'_+}(-1)^l\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{lml'm'}^{++} - (l'-m'+1)\chi_{lml'm'}^{+-}\bigg)\\
-&+\x \Im\bigg((l'+m'+1)\chi_{l,m,l',-m'}^{+-} - (l'-m'+1)\chi_{l,m,l',-m'}^{++}\bigg)\\
-&+\x \Im\bigg((l'-m'+1)\chi_{l,m,l',-m'}^{++} - (l'+m'+1)\chi_{l,m,l',-m'}^{+-}\bigg)\\
-&+\x \Im\bigg((l'-m'+1)\chi_{lml'm'}^{+-} - (l'+m'+1)\chi_{lml'm'}^{++}\bigg)
-\end{aligned}
-\end{equation*}
-
-Now we want to compute the on-diagonal component of torque, which is where $m'=0$, and $m\in \mathbb{Z}.$ That's
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{lm}(-1)^l\J_{lm}\sum_{l'}(l'+1)S_{l+l',m}(\bm D) \\
-&[(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}].
-\end{aligned}
-\end{equation*}
-Now we combine $\pm m$,
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{lm_+}(-1)^l\Bigg\{\J_{lm}\sum_{l'}(l'+1)S_{l+l',m}(\bm D) \\
-&[(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}]\\
-& + \J_{l,-m}\sum_{l'}(l'+1)S_{l+l',-m}(\bm D) \\
-& [(i\x + \y)\K^*_{l',-1}+(i\x-\y)\K^*_{l',1}]\Big\}\\
-& - \frac{1}{2}\sum_{l}(-1)^l \J_{l0} \sum_{l'}(l'+1)S_{l+l',0}(\bm D)\\
-& [(i\x + \y)\K^*_{l',-1} + (i\x - \y \K^*_{l',1})].
-\end{aligned}
-\end{equation*}
-Note that
-$$\chi_{lml'0}^{\pm,s} = \pm S_{l+l',m}(\bm D)\J_{lm} \K^*_{l',s},$$
-so
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{ \\
-&[(-i\x - \y)\chi_{lml'0}^{--}+(i\x-\y)\chi_{lml'0}^{++}]\\
-& + [(-i\x - \y){\chi_{lml'0}^{++}}^*+(i\x-\y){\chi_{lml'0}^{--}}^*]\Big\}\\
-& - \frac{1}{2}\sum_{l}(-1)^l \sum_{l'}(l'+1)\\
-& [(-i\x - \y)\chi_{l0l'0}^{--} + (i\x - \y)\chi_{l0l'0}^{++}].
-\end{aligned}
-\end{equation*}
-Since $\chi_{l0l'0}^{--}={\chi_{l0l'0}^{++}}^*$, this simplifies as follows:
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Big( \\
-&\Re[(-i\x - \y)\chi_{lml'0}^{--}]+\Re[(i\x-\y)\chi_{lml'0}^{++}]\Big)\\
-& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \Re[(i\x - \y)\chi_{l0l'0}^{++}]
-\end{aligned}
-\end{equation*}
-or
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
-&\parens{-\y\Re\chi_{lml'0}^{--} + \x\Im\chi_{lml'0}^{--}}\\
-&+\parens{-\y\Re\chi_{lml'0}^{++}-\x\Im\chi_{lml'0}^{++}}\Bigg\}\\
-& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}]}
-\end{aligned}
-\end{equation*}
-which is
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
-&\x\Im\parens{\chi_{lml'0}^{--}-\chi_{lml'0}^{++}} -\y\Re\parens{\chi_{lml'0}^{++}+\chi_{lml'0}^{--}} \Bigg\}\\
-& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}}.
-\end{aligned}
-\end{equation*}
-We can also write this as
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
-&\x\Im\parens{\chi_{lml'0}^{--}+\chi_{lml'0}^{-+}} - \y\Re\parens{\chi_{lml'0}^{++} - \chi_{lml'0}^{+-}} \Bigg\}\\
-& - \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{-\y\Re\chi_{l0l'0}^{++} - \x\Im\chi_{l0l'0}^{++}}
-\end{aligned}
-\end{equation*}
-which is
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm_+}(-1)^l\sum_{l'}(l'+1)\Bigg\{\\
-&\x\Im\parens{\chi_{lml'0}^{--}+\chi_{l,-m,l',0}^{--}} - \y\Re\parens{\chi_{lml'0}^{++} + \chi_{l,-m,l',0}^{++}} \Bigg\}\\
-& + \sum_{l}(-1)^l \sum_{l'}(l'+1) \parens{\y\Re\chi_{l0l'0}^{++} + \x\Im\chi_{l0l'0}^{++}}
-\end{aligned}
-\end{equation*}
-or
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm}(-1)^l\sum_{l'}(l'+1)\Bigg\{\x\Im\chi_{lml'0}^{--} - \y\Re\chi_{lml'0}^{++}\Bigg\}.
-\end{aligned}
-\end{equation*}
-Note that the sum now extends over all $m$.
-
-I forgot to add the case where $m=0$, $m'\neq 0$. So add this part:
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'\neq 0}S_{l+l',m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)]
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
-&\bigg[(i\x + \y)(l'-m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'+1}\\
-&+2im'\z S_{l+l',m'}(\bm D)\K^*_{l'm'}\bigg]\\
-&+\bigg[(i\x + \y)(l'+m'+1)S_{l+l',-m'}(\bm D)\K^*_{l',-m'-1}\\
-&+(i\x-\y)(l'-m'+1)S_{l+l',-m'}(\bm D)\K^*_{l',-m'+1}\\
-&-2im'\z S_{l+l',-m'}(\bm D)\K^*_{l'-m'}\bigg]\Bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
-&\bigg[(i\x + \y)(l'-m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)S_{l+l',m'}(\bm D)\K^*_{l',m'+1}\\
-&+2im'\z S_{l+l',m'}(\bm D)\K^*_{l'm'}\bigg]\\
-&+\bigg[-(i\x + \y)(l'+m'+1)S^*_{l+l',m'}(\bm D)\K_{l',m'+1}\\
-&-(i\x-\y)(l'-m'+1)S^*_{l+l',m'}(\bm D)\K_{l',m'-1}\\
-&-2im'\z S^*_{l+l',m'}(\bm D)\K_{l'm'}\bigg]\Bigg\}
-\end{aligned}
-\end{equation*}
-
-\begin{equation}
-\begin{aligned}
-\chi_{l0l'm'}^{\pm,s}&= (\pm 1)^{m'+1}S_{l+l',\pm m'}(\bm D)\J_{l0} \K^*_{l',m'+s},\\
-\end{aligned}
-\label{eqn:chi}
-\end{equation}
-
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\frac{1}{2}\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\Bigg\{ \\
-&\bigg[(i\x + \y)(l'-m'+1)\chi_{l0l'm'}^{+-}\\
-&+(i\x-\y)(l'+m'+1)\chi_{l0l'm'}^{++} +2im'\z \chi_{l0l'm'}^{+0}\bigg]\\
-&+\bigg[(-i\x - \y)(l'+m'+1){\chi_{l0l'm'}^{++}}^*\\
-&+(-i\x+\y)(l'-m'+1){\chi_{l0l'm'}^{+-}}^* -2im'\z {\chi_{l0l'm'}^{+0}}^*\bigg]\Bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
-&\Re[(i\x + \y)(l'-m'+1)\chi_{l0l'm'}^{+-}]\\
-&+\Re[(i\x-\y)(l'+m'+1)\chi_{l0l'm'}^{++}]\\
-&-2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
-&\y\Re\chi_{l0l'm'}^{+-}(l'-m'+1) - \x\Im\chi_{l0l'm'}^{+-}(l'-m'+1)\\
-&-\y\Re\chi_{l0l'm'}^{++}(l'+m'+1) - \x\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
-&-2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
-&\x\Im\parens{\chi_{l0l'm'}^{+-}(l'-m'+1) +\chi_{l0l'm'}^{++}(l'+m'+1)}\\
-&+\y\Re\parens{\chi_{l0l'm'}^{++}(l'+m'+1)-\chi_{l0l'm'}^{+-}(l'-m'+1)}\\
-&+2m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &\sum_{l}(-1)^l\J_{l0}\sum_{l',m'_+}\bigg\{ \\
-&\x\Im\parens{\chi_{l,0,l',-m'}^{++}(l'-m'+1) +\chi_{l0l'm'}^{++}(l'+m'+1)}\\
-&+\y\Re\parens{\chi_{l0l'm'}^{++}(l'+m'+1)+\chi_{l,0,l',-m'}^{++}(l'-m'+1)}\\
-&+m'\z \Im\chi_{l0l'm'}^{+0}-m'\z \Im\chi_{l,0,l',-m'}^{+0}\bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &\sum_{l}(-1)^l\sum_{l',m'\neq 0}\bigg\{ \\
-&\x\Im\chi_{l0l'm'}^{++}(l'+m'+1)+\y\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
-&+m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}
-\end{aligned}
-\end{equation*}
-So in all,
-\begin{equation*}
-\begin{aligned}
-\bm \tau_d = &-\sum_{lm}(-1)^l\sum_{l'}(l'+1)\Bigg\{\x\Im\chi_{lml'0}^{--} - \y\Re\chi_{lml'0}^{++}\Bigg\}+\\
- &\sum_{l}(-1)^l\sum_{l',m'\neq 0}\bigg\{ \\
-&\x\Im\chi_{l0l'm'}^{++}(l'+m'+1)+\y\Re\chi_{l0l'm'}^{++}(l'+m'+1)\\
-&+m'\z \Im\chi_{l0l'm'}^{+0}\bigg\}.
-\end{aligned}
-\end{equation*}
-When the limits are extended to $m_-,m'_- \cup m\geq 0, m' \geq 0$, the off diagonal formula reduces to
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{l'}\sum_{l,m\geq0}(-1)^l(l'+1)\Bigg\{\\
-&\x \Im\bigg(\chi_{lml'0}^{++} + \chi_{lml'0}^{--}\bigg)+\y \Re\bigg(\chi_{lml'0}^{++} + \chi_{lml'0}^{--}\bigg)\Bigg\}\\
-&+\sum_{l}(-1)^l\sum_{l',m'>0}\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'-m'+1)\chi_{l0l'm'}^{--}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'-m'+1)\chi_{l0l'm'}^{--}\bigg)\\
-&+m'\z\Im\bigg(\chi_{l0l'm'}^{+0}+\chi_{l0l'm'}^{-0}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-\begin{equation*}
-\begin{aligned}
-\bm \tau_o = &\sum_{l'}\sum_{l,m\geq0}(-1)^l(l'+1)\Bigg\{\\
-&\x \Im\bigg(-\chi_{l,-m,l',0}^{--} + \chi_{lml'0}^{--}\bigg)+\y \Re\bigg(\chi_{lml'0}^{++} + \chi_{l,-m,l',0}^{++}\bigg)\Bigg\}\\
-&+\sum_{l}(-1)^l\sum_{l',m'>0}\Bigg\{\\
-&\x \Im\bigg((l'+m'+1)\chi_{l0l'm'}^{++} + (l'+m'+1)\chi_{l,0,l',-m'}^{-+}\bigg)\\
-&+\y \Re\bigg((l'+m'+1)\chi_{l0l'm'}^{++} - (l'+m'+1)\chi_{l,0,l',-m'}^{-+}\bigg)\\
-&+m'\z\Im\bigg(\chi_{l0l'm'}^{+0}+\chi_{l0l'm'}^{-0}\bigg)\Bigg\}
-\end{aligned}
-\end{equation*}
-\comment{So it doesn't really work out. I'll have to do this later.}
-
-\clearpage
+which evidently obeys unit analysis, since $\J_{lm}$ and $\K_{lm}$ are unit-less.
+This equation is also real, but the proof is nontrivial.
+We will instead investigate the outcomes of this equation under the simplifying assumptions that $l=m=0$ and $l'=2$.
+But first, we discuss the torque in relation to the equations of motion.
 
@@
 Then we can write the above in terms of $R_{2m}$:
-$$I_{xx}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)+2R_{2,-2}+2R_{22}$$
-$$I_{yy}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-1)-2R_{2,-2}-2R_{22}$$
-$$I_{zz}=\int d^3r \rho(\bm r)\frac{4}{3}R_{20}+\frac{1}{3}$$
+$$I_{xx}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-r^2)+2R_{2,-2}+2R_{22}$$
+$$I_{yy}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-r^2)-2R_{2,-2}-2R_{22}$$
+$$I_{zz}=\int d^3r \rho(\bm r)\frac{4}{3}R_{20}+\frac{r^2}{3}$$
 $$I_{xz}=-\int d^3r \rho(\bm r)R_{21}-R_{2,-1}$$
@@
 and therefore
-$$I_{xx}=\frac{2}{3}\K_{20}-2\K_{2,-2}-2\K_{22}+\frac{2}{5}\K_{00}$$
-$$I_{yy}=\frac{2}{3}\K_{20}+2\K_{2,-2}+2\K_{22}+\frac{2}{5}\K_{00}$$
-$$I_{zz}=-\frac{4}{3}\K_{20} + \frac{2}{5}\K_{00}$$
-$$I_{xz}=\K_{21}-\K_{2,-1}$$
-$$I_{yz}=\frac{\K_{21}+\K_{2,-1}}{i}$$
-$$I_{xy}=-2\frac{\K_{22}-\K_{2,-2}}{i}.$$
+$$I_{xx}=\parens{\frac{2}{3}\K_{20}-2\K_{2,-2}-2\K_{22}+\frac{2}{3}}M_ma_m^2$$
+$$I_{yy}=\parens{\frac{2}{3}\K_{20}+2\K_{2,-2}+2\K_{22}+\frac{2}{3}}M_ma_m^2$$
+$$I_{zz}=\parens{-\frac{4}{3}\K_{20} + \frac{2}{3}}M_ma_m^2$$
+$$I_{xz}=\parens{\K_{21}-\K_{2,-1}}M_ma_m^2$$
+$$I_{yz}=\parens{\frac{\K_{21}+\K_{2,-1}}{i}}M_ma_m^2$$
+$$I_{xy}=\parens{-2\frac{\K_{22}-\K_{2,-2}}{i}}M_ma_m^2.$$
+Here, we have judiciously defined $a_m$ so that the above equations are true. That definition is
+\begin{equation}
+a_m^2 = \brackets{\int d^3 r \rho(\bm r) r^2}\brackets{\int d^3 r \rho(\bm r)}^{-1}
+\label{eqn:am}
+\end{equation}
+and it is something like the radius of the asteroid. If the asteroid were a sphere of radius $R$, we would have $a_m = R\sqrt{3/5}$
 
-Thus, the moment of inertia is determined entirely by $\K_{lm}$ and therefore by $C_{lms}$.
-The reader will notice that the moment of inertia depends counter-intuitively on the asteroid mass $\K_{00}$.
-However, we may write the moment of inertia as $I_\perp+\mathbb{I}\frac{2}{5}\K_{00}$, where $\mathbb{I}$ is the identity matrix, and $I_\perp$ depends only on $K_{2m}$.
-Then equation $$\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times \parens{I_\perp+\mathbb{I}\frac{2}{5}\K_{00}} \bm \omega}$$
-$$\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times I_\perp\bm \omega}$$
-because the identity matrix does not change the direction of a vector multiplied by it.
-However, due to the first term, the mass of the asteroid must indeed be known to integrate the equation of motion.
+Thus, the moment of inertia is determined entirely by $\K_{lm}$
 
 \section{Computing torque}
-Since the proof that our torque in equation \ref{eqn:complex-torque} is real is generally difficult and does not seem very enlightening, we will move on for now.
-
 Note that the $S$ present in equation \ref{eqn:complex-torque} forces $l$ and $l'$ to be low in the dominant terms.
@@
 \dot \omega_z = I_z^{-1}\parens{\tau_z + (I_x - I_y)\omega_x \omega_y}\\
+\label{eqn:sep-euler}
 \end{aligned}
@@
 The only free parameters with $l\leq 2$ are $\K_{00}$, $\K_{20}$, and $\Re \K_{22}$, which is three total.
+
+Equation \ref{eqn:sep-euler} indicates that the mass of the asteroid $M_m$ factors out of all the physics of the simulation.
+Both the inertia and the torque are directly proportional to $M_m$, and they always appear in ratios.
+So the mass of the asteroid cannot be computed from tidal torque observation.
+
+Furthermore, unless $\K_{l>2}$ are regressed for, $a_m$ cannot be determined either since it cancels out of the angular part of equation \ref{eqn:sep-euler}, and out of the torque part except when $\K_{l>2}$ terms are introduced.
+
+\section{First order torque}
+I want to reduce equation \ref{eqn:complex-torque} to a real form for $l=m=0$, $l'=2$.
+After this, I will demonstrate that the equation of motion is non-degenerate in $\K_{lm}$.
+Thus, $\K_{lm}$ and the initial position $\theta_0$ can be fitted to data without fear of degeneracy.
+Unfortunately, the radius $a_m$ cannot be fitted because scaling up the radius is equivalent to scaling up $K_{l>2}$.
+However, it can be guessed, and then $K_{l}$ fitted without harm.
+Then it can be later chosen such that $K_l$ have desired properties: that they decay or remain of equivalent size with larger $l$, for instance.
+
+Now for the reduction. Removing the sums and remembering that $\J_{00}=1$, we get
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2} \sum_{m'=-2}^2 S_{2,m'}a_m^2\\
+&\bigg[(i\x + \y)(3-m')\K^*_{l',m'-1}\\
+&+(i\x-\y)(3+m')\K^*_{2,m'+1}+2im'\z \K^*_{2,m'}\bigg].
+\end{aligned}
+\end{equation*}
+Choosing $\K_{21}=\K{2,-1}=0$ and $\Im \K_{22}=\Im \K_{2,-2}=0$, we have
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2} a_m^2\\
+&\bigg[(i\x + \y)(4S_{2,-1}\K^*_{2,-2}+2S_{21}\K^*_{20})\\
+&+(i\x-\y)(4S_{2,1}K^*_{22}+2S_{2,-1}\K^*_{20})\\
+&+4i\z (S_{2,2}\K^*_{2,2}-S_{2,-2}\K^*_{2,-2})\bigg].
+\end{aligned}
+\end{equation*}
+Recalling the $\pm m$ relation for $\K_{lm}$, the $\bm{\hat z}$ term vanishes, and we have
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2}a_m^2\\
+&\bigg[(i\x + \y)(4S_{2,-1}\K_{22}+2S_{21}\K_{20})\\
+&+(-i\x-\y)^*(-4S_{2,-1}K_{22}-2S_{2,1}\K_{20})^*\bigg]
+\end{aligned}
+\end{equation*}
+where we have removed conjugates over $\K_{20}$ because it is real. This in turn becomes
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-2GM_M a_m^2\\
+&\Re\big[(i\x + \y)(2S_{2,-1}\K_{22}+S_{21}\K_{20})\big].
+\end{aligned}
+\end{equation*}
+Since $S$ is complex, we can expand this as follows:
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-2GM_M  a_m^2\\
+&\bigg[-\x\Im(2S_{2,-1}\K_{22}+S_{21}\K_{20})\\
+&+\y\Re(2S_{2,-1}\K_{22}+S_{21}\K_{20})\bigg].
+\end{aligned}
+\end{equation*}
+Since $\Re S_{2,-1}=-\Re S_{21}$ and $\Im S_{2,-1}=\Im S_{21}$,
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &-2GM_M a_m^2\\
+&\bigg[-\x \Im S_{21}(2\K_{22}+\K_{20})+\y \Re S_{21}(-2\K_{22}+\K_{20})\bigg].
+\end{aligned}
+\end{equation*}
+These differences can be expressed in a neater manner, because $(I_{yy}-I_{zz})/2=2\K_{22}+\K_{20}$ and $(I_{xx}-I_{zz})/2=-2\K_{22}+\K_{20}$. Thus,
+\begin{equation*}
+\begin{aligned}
+\frac{\bm \tau}{M_m} = &GM_M \sum_{m'=-2}^2 a_m^2\\
+&\bigg[\x \Im S_{21}(I_{yy}-I_{zz})+\y \Re S_{21}(I_{zz}-I_{xx})\bigg].
+\end{aligned}
+\end{equation*}
+Plugging this into the equations of motion (eq. \ref{eqn:sep-euler}),
+\begin{equation*}
+\bm{\dot \omega} = GM_M\parens{\begin{matrix}
+\parens{\frac{I_{yy}-I_{zz}}{I_{xx}}}\parens{\Im S_{21}+\omega_y\omega_z}\\
+\parens{\frac{I_{zz}-I_{xx}}{I_{yy}}}\parens{\Re S_{21}+\omega_z\omega_x}\\
+\parens{\frac{I_{zz}-I_{xx}}{I_{yy}}}\parens{\omega_x\omega_y}\\
+\end{matrix}}
+\end{equation*}
+
+$S_{21}$ and $\omega$ vary non-trivially over time, so if degeneracy were to occur, the ratios in each component would have to be degenerate for multiple combinations of $\K_{lm}$.
+This is true for the general case of torque, not just low order $l$ and $l'$.
+We may test if this is possible by letting $\K_{20}\rightarrow \alpha \K_{20}$ and $\K_{22}\rightarrow \beta \K_{22}$.
+We require that the MOI ratio in the $x$-component be preserved under this transformation by fixing $\beta$ in terms of $\alpha$.
+Only one solution is possible.
+Then require that the second ratio be conserved.
+That fixes $\alpha=1$.
+This was done in Mathematica and demonstrates that no degeneracy is present between $\K_{lm}$.
 
@@
 
-\comment{I thought about a way of subdividing the sphere. Do that?}
-
 \bibliography{../asteroid-flybys.bib}

### 2021-10-31 code/fit_resolved/random_vector.py

@@ -14,24 +14,39 @@ def vdot(a, b):
 def vnorm(a):
     return np.sqrt(np.sum([ai * ai for ai in a]))
 
+# Make an un_uniform randomizer
+def randomize_rotate_uniform_err(theta, phi, sigma):
+    return np.sqrt(np.array([
+            1/2 * np.sinh(sigma**2) * (np.cos(theta)**2 * np.cos(phi)**2 + np.sin(phi)**2) + (np.cosh(sigma**2) - 1) * np.cos(phi)**2 * np.sin(theta)**2,
+            1/2 * np.sinh(sigma**2) * (np.cos(theta)**2 * np.sin(phi)**2 + np.cos(phi)**2) + (np.cosh(sigma**2) - 1) * np.sin(phi)**2 * np.sin(theta)**2,
+            1/2 * np.sinh(sigma**2) * np.sin(theta)**2 + (np.cosh(sigma**2) - 1) * np.cos(theta)**2]))
+
 # Do the sophisticated, turning error
-def randomize_rotate(y, sigma):
+def randomize_rotate_uniform(y, sigma):
     newy = []
     yerr = []
     assert(len(y) % 3 == 0)
     for i in range(0, len(y), 3):
-        norm_squared = y[i]**2 + y[i+1]**2 + y[i+2]**2
-        errx = sigma * np.sqrt(1 - y[i]**2 / norm_squared)
-        erry = sigma * np.sqrt(1 - y[i+1]**2 / norm_squared)
-        errz = sigma * np.sqrt(1 - y[i+2]**2 / norm_squared)
-        yerr.append(errx)
-        yerr.append(erry)
-        yerr.append(errz)
-        newy.append(y[i] + errx * (1 - 2 * random.random()))
-        newy.append(y[i+1] + erry * (1 - 2 * random.random()))
-        newy.append(y[i+2] + errz * (1 - 2 * random.random()))
+        norm = np.sqrt(y[i]**2 + y[i+1]**2 + y[i+2]**2)
+        theta = np.arccos(y[i+2] / norm)
+        phi = np.arctan2(y[i+1], y[i])
+        rot_mat = np.matmul(
+            np.array([[np.cos(-theta), 0, np.sin(-theta)], [0, 1, 0], [-np.sin(-theta), 0, np.cos(-theta)]]),
+            np.array([[np.cos(-phi), -np.sin(-phi), 0], [np.sin(-phi), np.cos(-phi), 0], [0, 0, 1]])
+        )
[…]

### 2021-11-05 summaries/21-11/21-11.tex
About to make my own double class

@@
-\documentclass[aps,twocolumn,secnumarabic,balancelastpage,amsmath,amssymb,nofootinbib,floatfix]{revtex4-1}
+\documentclass[11pt]{article}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage{graphicx}      % tools for importing graphics
-%\usepackage{lgrind}        % convert program code listings to a form
-                            % includable in a LaTeX document
-%\usepackage{xcolor}        % produces boxes or entire pages with
-                            % colored backgrounds
-%\usepackage{longtable}     % helps with long table options
-%\usepackage{epsf}          % old package handles encapsulated postscript issues
-\usepackage{bm}            % special bold-math package. usge: \bm{mathsymbol}
-\usepackage{subcaption}
-%\usepackage{asymptote}     % For typesetting of mathematical illustrations
-%\usepackage{thumbpdf}
-\usepackage[colorlinks=true]{hyperref}  % this package should be added after
-                                        % all others.
-                                        % usage: \url{http://web.mit.edu/8.13}
-\usepackage{wasysym}
+\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
 
 \begin{document}
-\title{Summary for August, 2021}
-\author{Jack Dinsmore}
-\email{jtdinsmo@mit.edu}
-\date{\today}
-\affiliation{MIT Department of Physics}
-
-\newcommand{\abs}[1]{\left| #1 \right|}
-\newcommand{\parens}[1]{\left( #1 \right)}
-\newcommand{\brackets}[1]{\left[ #1 \right]}
-\newcommand{\comment}[1]{\textcolor{red}{\emph{ #1 }}}
-\newcommand{\x}{\bm{\hat x}}
-\newcommand{\y}{\bm{\hat y}}
-\newcommand{\z}{\bm{\hat z}}
-\newcommand{\J}{\mathcal{J}}
-\newcommand{\K}{\mathcal{K}}
-\newcommand{\R}{\mathcal{R}}
-
-\begin{abstract}
-    The purpose of this summary is to derive the math governing the way an asteroid reacts to a non-point source.
-It was motivated by the discovery that, under the assumption of a gravitating point source and a small asteroid, the tidal torque can be written in terms of components of the moment of inertia, which means inference is limited to the six components of the inertia matrix.
-By violating these assumptions and considering other effects (oblateness, etc.), we can break the degeneracy.
-This month I correct some old mistakes.
-\end{abstract}
+\title{Asteroid project summary}
+\author{Jack Dinsmore, Julien de Wit}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Definitions}
-Please see \href{https://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.56.5257&rep=rep1&type=pdf}{info on spherical harmonics}
-$$P_{lm}=\frac{1}{2^ll!}(1-t^2)^{m/2} \frac{d^{l+m}}{dl^{l+m}}(t^2-1)^l$$
-$$Y_{lm}(\theta, \phi) = P_{lm}(\cos\theta)e^{im\phi}$$
-$$\bar Y_{lm}(\theta, \phi) = (-1)^m \sqrt{\frac{2l+1}{4\pi}\frac{(l-m)!}{(l+m)!}} Y_{lm}(\theta, \phi)$$
-$$R_{lm}(\bm r) = (-1)^m \frac{r^l}{(l+m)!}Y_{lm}(\bm r)$$
-$$S_{lm}(\bm r) = (-1)^m \frac{(l-m)!}{r^{l+1}}Y_{lm}(\bm r)$$
-We write $Y(\bm r)=Y(\hat{\bm r})$.
-
-These definitions lead to several key facts. For $r' < r$,
-\begin{equation}
-\frac{1}{|\bm r - \bm r'|}=\sum_{lm}R_{lm}(\bm r')S^*_{lm}(\bm r).
-\label{eqn:expansion}
-\end{equation}
-We also have a translation rule:
-\begin{equation}
-S_{lm}(\bm r' - \bm r)=(-1)^l\sum_{l'm'}R^*_{l'm'}(\bm r')S_{l+l',m+m'}(\bm r)
-\label{eqn:trans}.
-\end{equation}
-Similarly, we have some gradient formulas that result in
-\begin{equation}
-\begin{aligned}
-\bm r \times \nabla R_{lm}^*=&-\frac{1}{2}[(i\x + \y)(l-m+1)R^*_{l,m-1}\\
-&+(i\x-\y)(l+m+1)R^*_{l,m+1}+2im\z R^*_{lm}].
-\end{aligned}
-\label{eqn:grad}
-\end{equation}
-Finally, we have the symmetry relations $R_{l,-m}=(-1)^mR_{lm}^*$, $S_{l,-m}=(-1)^mS_{lm}^*$.
-
-\section{Linear law of motion}
-We use Newton's law of gravity for the linear law of motion:
-\begin{equation}
-\ddot{\bm D} = \hat {\bm D} \frac{\mu}{D^2}
-\label{eqn:linear-eom}
-\end{equation}
-where $\bm D$ points from the asteroid to the planet, and $\mu$ is the reduced mass of the system.
-We assume that the asteroid mass is so much smaller than the planet's mass that the difference between $\mu$ and the mass of the planet cannot be detected.
-The initial conditions for $\bm D$ should have large magnitude of $D$ and $\dot D$ greater than the escape velocity of the system.
-
-\section{Angular law of motion}
-Recall that angular momentum satisfies $ \dot{\bm L} = \bm \tau = \frac{d}{dt}(I \bm \omega)$,
-where $I$ is the moment of inertia matrix. This equation is not easily simplified in general, but in a coordinate system fixed to the rotating body, we make use of the fact that $\dot I = 0$. Also,
-$$\dot{\bm L} = \dot{\bm L}_\text{rot} + L_x \dot{\x} + L_y \dot{\y} + L_z \dot{\z},$$
-where $\dot{\bm L}_\text{rot} = \dot L_x \x + \dot L_y \y + \dot L_z \z$. By considering $\bm\omega \parallel \z$, we see that
-$$L_x \dot{\x} + L_y \dot{\y} + L_z \dot{\z} = \bm\omega \times \bm L,$$
-and since this pattern is replicated for all axes, it must be generally true.
-Furthermore, $\dot{\bm L}_\text{rot} = \dot I_\text{rot} \bm \omega + I \dot{\bm \omega}_\text{rot}$, and since $\dot I_\text{rot} = 0$, we have
-$$\bm \tau = I \dot{\bm \omega} + \bm\omega \times \bm L.$$
-Here we have removed the rot subscript on $\dot{\bm \omega}$ because $\dot{\bm \omega} = \dot{\bm \omega}_\text{rot} + \omega \times \omega =  \dot{\bm \omega}_\text{rot}.$ Reversing to solve for $\dot{\bm \omega}$, we have
-\begin{equation}
-\dot{\bm \omega} = I^{-1}\parens{\bm \tau - \bm \omega \times (I \bm \omega)}.
-\label{eqn:euler}
-\end{equation}
-Once again, this is valid only in a frame fixed to the body. The torque $\bm \tau$ will be calculated in the next section.
-
-The initial conditions are that $\omega$ is initially parallel to the eigenvector of $I$ with the largest eigenvalue, to minimize energy. The norm and direction of $\omega$ is observed.
-
-It will turn out that our equation for $\tau$ will invoke the use of $\bm D$ in the rotating frame. To track $\bm D$ in that frame, we need $\dot{\bm D}_\text{rot}$. To find it,
-$$\dot{\bm D} = \dot{\bm D}_\text{rot} + \bm \omega \times \bm D$$
-or
-\begin{equation}
-\dot{\bm D}_\text{rot} = \bm D \times \bm \omega + \hat{\bm D}.
-\label{eqn:d-eom}
-\end{equation}
-where $\dot D$ is given by the evolution of equation \ref{eqn:linear-eom}
-
-\section{Torque}
-By definition, the differential torque on a small unit of mass $dm$ within an asteroid is $d\bm \tau = \bm r \times d\bm F$, where $\bm r$ points to $dm$ from the center of mass of the asteroid.
-In the regime where $d\bm F$ is constant, there is no tidal torque.
-But if $d\bm F$ is allowed to vary across the asteroid, we will get tidal torque as shown.
-
-The differential force is $d\bm F = -dm \nabla_{\bm R} V(\bm R)$, where
-$$V(\bm R) = -\int d^3 r' \frac{\rho_M(\bm r')}{|\bm r' - \bm R|}$$
-is the gravitational potential field of the planet, and $\bm R = \bm r - \bm D$ points from $dm$ to the center of mass of the planet.
-Also, we have $\rho_M$ as the mass distribution of the planet.
-Expanding this potential field using equation \ref{eqn:expansion}, we get
-$$V(\bm R) = -\sum_{lm}S^*_{lm}(\bm R)\int d^3 r' \rho_M(\bm r') R_{lm}(\bm r').$$
-We introduce the useful symbol
-\begin{equation}
-\J_{lm} = \frac{1}{M_M}\int d^3 r \rho_M(\bm r) a_M^{-l} R_{lm} (\bm r)
-\label{eqn:jlm-def}
-\end{equation}
-where $M_M$ is the mass of the Earth and $a_M$ is its radius. Then we have
-\begin{equation}
-V(\bm R) = -M_M\sum_{lm} a_M^{l} S^*_{lm} (\bm R) \J_{lm}.
-\label{eqn:potential}
-\end{equation}
-Incidentally, since $R_{00} = 1$, we have that $\J_{00}=1$. Choosing coordinates in which the Earth's center of mass is at the origin, we have $\J_{1m}=0$ as well.
-
-The total torque on the asteroid can therefore be written as
-\begin{equation}
-\bm \tau = GM_M \int d^3 r \rho(\bm r) \bm r \times \nabla_{\bm R} \sum_{lm} a_M^l S^*_{lm}(\bm R) \J_{lm}.
-\label{eqn:first-torque}
-\end{equation}
-Here, $\rho(\bm r)$ is now the mass density of the asteroid. Since $\nabla_{\bm R} = \nabla_{\bm r}$, we will drop the subscript henceforth.
-
-Note that the bounds of integration of equations \ref{eqn:jlm-def} and \ref{eqn:first-torque} can be chosen to be the surfaces of the bodies in question, or any surface encompassing the bodies.
-It will be useful in the future to imagine these bounds as spherically symmetrical.
-
-We expand equation \ref{eqn:first-torque} using equation \ref{eqn:trans}:
-\begin{equation*}
-\begin{aligned}
-\bm \tau = &GM_M \sum_{lm}(-1)^l a_M^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) \bm r \times \nabla R^*_{l'm'}(\bm r).
-\end{aligned}
-\end{equation*}
-Now we can move straight on to substitution equation \ref{eqn:grad}:
-\begin{equation*}
-\begin{aligned}
-\bm \tau = &-\frac{GM_M}{2}\sum_{lm}(-1)^l a_M^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) \\
-&\int d^3 r \rho(\bm r) [(i\x + \y)(l'-m'+1)R^*_{l',m'-1}(\bm r)\\
-&+(i\x-\y)(l'+m'+1)R^*_{l',m'+1}(\bm r)+2im'\z R^*_{l'm'}(\bm r)].
-\end{aligned}
-\end{equation*}
-We define the new varialble
-\begin{equation}
-\K_{lm} = m\int d^3 a_m^{-l}r \rho(\bm r) R_{lm} (\bm r),
-\label{eqn:klm-def}
-\end{equation}
-where $M_m$ is the mass of the asteroid and $a_m$ is a constant with units of length which we define later. Think of it as something like the radius of the asteroid. Note the convenient fact that
-\begin{equation}
-\begin{aligned}
-\K_{lm}^* = &M_m\int d^3 a_m^{-l}r \rho(\bm r) R_{lm}^* (\bm r) \\
-= &(-1)^mM_m\int d^3 a_m^{-l}r \rho(\bm r) R_{l,-m} (\bm r) = (-1)^mK_{l,-m}.\\
-\label{eqn:klm-def}
-\end{aligned}
-\end{equation}
-
-We can simplify the torque to
-\begin{equation}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2}\sum_{lm}(-1)^l \J_{lm}\sum_{l'm'}S_{l+l',m+m'}(\bm D) a_M^l a_m^{l'}\\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
-\label{eqn:complex-torque}
-\end{aligned}
-\end{equation}
-which evidently obeys unit analysis, since $\J_{lm}$ and $\K_{lm}$ are unit-less.
-This equation is also real, but the proof is nontrivial.
-We will instead investigate the outcomes of this equation under the simplifying assumptions that $l=m=0$ and $l'=2$.
-But first, we discuss the torque in relation to the equations of motion.
-
-\section{Moment of inertia}
-The moment of inertia matrix of an object is written as
-$$I_{xx}=\int d^3 r \rho(\bm r) (y^2 + z^2), \indent \dots$$
-$$I_{xy}=-\int d^3 r \rho(\bm r) xy, \indent \dots.$$
-Note that
-$$x^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)+2Y_{2,-2}+\frac{1}{12}Y_{22}}$$
-$$y^2=r^2\brackets{-\frac{1}{3}(Y_{20}-1)-2Y_{2,-2}-\frac{1}{12}Y_{22}}$$
-$$z^2=r^2\brackets{\frac{2}{3}Y_{20}+\frac{1}{3}}$$
-$$xz=r^2\brackets{\frac{Y_{21}}{6}-Y_{2,-1}}$$
-$$yz=r^2\brackets{\frac{Y_{21}}{6i}+\frac{Y_{2,-1}}{i}}$$
-$$xy=r^2\brackets{\frac{Y_{22}}{12i}-2\frac{Y_{2,-2}}{i}}.$$
-Then we can write the above in terms of $R_{2m}$:
-$$I_{xx}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-r^2)+2R_{2,-2}+2R_{22}$$
-$$I_{yy}=\int d^3r \rho(\bm r)-\frac{1}{3}(2R_{20}-r^2)-2R_{2,-2}-2R_{22}$$
-$$I_{zz}=\int d^3r \rho(\bm r)\frac{4}{3}R_{20}+\frac{r^2}{3}$$
-$$I_{xz}=-\int d^3r \rho(\bm r)R_{21}-R_{2,-1}$$
-$$I_{yz}=-\int d^3r \rho(\bm r)\frac{R_{21}+R_{2,-1}}{i}$$
-$$I_{xy}=-\int d^3r \rho(\bm r)2\frac{R_{22}-R_{2,-2}}{i}$$
-and therefore
-$$I_{xx}=\parens{\frac{2}{3}\K_{20}-2\K_{2,-2}-2\K_{22}+\frac{2}{3}}M_ma_m^2$$
-$$I_{yy}=\parens{\frac{2}{3}\K_{20}+2\K_{2,-2}+2\K_{22}+\frac{2}{3}}M_ma_m^2$$
-$$I_{zz}=\parens{-\frac{4}{3}\K_{20} + \frac{2}{3}}M_ma_m^2$$
-$$I_{xz}=\parens{\K_{21}-\K_{2,-1}}M_ma_m^2$$
-$$I_{yz}=\parens{\frac{\K_{21}+\K_{2,-1}}{i}}M_ma_m^2$$
-$$I_{xy}=\parens{-2\frac{\K_{22}-\K_{2,-2}}{i}}M_ma_m^2.$$
-Here, we have judiciously defined $a_m$ so that the above equations are true. That definition is
-\begin{equation}
-a_m^2 = \brackets{\int d^3 r \rho(\bm r) r^2}\brackets{\int d^3 r \rho(\bm r)}^{-1}
-\label{eqn:am}
-\end{equation}
-and it is something like the radius of the asteroid. If the asteroid were a sphere of radius $R$, we would have $a_m = R\sqrt{3/5}$
-
-Thus, the moment of inertia is determined entirely by $\K_{lm}$
-
-\section{Computing torque}
-Note that the $S$ present in equation \ref{eqn:complex-torque} forces $l$ and $l'$ to be low in the dominant terms.
-However, $l'=0$ contributes nothing to torque, nor does $l'=1$ due to the fact that $\K_{1m}=0$, which is caused by $\K_{lm}$ being centered on the center of mass of the asteroid.
-Therefore, $l'=2$ is the minimum value, and the dominant torque term is proportional to $D^{-3}$.
-
-Note that $\K_{lm}$ are constants, since we are using coordinates fixed to the body.
-Our derivation requires that we use the same coordinates for $\J_{lm}$, which are therefore not constant.
-We can find their values at any point in the orbit using the \href{https://en.wikipedia.org/wiki/Wigner_D-matrix#Relation_to_spherical_harmonics_and_Legendre_polynomials}{Wigner-$D$ matrices}, which rotate spherical harmonics according to
-$$Y_{lm}(\bm r') = \sum_{m'=-l}^l\sqrt{\frac{(l+m)!}{(l-m)!}\frac{(l-m')!}{(l+m')!}}\parens{D^l_{mm'}(\R}^*Y_{lm'}(\bm r),$$
-where $\R$ indicates a rotation, and $\bm r' = \R \bm r$. Generally, $\R$ is represented by Euler angles.
-
-Let $\R$ rotate from the body-fixed axes to some inertial coordinate system.
-We choose this coordinate system so that the orbit of the asteroid lies in the $xz$-plane, but the exact orientation of the axes is left to the reader.
-The constants $\J_{lm}$ are then fixed in this frame at $\J_{lm}^0$.
-Then we must rotate both the $\J_{lm}$ in equation \ref{eqn:complex-torque} according to
-\begin{equation*}
-\begin{aligned}
-\J^\text{rot}_{lm} =&\sum_{m'=-l}^l\sqrt{\frac{(l-m')!}{(l-m)!}\frac{(l+m')!}{(l+m)!}}\parens{D^l_{mm'}(t)}^*\J_{lm'}.
-\end{aligned}
-\end{equation*}
-Thus, equation \ref{eqn:complex-torque} becomes
-\begin{equation*}
-\begin{aligned}
-\bm \tau = &-\frac{1}{2}\sum_{lm}(-1)^l\sum_{l'm'}S_{l+l',m+m'}(\bm D)\\
-&\brackets{\sum_{m''=-l}^l\sqrt{\frac{(l-m'')!}{(l-m)!}\frac{(l+m'')!}{(l+m)!}}\parens{D^l_{mm''}(\R)}^*\J_{lm''}^0}\\
-&\bigg[(i\x + \y)(l'-m'+1)\K^*_{l',m'-1}\\
-&+(i\x-\y)(l'+m'+1)\K^*_{l',m'+1}+2im'\z \K^*_{l'm'}\bigg].
-\label{eqn:torque-final}
-\end{aligned}
-\end{equation*}
-The only value left unfixed is the body-fixed coordinate system.
-We fix it to the principal axes of the asteroid, so that $\z$ aligns with the axis with maximal inertia.
-Then $\bm\omega = \omega \z$ initially in the body-fixed system.
-Now everything is determined; the choice of $\J_{lm}$ determines position and velocity $\bm D$ and $\bm v$ which evolve via the linear equation of motion, equation \ref{eqn:linear-eom}.
-The body's initial orientation--unknown when the spin axis has not been resolved and known up to a roll parameter when the spin axis is resolved---fixes the initial orientation, represented by $\R$.
-The orientation and angular velocity $\omega$ then evolve according to equation \ref{eqn:euler}, which references the torque displayed in equation \ref{eqn:torque-final}.
-
-In practice, we represent the orientation as a quaternion $\bm q$ and evolve it according to the quaternion equation of motion
-$$\dot {\bm q} = \frac{1}{2}\bm \omega \bm q$$
-and we extract Euler angles from it to get $\R$, and a matrix from it to convert $\bm D$. from the inertial axes to the body-fixed system.
-
-A benefit to requiring that the body-fixed system be aligned with principal axes is that, in this regime, equation \ref{eqn:euler} simplifies to
-\begin{equation}
-\begin{aligned}
-\dot \omega_x = I_x^{-1}\parens{\tau_x + (I_y - I_z)\omega_y \omega_z}\\
-\dot \omega_y = I_y^{-1}\parens{\tau_y + (I_z - I_x)\omega_z \omega_x}\\
-\dot \omega_z = I_z^{-1}\parens{\tau_z + (I_x - I_y)\omega_x \omega_y}\\
-\label{eqn:sep-euler}
-\end{aligned}
-\end{equation}
-and the inertial matrix is diagonal, meaning that
-$$\K_{21} = \K_{2,-1}=\Im K_{22} = \Im K_{2,-2}= 0.$$
-The only free parameters with $l\leq 2$ are $\K_{00}$, $\K_{20}$, and $\Re \K_{22}$, which is three total.
-
-Equation \ref{eqn:sep-euler} indicates that the mass of the asteroid $M_m$ factors out of all the physics of the simulation.
-Both the inertia and the torque are directly proportional to $M_m$, and they always appear in ratios.
-So the mass of the asteroid cannot be computed from tidal torque observation.
-
-Furthermore, unless $\K_{l>2}$ are regressed for, $a_m$ cannot be determined either since it cancels out of the angular part of equation \ref{eqn:sep-euler}, and out of the torque part except when $\K_{l>2}$ terms are introduced.
-
-\section{First order torque}
-I want to reduce equation \ref{eqn:complex-torque} to a real form for $l=m=0$, $l'=2$.
-After this, I will demonstrate that the equation of motion is non-degenerate in $\K_{lm}$.
-Thus, $\K_{lm}$ and the initial position $\theta_0$ can be fitted to data without fear of degeneracy.
-Unfortunately, the radius $a_m$ cannot be fitted because scaling up the radius is equivalent to scaling up $K_{l>2}$.
-However, it can be guessed, and then $K_{l}$ fitted without harm.
-Then it can be later chosen such that $K_l$ have desired properties: that they decay or remain of equivalent size with larger $l$, for instance.
-
-Now for the reduction. Removing the sums and remembering that $\J_{00}=1$, we get
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2} \sum_{m'=-2}^2 S_{2,m'}a_m^2\\
-&\bigg[(i\x + \y)(3-m')\K^*_{l',m'-1}\\
-&+(i\x-\y)(3+m')\K^*_{2,m'+1}+2im'\z \K^*_{2,m'}\bigg].
-\end{aligned}
-\end{equation*}
-Choosing $\K_{21}=\K{2,-1}=0$ and $\Im \K_{22}=\Im \K_{2,-2}=0$, we have
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2} a_m^2\\
-&\bigg[(i\x + \y)(4S_{2,-1}\K^*_{2,-2}+2S_{21}\K^*_{20})\\
-&+(i\x-\y)(4S_{2,1}K^*_{22}+2S_{2,-1}\K^*_{20})\\
-&+4i\z (S_{2,2}\K^*_{2,2}-S_{2,-2}\K^*_{2,-2})\bigg].
-\end{aligned}
-\end{equation*}
-Recalling the $\pm m$ relation for $\K_{lm}$, the $\bm{\hat z}$ term vanishes, and we have
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-\frac{GM_M}{2}a_m^2\\
-&\bigg[(i\x + \y)(4S_{2,-1}\K_{22}+2S_{21}\K_{20})\\
-&+(-i\x-\y)^*(-4S_{2,-1}K_{22}-2S_{2,1}\K_{20})^*\bigg]
-\end{aligned}
-\end{equation*}
-where we have removed conjugates over $\K_{20}$ because it is real. This in turn becomes
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-2GM_M a_m^2\\
-&\Re\big[(i\x + \y)(2S_{2,-1}\K_{22}+S_{21}\K_{20})\big].
-\end{aligned}
-\end{equation*}
-Since $S$ is complex, we can expand this as follows:
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-2GM_M  a_m^2\\
-&\bigg[-\x\Im(2S_{2,-1}\K_{22}+S_{21}\K_{20})\\
-&+\y\Re(2S_{2,-1}\K_{22}+S_{21}\K_{20})\bigg].
-\end{aligned}
-\end{equation*}
-Since $\Re S_{2,-1}=-\Re S_{21}$ and $\Im S_{2,-1}=\Im S_{21}$,
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &-2GM_M a_m^2\\
-&\bigg[-\x \Im S_{21}(2\K_{22}+\K_{20})+\y \Re S_{21}(-2\K_{22}+\K_{20})\bigg].
-\end{aligned}
-\end{equation*}
-These differences can be expressed in a neater manner, because $(I_{yy}-I_{zz})/2=2\K_{22}+\K_{20}$ and $(I_{xx}-I_{zz})/2=-2\K_{22}+\K_{20}$. Thus,
-\begin{equation*}
-\begin{aligned}
-\frac{\bm \tau}{M_m} = &GM_M \sum_{m'=-2}^2 a_m^2\\
-&\bigg[\x \Im S_{21}(I_{yy}-I_{zz})+\y \Re S_{21}(I_{zz}-I_{xx})\bigg].
-\end{aligned}
-\end{equation*}
-Plugging this into the equations of motion (eq. \ref{eqn:sep-euler}),
-\begin{equation*}
-\bm{\dot \omega} = GM_M\parens{\begin{matrix}
-\parens{\frac{I_{yy}-I_{zz}}{I_{xx}}}\parens{\Im S_{21}+\omega_y\omega_z}\\
-\parens{\frac{I_{zz}-I_{xx}}{I_{yy}}}\parens{\Re S_{21}+\omega_z\omega_x}\\
-\parens{\frac{I_{zz}-I_{xx}}{I_{yy}}}\parens{\omega_x\omega_y}\\
-\end{matrix}}
-\end{equation*}
-
-$S_{21}$ and $\omega$ vary non-trivially over time, so if degeneracy were to occur, the ratios in each component would have to be degenerate for multiple combinations of $\K_{lm}$.
-This is true for the general case of torque, not just low order $l$ and $l'$.
-We may test if this is possible by letting $\K_{20}\rightarrow \alpha \K_{20}$ and $\K_{22}\rightarrow \beta \K_{22}$.
-We require that the MOI ratio in the $x$-component be preserved under this transformation by fixing $\beta$ in terms of $\alpha$.
-Only one solution is possible.
-Then require that the second ratio be conserved.
-That fixes $\alpha=1$.
-This was done in Mathematica and demonstrates that no degeneracy is present between $\K_{lm}$.
-
-\section{Evolution of Euler Angles}
-The Wigner-$D$ matrices are commonly expressed in terms of the Euler angles, so we will use these to track the evolution of the body.
-Let us use $z-y-z$ Euler angles, or $\bm E = (\alpha, \beta, \gamma)$, with
-\begin{equation}
-\R = R_z(\alpha) R_y(\beta) R_z(\gamma)
-\label{eqn:euler-angle-rotation}
-\end{equation}
-where $R_z$ and $R_y$ represent right-handed rotations around the $\z$ and $\y$ axes respectively.
-These angles control the orientation of the asteroid, so we need an equation of motion to describe them.
-
-By definition of angular velocity, we know $\frac{d}{dt}(\R \bm v) = \bm \omega \times \bm v,$ where $\bm v$ is any constant vector, and therefore $\dot \R \bm v = \bm \omega \times \bm v,$.
-Let $\omega_{\times}$ be the skew-symmetric matrix for $\omega$, such that $\omega_{\times} \bm v = \bm\omega \times \bm v$.
-Then $\dot \R \bm v = \omega_\times \bm v$.
-Since this is true for all $\bm v$, we see that $\dot \R = \omega_\times$, or
-$$\frac{d}{dt}\parens{R_z(\alpha)R_y(\beta)R_z(\gamma)} = \parens{\begin{matrix}
-0 & -\omega_z & \omega_y \\
-\omega_z & 0 & -\omega_x \\
--\omega_y & \omega_x & 0
- \end{matrix}}.$$
- This is
- $$\dot \alpha \dot R_z(\alpha)R_y(\beta)R_z(\gamma) + \dot \beta R_z(\alpha)\dot R_y(\beta)R_z(\gamma) + \dot \gamma R_z(\alpha)R_y(\beta)\dot R_z(\gamma) = \parens{\begin{matrix}
- 0 & -\omega_z & \omega_y \\
- \omega_z & 0 & -\omega_x \\
- -\omega_y & \omega_x & 0
-  \end{matrix}}.$$
-  This looks hard, so instead, I suggest using the old Quaternion strategy.
-
-\section{Shape model}
-When asteroid density is allowed to vary, there is not a direct connection between asteroid shape and $\K_{lm}$, because $\K_{lm}$ has two dimensions whereas shape parameters should have three: one for $\theta$, one for $\phi$, and one for $r$.
-This argument is far from rigorous and probably incorrect, but it poses a difficult problem to overcome.
-
-We could establish shape coordinates $C_{lmn}$ and allow $\K_{lm}$ to define a combination of $C_{lmn}$.
-This is made difficult, however, since there is no basis of functions orthogonal to $r^n$ for all $n \in \mathbb{N}$ over $\mathbb{R}$.
-The basis exists for $n < N$ for some $N$, and can be written in terms of the Legendre polynomials.
-But as $N\rightarrow\infty$, the basis functions get very squigally and they diverge in the limit.
-So, the combination would be more complicated than some kind of orthonormal basis.
-
-\subsection{Unfitted density}
-Suppose we don't want to deal with density distribution, as a start. Then there is a good shape model available to us. Let
-\begin{equation}
-    \rho(\bm r) = \sum_{lm} Y_{lm}^* \rho_{lm} \begin{cases}
-        1 & r < \R_{lm}\\
-        0 & \text{else}
-    \end{cases}.
-\end{equation}
-with $\rho_{lm} \in \mathbb{C}$, $\R_{lm} \in \mathbb{R}$. Then equation \ref{eqn:klm-def} becomes
-\begin{equation*}
-    \K_{lm} = \int r^2 dr \int d\Omega \sum_{l'm'} Y_{l'm'}^* R_{lm}(\bm r) \begin{cases}
-        \rho_{lm} & r < \R_{lm}\\
-        0 & \text{else}
-    \end{cases}.
-\end{equation*}
-Recall that $R_{lm}(\bm r) \propto Y_{lm}(\bm r)$, and
-$$\int d\Omega Y_{lm}Y^*_{l'm'} = \delta_{ll'}\delta_{mm'} \frac{4\pi (l+m)!}{(2l+1)(l-m)!}$$
-so
-\begin{equation*}
-    \K_{lm} = \frac{4\pi (-1)^m }{(2l+1)(l-m)!} \int r^{2+l} dr \begin{cases}
-        \rho_{lm} & r < \R_{lm}\\
-        0 & \text{else}
-    \end{cases}.
-\end{equation*}
-This in turn is
-\begin{equation*}
-    \K_{lm} = \parens{\frac{4\pi (-1)^m \rho_{lm}}{(2l+1)(l-m)!}} \parens{\frac{\R_{lm}^{3+l}}{3+l}}
-\end{equation*}
-Thus, there are three parameters $\rho_{lm}$ and $\R_{lm}$ to match with two parameters $\K_{lm}$ (counting complex numbers as two parameters), and the problem is nearly determined.
-Setting $\rho_{lm}$ independentently will cause it to be entirely determined.
-
-It is not at all clear that this setup will give us a good asteroid model, however.
-If all $\rho_{lm}$ were positive in some sense (they are complex after all), then the center would be denser than the edges.
-It would be better to have some holistic model without these sharp edges, but those will not integrate as well.
-
-\bibliography{../asteroid-flybys.bib}
 \end{document}

### 2021-11-09 summaries/21-11/21-11.tex
Updated paper

@@
 \usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
+\usepackage{bm}
+\usepackage{amsmath}
+\usepackage{tikz}
+\usepackage{xcolor}
+\usepackage{bbold}
 
@@
 
+\newcommand{\unit}[1]{\hat{\mathbf{#1}}}
+\newcommand{\parens}[1]{\left( #1 \right)}
+\newcommand{\brackets}[1]{\left[ #1 \right]}
+\newcommand{\jtd}[1]{{\color{red}\textit{#1}}}
+\usetikzlibrary{arrows.meta}
+
 \maketitle
 
+\section{Introduction}
+
+\section{Asteroid Model}
+In an effort to make a general asteroid model, we will consider the entire effect of the tidal torque applied to an asteroid from a planet, rather than solving for the first order perturbation.
+To better understand the effect, we will not model perturbing effects from other bodies such as the Sun or other planets.
+However, nearby bodies, such as moons or rings, are considered in a later section.
+We will also model the asteroid as a rigid body, whose density distribution is fixed throughout the flyby.
+
+Most asteroids are observed to have attained their minimum energy rotation state, so we will also assume that the asteroid's initial state aligns its rotational velocity parallel to the principal axis with maximal moment of inertia.
+
+\subsection{Coordinates}
+\label{sec:coordinates}
+We will make use of two frames of reference to model this system.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$.
+As the name suggests, these axes are inertial, with $\unit{X}$ pointing to the asteroid pericenter and $\unit{Z}$ pointing parallel to the orbit angular momentum.
+The origin of this frame is set to the center of mass of the central body.
+We will assume that the mass distribution of the central body is known in this inertial frame.
+
+Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
+This frame is fixed with respect to the body's principle axes and rotates with the body, with its origin at the body's center of mass.
+We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI, and $\unit{x}$ to have minimal MOI.
+
+We define a rotation matrix $M$ such that $M\bm{r} = \bm{R}$, where $\bm{r}$ is in the body-fixed frame and $\bm{R}$ is in the inertial frame.
+We write this matrix in terms of the $z-y-z$ Euler angles, named $\alpha$, $\beta$, and $\gamma$, defined in figure \ref{fig:euler-angles}.
+These Euler angles, together with the position and momentum of the asteroid, are our dynamical variables.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit x$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (2, -3) node[anchor=west] {$\unit y$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
+
+\draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
+
+\draw[-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
+
+\draw (0.5, -0.75) arc (290:310:1.5);
+\draw (0.9, -0.9) node[anchor=center] {$\alpha$};
+
+\draw (0, 1) arc (90:123.7:1);
+\draw (-0.4, 1.2) node[anchor=center] {$\beta$};
+
+\draw (0.95, -0.5) arc (320:361:1);
+\draw (1.4, -0.25) node[anchor=center] {$\gamma$};
+
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0) node[anchor=west] {$\unit Y$};
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
+
+\end{tikzpicture}
+\caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid. Orientation is expressed as a rotation from the body-fixed axes to the inertial axes.}
+\label{fig:euler-angles}
+\end{figure}
+
+\subsection{Potential energy}
+We start by expressing the gravitational potential energy of the system in its most general form:
+\begin{equation}
+V = -G\int_\mathcal{A} d^3 r' \rho_m(\bm r')\int_\mathcal{P} d^3 r \rho_M(\bm r) \frac{1}{|\bm{r}-\bm{r'}|}.
+\label{eqn:first-pe}
+\end{equation}
+This integral is computed in the inertial frame.
+Here, $\bm{\omega}$ is the rotational velocity of the asteroid and $I$ is the inertia tensor, both in the body fixed frame.
+We also use the asteroid density $\rho_m$ and the central body density $\rho_M$.
+The symbol $\mathcal{A}$ denotes the volume of the asteroid and $\mathcal{P}$ denotes the volume of the central body.
+To reduce equation \ref{eqn:first-pe}, we define the unnormalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
+The regular and irregular spherical harmonics are then defined as
+\begin{equation}
+S_{\ell m}(\bm r) = (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \qquad R_{\ell m} (\bm r) = (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
+\end{equation}
+
+Assume that we can construct a sphere, centered at the center of mass of the central body, so that $\rho_M = 0$ outside the sphere and $\rho_m = 0$ inside the sphere.
+Then $r' > r$ in equation \ref{eqn:first-pe}, and Ref.~\cite{Gelderen1998TheSO} gives the identity
+\begin{equation}
+\frac{1}{|\bm r - \bm r'|} = \sum_{\ell, m} R_{\ell m}(\bm r) S_{\ell m}^*(\bm r'),
+\label{eqn:1-over-r-expansion}
+\end{equation}
+where the sum is shorthand for $\sum_{\ell, m} = \sum_{\ell = 0}^\infty \sum_{m=-\ell}^\ell$.
+
+Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid.
+Then we may write $ \bm r' = \bm D + \bm u$, and Ref.~\cite{Gelderen1998TheSO} gives
+\begin{equation}
+S_{\ell m}(\bm r') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm u)S_{\ell+\ell', m + m'} (\bm D).
+\end{equation}
+
+Let us define complex, unitless constants
+\begin{equation}
+J_{\ell m} = \int_\mathcal{P} d^3 r \rho_M(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_M a_M^\ell}
+\qquad
+K_{\ell m} = \int_\mathcal{P} d^3 r \rho_m(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_m a_m^\ell}
+\label{eqn:jlm}
+\end{equation}
+where the integrals are taken in the inertial and the body-fixed frames respectively.
+The symmetry relations of $R_{\ell m}$ guarantee $J_{\ell m} = (-1)^m J_{\ell, -m}$ and similarly for $K_{\ell m}$.
+We have chosen $\mu_M$, $\mu_m$ to be the masses of the central body and asteroid respectively, and $a_M$ and $a_m$ to be scale lengths of both bodies (defined more precisely later).
+Then, by rotating $K_{\ell m}$ from the body-fixed axis orientation to the inertial axis orientation, we may use $J_{\ell m}$ and $K_{\ell m}$ to simplify the potential energy.
+Rotations of the spherical harmonics are given by the Wigner-D matrices, via the formula
+\begin{equation}
+Y_{\ell m}(M\bm r) = \sum_{m'=-\ell}^\ell \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm r).
+\end{equation}
+The corrolary of this formula for the regular solid spherical harmonic is
+\begin{equation}
+R_{\ell m} (M \bm r) = \sum_{m'=-\ell}^\ell (-1)^{m+m'} \frac{(\ell + m')!}{(\ell + m)!}\mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\bm r)
+\end{equation}
+where $\mathcal{D}^\ell_{mm'}$ are the Wigner-D matrix elements.
+In practice, these are computed from the Euler angles corresponding to the rotation $M$, which we specified in section \ref{sec:coordinates} are $z-y-z$ Euler angles.
+With this choice of axes, the Wigner-D matrix elements are real with matrix elements given by
+\begin{equation}
+\begin{aligned}
+d^\ell_{mm'}(\beta) = &\sqrt{(\ell+m)!(\ell-m)!(\ell+m')!(\ell-m')!}\\
+& \sum_{s=s_\text{min}}^{s_\text{max}} \brackets{\frac{(-1)^{m-m'+s}\parens{\cos\frac{\beta}{2}}^{2\ell + m' - m - 2s}\parens{\sin \frac{\beta}{2}}^{m-m'+2s}}{(\ell+m'-s)!(\ell-m-s)!(m-m'+s)!s!}}
+\end{aligned}
+\label{eqn:wigner-d-elements}
+\end{equation}
+where $s_\text{min} = \max(0, m'-m)$ and $s_\text{max} = \min(\ell+m', \ell-m)$,
+and $\mathcal{D}^\ell_{mm'}(\alpha, \beta, \gamma) = d^j_{mm'}e^{-im\alpha} e^{-im'\gamma}$. For neatness, we define the unitless constants
+\begin{equation}
+C_{\ell \ell' m m' m''}(\alpha, \beta, \gamma, t) = D(t)(-1)^{\ell'+m'+m''} S^*_{\ell+\ell', m + m'} (\bm D (t)) a_M^\ell a_m^{\ell'} \frac{(\ell' + m'')!}{(\ell' + m')!} \mathcal{D}(\bm q)^\ell_{m'm''}(M)^*
+\label{eqn:c}
+\end{equation}
+where $\bm D(t)$ is purely dependent on time because the orbital path of the asteroid is assumed to be Keplerian.
+Then, combining equations \ref{eqn:1-over-r-expansion} through \ref{eqn:wigner-d-elements}, we get a potential energy of
+\begin{equation}
+V = -\frac{G \mu_M \mu_m}{D(t)}\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\alpha, \beta, \gamma, t) J_{\ell, m} K_{\ell' m''}.
+\label{eqn:pe}
+\end{equation}
+
+\subsection{Kinetic energy}
+The inertia tensor of the asteroid is expressed as a matrix $I$. Written in terms of spherical harmonics in the body-fixed frame, we have
+\begin{equation}
+\begin{aligned}
+I = &\int_\mathcal{A} d^3 r\rho_m(\bm r) \parens{\begin{matrix}
+y^2 + z^2 & -xy & -xz \\
+-xy & x^2 + z^2 & -xz \\
+-xz & -yz & x^2 + y^2 \\
+\end{matrix}}\\
+= &\frac{2}{3}\mu_m a_m^2\parens{\begin{matrix}
+K_{20}-3K_{2,-2}-3K_{22}+1 & 3i \parens{K_{22}-K_{2,-2}} & \frac{3}{2}\parens{K_{21}-K_{2,-1}}\\
+3i \parens{K_{22}-K_{2,-2}} & K_{20}+3K_{2,-2}+3K_{22}+1 & -\frac{3}{2}i\parens{K_{21}-K_{2,-1}}\\
+\frac{3}{2}\parens{K_{21}-K_{2,-1}} & -\frac{3}{2}i\parens{K_{21}-K_{2,-1}} & -2K_{20}+1\\
+\end{matrix}}
+\end{aligned}
+\label{eqn:moi}
+\end{equation}
+where we have defined, for neatness,
+\begin{equation}
+a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\bm r) r^2.
+\label{eqn:am}
+\end{equation}
+With this definition of $a_m$, and an arbitrary definition of $a_M$ which may be taken to be similar to equation \ref{eqn:am} or a more convenient unit such as the central body radius, the parameters $J_{\ell m}$ and $K_{\ell m}$ of equation \ref{eqn:jlm} are completely defined.
+Note that $a_m$ is similar to the radius of the asteroid; if the asteroid is a sphere of uniform density and radius $r$, then $a_m = r\sqrt{3/5}$.
+
+Henceforth, we define the body-fixed axis to be coincident with the principal axes of the asteroids, so that the off-diagonal components of $I$ are zero.
+
+To calculate the kinetic energy, we write the angular velocity in the body-fixed frame in terms of the Euler angles:
+\begin{equation}
+\bm \omega_{xyz} = \parens{\begin{matrix}
+0 & -\sin \alpha & \sin \beta \cos \alpha \\
+0 & \cos \alpha & \sin \beta \sin \alpha \\
+1 & 0 & \cos \beta
+\end{matrix}}
+\parens{\begin{matrix}
+\dot \alpha\\
+\dot \beta \\
+\dot \gamma
+\end{matrix}}.
+\label{eqn:ang-vel}
+\end{equation}
+The rotational kinetic energy is then
+\begin{equation}
+K = \frac{1}{2} \bm\omega^T I \bm \omega
+\label{eqn:ke}
+\end{equation}
+where $\bm \omega$ and $I$ are both given in the body-fixed frame.
+
+\subsection{Hamiltonian and Equations of motion}
+As a simplifying assumption, we will not model the effect of the central body's non-sphericity on the asteroid orbit.
+This effect has been studied in much detail and is small.
+We therefore separate the position dynamical variables from the angular variables and derive the standard equations of motion for asteroid position:
+\begin{equation}
+\dot{\bm{v}} = -\frac{GM}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
+\end{equation}
+The position variables will no longer be discussed.
+
+The Lagrangian for the rotating part of the system is $L=T-V$, with kinetic and potential energy given by equations \ref{eqn:ke} and \ref{eqn:pe} respectively.
+Defining $\bm q = \parens{\alpha, \beta, \gamma}^T$, we can write equation \ref{eqn:ang-vel} as $\bm \omega_{xyz} = A\bm {\dot q}$, in which case
+\begin{equation}
+L = \frac{1}{2}\bm {\dot q}^T A^T I A \bm {\dot q} - V_0\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\bm q, t) J_{\ell, m} K_{\ell' m''}.
+\end{equation}
+where $V_0= -G \mu_M \mu_m / D(t)$ is the Newtonian potential energy of point masses $\mu_M$ and $\mu_m$. This corresponds to a Hamiltonian of
+\begin{equation}
+H = \frac{1}{2}\bm p^T (A^{-1}(\bm q)) I^{-1} (A^{-1}(\bm q))^T \bm p + V_0\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\bm q, t) J_{\ell, m} K_{\ell' m''}
+\label{eqn:hamiltonian}
+\end{equation}
+with the conjugate momenta defined as
+\begin{equation}
+\bm p = A^T I A \bm {\dot q} = A^T I \bm \omega_{xyz}
+\qquad
+\bm \omega_{xyz} = A \bm {\dot q} = I^{-1}(A^{-1})^T \bm p.
+\label{eqn:momenta}
+\end{equation}
+The inverse of $A$ is computed as
+\begin{equation}
+A^{-1} = \frac{1}{\sin{\beta}} \parens{\begin{matrix}
+-\cos\alpha \cos \beta & -\sin \alpha \cos \beta & \sin \beta \\
+-\sin \alpha \sin \beta & \cos \alpha \sin \beta & 0 \\
+\cos \alpha & \sin \alpha & 0
+\end{matrix}}.
+\label{eqn:a-inv}
+\end{equation}
+The equations of motion of the system are then a system of six first-order ordinary differential equations:
+\begin{equation}
+\bm{\dot q} = \nabla_{\bm{p}} H \qquad \bm{\dot p} = -\nabla_{\bm{q}} H.
+\label{eqn:first-eom}
+\end{equation}
+We compute these derivatives manually:
+\begin{equation}
+\bm{\dot q} = A^{-1}I^{-1}(A^{-1})^T\bm p
+\label{eqn:eom-q}
+\end{equation}
+and
+\begin{equation}
+\dot p_i = \bm p^T \frac{\partial A^{-1}}{\partial q_i} I^{-1} (A^{-1})^T \bm p -V_0 \sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} J_{\ell, m} K_{\ell' m''} \frac{\partial}{\partial q_i}C_{\ell \ell' m m' m''}(\bm q, t).
+\label{eqn:eom-p}
+\end{equation}
+Explicitly, the derivatives of $A^{-1}$ are
+\begin{equation}
+\begin{aligned}
+\frac{\partial A^{-1}}{\partial \alpha} = & \frac{1}{\sin \beta}\parens{\begin{matrix}
+\sin \alpha \cos \beta & -\cos \alpha \cos \beta & 0\\
+-\cos \alpha \sin \beta & -\sin \alpha \sin \beta & 0 \\
+-\sin \alpha & \cos \alpha & 0\\
+\end{matrix}}\\
+\frac{\partial A^{-1}}{\partial \beta} = & \frac{1}{\sin^2\beta}\parens{\begin{matrix}
+\cos \alpha & \sin \alpha & 0\\
+0 & 0 & 0\\
+-\cos\alpha \cos\beta & -\sin \alpha \cos \beta & 0\\
+\end{matrix}}\qquad
+\frac{\partial A^{-1}}{\partial \gamma} = 0.
+\end{aligned}
+\end{equation}
+The $C$ coefficients depend on $\bm q$ through the Wigner-D matrices, which obey
+\begin{equation}
+\nabla_{\bm q}\mathcal{D}^\ell_{m m'}(\bm q) = \parens{\begin{matrix}
+-im\alpha \mathcal{D}^\ell_{m m'}(\bm q)\\
+e^{-im\alpha} e^{-im'\gamma}\frac{\partial}{\partial \beta} d^j_{mm'}\\
+-im'\gamma \mathcal{D}^\ell_{m m'}(\bm q)\\
+\end{matrix}}.
+\label{eqn:wigner-d-derivatives}
+\end{equation}
+Finally, the derivative of the matrix elements $d^j_{mm'}$ are given by multiplying each term in the sum over $s$ of equation \ref{eqn:wigner-d-elements} by
+$$\frac{1}{2}\parens{(m-m'+2s) \cot \frac{\beta}{2} - (2\ell + m' - m - 2s) \tan \frac{\beta}{2}},$$
+except when $\beta = 0$ or $\pi$.
+In these cases, the derivative is zero except when $\beta=0$ and $m-m'+2s=1$, or $\beta = \pi$ and $2 \ell + m' - m - 2s=1$, in which case the derivative of the trigonometric functions is $1/2$.
+
+The dynamical variables $\bm q$, $\bm p$ can then be integrated numerically to solve for the full dynamics of the system.
+
+\subsection{Initial values}
+To solve for $\bm q$, $\bm p$ as functions of time, we need their values at some point in time.
+We study their values far from the central body before the flyby, when they are assumed to be in steady state.
+Here, the spin axis $\bm \omega$ is parallel to the body-fixed unit axis $\unit z$.
+This fixes $\beta$ and $\gamma$ while $\alpha$ is left free, expressing the initial orientation of the asteroid.
+
+For the initial conjugate momenta, we use equation \ref{eqn:momenta} and the fact that $\bm \omega_{xyz}=\omega \unit z$ at the initial position. Specifically:
+\begin{equation}
+\bm p_0 = \frac{2}{3}\mu_m a_m^2 (-2K_{20}+1) \omega \parens{\begin{matrix}1 \\0 \\ \cos \beta\end{matrix}}.
+\end{equation}
+
+\subsection{Fit parameters}
+By requiring that the $\unit x, \unit y, \unit z$ axes coincide with principal axes, we force the diagonal components of $I$ to be zero.
+Thus, we may require $K_{21}=K_{2,-1}=0$ and $\Im K_{22}=\Im K_{2,-2}=0$ with no loss of generality.
+By requiring that the body-fixed frame be located at the center of mass of the asteroid, we also require $K_{1m}=0$.
+Finally, $K_{00}=1$ follows automatically from the definition.
+Thus, $K_{20}$, $\Re K_{22}$, and $K_{\ell>2, m}$ are the only physical parameters of the asteroid density distribution, beyond $a_m$.
+
+Note from equation \ref{eqn:c} that $C_{\ell=\ell'=0}=0$.
+Since $J_{\ell=1}=K_{\ell=1} = 0$ as well, the Hamiltonian in equation \ref{eqn:hamiltonian} is proportional to $\mu_m a_m^2$.
+Factoring out this product results in a Hamiltonian independent of $\mu_m$, meaning that the asteroid dynamics are unaffected by the mass of the asteroid.
+This is expected, and it means that the density distribution of the asteroid can only be determined up to a scale factor.
+
+Also note that $C_{\ell \ell' m m' m''} \propto a_M^\ell a_m^{\ell'} / D^{\ell+\ell'}$.
+Usually, $D \gg a_M \gg a_m$, so we expect this fraction to be small.
+The nonzero term first order in this fraction in the potential energy has $\ell = 0$ and $\ell'=2$.
+To first order in the asteroid density distribution, therefore, the system is also independent of $a_m$.
+When $K_{\ell' > 2}$ terms are included, $a_m$ scales the size of the higher order terms.
+
+We require that the moment of inertia matrix be positive-definite, which bounds our asteroid parameters.
+Specifically, we have $K_{20} \leq \frac{1}{2}$, and $|K_{22}| \leq (K_{20}+1)/6$.
+We can also choose without loss of generality to let the maximum moment of inertia align with $\unit z$, so that $1-2K_{20}\geq K_{20}+1+6|K_{22}|.$ Finally, we wish to require that the density of the asteroid be everywhere positive.
+One consequence of this requirement is that the sum of any two distinct moments of inertia cannot be greater than the third, by the integral definition of moment of inertia in equation \ref{eqn:moi}.
+Three inequalities result from this, but only one is not covered by the above restrictions.
+Namely, $I_{xx} + I_{yy}\geq I_{zz} \implies K_{20} \geq -1/4$.
+The intersection of these requirements forces $K_{20}$ and $K_{22}$ to lie in the triangle defined by
+\begin{equation}
+-\frac{1}{4} \leq K_{20} \leq 0 \qquad |K_{22}| \leq -\frac{K_{20}}{2}.
+\label{eqn:parameter-bounds}
+\end{equation}
+
+We have one additional fit parameter, which is the only initial condition not fixed by the problem setup or observations.
+Namely, the initial value of the first Euler angle $\alpha_0$.
+Due to the fact that the principal axes $\unit x$ and $\unit y$ are orthogonal, Increments of $\alpha_0$ by $\pi/2$ correspond to flipping the body-fixed axes so that no physical change in the asteroid model occurs.
+We must therefore limit the range of $\alpha_0$ to width $\pi/2$.
+Arbitrarily, we choose $\alpha_0 \in [-\pi/4, \pi/4)$
+
+\section{Experiment design}
+\subsection{Simulation design}
+\label{sec:simulation}
+Given the observed orbit of an asteroid and observational data of its resolved spin over time, we built a simulation that would integrate equations \ref{eqn:eom-p} and \ref{eqn:eom-q} to generate synthetic data.
+Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:pe}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) a guess at the asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+
+Once the inputs were specified, the moments of inertia were pre-computed from $K_{\ell m}$, as was the orbital path of the satellite as a function of time.
+Equations \ref{eqn:eom-p} and \ref{eqn:eom-q} were then integrated by the fourth order Runge-Kutta method with a time step of \jtd{Insert time step}, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
+At fixed time intervals, the rotational velocity in the body-fixed frame $\bm\omega_{xyz}$ was computed via equation \ref{eqn:ang-vel} from the Euler angles and rotated into the global frame to produce synthetic data.
+
+Since the leading order of the equations of motion is \jtd{What is it?}, we begin our simulation at $t=-$ \jtd{When do we begin the simulation?} and end at $t=+$, where $t=0$ is the time at periapsis.
+
+\subsection{Fitting method}
+To analyze the degree to which asteroid density distributions can be determined from flyby rotational velocity data, we use the forward model defined in section \ref{sec:simulation} to generate synthetic data, randomize the data according to one of the observational uncertainty model defined in section \ref{sec:uncertainty-models}, then use the same forward model to fit to the data and recover parameters.
+
+After randomizing the data, we isolate a set of parameters which are likely to provide good fits.
+To do this, we minimize the $\chi^2$ value of the data given the model using the BFGS algorithm.
+Our starting points for the minimization are spaced uniformly randomly across the allowed parameter space, which is the set of parameters with the triangle described by equation \ref{eqn:parameter-bounds}.
+The other parameter bounds are $\alpha_0 \in [-\pi/4, \pi/4)$, and $|\Re K_{l>2}| \leq  1$, $|\Im K_{l>2}| \leq  1$.
+
+If the minimization is conducted over too many parameter dimensions, convergence can be slow and potentially inaugurate.
+However, the parameters $K_{\ell m}$ are naturally separated into groups by order of $\ell$, since the torque applied by successive increment to $\ell$ is suppressed by $a_m/D$.
+Thus, we fit the $\ell=2$ and $\alpha_0$ parameters first, then lock them in place and fit the $\ell=3$ parameters, etc.
+The result is a set of points in parameter space which minimize the $\chi^2$.
+
+We are interested in finding not just the optimal parameters, but the probability distributions of each fit parameter.
+To do this, we use an Affine Invariant Markov Chain Monte Carlo Ensemble Sampler (MCMC), implemented in the Python package \texttt{emcee}, to conduct the fit to data \cite{ForemanMackey2013emceeTM}.
+This fit method requires the parameter space to be populated with ``walkers,'' indicating the a guess at the true parameters of the system.
+We center these walkers on the minimizing parameters computed by the minimization of $\chi^2$, and spread out the walkers such that the number density of walkers is proportional to the likelihood ($\ln \mathcal{L} = -\chi^2$) at each point.
+This is done explicitly by computing the Hessian $\Sigma$ of the likelihood at each minimizing point $\theta_0$ and expressing the likelihood locally as a multi-dimensional Gaussian
+\begin{equation}
+\mathcal{L}(\bm \theta) \propto \text{exp}\parens{\frac{1}{2}(\bm \theta-\bm \theta_0)^T \Sigma (\bm \theta-\bm \theta_0)}.
+\end{equation}
+We may change bases into a frame in which the parameters are uncorrelated by multiplying by $D^T$, which is the matrix of eigenvectors of $\Sigma$.
+Populating the walkers in this uncorrelated space according to Gaussian standard deviations given by the eigenvalues of $\Sigma$, we can convert these walkers back to $\bm \theta$-space by multiplying by $D$.
+
+With the initial walkers distributed, we use the $\chi^2$ value as the log-likelihood to compute the posterior probability distribution of $\bm \theta$ given flat priors in the range outlined above for each parameter.
+
+\subsection{Uncertainty models}
+\label{sec:uncertainty-models}
+We model uncertainties in experimental data according to several methods, comparing them to determine the dependence of our conclusions on the sensitivity model used.
+In every case, the sensitivity model is used both to add randomness to the data set after it is generated, and to weight the $\chi^2$ statistic.
+
+\subsubsection{Nominal method}
+The most detailed uncertainty model we use, and the one we use most often, is called the ``nominal method.'' It rotates each angular velocity vector by some angle $\Theta$ drawn from a normal distribution centered on $\Theta=0$ with standard deviation $\sigma_\theta$.
+The period is assumed to be known to arbitrary precision at each cadence.
+The direction in which the velocity is rotated is chosen from a uniformly random distribution.
+$\sigma_\theta$ is a general parameter which can be tweaked to model resolution of the spin axis direction.
+
+Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\bm \omega$.
+This same rotation matrix is then used to rotate the random vector $\bm \Omega = \sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z$ to the randomized velocity vector.
+Here, $\Phi$ is a uniformly random variable in the range $[0, \pi)$.
+Specifically, we write this rotation matrix as
+\begin{equation}
+M = \parens{\begin{matrix}
+\cos \phi & -\sin \phi & 0\\
+\sin \phi & \cos \phi & 0\\
+0 & 0 & 1
+\end{matrix}}
+\parens{\begin{matrix}
+\cos \theta & 0 & \sin \theta \\
+0 & 1 & 0\\
+-\sin \theta & 0 & \cos \theta
+\end{matrix}}
+\label{eqn:rotate-uncertainty-matrix}
+\end{equation}
+where $\theta$ and $\phi$ are the spherical coordinates of the original velocity vector $\bm \omega.$
+
+Equation \ref{eqn:rotate-uncertainty-matrix} is sufficient to randomize synthetic data, but an analytical expression for the coordinates of $\bm \omega$ is required to define the $\chi^2$ value used for fitting.
+We approximate the distribution of each spin coordinate as normal, with covariance given by the covariance of the true distribution.
+Based on equation \ref{eqn:rotate-uncertainty-matrix}, the covariance matrix is
+\begin{equation}
+\text{Cov}(\omega^*_i, \omega^*_j) = \frac{1}{4 \omega^2}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
+\omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
+\omega_x \omega_y & \omega_y^2 & \omega_y \omega_z\\
+\omega_x \omega_z & \omega_y \omega_z& \omega_z^2
+\end{matrix}} +  \frac{1}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathbb{1}.
+\label{eqn:rotate-uncertainty-var}
+\end{equation}
+
+We then define the $\chi^2$ statistic to be
+\begin{equation}
+\chi^2 = \sum_{i=0} (\bm \omega_i^* - \bm \omega_i)^T\text{Cov}^{-1}(\omega^*_i, \omega^*_j)(\bm \omega_i^* - \bm \omega_i)
+\end{equation}
+where $\bm \omega_i$ is the $i$th expected spin and $\bm \omega_i^*$ is the data.
+
+\section{Results}
+
+\section{Uncertainty Testing}
+
+\section{Conclusion}
+
+\bibliographystyle{unsrt}
+\bibliography{asteroids}
+
 \end{document}

### 2021-11-11 summaries/21-11/21-11.tex
Pulled sigma data

@@
 
-\draw[-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
-\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
-\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
 
-\draw (0.5, -0.75) arc (290:310:1.5);
+\draw (0.5, -0.75) arc (290:302:2.5);
 \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
@@
 
-\draw (0.95, -0.5) arc (320:361:1);
+\draw (0.97, -0.52) arc (330:360:1.3);
 \draw (1.4, -0.25) node[anchor=center] {$\gamma$};

### 2021-11-11 code/fit_resolved/uncertainty/tester.py

@@ -3,7 +3,7 @@ import numpy as np
 from scipy.spatial.transform import Rotation as R
 
 SIGMA = 0.1
-SHAPE = 10000
+SHAPE = 1000000
 
 def randomize_rotate_uniform(vec):
     theta = np.arccos(vec[2] / np.linalg.norm(vec))
@@ -23,25 +23,29 @@ def randomize_rotate_uniform(vec):
         vecs.append(np.matmul(displace, vec))
     return np.array(vecs)
 
-def randomize_rotate_uniform_err(theta, phi, sigma):
-    return np.sqrt(np.array([
+def randomize_rotate_uniform_err(vec, sigma):
+    #Old method, with no covariance
+    '''return np.sqrt(np.array([
             1/2 * np.sinh(sigma**2) * (np.cos(theta)**2 * np.cos(phi)**2 + np.sin(phi)**2) + (np.cosh(sigma**2) - 1) * np.cos(phi)**2 * np.sin(theta)**2,
             1/2 * np.sinh(sigma**2) * (np.cos(theta)**2 * np.sin(phi)**2 + np.cos(phi)**2) + (np.cosh(sigma**2) - 1) * np.sin(phi)**2 * np.sin(theta)**2,
-            1/2 * np.sinh(sigma**2) * np.sin(theta)**2 + (np.cosh(sigma**2) - 1) * np.cos(theta)**2]))
-
+            1/2 * np.sinh(sigma**2) * np.sin(theta)**2 + (np.cosh(sigma**2) - 1) * np.cos(theta)**2]))'''
+    # New method, with covariance.
+    diag = np.linalg.norm(vec)**2/4 * (1 - np.exp(-2 * sigma**2))
+    const = 1/4 * (1 - np.exp(-sigma**2)) * (1 - 3 * np.exp(-sigma**2))
+    return np.array([
+            [diag + const * vec[0]**2, const * vec[0] * vec[1], const * vec[0] * vec[2]],
+            [const * vec[0] * vec[1], diag + const * vec[1]**2, const * vec[1] * vec[2]],
+            [const * vec[0] * vec[2], const * vec[1] * vec[2], diag + const * vec[2]**2]])
 
 def display_one(vec):
     vecs = randomize_rotate_uniform(vec).transpose()
-    theta = np.arccos(vec[2] / np.linalg.norm(vec))
-    phi = np.arctan2(vec[1], vec[0])
-    bins = np.linspace(-1, 1, 100)
[…]

### 2021-11-11 summaries/hamiltonian/21-11.tex
Moved hamiltonian summary

--- 2021-11-11 summaries/21-11/21-11.tex
@@
 \begin{equation}
-\dot{\bm{v}} = -\frac{GM}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
+\dot{\bm{v}} = -\frac{G\mu_M}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
+\label{eqn:translaton-eom}
 \end{equation}
@@
 This fixes $\beta$ and $\gamma$ while $\alpha$ is left free, expressing the initial orientation of the asteroid.
+Specifically, $\cos\beta = \omega_Z / \omega$ and $\tan\gamma = \omega_Y/\omega_X$.
 
@@
 Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:pe}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) a guess at the asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+
+The orbital parameters we use to describe the orbit are the hyperbolic excess velocity $v_\infty$ and the pericenter altitude $r_p$.
+The orbit orientation is fixed to lie in the $\unit X-\unit Y$ plane, with pericenter lying on $\hat X$.
+The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\bm r(t=0) = r_p \unit X$ and $\bm v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
 

### 2021-11-11 summaries/21-11/21-11.tex
Started writing summary

--- 2021-11-05 summaries/21-11/21-11.tex
@@
 \usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
+\usepackage{bm}
+\usepackage{amsmath}
+\usepackage{tikz}
+\usepackage{xcolor}
+\usepackage{bbold}
+
+\newcommand{\unit}[1]{\hat{\mathbf{#1}}}
+\newcommand{\parens}[1]{\left( #1 \right)}
+\newcommand{\brackets}[1]{\left[ #1 \right]}
+\newcommand{\jtd}[1]{{\color{red}\textit{#1}}}
+\usetikzlibrary{arrows.meta}
 
@@
 
+\section{Introduction}
+
+\section{Asteroid model}
+In an effort to make a general asteroid model, we will consider the entire effect of the tidal torque applied to an asteroid from a planet, rather than solving for the first order perturbation.
+To better understand the effect, we will not model perturbing effects from other bodies such as the Sun or other planets.
+However, nearby bodies, such as moons or rings, are considered in a later section.
+We will also model the asteroid as a rigid body, whose density distribution is fixed throughout the flyby.
+
+Most asteroids are observed to have attained their minimum energy rotation state, so we will also assume that the asteroid's initial state aligns its rotational velocity parallel to the principal axis with maximal moment of inertia.
+
+\subsection{Coordinates}
+\label{sec:coordinates}
+We will make use of two frames of reference to model this system.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$.
+As the name suggests, these axes are inertial, with $\unit{X}$ pointing to the asteroid pericenter and $\unit{Z}$ pointing parallel to the orbit angular momentum.
+The origin of this frame is set to the center of mass of the central body.
+We will assume that the mass distribution of the central body is known in this inertial frame.
+
+Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
+This frame is fixed with respect to the body's principle axes and rotates with the body, with its origin at the body's center of mass.
+We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI, and $\unit{x}$ to have minimal MOI.
+
+We define a rotation matrix $M$ such that $M\bm{r} = \bm{R}$, where $\bm{r}$ is in the body-fixed frame and $\bm{R}$ is in the inertial frame.
+It will be useful for us to represent this matrix in two different ways; one is with a quaternion $\bm q$, and the other is with $z-y-z$ Euler angles named $\alpha$, $\beta$, and $\gamma$.
+In particular, we define $M = R_z(\gamma) R_y(\beta) R_z(\alpha)$ where $R_i(\theta)$ is a rotation around the $i$th unit vector by $\theta$.
+
+The Euler angles are necessary for our calculations, but we do not use them as dynamical variables because they suffer from gimbal lock. Instead, we use the quaternion $\bm q$
+
+\begin{figure}
+\centering
+\begin{tikzpicture}
+\draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit x$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (2, -3) node[anchor=west] {$\unit y$};
+\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
+
+\draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
+
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
+\draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
+
+\draw (0.5, -0.75) arc (290:302:2.5);
+\draw (0.9, -0.9) node[anchor=center] {$\alpha$};
+
+\draw (0, 1) arc (90:123.7:1);
+\draw (-0.4, 1.2) node[anchor=center] {$\beta$};
+
+\draw (0.97, -0.52) arc (330:360:1.3);
+\draw (1.4, -0.25) node[anchor=center] {$\gamma$};
+
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0) node[anchor=west] {$\unit Y$};
+%\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
+
+\end{tikzpicture}
+\caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid. Orientation is expressed as a rotation from the body-fixed axes to the inertial axes.}
+\label{fig:euler-angles}
+\end{figure}
+
+\section{Experiment design}
+
+\section{Results}
+
+\section{Uncertainty testing}
+
+\section{Conclusion}
+
+\bibliographystyle{unsrt}
+\bibliography{asteroids}
+
 \end{document}

### 2021-11-12 summaries/hamiltonian/21-11.tex
resolve problem

@@
 
-To calculate the kinetic energy, we write the angular velocity in the body-fixed frame in terms of the Euler angles:
+To calculate the kinetic energy, we write the angular velocity in the inertial frame in terms of the Euler angles:
 \begin{equation}
-\bm \omega_{xyz} = \parens{\begin{matrix}
-0 & -\sin \alpha & \sin \beta \cos \alpha \\
-0 & \cos \alpha & \sin \beta \sin \alpha \\
-1 & 0 & \cos \beta
+\bm \omega_{XYZ} = \parens{\begin{matrix}
+-\sin\beta \cos \gamma & \sin \gamma & 0\\
+\sin \beta \sin \gamma & \cos \gamma & 0 \\
+\cos \beta & 0 & 1
 \end{matrix}}
@@
 \begin{equation}
-K = \frac{1}{2} \bm\omega^T I \bm \omega
+K = \frac{1}{2} \bm\omega_{XYZ}^T M I M^T \bm \omega_{XYZ}
 \label{eqn:ke}
@@
 where $\bm \omega$ and $I$ are both given in the body-fixed frame.
+
+\jtd{The below does not have the Ms here because I added them after realizing that it's invalid to write $K$ in the rotating frame. But it complicates the derivatives too much.}
 
@@
 \end{equation}
+If in fact $\omega_{xyz} = \omega \unit z + \epsilon \omega \unit x$, we would have
 

### 2021-11-12 code/sim/backend.cpp

@@ -125,10 +125,19 @@ Vector3 Asteroid::extract_spin(Vector3 angles, Vector3 momenta) {
     double sa = sin(angles[0]);
     double cb = cos(angles[1]);
     double sb = sin(angles[1]);
-    Matrix3 a_inv = 1 / sb * Matrix3({
+    double cc = cos(angles[2]);
+    double sc = sin(angles[2]);
+    /*Matrix3 a_inv = 1 / sb * Matrix3({
         -ca * cb, -sa * cb, sb,
         -sa * sb, ca * sb, 0,
-        ca, sa, 0});
+        ca, sa, 0});*/
+
+
+    const Matrix3 a_inv = 1 / sb * Matrix3({
+        -cc, sc, 0,
+        sc * sb, cc * sb, 0,
+        cc * cb, -sc * cb, 1});
+
     return inv_moi * a_inv.transpose() * momenta;
     /// Check to make sure the multiplication is done in the correct order.
 }
@@ -160,6 +169,8 @@ Matrix3 Asteroid::local_to_global(Vector3 angles) {
     const double cc = cos(angles[2]);
     const double sc = sin(angles[2]);
 
+    return Matrix3::identity();
+
     return Matrix3({cc, -sc, 0, sc, cc, 0, 0, 0, 1})
         * Matrix3({cb, 0, sb, 0, 1, 0, -sb, 0, cb})
         * Matrix3({ca, -sa, 0, sa, ca, 0, 0, 0, 1});
@@ -170,10 +181,12 @@ void Asteroid::get_derivatives(Vector3 position, const Vector3 angles, const Vec
     const double sa = sin(angles[0]);
     const double cb = cos(angles[1]);
     const double sb = sin(angles[1]);
+    const double cc = cos(angles[2]);
+    const double sc = sin(angles[2]);
     const double pos_costheta = position[2] / position.mag();
     const double pos_phi = atan2(position[1], position[0]);
     DMatGen wignerd = DMatGen(angles[0], angles[1], angles[2]);
-    const Matrix3 a_inv = 1 / sb * Matrix3({
+    /*const Matrix3 a_inv = 1 / sb * Matrix3({
         -ca * cb, -sa * cb, sb,
         -sa * sb, ca * sb, 0,
         ca, sa, 0});
@@ -185,14 +198,29 @@ void Asteroid::get_derivatives(Vector3 position, const Vector3 angles, const Vec
[…]

### 2021-11-13 summaries/21-11/21-11.tex
Finished analysis and runge-kutta

--- 2021-11-11 summaries/21-11/21-11.tex
@@
 \usepackage{bbold}
-
-\begin{document}
-\title{Asteroid project summary}
-\author{Jack Dinsmore, Julien de Wit}
+\usepackage{siunitx}
 
@@
 \newcommand{\jtd}[1]{{\color{red}\textit{#1}}}
+\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
 \usetikzlibrary{arrows.meta}
+
+\begin{document}
+\title{Asteroid project summary}
+\author{Jack Dinsmore, Julien de Wit}
 
@@
 We define a rotation matrix $M$ such that $M\bm{r} = \bm{R}$, where $\bm{r}$ is in the body-fixed frame and $\bm{R}$ is in the inertial frame.
-We write this matrix in terms of the $z-y-z$ Euler angles, named $\alpha$, $\beta$, and $\gamma$, defined in figure \ref{fig:euler-angles}.
-These Euler angles, together with the position and momentum of the asteroid, are our dynamical variables.
+It will be useful for us to represent this matrix in two different ways; one is with a normalized quaternion $\quat q$, and the other is with $z-y-z$ Euler angles named $\alpha$, $\beta$, and $\gamma$.
+In particular, we define
+\begin{equation}
+M = R_z(\alpha) R_y(\beta) R_z(\gamma)
+\label{eqn:euler-angles}
+\end{equation}
+where $R_i(\theta)$ is a rotation around the $i$th unit vector by $\theta$ (figure \ref{fig:euler-angles}).
 
@@
 
-\subsection{Potential energy}
-We start by expressing the gravitational potential energy of the system in its most general form:
+We use the quaternion $\quat q$ as our dynamical variable because Euler angles suffer from gimbal lock.
+For the sake of this paper, we write quaternions as $\quat q = r + i \bm i + j \bm j + k \bm k$, with the complex conjugate written as $\quat q^* = r - i \bm i - j \bm j - k \bm k$.
+The inverse is then $\quat q^{-1} = \quat q^* / (\quat q \quat q^*)$, and we define real and imaginary parts as $\Re \quat q = r$; $\Im \quat q = i \unit x + j \unit y + k \unit z$.
+See a description of quaternions in Ref.~\cite{2008arXiv0811.2889G}
+
+Normalized quaternions express rotations of an angle $\theta$ by $\quat q = \cos\frac{\theta}{2} + \sin\frac{\theta}{2}\quat n$ where $\quat n = 0 + n_x \bm i + n_y \bm j + n_z\bm k$.
+This rotation may be applied to any vector $\bm r$ by
 \begin{equation}
-V = -G\int_\mathcal{A} d^3 r' \rho_m(\bm r')\int_\mathcal{P} d^3 r \rho_M(\bm r) \frac{1}{|\bm{r}-\bm{r'}|}.
+\bm R = \Im \brackets{\quat q^{-1} \quat r\quat q }.
+\label{eqn:quat-rot}
+\end{equation}
+Due to the real part of $\quat q$ which does not vanish for $\theta \rightarrow 0$, quaternions do not suffer from gimbal lock.
+Using the above notation, we can give the full equation of quaternion multiplication:
+\begin{equation}
+(q_0 + \quat q) (p_0 + \quat p) = q_0 p_0 - \bm p \cdot \bm q + p_0 \bm q + q_0 \bm p + \bm q \times \bm p.
+\label{eqn:quat-mult}
+\end{equation}
+Note that quaternion multiplication is not commutative.
+
+We convert from Euler angles to quaternions by writing equation \ref{eqn:euler-angles} in terms of quaternions:
+\begin{equation}
+\quat q = \parens{\begin{matrix} \cos \frac{\alpha}{2} \\ 0\\ 0 \\\sin \frac{\alpha}{2}\end{matrix}}
+\parens{\begin{matrix} \cos \frac{\beta}{2} \\ 0 \\\sin \frac{\beta}{2}\\ 0\end{matrix}}
+\parens{\begin{matrix} \cos \frac{\gamma}{2} \\ 0\\ 0 \\\sin \frac{\gamma}{2}\end{matrix}} = \parens{\begin{matrix}
+\frac{\alpha}{2} \cos \frac{\beta}{2} \cos  \cos \frac{\gamma}{2} - \frac{\alpha}{2} \cos \frac{\beta}{2}\sin \sin \frac{\gamma}{2}\\
+\frac{\alpha}{2} \sin \frac{\beta}{2} \cos  \sin \frac{\gamma}{2} - \frac{\alpha}{2} \sin \frac{\beta}{2}\sin \cos \frac{\gamma}{2}\\
+\frac{\alpha}{2} \sin \frac{\beta}{2} \cos  \cos \frac{\gamma}{2} + \frac{\alpha}{2} \sin \frac{\beta}{2}\sin \sin \frac{\gamma}{2}\\
+\frac{\alpha}{2} \cos \frac{\beta}{2} \cos  \sin \frac{\gamma}{2} + \frac{\alpha}{2} \cos \frac{\beta}{2}\sin \cos \frac{\gamma}{2}\\
+\end{matrix}}.
+\label{eqn:euler-to-quat}
+\end{equation}
+This equation can be reversed for $\alpha$, $\beta$, $\gamma$ as follows:
+\begin{equation}
+\tan \alpha = \frac{jk - ir}{jr + ik}\qquad \cos \beta = 1 - 2(i^2 + j^2) \qquad \tan \gamma = \frac{jk + ir}{jr - ik} .
+\label{eqn:quat-to-euler}
+\end{equation}
+
+\subsection{Tidal Torque}
+We start by expressing the gravitational potential energy of the central body in its most general form:
+\begin{equation}
+V(\bm R') = -G\int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
 \label{eqn:first-pe}
@@
 This integral is computed in the inertial frame.
-Here, $\bm{\omega}$ is the rotational velocity of the asteroid and $I$ is the inertia tensor, both in the body fixed frame.
-We also use the asteroid density $\rho_m$ and the central body density $\rho_M$.
-The symbol $\mathcal{A}$ denotes the volume of the asteroid and $\mathcal{P}$ denotes the volume of the central body.
+We represent the central body density as $\rho_M$ and its volume as $\mathcal{P}$.
 To reduce equation \ref{eqn:first-pe}, we define the unnormalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
@@
 Assume that we can construct a sphere, centered at the center of mass of the central body, so that $\rho_M = 0$ outside the sphere and $\rho_m = 0$ inside the sphere.
-Then $r' > r$ in equation \ref{eqn:first-pe}, and Ref.~\cite{Gelderen1998TheSO} gives the identity
+Then $R' > R$ in equation \ref{eqn:first-pe}, and Ref.~\cite{Gelderen1998TheSO} gives the identity
 \begin{equation}
-\frac{1}{|\bm r - \bm r'|} = \sum_{\ell, m} R_{\ell m}(\bm r) S_{\ell m}^*(\bm r'),
+\frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
 \label{eqn:1-over-r-expansion}
@@
 
-Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid.
-Then we may write $ \bm r' = \bm D + \bm u$, and Ref.~\cite{Gelderen1998TheSO} gives
+Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
+Then we may write $ \bm R' = \bm D + \bm R$, and Ref.~\cite{Gelderen1998TheSO} gives
 \begin{equation}
-S_{\ell m}(\bm r') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm u)S_{\ell+\ell', m + m'} (\bm D).
+S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D).
 \end{equation}
 
-Let us define complex, unitless constants
+Define the complex, unitless constants
 \begin{equation}
-J_{\ell m} = \int_\mathcal{P} d^3 r \rho_M(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_M a_M^\ell}
+J_{\ell m} = \int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{R_{\ell m}(\bm R)}{\mu_M a_M^\ell}
 \qquad
-K_{\ell m} = \int_\mathcal{P} d^3 r \rho_m(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_m a_m^\ell}
+K_{\ell m} = \int_\mathcal{A} d^3 r \rho_m(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_m a_m^\ell}
 \label{eqn:jlm}
@@
 where the integrals are taken in the inertial and the body-fixed frames respectively.
+Here, $\rho_m$ denotes the density of the asteroid and $\mathcal{A}$ denotes its volume.
 The symmetry relations of $R_{\ell m}$ guarantee $J_{\ell m} = (-1)^m J_{\ell, -m}$ and similarly for $K_{\ell m}$.
 We have chosen $\mu_M$, $\mu_m$ to be the masses of the central body and asteroid respectively, and $a_M$ and $a_m$ to be scale lengths of both bodies (defined more precisely later).
-Then, by rotating $K_{\ell m}$ from the body-fixed axis orientation to the inertial axis orientation, we may use $J_{\ell m}$ and $K_{\ell m}$ to simplify the potential energy.
-Rotations of the spherical harmonics are given by the Wigner-D matrices, via the formula
+Then we can express the potential as
 \begin{equation}
-Y_{\ell m}(M\bm r) = \sum_{m'=-\ell}^\ell \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm r).
+V(\bm U) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}R_{\ell' m'}(\bm U)S^*_{\ell+\ell', m + m'} (\bm D)}.
+\label{eqn:pe-unrotated}
 \end{equation}
-The corrolary of this formula for the regular solid spherical harmonic is
+To make use of $K_{\ell m}$ in equation \ref{eqn:jlm}, we need to rotate $\bm U$ from the inertial frame into $\bm u$ in the body fixed frame via $\bm U = M \bm u$.
+The rotation of a spherical harmonic satisfies
 \begin{equation}
-R_{\ell m} (M \bm r) = \sum_{m'=-\ell}^\ell (-1)^{m+m'} \frac{(\ell + m')!}{(\ell + m)!}\mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\bm r)
+Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).
+\end{equation}
+where $\mathcal{D}$ are the Wigner-$D$ matrices. The corollary of this formula for the regular solid spherical harmonic is
+\begin{equation}
+R_{\ell m} (M \bm u) = \sum_{m'=-\ell}^\ell \sqrt{\frac{(\ell-m')!(\ell+m')!}{(\ell-m)!(\ell+m)!}} \mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\bm u)
+\label{eqn:rlm-rotations}
 \end{equation}
@@
 In practice, these are computed from the Euler angles corresponding to the rotation $M$, which we specified in section \ref{sec:coordinates} are $z-y-z$ Euler angles.
-With this choice of axes, the Wigner-D matrix elements are real with matrix elements given by
+With this choice of Euler angles, the Wigner-D matrix elements are real with matrix elements given by
 \begin{equation}
@@
 where $s_\text{min} = \max(0, m'-m)$ and $s_\text{max} = \min(\ell+m', \ell-m)$,
-and $\mathcal{D}^\ell_{mm'}(\alpha, \beta, \gamma) = d^j_{mm'}e^{-im\alpha} e^{-im'\gamma}$. For neatness, we define the unitless constants
+and $\mathcal{D}^\ell_{mm'}(\alpha, \beta, \gamma) = d^j_{mm'}e^{-im\alpha} e^{-im'\gamma}$.
+
+Combining equations \ref{eqn:rlm-rotations} and \ref{eqn:pe-unrotated},
 \begin{equation}
-C_{\ell \ell' m m' m''}(\alpha, \beta, \gamma, t) = D(t)(-1)^{\ell'+m'+m''} S^*_{\ell+\ell', m + m'} (\bm D (t)) a_M^\ell a_m^{\ell'} \frac{(\ell' + m'')!}{(\ell' + m')!} \mathcal{D}(\bm q)^\ell_{m'm''}(M)^*
-\label{eqn:c}
-\end{equation}
-where $\bm D(t)$ is purely dependent on time because the orbital path of the asteroid is assumed to be Keplerian.
-Then, combining equations \ref{eqn:1-over-r-expansion} through \ref{eqn:wigner-d-elements}, we get a potential energy of
-\begin{equation}
-V = -\frac{G \mu_M \mu_m}{D(t)}\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\alpha, \beta, \gamma, t) J_{\ell, m} K_{\ell' m''}.
-\label{eqn:pe}
+V(\bm u) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)}.
 \end{equation}
 
-\subsection{Kinetic energy}
+The tidal torque applied to an asteroid at a point $\bm u$ is given by $d\bm \tau(\bm u) = -\rho_m(\bm u) d^3u (\bm u \times (\nabla V_{\bm u}(\bm u)))$ in the body-fixed frame, which leaves
+\begin{equation}
+\begin{aligned}
+\bm\tau = &G\int_\mathcal{A}d^3u \rho_m(\bm u)  \bm u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)
+\right.\\
+& \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)\right].
+\end{aligned}
+\label{eqn:first-tidal-torque}
+\end{equation}
+Using the identity
+\begin{equation}
+\begin{aligned}
+\bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
+&+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)+2im\unit z R_{\ell m}(\bm u)],
+\end{aligned}
+\end{equation}
+which was derived from Ref.~\cite{Gelderen1998TheSO}'s analysis of the angular momentum operators applied to spherical harmonics, we write equation \ref{eqn:first-tidal-torque} as
+\begin{equation}
+\begin{aligned}
+\bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
+\\
+&\bigg[(i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\bigg] \Bigg].
+\label{eqn:tidal-torque}
+\end{aligned}
+\end{equation}
+This equation contains complex values, but it was numerically confirmed that $\bm \tau$ is a real-valued vector.
+
+Note that each sum in this equation is weighted by a factor of $a_M^\ell a_m^{\ell'}/D^{\ell+\ell'}$.
+Since $D \gg a_M \gg a_m$ in general, the leading order torques come from low $\ell$ and $\ell'$.
+However, $\ell'$ contributes nothing because the inner bracketed term is zero, and $K_{\ell' = 1} = 0$ if we choose the origin of the body-fixed axes to be the center of mass of the asteroid.
+The leading order of equation \ref{eqn:tidal-torque} is therefore $1/D^3$ with $\ell = 0$ and $\ell' = 2$.
+
+\subsection{Moment of Inertia}
 The inertia tensor of the asteroid is expressed as a matrix $I$. Written in terms of spherical harmonics in the body-fixed frame, we have
@@
 
-To calculate the kinetic energy, we write the angular velocity in the body-fixed frame in terms of the Euler angles:
-\begin{equation}
-\bm \omega_{xyz} = \parens{\begin{matrix}
-0 & -\sin \alpha & \sin \beta \cos \alpha \\
-0 & \cos \alpha & \sin \beta \sin \alpha \\
-1 & 0 & \cos \beta
-\end{matrix}}
-\parens{\begin{matrix}
-\dot \alpha\\
-\dot \beta \\
-\dot \gamma
-\end{matrix}}.
-\label{eqn:ang-vel}
-\end{equation}
-The rotational kinetic energy is then
-\begin{equation}
-K = \frac{1}{2} \bm\omega^T I \bm \omega
-\label{eqn:ke}
-\end{equation}
-where $\bm \omega$ and $I$ are both given in the body-fixed frame.
-
-\subsection{Hamiltonian and Equations of motion}
+\subsection{Equation of Motion}
 As a simplifying assumption, we will not model the effect of the central body's non-sphericity on the asteroid orbit.
 This effect has been studied in much detail and is small.
-We therefore separate the position dynamical variables from the angular variables and derive the standard equations of motion for asteroid position:
+We therefore separate the position dynamical variables from the angular variables and derive the standard equations of motion for asteroid position in the inertial frame:
 \begin{equation}
-\dot{\bm{v}} = -\frac{GM}{r^3}\bm{r}\qquad \dot{\bm{r}} = \bm{v}.
+\dot{\bm{V}} = -\frac{G\mu_M}{r^3}\bm{D}\qquad \dot{\bm{D}} = \bm{V}.
+\label{eqn:translaton-eom}
 \end{equation}
@@
 
-The Lagrangian for the rotating part of the system is $L=T-V$, with kinetic and potential energy given by equations \ref{eqn:ke} and \ref{eqn:pe} respectively.
-Defining $\bm q = \parens{\alpha, \beta, \gamma}^T$, we can write equation \ref{eqn:ang-vel} as $\bm \omega_{xyz} = A\bm {\dot q}$, in which case
+Let $\bm\omega$ be the rotational velocity of the asteroid in the body-fixed frame.
+We have two equations of motion for our system; one governs the evolution of $\bm \omega$ and the other governs the evolution of $\bm q$.
+Starting with the latter, consider a fixed point $\bm r$ in the body-fixed frame on a rotating asteroid.
+The corresponding point $\bm R$ in the inertial frame satisfies $\dot{\bm R} = \Im[\quat q^{-1}(\bm \omega \times \bm r )\quat q]$.
+Furthermore, we can demand that $\bm \omega \perp \bm r$ such that $\bm \omega \times \bm r = \Im[\quat \omega \quat r]$ Plugging this into equation \ref{eqn:quat-rot}, we have
+\begin{equation*}
+\dot{\quat q^{-1}} \quat r \quat q + \quat q^{-1} \quat r \dot{\quat q} = \quat q^{-1}\quat \omega \quat r \quat q.
+\end{equation*}
+Substituting $\bm r \rightarrow \bm R$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}]$,
+\begin{equation*}
+2\dot{\quat q^{-1}}\quat q\quat R = \quat q^{-1}\quat \omega \quat q \quat R.
+\end{equation*}
+Since $\bm R$ is arbitrary, this simplifies to
 \begin{equation}
-L = \frac{1}{2}\bm {\dot q}^T A^T I A \bm {\dot q} - V_0\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\bm q, t) J_{\ell, m} K_{\ell' m''}.
+\dot{\quat q} = \frac{1}{2}\quat \omega\quat q.
+\label{eqn:quat-eom}
 \end{equation}
-where $V_0= -G \mu_M \mu_m / D(t)$ is the Newtonian potential energy of point masses $\mu_M$ and $\mu_m$. This corresponds to a Hamiltonian of
-\begin{equation}
-H = \frac{1}{2}\bm p^T (A^{-1}(\bm q)) I^{-1} (A^{-1}(\bm q))^T \bm p + V_0\sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} C_{\ell \ell' m m' m''}(\bm q, t) J_{\ell, m} K_{\ell' m''}
-\label{eqn:hamiltonian}
-\end{equation}
-with the conjugate momenta defined as
-\begin{equation}
-\bm p = A^T I A \bm {\dot q} = A^T I \bm \omega_{xyz}
-\qquad
-\bm \omega_{xyz} = A \bm {\dot q} = I^{-1}(A^{-1})^T \bm p.
-\label{eqn:momenta}
-\end{equation}
-The inverse of $A$ is computed as
-\begin{equation}
-A^{-1} = \frac{1}{\sin{\beta}} \parens{\begin{matrix}
--\cos\alpha \cos \beta & -\sin \alpha \cos \beta & \sin \beta \\
--\sin \alpha \sin \beta & \cos \alpha \sin \beta & 0 \\
-\cos \alpha & \sin \alpha & 0
-\end{matrix}}.
-\label{eqn:a-inv}
-\end{equation}
-The equations of motion of the system are then a system of six first-order ordinary differential equations:
-\begin{equation}
-\bm{\dot q} = \nabla_{\bm{p}} H \qquad \bm{\dot p} = -\nabla_{\bm{q}} H.
-\label{eqn:first-eom}
-\end{equation}
-We compute these derivatives manually:
-\begin{equation}
-\bm{\dot q} = A^{-1}I^{-1}(A^{-1})^T\bm p
-\label{eqn:eom-q}
-\end{equation}
-and
-\begin{equation}
-\dot p_i = \bm p^T \frac{\partial A^{-1}}{\partial q_i} I^{-1} (A^{-1})^T \bm p -V_0 \sum_{\ell, m}\sum_{\ell', m'} \sum_{m''=-\ell'}^{\ell'} J_{\ell, m} K_{\ell' m''} \frac{\partial}{\partial q_i}C_{\ell \ell' m m' m''}(\bm q, t).
-\label{eqn:eom-p}
-\end{equation}
-Explicitly, the derivatives of $A^{-1}$ are
+
+The second equation of motion are Euler's equations of motion given our expression for tidal torque. Namely,
 \begin{equation}
 \begin{aligned}
-\frac{\partial A^{-1}}{\partial \alpha} = & \frac{1}{\sin \beta}\parens{\begin{matrix}
-\sin \alpha \cos \beta & -\cos \alpha \cos \beta & 0\\
--\cos \alpha \sin \beta & -\sin \alpha \sin \beta & 0 \\
--\sin \alpha & \cos \alpha & 0\\
-\end{matrix}}\\
-\frac{\partial A^{-1}}{\partial \beta} = & \frac{1}{\sin^2\beta}\parens{\begin{matrix}
-\cos \alpha & \sin \alpha & 0\\
-0 & 0 & 0\\
--\cos\alpha \cos\beta & -\sin \alpha \cos \beta & 0\\
-\end{matrix}}\qquad
-\frac{\partial A^{-1}}{\partial \gamma} = 0.
+I_1 \dot \omega_1 - \omega_2 \omega_3 (I_2 - I_3) &= \tau_1\\
+I_2 \dot \omega_2 - \omega_3 \omega_1 (I_3 - I_1) &= \tau_2\\
+I_3 \dot \omega_3 - \omega_1 \omega_2 (I_1 - I_2) &= \tau_3\\
 \end{aligned}
+\label{eqn:omega-eom}
 \end{equation}
-The $C$ coefficients depend on $\bm q$ through the Wigner-D matrices, which obey
-\begin{equation}
-\nabla_{\bm q}\mathcal{D}^\ell_{m m'}(\bm q) = \parens{\begin{matrix}
--im\alpha \mathcal{D}^\ell_{m m'}(\bm q)\\
-e^{-im\alpha} e^{-im'\gamma}\frac{\partial}{\partial \beta} d^j_{mm'}\\
--im'\gamma \mathcal{D}^\ell_{m m'}(\bm q)\\
-\end{matrix}}.
-\label{eqn:wigner-d-derivatives}
-\end{equation}
-Finally, the derivative of the matrix elements $d^j_{mm'}$ are given by multiplying each term in the sum over $s$ of equation \ref{eqn:wigner-d-elements} by
-$$\frac{1}{2}\parens{(m-m'+2s) \cot \frac{\beta}{2} - (2\ell + m' - m - 2s) \tan \frac{\beta}{2}},$$
-except when $\beta = 0$ or $\pi$.
-In these cases, the derivative is zero except when $\beta=0$ and $m-m'+2s=1$, or $\beta = \pi$ and $2 \ell + m' - m - 2s=1$, in which case the derivative of the trigonometric functions is $1/2$.
+The components of $\bm \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
 
-The dynamical variables $\bm q$, $\bm p$ can then be integrated numerically to solve for the full dynamics of the system.
+\subsection{Initial Values}
+We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\bm \omega \parallel \unit z$.
+The initial conditions are therefore that $\bm \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\bm \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\gamma$.
+The third Euler angle $\alpha$ represents the initial roll of the asteroid, and therefore cannot be determined from physical data.
+However, it is an initial condition of the simulation.
+Once the Euler angles are known, the quaternion is computed via equation \ref{eqn:euler-to-quat}.
 
-\subsection{Initial values}
-To solve for $\bm q$, $\bm p$ as functions of time, we need their values at some point in time.
-We study their values far from the central body before the flyby, when they are assumed to be in steady state.
-Here, the spin axis $\bm \omega$ is parallel to the body-fixed unit axis $\unit z$.
-This fixes $\beta$ and $\gamma$ while $\alpha$ is left free, expressing the initial orientation of the asteroid.
-
-For the initial conjugate momenta, we use equation \ref{eqn:momenta} and the fact that $\bm \omega_{xyz}=\omega \unit z$ at the initial position. Specifically:
-\begin{equation}
-\bm p_0 = \frac{2}{3}\mu_m a_m^2 (-2K_{20}+1) \omega \parens{\begin{matrix}1 \\0 \\ \cos \beta\end{matrix}}.
-\end{equation}
-
-\subsection{Fit parameters}
+\subsection{Fit Parameters}
 By requiring that the $\unit x, \unit y, \unit z$ axes coincide with principal axes, we force the diagonal components of $I$ to be zero.
@@
 
-Note from equation \ref{eqn:c} that $C_{\ell=\ell'=0}=0$.
-Since $J_{\ell=1}=K_{\ell=1} = 0$ as well, the Hamiltonian in equation \ref{eqn:hamiltonian} is proportional to $\mu_m a_m^2$.
-Factoring out this product results in a Hamiltonian independent of $\mu_m$, meaning that the asteroid dynamics are unaffected by the mass of the asteroid.
+As discussed before, the leading order of equation \ref{eqn:tidal-torque} is $\ell' = 2$.
+Therefore, the equation is proportional to $\mu_m a_m^2$.
+Factoring out this product results in an equation of motion independent of $\mu_m$, meaning that the asteroid dynamics are unaffected by the mass of the asteroid.
 This is expected, and it means that the density distribution of the asteroid can only be determined up to a scale factor.
 
-Also note that $C_{\ell \ell' m m' m''} \propto a_M^\ell a_m^{\ell'} / D^{\ell+\ell'}$.
-Usually, $D \gg a_M \gg a_m$, so we expect this fraction to be small.
-The nonzero term first order in this fraction in the potential energy has $\ell = 0$ and $\ell'=2$.
-To first order in the asteroid density distribution, therefore, the system is also independent of $a_m$.
+Since the coefficient of $J_{lm}K_{l'm'}$ is proportional to $a_M^\ell a_m^{\ell'} / D^{\ell+\ell'}$, to first order in the asteroid density distribution, the system is also independent of $a_m$.
 When $K_{\ell' > 2}$ terms are included, $a_m$ scales the size of the higher order terms.
@@
 
-\section{Experiment design}
-\subsection{Simulation design}
+\section{Experiment Design}
+\subsection{Simulation Design}
 \label{sec:simulation}
-Given the observed orbit of an asteroid and observational data of its resolved spin over time, we built a simulation that would integrate equations \ref{eqn:eom-p} and \ref{eqn:eom-q} to generate synthetic data.
-Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:pe}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) a guess at the asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+Given the observed orbit of an asteroid and observational data of its resolved spin over time, we built a simulation that would integrate equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} to generate synthetic data.
+Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:tidal-torque}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) a guess at the asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+
+The orbital parameters we use to describe the orbit are the hyperbolic excess velocity $v_\infty$ and the pericenter altitude $r_p$.
+The orbit orientation is fixed to lie in the $\unit X-\unit Y$ plane, with pericenter lying on $\hat X$.
+The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\bm r(t=0) = r_p \unit X$ and $\bm v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
 
 Once the inputs were specified, the moments of inertia were pre-computed from $K_{\ell m}$, as was the orbital path of the satellite as a function of time.
-Equations \ref{eqn:eom-p} and \ref{eqn:eom-q} were then integrated by the fourth order Runge-Kutta method with a time step of \jtd{Insert time step}, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
-At fixed time intervals, the rotational velocity in the body-fixed frame $\bm\omega_{xyz}$ was computed via equation \ref{eqn:ang-vel} from the Euler angles and rotated into the global frame to produce synthetic data.
+Equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} were then integrated by the fourth order Runge-Kutta fourth order method with a time step of 100 seconds, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
+This time step was observed to produce equivalent spin data to data made by lower time step.
+At fixed time intervals, the rotational velocity in the body-fixed frame $\bm\omega_{xyz}$ was converted via equation \ref{eqn:quat-rot} to the inertial frame to produce synthetic data.
 
-Since the leading order of the equations of motion is \jtd{What is it?}, we begin our simulation at $t=-$ \jtd{When do we begin the simulation?} and end at $t=+$, where $t=0$ is the time at periapsis.
+Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, we begin our simulation at $D = D f^{-1/3}$, where $f$ is a manually set parameter to control the length of the simulation.
+For all simulations done here, $f = \SI{e-3}.$ We end the simulation also at $D f^{-1/3}$ on the other side of the orbit.
 
-\subsection{Fitting method}
+\subsection{Fitting Method}
 To analyze the degree to which asteroid density distributions can be determined from flyby rotational velocity data, we use the forward model defined in section \ref{sec:simulation} to generate synthetic data, randomize the data according to one of the observational uncertainty model defined in section \ref{sec:uncertainty-models}, then use the same forward model to fit to the data and recover parameters.
@@
 
-\subsection{Uncertainty models}
+\subsection{Uncertainty Models}
 \label{sec:uncertainty-models}
@@
 
-\subsubsection{Nominal method}
+\subsubsection{Nominal Method}
 The most detailed uncertainty model we use, and the one we use most often, is called the ``nominal method.'' It rotates each angular velocity vector by some angle $\Theta$ drawn from a normal distribution centered on $\Theta=0$ with standard deviation $\sigma_\theta$.
@@
 
+\subsection{System Setup}
+We study several environments for our asteroid, including (1) a flyby of a single, spherical planet, (2) a close flyby of a ringed planet, (3) a flyby of a planet with a moon, and (4) a close flyby of a planet with a moon.
+The qualitative and quantitative differences between these flyby types are discussed below.
+
+\subsubsection{One Spherical Planet}
+The simplest setup for an asteroid flyby is a close flyby of a single, spherical body.
+We call this central body a ``planet'' because it is likely that a body massive enough to observably torque an asteroid would be a planet.
+For such a body, the only relevant physical parameter is its mass, $\mu_M$, since $J_{00} = 1$ and the other $J_{\ell m}$ parameters are zero.
+
+\subsubsection{Ringed Planet}
+Equation \ref{eqn:tidal-torque} demonstrates that parameters controlling non-sphericity in the central body ($J_{2m}$, $J_{3m}$, etc.) are damped by a factor of $(a_M/D)^\ell$, where $a_M$ can be thought to be the radius of the central body.
+Furthermore, the $J_{1m}$ terms are all zero by choosing the center of mass of the central body to be the origin of the coordinate system.
+Thus, we are interested in the extreme values of $J_{\ell \geq 2}$ and whether they have a significant effect on the observability of asteroid density distributions.
+An example of such an extreme value is the presence of a planetary ring.
+
+For a ring of inner radius $a$, outer radius $b$, and mass $\mu_r$ oriented in the $\unit X-\unit Y$ plane, the only changed $J_{\ell m}$s have $m = 0$ by rotational symmetry.
+Furthermore, $Y_{\ell, m} = 0$ on the equator for odd $m$, and $(-1)^{\ell/2} \ell!
+/ (2^\ell (\ell/2)!^2)$ otherwise.
+Thus, we have
+\begin{equation}
+J_{\ell m} = \begin{cases}
+\frac{2 \pi \sigma}{\mu_M + \pi(b^2-a^2)\sigma}\frac{(-1)^{\ell/2}}{a_M^\ell}\frac{b^{\ell+2} - a^{\ell+2}}{2^\ell (\ell/2)!^2 (\ell + 2)}
+ & \text{for}\ m = 0,\ l\ \text{even},\ l \neq 0\\
+1 & \ell = 1\\
+0 & \text{else}
+\end{cases}
+\label{eqn:ring-jlm}
+\end{equation}
+where $\mu_M$ is the mass of the planet without the ring and $\sigma_s$ is the surface density of the ring.
+
+The oblateness $\epsilon$, also called $J_2$ of a body is defined as $\epsilon = (I_z - I_x)/(\mu_M a_M^2)$, where $I_x = I_y$ (that is, $J_{22} = 0$) and $a_M$ is the true radius of the body, not the value defined in equation \ref{eqn:am}.
+Expressed in terms of $J_{\ell m}$, this is $\epsilon = -2J_{20}$.
+We can compare typical oblateness to the $J_{20}$ value from equation \ref{eqn:ring-jlm} to see which effect is more dramatic.
+
+Using data from the NASA Saturn Fact Sheet, we arrive at $J_{20}\sim \SI{e-8}{}$ from rings, but $\SI{e-4}{}$ from oblateness. So oblateness is in fact the stronger effect.
+
+\jtd{Don't actually use this section in the paper. I'm keeping it here as a math repository. Change the section to an oblate planet.}
+
+\subsection{Planet with a Moon: Distant Flyby}
+Consider a system with a moon of mass $\mu_{o}$ at constant displacement $\bm R$ from the central body.
+We assume that both the planet and the moon are spherical.
+As long as the distance from the barycenter of the planet-moon system to the asteroid $D$ always satisfies $D>r$ we are free to use the formalism developed above, absorbing the moon into $J_{\ell m}$.
+Making use of the identity \cite{Gelderen1998TheSO}
+\begin{equation}
+R_{\ell m}(\bm R + \bm R') = \sum_{\ell' = 0}^\ell \sum_{m'=-\ell'}^\ell R_{\ell' m'}(\bm R') R_{\ell-\ell', m-m'}(\bm R)
+\end{equation}
+\jtd{Is this true?}
+for $R > R'$, we have
+\begin{equation}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0) a_M^\ell}\brackets{\delta_{\ell 0}\delta_{m0}\mu_M + \int_\mathcal{P} d^3 r' \rho_o(\bm r') R_{\ell m}(\bm R + \bm r')}
+\end{equation}
+\begin{equation}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0)}\brackets{\mu_M\delta_{\ell 0}\delta_{m0} + \mu_o \frac{R_{\ell m}(\bm R)}{ a_M^\ell}}
+\end{equation}
+where the $\delta$s are Kroneker deltas.
+It is apparent that if $a_M^\ell$ remains the radius of the planet, $|J_{\ell m}| \rightarrow \infty$ as $\ell \rightarrow \infty$.
+However, since each $J_{\ell m}$ is damped by $a_M^\ell / D^\ell$ and since $R < D$ by construction, the series in equation \ref{eqn:tidal-torque} remains roughly geometric and does not blow up.
+For the sake of this calculation, we neglect motion of the moon during the flyby.
+
+For our tests, we use parameters similar to our Moon: we set $\mu_o = 0.01 \mu_M$ and $R = 60 a_M$
+
+\subsection{Planet with a Moon: Close Flyby}
+If, contrary to the previous section, we want to fly by both the moon and the planet of a binary system, we must consider the tidal torque contributions from both bodies separately.
+The formalism above cannot be extended to write one set of $J_{\ell m}$ for both the moon and planet.
+To do this, we generate two separate paths of $\bm D(t)$, one pointing from the central body to the asteroid and one pointing from the moon the asteroid.
+Both are defined in the inertial reference frames.
+Then the torque from both can be computed by equation \ref{eqn:tidal-torque} and added to get the net torque on the asteroid.
+Again, we neglect motion of the moon during the flyby.
+
 \section{Results}
+
+\section{Interpretation of the Fit Parameters}
+The physical parameters $K_{\ell m}$ resulting from a fit to flyby data, while physical, do not completely describe an asteroid.
+They can be converted into more concrete observables with the use of judicious assumptions.
+
+\subsection{Constant Density Ellipsoid}
+Suppose we assume that the density of the asteroid is constant and its shape is elliptical. Then the combination of $a_m$, $K_{20}$, and $K_{22}$ fix the asteroid's shape according to the relations
+\begin{equation}
+a = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}+12K_{22}} \qquad b = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}-12K_{22}} \qquad c = \sqrt{\frac{5}{3}}a_m\sqrt{1+4K_{20}}
+\label{eqn:ellipsoid-klm}
+\end{equation}
+which arise out of computing the moments of inertia for a constant density ellipsoid and using equation \ref{eqn:moi} to relate the result to $K_{\ell m}$ and $a_m$.
+The values $a$, $b$, and $c$, represent semi-axes aligned with $\unit x$, $\unit y$, and $\unit z$ respectively.
+
+The density of this asteroid cannot be extracted because, as is a general principle of gravitational interactions, the mass of the asteroid does not affect its dynamics.
+
+\subsection{Ellipsoid of Varying Density}
+
+\subsection{Body of Known Surface}
 

### 2021-11-13 code/sim/backend.cpp

@@ -1,82 +1,125 @@
 #include "backend.hpp"
 
+#define my_min(a, b) ((a) < (b) ? (a) : (b))
+
 const int max_k = (ASTEROIDS_MAX_K + 1) * (ASTEROIDS_MAX_K + 1);
 const int max_j = (ASTEROIDS_MAX_J + 1) * (ASTEROIDS_MAX_J + 1);
 
 Asteroid::Asteroid(const cdouble* jlms, const cdouble* klms, double asteroid_radius,
-    Vector3 spin, double initial_roll, double perigee, double speed,
-    double distance_ratio_cut) :
+    Vector3 spin, double initial_roll, double perigee, double speed, double central_mu,
+    double central_radius, double distance_ratio_cut) :
     jlms(jlms), klms(klms), asteroid_radius(asteroid_radius), distance_ratio_cut(distance_ratio_cut),
-    velocity(Vector3({0, 0, speed})), spin(spin), perigee(perigee) {
+    mu(central_mu), pericenter_pos(perigee), excess_vel(speed), initial_spin(spin),
+    initial_roll(initial_roll) {
 
-    klmcs = new cdouble[(ASTEROIDS_MAX_K + 1) * (ASTEROIDS_MAX_K + 1)];
     for (int i = 0; i < (ASTEROIDS_MAX_K + 1) * (ASTEROIDS_MAX_K + 1); i++) {
         klmcs[i] = klms[i].conj();
     }
 
     calculate_moi(initial_roll);
-    set_pos(speed);
+    calculate_poses();
 
-    #ifdef _DEBUG
-    std::cout<< "Klms: ";
-    for (int i = 0; i < (ASTEROIDS_MAX_K + 1) * (ASTEROIDS_MAX_K + 1); i++) {
-        std::cout << klms[i] << ' ';
+    #ifdef TEXT_DEBUG
+    std::cout<< "Klms: " << std::endl;
+    for (int l = 0; l <= ASTEROIDS_MAX_K; l++){
+        for (int m = -l; m<= l; m++) {
+            std::cout << l << ' ' << m << ": " << klm(l, m) << std::endl;
+        }
     }
-    std::cout << std::endl;
-
-    std::cout << "Jlms: ";
-    for (int i = 0; i < (ASTEROIDS_MAX_J + 1) * (ASTEROIDS_MAX_K + 1); i++) {
-        std::cout << jlms[i] << ' ';
+    std::cout<< "Jlms: " << std::endl;
[…]

### 2021-11-13 code/sim/wignerd.hpp

@@ -9,9 +9,6 @@
 #define min_me(a, b) ((a) > (b) ? (b) : (a))
 #define parity(a) ((a) % 2 == 0 ? (1) : (-1))
 
-using uint = unsigned int;
-
-
 
 struct cdouble {
     cdouble(double r, double i) : r(r), i(i) {}
@@ -38,16 +35,16 @@ struct cdouble {
     double i;
 };
 
-uint fact(uint i);
-uint choose(uint a, uint b);
-double gen_choose(double a, uint b);
+int fact(int i);
+int choose(int a, int b);
+double gen_choose(double a, int b);
 
 class DMatGen {
 public:
     DMatGen(double alpha, double beta, double gamma);
-    cdouble operator()(uint l, int m, int mp);
+    cdouble operator()(int l, int m, int mp);
 
-    double wigner_small_d(uint j, int mp, int m);
+    double wigner_small_d(int j, int mp, int m);
 
 private:
     std::map<std::tuple<int, int, int>, double> small_d_state;
@@ -58,8 +55,8 @@ private:
     cdouble gamma;
 };
 
-cdouble slm_c(uint l, int m, double r, double costheta, double phi);
-cdouble ylm_c(uint l, int m, double costheta, double phi);
+cdouble slm_c(int l, int m, double r, double costheta, double phi);
+cdouble ylm_c(int l, int m, double costheta, double phi);
 
 std::ostream& operator<<(std::ostream& os, const cdouble& c);
 cdouble operator*(double d, cdouble c);

### 2021-11-15 summaries/21-11/21-11.tex
Fixed segfault
Got param scan and oblateness scan ready

@@
 \subsection{Tidal Torque}
-We start by expressing the gravitational potential energy of the central body in its most general form:
+We start by expressing the gravitational potential energy field of the central body in its most general form:
 \begin{equation}
@@
 \end{equation}
-This integral is computed in the inertial frame.
+This integral is computed in the inertial frame and has units of energy per unit mass.
 We represent the central body density as $\rho_M$ and its volume as $\mathcal{P}$.
@@
 Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
-Then we may write $ \bm R' = \bm D + \bm R$, and Ref.~\cite{Gelderen1998TheSO} gives
+Then we may write $ \bm R' = \bm D + \bm U$, and Ref.~\cite{Gelderen1998TheSO} gives
 \begin{equation}
@@
 
-Note that each sum in this equation is weighted by a factor of $a_M^\ell a_m^{\ell'}/D^{\ell+\ell'}$.
+Note that each sum in this equation is weighted by a factor of $a_M^\ell a_m^{\ell'}/D^{\ell+\ell'+1}$.
 Since $D \gg a_M \gg a_m$ in general, the leading order torques come from low $\ell$ and $\ell'$.
-However, $\ell'$ contributes nothing because the inner bracketed term is zero, and $K_{\ell' = 1} = 0$ if we choose the origin of the body-fixed axes to be the center of mass of the asteroid.
+However, $\ell'=0$ contributes nothing because the inner bracketed term is zero, and $K_{\ell' = 1} = 0$ if we choose the origin of the body-fixed axes to be the center of mass of the asteroid.
 The leading order of equation \ref{eqn:tidal-torque} is therefore $1/D^3$ with $\ell = 0$ and $\ell' = 2$.
@@
 
-Since the coefficient of $J_{lm}K_{l'm'}$ is proportional to $a_M^\ell a_m^{\ell'} / D^{\ell+\ell'}$, to first order in the asteroid density distribution, the system is also independent of $a_m$.
+Since the coefficient of $J_{lm}K_{l'm'}$ is proportional to $a_M^\ell a_m^{\ell'} / D^{\ell+\ell'+1}$, to first order in the asteroid density distribution, the system is also independent of $a_m$.
 When $K_{\ell' > 2}$ terms are included, $a_m$ scales the size of the higher order terms.
@@
 For all simulations done here, $f = \SI{e-3}.$ We end the simulation also at $D f^{-1/3}$ on the other side of the orbit.
+
+Except when otherwise mentioned, we use the following fit parameters when running the simulation.
+\begin{enumerate}
+\item An orbit around Earth with $\SI{4}{\kilo\meter\per\second}$ excess velocity and perigee at 5 Earth radii
+\item An asteroid with radius $a_m = \SI{1}{\kilo\meter}$ and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values.
+One with $(K_{22}, K_{20}) = (0.052, -0.202)$ and one with $(0, -0.097)$.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and the standard values
+\item An initial roll of $\alpha_m=\pi/8$
+\item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$
+\item A rotational period of 5 hours, with spin axis pointing 45$^\circ$ below the orbital plane
+\end{enumerate}
 
@@
 \begin{equation}
-\text{Cov}(\omega^*_i, \omega^*_j) = \frac{1}{4 \omega^2}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
+\text{Cov}(\omega^*_i, \omega^*_j) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
 \omega_x \omega_z & \omega_y \omega_z& \omega_z^2
-\end{matrix}} +  \frac{1}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathbb{1}.
+\end{matrix}} +  \frac{\omega^2}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathbb{1}.
 \label{eqn:rotate-uncertainty-var}
@@
 where $\bm \omega_i$ is the $i$th expected spin and $\bm \omega_i^*$ is the data.
+
+\subsubsection{Position dependent method}
+In practice, precision on the asteroid spin axis will increase with decreasing distance \jtd{Citation needed}.
+The nominal sensitivity model does not account for this; however, we can approximate this effect by choosing $\sigma_\theta$ from the nominal method to be position-dependent.
+Specifically, we choose
+\begin{equation}
+\sigma_\theta(D) = slb.
+\label{eqn:pos-dependent-sensitivity}
+\end{equation}
+We do not expect this change to differ qualitatively from the nominal method because resolution is most important near pericenter, where $D$ is stationary to first order.
 
@@
 
-For our tests, we use parameters similar to our Moon: we set $\mu_o = 0.01 \mu_M$ and $R = 60 a_M$
+For our tests, we use parameters similar to our Moon: we set $\mu_o = 0.01 \mu_M$ and $R = 60 a_M$.
 
@@
 \section{Results}
+\subsection{Dependence on asteroid parameters}
+
+\subsection{Dependence on observational precision}
+
+\subsection{Dependence on orbital parameters}
+
+\subsection{Dependence on spin pole}
+
+\subsection{Exotic scenarios}
+
+\subsubsection{Oblate planet}
+
+\subsubsection{Distant moon}
+
+\subsubsection{Close moon}
 

### 2021-11-15 code/fit_resolved/fit.py

@@ -35,6 +35,7 @@ MIN_SPREAD = 1e-4 ** 2
 
 DISTANCE_RATIO_CUT = 10
 MIN_THETA_DIST = 0.01
+LARGE_NUMBER = 1e100
 
 if len(sys.argv) not in [2, 3]:
     raise Exception("Please pass a file to describe the fit")
@@ -106,16 +107,20 @@ def fit_function(theta):
         elif ASTEROIDS_MAX_J == 3:
             resolved_data = asteroids_3_2.simulate(cadence, jlms, theta[1:], radius,
                 spin[0], spin[1], spin[2], theta[0], perigee, speed, GM, EARTH_RADIUS, -1)
-    return np.asarray(resolved_data)
+    return np.asarray(resolved_data).reshape(-1, 3)
 
 
-def log_likelihood(theta, y, yerr):
+def log_likelihood(theta, y, y_inv_covs):
     # Normal likelihood
     try:
         model = fit_function(theta)
     except RuntimeError:
         return -np.inf # Zero likelihood
-    return -np.sum((y - model) ** 2 /  yerr ** 2)
+    # Return chisq
+    chisq = 0
+    for i in range(len(y)):
+        chisq += np.matmul(y[i] - model[i], np.matmul(y_inv_covs[i], y[i] - model[i]))
+    return chisq
 
 def log_prior(theta):
     for i, param in enumerate(theta):
@@ -137,50 +142,33 @@ start = time.time()
 y = fit_function(theta_true)
 print("Data generation took {} s".format(time.time() - start))
 if UNCERTAINTY_MODEL == 1:
-    y, yerr = random_vector.randomize_rotate_uniform(y, sigma)
+    y, y_inv_covs = random_vector.randomize_rotate_uniform(y, sigma)
 if UNCERTAINTY_MODEL == 2:
-    a = GM / speed**2
-
-    edge_dist = perigee * pow(INTEGRAL_LIMIT_FRAC, -1/3.0)
-    semi_major_axis = GM / speed / speed
-    eccentricity = perigee / semi_major_axis + 1
-    perigee = semi_major_axis * np.sqrt(eccentricity * eccentricity - 1)
-    ang_mom = [perigee * speed, 0, 0]
-    semi_latus_rectum = random_vector.vnorm(ang_mom)**2 / GM
-    nu = -np.arccos((semi_latus_rectum / edge_dist - 1) / eccentricity)
-    alt = [0, edge_dist * np.cos(nu), edge_dist * np.sin(nu)]
[…]

### 2021-12-08 summaries/21-11/21-11.tex
Terminal program

@@
 The physical parameters $K_{\ell m}$ resulting from a fit to flyby data, while physical, do not completely describe an asteroid.
-They can be converted into more concrete observables with the use of judicious assumptions.
+Since the density distribution of the asteriod has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
+As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\bm r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
+Then we have
+\begin{equation}
+K_{\ell m} = N_{\ell m} \frac{(-1)^m}{(\ell + m)!(\mu_m a_m^\ell)}\int_0^A r^{2+\ell} dr f_{\ell m}(r)
+\end{equation}
+where $N_{\ell m}$ is given by equation \ref{eqn:nlm}.
+Thus, $K_{\ell m}$ constrains only the integrals of $f_{\ell m}$, not the functions themselves.
+By relaxing the assumption that the asteroid is a sphere, even more degeneracy is introduced.
 
-\subsection{Constant Density Ellipsoid}
-Suppose we assume that the density of the asteroid is constant and its shape is elliptical. Then the combination of $a_m$, $K_{20}$, and $K_{22}$ fix the asteroid's shape according to the relations
+To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\bm r)$.
+In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}) or by using a numerical approach to find a more characteristic density distribution (section \ref{sec:numerical-density}).
+
+\jtd{Not all of these models will be in the paper.
+This is a list of all the models I've thought of.
+I'll give some examples of applying these models to ``realistic'' asteroid density profiles (uniform, regolith over rock, etc) and see what they get, using that filter to describe the best.}
+
+\subsection{Constant Density Asteroid Model}
+Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m$.
+We do not expect to solve for $\rho_0$ or equivalently $\mu_m$ since the mass of the asteroid cannot be extracted from tidal torque.
+However, we can solve for the asteorid shape required to match the known $K_{\ell m}$.
+In this process, we ignore $a_m$ until the last step, when we rescale the asteorid shape model until the correct $a_m$ is yielded.
+
+Suppose the asteroid is ``star shaped'' in that every point on its surface maps to a unique set of spherical coordinates $\theta, \phi$, and $r(\theta, \phi)$. We use the helpful identity
 \begin{equation}
-a = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}+12K_{22}} \qquad b = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}-12K_{22}} \qquad c = \sqrt{\frac{5}{3}}a_m\sqrt{1+4K_{20}}
+  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\bm r)
+   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \bm v (\bm r)
+    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
+\end{equation}
+where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $.
+We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \propto \unit r$, this gives
+\begin{equation}
+  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell(3 + \ell)} \int_0^\pi d\theta \sin \theta\int_0^{2\pi}d\phi r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
+  \label{eqn:constant-density-klm}
+\end{equation}
+The integrand of each $K_{\ell m}$ therefore is proportional to $r(\theta, \phi)^(3+\ell)$ times constants and a spherical harmonic.
+We can write $r(\theta \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality, in which case equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
+These integrals can be precomputed, since they are taken over the whole sphere $\theta \in (0, \pi)$ and $\phi \in (0, 2\pi)$.
+Equation \ref{eqn:constant-density-klm} can then be numerically solved to get $C_{\ell m}$.
+Specifically, the ratios of $K_{\ell m} / K_{\ell 0}$ can be solved for to eliminate the prefactor, then $\rho_m / \mu_m$ chosen such that $K_{00} = 1$.
+If $n$ values of $K_{\ell m}$ are known, then this method solves exactly for $n$ values of $C_{\ell m}$.
+\jtd{Implement this as a check.}
+
+\subsubsection{Special Case: Constant Density Ellipsoid}
+\label{sec:constant-density-ellipsoid}
+Suppose that only $K_{\ell = 2}$ are known.
+Then the above method is not necessary to compute the uniform density shape; we can assume the asteroid is an ellipsoid and solve for the axis lengths, which are
+\begin{equation}
+a = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}+12K_{22}} \qquad b = \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}-12K_{22}} \qquad c = \sqrt{\frac{5}{3}}a_m\sqrt{1+4K_{20}}.
 \label{eqn:ellipsoid-klm}
 \end{equation}
-which arise out of computing the moments of inertia for a constant density ellipsoid and using equation \ref{eqn:moi} to relate the result to $K_{\ell m}$ and $a_m$.
+These arise out of computing the moments of inertia for a constant density ellipsoid and using equation \ref{eqn:moi} to relate the result to $K_{\ell m}$ and $a_m$.
 The values $a$, $b$, and $c$, represent semi-axes aligned with $\unit x$, $\unit y$, and $\unit z$ respectively.
 
-The density of this asteroid cannot be extracted because, as is a general principle of gravitational interactions, the mass of the asteroid does not affect its dynamics.
+Again, the density of this asteroid cannot be extracted because, as is a general principle of gravitational interactions, the mass of the asteroid does not affect its dynamics.
 
-\subsection{Ellipsoid of Varying Density}
+\subsection{Fixed Surface $\nabla^2 \rho = 0$ model}
+Now suppose the shape of the asteroid is known, perhaps by a simplifying guess or perhaps by direct observation during a flyby.
+Then a density distribution $\rho(\bm r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
+Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
+Thus, $K_{\ell m} = \sum_{\ell' m'} C_{\ell' m'} B_{\ell \ell' m m'}$ where
+\begin{equation}
+  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m')}(\bm r)
+  \label{eqn:blm}
+\end{equation}
+can be precomputeded due to the shape of $\mathcal{A}$ being known.
+If we write $K_{\ell m}$ as a vector $\bm K$ and similarly for $\bm C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\bm K = \hat B \bm C$.
+It follows that the density distribution coefficients are given by
+\begin{equation}
+\bm C = \hat B^{-1} \bm K.
+\end{equation}
+The scale parameter $a_m$ can be computed from the resulting values of $\bm C$ and the distance scale can be adjusted until $a_m$ matches the true value.
+As before, $\mu_m$ is a free parameter representing the impossibility of fitting for the mass of the asteroid.
+Since only a finite number of $K_{\ell m}$ are known, we can only solve for a finite number of $C_{\ell m}$ and neglect the higher order terms.
 
-\subsection{Body of Known Surface}
+Physically, there is no reason to expect $\nabla^2 \rho = 0$.
+However, the space of density distributions with $\nabla^2 \rho = 0$ is a useful proxy for the true density distribution, since this section demonstrates how the denisty distribution can be solved for within this subspace.
+Conceptually, the density distribution derived from the $C_{\ell m}$s can be viewed as a projection from the true density distribution into the closest density distribution with $\nabla^2 \rho = 0$ everywhere.
+
+Note that if $\mathcal{A}$ is assumed to be a sphere, $B_{\ell \ell' m m'} \propto \delta_{\ell \ell'} \delta_{m m'}$ and $B_{\ell \ell m m}$ can be computed analytically.
+Thus, the matrix inversion step is not required in this case.
+
+\subsection{Fixed Surface Numerical Model}
+Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
+Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathbb{1}(\bm r)$ exists such that $\mathbb{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
+Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution.
+Given $n$ known values of $K_{\ell m}$, the algorithm proceeds as follows.
+\begin{enumerate}
+\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathbb{1}(\bm r_i) = 0.$
+\item Construct $n$ regions $\mathcal{R}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
+Suppose $R_i$ has uniform density $\rho_i$.
+\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\bm r)$.
+Once again, $\mu_m$ is a free parameter and units can be chosen such that $a_m=1$.
+Then %we can write $K_{\ell m} = \sum_i \rho_i \overline K_{\ell m}^i$.
+\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$. Invert it to get $\bm \rho = \hat {\overline K}^{-1} \bm K$.
+\item Go back to step 1 and compute new density maps with new draws of seed points.
+Since $K_{\ell m}$ is linear in $\rho$, the average density distribution also satisfies the fitted $K_{\ell m}$.
+Use the average as the asteroid density distribution.
+\end{enumerate}
+
+\jtd{What does this give mathematically?}
 

### 2021-12-15 summaries/21-11/21-11.tex
Need to fix some bugs in fit.py
Math checks

@@
 Here, $\rho_m$ denotes the density of the asteroid and $\mathcal{A}$ denotes its volume.
-The symmetry relations of $R_{\ell m}$ guarantee $J_{\ell m} = (-1)^m J_{\ell, -m}$ and similarly for $K_{\ell m}$.
+The symmetry relations of $R_{\ell m}$ guarantee $J_{\ell m} = (-1)^m J_{\ell, -m}^*$ and similarly for $K_{\ell m}$.
 We have chosen $\mu_M$, $\mu_m$ to be the masses of the central body and asteroid respectively, and $a_M$ and $a_m$ to be scale lengths of both bodies (defined more precisely later).
@@
 K_{20}-3K_{2,-2}-3K_{22}+1 & 3i \parens{K_{22}-K_{2,-2}} & \frac{3}{2}\parens{K_{21}-K_{2,-1}}\\
-3i \parens{K_{22}-K_{2,-2}} & K_{20}+3K_{2,-2}+3K_{22}+1 & -\frac{3}{2}i\parens{K_{21}-K_{2,-1}}\\
-\frac{3}{2}\parens{K_{21}-K_{2,-1}} & -\frac{3}{2}i\parens{K_{21}-K_{2,-1}} & -2K_{20}+1\\
+3i \parens{K_{22}-K_{2,-2}} & K_{20}+3K_{2,-2}+3K_{22}+1 & -\frac{3}{2}i\parens{K_{21}+K_{2,-1}}\\
+\frac{3}{2}\parens{K_{21}-K_{2,-1}} & -\frac{3}{2}i\parens{K_{21}+K_{2,-1}} & -2K_{20}+1\\
 \end{matrix}}
@@
 \begin{equation}
-\text{Cov}(\omega^*_i, \omega^*_j) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
+\text{Cov}(\bm \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
 \begin{equation}
-\chi^2 = \sum_{i=0} (\bm \omega_i^* - \bm \omega_i)^T\text{Cov}^{-1}(\omega^*_i, \omega^*_j)(\bm \omega_i^* - \bm \omega_i)
+\chi^2 = \sum_{i=0} (\bm \omega_i^* - \bm \omega_i)^T\text{Cov}^{-1}(\bm\omega^*_i)(\bm \omega_i^* - \bm \omega_i)
 \end{equation}
 where $\bm \omega_i$ is the $i$th expected spin and $\bm \omega_i^*$ is the data.
+We also refer to the reduced chi squared, $\chi^2_r = \chi^2 / (3N)$, where $N$ is the number of $\bm \omega_i$ in the data set.
 
@@
 \begin{equation}
-\sigma_\theta(D) = slb.
+\sigma_\theta(D) = unimplemented.
 \label{eqn:pos-dependent-sensitivity}

### 2021-12-15 code/generate/display.py

@@ -31,6 +31,15 @@ for line in f.readlines():
     ys.append(float(y))
     zs.append(float(z))
 
+while len(xs) < len(perfect_xs):
+    xs.append(xs[-1])
+    ys.append(ys[-1])
+    zs.append(zs[-1])
+while len(xs) > len(perfect_xs):
+    del xs[-1]
+    del ys[-1]
+    del zs[-1]
+
 time = np.arange(0, len(zs), 1) * 120/3600
 
 plt.plot(time, xs, label=f'x')

### 2021-12-15 code/sim/algebra.hpp

@@ -113,6 +113,7 @@ public:
 
     Quaternion inverse() const;
     Vector3 rotate(const Vector3 v) const;
+    Matrix3 matrix() const;
     Vector3 vec() const;
     double mag();
     double mag2() const;

### 2022-01-07 summaries/21-11/21-11.tex
Made likelihood half chisq
Redid probe space for new likelihood and started sigma

@@
-\documentclass[11pt]{article}
+\documentclass[linenumbers]{aastex631}
 
-\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
-\usepackage{bm}
-\usepackage{amsmath}
+% Documentation: https://www.overleaf.com/project/61d88bb8ee06e1e18cf4ea76
+
 \usepackage{tikz}
-\usepackage{xcolor}
-\usepackage{bbold}
-\usepackage{siunitx}
+\usepackage{dsfont}
 
@@
 \newcommand{\quat}[1]{\widetilde{\bm{#1}}}
+\newcommand{\siunit}[1]{\ \textrm{#1}}
+\newcommand{\per}[1]{\ \textrm{#1}^{-1}}
 \usetikzlibrary{arrows.meta}
 
+\shorttitle{Asteroid project summary}
+\shortauthors{Dinsmore and de Wit}
+
+\graphicspath{figs/}
+
 \begin{document}
+
 \title{Asteroid project summary}
-\author{Jack Dinsmore, Julien de Wit}
 
-\maketitle
+\author[0000-0002-6401-778X]{Jack T. Dinsmore}
+\affiliation{Massachusetts Institute of Technology \\
+Cambridge, MA 02139}
+\email{jtdinsmo@mit.edu}
+
+\author{Julien de Wit}
+\affiliation{Massachusetts Institute of Technology \\
+Cambridge, MA 02139}
+
+\begin{abstract}
+
+Abstract. 
+\end{abstract}
+
+\keywords{Keywords, em-dash separated}
 
@@
     \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
-
     \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
-
     \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
@@
     \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
-
     \draw (0.5, -0.75) arc (290:302:2.5);
     \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
-
     \draw (0, 1) arc (90:123.7:1);
     \draw (-0.4, 1.2) node[anchor=center] {$\beta$};
-
     \draw (0.97, -0.52) arc (330:360:1.3);
     \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
-
     %\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
@@
     %\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
-
     \end{tikzpicture}
@@
 \begin{equation}
-\quat q = \parens{\begin{matrix} \cos \frac{\alpha}{2} \\ 0\\ 0 \\\sin \frac{\alpha}{2}\end{matrix}}
-\parens{\begin{matrix} \cos \frac{\beta}{2} \\ 0 \\\sin \frac{\beta}{2}\\ 0\end{matrix}}
-\parens{\begin{matrix} \cos \frac{\gamma}{2} \\ 0\\ 0 \\\sin \frac{\gamma}{2}\end{matrix}} = \parens{\begin{matrix}
+\quat q = \parens{\begin{array}{c} \cos \frac{\alpha}{2} \\ 0\\ 0 \\\sin \frac{\alpha}{2}\end{array}}
+\parens{\begin{array}{c} \cos \frac{\beta}{2} \\ 0 \\\sin \frac{\beta}{2}\\ 0\end{array}}
+\parens{\begin{array}{c} \cos \frac{\gamma}{2} \\ 0\\ 0 \\\sin \frac{\gamma}{2}\end{array}} = \parens{\begin{array}{c}
 \frac{\alpha}{2} \cos \frac{\beta}{2} \cos  \cos \frac{\gamma}{2} - \frac{\alpha}{2} \cos \frac{\beta}{2}\sin \sin \frac{\gamma}{2}\\
@@
 \frac{\alpha}{2} \cos \frac{\beta}{2} \cos  \sin \frac{\gamma}{2} + \frac{\alpha}{2} \cos \frac{\beta}{2}\sin \cos \frac{\gamma}{2}\\
-\end{matrix}}.
+\end{array}}.
 \label{eqn:euler-to-quat}
@@
 With this choice of Euler angles, the Wigner-D matrix elements are real with matrix elements given by
-\begin{equation}
-\begin{aligned}
+\begin{eqnarray}
 d^\ell_{mm'}(\beta) = &\sqrt{(\ell+m)!(\ell-m)!(\ell+m')!(\ell-m')!}\\
-& \sum_{s=s_\text{min}}^{s_\text{max}} \brackets{\frac{(-1)^{m-m'+s}\parens{\cos\frac{\beta}{2}}^{2\ell + m' - m - 2s}\parens{\sin \frac{\beta}{2}}^{m-m'+2s}}{(\ell+m'-s)!(\ell-m-s)!(m-m'+s)!s!}}
-\end{aligned}
+& \sum_{s=s_\textrm{min}}^{s_\textrm{max}} \brackets{\frac{(-1)^{m-m'+s}\parens{\cos\frac{\beta}{2}}^{2\ell + m' - m - 2s}\parens{\sin \frac{\beta}{2}}^{m-m'+2s}}{(\ell+m'-s)!(\ell-m-s)!(m-m'+s)!s!}}
 \label{eqn:wigner-d-elements}
-\end{equation}
-where $s_\text{min} = \max(0, m'-m)$ and $s_\text{max} = \min(\ell+m', \ell-m)$,
+\end{eqnarray}
+where $s_\textrm{min} = \max(0, m'-m)$ and $s_\textrm{max} = \min(\ell+m', \ell-m)$,
 and $\mathcal{D}^\ell_{mm'}(\alpha, \beta, \gamma) = d^j_{mm'}e^{-im\alpha} e^{-im'\gamma}$.
@@
 The tidal torque applied to an asteroid at a point $\bm u$ is given by $d\bm \tau(\bm u) = -\rho_m(\bm u) d^3u (\bm u \times (\nabla V_{\bm u}(\bm u)))$ in the body-fixed frame, which leaves
-\begin{equation}
-\begin{aligned}
+\begin{eqnarray}
 \bm\tau = &G\int_\mathcal{A}d^3u \rho_m(\bm u)  \bm u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)
@@
 & \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)\right].
-\end{aligned}
 \label{eqn:first-tidal-torque}
-\end{equation}
+\end{eqnarray}
 Using the identity
-\begin{equation}
-\begin{aligned}
+\begin{eqnarray}
 \bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
 &+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)+2im\unit z R_{\ell m}(\bm u)],
-\end{aligned}
-\end{equation}
+\end{eqnarray}
 which was derived from Ref.~\cite{Gelderen1998TheSO}'s analysis of the angular momentum operators applied to spherical harmonics, we write equation \ref{eqn:first-tidal-torque} as
-\begin{equation}
-\begin{aligned}
+\begin{eqnarray}
 \bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
@@
 \label{eqn:tidal-torque}
-\end{aligned}
-\end{equation}
+\end{eqnarray}
 This equation contains complex values, but it was numerically confirmed that $\bm \tau$ is a real-valued vector.
@@
 The inertia tensor of the asteroid is expressed as a matrix $I$. Written in terms of spherical harmonics in the body-fixed frame, we have
-\begin{equation}
-\begin{aligned}
-I = &\int_\mathcal{A} d^3 r\rho_m(\bm r) \parens{\begin{matrix}
+\begin{eqnarray}
+I = &\int_\mathcal{A} d^3 r\rho_m(\bm r) \parens{\begin{array}{ccc}
 y^2 + z^2 & -xy & -xz \\
@@
 -xz & -yz & x^2 + y^2 \\
-\end{matrix}}\\
-= &\frac{2}{3}\mu_m a_m^2\parens{\begin{matrix}
+\end{array}}\\
+= &\frac{2}{3}\mu_m a_m^2\parens{\begin{array}{ccc}
 K_{20}-3K_{2,-2}-3K_{22}+1 & 3i \parens{K_{22}-K_{2,-2}} & \frac{3}{2}\parens{K_{21}-K_{2,-1}}\\
@@
 \frac{3}{2}\parens{K_{21}-K_{2,-1}} & -\frac{3}{2}i\parens{K_{21}+K_{2,-1}} & -2K_{20}+1\\
-\end{matrix}}
-\end{aligned}
+\end{array}}
 \label{eqn:moi}
-\end{equation}
+\end{eqnarray}
 where we have defined, for neatness,
-\begin{equation}
+\begin{eqnarray}
 a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\bm r) r^2.
 \label{eqn:am}
-\end{equation}
+\end{eqnarray}
 With this definition of $a_m$, and an arbitrary definition of $a_M$ which may be taken to be similar to equation \ref{eqn:am} or a more convenient unit such as the central body radius, the parameters $J_{\ell m}$ and $K_{\ell m}$ of equation \ref{eqn:jlm} are completely defined.
@@
 Furthermore, we can demand that $\bm \omega \perp \bm r$ such that $\bm \omega \times \bm r = \Im[\quat \omega \quat r]$ Plugging this into equation \ref{eqn:quat-rot}, we have
-\begin{equation*}
+\begin{equation}
 \dot{\quat q^{-1}} \quat r \quat q + \quat q^{-1} \quat r \dot{\quat q} = \quat q^{-1}\quat \omega \quat r \quat q.
-\end{equation*}
+\nonumber
+\end{equation}
 Substituting $\bm r \rightarrow \bm R$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}]$,
-\begin{equation*}
+\begin{equation}
 2\dot{\quat q^{-1}}\quat q\quat R = \quat q^{-1}\quat \omega \quat q \quat R.
-\end{equation*}
+\nonumber
+\end{equation}
 Since $\bm R$ is arbitrary, this simplifies to
@@
 The second equation of motion are Euler's equations of motion given our expression for tidal torque. Namely,
-\begin{equation}
-\begin{aligned}
+\begin{eqnarray}
 I_1 \dot \omega_1 - \omega_2 \omega_3 (I_2 - I_3) &= \tau_1\\
@@
 I_3 \dot \omega_3 - \omega_1 \omega_2 (I_1 - I_2) &= \tau_3\\
-\end{aligned}
 \label{eqn:omega-eom}
-\end{equation}
+\end{eqnarray}
 The components of $\bm \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
@@
 Three inequalities result from this, but only one is not covered by the above restrictions.
-Namely, $I_{xx} + I_{yy}\geq I_{zz} \implies K_{20} \geq -1/4$.
+Namely, $I_{xx} + I_{yy}\geq I_{zz} \Rightarrow K_{20} \geq -1/4$.
 The intersection of these requirements forces $K_{20}$ and $K_{22}$ to lie in the triangle defined by
@@
 Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, we begin our simulation at $D = D f^{-1/3}$, where $f$ is a manually set parameter to control the length of the simulation.
-For all simulations done here, $f = \SI{e-3}.$ We end the simulation also at $D f^{-1/3}$ on the other side of the orbit.
+For all simulations done here, $f = 10^{-3}.$ We end the simulation also at $D f^{-1/3}$ on the other side of the orbit.
 
@@
 \begin{enumerate}
-\item An orbit around Earth with $\SI{4}{\kilo\meter\per\second}$ excess velocity and perigee at 5 Earth radii
-\item An asteroid with radius $a_m = \SI{1}{\kilo\meter}$ and $K_{3m}=0$.
+\item An orbit around Earth with $4\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii
+\item An asteroid with radius $a_m = 1\siunit{km}$ and $K_{3m}=0$.
 For $K_{22}$ and $K_{20}$, we use two standard values.
@@
 \begin{equation}
-M = \parens{\begin{matrix}
+M = \parens{\begin{array}{ccc}
 \cos \phi & -\sin \phi & 0\\
@@
 0 & 0 & 1
-\end{matrix}}
-\parens{\begin{matrix}
+\end{array}}
+\parens{\begin{array}{ccc}
 \cos \theta & 0 & \sin \theta \\
@@
 -\sin \theta & 0 & \cos \theta
-\end{matrix}}
+\end{array}}
 \label{eqn:rotate-uncertainty-matrix}
@@
 \begin{equation}
-\text{Cov}(\bm \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{matrix}
+\text{Cov}(\bm \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{array}{ccc}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
 \omega_x \omega_z & \omega_y \omega_z& \omega_z^2
-\end{matrix}} +  \frac{\omega^2}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathbb{1}.
+\end{array}} +  \frac{\omega^2}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathds{1}.
 \label{eqn:rotate-uncertainty-var}
@@
 \begin{equation}
-J_{\ell m} = \begin{cases}
+J_{\ell m} = \begin{array}{cc}
 \frac{2 \pi \sigma}{\mu_M + \pi(b^2-a^2)\sigma}\frac{(-1)^{\ell/2}}{a_M^\ell}\frac{b^{\ell+2} - a^{\ell+2}}{2^\ell (\ell/2)!^2 (\ell + 2)}
@@
 0 & \text{else}
-\end{cases}
+\end{array}
 \label{eqn:ring-jlm}
@@
 
-Using data from the NASA Saturn Fact Sheet, we arrive at $J_{20}\sim \SI{e-8}{}$ from rings, but $\SI{e-4}{}$ from oblateness. So oblateness is in fact the stronger effect.
+Using data from the NASA Saturn Fact Sheet, we arrive at $J_{20}\sim 10^{-8}$ from rings, but $10^{-4}$ from oblateness. So oblateness is in fact the stronger effect.
 
@@
 \subsection{Dependence on spin pole}
+
+\subsection{Dependence on cadence}
+
+\subsection{Dependence on blocking out perigee}
 
@@
 Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
-Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathbb{1}(\bm r)$ exists such that $\mathbb{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
+Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\bm r)$ exists such that $\mathds{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
 Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution.
@@
 \begin{enumerate}
-\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathbb{1}(\bm r_i) = 0.$
+\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathds{1}(\bm r_i) = 0.$
 \item Construct $n$ regions $\mathcal{R}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
@@
 
-\bibliographystyle{unsrt}
-\bibliography{asteroids}
+\jtd{Talk about the walker spacing: the clamps, the scale with sigma, and the block diagonal hermitian matrices}
+
+\jtd{Talk about the breaking up of the likelihood function during minimization}
+
+\jtd{Talk about first order torque}
+
+\jtd{Talk about how numerical accuracy was chosen}
+
+\jtd{Show plot of likelihood}
+
+\jtd{Show plot of simulation}
+
+\jtd{Move up error bar section so that plots can be explained}
+
+\jtd{Show corner plot}
+
+\jtd{Talk about how the representative points were chosen.}
+
+\vspace{5mm}
+\facilities{MIT Supercloud}
+
+%% Similar to \facility{}, there is the optional \software command to allow 
+%% authors a place to specify which programs were used during the creation of 
+%% the manuscript. Authors should list each code and include either a
+%% citation or url to the code inside ()s when available.
+
+\software{emcee, scipy.optimize.minimize, numdifftools.Hessian}
+
+\appendix
+
+\section{Representative flyby configurations}
+
+\section{Initial MCMC walker positions}
+
+\bibliography{asteroids}{}
+\bibliographystyle{aasjournal}
 

### 2022-01-10 summaries/21-11/21-11.tex
Updated summary with recent data

@@
 \newcommand{\jtd}[1]{{\color{red}\textit{#1}}}
-\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
+\newcommand{\quat}[1]{\widetilde{\mathbf{#1}}}
 \newcommand{\siunit}[1]{\ \textrm{#1}}
@@
 
-\graphicspath{figs/}
+\graphicspath{{./}{figs/}}
 
@@
 Cambridge, MA 02139}
+\email{jdewit@mit.edu}
 
@@
 
-We define a rotation matrix $M$ such that $M\bm{r} = \bm{R}$, where $\bm{r}$ is in the body-fixed frame and $\bm{R}$ is in the inertial frame.
+We define a rotation matrix $M$ such that $M\mathbf{r} = \mathbf{R}$, where $\mathbf{r}$ is in the body-fixed frame and $\mathbf{R}$ is in the inertial frame.
 It will be useful for us to represent this matrix in two different ways; one is with a normalized quaternion $\quat q$, and the other is with $z-y-z$ Euler angles named $\alpha$, $\beta$, and $\gamma$.
@@
 We use the quaternion $\quat q$ as our dynamical variable because Euler angles suffer from gimbal lock.
-For the sake of this paper, we write quaternions as $\quat q = r + i \bm i + j \bm j + k \bm k$, with the complex conjugate written as $\quat q^* = r - i \bm i - j \bm j - k \bm k$.
+For the sake of this paper, we write quaternions as $\quat q = r + i \mathbf i + j \mathbf j + k \mathbf k$, with the complex conjugate written as $\quat q^* = r - i \mathbf i - j \mathbf j - k \mathbf k$.
 The inverse is then $\quat q^{-1} = \quat q^* / (\quat q \quat q^*)$, and we define real and imaginary parts as $\Re \quat q = r$; $\Im \quat q = i \unit x + j \unit y + k \unit z$.
@@
 
-Normalized quaternions express rotations of an angle $\theta$ by $\quat q = \cos\frac{\theta}{2} + \sin\frac{\theta}{2}\quat n$ where $\quat n = 0 + n_x \bm i + n_y \bm j + n_z\bm k$.
-This rotation may be applied to any vector $\bm r$ by
+Normalized quaternions express rotations of an angle $\theta$ by $\quat q = \cos\frac{\theta}{2} + \sin\frac{\theta}{2}\quat n$ where $\quat n = 0 + n_x \mathbf i + n_y \mathbf j + n_z\mathbf k$.
+This rotation may be applied to any vector $\mathbf r$ by
 \begin{equation}
-\bm R = \Im \brackets{\quat q^{-1} \quat r\quat q }.
+\mathbf R = \Im \brackets{\quat q^{-1} \quat r\quat q }.
 \label{eqn:quat-rot}
@@
 \begin{equation}
-(q_0 + \quat q) (p_0 + \quat p) = q_0 p_0 - \bm p \cdot \bm q + p_0 \bm q + q_0 \bm p + \bm q \times \bm p.
+(q_0 + \quat q) (p_0 + \quat p) = q_0 p_0 - \mathbf p \cdot \mathbf q + p_0 \mathbf q + q_0 \mathbf p + \mathbf q \times \mathbf p.
 \label{eqn:quat-mult}
@@
 \begin{equation}
-V(\bm R') = -G\int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
+V(\mathbf R') = -G\int_\mathcal{P} d^3 R \rho_M(\mathbf R) \frac{1}{|\mathbf{R}-\mathbf{R'}|}.
 \label{eqn:first-pe}
@@
 \begin{equation}
-S_{\ell m}(\bm r) = (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \qquad R_{\ell m} (\bm r) = (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
+S_{\ell m}(\mathbf r) = (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \qquad R_{\ell m} (\mathbf r) = (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
 \end{equation}
@@
 \begin{equation}
-\frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
+\frac{1}{|\mathbf R - \mathbf R'|} = \sum_{\ell, m} R_{\ell m}(\mathbf R) S_{\ell m}^*(\mathbf R'),
 \label{eqn:1-over-r-expansion}
@@
 
-Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
-Then we may write $ \bm R' = \bm D + \bm U$, and Ref.~\cite{Gelderen1998TheSO} gives
+Suppose the vector $\mathbf{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
+Then we may write $ \mathbf R' = \mathbf D + \mathbf U$, and Ref.~\cite{Gelderen1998TheSO} gives
 \begin{equation}
-S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D).
+S_{\ell m}(\mathbf R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\mathbf U)S_{\ell+\ell', m + m'} (\mathbf D).
 \end{equation}
@@
 \begin{equation}
-J_{\ell m} = \int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{R_{\ell m}(\bm R)}{\mu_M a_M^\ell}
+J_{\ell m} = \int_\mathcal{P} d^3 R \rho_M(\mathbf R) \frac{R_{\ell m}(\mathbf R)}{\mu_M a_M^\ell}
 \qquad
-K_{\ell m} = \int_\mathcal{A} d^3 r \rho_m(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_m a_m^\ell}
+K_{\ell m} = \int_\mathcal{A} d^3 r \rho_m(\mathbf r) \frac{R_{\ell m}(\mathbf r)}{\mu_m a_m^\ell}
 \label{eqn:jlm}
@@
 \begin{equation}
-V(\bm U) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}R_{\ell' m'}(\bm U)S^*_{\ell+\ell', m + m'} (\bm D)}.
+V(\mathbf U) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}R_{\ell' m'}(\mathbf U)S^*_{\ell+\ell', m + m'} (\mathbf D)}.
 \label{eqn:pe-unrotated}
 \end{equation}
-To make use of $K_{\ell m}$ in equation \ref{eqn:jlm}, we need to rotate $\bm U$ from the inertial frame into $\bm u$ in the body fixed frame via $\bm U = M \bm u$.
+To make use of $K_{\ell m}$ in equation \ref{eqn:jlm}, we need to rotate $\mathbf U$ from the inertial frame into $\mathbf u$ in the body fixed frame via $\mathbf U = M \mathbf u$.
 The rotation of a spherical harmonic satisfies
 \begin{equation}
-Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).
+Y_{\ell m}(M\mathbf u) = \sum_{m'=-\ell}^\ell (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\mathbf u).
 \end{equation}
@@
 \begin{equation}
-R_{\ell m} (M \bm u) = \sum_{m'=-\ell}^\ell \sqrt{\frac{(\ell-m')!(\ell+m')!}{(\ell-m)!(\ell+m)!}} \mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\bm u)
+R_{\ell m} (M \mathbf u) = \sum_{m'=-\ell}^\ell \sqrt{\frac{(\ell-m')!(\ell+m')!}{(\ell-m)!(\ell+m)!}} \mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\mathbf u)
 \label{eqn:rlm-rotations}
@@
 \begin{equation}
-V(\bm u) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)}.
+V(\mathbf u) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D)\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\mathbf u)}.
 \end{equation}
 
-The tidal torque applied to an asteroid at a point $\bm u$ is given by $d\bm \tau(\bm u) = -\rho_m(\bm u) d^3u (\bm u \times (\nabla V_{\bm u}(\bm u)))$ in the body-fixed frame, which leaves
+The tidal torque applied to an asteroid at a point $\mathbf u$ is given by $d\mathbf \tau(\mathbf u) = -\rho_m(\mathbf u) d^3u (\mathbf u \times (\nabla V_{\mathbf u}(\mathbf u)))$ in the body-fixed frame, which leaves
 \begin{eqnarray}
-\bm\tau = &G\int_\mathcal{A}d^3u \rho_m(\bm u)  \bm u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)
+\mathbf\tau = &G\int_\mathcal{A}d^3u \rho_m(\mathbf u)  \mathbf u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D)
 \right.\\
-& \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)\right].
+& \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\mathbf u)\right].
 \label{eqn:first-tidal-torque}
@@
 \begin{eqnarray}
-\bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
-&+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)+2im\unit z R_{\ell m}(\bm u)],
+\mathbf u \times \nabla R_{\ell m}(\mathbf u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\mathbf u)\\
+&+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\mathbf u)+2im\unit z R_{\ell m}(\mathbf u)],
 \end{eqnarray}
@@
 \begin{eqnarray}
-\bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
+\mathbf \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
 \\
@@
 \end{eqnarray}
-This equation contains complex values, but it was numerically confirmed that $\bm \tau$ is a real-valued vector.
+This equation contains complex values, but it was numerically confirmed that $\mathbf \tau$ is a real-valued vector.
 
@@
 \begin{eqnarray}
-I = &\int_\mathcal{A} d^3 r\rho_m(\bm r) \parens{\begin{array}{ccc}
+I & = &\int_\mathcal{A} d^3 r\rho_m(\mathbf r) \parens{\begin{array}{ccc}
 y^2 + z^2 & -xy & -xz \\
@@
 \end{array}}\\
-= &\frac{2}{3}\mu_m a_m^2\parens{\begin{array}{ccc}
+& = &\frac{2}{3}\mu_m a_m^2\parens{\begin{array}{ccc}
 K_{20}-3K_{2,-2}-3K_{22}+1 & 3i \parens{K_{22}-K_{2,-2}} & \frac{3}{2}\parens{K_{21}-K_{2,-1}}\\
@@
 \begin{eqnarray}
-a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\bm r) r^2.
+a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\mathbf r) r^2.
 \label{eqn:am}
@@
 \begin{equation}
-\dot{\bm{V}} = -\frac{G\mu_M}{r^3}\bm{D}\qquad \dot{\bm{D}} = \bm{V}.
+\dot{\mathbf{V}} = -\frac{G\mu_M}{r^3}\mathbf{D}\qquad \dot{\mathbf{D}} = \mathbf{V}.
 \label{eqn:translaton-eom}
@@
 
-Let $\bm\omega$ be the rotational velocity of the asteroid in the body-fixed frame.
-We have two equations of motion for our system; one governs the evolution of $\bm \omega$ and the other governs the evolution of $\bm q$.
-Starting with the latter, consider a fixed point $\bm r$ in the body-fixed frame on a rotating asteroid.
-The corresponding point $\bm R$ in the inertial frame satisfies $\dot{\bm R} = \Im[\quat q^{-1}(\bm \omega \times \bm r )\quat q]$.
-Furthermore, we can demand that $\bm \omega \perp \bm r$ such that $\bm \omega \times \bm r = \Im[\quat \omega \quat r]$ Plugging this into equation \ref{eqn:quat-rot}, we have
+Let $\mathbf\omega$ be the rotational velocity of the asteroid in the body-fixed frame.
+We have two equations of motion for our system; one governs the evolution of $\mathbf \omega$ and the other governs the evolution of $\mathbf q$.
+Starting with the latter, consider a fixed point $\mathbf r$ in the body-fixed frame on a rotating asteroid.
+The corresponding point $\mathbf R$ in the inertial frame satisfies $\dot{\mathbf R} = \Im[\quat q^{-1}(\mathbf \omega \times \mathbf r )\quat q]$.
+Furthermore, we can demand that $\mathbf \omega \perp \mathbf r$ such that $\mathbf \omega \times \mathbf r = \Im[\quat \omega \quat r]$ Plugging this into equation \ref{eqn:quat-rot}, we have
 \begin{equation}
@@
 \end{equation}
-Substituting $\bm r \rightarrow \bm R$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}]$,
+Substituting $\mathbf r \rightarrow \mathbf R$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}]$,
 \begin{equation}
@@
 \end{equation}
-Since $\bm R$ is arbitrary, this simplifies to
+Since $\mathbf R$ is arbitrary, this simplifies to
 \begin{equation}
@@
 I_2 \dot \omega_2 - \omega_3 \omega_1 (I_3 - I_1) &= \tau_2\\
-I_3 \dot \omega_3 - \omega_1 \omega_2 (I_1 - I_2) &= \tau_3\\
+I_3 \dot \omega_3 - \omega_1 \omega_2 (I_1 - I_2) &= \tau_3
 \label{eqn:omega-eom}
 \end{eqnarray}
-The components of $\bm \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
+The components of $\mathbf \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
 
 \subsection{Initial Values}
-We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\bm \omega \parallel \unit z$.
-The initial conditions are therefore that $\bm \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\bm \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\gamma$.
+We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\mathbf \omega \parallel \unit z$.
+The initial conditions are therefore that $\mathbf \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\mathbf \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\gamma$.
 The third Euler angle $\alpha$ represents the initial roll of the asteroid, and therefore cannot be determined from physical data.
@@
 Given the observed orbit of an asteroid and observational data of its resolved spin over time, we built a simulation that would integrate equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} to generate synthetic data.
-Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:tidal-torque}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) a guess at the asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:tidal-torque}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) trial asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
 
@@
 The orbit orientation is fixed to lie in the $\unit X-\unit Y$ plane, with pericenter lying on $\hat X$.
-The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\bm r(t=0) = r_p \unit X$ and $\bm v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
+The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\mathbf r(t=0) = r_p \unit X$ and $\mathbf v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
 
 Once the inputs were specified, the moments of inertia were pre-computed from $K_{\ell m}$, as was the orbital path of the satellite as a function of time.
-Equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} were then integrated by the fourth order Runge-Kutta fourth order method with a time step of 100 seconds, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
-This time step was observed to produce equivalent spin data to data made by lower time step.
-At fixed time intervals, the rotational velocity in the body-fixed frame $\bm\omega_{xyz}$ was converted via equation \ref{eqn:quat-rot} to the inertial frame to produce synthetic data.
+Equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} were then integrated by the Runge-Kutta fourth order method with a time step of \jtd{describe} seconds, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
+At fixed time intervals of one cadence, the rotational velocity in the body-fixed frame $\mathbf\omega_{xyz}$ was converted via equation \ref{eqn:quat-rot} to the inertial frame to produce the synthetic data set.
 
-Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, we begin our simulation at $D = D f^{-1/3}$, where $f$ is a manually set parameter to control the length of the simulation.
-For all simulations done here, $f = 10^{-3}.$ We end the simulation also at $D f^{-1/3}$ on the other side of the orbit.
-
-Except when otherwise mentioned, we use the following fit parameters when running the simulation.
-\begin{enumerate}
-\item An orbit around Earth with $4\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii
-\item An asteroid with radius $a_m = 1\siunit{km}$ and $K_{3m}=0$.
-For $K_{22}$ and $K_{20}$, we use two standard values.
-One with $(K_{22}, K_{20}) = (0.052, -0.202)$ and one with $(0, -0.097)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and the standard values
-\item An initial roll of $\alpha_m=\pi/8$
-\item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$
-\item A rotational period of 5 hours, with spin axis pointing 45$^\circ$ below the orbital plane
-\end{enumerate}
+We begin our simulation at $D = 10 r_p$.
+Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
+Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
 
 \subsection{Fitting Method}
+\label{sec:fitting-method}
 To analyze the degree to which asteroid density distributions can be determined from flyby rotational velocity data, we use the forward model defined in section \ref{sec:simulation} to generate synthetic data, randomize the data according to one of the observational uncertainty model defined in section \ref{sec:uncertainty-models}, then use the same forward model to fit to the data and recover parameters.
@@
 After randomizing the data, we isolate a set of parameters which are likely to provide good fits.
-To do this, we minimize the $\chi^2$ value of the data given the model using the BFGS algorithm.
+To do this, we minimize the $\chi^2$ value of the data given the model using the Nelder-Mead algorithm, implemented in \texttt{scipy} \cite{NelderMead}.
 Our starting points for the minimization are spaced uniformly randomly across the allowed parameter space, which is the set of parameters with the triangle described by equation \ref{eqn:parameter-bounds}.
-The other parameter bounds are $\alpha_0 \in [-\pi/4, \pi/4)$, and $|\Re K_{l>2}| \leq  1$, $|\Im K_{l>2}| \leq  1$.
+The other parameter bounds are $\alpha_0 \in [-\pi/4, \pi/4)$, $|\Re K_{l>2}| \leq 1$, and $|\Im K_{l>2}| \leq  1$.
 
-If the minimization is conducted over too many parameter dimensions, convergence can be slow and potentially inaugurate.
+If the minimization is conducted over too many parameter dimensions, convergence can be slow or can fail.
 However, the parameters $K_{\ell m}$ are naturally separated into groups by order of $\ell$, since the torque applied by successive increment to $\ell$ is suppressed by $a_m/D$.
@@
 
+Even with this ordering of parameters, the system's strong dependence on asteroid shape makes convergence rare.
+The data is therefore truncated at distance $D = f r_p$, where $f$ is a manually-set fraction.
+Once minimization is conducted for the truncated data, the resulting parameters are used as the initial point for a minimization over the entire data set.
+Experimentation revealed that $f=2$ was appropriate, where the cut is performed after the perigee for the $\ell = 2$ parameters and before the perigee for the $\ell = 3$ parameters.
+
 We are interested in finding not just the optimal parameters, but the probability distributions of each fit parameter.
@@
 This fit method requires the parameter space to be populated with ``walkers,'' indicating the a guess at the true parameters of the system.
-We center these walkers on the minimizing parameters computed by the minimization of $\chi^2$, and spread out the walkers such that the number density of walkers is proportional to the likelihood ($\ln \mathcal{L} = -\chi^2$) at each point.
-This is done explicitly by computing the Hessian $\Sigma$ of the likelihood at each minimizing point $\theta_0$ and expressing the likelihood locally as a multi-dimensional Gaussian
+We center 32 walkers on the minimizing parameters computed by the minimization of $\chi^2$, and spread out the walkers such that the number density of walkers is proportional to the likelihood ($\ln \mathcal{L} = -\chi^2/2$) at each point.
+This is done explicitly by computing the Hessian $\Sigma$ of the $\chi^2$ value at each minimizing point $\theta_0$ and expressing the likelihood locally as a multi-dimensional Gaussian
 \begin{equation}
-\mathcal{L}(\bm \theta) \propto \text{exp}\parens{\frac{1}{2}(\bm \theta-\bm \theta_0)^T \Sigma (\bm \theta-\bm \theta_0)}.
+\mathcal{L}(\mathbf \theta) \propto \text{exp}\parens{-\frac{1}{2}(\mathbf \theta-\mathbf \theta_0)^T \Sigma (\mathbf \theta-\mathbf \theta_0)}.
 \end{equation}
-We may change bases into a frame in which the parameters are uncorrelated by multiplying by $D^T$, which is the matrix of eigenvectors of $\Sigma$.
-Populating the walkers in this uncorrelated space according to Gaussian standard deviations given by the eigenvalues of $\Sigma$, we can convert these walkers back to $\bm \theta$-space by multiplying by $D$.
+We may change bases into a frame in which the parameters are uncorrelated by multiplying by $V^T$, where $V$ is the matrix of eigenvectors of $\Sigma$.
+Populating the walkers in this uncorrelated space according to Gaussian standard deviations given by the eigenvalues of $\Sigma$, we can convert these walkers back to $\mathbf \theta$-space by multiplying by $V$.
+In practice, we only compute the components of $\Sigma$ for parameters that are found in the same minimization step; for example, we do not compute the entries of $\Sigma$ corresponding to $K_{20}$ and $K{30}$, setting it equal to zero instead.
 
-With the initial walkers distributed, we use the $\chi^2$ value as the log-likelihood to compute the posterior probability distribution of $\bm \theta$ given flat priors in the range outlined above for each parameter.
+Occasionally, the likelihood is non-Gaussian enough for $\Sigma$ to have negative or otherwise nonsensical eigenvalues (this occurs for strongly varying likelihood or due to numerical errors in the calculation of the Hessian).
+In these cases, we choose eigenvalues of between \jtd{limit} and \jtd{limit}.
+
+With the initial walkers distributed, we compute the posterior probability distribution of $\mathbf \theta$ given flat priors in the range outlined above for each parameter.
+We run the MCMC until results converge (defined as the condition that the autocorrelation time is less than one hundredth of the current iteration number and that the fractional difference between autocorrelation times is under 1\%), or for 100,000 iterations, whichever is smaller.
+The MCMC is observed only to run for all 100,000 iterations if the data is insufficiently precise to constrain some parameters.
 
@@
 
-Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\bm \omega$.
-This same rotation matrix is then used to rotate the random vector $\bm \Omega = \sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z$ to the randomized velocity vector.
+Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\mathbf \omega$.
+This same rotation matrix is then used to rotate the random vector $\mathbf \Omega = \sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z$ to the randomized velocity vector.
 Here, $\Phi$ is a uniformly random variable in the range $[0, \pi)$.
@@
 \end{equation}
-where $\theta$ and $\phi$ are the spherical coordinates of the original velocity vector $\bm \omega.$
+where $\theta$ and $\phi$ are the spherical coordinates of the original velocity vector $\mathbf \omega.$
 
-Equation \ref{eqn:rotate-uncertainty-matrix} is sufficient to randomize synthetic data, but an analytical expression for the coordinates of $\bm \omega$ is required to define the $\chi^2$ value used for fitting.
+Equation \ref{eqn:rotate-uncertainty-matrix} is sufficient to randomize synthetic data, but an analytical expression for the coordinates of $\mathbf \omega$ is required to define the $\chi^2$ value used for fitting.
 We approximate the distribution of each spin coordinate as normal, with covariance given by the covariance of the true distribution.
@@
 \begin{equation}
-\text{Cov}(\bm \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{array}{ccc}
+\text{Cov}(\mathbf \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{array}{ccc}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
 \begin{equation}
-\chi^2 = \sum_{i=0} (\bm \omega_i^* - \bm \omega_i)^T\text{Cov}^{-1}(\bm\omega^*_i)(\bm \omega_i^* - \bm \omega_i)
+\chi^2 = \sum_{i=0} (\mathbf \omega_i^* - \mathbf \omega_i)^T\text{Cov}^{-1}(\mathbf\omega^*_i)(\mathbf \omega_i^* - \mathbf \omega_i)
+\label{eqn:chisq-nominal}
 \end{equation}
-where $\bm \omega_i$ is the $i$th expected spin and $\bm \omega_i^*$ is the data.
-We also refer to the reduced chi squared, $\chi^2_r = \chi^2 / (3N)$, where $N$ is the number of $\bm \omega_i$ in the data set.
+where $\mathbf \omega_i$ is the $i$th expected spin and $\mathbf \omega_i^*$ is the data.
+We also refer to the reduced chi squared, $\chi^2_r = \chi^2 / (3N)$, where $N$ is the number of $\mathbf \omega_i$ in the data set.
+
+In figure \ref{fig:example-data} we present example data for this asteroid using the two reference asteroid and orbit parameters described in appendix \ref{app:reference-config}.
+Additionally, one thousand simulations are also run with asteroid parameters $\alpha$, $K_{20}$, and $K_{22}$ changed slightly, distributed according to the likelihood defined by equation \ref{eqn:likelihood} with this nominal uncertainty method and $\sigma_\theta = 0.2$.
+The method for distributing these shape parameters is the same as the method for distributing the MCMC initial walker positions, described in section \ref{sec:fitting-method}.
+Bands containing 68.3\%, 95.5\%, and 99.7\% of these additional simulations are also plotted in figure \ref{fig:example-data}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{nominal-data-sym.pdf}
+  \includegraphics[width=0.7\textwidth]{nominal-data-asym.pdf}
+  \caption{Angular velocity data simulated for the symmetric and asymmetric reference asteroid densities and the reference orbit (black lines).
+Also plotted is the deviation of the data for likelihood-distributed changes to the asteroid shape (bands) using the nominal uncertainty method.
+Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
+  \label{fig:example-data}
+\end{figure}
 
@@
 \begin{equation}
-J_{\ell m} = \begin{array}{cc}
+J_{\ell m} = \left\{\begin{array}{cc}
 \frac{2 \pi \sigma}{\mu_M + \pi(b^2-a^2)\sigma}\frac{(-1)^{\ell/2}}{a_M^\ell}\frac{b^{\ell+2} - a^{\ell+2}}{2^\ell (\ell/2)!^2 (\ell + 2)}
@@
 0 & \text{else}
-\end{array}
+\end{array}\right.
 \label{eqn:ring-jlm}
@@
 \subsection{Planet with a Moon: Distant Flyby}
-Consider a system with a moon of mass $\mu_{o}$ at constant displacement $\bm R$ from the central body.
+Consider a system with a moon of mass $\mu_{o}$ at constant displacement $\mathbf R$ from the central body.
 We assume that both the planet and the moon are spherical.
@@
 \begin{equation}
-R_{\ell m}(\bm R + \bm R') = \sum_{\ell' = 0}^\ell \sum_{m'=-\ell'}^\ell R_{\ell' m'}(\bm R') R_{\ell-\ell', m-m'}(\bm R)
+R_{\ell m}(\mathbf R + \mathbf R') = \sum_{\ell' = 0}^\ell \sum_{m'=-\ell'}^\ell R_{\ell' m'}(\mathbf R') R_{\ell-\ell', m-m'}(\mathbf R)
 \end{equation}
@@
 \begin{equation}
-J_{\ell m} = \frac{1}{(\mu_M+\mu_0) a_M^\ell}\brackets{\delta_{\ell 0}\delta_{m0}\mu_M + \int_\mathcal{P} d^3 r' \rho_o(\bm r') R_{\ell m}(\bm R + \bm r')}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0) a_M^\ell}\brackets{\delta_{\ell 0}\delta_{m0}\mu_M + \int_\mathcal{P} d^3 r' \rho_o(\mathbf r') R_{\ell m}(\mathbf R + \mathbf r')}
 \end{equation}
 \begin{equation}
-J_{\ell m} = \frac{1}{(\mu_M+\mu_0)}\brackets{\mu_M\delta_{\ell 0}\delta_{m0} + \mu_o \frac{R_{\ell m}(\bm R)}{ a_M^\ell}}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0)}\brackets{\mu_M\delta_{\ell 0}\delta_{m0} + \mu_o \frac{R_{\ell m}(\mathbf R)}{ a_M^\ell}}
 \end{equation}
@@
 The formalism above cannot be extended to write one set of $J_{\ell m}$ for both the moon and planet.
-To do this, we generate two separate paths of $\bm D(t)$, one pointing from the central body to the asteroid and one pointing from the moon the asteroid.
+To do this, we generate two separate paths of $\mathbf D(t)$, one pointing from the central body to the asteroid and one pointing from the moon the asteroid.
 Both are defined in the inertial reference frames.
@@
 \section{Results}
+To interpret the capacity of this tidal torque technique to constrain the density distribution of asteroids, we generate synthetic data in multiple simulated settings and fit to this data using an MCMC, reporting the standard deviation of the posterior parameter distributions as a measure of the effectiveness of the fit.
+Fits with narrow posterior distributions are considered more effective than those with wide posterior distributions, and the correlations between parameters are also of interest when computing uncertainties on physical models for the asteroid shape.
+
+The distributions are nearly Gaussian in most cases (see appendix \ref{app:gaussian-posteriors}) and all fits are run until convergence.
+
 \subsection{Dependence on asteroid parameters}
+Of first importance is the dependence of parameter uncertainties on the true parameter values.
+To measure this, we run 120 fits, all for the two $K_{\ell = 2}$ parameters and $\alpha$ with the standard orbit (appendix \ref{app:standard}) and experimental uncertainty $\sigma_\theta = 0.01$ with the nominal uncertainty model(section \ref{sec:uncertainty-models}).
+Each fit is run for $\alpha=\pi/8$ and $K_{20}, K_{22}$ distributed in a triangular lattice with 17 layers, spanning the parameter space.
+The 33 cases with extremal values of $K_{22}$ are not fitted as being too close to the edge of the parameter space.
+
+The parameters $K_{22}$ and $K_{20}$ are then converted to the more physical parameters $a/c$ and $b/c$ under the assumption of an elliptical asteroid of uniform density with minor axes $a, b, c$ (section \ref{sec:constant-density-ellipsoid}).
+Uncertainties on $\alpha$ and the two shape parameters are given in figure \ref{fig:probe-space-sigma}, and correlations between pairs of parameters ($\mathrm{Corr}(X, Y) = \mathrm{Var}(X, Y) / (\sigma_X \sigma_Y)$ are given in figure \ref{fig:probe-space-corr}.
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{probe-space-theta-1-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-theta-2-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-theta-3-sigma.pdf}
+
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-1-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-a-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-b-sigma.pdf}
+
+  \caption{Ratios of fit uncertainties (the standard deviations of parameter posterior distributions) to experimental uncertainty ($\sigma_\theta$) for fit parameters $\alpha$, $K_{22}$, and $K_{20}$ (top row) and $\alpha$, $a/c$, and $b/c$ (bottom row).
+Also shown are the reference asteroid shapes used elsewhere in this paper (appendix \ref{app:reference-config}); the symmetric case is marked with a circle and the asymmetric with a square.}
+  \label{fig:probe-space-sigma}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.3\textwidth]{probe-space-corr12.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-corr13.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-corr23.pdf}
+
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-1a.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-1b.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{probe-space-ab-ab.pdf}
+
+  \caption{Correlations between fit uncertainties and experimental uncertainty ($\sigma_\theta$) for fit parameters $\alpha$, $K_{22}$, and $K_{20}$ (top row) and $\alpha$, $a/c$, and $b/c$ (bottom row).
+Also shown are the reference asteroid shapes used elsewhere in this paper (appendix \ref{app:reference-config}); the symmetric case is marked with a circle and the asymmetric with a square.}
+  \label{fig:probe-space-corr}
+\end{figure}
+
+These figures demonstrate several key properties.
+Figure \ref{fig:probe-space-sigma} demonstrates that fit uncertainties for all three parameters are generally for asteroids with an axis of rotational symmetry --- i.e.
+$a=b$ or $K_{22} = 0$.
+This is likely due to the fact that the local axes, which are required to define the parameters, are set such that they align with the asteroid principal axes, and therefore are degenerate in the case of a symmetrical asteroid.
+For similar reasons, uncertainty in $\alpha$ especially is large for $a \approx b \approx c$, which is the spherical case in which no tidal torque is generated.
+Beyond these two trends, uncertainty in $a/c$ and $b/c$ appear to scale linearly with these ratios.
+
+Figure \ref{fig:probe-space-corr} demonstrates that the parameters are generally correlated.
+Specficically, $\alpha$ and $|K_{22}|$ are strongly correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
+Likewise, for the correlation of $a/c$ and $b/c$ with $\alpha$.
+$\mathrm{Corr}(\alpha, K_{20})$ shows slightly different behavior, since they are still correlated for asteroids with $a=b$.
+However, the correlation still increases for highly asymmetric asteroids.
+The correlation between shape parameters $K_{20}$ and $K_{22}$ is often near zero except in highly asymmetric asteroids, but the correlation between $a/c$ and $b/c$ is rarely zero; these correlate for $a\approx b$ and anti-correlate for $a \not \approx b$.
+The $K_{\ell m}$ coordinates may therefore be a better lens through which to view asteroid shape, due to their low correlation.
+
+Also shown in figures \ref{fig:probe-space-sigma} and \ref{fig:probe-space-corr} are the reference asteroid configurations which we study when fixing the asteroid shape and varying other parameters.
+We note that these reference configurations capture the above trends in variance and correlation, so that they can be viewed as representative of all but the most extreme asteroid configurations.
+The measured values of variance and covariance are displayed in table \ref{tab:probe-space-refernece-var-covar}.
+
+\begin{table}
+  \centering
+  \begin{tabular}{c c c c c c c}
+    \hline \hline
+    Reference point & $\sigma(\alpha)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\alpha, K_{22})}$ & $\mathrm{Corr(\alpha, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
+    Symmetric: $a=b$ & 0.190 & 0.000763 & 0.00726 & 0.707 & 0.508 & -0.205\\
+    & & 0.0412 & 0.0390 & -0.400 & -0.614 & 0.966\\
+    Asymmetric: $a<b$ & 0.0148 & 0.000410 & 0.000505 & -0.553 & -0.0716 & -0.356\\
+    & & 0.0142 & 0.0153 & -0.190 & 0.213 & 0.791\\
+    Asymmetric: $a>b$ & 0.0110 & 0.000582 & 0.000651 & 0.913 & -0.138 & -0.432\\ 
+    & & 0.0238 & 0.0128 & 0.328 & -0.485 & 0.636\\ \hline
+  \end{tabular}
+  \caption{Values for the standard deviation and correlation of $\alpha$, $K_{22}$, and $K_{20}$ (top entry of each row) or $\alpha$, $a/c$, and $b/c$ respectively (bottom entry of each row) for the symmetric and asymmetric reference points.}
+  \label{tab:probe-space-refernece-var-covar}
+\end{table}
 
@@
 The physical parameters $K_{\ell m}$ resulting from a fit to flyby data, while physical, do not completely describe an asteroid.
-Since the density distribution of the asteriod has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
-As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\bm r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
+Since the density distribution of the asteroid has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
+As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\mathbf r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
 Then we have
@@
 
-To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\bm r)$.
+To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\mathbf r)$.
 In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}) or by using a numerical approach to find a more characteristic density distribution (section \ref{sec:numerical-density}).
@@
 We do not expect to solve for $\rho_0$ or equivalently $\mu_m$ since the mass of the asteroid cannot be extracted from tidal torque.
-However, we can solve for the asteorid shape required to match the known $K_{\ell m}$.
-In this process, we ignore $a_m$ until the last step, when we rescale the asteorid shape model until the correct $a_m$ is yielded.
+However, we can solve for the asteroid shape required to match the known $K_{\ell m}$.
+In this process, we ignore $a_m$ until the last step, when we rescale the asteroid shape model until the correct $a_m$ is yielded.
 
@@
 \begin{equation}
-  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\bm r)
-   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \bm v (\bm r)
-    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
+  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\mathbf r)
+   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \mathbf v (\mathbf r)
+    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \mathbf r \cdot \mathbf v (\mathbf r)
 \end{equation}
-where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $.
-We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \propto \unit r$, this gives
+where $\mathbf v (\mathbf r) = \unit r R_{\ell m} (\mathbf r) r / (3+\ell) $.
+We know the area element satisfies $d^2 \mathbf r = \partial \mathbf r / \partial \theta \times \partial \mathbf r / \partial \phi$ in our coordinates, and when dotted with $\mathbf v \propto \unit r$, this gives
 \begin{equation}
@@
 Again, the density of this asteroid cannot be extracted because, as is a general principle of gravitational interactions, the mass of the asteroid does not affect its dynamics.
+If $a_m$ is unknown, the ratios $a/c$ and $b/c$ can be computed instead.
+Since $I_{zz}$, is the greatest of the moments of inertia, we expect $a/c > 1$ and $b/c > 1$.
 
@@
 Now suppose the shape of the asteroid is known, perhaps by a simplifying guess or perhaps by direct observation during a flyby.
-Then a density distribution $\rho(\bm r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
-Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
+Then a density distribution $\rho(\mathbf r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
+Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\mathbf r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
 Thus, $K_{\ell m} = \sum_{\ell' m'} C_{\ell' m'} B_{\ell \ell' m m'}$ where
 \begin{equation}
-  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m')}(\bm r)
+  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\mathbf r) R_{\ell' m')}(\mathbf r)
   \label{eqn:blm}
@@
 can be precomputeded due to the shape of $\mathcal{A}$ being known.
-If we write $K_{\ell m}$ as a vector $\bm K$ and similarly for $\bm C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\bm K = \hat B \bm C$.
+If we write $K_{\ell m}$ as a vector $\mathbf K$ and similarly for $\mathbf C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\mathbf K = \hat B \mathbf C$.
 It follows that the density distribution coefficients are given by
 \begin{equation}
-\bm C = \hat B^{-1} \bm K.
+\mathbf C = \hat B^{-1} \mathbf K.
 \end{equation}
-The scale parameter $a_m$ can be computed from the resulting values of $\bm C$ and the distance scale can be adjusted until $a_m$ matches the true value.
+The scale parameter $a_m$ can be computed from the resulting values of $\mathbf C$ and the distance scale can be adjusted until $a_m$ matches the true value.
 As before, $\mu_m$ is a free parameter representing the impossibility of fitting for the mass of the asteroid.
@@
 Physically, there is no reason to expect $\nabla^2 \rho = 0$.
-However, the space of density distributions with $\nabla^2 \rho = 0$ is a useful proxy for the true density distribution, since this section demonstrates how the denisty distribution can be solved for within this subspace.
+However, the space of density distributions with $\nabla^2 \rho = 0$ is a useful proxy for the true density distribution, since this section demonstrates how the density distribution can be solved for within this subspace.
 Conceptually, the density distribution derived from the $C_{\ell m}$s can be viewed as a projection from the true density distribution into the closest density distribution with $\nabla^2 \rho = 0$ everywhere.
@@
 Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
-Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\bm r)$ exists such that $\mathds{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
+Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\mathbf r)$ exists such that $\mathds{1}(\mathbf r) = 1$  inside the asteroid and 0 elsewhere.
 Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution.
@@
 \begin{enumerate}
-\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathds{1}(\bm r_i) = 0.$
+\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\mathbf r_i$ such that $\mathds{1}(\mathbf r_i) = 0.$
 \item Construct $n$ regions $\mathcal{R}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
 Suppose $R_i$ has uniform density $\rho_i$.
-\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\bm r)$.
+\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\mathbf r)$.
 Once again, $\mu_m$ is a free parameter and units can be chosen such that $a_m=1$.
 Then %we can write $K_{\ell m} = \sum_i \rho_i \overline K_{\ell m}^i$.
-\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$. Invert it to get $\bm \rho = \hat {\overline K}^{-1} \bm K$.
+\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$.
+Invert it to get $\mathbf \rho = \hat {\overline K}^{-1} \mathbf K$.
 \item Go back to step 1 and compute new density maps with new draws of seed points.
@@
 
-\jtd{Show plot of likelihood}
+\jtd{Show plot of likelihood? (May not be necessary, since the corner plots are also shown)}
 
-\jtd{Show plot of simulation}
-
-\jtd{Move up error bar section so that plots can be explained}
+\jtd{Move up error bar section so that plots can be explained?}
 
@@
 
-\jtd{Talk about how the representative points were chosen.}
+\jtd{Compare the results to gaussians (they are not gaussian near the edges). Could do moment testing, or the Shapiro-Wilk test, which is frequentist so I don't want to do it.}
+
+\jtd{Question: How to express non-gaussianity of distro?}
 
@@
 
-\section{Representative flyby configurations}
+\section{Reference flyby configurations}
+\label{app:reference-config}
+Except when otherwise mentioned, we use the following fit parameters when running the simulation.
+Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that if it is desired to test the dependence of fit results on perigee distance, for instance, the other parameters will not be fixed at values that are so unfavorable to observations that good fits are already excluded.
+Otherwise, the fit results for all perigee distances would always be poor and the dependence on perigee would be difficult to measure.
+\begin{enumerate}
+  \item An orbit around Earth with $4\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii.
+  \item An initial roll of $\alpha_0=\pi/8$.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$.
+  \item A rotational period of 5 hours, with spin axis pointing 45$^\circ$ below the orbital plane, toward the pericenter.
+  \item An asteroid with radius $a_m = 1\siunit{km}$ and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values.
+One with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
+The second case and its reflection are called the asymmetric cases.
+Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
+If not specified, we use the $a < b$ case.
+\end{enumerate}
 
-\section{Initial MCMC walker positions}
+\section{Example fit results}
+In the interest of demonstrating the result of a fit to synthetic data, we present the results of a fit to synthetic data generated with the nominal sensitivity model and $\sigma_\theta = 10^{-5}$.
+The symmetric reference asteroid is used.
+The reduced $\chi^2$ value of this fit (defined as $\chi^2 / N$, where $N$ is the number of degrees of freedom) was 0.83, and fit results were in good agreement with the true parameters.
+Nearly 12,000 MCMC iterations were required before convergence.
+
+Figure \ref{fig:example-residuals} shows the data with the best-fit overlayed and the residuals.
+Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix --- i.e., 1-$\sigma$ uncertainties.
+However, the data often exceeds these uncertainty bands.
+This is because uncertainties are correlated in truth, and points that fall outside of the band are not necessary in conflict with the best fit.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{example-residuals.pdf}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for a symmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.83.}
+  \label{fig:example-residuals}
+\end{figure}
+
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, both marginalized to be a function of one variable and of two.
+The true parameters are shown as lines.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{example-corner.pdf}
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for a symmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
+Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
+True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
+  \label{fig:example-corner}
+\end{figure}
+
+Figure \ref{fig:example-residuals} demonstrates that a good fit to data was achieved, despite the small error bars and strong dependence of the model on initial conditions.
+Figure \ref{fig:example-corner} shows that the posterior distributions are largely Gaussian-distributed, with several of the parameters strongly correlated.
+The true values lie within $2\sigma$ contours in most cases, as expected.
+Parameters are computed to very high accuracy --- $O(10^{-7})$ for $\alpha_0$ and $O(10^{-9})$ for $K_{2m}$ (the first tier of parameters as ordered by the sensitivity of the asteroid system to their values), and $O(10^{-4})-O(10^{-6})$ for $K_{3m}$.
+These ranges should be compared to the width of the prior distributions for these parameters, which is $O(1)$ for all.
+The success of this fit demonstrates that these higher order parameters can be fitted to data as long as good enough precision on the data is achieved.
+
+\section{Gaussianity of Parameter Posterior Distributions}
+\label{app:gaussian-posteriors}
 

### 2022-01-10 code/other-figs/example-corner/example-corner-l2.py

@@ -1,47 +1,0 @@
-import sys, corner, os
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-
-THETA_TRUE = [0.2, 0.07142857142857142, -0.14285714285714285]
-
-plt.style.use("jcap")
-mpl.rcParams['xtick.labelsize'] = 12
-mpl.rcParams['ytick.labelsize'] = 12
-
-Ixx = 2/3.0 * THETA_TRUE[2] - 4 * THETA_TRUE[1] + 2/3.0
-Iyy = 2/3.0 * THETA_TRUE[2] + 4 * THETA_TRUE[1] + 2/3.0
-Izz = -4/3.0 * THETA_TRUE[2] + 2/3.0
-asquared = 0.9 * (Iyy + Izz - Ixx)
-bsquared = 0.9 * (Ixx + Izz - Iyy) / asquared
-csquared = 0.9 * (Ixx + Iyy - Izz) / asquared
-theta_true = (THETA_TRUE[0], np.sqrt(bsquared), np.sqrt(csquared))
-
-samples = np.loadtxt("param-scan-1.14-0-samples.npy")
-
-labels = ["$\phi_0$", "$b/a$", "$c/a$"]
-
-new_samples = []
-for phi, k22, k20 in samples.transpose():
-    Ixx = 2/3.0 * k20 - 4 * k22 + 2/3.0
-    Iyy = 2/3.0 * k20 + 4 * k22 + 2/3.0
-    Izz = -4/3.0 * k20 + 2/3.0
-    asquared = 0.9 * (Iyy + Izz - Ixx)
-    bsquared = 0.9 * (Ixx + Izz - Iyy) / asquared
-    csquared = 0.9 * (Ixx + Iyy - Izz) / asquared
-    new_samples.append((phi, np.sqrt(bsquared), np.sqrt(csquared)))
-
-fig = corner.corner(
-    np.array(new_samples), labels=labels, truths=theta_true, truth_color=[0.3, 0.3, 1]
-)
-
-median = np.percentile(new_samples, 50, axis=0)
-top = np.percentile(new_samples, 95, axis=0)
-bottom = np.percentile(new_samples, 5, axis=0)
-
-corner.overplot_lines(fig, median, color=[1, 0, 0, 1], linewidth=1)
-corner.overplot_lines(fig, top, color=[1, 0, 0, 0.5], linestyle='dotted', linewidth=1)
[…]

### 2022-01-11 summaries/21-11/21-11.tex
Fixed quaternion update and ready to rerun probe space

@@
     \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
-    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 0.5) node[anchor=south] {$\unit Y$};
-    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-2, 3) node[anchor=south] {$\unit Z$};
-    \draw (0.5, -0.75) arc (290:302:2.5);
+    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
+    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
+    \draw[->] (0.5, -0.75) arc (290:302:2.5);
     \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
-    \draw (0, 1) arc (90:123.7:1);
-    \draw (-0.4, 1.2) node[anchor=center] {$\beta$};
-    \draw (0.97, -0.52) arc (330:360:1.3);
+    \draw[->] (0, 1.2) arc (130:161:1.3);
+    \draw (-0.3, 1.3) node[anchor=center] {$\beta$};
+    \draw[->] (0.97, -0.52) arc (330:368:1.3);
     \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
@@
 \begin{equation}
-\mathbf R = \Im \brackets{\quat q^{-1} \quat r\quat q }.
+\mathbf R = \Im \brackets{\quat q \quat r\quat q^{-1} }.
 \label{eqn:quat-rot}
@@
 Starting with the latter, consider a fixed point $\mathbf r$ in the body-fixed frame on a rotating asteroid.
-The corresponding point $\mathbf R$ in the inertial frame satisfies $\dot{\mathbf R} = \Im[\quat q^{-1}(\mathbf \omega \times \mathbf r )\quat q]$.
-Furthermore, we can demand that $\mathbf \omega \perp \mathbf r$ such that $\mathbf \omega \times \mathbf r = \Im[\quat \omega \quat r]$ Plugging this into equation \ref{eqn:quat-rot}, we have
+The corresponding point $\mathbf R=\Im[\quat q \mathbf r \quat q^{-1}]$ in the inertial frame satisfies $\dot{\mathbf R} = \Im[\quat q(\mathbf \omega \times \mathbf r )\quat q^{-1}]$.
+Furthermore, we can demand that $\mathbf \omega \perp \mathbf r$ so that $\mathbf \omega \times \mathbf r = \Im[\quat \omega \quat r]$.
+We obtain another equation for $\dot{\mathbf R}$ by differentiating equation \ref{eqn:quat-rot} with $\dot{\mathbf r} = 0$.
+Setting these equal,
 \begin{equation}
-\dot{\quat q^{-1}} \quat r \quat q + \quat q^{-1} \quat r \dot{\quat q} = \quat q^{-1}\quat \omega \quat r \quat q.
+\dot{\quat q} \quat r \quat q^{-1} + \quat q \quat r \dot{\quat q}^{-1} = \quat q\quat \omega \quat r \quat q^{-1}.
 \nonumber
 \end{equation}
-Substituting $\mathbf r \rightarrow \mathbf R$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}]$,
+Substituting $\mathbf r \rightarrow \quat q^{-1}\mathbf R \quat q$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}] = 0$,
 \begin{equation}
-2\dot{\quat q^{-1}}\quat q\quat R = \quat q^{-1}\quat \omega \quat q \quat R.
+  \dot{\quat q} \quat q^{-1}\mathbf R + \mathbf R \quat q \dot{\quat q}^{-1} = 2\dot{\quat q}\quat q^{-1}\quat R = \quat q\quat \omega \quat q^{-1}\mathbf R.
 \nonumber
@@
 \begin{equation}
-\dot{\quat q} = \frac{1}{2}\quat \omega\quat q.
+  2\dot{\quat q}\quat q^{-1} =  \quat q\quat \omega \quat q^{-1} \Rightarrow \dot{\quat q} = \frac{1}{2}\quat q\quat \omega.
 \label{eqn:quat-eom}
@@
 We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\mathbf \omega \parallel \unit z$.
-The initial conditions are therefore that $\mathbf \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\mathbf \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\gamma$.
-The third Euler angle $\alpha$ represents the initial roll of the asteroid, and therefore cannot be determined from physical data.
+The initial conditions are therefore that $\mathbf \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\mathbf \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\alpha$.
+The third Euler angle $\gamma$ represents the initial roll of the asteroid, and therefore cannot be determined from physical data.
 However, it is an initial condition of the simulation.
@@
 Namely, the initial value of the first Euler angle $\alpha_0$.
-Due to the fact that the principal axes $\unit x$ and $\unit y$ are orthogonal, Increments of $\alpha_0$ by $\pi/2$ correspond to flipping the body-fixed axes so that no physical change in the asteroid model occurs.
-We must therefore limit the range of $\alpha_0$ to width $\pi/2$.
-Arbitrarily, we choose $\alpha_0 \in [-\pi/4, \pi/4)$
+Due to the fact that the principal axes $\unit x$ and $\unit y$ are orthogonal, Increments of $\gamma_0$ by $\pi/2$ correspond to flipping the body-fixed axes so that no physical change in the asteroid model occurs.
+We must therefore limit the range of $\gamma_0$ to width $\pi/2$.
+Arbitrarily, we choose $\gamma_0 \in [-\pi/4, \pi/4)$
 
@@
 Given the observed orbit of an asteroid and observational data of its resolved spin over time, we built a simulation that would integrate equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} to generate synthetic data.
-Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:tidal-torque}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) trial asteroid parameters $K_{\ell m}$, $\alpha_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
+Inputs to the simulation were (1) the $\ell$ and $\ell'$ values at which to truncate the potential energy sum in equation \ref{eqn:tidal-torque}, (2) the cadence of observations, (3) the $J_{\ell m}$ parameters and mass and radius of the central body, (4) trial asteroid parameters $K_{\ell m}$, $\gamma_0$ and $a_m$, (5) the initial rotational velocity of the asteroid in the inertial frame, and (6) the asteroid's orbital parameters.
 
@@
 Our starting points for the minimization are spaced uniformly randomly across the allowed parameter space, which is the set of parameters with the triangle described by equation \ref{eqn:parameter-bounds}.
-The other parameter bounds are $\alpha_0 \in [-\pi/4, \pi/4)$, $|\Re K_{l>2}| \leq 1$, and $|\Im K_{l>2}| \leq  1$.
+The other parameter bounds are $\gamma_0 \in [-\pi/4, \pi/4)$, $|\Re K_{l>2}| \leq 1$, and $|\Im K_{l>2}| \leq  1$.
 
@@
 However, the parameters $K_{\ell m}$ are naturally separated into groups by order of $\ell$, since the torque applied by successive increment to $\ell$ is suppressed by $a_m/D$.
-Thus, we fit the $\ell=2$ and $\alpha_0$ parameters first, then lock them in place and fit the $\ell=3$ parameters, etc.
+Thus, we fit the $\ell=2$ and $\gamma_0$ parameters first, then lock them in place and fit the $\ell=3$ parameters, etc.
 The result is a set of points in parameter space which minimize the $\chi^2$.
@@
 In figure \ref{fig:example-data} we present example data for this asteroid using the two reference asteroid and orbit parameters described in appendix \ref{app:reference-config}.
-Additionally, one thousand simulations are also run with asteroid parameters $\alpha$, $K_{20}$, and $K_{22}$ changed slightly, distributed according to the likelihood defined by equation \ref{eqn:likelihood} with this nominal uncertainty method and $\sigma_\theta = 0.2$.
+Additionally, one thousand simulations are also run with asteroid parameters $\gamma_0$, $K_{20}$, and $K_{22}$ changed slightly, distributed according to the likelihood defined by equation \ref{eqn:likelihood} with this nominal uncertainty method and $\sigma_\theta = 0.2$.
 The method for distributing these shape parameters is the same as the method for distributing the MCMC initial walker positions, described in section \ref{sec:fitting-method}.
@@
   \includegraphics[width=0.7\textwidth]{nominal-data-asym.pdf}
-  \caption{Angular velocity data simulated for the symmetric and asymmetric reference asteroid densities and the reference orbit (black lines).
+  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroid densities and the reference orbit (black lines).
 Also plotted is the deviation of the data for likelihood-distributed changes to the asteroid shape (bands) using the nominal uncertainty method.
@@
 Of first importance is the dependence of parameter uncertainties on the true parameter values.
-To measure this, we run 120 fits, all for the two $K_{\ell = 2}$ parameters and $\alpha$ with the standard orbit (appendix \ref{app:standard}) and experimental uncertainty $\sigma_\theta = 0.01$ with the nominal uncertainty model(section \ref{sec:uncertainty-models}).
-Each fit is run for $\alpha=\pi/8$ and $K_{20}, K_{22}$ distributed in a triangular lattice with 17 layers, spanning the parameter space.
+To measure this, we run 120 fits, all for the two $K_{\ell = 2}$ parameters and $\gamma_0$ with the standard orbit (appendix \ref{app:standard}) and experimental uncertainty $\sigma_\theta = 0.01$ with the nominal uncertainty model(section \ref{sec:uncertainty-models}).
+Each fit is run for $\gamma_0=\pi/8$ and $K_{20}, K_{22}$ distributed in a triangular lattice with 17 layers, spanning the parameter space.
 The 33 cases with extremal values of $K_{22}$ are not fitted as being too close to the edge of the parameter space.
@@
 The parameters $K_{22}$ and $K_{20}$ are then converted to the more physical parameters $a/c$ and $b/c$ under the assumption of an elliptical asteroid of uniform density with minor axes $a, b, c$ (section \ref{sec:constant-density-ellipsoid}).
-Uncertainties on $\alpha$ and the two shape parameters are given in figure \ref{fig:probe-space-sigma}, and correlations between pairs of parameters ($\mathrm{Corr}(X, Y) = \mathrm{Var}(X, Y) / (\sigma_X \sigma_Y)$ are given in figure \ref{fig:probe-space-corr}.
+Uncertainties on $\gamma_0$ and the two shape parameters are given in figure \ref{fig:probe-space-sigma}, and correlations between pairs of parameters ($\mathrm{Corr}(X, Y) = \mathrm{Var}(X, Y) / (\sigma_X \sigma_Y)$ are given in figure \ref{fig:probe-space-corr}.
 \begin{figure}
-  \includegraphics[width=0.3\textwidth]{probe-space-theta-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-theta-2-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-theta-3-sigma.pdf}
+  \includegraphics[width=0.33\textwidth]{probe-space-theta-1-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-theta-2-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-theta-3-sigma.pdf}
 
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-a-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-b-sigma.pdf}
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-1-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-a-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-b-sigma.pdf}
 
-  \caption{Ratios of fit uncertainties (the standard deviations of parameter posterior distributions) to experimental uncertainty ($\sigma_\theta$) for fit parameters $\alpha$, $K_{22}$, and $K_{20}$ (top row) and $\alpha$, $a/c$, and $b/c$ (bottom row).
+  \caption{Ratios of fit uncertainties (the standard deviations of parameter posterior distributions) to experimental uncertainty ($\sigma_\theta$) for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (top row) and $\gamma_0$, $a/c$, and $b/c$ (bottom row).
 Also shown are the reference asteroid shapes used elsewhere in this paper (appendix \ref{app:reference-config}); the symmetric case is marked with a circle and the asymmetric with a square.}
@@
 \begin{figure}
-  \includegraphics[width=0.3\textwidth]{probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-corr23.pdf}
+  \includegraphics[width=0.33\textwidth]{probe-space-corr12.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-corr13.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-corr23.pdf}
 
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{probe-space-ab-ab.pdf}
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-1b.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-1a.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{probe-space-ab-ab.pdf}
 
-  \caption{Correlations between fit uncertainties and experimental uncertainty ($\sigma_\theta$) for fit parameters $\alpha$, $K_{22}$, and $K_{20}$ (top row) and $\alpha$, $a/c$, and $b/c$ (bottom row).
+  \caption{Correlations between fit uncertainties and experimental uncertainty ($\sigma_\theta$) for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (top row) and $\gamma_0$, $a/c$, and $b/c$ (bottom row).
 Also shown are the reference asteroid shapes used elsewhere in this paper (appendix \ref{app:reference-config}); the symmetric case is marked with a circle and the asymmetric with a square.}
@@
 This is likely due to the fact that the local axes, which are required to define the parameters, are set such that they align with the asteroid principal axes, and therefore are degenerate in the case of a symmetrical asteroid.
-For similar reasons, uncertainty in $\alpha$ especially is large for $a \approx b \approx c$, which is the spherical case in which no tidal torque is generated.
+For similar reasons, uncertainty in $\gamma_0$ especially is large for $a \approx b \approx c$, which is the spherical case in which no tidal torque is generated.
 Beyond these two trends, uncertainty in $a/c$ and $b/c$ appear to scale linearly with these ratios.
@@
 Figure \ref{fig:probe-space-corr} demonstrates that the parameters are generally correlated.
-Specficically, $\alpha$ and $|K_{22}|$ are strongly correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
-Likewise, for the correlation of $a/c$ and $b/c$ with $\alpha$.
-$\mathrm{Corr}(\alpha, K_{20})$ shows slightly different behavior, since they are still correlated for asteroids with $a=b$.
+Specficically, $\gamma_0$ and $|K_{22}|$ are strongly correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
+Likewise, for the correlation of $a/c$ and $b/c$ with $\gamma_0$.
+$\mathrm{Corr}(\v, K_{20})$ shows slightly different behavior, since they are still correlated for asteroids with $a=b$.
 However, the correlation still increases for highly asymmetric asteroids.
@@
     \hline \hline
-    Reference point & $\sigma(\alpha)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\alpha, K_{22})}$ & $\mathrm{Corr(\alpha, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
+    Reference point & $\sigma(\gamma_0)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\gamma_0, K_{22})}$ & $\mathrm{Corr(\gamma_0, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
     Symmetric: $a=b$ & 0.190 & 0.000763 & 0.00726 & 0.707 & 0.508 & -0.205\\
@@
   \end{tabular}
-  \caption{Values for the standard deviation and correlation of $\alpha$, $K_{22}$, and $K_{20}$ (top entry of each row) or $\alpha$, $a/c$, and $b/c$ respectively (bottom entry of each row) for the symmetric and asymmetric reference points.}
+  \caption{Values for the standard deviation and correlation of $\gamma_0$, $K_{22}$, and $K_{20}$ (top entry of each row) or $\gamma_0$, $a/c$, and $b/c$ respectively (bottom entry of each row) for the symmetric and asymmetric reference points.}
   \label{tab:probe-space-refernece-var-covar}
@@
 
-\jtd{Talk about the breaking up of the likelihood function during minimization}
-
 \jtd{Talk about first order torque}
@@
 \jtd{Move up error bar section so that plots can be explained?}
-
-\jtd{Show corner plot}
 
@@
   \item An orbit around Earth with $4\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii.
-  \item An initial roll of $\alpha_0=\pi/8$.
+  \item An initial roll of $\gamma_0=\pi/8$.
   \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$.
@@
 The true values lie within $2\sigma$ contours in most cases, as expected.
-Parameters are computed to very high accuracy --- $O(10^{-7})$ for $\alpha_0$ and $O(10^{-9})$ for $K_{2m}$ (the first tier of parameters as ordered by the sensitivity of the asteroid system to their values), and $O(10^{-4})-O(10^{-6})$ for $K_{3m}$.
+Parameters are computed to very high accuracy --- $O(10^{-7})$ for $\gamma_0$ and $O(10^{-9})$ for $K_{2m}$ (the first tier of parameters as ordered by the sensitivity of the asteroid system to their values), and $O(10^{-4})-O(10^{-6})$ for $K_{3m}$.
 These ranges should be compared to the width of the prior distributions for these parameters, which is $O(1)$ for all.

### 2022-01-12 summaries/21-11/21-11.tex
Updated summary

@@
 \section{Introduction}
+
+\begin{itemize}
+\item Asteroids simulated in binaries \cite{Naidu_2015}
+\item Previous work on the math of asteroid rotations \cite{ashenberg07, paul88}
+\item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
+\end{itemize}
 
@@
 \subsubsection{Nominal Method}
-The most detailed uncertainty model we use, and the one we use most often, is called the ``nominal method.'' It rotates each angular velocity vector by some angle $\Theta$ drawn from a normal distribution centered on $\Theta=0$ with standard deviation $\sigma_\theta$.
-The period is assumed to be known to arbitrary precision at each cadence.
-The direction in which the velocity is rotated is chosen from a uniformly random distribution.
-$\sigma_\theta$ is a general parameter which can be tweaked to model resolution of the spin axis direction.
+The most detailed uncertainty model we use, and the one we use most often, is called the ``nominal method.'' It rotates each angular velocity vector $\omega$ by some angle $\Theta$ drawn from a normal distribution centered on $\Theta=0$ with standard deviation $\sigma_\theta$.
+The rotation is done around an arbitrary axis perpendicular to $\omega$.
+We also allow the length of $\omega$ to change by a fraction $\rho$ drawn from a log-normal distribution
+\begin{equation}
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \mathrm{\exp}\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}
+\end{equation}
+so that $\mathrm{ln} \rho$ is normally distributed with mean zero (no change in the length of $\omega$).
+Both uncertainties $\sigma_\theta$ and $\sigma_\rho$ are general parameters that can be tweaked to model uncertainty in spin axis direction and period.
+In our case, we often set $\sigma_\rho = 0$ for simplicity.
+\jtd{Explain why with evidence}.
 
 Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\mathbf \omega$.
-This same rotation matrix is then used to rotate the random vector $\mathbf \Omega = \sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z$ to the randomized velocity vector.
+This same rotation matrix is then used to rotate the random vector $\mathbf \Omega = \rho \omega (\sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z)$ to the randomized velocity vector.
 Here, $\Phi$ is a uniformly random variable in the range $[0, \pi)$.
-Specifically, we write this rotation matrix as
+Specifically, we write this matrix as
 \begin{equation}
-M = \parens{\begin{array}{ccc}
+M = \rho\parens{\begin{array}{ccc}
 \cos \phi & -\sin \phi & 0\\
@@
 \begin{equation}
-\text{Cov}(\mathbf \omega) = \frac{1}{4}\parens{1-e^{-\sigma_\theta^2}} \parens{1-3e^{-\sigma_\theta^2}}\parens{\begin{array}{ccc}
+\text{Cov}(\mathbf \omega) = \frac{1}{2}e^{-\sigma_\theta^2 + 2 \sigma_\rho^2}\brackets{\parens{e^{-\sigma_\theta^2}-2e^{-\sigma_\rho^2}+\textrm{cosh}(\sigma_\theta^2)} \parens{\begin{array}{ccc}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
 \omega_x \omega_z & \omega_y \omega_z& \omega_z^2
-\end{array}} +  \frac{\omega^2}{4}\parens{1 - e^{-2\sigma_\theta^2}} \mathds{1}.
+\end{array}} +  \mathrm{sinh}(\sigma_\theta^2) \mathds{1}}.
 \label{eqn:rotate-uncertainty-var}
 \end{equation}
+The difference between this Gaussian approximation and the true distribution are shown in figure \ref{fig:nominal-spin-distro}, which shows the distribution of $10^5$ angular velocity vectors randomly generated for a true velocity vector given by the reference value (appendix \ref{app:reference-config}), both using the true uncertainty method and the Gaussian approximation.
+The true distribution is more likely to yield results close to the true value than the Gaussian approximation.
+Agreement also worsens in the case where one of the components of $\omega$ nears zero.
+This may have the result of our likelihood not perfectly representing our system, and the fit probabilities will be slightly inaccurate.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{nominal-covariance.pdf}
+  \caption{The distributions of $10^5$ spin vectors generated via the nominal uncertainty method from a true vector given in appendix \ref{app:reference-config}.
+The true distribution (blue) and the Gaussian approximation (orange) are compared.}
+  \label{fig:nominal-spin-distro}
+\end{figure}
 
@@
 \subsection{Dependence on asteroid parameters}
+\label{sec:probe-space}
 Of first importance is the dependence of parameter uncertainties on the true parameter values.
@@
     Reference point & $\sigma(\gamma_0)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\gamma_0, K_{22})}$ & $\mathrm{Corr(\gamma_0, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
-    Symmetric: $a=b$ & 0.190 & 0.000763 & 0.00726 & 0.707 & 0.508 & -0.205\\
-    & & 0.0412 & 0.0390 & -0.400 & -0.614 & 0.966\\
-    Asymmetric: $a<b$ & 0.0148 & 0.000410 & 0.000505 & -0.553 & -0.0716 & -0.356\\
-    & & 0.0142 & 0.0153 & -0.190 & 0.213 & 0.791\\
-    Asymmetric: $a>b$ & 0.0110 & 0.000582 & 0.000651 & 0.913 & -0.138 & -0.432\\ 
-    & & 0.0238 & 0.0128 & 0.328 & -0.485 & 0.636\\ \hline
+    Symmetric: $a=b$ &  &  &  &  &  & \\
+    &  &  &  &  &  & \\
+    Asymmetric: $a<b$ &  &  &  &  &  & \\
+    &  &  &  &  &  & \\
+    Asymmetric: $a>b$  &  &  &  &  &  & \\
+    &  &  &  &  &  & \\
   \end{tabular}
@@
 \subsection{Dependence on observational precision}
+\label{sec:probe-sigma}
+
+\jtd{Running Jan 11?}
 
@@
 
+\jtd{Do v and rp separately? Perhaps do not map}
+
 \subsection{Dependence on spin pole}
+
+\jtd{The period is also important, but probably depends too much on the start of the simulation. I'm more interested in the spin pole.}
 
@@
 \subsection{Dependence on blocking out perigee}
+\label{sec:block-perigee}
+Much of the data available concerning an asteroid's rotational velocity is captured much before or much after the flyby perigee, where tidal torque is low.
+The angular velocity evolution here is dominated by torque-free precession dictated by the moment of inertia components, so that zero-torque data can still be used to fix $K_{20}$ and $K_{22}$.
+However, $K_{3m}$ are not extractable from precession data alone.
+We are therefore curious how much of the sensitivity of the system to $K_{3m}$ components is due only data taken during the encounter perigee.
+
+To test this, we mask the perigee of the counter by removing data from the period when $D < f_\textrm{mask} r_p$, where $f_\textrm{mask}>1$ is a unit-less fraction.
+We also allow the simulation to continue beyond the standard $f = 10$, so that the actual length of the data set is unaffected by the mask and induces no lack of precision on the fit of $K_{3m}$.
+We then fit to synthetic data for each mask and plot the standard deviations of the parameter posterior PDFs for (1) $\gamma_0$ and $K_{2m}$ as a control, and (2) $K_{3m}$, to test whether they can still be fitted for without data concerning the perigee.
+To maximize the changes in posterior PDF, we use an experimental error of $\sigma_\theta = 10^{-5}$, the lowest we test in this study.
 
@@
 \subsection{Constant Density Asteroid Model}
+\label{sec:constant-density}
 Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m$.
@@
 \subsection{Fixed Surface $\nabla^2 \rho = 0$ model}
+\label{sec:laplace-rho}
 Now suppose the shape of the asteroid is known, perhaps by a simplifying guess or perhaps by direct observation during a flyby.
@@
 \subsection{Fixed Surface Numerical Model}
+\label{sec:numerical-density}
 Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
@@
 \jtd{Question: How to express non-gaussianity of distro?}
+\jtd{Question: How important is it that the true value is not reproduced by the fit?
+Should I try to fix this?
+It's caused by the Gaussian approximation of the likelihood being incorrectm and by the fact that the data is not quite drawn from the distributions we model in the likeihood (it's drawn from the distribution of the true spin, not the data spin).}
 
@@
 \begin{enumerate}
-  \item An orbit around Earth with $4\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii.
+  \item An orbit around Earth with $6\siunit{km}\per{s}$ excess velocity and perigee at 5 Earth radii. \jtd{Cite Apophis close approach}
   \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$.
-  \item A rotational period of 5 hours, with spin axis pointing 45$^\circ$ below the orbital plane, toward the pericenter.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho$ = 0.
+  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a 1:2:$-2$ ratio.
   \item An asteroid with radius $a_m = 1\siunit{km}$ and $K_{3m}=0$.

### 2022-01-13 summaries/21-11/21-11.tex
Now I understand why the likelihood function is bad

@@
-\documentclass[linenumbers]{aastex631}
+\documentclass{aastex631}
 
@@
 \item Asteroids simulated in binaries \cite{Naidu_2015}
-\item Previous work on the math of asteroid rotations \cite{ashenberg07, paul88}
+\item Previous work on the math of asteroid rotations %\cite{ashenberg07, paul88}
 \item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
@@
 \end{equation}
-The difference between this Gaussian approximation and the true distribution are shown in figure \ref{fig:nominal-spin-distro}, which shows the distribution of $10^5$ angular velocity vectors randomly generated for a true velocity vector given by the reference value (appendix \ref{app:reference-config}), both using the true uncertainty method and the Gaussian approximation.
+The difference between this Gaussian approximation and the true distribution are shown in figure \ref{fig:nominal-spin-distro} (a), which shows the distribution of the components of $10^5$ angular velocity vectors and their correlations, randomly generated for a true velocity vector given by the reference value (appendix \ref{app:reference-config}), both using the true uncertainty method and the Gaussian approximation.
 The true distribution is more likely to yield results close to the true value than the Gaussian approximation.
-Agreement also worsens in the case where one of the components of $\omega$ nears zero.
+Agreement also worsens in the case where one of the components of $\omega$ nears zero (not shown).
 This may have the result of our likelihood not perfectly representing our system, and the fit probabilities will be slightly inaccurate.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{nominal-covariance.pdf}
-  \caption{The distributions of $10^5$ spin vectors generated via the nominal uncertainty method from a true vector given in appendix \ref{app:reference-config}.
-The true distribution (blue) and the Gaussian approximation (orange) are compared.}
+  \gridline{
+    \fig{nominal-covariance.pdf}{0.5\textwidth}{
+        (a) Pairwise-distributions of components of $\mathbf \omega$ show good agreement between the true distribution and the Gaussian approximation.
+      }
+      \fig{nominal-norm.pdf}{0.45\textwidth}{
+        (b) The norm of $\omega$ (a function of all three coordinates) differs between the approximation and true distribution.
+      }
+    }
+  \caption{The true distribution (blue) and the Gaussian approximation (orange) with the same covariance (orange)  for the components of angular velocity $\mathbf \omega$ under the nominal uncertainty method.}
   \label{fig:nominal-spin-distro}
@@
 
-We then define the $\chi^2$ statistic to be
+A larger source of disagreement between the Gaussian approximated likelihood and the true distribution is the correlation between all three components of $\omega$.
+If two components of $\omega$, the third component is known up to its sign except when $\sigma_\rho \neq 0$.
+However, the covariance matrix of $\mathbf \omega$ does not capture this, nor do the distributions displayed in figure \ref{fig:nominal-spin-distro} (a).
+Therefore, when $\sigma_\rho \simeq 0$, the Gaussian likelihood function may poorly represent the model.
+To demonstrate this, we show a histogram of the norm of $\omega$ for the Gaussian approximated distribution and the true distribution in figure  \ref{fig:nominal-spin-distro} (b), which demonstrates that statistics involving all three components of $\mathbf \omega$ can differ highly between the approximation and the true distribution.
+
+Aware of the failings of the Gaussian likelihood assumption, we then define the $\chi^2$ statistic to be
 \begin{equation}

### 2022-01-13 code/fit_resolved/random_vector.py

@@ -38,12 +38,6 @@ def randomize_rotate_uniform_err(spin, sigma):
     sigma_theta, ratio = sigma
     norm2 = spin[0]**2 + spin[1]**2 + spin[2]**2
 
-    '''return 0.25 * (1 - np.exp(-sigma**2)) * (1 - 3 * np.exp(-sigma**2)) * np.array([
-        [spin[0]**2, spin[0] * spin[1], spin[0] * spin[2]],
-        [spin[0] * spin[1], spin[1]**2, spin[1] * spin[2]],
-        [spin[0] * spin[2], spin[1] * spin[2], spin[2]**2]
-    ]) + norm2 / 4 * (1 - np.exp(-2 * sigma**2)) * np.array([[1, 0, 0], [0, 1, 0], [0, 0, 1]])'''
-
     return 0.5 * np.exp(sigma_theta**2 * (-1+ 2 * ratio**2)) * (
         (np.exp(-sigma_theta**2) - 2 * np.exp(-sigma_theta**2 * ratio**2) + np.cosh(sigma_theta**2)) * np.array([
         [spin[0]**2, spin[0] * spin[1], spin[0] * spin[2]],
@@ -60,7 +54,7 @@ def randomize_rotate_uniform(data, sigma):
 
     for x, y, z in data:
         norm = np.sqrt(x**2 + y**2 + z**2)
-        new_norm = norm * (1 + np.random.randn(1) * ratio * sigma_theta)
+        new_norm = norm * np.random.lognormal(sigma=sigma_theta * ratio)
         theta = np.arccos(z / norm)
         phi = np.arctan2(y, x)
         rot_mat = np.matmul(
@@ -74,6 +68,7 @@ def randomize_rotate_uniform(data, sigma):
         covs = randomize_rotate_uniform_err(newvec, sigma)
         newy.append(newvec)
         ycovs.append(scipy.linalg.pinvh(covs))
+
     return np.array(newy), np.array(ycovs)
 
 def randomize_rotate_gauss(data, sigma):
@@ -119,6 +114,19 @@ if __name__ == "__main__":
 
     plt.savefig("random-figs/random-vector-unc.pdf")
     plt.savefig("random-figs/random-vector-unc.png")
+
+    plt.figure()
+    true_norms = np.linalg.norm(newspin, axis=1)
+    gauss_norms = np.linalg.norm(gauss_spin, axis=1)
+    bins=np.linspace(np.min(gauss_norms), np.max(gauss_norms), 20)
[…]

### 2022-01-13 data/probe-space/compile.py

@@ -158,7 +158,8 @@ def covariance():
                     cov = np.array([[np.nan, np.nan, np.nan], [np.nan, np.nan, np.nan], [np.nan, np.nan, np.nan]])
                 else:
                     min_index = np.argmin(weights)
-                    _, _, cov = data[min_index]
+                    min_file, min_diffs, cov = data[min_index]
+                    print(f"Min file: {min_file}; Min diffs: {min_diffs}")
                 
             corr12 = cov[1][2] / np.sqrt(cov[1][1] * cov[2][2])
             corr01 = cov[0][1] / np.sqrt(cov[0][0] * cov[1][1])

### 2022-01-14 summaries/21-11/21-11.tex
Probe space data compiled

@@
 \usepackage{dsfont}
+\usepackage{bm}
 
-\newcommand{\unit}[1]{\hat{\mathbf{#1}}}
+\newcommand{\unit}[1]{\hat{\bm{#1}}}
 \newcommand{\parens}[1]{\left( #1 \right)}
@@
 \newcommand{\jtd}[1]{{\color{red}\textit{#1}}}
-\newcommand{\quat}[1]{\widetilde{\mathbf{#1}}}
+\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
 \newcommand{\siunit}[1]{\ \textrm{#1}}
@@
 \item Asteroids simulated in binaries \cite{Naidu_2015}
-\item Previous work on the math of asteroid rotations %\cite{ashenberg07, paul88}
+\item Previous work on the math of asteroid rotations \cite{ashenberg07, paul88}
 \item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
@@
 
-We define a rotation matrix $M$ such that $M\mathbf{r} = \mathbf{R}$, where $\mathbf{r}$ is in the body-fixed frame and $\mathbf{R}$ is in the inertial frame.
+We define a rotation matrix $M$ such that $M\bm{r} = \bm{R}$, where $\bm{r}$ is in the body-fixed frame and $\bm{R}$ is in the inertial frame.
 It will be useful for us to represent this matrix in two different ways; one is with a normalized quaternion $\quat q$, and the other is with $z-y-z$ Euler angles named $\alpha$, $\beta$, and $\gamma$.
@@
 We use the quaternion $\quat q$ as our dynamical variable because Euler angles suffer from gimbal lock.
-For the sake of this paper, we write quaternions as $\quat q = r + i \mathbf i + j \mathbf j + k \mathbf k$, with the complex conjugate written as $\quat q^* = r - i \mathbf i - j \mathbf j - k \mathbf k$.
+For the sake of this paper, we write quaternions as $\quat q = r + i \bm i + j \bm j + k \bm k$, with the complex conjugate written as $\quat q^* = r - i \bm i - j \bm j - k \bm k$.
 The inverse is then $\quat q^{-1} = \quat q^* / (\quat q \quat q^*)$, and we define real and imaginary parts as $\Re \quat q = r$; $\Im \quat q = i \unit x + j \unit y + k \unit z$.
@@
 
-Normalized quaternions express rotations of an angle $\theta$ by $\quat q = \cos\frac{\theta}{2} + \sin\frac{\theta}{2}\quat n$ where $\quat n = 0 + n_x \mathbf i + n_y \mathbf j + n_z\mathbf k$.
-This rotation may be applied to any vector $\mathbf r$ by
+Normalized quaternions express rotations of an angle $\theta$ by $\quat q = \cos\frac{\theta}{2} + \sin\frac{\theta}{2}\quat n$ where $\quat n = 0 + n_x \bm i + n_y \bm j + n_z\bm k$.
+This rotation may be applied to any vector $\bm r$ by
 \begin{equation}
-\mathbf R = \Im \brackets{\quat q \quat r\quat q^{-1} }.
+\bm R = \Im \brackets{\quat q \quat r\quat q^{-1} }.
 \label{eqn:quat-rot}
@@
 \begin{equation}
-(q_0 + \quat q) (p_0 + \quat p) = q_0 p_0 - \mathbf p \cdot \mathbf q + p_0 \mathbf q + q_0 \mathbf p + \mathbf q \times \mathbf p.
+(q_0 + \quat q) (p_0 + \quat p) = q_0 p_0 - \bm p \cdot \bm q + p_0 \bm q + q_0 \bm p + \bm q \times \bm p.
 \label{eqn:quat-mult}
@@
 \begin{equation}
-V(\mathbf R') = -G\int_\mathcal{P} d^3 R \rho_M(\mathbf R) \frac{1}{|\mathbf{R}-\mathbf{R'}|}.
+V(\bm R') = -G\int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
 \label{eqn:first-pe}
@@
 \begin{equation}
-S_{\ell m}(\mathbf r) = (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \qquad R_{\ell m} (\mathbf r) = (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
+S_{\ell m}(\bm r) = (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \qquad R_{\ell m} (\bm r) = (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
 \end{equation}
@@
 \begin{equation}
-\frac{1}{|\mathbf R - \mathbf R'|} = \sum_{\ell, m} R_{\ell m}(\mathbf R) S_{\ell m}^*(\mathbf R'),
+\frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
 \label{eqn:1-over-r-expansion}
@@
 
-Suppose the vector $\mathbf{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
-Then we may write $ \mathbf R' = \mathbf D + \mathbf U$, and Ref.~\cite{Gelderen1998TheSO} gives
+Suppose the vector $\bm{D}$ points from the center of mass of the central body to the center of mass of the asteroid, again in the inertial frame.
+Then we may write $ \bm R' = \bm D + \bm U$, and Ref.~\cite{Gelderen1998TheSO} gives
 \begin{equation}
-S_{\ell m}(\mathbf R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\mathbf U)S_{\ell+\ell', m + m'} (\mathbf D).
+S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D).
 \end{equation}
@@
 \begin{equation}
-J_{\ell m} = \int_\mathcal{P} d^3 R \rho_M(\mathbf R) \frac{R_{\ell m}(\mathbf R)}{\mu_M a_M^\ell}
+J_{\ell m} = \int_\mathcal{P} d^3 R \rho_M(\bm R) \frac{R_{\ell m}(\bm R)}{\mu_M a_M^\ell}
 \qquad
-K_{\ell m} = \int_\mathcal{A} d^3 r \rho_m(\mathbf r) \frac{R_{\ell m}(\mathbf r)}{\mu_m a_m^\ell}
+K_{\ell m} = \int_\mathcal{A} d^3 r \rho_m(\bm r) \frac{R_{\ell m}(\bm r)}{\mu_m a_m^\ell}
 \label{eqn:jlm}
@@
 \begin{equation}
-V(\mathbf U) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}R_{\ell' m'}(\mathbf U)S^*_{\ell+\ell', m + m'} (\mathbf D)}.
+V(\bm U) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}R_{\ell' m'}(\bm U)S^*_{\ell+\ell', m + m'} (\bm D)}.
 \label{eqn:pe-unrotated}
 \end{equation}
-To make use of $K_{\ell m}$ in equation \ref{eqn:jlm}, we need to rotate $\mathbf U$ from the inertial frame into $\mathbf u$ in the body fixed frame via $\mathbf U = M \mathbf u$.
+To make use of $K_{\ell m}$ in equation \ref{eqn:jlm}, we need to rotate $\bm U$ from the inertial frame into $\bm u$ in the body fixed frame via $\bm U = M \bm u$.
 The rotation of a spherical harmonic satisfies
 \begin{equation}
-Y_{\ell m}(M\mathbf u) = \sum_{m'=-\ell}^\ell (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\mathbf u).
+Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).
 \end{equation}
@@
 \begin{equation}
-R_{\ell m} (M \mathbf u) = \sum_{m'=-\ell}^\ell \sqrt{\frac{(\ell-m')!(\ell+m')!}{(\ell-m)!(\ell+m)!}} \mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\mathbf u)
+R_{\ell m} (M \bm u) = \sum_{m'=-\ell}^\ell \sqrt{\frac{(\ell-m')!(\ell+m')!}{(\ell-m)!(\ell+m)!}} \mathcal{D}^\ell_{mm'}(M)^* R_{\ell m'} (\bm u)
 \label{eqn:rlm-rotations}
@@
 \begin{equation}
-V(\mathbf u) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D)\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\mathbf u)}.
+V(\bm u) = -G \brackets{\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)}.
 \end{equation}
 
-The tidal torque applied to an asteroid at a point $\mathbf u$ is given by $d\mathbf \tau(\mathbf u) = -\rho_m(\mathbf u) d^3u (\mathbf u \times (\nabla V_{\mathbf u}(\mathbf u)))$ in the body-fixed frame, which leaves
+The tidal torque applied to an asteroid at a point $\bm u$ is given by $d\bm \tau(\bm u) = -\rho_m(\bm u) d^3u (\bm u \times (\nabla V_{\bm u}(\bm u)))$ in the body-fixed frame, which leaves
 \begin{eqnarray}
-\mathbf\tau = &G\int_\mathcal{A}d^3u \rho_m(\mathbf u)  \mathbf u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D)
+\bm\tau = &G\int_\mathcal{A}d^3u \rho_m(\bm u)  \bm u \times \nabla \left[\sum_{\ell, m} \mu_M a_M^\ell J_{\ell m} \sum_{\ell', m'} (-1)^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D)
 \right.\\
-& \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\mathbf u)\right].
+& \left. \sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'-m')!}} \mathcal{D}^{\ell'}_{m'm''}(M)^* R_{\ell' m''} (\bm u)\right].
 \label{eqn:first-tidal-torque}
@@
 \begin{eqnarray}
-\mathbf u \times \nabla R_{\ell m}(\mathbf u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\mathbf u)\\
-&+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\mathbf u)+2im\unit z R_{\ell m}(\mathbf u)],
+\bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
+&+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)+2im\unit z R_{\ell m}(\bm u)],
 \end{eqnarray}
@@
 \begin{eqnarray}
-\mathbf \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\mathbf D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
+\bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(M)^* \right.
 \\
@@
 \end{eqnarray}
-This equation contains complex values, but it was numerically confirmed that $\mathbf \tau$ is a real-valued vector.
+This equation contains complex values, but it was numerically confirmed that $\bm \tau$ is a real-valued vector.
 
@@
 \begin{eqnarray}
-I & = &\int_\mathcal{A} d^3 r\rho_m(\mathbf r) \parens{\begin{array}{ccc}
+I & = &\int_\mathcal{A} d^3 r\rho_m(\bm r) \parens{\begin{array}{ccc}
 y^2 + z^2 & -xy & -xz \\
@@
 \begin{eqnarray}
-a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\mathbf r) r^2.
+a_m^2=\frac{1}{\mu_m}\int_\mathcal{A} d^3 r \rho_m(\bm r) r^2.
 \label{eqn:am}
@@
 \begin{equation}
-\dot{\mathbf{V}} = -\frac{G\mu_M}{r^3}\mathbf{D}\qquad \dot{\mathbf{D}} = \mathbf{V}.
+\dot{\bm{V}} = -\frac{G\mu_M}{r^3}\bm{D}\qquad \dot{\bm{D}} = \bm{V}.
 \label{eqn:translaton-eom}
@@
 
-Let $\mathbf\omega$ be the rotational velocity of the asteroid in the body-fixed frame.
-We have two equations of motion for our system; one governs the evolution of $\mathbf \omega$ and the other governs the evolution of $\mathbf q$.
-Starting with the latter, consider a fixed point $\mathbf r$ in the body-fixed frame on a rotating asteroid.
-The corresponding point $\mathbf R=\Im[\quat q \mathbf r \quat q^{-1}]$ in the inertial frame satisfies $\dot{\mathbf R} = \Im[\quat q(\mathbf \omega \times \mathbf r )\quat q^{-1}]$.
-Furthermore, we can demand that $\mathbf \omega \perp \mathbf r$ so that $\mathbf \omega \times \mathbf r = \Im[\quat \omega \quat r]$.
-We obtain another equation for $\dot{\mathbf R}$ by differentiating equation \ref{eqn:quat-rot} with $\dot{\mathbf r} = 0$.
+Let $\bm\omega$ be the rotational velocity of the asteroid in the body-fixed frame.
+We have two equations of motion for our system; one governs the evolution of $\bm \omega$ and the other governs the evolution of $\bm q$.
+Starting with the latter, consider a fixed point $\bm r$ in the body-fixed frame on a rotating asteroid.
+The corresponding point $\bm R=\Im[\quat q \bm r \quat q^{-1}]$ in the inertial frame satisfies $\dot{\bm R} = \Im[\quat q(\bm \omega \times \bm r )\quat q^{-1}]$.
+Furthermore, we can demand that $\bm \omega \perp \bm r$ so that $\bm \omega \times \bm r = \Im[\quat \omega \quat r]$.
+We obtain another equation for $\dot{\bm R}$ by differentiating equation \ref{eqn:quat-rot} with $\dot{\bm r} = 0$.
 Setting these equal,
@@
 \end{equation}
-Substituting $\mathbf r \rightarrow \quat q^{-1}\mathbf R \quat q$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}] = 0$,
+Substituting $\bm r \rightarrow \quat q^{-1}\bm R \quat q$ and acknowledging that $\Re[\dot{\quat q} \quat q^{-1}] = 0$,
 \begin{equation}
-  \dot{\quat q} \quat q^{-1}\mathbf R + \mathbf R \quat q \dot{\quat q}^{-1} = 2\dot{\quat q}\quat q^{-1}\quat R = \quat q\quat \omega \quat q^{-1}\mathbf R.
+  \dot{\quat q} \quat q^{-1}\bm R + \bm R \quat q \dot{\quat q}^{-1} = 2\dot{\quat q}\quat q^{-1}\quat R = \quat q\quat \omega \quat q^{-1}\bm R.
 \nonumber
 \end{equation}
-Since $\mathbf R$ is arbitrary, this simplifies to
+Since $\bm R$ is arbitrary, this simplifies to
 \begin{equation}
@@
 \end{eqnarray}
-The components of $\mathbf \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
+The components of $\bm \tau$ are given by equation \ref{eqn:tidal-torque}, which was also in the body-fixed frame.
 
 \subsection{Initial Values}
-We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\mathbf \omega \parallel \unit z$.
-The initial conditions are therefore that $\mathbf \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\mathbf \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\alpha$.
+We assume that the asteroid begins the simulation in its minimum energy configuration; that is, with $\bm \omega \parallel \unit z$.
+The initial conditions are therefore that $\bm \omega = \omega \unit z$, and the quaternion is fixed to rotate $\hat z$ to $\bm \Omega$ in the inertial frame, which fixes Euler angles $\beta$ and $\alpha$.
 The third Euler angle $\gamma$ represents the initial roll of the asteroid, and therefore cannot be determined from physical data.
@@
 The orbit orientation is fixed to lie in the $\unit X-\unit Y$ plane, with pericenter lying on $\hat X$.
-The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\mathbf r(t=0) = r_p \unit X$ and $\mathbf v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
+The position of the satellite as a function of time is therefore generated by numerically integrating the Newtonian equation of motion (equation \ref{eqn:translaton-eom}) from initial values $\bm r(t=0) = r_p \unit X$ and $\bm v(t=0)=\unit Y \sqrt{v_\infty^2 + 2G\mu_M / r_p}$
 
@@
 Equations \ref{eqn:quat-eom} and \ref{eqn:omega-eom} were then integrated by the Runge-Kutta fourth order method with a time step of \jtd{describe} seconds, with a custom implementation of the spherical harmonics and Wigner-D matrices to improve runtime.
-At fixed time intervals of one cadence, the rotational velocity in the body-fixed frame $\mathbf\omega_{xyz}$ was converted via equation \ref{eqn:quat-rot} to the inertial frame to produce the synthetic data set.
+At fixed time intervals of one cadence, the rotational velocity in the body-fixed frame $\bm\omega_{xyz}$ was converted via equation \ref{eqn:quat-rot} to the inertial frame to produce the synthetic data set.
 
@@
 \begin{equation}
-\mathcal{L}(\mathbf \theta) \propto \text{exp}\parens{-\frac{1}{2}(\mathbf \theta-\mathbf \theta_0)^T \Sigma (\mathbf \theta-\mathbf \theta_0)}.
+\mathcal{L}(\bm \theta) \propto \text{exp}\parens{-\frac{1}{2}(\bm \theta-\bm \theta_0)^T \Sigma (\bm \theta-\bm \theta_0)}.
 \end{equation}
 We may change bases into a frame in which the parameters are uncorrelated by multiplying by $V^T$, where $V$ is the matrix of eigenvectors of $\Sigma$.
-Populating the walkers in this uncorrelated space according to Gaussian standard deviations given by the eigenvalues of $\Sigma$, we can convert these walkers back to $\mathbf \theta$-space by multiplying by $V$.
+Populating the walkers in this uncorrelated space according to Gaussian standard deviations given by the eigenvalues of $\Sigma$, we can convert these walkers back to $\bm \theta$-space by multiplying by $V$.
 In practice, we only compute the components of $\Sigma$ for parameters that are found in the same minimization step; for example, we do not compute the entries of $\Sigma$ corresponding to $K_{20}$ and $K{30}$, setting it equal to zero instead.
@@
 
-With the initial walkers distributed, we compute the posterior probability distribution of $\mathbf \theta$ given flat priors in the range outlined above for each parameter.
+With the initial walkers distributed, we compute the posterior probability distribution of $\bm \theta$ given flat priors in the range outlined above for each parameter.
 We run the MCMC until results converge (defined as the condition that the autocorrelation time is less than one hundredth of the current iteration number and that the fractional difference between autocorrelation times is under 1\%), or for 100,000 iterations, whichever is smaller.
@@
 \begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \mathrm{\exp}\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}
 \end{equation}
@@
 
-Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\mathbf \omega$.
-This same rotation matrix is then used to rotate the random vector $\mathbf \Omega = \rho \omega (\sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z)$ to the randomized velocity vector.
+Practically, the randomization of the data is done by creating a rotation matrix $M$ that rotates $\unit Z$ to the true rotational velocity vector $\bm \omega$.
+This same rotation matrix is then used to rotate the random vector $\bm \Omega = \rho \omega (\sin \Theta \cos\Phi \unit X + \sin \Theta \sin \Phi\unit Y + \cos \Theta\unit Z)$ to the randomized velocity vector.
 Here, $\Phi$ is a uniformly random variable in the range $[0, \pi)$.
@@
 \end{equation}
-where $\theta$ and $\phi$ are the spherical coordinates of the original velocity vector $\mathbf \omega.$
+where $\theta$ and $\phi$ are the spherical coordinates of the original velocity vector $\bm \omega.$
 
-Equation \ref{eqn:rotate-uncertainty-matrix} is sufficient to randomize synthetic data, but an analytical expression for the coordinates of $\mathbf \omega$ is required to define the $\chi^2$ value used for fitting.
+Equation \ref{eqn:rotate-uncertainty-matrix} is sufficient to randomize synthetic data, but an analytical expression for the coordinates of $\bm \omega$ is required to define the $\chi^2$ value used for fitting.
 We approximate the distribution of each spin coordinate as normal, with covariance given by the covariance of the true distribution.
@@
 \begin{equation}
-\text{Cov}(\mathbf \omega) = \frac{1}{2}e^{-\sigma_\theta^2 + 2 \sigma_\rho^2}\brackets{\parens{e^{-\sigma_\theta^2}-2e^{-\sigma_\rho^2}+\textrm{cosh}(\sigma_\theta^2)} \parens{\begin{array}{ccc}
+\text{Cov}(\bm \omega) = \frac{1}{2}e^{-\sigma_\theta^2 + 2 \sigma_\rho^2}\brackets{\parens{e^{-\sigma_\theta^2}-2e^{-\sigma_\rho^2}+\textrm{cosh}(\sigma_\theta^2)} \parens{\begin{array}{ccc}
 \omega_x^2 & \omega_x \omega_y& \omega_x \omega_z\\
@@
     \fig{nominal-covariance.pdf}{0.5\textwidth}{
-        (a) Pairwise-distributions of components of $\mathbf \omega$ show good agreement between the true distribution and the Gaussian approximation.
+        (a) Pairwise-distributions of components of $\bm \omega$ show good agreement between the true distribution and the Gaussian approximation.
       }
@@
     }
-  \caption{The true distribution (blue) and the Gaussian approximation (orange) with the same covariance (orange)  for the components of angular velocity $\mathbf \omega$ under the nominal uncertainty method.}
+  \caption{The true distribution (blue) and the Gaussian approximation (orange) with the same covariance (orange)  for the components of angular velocity $\bm \omega$ under the nominal uncertainty method.}
   \label{fig:nominal-spin-distro}
@@
 If two components of $\omega$, the third component is known up to its sign except when $\sigma_\rho \neq 0$.
-However, the covariance matrix of $\mathbf \omega$ does not capture this, nor do the distributions displayed in figure \ref{fig:nominal-spin-distro} (a).
+However, the covariance matrix of $\bm \omega$ does not capture this, nor do the distributions displayed in figure \ref{fig:nominal-spin-distro} (a).
 Therefore, when $\sigma_\rho \simeq 0$, the Gaussian likelihood function may poorly represent the model.
-To demonstrate this, we show a histogram of the norm of $\omega$ for the Gaussian approximated distribution and the true distribution in figure  \ref{fig:nominal-spin-distro} (b), which demonstrates that statistics involving all three components of $\mathbf \omega$ can differ highly between the approximation and the true distribution.
+To demonstrate this, we show a histogram of the norm of $\omega$ for the Gaussian approximated distribution and the true distribution in figure  \ref{fig:nominal-spin-distro} (b), which demonstrates that statistics involving all three components of $\bm \omega$ can differ highly between the approximation and the true distribution.
 
@@
 \begin{equation}
-\chi^2 = \sum_{i=0} (\mathbf \omega_i^* - \mathbf \omega_i)^T\text{Cov}^{-1}(\mathbf\omega^*_i)(\mathbf \omega_i^* - \mathbf \omega_i)
+\chi^2 = \sum_{i=0} (\bm \omega_i^* - \bm \omega_i)^T\text{Cov}^{-1}(\bm\omega^*_i)(\bm \omega_i^* - \bm \omega_i)
 \label{eqn:chisq-nominal}
 \end{equation}
-where $\mathbf \omega_i$ is the $i$th expected spin and $\mathbf \omega_i^*$ is the data.
-We also refer to the reduced chi squared, $\chi^2_r = \chi^2 / (3N)$, where $N$ is the number of $\mathbf \omega_i$ in the data set.
+where $\bm \omega_i$ is the $i$th expected spin and $\bm \omega_i^*$ is the data.
+We also refer to the reduced chi squared, $\chi^2_r = \chi^2 / (3N)$, where $N$ is the number of $\bm \omega_i$ in the data set.
+
+\jtd{All this text is explanatory material for what I've been doing, but in the paper only the true likelihood will be there probably.}
+
+Given the above explanation of the nominal uncertainty method, we define the likelihood of our data to be
+\begin{equation}
+  \ln \mathcal{L} = \sum_{i = 0}-\frac{\cos^{-1} (\bm \omega_i^* \cdot \bm \omega_i)^2}{2\sigma_\theta^2}-\frac{\ln \parens{\omega_i^* /\omega_i}^2}{2\sigma_\rho^2} - \ln\frac{\omega_i^*}{\omega_i}.
+  \label{eqn:log-likelihood}
+\end{equation}
+Sometimes we compute the value $\chi^2_r = -2\ln \mathcal{L} / N$ where $N$ is the number of spin vectors in the data set.
+For uncorrelated uncertainty \jtd{Check the assumptions on which the chi squared distribution is met} we expect $\chi^2 \approx 1$ for large $N$.
+However, due to the highly correlated nature of our data, this limit occurs in our data set.
 
@@
 \subsection{Planet with a Moon: Distant Flyby}
-Consider a system with a moon of mass $\mu_{o}$ at constant displacement $\mathbf R$ from the central body.
+Consider a system with a moon of mass $\mu_{o}$ at constant displacement $\bm R$ from the central body.
 We assume that both the planet and the moon are spherical.
@@
 \begin{equation}
-R_{\ell m}(\mathbf R + \mathbf R') = \sum_{\ell' = 0}^\ell \sum_{m'=-\ell'}^\ell R_{\ell' m'}(\mathbf R') R_{\ell-\ell', m-m'}(\mathbf R)
+R_{\ell m}(\bm R + \bm R') = \sum_{\ell' = 0}^\ell \sum_{m'=-\ell'}^\ell R_{\ell' m'}(\bm R') R_{\ell-\ell', m-m'}(\bm R)
 \end{equation}
@@
 \begin{equation}
-J_{\ell m} = \frac{1}{(\mu_M+\mu_0) a_M^\ell}\brackets{\delta_{\ell 0}\delta_{m0}\mu_M + \int_\mathcal{P} d^3 r' \rho_o(\mathbf r') R_{\ell m}(\mathbf R + \mathbf r')}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0) a_M^\ell}\brackets{\delta_{\ell 0}\delta_{m0}\mu_M + \int_\mathcal{P} d^3 r' \rho_o(\bm r') R_{\ell m}(\bm R + \bm r')}
 \end{equation}
 \begin{equation}
-J_{\ell m} = \frac{1}{(\mu_M+\mu_0)}\brackets{\mu_M\delta_{\ell 0}\delta_{m0} + \mu_o \frac{R_{\ell m}(\mathbf R)}{ a_M^\ell}}
+J_{\ell m} = \frac{1}{(\mu_M+\mu_0)}\brackets{\mu_M\delta_{\ell 0}\delta_{m0} + \mu_o \frac{R_{\ell m}(\bm R)}{ a_M^\ell}}
 \end{equation}
@@
 The formalism above cannot be extended to write one set of $J_{\ell m}$ for both the moon and planet.
-To do this, we generate two separate paths of $\mathbf D(t)$, one pointing from the central body to the asteroid and one pointing from the moon the asteroid.
+To do this, we generate two separate paths of $\bm D(t)$, one pointing from the central body to the asteroid and one pointing from the moon the asteroid.
 Both are defined in the inertial reference frames.
@@
 Figure \ref{fig:probe-space-corr} demonstrates that the parameters are generally correlated.
-Specficically, $\gamma_0$ and $|K_{22}|$ are strongly correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
+Specficically, $\gamma_0$ and $|K_{22}|$ are correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
 Likewise, for the correlation of $a/c$ and $b/c$ with $\gamma_0$.
-$\mathrm{Corr}(\v, K_{20})$ shows slightly different behavior, since they are still correlated for asteroids with $a=b$.
-However, the correlation still increases for highly asymmetric asteroids.
-The correlation between shape parameters $K_{20}$ and $K_{22}$ is often near zero except in highly asymmetric asteroids, but the correlation between $a/c$ and $b/c$ is rarely zero; these correlate for $a\approx b$ and anti-correlate for $a \not \approx b$.
-The $K_{\ell m}$ coordinates may therefore be a better lens through which to view asteroid shape, due to their low correlation.
+$\mathrm{Corr}(\v, K_{20})$ are less correlated however.
+$K_{20}$ and $K_{22}$ are strongly correlated in general as are $a/c$ and $b/c$.
 
@@
     \hline \hline
-    Reference point & $\sigma(\gamma_0)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\gamma_0, K_{22})}$ & $\mathrm{Corr(\gamma_0, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
-    Symmetric: $a=b$ &  &  &  &  &  & \\
-    &  &  &  &  &  & \\
-    Asymmetric: $a<b$ &  &  &  &  &  & \\
-    &  &  &  &  &  & \\
-    Asymmetric: $a>b$  &  &  &  &  &  & \\
-    &  &  &  &  &  & \\
+    Benchmark configurations & $\sigma(\gamma_0)$ / $\sigma_\theta$ & $\sigma(K_{22}\ [a/c])$ / $\sigma_\theta$ & $\sigma(K_{20}\ [b/c])$ / $\sigma_\theta$ & $\mathrm{Corr(\gamma_0, K_{22})}$ & $\mathrm{Corr(\gamma_0, K_{20})}$ & $\mathrm{Corr(K_{22}, K_{20})}$ \\ \hline
+    Symmetric: $a=b$ & 36 & $1.9 \times 10^{-6}$ & $1.7 \times 10^{-5}$ & -0.40 & 0.36 & 0.19\\%24
+    & 36 & $9.4\times 10^{-5}$ & $1.9\times 10^{-4}$ & -0.42 & -0.29 & 0.96 \\
+    Asymmetric: $a<b$ & $1.6 \times 10^{-5}$ & $1.5 \times 10^{-6}$ & $5.4 \times 10^{-6}$ & 0.32 & -0.0053 & 0.88\\%94
+    & $1.6\times 10^{-5}$ & $9.4\times 10^{-5}$ & $1.8\times 10^{-4}$ & 0.082 & -0.019 & 0.99\\
+    Asymmetric: $a>b$  & $1.5 \times 10^{-5}$ & $9.1 \times 10^{-7}$ & $4.8 \times 10^{-6}$ & -0.58 & 0.017 & 0.15 \\%101
+    & $1.5\times 10^{-5}$ & $1.5\times 10^{-4}$ & $1.0\times 10^{-4}$ & -0.049 & 0.061 & 0.98\\
   \end{tabular}
-  \caption{Values for the standard deviation and correlation of $\gamma_0$, $K_{22}$, and $K_{20}$ (top entry of each row) or $\gamma_0$, $a/c$, and $b/c$ respectively (bottom entry of each row) for the symmetric and asymmetric reference points.}
+  \caption{Values for the standard deviation and correlation of $\gamma_0$, $K_{22}$, and $K_{20}$ (top entry of each row) or $\gamma_0$, $a/c$, and $b/c$ respectively (bottom entry of each row) for the symmetric and asymmetric reference points.
+The large $\sigma(\gamma_0)$ for the symmetric benchmark reflects the fact that $\gamma_0$ is not defined for a symmetric body, and the posterior probability distribution is poorly constrained.}
   \label{tab:probe-space-refernece-var-covar}
@@
 
-\jtd{Running Jan 11?}
+\jtd{Running Jan 13}
 
@@
 Since the density distribution of the asteroid has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
-As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\mathbf r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
+As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\bm r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
 Then we have
@@
 
-To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\mathbf r)$.
+To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\bm r)$.
 In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}) or by using a numerical approach to find a more characteristic density distribution (section \ref{sec:numerical-density}).
@@
 \begin{equation}
-  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\mathbf r)
-   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \mathbf v (\mathbf r)
-    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \mathbf r \cdot \mathbf v (\mathbf r)
+  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\bm r)
+   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \bm v (\bm r)
+    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
 \end{equation}
-where $\mathbf v (\mathbf r) = \unit r R_{\ell m} (\mathbf r) r / (3+\ell) $.
-We know the area element satisfies $d^2 \mathbf r = \partial \mathbf r / \partial \theta \times \partial \mathbf r / \partial \phi$ in our coordinates, and when dotted with $\mathbf v \propto \unit r$, this gives
+where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $.
+We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \propto \unit r$, this gives
 \begin{equation}
@@
 Now suppose the shape of the asteroid is known, perhaps by a simplifying guess or perhaps by direct observation during a flyby.
-Then a density distribution $\rho(\mathbf r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
-Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\mathbf r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
+Then a density distribution $\rho(\bm r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
+Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
 Thus, $K_{\ell m} = \sum_{\ell' m'} C_{\ell' m'} B_{\ell \ell' m m'}$ where
 \begin{equation}
-  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\mathbf r) R_{\ell' m')}(\mathbf r)
+  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m')}(\bm r)
   \label{eqn:blm}
@@
 can be precomputeded due to the shape of $\mathcal{A}$ being known.
-If we write $K_{\ell m}$ as a vector $\mathbf K$ and similarly for $\mathbf C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\mathbf K = \hat B \mathbf C$.
+If we write $K_{\ell m}$ as a vector $\bm K$ and similarly for $\bm C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\bm K = \hat B \bm C$.
 It follows that the density distribution coefficients are given by
 \begin{equation}
-\mathbf C = \hat B^{-1} \mathbf K.
+\bm C = \hat B^{-1} \bm K.
 \end{equation}
-The scale parameter $a_m$ can be computed from the resulting values of $\mathbf C$ and the distance scale can be adjusted until $a_m$ matches the true value.
+The scale parameter $a_m$ can be computed from the resulting values of $\bm C$ and the distance scale can be adjusted until $a_m$ matches the true value.
 As before, $\mu_m$ is a free parameter representing the impossibility of fitting for the mass of the asteroid.
@@
 Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
-Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\mathbf r)$ exists such that $\mathds{1}(\mathbf r) = 1$  inside the asteroid and 0 elsewhere.
+Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\bm r)$ exists such that $\mathds{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
 Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution.
@@
 \begin{enumerate}
-\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\mathbf r_i$ such that $\mathds{1}(\mathbf r_i) = 0.$
+\item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathds{1}(\bm r_i) = 0.$
 \item Construct $n$ regions $\mathcal{R}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
 Suppose $R_i$ has uniform density $\rho_i$.
-\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\mathbf r)$.
+\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\bm r)$.
 Once again, $\mu_m$ is a free parameter and units can be chosen such that $a_m=1$.
 Then %we can write $K_{\ell m} = \sum_i \rho_i \overline K_{\ell m}^i$.
-\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$.
-Invert it to get $\mathbf \rho = \hat {\overline K}^{-1} \mathbf K$.
+\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$. Invert it to get $\bm \rho = \hat {\overline K}^{-1} \bm K$.
 \item Go back to step 1 and compute new density maps with new draws of seed points.
@@
 
-\bibliography{asteroids}{}
+\bibliography{blank}{}
 \bibliographystyle{aasjournal}

### 2022-01-15 summaries/21-11/21-11.tex
Achieve fewer minima and remove the terminate.py code from fit.py

@@
   \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho$ = 0.
-  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a 1:2:$-2$ ratio.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho / \sigma_\theta = 10^{-5}$.
+  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
   \item An asteroid with radius $a_m = 1\siunit{km}$ and $K_{3m}=0$.
@@
   \includegraphics[width=0.7\textwidth]{example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for a symmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.83.}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
   \label{fig:example-residuals}
@@
   \includegraphics[width=\textwidth]{example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for a symmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
 Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).

### 2022-01-15 code/fit_resolved/fit.py

@@ -383,7 +383,6 @@ def get_minimum(arg):
             if np.any(np.asarray(new_evals) < 0.0):
                 return None, None, None, None
             else:
-                print(l)
                 logging.warning("Allowing the Hessian to pass with reversed first eigenvalue.")
 
         if l == 3:
@@ -465,7 +464,8 @@ def minimize(l, fix_theta):
             continue
         choose = True
         for distinct_theta, _, _, _ in distinct_results:
-            if np.all((np.abs(distinct_theta - theta) < MIN_THETA_DIST)[1:]):
+            if np.all((np.abs(distinct_theta - theta) < MIN_THETA_DIST)[1:3]):
+                # Only scan for theta 1 and 2 (K2m)
                 choose = False
                 break
         if choose:
@@ -610,56 +610,3 @@ def mcmc_fit(theta_start, evals, evecs, index):
 
 for i, (theta, evals, evecs) in enumerate(kernel):
     mcmc_fit(theta, evals, evecs, i)
-
-
-####################################################################
-# Process data
-####################################################################
-
-i = 0
-while True:
-    logging.info("Showing i = {}".format(i))
-    try:
-        disp = display.Display("{0}".format(output_name), "{0}-{1}".format(output_name, i))
-    except Exception as e:
-        if i == 0:
-            raise e
-        break
-    disp.show_redchi()
-    disp.show_params()
-    disp.show_corner()
-    disp.show_compare()
-    disp.show_results()
-    plt.show()
-    if not collect.collect(output_name + "-" + str(i), output_name):
-        break
-    del disp
-    i += 1
-
-####################################################################
-# Save samples
-####################################################################
-
-for index in range(len(kernel)):
-    reader = emcee.backends.HDFBackend(output_name+"-{}.h5".format(index), read_only=True)
-
-    try:
-        tau = reader.get_autocorr_time()
-        burnin = int(2 * np.max(tau))
-        thin = DEFAULT_THIN#int(0.5 * np.min(tau))
-    except:
-        print("Could not find autocorrelation time because the chain is too short.")
-        thin = DEFAULT_THIN
-        burnin = 1000
-
-    samples = reader.get_chain(discard=burnin, thin=thin)
-    log_prob_samples = -reader.get_log_prob(discard=burnin, thin=thin) / 3 / n_data 
[…]

### 2022-01-17 summaries/21-11/21-11.tex
Added references to paper

@@
 \item CNEOS: 4 asteroids $D > 100 m$ are coming to within 1 LD of Earth in the next 10 years, 29 with $D > 10 m$.
+\item Moskowitz survey of Duende: \cite{BENSON2020113518} with companion observational article \cite{MOSKOVITZ2020113519}.
+Demonstrates that moment of inertia can be extracted from a tumbling asteroid via lightcurve analysis in the zero-torque regime (fourier transform of lightcurve to pick up on two frequencies and assign precession and nutation frequencies to them.) Assumes constant geometry.
+\item Study of asteroid binary to extract density \cite{DESCAMPS2020113726}
+\item Scheeres theoretical paper \cite{HouMar2017} detailing the different forces and torques felt by an asteroid.
+\item Paper stating in general that asteroids can be tidally disrupted on hyperbolic flyby. \cite{SCHEERES2000106}, plus similar paper \cite{RICHARDSON199847} for tidal disruption
+\item Another theoretical paper \cite{BOUE2009750} inspired by Paul
+\item Apophis will definitely pass by Earth and will definitely significantly change its rotation state, but will not undergo tidal disruption. \cite{SCHEERES2005281}
 \end{itemize}
@@
 \subsection{Tidal Torque}
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, sometimes in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+We present a novel derivation of the tidal torque experienced by a rigid body in a gravitational field of another in terms of (complex) spherical harmonic coefficients of the bodies' mass distributions, which are closely related to their moments of inertia.
+This formulation of the problem will be more useful for this study.
+The calculation is performed to all orders of distance between the two bodies.
+
 We start by expressing the gravitational potential energy field of the central body in its most general form:
@@
 With this definition of $a_m$, and an arbitrary definition of $a_M$ which may be taken to be similar to equation \ref{eqn:am} or a more convenient unit such as the central body radius, the parameters $J_{\ell m}$ and $K_{\ell m}$ of equation \ref{eqn:jlm} are completely defined.
-Note that $a_m$ is similar to the radius of the asteroid; if the asteroid is a sphere of uniform density and radius $r$, then $a_m = r\sqrt{3/5}$.
+Note that $a_m$ is roughly to the radius of the asteroid under certain assumptions; if the asteroid is a sphere of uniform density and radius $r$, then $a_m = r\sqrt{3/5}$.
 
@@
 \end{equation}
-where the $\delta$s are Kroneker deltas.
+where the $\delta$s are Kronecker deltas.
 It is apparent that if $a_M^\ell$ remains the radius of the planet, $|J_{\ell m}| \rightarrow \infty$ as $\ell \rightarrow \infty$.
@@
 Figure \ref{fig:probe-space-corr} demonstrates that the parameters are generally correlated.
-Specficically, $\gamma_0$ and $|K_{22}|$ are correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
+Specifically, $\gamma_0$ and $|K_{22}|$ are correlated for large $|K_{22}|$ which corresponds to highly asymmetric asteroids.
 Likewise, for the correlation of $a/c$ and $b/c$ with $\gamma_0$.
-$\mathrm{Corr}(\v, K_{20})$ are less correlated however.
+$\mathrm{Corr}(\gamma_0, K_{20})$ is less, however.
 $K_{20}$ and $K_{22}$ are strongly correlated in general as are $a/c$ and $b/c$.
@@
 
-Figure \ref{fig:example-residuals} shows the data with the best-fit overlayed and the residuals.
+Figure \ref{fig:example-residuals} shows the data with the best-fit overlaid and the residuals.
 Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix --- i.e., 1-$\sigma$ uncertainties.
@@
 
-\bibliography{blank}{}
+\bibliography{asteroids}{}
 \bibliographystyle{aasjournal}

### 2022-01-17 summaries/21-11/21-11.tex
Updated summary for probe sigma

@@
     Asymmetric: $a>b$  & $1.5 \times 10^{-5}$ & $9.1 \times 10^{-7}$ & $4.8 \times 10^{-6}$ & -0.58 & 0.017 & 0.15 \\%101
-    & $1.5\times 10^{-5}$ & $1.5\times 10^{-4}$ & $1.0\times 10^{-4}$ & -0.049 & 0.061 & 0.98\\
+    & $1.5\times 10^{-5}$ & $1.5\times 10^{-4}$ & $1.0\times 10^{-4}$ & -0.049 & 0.061 & 0.98\\ \hline
   \end{tabular}
@@
 
-\jtd{Running Jan 13}
+Depending on the size of the asteroid, its orbital elements, and the availability of observation, uncertainty on the rotational pole of the asteroid is expected to vary between flybys.
+A detailed model of uncertainty in the rotational pole of the asteroid (a model that might simulate a full lightcurve, for example) is beyond the scope of this paper.
+However, in this section we demonstrate how the uncertainty in the fit parameters is governed by the experimental uncertainty in rotational pole $\sigma_\theta$ as a rule-of-thumb to guide future investigation.
+
+We represent 1-$\sigma$ uncertainty in the fit parameters as the difference between the 84th or 15th percentile of the marginal posterior PDF for each fit parameter and its mean.
+For a multivariate gaussian posterior PDF (which must also have gaussian marginal PDFs), this 1-$\sigma$ uncertainty is exactly the standard deviation of the marginal PDF.
+We perform a similar exercise for the 2-$\sigma$ uncertainty.
+
+These uncertainties in fit parameters are observed to scale precisely with $\sigma_\theta$, except where $\sigma_\theta$ is large enough that the fit parameter uncertainty is comparable to the size of the prior PDF.
+Figure \ref{fig:probe-sigma} shows the $\sigma / \sigma_\theta$ ratio for all 10 of the first two orders of parameters ($\gamma_0$, $K_{2m}$, and $K_{3m}$).
+The ratio of $\sigma_\rho$ to $\sigma_\theta$ is kept constant.
+The result is executed for the asymmetric asteroid model.
+The figure demonstrates that the ratio $\sigma/\sigma_\theta$ is constant for all values of $\sigma_\theta$ except large values.
+It also demonstrates that the posterior marginal PDFs are largely symmetric, in that the lower uncertainty is roughly equal to the upper uncertainty.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{probe-sigma.pdf}
+  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of $\sigma_\theta$.
+Except at large $\sigma_\theta$, the ratio is observed to be constant.
+The asymmetric asteroid benchmark is used.
+Values of the ratio for other asteroid models can be computed from figure \ref{fig:probe-space-sigma}.}
+  \label{fig:probe-sigma}
+\end{figure}
+
+Due to the constancy of the ratio of fit to observational uncertainty, the ratio can be extracted for other asteroid configurations from figure \ref{fig:probe-space-sigma}, and we are not much concerned with the value of $\sigma_\theta$ used throughout this paper because we are aware that results can be easily rescaled.
+
+\subsection{Dependence on cadence}
 
@@
 \jtd{The period is also important, but probably depends too much on the start of the simulation. I'm more interested in the spin pole.}
-
-\subsection{Dependence on cadence}
 

### 2022-01-18 summaries/21-11/21-11.tex
Updated summary for oblateness

@@
 \subsection{Exotic scenarios}
+Until this point, we have assumed an asteroid flyby of Earth because observations are most plentiful for near-Earth asteroids.
+However, it is worth considering how observations taken around another planet --- by a large Earth-orbiting telescope or an interplanetary mission, for instance --- could affect the efficacy of this model.
+
+In particular, we consider how high planetary oblateness and the presence of moons affects the torque dynamics of asteroids.
+Other central body parameters worth of mention are the central body mass and radius.
+However, the dependence of tidal torque on these properties is clear from equation \ref{eqn:tidal-torque} without requiring a simulation.
+If the central planet mass $\mu_M$ is increased, tidal torque increases uniformly and we expect greater precision in our measurements.
+If the planetary radius is increased, we also expect an increase in the distance $D$ to the planet.
+Therefore, we consider changes in $(a_M/D)$.
+Each $J_{\ell m}$ term is multiplied by a factor of $(a_M/D)^\ell$, so an increase in planetary radius without a change in mass only affects the subdominant terms of \ref{eqn:tidal-torque}.
 
 \subsubsection{Oblate planet}
+
+Depending on the composition and rotation rate of the planet which the asteroid is encountering, the oblateness (equivalently, the planet's $J_{20}$ or $J_2$ value) may vary.
+The $J_{1m}$ values are fixed at zero by the constraint that the center of mass of the central body must be at the origin.
+Equation \ref{eqn:tidal-torque} shows that the presence of a large $J_{20}$ value introduces a second factor through which the $K_{2m}$ parameters can affect the tidal torque, which is damped by an extra factor of $D^{-2}$ compared to the $J_{00}$ term.
+In this section, we ask what can be gained by a large oblateness.
+
+Another factor work consideration is the presence of a planetary ring, which will affect $J_{2}$.
+However, using the properties of Saturn's rings as an benchmark, we compute that the oblateness of the planet far outstrips the increase in $J_{2}$ caused by the ring, so we ignore this scenario henceforth.
+\jtd{Cite an appendix?}
+
+For our purposes, we define oblateness to be $\epsilon = (I_z - I_x)/(\mu_M a_M^2)$ for central body moments of inertia $I_{x,y,z}$ where $I_x = I_y$ (that is, $J_{22} = 0$) and $a_M$ is the true radius of the body, not the value defined in equation \ref{eqn:am}.
+Expressed in terms of $J_{\ell m}$, this is $\epsilon = -2J_{20}$.
+Given this conversion between $\epsilon$ and $J_2$, we generate simulated data sets and fit $K_{2m}$ parameters to them for logarithmically spaced values of $\epsilon$ between $10^{-4}$ and $10^{-1}$.
+The 68th and 95th percentiles deviations, computed as in figure \ref{fig:probe-space-sigma}, are shown in figure \ref{fig:oblateness}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{oblateness.pdf}
+  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet.
+Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
+  \label{fig:oblateness}
+\end{figure}
+
+Figure \ref{fig:oblateness} shows no strong dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{2}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term.
+However, the fit parameter uncertainty does slightly decrease as oblateness increases on further study.
+\jtd{Give some quotes}.
+Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees.
+It is therefore reasonable to include that the presence of a large $J_2$ will not substantially affect the ability of this model to constrain asteroid interiors.
+
+Figure \ref{fig:oblateness} also includes reference Solar System $J_2$ values listed in \cite{pater_lissauer_2015} for comparison.
+However truly comparing these reference oblatenesses is complicated by the fact that the $J_2$ term of equation \ref{eqn:tidal-torque} is modified by a factor of $(a_M/D)^2$.
+If the perigee of the orbit is fixed at the benchmark value of 5 planetary radii, we expect this term to remain roughly comparable between the different reference planets.
+However, if $a_M / D$ increases for larger planet mass, which seems likely given that a larger planet presents a larger target, we expect the large-mass reference planets to show more dependence on oblateness than figure \ref{fig:oblateness} suggests.
+In general, larger mass planets are gas giants and therefore have higher oblatenesses than rocky planets.
+Therefore, we expect more dependence on oblateness for gas giants.
 

### 2022-01-18 summaries/21-11/21-11.tex
Corrected cited oblatenesses

@@
 For our purposes, we define oblateness to be $\epsilon = (I_z - I_x)/(\mu_M a_M^2)$ for central body moments of inertia $I_{x,y,z}$ where $I_x = I_y$ (that is, $J_{22} = 0$) and $a_M$ is the true radius of the body, not the value defined in equation \ref{eqn:am}.
+(Some sources such as \cite{pater_lissauer_2015} take this definition of $\epsilon$ as their definition of $J_2$.
 Expressed in terms of $J_{\ell m}$, this is $\epsilon = -2J_{20}$.
-Given this conversion between $\epsilon$ and $J_2$, we generate simulated data sets and fit $K_{2m}$ parameters to them for logarithmically spaced values of $\epsilon$ between $10^{-4}$ and $10^{-1}$.
+Given this conversion between $\epsilon$ and $J_{20}$, we generate simulated data sets and fit $K_{2m}$ parameters to them for logarithmically spaced values of $\epsilon$ between $10^{-4}$ and $10^{-1}$.
 The 68th and 95th percentiles deviations, computed as in figure \ref{fig:probe-space-sigma}, are shown in figure \ref{fig:oblateness}.
@@
 
-Figure \ref{fig:oblateness} shows no strong dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{2}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term.
+Figure \ref{fig:oblateness} shows no strong dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{20}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term.
 However, the fit parameter uncertainty does slightly decrease as oblateness increases on further study.
@@
 Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees.
-It is therefore reasonable to include that the presence of a large $J_2$ will not substantially affect the ability of this model to constrain asteroid interiors.
+It is therefore reasonable to include that the presence of a large $J_{20}$ will not substantially affect the ability of this model to constrain asteroid interiors.
 
-Figure \ref{fig:oblateness} also includes reference Solar System $J_2$ values listed in \cite{pater_lissauer_2015} for comparison.
-However truly comparing these reference oblatenesses is complicated by the fact that the $J_2$ term of equation \ref{eqn:tidal-torque} is modified by a factor of $(a_M/D)^2$.
+Figure \ref{fig:oblateness} also includes reference Solar System $J_{2}$ values listed in \cite{pater_lissauer_2015} for comparison.
+However truly comparing these reference oblatenesses is complicated by the fact that the $J_{20}$ term of equation \ref{eqn:tidal-torque} is modified by a factor of $(a_M/D)^2$.
 If the perigee of the orbit is fixed at the benchmark value of 5 planetary radii, we expect this term to remain roughly comparable between the different reference planets.

### 2022-01-19 summaries/21-11/21-11.tex
Updated oblateness plot

@@
   \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet.
+Linear best fit lines (black, dotted) are plotted over the 1- and 2-$\sigma$ uncertainties.
 Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
@@
 
-Figure \ref{fig:oblateness} shows no strong dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{20}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term.
+Figure \ref{fig:oblateness} shows a slight dependence of best-fit uncertainty on oblateness, as expected due to the weakness of the $J_{20}$ term in equation \ref{eqn:tidal-torque} compared to the dominant $J_{00}$ term.
 However, the fit parameter uncertainty does slightly decrease as oblateness increases on further study.
-\jtd{Give some quotes}.
-Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees.
-It is therefore reasonable to include that the presence of a large $J_{20}$ will not substantially affect the ability of this model to constrain asteroid interiors.
+The trend of the decrease is linear, as shown by the close agreement between the overlaid best fit linear trend between the 1- and 2-$\sigma$ best fit uncertainties to the measured values.
+We compute an average slope by assuming that the true 2-$\sigma$ slope is twice the true 1-$\sigma$ slope, arriving at $\Delta \sigma / \Delta \epsilon = 1.9 \times 10^{-5}$ for $\gamma_0$, $1.35 \times 10^{-5}$ for $K_{22}$, and $1.8 \times 10^{-4}$ for $K_{22}$.
+Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees, however fitting these extra parameters is computationally more expensive.
+\jtd{I could scan over them}.
 

### 2022-01-19 data/probe-ratio/compile.py

@@ -5,7 +5,7 @@ from matplotlib.lines import Line2D
 
 plt.style.use("jcap")
 
-param_names = ["\\gamma_0", "K_{20}", "K_{22}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
+param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
 
 percentiles = {}
 name_index = {}
@@ -66,30 +66,31 @@ for i in range(N_DIM):
     for f in percentiles.keys():
         param_data[:,name_index[f]] = percentiles[f][i]
     scale = 1
+    sigma_rho = sigma_rat * true_sigma
 
-    axs[i].plot(sigma_rat, (param_data[1]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].plot(sigma_rat, (param_data[-1]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].fill_between(sigma_rat, (param_data[1]-param_data[0]) / true_sigma * scale, 
-        (param_data[-1]-param_data[0]) / true_sigma * scale,  color=f"C{i}", alpha=0.3)
+    axs[i].plot(sigma_rho, (param_data[1]-param_data[0]) / sigma_rho * scale, color=f"C{i}", linewidth=1)
+    axs[i].plot(sigma_rho, (param_data[-1]-param_data[0]) / sigma_rho * scale, color=f"C{i}", linewidth=1)
+    axs[i].fill_between(sigma_rho, (param_data[1]-param_data[0]) / sigma_rho * scale, 
+        (param_data[-1]-param_data[0]) / sigma_rho * scale,  color=f"C{i}", alpha=0.3)
 
-    axs[i].plot(sigma_rat, (param_data[2]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].plot(sigma_rat, (param_data[-2]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].fill_between(sigma_rat, (param_data[2]-param_data[0]) / true_sigma * scale,
[…]

### 2022-01-20 summaries/21-11/21-11.tex
Added new density model and implemented the constant density model

@@
 
-\subsection{Exotic scenarios}
+\subsection{Oblate planet}
+
 Until this point, we have assumed an asteroid flyby of Earth because observations are most plentiful for near-Earth asteroids.
@@
 
-\subsubsection{Oblate planet}
-
 Depending on the composition and rotation rate of the planet which the asteroid is encountering, the oblateness (equivalently, the planet's $J_{20}$ or $J_2$ value) may vary.
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{oblateness.pdf}
+  \includegraphics[width=0.4\textwidth]{oblateness.pdf}
   \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet.
@@
 The trend of the decrease is linear, as shown by the close agreement between the overlaid best fit linear trend between the 1- and 2-$\sigma$ best fit uncertainties to the measured values.
-We compute an average slope by assuming that the true 2-$\sigma$ slope is twice the true 1-$\sigma$ slope, arriving at $\Delta \sigma / \Delta \epsilon = 1.9 \times 10^{-5}$ for $\gamma_0$, $1.35 \times 10^{-5}$ for $K_{22}$, and $1.8 \times 10^{-4}$ for $K_{22}$.
+We compute an average slope of the 1-$\sigma$ trend divided by the uncertainty for zero eccentricity as $\Delta \sigma / \Delta \epsilon / \sigma_{\epsilon=0}= -0.25$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{22}$.
 Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees, however fitting these extra parameters is computationally more expensive.
-\jtd{I could scan over them}.
 
@@
 
-\subsubsection{Distant moon}
-
-\subsubsection{Close moon}
-
 \section{Interpretation of the Fit Parameters}
@@
 Since the density distribution of the asteroid has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
-As an example, consider a spherical asteroid of radius $A$ and density distribution of the form $\rho(\bm r) = \sum_{\ell m} f_{\ell m}(r) Y_{\ell m}^*(\unit r)$.
-Then we have
-\begin{equation}
-K_{\ell m} = N_{\ell m} \frac{(-1)^m}{(\ell + m)!(\mu_m a_m^\ell)}\int_0^A r^{2+\ell} dr f_{\ell m}(r)
-\end{equation}
-where $N_{\ell m}$ is given by equation \ref{eqn:nlm}.
-Thus, $K_{\ell m}$ constrains only the integrals of $f_{\ell m}$, not the functions themselves.
-By relaxing the assumption that the asteroid is a sphere, even more degeneracy is introduced.
-
-To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for $\rho(\bm r)$.
-In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}) or by using a numerical approach to find a more characteristic density distribution (section \ref{sec:numerical-density}).
-
-\jtd{Not all of these models will be in the paper.
-This is a list of all the models I've thought of.
-I'll give some examples of applying these models to ``realistic'' asteroid density profiles (uniform, regolith over rock, etc) and see what they get, using that filter to describe the best.}
-
-\subsection{Constant Density Asteroid Model}
+
+To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for the density distribution under various assumptions.
+(sections \ref{sec:laplace-rho}, \ref{sec:numerical-density}, and \ref{sec:like-density}).
+In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}), by using a numerical approach to find an average density distribution (section \ref{sec:numerical-density}), or by associating a likelihood with each density distribution and taking the distribution with maximum likelihood (section \ref{sec:like-density}).
+
+\subsection{Constant Density Model}
 \label{sec:constant-density}
@@
 \end{equation}
-The integrand of each $K_{\ell m}$ therefore is proportional to $r(\theta, \phi)^(3+\ell)$ times constants and a spherical harmonic.
-We can write $r(\theta \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality, in which case equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
+The integrand of each $K_{\ell m}$ therefore is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
+We can write $r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality, in which case equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
 These integrals can be precomputed, since they are taken over the whole sphere $\theta \in (0, \pi)$ and $\phi \in (0, 2\pi)$.
 Equation \ref{eqn:constant-density-klm} can then be numerically solved to get $C_{\ell m}$.
-Specifically, the ratios of $K_{\ell m} / K_{\ell 0}$ can be solved for to eliminate the prefactor, then $\rho_m / \mu_m$ chosen such that $K_{00} = 1$.
-If $n$ values of $K_{\ell m}$ are known, then this method solves exactly for $n$ values of $C_{\ell m}$.
-\jtd{Implement this as a check.}
+To remove the degeneracy caused by the factor of $\rho_m$, we instead solve given constraints of $K_{\ell m} / K_{00}$.
+(Note that $K_{00} = \rho_m / \mu_m$).
+We force the solution to reproduce the correct value of $a_m^2/K_{00}$, defined in equation \ref{eqn:am}.
+We calculate this via
+\begin{equation}
+  a_m^2 = \frac{\rho_m}{\mu_m}\int_\mathcal{A} d^3 r r^2 = \frac{K_{00}}{5}\oint_\mathcal{A} d^2 \bm r \cdot \bm r(r^2) = \frac{K_{00}}{5}\int_0^\pi d\theta \sin\theta \int_0^{2\pi}d\phi r(\theta, \phi)^5.
+\end{equation}
+
+Unfortunately, this method is extremely slow.
+As mentioned above, the polynomial to be solved is order $3+\ell$ with $L^2$ $C_{\ell m}$ components, where $L$ is the maximum value of $\ell$ considered.
+This makes the number of terms $(L^2)^{3+L} = O(L^L)$.
+It is therefore exponential in the level of $L$ fitted.
 
@@
 \begin{equation}
-  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m')}(\bm r)
+  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m'}(\bm r)
   \label{eqn:blm}
@@
 
-\subsection{Fixed Surface Numerical Model}
+\subsection{Fixed Surface Ensemble Average Model}
 \label{sec:numerical-density}
@@
 \jtd{What does this give mathematically?}
+
+\subsection{Fixed Surface Maximum Likelihood Finite Element Model}
+\label{sec:like-density}
+We present a final method to extract the density distribution of an asteroid with fixed surface and parameters $K_{\ell m}$.
+Suppose the asteroid is divided into $N$ finite, constant density units with volume $\Delta V$ (a square grid, for instance).
+We further write the density of the $i$th unit as $\mu_m / (N \Delta V)C_i$, where $C_i$ is a free real parameter.
+Approximating each unit as small, we may write
+\begin{equation}
+  K_{\ell m} = \frac{1}{Na_m^\ell} \sum_i^N C_i R_{\ell m}(\bm r_i)
+  \label{eqn:klm-finite-constraint}
+\end{equation}
+where $\bm r_i$ are the centers of the units.
+Equation \ref{eqn:klm-finite-constraint} is a matrix equation, which can be written in the form $\bm K = A \bm C$ where $K_{\ell m}$ have been arranged as a vector and $\bm C$ contains the $N$ values of $C_i$.
+The matrix $A$ is non-square and cannot be inverted to find $\bm C$ because equation \ref{eqn:klm-finite-constraint} has many solutions.
+However, by imposing a probability distribution on $\bm C$, we find one configuration of $\bm C$ that maximizes likelihood.
+
+Suppose that the likelihood for $\bm C$ is multivariate-Gaussian distributed with no correlation, meaning that the log-likelihood is $\ln \mathcal{L} \propto -(x - \mu)^2$.
+We expect that $C_{i}$ average to one by the definition of $C_i$, so we set $\mu = 1$.
+Thus, the value of $\bm C$ we choose is the value which minimizes $|\bm C - \bm 1|^2$, where $\bm 1$ is an $N$-dimensional vector of only ones.
+
+This problem has already been solved in the context of the Moore-Penrose pseudoinverse.
+First, we define $\bm k = \bm K - A\bm 1$, so that if $\bm k = A \bm c$, then $\bm C = \bm c + 1$ solves equation \ref{eqn:klm-finite-constraint}.
+We therefore attempt to minimize $|\bm c|^2$ to maximize the likelihood of density distributions.
+
+The Moore-Penrose pseudoinverse of $A$ is defined as $A^+ = A^* (AA^*)^{-1}$, where $A^*$ is the adjoint of $A$.
+Ref.
+\cite{Barata2012} gives that all solutions to $\bm k = A \bm c$ are given by $\bm c = A^+\bm k + (\mathds{1}-A^+A)\bm z$ for any vector $\bm z$.
+Solving $\nabla_z c^2 = 0$ with this formula requires that $\bm z$ is an eigenvector of $\mathds{1}-A^+A$ with eigenvalue zero.
+The linearity of equation \ref{eqn:klm-finite-constraint} requires that, even if there are multiple zero-eigenvalue eigenvectors of $\mathds{1}-A^+A$, they must correspond to the same solution of $\bm c$.
+Thus, the density distribution of the asteroid is uniquely determined.
 
@@
 
+%\bibliography{asteroids}{}
 \bibliography{blank}{}

### 2022-01-20 code/density/constant-density/extract.py

@@ -1,0 +1,156 @@
+import numpy as np
+from scipy.special import lpmv, factorial
+from scipy.optimize import root
+from multiprocessing import Pool
+
+INTEGRAL_WIDTH = 200
+
+klms = [
+    1.0,
+    0, 0, 0,
+    0.03, 0, 0, 0, -0.1,
+]
+radius = 1000
+
+klms_and_radius_squared = np.array(klms)[1:] / klms[0]
+klms_and_radius_squared = np.append(klms_and_radius_squared, radius**2)
+
+MAX_L = int(np.sqrt(len(klms))) - 1
+
+
+def surface_integrate(theta_func, phi_func):
+    integral_theta = 0
+    integral_phi = 0
+    for theta in np.linspace(0, np.pi, INTEGRAL_WIDTH):
+        integral_theta += theta_func(theta) * np.sin(theta) * np.pi / INTEGRAL_WIDTH
+    for phi in np.linspace(0, 2 * np.pi, 2 * INTEGRAL_WIDTH):
+        integral_phi += phi_func(phi) * np.pi / INTEGRAL_WIDTH
+    return integral_theta * integral_phi
+
+def rlm_precursor_theta(l, m, theta):
+    return 1 / radius ** l / (3 + l) * lpmv(m, l, np.cos(theta)) / factorial(l + m)
+
+
+def rlm_precursor_phi(l, m, phi):
+    return np.exp(1j * m * phi)
+
+def ylm_coeff_theta(lmps, theta):
+    # Coefficients
+    value = 1
+    for lp, mp in lmps:
+        value *= (-1)**mp * lpmv(mp, lp, np.cos(theta))
+    return value
+
+def ylm_coeff_phi(lmps, phi):
+    # Coefficients
+    value = 1
+    for lp, mp in lmps:
+        value *= np.exp(1j * mp * phi)
+    return value
+
+def get_clm_coeff(args):
+    l, m, lmps = args
+    return surface_integrate(lambda theta: rlm_precursor_theta(l, m, theta) * ylm_coeff_theta(lmps, theta),
+                            lambda phi: rlm_precursor_phi(l, m, phi) * ylm_coeff_phi(lmps, phi))
+
+def get_volume_coeff(lmps):
+    return surface_integrate(lambda theta: 1/3 * ylm_coeff_theta(lmps, theta),
+                            lambda phi: ylm_coeff_phi(lmps, phi))
+
+def get_radius_coeff(lmps):
[…]

### 2022-01-21 summaries/21-11/21-11.tex
Finished ratio prod

@@
 A detailed model of uncertainty in the rotational pole of the asteroid (a model that might simulate a full lightcurve, for example) is beyond the scope of this paper.
-However, in this section we demonstrate how the uncertainty in the fit parameters is governed by the experimental uncertainty in rotational pole $\sigma_\theta$ as a rule-of-thumb to guide future investigation.
+However, in this section we demonstrate how the uncertainty in the fit parameters is governed by the observational uncertainty in rotational pole $\sigma_\theta$ and in the period $\sigma_\rho$  as a rule-of-thumb to guide future investigation.
 
@@
 
-These uncertainties in fit parameters are observed to scale precisely with $\sigma_\theta$, except where $\sigma_\theta$ is large enough that the fit parameter uncertainty is comparable to the size of the prior PDF.
-Figure \ref{fig:probe-sigma} shows the $\sigma / \sigma_\theta$ ratio for all 10 of the first two orders of parameters ($\gamma_0$, $K_{2m}$, and $K_{3m}$).
-The ratio of $\sigma_\rho$ to $\sigma_\theta$ is kept constant.
-The result is executed for the asymmetric asteroid model.
-The figure demonstrates that the ratio $\sigma/\sigma_\theta$ is constant for all values of $\sigma_\theta$ except large values.
-It also demonstrates that the posterior marginal PDFs are largely symmetric, in that the lower uncertainty is roughly equal to the upper uncertainty.
+We expect that high observational uncertainty corresponds to high uncertainty in the best-fit parameters.
+To show this trend, in figure \ref{fig:probe-sigma-product} we plot the best-fit uncertainty as a function of the product of the two uncertainty types, with the ratio fixed at $\sigma_\rho / \sigma_\theta = 10^{-5}$ (the benchmark value) so that we are only sensitive to the total uncertainty.
+To check deviation from a linear trend, we plot the ratio of fit uncertainty to $\sigma_\theta$.
+The figure shows no deviation from a linear trend except for high observational uncertainty, at which point the posterior distributions begin to fill the prior distributions and are no longer Gaussian.observations.
 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{probe-sigma.pdf}
-  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of $\sigma_\theta$.
+  \includegraphics[width=0.9\textwidth]{sigma-products.pdf}
+  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the product $\sigma_\theta\sigma_\rho$.
+A horizontal line divides the precise $\ell=2$ parameters from the others.
 Except at large $\sigma_\theta$, the ratio is observed to be constant.
@@
 Values of the ratio for other asteroid models can be computed from figure \ref{fig:probe-space-sigma}.}
-  \label{fig:probe-sigma}
+  \label{fig:probe-sigma-product}
 \end{figure}
 
-Due to the constancy of the ratio of fit to observational uncertainty, the ratio can be extracted for other asteroid configurations from figure \ref{fig:probe-space-sigma}, and we are not much concerned with the value of $\sigma_\theta$ used throughout this paper because we are aware that results can be easily rescaled.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\textwidth]{sigma-ratios.pdf}
+  \caption{1- and 2-$\sigma$ uncertainties of the marginal PDFs as a function of the ratio $\sigma_\rho / \sigma_\theta$.
+A horizontal line divides the precise $\ell=2$ parameters from the others.
+Period uncertainty $\sigma_\rho$ is shown to be more vital than pole uncertainty $\sigma_\theta$.}
+  \label{fig:probe-sigma-ratio}
+\end{figure}
+
+To test the relative importance of $\sigma_\rho$ and $\sigma_\theta$, we also show best-fit uncertainty as a function of the ratio $\sigma_\rho / \sigma_\theta$ with the product fixed at $\sigma_\rho \sigma_\theta = 10^{-7}$ (the benchmark value) in figure \ref{fig:probe-sigma-ratio}.
+If $\sigma_\rho$ and $\sigma_\theta$ were interchangeable in terms of their effect on precision of the posterior distributions, (e.g., if the experimental uncertainty were a function of $\sigma_\rho \sigma_\theta$ we might expect no dependence on the ratio of the uncertainties.
+However, we see relatively low uncertainty for low $\sigma_\rho / \sigma_\theta$ in figure \ref{fig:probe-sigma-ratio}, with roughly stable (or slightly decreasing) fit uncertainty for $\sigma_\rho \approx \sigma_\theta$.
+Therefore, for fixed product $\sigma_\rho \sigma_\theta$, low $\sigma_\rho$ compared to $\sigma_\theta$ will yield more precise fits.
+
+Due to the constancy of the ratio of fit to observational uncertainty for fixed $\sigma_\rho \sigma_\theta$, the ratio can be extracted for other asteroid configurations from figure \ref{fig:probe-space-sigma}, and we are not much concerned with the value of $\sigma_\theta$ used throughout this paper because we are aware that results can be easily rescaled.
 
@@
 \section{Interpretation of the Fit Parameters}
-The physical parameters $K_{\ell m}$ resulting from a fit to flyby data, while physical, do not completely describe an asteroid.
-Since the density distribution of the asteroid has many more degrees of freedom in general than the number of known $K_{\ell m}$, there are often many degenerate density distributions associated with one set of $K_{\ell m}$.
-
-To avoid this degeneracy, we either (1) assume that the density is constant and solve for the asteroid surface (section \ref{sec:constant-density}), (2) assume that the surface of the asteroid is fixed and solve for the density distribution under various assumptions.
-(sections \ref{sec:laplace-rho}, \ref{sec:numerical-density}, and \ref{sec:like-density}).
-In the latter case, we can avoid the above degeneracy either by assuming $\nabla^2 \rho = 0$ (section \ref{sec:laplace-rho}), by using a numerical approach to find an average density distribution (section \ref{sec:numerical-density}), or by associating a likelihood with each density distribution and taking the distribution with maximum likelihood (section \ref{sec:like-density}).
+The previous sections have demonstrated that the parameters $K_{\ell m}$ can be extracted from a fit to spin data taken of an asteroid encounter given $a_m$.
+However, the most interesting physical property of the asteroid is the interior density distribution $\rho(\bm r)$.
+Unfortunately, the density distribution is strongly degenerate given fixed parameters $K_{\ell m}$ and $a_m$.
+In this section, we outline four methods to extract density distributions under assumptions that reduce the degeneracy.
+
+The first simplifying step we take is to extract $\eta(\bm r) = \rho(\bm r) / \mu_m$ instead of $\rho(\bm r)$ from $K_{\ell m}$ and $a_m$; we do this because tidal torque data is not affected by the mass of the asteroid and the average density of the asteroid will therefore never be constrained.
+We further simplify matters by defining $H_{\ell m} = a_m^\ell K_{\ell m}$, so that the task is to find $\eta(\bm r)$ such that
+\begin{equation}
+  a_m^2 = \int_{\mathcal{A}} d^3 r \eta(\bm r) r^2 \qquad H_{\ell m} = \int_{\mathcal{A}} d^3 r \eta(\bm r) R_{\ell m}(\bm r) 
+  \label{eqn:density-constraints}
+\end{equation}
+is satisfied with $a_m^2$ and $H_{\ell m}$ known.
+We made the shift from $K_{\ell m}$ to $H_{\ell m}$ because the constraints are now linear in $\eta(\bm r)$; thus, if $\eta_1(\bm r)$ and $\eta_2(\bm r)$ both satisfy equation \ref{eqn:density-constraints}, then $(\eta_1 + \eta_2) / 2$ does as well.
+
+Equation \ref{eqn:density-constraints} amounts to $N$ constraints, when $N$ values of $H_{\ell m}$ are known. This is because $H_{00} = 1$ by definition.
+
+To resolve further degeneracy, we either assume (1) that the density $\eta$ is constant and solve for the shape (section \ref{sec:constant-density}), or (2) that the shape is fixed and solve for $\eta(\bm r)$.
+In the latter case, a further simplification is needed.
+We propose three models: one in which $\nabla^2 \eta = 0$ (section \ref{sec:laplace-rho}), one which averages over an ensemble of extracted distributions (section \ref{sec:numerical-density}), and one which defines a likelihood on density distributions and find that which maximizes the likelihood (section \ref{sec:like-density}).
 
@@
 \label{sec:constant-density}
-Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m$.
-We do not expect to solve for $\rho_0$ or equivalently $\mu_m$ since the mass of the asteroid cannot be extracted from tidal torque.
-However, we can solve for the asteroid shape required to match the known $K_{\ell m}$.
-In this process, we ignore $a_m$ until the last step, when we rescale the asteroid shape model until the correct $a_m$ is yielded.
-
-Suppose the asteroid is ``star shaped'' in that every point on its surface maps to a unique set of spherical coordinates $\theta, \phi$, and $r(\theta, \phi)$. We use the helpful identity
-\begin{equation}
-  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r R_{\ell m} (\bm r)
-   = \frac{\rho_m}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \nabla \cdot \bm v (\bm r)
-    = \frac{\rho_m}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
+Suppose our asteroid has constant density $\eta_0$ and known parameters $H_{\ell m}$ and $a_m^2$, and that the asteroid is ``star shaped'' in that every point on its surface maps to a unique set of spherical coordinates $\theta, \phi$, and $r(\theta, \phi)$.
+We use the helpful identity
+\begin{equation}
+  H_{\ell m} = \eta_0 \int_\mathcal{A} d^3 r R_{\ell m} (\bm r)
+   = \eta_0 \int_\mathcal{A} d^3 r \nabla \cdot \bm v (\bm r)
+    = \eta_0 \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
 \end{equation}
@@
 \begin{equation}
-  K_{\ell m} = \frac{\rho_m}{\mu_m a_m^\ell(3 + \ell)} \int_0^\pi d\theta \sin \theta\int_0^{2\pi}d\phi r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
+  H_{\ell m} = \frac{\eta_0 }{3 + \ell} \int_0^\pi d\theta \sin \theta\int_0^{2\pi}d\phi r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
   \label{eqn:constant-density-klm}
 \end{equation}
-The integrand of each $K_{\ell m}$ therefore is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
+The integrand of each $H_{\ell m}$ therefore is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
 We can write $r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality, in which case equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
@@
 Equation \ref{eqn:constant-density-klm} can then be numerically solved to get $C_{\ell m}$.
-To remove the degeneracy caused by the factor of $\rho_m$, we instead solve given constraints of $K_{\ell m} / K_{00}$.
-(Note that $K_{00} = \rho_m / \mu_m$).
-We force the solution to reproduce the correct value of $a_m^2/K_{00}$, defined in equation \ref{eqn:am}.
-We calculate this via
-\begin{equation}
-  a_m^2 = \frac{\rho_m}{\mu_m}\int_\mathcal{A} d^3 r r^2 = \frac{K_{00}}{5}\oint_\mathcal{A} d^2 \bm r \cdot \bm r(r^2) = \frac{K_{00}}{5}\int_0^\pi d\theta \sin\theta \int_0^{2\pi}d\phi r(\theta, \phi)^5.
+To remove the degeneracy caused by the factor of $\eta_0$, we evaluate $H_{\ell m} / H_{00}$ instead of $H_{\ell m}$.
+We also force the solution to reproduce the correct value of $a_m^2/H_{00}$, calculated as
+\begin{equation}
+  a_m^2 = \eta_0 \int_\mathcal{A} d^3 r r^2 = \frac{\eta_0}{5}\oint_\mathcal{A} d^2 \bm r \cdot \bm r(r^2) = \frac{\eta_0}{5}\int_0^\pi d\theta \sin\theta \int_0^{2\pi}d\phi r(\theta, \phi)^5.
 \end{equation}
@@
 This makes the number of terms $(L^2)^{3+L} = O(L^L)$.
-It is therefore exponential in the level of $L$ fitted.
 
@@
 Now suppose the shape of the asteroid is known, perhaps by a simplifying guess or perhaps by direct observation during a flyby.
-Then a density distribution $\rho(\bm r)$ can be solved for which is consistent with observed values of $K_{\ell m}$.
-Supposing $\nabla^2 \rho = 0$ and removing terms which are undefined at $r=0$, we write $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}^* a_m^\ell \mu_m$.
-Thus, $K_{\ell m} = \sum_{\ell' m'} C_{\ell' m'} B_{\ell \ell' m m'}$ where
-\begin{equation}
-  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m'}(\bm r)
+Then a density distribution $\eta(\bm r)$ can be solved for which is consistent with observed values of $H_{\ell m}$ and $a_m^2$.
+Supposing $\nabla^2 \eta = 0$, we write $\eta(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*$.
+Thus, $H_{\ell m} = \sum_{\ell' m'} C_{\ell' m'} B_{\ell \ell' m m'}$ and $a_m^2 = \sum_{\ell' m'} C_{\ell' m'} v_{\ell' m'}$ where
+\begin{equation}
+  B_{\ell \ell' m m'} = \int_{\mathcal{A}}d^3 r R_{\ell m}(\bm r) R_{\ell' m'}(\bm r)^* \qquad v_{\ell' m'} = \int_{\mathcal{A}}d^3 r R_{\ell' m'}(\bm r)^* r^2
   \label{eqn:blm}
@@
 can be precomputeded due to the shape of $\mathcal{A}$ being known.
-If we write $K_{\ell m}$ as a vector $\bm K$ and similarly for $\bm C$, we can write $B_{\ell \ell' m m'}$ as a matrix $\hat B$, obtaining $\bm K = \hat B \bm C$.
-It follows that the density distribution coefficients are given by
-\begin{equation}
-\bm C = \hat B^{-1} \bm K.
-\end{equation}
-The scale parameter $a_m$ can be computed from the resulting values of $\bm C$ and the distance scale can be adjusted until $a_m$ matches the true value.
-As before, $\mu_m$ is a free parameter representing the impossibility of fitting for the mass of the asteroid.
-Since only a finite number of $K_{\ell m}$ are known, we can only solve for a finite number of $C_{\ell m}$ and neglect the higher order terms.
+If we write $H_{\ell m}$ as a vector $\bm H$ and similarly for $\bm C$, we can write $B_{\ell \ell' m m'}$ as a matrix $B$, obtaining $\bm H = B \bm C$.
+Combining this with the equation $a_m^2 = \bm v \cdot \bm C$, we get an overdetermined matrix equation $\bm d = A \bm C$ where $A$ is $B$ with $\bm v$ added as an additional row, and $\bm d$ is $\bm H$ with $a_m^2$ added.
+It follows that the density distribution coefficients that minimize the least squares distance between $\bm d$ and $A \bm C$ are
+\begin{equation}
+\bm C = A^+ \bm d
+\end{equation}
+where $A^+$ is the Moore-Penrose pseudoinverse \cite{Barata2012}, defined by $A^+ = A^* (AA^*)^{-1}$ where $A^*$ is the adjoint of $A$.
 
 Physically, there is no reason to expect $\nabla^2 \rho = 0$.
-However, the space of density distributions with $\nabla^2 \rho = 0$ is a useful proxy for the true density distribution, since this section demonstrates how the density distribution can be solved for within this subspace.
-Conceptually, the density distribution derived from the $C_{\ell m}$s can be viewed as a projection from the true density distribution into the closest density distribution with $\nabla^2 \rho = 0$ everywhere.
-
-Note that if $\mathcal{A}$ is assumed to be a sphere, $B_{\ell \ell' m m'} \propto \delta_{\ell \ell'} \delta_{m m'}$ and $B_{\ell \ell m m}$ can be computed analytically.
-Thus, the matrix inversion step is not required in this case.
+However, the density distribution derived from the $C_{\ell m}$s can be viewed as a projection from the true density distribution into the closest density distribution with $\nabla^2 \rho = 0$ everywhere, and therefore an approximation of the true distribution.
+This formulation for the density distribution of the asteroid is also conceptually useful because when $\mathcal{A}$ is spherical, $B_{\ell \ell' m m'} \propto \delta_{\ell \ell'} \delta_{m m'}$.
+Thus, the fit coefficients $K_{\ell m}$ are proportional to $C_{\ell m}$, with proportionality constants governed by the values of $B_{\ell \ell' m m'}$ and $a_m^\ell$.
+For a nearly spherical asteroid, small off-diagonal terms will be added to $B$, but we still expect $K_{\ell m}$ to roughly correspond to $C_{\ell m}$.
 
@@
 \label{sec:numerical-density}
-Now we approach the problem of solving for the density distribution of an asteroid from the $K_{\ell m}$ parameters with more general assumptions.
+Now we approach the problem of solving for the density distribution of an asteroid from $H_{\ell m}$ and $a_m$ with more general assumptions.
 Suppose the shape of the asteroid is known, where ``known'' in this case means that an indicator function $\mathds{1}(\bm r)$ exists such that $\mathds{1}(\bm r) = 1$  inside the asteroid and 0 elsewhere.
-Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution.
-Given $n$ known values of $K_{\ell m}$, the algorithm proceeds as follows.
+Then we suggest a numerical algorithm to compute a representative distribution of the asteroid density distribution as follows.
 \begin{enumerate}
 \item Fill the asteroids with $n$ uniformly random ``seed points'' by distributing them inside a bounding box containing the asteroid and rejecting those with positions $\bm r_i$ such that $\mathds{1}(\bm r_i) = 0.$
-\item Construct $n$ regions $\mathcal{R}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
-Suppose $R_i$ has uniform density $\rho_i$.
-\item For each region, compute $\overline K_{\ell m}^i = \frac{1}{\mu_m a_m^\ell}\int_{\mathcal{R}_i} d^3 r R_{\ell m}(\bm r)$.
-Once again, $\mu_m$ is a free parameter and units can be chosen such that $a_m=1$.
-Then %we can write $K_{\ell m} = \sum_i \rho_i \overline K_{\ell m}^i$.
-\item Write $\overline K_{\ell m}^i$ as a square matrix $\hat{\overline K}$ with columns indexed by $i$ and rows indexed by $\ell$ and $m$. Invert it to get $\bm \rho = \hat {\overline K}^{-1} \bm K$.
-\item Go back to step 1 and compute new density maps with new draws of seed points.
-Since $K_{\ell m}$ is linear in $\rho$, the average density distribution also satisfies the fitted $K_{\ell m}$.
-Use the average as the asteroid density distribution.
+\item Construct $n$ regions $\mathcal{V}_i$around each point such that the $i$th region is the set of all points inside the asteroid closest to the $i$th point.
+Suppose $\mathcal{V}_i$ has uniform density $\rho_i$.
+\item Equation \ref{eqn:density-constraints} then becomes two linear equations $a_m^2 = \bm v \cdot \bm \rho$ and $\bm H = A \bm \rho$ where $\rho_i$ are the components of $\bm \rho$ and $\bm H$ are $H_{\ell m}$ arranged as a vector.
+The components of $\bm v$ and the matrix $A$ are given by
+\begin{equation}
+  v_i = \int_{\mathcal{V}_i} d^3 r r^2 \qquad A_{(\ell m),j} = \int_{\mathcal{V}_i} d^3 r R_{\ell m}.
+\end{equation}
+Precompute $\bm v$ and $A$.
+\item We can write equation \ref{eqn:density-constraints} now as a matrix equation $\bm d = M\rho$, where $M = A$ with $\bm v$ added as an additional row, and $\bm d = \bm K$ with $a_m^2$ added in the corresponding entry.
+Thus, $\bm \rho = M^{-1} \bm d$ can be directly computed.
+Note that $M$ is $N +1 \times N+1$, with the extra constraint enforcing that $\int_\mathcal{A} d^3 r\eta(\bm r) = 1$.
+\item Go back to step 1 and compute new density maps with new draws of seed points. After sufficiently many computations, return the average of all the density distributions.
 \end{enumerate}
-
-\jtd{What does this give mathematically?}
 
@@
 \label{sec:like-density}
-We present a final method to extract the density distribution of an asteroid with fixed surface and parameters $K_{\ell m}$.
+We present a final method to extract the density distribution of an asteroid with fixed surface and parameters $H_{\ell m}$ and $a_m^2$.
 Suppose the asteroid is divided into $N$ finite, constant density units with volume $\Delta V$ (a square grid, for instance).
-We further write the density of the $i$th unit as $\mu_m / (N \Delta V)C_i$, where $C_i$ is a free real parameter.
+We further write the density of the $i$th unit as $\eta_i = C_i / \Delta V$, where $C_i$ is a free real parameter.
 Approximating each unit as small, we may write
 \begin{equation}
-  K_{\ell m} = \frac{1}{Na_m^\ell} \sum_i^N C_i R_{\ell m}(\bm r_i)
+  a_m^2 = \sum_i^N C_i r_i^2 \qquad H_{\ell m} = \sum_i^N C_i R_{\ell m}(\bm r_i)
   \label{eqn:klm-finite-constraint}
@@
 where $\bm r_i$ are the centers of the units.
-Equation \ref{eqn:klm-finite-constraint} is a matrix equation, which can be written in the form $\bm K = A \bm C$ where $K_{\ell m}$ have been arranged as a vector and $\bm C$ contains the $N$ values of $C_i$.
+Equation \ref{eqn:klm-finite-constraint} is a matrix equation, which can be written in the form $\bm d = A \bm C$ where $a_m$ and $H_{\ell m}$ have been arranged as a vector $\bm d$ and $\bm C$ contains the $N$ values of $C_i$.
 The matrix $A$ is non-square and cannot be inverted to find $\bm C$ because equation \ref{eqn:klm-finite-constraint} has many solutions.
@@
 
-Suppose that the likelihood for $\bm C$ is multivariate-Gaussian distributed with no correlation, meaning that the log-likelihood is $\ln \mathcal{L} \propto -(x - \mu)^2$.
-We expect that $C_{i}$ average to one by the definition of $C_i$, so we set $\mu = 1$.
-Thus, the value of $\bm C$ we choose is the value which minimizes $|\bm C - \bm 1|^2$, where $\bm 1$ is an $N$-dimensional vector of only ones.
+Suppose that the likelihood for $\bm C$ is multivariate independent Gaussian distributed with each $C_i$ having the same standard deviation.
+The log-likelihood is therefore $\ln \mathcal{L} \propto -(x - \mu)^2$.
+We expect that $C_{i}$ sum to one by the definition of $C_i$, so we set $\mu = 1/N$.
+Thus, the value of $\bm C$ we choose is the value which minimizes $|\bm C - \bm 1 /N|^2$, where $\bm 1$ is an $N$-dimensional vector of only ones.
 
 This problem has already been solved in the context of the Moore-Penrose pseudoinverse.
-First, we define $\bm k = \bm K - A\bm 1$, so that if $\bm k = A \bm c$, then $\bm C = \bm c + 1$ solves equation \ref{eqn:klm-finite-constraint}.
+First, we define $\bm k = \bm K - A\bm 1/N$, so that if $\bm k = A \bm c$, then $\bm C = \bm c + \bm 1/N$ solves equation \ref{eqn:klm-finite-constraint}.
 We therefore attempt to minimize $|\bm c|^2$ to maximize the likelihood of density distributions.
 
-The Moore-Penrose pseudoinverse of $A$ is defined as $A^+ = A^* (AA^*)^{-1}$, where $A^*$ is the adjoint of $A$.
-Ref.
-\cite{Barata2012} gives that all solutions to $\bm k = A \bm c$ are given by $\bm c = A^+\bm k + (\mathds{1}-A^+A)\bm z$ for any vector $\bm z$.
-Solving $\nabla_z c^2 = 0$ with this formula requires that $\bm z$ is an eigenvector of $\mathds{1}-A^+A$ with eigenvalue zero.
-The linearity of equation \ref{eqn:klm-finite-constraint} requires that, even if there are multiple zero-eigenvalue eigenvectors of $\mathds{1}-A^+A$, they must correspond to the same solution of $\bm c$.
-Thus, the density distribution of the asteroid is uniquely determined.
+The Moore-Penrose pseudoinverse of $A$ is defined as $A^+ = A^* (AA^*)^{-1}$, where $A^*$ is the adjoint of $A$ \cite{Barata2012}. The solution that minimizes $|\bm c|^2$ is $\bm c = A^+\bm k$.
 

### 2022-01-21 data/probe-ratio-prod/compile.py

@@ -18,8 +18,6 @@ LEGEND_SIZE = 12
 N_DIM = None
 N_PERCENTILES = None
 
-SCALE_Y = 1.1
-
 # Get percentiles
 with open("percentiles.dat", 'r') as f:
     for line in f.readlines():
@@ -37,7 +35,7 @@ with open("percentiles.dat", 'r') as f:
 # Get true sigmas
 index = 0
 for name in percentiles.keys():
-    dir_name = name[:10]
+    dir_name = name[:15]
     with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
         max_j, max_l = f.readline().split(", ")
         max_j, max_l = (int(max_j), int(max_l))
@@ -54,49 +52,62 @@ for name in percentiles.keys():
     name_index[name] = index
     index += 1
     true_sigmas.append(sigma[0])
+    print(sigma[0]**2 * sigma[1])
     sigma_rat.append(sigma[1])
 
 sigma_rat = np.array(sigma_rat)
 true_sigmas = np.array(true_sigmas)
 
-fig, axs = plt.subplots(figsize=(10, 8), ncols=2, nrows=5, sharex=True)
+fig, axs = plt.subplots(figsize=(14, 8), ncols=3, nrows=4, sharex=True)
 axs = axs.reshape(-1)
 
-for i in range(N_DIM):
+i = 0
+for plot_index in range(N_DIM+1):
+    if plot_index == 9:
+        continue
+
     param_data = np.zeros(len(sigma_rat) * N_PERCENTILES).reshape(N_PERCENTILES, len(sigma_rat))
     for f in percentiles.keys():
         param_data[:,name_index[f]] = percentiles[f][i]
-    scale = 1
+    scale = 10**5 if i < 3 else 1
 
-    axs[i].plot(sigma_rat, (param_data[1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[i].plot(sigma_rat, (param_data[-1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[i].fill_between(sigma_rat, (param_data[1]-param_data[0]) / true_sigmas * scale, 
-        (param_data[-1]-param_data[0]) / true_sigmas * scale,  color=f"C{i}", alpha=0.3)
[…]

### 2022-01-21 data/probe-sigma/compile.py

@@ -51,47 +51,62 @@ for name in percentiles.keys():
     name_index[name] = int(dir_name[-2:])
     true_sigmas.append(sigma[0])
     ratio = sigma[1]
+    print(ratio)
 
 true_sigmas = np.array(true_sigmas)
 
-fig, axs = plt.subplots(figsize=(10, 8), ncols=2, nrows=5, sharex=True)
+fig, axs = plt.subplots(figsize=(14, 8), ncols=3, nrows=4, sharex=True)
 axs = axs.reshape(-1)
+i = 0
 
-for i in range(N_DIM):
-    param_data = np.zeros(len(true_sigmas) * N_PERCENTILES).reshape(N_PERCENTILES, len(true_sigmas))
+for plot_index in range(N_DIM+1):
+    if plot_index == 9:
+        continue
+    product = true_sigmas**2 * ratio
+    param_data = np.zeros(len(product) * N_PERCENTILES).reshape(N_PERCENTILES, len(product))
     for f in percentiles.keys():
         param_data[:,name_index[f]] = percentiles[f][i]
     scale = 10**5 if i < 3 else 1
-    axs[i].plot(true_sigmas**2 * ratio, (param_data[1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[i].plot(true_sigmas**2 * ratio, (param_data[-1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[i].fill_between(true_sigmas**2 * ratio, (param_data[1]-param_data[0]) / true_sigmas * scale, 
+
+    axs[plot_index].plot(product, (param_data[1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
+    axs[plot_index].plot(product, (param_data[-1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
+    axs[plot_index].fill_between(product, (param_data[1]-param_data[0]) / true_sigmas * scale, 
         (param_data[-1]-param_data[0]) / true_sigmas * scale,  color=f"C{i}", alpha=0.3)
 
-    axs[i].plot(true_sigmas**2 * ratio, (param_data[2]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
[…]

### 2022-01-21 summaries/21-11/21-11.tex
Finished oblateness-differ

@@
   \includegraphics[width=0.4\textwidth]{oblateness.pdf}
-  \caption{Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet.
+  \includegraphics[width=0.4\textwidth]{oblateness-differ.pdf}
+  \caption{(\textit{Left}) Ratio of 1- and 2-$\sigma$ uncertainties of the marginal PDFs to the observational uncertainty $\sigma_\theta$ as a function of the oblateness $\epsilon$ of the central planet.
 Linear best fit lines (black, dotted) are plotted over the 1- and 2-$\sigma$ uncertainties.
-Also shown are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
+(\textit{Right}) The deviation of fit parameters from the true parameters when a zero oblateness model is fitted to data with oblateness $\epsilon$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies \cite{pater_lissauer_2015}.}
   \label{fig:oblateness}
@@
 Other asteroid parameters $K_{3m}$ will likely be affected by oblateness to similar degrees, however fitting these extra parameters is computationally more expensive.
+
+The second figure of figure \ref{fig:oblateness} shows divergence of best-fit parameters from the true values when an incorrect oblateness is used.
+Specifically, the figure shows the difference between parameter values extracted via a model with $\epsilon=0$ and the true parameter values used to generate data with oblateness $\epsilon \neq 0$.
+The uncertainty on fit parameters is roughly constant over variations in $\epsilon_\textrm{true}$, but very quickly (even for $\epsilon_\textrm{true} = 10^{-4}$) the fit values become inconsistent with the true values.
+The observational uncertainty used here was the benchmark value, but even if observational uncertainty were increased by a factor of 10 (resulting in a factor of 10 increase in best-fit uncertainty --- see section \ref{sec:probe-sigma}) the figure shows that the best fit results would still exclude the true results by $>2\sigma$ if the oblateness of Earth were approximated as zero.
+For 100-fold increase in uncertainty, mismodeling Earth's oblateness would not lead to by $2\sigma$  divergence, but mismodeling Jupiter would.
 

### 2022-01-21 data/oblateness-differ/compile.py

@@ -18,6 +18,7 @@ percentiles = {}
 name_index = {}
 true_sigma = []
 j2s = []
+THETA_TRUE = []
 
 AXIS_SIZE = 12
 LEGEND_SIZE = 12
@@ -26,7 +27,7 @@ N_DIM = None
 N_PERCENTILES = None
 
 def plot_best_fit(ax, xs, ys, scale):
-    slope = np.cov(ys, xs)[0][1] / np.var(xs)
+    slope = np.cov(ys, xs)[0][1] / np.var(xs    )
     yint = np.mean(ys) - slope * np.mean(xs)
     ax.plot(xs, (xs * slope + yint) * scale, color='k', linewidth=1, linestyle='dotted')
     return slope
@@ -47,7 +48,7 @@ with open("percentiles.dat", 'r') as f:
 
 # Get true sigmas
 for name in percentiles.keys():
-    dir_name = name[:7]
+    dir_name = name[:8]
     with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
         max_j, max_l = f.readline().split(", ")
         max_j, max_l = (int(max_j), int(max_l))
@@ -61,6 +62,7 @@ for name in percentiles.keys():
         theta_high = [float(x) for x in f.readline().split(',')]
         theta_low = [float(x) for x in f.readline().split(',')]
         sigma = [float(d) for d in f.readline().split(',')]
+    THETA_TRUE = theta_true
     name_index[name] = int(dir_name[-2:])
     true_sigma = sigma[0]
     j2s.append(jlms[-1])
@@ -74,39 +76,39 @@ for i in range(N_DIM):
     param_data = np.zeros(len(oblatenesses) * N_PERCENTILES).reshape(N_PERCENTILES, len(oblatenesses))
     for f in percentiles.keys():
         param_data[:,name_index[f]] = percentiles[f][i]
-    scale = 10**5 if i < 3 else 1
-    axs[i].plot(oblatenesses, (param_data[1]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].plot(oblatenesses, (param_data[-1]-param_data[0]) / true_sigma * scale, color=f"C{i}", linewidth=1)
-    axs[i].fill_between(oblatenesses, (param_data[1]-param_data[0]) / true_sigma * scale, 
[…]

### 2022-01-21 code/density/ensemble.py
Implemented asymmetric ellipsoid test

@@ -1,4 +1,3 @@
-import density
 from setup import *
 from multiprocessing import Pool
 import numpy as np
@@ -63,7 +62,7 @@ if __name__ == "__main__":
     
     densities = np.mean(density_list, axis=0)
 
-    with open("data/ensemble.dat", 'wb') as f:
+    with open("data/"+TAG+"-ensemble.dat", 'wb') as f:
         np.save(f, densities)
     
     radius = get_radius(densities)

### 2022-01-27 summaries/21-11/21-11.tex
Implemented asymmetric ellipsoid test
Added density distribution section to summary

@@
 \subsection{Dependence on cadence}
+To analyze the degree to which our fit accuracy and precision depends on the rapidity of observation, we simulate a flyby of the reference asteroid with data taken at fixed intervals (``cadences'') of 2 minutes to one hour, perform a fit to each, and compare the precision and accuracy of the fit results as a function of cadence.
+
+Figure \ref{fig:cadence-precision} shows the 68th and 95th percentiles of the posterior PDF for each fit parameter as a function of evenly-spaced cadences from 2 to 60 minutes.
+The percentiles are divided by $\sigma_\theta$ (which is constant in this figure) since they are expected to be linearly proportional to $\sigma_\theta$ in general.
+As expected, the precision of the fit result decreases with increased cadence (less data).
+However, the decrease is not uniform.
+All parameters show a slow increase in posterior PDF width until $\Delta t \approx 40 \siunit{min}$, at when a sharp increase PDF width occurs, often followed by a slight decrease before the uncertainty rises again.
+\jtd{Say more about this once the orbital information comes through}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{cadence-precision.pdf}
+  \caption{The 68th and 95th percentile envelopes for the posterior PDFs associated with ten fit parameters as a function of the cadence of the data set, plotted as a function of cadence.}
+  \label{fig:cadence-precision}
+\end{figure}
+
+Figure \ref{fig:cadence-accuracy} shows the difference between best fit parameter results and the true values as a function of cadence.
+No divergence is seen between then true and best-fit results for high cadence, demonstrating that even a small amount of data is sufficient to extract accurate parameters for the asteroid density distribution, albeit with the precision penalties shown in figure \ref{fig:cadence-precision}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{cadence-accuracy.pdf}
+  \caption{The difference between the fit parameters and the true parameters, with 68th and 95th percentile envelopes shown, for ten fit parameters as a function of cadence.
+No significant divergence is seen for high cadence.}
+  \label{fig:cadence-accuracy}
+\end{figure}
 
@@
 The integrand of each $H_{\ell m}$ therefore is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
-We can write $r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality, in which case equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
+We can write $r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}$ without loss of generality.
+To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m (\ell-m)!/(\ell+m) C_{l,-m}$ so that the $\ell, m$ term of the sum for $r$ is the conjugate of the $\ell, -m$ term.
+
+With this definition of $r(\theta, \phi)$, equation \ref{eqn:constant-density-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
 These integrals can be precomputed, since they are taken over the whole sphere $\theta \in (0, \pi)$ and $\phi \in (0, 2\pi)$.
@@
 \end{equation}
-
-Unfortunately, this method is extremely slow.
-As mentioned above, the polynomial to be solved is order $3+\ell$ with $L^2$ $C_{\ell m}$ components, where $L$ is the maximum value of $\ell$ considered.
-This makes the number of terms $(L^2)^{3+L} = O(L^L)$.
 
@@
 
+\subsection{Comparison of density distribution models}
+In this section, we compare the above methods of extracting asteroid density distributions given sample values for $K_{\ell m}$, to demonstrate their differences in behavior.
+
+The sample $K_{\ell m}$ values we investigate are the symmetric and asymmetric benchmark values listed in appendix \ref{app:reference-config}.
+We execute the models for both benchmarks, and for the three models which require a fixed surface, we use both a spherical surface (radius equal to $\sqrt{5/3} a_m$) and an elliptical (axes set by section \ref{sec:constant-density-ellipsoid}) model.
+
+Figure \ref{fig:fix-ellipsoid-model-test} shows the density distribution produced by the three methods that fix the surface of the asteroid (the harmonic, ensemble average, and likelihood methods) for the symmetric and asymmetric benchmarks.
+Since the fixed shape is that of the constant-density ellipsoid associated with the same $K_{\ell m}$s, we expect nearly constant density distributions.
+The harmonic and likelihood models produce the most uniform density distributions, with the likelihood model producing slightly less uniform distributions for the asymmetric case.
+The non-uniformity of the harmonic model appears to occur by extreme edges of the asteroid possessing different densities than the majority of the asteroid, whereas the likelihood model appears to establish a more radial gradient.
+The ensemble average shows a stochastic randomness of the density distribution throughout the asteroid.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{harmonic-asym-ell.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-asym-ell.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-asym-ell.pdf}
+
+  \includegraphics[width=0.32\textwidth]{harmonic-sym-ell.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-sym-ell.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-sym-ell.pdf}
+  \caption{Density distributions extracted for the harmonic (\textit{left}), ensemble average (\textit{center}), and likelihood (\textit{right}) models, with $K_{\ell m}$ values equal to the asymmetric (\textit{top}) and symmetric (\textit{bottom}) benchmark values, and ellipsoidal shapes equal to the shape of the associated constant-density ellipsoid.
+The same length scale is used in all six images.}
+  \label{fig:fix-ellipsoid-model-test}
+\end{figure}
+
+In contrast, figure \ref{fig:fix-sphere-model-test} shows density distributions extracted for spherical shapes with the asymmetric and symmetric benchmark $K_{\ell m}$ parameters.
+As expected, distinctly non-uniform densities are produced; indeed, negative densities are produced.
+For the ensemble average model, solutions with negative density regions could be discarded.
+But negative density values for the other two models are unavoidable without changes to the model, such as a different likelihood distribution for the density of each chunk.
+
+Figure \ref{fig:fix-sphere-model-test} shows that the harmonic and likelihood models produce very similar results \jtd{Is this because of non-uniformity in density or because of the spherical surface?}.
+The ensemble average value again produces a more noisy distribution.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{harmonic-asym-sph.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-asym-sph.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-asym-sph.pdf}
+
+  \includegraphics[width=0.32\textwidth]{harmonic-sym-sph.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-sym-sph.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-sym-sph.pdf}
+  \caption{Density distributions extracted for the harmonic (\textit{left}), ensemble average (\textit{center}), and likelihood (\textit{right}) models, with $K_{\ell m}$ values equal to the asymmetric (\textit{top}) and symmetric (\textit{bottom}) benchmark values, and spherical shapes with radius $r=\sqrt{5/3} a_m$.
+The same length scale is used in all six images.}
+  \label{fig:fix-sphere-model-test}
+\end{figure}
+
+In addition to these two shape constraints placed on benchmark asteroid parameters, we consider two asteroid shapes of note: a tetrahedron and a ``dumb-bell.'' These shapes are interesting because tetrahedral shape models for asteroids have hitherto been explored \jtd{Citation needed} and a dumb-bell shape can be taken as a proxy for a contact binary asteroid.
+The tetrahedron is composed out of four equilateral triangular sides and the dumb-bell consists of two spheres with radius $r$, separated by distance $r/2$.
+These shapes are fixed and values of $K_{\ell m}$ are calculated assuming constant density.
+Then the three shape models are run on the resulting $K_{\ell m}$ to reproduce the density distribution of the asteroid (figure \ref{fig:tet-and-db}).
+Once again, the harmonic and the likelihood models produce nearly uniform density distributions, with the ensemble method also producing a nearly uniform distribution.
+Similar to before, the likelihood model tends to show radial density distribution and the harmonic model tends to produce axial differences in density.
+All three models seem well suited for the both shapes.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{harmonic-tet.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-tet.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-tet.pdf}
+
+  \includegraphics[width=0.32\textwidth]{harmonic-dumb-bell.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-dumb-bell.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-dumb-bell.pdf}
+  \caption{Density distributions extracted for the harmonic (\textit{left}), ensemble average (\textit{center}), and likelihood (\textit{right}) models, with a tetrahedral asteroid shape (\textit{top}) and a ``dumb-bell'' asteroid shape (\textit{bottom}).
+$K_{\ell m}$ values were extracted assuming uniform density for both asteroids.}
+  \label{fig:tet-and-db}
+\end{figure}
+
+Finally, we discuss the model which fixes constant density and solves for the asteroid surface.
+This model was run for the two benchmark $K_{\ell m}$ cases considered.
+A cutout diagram of the resulting density distribution is shown in figure \ref{fig:surface-density-distro}.
+For the symmetric case, we see an ellipsoid of revolution closely resembling the true asteroid ellipsoid.
+For the asymmetric case, we see a two-lobed asymmetric formation with equal $K_{\ell m}$ to the asymmetric ellipsoid because a triaxial ellipsoid cannot be represented with spherical harmonics of degree $\ell \leq 2$.
+The model therefore takes the closest approximating route.
+
+The figure demonstrates the limitations on the uniform density model: only a small number of shapes are accessible given fixed parameters $K_{\ell m}$ which may in fact be drawn from a diverse set of shapes from ellipsoids to tetrahedra to dumb-bells.
+However, a smooth shape distribution approximating the true distribution can nevertheless be fitted.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{surface-asym.pdf}
+  \includegraphics[width=0.32\textwidth]{surface-sym.pdf}
+  \caption{Density distributions extracted for the constant-density model, from the asymmetric (\textit{left}) and symmetric (\textit{right}) benchmark $K_{\ell m}$ parameters.}
+  \label{fig:surface-density-distro}
+\end{figure}
+
 \section{Uncertainty Testing}
@@
 \section{Conclusion}
-
-\jtd{Talk about the walker spacing: the clamps, the scale with sigma, and the block diagonal hermitian matrices}
-
-\jtd{Talk about first order torque}
-
-\jtd{Talk about how numerical accuracy was chosen}
-
-\jtd{Show plot of likelihood? (May not be necessary, since the corner plots are also shown)}
-
-\jtd{Move up error bar section so that plots can be explained?}
-
-\jtd{Compare the results to gaussians (they are not gaussian near the edges). Could do moment testing, or the Shapiro-Wilk test, which is frequentist so I don't want to do it.}
-
-\jtd{Question: How to express non-gaussianity of distro?}
-\jtd{Question: How important is it that the true value is not reproduced by the fit?
-Should I try to fix this?
-It's caused by the Gaussian approximation of the likelihood being incorrectm and by the fact that the data is not quite drawn from the distributions we model in the likeihood (it's drawn from the distribution of the true spin, not the data spin).}
 
@@
 If not specified, we use the $a < b$ case.
+Specifically, the asymmetric case has $a=1839\siunit{m}$, $b=1140\siunit{m}$, and $c=565\siunit{m}$, while the symmetric case has $a=b=1411\siunit{m}$ and $c=1008\siunit{m}$.
 \end{enumerate}
@@
 
-\section{Gaussianity of Parameter Posterior Distributions}
-\label{app:gaussian-posteriors}
-
 %\bibliography{asteroids}{}

### 2022-01-27 code/density/ensemble.py

@@ -69,4 +69,4 @@ if __name__ == "__main__":
     print(f"Radius: {radius}\tTrue radius: {A_M}")
     for l in range(MAX_L+1):
         for m in range(-l, l+1):
-            print(f"Klm: {get_hlms(l, m, densities)}\tTrue Klm: {complex_hlms[get_index(l, m)]}")
+            print(f"Hlm: {get_hlms(l, m, densities)}\tTrue Hlm: {complex_hlms[get_index(l, m)]}")

### 2022-01-27 summaries/21-11/21-11.tex
Pulled vex

@@
   \caption{The difference between the fit parameters and the true parameters, with 68th and 95th percentile envelopes shown, for ten fit parameters as a function of cadence.
-No significant divergence is seen for high cadence.}
+No significant divergence is seen for high cadence.
+\jtd{Is this figure necessary?}}
   \label{fig:cadence-accuracy}
@@
 
-\jtd{Do v and rp separately? Perhaps do not map}
+The dependency of the best-fit parameter uncertainty on the orbit of the asteroid is analyzed in this section.
+We parameterize the orbit by $v_\infty$, the excess velocity, and $r_p$, the distance of the perigee.
+We do not change the plane of the orbit because this is equivalent to rotating $J_{\ell m}$, and since we use the benchmark model for this section (with a spherical planet) orbital plane changes have no effect.
+
+Figure \ref{fig:scan-vex} shows the best-fit uncertainty divided by (constant) $\sigma_\theta$ as a function of $v_\infty$.
+The true $K_{\ell m}$ parameters are extracted in all cases, generally with larger uncertainty for large $v_\infty$.
+This trend is in agreement with intuition, since flybys with larger $v_\infty$ occur over a faster time range.
+Uncertainty in the high- and low-order parameters increases at a similar rate with $v_\infty$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{scan-vex.pdf}
+  \caption{Best-fit uncertainties as a function of $v_\infty$, the excess velocity of the asteroid orbit.
+The three higher order parameters (top) are plotted with the seven lower order parameters.
+A general trend of increasing uncertainty for higher $v_\infty$ is visible.}
+  \label{fig:scan-vex}
+\end{figure}
+
+Figure \ref{fig:scan-vex} also demonstrates a strong dependence on the exact value of $v_\infty$ through small-scale oscillations in precision as a function of $v_\infty$.
+This is because uncertainty is strongly dependent on the amplitude of oscillations after the encounter \jtd{how?}, and these oscillations are highly sensitive to initial conditions such as $v_\infty$.
 
@@
 \label{sec:block-perigee}
-Much of the data available concerning an asteroid's rotational velocity is captured much before or much after the flyby perigee, where tidal torque is low.
+Much of the data available concerning an asteroid's rotational velocity is captured long before or after the flyby perigee, where tidal torque is low.
 The angular velocity evolution here is dominated by torque-free precession dictated by the moment of inertia components, so that zero-torque data can still be used to fix $K_{20}$ and $K_{22}$.
@@
 
-To test this, we mask the perigee of the counter by removing data from the period when $D < f_\textrm{mask} r_p$, where $f_\textrm{mask}>1$ is a unit-less fraction.
-We also allow the simulation to continue beyond the standard $f = 10$, so that the actual length of the data set is unaffected by the mask and induces no lack of precision on the fit of $K_{3m}$.
-We then fit to synthetic data for each mask and plot the standard deviations of the parameter posterior PDFs for (1) $\gamma_0$ and $K_{2m}$ as a control, and (2) $K_{3m}$, to test whether they can still be fitted for without data concerning the perigee.
-To maximize the changes in posterior PDF, we use an experimental error of $\sigma_\theta = 10^{-5}$, the lowest we test in this study.
+To test this, we mask the perigee of the counter by removing data within time $T$ of the perigee, where $T$ ranges from 0 to 1 hour.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 1 hr$-T$ from the beginning and end of the data set, so that all data sets produced for all $T$ have the same length of data before and after the perigee.
+We then fit the same asteroid model to the cut data for all $T$ and plot the standard deviations of the parameter posterior PDFs for (1) $\gamma_0$ and $K_{2m}$ as a control, and (2) $K_{3m}$, to test whether they can still be fitted for without data concerning the perigee.
+We use the asymmetric benchmark asteroid configuration.
 
@@
 In this section, we compare the above methods of extracting asteroid density distributions given sample values for $K_{\ell m}$, to demonstrate their differences in behavior.
+To display the density distributions (and to derive them for the likelihood and ensemble average models), we subdivide the asteroid into a lattice of uniform-density cubes, each with a side length of ten meters.
+In the case of the ensemble average model, we average over 48 ensembles.
 

### 2022-01-28 summaries/21-11/21-11.tex
Made scatter for spin pole

@@
 \section{Example fit results}
-In the interest of demonstrating the result of a fit to synthetic data, we present the results of a fit to synthetic data generated with the nominal sensitivity model and $\sigma_\theta = 10^{-5}$.
+In the interest of demonstrating the result of a fit to synthetic data, we present the results of a fit to synthetic data generated with the nominal sensitivity model and $\sigma_\theta = 9.5 \times 10^{-3}$.
 The symmetric reference asteroid is used.
@@
   \includegraphics[width=0.7\textwidth]{example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
 The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
@@
   \includegraphics[width=\textwidth]{example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 10^{-5}$.
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
 Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
@@
 The true values lie within $2\sigma$ contours in most cases, as expected.
-Parameters are computed to very high accuracy --- $O(10^{-7})$ for $\gamma_0$ and $O(10^{-9})$ for $K_{2m}$ (the first tier of parameters as ordered by the sensitivity of the asteroid system to their values), and $O(10^{-4})-O(10^{-6})$ for $K_{3m}$.
+Parameters are computed to very high accuracy --- $O(10^{-6})$ for $\gamma_0$ and $O(10^{-7})$ for $K_{2m}$ (the first tier of parameters as ordered by the sensitivity of the asteroid system to their values), and $O(10^{-4})-O(10^{-2})$ for $K_{3m}$.
 These ranges should be compared to the width of the prior distributions for these parameters, which is $O(1)$ for all.

### 2022-02-01 summaries/21-11/21-11.tex
Staged gap for 3 hours

@@
 \item Moskowitz survey of Duende: \cite{BENSON2020113518} with companion observational article \cite{MOSKOVITZ2020113519}.
-Demonstrates that moment of inertia can be extracted from a tumbling asteroid via lightcurve analysis in the zero-torque regime (fourier transform of lightcurve to pick up on two frequencies and assign precession and nutation frequencies to them.) Assumes constant geometry.
+Demonstrates that moment of inertia can be extracted from a tumbling asteroid via lightcurve analysis in the zero-torque regime (Fourier transform of lightcurve to pick up on two frequencies and assign precession and nutation frequencies to them.) Assumes constant geometry.
 \item Study of asteroid binary to extract density \cite{DESCAMPS2020113726}
@@
 We represent 1-$\sigma$ uncertainty in the fit parameters as the difference between the 84th or 15th percentile of the marginal posterior PDF for each fit parameter and its mean.
-For a multivariate gaussian posterior PDF (which must also have gaussian marginal PDFs), this 1-$\sigma$ uncertainty is exactly the standard deviation of the marginal PDF.
+For a multivariate Gaussian posterior PDF (which must also have Gaussian marginal PDFs), this 1-$\sigma$ uncertainty is exactly the standard deviation of the marginal PDF.
 We perform a similar exercise for the 2-$\sigma$ uncertainty.
@@
 We use the asymmetric benchmark asteroid configuration.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{observation-gap.pdf}
+  \caption{Observation gap}
+  \label{fig:observation-gap}
+\end{figure}
 

### 2022-02-02 summaries/21-11/21-11.tex
Tried out spin pole map
Finished rotation pole data; still need to work on some aspects

@@
 \subsection{Dependence on spin pole}
-
-\jtd{The period is also important, but probably depends too much on the start of the simulation. I'm more interested in the spin pole.}
+In addition to the physical parameters of the asteroid, the initial orientation of the asteroid spin pole strongly effects the precision of the best-fit parameters attainable from the data.
+For example, an asteroid with initial spin pole parallel to the orbital plane ($\beta=0$) gives Wigner-$D$ matrix elements $D^\ell_{m m'} \propto \delta_{m m'}$ and $D^\ell_{mm}={D^\ell_{-m,-m}}^*$.
+Note that the inner bracketed term of equation \ref{eqn:tidal-torque} transforms under $m \rightarrow -m$ as $[\cdot ] \rightarrow -(-1)^m[\cdot]^*$.
+Since $S_{\ell m}$ and $D_{\ell m}$ transform to their conjugates and $J_{\ell m} \rightarrow (-1)^m J_{\ell m}^*$ while none of the other terms transform, the entire equation for tidal torque transforms to the opposite of its conjugate.
+Since $\tau$ is invariant under this transformation, which is equivalent to a rearrangement of terms, we must have $\tau = -\tau^*$.
+Since $\tau \in \mathds{R}^3$, we have $\tau = 0$.
+Therefore the fit parameters $K_{\ell m}$ are entirely invisible when $\omega \propto \unit Z$ initially, and we expect to see decreasing fit precision near this limit.
+
+Figure \ref{fig:spin-pole} displays the $1-\sigma$ uncertainties on the first ten fit parameters of the asymmetric reference asteroid flyby as a function of the initial direction of the spin pole.
+In all cases, the asteroid's initial period was set to the reference 9 hours.
+The data is presented mapped onto a sphere which indicates the direction of the spin pole, in the Mollweide projection.
+To highlight common features between the ten parameters, the average standard deviation is presented in figure \ref{fig:spin-pole-avg}.
+The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each is set to one-tenth of its mean).
+Also shown in \ref{fig:spin-pole-avg} is the map of the average uncertainty with a polar projection, to show the high uncertainty near $\omega \propto \unit Z$.
+
+To generate figures \ref{fig:spin-pole} and \ref{fig:spin-pole-avg}, the sphere was populated with 64 sample sites spaced on a Fibonacci sphere $(\theta_i, \phi_i) = (1-(2i + 1) / 64, 2\pi  i/\varphi)$, where $\varphi\approx 1.618$ is the golden ratio.
+This yielded points that were roughly evenly distributed to avoid discontinuities in the figures.
+The locations of these 64 points are plotted in figure \ref{fig:spin-pole-avg} for reference.
+
+Figure \ref{fig:spin-pole-avg} displays other points of lack of precision: those of $\bm \omega \propto \pm \unit Y+ \frac{1}{2}\unit Z$ and to some degree $\unit X - \unit Z$.
+Not all of the parameters shown in figure \ref{fig:spin-pole} demonstrate this bare point, and some show lack of precision at $\bm \omega \propto -\unit Y+ \frac{1}{2}\unit Z$ as well.
+Better precision, however, was generally attained when aligning parallel or antiparallel to $\unit X$, the perigee vector.
+Initial poles with negative latitude also often relatively precise estimates.
+However, the average best-fit is not very volatile; it rarely grows to twice its mean over the sphere.
+Exactly which regions of the sphere yield better precision is likely controlled by particulars of the reference asteroid rather than fundamental properties of asteroid flybys, since no cases except when $\bm \omega \propto \unit Z$ does $\bm \tau = 0$.
+
+The increased uncertainty in the non-polar regions stems from the way the $K_{\ell m}$ are correlated.
+(If two $K_{\ell m}$ are highly correlated, we ``double count'' uncertainty because uncertainty in one parameter will yield uncertainty in the other).
+A metric of average uncertainty which is immune to correlation is the trace of the covariance matrix, since the trace of a covariance matrix transformed by an orthogonal matrix is the trace of the original covariance matrix.
+Note that this trace is also the sum of eigenvectors of the covariance matrix, which is the sum of the variances of uncorrelated parameters.
+This covariance matrix trace is plotted in figure \ref{fig:spin-pole-avg-trace}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{spin-pole.pdf}
+  \caption{$1-\sigma$ uncertainties in the first 10 asteroid fit parameters as a function of the initial direction of spin.
+All maps are made in the Mollweide projection and shown in the inertial $\unit X-\unit Y-\unit Z$ frame.}
+  \label{fig:spin-pole}
+\end{figure}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.45\textwidth]{spin-pole-avg-mollweide.pdf}
+  \includegraphics[width=0.45\textwidth]{spin-pole-avg-polar.pdf}
+  \caption{The weighted average of the uncertainties shown in figure \ref{fig:spin-pole}, in Mollweide (\textit{left}) and polar (\textit{right}) projections.
+See text for a description of how the average was computed.}
+  \label{fig:spin-pole-avg}
+\end{figure}
 

### 2022-02-02 code/sim/backend.cpp

@@ -154,7 +154,6 @@ void Asteroid::calculate_poses() {
     positions.push_back(position);
     velocities.push_back(velocity);
 
-
     expire_time = time;
 
     #ifdef TEXT_DEBUG
@@ -220,6 +219,7 @@ void Asteroid::get_derivatives(Vector3 position, Vector3 spin, Quaternion quat, 
     
     #ifndef FIRST_ORDER
     Vector3 angles = quat.euler_angles();
+    std::cout << angles << std::endl;
     DMatGen dgen = DMatGen(angles[0], angles[1], angles[2]);
     double pos_r = position.mag();
     double pos_ct = position[2] / position.mag();
@@ -243,6 +243,7 @@ void Asteroid::get_derivatives(Vector3 position, Vector3 spin, Quaternion quat, 
         }
     }
     torque = Vector3({x_torque.r, y_torque.r, z_torque.r});
+    std::cout << torque << std::endl;
     
     #else
 

### 2022-02-03 summaries/21-11/21-11.tex
Updated observation gap

@@
 In figure \ref{fig:example-data} we present example data for this asteroid using the two reference asteroid and orbit parameters described in appendix \ref{app:reference-config}.
-Additionally, one thousand simulations are also run with asteroid parameters $\gamma_0$, $K_{20}$, and $K_{22}$ changed slightly, distributed according to the likelihood defined by equation \ref{eqn:likelihood} with this nominal uncertainty method and $\sigma_\theta = 0.2$.
-The method for distributing these shape parameters is the same as the method for distributing the MCMC initial walker positions, described in section \ref{sec:fitting-method}.
-Bands containing 68.3\%, 95.5\%, and 99.7\% of these additional simulations are also plotted in figure \ref{fig:example-data}.
+Additionally, one thousand simulations are also run with asteroid parameters $\gamma_0$, $K_{20}$, and $K_{22}$ changed slightly, distributed according to the posterior distribution obtained by a fit to synthetic data altered according to the nominal uncertainty method (section \ref{sec:uncertainty-models}) and a fit method described in section \ref{sec:fitting-method}.
+An observational uncertainty of $\sigma_\theta = 1.0$ was used.
+However, due to the large amount of data, even this large observational uncertainty does not lead to visible deviations from the true data.
+So the posterior distribution is widened by a factor $N$, where $N$ is the number of data points in the data set.
+Bands containing 68.3\%, 95.5\%, and 99.7\% of these additional simulations are plotted in figure \ref{fig:example-data}.
+This choice of $N$ is made merely for illustrative purposes; the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but are meaningful when comparing two bands or two points in one band.
 
@@
   \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroid densities and the reference orbit (black lines).
-Also plotted is the deviation of the data for likelihood-distributed changes to the asteroid shape (bands) using the nominal uncertainty method.
+Also plotted is the deviation of the data for posterior-PDF-distributed perturbations to the asteroid shape (bands) using the nominal uncertainty method.
 Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
@@
 
-To test this, we mask the perigee of the counter by removing data within time $T$ of the perigee, where $T$ ranges from 0 to 1 hour.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 1 hr$-T$ from the beginning and end of the data set, so that all data sets produced for all $T$ have the same length of data before and after the perigee.
+To test this, we mask the perigee of the counter by removing data within time $T$ of the perigee, where $T$ ranges from 0 to 3 hours.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the beginning and end of the data set, so that all data sets produced for all $T$ have the same length of data before and after the perigee.
 We then fit the same asteroid model to the cut data for all $T$ and plot the standard deviations of the parameter posterior PDFs for (1) $\gamma_0$ and $K_{2m}$ as a control, and (2) $K_{3m}$, to test whether they can still be fitted for without data concerning the perigee.
@@
 
+Figure \ref{fig:observation-gap} shows the best fit $1-\sigma$ and $2-\sigma$ uncertainty in the first order $K_{2m}$ and $\gamma_0$ and higher order $K_{3m}$ parameters as a function of the amount of perigee data $T$ that has been cut from the synthetic data set.
+Since torque is highest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore that uncertainty should increase monotonically with $T$, which is observed.
+We also see that this increase halts after about 2 hours of data has been cut for the first order parameters, likely because the majority of the tidal torque occurs within 2 hours of perigee.
+The exact time of this threshold is dependent on the asteroid orbital parameters.
+
+The higher order parameters show different behavior, increasing in $\sigma$ at smaller $T$ than the first-order parameters, and continuing to increase even for $T>2\siunit{hr}$.
+Qualitatively, this is expected since the torque is sensitive to the first-order parameters to order $D^{-3}$ and to the second-order parameters to order $D^{-4}$, so that the second-order parameters are expected to be more dominated by data near the center of the orbit than the first-order parameters.
+It is clear from figure \ref{fig:observation-gap}, however, that not all the higher order parameters increase in uncertainty at the same rate as each other, nor do they increase in uncertainty uniformly with $T$; once $T\sim 1 \siunit{hr}$ is cut out, further cuts to $T$ do not damage precision in $K_{3m}$ as much until $T\gtrsim 2\siunit{hr}$ is reached.
+
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{observation-gap.pdf}
-  \caption{Observation gap}
+  \caption{Best fit uncertainty in the first (top row) and second (bottom three rows) order parameters as a function of $T$, the amount of perigee observational data cut from the data set.
+All data within $T$ hours of perigee is cut, and the data set is correspondingly extended before and after the perigee so that its total size is unchanged.}
   \label{fig:observation-gap}

### 2022-02-03 code/fit_resolved/fit-gap.py

@@ -1,4 +1,4 @@
-TEST = False
+TEST = True
 
 import numpy as np
 import matplotlib.pyplot as plt
@@ -113,11 +113,6 @@ logging.info("Theta low {}".format(theta_low))
 logging.info("Sigma {}".format(sigma))
 logging.info("Name {}".format(output_name))
 N_DIM = len(theta_true)
-
-reload = False
-if len(sys.argv) == 3 and sys.argv[2] == "reload":
-    reload = True
-    REGENERATE_DATA = False
 
 uncut_mask = []
 cut_masks = []
@@ -599,33 +594,25 @@ def populate(evals, diagonalizer, count, start):
 def mcmc_fit(theta_start, evals, evecs, index):
     backend = emcee.backends.HDFBackend(output_name+"-{}.h5".format(index))
 
-    if not reload:
-        pos = populate(evals, evecs, N_WALKERS, theta_start)
+    pos = populate(evals, evecs, N_WALKERS, theta_start)
 
-
-        if PLOT_POSES:
-            for i in range(len(pos[0])):
-                print(plotille.histogram(
-                    pos[:,i],
-                    bins=8,
-                    width=80,
-                    height=15,
-                    X_label='theta {}'.format(i),
-                    Y_label='Counts',
-                    linesep='\n',
-                ))
-        backend.reset(N_WALKERS, N_DIM)
-    else:
-        pos=None
-        logging.info("Initial size: {}".format(backend.iteration))
+    if PLOT_POSES:
+        for i in range(len(pos[0])):
+            print(plotille.histogram(
+                pos[:,i],
+                bins=8,
+                width=80,
+                height=15,
+                X_label='theta {}'.format(i),
+                Y_label='Counts',
+                linesep='\n',
+            ))
+    backend.reset(N_WALKERS, N_DIM)
 
     old_tau = np.inf
     with Pool() as pool:
         sampler = emcee.EnsembleSampler(N_WALKERS, N_DIM, log_probability,
             args=(y, y_inv_covs), backend=backend, pool=pool)
-
-        if reload:
-            pos = sampler._previous_state
 
         if not emcee.walkers_independent(pos):
             f = open("errors.dat", 'a')
@@ -653,11 +640,7 @@ def mcmc_fit(theta_start, evals, evecs, index):
                 redchis = -2 * sample.log_prob / len(y) / 3
[…]

### 2022-02-03 data/observation-gap-fake/compile.py

@@ -1,0 +1,117 @@
+# Goal: spawn a bunch of runs that cover the parameter space.
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.lines import Line2D
+
+plt.style.use("jcap")
+
+param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
+
+percentiles = {}
+name_index = {}
+true_sigma = None
+gaps = []
+
+AXIS_SIZE = 12
+LEGEND_SIZE = 12
+
+N_DIM = None
+N_PERCENTILES = None
+
+SCALE_Y = 1.1
+
+# Get percentiles
+with open("percentiles.dat", 'r') as f:
+    for line in f.readlines():
+        if line == '': continue
+        elements = line.split(':')
+        name = elements[0]
+        perc_array = []
+        for percs in elements[1:]:
+            perc_array.append([float(x) for x in percs.split(',')])
+        perc_array = np.array(perc_array)
+        N_DIM = perc_array.shape[0]
+        N_PERCENTILES = perc_array.shape[1]
+        percentiles[name] = perc_array
+
+# Get true sigmas
+index = 0
+for name in percentiles.keys():
+    dir_name = name[:6]
+    with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
+        max_j, max_l = f.readline().split(", ")
+        max_j, max_l = (int(max_j), int(max_l))
+        cadence = int(f.readline())
+        perigee = int(f.readline())
+        radius = float(f.readline())
+        speed = float(f.readline())
+        spin = [float(x) for x in f.readline().split(',')]
+        jlms = [float(x) for x in f.readline().split(',')]
+        theta_true = [float(x) for x in f.readline().split(',')]
+        theta_high = [float(x) for x in f.readline().split(',')]
+        theta_low = [float(x) for x in f.readline().split(',')]
+        sigma = [float(d) for d in f.readline().split(',')]
+        gap_size = float(f.readline())
+    name_index[name] = index
+    index += 1
+    true_sigma = sigma[0]
+    gaps.append(gap_size)
[…]

### 2022-02-03 data/observation-gap/compile.py

@@ -55,7 +55,7 @@ for name in percentiles.keys():
     name_index[name] = index
     index += 1
     true_sigma = sigma[0]
-    gaps.append(gap_size * 60 * 60)
+    gaps.append(gap_size)
 
 gaps = np.array(gaps)
 

### 2022-02-04 summaries/21-11/21-11.tex
Finished spin pole clarification

@@
 
-Note that each sum in this equation is weighted by a factor of $a_M^\ell a_m^{\ell'}/D^{\ell+\ell'+1}$.
+\subsection{Interpretation of Tidal Torque}
+\label{sec:torque-interpretation}
+The rest of this paper is devoted to interpreting the properties of equation \ref{eqn:tidal-torque} through a fit to data generated with this equation of motion, but several properties are already evident through the functional form.
+
+Firstly, each term is weighted by a factor of $a_M^\ell a_m^{\ell'}/D^{\ell+\ell'+1}$.
 Since $D \gg a_M \gg a_m$ in general, the leading order torques come from low $\ell$ and $\ell'$.
 However, $\ell'=0$ contributes nothing because the inner bracketed term is zero, and $K_{\ell' = 1} = 0$ if we choose the origin of the body-fixed axes to be the center of mass of the asteroid.
-The leading order of equation \ref{eqn:tidal-torque} is therefore $1/D^3$ with $\ell = 0$ and $\ell' = 2$.
+The leading order of equation \ref{eqn:tidal-torque} is therefore proportional to $1/D^3$ with $\ell = 0$ and $\ell' = 2$.
+We therefore call $K_{2m}$ and $\gamma_0$ the ``low-order'' parameters because they are found in the leading order term of equation \ref{eqn:tidal-torque}.
+The next order is $K_{3m}$, and other orders after that are terms with $J_{2m}$ and $K_{2m}$ as well as $J_{00}$ and $K_{4m}$.
+
+It is also useful to note when equation \ref{eqn:tidal-torque} is zero, since in these cases we expect to be able to determine little about the asteroid.
+Most important is when $\omega \parallel \unit Z$; i.e., when $\beta=0$.
+In this case, the Wigner-$D$ matrix elements are $D^\ell_{m m'} \propto \delta_{m m'}$ and $D^\ell_{mm}={D^\ell_{-m,-m}}^*$.
+Note that the inner bracketed term of equation \ref{eqn:tidal-torque} transforms under $m \rightarrow -m$ as $[\cdot ] \rightarrow -(-1)^m[\cdot]^*$.
+Since $S_{\ell m}$ and $D_{\ell m}$ transform to their conjugates and $J_{\ell m} \rightarrow (-1)^m J_{\ell m}^*$ while none of the other terms transform, the entire equation for tidal torque transforms to the opposite of its conjugate.
+Since $\tau$ is invariant under this transformation, which is equivalent to a rearrangement of terms, we must have $\tau = -\tau^*$.
+Since $\tau \in \mathds{R}^3$, we have $\tau = 0$.
+
+Restricting to the first order of equation \ref{eqn:tidal-torque}, $\bm \tau$ has two other important zeros.
+Writing the position vector $\bm D$ in spherical coordinates $D, \theta, \phi$ and setting $\theta = \pi/2$ for simplicity, we note that $\bm \tau = 0$ when (1) $\alpha=\phi$ and $\beta = \pi/2$, and when (2) $\alpha=\phi+\pi/2$ and $\gamma$ is an integer multiple of $\pi/2$.
+At $\phi=0$, where $D$ is smallest and $\bm \tau$ is generally greatest, these positions correspond to (1) $\bm \omega \parallel \unit X$ and (2) $\bm \omega$ is in the $\unit Y-\unit Z$ with a condition on $\gamma$.
+When the latter condition on $\gamma$ is not met, $\bm \tau \propto \unit Z K_{22} \sin(2\gamma)$.
+Since $\gamma$ changes as the asteroid rotates and depends on the initial condition $\gamma_0$, whether the $\gamma$ condition is met at perigee is more or less random.
 
@@
 In addition to the physical parameters of the asteroid, the initial orientation of the asteroid spin pole strongly effects the precision of the best-fit parameters attainable from the data.
-For example, an asteroid with initial spin pole parallel to the orbital plane ($\beta=0$) gives Wigner-$D$ matrix elements $D^\ell_{m m'} \propto \delta_{m m'}$ and $D^\ell_{mm}={D^\ell_{-m,-m}}^*$.
-Note that the inner bracketed term of equation \ref{eqn:tidal-torque} transforms under $m \rightarrow -m$ as $[\cdot ] \rightarrow -(-1)^m[\cdot]^*$.
-Since $S_{\ell m}$ and $D_{\ell m}$ transform to their conjugates and $J_{\ell m} \rightarrow (-1)^m J_{\ell m}^*$ while none of the other terms transform, the entire equation for tidal torque transforms to the opposite of its conjugate.
-Since $\tau$ is invariant under this transformation, which is equivalent to a rearrangement of terms, we must have $\tau = -\tau^*$.
-Since $\tau \in \mathds{R}^3$, we have $\tau = 0$.
-Therefore the fit parameters $K_{\ell m}$ are entirely invisible when $\omega \propto \unit Z$ initially, and we expect to see decreasing fit precision near this limit.
-
-Figure \ref{fig:spin-pole} displays the $1-\sigma$ uncertainties on the first ten fit parameters of the asymmetric reference asteroid flyby as a function of the initial direction of the spin pole.
+For example, it was pointed out that $\omega \propto \unit Z$ gives $\bm \tau = 0$ in section \ref{sec:torque-interpretation}.
+Since $\dot {\bm \omega} = 0$ until torque is applied to start tumbling, we expect $\bm \omega$ to be constant throughout the data set in this case, and the fit parameters $K_{\ell m}$ will be invisible.
+We also expect to see decreasing fit precision near this limit.
+
+Figure \ref{fig:spin-pole} displays the $1\sigma$ uncertainties on the first ten fit parameters of the asymmetric reference asteroid flyby as a function of the initial direction of the spin pole.
 In all cases, the asteroid's initial period was set to the reference 9 hours.
@@
 
-Figure \ref{fig:spin-pole-avg} displays other points of lack of precision: those of $\bm \omega \propto \pm \unit Y+ \frac{1}{2}\unit Z$ and to some degree $\unit X - \unit Z$.
-Not all of the parameters shown in figure \ref{fig:spin-pole} demonstrate this bare point, and some show lack of precision at $\bm \omega \propto -\unit Y+ \frac{1}{2}\unit Z$ as well.
+Figure \ref{fig:spin-pole-avg} confirms our expectation that the fit parameters would be uncertain near $\bm \omega \propto \unit Z$, and it displays other points of lack of precision: those of $\bm \omega \propto \pm \unit Y$.
+Not all of the parameters shown in figure \ref{fig:spin-pole} demonstrate this bare point: for example, $K_{20}$ and $K_{30}$ are not as affected by $\bm \omega \propto \unit Y$.
+The fact that these regions of imprecision line up with $\pm \unit Y$ is not guaranteed, and it is a coincidence that the reference asteroid happens to.
+In general, these region will be placed at other points on the equator at a location determined by the asteroid's $K_{\ell m}$ and $\gamma_0$.
+
+This dependence on asteroid parameters is because, as section \ref{sec:torque-interpretation} points out, certain directions of $\bm \omega$ give can be shown via equation \ref{eqn:tidal-torque} to give $\bm \tau = 0$ regardless of $K_{\ell m}$.
+Other locations give $\bm \tau \parallel \unit Z \perp \bm \omega$, which may cause imprecision both because it restricting $\bm \tau$ to only one coordinate lowers its magnitude, and because $d/dt |\bm \omega|$ is minimized when $\bm \tau \perp \bm \omega$ and the asteroid is not tumbling.
+Of these low-torque locations, those that do not depend on $\gamma$ all satisfy either $\bm \omega \parallel \unit Z$ (zero torque) or $\omega_\phi = \phi + n\pi/2$, where $n$ is an integer, $\omega_\phi$ is the azimuthal coordinate of $\bm \omega$ in the global frame, and $\phi$ is the azimuthal location of the asteroid.
+As the asteroid encounters the central body, $\phi$ sweeps over a large range so that the low-torque loci associated with several values of $n$ affect the dynamics of the asteroid, and the degree to which the asteroid's dynamics are affected depends on $K_{ell m}$.
+Thus, exactly what initial spin pole direction maximizes uncertainty in the fit parameters depends on $K_{\ell m}$, but it is expected to lie in the orbital plane.
+
+Since $K_{20}$ is not controlled by torque at this point,  and some show lack of precision at $\bm \omega \propto -\unit Y+ \frac{1}{2}\unit Z$ as wel.
 Better precision, however, was generally attained when aligning parallel or antiparallel to $\unit X$, the perigee vector.
@@
 
-Figure \ref{fig:observation-gap} shows the best fit $1-\sigma$ and $2-\sigma$ uncertainty in the first order $K_{2m}$ and $\gamma_0$ and higher order $K_{3m}$ parameters as a function of the amount of perigee data $T$ that has been cut from the synthetic data set.
+Figure \ref{fig:observation-gap} shows the best fit $1\sigma$ and $2\sigma$ uncertainty in the first order $K_{2m}$ and $\gamma_0$ and higher order $K_{3m}$ parameters as a function of the amount of perigee data $T$ that has been cut from the synthetic data set.
 Since torque is highest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore that uncertainty should increase monotonically with $T$, which is observed.

### 2022-02-04 data/scan-spin-pole/compile.py

@@ -98,7 +98,8 @@ for plot_index in range(N_DIM+1):
             cart_line.append(interp(p[0], p[1], p[2]))
         cart_array.append(cart_line)
 
-    im = axs[plot_index].pcolormesh(Lon, Lat, cart_array, vmin=0, cmap='Blues_r')#, vmax=np.max(data), vmin=np.min(data))
+    vmax=np.mean(cart_array) * 3
+    im = axs[plot_index].pcolormesh(Lon, Lat, cart_array, vmin=0, cmap='Blues_r', vmax=vmax)#, vmax=np.max(data), vmin=np.min(data))
     cbar = fig.colorbar(im, ax=axs[plot_index])
     if i < 3:
         cbar.set_label(f"$\sigma({param_names[i]}) / \sigma_\\theta$ ($\\times 10^{{-5}})$")

### 2022-02-04 data/scan-spin-pole/scatter.py

@@ -39,7 +39,7 @@ for pole_index in range(NUM_DIVISIONS):
     spin_x = POLE_NORM * np.sin(theta) * np.cos(phi)
     spin_y = POLE_NORM * np.sin(theta) * np.sin(phi)
     spin_z = POLE_NORM * np.cos(theta)
-    d = np.cos(2*theta) * np.sin(2*phi)
+    d = np.sin(2 * theta) * np.sin(2  * phi)
     pts.append([np.sin(theta) * np.cos(phi), np.sin(theta) * np.sin(phi), np.cos(theta)])
     theta_phis.append((np.pi / 2 - theta, phi))
     data.append(d)
@@ -47,23 +47,32 @@ for pole_index in range(NUM_DIVISIONS):
     #f.close()
 theta_phis = np.array(theta_phis)
 
-lons = np.linspace(-np.pi, np.pi, 100)
-lats = np.linspace(-np.pi/2, np.pi/2, 50)
+lons = np.linspace(-np.pi, np.pi, 180)
+lats = np.linspace(-np.pi/2, np.pi/2, 90)
 Lon, Lat = np.meshgrid(lons, lats)
 interp = LinearNDInterpolator(pts, data)
+try:
+    with open("projecteds.dat", 'rb') as f:
+        projected_vecs = np.load(f)
+except Exception:
+    projected_vecs = None
 
 cart_array = []
-for lat in lats:
+for pi, lat in enumerate(lats):
     cart_line = []
-    for lon in lons:
-        shrink = 0.8
-        x, y, z = np.cos(lat) * np.cos(lon) * shrink, np.cos(lat) * np.sin(lon) * shrink, np.sin(lat) * shrink
-        cart_line.append(interp(x, y, z))
+    for pj, lon in enumerate(lons):
+        if projected_vecs is not None:
+            p = projected_vecs[pi][pj]
+            cart_line.append(interp(p[0], p[1], p[2]))
+        else:
+            shrink = 0.8
+            x, y, z = np.cos(lat) * np.cos(lon) * shrink, np.cos(lat) * np.sin(lon) * shrink, np.sin(lat) * shrink
+            cart_line.append(interp(x, y, z))
     cart_array.append(cart_line)
 
 fig = plt.figure()
 ax = fig.add_subplot(111, projection="mollweide")
[…]

### 2022-02-10 summaries/21-11/21-11.tex
Pulled perigee probes up to 25

@@
 
-\shorttitle{Asteroid project summary}
+\shorttitle{Constraining the Interiors of Asteroids Through Close Encounters}
 \shortauthors{Dinsmore and de Wit}
@@
 
-\title{Asteroid project summary}
+\title{Constraining the Interiors of Asteroids Through Close Encounters}
 
@@
 \begin{abstract}
-
-Abstract. 
+We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
+We derive the equations of motion for an asteroid's orientation and angular velocity during a close encounter to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth flyby.
+We re-extract the properties of the asteroid from this synthetic data and confirm the fit's accuracy.
+We investigate the dependence of the best fit uncertainty on asteroid moment of inertia, observational precision and cadence, the flyby's orbital parameters, the initial spin pole direction, the quantity of near-pericenter data, and the oblateness of the central body.
+Finally, we discuss the degeneracy between the parameters that can be extracted from flyby data and the actual density distribution and propose four models to construct a representative density distribution.
 \end{abstract}

### 2022-02-16 summaries/21-11/21-11.tex
High order summary

@@
 \subsection{Comparison of density distribution models}
+\label{sec:density-results}
 In this section, we compare the above methods of extracting asteroid density distributions given sample values for $K_{\ell m}$, to demonstrate their differences in behavior.
@@
 
-\section{Uncertainty Testing}
+\subsection{High order parameters}
+In the above demonstrations of the four density distribution models, we test examples where only the $K_{2m}$ parameters are known.
+In this section, we show density distributions extracted for example values of known $K_{3m}$.
+
+Suppose $K_{2m} = 0$.
+For the models that fix the surface of the asteroid, we assume a spherical shape, which is the uniform-density shape associated with $K_{2m} = 0$.
+We introduce $K_{3m}$ parameters uniformly randomly chosen in $(-0.01, 0.01)$; larger values of $K_{3m}$ tended to lead to highly negative density distributions.
+The three fixed-shape density distributions are shown in figure \ref{fig:high-order-fixed} and the constant-density distribution is shown in figure \ref{fig:high-order-surface}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{harmonic-high.pdf}
+  \includegraphics[width=0.32\textwidth]{likelihood-high.pdf}
+  \includegraphics[width=0.32\textwidth]{ensemble-high.pdf}
+  \caption{Density distributions extracted for the three fixed-surface models, for a spherical asteroid with $I_x=I_y=I_z$ but nonzero $K_{3m}$.}
+  \label{fig:high-order-fixed}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{surface-high.pdf}
+  \caption{Asteroid shape extracted for an asteroid with $I_x = I_y = I_z$ but nonzero $K_{3m}$ as a demonstration of the effects of the higher order $K_{3m}$ moments.}
+  \label{fig:high-order-surface}
+\end{figure}
+
+Beyond demonstrating the effectiveness of the density distribution algorithms when $K_{3m}$ parameters are introduced, figure \ref{fig:high-order-fixed} demonstrates again the similarity between the likelihood and the harmonic models, and shows that both still prefer smoothly varying distributions.
+The ensemble distribution is much less smoothly varying.
+More drawings of Voronoi cells would likely smooth the distribution further.
+All three density distributions produce negative (and therefore unphysical) density distributions.
+
+Figure \ref{fig:high-order-surface} shows that the constant density model is able to find a smooth surface to match an asteroid with nonzero $K_{3m}$ despite the negative densities in the fixed-surface model.
+Specifically, the surface model appears to have removed parts of the sphere that corresponded to low density in the fixed-surface model and extruded the asteroid shape in regions of high density.
+This fact demonstrates the sensitivity of the fixed-surface density distributions of figure \ref{fig:high-order-fixed} to the surface model; a relatively small change to the shape of the distribution can change the density distribution from unphysical (negative) to physical (positive --- indeed constant).
+It also suggests that a reasonable way to adjust a surface model to avoid unphysical density distributions is to remove regions with low density and add to regions with high density.
+
+\jtd{Should I explore the location / size of a rock?}
+\jtd{How should I talk about the scale size of the high order moments? By my random draw method? By calculating them for an ellipsoid, tetrahedron, and dumbbell?}
+
+\subsection{Structure of density moments}
+In this section, we qualitatively describe the properties of the density moments for the sake of interpreting them.
+
+First, we mention the symmetry property $K_{\ell m} = (-)^m K_{\ell,-m}^*$ which causes each degree $\ell$ to contain $2\ell + 1$ degrees of freedom (Further degrees of freedom are removed by fixing the origin of the coordinate system, its orientation, and the asteroid's mass).
+Also, $\Im K_{\ell 0} = 0$.
+Each $K_{\ell m}$ contains a factor of $r^\ell / a_m^\ell$ in its integrand, and since we generally expect $r \sim a_m$, naively we expect all $K_{\ell m}$ to be of the same order of magnitude.
+However, the fact that $\rho > 0$ everywhere induces other complications.
+Specifically, \jtd{The part listed in the paper for $K_{20}$}.
+For the allowed values of $K_{3 m}$ are more difficult to constrain, but we note that $|K_{\ell m}| \gtrsim 0.01$ often lead to negative density distributions.
+Furthermore, of the four shapes studied in section \ref{sec:density-results} (a sphere, ellipsoid, tetrahedron, and dumbbell), only the tetrahedron has nonzero $K_{3 m}$ and even for the tetrahedron, $K_{3m}=0$ except $\Re K_{32} = -0.036$.
+
+Symmetries of the asteroid density model may set some $K_{\ell m}=0$.
+Specifically, the parity properties of $R_{\ell m}$ under axis flips along $x$, $y$, and $z$ guarantee that asteroid density distributions that are flip-symmetric along $z$ have $K_{\ell m}=0$ when $\ell + m$ is odd.
+Flip-symmetry along $x$ guarantees $\Re K_{\ell m} = 0$ for $m$ odd and $\Im K_{\ell m} = 0$ for $m$ even.
+Flip-symmetry along $y$ guarantees $\Im K_{\ell m} = 0$ always.
+These results are summarized in table \ref{tab:symmetries}.
+
+The first three rows of table \ref{tab:symmetries} are as intuitively expected.
+$K_{00}$ (mass) is not zeroed by any mirror symmetries.
+This fact is even more clear from the definition of $K_{\ell m}$, which normalizes by mass such that $K_{00}=1$.
+But even without this normalization, $K_{00}$ would not be zeroed by symmetries.
+Also, $K_{1m}$ each correspond to one symmetry axis because they are the coordinates of the center of mass.
+Finally, $K_{21}$ and $\Im K_{22}$ are each zeroed by two symmetry axes because they express coordinate system orientation.
+The other two degree-two moments $K_{20}$ and $\Re K_{22}$ are not zeroed by mirror symmetries because they are moment of inertia ratios and must be positive.
+
+The last row of table \ref{tab:symmetries} shows that all $K_{3m}$ moments are zeroed by at least one symmetry.
+Therefore, a highly non-mirror symmetric distribution is necessary to produce large $K_{3m}$ values.
+This is why the constant density sphere, ellipsoid, and dumbbell shapes all have $K_{3m} = 0$.
+
+\begin{table}
+  \centering
+  \begin{tabular}{c|ccccccc}
+    \hline\hline
+    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
+    0&   &   &   &   &   &   &$-$\\
+    1&   &   &   &   &$x$&$y$&$z$\\
+    2&   &   &$-$&$x,y$&$x,z$&$y,z$&$-$\\
+    3&$x$&$y$&$z$&$x,y,z$&$x$&$y$&$z$\\ \hline \hline
+  \end{tabular}
+  \caption{For each $K_{\ell m}$ value from $\ell = 0$ to 3, the density distribution mirror symmetries which set $K_{\ell m} = 0$ are listed.
+Mirror symmetries around the axis $x$ are marked with $x$ and so on.
+A dash indicates that no mirror symmetries set $K_{\ell m} = 0$.}
+  \label{tab:symmetries}
+\end{table}
 

### 2022-02-24 summaries/21-11/21-11.tex
Added density moments

@@
 \newcommand{\per}[1]{\ \textrm{#1}^{-1}}
+\newcommand{\Cov}{\textrm{Cov}}
+\newcommand{\Var}{\textrm{Var}}
 \usetikzlibrary{arrows.meta}
@@
 
+\section{Density distributions, but redone}
+
+In this section, we describe a pipeline to convert the density moments $K_{\ell m}$ to a density distribution $\rho(\bm r)$ which correctly reproduces the density moments via equation \ref{eqn:jlm}.
+We will also produce a function $\sigma_\rho(\bm r)$ which represents the uncertainty in density propagated from uncertainty in the $K_{\ell m}$ moments.
+Unfortunately, $\rho(\bm r)$ represents infinitely many degrees of freedom, whereas generally only a few $K_{\ell m}$ are known.
+Additional assumptions must therefore be made to produce one $\rho(\bm r)$ solution.
+One assumption we will make is that the surface of the asteroid has been accurately determined, from light curve data for instance.
+A method of computing a density distribution when no asteroid surface is known is presented in appendix \jtd{Appendix}.
+A few example sets of solutions are described below, but first we investigate the problem in a general formulation, agnostic of what assumptions beyond a known surface are chosen to eliminate the degeneracy.
+
+\subsection{General formulation}
+We assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
+The initial orientation of the asteroid's spin pole with respect to Earth is also known, which fixes the initial orientation of the local frame (the asteroid's frame) with respect to Earth up to one parameter $\gamma_0$, which is attained by a fit as seen in previous sections.
+
+We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
+The indicator function $\mathds{1}$ is then assumed to be known exactly in this frame, and the $K_{\ell m}$ components are known in the local frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ and the known $a_m$.
+
+The density moments $K_{\ell m}$ defined in equation \ref{eqn:jlm} are not linear in $\rho(\bm r)$, but we may fix $a_m$ at the value assumed during the fit, removing the non-linearity induced by division by $a_m$.
+Furthermore, since the system is independent of the total asteroid mass, we set $\mu_m$ equal to an arbitrary constant which makes equation \ref{eqn:jlm} linear in $\rho(\bm r)$.
+Similarly, the form of equation \ref{eqn:am} guarantees that $a_m^2$ is linear in $\rho(\bm r)$.
+Equations \ref{eqn:am} and the $\ell, m = 0, 0$ component of equation \ref{eqn:jlm} can be used to enforce the choices of $\mu_m$ and $a_m^2$.
+
+Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm D)$ for an $m$-dimensional vector $\bm D$ which controls the free parameters of $\rho$.
+We will leave the explicit definition of $\rho$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm D$; i.e.,
+\begin{equation}
+  \rho(\bm r, \bm D) = \bm B(\bm r) \cdot \bm D
+  \label{eqn:density-distro}
+\end{equation}
+for a $m$-dimensional vector $\bm B(\bm r)$.
+Thus, equations \ref{eqn:hlm-constraint} and \ref{eqn:b-constraint} represent a linear function that gives $K_{\ell m}$ in terms of $\bm D$.
+We further assume that the model describes a way to reverse this equation, to write
+\begin{equation}
+  \bm D = A \bm K.
+  \label{eqn:density-model}
+\end{equation}
+Here, we have arranged $a_m^2$ and the components of $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions. The order of this arrangement is irrelevant, as long as it is kept consistent.
+
+To calculate the uncertainty on $\bm D$ and therefore $\rho(\bm r)$, we first need the covariance matrix $\Sigma_K$ for $\bm K$.
+First, assume that the hybrid frame is offset from the local frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
+Then
+\begin{equation}
+  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{local}.
+  \label{eqn:local-to-hybrid}
+\end{equation}
+Since $K_{\ell m}^\mathrm{local}$ was obtained by an MCMC fit, a large set of posterior-distributed samples are available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{local}$, and the covariance matrix $\Sigma_K$ can be computed statistically by applying equation \ref{eqn:local-to-hybrid} to the samples.
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm D$ is $\Sigma_D = A \Sigma_K A^T$
+and the density distribution and uncertainty on density distribution are equal to
+\begin{equation}
+  \rho(\bm r) = \rho(\bm r, A\bm K) \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
+  \label{eqn:unc-rho}
+\end{equation}
+
+The job of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
+
+\subsection{Likelihood model}
+In order to restrict the space of density distributions that correspond to the known $H_{\ell m}$ so that only one distribution remains, we define a function $\mathcal{L}$ which takes large values for ``nice'' density distributions according to some metric of niceness.
+We then take the density distribution which maximizes $\mathcal{L}$.
+In this way, $\mathcal{L}$ can be thought of a likelihood for the density distribution, but it should not be confused with the likelihood used to extract the fit parameters $K_{\ell m}$.
+
+To employ this method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have constant density $\rho_0$ plus some deviation $D_i$.
+This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
+
+The task is to define a likelihood $\mathcal{L}(\bm D)$ such that the minimum satisfies equation \ref{eqn:density-model}. This happens to be an uncorrelated Gaussian likelihood
+\begin{equation}
+  \mathcal{L}(\bm D) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{D_i^2}{2 \sigma^2}}
+\end{equation}
+with free parameters $\mu$ and $\sigma$.
+These parameters do not affect the location of the maximum, so we do not define them.
+Given this likelihood, the log likelihood is proportional to $-|\bm D|^2$.
+Minimizing the norm of $\bm D$ is therefore equivalent to finding the maximum likelihood.
+
+To minimize this norm, we use the fact that equations \ref{eqn:jlm} and \ref{eqn:am} correspond exactly to a matrix equation $\bm K = M \bm D$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in \ref{eqn:jlm} or \ref{eqn:am} evaluated over the $i$th finite element.
+Since $m>n$, we define the Moore-Penrose inverse of $M$ as
+\begin{equation}
+  M^+ = M^*(MM^*)^{-1}
+  \label{eqn:mpi-underdetermined}
+\end{equation}
+where $M^*$ is the adjoint of $M$. The value of $\bm D$ that minimizes $|\bm D|^2$ and also satisfies equation \ref{eqn:density-model} is then $A=M^+$, which fully defines the model.
+
+Note that this model is fast to compute; assuming fast matrix multiplication, the most time-consuming step is the matrix inversion of equation \ref{eqn:mpi-underdetermined}.
+However, $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+
+\subsection{Harmonic model}
+We now explore a model that seeks to narrow down the space of allowed density distributions a different way than the likelihood model; we define the ``nice'' density distributions directly.
+They are the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid.
+The expansion of such a function in spherical coordinates is given by
+\begin{equation}
+  \rho(\bm r) = \sum_{\ell, m} D_{\ell m} R_{\ell m}^*(\bm r)
+  \label{eqn:harmonic-rho}
+\end{equation}
+where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $D_{\ell m}$ are free parameters.
+The complex conjugate was added for convenience.
+By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
+Choosing the same maximum $\ell$ as the maximum $\ell$ for the $H_{\ell m}$ moments, we have $m=n-1$ coefficients $D_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm D$.
+
+Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:hlm-constraint} and \ref{eqn:b-constraint}, we get 
+\begin{equation}
+  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'}} D_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r)
+\end{equation}
+This is an over-determined matrix equation $\bm K = M \bm D$, where $M$ is an $n \times m$ matrix.
+The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm D$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm D$ is minimized).
+However, the form of the inverse changes due to the matrix now being taller than it is wide.
+The Moore-Penrose is now
+\begin{equation}
+  M^+ = (M^*M)^{-1} M^*
+  \label{eqn:mpi-overdetermined}
+\end{equation}
+and the model concludes with $A=M^+$.
+
+\subsection{Lump model}
+\jtd{Continue}
+
 \section{Conclusion}

### 2022-02-24 code/density/get-exotic-moments.py

@@ -1,0 +1,52 @@
+import numpy as np
+import sys
+sys.path.append("../../code/density")
+from core import Asteroid, Indicator
+from multiprocessing import Pool
+
+division = 9
+max_radius = 1500
+am = 1000
+k22a, k20a = 0.05200629, -0.2021978
+k22s, k20s = 0, -0.09766608
+b = np.sqrt(5/3) * am * np.sqrt(1 - 2 * k20s - 12 * k22s)
+a = np.sqrt(5/3) * am * np.sqrt(1 - 2 * k20s + 12 * k22s)
+c = np.sqrt(5/3) * am * np.sqrt(1 + 4 * k20s)
+
+
+asteroids = [
+    ("sph", Indicator.sph(am), lambda x,y,z: 1),
+    ("ells", Indicator.ell(am, k22s, k20s), lambda x,y,z: 1),
+    ("ella", Indicator.ell(am, k22a, k20a), lambda x,y,z: 1),
+    ("tet", Indicator.tet(am), lambda x,y,z: 1),
+    ("db", Indicator.dumbbell(am), lambda x,y,z: 1),
+    ("in", Indicator.ell(am, k22a, k20a), lambda x,y,z: np.exp(-0.5 * x*x/(a*a) + y*y/(b*b) + z*z/(c*c))),
+    ("out", Indicator.ell(am, k22a, k20a), lambda x,y,z: np.exp(0.5 * x*x/(a*a) + y*y/(b*b) + z*z/(c*c))),
+]
+
+def get_klms(index):
+    name, indicator, generator = asteroids[index]
+    asteroid = Asteroid("", am, division, max_radius, indicator)
+    rlms = asteroid.moment_field(max_l=3)
+
+    density = asteroid.map_np(generator)
+
+    i = 0
+    klms = []
+    for l in range(0, 4):
+        for m in range(-l, l+1):
+            klms.append(np.sum(rlms[i] * density) / am**l * division**3)
+            i += 1
+    klms.append(np.sqrt(np.sum(rlms[i]) / division**3))
+
+    return name, klms / klms[0]
+
+with Pool() as pool:
+    results = pool.map(get_klms, range(len(asteroids)))
+
+for name, klms in results:
+    print(name)
+    for k in klms:
+        print(k)
+    print()
+    

### 2022-02-25 summaries/21-11/21-11.tex
Added lump model to summary

@@
 \usepackage{bm}
+\usepackage{colortbl}
 
@@
 \subsection{Lump model}
-\jtd{Continue}
+The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
+In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the $K_{\ell m}$ fit results.
+
+Suppose the asteroid contains $N$ `lumps' of constant mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid center of mass, and immersed in a constant density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
+(For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.) Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the center of mass of the asteroid.
+The displacement of the asteroid shape from the center of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
+The model therefore has $4N-3$ positional degrees of freedom and rotational degrees of freedom laid out in table \ref{tab:lump-dof}.
+These degrees of freedom should be compared to the known density moments, of which there is a square number $(L+1)^2$.
+However, three of these are the center of mass of the asteroid which is guaranteed, and one is the unconstrained total mass.
+So the total number of known parameters is $(L+1)^2 - 4$.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cc|cccc}
+    \hline \hline
+        &  & \multicolumn{4}{c}{$N$} \\
+        &  & 1  & 2  & 3  & 4  \\ \hline 
+        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 8 & \cellcolor{gray}\color{white} 11 \\
+    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 8 & \cellcolor{gray}\color{white} 11& 14 \\
+        & 3& \cellcolor{gray}\color{white}  7 & \cellcolor{gray}\color{white} 10 & 13 & 16 \\
+    \hline \hline
+  \end{tabular}
+  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modeled, and $d$, the number of independent moment of inertia axes considered for each lump.
+The configurations with $D \leq$ the five known parameters not including $K_{3m}$ are colored black, and those including seven $K_{3m}$ parameters are colored gray.}
+  \label{tab:lump-dof}
+\end{table}
+
+The net $K_{\ell m}$ components of such an ensemble obey
+\begin{equation}
+  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_m^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
+  \label{eqn:klm-stack}
+\end{equation}
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:jlm} and $a_m$ in equation \ref{eqn:am} respectively.
+Crucially, note that the normalizing factors $1/(\mu_m a_m^\ell)$ and $1/\mu_m$ in equations \ref{eqn:jlm} and \ref{eqn:am} do not change to their counterparts for each lump; they remain the known asteroid-wide values.
+The zero-indexed parameters indicate the density moments of the asteroid medium surrounding the lumps.
+
+The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame.
+We can relate the primed moments to the moments calculated relative to each body's center of mass via the translation rules for solid spherical harmonics:
+\begin{equation}
+  K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i \qquad a_i'^2 = a_i^2 + x_i^2 K_{00}
+  \label{eqn:translate-klm}
+\end{equation}
+Here, $K_{00}^i$ is the added mass $\mu_i$ of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate its orientation and moment of inertia ratios.
+The volume is constrained by $a_i^2$.
+These values map directly onto an ellipsoid representation via equations \ref{eqn:ellipsoid-klm}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution is known.
+Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$.
+Therefore, if we define $\bm D$ to contain $K_{2m}^i$ and $a_i^2$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm D$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$.
+Henceforth, we assume that the dimensions of $\bm D$ are less than or equal to the number of known parameters (the shaded regions of table \ref{tab:lump-dof}), so that $A$ is given by equation \ref{eqn:mpi-overdetermined}).
+Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its center of mass.
+
+This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a nonlinear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in the introduction to this section.
+The constraints on $\bm x_i$ and $|mu_i$ are primarily
+\begin{equation}
+  \sum_{i=1}^N \bm x_i \mu_i = \mu_0 \bm x_0
+  \label{eqn:lump-constraints}
+\end{equation}
+where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the center of mass.
+There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
+The overall mass of the asteroid is $\mu_m = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
+The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
+We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with solutions.
+This is done by minimizing
+\begin{equation}
+  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
+  \label{eqn:lump-minimize}
+\end{equation}
+If $\bm x_i$ and $\mu_i$ are chosen to minimize this function, with the constraint of \ref{eqn:lump-constraints} obeyed, then $A=M^+$ and $\bm B(\bm r)$ following from the resulting values of $K_{\ell m}^i$ and $a_i^2$ defines the model.
+If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
 

### 2022-03-01 summaries/21-11/21-11.tex
Lumpy model written

@@
 \begin{equation}
-  \rho(\bm r) = \sum_{\ell, m} D_{\ell m} R_{\ell m}^*(\bm r)
+  \rho(\bm r) = \sum_{\ell, m} \frac{D_{\ell m}}{a_m^\ell} R_{\ell m}^*(\bm r)
   \label{eqn:harmonic-rho}
@@
 \begin{equation}
-  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'}} D_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r)
+  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'} a_m^\ell} D_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r)
+  \label{eqn:harmonic-mat}
 \end{equation}
@@
 and the model concludes with $A=M^+$.
+
+Note that, in the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
+\begin{equation}
+  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_m} \frac{R^{2\ell}}{a_m^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
+\end{equation}
+A nonspherical perturbation will introduce small off-diagonal entries to $M$.
+This diagonal represents an interpretation of the physical meaning of $K_{\ell m}$; they are directly related through this form of $M$ and the matrix equation $\bm K = M \bm D$ to the coefficients of the spherical harmonic expansion of the asteroid in the spherical case.
 
@@
 \end{equation}
+The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
 Here, $K_{00}^i$ is the added mass $\mu_i$ of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate its orientation and moment of inertia ratios.
@@
 \begin{equation}
-  \sum_{i=1}^N \bm x_i \mu_i = \mu_0 \bm x_0
+  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
   \label{eqn:lump-constraints}

### 2022-03-26 paper/main.tex
Worked on paper

\documentclass[fleqn,usenatbib]{mnras}

\usepackage[T1]{fontenc}

\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{bm}
\usetikzlibrary{arrows.meta}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
\newcommand{\jtd}[1]{ {\bf{\color{red} JTD: #1}} }
\newcommand{\unit}[1]{\bm{\hat{#1}}}

\newcommand{\parens}[1]{\left( #1 \right)}
\newcommand{\brackets}[1]{\left[ #1 \right]}
\newcommand{\quat}[1]{\widetilde{\bm{#1}}}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

\title[Flyby Constraints on Asteroids Interiors]{Constraining the Interiors of Asteroids Through Close Encounters}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Jack T. Dinsmore]{
Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
Julien de Wit$^{2}$
\\
% List of institutions
$^{1}$Department of Physics, Massachusetts Institute of Technology\\
$^{2}$Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2022}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
  We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter. We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth flyby. Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best fit precision is affected. Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericenter data and the central body oblateness. Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose four models to construct a representative density distribution from fit results.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
  minor planets, asteroids: general -- methods: data analysis
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

\cite{MOSKOVITZ2020113519}

In this paper, \jtd{Etc.} Section \ref{sec:methods} describes the coordinates and parameters we use to model the encounter and gives the equation of motion and simulation design used to generate synthetic encounter data. Section \ref{sec:fit} describes how density moments are re-extracted from synthetic data and the sensitivity of the precision of re-extracted moments on various system parameters. Section \ref{sec:results} describes how our posterior uncertainties on density moments depend on various physical parameters of the system. Finally, we provide several models to extract density distributions from the density moments in section \ref{sec:distros} and compare their accuracy and precision.

\section{Methods}
\label{sec:methods}

In this section, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (subsection \ref{sec:moments}). Then we derive arbitrary-order equations of motion in section \ref{sec:eom} to simulate an asteroid encounter. Finally, in section \ref{sec:sim}, we describe the simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time.

\subsection{Coordinates}
\label{sec:coordinates}

Throughout this paper, we assume that the asteroid under study is on a hyperbolic flyby with pericenter $r_p$ and excess velocity $v_\infty$. We do not consider any third-body perturbations, and we assume that the body being encountered is much more massive than the asteroid (e.g., Earth, Jupiter).

We make use of two frames of reference to model this system. One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's center of mass. $\unit{X}$ points from the central body to the asteroid pericenter and $\unit{Z}$ pointing parallel to the orbit angular momentum. We will assume that the mass distribution of the central body is known in this inertial frame. In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.

Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$. This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's center of mass. We will solve for the asteroid's mass distribution with reference to the body-fixed frame. For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI.

The relative positions of the body-fixed and inertial frames is given by the position of the asteroid. The relative orientations are of more physical interest. They are represented by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
\begin{equation}
M = R_z(\alpha) R_y(\beta) R_z(\gamma).
\label{eqn:euler-angles}
\end{equation}
Here, $R_i(\theta)$ is a rotation around the unit vector $i$ by $\theta$ (figure \ref{fig:euler-angles}).

\begin{figure}
    \centering
    \begin{tikzpicture}
    \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit x$};
    \draw[-{Latex[length=3mm]}] (0, 0) -- (2, -3) node[anchor=west] {$\unit y$};
    \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
    \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
    \draw[->] (0.5, -0.75) arc (290:302:2.5);
    \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
    \draw[->] (0, 1.2) arc (130:161:1.3);
    \draw (-0.3, 1.3) node[anchor=center] {$\beta$};
    \draw[->] (0.97, -0.52) arc (330:368:1.3);
    \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
    %\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
    %\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0) node[anchor=west] {$\unit Y$};
    %\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
    \end{tikzpicture}
    \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid. Orientation is expressed as a rotation from the body-fixed axes to the inertial axes.}
    \label{fig:euler-angles}
\end{figure}

\subsection{Parameters: density moments}
\label{sec:moments}

In the next section, it will be shown that only certain aspects of the asteroid density distribution affect tidal torque. We isolate those aspects according to parameters we call ``density moments.'' First, we define the unnormalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase. The regular and irregular spherical harmonics are also defined:
\begin{equation}
  \begin{split}
    S_{\ell m}(\bm r) &= (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \\
    R_{\ell m} (\bm r) &= (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
  \end{split}
\end{equation}
These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}.

The density moments of an asteroid are defined as
\begin{equation}
  K_{\ell m} \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
  \label{eqn:klm}
\end{equation}
Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_m$ is the mass of the asteroid, $\rho_m(\bm r)$ is the density distribution, and $a_m$ is a length scale defined (for reasons covered later) as 
\begin{equation}
  a_m^2 = \frac{1}{\mu_m} \int_\mathcal{A} d^3 r \rho(\bm r) r^2.
  \label{eqn:am}
\end{equation}
This length scale can be thought of as akin to the radius of the asteroid (although a spherical asteroid has radius $\sqrt{5/3} a_m$).
Both of these equations should be computed in the body-fixed axes. These equations can be extended to the central body:
\begin{equation}
  \begin{split}
    &J_{\ell m} = \frac{1}{\mu_M a_M^\ell} \int_\mathcal{B} d^3 r \rho_M(\bm r) R_{\ell m}(\bm r)\\
    &a_M^2 = \frac{1}{\mu_M} \int_\mathcal{B} d^3 r \rho(\bm r) r^2.
  \label{eqn:jlm}
  \end{split}
\end{equation}
which should be computed in the inertial axes. Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless. We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th mass moment of the asteroid.

These moments share several key properties which we discuss before continuing. Firstly, for real mass density, properties of the spherical harmonics imply that $K_{\ell m} = (-1)^m K_{\ell, -m}^*$. Therefore, the set of $K_{\ell m}$ for $\ell < L$ provides $L^2$ degrees of freedom. However, some of these degrees of freedom should be removed as discussed below.

By definition, $K_{00}=1$. Furthermore, $K_{1m} = 0$ since the body-fixed frame is centered on the asteroid center of mass. Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}=K_{2,-1} = 0$ and $\Im K_{22}=0$. The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by
\begin{equation}
  \begin{split}
    I_x &= \frac{2}{3}\mu_m a_m^2 \parens{K_{20} - 6 K_{22} + 1}\\
    I_y &= \frac{2}{3}\mu_m a_m^2 \parens{K_{20} + 6 K_{22} + 1}\\
    I_z &= \frac{2}{3}\mu_m a_m^2 \parens{-2K_{20} + 1}.
  \end{split}
  \label{eqn:moi}
\end{equation}
Incidentally, the definition of $a_m$ was chosen to satisfy equation \ref{eqn:moi}.

The physical meaning of $K_{22}$ and $K_{20}$ can be made even more clear in the case that the asteroid is a uniform-density triaxial ellipsoid. In this case, equating equation \ref{eqn:moi} with the moments of inertia of such a body yields semi-major axes of 
\begin{equation}
  \begin{split}
  a &= \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}+12K_{22}}\\
  b &= \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}-12K_{22}}\\
  c &= \sqrt{\frac{5}{3}}a_m\sqrt{1+4K_{20}}.
  \label{eqn:ellipsoid-axes}
  \end{split}
\end{equation}

The physical meaning of the higher-order moments $K_{3m}$ can be gleaned by assessing their symmetry properties. An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_m(x,y,z)=\rho_m(-x,y,z)$) necessarily sets certain density moments to zero. Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}. Note that, while no mirror symmetries set $K_{00}$, $K_{20}$, or $K_{22}=0$, mirror symmetries exist which zero all the other moments, including $K_{3m}$. $\Re K_{32}$, $K_{31}$, and $K_{30}$ are the only $K_{3m}$ components zeroed by only one axis. We will see later that \jtd{see what?}.
\begin{table}
  \centering
  \begin{tabular}{c|ccccccc}
    \hline
    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
    0 &  &  &  &  &  &  & -\\ 
    1 &  &  &  &  & x & y & z\\ 
    2 &  &  & - & x,y & y,z & x,z & -\\ 
    3 & x,z & y,z & z & x,y,z & x & y & z\\ \hline
  \end{tabular}
  \caption{Axes of mirror symmetry that imply zeroed density moments. For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$. Mirror symmetry along $\unit x$ means $\rho_m(x, y, z) = \rho_m(-x, y, z)$. Hyphens indicate that none of the mirror symmetries zero the moment in question. Since $r^2>0$ for $r\neq 0$, no symmetries set $a_m=0$ either.}
  \label{tab:klm-symmetries}
\end{table}

We make one final observation about $K_{\ell m}$: the requirement that $\rho_m(\bm r) \geq 0$ everywhere restricts $K_{\ell m}$. In the case of $K_{2m}$, this fact and the constraint that $I_z$ is larger than $I_x$ or $I_y$ requires $K_{20}$ and $K_{22}$ to fall in the triangle
\begin{equation}
  -\frac{1}{4} \leq K_{20} \leq 0, \qquad |K_{22}| \leq -\frac{K_{20}}{2}.
  \label{eqn:parameter-bounds}
\end{equation}
In practice, we also observe that $|K_{3m}| < 1$; typically, $|K_{3m}| < 0.1$ even.

\subsection{Equations of motion}
\label{sec:eom}

Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision. We present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}. This formulation of the problem will be more useful for this study.

Throughout this paper, we assume that the asteroid remains rigid throughout the encounter. We also assume no third-body perturbations from other Solar System objects. (More precisely, we assume that all third-body perturbing objects are closer to the central body's center of mass than the asteroid perigee distance. Thus, their density moments can be included in the density moments of the central body.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time.

Below follows a derivation of the tidal torque experienced by an asteroid, followed by the system equations of motion.

The gravitational potential energy of the central body is, in its most general form,
\begin{equation}
V(\bm R') = -G\int_\mathcal{B} d^3 R \rho_M(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
\label{eqn:first-pe}
\end{equation}
where $\rho_M$ is the density distribution of the central body and $\mathcal{B}$ indicates the central body's volume. All vectors here are written in the inertial frame. Given $|\bm{R}| < |\bm{R'}|$, Ref.~\cite{Gelderen1998TheSO} gives the identity
\begin{equation}
  \frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
  \label{eqn:ylm-expansion}
\end{equation}
where the sum is shorthand for $\sum_{\ell, m} = \sum_{\ell = 0}^\infty \sum_{m=-\ell}^\ell$.
We are interested in translating the potential energy of equation \ref{eqn:first-pe} to the body-fixed frame. To do this, we let $\bm{R'} = \bm D + \bm U$, where $\bm D$ is the location of the asteroid in the inertial frame. We further define $\bm U = M\bm u$, where $\bm u$ is in the body-fixed frame and $M$ is a rotation matrix given by the Euler angles $\alpha$, $\beta$, and $\gamma$ (see section \ref{sec:coordinates}). The translation from $\bm {R'}$ to $\bm U$ is then attained by the identity 
\begin{equation}
  S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D),
  \label{eqn:ylm-translation}
\end{equation}  
provided by Ref.~\cite{Gelderen1998TheSO}, and from $\bm U$ to $\bm u$ is given by
\begin{equation}
  \begin{split}
    Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell & (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \\
    & \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).\\
  \end{split}
  \label{eqn:ylm-rotation}
\end{equation}
Here, $\mathcal{D}^\ell_{mm'}(M)$ are the Wigner-$D$ matrices, which are determined by the Euler angles $\alpha$, $\beta$, and $\gamma$ of $M$.

Equations \ref{eqn:first-pe} to \ref{eqn:ylm-rotation} then provide formula for $V(\bm u)$ expressed as a a sum of integrals over $\mathcal{B}$ of the central body density $\rho_M(\bm R)$ times $R_{\ell m}(\bm R)$. These are expressed via equation \ref{eqn:jlm} as $J_{\ell m}$.

The tidal torque experienced by the asteroid (in the body-fixed frame) is given by
\begin{equation}
  \bm{\tau}(\bm u) = \int_\mathcal{A} d^3 u \rho_m(\bm u) (\bm u \times (-\nabla_{\bm u} V(\bm u)))
\end{equation}
where $\rho_m$ is the density distribution of the asteroid and $\mathcal{A}$ indicates the volume of the asteroid. Making use of one more identity concerning the derivatives of spherical harmonics:
\begin{equation}
  \begin{split}
  \bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}\Big[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
  &+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)\\
  & +2im\unit z R_{\ell m}(\bm u)\Big],
  \end{split}
\end{equation}
tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, and the asteroid orientation and position. Explicitly,
\begin{equation}
  \begin{split}
  \bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
  &\left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
  &\Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
  &+(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg].
  \end{split}
  \label{eqn:tidal-torque}
\end{equation}

Equation \ref{eqn:tidal-torque} possesses a few explicit properties which we discuss before writing the asteroid equations of motion. Firstly, $K_{00}$ does not appear, so that $\bm \tau$ is independent of asteroid mass. The mean density of the asteroid is therefore not constrained by tidal torque analysis. Secondly, torque is largest when $D$ is small (as expected). Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(D/a_M)^\ell (D/a_m)^{\ell'}$, the latter of which especially is a small number in most cases. Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$. For our analysis, we remove $\ell > 3$.

Further insight can be gained by asking when $\bm \tau = 0$. This occurs to first order when (1) $\alpha=\phi$ (or  $\alpha=\phi+\pi$) and $\beta =\pi/2$, and (2) when $\alpha=\phi\pm\pi/2$ and $\gamma$ is an integer multiple of $\pi/2$. Here, $\phi$ is the angle between perigee and $\bm D$. At perigee ($\phi=0$), these correspond to (1) $\unit z \parallel \unit X$ and (2) $\unit z$ is in the $\unit{Y}\unit{Z}$-plane with an additional condition on $\gamma$.

Also important is when $\bm \tau \parallel \unit z$; this case has special meaning because for a non-tumbling asteroid, $\omega \parallel \unit z$, and $\tau \parallel \unit z$ ensures that the asteroid will continue not to tumble. Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first order. Setting $\alpha = \phi \pm \pi/2$ also forces $\bm \tau \parallel \unit z$ to first order.

The equations of motion of the asteroid position $\bm D$ are given by Newton's law of gravitation:
\begin{equation}
  \dot{\bm V} = -\frac{G \mu_M}{r^3} \bm D \qquad \dot{\bm D} = \bm V
  \label{eqn:pos-eom}
\end{equation}
Rather than derive equations of motion for the Euler angles (which suffer from gimbal lock), we instead represent the orientation of the asteroid with a quaternion $\quat q$ which can be converted into Euler angles to compute $\mathcal{D}(\alpha, \beta, \gamma)$. This quaternion evolves as 
\begin{equation}
  \dot{\quat q} = \frac{1}{2}\quat q\quat \omega.
  \label{eqn:quat-eom}
\end{equation}
for angular velocity $\bm \omega$ given in the body-fixed frame. The equations of motion of $\bm \omega$ in turn are given by
\begin{equation}
  \begin{split}
    I_x \dot \omega_1 - \omega_y \omega_z (I_y - I_z) &= \tau_x\\
    I_y \dot \omega_2 - \omega_z \omega_x (I_z - I_x) &= \tau_y\\
    I_z \dot \omega_3 - \omega_x \omega_y (I_x - I_y) &= \tau_z.
  \end{split}
  \label{eqn:omega-eom}
\end{equation}
Equations \ref{eqn:pos-eom} to \ref{eqn:omega-eom} and \ref{eqn:tidal-torque} form a set of nonlinear, first-order coupled differential equations which can be numerically integrated. They are expressed in terms of the physical parameters $\mu_{M/m}$, $a_{M/m}$, $J_{\ell m}$ and $K_{\ell m}$ given the density moment-moment of inertia relations given by equation \ref{eqn:moi}.

\subsection{Simulation design}
\label{sec:sim}

We built a simulation to produce angular velocity data (in the inertial frame) as a function of time. This simulation requires as input (1) the orbital parameters of the asteroid; (2) the cadence of angular velocity observation; (3) the central body moments, mass, and $a_m$; (4) the initial asteroid angular velocity in the inertial frame; (5) the asteroid radius $a_m$, and (6) the asteroid's density moments and initial Euler angle $\gamma_0$. All parameters except (6) are assumed to be known to high accuracy. One can imagine that $a_m$ is determined by light-curve analysis, but if not, it is still necessary to fix $a_m$ or else the values of $K_{\ell m}$ are degenerate with $a_m$.

We further assume that the asteroid is initially not tumbling. Thus, the rotational velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia). This sets $\beta = 0$ and we can further choose $\alpha = 0$. Thus, only one Euler angle $\gamma = 0$ is necessary to provide initial data for the simulation.

We begin our simulation at $D = 10 r_p$. Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee. Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.

With the simulation inputs specified, the equations of motion were integrated via the Runge-Kutta fourth order method, with a variable time step
\begin{equation}
  \Delta t = \Delta t_\text{min} + 10^{-3}(\Delta t_\text{max} - \Delta t_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
\end{equation}
The parameters $\Delta t_\text{max}$ and $\Delta t_\text{min}$ (20 and 10 seconds respectively) were chosen such that the finite-integration error \jtd{Is this the correct name?} was ~100 times the numerical error, and that neighboring values of $K_{\ell m}$ yielded significantly different spin pole data.

\section{Injection-retrieval tests}
\label{sec:injection-retrieval}

In this section, we discuss how the simulation presented in the previous section was used to generate synthetic data and re-extract the density moments to assess how the precision of the re-extracted moments depends on the system parameters (e.g., true density moments, orbital parameters, etc.)

\subsection{Fit process}
\label{sec:fit}
Given synthetic data, a Markov Chain Monte Carlo (MCMC) \jtd{find the Ensemble full name and cite} method was used to generate posterior distributions based on flat priors. \jtd{How detailed about the MCMC do I need to be?} Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{\ell m}$ given in section \ref{sec:moments}. Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to relabeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.

Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \jtd{Cite?}. It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate. Walkers were initialized near this local minimum, with spread given by the inverse Hessian of the likelihood at that point. Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood. Therefore, a simpler simulation with the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find $K_{3m}$, with $\gamma_0$ and $K_{2m}$ fixed. This tiered miniimzation process motivates us to call $\gamma_0$ and $K_{2m}$ the ``first-order parameters'' and $K_{3m}$ the ``higher order parameters.''

We further subdivided the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$. In practice, $f=2$ often led to success. The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial guess.

\subsection{Uncertainty model}
\label{sec:uncertainty}

We model uncertainty in each spin vector $\bm \omega$ as uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated. Consider a true spin vector $\bm \omega^*$. Coordinates can be chosen in which $\bm \omega^* \parallel \unit Z$. Then, expressing the observed spin vector $\bm \omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centered on zero and the azimuthal angle from a uniform distribution. We also draw the ratio $\rho=\omega/\omega^*$ from a log-normal distribution centered on one, with width $\sigma_\rho$. We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole. Explicitly, the probability density function (PDF) of $\rho$ is 
\begin{equation}
  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}
\end{equation}
See figure \ref{fig:uncertainty-model} for a representation of the uncertainty model.

\begin{figure}
  \centering
  \begin{tikzpicture}
  \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit X$};
  \draw[-{Latex[length=3mm]}] (0, 0) -- (1, -1.5) node[anchor=west] {$\unit Y$};
  \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};

  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \omega^*$};
  \draw[dashed] (-3, -2) -- (-3, 3);
  \draw[dashed] (-3, -2) -- (0, 0);

  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \omega$};
  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
  \draw (-3, 3) arc (110:93:6);
  \draw (-2, 3.5) node[anchor=center] {$\theta$};
  \draw (-1, 1.8) node[anchor=center] {$\rho \omega^*$};

  \end{tikzpicture}
  \caption{Diagram of the uncertainty model used to define the probability that the true spin vector $\bm \omega^*$ should be observed as $\bm \omega$. The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
  \label{fig:uncertainty-model}
\end{figure}

The log likelihood resulting from this uncertainty model is (excluding additive constants)
\begin{equation}
  \ln \mathcal{L} = -\sum_{i = 0}\frac{\cos^{-1} (\bm \omega_i^* \cdot \bm \omega_i/(\omega_i^* \omega_i))^2}{2\sigma_\theta^2}+\frac{\ln \parens{\omega_i /\omega_i^*}^2}{2\sigma_\rho^2} + \ln\frac{\omega_i}{\omega_i^*}.
  \label{eqn:log-likelihood}
\end{equation}

In figure \ref{fig:example-data}, we present example spin data generated via this simulation. A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter. The exact parameters used were the symmetric and asymmetric cases described in appendix \ref{app:reference-configs}. Bands containing 68.3\%, 95.5\%, and 99.7\% of the population's spin are shown, as is the spin of the reference asteroids in black.

\begin{figure*}
  \centering
  \includegraphics[width=0.7\linewidth]{figs/nominal-data-sym.pdf}
  \includegraphics[width=0.7\linewidth]{figs/nominal-data-asym.pdf}
  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroid densities and the reference orbit (black lines). Also plotted is the deviation of the data for posterior-PDF-distributed perturbations to the asteroid shape (bands). Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
  \label{fig:example-data}
\end{figure*}

To choose the initial values of $\gamma_0$, $K_{20}$, and $K_{22}$, spin data for the reference asteroids of appendix \ref{app:reference-configs} was first generated. Then $\gamma_0$, $K_{20}$, and $K_{22}$ were re-extracted via the fit described in section \ref{sec:fit}. The population's values for these parameters were posterior-distributed. However, the posterior distribution was widened by a factor of 1000 to make the band widths visible. Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in one band.

The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged. The asymmetric case leads to more divergence than the symmetric case --- a feature which will be generalized in the next section.

\section{Results}
\label{sec:results}

In this section, we assess the sensitivity of the posterior distributions for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations. Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the central body oblateness, and the asteroid period. These effects are presented roughly in order of how much they affect the parameter precision, from highest to lowest.

Parameter precision of 1-$\sigma$ is defined such that 68.27\% of the posterior distribution lies within 1-$\sigma$ of the mean of the posterior distribution. 2-$\sigma$ is defined likewise for 95.45\% of the posterior. The posteriors are usually roughly Gaussian, so that 1-$\sigma$ is roughly the standard deviation of the posterior.

In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated. We further present a test of how precision depends on cadence, asteroid period, and the duration of the flyby in appendix \ref{app:cadence-tests}, and we compare precision for a Jupiter and an Earth flyby in appendix \ref{app:jupiter-earth}.

\subsection{Orbital elements}
\label{sec:scan-orbit}
A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body. The orbit can be rotated to the $\unit X \unit Y$-plane by changing the density moments of the central body. Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant up to the $J_{2m}$ terms of equation \ref{eqn:tidal-torque} we do not investigate them here.

We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$. Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 68 and 95\% confidence intervals are displayed in figures \ref{fig:scan-perigee} for $r_p$ and \ref{fig:scan-vex} for $v_\infty$.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$. The vertical dashed line indicates the reference asteroid value.}
  \label{fig:scan-vex}
\end{figure}

Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$. This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest. There are also smaller-scale oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying. The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee, so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$. This effect explains why these small-scale oscillations have the same period for all parameters.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$. The vertical dashed line indicates the reference asteroid value. The dotted curve indicates a power-law fit (see text).}
  \label{fig:scan-perigee}
\end{figure}

Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_m/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:eom}. For $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution, with uncertainty ranging from -1 to 1. Near $r_p \approx 40$ Earth radii, the $K_{32}$ and $K_{31}$ components also fill the prior. However, the width of the prior was arbitrarily chosen, and all the physical density distributions have $|K_{3m}| < 0.1$ \jtd{Check}, so the actual Earth radii cutoff at which the $K_{3m}$ parameter estimates become too imprecise to be usable likely occurs at lower $r_p$. The exact value depends on the shape of the asteroid, but \jtd{When is it 0.1?}

\begin{table}
  \centering
  \begin{tabular}{l|c}
    \hline
    Parameter & $\alpha$ \\ \hline
    $\gamma_0$ & $2.05$ \\
    $K_{22}$ & $5.47$ \\
    $K_{20}$ & $5.47$ \\ \hline
    $\Re K_{33}$ & $3.35$ \\
    $\Im K_{33}$ & $3.37$ \\
    $\Re K_{32}$ & $3.05$ \\
    $\Im K_{32}$ & $3.27$ \\
    $\Re K_{31}$ & $3.53$ \\
    $\Im K_{31}$ & $4.02$ \\
    $K_{30}$ & $5.75$ \\ \hline
  \end{tabular}
  \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
  \label{tab:scan-perigee-alpha}
\end{table}

Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties, $\sigma \propto r_p^\alpha$. These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior. The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}. These slope values express how much each parameter is dependent on $r_p$. It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$. The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$. The second-order parameters have milder slopes between 3 and 4, except for $K_{3m}$, which is fortunate from the perspective of observation, since it make render larger values of $r_p$ accessible to measuring $K_{3m}$.

The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{3m}$ to other $K_{3m}$ values. This is likely because \jtd{Something to do with uncertainty in orientaiton combining with high-frequency denisty sensitivity.}. This pattern will be seen in the following sections as well.

The very strong dependence of $\sigma$ on $r_p$ makes this analysis only usable on close flybys. Fortunately, in the case of Earth, these flybys are also likely to have the best associated observational uncertainty due to their proximity. \jtd{Unfounded speculation, but hopefully this is ok.}

\subsection{Observational Uncertainty}
\label{sec:scan-uncertainty}
There are two variables, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}). Rather than explore the full space spanned by these two values, we measure how parameter uncertainties depend on the product of uncertainties $\sigma_\theta\sigma_\rho$ (with the radio fixed), and the ratio $\sigma_\rho / \sigma_\theta$ (with the product fixed).

We choose these metrics because we generally expect that the parameter uncertainty $\sigma$ be proportional to the observational uncertainty, but whether the dependence is stronger on $\sigma_\theta$ or $\sigma_\rho$ is not immediately clear. We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their product, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}. Indeed we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$. For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma_\theta = 1$ at this point, so that $\sigma(K_{30}) \approx 1$ which fills the prior. Uncertainty cannot increase beyond this value.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$. The vertical dashed line indicates the reference asteroid value.}
  \label{fig:scan-product}
\end{figure}

We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}. If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then we would have no dependence of $\sigma$ on $\sigma_\rho / \sigma_\theta$. Any dependence shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$. The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.}
  \label{fig:scan-ratio}
\end{figure}

Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$. We summarize this pattern my stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period. This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by lightcurve analysis, but I have no evidence.}

Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that all parameters depend on $\sigma_\theta$ and $\sigma_\rho$ in nearly the same way (at least in the data presented). The only differences between parameters is the overall size of $\sigma$ (which shows the same dependence on $\ell$ and $m$ mentioned previously) and the fact that $\sigma$ behaves erratically when near $\pm 1$, where it fills the prior.

\jtd{I should probably be commenting on when the parameter uncertainties are too large.}

\subsection{Asteroid shape}
\label{sec:scan-shape}

The true values of $K_{\ell m}$, $\gamma_0$, and $a_m$ affect the uncertainties in extracted density moments $\sigma$. Here, we only investigate the sensitivity of $\sigma$ on the first order parameters and $a_m$. The $K_{2m}$ moments can therefore also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).

In figure \ref{fig:scan-space-sigma}, we show the 1-$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$. We use axis ratios rather than the values of $a$, $b$, and $c$ exactly to remove the $a_m$ dependence of equation \ref{eqn:ellipsoid-axes}. The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis. The two are uncorrelated and therefore the data has no physical dependence on $\gamma_0$ when $K_{22}=0$. This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.

\begin{figure*}
  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-3-sigma.pdf}

  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-b-sigma.pdf}

  \caption{1-$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}). Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a square.}
  \label{fig:scan-space-sigma}
\end{figure*}

To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid with free parameters $K_{20}$ and $K_{30}$ only and run a fit. For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter. This task is beyond the scope of this paper, so we consider mostly asymmetric asteroids throughout.

Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different or when $|K_{22}|$ is large. Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ increase for large $K_{20}$, which is large axis ratios in the ellipsoid case (non-sphericity). For flat, disk-like asteroids, a different parametrization might therefore be more appropriate.

Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters for reference. They show that $\gamma_0$ and $K_{22}$ are highly correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are generally uncorrelated. This is expected $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not. They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated. The latter is expected due to the $1/c$ dependence. As for the former, this correlation could likely be removed by an alternate parametrization, reducing uncertainties in the shape parameters. However, it is not clear whether these new parameters would have an obvious physical interpretation or whether they would be useful.

\begin{figure*}
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr12.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr13.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr23.pdf}

  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-ab.pdf}

  \caption{Correlations between parameter posteriors for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).  Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a square.}
  \label{fig:scan-space-corr}
\end{figure*}

Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner). It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating a flyby, as we do in this paper. The uncertainty then can be expected to differ across other shapes by a factor of about two or less.

\subsection{Cadence}
\label{sec:scan-cadence}

The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes. We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.}
  \label{fig:scan-cadence}
\end{figure}

Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence ($\Delta t$) for $\Delta t \lesssim 40$ min. We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points. However, uncertainty dramatically increases for many parameters at about $\Delta t = 40$ min, a time scale which is likely characteristic of the asteroid system. We name this rough cadence limit $T_\text{cad}$.

By dimensional analysis, we expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P$ and the time spent near perigee $T_p$. The latter can be estimated by the unitless combination
\begin{equation}
  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{M}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
  \label{eqn:tp}
\end{equation}
which is the ratio of the perigee radius to velocity at perigee. The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible. For the simulated asteroid, $P = 9$ hr and $T_p = 42$ min by this definition. Immediately we see $T_p \approx T_\text{cad}$, but this is not necessarily significant because $T_p$ is an estimate.

Which of $P$ and $T_p$ is more important to the determination of $T_\text{cad}$ is assessed in appendix \ref{app:cadence-tests}.

Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal. However, it is generally better to have short cadence when possible.

\subsection{Perigee gap}
\label{sec:scan-gap}
In certain negative circumstances, spin data might not be able to be captured for a close encounter at perigee. The asteroid might dip below the horizon, or it might pass too close to the sun to be observed. Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low. The angular velocity evolution here is dominated by torque-free precession dictated by the moment of inertia components. so that zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ \cite{MOSKOVITZ2020113519}. However, $K_{3m}$ are not extractable from precession data alone. We are therefore curious as to how our posterior uncertainties change due to lack of data during the encounter perigee.

To test this, we mask the perigee of the counter by removing data within time $T$ of the perigee, where $T$ ranges from 0 to 3 hours. To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee. We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma$ in figure \ref{fig:observation-gap}.

\begin{figure}
  \centering
  \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.}
  \label{fig:observation-gap}
\end{figure}

Since torque is highest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore that uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}. We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.

Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range. This cutoff is likely determined by the orbital elements of the encounter, which control how much time the asteroid spends in the high-torque region. On the other hand, none of the uncertainties increase noticeably for $T < 30$ min. Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.

Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$. They also have quantitatively the same cutoff of 30 min before uncertainty is markedly affected. This suggests that the factors that govern uncertainty due to cadence and uncertainty due to lack of data at perigee are the same.

\subsection{Initial spin pole}
\label{sec:scan-spin}

The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \omega_0$ both because spin sets the initial asteroid orientation (up to $\gamma_0$) and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}). As an example, in section \ref{sec:eom}, we noted that $\bm \omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.

In figure \ref{fig:scan-spin}, we display 1-$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \omega_0$, mapped onto the sky in the inertial frame. Our samples for $\bm \omega_0$ were laid out on a Fibonacci sphere to ensure they were evenly spaced (marked in figure \ref{fig:scan-spin-avg}). To highlight common features across the parameters, we also display the average 1-$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}. The average is weighted such that the uncertainty map for each parameter contributes an equal amount
(the weight of each map is set to one-tenth of the map's mean). This average map is presented in two different projections to allow data at $\unit Z$ to be read.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
  \caption{$1-\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin. All maps are made in the Mollweide projection and shown in the inertial $\unit X-\unit Y-\unit Z$ frame. The orange star indicates the reference spin pole.}
  \label{fig:scan-spin}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-mollweide.pdf}
  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
  \caption{The weighted average of the uncertainties shown in figure \ref{fig:spin-pole}, in Mollweide (\textit{left}) and polar (\textit{right}) projections. See text for a description of how the average was computed. Black dots indicate the locations of sample spin poles, and the orange star indicates the reference spin pole.}
  \label{fig:scan-spin-avg}
\end{figure*}

Figure \ref{fig:scan-spin-avg} confirms our expectation that the fit parameters would be uncertain near $\bm \omega \propto \unit Z$, where $\bm \tau \parallel \unit z$. The $\unit z \parallel \unit X$ zero-torque setting doesn't appear in the figure however, likely because torque is large enough at $\phi \neq 0$ that the fact that $\unit z \parallel \unit X$ provides $\bm \tau = 0$ at $\phi = 0$ is not enough.

The other predicted $\bm \omega_0$ resulting in lack of precision were for $\alpha = \phi \pm \pi/2$, which causes $\bm \tau \propto \unit z$ and $\bm \tau = 0$ when $\gamma$ is an integer multiple of $\pi/2$. There does appear to be an associated lack of precision at $\bm \omega_0 \propto \unit Y$ (the $\phi=0$ case) \jtd{Why?}

\subsection{Oblateness}
\label{sec:scan-oblateness}

\subsection{Rotational period}
\label{sec:scan-period}

\section{Density distributions}
\label{sec:distros}

\subsection{General density model design}

\subsection{The Likelihood model}

\subsection{The Harmonic model}

\subsection{The Lumpy model}

\subsection{Comparisons between density models.}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data Availability}

The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

\bibliographystyle{mnras}
\bibliography{asteroids.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Reference asteroid configurations}
\label{app:reference-configs}

\section{What sets the cadence cutoff?}
\label{app:cadence-tests}

\section{Comparison of Jupiter and Earth flyby}
\label{app:jupiter-earth}

\section{Similarity between cadence and lack of perigee data.}
\label{app:cadence-perigee-test}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2022-03-26 data/probe-sigma/compile.py

@@ -54,64 +54,60 @@ for name in percentiles.keys():
 
 true_sigmas = np.array(true_sigmas)
 
-fig, axs = plt.subplots(figsize=(14, 8), ncols=3, nrows=4, sharex=True)
-axs = axs.reshape(-1)
-i = 0
+fig = plt.figure(figsize=(6.6, 19))
 
-for plot_index in range(N_DIM+1):
-    if plot_index == 9:
-        continue
+for plot_index in range(N_DIM):
+    offset = 1 if plot_index > 2 else 0
+    ax = plt.subplot2grid((31, 1), (plot_index * 3 + offset, 0), rowspan=3)
+
     product = true_sigmas**2 * ratio
     param_data = np.zeros(len(product) * N_PERCENTILES).reshape(N_PERCENTILES, len(product))
     for f in percentiles.keys():
-        param_data[:,name_index[f]] = percentiles[f][i]
-    scale = 10**5 if i < 3 else 1
+        param_data[:,name_index[f]] = percentiles[f][plot_index]
+    scale = 10**5 if plot_index < 3 else 1
 
-    axs[plot_index].plot(product, (param_data[1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].plot(product, (param_data[-1]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].fill_between(product, (param_data[1]-param_data[0]) / true_sigmas * scale, 
-        (param_data[-1]-param_data[0]) / true_sigmas * scale,  color=f"C{i}", alpha=0.3)
+    ax.plot(product, (param_data[1]-param_data[0]) / true_sigmas * scale, color=f"C{plot_index}", linewidth=1)
+    ax.plot(product, (param_data[-1]-param_data[0]) / true_sigmas * scale, color=f"C{plot_index}", linewidth=1)
+    ax.fill_between(product, (param_data[1]-param_data[0]) / true_sigmas * scale, 
+        (param_data[-1]-param_data[0]) / true_sigmas * scale,  color=f"C{plot_index}", alpha=0.3)
 
-    axs[plot_index].plot(product, (param_data[2]-param_data[0]) / true_sigmas * scale, color=f"C{i}", linewidth=1)
[…]

### 2022-03-26 data/scan-period/compile.py

@@ -58,59 +58,53 @@ for name in percentiles.keys():
 
 period = np.array(period)
 
-fig, axs = plt.subplots(figsize=(14, 8), ncols=3, nrows=4, sharex=True)
-axs = axs.reshape(-1)
-i = 0
+fig = plt.figure(figsize=(6.6, 19))
 
-for plot_index in range(N_DIM+1):
-    if plot_index == 9:
-        continue
+for plot_index in range(N_DIM):
+    offset = 1 if plot_index > 2 else 0
+    ax = plt.subplot2grid((31, 1), (plot_index * 3 + offset, 0), rowspan=3)
     param_data = np.zeros(len(period) * N_PERCENTILES).reshape(N_PERCENTILES, len(period))
     for f in percentiles.keys():
-        param_data[:,name_index[f]] = percentiles[f][i]
-    scale = 1e7 if i < 3 else 1e2
+        param_data[:,name_index[f]] = percentiles[f][plot_index]
+    scale = 1e7 if plot_index < 3 else 1e2
 
-    axs[plot_index].plot(period, (param_data[1]-param_data[0]) * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].plot(period, (param_data[-1]-param_data[0]) * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].fill_between(period, (param_data[1]-param_data[0]) * scale, 
-        (param_data[-1]-param_data[0]) * scale,  color=f"C{i}", alpha=0.3)
+    ax.plot(period, (param_data[1]-param_data[0]) * scale, color=f"C{plot_index}", linewidth=1)
+    ax.plot(period, (param_data[-1]-param_data[0]) * scale, color=f"C{plot_index}", linewidth=1)
+    ax.fill_between(period, (param_data[1]-param_data[0]) * scale, 
+        (param_data[-1]-param_data[0]) * scale,  color=f"C{plot_index}", alpha=0.3)
 
-    axs[plot_index].plot(period, (param_data[2]-param_data[0]) * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].plot(period, (param_data[-2]-param_data[0]) * scale, color=f"C{i}", linewidth=1)
-    axs[plot_index].fill_between(period, (param_data[2]-param_data[0]) * scale,
[…]

### 2022-03-26 paper/main.tex
Trying to figure out why the spin behaves so weirdly

@@
 
+\jtd{To figure this out, I'm running some searches for spins along the equator. Hope to see the same peak at Y, and I'll see if it goes away for an iteration when gamma zero changes.}
+
+\jtd{Tomorrow, I plan to do the rest of this paper and skip this section. If I can't figure it out, I'll remove it.}
+
+\jtd{Remember to include the changes when a fast rotator comes in.}
+
 \subsection{Oblateness}

### 2022-03-26 code/fit_resolved/fit.py

@@ -1,5 +1,7 @@
 TEST = False
 
+VELOCITY_MUL = 1
+
 import numpy as np
 import matplotlib.pyplot as plt
 import emcee, time, sys, logging
@@ -30,7 +32,7 @@ except:
 logging.basicConfig(level=logging.INFO)
 
 PLOT_POSES = True
-NUM_MINIMIZE_POINTS_PER = 8
+NUM_MINIMIZE_POINTS_PER = 4 # Used to be 8
 NUM_L3_MINIMIZATIONS = 2
 DISTANCE_RATIO_CUTS = [
     [2.0, None],
@@ -99,6 +101,7 @@ logging.info("Theta high {}".format(theta_high))
 logging.info("Theta low {}".format(theta_low))
 logging.info("Sigma {}".format(sigma))
 logging.info("Name {}".format(output_name))
+logging.info("Velocity multiplier {}".format(VELOCITY_MUL))
 N_DIM = len(theta_true)
 
 reload = False
@@ -110,23 +113,23 @@ def fit_function(theta, target_length=None):
     if ASTEROIDS_MAX_K == 3:
         if ASTEROIDS_MAX_J == 0:
             resolved_data = asteroids_0_3.simulate(cadence, jlms, theta, radius,
-                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False)
+                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False, VELOCITY_MUL)
         elif ASTEROIDS_MAX_J == 2:
             resolved_data = asteroids_2_3.simulate(cadence, jlms, theta, radius,
-                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False)
+                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False, VELOCITY_MUL)
         elif ASTEROIDS_MAX_J == 3:
             resolved_data = asteroids_3_3.simulate(cadence, jlms, theta, radius,
-                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False)
+                spin[0], spin[1], spin[2], perigee, speed, GM, EARTH_RADIUS, 0, False, VELOCITY_MUL)
     elif ASTEROIDS_MAX_K == 2:
         if ASTEROIDS_MAX_J == 0:
             resolved_data = asteroids_0_2.simulate(cadence, jlms, theta, radius,
[…]

### 2022-03-26 paper/main.tex
Finished parameter overview

@@
 
+In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
+By assumption that $\mu_M \gg \mu_m$ (so that the asteroid orbit's focus is the center of mass of the central body), we have $J_{1m} = 0$.
+The effect of oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_M / D)^2$.
+We expect these parameters to have little effect on the asteroid.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_M R_M^2)$, where  $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_M$ is the true radius of the body (not $a_M)$.
+Note that $J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
+But for an equatorial orbit, the principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
+(Some sources such as Ref.~\cite{paterLissauer2015} take this definition of $\epsilon$ as their definition of $J_{20}$).
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range ofittedf oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in figure \ref{fig:scan-oblateness}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
+  \vfill
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
+  \caption{\textit{Left}: 1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
+Linear best fit lines to $\sigma$ (black, dotted) are plotted.
+\textit{Right}: The deviation of posterior mean extracted from a zero-oblateness model from the true parameters given a model with oblateness $\epsilon \neq 0$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies.}
+  \label{fig:scan-oblateness}
+\end{figure}
+
+Figure \ref{fig:scan-oblateness} (top pane) demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from the effect of other factors studied above.
+Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
+The linear best-fit lines match the data well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+Other parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive.
+
+Note that if a flyby is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_M$ and $\mu_M$ will change in addition to $\epsilon$.
+These two parameters do affect the precision of the fit parameters, so the figure does not state that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+
+Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the effect of planetary oblateness when fitting $K_{\ell m}$ to data.
+However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that this is not valid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated by assuming nonzero $\epsilon$.
+The difference between the posterior mean $K_{\ell m}$ and true $K_{\ell m}$ are shown.
+Posterior uncertainties are also shown as bands.
+The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m} = 0$ is not contained in the 2-$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
+Therefore, accurately modeling oblateness to high precision is essential for accurate estimation of fit parameters.
+For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, so it is also vital to use the correct asteroid orbital plane.
+
+Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, including it in $J_{20}$.
+Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body center of mass (though the effect is not quite quadratic because $a_m$ also increases for large distances).
+This process is only valid when the asteroid never passes closer to the central body than the moon.
+
+As an order-of-magnitude estimate for this effect, two spherical masses with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
+Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
+
+This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
+Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
+However, correct representation of oblateness is essential to correctly estimate $K_{\ell m}$.
+
 \subsection{Rotational period}
 \label{sec:scan-period}
+
+The final encounter parameter we study is the initial rotational period of the asteroid $P_\omega$.
+The dynamical time scales $r_p/v_\infty$ and $\mu_m / (r_p v_\infty)$ have already been mentioned and the ratio between them and $P$ in principal may affect the posterior uncertainty $\sigma$.
+In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
+  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P$.
+The reference value of 9 hr is shown as a vertical dotted line.}
+  \label{fig:scan-period}
+\end{figure}
+
+Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
+But a large-scale trend is also visible in many parameters.
+$K_{20}$ and $K_{22}$ show very large uncertainty for low $P_\omega$ because these asteroids do not tumble after perigee, and tumbling after the perigee allows better refinement of the $K_{2m}$ parameters.
+
+We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, $\beta$, and which affect $\bm \tau$ vary much smaller than $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and we see that each rotation has zero average first-order torque.
+Since the first-order torque over each rotational period cancels out, there is no secular torque to force the asteroid to tumble.
+However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
+
+Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
+This is most visible in the figure for $K_{30}$.
+The cause of this is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
+We already discussed that asteroids with $P_\omega$ large do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ don't affect.
+
+The most severe effect of period on $\sigma$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
+The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
+It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids still have better uncertainty.
 

### 2022-03-26 data/oblateness/compile.py

@@ -16,7 +16,6 @@ oblateness_markers = {
 
 percentiles = {}
 name_index = {}
-true_sigma = []
 j2s = []
 
 AXIS_SIZE = 12
@@ -62,7 +61,6 @@ for name in percentiles.keys():
         theta_low = [float(x) for x in f.readline().split(',')]
         sigma = [float(d) for d in f.readline().split(',')]
     name_index[name] = int(dir_name[-2:])
-    true_sigma = sigma[0]
     j2s.append(jlms[-1])
 
 oblatenesses = -np.array(j2s) / 2

### 2022-03-26 paper/main.tex
Added density distribution section

@@
 \usepackage{tikz}
+\usepackage{colortbl}
+\usepackage{dsfont}
 \usepackage{bm}
@@
 
+Hitherto, we have only discussed the density moments $K_{\ell m}$ of the asteroid rather than the true density distribution $\rho(\bm r)$.
+This is because only the density moments are observable by tidal torque interactions.
+However, by making assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
+
+In this section, we outline three different assumptions which yield different types of density distributions for the same $K_{\ell m}$.
+One of them can be chosen, or a fourth created, depending on what features are desired to be represented in the density distribution.
+All three of these models assume that the asteroid shape is known (for example, by light curve or radar data).
+Uncertainty on this shape estimate is assumed to be small.
+The models then produce a density distribution $\rho(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho$.
+
+Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
+Only the differences in $\rho$ across the body are measurable.
+
+In section \ref{sec:general-density}, we describe the general form our three models must take.
+Then we lay out each individually and compare them in section \ref{sec:density-compare}.
+In appendix \ref{app:find-surface}, we do not assume that the asteroid shape is known and instead assume that the density is constant.
+This allows us to compute the asteroid shape from $K_{\ell m}$.
+
 \subsection{General density model design}
+\label{sec:general-density}
+
+To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
+Since the asteroid rotates around its center of mass during observations, we assume that the location of the center of mass is also known in this frame, so that we can set it to be the origin.
+
+We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
+The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exactly in the hybrid frame, and the $K_{\ell m}$ components are known in the local frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ and the known $a_m$.
+
+The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_m$ at the value assumed during the fit, removing the non-linearity induced by division by $a_m$.
+Furthermore, since the system is independent of the total asteroid mass, we set $\mu_m$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
+Similarly, the form of equation \ref{eqn:am} guarantees that $a_m^2$ is linear in $\rho(\bm r)$.
+Equation \ref{eqn:am} and equation \ref{eqn:klm} applied to $K_{00}=1$ can be used to enforce the choices of $\mu_m$ and $a_m^2$.
+
+Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm D)$ for an $m$-dimensional vector $\bm D$ which controls the free parameters of $\rho$.
+We will leave the explicit definition of $\rho(\bm r, \bm D)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm D$; i.e.,
+\begin{equation}
+  \rho(\bm r, \bm D) = \bm B(\bm r) \cdot \bm D
+  \label{eqn:density-distro}
+\end{equation}
+for a $m$-dimensional vector $\bm B(\bm r)$.
+Thus, the defining equations of $a_m^2$ and $K_{\ell m}$ represent a linear function that give the parameters in terms of $\bm D$.
+We further assume that the model describes a way to reverse this equation, to write
+\begin{equation}
+  \bm D = A \bm K
+  \label{eqn:density-model}
+\end{equation}
+where $A$ is a matrix.
+Here, we have arranged $a_m^2$ and the known components of $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
+The order of this arrangement is irrelevant, as long as it is kept consistent.
+
+To propagate uncertainties from $\bm K$ to $\bm D$ and therefore $\rho(\bm r)$, we first need the covariance matrix $\Sigma_K$ for $\bm K$.
+First, assume that the hybrid frame is offset from the local frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
+Then
+\begin{equation}
+  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{local}.
+  \label{eqn:local-to-hybrid}
+\end{equation}
+Since $K_{\ell m}^\mathrm{local}$ was obtained by an MCMC fit, a large set of posterior-distributed samples are available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{local}$, and the covariance matrix $\Sigma_K$ can be computed statistically by applying equation \ref{eqn:local-to-hybrid} to the samples.
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm D$ is $\Sigma_D = A \Sigma_K A^T$
+and the density distribution and uncertainty on density distribution are equal to
+\begin{equation}
+  \rho(\bm r) = \bm B(\bm r)^T A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
+  \label{eqn:unc-rho}
+\end{equation}
+
+The job of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
 
 \subsection{The Likelihood model}
+For the likelihood model, we restrict the degrees of freedom of $\rho(\bm r)$ by defining a likelihood function $\mathcal{L}$ on the density distribution, and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
+This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
+The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require an uncorrelated Gaussian likelihood.
+
+To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0$ plus some deviation $D_i$, where $\rho_0$ is constant across the asteroid.
+This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
+
+We use a likelihood of 
+\begin{equation}
+  \mathcal{L}(\bm D) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{D_i^2}{2 \sigma^2}}
+\end{equation}
+with free parameters $\mu$ and $\sigma$.
+These parameters do not affect the location of the maximum, so we do not define them.
+Given this likelihood, the log likelihood is proportional to $-|\bm D|^2$.
+Minimizing the norm of $\bm D$ is therefore equivalent to finding the maximum likelihood.
+
+Putting aside the problem of minimizing the norm for a moment, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm D$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:jlm} or \ref{eqn:am}, evaluated over the $i$th finite element.
+We want to solve $\bm K = M \bm D$ for $\bm D$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
+Since $m>n$, the Moore-Penrose inverse of $M$ is
+\begin{equation}
+  A=M^+ = M^*(MM^*)^{-1}
+  \label{eqn:mpi-underdetermined}
+\end{equation}
+where $M^*$ is the adjoint of $M$.
+The vector $\bm D=M^+\bm K$ is guaranteed to solve $\bm K = M \bm D$, and by the properties of the Moore-Penrose inverse, this $\bm D$ also happens to minimize the norm of all possible $\bm D$ that satisfy the equation.
+Thus, we define $A=M^+$, which fully defines the model.
+
+Note that this model is fast to compute; assuming fast matrix multiplication, the most time-consuming step is the matrix inversion of equation \ref{eqn:mpi-underdetermined}.
+But $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
 
 \subsection{The Harmonic model}
+We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
+The expansion of such a function in spherical coordinates is given by
+\begin{equation}
+  \rho(\bm r) = \sum_{\ell, m} \frac{D_{\ell m}}{a_m^\ell} R_{\ell m}^*(\bm r)
+  \label{eqn:harmonic-rho}
+\end{equation}
+where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $D_{\ell m}$ are free (complex) parameters.
+By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
+Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $D_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm D$.
+
+Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:klm} and \ref{eqn:am}, we get 
+\begin{equation}
+  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'} a_m^\ell} D_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
+  \label{eqn:harmonic-mat}
+\end{equation}
+This is an over-determined matrix equation $\bm K = M \bm D$, where $M$ is an $n \times m$ matrix.
+The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm D$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm D$ is minimized).
+However, the form of the inverse changes due to the equation being overdetermined:
+\begin{equation}
+  A=M^+ = (M^*M)^{-1} M^*
+  \label{eqn:mpi-overdetermined}
+\end{equation}
+
+In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
+\begin{equation}
+  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_m} \frac{R^{2\ell}}{a_m^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
+\end{equation}
+A nonspherical perturbation will introduce small off-diagonal entries to $M$.
+This diagonal represents an interpretation of the physical meaning of $K_{\ell m}$; they are directly related through this form of $M$ and the matrix equation $\bm K = M \bm D$ to the coefficients of the spherical harmonic expansion of the asteroid in the case of a spherical asteroid.
 
@@
 
+The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
+In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
+
+Suppose the asteroid contains $N$ `lumps' of constant mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid center of mass, and immersed in a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
+(For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.) Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the center of mass of the asteroid.
+The displacement of the shape centroid from the center of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
+The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3.
+The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
+These degrees of freedom should be compared to the known density moments, of which there is a square number $(L+1)^2$.
+However, three of these are the center of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass.
+One is then added, representing $a_m$.
+So the total number of known parameters is $(L+1)^2 - 3$, which is 13 when the second-order density moments are known.
+We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cc|ccc}
+    \hline \hline
+        &  & & $N$ &  \\
+        &  & 1  & 2  & 3  \\ \hline 
+        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{gray}\color{white} 7 & \cellcolor{gray}\color{white} 12\\
+    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 13 & 21 \\
+        & 3& \cellcolor{gray}\color{white}  7 &  17 &  27 \\
+    \hline \hline
+  \end{tabular}
+  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modeled, and $d$, the number of independent moment of inertia axes considered for each lump.
+The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are colored black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are colored gray.}
+  \label{tab:lump-dof}
+\end{table}
+
+The net $K_{\ell m}$ components of such an ensemble obey
+\begin{equation}
+  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_m^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
+  \label{eqn:klm-stack}
+\end{equation}
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:jlm} and $a_m$ in equation \ref{eqn:am} respectively.
+Crucially, note that we set normalizing factors $1/(\mu_m a_m^\ell)$ and $1/\mu_m$ in equations \ref{eqn:jlm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
+The zero-indexed parameters indicate the density moments of the asteroid medium surrounding the lumps.
+The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame.
+
+We can relate the primed moments to the moments calculated relative to each body's center of mass via the translation rules for solid spherical harmonics:
+\begin{equation}
+  \begin{split}
+  & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
+  & a_i'^2 = a_i^2 + x_i^2 K_{00}
+  \end{split}
+  \label{eqn:translate-klm}
+\end{equation}
+The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
+Here, $K_{00}^i$ is the added mass $\mu_i$ of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate its orientation and moment of inertia ratios.
+Its volume is constrained by $a_i^2$.
+These values map directly onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
+
+Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$.
+Therefore, if we define $\bm D$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm D$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm D$ is overdetermined).
+Henceforth, we assume that the dimensions of $\bm D$ are less than or equal to the number of known parameters (the shaded regions of table \ref{tab:lump-dof}), so that $A$ is given by equation \ref{eqn:mpi-overdetermined}).
+Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its center of mass.
+
+This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a nonlinear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
+The constraints on $\bm x_i$ and $\mu_i$ are primarily
+\begin{equation}
+  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
+  \label{eqn:lump-constraints}
+\end{equation}
+where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the center of mass.
+There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
+The overall mass of the asteroid is $\mu_m = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
+The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
+We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with solutions.
+This is done by minimizing
+\begin{equation}
+  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
+  \label{eqn:lump-minimize}
+\end{equation}
+Then $A=M^+$ and $\bm B(\bm r)$ following from the resulting values of $K_{\ell m}^i$ and $a_i^2$ defines the model.
+If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
+
 \subsection{Comparisons between density models.}
+\label{sec:density-compare}
 
@@
 
+\section{Computing asteroid shape from density moments}
+\label{app:find-surface}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-03-26 paper/main.tex
Prepared cadence measured vs speed

@@
 
-\cite{MOSKOVITZ2020113519}
+\jtd{Write}
 
@@
 
+\jtd{Write}
+
 \section{Conclusions}
 
+\jtd{Write}
 The last numbered section should briefly summarise what has been done, and describe
@@
 
+\jtd{Write}
 The Acknowledgements section is not numbered. Here you can thank helpful
@@
 
-The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS.
-Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article.
-The statement may refer to original data generated in the course of the study or to third-party data analysed in the article.
-The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.
+The code used to generate data, fit density moments to it, and extract density distributions from the moments is available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}, or by contacting JTD.
 
@@
 
+\jtd{Write}
+
 \section{What sets the cadence cutoff?}
@@
 
+\jtd{Write}
+
 \section{Comparison of Jupiter and Earth flyby}
@@
 
+\jtd{Write}
+
 \section{Similarity between cadence and lack of perigee data.}
 \label{app:cadence-perigee-test}
+
+\jtd{Write}
 

### 2022-03-26 data/scan-eq-spin/compile.py

@@ -20,8 +20,10 @@ N_PERCENTILES = None
 
 SCALE_Y = 1.1
 
+TYPE = 'off'
+
 # Get percentiles
-with open("percentiles.dat", 'r') as f:
+with open(f"percentiles{TYPE}.dat", 'r') as f:
     for line in f.readlines():
         if line == '': continue
         elements = line.split(':')
@@ -108,5 +110,5 @@ custom_lines = [Line2D([0], [0], color='k', lw=4, alpha=0.3),
                 Line2D([0], [0], color='k', lw=1, linestyle='dashed')]
 fig.legend(custom_lines, ['95\%', '68\%', '50\%'], ncol=3, loc='upper center', prop={'size': LEGEND_SIZE}, bbox_to_anchor=(0.5,0.91))
 
-plt.savefig("eq-spins.pdf", bbox_inches="tight")
-plt.savefig("eq-spins.png", bbox_inches="tight")
+plt.savefig(f"eq-spins{TYPE}.pdf", bbox_inches="tight")
+plt.savefig(f"eq-spins{TYPE}.png", bbox_inches="tight")

### 2022-03-27 paper/main.tex
Updated density comparisons

@@
 
-\jtd{Write}
+To test the properties of the three density models defined above, we simulate several asteroids with different shapes and density distributions on a close Earth encounter, with the reference asteroid orbital and observational parameters.
+Density moments are extracted via our fit process and density distributions by the three methods.
+Below, we compare them.
+
+\subsubsection{Uniform density test asteroids}
+
+First, we simulate several asteroids with uniform density distributions and ask whether a distribution is recovered.
+The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the center of the other), and a tetrahedron.
+The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
+Also in each figure is $\Delta K_{\ell m}$, the magnitude of difference between the fitted density moments and the density moments of the final distribution.
+This difference is nonzero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed to exactly reproduce the input density moments), they express the inability of the density model to exactly reproduce the density moments.
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/sym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/db-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/db-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/db-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/tet-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/tet-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/tet-lumpy.pdf}
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
+The asteroid shapes are, from top to bottom, the reference asymmetric ellipsoid, the reference symmetric asteroid, the dumbbell model, and a tetrahedron.
+Density is normalized so that mean density is one.
+The same distance scale is used in all figures.}
+  \label{fig:uniform-density}
+\end{figure*}
+
+From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions.
+This is generally true for uniform density asteroids.
+This is a useful property because it lends confidence that the models produced are truly representative of the asteorid.
+The fact that the harmonic model produces very little density moment error ($\Delta K_{\ell m}$) also lends confidence to the distribution; the harmonic model is overdetermined and is not guaranteed to perfectly match the fit-extracted moments.
+
+The asymmetric and dumbbell asteroids produce distributions whose non-uniformity is limited to a factor of 2 or less for the harmonic and likelihood models.
+This non-uniformity is driven by error in the estimates of the density moments.
+Note that most of the asteroid does indeed have density close to one in both cases.
+The lumpy model yields a much more uniform distribution, but only because it is designed to produce uniform lumps.
+Note that its uncertainty $\Delta K_{\ell m}$ is usually large, both because the model is severely overdetermined (it has 2 degrees of freedom) and because the lump found extends outside the asteroid, violating the assumptions of the model.
+This is a sign that the lump found does not really exist inside the asteroid.
+
+The symmetric and tetrahedral asteroids are less-well represented.
+In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
+This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy and inflated uncertainty in the model.
+Estimates of $K_{\ell m}$ are therefore incorrect.
+In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the ill-constrained $K_{3m}$ components.
+
+Uncertainty in each distribution was calculated but not shown.
+The size of uncertainty is such that the density distribution is consistent with uniform at all points (within 1-2$\sigma$), except for the tetrahedron model, which contains a small number of points with very small uncertainty that exclude uniform density to $5\sigma$.
+In general, uncertainty is greater towards the edge of the asteroid.
+\jtd{Why do these low-uncertainty points exist in tet?}
+
+From these examples, we may draw the conclusions that all three models produce density distributions consistent with uniform for uniform asteroids.
+The most likely distributions are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
+Asymmetric asteroids such as the dumbbell and the asymmetric reference asteroids yield the best results because they have $K_{22} \neq 0$ and therefore do not suffer from degeneracy in initial orientation.
+Finally, the lumpy model can generally be ruled out in these cases because it produces nonphysical results.
+
+\subsubsection{Spherical shape test}
+We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and attempting to extract density distributions assuming a spherical shape.
+We do this for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.33\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-sph-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/sym-sph-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/sym-sph-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/sym-sph-lumpy.pdf}\
+
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
+The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids.
+In both cases, the density distributions have been extracted assuming a spherical shape.
+Density is normalized so that mean density is one.
+The same distance scale is used in all figures.}
+  \label{fig:sphere-density}
+\end{figure*}
+
+Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
+Before, we took this fact as a signal that the distributions are likely to be correct.
+However, now they both produce negative density distributions for both asteroid shapes.
+This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
+In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (up in the figure).
+The density is large at large $|y|$ (front right in the figure).
+Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
+In other words, the shape can be corrected by extending it where density is large and retracting it where density is low.
+
+A similar statement is true for the symmetric ellipsoid case in that density is low near the poles, but this time the regions with large density are evenly distributed around the equator, indicating the symmetry of the original asteroid.
+
+The lumpy model produces zero-mass lumps in this case, and produces very small $\Delta K_{\ell m}$. \jtd{What are the exact parameters of the lump? Look at log files}.
+
+In short, severely incorrect shape estimates can be caught for all three models by negative predicted densities or by the failure of the density distribution model to match the extracted density moments.
+The shape can be corrected by extending it where the density distribution is high and retracting it where the density distribution is low.
+
+\subsubsection{Nonuniformity test}
+
+We also test several non-uniform density asteroids and compare the generated density distributions for all three models to see if the non-uniformities are recovered.
+We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated symmetrically around the edges.
+(Specifically, the mass distribution follows a Gaussian which falls to a fraction $e^{\pm 0.5}$ of the central density on the surface of the asteroid.) To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
+The extracted density distributions are shown in figure \ref{fig:non-uniform-density}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.33\textwidth]{figs/in-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/in-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/in-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/out-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/out-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/out-lumpy.pdf}\
+
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).Density is normalized so that mean density is one.
+The same distance scale is used in all figures.}
+  \label{fig:non-uniform-density}
+\end{figure*}
+
+For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
+However, the two models do give similar results.
+Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case does indeed place more mass in the center of the asteroid shape for the harmonic and likelihood models.
+The edge-weighted asteroid does not have as clear high-density at its surface, due to the fact that uncertainty is generally greater near the edges (where $R_{\ell m}$ is large).
+
+\jtd{Why do the densities go negative?}
+
+\jtd{What's wrong with the lumpy model? Wasn't it giving really good results before?}
+
+\subsubsection{Lump test}
+
+Finally, we test an asteroid with a discrete change in density distribution (for example, a boulder), of the kind that the lumpy model is designed to detect.
+We place a spherical mass of density six times the density of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
+The rest of the asteroid we set to uniform density.
+The density distributions found by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}
+
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-center lump.
+Density is normalized so that mean density is one.
+The same distance scale is used in all figures.}
+  \label{fig:blob-density}
+\end{figure*}
+
+We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail completely to recover the presence or location of the lump.
+There appears to be a slight increase of density in roughly the correct location for both models, but this is not a statistically significant effect, and can be seen in other asteroid such as the center-weighted asteroid of figure \ref{fig:non-uniform-density}.
+Also like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
+
+The failure of these models to find lumps is expected, since $K_{\ell m}$ is most sensitive to non-uniformities of characteristic size $\pi/(\ell + 1)$ radians in the polar direction, and $2\pi / (|m|+1)$ in the azimuthal direction by the definition of $Y_{\ell m}$.
+This lump is too small to be resolvable by $K_{3m}$, so we do not expect most models to find it.
+
+However, the lumpy model exactly computes the location and density of the mass.
+\jtd{But it's not quite exact.
+Why?}.
+\jtd{Would like to say that there's no error in klm.} We see therefore that the lumpy model is capable of recreating the location of lumps accurately (in simple cases such as this).
+But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analyzed here.
 
@@
 
-\jtd{Write}
-
 \section{What sets the cadence cutoff?}

### 2022-03-27 paper/main.tex
Wote two appendices and the acknowledgments

@@
 \subsubsection{Nonuniformity test}
+\label{sec:non-uniform-density}
 
@@
 
-\jtd{Write}
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin \jtd{What's Marin's last name?} for meeting with the authors to discuss this work, and pointing out possible future directions to take it.
+JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
+The work of JdW was funded by \textit{Who funds Julien?}.
+Much of the computation shown in this paper was executed on MIT Supercloud's facilities.
 
@@
 
+Except when otherwise mentioned, we use the following asteroid encounter parameters.
+Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our uncertainties have room to grow; if the reference asteroid has low uncertainty,
+
+\begin{enumerate}
+  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii. This orbit was chosen to roughly match that of \jtd{Number} Apophi s\jtd{Cite Apophis close approach}
+  \item An initial roll of $\gamma_0=\pi/8$.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho / \sigma_\theta = 10^{-5}$.
+  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
+  \item An asteroid with radius $a_m = 1$ km and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values.
+One with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
+The second case and its reflection are called the asymmetric cases.
+Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
+If not specified, we use the $a < b$ case.
+Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
+\end{enumerate}
+
+We use the asymmetric ellipsoid in nearly all runs, do to the degeneracy induced in our model when $K_{22} = 0$.
+
 \section{What sets the cadence cutoff?}
@@
 \label{app:find-surface}
+
+In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_m$ if a uniform density distribution is assumed.
+We do not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is nonlinear.
+However, it may be a useful technique so it is mentioned here.
+A similar model was also studied in \jtd{Cite that paper}.
+
+Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m^2$, and that the asteroid is ``star shaped'' in that every ray passing through the center of mass of the asteroid (the origin of the local frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
+By the divergence theorem, we write
+\begin{equation}
+  K_{\ell m} = \frac{\rho_0}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
+\end{equation}
+where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $ so that $\nabla \cdot \bm v(\bm r) = R_{\ell m}(\bm r)$.
+The integral is carried out over the surface of the asteorid.
+We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \propto \unit r$, this gives
+\begin{equation}
+  K_{\ell m} = \frac{\rho_0 }{\mu_m a_m^\ell (3 + \ell)} \int d\Omega r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
+  \label{eqn:surface-klm}
+\end{equation}
+where the integral is carried out over the unit sphere. Note that the integrand of each $K_{\ell m}$ is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
+
+We write 
+\begin{equation}
+  r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}
+\end{equation}
+without loss of generality.
+To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m (\ell-m)!/(\ell+m) C_{l,-m}$.
+With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
+These integrals can be pre-computed so that equation \ref{eqn:surface-klm} can then be numerically solved via standard polynomial solution methods to find $C_{\ell m}$.
+A similar equation to equation \ref{eqn:surface-klm} can be written for $a_m$
+\begin{equation}
+  a_m^2 = \frac{\rho_0}{5\mu_m}\int d\Omega r(\theta, \phi)^5
+  \label{eqn:surface-am}
+\end{equation}
+which can also be solved via polynomial methods.
+
+Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form a set of $n+1$ constraints, where $n$ is the number of density moments known.
+I.e., $n=(\ell_\text{max}+1)^2$, where $\ell_\text{max}$ is the maximum degree of $K_{\ell m}$ known.
+By setting the same maximum degree on $C_\ell m$, we also have $n$ variables plus one for $\rho_0$.
+The system is therefore well-determined and will yield finitely many solutions.
+These solutions can be further refined by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
+The result shapes consistent with the fitted $K_{\ell m}$.
+We do not attempt to model uncertainty on the shape.
+
+To test the model, this process was run for an asteroid with $K_{1m}=K_{2m'}=0$, but randomly chosen $K_{3m}$.
+The resulting surface is shown in figure \ref{fig:surface-density}.
+The figure shows a near-spherical asteroid, which is expected for $K_{\ell m} = 0$ for $\ell > 0$.
+However, the additional $K_{3m}$ components clearly induce non-sphericity in the asteroid which is captured by the surface model.
+
+\begin{figure*}
+  \centering
+  \hfill
+  \includegraphics[width=0.4\textwidth]{figs/high-surface.pdf}\hfill
+  \includegraphics[width=0.4\textwidth]{figs/high-likelihood.pdf}\hfill
+  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface method.
+\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
+The same length scale is used in both figures.}
+  \label{fig:surface-density}
+\end{figure*}
+
+To give an alternate view of the non-sphericities found via this new surface model, figure \ref{fig:surface-density} also displays the density distribution extracted via the likelihood model assuming a spherical asteroid shape, but with the same density moments.
+(Uncertainty in the moments is not modeled in this figure, to better compare the two.) Where the likelihood model displays low density, the surface model clearly retreats into the asteroid.
+Where the likelihood model yields high density, the surface model extends.
+Thus, the connection made in section \ref{sec:non-uniform-density} between non-uniformities in the densities of the likelihood and harmonic models at the asteroid surface and inaccuracies in the surface is more firmly represented.
+
+This surface model could, in principle, be used to improve estimates of the surface of an asteroid made by light curve analysis, since it connects rotational data to the asteroid surface.
+Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
+We only suggest this as a possibility, however, since it is beyond the scope of this paper.
+
+\section{Example fit results}
+\label{app:example}
+
+Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to flyby data of the asymmetric reference asteroid.
+The fit results were consistent with the true density moments, and produced consistent data.
+
+Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid and the residuals in the bottom pane.
+Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix --- i.e., 1-$\sigma$ uncertainties (correlations are not included).
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
+  \label{fig:example-residuals}
+\end{figure*}
+
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, both marginalized to be a function of one variable and of two.
+The true parameters are shown as lines.
+Note that the true parameters always lie within 1- or 2-$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
+Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
+Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
+True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
+  \label{fig:example-corner}
+\end{figure*}
+
+\jtd{Pull the correct plots from supercloud.}
 

### 2022-03-28 paper/main.tex
Pulled cad period and started cad speed
Made cadence period figures

@@
 However, it may be a useful technique so it is mentioned here.
-A similar model was also studied in \jtd{Cite that paper}.
+A similar model was also studied in Ref.~\cite{BAXANSKY2007756}.
 
@@
   \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
 The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
@@
 
-\jtd{Pull the correct plots from supercloud.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-03-28 paper/main.tex
Staged new density moments

@@
 Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m} = 0$ is not contained in the 2-$\sigma$ band.
+The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m}| = 0$ is not contained in the 2-$\sigma$ band.
 This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
@@
 The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
-Also in each figure is $\Delta K_{\ell m}$, the magnitude of difference between the fitted density moments and the density moments of the final distribution.
+Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
 This difference is nonzero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed to exactly reproduce the input density moments), they express the inability of the density model to exactly reproduce the density moments.
@@
 
-The lumpy model produces zero-mass lumps in this case, and produces very small $\Delta K_{\ell m}$. \jtd{What are the exact parameters of the lump? Look at log files}.
+The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$..
+The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|$ for the original asteroids.
 
@@
 We also test several non-uniform density asteroids and compare the generated density distributions for all three models to see if the non-uniformities are recovered.
-We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated symmetrically around the edges.
-(Specifically, the mass distribution follows a Gaussian which falls to a fraction $e^{\pm 0.5}$ of the central density on the surface of the asteroid.) To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
+We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated around the edges.
+(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_m^2}$).
+To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
 The extracted density distributions are shown in figure \ref{fig:non-uniform-density}
@@
 
-\jtd{Why do the densities go negative?}
-
-\jtd{What's wrong with the lumpy model? Wasn't it giving really good results before?}
+\jtd{Rewrite after new model comes through}
+
+The lumpy model has one caveat that has not yet been illustrated, which applies for $N=d=1$ if (1) the center of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape assuming uniform density are proportional to the fitted density moments.
+(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
+The lump radius will then be set to zero because the fitted density moments are already matched.
+This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
+
+An example of this caveat applied is an elliptical lump inside a similar elliptical asteroid.
+This is why, in the center-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an ellipsoidal distribution.
+Thus, the caveat is avoided.
 
@@
 Why?}.
-\jtd{Would like to say that there's no error in klm.} We see therefore that the lumpy model is capable of recreating the location of lumps accurately (in simple cases such as this).
+\jtd{Would like to say that there's no error in klm.} We see therefore that the lumpy model is capable of recreating the location of lumps accurately (except for the caveat mentioned in the previous section).
 But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analyzed here.
@@
 JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
-The work of JdW was funded by \textit{Who funds Julien?}.
+The work of JdW was funded by \jtd{Who funds Julien?}.
 Much of the computation shown in this paper was executed on MIT Supercloud's facilities.
@@
 \begin{enumerate}
-  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii. This orbit was chosen to roughly match that of \jtd{Number} Apophi s\jtd{Cite Apophis close approach}
+  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii. This orbit was chosen to roughly match that of 99942 Apophis \jtd{Cite Apophis close approach}
   \item An initial roll of $\gamma_0=\pi/8$.

### 2022-03-29 paper/main.tex
Ready to rerun blob

@@
   \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
-The vertical dashed line indicates the reference asteroid value.}
+The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.}
   \label{fig:scan-vex}
@@
   \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
-The vertical dashed line indicates the reference asteroid value.
+The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
 The dotted curve indicates a power-law fit (see text).}
@@
   \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
-The vertical dashed line indicates the reference asteroid value.}
+The vertical dashed line indicates the reference asteroid value of $10^{-7}$.}
   \label{fig:scan-product}

### 2022-03-29 paper/main.tex
Ready to run blob

@@
 However, the two models do give similar results.
-Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case does indeed place more mass in the center of the asteroid shape for the harmonic and likelihood models.
-The edge-weighted asteroid does not have as clear high-density at its surface, due to the fact that uncertainty is generally greater near the edges (where $R_{\ell m}$ is large).
-
-\jtd{Rewrite after new model comes through}
+Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case indeed places more mass in the center of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.
+
+Though the general mass placement arrived at by both the likelihood and harmonic models is accurate, the precise density distributions are inaccurate because they predict negative densities.
+This might be addressed for the likelihood model by selecting a likelihood that strongly disfavors negative densities, such as a log-normal distribution.
+However, this would sacrifice the linearity of the model, so we do not do so here, accepting the fact that for strongly varying distributions, the harmonic and likelihood models may predict negative density distributions.
+
+Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the center-weighted asteroid and less density for the edge-weighted asteroid, as expected.
+Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
+Note that the lumpy model predicts negative density in the the edge-weighted scenario like the other two models.
 

### 2022-03-29 code/density/run.py

@@ -91,9 +91,9 @@ elif len(sys.argv) == 3:
     print("Getting densities")
     method.map_density()
     method.save_density()
-    #print("Getting uncertainties")
-    #method.map_unc()
-    #method.save_unc()
+    print("Getting uncertainties")
+    method.map_unc()
+    method.save_unc()
     method.check()
 
     method.display()

### 2022-03-29 code/density/submit.py

@@ -1,15 +1,15 @@
 import sys, os
 
 names = [
-    "sym-sph", 
-    "asym-sph", 
-    "sym-ell", 
-    "asym-ell", 
-    "tet", 
-    "db", 
-    "high", 
-    "in", 
-    "out", 
+    #"sym-sph", 
+    #"asym-sph", 
+    #"sym-ell", 
+    #"asym-ell", 
+    #"tet", 
+    #"db", 
+    #"high", 
+    #"in", 
+    #"out", 
     "blob"
 ]
 

### 2022-03-31 paper/main.tex
changed uncertainty model
Analyzed initial spin direction

@@
 
-\subsection{Equations of motion}
-\label{sec:eom}
+\subsection{Tidal torque}
+\label{sec:tidal-torque}
 
@@
 
-Further insight can be gained by asking when $\bm \tau = 0$.
-This occurs to first order when (1) $\alpha=\phi$ (or  $\alpha=\phi+\pi$) and $\beta =\pi/2$, and (2) when $\alpha=\phi\pm\pi/2$ and $\gamma$ is an integer multiple of $\pi/2$.
-Here, $\phi$ is the angle between perigee and $\bm D$.
-At perigee ($\phi=0$), these correspond to (1) $\unit z \parallel \unit X$ and (2) $\unit z$ is in the $\unit{Y}\unit{Z}$-plane with an additional condition on $\gamma$.
-
-Also important is when $\bm \tau \parallel \unit z$; this case has special meaning because for a non-tumbling asteroid, $\omega \parallel \unit z$, and $\tau \parallel \unit z$ ensures that the asteroid will continue not to tumble.
+Further insight can be gained by remarking the value of the first order of $\bm \tau$ for particular Euler angle cases.
 Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first order.
-Setting $\alpha = \phi \pm \pi/2$ also forces $\bm \tau \parallel \unit z$ to first order.
+Further, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$.
+
+For $\beta = \pi/2$, there are two interesting cases.
+One is for $\alpha = \phi$ or $\alpha = \pi + \phi$, where $\phi$ is the angle between the asteroid and the perigee.
+In this case, $\tau = 0$ to first order.
+The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$ and $\tau_z$ oscillates.
+At perigee ($\phi=0$), these conditions are equivalent to $\unit z \parallel \unit X$ and $\unit z \parallel \unit Y$ respectively.
+
+The $\bm \tau \parallel \unit z$ cases are interesting because they do not induce tumbling.
+If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
+These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$, and in general we see that $|\tau_z|$ is the smallest of the torque components.
+
+\subsection{Equations of motion}
+\label{sec:eom}
 
@@
 
-Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_m/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:eom}.
+Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_m/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
 For $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution, with uncertainty ranging from -1 to 1.
@@
 The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \omega_0$ both because spin sets the initial asteroid orientation (up to $\gamma_0$) and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-As an example, in section \ref{sec:eom}, we noted that $\bm \omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.
+As an example, in section \ref{sec:tidal-torque}, we noted that $\bm \omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.
 
@@
   \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
-  \caption{$1-\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin.
+  \caption{$1-\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
 All maps are made in the Mollweide projection and shown in the inertial $\unit X-\unit Y-\unit Z$ frame.
@@
 
-Figure \ref{fig:scan-spin-avg} confirms our expectation that the fit parameters would be uncertain near $\bm \omega \propto \unit Z$, where $\bm \tau \parallel \unit z$.
-The $\unit z \parallel \unit X$ zero-torque setting doesn't appear in the figure however, likely because torque is large enough at $\phi \neq 0$ that the fact that $\unit z \parallel \unit X$ provides $\bm \tau = 0$ at $\phi = 0$ is not enough.
-
-The other predicted $\bm \omega_0$ resulting in lack of precision were for $\alpha = \phi \pm \pi/2$, which causes $\bm \tau \propto \unit z$ and $\bm \tau = 0$ when $\gamma$ is an integer multiple of $\pi/2$.
-There does appear to be an associated lack of precision at $\bm \omega_0 \propto \unit Y$ (the $\phi=0$ case) \jtd{Why?}
-
-\jtd{To figure this out, I'm running some searches for spins along the equator. Hope to see the same peak at Y, and I'll see if it goes away for an iteration when gamma zero changes.}
-
-\jtd{Tomorrow, I plan to do the rest of this paper and skip this section. If I can't figure it out, I'll remove it.}
-
-\jtd{Remember to include the changes when a fast rotator comes in.}
+The characteristics of tidal torque discussed in section \ref{sec:tidal-torque} indicate that certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque: $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first order.
+We relate this to the initial direction of $\bm \omega_0$, via the crude assumption that $\bm \tau$ is small until perigee.
+Then, since $\bm \omega_0 \parallel \unit z$ by assumption that the asteroid is not tumbling, we have that $\bm \omega_0 \parallel \unit Y$ and $\bm \omega_0 \parallel \unit Z$ lead to $\bm \tau \parallel \unit z$, and $\bm \omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
+
+Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \omega_0 \parallel \unit Z$ and $\bm \omega_0 \parallel \unit Y$, but not the $\unit X$ case.
+This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
+Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the flyby.
+Also, $\tau_z$ is small and affected by fewer parameters than $\tau_x$ or $\tau_y$.
+Both of these are reasons why $\bm \tau \parallel z$ might inhibit precise fits to spin data.
+If $\bm \tau = 0$ to first order, then second-order $\tau$ and non-perigee $\bm \tau$ will dominate, and these may indeed induce precession.
+
+It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \omega_0 \parallel \unit Z$ and $\bm \omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
+Within the imprecise regions, uncertainty can grow up to four times the uncertainty at other $\bm \omega_0$ values, and possibly higher.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in figure \ref{fig:scan-spin-avg}
 
@@
 \begin{enumerate}
-  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii. This orbit was chosen to roughly match that of 99942 Apophis \jtd{Cite Apophis close approach}
+  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
+This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, smalley20052004}.
   \item An initial roll of $\gamma_0=\pi/8$.

### 2022-04-01 paper/main.tex
Added intro draft

@@
 
-\jtd{Write}
-
-In this paper, \jtd{Etc.} Section \ref{sec:methods} describes the coordinates and parameters we use to model the encounter and gives the equation of motion and simulation design used to generate synthetic encounter data.
-Section \ref{sec:fit} describes how density moments are re-extracted from synthetic data and the sensitivity of the precision of re-extracted moments on various system parameters.
-Section \ref{sec:results} describes how our posterior uncertainties on density moments depend on various physical parameters of the system.
-Finally, we provide several models to extract density distributions from the density moments in section \ref{sec:distros} and compare their accuracy and precision.
+The recent increase in the quantity and quality of high-sensitivity, all-sky surveys, such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide} has prompted the discovery of numerous asteroids, some kilometer-sized, and some predicted to encounter Earth or other planets closely in the near future.
+Theoretical work has demonstrated that many of these asteroids incur altered rotational velocities due to tidal torque \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}; this two-body generalized system has been studied to several orders and with several different methods.
+The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}.
+Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
+Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281}.
+Altered rotational states have been excluded for 1I/2017 U1 'Oumuamua \cite{KWIECINSKI2018170}.
+
+Such asteroid encounters have further been shown to reveal the physical properties of the encountering asteroid.
+Refs.~\cite{MOSKOVITZ2020113519, benson2020spin} extract best-fit dimensions for a triaxial ellipsoid model of Duende from light-curve data, and Refs.~\cite{DESCAMPS2020113726} and \cite{BERTHIER2020113990} extract bulk densities and rotational periods for asteroid binaries (3905) Doppler and (617) Patroclus respectively.
+
+More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the James Webb Space Telescope (JWST) or Large-aperture Synoptic Survey Telescope (LSST), and general methods for assessing whether an asteroid's encounter properties are conducive to the extraction physical asteroid characteristics from light-curve data is necessary.
+However, such general statements are not very well studied, since much of previous research has focused on specific encounters.
+
+Additionally, asteroid properties which are constrained only by beyond-leading-order tidal torque effects have not yet been extracted, and more research is needed to study whether these effects are, in fact, observable.
+
+In this paper, we address these two topics by deriving a new equation of motion for an asteroid encounter system in section \ref{sec:methods}.
+This equation is simple and exact to arbitrary order, given assumptions reasonable for a planetary encounter (and many binary systems).
+It is also fast in that it allows volume integrals over the asteroid to be pre-computed.
+We use this equation of motion to simulate a generic asteroid flyby of Earth, and extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit, described in section \ref{sec:fit}.
+We measure the uncertainties in the posterior distribution of density moments as a function of various encounter parameters such as the observational uncertainty, cadence of observation, encounter orbital parameters, and more.
+We express which parameters most affect the precision of fit results in section \ref{sec:results}.
+Finally, we propose methods to extract full density distributions with uncertainties from these density moments in section \ref{sec:distros}.
 
@@
 \begin{equation}
-  K_{\ell m} \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
+  K_{\ell m} - \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
   \label{eqn:klm}
 \end{equation}
-Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_m$ is the mass of the asteroid, $\rho_m(\bm r)$ is the density distribution, and $a_m$ is a length scale defined (for reasons covered later) as
+Note that these are complex.
+Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_m$ is the mass of the asteroid, $\rho_m(\bm r)$ is the density distribution, and $a_m$ is a real length scale defined (for reasons covered later) as
 \begin{equation}
@@
 \end{equation}
-This length scale can be thought of as akin to the radius of the asteroid (although a spherical asteroid has radius $\sqrt{5/3} a_m$).
-Both of these equations should be computed in the body-fixed axes. These equations can be extended to the central body:
+This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $\sqrt{5/3} a_m$).
+Both of these equations should be computed in the body-fixed axes.
+
+Equations \ref{eqn:klm} and \ref{eqn:am} can be extended to the central body:
 \begin{equation}
@@
 which should be computed in the inertial axes.
+
 Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless.
@@
 Firstly, for real mass density, properties of the spherical harmonics imply that $K_{\ell m} = (-1)^m K_{\ell, -m}^*$.
-Therefore, the set of $K_{\ell m}$ for $\ell < L$ provides $L^2$ degrees of freedom.
-However, some of these degrees of freedom should be removed as discussed below.
+Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ provides $\ell_\text{max}^2$ degrees of freedom.
+However, some of these degrees of freedom are additionally constrained as discussed below.
 
@@
 $\Re K_{32}$, $K_{31}$, and $K_{30}$ are the only $K_{3m}$ components zeroed by only one axis.
-We will see later that \jtd{see what?}.
+This will not affect our fit results for $K_{3m}$, but when we extract density distributions from $K_{3m}$, we will see that our sample shapes have most $K_{3m}=0$.
+
 \begin{table}
@@
 \end{equation}
-In practice, we also observe that $|K_{3m}| < 1$; typically, $|K_{3m}| < 0.1$ even.
+In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
 
@@
 Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+
 We present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
+These density moments can be pre-computed and do not have to be re-evaluated every time step.
 This formulation of the problem will be more useful for this study.
@@
 
-Below follows a derivation of the tidal torque experienced by an asteroid, followed by the system equations of motion.
-
 The gravitational potential energy of the central body is, in its most general form,
@@
 To do this, we let $\bm{R'} = \bm D + \bm U$, where $\bm D$ is the location of the asteroid in the inertial frame.
-We further define $\bm U = M\bm u$, where $\bm u$ is in the body-fixed frame and $M$ is a rotation matrix given by the Euler angles $\alpha$, $\beta$, and $\gamma$ (see section \ref{sec:coordinates}).
+We further define $\bm U = M\bm u$, where $\bm u$ is in the body-fixed frame and $M$ is the rotation matrix given by the Euler angles $\alpha$, $\beta$, and $\gamma$ (see section \ref{sec:coordinates}).
 The translation from $\bm {R'}$ to $\bm U$ is then attained by the identity
@@
 Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(D/a_M)^\ell (D/a_m)^{\ell'}$, the latter of which especially is a small number in most cases.
-Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$.
-For our analysis, we remove $\ell > 3$.
+Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
+For our analysis, we remove $\ell' > 3$ and we usually keep only $\ell=0$.
 
@@
 
+Note that equation \ref{eqn:omega-eom} is independent of $a_m$ to first order in $\bm \tau$, because $I_{j} \propto a_m^2$ for all $j$ and $\bm \tau \propto a_m^2$.
+Therefore, scaling $a_m$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
+
 \subsection{Simulation design}
@@
 We built a simulation to produce angular velocity data (in the inertial frame) as a function of time.
-This simulation requires as input (1) the orbital parameters of the asteroid; (2) the cadence of angular velocity observation; (3) the central body moments, mass, and $a_m$; (4) the initial asteroid angular velocity in the inertial frame; (5) the asteroid radius $a_m$, and (6) the asteroid's density moments and initial Euler angle $\gamma_0$.
+This simulation requires as input (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_M$, and $a_m$; (4) the initial asteroid angular velocity in the inertial frame $\bm \omega_0$; (5) the asteroid radius $a_m$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
@@
 This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Thus, only one Euler angle $\gamma = 0$ is necessary to provide initial data for the simulation.
-
-We begin our simulation at $D = 10 r_p$.
+Thus, only Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
+
+We begin our simulation at $D = 10 r_p$, with velocity predicted by Kepler's laws given by the orbital parameters.
 Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
@@
 \begin{equation}
-  \Delta t = \Delta t_\text{min} + 10^{-3}(\Delta t_\text{max} - \Delta t_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
-\end{equation}
-The parameters $\Delta t_\text{max}$ and $\Delta t_\text{min}$ (20 and 10 seconds respectively) were chosen such that the finite-integration error \jtd{Is this the correct name?} was ~100 times the numerical error, and that neighboring values of $K_{\ell m}$ yielded significantly different spin pole data.
+  dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
+\end{equation}
+The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was ~100 times the floating point error, and that neighboring values of $K_{\ell m}$ yielded significantly different spin pole data.
 
@@
 \label{sec:fit}
-Given synthetic data, a Markov Chain Monte Carlo (MCMC) \jtd{find the Ensemble full name and cite} method was used to generate posterior distributions based on flat priors.
+Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate posterior distributions based on flat priors.
+We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
 \jtd{How detailed about the MCMC do I need to be?} Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{\ell m}$ given in section \ref{sec:moments}.
 Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to relabeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
-
-Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \jtd{Cite?}.
+The other bounds were $|K_{3m}| < 1$.
+
+Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
 It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
@@
 Near $r_p \approx 40$ Earth radii, the $K_{32}$ and $K_{31}$ components also fill the prior.
-However, the width of the prior was arbitrarily chosen, and all the physical density distributions have $|K_{3m}| < 0.1$ \jtd{Check}, so the actual Earth radii cutoff at which the $K_{3m}$ parameter estimates become too imprecise to be usable likely occurs at lower $r_p$.
-The exact value depends on the shape of the asteroid, but \jtd{When is it 0.1?}
+However, the width of the prior was arbitrarily chosen, and all the physical density distributions have $|K_{3m}|$ smaller, so the actual Earth radii cutoff at which the $K_{3m}$ parameter estimates become too imprecise to be usable likely occurs at lower $r_p$.
+The exact value depends on the shape of the asteroid, but \jtd{When is it 0.01?}
 

### 2022-04-01 paper/main.tex
Updated density to make it faster

@@
 Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
-Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281}.
+Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
 Altered rotational states have been excluded for 1I/2017 U1 'Oumuamua \cite{KWIECINSKI2018170}.

### 2022-04-02 paper/main.tex
Updated paper

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[Jack T. Dinsmore]{
+\author[Jack T. Dinsmore, Julien de Wit]{
 Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
@@
 
+In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim 30-40$ min.
+We mentioned that this cadence cutoff is likely a function both of the period of the asteroid and the time spent near perigee.
+We study this cutoff in closer detal in this appendix.
+
 \jtd{Write}
+
+\ref{fig:cad-period} 
+\ref{fig:cad-speed}
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
+  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid colored lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
+Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
+  \label{fig:cad-period}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
+  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t/t_0$ for no scaling (the reference asteroid, solid colored lines), time doubling (dotted lines), and halving (dashed lines).
+See text for the definition of $t/t_0$.
+Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
+  \label{fig:cad-speed}
+\end{figure}
 

### 2022-04-02 paper/main.tex
Added cadence section

--- 2022-04-01 paper/main.tex
@@
 This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, smalley20052004}.
+These orbital parameters correspond to an eccentricity of 3.88.
   \item An initial roll of $\gamma_0=\pi/8$.
@@
 
-\section{What sets the cadence cutoff?}
+\section{The cadence cutoff}
 \label{app:cadence-tests}
 
-\jtd{Write}
+In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
+We mentioned that this cadence cutoff is likely a function both of the rotational period of the asteroid and the time spent near perigee.
+We study this cutoff in closer detal in this appendix.
+
+We measure the dependence of the cadence cutoff on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
+Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference 9 hr.
+The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ and therefore irrelevant here (i.e., those studied in section \ref{sec:scan-period}), are removed.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
+  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid colored lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
+Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
+  \label{fig:cad-period}
+\end{figure}
+
+We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
+Instead, we adjust the speed at which the asteroid moves through the orbit.
+In one instance, the asteroid's path is artificially slowed by a factor of 2, which we denote as $t_\text{spin}/t_\text{orbit}=0.5$; in the other instance, $t_\text{spin}/t_\text{orbit}=2$, meaning that the orbit is sped up.
+This approach of changing the speed of the orbit is meant to approximate changes to $T_p$ defined in equation \ref{eqn:tp}.
+The posterior uncertainties for these two cases and the original case are shown in figure \ref{fig:cad-speed}.
+Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
+However, the $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
+  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid colored lines), time doubling (dotted lines), and halving (dashed lines).
+See text for the definition of $t_\text{spin}/t_\text{orbit}$.
+Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
+  \label{fig:cad-speed}
+\end{figure}
+
+Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cutoff at $T_\text{cad} \sim 30-60$ min.
+Those that show no cutoff (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cutoff $T_\text{cad} > 60$ min, which is off the plot.
+By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dotted lines often (but not always) reach the cadence cutoff before the solid line.
+For example, in figure \ref{fig:cad-period}, this effect is especially clear for $K_{22}$, $K_{33}$, $\Im K_{22}$, and $\Re K_{31}$, but the opposite appears for $\Re K_{32}$.
+The dotted curves are significant in both figures because they represent smaller $\sigma$ cases.
+Section \ref{sec:scan-period} reveals that long-rotational-period asteroids lead to smaller $\sigma$, and $t_\text{spin}/t_\text{orbit} < 1$ leads to smaller $\sigma$ because of the presence of more perigee data.
+It therefore appears that large $P_\omega$ and large times spent at perigee move the cadence cutoff to larger $\Delta t$.
+
+The dependence of the exact location of the cadence cutoff is likely more complicated than the above analysis indicates.
+However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-speed} was) to study these regimes.
+Computation time and random variation in $\sigma$ also limits us.
+We therefore do not attempt to explore the dependence between $T_\text{cad}$ and the encounter parameters further.
+If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence}.
 
@@
 
-\jtd{Write}
-
-\section{Similarity between cadence and lack of perigee data.}
-\label{app:cadence-perigee-test}
+Note: $v_\infty^2 = \sqrt{\mu/r_p (e-1)}$.
 

### 2022-04-03 paper/main.tex
Updated paper

@@
 In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
+For the rest of this paper, we therefore treat $|K_{3m}| \sim 0.01$ as a practical limit on observability, although it should be understood that this is an order-of-magnitude bound.
 
@@
   \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
-The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.}
+The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
+The red vertical lines indicate when $\sigma = 0.01$.}
   \label{fig:scan-vex}
@@
 This effect explains why these small-scale oscillations have the same period for all parameters.
+Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$.
 
@@
 The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
-The dotted curve indicates a power-law fit (see text).}
+The dotted curve indicates a power-law fit (see text).
+The red vertical lines indicate when $\sigma = 0.01$.}
   \label{fig:scan-perigee}
@@
 However, the width of the prior was arbitrarily chosen, and all the physical density distributions have $|K_{3m}|$ smaller, so the actual Earth radii cutoff at which the $K_{3m}$ parameter estimates become too imprecise to be usable likely occurs at lower $r_p$.
-The exact value depends on the shape of the asteroid, but \jtd{When is it 0.01?}
+The exact value depends on the shape of the asteroid, but for this asteroid, the figure demonstrates  $r_p \sim 10$ Earth radii causes $\sigma(K_{\ell m}) \sim 0.01$ for some moments, and 0.01 is large enough that most density distributions would then be within consistent with observations.
 
@@
 
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{3m}$ to other $K_{3m}$ values.
-This is likely because \jtd{Something to do with uncertainty in orientaiton combining with high-frequency denisty sensitivity.}.
-This pattern will be seen in the following sections as well.
+The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
+Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
+This pattern of large $m$ corresponding to low uncertainty will be seen in the following sections as well.
 
@@
   \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
-The vertical dashed line indicates the reference asteroid value of $10^{-7}$.}
+The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
+The red vertical lines indicate when $\sigma =0.01$.}
   \label{fig:scan-product}
@@
   \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
-The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.}
+The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
+The red vertical lines indicate when $\sigma = 0.01$.
+(Lines are not shown for $K_{3m}$, $m < 3$ because they coincide with the vertical axis.)}
   \label{fig:scan-ratio}
@@
 
-\jtd{I should probably be commenting on when the parameter uncertainties are too large.}
+The location of the $\sigma > 0.01$ limit demonstrates the great incluence of observational precision on fit uncertainty: increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
 
@@
   \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.}
+  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
+The red vertical lines indicate when $\sigma = 0.01$.}
   \label{fig:scan-cadence}
@@
   \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.}
+  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
+The red vertical lines indicate when $\sigma = 0.01$.}
   \label{fig:observation-gap}
@@
 All maps are made in the Mollweide projection and shown in the inertial $\unit X-\unit Y-\unit Z$ frame.
-The orange star indicates the reference spin pole.}
+The orange star indicates the reference spin pole.
+The red contours enclose regions where $\sigma \geq 0.01$.}
   \label{fig:scan-spin}
@@
   \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P$.
-The reference value of 9 hr is shown as a vertical dotted line.}
+The reference value of 9 hr is shown as a vertical dotted line.
+The red vertical lines indicate when $\sigma = 0.01$.}
   \label{fig:scan-period}
@@
 The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the center of the other), and a tetrahedron.
+We use these shapes as rough approximations of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron), but also to demonstrate the density models' efficacy on sharp corners.
 The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
 Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is nonzero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed to exactly reproduce the input density moments), they express the inability of the density model to exactly reproduce the density moments.
+This difference is nonzero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed exactly to reproduce the input density moments), they express the degree to which the extracted distribution cannot be represented with harmonic or lumpy distributions respectively.
+
 \begin{figure*}
@@
 In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
-This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy and inflated uncertainty in the model.
-Estimates of $K_{\ell m}$ are therefore incorrect.
-In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the ill-constrained $K_{3m}$ components.
+This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy in $\gamma_0$ and inflated uncertainty in the density moments.
+In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the small and ill-constrained $K_{3m}$ components.
 
 Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is consistent with uniform at all points (within 1-2$\sigma$), except for the tetrahedron model, which contains a small number of points with very small uncertainty that exclude uniform density to $5\sigma$.
-In general, uncertainty is greater towards the edge of the asteroid.
-\jtd{Why do these low-uncertainty points exist in tet?}
-
-From these examples, we may draw the conclusions that all three models produce density distributions consistent with uniform for uniform asteroids.
+The size of uncertainty is such that the density distribution is largely consistent with uniform at all points for all models(within 1-2$\sigma$), with a small fraction of low-uncertainty regions which are inconsistent with uniform.
+Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
+
+From these examples, we may draw the conclusions that all three models produce density distributions generally consistent with uniform for uniform asteroids.
 The most likely distributions are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
@@
 
-However, the lumpy model exactly computes the location and density of the mass.
-\jtd{But it's not quite exact.
-Why?}.
-\jtd{Would like to say that there's no error in klm.} We see therefore that the lumpy model is capable of recreating the location of lumps accurately (except for the caveat mentioned in the previous section).
+However, the lumpy model computes the location and density of the mass very well.
+Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
+This in turn causes a 70 m inaccuracy in the lump's radius.
+Nevertheless, the accuracy is still very good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
 But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analyzed here.

### 2022-04-03 code/density/core.py

@@ -72,7 +72,6 @@ class Method:
         return out.real
 
     def get_unc(self, x,y,z):
-
         if self.final_uncertainty:
             b = self.get_b(x,y,z)
             if self.finite_element:

### 2022-04-03 data/probe-ratio/compile.py

@@ -84,6 +84,12 @@ for i in range(N_DIM):
     y_max_norm = np.max((param_data[1]-param_data[0]) / sigma_rho * scale)
     axs[i].set_ylim(y_min_norm * SCALE_Y, y_max_norm * SCALE_Y)
 
+    thresh = sigma_rho[(np.abs(param_data[2]-param_data[0]) > 0.01) | np.abs((param_data[-2]-param_data[0]) > 0.01)]
+    if len(thresh) > 0 and thresh[0] == sigma_rho[0]:
+        thresh = sigma_rho[(np.abs(param_data[2]-param_data[0]) < 0.01) & np.abs((param_data[-2]-param_data[0]) < 0.01)]
+    if len(thresh) > 0:
+        axs[i].axvline(x=thresh[0], color='r', linewidth=1)
+
     axs[i].set_ylabel(f"$\sigma({param_names[i]}) / \sigma_\\rho$", size=AXIS_SIZE)
 
     axs[i].set_xscale('log')

### 2022-04-03 data/scan-cadence/compile.py

@@ -85,7 +85,11 @@ for plot_index in range(N_DIM):
     ax.set_ylim(y_min_norm * SCALE_Y, y_max_norm * SCALE_Y)
 
     ax.set_xlim(np.min(cadences), np.max(cadences))
-    #ax.axvline(x=6, color='k', linewidth=1, linestyle='dashed')
+    #ax.axvline(x=1/30, color='k', linewidth=1, linestyle='dashed')
+
+    thresh = cadences[(np.abs(param_data[2]-param_data[0]) > 0.01) | np.abs((param_data[-2]-param_data[0]) > 0.01)]
+    if len(thresh) > 0:
+        ax.axvline(x=thresh[0], color='r', linewidth=1)
 
     if plot_index >= 3:
         ax.set_ylabel(f"$\sigma({param_names[plot_index]})$ ($\\times 10^{{-2}}$)", size=AXIS_SIZE)

### 2022-04-03 data/scan-perigee/compile.py

@@ -115,6 +115,10 @@ for plot_index in range(N_DIM):
     y_max_norm = np.max((param_data[1]-param_data[0]) * scale)
     ax.set_ylim(y_min_norm * SCALE_Y, y_max_norm * SCALE_Y)
 
+    thresh = perigees[(np.abs(param_data[2]-param_data[0]) > 0.01) | np.abs((param_data[-2]-param_data[0]) > 0.01)]
+    if len(thresh) > 0:
+        ax.axvline(x=thresh[0], color='r', linewidth=1)
+
     if plot_index < 1:
         ax.set_ylabel(f"$\sigma({param_names[plot_index]}) (\\times 10^{{-5}})$", size=AXIS_SIZE)
     elif plot_index < 3:

### 2022-04-03 data/scan-vex/compile.py

@@ -86,6 +86,10 @@ for plot_index in range(N_DIM):
     y_max_norm = np.max((param_data[1]-param_data[0]) * scale)
     ax.set_ylim(y_min_norm * SCALE_Y, y_max_norm * SCALE_Y)
 
+    thresh = v_excess[(np.abs(param_data[2]-param_data[0]) > 0.01) | np.abs((param_data[-2]-param_data[0]) > 0.01)]
+    if len(thresh) > 0:
+        ax.axvline(x=thresh[0], color='r', linewidth=1)
+
 
     if plot_index < 3:
         ax.set_ylabel(f"$\sigma({param_names[plot_index]}) (\\times 10^{{-7}})$", size=AXIS_SIZE)

### 2022-04-04 paper/main.tex
Continued to update paper

@@
 The mean density of the asteroid is therefore not constrained by tidal torque analysis.
-Secondly, torque is largest when $D$ is small (as expected).
-Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(D/a_M)^\ell (D/a_m)^{\ell'}$, the latter of which especially is a small number in most cases.
+Secondly, torque is largest when $D$ is small (as expected), with the leading order of $\bm \tau$ proportional to $D^{-3}$.
+Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_M/D)^\ell (a_m/D)^{\ell'}$, the latter of which especially is a small number in most cases.
 Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
@@
 
-Note: $v_\infty^2 = \sqrt{\mu/r_p (e-1)}$.
+If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
+In this appendix, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
+
+The physical parameters of the asteroid are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
+The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
+We perform two fits for two different values of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
+The latter requires $v_\infty = \sqrt{G\mu_M/r_p (e-1)}=32$ km s$^{-1}$.
+The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchagned, although the asteroid speed is dramatically increased.
 
 \jtd{Write}
+
+\begin{table}
+  \centering
+  \begin{tabular}{c|cc}
+    \hline 
+    $K_{\ell m}$ & $v_\infty=6$ km $s^{-1}$ & $v_\infty = 32$ km s$^{-1}$\\ \hline 
+    $\gamma_0$ & & 1.58 \\
+    $K_{22}$ & & 2.32 \\
+    $K_{20}$ & & 11.2 \\
+    $\Re K_{33}$ & & 17.5 \\
+    $\Im K_{33}$ & & 18.0 \\
+    $\Re K_{32}$ & & 17.7 \\
+    $\Im K_{32}$ & & 18.3 \\
+    $\Re K_{31}$ & & 24.9 \\
+    $\Im K_{31}$ & & 10.4 \\
+    $K_{30}$ & & 51.8 \\ \hline
+  \end{tabular}
+  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee and an excess velocity $v_\infty$ given as the column headers.}
+  \label{tab:jupiter-uncertainty}
+\end{table}
+
+There are additional effects of central body mass which are not captured in this analysis.
+For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_m$, small $r_p$, etc.).
+The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
+\begin{equation}
+  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_M}{r_p v_\infty^2}}.
+\end{equation}
+It was mentioned above that the observable perigee distance $r_p$ increases with $a_M \sim \mu_M^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
+Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
+However, the two effects we mention here both increase the number of encounters with properties conducive to accurate density moment extraction.
 

### 2022-04-06 paper/main.tex
Draft zero

@@
 
-\jtd{Write}
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+We assess the feasibility of extracting density moments and density distributions for a general asteroid encounters, and ask what encounter properties are necessary to obtain the most information about asteroid density.
+
+We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
+The tidal torque (equation \ref{eqn:tidal-torque}) is a function only of the density moments of the asteroid $K_{\ell m}$, the asteroid orbit, and the initial asteroid orientation.
+This equation revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
+
+We built a fast simulation for an asteroid flyby, truncating the equation at second order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
+Other studies have extracted the first-order moments from encounters, but not second order.
+We observe the following general properties of the moments:
+\begin{enumerate}
+  \item The second-order moments $K_{3m}$ are generally a factor of $~\frac{a_m}{r_p}$ more uncertain than the first-order moments, where $a_m$ is the asteroid radius and $r_p$ is the perigee distance.
+For our reference asteroid, this fraction was about $10^{-5}$.
+  \item Of the seven second-order moments, those that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
+  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a nonzero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
+\end{enumerate}
+
+We assessed the posterior uncertainty generated by the fit process by adjusting eleven parameters of an asteroid on an Earth flyby. The main conclusions are listed below.
+
+\begin{enumerate}
+  \item Highly precise rotational velocity data is required to produce precise  moments.
+Especially the uncertainty on the asteroid rotational period must be small compared to the uncertainty on asteroid spin pole.
+Our reference asteroid, with $\sigma P/P = 10^{-5}$ and the spin pole known to within a few degrees of error, was accurate enough.
+  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters, extending to about a third of a Lunar distance for the reference asteroid.
+  \item The asteroid rotational period must not be too small (smaller than about 5 hours, although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
+Nor must the asteroid's rotational velocity point in an inconvenient direction (orthogonal to the orbital plane, or in the orbital plane and perpendicular to the perigee vector).
+  \item The cadence of observation should be shorted than about 30 minutes (except $K_{30}$ will become unresolved for cadence worse than 10 minutes).
+Gaps of data can appear, specifically at perigee, but only for a little over an hour given 2 minute cadence before the posterior uncertainty significantly increases.
+\end{enumerate}
+
+Finally, we present three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid as obtained by light-curve analysis.
+The extracted density distributions largely are consistent with the true distributions in all cases we tested.
+Slight errors in $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
+Indeed, the models sometimes predict negative density (though more complicated models could be made not to).
+Errors in the shape estimate of teh asteroid also distort the density distribution.
+Nevertheless, large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
+Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.
+
+In the appendices, we answer more specific questions about the behavior of the tidal torque system and the fit process that might arise.
 
@@
 
-The physical parameters of the asteroid are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
+The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
 The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
@@
 The latter requires $v_\infty = \sqrt{G\mu_M/r_p (e-1)}=32$ km s$^{-1}$.
-The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchagned, although the asteroid speed is dramatically increased.
-
-\jtd{Write}
+The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
+
+Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
+The ratio between the posterior uncertainties in the Jupiter and the Earth flybys are shown in table \ref{tab:jupiter-uncertainty}.
+In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
 
@@
     \hline 
-    $K_{\ell m}$ & $v_\infty=6$ km $s^{-1}$ & $v_\infty = 32$ km s$^{-1}$\\ \hline 
-    $\gamma_0$ & & 1.58 \\
-    $K_{22}$ & & 2.32 \\
-    $K_{20}$ & & 11.2 \\
-    $\Re K_{33}$ & & 17.5 \\
-    $\Im K_{33}$ & & 18.0 \\
-    $\Re K_{32}$ & & 17.7 \\
-    $\Im K_{32}$ & & 18.3 \\
-    $\Re K_{31}$ & & 24.9 \\
-    $\Im K_{31}$ & & 10.4 \\
-    $K_{30}$ & & 51.8 \\ \hline
+    $K_{\ell m}$ & $\sigma_\text{Jupiter}/\sigma_\text{Earth}$\\ \hline 
+    $\gamma_0$ & 1.6 \\
+    $K_{22}$ & 2.3 \\
+    $K_{20}$ & 11 \\
+    $\Re K_{33}$ & 18 \\
+    $\Im K_{33}$ & 18 \\
+    $\Re K_{32}$ & 18 \\
+    $\Im K_{32}$ & 18 \\
+    $\Re K_{31}$ & 25 \\
+    $\Im K_{31}$ & 10 \\
+    $K_{30}$ & 53 \\ \hline
   \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee and an excess velocity $v_\infty$ given as the column headers.}
+  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
   \label{tab:jupiter-uncertainty}
 \end{table}
+
+This uncertainty can be understood as follows.
+The leading order of tidal torque is proportional to $\mu_m / D^3$.
+If $D/a_M$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_M=5$), then $\mu_m / D^3 \propto \rho_M$ where $\rho_M$ is the density of the central body.
+Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
+Since Jupiter is less dense than Earth, we expect that uncertainty in the first order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab-jupiter-uncertainty}.
+
+Additionally, the second-order terms are damped by an additional factor of $a_m/D$, which decreases if a massive central body is used.
+Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
+
+The $K_{\ell 0}$ components violate the norm, with $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
+In fact, $K_{30}$ essentially fills the prior.
+The special properties of $K_{\ell 0}$ have been analyzed noted before, in that they are always more uncertain than other moments and only enter certain parts of the tidal torque equation.
+\jtd{I did note this, right?} Table \ref{tab:jupiter-uncertainty} shows that these effects strengthen when a more massive central body is used.
 
@@
 Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
-However, the two effects we mention here both increase the number of encounters with properties conducive to accurate density moment extraction.
+
+Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
+However, we also mention biases that will cause more large-$a_m$ and small-$r_p$ asteroids to encounter Jupiter, and these will yield increased precision.
+Which of these contradicting effects dominates depends on the specific asteroid population near Jupiter.
 

### 2022-04-07 paper/main.tex
Paper draft 1

@@
   We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth flyby.
+We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
 Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best fit precision is affected.
 Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericenter data and the central body oblateness.
-Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose four models to construct a representative density distribution from fit results.
+Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
 \end{abstract}
@@
 
-The recent increase in the quantity and quality of high-sensitivity, all-sky surveys, such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide} has prompted the discovery of numerous asteroids, some kilometer-sized, and some predicted to encounter Earth or other planets closely in the near future.
-Theoretical work has demonstrated that many of these asteroids incur altered rotational velocities due to tidal torque \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}; this two-body generalized system has been studied to several orders and with several different methods.
-The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}.
+Over the past twenty years, the increase in quantity and quality of high-sensitivity, all-sky surveys has prompted the discovery of numerous asteroids.
+Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln} as well as space-based instruments such as he Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
+Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
+Light curve analysis has been performed on many of these new asteroids to study their surface properties, but analyses that are sensitive to the interior structure of the asteroid are rarer.
+
+Theoretical work has demonstrated that tidal torque alters the angular velocity of an asteroid during a gravitational encounter with another body, and that this tidal torque is sensitive to the interior density distribution of the asteroid \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+This two-body generalized system has been studied to different orders and with several different methods.
+The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015, Makarov2022ChaosOO}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}.
 Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
-Some examples of altered rotational velocity have recently been observed, including for (367943) Duende \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
-Altered rotational states have been excluded for 1I/2017 U1 'Oumuamua \cite{KWIECINSKI2018170}.
+Some examples of altered rotational velocity have recently been observed, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
+The upcoming encounter of Apophis is of particular interest and much attention has been devoted to accurate estimates of its orbital and physical properties \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis}, and in particular how its angular velocity will be affected by tidal torque \cite{souchay2014rotational, souchay2018changes}.
+Altered rotational states have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
 
@@
 
-Additionally, asteroid properties which are constrained only by beyond-leading-order tidal torque effects have not yet been extracted, and more research is needed to study whether these effects are, in fact, observable.
+Furthermore, asteroid properties which appear in the beyond-leading-order terms of tidal torque have not yet been extracted, and more research is needed to study in what cases these effects are observable.
 
 In this paper, we address these two topics by deriving a new equation of motion for an asteroid encounter system in section \ref{sec:methods}.
-This equation is simple and exact to arbitrary order, given assumptions reasonable for a planetary encounter (and many binary systems).
+This equation is simple and exact to arbitrary order, given assumptions reasonable for a planetary encounter (and many binary asteroid systems).
 It is also fast in that it allows volume integrals over the asteroid to be pre-computed.
-We use this equation of motion to simulate a generic asteroid flyby of Earth, and extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit, described in section \ref{sec:fit}.
+We use this equation of motion to simulate a generic asteroid encounter of Earth, and extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit, described in section \ref{sec:fit}.
 We measure the uncertainties in the posterior distribution of density moments as a function of various encounter parameters such as the observational uncertainty, cadence of observation, encounter orbital parameters, and more.
@@
 Finally, we propose methods to extract full density distributions with uncertainties from these density moments in section \ref{sec:distros}.
+We test the behaviour of these methods, highlight their strengths and weaknesses, and suggest ways in which they may be altered to suit the needs of the user.
 
@@
 
-In this section, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (subsection \ref{sec:moments}).
-Then we derive arbitrary-order equations of motion in section \ref{sec:eom} to simulate an asteroid encounter.
-Finally, in section \ref{sec:sim}, we describe the simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time.
+In this section, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (section \ref{sec:moments}).
+Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}), write the equations of motion for the system (section \ref{sec:eom}), and describe a simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time (section \ref{sec:sim}).
 
@@
 
-Throughout this paper, we assume that the asteroid under study is on a hyperbolic flyby with pericenter $r_p$ and excess velocity $v_\infty$.
-We do not consider any third-body perturbations, and we assume that the body being encountered is much more massive than the asteroid (e.g., Earth, Jupiter).
+Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with pericenter $r_p$ and excess velocity $v_\infty$.
+We do not consider any third-body perturbations, and we assume that the body being encountered is much more massive than the asteroid (e.g., Earth or Jupiter).
 
@@
 One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's center of mass.
-$\unit{X}$ points from the central body to the asteroid pericenter and $\unit{Z}$ pointing parallel to the orbit angular momentum.
+$\unit{X}$ points from the central body to the asteroid pericenter and $\unit{Z}$ points parallel to the orbit angular momentum.
 We will assume that the mass distribution of the central body is known in this inertial frame.
-In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
 
@@
 For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI.
+In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
 
 The relative positions of the body-fixed and inertial frames is given by the position of the asteroid.
-The relative orientations are of more physical interest.
-They are represented by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
+We represent the relative orientations by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
 \begin{equation}
@@
     \end{tikzpicture}
-    \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid. Orientation is expressed as a rotation from the body-fixed axes to the inertial axes.}
+    \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid.
+Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold and uppercase).}
     \label{fig:euler-angles}
@@
 In the next section, it will be shown that only certain aspects of the asteroid density distribution affect tidal torque.
-We isolate those aspects according to parameters we call ``density moments.'' First, we define the unnormalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
-The regular and irregular spherical harmonics are also defined:
+We isolate those aspects according to parameters we call ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
+The regular and irregular spherical harmonics then defined as:
 \begin{equation}
@@
 
-The density moments of an asteroid are defined as
-\begin{equation}
-  K_{\ell m} - \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
+We define the density moments of an asteroid as
+\begin{equation}
+  K_{\ell m} = \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
   \label{eqn:klm}
@@
 \end{equation}
-This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $\sqrt{5/3} a_m$).
-Both of these equations should be computed in the body-fixed axes.
+This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_m\sqrt{5/3} $).
+Both equations \ref{eqn:klm} and \ref{eqn:am} should be computed in the body-fixed axes.
 
@@
     &J_{\ell m} = \frac{1}{\mu_M a_M^\ell} \int_\mathcal{B} d^3 r \rho_M(\bm r) R_{\ell m}(\bm r)\\
-    &a_M^2 = \frac{1}{\mu_M} \int_\mathcal{B} d^3 r \rho(\bm r) r^2.
+    &a_M^2 = \frac{1}{\mu_M} \int_\mathcal{B} d^3 r \rho_M(\bm r) r^2.
   \label{eqn:jlm}
@@
 Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless.
-We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th mass moment of the asteroid.
+We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
+The gravitational potential field of the asteroid can be written entirely in terms of $K_{\ell, m}$ and $a_m$, so we expect not to need any information about the density distribution of the asteroid beyond these parameters to compute tidal torque.
 
@@
 Firstly, for real mass density, properties of the spherical harmonics imply that $K_{\ell m} = (-1)^m K_{\ell, -m}^*$.
-Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ provides $\ell_\text{max}^2$ degrees of freedom.
-However, some of these degrees of freedom are additionally constrained as discussed below.
+Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ contains $\ell_\text{max}^2$ degrees of freedom.
+However, some of these degrees of freedom are redundant with the choice of coordinates as we discuss next.
 
 By definition, $K_{00}=1$.
-Furthermore, $K_{1m} = 0$ since the body-fixed frame is centered on the asteroid center of mass.
+Furthermore, $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid center of mass.
 Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}=K_{2,-1} = 0$ and $\Im K_{22}=0$.
@@
 
-The physical meaning of $K_{22}$ and $K_{20}$ can be made even more clear in the case that the asteroid is a uniform-density triaxial ellipsoid.
-In this case, equating equation \ref{eqn:moi} with the moments of inertia of such a body yields semi-major axes of
+The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the axis lengths and can be compared to those found in equation \ref{eqn:moi}.
+This yields semi-axis lengths of
 \begin{equation}
@@
 
-The physical meaning of the higher-order moments $K_{3m}$ can be gleaned by assessing their symmetry properties.
+The physical meaning of the higher-order moments $K_{3m}$ can be aided by assessing their symmetry properties.
 An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_m(x,y,z)=\rho_m(-x,y,z)$) necessarily sets certain density moments to zero.
 Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}.
-Note that, while no mirror symmetries set $K_{00}$, $K_{20}$, or $K_{22}=0$, mirror symmetries exist which zero all the other moments, including $K_{3m}$.
+Note that, while no mirror symmetries set $K_{00}$, $K_{20}$, or $K_{22}$ equal to zero, mirror symmetries exist which zero all the other moments, including $K_{3m}$.
 $\Re K_{32}$, $K_{31}$, and $K_{30}$ are the only $K_{3m}$ components zeroed by only one axis.
-This will not affect our fit results for $K_{3m}$, but when we extract density distributions from $K_{3m}$, we will see that our sample shapes have most $K_{3m}=0$.
+This will not affect our fit results for $K_{3m}$, but when we compute density moments for sample distributions, we find that most $K_{3m}=0$.
 
@@
 Mirror symmetry along $\unit x$ means $\rho_m(x, y, z) = \rho_m(-x, y, z)$.
-Hyphens indicate that none of the mirror symmetries zero the moment in question.
+Dashes indicate that none of the mirror symmetries zero the moment in question.
 Since $r^2>0$ for $r\neq 0$, no symmetries set $a_m=0$ either.}
@@
 In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
-For the rest of this paper, we therefore treat $|K_{3m}| \sim 0.01$ as a practical limit on observability, although it should be understood that this is an order-of-magnitude bound.
+For the rest of this paper, we therefore treat an uncertainty on $|K_{3m}|$ of $0.01$ or less as a practical limit on observability, in that uncertainty greater than 0.01 means $K_{3m}$ are effectively unknown.
+This is only a rough estimate, however.
 
@@
 Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
-
-We present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
-These density moments can be pre-computed and do not have to be re-evaluated every time step.
-This formulation of the problem will be more useful for this study.
+A simple, first-order derivation is also easily computable via a power series expansion of the gravitational force of the asteroid, and the result is easily expressed in terms of the asteroid moment of inertia in the inertial frame.
+
+Here, we present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
+These density moments can be pre-computed and do not have to be re-evaluated every time-step.
 
@@
 We also assume no third-body perturbations from other Solar System objects.
-(More precisely, we assume that all third-body perturbing objects are closer to the central body's center of mass than the asteroid perigee distance.
-Thus, their density moments can be included in the density moments of the central body.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time.
+(Actually, third-body perturbing objects are allowed if they are closer to the central body's center of mass than the asteroid perigee distance.
+Thus, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time.
+(I.e., the central body does not rotate).
 
@@
     Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell & (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \\
-    & \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).\\
+    & \times \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).\\
   \end{split}
@@
 \end{equation}
-tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, and the asteroid orientation and position. Explicitly,
+tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_m$, $a_M$, and the asteroid orientation and position. Explicitly,
 \begin{equation}
@@
 Secondly, torque is largest when $D$ is small (as expected), with the leading order of $\bm \tau$ proportional to $D^{-3}$.
-Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_M/D)^\ell (a_m/D)^{\ell'}$, the latter of which especially is a small number in most cases.
+Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_M/D)^\ell (a_m/D)^{\ell'}$, the latter of which especially is small in most cases.
 Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
 For our analysis, we remove $\ell' > 3$ and we usually keep only $\ell=0$.
+Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
 
@@
 Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first order.
-Further, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$.
+Also, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
 
 For $\beta = \pi/2$, there are two interesting cases.
-One is for $\alpha = \phi$ or $\alpha = \pi + \phi$, where $\phi$ is the angle between the asteroid and the perigee.
+One is for $\alpha = \phi$ (or $\alpha = \pi + \phi$), where $\phi$ is the angle between the asteroid and the perigee.
 In this case, $\tau = 0$ to first order.
@@
 The $\bm \tau \parallel \unit z$ cases are interesting because they do not induce tumbling.
-If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
+If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state, since $\unit z$ is a principal axis), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
 These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$, and in general we see that $|\tau_z|$ is the smallest of the torque components.
@@
 \end{equation}
-Equations \ref{eqn:pos-eom} to \ref{eqn:omega-eom} and \ref{eqn:tidal-torque} form a set of nonlinear, first-order coupled differential equations which can be numerically integrated.
-They are expressed in terms of the physical parameters $\mu_{M/m}$, $a_{M/m}$, $J_{\ell m}$ and $K_{\ell m}$ given the density moment-moment of inertia relations given by equation \ref{eqn:moi}.
+Equations \ref{eqn:tidal-torque} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
+They are expressed in terms of the constant physical parameters $\mu_{M/m}$, $a_{M/m}$, $J_{\ell m}$ and $K_{\ell m}$ given the density moment-moment of inertia relations given by equation \ref{eqn:moi}.
 
@@
 
-We built a simulation to produce angular velocity data (in the inertial frame) as a function of time.
-This simulation requires as input (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_M$, and $a_m$; (4) the initial asteroid angular velocity in the inertial frame $\bm \omega_0$; (5) the asteroid radius $a_m$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+We built a simulation to produce angular velocity data (in the inertial frame, where it is observed from Earth) as a function of time.
+This simulation requires as input (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_M$, and radius $a_M$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid ``radius'' $a_m$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
-One can imagine that $a_m$ is determined by light-curve analysis, but if not, it is still necessary to fix $a_m$ or else the values of $K_{\ell m}$ are degenerate with $a_m$.
+One can imagine that $a_m$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_m$ or else the values of $K_{\ell m}$ are degenerate with $a_m$.
 
@@
 This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Thus, only Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
+Thus, only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
 
@@
 \end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was ~100 times the floating point error, and that neighboring values of $K_{\ell m}$ yielded significantly different spin pole data.
+The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was ~100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
+This choice of $dt$ was made for the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
 
@@
 
-In this section, we discuss how the simulation presented in the previous section was used to generate synthetic data and re-extract the density moments to assess how the precision of the re-extracted moments depends on the system parameters (e.g., true density moments, orbital parameters, etc.)
+In this section, we discuss how the simulation presented in the previous section was used to generate synthetic data and extract posterior distributions for the density moments.
 
@@
 We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
-\jtd{How detailed about the MCMC do I need to be?} Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{\ell m}$ given in section \ref{sec:moments}.
-Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to relabeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
+Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{\ell m}$ given in section \ref{sec:moments}.
+Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to re-labeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
 The other bounds were $|K_{3m}| < 1$.
+
+The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
+The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low quality to resolve the parameters.
+$~10^4$ iterations was often required, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
 
@@
 It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
-Walkers were initialized near this local minimum, with spread given by the inverse Hessian of the likelihood at that point.
+Walkers were initialized near this local minimum, distributed with probability given by the likelihood as determined via the inverse Hessian of the likelihood at the minimum.
 Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
-Therefore, a simpler simulation with the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find $K_{3m}$, with $\gamma_0$ and $K_{2m}$ fixed.
-This tiered miniimzation process motivates us to call $\gamma_0$ and $K_{2m}$ the ``first-order parameters'' and $K_{3m}$ the ``higher order parameters.''
+Therefore, a simpler simulation without the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find $K_{3m}$, with $\gamma_0$ and $K_{2m}$ fixed.
+This tiered minimization process motivates us to call $\gamma_0$ and $K_{2m}$ the ``first-order parameters'' and $K_{3m}$ the ``second-order parameters.''
 
@@
 
-We model uncertainty in each spin vector $\bm \omega$ as uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
-Consider a true spin vector $\bm \omega^*$.
-Coordinates can be chosen in which $\bm \omega^* \parallel \unit Z$.
-Then, expressing the observed spin vector $\bm \omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centered on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\rho=\omega/\omega^*$ from a log-normal distribution centered on one, with width $\sigma_\rho$.
+We model uncertainty in each asteroid spin vector $\bm \Omega$ in the as uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
+Consider a true spin vector $\bm \Omega^*$.
+For the sake of description, we work in coordinates in which $\bm \Omega^* \parallel \unit z$.
+Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
+We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
 We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole.
@@
 \begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}
-\end{equation}
-See figure \ref{fig:uncertainty-model} for a representation of the uncertainty model.
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
+\end{equation}
+See figure \ref{fig:uncertainty-model} for a representation of the uncertainty model shown in the inertial frame.
 
@@
 
-  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \omega^*$};
+  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
   \draw[dashed] (-3, -2) -- (-3, 3);
@@
 
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \omega$};
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
   \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
@@
   \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-1, 1.8) node[anchor=center] {$\rho \omega^*$};
+  \draw (-1, 1.8) node[anchor=center] {$\rho \Omega^*$};
 
   \end{tikzpicture}
-  \caption{Diagram of the uncertainty model used to define the probability that the true spin vector $\bm \omega^*$ should be observed as $\bm \omega$.
+  \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
 The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
@@
 \begin{equation}
-  \ln \mathcal{L} = -\sum_{i = 0}\frac{\cos^{-1} (\bm \omega_i^* \cdot \bm \omega_i/(\omega_i^* \omega_i))^2}{2\sigma_\theta^2}+\frac{\ln \parens{\omega_i /\omega_i^*}^2}{2\sigma_\rho^2} + \ln\frac{\omega_i}{\omega_i^*}.
+  \begin{split}
+  \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
+  +&\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
+  \end{split}
   \label{eqn:log-likelihood}
@@
 However, the posterior distribution was widened by a factor of 1000 to make the band widths visible.
-Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in one band.
+Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
 
 The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
-The asymmetric case leads to more divergence than the symmetric case --- a feature which will be generalized in the next section.
 
@@
 In this section, we assess the sensitivity of the posterior distributions for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations.
-Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the central body oblateness, and the asteroid period.
+Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the asteroid period, and the central body oblateness.
 These effects are presented roughly in order of how much they affect the parameter precision, from highest to lowest.
@@
 2-$\sigma$ is defined likewise for 95.45\% of the posterior.
-The posteriors are usually roughly Gaussian, so that 1-$\sigma$ is roughly the standard deviation of the posterior.
+The posteriors are usually roughly Gaussian, so that the upper and lower error bars are equal and 1-$\sigma$ is roughly the standard deviation of the posterior.
 
 In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-We further present a test of how precision depends on cadence, asteroid period, and the duration of the flyby in appendix \ref{app:cadence-tests}, and we compare precision for a Jupiter and an Earth flyby in appendix \ref{app:jupiter-earth}.
+We further present a test of how precision depends on cadence, asteroid period, and the duration of the encounter in appendix \ref{app:cadence-tests}, and we compare precision for a Jupiter and an Earth encounter in appendix \ref{app:jupiter-earth}.
 
@@
 The orbit can be rotated to the $\unit X \unit Y$-plane by changing the density moments of the central body.
-Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant up to the $J_{2m}$ terms of equation \ref{eqn:tidal-torque} we do not investigate them here.
+Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant up to the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
 
 We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 68 and 95\% confidence intervals are displayed in figures \ref{fig:scan-perigee} for $r_p$ and \ref{fig:scan-vex} for $v_\infty$.
+Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 68 and 95\% confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
 
@@
 This effect explains why these small-scale oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$.
+Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
 
@@
 Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_m/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution, with uncertainty ranging from -1 to 1.
-Near $r_p \approx 40$ Earth radii, the $K_{32}$ and $K_{31}$ components also fill the prior.
-However, the width of the prior was arbitrarily chosen, and all the physical density distributions have $|K_{3m}|$ smaller, so the actual Earth radii cutoff at which the $K_{3m}$ parameter estimates become too imprecise to be usable likely occurs at lower $r_p$.
-The exact value depends on the shape of the asteroid, but for this asteroid, the figure demonstrates  $r_p \sim 10$ Earth radii causes $\sigma(K_{\ell m}) \sim 0.01$ for some moments, and 0.01 is large enough that most density distributions would then be within consistent with observations.
+For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the reference 0.01 limit.
+At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second order component, becomes unresolved.
+Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
+The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
 
@@
 
-Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties, $\sigma \propto r_p^\alpha$.
+Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
 These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
@@
 The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4, except for $K_{3m}$, which is fortunate from the perspective of observation, since it make render larger values of $r_p$ accessible to measuring $K_{3m}$.
+The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since it make render larger values of $r_p$ accessible to measuring $K_{3m}$.
 
@@
 
-The very strong dependence of $\sigma$ on $r_p$ makes this analysis only usable on close flybys.
-Fortunately, in the case of Earth, these flybys are also likely to have the best associated observational uncertainty due to their proximity.
-\jtd{Unfounded speculation, but hopefully this is ok.}
+The very strong dependence of $\sigma$ on $r_p$ makes this analysis only to extract second-order moments on close encounters.
+Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty due to their proximity.
+The first-order moments can still be extracted at much larger perigee distances in our model.
 
@@
 \label{sec:scan-uncertainty}
-There are two variables, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}).
+There are two parameters, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}).
 Rather than explore the full space spanned by these two values, we measure how parameter uncertainties depend on the product of uncertainties $\sigma_\theta\sigma_\rho$ (with the radio fixed), and the ratio $\sigma_\rho / \sigma_\theta$ (with the product fixed).
@@
 We choose these metrics because we generally expect that the parameter uncertainty $\sigma$ be proportional to the observational uncertainty, but whether the dependence is stronger on $\sigma_\theta$ or $\sigma_\rho$ is not immediately clear.
-We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their product, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
+We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their ratio, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
 Indeed we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
@@
 We summarize this pattern my stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
-This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by lightcurve analysis, but I have no evidence.}
+This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I don't know enough about light curve analysis to be sure.}
 
@@
 
-The location of the $\sigma > 0.01$ limit demonstrates the great incluence of observational precision on fit uncertainty: increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
+The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty: increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
 
@@
 
-Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different or when $|K_{22}|$ is large.
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ increase for large $K_{20}$, which is large axis ratios in the ellipsoid case (non-sphericity).
-For flat, disk-like asteroids, a different parametrization might therefore be more appropriate.
+Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
+Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which is large axis ratios in the ellipsoid case.
 
 Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters for reference.
-They show that $\gamma_0$ and $K_{22}$ are highly correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are generally uncorrelated.
-This is expected $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
+They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
+This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
 They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
@@
 Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
-It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating a flyby, as we do in this paper.
-The uncertainty then can be expected to differ across other shapes by a factor of about two or less.
+It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
+The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
 
@@
 
-The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes.
+The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
 We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
@@
 
-Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence ($\Delta t$) for $\Delta t \lesssim 40$ min.
+Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
 We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 40$ min, a time scale which is likely characteristic of the asteroid system.
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
 We name this rough cadence limit $T_\text{cad}$.
 
-By dimensional analysis, we expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P$ and the time spent near perigee $T_p$.
+We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P$ and the time spent near perigee $T_p$.
 The latter can be estimated by the unitless combination
@@
 
-Which of $P$ and $T_p$ is more important to the determination of $T_\text{cad}$ is assessed in appendix \ref{app:cadence-tests}.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal.
-However, it is generally better to have short cadence when possible.
+We further study the effect of $P$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
+
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is slightly exceeded).
+However, shorter cadence almost always leads to lower uncertainties.
 
@@
 \label{sec:scan-gap}
-In certain negative circumstances, spin data might not be able to be captured for a close encounter at perigee.
+In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
 The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
 Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-The angular velocity evolution here is dominated by torque-free precession dictated by the moment of inertia components.
-so that zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ \cite{MOSKOVITZ2020113519}.
+There, the angular velocity evolution is dominated by torque-free precession dictated by the moment of inertia components.
+That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
 However, $K_{3m}$ are not extractable from precession data alone.
@@
 
-To test this, we mask the perigee of the counter by removing data within time $T$ of the perigee, where $T$ ranges from 0 to 3 hours.
+To test this, we mask the perigee of the counter by removing a duration $T$ of data from the perigee, where $T$ ranges from 0 to 3 hours.
 To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
@@
 Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-This cutoff is likely determined by the orbital elements of the encounter, which control how much time the asteroid spends in the high-torque region.
 On the other hand, none of the uncertainties increase noticeably for $T < 30$ min.
@@
 Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$.
-They also have quantitatively the same cutoff of 30 min before uncertainty is markedly affected.
-This suggests that the factors that govern uncertainty due to cadence and uncertainty due to lack of data at perigee are the same.
+They also both have cut-offs where uncertainty markedly increases, and these cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
+This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
 
@@
 
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \omega_0$ both because spin sets the initial asteroid orientation (up to $\gamma_0$) and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-As an example, in section \ref{sec:tidal-torque}, we noted that $\bm \omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.
-
-In figure \ref{fig:scan-spin}, we display 1-$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \omega_0$, mapped onto the sky in the inertial frame.
-Our samples for $\bm \omega_0$ were laid out on a Fibonacci sphere to ensure they were evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+As an example, in section \ref{sec:tidal-torque}, we noted that $\bm \Omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.
+
+In figure \ref{fig:scan-spin}, we display 1-$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
+Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
 To highlight common features across the parameters, we also display the average 1-$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
@@
   \caption{$1-\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection and shown in the inertial $\unit X-\unit Y-\unit Z$ frame.
+All maps are made in the Mollweide projection and shown in the inertial frame.
 The orange star indicates the reference spin pole.
@@
   \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:spin-pole}, in Mollweide (\textit{left}) and polar (\textit{right}) projections.
+  \caption{The weighted average of the uncertainties shown in figure \ref{fig:spin-pole}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
 See text for a description of how the average was computed.
-Black dots indicate the locations of sample spin poles, and the orange star indicates the reference spin pole.}
+Black dots indicate the locations of sample spin poles, and the orange star indicates the reference spin pole.
+The polar projection is centred at the south pole, or $-\unit Z$}
   \label{fig:scan-spin-avg}
@@
 
-The characteristics of tidal torque discussed in section \ref{sec:tidal-torque} indicate that certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque: $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first order.
-We relate this to the initial direction of $\bm \omega_0$, via the crude assumption that $\bm \tau$ is small until perigee.
-Then, since $\bm \omega_0 \parallel \unit z$ by assumption that the asteroid is not tumbling, we have that $\bm \omega_0 \parallel \unit Y$ and $\bm \omega_0 \parallel \unit Z$ lead to $\bm \tau \parallel \unit z$, and $\bm \omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
+Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
+For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first order.
+We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
+Then, since $\bm \omega_0 \parallel \unit z$ in the body-fixed frame as an initial condition (section \ref{sec:sim}), we have that $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
 
@@
 This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the flyby.
+Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
 Also, $\tau_z$ is small and affected by fewer parameters than $\tau_x$ or $\tau_y$.
 Both of these are reasons why $\bm \tau \parallel z$ might inhibit precise fits to spin data.
-If $\bm \tau = 0$ to first order, then second-order $\tau$ and non-perigee $\bm \tau$ will dominate, and these may indeed induce precession.
+If $\bm \tau = 0$ to first order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters.
 
 It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \omega_0 \parallel \unit Z$ and $\bm \omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times the uncertainty at other $\bm \omega_0$ values, and possibly higher.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in figure \ref{fig:scan-spin-avg}
-
-\subsection{Oblateness}
-\label{sec:scan-oblateness}
-
-In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_M \gg \mu_m$ (so that the asteroid orbit's focus is the center of mass of the central body), we have $J_{1m} = 0$.
-The effect of oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_M / D)^2$.
-We expect these parameters to have little effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_M R_M^2)$, where  $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_M$ is the true radius of the body (not $a_M)$.
-Note that $J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-But for an equatorial orbit, the principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
-(Some sources such as Ref.~\cite{paterLissauer2015} take this definition of $\epsilon$ as their definition of $J_{20}$).
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range ofittedf oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in figure \ref{fig:scan-oblateness}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
-  \vfill
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Left}: 1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
-Linear best fit lines to $\sigma$ (black, dotted) are plotted.
-\textit{Right}: The deviation of posterior mean extracted from a zero-oblateness model from the true parameters given a model with oblateness $\epsilon \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.}
-  \label{fig:scan-oblateness}
-\end{figure}
-
-Figure \ref{fig:scan-oblateness} (top pane) demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from the effect of other factors studied above.
-Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
-The linear best-fit lines match the data well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
-Other parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive.
-
-Note that if a flyby is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_M$ and $\mu_M$ will change in addition to $\epsilon$.
-These two parameters do affect the precision of the fit parameters, so the figure does not state that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
-
-Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the effect of planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that this is not valid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated by assuming nonzero $\epsilon$.
-The difference between the posterior mean $K_{\ell m}$ and true $K_{\ell m}$ are shown.
-Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m}| = 0$ is not contained in the 2-$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
-Therefore, accurately modeling oblateness to high precision is essential for accurate estimation of fit parameters.
-For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, so it is also vital to use the correct asteroid orbital plane.
-
-Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, including it in $J_{20}$.
-Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body center of mass (though the effect is not quite quadratic because $a_m$ also increases for large distances).
-This process is only valid when the asteroid never passes closer to the central body than the moon.
-
-As an order-of-magnitude estimate for this effect, two spherical masses with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
-Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
-
-This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
-Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
-However, correct representation of oblateness is essential to correctly estimate $K_{\ell m}$.
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in figure \ref{fig:scan-spin-avg}.
 
@@
 
-The final encounter parameter we study is the initial rotational period of the asteroid $P_\omega$.
-The dynamical time scales $r_p/v_\infty$ and $\mu_m / (r_p v_\infty)$ have already been mentioned and the ratio between them and $P$ in principal may affect the posterior uncertainty $\sigma$.
+We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma$.
+The dynamical time scales $r_p/v_\infty$ and $\mu_m / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P$ in principal may affect $\sigma$.
 In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
@@
 But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for low $P_\omega$ because these asteroids do not tumble after perigee, and tumbling after the perigee allows better refinement of the $K_{2m}$ parameters.
+$K_{20}$ and $K_{22}$ show very large uncertainty for low $P_\omega$ because these fast-rotators leave perigee tumbling very little or not at all.
+This increases uncertainty on the $K_{2m}$ parameters, which is measured by tumbling.
 
@@
 This is most visible in the figure for $K_{30}$.
-The cause of this is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
+The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
 We already discussed that asteroids with $P_\omega$ large do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ don't affect.
@@
 
+\subsection{Oblateness}
+\label{sec:scan-oblateness}
+
+In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
+By assumption that $\mu_M \gg \mu_m$ (so that the asteroid orbit's focus is the center of mass of the central body), we have $J_{1m} = 0$.
+The effect of oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_M / D)^2$.
+We expect these parameters to have little effect on the asteroid.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_M R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_M$ is the true radius of the body (not $a_M$ from equation \ref{eqn:jlm}).
+Note that $J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
+
+For an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
+(Some sources such as Ref.~\cite{paterLissauer2015} take $\epsilon=J_{20}$ as their definition of $J_{20}$).
+For simplicity, we use this equatorial orbit case.
+If the orbit is non-equatorial, the other $J_{2m}$ terms will be non-zero.
+Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $K_{3m}$ are all zero.
+The next order of precision after this oblateness approximation is therefore $J_{4m}$ and  non-ellipsoid corrections to the central body shape.
+
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in figure \ref{fig:scan-oblateness}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
+  \vfill
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
+  \caption{\textit{Top}: 1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
+Linear best fit lines to $\sigma$ (black, dotted) are plotted.
+\textit{Bottom}: The difference between posterior means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies.}
+  \label{fig:scan-oblateness}
+\end{figure}
+
+Figure \ref{fig:scan-oblateness} (top pane) demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from the effect of other factors studied above.
+Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
+The linear best-fit curves match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+Other parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
+
+Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_M$ and $\mu_M$ will change in addition to $\epsilon$.
+These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not state that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+
+Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
+However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is not valid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated by assuming non-zero $\epsilon$.
+The difference between the posterior means and true parameters are shown.
+Posterior uncertainties are also shown as bands.
+The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m}| = 0$ is not contained in the 2-$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
+Therefore, accurately modelling oblateness to high precision is essential for accurate estimation of fit parameters.
+For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
+
+Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, including it in $J_{20}$.
+Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body center of mass (though the effect is not quite quadratic because $a_M$ also increases for large distances, and $J_{20}$ is divided by $a_M^2$.).
+This process is only valid when the asteroid never passes inside the moon's orbit.
+
+As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
+Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
+
+This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
+Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
+However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
+
 \section{Density distributions}
@@
 One of them can be chosen, or a fourth created, depending on what features are desired to be represented in the density distribution.
-All three of these models assume that the asteroid shape is known (for example, by light curve or radar data).
+All three of these models assume that $a_m$ and the asteroid shape is known (for example, by light curve or radar data).
 Uncertainty on this shape estimate is assumed to be small.
@@
 
+In section \ref{sec:results}, we were forced to fix $a_m$ rather than fit for it because $a_m$ is degenerate with scaling the $K_{3m}$ components.
+However, $a_m$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
+It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
+If $a_m$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_m$ constraint can be removed.
+
 Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
@@
 In section \ref{sec:general-density}, we describe the general form our three models must take.
-Then we lay out each individually and compare them in section \ref{sec:density-compare}.
+Then in sections \ref{sec:likelihood} to \ref{sec:lumpy} we lay out each individually and compare them in section \ref{sec:density-compare}.
 In appendix \ref{app:find-surface}, we do not assume that the asteroid shape is known and instead assume that the density is constant.
@@
 
-We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
-The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exactly in the hybrid frame, and the $K_{\ell m}$ components are known in the local frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ and the known $a_m$.
+We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
+The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame.
+The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_m$ (equal in all frames).
 
@@
 Similarly, the form of equation \ref{eqn:am} guarantees that $a_m^2$ is linear in $\rho(\bm r)$.
-Equation \ref{eqn:am} and equation \ref{eqn:klm} applied to $K_{00}=1$ can be used to enforce the choices of $\mu_m$ and $a_m^2$.
-
-Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm D)$ for an $m$-dimensional vector $\bm D$ which controls the free parameters of $\rho$.
-We will leave the explicit definition of $\rho(\bm r, \bm D)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm D$; i.e.,
-\begin{equation}
-  \rho(\bm r, \bm D) = \bm B(\bm r) \cdot \bm D
+Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_m^2$ and $\mu_m$.
+
+Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm \Theta)$ for an $m$-dimensional vector $\bm \Theta$ which contains the free parameters of $\rho$.
+We will leave the explicit definition of $\rho(\bm r, \bm \Theta)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm \Theta$; i.e.,
+\begin{equation}
+  \rho(\bm r, \bm \Theta) = \bm B(\bm r) \cdot \bm \Theta
   \label{eqn:density-distro}
@@
 for a $m$-dimensional vector $\bm B(\bm r)$.
-Thus, the defining equations of $a_m^2$ and $K_{\ell m}$ represent a linear function that give the parameters in terms of $\bm D$.
+($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_m^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
 We further assume that the model describes a way to reverse this equation, to write
 \begin{equation}
-  \bm D = A \bm K
+  \bm \Theta = A \bm K
   \label{eqn:density-model}
@@
 
-To propagate uncertainties from $\bm K$ to $\bm D$ and therefore $\rho(\bm r)$, we first need the covariance matrix $\Sigma_K$ for $\bm K$.
-First, assume that the hybrid frame is offset from the local frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
+To propagate uncertainties from $\bm K$ to $\bm \Theta$ and therefore $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
+First, assume that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
 Then
 \begin{equation}
-  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{local}.
-  \label{eqn:local-to-hybrid}
-\end{equation}
-Since $K_{\ell m}^\mathrm{local}$ was obtained by an MCMC fit, a large set of posterior-distributed samples are available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{local}$, and the covariance matrix $\Sigma_K$ can be computed statistically by applying equation \ref{eqn:local-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm D$ is $\Sigma_D = A \Sigma_K A^T$
-and the density distribution and uncertainty on density distribution are equal to
+  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{body-fixed}.
+  \label{eqn:body-fixed-to-hybrid}
+\end{equation}
+by equation \ref{eqn:ylm-rotation}.
+Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of posterior-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
 \begin{equation}
@@
 \subsection{The Likelihood model}
-For the likelihood model, we restrict the degrees of freedom of $\rho(\bm r)$ by defining a likelihood function $\mathcal{L}$ on the density distribution, and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
+\label{sec:likelihood}
+
+For the likelihood model, we restrict the degrees of freedom of $\rho(\bm r)$ by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
 This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
-The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require an uncorrelated Gaussian likelihood.
-
-To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0$ plus some deviation $D_i$, where $\rho_0$ is constant across the asteroid.
+The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require a Gaussian likelihood.
+
+To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
 This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
@@
 \begin{equation}
-  \mathcal{L}(\bm D) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{D_i^2}{2 \sigma^2}}
+  \mathcal{L}(\bm \Theta) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{\Theta_i^2}{2 \sigma^2}}
 \end{equation}
@@
 These parameters do not affect the location of the maximum, so we do not define them.
-Given this likelihood, the log likelihood is proportional to $-|\bm D|^2$.
-Minimizing the norm of $\bm D$ is therefore equivalent to finding the maximum likelihood.
-
-Putting aside the problem of minimizing the norm for a moment, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm D$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:jlm} or \ref{eqn:am}, evaluated over the $i$th finite element.
-We want to solve $\bm K = M \bm D$ for $\bm D$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
+Given this likelihood, the log likelihood is proportional to $-|\bm \Theta|^2$.
+Minimizing the norm of $\bm \Theta$ is therefore equivalent to finding the maximum likelihood.
+
+Putting aside the problem of minimizing the norm for a moment, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:jlm} or \ref{eqn:am}, evaluated over the $i$th finite element.
+We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
 Since $m>n$, the Moore-Penrose inverse of $M$ is
@@
 where $M^*$ is the adjoint of $M$.
-The vector $\bm D=M^+\bm K$ is guaranteed to solve $\bm K = M \bm D$, and by the properties of the Moore-Penrose inverse, this $\bm D$ also happens to minimize the norm of all possible $\bm D$ that satisfy the equation.
-Thus, we define $A=M^+$, which fully defines the model.
-
-Note that this model is fast to compute; assuming fast matrix multiplication, the most time-consuming step is the matrix inversion of equation \ref{eqn:mpi-underdetermined}.
-But $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
+Thus, defining $A=M^+$ also minimizes $\mathcal{L}$ and fully defines the model.
+
+Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
 
 \subsection{The Harmonic model}
+\label{sec:harmonic}
+
 We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
@@
 \begin{equation}
-  \rho(\bm r) = \sum_{\ell, m} \frac{D_{\ell m}}{a_m^\ell} R_{\ell m}^*(\bm r)
+  \rho(\bm r) = \sum_{\ell, m} \frac{\Theta_{\ell m}}{a_m^\ell} R_{\ell m}^*(\bm r)
   \label{eqn:harmonic-rho}
 \end{equation}
-where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $D_{\ell m}$ are free (complex) parameters.
+where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $\Theta_{\ell m}$ are free (complex) parameters.
+Since $\rho$ is real, we have $\Theta_{\ell m}=(-1)^m \Theta_{\ell,-m}^*$.
 By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
-Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $D_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm D$.
+Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $\Theta_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm \Theta$.
 
@@
 \begin{equation}
-  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'} a_m^\ell} D_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
+  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'} a_m^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
   \label{eqn:harmonic-mat}
 \end{equation}
-This is an over-determined matrix equation $\bm K = M \bm D$, where $M$ is an $n \times m$ matrix.
-The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm D$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm D$ is minimized).
+This is an over-determined matrix equation $\bm K = M \bm \Theta$, where $M$ is an $n \times m$ matrix.
+The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm \Theta$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm \Theta$ is minimized).
 However, the form of the inverse changes due to the equation being overdetermined:
@@
 \end{equation}
-A nonspherical perturbation will introduce small off-diagonal entries to $M$.
-This diagonal represents an interpretation of the physical meaning of $K_{\ell m}$; they are directly related through this form of $M$ and the matrix equation $\bm K = M \bm D$ to the coefficients of the spherical harmonic expansion of the asteroid in the case of a spherical asteroid.
+A non-spherical perturbation will introduce small off-diagonal entries to $M$.
+This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
 
 \subsection{The Lumpy model}
+\label{sec:lumpy}
 
@@
 
-Suppose the asteroid contains $N$ `lumps' of constant mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid center of mass, and immersed in a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid center of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
 For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
-(For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.) Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the center of mass of the asteroid.
+For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
+Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the center of mass of the asteroid.
 The displacement of the shape centroid from the center of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
@@
 The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
-These degrees of freedom should be compared to the known density moments, of which there is a square number $(L+1)^2$.
-However, three of these are the center of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass.
-One is then added, representing $a_m$.
-So the total number of known parameters is $(L+1)^2 - 3$, which is 13 when the second-order density moments are known.
+These degrees of freedom should be compared to the known density moments and $a_m$, of which there are $(\ell_\text{max}+1)^2+1$.
+However, three of these are the center of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
 We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
@@
   \end{tabular}
-  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modeled, and $d$, the number of independent moment of inertia axes considered for each lump.
-The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are colored black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are colored gray.}
+  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
+The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are coloured gray.}
   \label{tab:lump-dof}
@@
 \end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:jlm} and $a_m$ in equation \ref{eqn:am} respectively.
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:jlm} and $a_m$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
 Crucially, note that we set normalizing factors $1/(\mu_m a_m^\ell)$ and $1/\mu_m$ in equations \ref{eqn:jlm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
-The zero-indexed parameters indicate the density moments of the asteroid medium surrounding the lumps.
-The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame.
+The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
+The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid center of mass.
 
@@
   & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
-  & a_i'^2 = a_i^2 + x_i^2 K_{00}
+  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_m}
   \end{split}
@@
 \end{equation}
+from Ref.~\cite{Gelderen1998TheSO}.
 The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
-Here, $K_{00}^i$ is the added mass $\mu_i$ of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate its orientation and moment of inertia ratios.
+Here, $\mu_i$ is the added mass of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate the lump's orientation and moment of inertia ratios.
 Its volume is constrained by $a_i^2$.
@@
 Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$.
-Therefore, if we define $\bm D$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm D$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm D$ is overdetermined).
-Henceforth, we assume that the dimensions of $\bm D$ are less than or equal to the number of known parameters (the shaded regions of table \ref{tab:lump-dof}), so that $A$ is given by equation \ref{eqn:mpi-overdetermined}).
-Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its center of mass.
-
-This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a nonlinear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
-The constraints on $\bm x_i$ and $\mu_i$ are primarily
+Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
+Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its center of mass and the already known surface shape.
+
+This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
+The constraints on $\bm x_i$ and $\mu_i$ are
 \begin{equation}
@@
 The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
-We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with solutions.
+We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with close solutions.
 This is done by minimizing
@@
 \end{equation}
-Then $A=M^+$ and $\bm B(\bm r)$ following from the resulting values of $K_{\ell m}^i$ and $a_i^2$ defines the model.
+which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
+Then $A=M^+$ and $\bm B(\bm r)$ following from the values of $\bm x_i$ and $\mu_i$ defines the model.
 If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
@@
 
-To test the properties of the three density models defined above, we simulate several asteroids with different shapes and density distributions on a close Earth encounter, with the reference asteroid orbital and observational parameters.
-Density moments are extracted via our fit process and density distributions by the three methods.
-Below, we compare them.
+To test the properties of the three density models defined above, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
+Density moments are extracted via our fit process and density distributions extracted by the three above methods.
+Below, we compare the resulting distributions to understand the performance of the extraction methods.
 
@@
 
-First, we simulate several asteroids with uniform density distributions and ask whether a distribution is recovered.
+First, we simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
 The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the center of the other), and a tetrahedron.
@@
 Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is nonzero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed exactly to reproduce the input density moments), they express the degree to which the extracted distribution cannot be represented with harmonic or lumpy distributions respectively.
+This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed exactly to reproduce the input density moments), they express the degree to which the extracted distribution cannot be represented with harmonic or lumpy distributions respectively.
 
@@
 This is generally true for uniform density asteroids.
-This is a useful property because it lends confidence that the models produced are truly representative of the asteorid.
+This similarity is a useful property because it lends confidence that the models produced are truly representative of the asteroid.
 The fact that the harmonic model produces very little density moment error ($\Delta K_{\ell m}$) also lends confidence to the distribution; the harmonic model is overdetermined and is not guaranteed to perfectly match the fit-extracted moments.
@@
 This non-uniformity is driven by error in the estimates of the density moments.
-Note that most of the asteroid does indeed have density close to one in both cases.
+Note that most of the asteroid has density close to one in both cases, with the factor of two reached only by small regions.
 The lumpy model yields a much more uniform distribution, but only because it is designed to produce uniform lumps.
@@
 Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is largely consistent with uniform at all points for all models(within 1-2$\sigma$), with a small fraction of low-uncertainty regions which are inconsistent with uniform.
+The size of uncertainty is such that the density distribution is consistent with uniform at most points for all models(within 1-2$\sigma$), with a small number of low-uncertainty regions that are less consistent with uniform.
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
@@
 From these examples, we may draw the conclusions that all three models produce density distributions generally consistent with uniform for uniform asteroids.
-The most likely distributions are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
+The most likely distributions (i.e., the ones shown in the figures) are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
 Asymmetric asteroids such as the dumbbell and the asymmetric reference asteroids yield the best results because they have $K_{22} \neq 0$ and therefore do not suffer from degeneracy in initial orientation.
-Finally, the lumpy model can generally be ruled out in these cases because it produces nonphysical results.
+Finally, the lumpy model can generally be ruled out in these cases because it produces unphysical results.
+
+If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
+However, doing so ignores the observational insight we gain from our fits to $K_{3m}$, so it is only valid when $K_{3m}$ are too poorly constrained to be used.
 
 \subsubsection{Spherical shape test}
-We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and attempting to extract density distributions assuming a spherical shape.
+We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and extracting density distributions assuming a spherical shape.
 We do this for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
@@
 Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
-Before, we took this fact as a signal that the distributions are likely to be correct.
 However, now they both produce negative density distributions for both asteroid shapes.
-This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
-In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (up in the figure).
+(Before, only the symmetric model did.) This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
+In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top of the figure).
 The density is large at large $|y|$ (front right in the figure).
@@
 
-The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$..
-The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|$ for the original asteroids.
+The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
+The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|$ for the original asteroids, making it clearly a poor model.
 
@@
 
-Though the general mass placement arrived at by both the likelihood and harmonic models is accurate, the precise density distributions are inaccurate because they predict negative densities.
-This might be addressed for the likelihood model by selecting a likelihood that strongly disfavors negative densities, such as a log-normal distribution.
-However, this would sacrifice the linearity of the model, so we do not do so here, accepting the fact that for strongly varying distributions, the harmonic and likelihood models may predict negative density distributions.
+Though the general patterns in mass placement arrived at by both the likelihood and harmonic models is accurate, the precise density distributions are inaccurate because they predict negative densities.
+This might be addressed for the likelihood model by selecting a likelihood that strongly disfavours negative densities, such as a log-normal distribution.
+A log-normal likelihood however would no longer yield a linear model, so we do not use one here, accepting the fact that the harmonic and likelihood models may predict negative density distributions for strongly varying distributions.
 
 Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the center-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
+Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
 Note that the lumpy model predicts negative density in the the edge-weighted scenario like the other two models.
-
-The lumpy model has one caveat that has not yet been illustrated, which applies for $N=d=1$ if (1) the center of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape assuming uniform density are proportional to the fitted density moments.
+This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
+
+The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ if (1) the center of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
 (1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
@@
 This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
-
-An example of this caveat applied is an elliptical lump inside a similar elliptical asteroid.
-This is why, in the center-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an ellipsoidal distribution.
+The lump model will therefore fail to recognize the lump in the true density distribution.
+
+An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
+This is why, in the center-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an a distribution that conforms to the asteroid shape.
 Thus, the caveat is avoided.
@@
 We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail completely to recover the presence or location of the lump.
-There appears to be a slight increase of density in roughly the correct location for both models, but this is not a statistically significant effect, and can be seen in other asteroid such as the center-weighted asteroid of figure \ref{fig:non-uniform-density}.
+There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect, and can be seen in other asteroid such as the center-weighted asteroid of figure \ref{fig:non-uniform-density}.
 Also like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
@@
 Nevertheless, the accuracy is still very good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
-But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analyzed here.
+But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analysed here.
 
@@
 
-We built a fast simulation for an asteroid flyby, truncating the equation at second order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
-Other studies have extracted the first-order moments from encounters, but not second order.
+We built a fast simulation for an asteroid encounter, truncating the equation at second order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
 We observe the following general properties of the moments:
@@
   \item Of the seven second-order moments, those that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
-  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a nonzero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
+  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a non-zero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
 \end{enumerate}
 
-We assessed the posterior uncertainty generated by the fit process by adjusting eleven parameters of an asteroid on an Earth flyby. The main conclusions are listed below.
+We assessed the posterior uncertainty generated by the fit process by adjusting eleven parameters of an asteroid on an Earth encounter. The main conclusions are listed below.
 
 \begin{enumerate}
-  \item Highly precise rotational velocity data is required to produce precise  moments.
+  \item Highly precise rotational velocity data is required to produce precise second-order moments.
 Especially the uncertainty on the asteroid rotational period must be small compared to the uncertainty on asteroid spin pole.
-Our reference asteroid, with $\sigma P/P = 10^{-5}$ and the spin pole known to within a few degrees of error, was accurate enough.
+Our reference asteroid, with $\sigma_P/P = 10^{-5}$ and the spin pole known to within a few degrees of error, was accurate enough.
   \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters, extending to about a third of a Lunar distance for the reference asteroid.
-  \item The asteroid rotational period must not be too small (smaller than about 5 hours, although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
-Nor must the asteroid's rotational velocity point in an inconvenient direction (orthogonal to the orbital plane, or in the orbital plane and perpendicular to the perigee vector).
-  \item The cadence of observation should be shorted than about 30 minutes (except $K_{30}$ will become unresolved for cadence worse than 10 minutes).
-Gaps of data can appear, specifically at perigee, but only for a little over an hour given 2 minute cadence before the posterior uncertainty significantly increases.
+  \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
+  \item If the asteroid rotational period is too small, the asteroid will not tumble after perigee.
+This inhibits the precise determination of $K_{2m}$, though $K_{3m}$ are largely unaffected.
+For the reference asteroid, the threshold was about 5 hours (although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
+For similar reasons, initial rotational velocities orthogonal to the orbital plane or in the plane and perpendicular to the perigee vector will yield poor-quality fits, though this effect is smaller than the effect of rotational period.
+  \item The cadence of observation should be shorter than about 30 minutes (except $K_{30}$ will become unresolved for cadence longer than 10 minutes).
+Gaps of data can appear, specifically at perigee, but only for a little over an hour given 2 minute cadence before the posterior uncertainty greatly increases.
 \end{enumerate}
+
+If some of these conditions are not met, the first-order $K_{2m}$ moments may still be resolvable.
 
@@
 The extracted density distributions largely are consistent with the true distributions in all cases we tested.
-Slight errors in $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
+Slight adjustments to $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
 Indeed, the models sometimes predict negative density (though more complicated models could be made not to).
-Errors in the shape estimate of teh asteroid also distort the density distribution.
-Nevertheless, large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
+Errors in the shape estimate of the asteroid also distort the density distribution, but the resulting distributions provide hints as to exactly where the shape is incorrect.
+Large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
 Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.
 
-In the appendices, we answer more specific questions about the behavior of the tidal torque system and the fit process that might arise.
+In the appendices, we answer more specific questions about the behaviour of the tidal torque system and the fit process that might arise.
 
@@
 
-We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin \jtd{What's Marin's last name?} for meeting with the authors to discuss this work, and pointing out possible future directions to take it.
+We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work, and pointing out possible future directions to take it.
 JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
 The work of JdW was funded by \jtd{Who funds Julien?}.
-Much of the computation shown in this paper was executed on MIT Supercloud's facilities.
+Much of the computation behind this paper was executed on MIT Supercloud's facilities.
 
@@
 \begin{enumerate}
-  \item An orbit around Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
-This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, smalley20052004}.
+  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
+This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, discovered on June 19, 2004 by R.
+A.
+Tucker, D.
+J.
+Tholen, and F.
+Bernardi.
 These orbital parameters correspond to an eccentricity of 3.88.
+The comparison to Apophis is complicated by the fact that Apophis is tumbling \cite{PRAVEC201448} and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}, and therefore is not entirely comparable to our analysis.
   \item An initial roll of $\gamma_0=\pi/8$.
@@
 
-We use the asymmetric ellipsoid in nearly all runs, do to the degeneracy induced in our model when $K_{22} = 0$.
-
-\section{The cadence cutoff}
+We use the asymmetric ellipsoid in nearly all runs, due to the degeneracy induced in our model when $K_{22} = 0$.
+
+\section{The cadence cut-off}
 \label{app:cadence-tests}
@@
 In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-We mentioned that this cadence cutoff is likely a function both of the rotational period of the asteroid and the time spent near perigee.
-We study this cutoff in closer detal in this appendix.
-
-We measure the dependence of the cadence cutoff on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
-Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference 9 hr.
-The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ and therefore irrelevant here (i.e., those studied in section \ref{sec:scan-period}), are removed.
+We mentioned that this cadence cut-off is likely a function both of the rotational period of the asteroid and the time spent near perigee.
+We study this cut-off in closer detail in this appendix.
+
+We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
+Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference $P_\omega=9$ hr.
+The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ (i.e., those studied in section \ref{sec:scan-period}), are removed; they are irrelevant here.
 
@@
   \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid colored lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
+  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
 Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
@@
 We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
-Instead, we adjust the speed at which the asteroid moves through the orbit.
+Instead, we (un-physically) manipulate the speed at which the asteroid moves through the orbit.
 In one instance, the asteroid's path is artificially slowed by a factor of 2, which we denote as $t_\text{spin}/t_\text{orbit}=0.5$; in the other instance, $t_\text{spin}/t_\text{orbit}=2$, meaning that the orbit is sped up.
@@
 Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
-However, the $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
+The $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
 
@@
   \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid colored lines), time doubling (dotted lines), and halving (dashed lines).
+  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
 See text for the definition of $t_\text{spin}/t_\text{orbit}$.
@@
 
-Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cutoff at $T_\text{cad} \sim 30-60$ min.
-Those that show no cutoff (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cutoff $T_\text{cad} > 60$ min, which is off the plot.
-By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dotted lines often (but not always) reach the cadence cutoff before the solid line.
+Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
+Those that show no cut-off (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cut-off $T_\text{cad} > 60$ min, which is off the plot.
+By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dashed lines often (but not always) reach the cadence cut-off at lower $\Delta t$ than the solid line.
 For example, in figure \ref{fig:cad-period}, this effect is especially clear for $K_{22}$, $K_{33}$, $\Im K_{22}$, and $\Re K_{31}$, but the opposite appears for $\Re K_{32}$.
-The dotted curves are significant in both figures because they represent smaller $\sigma$ cases.
-Section \ref{sec:scan-period} reveals that long-rotational-period asteroids lead to smaller $\sigma$, and $t_\text{spin}/t_\text{orbit} < 1$ leads to smaller $\sigma$ because of the presence of more perigee data.
-It therefore appears that large $P_\omega$ and large times spent at perigee move the cadence cutoff to larger $\Delta t$.
-
-The dependence of the exact location of the cadence cutoff is likely more complicated than the above analysis indicates.
-However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-speed} was) to study these regimes.
+The dashed curves are significant in both figures because they represent larger $\sigma$ cases ($P_\omega=5$ hours, or $t_\text{spin}/t_\text{orbit}=2$); section \ref{sec:scan-period} reveals that fast rotators lead to larger $\sigma$, and $t_\text{spin}/t_\text{orbit} > 1$ leads to larger $\sigma$ because of the presence of less perigee data.
+It therefore appears that small $P_\omega$ and small times spent at perigee move the cadence cut-off to smaller $T_\text{cad}$.
+
+The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
+However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-speed} is) to study these regimes.
 Computation time and random variation in $\sigma$ also limits us.
 We therefore do not attempt to explore the dependence between $T_\text{cad}$ and the encounter parameters further.
-If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence}.
-
-\section{Comparison of Jupiter and Earth flyby}
+If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence} to yield more information.
+
+\section{Comparison of Jupiter and Earth encounters}
 \label{app:jupiter-earth}
@@
 The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
-The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
+The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compare to perigee radius $r_p=5$ Earth radii for the Earth encounter).
 We perform two fits for two different values of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
@@
 Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
-The ratio between the posterior uncertainties in the Jupiter and the Earth flybys are shown in table \ref{tab:jupiter-uncertainty}.
+We therefore do not distinguish between the two cases further.
+The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
 In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
@@
 Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab-jupiter-uncertainty}.
-
-Additionally, the second-order terms are damped by an additional factor of $a_m/D$, which decreases if a massive central body is used.
+Since Jupiter is less dense than Earth, we expect that uncertainty in the first order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
+
+The second-order terms are damped by an additional factor of $a_m/D$, which decreases if a massive central body is used.
 Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
@@
 In fact, $K_{30}$ essentially fills the prior.
-The special properties of $K_{\ell 0}$ have been analyzed noted before, in that they are always more uncertain than other moments and only enter certain parts of the tidal torque equation.
-\jtd{I did note this, right?} Table \ref{tab:jupiter-uncertainty} shows that these effects strengthen when a more massive central body is used.
+The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
+In this case, the Jupiter encounter did result in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
 
@@
 Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
-However, we also mention biases that will cause more large-$a_m$ and small-$r_p$ asteroids to encounter Jupiter, and these will yield increased precision.
-Which of these contradicting effects dominates depends on the specific asteroid population near Jupiter.
+However, these selection biases will cause more large-$a_m$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
+Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
 
@@
 In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_m$ if a uniform density distribution is assumed.
-We do not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is nonlinear.
+We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.
 However, it may be a useful technique so it is mentioned here.
@@
 
-Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m^2$, and that the asteroid is ``star shaped'' in that every ray passing through the center of mass of the asteroid (the origin of the local frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
+Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m^2$, and that the asteroid is ``star shaped'' in that every ray originating from the center of mass of the asteroid (the origin of the body-fixed frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
 By the divergence theorem, we write
@@
 where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $ so that $\nabla \cdot \bm v(\bm r) = R_{\ell m}(\bm r)$.
-The integral is carried out over the surface of the asteorid.
-We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \propto \unit r$, this gives
+The integral is carried out over the surface of the asteroid.
+We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \parallel \unit r$, this gives
 \begin{equation}
@@
 To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m (\ell-m)!/(\ell+m) C_{l,-m}$.
-With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell' m'}$ and integrals of products of spherical harmonics.
+With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell m}$ and integrals of products of spherical harmonics.
 These integrals can be pre-computed so that equation \ref{eqn:surface-klm} can then be numerically solved via standard polynomial solution methods to find $C_{\ell m}$.
@@
 Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form a set of $n+1$ constraints, where $n$ is the number of density moments known.
-I.e., $n=(\ell_\text{max}+1)^2$, where $\ell_\text{max}$ is the maximum degree of $K_{\ell m}$ known.
-By setting the same maximum degree on $C_\ell m$, we also have $n$ variables plus one for $\rho_0$.
+That is, $n=(\ell_\text{max}+1)^2+1$, where $\ell_\text{max}$ is the maximum degree of $K_{\ell m}$ known.
+By setting the same maximum degree on $C_{\ell m}$, we also have $n$ variables plus one for $\rho_0$.
 The system is therefore well-determined and will yield finitely many solutions.
 These solutions can be further refined by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
-The result shapes consistent with the fitted $K_{\ell m}$.
 We do not attempt to model uncertainty on the shape.
@@
   \centering
-  \hfill
-  \includegraphics[width=0.4\textwidth]{figs/high-surface.pdf}\hfill
-  \includegraphics[width=0.4\textwidth]{figs/high-likelihood.pdf}\hfill
-  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface method.
-\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
+  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
+  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
+  \caption{\textit{Right}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface method.
+\textit{Left}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
 The same length scale is used in both figures.}
@@
 To give an alternate view of the non-sphericities found via this new surface model, figure \ref{fig:surface-density} also displays the density distribution extracted via the likelihood model assuming a spherical asteroid shape, but with the same density moments.
-(Uncertainty in the moments is not modeled in this figure, to better compare the two.) Where the likelihood model displays low density, the surface model clearly retreats into the asteroid.
+(Uncertainty in the moments is not modelled in this figure, to better compare the two.) Where the likelihood model displays low density, the surface model clearly retracts into the asteroid.
 Where the likelihood model yields high density, the surface model extends.
-Thus, the connection made in section \ref{sec:non-uniform-density} between non-uniformities in the densities of the likelihood and harmonic models at the asteroid surface and inaccuracies in the surface is more firmly represented.
-
-This surface model could, in principle, be used to improve estimates of the surface of an asteroid made by light curve analysis, since it connects rotational data to the asteroid surface.
+Thus, the connection made in section \ref{sec:spherical-density} between non-uniformities in the densities of the likelihood and harmonic models at the asteroid surface and inaccuracies in the surface is more firmly represented.
+
+This surface model could, in principle, be used to improve estimates of the surface of an asteroid made by light curve analysis, since it connects rotational data to the asteroid surface which reflects the light we observe.
 Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
@@
 
-Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to flyby data of the asymmetric reference asteroid.
+Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
 The fit results were consistent with the true density moments, and produced consistent data.
 
-Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid and the residuals in the bottom pane.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix --- i.e., 1-$\sigma$ uncertainties (correlations are not included).
+Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid in the top pane and the residuals in the bottom pane.
+Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
 
@@
   \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points, so that the fact that many residuals lie outside the band does not disqualify the fit, which has a reduced $\chi^2$ value of 0.68.}
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
   \label{fig:example-residuals}
@@
 
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, both marginalized to be a function of one variable and of two.
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, marginalized to functions of one or two variables.
 The true parameters are shown as lines.
-Note that the true parameters always lie within 1- or 2-$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+Note that the true parameters usually lie within 1- or 2-$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
 
@@
   \includegraphics[width=\textwidth]{figs/example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid with $\sigma_\theta = 9.5 \times 10^{-3}$.
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
 Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).

### 2022-04-10 paper/main.tex
Added am dependence plot

@@
 The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
+
+On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid ``radius'' $a_m$.
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_m$, defined in equation \ref{eqn:am}.
+The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
+  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid ``radius'' $a_m$.
+The reference cadence is 2 minutes.
+The red vertical lines indicate when $\sigma = 0.01$.
+The black dashed line indicates the reference value of $a_m=1000$ m.}
+  \label{fig:scan-am}
+\end{figure}
+
+As was mentioned in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_m$ since the $a_m^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_m^2$ in the moment of inertia (equation \ref{eqn:moi}).
+The $K_{3m}$ uncertainty is strongly dependent on $a_m$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_m/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
+At $a_m \lesssim 700$ m, $K_{30}$ becomes unresolved.
+The other parameters become unresolved for $a_m \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
+This $a_m$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_m)$ for low $a_m$, with an approximate functional form of $\sigma(a_m) \sim e^{(a_m/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
+(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.07$.) This sharpness indicates that the cut-off value of $a_m$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma$.
+It therefore appears that extracting precise $K_{30}$ from asteroids with $a_m \lesssim 700$ m is very unlikely with this analysis, and for $a_m \lesssim 100$ m, all $K_{3m}$ will likely be unresolved.
+
+For uniform density asteroids, large $a_m$ is equivalent to large asteroid radius, which was mentioned in section \ref{sec:moments} and explicitly shown in equation \ref{eqn:ellipsoid-axes}.
+In non-uniform density asteroids, large $a_m$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_m$ causes the density of regions distant from the asteroid center of mass to dominate $a_m$.
 

### 2022-04-11 paper/main.tex
Draft 2

--- 2022-04-07 paper/main.tex
@@
   We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary precision and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best fit precision is affected.
-Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericenter data and the central body oblateness.
+We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
+Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
+Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericentre data and the central body oblateness.
 Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
@@
 Over the past twenty years, the increase in quantity and quality of high-sensitivity, all-sky surveys has prompted the discovery of numerous asteroids.
-Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln} as well as space-based instruments such as he Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
+Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
 Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
@@
 Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
-Some examples of altered rotational velocity have recently been observed, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
+Some examples of rotational velocity altered during an encounter have recently been observed, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
 The upcoming encounter of Apophis is of particular interest and much attention has been devoted to accurate estimates of its orbital and physical properties \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis}, and in particular how its angular velocity will be affected by tidal torque \cite{souchay2014rotational, souchay2018changes}.
-Altered rotational states have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
+Altered rotational states altered by Solar tidal torque have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
 
 Such asteroid encounters have further been shown to reveal the physical properties of the encountering asteroid.
-Refs.~\cite{MOSKOVITZ2020113519, benson2020spin} extract best-fit dimensions for a triaxial ellipsoid model of Duende from light-curve data, and Refs.~\cite{DESCAMPS2020113726} and \cite{BERTHIER2020113990} extract bulk densities and rotational periods for asteroid binaries (3905) Doppler and (617) Patroclus respectively.
-
-More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the James Webb Space Telescope (JWST) or Large-aperture Synoptic Survey Telescope (LSST), and general methods for assessing whether an asteroid's encounter properties are conducive to the extraction physical asteroid characteristics from light-curve data is necessary.
-However, such general statements are not very well studied, since much of previous research has focused on specific encounters.
+Refs.~\cite{MOSKOVITZ2020113519, benson2020spin} extract best-fitting dimensions for a triaxial ellipsoid model of Duende from light-curve data, and Refs.~\cite{DESCAMPS2020113726} and \cite{BERTHIER2020113990} extract bulk densities and rotational periods for asteroid binaries (3905) Doppler and (617) Patroclus respectively.
+
+More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the James Webb Space Telescope (JWST) or Large-aperture Synoptic Survey Telescope (LSST), and general methods for assessing whether an asteroid's encounter properties are conducive to the extraction of physical asteroid characteristics from light-curve data is necessary.
+However, such general encounters are not very well studied, since much of previous research has focused on specific encounters.
 
@@
 
-Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with pericenter $r_p$ and excess velocity $v_\infty$.
-We do not consider any third-body perturbations, and we assume that the body being encountered is much more massive than the asteroid (e.g., Earth or Jupiter).
+Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with periapse $r_p$ and excess velocity $v_\infty$.
+We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
 
 We make use of two frames of reference to model this system.
-One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's center of mass.
-$\unit{X}$ points from the central body to the asteroid pericenter and $\unit{Z}$ points parallel to the orbit angular momentum.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass and each axis aligned with an asteroid principal axis.
+$\unit{X}$ points from the central body to the asteroid periapse and $\unit{Z}$ points parallel to the orbit angular momentum.
 We will assume that the mass distribution of the central body is known in this inertial frame.
@@
 Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
-This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's center of mass.
+This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's centre of mass.
 We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
@@
 
-The relative positions of the body-fixed and inertial frames is given by the position of the asteroid.
+The difference between the origins of the body-fixed and inertial frames is the position of the asteroid.
 We represent the relative orientations by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
@@
     \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid.
-Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold and uppercase).}
+Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold and uppercase).
+The origins are co-located for demonstration purposes.}
     \label{fig:euler-angles}
@@
 
-In the next section, it will be shown that only certain aspects of the asteroid density distribution affect tidal torque.
-We isolate those aspects according to parameters we call ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
+In the next section, it will be shown that only certain parameters of the asteroid density distribution affect tidal torque called ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
 The regular and irregular spherical harmonics then defined as:
@@
 \end{equation}
-These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}.
+These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which derives spherical harmonic identities useful for quantum mechanics.
 
@@
 \begin{equation}
-  K_{\ell m} = \frac{1}{\mu_m a_m^\ell} \int_\mathcal{A} d^3 r \rho_m(\bm r) R_{\ell m}(\bm r).
+  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
   \label{eqn:klm}
@@
 Note that these are complex.
-Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_m$ is the mass of the asteroid, $\rho_m(\bm r)$ is the density distribution, and $a_m$ is a real length scale defined (for reasons covered later) as
-\begin{equation}
-  a_m^2 = \frac{1}{\mu_m} \int_\mathcal{A} d^3 r \rho(\bm r) r^2.
+Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_\mathcal{A}$ is the mass of the asteroid, $\rho_\mathcal{A}(\bm r)$ is the density distribution, and $a_\mathcal{A}$ is a real length scale defined (for reasons covered later) as
+\begin{equation}
+  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2.
   \label{eqn:am}
 \end{equation}
-This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_m\sqrt{5/3} $).
+This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
 Both equations \ref{eqn:klm} and \ref{eqn:am} should be computed in the body-fixed axes.
@@
   \begin{split}
-    &J_{\ell m} = \frac{1}{\mu_M a_M^\ell} \int_\mathcal{B} d^3 r \rho_M(\bm r) R_{\ell m}(\bm r)\\
-    &a_M^2 = \frac{1}{\mu_M} \int_\mathcal{B} d^3 r \rho_M(\bm r) r^2.
+    &J_{\ell m} = \frac{1}{\mu_\mathcal{B} a_\mathcal{B}^\ell} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) R_{\ell m}(\bm r)\\
+    &a_\mathcal{B}^2 = \frac{1}{\mu_\mathcal{B}} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) r^2.
+  \end{split}
   \label{eqn:jlm}
-  \end{split}
 \end{equation}
@@
 We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
-The gravitational potential field of the asteroid can be written entirely in terms of $K_{\ell, m}$ and $a_m$, so we expect not to need any information about the density distribution of the asteroid beyond these parameters to compute tidal torque.
+The gravitational potential field of the asteroid can be written entirely in terms of $K_{\ell m}$ and $a_\mathcal{A}$, so we expect not to need any information about the density distribution of the asteroid beyond these parameters to compute tidal torque.
 
@@
 By definition, $K_{00}=1$.
-Furthermore, $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid center of mass.
-Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}=K_{2,-1} = 0$ and $\Im K_{22}=0$.
+Furthermore, $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid centre of mass.
+Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$ and the same for $m<0$.
 The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by
@@
   \begin{split}
-    I_x &= \frac{2}{3}\mu_m a_m^2 \parens{K_{20} - 6 K_{22} + 1}\\
-    I_y &= \frac{2}{3}\mu_m a_m^2 \parens{K_{20} + 6 K_{22} + 1}\\
-    I_z &= \frac{2}{3}\mu_m a_m^2 \parens{-2K_{20} + 1}.
+    I_x &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} - 6 K_{22} + 1}\\
+    I_y &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} + 6 K_{22} + 1}\\
+    I_z &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{-2K_{20} + 1}.
   \end{split}
@@
 \end{equation}
-Incidentally, the definition of $a_m$ was chosen to satisfy equation \ref{eqn:moi}.
-
-The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the axis lengths and can be compared to those found in equation \ref{eqn:moi}.
+Incidentally, the definition of $a_\mathcal{A}$ was chosen to satisfy equation \ref{eqn:moi}.
+
+The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the semi-axis lengths and can be compared to those found in equation \ref{eqn:moi}.
 This yields semi-axis lengths of
@@
   \begin{split}
-  a &= \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}+12K_{22}}\\
-  b &= \sqrt{\frac{5}{3}}a_m\sqrt{1-2K_{20}-12K_{22}}\\
-  c &= \sqrt{\frac{5}{3}}a_m\sqrt{1+4K_{20}}.
+  a &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}+12K_{22}}\\
+  b &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}-12K_{22}}\\
+  c &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1+4K_{20}}.
   \label{eqn:ellipsoid-axes}
@@
 The physical meaning of the higher-order moments $K_{3m}$ can be aided by assessing their symmetry properties.
-An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_m(x,y,z)=\rho_m(-x,y,z)$) necessarily sets certain density moments to zero.
+An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_\mathcal{A}(x,y,z)=\rho_\mathcal{A}(-x,y,z)$) necessarily sets certain density moments to zero.
 Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}.
@@
 For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$.
-Mirror symmetry along $\unit x$ means $\rho_m(x, y, z) = \rho_m(-x, y, z)$.
+Mirror symmetry along $\unit x$ means $\rho_\mathcal{A}(x, y, z) = \rho_\mathcal{A}(-x, y, z)$.
 Dashes indicate that none of the mirror symmetries zero the moment in question.
-Since $r^2>0$ for $r\neq 0$, no symmetries set $a_m=0$ either.}
+Since $r^2>0$ for $r\neq 0$, no symmetries set $a_\mathcal{A}=0$ either.}
   \label{tab:klm-symmetries}
@@
 
-We make one final observation about $K_{\ell m}$: the requirement that $\rho_m(\bm r) \geq 0$ everywhere restricts $K_{\ell m}$.
+Finally, the requirement that $\rho_\mathcal{A}(\bm r) \geq 0$ everywhere restricts $K_{\ell m}$.
 In the case of $K_{2m}$, this fact and the constraint that $I_z$ is larger than $I_x$ or $I_y$ requires $K_{20}$ and $K_{22}$ to fall in the triangle
@@
 Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
-A simple, first-order derivation is also easily computable via a power series expansion of the gravitational force of the asteroid, and the result is easily expressed in terms of the asteroid moment of inertia in the inertial frame.
+A simple, first-order derivation is also easily computable in terms of the asteroid moment of inertia in the inertial frame.
 
@@
 We also assume no third-body perturbations from other Solar System objects.
-(Actually, third-body perturbing objects are allowed if they are closer to the central body's center of mass than the asteroid perigee distance.
-Thus, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time.
-(I.e., the central body does not rotate).
+(Actually, third-body perturbing objects are allowed if they are closer to the central body's centre of mass than the asteroid perigee distance.
+Then, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body does not rotate).
 
@@
 \begin{equation}
-V(\bm R') = -G\int_\mathcal{B} d^3 R \rho_M(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
+V(\bm R') = -G\int_\mathcal{B} d^3 R \rho_\mathcal{B}(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
 \label{eqn:first-pe}
 \end{equation}
-where $\rho_M$ is the density distribution of the central body and $\mathcal{B}$ indicates the central body's volume.
+where $\rho_\mathcal{B}$ is the density distribution of the central body and $\mathcal{B}$ indicates the central body's volume.
 All vectors here are written in the inertial frame.
@@
 
-Equations \ref{eqn:first-pe} to \ref{eqn:ylm-rotation} then provide formula for $V(\bm u)$ expressed as a a sum of integrals over $\mathcal{B}$ of the central body density $\rho_M(\bm R)$ times $R_{\ell m}(\bm R)$.
+Equations \ref{eqn:first-pe} to \ref{eqn:ylm-rotation} then provide formula for $V(\bm u)$ expressed as a sum of integrals over $\mathcal{B}$ of the central body density $\rho_\mathcal{B}(\bm R)$ times $R_{\ell m}(\bm R)$.
 These are expressed via equation \ref{eqn:jlm} as $J_{\ell m}$.
@@
 \begin{equation}
-  \bm{\tau}(\bm u) = \int_\mathcal{A} d^3 u \rho_m(\bm u) (\bm u \times (-\nabla_{\bm u} V(\bm u)))
-\end{equation}
-where $\rho_m$ is the density distribution of the asteroid and $\mathcal{A}$ indicates the volume of the asteroid. Making use of one more identity concerning the derivatives of spherical harmonics:
+  \bm{\tau}(\bm u) = \int_\mathcal{A} d^3 u \rho_\mathcal{A}(\bm u) (\bm u \times (-\nabla_{\bm u} V(\bm u)))
+\end{equation}
+where $\rho_\mathcal{A}$ is the density distribution of the asteroid and $\mathcal{A}$ indicates the volume of the asteroid.
+Making use of one more identity concerning the derivatives of spherical harmonics:
 \begin{equation}
@@
 \end{equation}
-tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_m$, $a_M$, and the asteroid orientation and position. Explicitly,
+tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A}$, $a_\mathcal{B}$, and the asteroid orientation and position. Explicitly,
 \begin{equation}
   \begin{split}
-  \bm \tau = &G\frac{\mu_m\mu_M}{2}\left[\sum_{\ell, m} a_M^\ell J_{\ell m} \sum_{\ell', m'}a_m^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
-  &\left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
-  &\Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
-  &+(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg].
+  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell, m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell', m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
+  \times & \Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
+  & +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg].
   \end{split}
@@
 \end{equation}
+Some $K_{\ell m}$ terms are included in this equation with $|m|>\ell$; these should all be taken to be zero.
 
@@
 Secondly, torque is largest when $D$ is small (as expected), with the leading order of $\bm \tau$ proportional to $D^{-3}$.
-Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_M/D)^\ell (a_m/D)^{\ell'}$, the latter of which especially is small in most cases.
+Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_\mathcal{B}/D)^\ell (a_\mathcal{A}/D)^{\ell'}$, the latter of which especially is small in most cases.
 Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
@@
 
-Further insight can be gained by remarking the value of the first order of $\bm \tau$ for particular Euler angle cases.
-Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first order.
+Further insight can be gained by remarking the value of the first-order of $\bm \tau$ for particular Euler angle cases.
+Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first-order.
 Also, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
@@
 One is for $\alpha = \phi$ (or $\alpha = \pi + \phi$), where $\phi$ is the angle between the asteroid and the perigee.
-In this case, $\tau = 0$ to first order.
+In this case, $\tau = 0$ to first-order.
 The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$ and $\tau_z$ oscillates.
@@
 If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state, since $\unit z$ is a principal axis), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
-These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$, and in general we see that $|\tau_z|$ is the smallest of the torque components.
+These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$.
 
@@
 \begin{equation}
-  \dot{\bm V} = -\frac{G \mu_M}{r^3} \bm D \qquad \dot{\bm D} = \bm V
+  \dot{\bm V} = -\frac{G \mu_\mathcal{B}}{D^3} \bm D \qquad \dot{\bm D} = \bm V
   \label{eqn:pos-eom}
@@
 
-Note that equation \ref{eqn:omega-eom} is independent of $a_m$ to first order in $\bm \tau$, because $I_{j} \propto a_m^2$ for all $j$ and $\bm \tau \propto a_m^2$.
-Therefore, scaling $a_m$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
+Note that equation \ref{eqn:omega-eom} is independent of $a_\mathcal{A}$ to first-order in $\bm \tau$, because $I_{j} \propto a_\mathcal{A}^2$ for all $j$ and $\bm \tau \propto a_\mathcal{A}^2$.
+Therefore, scaling $a_\mathcal{A}$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
 
@@
 
-We built a simulation to produce angular velocity data (in the inertial frame, where it is observed from Earth) as a function of time.
-This simulation requires as input (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_M$, and radius $a_M$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid ``radius'' $a_m$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+We built a custom simulation in C++ to produce angular velocity data (in the inertial frame, where it is observed from Earth) as a function of time.
+This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid ``radius'' $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
-One can imagine that $a_m$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_m$ or else the values of $K_{\ell m}$ are degenerate with $a_m$.
+One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
 
@@
 \end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was ~100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
-This choice of $dt$ was made for the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
+The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
+The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
 
@@
 
-In this section, we discuss how the simulation presented in the previous section was used to generate synthetic data and extract posterior distributions for the density moments.
+In this section, we discuss how we used the simulation described in the previous section to generate synthetic data and extract density moment posterior distributions from the data.
 
@@
 \label{sec:fit}
-Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate posterior distributions based on flat priors.
+Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate posterior distributions from flat priors.
 We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
-Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{\ell m}$ given in section \ref{sec:moments}.
+Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
 Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to re-labeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
@@
 It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
-Walkers were initialized near this local minimum, distributed with probability given by the likelihood as determined via the inverse Hessian of the likelihood at the minimum.
+Walkers were initialized near this local minimum, distributed with probability distributed as a Gaussian approximation of the likelihood, as determined via the inverse Hessian of the likelihood at the minimum.
 Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
@@
 In practice, $f=2$ often led to success.
-The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial guess.
+The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
 
@@
 \end{equation}
-See figure \ref{fig:uncertainty-model} for a representation of the uncertainty model shown in the inertial frame.
+See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model shown in the inertial frame.
 
@@
 \end{equation}
+where $\Omega_i$ is the $i$th spin vector in the data set.
 
@@
   \includegraphics[width=0.7\linewidth]{figs/nominal-data-asym.pdf}
-  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroid densities and the reference orbit (black lines).
+  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
+The true angular velocity evolution is shown as a black line.
 Also plotted is the deviation of the data for posterior-PDF-distributed perturbations to the asteroid shape (bands).
@@
 The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
+The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) vary within the population, showing that they can be used to constrain $K_{22}$ and $K_{20}$.
 
@@
 
-Parameter precision of 1-$\sigma$ is defined such that 68.27\% of the posterior distribution lies within 1-$\sigma$ of the mean of the posterior distribution.
-2-$\sigma$ is defined likewise for 95.45\% of the posterior.
-The posteriors are usually roughly Gaussian, so that the upper and lower error bars are equal and 1-$\sigma$ is roughly the standard deviation of the posterior.
+Parameter precision of 1$\sigma$ is defined such that 68.27\% of the posterior distribution lies within 1$\sigma$ of the mean of the posterior distribution.
+2$\sigma$ is defined likewise for 95.45\% of the posterior.
+The posteriors are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the posterior.
 
@@
 A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-The orbit can be rotated to the $\unit X \unit Y$-plane by changing the density moments of the central body.
-Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant up to the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
+The orbit can be rotated to the $\unit X \unit Y$-plane, as mandated by our coordinate definitions, by changing the density moments of the central body.
+Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant until the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
 
 We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 68 and 95\% confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
+Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
 
@@
   \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
 The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
 The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
@@
 
-Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_m/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
+Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
 For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the reference 0.01 limit.
-At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second order component, becomes unresolved.
+At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
 Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
@@
 The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since it make render larger values of $r_p$ accessible to measuring $K_{3m}$.
+The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
 
@@
 Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of large $m$ corresponding to low uncertainty will be seen in the following sections as well.
+This pattern of large $m$ corresponding to low uncertainty is a general trend and will be seen in the following sections as well.
 
 The very strong dependence of $\sigma$ on $r_p$ makes this analysis only to extract second-order moments on close encounters.
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty due to their proximity.
+Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
 The first-order moments can still be extracted at much larger perigee distances in our model.
@@
 We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their ratio, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
-Indeed we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
-For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma_\theta = 1$ at this point, so that $\sigma(K_{30}) \approx 1$ which fills the prior.
+Indeed, we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
+For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma(K_{30}) \approx 1$ which fills the prior.
 Uncertainty cannot increase beyond this value.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
+  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
 The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
@@
 We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}.
-If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then we would have no dependence of $\sigma$ on $\sigma_\rho / \sigma_\theta$.
-Any dependence shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.
+If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then $\sigma$ would have no dependence on $\sigma_\rho / \sigma_\theta$.
+Any deviation from constant $\sigma$ shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.
 
@@
   \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
 The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
@@
 Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$.
-We summarize this pattern my stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
-This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I don't know enough about light curve analysis to be sure.}
-
-Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that all parameters depend on $\sigma_\theta$ and $\sigma_\rho$ in nearly the same way (at least in the data presented).
-The only differences between parameters is the overall size of $\sigma$ (which shows the same dependence on $\ell$ and $m$ mentioned previously) and the fact that $\sigma$ behaves erratically when near $\pm 1$, where it fills the prior.
-
-The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty: increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
+We summarize this pattern by stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
+This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I do not know enough about light curve analysis to be sure.}
+
+Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that $\sigma(\sigma_\rho/\sigma_\theta)$ is proportional for all $K_{\ell m}$.
+The proportionality constant shows the same dependence on $\ell$ and $m$ mentioned previously.
+The proportionality is broken near $\sigma \approx \pm 1$, where $\sigma$ fills the prior.
+
+The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty; increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
 
@@
 
-The true values of $K_{\ell m}$, $\gamma_0$, and $a_m$ affect the uncertainties in extracted density moments $\sigma$.
-Here, we only investigate the sensitivity of $\sigma$ on the first order parameters and $a_m$.
+The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the uncertainties in extracted density moments $\sigma$.
+Here, we only investigate the sensitivity of $\sigma$ to the first-order parameters and $a_\mathcal{A}$.
 The $K_{2m}$ moments can therefore also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
 
-In figure \ref{fig:scan-space-sigma}, we show the 1-$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ exactly to remove the $a_m$ dependence of equation \ref{eqn:ellipsoid-axes}.
+In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
+We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
 The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The two are uncorrelated and therefore the data has no physical dependence on $\gamma_0$ when $K_{22}=0$.
+The data then have no physical dependence on $\gamma_0$ when $K_{22}=0$.
 This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
@@
 
-  \caption{1-$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a square.}
+  \caption{1$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
   \label{fig:scan-space-sigma}
@@
 
-To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid with free parameters $K_{20}$ and $K_{30}$ only and run a fit.
+To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
 For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
-This task is beyond the scope of this paper, so we consider mostly asymmetric asteroids throughout.
+This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
 
 Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which is large axis ratios in the ellipsoid case.
+Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
 
@@
 As for the former, this correlation could likely be removed by an alternate parametrization, reducing uncertainties in the shape parameters.
-However, it is not clear whether these new parameters would have an obvious physical interpretation or whether they would be useful.
 
@@
   \caption{Correlations between parameter posteriors for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a square.}
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
   \label{fig:scan-space-corr}
@@
 
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
+Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
 It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
@@
 
+On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid ``radius'' $a_\mathcal{A}$.
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
+The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid ``radius'' $a_\mathcal{A}$.
+The reference cadence is 2 minutes.
+The red vertical lines indicate when $\sigma = 0.01$.
+The black dashed line indicates the reference value of $a_\mathcal{A}=1000$ m.}
+  \label{fig:scan-am}
+\end{figure}
+
+As was mentioned in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
+The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
+At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
+The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
+This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
+(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma$.
+It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is very unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
+
+For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius, which was mentioned in section \ref{sec:moments} and explicitly shown in equation \ref{eqn:ellipsoid-axes}.
+In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
+
 \subsection{Cadence}
@@
   \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
 The red vertical lines indicate when $\sigma = 0.01$.}
@@
 
-We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P$ and the time spent near perigee $T_p$.
-The latter can be estimated by the unitless combination
-\begin{equation}
-  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{M}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
+We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the time spent near perigee $T_p$.
+The latter can be estimated by
+\begin{equation}
+  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
   \label{eqn:tp}
@@
 The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
-For the simulated asteroid, $P = 9$ hr and $T_p = 42$ min by this definition.
-Immediately we see $T_p \approx T_\text{cad}$, but this is not necessarily significant because $T_p$ is an estimate.
-
-We further study the effect of $P$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
+For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
+
+We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
 
@@
 
-To test this, we mask the perigee of the counter by removing a duration $T$ of data from the perigee, where $T$ ranges from 0 to 3 hours.
+To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
 To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
@@
   \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
 The red vertical lines indicate when $\sigma = 0.01$.}
@@
 
-Since torque is highest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore that uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
+Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
 We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
@@
 Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$.
-They also both have cut-offs where uncertainty markedly increases, and these cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
-This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
+They also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
+This suggests that the factors that govern uncertainty due to cadence (appendix \ref{app:cadence-tests}) also may govern sensitivity to lack of data at perigee in a similar way.
 
@@
 The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-As an example, in section \ref{sec:tidal-torque}, we noted that $\bm \Omega_0 \parallel \unit Z$ leads to $\bm \tau = 0$ and therefore all parameters are unconstrained.
-
-In figure \ref{fig:scan-spin}, we display 1-$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
+
+In figure \ref{fig:scan-spin}, we display 1$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
 Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
-To highlight common features across the parameters, we also display the average 1-$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
+To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
 The average is weighted such that the uncertainty map for each parameter contributes an equal amount
@@
   \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
-  \caption{$1-\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection and shown in the inertial frame.
+  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
+All maps are made in the Mollweide projection.
 The orange star indicates the reference spin pole.
@@
   \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:spin-pole}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
+  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
 See text for a description of how the average was computed.
-Black dots indicate the locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the south pole, or $-\unit Z$}
+Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
+The polar projection is centred at the south pole, or $-\unit Z$.}
   \label{fig:scan-spin-avg}
@@
 Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
-For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first order.
+For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
 We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
@@
 
-Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \omega_0 \parallel \unit Z$ and $\bm \omega_0 \parallel \unit Y$, but not the $\unit X$ case.
+Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
 This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
 Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
-Also, $\tau_z$ is small and affected by fewer parameters than $\tau_x$ or $\tau_y$.
-Both of these are reasons why $\bm \tau \parallel z$ might inhibit precise fits to spin data.
-If $\bm \tau = 0$ to first order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters.
-
-It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \omega_0 \parallel \unit Z$ and $\bm \omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in figure \ref{fig:scan-spin-avg}.
+Also, $\tau_z$ affected by fewer parameters than $\tau_x$ or $\tau_y$.
+Both of these are reasons why $\bm \tau \parallel \unit z$ might inhibit precise fits to spin data.
+If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma$.
+
+It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma$ (figure \ref{fig:scan-spin-avg}).
 
@@
 We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma$.
-The dynamical time scales $r_p/v_\infty$ and $\mu_m / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P$ in principal may affect $\sigma$.
+The dynamical time scales $r_p/v_\infty$ and $\mu_\mathcal{B} / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P_\omega$ in principal may affect $\sigma$.
 In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
-  \caption{1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
 The reference value of 9 hr is shown as a vertical dotted line.
@@
 But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for low $P_\omega$ because these fast-rotators leave perigee tumbling very little or not at all.
-This increases uncertainty on the $K_{2m}$ parameters, which is measured by tumbling.
-
-We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, $\beta$, and which affect $\bm \tau$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and we see that each rotation has zero average first-order torque.
+$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
+This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
+
+We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and reveal that each rotation has zero average first-order torque.
 Since the first-order torque over each rotational period cancels out, there is no secular torque to force the asteroid to tumble.
@@
 The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with $P_\omega$ large do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ don't affect.
+We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
 
@@
 
-\subsection{Oblateness}
+\subsection{Central body oblateness}
 \label{sec:scan-oblateness}
@@
 In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_M \gg \mu_m$ (so that the asteroid orbit's focus is the center of mass of the central body), we have $J_{1m} = 0$.
-The effect of oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_M / D)^2$.
+By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
+The effect of central body oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_\mathcal{B} / D)^2$.
 We expect these parameters to have little effect on the asteroid.
 
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_M R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_M$ is the true radius of the body (not $a_M$ from equation \ref{eqn:jlm}).
-Note that $J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-
-For an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_M$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
+
+$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
+However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
 (Some sources such as Ref.~\cite{paterLissauer2015} take $\epsilon=J_{20}$ as their definition of $J_{20}$).
@@
 If the orbit is non-equatorial, the other $J_{2m}$ terms will be non-zero.
-Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $K_{3m}$ are all zero.
-The next order of precision after this oblateness approximation is therefore $J_{4m}$ and  non-ellipsoid corrections to the central body shape.
+Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
+The next order of precision after this oblateness approximation is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and  non-ellipsoid corrections to the central body shape.
 
 Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in figure \ref{fig:scan-oblateness}.
+These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for $\sigma(\epsilon)$.
 
@@
   \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1- and 2-$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
-Linear best fit lines to $\sigma$ (black, dotted) are plotted.
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
+Linear best-fitting lines to $\sigma$ (black, dotted) are plotted.
 \textit{Bottom}: The difference between posterior means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
@@
 
-Figure \ref{fig:scan-oblateness} (top pane) demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from the effect of other factors studied above.
+The figure demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
 Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
-The linear best-fit curves match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
-Other parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
-
-Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_M$ and $\mu_M$ will change in addition to $\epsilon$.
-These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not state that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+The best-fitting lines match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
+
+Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
+These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
 
 Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is not valid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated by assuming non-zero $\epsilon$.
+However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
 The difference between the posterior means and true parameters are shown.
 Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $|\Delta K_{\ell m}| = 0$ is not contained in the 2-$\sigma$ band.
+The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
 This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
-Therefore, accurately modelling oblateness to high precision is essential for accurate estimation of fit parameters.
+Therefore, accurately modelling central-bodyoblateness to high precision is essential for accurate estimation of fit parameters.
 For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
@@
 Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, including it in $J_{20}$.
-Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body center of mass (though the effect is not quite quadratic because $a_M$ also increases for large distances, and $J_{20}$ is divided by $a_M^2$.).
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass.
+Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body centre of mass (though the effect is not quite quadratic because $a_\mathcal{B}$ also increases for large distances, and $J_{20}$ is divided by $a_\mathcal{B}^2$).
 This process is only valid when the asteroid never passes inside the moon's orbit.
@@
 This is because only the density moments are observable by tidal torque interactions.
-However, by making assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
+However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
 
@@
 One of them can be chosen, or a fourth created, depending on what features are desired to be represented in the density distribution.
-All three of these models assume that $a_m$ and the asteroid shape is known (for example, by light curve or radar data).
+All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
 Uncertainty on this shape estimate is assumed to be small.
@@
 
-In section \ref{sec:results}, we were forced to fix $a_m$ rather than fit for it because $a_m$ is degenerate with scaling the $K_{3m}$ components.
-However, $a_m$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
+In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
+However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
 It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_m$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_m$ constraint can be removed.
+If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
 
@@
 Then in sections \ref{sec:likelihood} to \ref{sec:lumpy} we lay out each individually and compare them in section \ref{sec:density-compare}.
-In appendix \ref{app:find-surface}, we do not assume that the asteroid shape is known and instead assume that the density is constant.
+In appendix \ref{app:find-surface}, we introduce a new model which does not assume that the asteroid shape is known, instead assuming that the density is constant.
 This allows us to compute the asteroid shape from $K_{\ell m}$.
@@
 To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
-Since the asteroid rotates around its center of mass during observations, we assume that the location of the center of mass is also known in this frame, so that we can set it to be the origin.
+Since the asteroid rotates around its centre of mass during observations, we assume that the location of the centre of mass is also known in this frame, so that we can set it to be the origin.
 
@@
 The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_m$ (equal in all frames).
-
-The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_m$ at the value assumed during the fit, removing the non-linearity induced by division by $a_m$.
-Furthermore, since the system is independent of the total asteroid mass, we set $\mu_m$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
-Similarly, the form of equation \ref{eqn:am} guarantees that $a_m^2$ is linear in $\rho(\bm r)$.
-Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_m^2$ and $\mu_m$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
+
+The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit, removing the non-linearity induced by division by $a_\mathcal{A}$.
+Furthermore, since the system is independent of the total asteroid mass, we set $\mu_\mathcal{A}$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
+Similarly, the form of equation \ref{eqn:am} guarantees that $a_\mathcal{A}^2$ is linear in $\rho(\bm r)$.
+Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
 
@@
 for a $m$-dimensional vector $\bm B(\bm r)$.
-($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_m^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
+($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
 We further assume that the model describes a way to reverse this equation, to write
@@
 where $A$ is a matrix.
-Here, we have arranged $a_m^2$ and the known components of $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
+Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
 The order of this arrangement is irrelevant, as long as it is kept consistent.
@@
 
-The job of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+The purpose of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
 Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
 
-\subsection{The Likelihood model}
+\subsection{The ``likelihood'' model}
 \label{sec:likelihood}
 
-For the likelihood model, we restrict the degrees of freedom of $\rho(\bm r)$ by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
+A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
+We call this method the ``likelihood'' model.
 This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
@@
 
-Putting aside the problem of minimizing the norm for a moment, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:jlm} or \ref{eqn:am}, evaluated over the $i$th finite element.
+Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:klm} or \ref{eqn:am}, evaluated over the $i$th finite element.
 We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
@@
 
-\subsection{The Harmonic model}
+\subsection{The ``harmonic'' model}
 \label{sec:harmonic}
@@
 We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
-The expansion of such a function in spherical coordinates is given by
-\begin{equation}
-  \rho(\bm r) = \sum_{\ell, m} \frac{\Theta_{\ell m}}{a_m^\ell} R_{\ell m}^*(\bm r)
+We therefore call this model the ``harmonic'' model.
+The expansion of a harmonic function in spherical coordinates is given by
+\begin{equation}
+  \rho(\bm r) = \sum_{\ell m} \Theta_{\ell m}\frac{R_{\ell m}^*(\bm r)}{a_\mathcal{A}^\ell} 
   \label{eqn:harmonic-rho}
@@
 \begin{equation}
-  K_{\ell', m'} = \sum_{\ell m} \frac{1}{\mu_m a_m^{\ell'} a_m^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
+  K_{\ell' m'} = \sum_{\ell m} \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^{\ell'} a_\mathcal{A}^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
   \label{eqn:harmonic-mat}
@@
 \begin{equation}
-  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_m} \frac{R^{2\ell}}{a_m^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
+  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
 \end{equation}
@@
 
-\subsection{The Lumpy model}
+\subsection{The ``lumpy'' model}
 \label{sec:lumpy}
@@
 In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
-
-Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid center of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+We call this model the ``lumpy'' model.
+
+Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
 For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
 For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
-Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the center of mass of the asteroid.
-The displacement of the shape centroid from the center of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
-The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3.
+Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
+The displacement of the shape centroid from the centre of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
+The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
 The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
-These degrees of freedom should be compared to the known density moments and $a_m$, of which there are $(\ell_\text{max}+1)^2+1$.
-However, three of these are the center of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
+These degrees of freedom should be compared to the known density moments and $a_\mathcal{A}$, of which there are $(\ell_\text{max}+1)^2+1$.
+However, three of these are the centre of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
 We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
@@
 \begin{equation}
-  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_m^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
+  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_\mathcal{A}^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
   \label{eqn:klm-stack}
 \end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:jlm} and $a_m$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
-Crucially, note that we set normalizing factors $1/(\mu_m a_m^\ell)$ and $1/\mu_m$ in equations \ref{eqn:jlm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
+Crucially, note that we set normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ in equations \ref{eqn:klm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
 The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
-The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid center of mass.
-
-We can relate the primed moments to the moments calculated relative to each body's center of mass via the translation rules for solid spherical harmonics:
+The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
+
+We can relate the primed moments to the moments calculated relative to each lump's centre of mass via the translation rules for solid spherical harmonics:
 \begin{equation}
@@
   & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
-  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_m}
+  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
   \end{split}
@@
 
-Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$.
+Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$ and $a_i^2$.
 Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
-Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its center of mass and the already known surface shape.
+Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the already-known surface shape.
 
 This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
-The constraints on $\bm x_i$ and $\mu_i$ are
+The constraints on $\bm x_i$ is
 \begin{equation}
@@
 \end{equation}
-where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the center of mass.
+where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the centre of mass.
 There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-The overall mass of the asteroid is $\mu_m = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
+The overall mass of the asteroid is $\mu_\mathcal{A} = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
 The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
@@
 which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
-Then $A=M^+$ and $\bm B(\bm r)$ following from the values of $\bm x_i$ and $\mu_i$ defines the model.
+Here, $\mathds{1}$ is the identity matrix.
+Then $A=M^+$ defines the model.
+We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
 If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
@@
 First, we simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
-The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the center of the other), and a tetrahedron.
+The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), and a tetrahedron.
 We use these shapes as rough approximations of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron), but also to demonstrate the density models' efficacy on sharp corners.
@@
 Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models (which are not guaranteed exactly to reproduce the input density moments), they express the degree to which the extracted distribution cannot be represented with harmonic or lumpy distributions respectively.
+This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models, they express the degree to which the extracted moments cannot be represented with harmonic or lumpy distributions respectively.
 
@@
 From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions.
-This is generally true for uniform density asteroids.
-This similarity is a useful property because it lends confidence that the models produced are truly representative of the asteroid.
-The fact that the harmonic model produces very little density moment error ($\Delta K_{\ell m}$) also lends confidence to the distribution; the harmonic model is overdetermined and is not guaranteed to perfectly match the fit-extracted moments.
+This is generally true for uniform density asteroids, which have harmonic density distributions.
+Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
+This similarity lends confidence that the models produced are truly representative of the asteroid since they are produced via two independent methods.
 
@@
 Note that most of the asteroid has density close to one in both cases, with the factor of two reached only by small regions.
-The lumpy model yields a much more uniform distribution, but only because it is designed to produce uniform lumps.
+The lumpy model yields a much more uniform distribution, because it is designed to produce uniform lumps.
 Note that its uncertainty $\Delta K_{\ell m}$ is usually large, both because the model is severely overdetermined (it has 2 degrees of freedom) and because the lump found extends outside the asteroid, violating the assumptions of the model.
@@
 
-The symmetric and tetrahedral asteroids are less-well represented.
+The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
 In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
@@
 \subsubsection{Spherical shape test}
+\label{sec:spherical-density}
 We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and extracting density distributions assuming a spherical shape.
@@
 However, now they both produce negative density distributions for both asteroid shapes.
-(Before, only the symmetric model did.) This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
-In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top of the figure).
-The density is large at large $|y|$ (front right in the figure).
+(In the previous section, only the symmetric model did.) This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
+In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top and bottom of the figure).
+The density is large at large $|y|$ (front right and back left in the figure).
 Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
@@
 We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated around the edges.
-(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_m^2}$).
+(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_\mathcal{A}^2}$).
 To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
@@
 However, the two models do give similar results.
-Comparing the center-weighted asteroid and the edge-weighted asteroid distributions, one can see that the center-weighted case indeed places more mass in the center of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.
-
-Though the general patterns in mass placement arrived at by both the likelihood and harmonic models is accurate, the precise density distributions are inaccurate because they predict negative densities.
+Comparing the centre-weighted asteroid and the edge-weighted asteroid distributions, one can see that the centre-weighted case indeed places more mass in the centre of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.
+
+Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the precise density distributions are inaccurate because they predict negative densities.
 This might be addressed for the likelihood model by selecting a likelihood that strongly disfavours negative densities, such as a log-normal distribution.
-A log-normal likelihood however would no longer yield a linear model, so we do not use one here, accepting the fact that the harmonic and likelihood models may predict negative density distributions for strongly varying distributions.
-
-Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the center-weighted asteroid and less density for the edge-weighted asteroid, as expected.
+A log-normal likelihood however would no longer yield a linear model, so we do not use one here.
+
+Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
 Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
-Note that the lumpy model predicts negative density in the the edge-weighted scenario like the other two models.
 This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
 
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ if (1) the center of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
+The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ if (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
 (1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
@@
 An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the center-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an a distribution that conforms to the asteroid shape.
-Thus, the caveat is avoided.
+This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an a distribution that conforms to the asteroid shape.
 
@@
 
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-center lump.
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
 Density is normalized so that mean density is one.
@@
 We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail completely to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect, and can be seen in other asteroid such as the center-weighted asteroid of figure \ref{fig:non-uniform-density}.
-Also like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
+There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
 
@@
 However, the lumpy model computes the location and density of the mass very well.
-Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
+Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
 This in turn causes a 70 m inaccuracy in the lump's radius.
-Nevertheless, the accuracy is still very good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
-But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in all the other asteroid distributions analysed here.
+Nevertheless, the accuracy is still good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
+But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in the other asteroid distributions analysed here.
 
@@
 We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque (equation \ref{eqn:tidal-torque}) is a function only of the density moments of the asteroid $K_{\ell m}$, the asteroid orbit, and the initial asteroid orientation.
-This equation revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
-
-We built a fast simulation for an asteroid encounter, truncating the equation at second order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
+The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
+
+We built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
 We observe the following general properties of the moments:
 \begin{enumerate}
-  \item The second-order moments $K_{3m}$ are generally a factor of $~\frac{a_m}{r_p}$ more uncertain than the first-order moments, where $a_m$ is the asteroid radius and $r_p$ is the perigee distance.
+  \item The second-order moments $K_{3m}$ are generally a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is the asteroid radius and $r_p$ is the perigee distance.
 For our reference asteroid, this fraction was about $10^{-5}$.
   \item Of the seven second-order moments, those that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
+It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
   \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a non-zero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
@@
 Especially the uncertainty on the asteroid rotational period must be small compared to the uncertainty on asteroid spin pole.
-Our reference asteroid, with $\sigma_P/P = 10^{-5}$ and the spin pole known to within a few degrees of error, was accurate enough.
+  \item Large $a_\mathcal{A}$ is required for $K_{3m}$ resolution, though the size of $a_\mathcal{A}$ has no effect on $K_{2m}$.
+The threshold on $a_\mathcal{A}$ for the reference asteroid was $\sim$700 m for $K_{30}$ and $\sim$50 m for $K_{33}$.
   \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters, extending to about a third of a Lunar distance for the reference asteroid.
@@
 This inhibits the precise determination of $K_{2m}$, though $K_{3m}$ are largely unaffected.
-For the reference asteroid, the threshold was about 5 hours (although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
-For similar reasons, initial rotational velocities orthogonal to the orbital plane or in the plane and perpendicular to the perigee vector will yield poor-quality fits, though this effect is smaller than the effect of rotational period.
+For the reference asteroid, the threshold was about 4 hours (although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
+For similar reasons, initial rotational velocities orthogonal to the orbital plane or in the plane and perpendicular to the perigee vector will yield poor-quality fits, though the spin pole effect is smaller than the effect of rotational period.
   \item The cadence of observation should be shorter than about 30 minutes (except $K_{30}$ will become unresolved for cadence longer than 10 minutes).
@@
 
-In the appendices, we answer more specific questions about the behaviour of the tidal torque system and the fit process that might arise.
+In the appendices, we answer more specific questions that might arise about the behaviour of the tidal torque system and the fit process.
 
@@
 Except when otherwise mentioned, we use the following asteroid encounter parameters.
-Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our uncertainties have room to grow; if the reference asteroid has low uncertainty,
+Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our uncertainties have room to grow; if the reference asteroid has low uncertainty, we would not be able to measure uncertainty increases as well when the encounter parameters are adjusted.
 
@@
 These orbital parameters correspond to an eccentricity of 3.88.
-The comparison to Apophis is complicated by the fact that Apophis is tumbling \cite{PRAVEC201448} and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}, and therefore is not entirely comparable to our analysis.
+The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
+It therefore is not entirely comparable to our analysis.
   \item An initial roll of $\gamma_0=\pi/8$.
@@
   \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
-  \item An asteroid with radius $a_m = 1$ km and $K_{3m}=0$.
-For $K_{22}$ and $K_{20}$, we use two standard values.
-One with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
+  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
 Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
@@
   \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-  \caption{1-$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
+  \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
 Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
@@
 This approach of changing the speed of the orbit is meant to approximate changes to $T_p$ defined in equation \ref{eqn:tp}.
-The posterior uncertainties for these two cases and the original case are shown in figure \ref{fig:cad-speed}.
+The posterior uncertainties for these two cases and the original case are shown as a function of $\Delta t$ in figure \ref{fig:cad-speed}.
 Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
@@
   \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-  \caption{1-$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
+  \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
 See text for the definition of $t_\text{spin}/t_\text{orbit}$.
@@
 The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
-However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-speed} is) to study these regimes.
+However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-vex} is) to study these regimes.
 Computation time and random variation in $\sigma$ also limits us.
@@
 The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
-The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compare to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-We perform two fits for two different values of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
-The latter requires $v_\infty = \sqrt{G\mu_M/r_p (e-1)}=32$ km s$^{-1}$.
+The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
+We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
+The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
 The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
@@
 
-This uncertainty can be understood as follows.
-The leading order of tidal torque is proportional to $\mu_m / D^3$.
-If $D/a_M$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_M=5$), then $\mu_m / D^3 \propto \rho_M$ where $\rho_M$ is the density of the central body.
+These uncertainty ratios can be understood as follows.
+The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
+If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
 Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
-
-The second-order terms are damped by an additional factor of $a_m/D$, which decreases if a massive central body is used.
+Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
+
+The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
 Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
 
-The $K_{\ell 0}$ components violate the norm, with $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
+The $K_{\ell 0}$ components differ in that $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
 In fact, $K_{30}$ essentially fills the prior.
 The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
-In this case, the Jupiter encounter did result in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
+In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
 
 There are additional effects of central body mass which are not captured in this analysis.
-For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_m$, small $r_p$, etc.).
+For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
 The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
 \begin{equation}
-  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_M}{r_p v_\infty^2}}.
-\end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_M \sim \mu_M^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
+  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
+\end{equation}
+It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
 Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
@@
 Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
-However, these selection biases will cause more large-$a_m$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
+However, these selection biases will cause more large-$a_\mathcal{A}$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
 Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
@@
 
-In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_m$ if a uniform density distribution is assumed.
+In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
 We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.
-However, it may be a useful technique so it is mentioned here.
+However, it may be a useful technique so it is mentioned here; we call it the ``surface'' model.
 A similar model was also studied in Ref.~\cite{BAXANSKY2007756}.
 
-Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_m^2$, and that the asteroid is ``star shaped'' in that every ray originating from the center of mass of the asteroid (the origin of the body-fixed frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
+Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, and that the asteroid is ``star shaped'' in that every ray originating from the centre of mass of the asteroid (the origin of the body-fixed frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
 By the divergence theorem, we write
 \begin{equation}
-  K_{\ell m} = \frac{\rho_0}{\mu_m a_m^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
+  K_{\ell m} = \frac{\rho_0}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
 \end{equation}
@@
 The integral is carried out over the surface of the asteroid.
-We know the area element satisfies $d^2 \bm r = \partial \bm r / \partial \theta \times \partial \bm r / \partial \phi$ in our coordinates, and when dotted with $\bm v \parallel \unit r$, this gives
-\begin{equation}
-  K_{\ell m} = \frac{\rho_0 }{\mu_m a_m^\ell (3 + \ell)} \int d\Omega r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
+We know the area element satisfies $d^2 \bm r = (\partial \bm r / \partial \theta \times \partial \bm r / \partial \phi) d\theta d\phi$ in our coordinates, and when dotted with $\bm v \parallel \unit r$, this gives
+\begin{equation}
+  K_{\ell m} = \frac{\rho_0 }{\mu_\mathcal{A} a_\mathcal{A}^\ell (3 + \ell)} \int d\Omega r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
   \label{eqn:surface-klm}
@@
 without loss of generality.
-To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m (\ell-m)!/(\ell+m) C_{l,-m}$.
+To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m C_{l,-m} (\ell-m)!/(\ell+m)$.
 With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell m}$ and integrals of products of spherical harmonics.
 These integrals can be pre-computed so that equation \ref{eqn:surface-klm} can then be numerically solved via standard polynomial solution methods to find $C_{\ell m}$.
-A similar equation to equation \ref{eqn:surface-klm} can be written for $a_m$
-\begin{equation}
-  a_m^2 = \frac{\rho_0}{5\mu_m}\int d\Omega r(\theta, \phi)^5
+A similar equation to equation \ref{eqn:surface-klm} can be written for $a_\mathcal{A}$
+\begin{equation}
+  a_\mathcal{A}^2 = \frac{\rho_0}{5\mu_\mathcal{A}}\int d\Omega r(\theta, \phi)^5
   \label{eqn:surface-am}
@@
   \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
-  \caption{\textit{Right}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface method.
-\textit{Left}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
+  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model.
+\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
 The same length scale is used in both figures.}
@@
 Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
-We only suggest this as a possibility, however, since it is beyond the scope of this paper.
+We only suggest this as a possibility, however, since light-curve analysis is beyond the scope of this paper.
 
@@
 The true parameters are shown as lines.
-Note that the true parameters usually lie within 1- or 2-$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+Note that the true parameters usually lie within 1- or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
 

### 2022-04-11 data/cad-period/compile.py

@@ -109,6 +109,7 @@ def show_plot(percentiles, axs, period):
         axs[plot_index].plot(cadences, (param_data[-1]-param_data[0]) * scale, color=color, linestyle=linestyle, linewidth=2)
 
         axs[plot_index].set_ylim(-SCALE_Y, SCALE_Y)
+        axs[plot_index].set_xlim(np.min(cadences), np.max(cadences))
 
         axs[plot_index].set_ylabel(f"$\sigma({param_names[plot_index]})$", size=AXIS_SIZE)
 

### 2022-04-14 paper/appendices.tex
Ready to stage new sigma scan

--- 2022-04-11 paper/main.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-\usepackage[T1]{fontenc}
-
-\DeclareRobustCommand{\VAN}[3]{#2}
-\let\VANthebibliography\thebibliography
-\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{xcolor}
-\usepackage{tikz}
-\usepackage{colortbl}
-\usepackage{dsfont}
-\usepackage{bm}
-\usetikzlibrary{arrows.meta}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\newcommand{\jtd}[1]{ {\bf{\color{red} JTD: #1}} }
-\newcommand{\unit}[1]{\bm{\hat{#1}}}
+%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
 
-\newcommand{\parens}[1]{\left( #1 \right)}
-\newcommand{\brackets}[1]{\left[ #1 \right]}
-\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
+\appendix
 
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
+\section{Tidal torque \& Equations of motion}
+\label{app:eom}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-\title[Flyby Constraints on Asteroids Interiors]{Constraining the Interiors of Asteroids Through Close Encounters}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[Jack T. Dinsmore, Julien de Wit]{
-Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
-Julien de Wit$^{2}$
-\\
-% List of institutions
-$^{1}$Department of Physics, Massachusetts Institute of Technology\\
-$^{2}$Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2022}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-  We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
-Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericentre data and the central body oblateness.
-Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-  minor planets, asteroids: general -- methods: data analysis
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Over the past twenty years, the increase in quantity and quality of high-sensitivity, all-sky surveys has prompted the discovery of numerous asteroids.
-Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
-Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
-Light curve analysis has been performed on many of these new asteroids to study their surface properties, but analyses that are sensitive to the interior structure of the asteroid are rarer.
-
-Theoretical work has demonstrated that tidal torque alters the angular velocity of an asteroid during a gravitational encounter with another body, and that this tidal torque is sensitive to the interior density distribution of the asteroid \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-This two-body generalized system has been studied to different orders and with several different methods.
-The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015, Makarov2022ChaosOO}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}.
-Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
-Some examples of rotational velocity altered during an encounter have recently been observed, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
-The upcoming encounter of Apophis is of particular interest and much attention has been devoted to accurate estimates of its orbital and physical properties \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis}, and in particular how its angular velocity will be affected by tidal torque \cite{souchay2014rotational, souchay2018changes}.
-Altered rotational states altered by Solar tidal torque have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
-
-Such asteroid encounters have further been shown to reveal the physical properties of the encountering asteroid.
-Refs.~\cite{MOSKOVITZ2020113519, benson2020spin} extract best-fitting dimensions for a triaxial ellipsoid model of Duende from light-curve data, and Refs.~\cite{DESCAMPS2020113726} and \cite{BERTHIER2020113990} extract bulk densities and rotational periods for asteroid binaries (3905) Doppler and (617) Patroclus respectively.
-
-More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the James Webb Space Telescope (JWST) or Large-aperture Synoptic Survey Telescope (LSST), and general methods for assessing whether an asteroid's encounter properties are conducive to the extraction of physical asteroid characteristics from light-curve data is necessary.
-However, such general encounters are not very well studied, since much of previous research has focused on specific encounters.
-
-Furthermore, asteroid properties which appear in the beyond-leading-order terms of tidal torque have not yet been extracted, and more research is needed to study in what cases these effects are observable.
-
-In this paper, we address these two topics by deriving a new equation of motion for an asteroid encounter system in section \ref{sec:methods}.
-This equation is simple and exact to arbitrary order, given assumptions reasonable for a planetary encounter (and many binary asteroid systems).
-It is also fast in that it allows volume integrals over the asteroid to be pre-computed.
-We use this equation of motion to simulate a generic asteroid encounter of Earth, and extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit, described in section \ref{sec:fit}.
-We measure the uncertainties in the posterior distribution of density moments as a function of various encounter parameters such as the observational uncertainty, cadence of observation, encounter orbital parameters, and more.
-We express which parameters most affect the precision of fit results in section \ref{sec:results}.
-Finally, we propose methods to extract full density distributions with uncertainties from these density moments in section \ref{sec:distros}.
-We test the behaviour of these methods, highlight their strengths and weaknesses, and suggest ways in which they may be altered to suit the needs of the user.
-
-\section{Methods}
-\label{sec:methods}
-
-In this section, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (section \ref{sec:moments}).
-Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}), write the equations of motion for the system (section \ref{sec:eom}), and describe a simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time (section \ref{sec:sim}).
+In this appendix, we derive the equations of motion used to simulate the asteroid angular velocity during the encounter.
+In particular, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (section \ref{sec:moments}).
+Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}) and write the equations of motion for the system (section \ref{sec:eom}).
 
@@
 
-We define the density moments of an asteroid as
-\begin{equation}
-  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
-  \label{eqn:klm}
-\end{equation}
+We define the density moments of an asteroid in equation \ref{eqn:klm}.
 Note that these are complex.
-Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_\mathcal{A}$ is the mass of the asteroid, $\rho_\mathcal{A}(\bm r)$ is the density distribution, and $a_\mathcal{A}$ is a real length scale defined (for reasons covered later) as
-\begin{equation}
-  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2.
-  \label{eqn:am}
-\end{equation}
-This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
+Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_\mathcal{A}$ is the mass of the asteroid, $\rho_\mathcal{A}(\bm r)$ is the density distribution, and $a_\mathcal{A}$ is a real length scale defined in equation \ref{eqn:am}.
+This length can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
 Both equations \ref{eqn:klm} and \ref{eqn:am} should be computed in the body-fixed axes.
@@
 (Actually, third-body perturbing objects are allowed if they are closer to the central body's centre of mass than the asteroid perigee distance.
-Then, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body does not rotate).
+Then, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body's rotation is marginal compared to the timescale of the encounter).
 
@@
 \end{equation}
-tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A}$, $a_\mathcal{B}$, and the asteroid orientation and position. Explicitly,
-\begin{equation}
-  \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell, m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell', m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
-  \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
-  \times & \Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
-  & +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg].
-  \end{split}
-  \label{eqn:tidal-torque}
-\end{equation}
+tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A}$, $a_\mathcal{B}$, and the asteroid orientation and position.
+This equation is given explicitly as equation \ref{eqn:tidal-torque}.
 Some $K_{\ell m}$ terms are included in this equation with $|m|>\ell$; these should all be taken to be zero.
@@
 Therefore, scaling $a_\mathcal{A}$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
-
-\subsection{Simulation design}
-\label{sec:sim}
-
-We built a custom simulation in C++ to produce angular velocity data (in the inertial frame, where it is observed from Earth) as a function of time.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid ``radius'' $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
-All parameters except (6) are assumed to be known to high accuracy.
-One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
-
-We further assume that the asteroid is initially not tumbling.
-Thus, the rotational velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia).
-This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Thus, only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
-
-We begin our simulation at $D = 10 r_p$, with velocity predicted by Kepler's laws given by the orbital parameters.
-Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
-Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
-
-With the simulation inputs specified, the equations of motion were integrated via the Runge-Kutta fourth order method, with a variable time step
-\begin{equation}
-  dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
-\end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
-The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
-
-\section{Injection-retrieval tests}
-\label{sec:injection-retrieval}
-
-In this section, we discuss how we used the simulation described in the previous section to generate synthetic data and extract density moment posterior distributions from the data.
-
-\subsection{Fit process}
-\label{sec:fit}
-Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate posterior distributions from flat priors.
-We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
-Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
-Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to re-labeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
-The other bounds were $|K_{3m}| < 1$.
-
-The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low quality to resolve the parameters.
-$~10^4$ iterations was often required, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
-
-Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
-It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
-Walkers were initialized near this local minimum, distributed with probability distributed as a Gaussian approximation of the likelihood, as determined via the inverse Hessian of the likelihood at the minimum.
-Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
-Therefore, a simpler simulation without the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find $K_{3m}$, with $\gamma_0$ and $K_{2m}$ fixed.
-This tiered minimization process motivates us to call $\gamma_0$ and $K_{2m}$ the ``first-order parameters'' and $K_{3m}$ the ``second-order parameters.''
-
-We further subdivided the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$.
-In practice, $f=2$ often led to success.
-The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
-
-\subsection{Uncertainty model}
-\label{sec:uncertainty}
-
-We model uncertainty in each asteroid spin vector $\bm \Omega$ in the as uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
-Consider a true spin vector $\bm \Omega^*$.
-For the sake of description, we work in coordinates in which $\bm \Omega^* \parallel \unit z$.
-Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole.
-Explicitly, the probability density function (PDF) of $\rho$ is
-\begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
-\end{equation}
-See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model shown in the inertial frame.
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit X$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (1, -1.5) node[anchor=west] {$\unit Y$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
-
-  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
-  \draw[dashed] (-3, -2) -- (-3, 3);
-  \draw[dashed] (-3, -2) -- (0, 0);
-
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
-  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
-  \draw (-3, 3) arc (110:93:6);
-  \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-1, 1.8) node[anchor=center] {$\rho \Omega^*$};
-
-  \end{tikzpicture}
-  \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
-The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
-  \label{fig:uncertainty-model}
-\end{figure}
-
-The log likelihood resulting from this uncertainty model is (excluding additive constants)
-\begin{equation}
-  \begin{split}
-  \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
-  +&\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
-  \end{split}
-  \label{eqn:log-likelihood}
-\end{equation}
-where $\Omega_i$ is the $i$th spin vector in the data set.
-
-In figure \ref{fig:example-data}, we present example spin data generated via this simulation.
-A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter.
-The exact parameters used were the symmetric and asymmetric cases described in appendix \ref{app:reference-configs}.
-Bands containing 68.3\%, 95.5\%, and 99.7\% of the population's spin are shown, as is the spin of the reference asteroids in black.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.7\linewidth]{figs/nominal-data-sym.pdf}
-  \includegraphics[width=0.7\linewidth]{figs/nominal-data-asym.pdf}
-  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
-The true angular velocity evolution is shown as a black line.
-Also plotted is the deviation of the data for posterior-PDF-distributed perturbations to the asteroid shape (bands).
-Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
-  \label{fig:example-data}
-\end{figure*}
-
-To choose the initial values of $\gamma_0$, $K_{20}$, and $K_{22}$, spin data for the reference asteroids of appendix \ref{app:reference-configs} was first generated.
-Then $\gamma_0$, $K_{20}$, and $K_{22}$ were re-extracted via the fit described in section \ref{sec:fit}.
-The population's values for these parameters were posterior-distributed.
-However, the posterior distribution was widened by a factor of 1000 to make the band widths visible.
-Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
-
-The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
-The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) vary within the population, showing that they can be used to constrain $K_{22}$ and $K_{20}$.
-
-\section{Results}
-\label{sec:results}
-
-In this section, we assess the sensitivity of the posterior distributions for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations.
-Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the asteroid period, and the central body oblateness.
-These effects are presented roughly in order of how much they affect the parameter precision, from highest to lowest.
-
-Parameter precision of 1$\sigma$ is defined such that 68.27\% of the posterior distribution lies within 1$\sigma$ of the mean of the posterior distribution.
-2$\sigma$ is defined likewise for 95.45\% of the posterior.
-The posteriors are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the posterior.
-
-In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-We further present a test of how precision depends on cadence, asteroid period, and the duration of the encounter in appendix \ref{app:cadence-tests}, and we compare precision for a Jupiter and an Earth encounter in appendix \ref{app:jupiter-earth}.
-
-\subsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-The orbit can be rotated to the $\unit X \unit Y$-plane, as mandated by our coordinate definitions, by changing the density moments of the central body.
-Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant until the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
-
-We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
-The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-vex}
-\end{figure}
-
-Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also smaller-scale oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee, so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.
-This effect explains why these small-scale oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
-The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
-The dotted curve indicates a power-law fit (see text).
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-perigee}
-\end{figure}
-
-Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the reference 0.01 limit.
-At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
-Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
-The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|c}
-    \hline
-    Parameter & $\alpha$ \\ \hline
-    $\gamma_0$ & $2.05$ \\
-    $K_{22}$ & $5.47$ \\
-    $K_{20}$ & $5.47$ \\ \hline
-    $\Re K_{33}$ & $3.35$ \\
-    $\Im K_{33}$ & $3.37$ \\
-    $\Re K_{32}$ & $3.05$ \\
-    $\Im K_{32}$ & $3.27$ \\
-    $\Re K_{31}$ & $3.53$ \\
-    $\Im K_{31}$ & $4.02$ \\
-    $K_{30}$ & $5.75$ \\ \hline
-  \end{tabular}
-  \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
-  \label{tab:scan-perigee-alpha}
-\end{table}
-
-Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
-These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
-The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
-These slope values express how much each parameter is dependent on $r_p$.
-It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
-The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
-
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of large $m$ corresponding to low uncertainty is a general trend and will be seen in the following sections as well.
-
-The very strong dependence of $\sigma$ on $r_p$ makes this analysis only to extract second-order moments on close encounters.
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
-The first-order moments can still be extracted at much larger perigee distances in our model.
-
-\subsection{Observational Uncertainty}
-\label{sec:scan-uncertainty}
-There are two parameters, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}).
-Rather than explore the full space spanned by these two values, we measure how parameter uncertainties depend on the product of uncertainties $\sigma_\theta\sigma_\rho$ (with the radio fixed), and the ratio $\sigma_\rho / \sigma_\theta$ (with the product fixed).
-
-We choose these metrics because we generally expect that the parameter uncertainty $\sigma$ be proportional to the observational uncertainty, but whether the dependence is stronger on $\sigma_\theta$ or $\sigma_\rho$ is not immediately clear.
-We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their ratio, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
-Indeed, we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
-For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma(K_{30}) \approx 1$ which fills the prior.
-Uncertainty cannot increase beyond this value.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
-The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
-The red vertical lines indicate when $\sigma =0.01$.}
-  \label{fig:scan-product}
-\end{figure}
-
-We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}.
-If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then $\sigma$ would have no dependence on $\sigma_\rho / \sigma_\theta$.
-Any deviation from constant $\sigma$ shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
-The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
-The red vertical lines indicate when $\sigma = 0.01$.
-(Lines are not shown for $K_{3m}$, $m < 3$ because they coincide with the vertical axis.)}
-  \label{fig:scan-ratio}
-\end{figure}
-
-Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$.
-We summarize this pattern by stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
-This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I do not know enough about light curve analysis to be sure.}
-
-Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that $\sigma(\sigma_\rho/\sigma_\theta)$ is proportional for all $K_{\ell m}$.
-The proportionality constant shows the same dependence on $\ell$ and $m$ mentioned previously.
-The proportionality is broken near $\sigma \approx \pm 1$, where $\sigma$ fills the prior.
-
-The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty; increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
-
-\subsection{Asteroid shape}
-\label{sec:scan-shape}
-
-The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the uncertainties in extracted density moments $\sigma$.
-Here, we only investigate the sensitivity of $\sigma$ to the first-order parameters and $a_\mathcal{A}$.
-The $K_{2m}$ moments can therefore also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
-
-In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
-The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The data then have no physical dependence on $\gamma_0$ when $K_{22}=0$.
-This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
-
-\begin{figure*}
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-3-sigma.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-b-sigma.pdf}
-
-  \caption{1$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
-  \label{fig:scan-space-sigma}
-\end{figure*}
-
-To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
-For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
-This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
-
-Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
-
-Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters for reference.
-They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
-This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
-They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
-The latter is expected due to the $1/c$ dependence.
-As for the former, this correlation could likely be removed by an alternate parametrization, reducing uncertainties in the shape parameters.
-
-\begin{figure*}
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr23.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-ab.pdf}
-
-  \caption{Correlations between parameter posteriors for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
-  \label{fig:scan-space-corr}
-\end{figure*}
-
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
-It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
-The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
-
-On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid ``radius'' $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
-The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid ``radius'' $a_\mathcal{A}$.
-The reference cadence is 2 minutes.
-The red vertical lines indicate when $\sigma = 0.01$.
-The black dashed line indicates the reference value of $a_\mathcal{A}=1000$ m.}
-  \label{fig:scan-am}
-\end{figure}
-
-As was mentioned in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
-The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
-At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
-The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
-This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
-(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma$.
-It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is very unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
-
-For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius, which was mentioned in section \ref{sec:moments} and explicitly shown in equation \ref{eqn:ellipsoid-axes}.
-In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
-
-\subsection{Cadence}
-\label{sec:scan-cadence}
-
-The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-cadence}
-\end{figure}
-
-Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
-We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-We name this rough cadence limit $T_\text{cad}$.
-
-We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the time spent near perigee $T_p$.
-The latter can be estimated by
-\begin{equation}
-  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
-  \label{eqn:tp}
-\end{equation}
-which is the ratio of the perigee radius to velocity at perigee.
-The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
-For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
-
-We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is slightly exceeded).
-However, shorter cadence almost always leads to lower uncertainties.
-
-\subsection{Perigee gap}
-\label{sec:scan-gap}
-In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
-The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
-Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-There, the angular velocity evolution is dominated by torque-free precession dictated by the moment of inertia components.
-That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
-However, $K_{3m}$ are not extractable from precession data alone.
-We are therefore curious as to how our posterior uncertainties change due to lack of data during the encounter perigee.
-
-To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
-We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma$ in figure \ref{fig:observation-gap}.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:observation-gap}
-\end{figure}
-
-Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
-We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
-
-Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-On the other hand, none of the uncertainties increase noticeably for $T < 30$ min.
-Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
-
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$.
-They also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
-This suggests that the factors that govern uncertainty due to cadence (appendix \ref{app:cadence-tests}) also may govern sensitivity to lack of data at perigee in a similar way.
-
-\subsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:scan-spin}, we display 1$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
-Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
-To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
-The average is weighted such that the uncertainty map for each parameter contributes an equal amount
-(the weight of each map is set to one-tenth of the map's mean). This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
-  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection.
-The orange star indicates the reference spin pole.
-The red contours enclose regions where $\sigma \geq 0.01$.}
-  \label{fig:scan-spin}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-mollweide.pdf}
-  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
-See text for a description of how the average was computed.
-Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the south pole, or $-\unit Z$.}
-  \label{fig:scan-spin-avg}
-\end{figure*}
-
-Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
-For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
-Then, since $\bm \omega_0 \parallel \unit z$ in the body-fixed frame as an initial condition (section \ref{sec:sim}), we have that $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
-
-Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
-This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
-Also, $\tau_z$ affected by fewer parameters than $\tau_x$ or $\tau_y$.
-Both of these are reasons why $\bm \tau \parallel \unit z$ might inhibit precise fits to spin data.
-If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma$.
-
-It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma$ (figure \ref{fig:scan-spin-avg}).
-
-\subsection{Rotational period}
-\label{sec:scan-period}
-
-We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma$.
-The dynamical time scales $r_p/v_\infty$ and $\mu_\mathcal{B} / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P_\omega$ in principal may affect $\sigma$.
-In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
-The reference value of 9 hr is shown as a vertical dotted line.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-period}
-\end{figure}
-
-Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
-But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
-This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
-
-We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and reveal that each rotation has zero average first-order torque.
-Since the first-order torque over each rotational period cancels out, there is no secular torque to force the asteroid to tumble.
-However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
-This is most visible in the figure for $K_{30}$.
-The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
-
-The most severe effect of period on $\sigma$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
-The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids still have better uncertainty.
-
-\subsection{Central body oblateness}
-\label{sec:scan-oblateness}
-
-In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
-The effect of central body oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have little effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_M$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
-
-$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
-(Some sources such as Ref.~\cite{paterLissauer2015} take $\epsilon=J_{20}$ as their definition of $J_{20}$).
-For simplicity, we use this equatorial orbit case.
-If the orbit is non-equatorial, the other $J_{2m}$ terms will be non-zero.
-Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
-The next order of precision after this oblateness approximation is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and  non-ellipsoid corrections to the central body shape.
-
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for $\sigma(\epsilon)$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
-  \vfill
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
-Linear best-fitting lines to $\sigma$ (black, dotted) are plotted.
-\textit{Bottom}: The difference between posterior means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.}
-  \label{fig:scan-oblateness}
-\end{figure}
-
-The figure demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
-Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
-The best-fitting lines match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
-The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
-
-Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
-
-Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
-The difference between the posterior means and true parameters are shown.
-Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
-Therefore, accurately modelling central-bodyoblateness to high precision is essential for accurate estimation of fit parameters.
-For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
-
-Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass.
-Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body centre of mass (though the effect is not quite quadratic because $a_\mathcal{B}$ also increases for large distances, and $J_{20}$ is divided by $a_\mathcal{B}^2$).
-This process is only valid when the asteroid never passes inside the moon's orbit.
-
-As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
-Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
-
-This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
-Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
-However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
-
-\section{Density distributions}
-\label{sec:distros}
-
-Hitherto, we have only discussed the density moments $K_{\ell m}$ of the asteroid rather than the true density distribution $\rho(\bm r)$.
-This is because only the density moments are observable by tidal torque interactions.
-However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
-
-In this section, we outline three different assumptions which yield different types of density distributions for the same $K_{\ell m}$.
-One of them can be chosen, or a fourth created, depending on what features are desired to be represented in the density distribution.
-All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
-Uncertainty on this shape estimate is assumed to be small.
-The models then produce a density distribution $\rho(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho$.
-
-In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
-However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
-It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
-
-Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
-Only the differences in $\rho$ across the body are measurable.
-
-In section \ref{sec:general-density}, we describe the general form our three models must take.
-Then in sections \ref{sec:likelihood} to \ref{sec:lumpy} we lay out each individually and compare them in section \ref{sec:density-compare}.
-In appendix \ref{app:find-surface}, we introduce a new model which does not assume that the asteroid shape is known, instead assuming that the density is constant.
-This allows us to compute the asteroid shape from $K_{\ell m}$.
-
-\subsection{General density model design}
-\label{sec:general-density}
-
-To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
-Since the asteroid rotates around its centre of mass during observations, we assume that the location of the centre of mass is also known in this frame, so that we can set it to be the origin.
-
-We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
-The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame.
-The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
-
-The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit, removing the non-linearity induced by division by $a_\mathcal{A}$.
-Furthermore, since the system is independent of the total asteroid mass, we set $\mu_\mathcal{A}$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
-Similarly, the form of equation \ref{eqn:am} guarantees that $a_\mathcal{A}^2$ is linear in $\rho(\bm r)$.
-Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
-
-Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm \Theta)$ for an $m$-dimensional vector $\bm \Theta$ which contains the free parameters of $\rho$.
-We will leave the explicit definition of $\rho(\bm r, \bm \Theta)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm \Theta$; i.e.,
-\begin{equation}
-  \rho(\bm r, \bm \Theta) = \bm B(\bm r) \cdot \bm \Theta
-  \label{eqn:density-distro}
-\end{equation}
-for a $m$-dimensional vector $\bm B(\bm r)$.
-($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
-We further assume that the model describes a way to reverse this equation, to write
-\begin{equation}
-  \bm \Theta = A \bm K
-  \label{eqn:density-model}
-\end{equation}
-where $A$ is a matrix.
-Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
-The order of this arrangement is irrelevant, as long as it is kept consistent.
-
-To propagate uncertainties from $\bm K$ to $\bm \Theta$ and therefore $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
-First, assume that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
-Then
-\begin{equation}
-  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{body-fixed}.
-  \label{eqn:body-fixed-to-hybrid}
-\end{equation}
-by equation \ref{eqn:ylm-rotation}.
-Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of posterior-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
-\begin{equation}
-  \rho(\bm r) = \bm B(\bm r)^T A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
-  \label{eqn:unc-rho}
-\end{equation}
-
-The purpose of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
-Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
-
-\subsection{The ``likelihood'' model}
-\label{sec:likelihood}
-
-A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
-We call this method the ``likelihood'' model.
-This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
-The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require a Gaussian likelihood.
-
-To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
-This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
-
-We use a likelihood of 
-\begin{equation}
-  \mathcal{L}(\bm \Theta) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{\Theta_i^2}{2 \sigma^2}}
-\end{equation}
-with free parameters $\mu$ and $\sigma$.
-These parameters do not affect the location of the maximum, so we do not define them.
-Given this likelihood, the log likelihood is proportional to $-|\bm \Theta|^2$.
-Minimizing the norm of $\bm \Theta$ is therefore equivalent to finding the maximum likelihood.
-
-Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:klm} or \ref{eqn:am}, evaluated over the $i$th finite element.
-We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
-Since $m>n$, the Moore-Penrose inverse of $M$ is
-\begin{equation}
-  A=M^+ = M^*(MM^*)^{-1}
-  \label{eqn:mpi-underdetermined}
-\end{equation}
-where $M^*$ is the adjoint of $M$.
-The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
-Thus, defining $A=M^+$ also minimizes $\mathcal{L}$ and fully defines the model.
-
-Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
-
-\subsection{The ``harmonic'' model}
-\label{sec:harmonic}
-
-We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
-We therefore call this model the ``harmonic'' model.
-The expansion of a harmonic function in spherical coordinates is given by
-\begin{equation}
-  \rho(\bm r) = \sum_{\ell m} \Theta_{\ell m}\frac{R_{\ell m}^*(\bm r)}{a_\mathcal{A}^\ell} 
-  \label{eqn:harmonic-rho}
-\end{equation}
-where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $\Theta_{\ell m}$ are free (complex) parameters.
-Since $\rho$ is real, we have $\Theta_{\ell m}=(-1)^m \Theta_{\ell,-m}^*$.
-By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
-Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $\Theta_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm \Theta$.
-
-Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:klm} and \ref{eqn:am}, we get 
-\begin{equation}
-  K_{\ell' m'} = \sum_{\ell m} \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^{\ell'} a_\mathcal{A}^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
-  \label{eqn:harmonic-mat}
-\end{equation}
-This is an over-determined matrix equation $\bm K = M \bm \Theta$, where $M$ is an $n \times m$ matrix.
-The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm \Theta$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm \Theta$ is minimized).
-However, the form of the inverse changes due to the equation being overdetermined:
-\begin{equation}
-  A=M^+ = (M^*M)^{-1} M^*
-  \label{eqn:mpi-overdetermined}
-\end{equation}
-
-In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
-\begin{equation}
-  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
-\end{equation}
-A non-spherical perturbation will introduce small off-diagonal entries to $M$.
-This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
-
-\subsection{The ``lumpy'' model}
-\label{sec:lumpy}
-
-The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
-In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
-We call this model the ``lumpy'' model.
-
-Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
-For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
-For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
-Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
-The displacement of the shape centroid from the centre of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
-The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
-The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
-These degrees of freedom should be compared to the known density moments and $a_\mathcal{A}$, of which there are $(\ell_\text{max}+1)^2+1$.
-However, three of these are the centre of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
-We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
-
-\begin{table}
-  \centering
-  \begin{tabular}{cc|ccc}
-    \hline \hline
-        &  & & $N$ &  \\
-        &  & 1  & 2  & 3  \\ \hline 
-        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{gray}\color{white} 7 & \cellcolor{gray}\color{white} 12\\
-    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 13 & 21 \\
-        & 3& \cellcolor{gray}\color{white}  7 &  17 &  27 \\
-    \hline \hline
-  \end{tabular}
-  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
-The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are coloured gray.}
-  \label{tab:lump-dof}
-\end{table}
-
-The net $K_{\ell m}$ components of such an ensemble obey
-\begin{equation}
-  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_\mathcal{A}^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
-  \label{eqn:klm-stack}
-\end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
-Crucially, note that we set normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ in equations \ref{eqn:klm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
-The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
-The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
-
-We can relate the primed moments to the moments calculated relative to each lump's centre of mass via the translation rules for solid spherical harmonics:
-\begin{equation}
-  \begin{split}
-  & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
-  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
-  \end{split}
-  \label{eqn:translate-klm}
-\end{equation}
-from Ref.~\cite{Gelderen1998TheSO}.
-The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
-Here, $\mu_i$ is the added mass of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate the lump's orientation and moment of inertia ratios.
-Its volume is constrained by $a_i^2$.
-These values map directly onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
-
-Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$ and $a_i^2$.
-Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
-Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the already-known surface shape.
-
-This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
-The constraints on $\bm x_i$ is
-\begin{equation}
-  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
-  \label{eqn:lump-constraints}
-\end{equation}
-where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the centre of mass.
-There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-The overall mass of the asteroid is $\mu_\mathcal{A} = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
-The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
-The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
-We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with close solutions.
-This is done by minimizing
-\begin{equation}
-  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
-  \label{eqn:lump-minimize}
-\end{equation}
-which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
-Here, $\mathds{1}$ is the identity matrix.
-Then $A=M^+$ defines the model.
-We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
-If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
-
-\subsection{Comparisons between density models.}
-\label{sec:density-compare}
-
-To test the properties of the three density models defined above, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
-Density moments are extracted via our fit process and density distributions extracted by the three above methods.
-Below, we compare the resulting distributions to understand the performance of the extraction methods.
-
-\subsubsection{Uniform density test asteroids}
-
-First, we simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
-The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), and a tetrahedron.
-We use these shapes as rough approximations of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron), but also to demonstrate the density models' efficacy on sharp corners.
-The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
-Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models, they express the degree to which the extracted moments cannot be represented with harmonic or lumpy distributions respectively.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/db-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/db-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/db-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/tet-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/tet-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/tet-lumpy.pdf}
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The asteroid shapes are, from top to bottom, the reference asymmetric ellipsoid, the reference symmetric asteroid, the dumbbell model, and a tetrahedron.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:uniform-density}
-\end{figure*}
-
-From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions.
-This is generally true for uniform density asteroids, which have harmonic density distributions.
-Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
-This similarity lends confidence that the models produced are truly representative of the asteroid since they are produced via two independent methods.
-
-The asymmetric and dumbbell asteroids produce distributions whose non-uniformity is limited to a factor of 2 or less for the harmonic and likelihood models.
-This non-uniformity is driven by error in the estimates of the density moments.
-Note that most of the asteroid has density close to one in both cases, with the factor of two reached only by small regions.
-The lumpy model yields a much more uniform distribution, because it is designed to produce uniform lumps.
-Note that its uncertainty $\Delta K_{\ell m}$ is usually large, both because the model is severely overdetermined (it has 2 degrees of freedom) and because the lump found extends outside the asteroid, violating the assumptions of the model.
-This is a sign that the lump found does not really exist inside the asteroid.
-
-The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
-In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
-This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy in $\gamma_0$ and inflated uncertainty in the density moments.
-In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the small and ill-constrained $K_{3m}$ components.
-
-Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is consistent with uniform at most points for all models(within 1-2$\sigma$), with a small number of low-uncertainty regions that are less consistent with uniform.
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
-
-From these examples, we may draw the conclusions that all three models produce density distributions generally consistent with uniform for uniform asteroids.
-The most likely distributions (i.e., the ones shown in the figures) are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
-Asymmetric asteroids such as the dumbbell and the asymmetric reference asteroids yield the best results because they have $K_{22} \neq 0$ and therefore do not suffer from degeneracy in initial orientation.
-Finally, the lumpy model can generally be ruled out in these cases because it produces unphysical results.
-
-If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
-However, doing so ignores the observational insight we gain from our fits to $K_{3m}$, so it is only valid when $K_{3m}$ are too poorly constrained to be used.
-
-\subsubsection{Spherical shape test}
-\label{sec:spherical-density}
-We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and extracting density distributions assuming a spherical shape.
-We do this for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids.
-In both cases, the density distributions have been extracted assuming a spherical shape.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:sphere-density}
-\end{figure*}
-
-Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
-However, now they both produce negative density distributions for both asteroid shapes.
-(In the previous section, only the symmetric model did.) This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
-In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top and bottom of the figure).
-The density is large at large $|y|$ (front right and back left in the figure).
-Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
-In other words, the shape can be corrected by extending it where density is large and retracting it where density is low.
-
-A similar statement is true for the symmetric ellipsoid case in that density is low near the poles, but this time the regions with large density are evenly distributed around the equator, indicating the symmetry of the original asteroid.
-
-The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
-The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|$ for the original asteroids, making it clearly a poor model.
-
-In short, severely incorrect shape estimates can be caught for all three models by negative predicted densities or by the failure of the density distribution model to match the extracted density moments.
-The shape can be corrected by extending it where the density distribution is high and retracting it where the density distribution is low.
-
-\subsubsection{Nonuniformity test}
-\label{sec:non-uniform-density}
-
-We also test several non-uniform density asteroids and compare the generated density distributions for all three models to see if the non-uniformities are recovered.
-We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated around the edges.
-(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_\mathcal{A}^2}$).
-To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
-The extracted density distributions are shown in figure \ref{fig:non-uniform-density}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.33\textwidth]{figs/in-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/in-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/in-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/out-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/out-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/out-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:non-uniform-density}
-\end{figure*}
-
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models do give similar results.
-Comparing the centre-weighted asteroid and the edge-weighted asteroid distributions, one can see that the centre-weighted case indeed places more mass in the centre of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.
-
-Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the precise density distributions are inaccurate because they predict negative densities.
-This might be addressed for the likelihood model by selecting a likelihood that strongly disfavours negative densities, such as a log-normal distribution.
-A log-normal likelihood however would no longer yield a linear model, so we do not use one here.
-
-Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
-This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
-
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ if (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
-(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
-The lump radius will then be set to zero because the fitted density moments are already matched.
-This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
-The lump model will therefore fail to recognize the lump in the true density distribution.
-
-An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an a distribution that conforms to the asteroid shape.
-
-\subsubsection{Lump test}
-
-Finally, we test an asteroid with a discrete change in density distribution (for example, a boulder), of the kind that the lumpy model is designed to detect.
-We place a spherical mass of density six times the density of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
-The rest of the asteroid we set to uniform density.
-The density distributions found by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:blob-density}
-\end{figure*}
-
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail completely to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
-
-The failure of these models to find lumps is expected, since $K_{\ell m}$ is most sensitive to non-uniformities of characteristic size $\pi/(\ell + 1)$ radians in the polar direction, and $2\pi / (|m|+1)$ in the azimuthal direction by the definition of $Y_{\ell m}$.
-This lump is too small to be resolvable by $K_{3m}$, so we do not expect most models to find it.
-
-However, the lumpy model computes the location and density of the mass very well.
-Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
-This in turn causes a 70 m inaccuracy in the lump's radius.
-Nevertheless, the accuracy is still good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
-But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in the other asteroid distributions analysed here.
-
-\section{Conclusions}
-
-We assess the feasibility of extracting density moments and density distributions for a general asteroid encounters, and ask what encounter properties are necessary to obtain the most information about asteroid density.
-
-We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
-
-We built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
-We observe the following general properties of the moments:
-\begin{enumerate}
-  \item The second-order moments $K_{3m}$ are generally a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is the asteroid radius and $r_p$ is the perigee distance.
-For our reference asteroid, this fraction was about $10^{-5}$.
-  \item Of the seven second-order moments, those that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
-It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
-  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a non-zero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
-\end{enumerate}
-
-We assessed the posterior uncertainty generated by the fit process by adjusting eleven parameters of an asteroid on an Earth encounter. The main conclusions are listed below.
-
-\begin{enumerate}
-  \item Highly precise rotational velocity data is required to produce precise second-order moments.
-Especially the uncertainty on the asteroid rotational period must be small compared to the uncertainty on asteroid spin pole.
-  \item Large $a_\mathcal{A}$ is required for $K_{3m}$ resolution, though the size of $a_\mathcal{A}$ has no effect on $K_{2m}$.
-The threshold on $a_\mathcal{A}$ for the reference asteroid was $\sim$700 m for $K_{30}$ and $\sim$50 m for $K_{33}$.
-  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters, extending to about a third of a Lunar distance for the reference asteroid.
-  \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
-  \item If the asteroid rotational period is too small, the asteroid will not tumble after perigee.
-This inhibits the precise determination of $K_{2m}$, though $K_{3m}$ are largely unaffected.
-For the reference asteroid, the threshold was about 4 hours (although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
-For similar reasons, initial rotational velocities orthogonal to the orbital plane or in the plane and perpendicular to the perigee vector will yield poor-quality fits, though the spin pole effect is smaller than the effect of rotational period.
-  \item The cadence of observation should be shorter than about 30 minutes (except $K_{30}$ will become unresolved for cadence longer than 10 minutes).
-Gaps of data can appear, specifically at perigee, but only for a little over an hour given 2 minute cadence before the posterior uncertainty greatly increases.
-\end{enumerate}
-
-If some of these conditions are not met, the first-order $K_{2m}$ moments may still be resolvable.
-
-Finally, we present three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid as obtained by light-curve analysis.
-The extracted density distributions largely are consistent with the true distributions in all cases we tested.
-Slight adjustments to $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
-Indeed, the models sometimes predict negative density (though more complicated models could be made not to).
-Errors in the shape estimate of the asteroid also distort the density distribution, but the resulting distributions provide hints as to exactly where the shape is incorrect.
-Large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
-Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.
-
-In the appendices, we answer more specific questions that might arise about the behaviour of the tidal torque system and the fit process.
-
-\section*{Acknowledgements}
-
-We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work, and pointing out possible future directions to take it.
-JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
-The work of JdW was funded by \jtd{Who funds Julien?}.
-Much of the computation behind this paper was executed on MIT Supercloud's facilities.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-The code used to generate data, fit density moments to it, and extract density distributions from the moments is available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}, or by contacting JTD.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{mnras}
-\bibliography{asteroids.bib}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
 
@@
 \label{app:example}
-
-Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
-The fit results were consistent with the true density moments, and produced consistent data.
-
-Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid in the top pane and the residuals in the bottom pane.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
-  \label{fig:example-residuals}
-\end{figure*}
-
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, marginalized to functions of one or two variables.
-The true parameters are shown as lines.
-Note that the true parameters usually lie within 1- or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
-Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
-Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
-True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
-  \label{fig:example-corner}
-\end{figure*}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2022-04-14 paper/main.tex
Ready to stage new sigma scan

@@
 \usepackage{bm}
+
+% For the sideways figure
+\usepackage{pdflscape}
+\usepackage{afterpage}
+
 \usetikzlibrary{arrows.meta}
@@
 \begin{abstract}
+  Knowledge of the interior distribution of an asteroid can reveal its composition and constrain its evolutionary history.
+However, most observations are not sensitive to interior structure.
 We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
@@
 
-Over the past twenty years, the increase in quantity and quality of high-sensitivity, all-sky surveys has prompted the discovery of numerous asteroids.
+Over the past twenty years, the increase in quantity and quality of sensitive all-sky surveys has prompted the discovery of numerous asteroids.
 Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
 Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
-Light curve analysis has been performed on many of these new asteroids to study their surface properties, but analyses that are sensitive to the interior structure of the asteroid are rarer.
-
-Theoretical work has demonstrated that tidal torque alters the angular velocity of an asteroid during a gravitational encounter with another body, and that this tidal torque is sensitive to the interior density distribution of the asteroid \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-This two-body generalized system has been studied to different orders and with several different methods.
-The angular velocity changes induced by tidal torque occur both in asteroid binaries \cite{Naidu_2015, Makarov2022ChaosOO}, and during planetary encounters \cite{RICHARDSON199847, scheeres2004evolution}.
-Such asteroids need not be tidally disrupted for their rotation state to be perturbed by tidal torque.
-Some examples of rotational velocity altered during an encounter have recently been observed, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and have been predicted for the 2029 encounter of (99942) Apophis with Earth \cite{SCHEERES2005281, DEMARTINI201993}.
-The upcoming encounter of Apophis is of particular interest and much attention has been devoted to accurate estimates of its orbital and physical properties \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis}, and in particular how its angular velocity will be affected by tidal torque \cite{souchay2014rotational, souchay2018changes}.
+More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the Large-aperture Synoptic Survey Telescope (LSST) or global telescope networks such as the Las Cumbres Observatory (LCO).
+Light curve analysis has been performed on many of these new asteroids to study their surface properties, but observations that are sensitive to the interior structure of the asteroid are rarer.
+
+However, tidal torque acting on an asteroid and perturbing its angular velocity during an encounter presents an opportunity to constrain the asteroid mass distribution.
+Such angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus respectively.
 Altered rotational states altered by Solar tidal torque have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
 
-Such asteroid encounters have further been shown to reveal the physical properties of the encountering asteroid.
-Refs.~\cite{MOSKOVITZ2020113519, benson2020spin} extract best-fitting dimensions for a triaxial ellipsoid model of Duende from light-curve data, and Refs.~\cite{DESCAMPS2020113726} and \cite{BERTHIER2020113990} extract bulk densities and rotational periods for asteroid binaries (3905) Doppler and (617) Patroclus respectively.
-
-More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the James Webb Space Telescope (JWST) or Large-aperture Synoptic Survey Telescope (LSST), and general methods for assessing whether an asteroid's encounter properties are conducive to the extraction of physical asteroid characteristics from light-curve data is necessary.
-However, such general encounters are not very well studied, since much of previous research has focused on specific encounters.
-
-Furthermore, asteroid properties which appear in the beyond-leading-order terms of tidal torque have not yet been extracted, and more research is needed to study in what cases these effects are observable.
-
-In this paper, we address these two topics by deriving a new equation of motion for an asteroid encounter system in section \ref{sec:methods}.
-This equation is simple and exact to arbitrary order, given assumptions reasonable for a planetary encounter (and many binary asteroid systems).
-It is also fast in that it allows volume integrals over the asteroid to be pre-computed.
-We use this equation of motion to simulate a generic asteroid encounter of Earth, and extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit, described in section \ref{sec:fit}.
-We measure the uncertainties in the posterior distribution of density moments as a function of various encounter parameters such as the observational uncertainty, cadence of observation, encounter orbital parameters, and more.
-We express which parameters most affect the precision of fit results in section \ref{sec:results}.
-Finally, we propose methods to extract full density distributions with uncertainties from these density moments in section \ref{sec:distros}.
-We test the behaviour of these methods, highlight their strengths and weaknesses, and suggest ways in which they may be altered to suit the needs of the user.
+The upcoming encounter of Apophis is of particular interest and much theoretical work has been devoted to accurate estimates of its orbital and physical properties, and predictions of how its angular velocity will be affected by tidal torque \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis, souchay2014rotational, souchay2018changes}.
+This research builds on a larger body of theoretical work showing that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
+This two-body generalized system has been studied to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+The success of this work is demonstrated by the recent extraction of moment of inertia ratios for Duende \cite{MOSKOVITZ2020113519}.
+However, density distribution information beyond the moment of inertia ratios have not yet been extracted for planetary encounters.
+More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these sub-dominant terms.
+
+In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system, using , and describe a simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time (section \ref{sec:sim}).it to simulate a generic asteroid encounter of Earth.
+In section  \ref{sec:methods}, we then extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit.
+We also describe methods to extract estimates of density distribution from these density moments.
+In section \ref{sec:results}, we demonstrate our fit process and evaluate our density distribution extraction methods on density moments extracted from fits to synthetic data.
+In section \ref{sec:discussion}, we measure the uncertainties in the Posterior Probability Distribution (PPD) of density moments as a function of various encounter parameters such as the observational uncertainty, encounter orbital parameters, asteroid physical properties, and more.
 
@@
 
-In this section, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (section \ref{sec:moments}).
-Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}), write the equations of motion for the system (section \ref{sec:eom}), and describe a simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time (section \ref{sec:sim}).
-
-\subsection{Coordinates}
-\label{sec:coordinates}
-
-Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with periapse $r_p$ and excess velocity $v_\infty$.
-We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
-
-We make use of two frames of reference to model this system.
-One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass and each axis aligned with an asteroid principal axis.
-$\unit{X}$ points from the central body to the asteroid periapse and $\unit{Z}$ points parallel to the orbit angular momentum.
-We will assume that the mass distribution of the central body is known in this inertial frame.
-
-Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
-This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI.
-In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
-
-The difference between the origins of the body-fixed and inertial frames is the position of the asteroid.
-We represent the relative orientations by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
-\begin{equation}
-M = R_z(\alpha) R_y(\beta) R_z(\gamma).
-\label{eqn:euler-angles}
-\end{equation}
-Here, $R_i(\theta)$ is a rotation around the unit vector $i$ by $\theta$ (figure \ref{fig:euler-angles}).
-
-\begin{figure}
-    \centering
-    \begin{tikzpicture}
-    \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit x$};
-    \draw[-{Latex[length=3mm]}] (0, 0) -- (2, -3) node[anchor=west] {$\unit y$};
-    \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
-    \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
-    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
-    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
-    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
-    \draw[->] (0.5, -0.75) arc (290:302:2.5);
-    \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
-    \draw[->] (0, 1.2) arc (130:161:1.3);
-    \draw (-0.3, 1.3) node[anchor=center] {$\beta$};
-    \draw[->] (0.97, -0.52) arc (330:368:1.3);
-    \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0) node[anchor=west] {$\unit Y$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
-    \end{tikzpicture}
-    \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid.
-Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold and uppercase).
-The origins are co-located for demonstration purposes.}
-    \label{fig:euler-angles}
-\end{figure}
-
-\subsection{Parameters: density moments}
-\label{sec:moments}
-
-In the next section, it will be shown that only certain parameters of the asteroid density distribution affect tidal torque called ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
-The regular and irregular spherical harmonics then defined as:
+In appendix \ref{app:eom}, we derive a novel equation for the tidal torque experienced by an asteroid in a two-body system, accurate to arbitrary order.
+The equation is written in terms of the asteroid ``length''
+\begin{equation}
+  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2
+  \label{eqn:am}
+\end{equation}
+and (complex) ``density moments''
+\begin{equation}
+  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r),
+  \label{eqn:klm}
+\end{equation}
+both of which are constant and only need to be computed once to generate data.
+Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see the appendix for details).
+They produce a tidal torque of
 \begin{equation}
   \begin{split}
-    S_{\ell m}(\bm r) &= (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \\
-    R_{\ell m} (\bm r) &= (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
-  \end{split}
-\end{equation}
-These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which derives spherical harmonic identities useful for quantum mechanics.
-
-We define the density moments of an asteroid as
-\begin{equation}
-  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
-  \label{eqn:klm}
-\end{equation}
-Note that these are complex.
-Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_\mathcal{A}$ is the mass of the asteroid, $\rho_\mathcal{A}(\bm r)$ is the density distribution, and $a_\mathcal{A}$ is a real length scale defined (for reasons covered later) as
-\begin{equation}
-  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2.
-  \label{eqn:am}
-\end{equation}
-This length scale can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
-Both equations \ref{eqn:klm} and \ref{eqn:am} should be computed in the body-fixed axes.
-
-Equations \ref{eqn:klm} and \ref{eqn:am} can be extended to the central body:
-\begin{equation}
-  \begin{split}
-    &J_{\ell m} = \frac{1}{\mu_\mathcal{B} a_\mathcal{B}^\ell} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) R_{\ell m}(\bm r)\\
-    &a_\mathcal{B}^2 = \frac{1}{\mu_\mathcal{B}} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) r^2.
-  \end{split}
-  \label{eqn:jlm}
-\end{equation}
-which should be computed in the inertial axes.
-
-Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless.
-We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
-The gravitational potential field of the asteroid can be written entirely in terms of $K_{\ell m}$ and $a_\mathcal{A}$, so we expect not to need any information about the density distribution of the asteroid beyond these parameters to compute tidal torque.
-
-These moments share several key properties which we discuss before continuing.
-Firstly, for real mass density, properties of the spherical harmonics imply that $K_{\ell m} = (-1)^m K_{\ell, -m}^*$.
-Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ contains $\ell_\text{max}^2$ degrees of freedom.
-However, some of these degrees of freedom are redundant with the choice of coordinates as we discuss next.
-
-By definition, $K_{00}=1$.
-Furthermore, $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid centre of mass.
-Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$ and the same for $m<0$.
-The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by
-\begin{equation}
-  \begin{split}
-    I_x &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} - 6 K_{22} + 1}\\
-    I_y &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} + 6 K_{22} + 1}\\
-    I_z &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{-2K_{20} + 1}.
-  \end{split}
-  \label{eqn:moi}
-\end{equation}
-Incidentally, the definition of $a_\mathcal{A}$ was chosen to satisfy equation \ref{eqn:moi}.
-
-The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the semi-axis lengths and can be compared to those found in equation \ref{eqn:moi}.
-This yields semi-axis lengths of
-\begin{equation}
-  \begin{split}
-  a &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}+12K_{22}}\\
-  b &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}-12K_{22}}\\
-  c &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1+4K_{20}}.
-  \label{eqn:ellipsoid-axes}
-  \end{split}
-\end{equation}
-
-The physical meaning of the higher-order moments $K_{3m}$ can be aided by assessing their symmetry properties.
-An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_\mathcal{A}(x,y,z)=\rho_\mathcal{A}(-x,y,z)$) necessarily sets certain density moments to zero.
-Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}.
-Note that, while no mirror symmetries set $K_{00}$, $K_{20}$, or $K_{22}$ equal to zero, mirror symmetries exist which zero all the other moments, including $K_{3m}$.
-$\Re K_{32}$, $K_{31}$, and $K_{30}$ are the only $K_{3m}$ components zeroed by only one axis.
-This will not affect our fit results for $K_{3m}$, but when we compute density moments for sample distributions, we find that most $K_{3m}=0$.
-
-\begin{table}
-  \centering
-  \begin{tabular}{c|ccccccc}
-    \hline
-    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
-    0 &  &  &  &  &  &  & -\\ 
-    1 &  &  &  &  & x & y & z\\ 
-    2 &  &  & - & x,y & y,z & x,z & -\\ 
-    3 & x,z & y,z & z & x,y,z & x & y & z\\ \hline
-  \end{tabular}
-  \caption{Axes of mirror symmetry that imply zeroed density moments.
-For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$.
-Mirror symmetry along $\unit x$ means $\rho_\mathcal{A}(x, y, z) = \rho_\mathcal{A}(-x, y, z)$.
-Dashes indicate that none of the mirror symmetries zero the moment in question.
-Since $r^2>0$ for $r\neq 0$, no symmetries set $a_\mathcal{A}=0$ either.}
-  \label{tab:klm-symmetries}
-\end{table}
-
-Finally, the requirement that $\rho_\mathcal{A}(\bm r) \geq 0$ everywhere restricts $K_{\ell m}$.
-In the case of $K_{2m}$, this fact and the constraint that $I_z$ is larger than $I_x$ or $I_y$ requires $K_{20}$ and $K_{22}$ to fall in the triangle
-\begin{equation}
-  -\frac{1}{4} \leq K_{20} \leq 0, \qquad |K_{22}| \leq -\frac{K_{20}}{2}.
-  \label{eqn:parameter-bounds}
-\end{equation}
-In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
-For the rest of this paper, we therefore treat an uncertainty on $|K_{3m}|$ of $0.01$ or less as a practical limit on observability, in that uncertainty greater than 0.01 means $K_{3m}$ are effectively unknown.
-This is only a rough estimate, however.
-
-\subsection{Tidal torque}
-\label{sec:tidal-torque}
-
-Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
-A simple, first-order derivation is also easily computable in terms of the asteroid moment of inertia in the inertial frame.
-
-Here, we present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
-These density moments can be pre-computed and do not have to be re-evaluated every time-step.
-
-Throughout this paper, we assume that the asteroid remains rigid throughout the encounter.
-We also assume no third-body perturbations from other Solar System objects.
-(Actually, third-body perturbing objects are allowed if they are closer to the central body's centre of mass than the asteroid perigee distance.
-Then, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body does not rotate).
-
-The gravitational potential energy of the central body is, in its most general form,
-\begin{equation}
-V(\bm R') = -G\int_\mathcal{B} d^3 R \rho_\mathcal{B}(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
-\label{eqn:first-pe}
-\end{equation}
-where $\rho_\mathcal{B}$ is the density distribution of the central body and $\mathcal{B}$ indicates the central body's volume.
-All vectors here are written in the inertial frame.
-Given $|\bm{R}| < |\bm{R'}|$, Ref.~\cite{Gelderen1998TheSO} gives the identity
-\begin{equation}
-  \frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
-  \label{eqn:ylm-expansion}
-\end{equation}
-where the sum is shorthand for $\sum_{\ell, m} = \sum_{\ell = 0}^\infty \sum_{m=-\ell}^\ell$.
-We are interested in translating the potential energy of equation \ref{eqn:first-pe} to the body-fixed frame.
-To do this, we let $\bm{R'} = \bm D + \bm U$, where $\bm D$ is the location of the asteroid in the inertial frame.
-We further define $\bm U = M\bm u$, where $\bm u$ is in the body-fixed frame and $M$ is the rotation matrix given by the Euler angles $\alpha$, $\beta$, and $\gamma$ (see section \ref{sec:coordinates}).
-The translation from $\bm {R'}$ to $\bm U$ is then attained by the identity
-\begin{equation}
-  S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D),
-  \label{eqn:ylm-translation}
-\end{equation}  
-provided by Ref.~\cite{Gelderen1998TheSO}, and from $\bm U$ to $\bm u$ is given by
-\begin{equation}
-  \begin{split}
-    Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell & (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \\
-    & \times \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).\\
-  \end{split}
-  \label{eqn:ylm-rotation}
-\end{equation}
-Here, $\mathcal{D}^\ell_{mm'}(M)$ are the Wigner-$D$ matrices, which are determined by the Euler angles $\alpha$, $\beta$, and $\gamma$ of $M$.
-
-Equations \ref{eqn:first-pe} to \ref{eqn:ylm-rotation} then provide formula for $V(\bm u)$ expressed as a sum of integrals over $\mathcal{B}$ of the central body density $\rho_\mathcal{B}(\bm R)$ times $R_{\ell m}(\bm R)$.
-These are expressed via equation \ref{eqn:jlm} as $J_{\ell m}$.
-
-The tidal torque experienced by the asteroid (in the body-fixed frame) is given by
-\begin{equation}
-  \bm{\tau}(\bm u) = \int_\mathcal{A} d^3 u \rho_\mathcal{A}(\bm u) (\bm u \times (-\nabla_{\bm u} V(\bm u)))
-\end{equation}
-where $\rho_\mathcal{A}$ is the density distribution of the asteroid and $\mathcal{A}$ indicates the volume of the asteroid.
-Making use of one more identity concerning the derivatives of spherical harmonics:
-\begin{equation}
-  \begin{split}
-  \bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}\Big[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
-  &+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)\\
-  & +2im\unit z R_{\ell m}(\bm u)\Big],
-  \end{split}
-\end{equation}
-tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A}$, $a_\mathcal{B}$, and the asteroid orientation and position. Explicitly,
-\begin{equation}
-  \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell, m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell', m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
   \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
   \times & \Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
-  & +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg].
+  & +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg],
   \end{split}
@@
 \end{equation}
-Some $K_{\ell m}$ terms are included in this equation with $|m|>\ell$; these should all be taken to be zero.
-
-Equation \ref{eqn:tidal-torque} possesses a few explicit properties which we discuss before writing the asteroid equations of motion.
-Firstly, $K_{00}$ does not appear, so that $\bm \tau$ is independent of asteroid mass.
-The mean density of the asteroid is therefore not constrained by tidal torque analysis.
-Secondly, torque is largest when $D$ is small (as expected), with the leading order of $\bm \tau$ proportional to $D^{-3}$.
-Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_\mathcal{B}/D)^\ell (a_\mathcal{A}/D)^{\ell'}$, the latter of which especially is small in most cases.
-Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
-For our analysis, we remove $\ell' > 3$ and we usually keep only $\ell=0$.
-Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
-
-Further insight can be gained by remarking the value of the first-order of $\bm \tau$ for particular Euler angle cases.
-Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first-order.
-Also, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
-
-For $\beta = \pi/2$, there are two interesting cases.
-One is for $\alpha = \phi$ (or $\alpha = \pi + \phi$), where $\phi$ is the angle between the asteroid and the perigee.
-In this case, $\tau = 0$ to first-order.
-The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$ and $\tau_z$ oscillates.
-At perigee ($\phi=0$), these conditions are equivalent to $\unit z \parallel \unit X$ and $\unit z \parallel \unit Y$ respectively.
-
-The $\bm \tau \parallel \unit z$ cases are interesting because they do not induce tumbling.
-If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state, since $\unit z$ is a principal axis), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
-These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$.
-
-\subsection{Equations of motion}
-\label{sec:eom}
-
-The equations of motion of the asteroid position $\bm D$ are given by Newton's law of gravitation:
-\begin{equation}
-  \dot{\bm V} = -\frac{G \mu_\mathcal{B}}{D^3} \bm D \qquad \dot{\bm D} = \bm V
-  \label{eqn:pos-eom}
-\end{equation}
-Rather than derive equations of motion for the Euler angles (which suffer from gimbal lock), we instead represent the orientation of the asteroid with a quaternion $\quat q$ which can be converted into Euler angles to compute $\mathcal{D}(\alpha, \beta, \gamma)$.
-This quaternion evolves as
-\begin{equation}
-  \dot{\quat q} = \frac{1}{2}\quat q\quat \omega.
-  \label{eqn:quat-eom}
-\end{equation}
-for angular velocity $\bm \omega$ given in the body-fixed frame. The equations of motion of $\bm \omega$ in turn are given by
-\begin{equation}
-  \begin{split}
-    I_x \dot \omega_1 - \omega_y \omega_z (I_y - I_z) &= \tau_x\\
-    I_y \dot \omega_2 - \omega_z \omega_x (I_z - I_x) &= \tau_y\\
-    I_z \dot \omega_3 - \omega_x \omega_y (I_x - I_y) &= \tau_z.
-  \end{split}
-  \label{eqn:omega-eom}
-\end{equation}
-Equations \ref{eqn:tidal-torque} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
-They are expressed in terms of the constant physical parameters $\mu_{M/m}$, $a_{M/m}$, $J_{\ell m}$ and $K_{\ell m}$ given the density moment-moment of inertia relations given by equation \ref{eqn:moi}.
-
-Note that equation \ref{eqn:omega-eom} is independent of $a_\mathcal{A}$ to first-order in $\bm \tau$, because $I_{j} \propto a_\mathcal{A}^2$ for all $j$ and $\bm \tau \propto a_\mathcal{A}^2$.
-Therefore, scaling $a_\mathcal{A}$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are Euler angles expressing the orientation of the asteroid; and  $\mu_\mathcal{B}$ and $J_{\ell m}$ are the mass and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+
+In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion and ins section
 
@@
 
-We built a custom simulation in C++ to produce angular velocity data (in the inertial frame, where it is observed from Earth) as a function of time.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid ``radius'' $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+We built a custom simulation in C++ to produce angular velocity data as a function of time.
+This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
@@
 
-With the simulation inputs specified, the equations of motion were integrated via the Runge-Kutta fourth order method, with a variable time step
+With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step
 \begin{equation}
@@
 
-\section{Injection-retrieval tests}
-\label{sec:injection-retrieval}
-
-In this section, we discuss how we used the simulation described in the previous section to generate synthetic data and extract density moment posterior distributions from the data.
+\subsection{Uncertainty model}
+\label{sec:uncertainty}
+
+To add noise to data generated via the above simulation, we use the following uncertainty model.
+Each asteroid spin vector $\bm \Omega$ is assumed to be uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
+Consider a true spin vector $\bm \Omega^*$.
+For the sake of description, we work in coordinates in which $\bm \Omega^* \parallel \unit z$.
+Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
+We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
+We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole.
+Explicitly, the probability density function (PDF) of $\rho$ is
+\begin{equation}
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
+\end{equation}
+See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model.
+
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit X$};
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (1, -1.5) node[anchor=west] {$\unit Y$};
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
+
+  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
+  \draw[dashed] (-3, -2) -- (-3, 3);
+  \draw[dashed] (-3, -2) -- (0, 0);
+
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
+  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
+  \draw (-3, 3) arc (110:93:6);
+  \draw (-2, 3.5) node[anchor=center] {$\theta$};
+  \draw (-1, 1.8) node[anchor=center] {$\rho \Omega^*$};
+
+  \end{tikzpicture}
+  \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
+The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
+  \label{fig:uncertainty-model}
+\end{figure}
+
+The log likelihood resulting from this uncertainty model is (excluding additive constants)
+\begin{equation}
+  \begin{split}
+  \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
+  +&\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
+  \end{split}
+  \label{eqn:log-likelihood}
+\end{equation}
+where $\Omega_i$ is the $i$th spin vector in the data set.
+
+This model was chosen because it separates spin pole and period uncertainty.
+Therefore, if one is more precisely determined by measurement, $\sigma_\theta$ and $\sigma_\rho$ can be adjusted separately in accordance.
 
@@
 \label{sec:fit}
-Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate posterior distributions from flat priors.
+Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate PPDs from flat priors.
 We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
@@
 The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low quality to resolve the parameters.
-$~10^4$ iterations was often required, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
+$~10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
 
@@
 
-\subsection{Uncertainty model}
-\label{sec:uncertainty}
-
-We model uncertainty in each asteroid spin vector $\bm \Omega$ in the as uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
-Consider a true spin vector $\bm \Omega^*$.
-For the sake of description, we work in coordinates in which $\bm \Omega^* \parallel \unit z$.
-Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole.
-Explicitly, the probability density function (PDF) of $\rho$ is
-\begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
-\end{equation}
-See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model shown in the inertial frame.
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit X$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (1, -1.5) node[anchor=west] {$\unit Y$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
-
-  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
-  \draw[dashed] (-3, -2) -- (-3, 3);
-  \draw[dashed] (-3, -2) -- (0, 0);
-
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
-  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
-  \draw (-3, 3) arc (110:93:6);
-  \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-1, 1.8) node[anchor=center] {$\rho \Omega^*$};
-
-  \end{tikzpicture}
-  \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
-The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
-  \label{fig:uncertainty-model}
-\end{figure}
-
-The log likelihood resulting from this uncertainty model is (excluding additive constants)
-\begin{equation}
-  \begin{split}
-  \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
-  +&\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
-  \end{split}
-  \label{eqn:log-likelihood}
-\end{equation}
-where $\Omega_i$ is the $i$th spin vector in the data set.
-
-In figure \ref{fig:example-data}, we present example spin data generated via this simulation.
+\section{Results}
+\label{sec:results}
+
+\subsection{Spin evolution}
+
+In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
 A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter.
@@
 The true angular velocity evolution is shown as a black line.
-Also plotted is the deviation of the data for posterior-PDF-distributed perturbations to the asteroid shape (bands).
+Also plotted is the deviation of the data for PPD-distributed perturbations to the asteroid shape (bands).
 Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
+  \label{fig:example-residuals}
+\end{figure*}
+
 To choose the initial values of $\gamma_0$, $K_{20}$, and $K_{22}$, spin data for the reference asteroids of appendix \ref{app:reference-configs} was first generated.
 Then $\gamma_0$, $K_{20}$, and $K_{22}$ were re-extracted via the fit described in section \ref{sec:fit}.
-The population's values for these parameters were posterior-distributed.
-However, the posterior distribution was widened by a factor of 1000 to make the band widths visible.
+The population's values for these parameters were PPD-distributed.
+However, the PPD distribution was widened by a factor of 1000 to make the band widths visible.
 Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
@@
 
-\section{Results}
-\label{sec:results}
-
-In this section, we assess the sensitivity of the posterior distributions for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations.
+\subsection{Example fit results}
+
+Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
+The fit results were consistent with the true density moments, and produced consistent data.
+
+Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid in the top pane and the residuals in the bottom pane.
+Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
+
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, marginalized to functions of one or two variables.
+The true parameters are shown as lines.
+Note that the true parameters usually lie within 1- or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
+Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
+Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
+True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
+  \label{fig:example-corner}
+\end{figure*}
+
+\subsection{Density stuff?}
+
+\section{Discussion}
+\label{sec:discussion}
+
+% \afterpage{
+%   \begin{landscape}
+%     \begin{figure}
+%     \centering
+%     \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
+%     \caption{caption}
+%     \label{fig:label}
+%     \end{figure}
+%   \end{landscape}
+% }
+% PLOTS THAT COULD BE HERE
+% rp
+% vp
+
+In this section, we assess the sensitivity of the PPDs for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations.
 Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the asteroid period, and the central body oblateness.
@@
 
-Parameter precision of 1$\sigma$ is defined such that 68.27\% of the posterior distribution lies within 1$\sigma$ of the mean of the posterior distribution.
-2$\sigma$ is defined likewise for 95.45\% of the posterior.
-The posteriors are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the posterior.
+Parameter precision of 1$\sigma$ is defined such that 68.27\% of the PPD lies within 1$\sigma$ of the mean of the PPD.
+2$\sigma$ is defined likewise for 95.45\% of the PPD.
+The PPDs are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the PPD.
 
@@
   \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
 The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
 The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
+  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
 The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
 The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
@@
   \caption{1$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
   \label{fig:scan-space-sigma}
@@
 
-  \caption{Correlations between parameter posteriors for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a circle and the asymmetric with a star.}
+  \caption{Correlations between PPDs for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
   \label{fig:scan-space-corr}
@@
 
-On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid ``radius'' $a_\mathcal{A}$.
+On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
 Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid ``radius'' $a_\mathcal{A}$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid length $a_\mathcal{A}$.
 The reference cadence is 2 minutes.
@@
   \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
 The red vertical lines indicate when $\sigma = 0.01$.}
@@
   \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
 The red vertical lines indicate when $\sigma = 0.01$.}
@@
   \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
 The reference value of 9 hr is shown as a vertical dotted line.
@@
   \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter posteriors as a function of oblateness $\epsilon$ .
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
 Linear best-fitting lines to $\sigma$ (black, dotted) are plotted.
-\textit{Bottom}: The difference between posterior means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
+\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
 Also shown in both figures are the oblatenesses of reference Solar System bodies.}
@@
 This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
-The difference between the posterior means and true parameters are shown.
+The difference between the PPD means and true parameters are shown.
 Posterior uncertainties are also shown as bands.
@@
 This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
-Therefore, accurately modelling central-bodyoblateness to high precision is essential for accurate estimation of fit parameters.
+Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
 For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
@@
 by equation \ref{eqn:ylm-rotation}.
-Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of posterior-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
+Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
 Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
@@
 JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
-The work of JdW was funded by \jtd{Who funds Julien?}.
 Much of the computation behind this paper was executed on MIT Supercloud's facilities.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Reference asteroid configurations}
-\label{app:reference-configs}
-
-Except when otherwise mentioned, we use the following asteroid encounter parameters.
-Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our uncertainties have room to grow; if the reference asteroid has low uncertainty, we would not be able to measure uncertainty increases as well when the encounter parameters are adjusted.
-
-\begin{enumerate}
-  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
-This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, discovered on June 19, 2004 by R.
-A.
-Tucker, D.
-J.
-Tholen, and F.
-Bernardi.
-These orbital parameters correspond to an eccentricity of 3.88.
-The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
-It therefore is not entirely comparable to our analysis.
-  \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho / \sigma_\theta = 10^{-5}$.
-  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
-  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
-For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
-The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
-The second case and its reflection are called the asymmetric cases.
-Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
-If not specified, we use the $a < b$ case.
-Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
-\end{enumerate}
-
-We use the asymmetric ellipsoid in nearly all runs, due to the degeneracy induced in our model when $K_{22} = 0$.
-
-\section{The cadence cut-off}
-\label{app:cadence-tests}
-
-In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-We mentioned that this cadence cut-off is likely a function both of the rotational period of the asteroid and the time spent near perigee.
-We study this cut-off in closer detail in this appendix.
-
-We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
-Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference $P_\omega=9$ hr.
-The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ (i.e., those studied in section \ref{sec:scan-period}), are removed; they are irrelevant here.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-  \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-  \label{fig:cad-period}
-\end{figure}
-
-We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
-Instead, we (un-physically) manipulate the speed at which the asteroid moves through the orbit.
-In one instance, the asteroid's path is artificially slowed by a factor of 2, which we denote as $t_\text{spin}/t_\text{orbit}=0.5$; in the other instance, $t_\text{spin}/t_\text{orbit}=2$, meaning that the orbit is sped up.
-This approach of changing the speed of the orbit is meant to approximate changes to $T_p$ defined in equation \ref{eqn:tp}.
-The posterior uncertainties for these two cases and the original case are shown as a function of $\Delta t$ in figure \ref{fig:cad-speed}.
-Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
-The $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-  \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
-See text for the definition of $t_\text{spin}/t_\text{orbit}$.
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-  \label{fig:cad-speed}
-\end{figure}
-
-Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
-Those that show no cut-off (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cut-off $T_\text{cad} > 60$ min, which is off the plot.
-By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dashed lines often (but not always) reach the cadence cut-off at lower $\Delta t$ than the solid line.
-For example, in figure \ref{fig:cad-period}, this effect is especially clear for $K_{22}$, $K_{33}$, $\Im K_{22}$, and $\Re K_{31}$, but the opposite appears for $\Re K_{32}$.
-The dashed curves are significant in both figures because they represent larger $\sigma$ cases ($P_\omega=5$ hours, or $t_\text{spin}/t_\text{orbit}=2$); section \ref{sec:scan-period} reveals that fast rotators lead to larger $\sigma$, and $t_\text{spin}/t_\text{orbit} > 1$ leads to larger $\sigma$ because of the presence of less perigee data.
-It therefore appears that small $P_\omega$ and small times spent at perigee move the cadence cut-off to smaller $T_\text{cad}$.
-
-The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
-However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-vex} is) to study these regimes.
-Computation time and random variation in $\sigma$ also limits us.
-We therefore do not attempt to explore the dependence between $T_\text{cad}$ and the encounter parameters further.
-If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence} to yield more information.
-
-\section{Comparison of Jupiter and Earth encounters}
-\label{app:jupiter-earth}
-
-If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
-In this appendix, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
-
-The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
-The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
-The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
-The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
-
-Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
-We therefore do not distinguish between the two cases further.
-The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
-In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
-
-\begin{table}
-  \centering
-  \begin{tabular}{c|cc}
-    \hline 
-    $K_{\ell m}$ & $\sigma_\text{Jupiter}/\sigma_\text{Earth}$\\ \hline 
-    $\gamma_0$ & 1.6 \\
-    $K_{22}$ & 2.3 \\
-    $K_{20}$ & 11 \\
-    $\Re K_{33}$ & 18 \\
-    $\Im K_{33}$ & 18 \\
-    $\Re K_{32}$ & 18 \\
-    $\Im K_{32}$ & 18 \\
-    $\Re K_{31}$ & 25 \\
-    $\Im K_{31}$ & 10 \\
-    $K_{30}$ & 53 \\ \hline
-  \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
-  \label{tab:jupiter-uncertainty}
-\end{table}
-
-These uncertainty ratios can be understood as follows.
-The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
-If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
-Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
-
-The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
-Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
-
-The $K_{\ell 0}$ components differ in that $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
-In fact, $K_{30}$ essentially fills the prior.
-The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
-In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
-
-There are additional effects of central body mass which are not captured in this analysis.
-For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
-The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
-\begin{equation}
-  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
-\end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
-Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
-
-Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
-However, these selection biases will cause more large-$a_\mathcal{A}$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
-Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
-
-\section{Computing asteroid shape from density moments}
-\label{app:find-surface}
-
-In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
-We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.
-However, it may be a useful technique so it is mentioned here; we call it the ``surface'' model.
-A similar model was also studied in Ref.~\cite{BAXANSKY2007756}.
-
-Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, and that the asteroid is ``star shaped'' in that every ray originating from the centre of mass of the asteroid (the origin of the body-fixed frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
-By the divergence theorem, we write
-\begin{equation}
-  K_{\ell m} = \frac{\rho_0}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
-\end{equation}
-where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $ so that $\nabla \cdot \bm v(\bm r) = R_{\ell m}(\bm r)$.
-The integral is carried out over the surface of the asteroid.
-We know the area element satisfies $d^2 \bm r = (\partial \bm r / \partial \theta \times \partial \bm r / \partial \phi) d\theta d\phi$ in our coordinates, and when dotted with $\bm v \parallel \unit r$, this gives
-\begin{equation}
-  K_{\ell m} = \frac{\rho_0 }{\mu_\mathcal{A} a_\mathcal{A}^\ell (3 + \ell)} \int d\Omega r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
-  \label{eqn:surface-klm}
-\end{equation}
-where the integral is carried out over the unit sphere. Note that the integrand of each $K_{\ell m}$ is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
-
-We write 
-\begin{equation}
-  r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}
-\end{equation}
-without loss of generality.
-To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m C_{l,-m} (\ell-m)!/(\ell+m)$.
-With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell m}$ and integrals of products of spherical harmonics.
-These integrals can be pre-computed so that equation \ref{eqn:surface-klm} can then be numerically solved via standard polynomial solution methods to find $C_{\ell m}$.
-A similar equation to equation \ref{eqn:surface-klm} can be written for $a_\mathcal{A}$
-\begin{equation}
-  a_\mathcal{A}^2 = \frac{\rho_0}{5\mu_\mathcal{A}}\int d\Omega r(\theta, \phi)^5
-  \label{eqn:surface-am}
-\end{equation}
-which can also be solved via polynomial methods.
-
-Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form a set of $n+1$ constraints, where $n$ is the number of density moments known.
-That is, $n=(\ell_\text{max}+1)^2+1$, where $\ell_\text{max}$ is the maximum degree of $K_{\ell m}$ known.
-By setting the same maximum degree on $C_{\ell m}$, we also have $n$ variables plus one for $\rho_0$.
-The system is therefore well-determined and will yield finitely many solutions.
-These solutions can be further refined by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
-We do not attempt to model uncertainty on the shape.
-
-To test the model, this process was run for an asteroid with $K_{1m}=K_{2m'}=0$, but randomly chosen $K_{3m}$.
-The resulting surface is shown in figure \ref{fig:surface-density}.
-The figure shows a near-spherical asteroid, which is expected for $K_{\ell m} = 0$ for $\ell > 0$.
-However, the additional $K_{3m}$ components clearly induce non-sphericity in the asteroid which is captured by the surface model.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
-  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
-  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model.
-\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
-The same length scale is used in both figures.}
-  \label{fig:surface-density}
-\end{figure*}
-
-To give an alternate view of the non-sphericities found via this new surface model, figure \ref{fig:surface-density} also displays the density distribution extracted via the likelihood model assuming a spherical asteroid shape, but with the same density moments.
-(Uncertainty in the moments is not modelled in this figure, to better compare the two.) Where the likelihood model displays low density, the surface model clearly retracts into the asteroid.
-Where the likelihood model yields high density, the surface model extends.
-Thus, the connection made in section \ref{sec:spherical-density} between non-uniformities in the densities of the likelihood and harmonic models at the asteroid surface and inaccuracies in the surface is more firmly represented.
-
-This surface model could, in principle, be used to improve estimates of the surface of an asteroid made by light curve analysis, since it connects rotational data to the asteroid surface which reflects the light we observe.
-Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
-We only suggest this as a possibility, however, since light-curve analysis is beyond the scope of this paper.
-
-\section{Example fit results}
-\label{app:example}
-
-Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
-The fit results were consistent with the true density moments, and produced consistent data.
-
-Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid in the top pane and the residuals in the bottom pane.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
-  \label{fig:example-residuals}
-\end{figure*}
-
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, marginalized to functions of one or two variables.
-The true parameters are shown as lines.
-Note that the true parameters usually lie within 1- or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
-Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
-Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
-True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
-  \label{fig:example-corner}
-\end{figure*}
+\include{appendices}
 

### 2022-04-14 data/probe-s-rho/scatter.py

@@ -1,0 +1,32 @@
+# Goal: spawn a bunch of runs that cover the parameter space.
+from matplotlib import pyplot as plt
+import numpy as np
+
+LOW_ORDER_INDEX = 1
+BASE_NAME = f"rho"
+LOW_RHO= -9
+HIGH_RHO = -4
+NUM_DIVISIONS = 48 # Run with 8 cores per process.
+LOW_ORDER = [(0.39269908169, 0, -0.09766608), (0.39269908169, 0.05200629, -0.2021978)][LOW_ORDER_INDEX]
+HIGH_ORDER = [0, 0, 0, 0, 0, 0, 0]
+
+# Fix product, vary ratio
+
+def get_text(sigma_rho):
+    return """0, 3
+120
+5
+1000
+5
+0.00006464182, 0.00012928364, -0.00012928364
+1.0
+{}, {}, {}, {}, {}, {}, {}, {}, {}, {}
+0.78539816339, 0.125, 0, 1, 1, 1, 1, 1, 1, 1
+-0.78539816339, -0.125, -0.25, -1, -1, -1, -1, -1, -1, -1
+1e-2, {}""".format(LOW_ORDER[0], LOW_ORDER[1], LOW_ORDER[2], HIGH_ORDER[0], HIGH_ORDER[1],
+    HIGH_ORDER[2], HIGH_ORDER[3], HIGH_ORDER[4], HIGH_ORDER[5], HIGH_ORDER[6], sigma_rho / 1e-2)
+
+for ratio_index, sigma_rho in enumerate(10**np.linspace(LOW_RHO, HIGH_RHO, NUM_DIVISIONS)):
+    f = open("../../staged/{}-{:02}.txt".format(BASE_NAME, ratio_index), 'w')
+    f.write(get_text(sigma_rho))
+    f.close()

### 2022-04-15 paper/appendices.tex
Updated paper

@@
 
+\section{Detailed analysis of the dependence of PPD width on encounter parameters}
+
+\subsection{Orbital elements}
+\label{sec:scan-orbit}
+A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
+The orbit can be rotated to the $\unit X \unit Y$-plane, as mandated by our coordinate definitions, by changing the density moments of the central body.
+Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant until the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
+
+We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$.
+Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
+The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
+The red vertical lines indicate when $\sigma = 0.01$.}
+  \label{fig:scan-vex}
+\end{figure}
+
+Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$.
+This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
+There are also smaller-scale oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
+The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee, so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.
+This effect explains why these small-scale oscillations have the same period for all parameters.
+Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
+The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
+The dotted curve indicates a power-law fit (see text).
+The red vertical lines indicate when $\sigma = 0.01$.}
+  \label{fig:scan-perigee}
+\end{figure}
+
+Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
+For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the reference 0.01 limit.
+At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
+Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
+The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
+
+\begin{table}
+  \centering
+  \begin{tabular}{l|c}
+    \hline
+    Parameter & $\alpha$ \\ \hline
+    $\gamma_0$ & $2.05$ \\
+    $K_{22}$ & $5.47$ \\
+    $K_{20}$ & $5.47$ \\ \hline
+    $\Re K_{33}$ & $3.35$ \\
+    $\Im K_{33}$ & $3.37$ \\
+    $\Re K_{32}$ & $3.05$ \\
+    $\Im K_{32}$ & $3.27$ \\
+    $\Re K_{31}$ & $3.53$ \\
+    $\Im K_{31}$ & $4.02$ \\
+    $K_{30}$ & $5.75$ \\ \hline
+  \end{tabular}
+  \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
+  \label{tab:scan-perigee-alpha}
+\end{table}
+
+Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
+These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
+The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
+These slope values express how much each parameter is dependent on $r_p$.
+It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
+The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
+The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
+
+The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
+Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
+This pattern of large $m$ corresponding to low uncertainty is a general trend and will be seen in the following sections as well.
+
+The very strong dependence of $\sigma$ on $r_p$ makes this analysis only to extract second-order moments on close encounters.
+Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
+The first-order moments can still be extracted at much larger perigee distances in our model.
+
+\subsection{Observational Uncertainty}
+\label{sec:scan-uncertainty}
+There are two parameters, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}).
+Rather than explore the full space spanned by these two values, we measure how parameter uncertainties depend on the product of uncertainties $\sigma_\theta\sigma_\rho$ (with the radio fixed), and the ratio $\sigma_\rho / \sigma_\theta$ (with the product fixed).
+
+We choose these metrics because we generally expect that the parameter uncertainty $\sigma$ be proportional to the observational uncertainty, but whether the dependence is stronger on $\sigma_\theta$ or $\sigma_\rho$ is not immediately clear.
+We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their ratio, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
+Indeed, we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
+For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma(K_{30}) \approx 1$ which fills the prior.
+Uncertainty cannot increase beyond this value.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
+The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
+The red vertical lines indicate when $\sigma =0.01$.}
+  \label{fig:scan-product}
+\end{figure}
+
+We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}.
+If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then $\sigma$ would have no dependence on $\sigma_\rho / \sigma_\theta$.
+Any deviation from constant $\sigma$ shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
+The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
+The red vertical lines indicate when $\sigma = 0.01$.
+(Lines are not shown for $K_{3m}$, $m < 3$ because they coincide with the vertical axis.)}
+  \label{fig:scan-ratio}
+\end{figure}
+
+Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$.
+We summarize this pattern by stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
+This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I do not know enough about light curve analysis to be sure.}
+
+Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that $\sigma(\sigma_\rho/\sigma_\theta)$ is proportional for all $K_{\ell m}$.
+The proportionality constant shows the same dependence on $\ell$ and $m$ mentioned previously.
+The proportionality is broken near $\sigma \approx \pm 1$, where $\sigma$ fills the prior.
+
+The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty; increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
+
+\subsection{Asteroid shape}
+\label{sec:scan-shape}
+
+The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the uncertainties in extracted density moments $\sigma$.
+Here, we only investigate the sensitivity of $\sigma$ to the first-order parameters and $a_\mathcal{A}$.
+The $K_{2m}$ moments can therefore also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
+
+In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
+We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
+The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
+The data then have no physical dependence on $\gamma_0$ when $K_{22}=0$.
+This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
+
+\begin{figure*}
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-3-sigma.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-b-sigma.pdf}
+
+  \caption{1$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
+  \label{fig:scan-space-sigma}
+\end{figure*}
+
+To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
+For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
+This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
+
+Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
+Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
+
+Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters for reference.
+They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
+This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
+They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
+The latter is expected due to the $1/c$ dependence.
+As for the former, this correlation could likely be removed by an alternate parametrization, reducing uncertainties in the shape parameters.
+
+\begin{figure*}
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr12.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr13.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr23.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-ab.pdf}
+
+  \caption{Correlations between PPDs for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
+  \label{fig:scan-space-corr}
+\end{figure*}
+
+Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
+It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
+The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
+
+On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
+The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid length $a_\mathcal{A}$.
+The reference cadence is 2 minutes.
+The red vertical lines indicate when $\sigma = 0.01$.
+The black dashed line indicates the reference value of $a_\mathcal{A}=1000$ m.}
+  \label{fig:scan-am}
+\end{figure}
+
+As was mentioned in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
+The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
+At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
+The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
+This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
+(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma$.
+It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is very unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
+
+For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius, which was mentioned in section \ref{sec:moments} and explicitly shown in equation \ref{eqn:ellipsoid-axes}.
+In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
+
+\subsection{Cadence}
+\label{sec:scan-cadence}
+
+The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
+We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
+The red vertical lines indicate when $\sigma = 0.01$.}
+  \label{fig:scan-cadence}
+\end{figure}
+
+Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
+We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
+We name this rough cadence limit $T_\text{cad}$.
+
+We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the time spent near perigee $T_p$.
+The latter can be estimated by
+\begin{equation}
+  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
+  \label{eqn:tp}
+\end{equation}
+which is the ratio of the perigee radius to velocity at perigee.
+The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
+For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
+
+We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
+
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is slightly exceeded).
+However, shorter cadence almost always leads to lower uncertainties.
+
+\subsection{Perigee gap}
+\label{sec:scan-gap}
+In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
+The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
+Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
+There, the angular velocity evolution is dominated by torque-free precession dictated by the moment of inertia components.
+That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
+However, $K_{3m}$ are not extractable from precession data alone.
+We are therefore curious as to how our posterior uncertainties change due to lack of data during the encounter perigee.
+
+To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
+We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma$ in figure \ref{fig:observation-gap}.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
+The red vertical lines indicate when $\sigma = 0.01$.}
+  \label{fig:observation-gap}
+\end{figure}
+
+Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
+We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
+
+Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
+On the other hand, none of the uncertainties increase noticeably for $T < 30$ min.
+Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
+
+Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$.
+They also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
+This suggests that the factors that govern uncertainty due to cadence (appendix \ref{app:cadence-tests}) also may govern sensitivity to lack of data at perigee in a similar way.
+
+\subsection{Initial spin pole}
+\label{sec:scan-spin}
+
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+
+In figure \ref{fig:scan-spin}, we display 1$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
+Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
+To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
+The average is weighted such that the uncertainty map for each parameter contributes an equal amount
+(the weight of each map is set to one-tenth of the map's mean). This average map is presented in two different projections to allow data at $\unit Z$ to be read.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
+  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
+All maps are made in the Mollweide projection.
+The orange star indicates the reference spin pole.
+The red contours enclose regions where $\sigma \geq 0.01$.}
+  \label{fig:scan-spin}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-mollweide.pdf}
+  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
+  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
+See text for a description of how the average was computed.
+Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
+The polar projection is centred at the south pole, or $-\unit Z$.}
+  \label{fig:scan-spin-avg}
+\end{figure*}
+
+Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
+For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
+We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
+Then, since $\bm \omega_0 \parallel \unit z$ in the body-fixed frame as an initial condition (section \ref{sec:sim}), we have that $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
+
+Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
+This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
+Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
+Also, $\tau_z$ affected by fewer parameters than $\tau_x$ or $\tau_y$.
+Both of these are reasons why $\bm \tau \parallel \unit z$ might inhibit precise fits to spin data.
+If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma$.
+
+It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma$ (figure \ref{fig:scan-spin-avg}).
+
+\subsection{Rotational period}
+\label{sec:scan-period}
+
+We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma$.
+The dynamical time scales $r_p/v_\infty$ and $\mu_\mathcal{B} / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P_\omega$ in principal may affect $\sigma$.
+In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
+
+\begin{figure}
+  \centering
+  \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
+The reference value of 9 hr is shown as a vertical dotted line.
+The red vertical lines indicate when $\sigma = 0.01$.}
+  \label{fig:scan-period}
+\end{figure}
+
+Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
+But a large-scale trend is also visible in many parameters.
+$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
+This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
+
+We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and reveal that each rotation has zero average first-order torque.
+Since the first-order torque over each rotational period cancels out, there is no secular torque to force the asteroid to tumble.
+However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
+
+Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
+This is most visible in the figure for $K_{30}$.
+The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
+We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
+
+The most severe effect of period on $\sigma$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
+The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
+It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids still have better uncertainty.
+
+\subsection{Central body oblateness}
+\label{sec:scan-oblateness}
+
+In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
+By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
+The effect of central body oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_\mathcal{B} / D)^2$.
+We expect these parameters to have little effect on the asteroid.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_M$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
+
+$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
+However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
+(Some sources such as Ref.~\cite{paterLissauer2015} take $\epsilon=J_{20}$ as their definition of $J_{20}$).
+For simplicity, we use this equatorial orbit case.
+If the orbit is non-equatorial, the other $J_{2m}$ terms will be non-zero.
+Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
+The next order of precision after this oblateness approximation is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and  non-ellipsoid corrections to the central body shape.
+
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for $\sigma(\epsilon)$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
+  \vfill
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
+Linear best-fitting lines to $\sigma$ (black, dotted) are plotted.
+\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies.}
+  \label{fig:scan-oblateness}
+\end{figure}
+
+The figure demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
+Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
+The best-fitting lines match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
+
+Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
+These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+
+Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
+However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
+The difference between the PPD means and true parameters are shown.
+Posterior uncertainties are also shown as bands.
+The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
+Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
+For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
+
+Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass.
+Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body centre of mass (though the effect is not quite quadratic because $a_\mathcal{B}$ also increases for large distances, and $J_{20}$ is divided by $a_\mathcal{B}^2$).
+This process is only valid when the asteroid never passes inside the moon's orbit.
+
+As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
+Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
+
+This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
+Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
+However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
+
 \section{The cadence cut-off}
@@
 
-\section{Comparison of Jupiter and Earth encounters}
-\label{app:jupiter-earth}
-
-If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
-In this appendix, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
-
-The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
-The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
-The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
-The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
-
-Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
-We therefore do not distinguish between the two cases further.
-The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
-In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
-
-\begin{table}
-  \centering
-  \begin{tabular}{c|cc}
-    \hline 
-    $K_{\ell m}$ & $\sigma_\text{Jupiter}/\sigma_\text{Earth}$\\ \hline 
-    $\gamma_0$ & 1.6 \\
-    $K_{22}$ & 2.3 \\
-    $K_{20}$ & 11 \\
-    $\Re K_{33}$ & 18 \\
-    $\Im K_{33}$ & 18 \\
-    $\Re K_{32}$ & 18 \\
-    $\Im K_{32}$ & 18 \\
-    $\Re K_{31}$ & 25 \\
-    $\Im K_{31}$ & 10 \\
-    $K_{30}$ & 53 \\ \hline
-  \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
-  \label{tab:jupiter-uncertainty}
-\end{table}
-
-These uncertainty ratios can be understood as follows.
-The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
-If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
-Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
-
-The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
-Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
-
-The $K_{\ell 0}$ components differ in that $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
-In fact, $K_{30}$ essentially fills the prior.
-The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
-In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
-
-There are additional effects of central body mass which are not captured in this analysis.
-For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
-The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
-\begin{equation}
-  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
-\end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
-Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
-
-Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
-However, these selection biases will cause more large-$a_\mathcal{A}$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
-Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
-
 \section{Computing asteroid shape from density moments}
@@
 
-In section \ref{sec:distros}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
+  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
+  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model.
+\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
+The same length scale is used in both figures.}
+  \label{fig:surface-density}
+\end{figure*}
+
+In section \ref{sec:general-density}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
 We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
-  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
-  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model.
-\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
-The same length scale is used in both figures.}
-  \label{fig:surface-density}
-\end{figure*}
-
 To give an alternate view of the non-sphericities found via this new surface model, figure \ref{fig:surface-density} also displays the density distribution extracted via the likelihood model assuming a spherical asteroid shape, but with the same density moments.
@@
 
-\section{Example fit results}
 \label{app:example}

### 2022-04-15 paper/main.tex
Updated paper

@@
 
-In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion and ins section
+In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion.
+In section \ref{sec:uncertainty}, we define the uncertainty model used to add noise to the data, and we describe how PPDs for density moments were extracted from spin-pole data in section \ref{sec:fit}.
+Finally, we outline a general model to extract density distributions from density moments in section \ref{sec:general-density} and define specific model implementations in section \ref{sec:specific-density}
 
@@
 
-\subsection{Fit process}
+\subsection{Extracting density moments from spin data}
 \label{sec:fit}
@@
 
+\subsection{Extracting density distributions from density moments: general model design}
+\label{sec:general-density}
+
+The asteroid density distribution $\rho_\mathcal{A}(\bm r)$ is not uniquely constrained via tidal torque interactions because only the density moments $K_{\ell m}$ contribute to equation \ref{eqn:tidal-torque}.
+However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
+Here, we outline three different assumptions which constitute three models for extracting density distributions from density moments.
+One of them can be chosen, or another created, depending on what features are desired to be represented in the density distribution.
+
+All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
+Uncertainty on this shape estimate is assumed to be small.
+The models then produce a density distribution $\rho_\mathcal{A}(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho_\mathcal{A}$.
+In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
+However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
+It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
+If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
+Likewise, if the asteroid shape is not known with certainty, a fourth model described in appendix \ref{app:find-surface} can be used to extract asteroid shape assuming constant density.
+
+Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
+Only the differences in $\rho$ across the body are measurable.
+
+To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
+Since the asteroid rotates around its centre of mass during observations, we assume that the location of the centre of mass is also known in this frame, so that we can set it to be the origin.
+
+We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
+The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame.
+The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
+
+The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit, removing the non-linearity induced by division by $a_\mathcal{A}$.
+Furthermore, since the system is independent of the total asteroid mass, we set $\mu_\mathcal{A}$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
+Similarly, the form of equation \ref{eqn:am} guarantees that $a_\mathcal{A}^2$ is linear in $\rho(\bm r)$.
+Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
+
+Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm \Theta)$ for an $m$-dimensional vector $\bm \Theta$ which contains the free parameters of $\rho$.
+We will leave the explicit definition of $\rho(\bm r, \bm \Theta)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm \Theta$; i.e.,
+\begin{equation}
+  \rho(\bm r, \bm \Theta) = \bm B(\bm r) \cdot \bm \Theta
+  \label{eqn:density-distro}
+\end{equation}
+for a $m$-dimensional vector $\bm B(\bm r)$.
+($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
+We further assume that the model describes a way to reverse this equation, to write
+\begin{equation}
+  \bm \Theta = A \bm K
+  \label{eqn:density-model}
+\end{equation}
+where $A$ is a matrix.
+Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
+The order of this arrangement is irrelevant, as long as it is kept consistent.
+
+To propagate uncertainties from $\bm K$ to $\bm \Theta$ and therefore $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
+First, assume that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
+Then
+\begin{equation}
+  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{body-fixed}.
+  \label{eqn:body-fixed-to-hybrid}
+\end{equation}
+by equation \ref{eqn:ylm-rotation}.
+Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
+\begin{equation}
+  \rho(\bm r) = \bm B(\bm r)^T A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
+  \label{eqn:unc-rho}
+\end{equation}
+
+The purpose of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
+
+\subsection{Model implementations for extracting density distributions from density moments}
+\label{sec:specific-density}
+In the following sections, three possible models for extracting density distributions from moments (i.e., choices of $\bm B(\bm r)$ and $A$ defined above) are given.
+
+\subsubsection{The ``likelihood'' model}
+\label{sec:likelihood}
+
+A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
+We call this method the ``likelihood'' model.
+This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
+The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require a Gaussian likelihood.
+
+To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
+This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
+
+We use a likelihood of 
+\begin{equation}
+  \mathcal{L}(\bm \Theta) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{\Theta_i^2}{2 \sigma^2}}
+\end{equation}
+with free parameters $\mu$ and $\sigma$.
+These parameters do not affect the location of the maximum, so we do not define them.
+Given this likelihood, the log likelihood is proportional to $-|\bm \Theta|^2$.
+Minimizing the norm of $\bm \Theta$ is therefore equivalent to finding the maximum likelihood.
+
+Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:klm} or \ref{eqn:am}, evaluated over the $i$th finite element.
+We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
+Since $m>n$, the Moore-Penrose inverse of $M$ is
+\begin{equation}
+  A=M^+ = M^*(MM^*)^{-1}
+  \label{eqn:mpi-underdetermined}
+\end{equation}
+where $M^*$ is the adjoint of $M$.
+The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
+Thus, defining $A=M^+$ also minimizes $\mathcal{L}$ and fully defines the model.
+
+Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+
+\subsubsection{The ``harmonic'' model}
+\label{sec:harmonic}
+
+We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
+We therefore call this model the ``harmonic'' model.
+The expansion of a harmonic function in spherical coordinates is given by
+\begin{equation}
+  \rho(\bm r) = \sum_{\ell m} \Theta_{\ell m}\frac{R_{\ell m}^*(\bm r)}{a_\mathcal{A}^\ell} 
+  \label{eqn:harmonic-rho}
+\end{equation}
+where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $\Theta_{\ell m}$ are free (complex) parameters.
+Since $\rho$ is real, we have $\Theta_{\ell m}=(-1)^m \Theta_{\ell,-m}^*$.
+By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
+Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $\Theta_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm \Theta$.
+
+Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:klm} and \ref{eqn:am}, we get 
+\begin{equation}
+  K_{\ell' m'} = \sum_{\ell m} \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^{\ell'} a_\mathcal{A}^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
+  \label{eqn:harmonic-mat}
+\end{equation}
+This is an over-determined matrix equation $\bm K = M \bm \Theta$, where $M$ is an $n \times m$ matrix.
+The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm \Theta$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm \Theta$ is minimized).
+However, the form of the inverse changes due to the equation being overdetermined:
+\begin{equation}
+  A=M^+ = (M^*M)^{-1} M^*
+  \label{eqn:mpi-overdetermined}
+\end{equation}
+
+In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
+\begin{equation}
+  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
+\end{equation}
+A non-spherical perturbation will introduce small off-diagonal entries to $M$.
+This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
+
+\subsubsection{The ``lumpy'' model}
+\label{sec:lumpy}
+
+The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
+In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
+We call this model the ``lumpy'' model.
+
+Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
+For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
+Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
+The displacement of the shape centroid from the centre of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
+The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
+The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
+These degrees of freedom should be compared to the known density moments and $a_\mathcal{A}$, of which there are $(\ell_\text{max}+1)^2+1$.
+However, three of these are the centre of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
+We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cc|ccc}
+    \hline \hline
+        &  & & $N$ &  \\
+        &  & 1  & 2  & 3  \\ \hline 
+        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{gray}\color{white} 7 & \cellcolor{gray}\color{white} 12\\
+    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 13 & 21 \\
+        & 3& \cellcolor{gray}\color{white}  7 &  17 &  27 \\
+    \hline \hline
+  \end{tabular}
+  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
+The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are coloured gray.}
+  \label{tab:lump-dof}
+\end{table}
+
+The net $K_{\ell m}$ components of such an ensemble obey
+\begin{equation}
+  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_\mathcal{A}^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
+  \label{eqn:klm-stack}
+\end{equation}
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
+Crucially, note that we set normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ in equations \ref{eqn:klm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
+The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
+The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
+
+We can relate the primed moments to the moments calculated relative to each lump's centre of mass via the translation rules for solid spherical harmonics:
+\begin{equation}
+  \begin{split}
+  & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
+  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
+  \end{split}
+  \label{eqn:translate-klm}
+\end{equation}
+from Ref.~\cite{Gelderen1998TheSO}.
+The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
+Here, $\mu_i$ is the added mass of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate the lump's orientation and moment of inertia ratios.
+Its volume is constrained by $a_i^2$.
+These values map directly onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
+
+Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$ and $a_i^2$.
+Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
+Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the already-known surface shape.
+
+This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
+The constraints on $\bm x_i$ is
+\begin{equation}
+  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
+  \label{eqn:lump-constraints}
+\end{equation}
+where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the centre of mass.
+There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
+The overall mass of the asteroid is $\mu_\mathcal{A} = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
+The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
+We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with close solutions.
+This is done by minimizing
+\begin{equation}
+  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
+  \label{eqn:lump-minimize}
+\end{equation}
+which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
+Here, $\mathds{1}$ is the identity matrix.
+Then $A=M^+$ defines the model.
+We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
+If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
+
 \section{Results}
@@
 
+\subsection{Density moment extraction}
+To demonstrate the success of our fit process, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
+The fit results were consistent with the true density moments, and produced consistent data.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
+The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
+  \label{fig:example-residuals}
+\end{figure*}
+
+Figure \ref{fig:example-residuals} shows the spin data with uncertainty added.
+Data simulated given the best-fitting density moments (the mean of the PPDs) is overlaid in the top pane and the residuals are shown the bottom pane.
+Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
+The fit results are clearly consistent with the data.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
+  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
+Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
+Individual points in the contours are samples from the MCMC fit, and the contours enclose 1, 2, and 3$\sigma$ of them.
+True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
+  \label{fig:example-corner}
+\end{figure*}
+
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted PPD, marginalized to functions of one or two variables.
+The true parameters are shown as lines.
+Note that the true parameters usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+The PPDs are generally Gaussian and no degeneracy between fit components is visible.
+We performed 48 independent minimizations of the likelihood before the MCMC fit began, each with an initial point chosen randomly in the parameter space.
+All converged to the same minimum, further showing that the model lacks degeneracy.
+
+\subsection{Density distribution extraction}
+\label{sec:asym-density}
+To demonstrate the success of our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
+These distributions were made given the density moment PPDs extracted in the previous section, with $a_\mathcal{A}$ fixed.
+The surface is fixed as a triaxial ellipsoid with semi-axis lengths such that the true values of $K_{\ell m}$ are consistent with uniform density (equation \ref{eqn:ellipsoid-axes}).
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+
+  \caption{Density distributions (\textit{top}) and uncertainties (\textit{bottom}) extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density, asymmetric reference asteroid.
+Density is normalized so that mean density is one.}
+  \label{fig:uniform-density-results}
+\end{figure*}
+
+Also in each pane of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
+This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models, they express the degree to which the extracted moments cannot be represented with harmonic or lumpy distributions respectively.
+
+The likelihood and harmonic models produce mostly the same density distributions.
+This is generally true for uniform density asteroids, which have harmonic density distributions.
+Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
+This similarity lends confidence that the models produced are truly representative of the asteroid since they are produced via two independent methods.
+
+The distributions' non-uniformity is limited for the harmonic and likelihood models.
+This non-uniformity is driven by error in the estimates of the density moments.
+Note that most of the asteroid has density close to one in both cases, with densities of 40\% or 160\% of the mean attained only in small regions.
+The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
+However, it does not produce a density distribution consistent with those extracted from spin data (i.e., $\Delta K_{\ell m}$ is usually large).
+This is because the lump found extends outside the asteroid, violating the assumptions of the model --- a sign that the lump found does not really exist inside the asteroid.
+
+The size of uncertainty is such that the density distribution is consistent with uniform at most points for the harmonic and likelihood models (within 1-2$\sigma$), with a small number of low-uncertainty regions that are less consistent with uniform.
+Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
+
+\section{Discussion}
+\label{sec:discussion}
+
+In this section, we discuss the physical properties of the asteroid encounter system (section \ref{sec:spin-evolution}), as well as the sensitivity of the density moment uncertainty to encounter properties (section \ref{sec:fit-uncertainty}), together with an analysis of advantages and disadvantages Jupiter encounters over Earth (section \ref{sec:jupiter-earth})Finally, we discuss the kinds of distributions produced by the density distribution extraction methods (section \ref{sec:density-compare}).
+
 \subsection{Spin evolution}
-
+\label{sec:spin-evolution}
 In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
-  \label{fig:example-residuals}
-\end{figure*}
-
 To choose the initial values of $\gamma_0$, $K_{20}$, and $K_{22}$, spin data for the reference asteroids of appendix \ref{app:reference-configs} was first generated.
@@
 
-\subsection{Example fit results}
-
-Here, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
-The fit results were consistent with the true density moments, and produced consistent data.
-
-Figure \ref{fig:example-residuals} shows the spin data with the best-fit overlaid in the top pane and the residuals in the bottom pane.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
-
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted parameters' posterior distributions, marginalized to functions of one or two variables.
-The true parameters are shown as lines.
-Note that the true parameters usually lie within 1- or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
-Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
-Individual points in the contours are samples from the MCMC fit, and the contours enclose 1-, 2-, and 3-$\sigma$ of them.
-True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
-  \label{fig:example-corner}
-\end{figure*}
-
-\subsection{Density stuff?}
-
-\section{Discussion}
-\label{sec:discussion}
-
-% \afterpage{
-%   \begin{landscape}
-%     \begin{figure}
-%     \centering
-%     \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
-%     \caption{caption}
-%     \label{fig:label}
-%     \end{figure}
-%   \end{landscape}
-% }
-% PLOTS THAT COULD BE HERE
-% rp
-% vp
-
-In this section, we assess the sensitivity of the PPDs for the first-order parameters ($\gamma_0$, $K_{20}$, and $K_{22}$), and the second-order parameters ($K_{3m}$) to many possible close encounter configurations.
-Specifically, we test sensitivity to the encounter's orbital parameters, the degree of observational uncertainty, the asteroid's radius, the cadence of observation, the amount of data collected at perigee, the direction of the initial spin pole, the asteroid period, and the central body oblateness.
-These effects are presented roughly in order of how much they affect the parameter precision, from highest to lowest.
-
+\subsection{Dependence of parameter uncertainty on encounter parameters}
+\label{sec:fit-uncertainty}
 Parameter precision of 1$\sigma$ is defined such that 68.27\% of the PPD lies within 1$\sigma$ of the mean of the PPD.
@@
 The PPDs are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the PPD.
-
 In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-We further present a test of how precision depends on cadence, asteroid period, and the duration of the encounter in appendix \ref{app:cadence-tests}, and we compare precision for a Jupiter and an Earth encounter in appendix \ref{app:jupiter-earth}.
-
-\subsection{Orbital elements}
+
+\subsubsection{Orbital elements}
 \label{sec:scan-orbit}
@@
 Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-vex.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of orbital excess velocity $v_\infty$.
-The vertical dashed line indicates the reference asteroid value of 6 km s$^{-1}$.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-vex}
-\end{figure}
 
@@
 Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-perigee.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of perigee distance $r_p$.
-The vertical dashed line indicates the reference asteroid value of 5 Earth radii.
-The dotted curve indicates a power-law fit (see text).
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-perigee}
-\end{figure}
 
@@
 
-\subsection{Observational Uncertainty}
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all-1.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
+The vertical dashed line indicates the reference asteroid values of the parameters.
+The red vertical lines indicate when $\sigma =0.01$.}
+    \label{fig:scan-perigee}
+    \label{fig:scan-vex}
+    \label{fig:scan-theta}
+    \label{fig:scan-rho}
+    \end{figure}
+  \end{landscape}
+}
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all-2.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
+The vertical dashed line indicates the reference asteroid values of the parameters.
+The red vertical lines indicate when $\sigma =0.01$.}
+    \label{fig:scan-am}
+    \label{fig:scan-cadence}
+    \label{fig:scan-period}
+    \label{fig:scan-gap}
+    \end{figure}
+  \end{landscape}
+}
+
+\subsubsection{Observational Uncertainty}
 \label{sec:scan-uncertainty}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-product.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals divided by $\sigma_\theta$ for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty product $\sigma_\theta \sigma_\rho$.
-The vertical dashed line indicates the reference asteroid value of $10^{-9}$.
-The red vertical lines indicate when $\sigma =0.01$.}
-  \label{fig:scan-product}
-\end{figure}
-
 We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-ratio.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational uncertainty ratios $\sigma_\rho / \sigma_\theta$.
-The reference asteroid value is $\sigma_\rho/ \sigma_\theta =10^{-5}$.
-The red vertical lines indicate when $\sigma = 0.01$.
-(Lines are not shown for $K_{3m}$, $m < 3$ because they coincide with the vertical axis.)}
-  \label{fig:scan-ratio}
-\end{figure}
-
 Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$.
@@
 
-\subsection{Asteroid shape}
+\subsubsection{Asteroid shape}
 \label{sec:scan-shape}
@@
 \begin{figure*}
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-theta-3-sigma.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-b-sigma.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-3-sigma.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-b-sigma.pdf}
 
@@
 The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-am.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of asteroid length $a_\mathcal{A}$.
-The reference cadence is 2 minutes.
-The red vertical lines indicate when $\sigma = 0.01$.
-The black dashed line indicates the reference value of $a_\mathcal{A}=1000$ m.}
-  \label{fig:scan-am}
-\end{figure}
 
@@
 
-\subsection{Cadence}
+\subsubsection{Cadence}
 \label{sec:scan-cadence}
@@
 We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-cadence.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of observational cadence $\Delta t$ The reference cadence is 2 minutes.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-cadence}
-\end{figure}
 
@@
 
-\subsection{Perigee gap}
+\subsubsection{Perigee gap}
 \label{sec:scan-gap}
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/observation-gap.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of a data gap of width $T$ at perigee.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:observation-gap}
-\end{figure}
-
 Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
@@
 
-\subsection{Initial spin pole}
+\subsubsection{Initial spin pole}
 \label{sec:scan-spin}
@@
   \centering
-  \includegraphics[width=\textwidth]{figs/spin-pole.pdf}
+  \includegraphics[width=0.8\textwidth]{figs/spin-pole.pdf}
   \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-mollweide.pdf}
-  \includegraphics[width=0.45\textwidth]{figs/spin-pole-avg-polar.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.pdf}
   \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
@@
 
-\subsection{Rotational period}
+\subsubsection{Rotational period}
 \label{sec:scan-period}
@@
 In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/scan-period.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of initial rotational period $P_\omega$.
-The reference value of 9 hr is shown as a vertical dotted line.
-The red vertical lines indicate when $\sigma = 0.01$.}
-  \label{fig:scan-period}
-\end{figure}
 
@@
 
-\subsection{Central body oblateness}
+\subsubsection{Central body oblateness}
 \label{sec:scan-oblateness}
@@
 
-\section{Density distributions}
-\label{sec:distros}
-
-Hitherto, we have only discussed the density moments $K_{\ell m}$ of the asteroid rather than the true density distribution $\rho(\bm r)$.
-This is because only the density moments are observable by tidal torque interactions.
-However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
-
-In this section, we outline three different assumptions which yield different types of density distributions for the same $K_{\ell m}$.
-One of them can be chosen, or a fourth created, depending on what features are desired to be represented in the density distribution.
-All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
-Uncertainty on this shape estimate is assumed to be small.
-The models then produce a density distribution $\rho(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho$.
-
-In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
-However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
-It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
-
-Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
-Only the differences in $\rho$ across the body are measurable.
-
-In section \ref{sec:general-density}, we describe the general form our three models must take.
-Then in sections \ref{sec:likelihood} to \ref{sec:lumpy} we lay out each individually and compare them in section \ref{sec:density-compare}.
-In appendix \ref{app:find-surface}, we introduce a new model which does not assume that the asteroid shape is known, instead assuming that the density is constant.
-This allows us to compute the asteroid shape from $K_{\ell m}$.
-
-\subsection{General density model design}
-\label{sec:general-density}
-
-To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
-Since the asteroid rotates around its centre of mass during observations, we assume that the location of the centre of mass is also known in this frame, so that we can set it to be the origin.
-
-We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
-The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame.
-The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
-
-The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit, removing the non-linearity induced by division by $a_\mathcal{A}$.
-Furthermore, since the system is independent of the total asteroid mass, we set $\mu_\mathcal{A}$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
-Similarly, the form of equation \ref{eqn:am} guarantees that $a_\mathcal{A}^2$ is linear in $\rho(\bm r)$.
-Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
-
-Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm \Theta)$ for an $m$-dimensional vector $\bm \Theta$ which contains the free parameters of $\rho$.
-We will leave the explicit definition of $\rho(\bm r, \bm \Theta)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm \Theta$; i.e.,
-\begin{equation}
-  \rho(\bm r, \bm \Theta) = \bm B(\bm r) \cdot \bm \Theta
-  \label{eqn:density-distro}
-\end{equation}
-for a $m$-dimensional vector $\bm B(\bm r)$.
-($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
-We further assume that the model describes a way to reverse this equation, to write
-\begin{equation}
-  \bm \Theta = A \bm K
-  \label{eqn:density-model}
-\end{equation}
-where $A$ is a matrix.
-Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
-The order of this arrangement is irrelevant, as long as it is kept consistent.
-
-To propagate uncertainties from $\bm K$ to $\bm \Theta$ and therefore $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
-First, assume that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
-Then
-\begin{equation}
-  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{body-fixed}.
-  \label{eqn:body-fixed-to-hybrid}
-\end{equation}
-by equation \ref{eqn:ylm-rotation}.
-Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
-\begin{equation}
-  \rho(\bm r) = \bm B(\bm r)^T A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
-  \label{eqn:unc-rho}
-\end{equation}
-
-The purpose of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
-Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
-
-\subsection{The ``likelihood'' model}
-\label{sec:likelihood}
-
-A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
-We call this method the ``likelihood'' model.
-This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
-The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require a Gaussian likelihood.
-
-To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
-This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
-
-We use a likelihood of 
-\begin{equation}
-  \mathcal{L}(\bm \Theta) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{\Theta_i^2}{2 \sigma^2}}
-\end{equation}
-with free parameters $\mu$ and $\sigma$.
-These parameters do not affect the location of the maximum, so we do not define them.
-Given this likelihood, the log likelihood is proportional to $-|\bm \Theta|^2$.
-Minimizing the norm of $\bm \Theta$ is therefore equivalent to finding the maximum likelihood.
-
-Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:klm} or \ref{eqn:am}, evaluated over the $i$th finite element.
-We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
-Since $m>n$, the Moore-Penrose inverse of $M$ is
-\begin{equation}
-  A=M^+ = M^*(MM^*)^{-1}
-  \label{eqn:mpi-underdetermined}
-\end{equation}
-where $M^*$ is the adjoint of $M$.
-The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
-Thus, defining $A=M^+$ also minimizes $\mathcal{L}$ and fully defines the model.
-
-Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
-
-\subsection{The ``harmonic'' model}
-\label{sec:harmonic}
-
-We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
-We therefore call this model the ``harmonic'' model.
-The expansion of a harmonic function in spherical coordinates is given by
-\begin{equation}
-  \rho(\bm r) = \sum_{\ell m} \Theta_{\ell m}\frac{R_{\ell m}^*(\bm r)}{a_\mathcal{A}^\ell} 
-  \label{eqn:harmonic-rho}
-\end{equation}
-where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $\Theta_{\ell m}$ are free (complex) parameters.
-Since $\rho$ is real, we have $\Theta_{\ell m}=(-1)^m \Theta_{\ell,-m}^*$.
-By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
-Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $\Theta_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm \Theta$.
-
-Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:klm} and \ref{eqn:am}, we get 
-\begin{equation}
-  K_{\ell' m'} = \sum_{\ell m} \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^{\ell'} a_\mathcal{A}^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
-  \label{eqn:harmonic-mat}
-\end{equation}
-This is an over-determined matrix equation $\bm K = M \bm \Theta$, where $M$ is an $n \times m$ matrix.
-The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm \Theta$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm \Theta$ is minimized).
-However, the form of the inverse changes due to the equation being overdetermined:
-\begin{equation}
-  A=M^+ = (M^*M)^{-1} M^*
-  \label{eqn:mpi-overdetermined}
-\end{equation}
-
-In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
-\begin{equation}
-  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
-\end{equation}
-A non-spherical perturbation will introduce small off-diagonal entries to $M$.
-This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
-
-\subsection{The ``lumpy'' model}
-\label{sec:lumpy}
-
-The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
-In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
-We call this model the ``lumpy'' model.
-
-Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
-For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
-For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
-Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
-The displacement of the shape centroid from the centre of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
-The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
-The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
-These degrees of freedom should be compared to the known density moments and $a_\mathcal{A}$, of which there are $(\ell_\text{max}+1)^2+1$.
-However, three of these are the centre of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
-We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
+\subsection{Comparison of Jupiter and Earth encounters}
+\label{app:jupiter-earth}
+
+If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
+In this appendix, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
+
+The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
+The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
+We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
+The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
+The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
+
+Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
+We therefore do not distinguish between the two cases further.
+The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
+In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
 
@@
   \centering
-  \begin{tabular}{cc|ccc}
-    \hline \hline
-        &  & & $N$ &  \\
-        &  & 1  & 2  & 3  \\ \hline 
-        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{gray}\color{white} 7 & \cellcolor{gray}\color{white} 12\\
-    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 13 & 21 \\
-        & 3& \cellcolor{gray}\color{white}  7 &  17 &  27 \\
-    \hline \hline
+  \begin{tabular}{c|cc}
+    \hline 
+    $K_{\ell m}$ & $\sigma_\text{Jupiter}/\sigma_\text{Earth}$\\ \hline 
+    $\gamma_0$ & 1.6 \\
+    $K_{22}$ & 2.3 \\
+    $K_{20}$ & 11 \\
+    $\Re K_{33}$ & 18 \\
+    $\Im K_{33}$ & 18 \\
+    $\Re K_{32}$ & 18 \\
+    $\Im K_{32}$ & 18 \\
+    $\Re K_{31}$ & 25 \\
+    $\Im K_{31}$ & 10 \\
+    $K_{30}$ & 53 \\ \hline
   \end{tabular}
-  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
-The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are coloured gray.}
-  \label{tab:lump-dof}
+  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
+  \label{tab:jupiter-uncertainty}
 \end{table}
 
-The net $K_{\ell m}$ components of such an ensemble obey
-\begin{equation}
-  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_\mathcal{A}^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
-  \label{eqn:klm-stack}
-\end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
-Crucially, note that we set normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ in equations \ref{eqn:klm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
-The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
-The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
-
-We can relate the primed moments to the moments calculated relative to each lump's centre of mass via the translation rules for solid spherical harmonics:
-\begin{equation}
-  \begin{split}
-  & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
-  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
-  \end{split}
-  \label{eqn:translate-klm}
-\end{equation}
-from Ref.~\cite{Gelderen1998TheSO}.
-The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
-Here, $\mu_i$ is the added mass of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate the lump's orientation and moment of inertia ratios.
-Its volume is constrained by $a_i^2$.
-These values map directly onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
-
-Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$ and $a_i^2$.
-Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
-Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the already-known surface shape.
-
-This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
-The constraints on $\bm x_i$ is
-\begin{equation}
-  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
-  \label{eqn:lump-constraints}
-\end{equation}
-where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the centre of mass.
-There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-The overall mass of the asteroid is $\mu_\mathcal{A} = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
-The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
-The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
-We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with close solutions.
-This is done by minimizing
-\begin{equation}
-  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
-  \label{eqn:lump-minimize}
-\end{equation}
-which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
-Here, $\mathds{1}$ is the identity matrix.
-Then $A=M^+$ defines the model.
-We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
-If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
-
-\subsection{Comparisons between density models.}
+These uncertainty ratios can be understood as follows.
+The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
+If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
+Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
+Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
+
+The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
+Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
+
+The $K_{\ell 0}$ components differ in that $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
+In fact, $K_{30}$ essentially fills the prior.
+The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
+In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
+
+There are additional effects of central body mass which are not captured in this analysis.
+For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
+The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
+\begin{equation}
+  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
+\end{equation}
+It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
+Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
+
+Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
+However, these selection biases will cause more large-$a_\mathcal{A}$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
+Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
+
+\subsection{Comparisons between density models}
 \label{sec:density-compare}
 
-To test the properties of the three density models defined above, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
+To test the properties of the three density models defined in section \ref{sec:specific-density}, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
 Density moments are extracted via our fit process and density distributions extracted by the three above methods.
@@
 
-First, we simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
-The shapes we use are the symmetric and asymmetric reference ellipsoids, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), and a tetrahedron.
+We simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
+This was already done in section \ref{sec:asym-density} for the asymmetric reference asteroid.
+Here, we perform the same process for the symmetric reference asteroid, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), and a tetrahedron.
 We use these shapes as rough approximations of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron), but also to demonstrate the density models' efficacy on sharp corners.
 The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
-Also in each figure is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models, they express the degree to which the extracted moments cannot be represented with harmonic or lumpy distributions respectively.
 
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
-
   \includegraphics[width=0.33\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
@@
   \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The asteroid shapes are, from top to bottom, the reference asymmetric ellipsoid, the reference symmetric asteroid, the dumbbell model, and a tetrahedron.
+The asteroid shapes are, from top to bottom, the reference symmetric asteroid, the dumbbell model, and a tetrahedron.
 Density is normalized so that mean density is one.
@@
 
-The asymmetric and dumbbell asteroids produce distributions whose non-uniformity is limited to a factor of 2 or less for the harmonic and likelihood models.
+The dumbbell asteroid, like the asymmetric asteroid of figure \ref{fig:uniform-density-results}, produces distributions whose non-uniformity is limited to a factor of 2 or less for the harmonic and likelihood models.
 This non-uniformity is driven by error in the estimates of the density moments.
@@
 
-\include{appendices}
+%\include{appendices}
 

### 2022-04-15 code/density/display.py

@@ -54,6 +54,9 @@ def make_frame(densities, pos_array, axis_name, cmap, percentile, balance, z_ind
     fig = plt.figure()
     csection = densities[:,:,z_index]
     want_min, want_max = np.nanpercentile(densities, 1), np.nanpercentile(densities, percentile)
+    if cmap == 'Greys_r': # Uncertainty
+        want_min = 0
+        
     if balance:
         want_max = max(want_max, -want_min)
         want_min = -want_max
@@ -99,6 +102,10 @@ def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percenti
     ax.grid(False)
 
     want_min, want_max = np.nanpercentile(densities, 1), np.nanpercentile(densities, percentile)
+
+    if cmap == 'Greys_r': # Uncertainty
+        want_min = 0
+
     if balance:
         want_max = min(want_max, -want_min)
         want_min = -want_max

### 2022-04-19 paper/main.tex
Updated density adjoints

@@
   \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
-  +&\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
+  &+\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
   \end{split}
@@
 Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^T$ and the density distribution and uncertainty on density distribution are equal to
-\begin{equation}
-  \rho(\bm r) = \bm B(\bm r)^T A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^T A \Sigma_K A^T \bm B(\bm r).
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^*$ and the density distribution and uncertainty on density distribution are equal to
+\begin{equation}
+  \rho(\bm r) = \bm B(\bm r)^* A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^* A \Sigma_K A^* \bm B(\bm r).
   \label{eqn:unc-rho}
 \end{equation}
+where $A^*$ is the adjoint of $A$.
 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
-The standard deviation of the data is plotted as an uncertainty band in the residuals plot, but these do not capture covariance between data points.}
+  \includegraphics[width=0.6\textwidth]{figs/example-residuals.pdf}
+  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. Uncertainty bands are also shown.}
   \label{fig:example-residuals}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.85\textwidth]{figs/example-corner.png}
+  \caption{PPDs extracted from synthetic encounter data for the asymmetric reference asteroid.
+Samples from the MCMC fit are shown as individual points, and the contours enclose 1, 2, and 3$\sigma$ confidence regions.
+True values are shown as blue lines.}
+  \label{fig:example-corner}
 \end{figure*}
@@
 The fit results are clearly consistent with the data.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{figs/example-corner.pdf}
-  \caption{A corner plot for the fit results ten parameters to synthetic data simulated for an asymmetric reference asteroid.
-Marginal posterior PDFs for each parameter are shown (histograms) along with two-dimensional PDFs (contours).
-Individual points in the contours are samples from the MCMC fit, and the contours enclose 1, 2, and 3$\sigma$ of them.
-True values (which are zero here due to the parameters being displayed relative to the true values) are also shown (blue lines).}
-  \label{fig:example-corner}
-\end{figure*}
 
@@
 
-In this section, we discuss the physical properties of the asteroid encounter system (section \ref{sec:spin-evolution}), as well as the sensitivity of the density moment uncertainty to encounter properties (section \ref{sec:fit-uncertainty}), together with an analysis of advantages and disadvantages Jupiter encounters over Earth (section \ref{sec:jupiter-earth})Finally, we discuss the kinds of distributions produced by the density distribution extraction methods (section \ref{sec:density-compare}).
+In this section, we discuss the physical properties of the asteroid encounter system (section \ref{sec:spin-evolution}), as well as the sensitivity of the density moment uncertainty to encounter properties (section \ref{sec:fit-uncertainty}), together with an analysis of advantages and disadvantages Jupiter encounters over Earth (section \ref{sec:jupiter-earth}).
+Finally, we discuss the kinds of distributions produced by the density distribution extraction methods (section \ref{sec:density-compare}).
 
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.7\linewidth]{figs/nominal-data-sym.pdf}
-  \includegraphics[width=0.7\linewidth]{figs/nominal-data-asym.pdf}
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{figs/nominal-data-sym.pdf}
+  \includegraphics[width=\linewidth]{figs/nominal-data-asym.pdf}
   \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
@@
   \label{fig:example-data}
-\end{figure*}
+\end{figure}
 
@@
 The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
+
+Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
+These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
+The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
+These slope values express how much each parameter is dependent on $r_p$.
+It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
+The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
+The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
 
@@
 
-Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
-These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
-The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
-These slope values express how much each parameter is dependent on $r_p$.
-It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
-The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
-
 The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/scan-all-1.pdf}
+    \includegraphics[width=\linewidth]{figs/scan-all.pdf}
     \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/scan-all-2.pdf}
+    \includegraphics[width=\linewidth]{figs/scan-all.pdf}
     \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
@@
 (the weight of each map is set to one-tenth of the map's mean). This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-
+`'
 \begin{figure*}
   \centering
-  \includegraphics[width=0.8\textwidth]{figs/spin-pole.pdf}
+  \includegraphics[width=0.8\textwidth]{figs/spin-pole.png}
   \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.pdf}
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.png}
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.png}
   \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.

### 2022-04-20 paper/main.tex
Updated Updated uncertainty model

@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
 
@@
 \begin{figure*}
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-corr23.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/probe-space-ab-ab.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}
 
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/db-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/db-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/db-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/tet-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/tet-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/tet-lumpy.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
   \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/in-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/in-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/in-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/out-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/out-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/out-lumpy.pdf}\
+  \includegraphics[width=0.3\textwidth]{figs/in-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/in-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/in-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/out-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/out-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/out-lumpy.pdf}\
 
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
 

### 2022-04-21 paper/appendices.tex
Reviewed paper

--- 2022-04-14 paper/appendices.tex
@@
 
-\subsection{Parameters: density moments}
+\subsection{Density moments}
 \label{sec:moments}
@@
 This length can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
-Both equations \ref{eqn:klm} and \ref{eqn:am} should be computed in the body-fixed axes.
+Both equations \ref{eqn:am} and \ref{eqn:klm} should be computed in the body-fixed axes.
 
-Equations \ref{eqn:klm} and \ref{eqn:am} can be extended to the central body:
+Equations \ref{eqn:am} and \ref{eqn:klm} can be extended to the central body:
 \begin{equation}
@@
 
+The surface of a spherical asteroid with this rotational period and $a_\mathcal{A}$ rotates at $\SI{25}{\centi\meter\per\second}$ at the equator.
+The asymmetric and symmetric ellipsoids have maximum equatorial velocities of $\SI{36}{\centi\meter\per\second}$ and $\SI{27}{\centi\meter\per\second}$ respectively.
+
 We use the asymmetric ellipsoid in nearly all runs, due to the degeneracy induced in our model when $K_{22} = 0$.
 
-\section{The cadence cut-off}
-\label{app:cadence-tests}
+% \section{The cadence cut-off}
+% \label{app:cadence-tests}
 
-In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
+% In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
 We mentioned that this cadence cut-off is likely a function both of the rotational period of the asteroid and the time spent near perigee.
@@
 
-We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
+% We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
 Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference $P_\omega=9$ hr.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-  \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
+% \begin{figure}
+%   \centering
+%   \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
+%   \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
 Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-  \label{fig:cad-period}
-\end{figure}
+%   \label{fig:cad-period}
+% \end{figure}
 
-We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
+% We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
 Instead, we (un-physically) manipulate the speed at which the asteroid moves through the orbit.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-  \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
+% \begin{figure}
+%   \centering
+%   \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
+%   \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
 See text for the definition of $t_\text{spin}/t_\text{orbit}$.
 Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-  \label{fig:cad-speed}
-\end{figure}
+%   \label{fig:cad-speed}
+% \end{figure}
 
-Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
+% Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
 Those that show no cut-off (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cut-off $T_\text{cad} > 60$ min, which is off the plot.
@@
 
-The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
+% The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
 However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-vex} is) to study these regimes.
@@
 We only suggest this as a possibility, however, since light-curve analysis is beyond the scope of this paper.
-
-\section{Example fit results}
-\label{app:example}

### 2022-04-21 paper/main.tex
Reviewed paper

@@
 \usepackage{dsfont}
+\usepackage{siunitx}
 \usepackage{bm}
@@
   Knowledge of the interior distribution of an asteroid can reveal its composition and constrain its evolutionary history.
-However, most observations are not sensitive to interior structure.
-We investigate the degree to which asteroid interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for an rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
+However, most asteroid observational techniques are not sensitive to interior structure.
+We investigate the degree to which interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
+We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
 Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
-Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the quantity of near-pericentre data and the central body oblateness.
+Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the planet being encountered, the quantity of near-pericentre data, and the central body oblateness.
 Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
@@
 Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
-More encounter candidates are likely to be discovered in the future --- for Earth or other planets --- potentially by the Large-aperture Synoptic Survey Telescope (LSST) or global telescope networks such as the Las Cumbres Observatory (LCO).
+More encounter candidates are likely to be discovered in the future by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) or the Las Cumbres Observatory (LCO).
 Light curve analysis has been performed on many of these new asteroids to study their surface properties, but observations that are sensitive to the interior structure of the asteroid are rarer.
 
-However, tidal torque acting on an asteroid and perturbing its angular velocity during an encounter presents an opportunity to constrain the asteroid mass distribution.
+However, tidal torque acting on an asteroid and perturbing its angular velocity during an encounter presents an opportunity to constrain the interior mass distribution.
 Such angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus respectively.
@@
 This two-body generalized system has been studied to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-The success of this work is demonstrated by the recent extraction of moment of inertia ratios for Duende \cite{MOSKOVITZ2020113519}.
-However, density distribution information beyond the moment of inertia ratios have not yet been extracted for planetary encounters.
-More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these sub-dominant terms.
-
-In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system, using , and describe a simulation used to integrate the equation of motion and produce synthetic data of angular velocity over time (section \ref{sec:sim}).it to simulate a generic asteroid encounter of Earth.
-In section  \ref{sec:methods}, we then extract physical characteristics of the asteroid (specifically, density moments) from synthetic data via a Markov Chain Monte Carlo (MCMC) fit.
-We also describe methods to extract estimates of density distribution from these density moments.
-In section \ref{sec:results}, we demonstrate our fit process and evaluate our density distribution extraction methods on density moments extracted from fits to synthetic data.
-In section \ref{sec:discussion}, we measure the uncertainties in the Posterior Probability Distribution (PPD) of density moments as a function of various encounter parameters such as the observational uncertainty, encounter orbital parameters, asteroid physical properties, and more.
+One success of this work was the recent extraction of moment of inertia ratios for Duende \cite{MOSKOVITZ2020113519}.
+However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
+More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
+
+In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system which is quickly computable and valid to arbitrary order.
+In section \ref{sec:methods}, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts physical characteristics of the asteroid (specifically, density moments) from the fit data.
+We then describe three methods to generate full density distributions from the density moments.
+Section \ref{sec:results} demonstrates the efficacy of this spin-data-to-density-distribution pipeline and explores the key properties.
+Finally, in section \ref{sec:discussion}, we measure the uncertainties of the best-fitting parameter estimates as a function of various encounter properties to determine which properties most inhibit accurate extraction of density distributions.
 
@@
 
-In appendix \ref{app:eom}, we derive a novel equation for the tidal torque experienced by an asteroid in a two-body system, accurate to arbitrary order.
-The equation is written in terms of the asteroid ``length''
+Only some aspects of an asteroid's density distribution affect tidal torque interactions. These are the asteroid ``length'' 
 \begin{equation}
@@
 \end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are Euler angles expressing the orientation of the asteroid; and  $\mu_\mathcal{B}$ and $J_{\ell m}$ are the mass and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$ and $J_{\ell m}$ are the mass and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
+Throughout the paper, we also refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also discussed in appendix \ref{app:eom}.
 
 In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion.
-In section \ref{sec:uncertainty}, we define the uncertainty model used to add noise to the data, and we describe how PPDs for density moments were extracted from spin-pole data in section \ref{sec:fit}.
-Finally, we outline a general model to extract density distributions from density moments in section \ref{sec:general-density} and define specific model implementations in section \ref{sec:specific-density}
+In section \ref{sec:uncertainty}, we define the uncertainty model used to add noise to the data, and we describe how posterior probability distributions (PPDs) for density moments were extracted from spin-pole data in section \ref{sec:fit}.
+Finally, we outline a general model to extract density distributions from density moments in section \ref{sec:general-density} and define specific model implementations in section \ref{sec:specific-density}.
 
@@
 
-We built a custom simulation in C++ to produce angular velocity data as a function of time.
+We built a publicly accessible, custom simulation in C++ to produce angular velocity data as a function of time.
 This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
@@
 \end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
+The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
 The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
@@
 We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-We generally represent $\sigma_\theta > \sigma_\rho$ under the assumption that period is better constrained by light-curve data than spin pole.
+This width is related to the more physical uncertainty in asteroid period $\sigma_P$ by $\sigma_P=P \sigma_\rho$ for small $\sigma_\rho$.
 Explicitly, the probability density function (PDF) of $\rho$ is
@@
   \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-1, 1.8) node[anchor=center] {$\rho \Omega^*$};
+  \draw (-0.5, 2.5) node[anchor=center] {$\rho \Omega^*$};
 
@@
 \label{sec:fit}
-Given synthetic data, an Affine Invariant Markov Chain Monte Carlo (MCMC) Ensemble sampler was used to generate PPDs from flat priors.
+Given synthetic data, an Affine Invariant MCMC Ensemble sampler was used to generate PPDs from flat priors.
 We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
@@
 The other bounds were $|K_{3m}| < 1$.
+In general, spin data is most sensitive to $\gamma_0$ and $K_{2m}$, which we call the ``first-order parameters.'' We call $K_{3m}$ the ``second-order parameters.''
 
 The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low quality to resolve the parameters.
-$~10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
+The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low-quality to resolve the parameters.
+$\sim 10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
 
 Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
-It was found that only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
-Walkers were initialized near this local minimum, distributed with probability distributed as a Gaussian approximation of the likelihood, as determined via the inverse Hessian of the likelihood at the minimum.
+Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
+Ensemble walkers were initialized near this local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
 Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
-Therefore, a simpler simulation without the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find $K_{3m}$, with $\gamma_0$ and $K_{2m}$ fixed.
-This tiered minimization process motivates us to call $\gamma_0$ and $K_{2m}$ the ``first-order parameters'' and $K_{3m}$ the ``second-order parameters.''
-
-We further subdivided the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$.
-In practice, $f=2$ often led to success.
+Therefore, a simpler simulation without the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of the first-order parameters $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find the second-order parameters $K_{3m}$ with the first-order parameters fixed.
+
+We further improved the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$.
+In practice, $f=2$ often led to likelihood minima successfully found.
 The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
@@
 Here, we outline three different assumptions which constitute three models for extracting density distributions from density moments.
+All three of them are (partially) linear to facilitate computational ease and uncertainty propagation.
 One of them can be chosen, or another created, depending on what features are desired to be represented in the density distribution.
@@
 We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
-The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame.
-The $K_{\ell m}$ components are known in the body-fixed frame which aligns with the hybrid frame up to uncertainty in $\gamma_0$.
+The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame and the body-fixed frame aligns with the hybrid frame up to uncertainty in $\gamma_0$.
 We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
 
-The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit, removing the non-linearity induced by division by $a_\mathcal{A}$.
-Furthermore, since the system is independent of the total asteroid mass, we set $\mu_\mathcal{A}$ equal to an arbitrary constant which makes equation \ref{eqn:klm} linear in $\rho(\bm r)$.
-Similarly, the form of equation \ref{eqn:am} guarantees that $a_\mathcal{A}^2$ is linear in $\rho(\bm r)$.
+The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit and set $\mu_\mathcal{A}$ equal to an arbitrary constant since the system is independent of the total asteroid mass.
+Thus, equations \ref{eqn:am} and \ref{eqn:klm} guarantees that $K_{\ell m}$ and $a_\mathcal{A}^2$ are linear in $\rho(\bm r)$.
 Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
@@
 for a $m$-dimensional vector $\bm B(\bm r)$.
-($\bm B$ need not be linear in $\bm r$.) Thus, the defining equations of $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
-We further assume that the model describes a way to reverse this equation, to write
+($\bm B$ need not be linear in $\bm r$.) Thus, $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
+We further assume that the model describes a way to reverse the relationship between $K_{\ell m}$ or $a_\mathcal{A}^2$ and $\bm \Theta$ so that
 \begin{equation}
@@
 where $A$ is a matrix.
-Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$, which we say has $n$ dimensions.
-The order of this arrangement is irrelevant, as long as it is kept consistent.
-
-To propagate uncertainties from $\bm K$ to $\bm \Theta$ and therefore $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
-First, assume that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
+Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$ which we say has $n$ dimensions.
+The order of this arrangement is irrelevant as long as it is kept consistent.
+
+To propagate uncertainties from $\bm K$ to $\bm \Theta$ to $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
+Suppose that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
 Then
@@
 Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^*$ and the density distribution and uncertainty on density distribution are equal to
-\begin{equation}
-  \rho(\bm r) = \bm B(\bm r)^* A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^* A \Sigma_K A^* \bm B(\bm r).
+Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^\dagger$ and the density distribution and uncertainty on density distribution are equal to
+\begin{equation}
+  \rho(\bm r) = \bm B(\bm r)^\dagger A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^\dagger A \Sigma_K A^\dagger \bm B(\bm r).
   \label{eqn:unc-rho}
 \end{equation}
-where $A^*$ is the adjoint of $A$.
-
-The purpose of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+where $A^\dagger$ is the adjoint of $A$.
+
+The role of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
 Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
+Three examples of possible models are given below.
 
@@
 \label{sec:specific-density}
-In the following sections, three possible models for extracting density distributions from moments (i.e., choices of $\bm B(\bm r)$ and $A$ defined above) are given.
 
@@
 This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
-The choice of the density $\mathcal{L}$ is arbitrary, but the linearity of the model design outlined in the previous section will require a Gaussian likelihood.
+The choice of $\mathcal{L}$ is arbitrary, but a Gaussian likelihood will produce a linear model.
 
@@
 
-Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:klm} and \ref{eqn:am} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:klm} or \ref{eqn:am}, evaluated over the $i$th finite element.
+Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:am} and \ref{eqn:klm} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:am} or \ref{eqn:klm}, evaluated over the $i$th finite element.
 We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
@@
 \begin{equation}
-  A=M^+ = M^*(MM^*)^{-1}
+  A=M^+ = M^\dagger(MM^\dagger)^{-1}.
   \label{eqn:mpi-underdetermined}
 \end{equation}
-where $M^*$ is the adjoint of $M$.
 The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
@@
 
-Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^*$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
 
@@
 
-We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with zero Laplacian: $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
-We therefore call this model the ``harmonic'' model.
+We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
+We  call this  the ``harmonic'' model.
 The expansion of a harmonic function in spherical coordinates is given by
@@
 
-Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:klm} and \ref{eqn:am}, we get 
+Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:am} and \ref{eqn:klm}, we get 
 \begin{equation}
@@
 \begin{equation}
-  A=M^+ = (M^*M)^{-1} M^*
+  A=M^+ = (M^\dagger M)^{-1} M^\dagger 
   \label{eqn:mpi-overdetermined}
@@
 
-In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal, with entries 
-\begin{equation}
-  M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
-\end{equation}
-A non-spherical perturbation will introduce small off-diagonal entries to $M$.
+In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal. %, with entries 
+% \begin{equation}
+%   M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
+%\end{equation}
+A non-spherical perturbation will introduce small, off-diagonal entries of $M$.
 This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
@@
 
-The above two simple models produce smooth density distributions that generally extend non-uniformity over large regions.
-In this section, we define a more complicated model which identifies discrete regions differing from the overall density of the asteroid to best fit the measured density moments.
+The above two simple models produce smooth density distributions.
+In this section, we define a more complicated model which identifies discrete regions differing from the overall density.
 We call this model the ``lumpy'' model.
 
-Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid shape which is known in the form of $\mathds{1}(\bm r)$.
+Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid ``medium'' with known shape given by $\mathds{1}(\bm r)$.
 For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
 For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
-Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
-The displacement of the shape centroid from the centre of mass, which is the opposite of the net displacement of the discrete regions, is therefore observable from light curve analysis.
-The model therefore has $3(N-1)$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
-The sum of these degrees of freedom are displayed in table \ref{tab:lump-dof}.
-These degrees of freedom should be compared to the known density moments and $a_\mathcal{A}$, of which there are $(\ell_\text{max}+1)^2+1$.
-However, three of these are the centre of mass of the asteroid which is guaranteed to be correct, and one is the unconstrained total mass so the total number of known parameters is $(\ell_\text{max}+1)^2 - 3$, which is 13 when the second-order density moments are known and six when only $K_{2m}$ are known.
-We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$ known, so that the model is overdetermined.
+The model therefore has $3N$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
+The medium adds one additional degree of freedom for its mass, but its position is determined by knowledge of the surface $\mathds{1}(\bm r)$.
+The total number of degrees of freedom are displayed in table \ref{tab:lump-dof}.
+They should be compared to the number of known asteroid parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, which is $(\ell_\text{max}+1)^2+1$, which is 17 when the second-order density moments are known and 10 when only $K_{2m}$ are known.
+We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$, so that the model is overdetermined.
+
+%Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
+The displacement of the shape's centroid from the centre of mass, called $\bm x_0$, is therefore observable from light curve analysis and therefore constrains $\bm x_i$ so that the asteroid centre of mass lies on the origin.
 
@@
         &  & 1  & 2  & 3  \\ \hline 
-        & 1& \cellcolor{black}\color{white} 2 & \cellcolor{gray}\color{white} 7 & \cellcolor{gray}\color{white} 12\\
-    $d$ & 2& \cellcolor{black}\color{white} 5 & \cellcolor{gray}\color{white} 13 & 21 \\
-        & 3& \cellcolor{gray}\color{white}  7 &  17 &  27 \\
+        & 1& \cellcolor{black}\color{white} 6 & \cellcolor{gray}\color{white} 11 & \cellcolor{gray}\color{white} 16\\
+    $d$ & 2& \cellcolor{black}\color{white} 9 & \cellcolor{gray}\color{white} 17 & 25 \\
+        & 3& \cellcolor{gray}\color{white}  11 &  21 &  31 \\
     \hline \hline
@@
   \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
-The configurations with $D \leq$ the six known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 13 parameters including $K_{3m}$ parameters are coloured gray.}
+The configurations with $D \leq$ the 10 known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 17 parameters including $K_{3m}$ parameters are coloured gray.}
   \label{tab:lump-dof}
@@
 \end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively, but integrated over the $i$th lump.
-Crucially, note that we set normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ in equations \ref{eqn:klm} and \ref{eqn:am} equal to the values for the entire asteroid, not their counterparts for each lump.
-The zero-indexed parameters indicate the moments of the uniform-density asteroid medium surrounding the lumps.
+where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively integrated over the $i$th lump, but we set the normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ equal to the values for the entire asteroid, not their counterparts for each lump.
+The zero-indexed parameters indicate the moments of the medium.
 The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
@@
 Its volume is constrained by $a_i^2$.
-These values map directly onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
-
-Note that if $\bm x_i$ is known, then equation \ref{eqn:translate-klm} are linear in $K_{\ell m}^i$ and $a_i^2$.
+These values map onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
+
+Fixing $\bm x_i$, equation \ref{eqn:translate-klm} is linear in $K_{\ell m}^i$ and $a_i^2$.
 Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
-Note that the $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the already-known surface shape.
-
-This model's strategy will be to choose $\bm x_i$ and $\mu_i$ via a non-linear process, then fit for the values $K_{\ell m}^i$ and $a_i^2$ using the linear format described in section \ref{sec:general-density}.
-The constraints on $\bm x_i$ is
-\begin{equation}
-  \sum_{i=1}^N \bm x_i \mu_i + \mu_0 \bm x_0 = 0
+The $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the surface shape.
+
+We use a non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described in section \ref{sec:general-density}.
+We must incorporate the centre-of-mass and total-mass constraints
+\begin{equation}
+  \mu_0 \bm x_0 + \sum_{i=1}^N \bm x_i \mu_i = 0 \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}
   \label{eqn:lump-constraints}
 \end{equation}
-where $\bm x_0$ is the known displacement of the centroid of the asteroid model from the centre of mass.
 There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-The overall mass of the asteroid is $\mu_\mathcal{A} = \mu_0 + \sum_{i=1}^N \mu_i$, and has been set, so we may eliminate $\mu_0$ from equation \ref{eqn:lump-constraints}.
-The constraint is now a function of $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+Combining both constraints in equation \ref{eqn:lump-constraints}, we can fix $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+
 The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
-We therefore solve for $\bm x_i$ and $\mu_i$ to yield an $M$ with close solutions.
+We therefore solve for $\bm x_i$ and $\mu_i$ by minimizing the difference between the known density moments and the output of the model.
 This is done by minimizing
@@
 \end{equation}
-which is the difference between $\bm K$ resulting from the model and the true $\bm K$.
-Here, $\mathds{1}$ is the identity matrix.
-Then $A=M^+$ defines the model.
+where $\mathds{1}$ is the identity matrix.
 We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
-If the resulting density distribution is somehow excluded (it predicts negative density distributions, the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
+If the resulting density distribution is somehow excluded (it predicts negative density distributions or the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
 
@@
 \subsection{Density moment extraction}
-To demonstrate the success of our fit process, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
+\label{sec:example-fit}
+To demonstrate our fit process, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
 The fit results were consistent with the true density moments, and produced consistent data.
@@
 
-Figure \ref{fig:example-residuals} shows the spin data with uncertainty added.
-Data simulated given the best-fitting density moments (the mean of the PPDs) is overlaid in the top pane and the residuals are shown the bottom pane.
+Figure \ref{fig:example-residuals} shows the spin data with noise added.
+The best-fitting model is overlaid in the top pane and residuals are shown the bottom pane.
+Specifically, we show the model whose parameters are the means of the PPDs.
 Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
@@
 Note that the true parameters usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-The PPDs are generally Gaussian and no degeneracy between fit components is visible.
+The PPDs are generally Gaussian and sometimes show correlation between parameters, but no continuous degeneracy occurs.
 We performed 48 independent minimizations of the likelihood before the MCMC fit began, each with an initial point chosen randomly in the parameter space.
-All converged to the same minimum, further showing that the model lacks degeneracy.
+All converged to the same minimum, demonstrating that the model lacks discrete degeneracy as well.
 
@@
 To demonstrate the success of our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
-These distributions were made given the density moment PPDs extracted in the previous section, with $a_\mathcal{A}$ fixed.
+These distributions were made given the density moment PPDs extracted above, with $a_\mathcal{A}$ fixed.
 The surface is fixed as a triaxial ellipsoid with semi-axis lengths such that the true values of $K_{\ell m}$ are consistent with uniform density (equation \ref{eqn:ellipsoid-axes}).
@@
 Also in each pane of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, but for the harmonic and the lumpy models, they express the degree to which the extracted moments cannot be represented with harmonic or lumpy distributions respectively.
-
-The likelihood and harmonic models produce mostly the same density distributions.
+This difference is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
+The harmonic and lumpy models have no such guarantee, however.
+
+The likelihood and harmonic models produce nearly identical density distributions.
 This is generally true for uniform density asteroids, which have harmonic density distributions.
 Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
-This similarity lends confidence that the models produced are truly representative of the asteroid since they are produced via two independent methods.
-
-The distributions' non-uniformity is limited for the harmonic and likelihood models.
-This non-uniformity is driven by error in the estimates of the density moments.
-Note that most of the asteroid has density close to one in both cases, with densities of 40\% or 160\% of the mean attained only in small regions.
+This similarity lends confidence to both models, because if one were unexpectedly biased towards certain distributions, the other would have to be equally biased in the same way in this case to produce the same distribution, which appears unlikely given that the models share little in common.
+
+The distributions are non-uniform for the harmonic and likelihood models (driven by error in the estimates of $K_{3m}$), but the non-uniformity is limited.
+Note that most of the asteroid has density close to the mean density (one) in both cases, with densities of 40\% or 160\% of the mean attained only in small regions.
 The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
-However, it does not produce a density distribution consistent with those extracted from spin data (i.e., $\Delta K_{\ell m}$ is usually large).
-This is because the lump found extends outside the asteroid, violating the assumptions of the model --- a sign that the lump found does not really exist inside the asteroid.
-
-The size of uncertainty is such that the density distribution is consistent with uniform at most points for the harmonic and likelihood models (within 1-2$\sigma$), with a small number of low-uncertainty regions that are less consistent with uniform.
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
+However, it does not produce a density distribution consistent with the moments extracted from spin data (i.e., $\Delta K_{\ell m}$ is large).
+This is because the lump found extends outside the asteroid, violating the assumptions of the model.
+This is a sign that the lump found does not really exist inside the asteroid.
+
+The size of uncertainty is such that the density distribution is consistent with uniform at most points for the harmonic and likelihood models (within 1.5$\sigma$).
+Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
 
@@
 \label{sec:discussion}
-
-In this section, we discuss the physical properties of the asteroid encounter system (section \ref{sec:spin-evolution}), as well as the sensitivity of the density moment uncertainty to encounter properties (section \ref{sec:fit-uncertainty}), together with an analysis of advantages and disadvantages Jupiter encounters over Earth (section \ref{sec:jupiter-earth}).
-Finally, we discuss the kinds of distributions produced by the density distribution extraction methods (section \ref{sec:density-compare}).
 
@@
 
-To choose the initial values of $\gamma_0$, $K_{20}$, and $K_{22}$, spin data for the reference asteroids of appendix \ref{app:reference-configs} was first generated.
-Then $\gamma_0$, $K_{20}$, and $K_{22}$ were re-extracted via the fit described in section \ref{sec:fit}.
-The population's values for these parameters were PPD-distributed.
-However, the PPD distribution was widened by a factor of 1000 to make the band widths visible.
+The initial values of $\gamma_0$, $K_{20}$, and $K_{22}$ were distributed proportional to the PPDs extracted via the MCMC fit shown in section \ref{sec:example-fit}.
+The PPDs were widened by a factor of 1000 to make the band widths visible.
 Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
@@
 The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
-The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) vary within the population, showing that they can be used to constrain $K_{22}$ and $K_{20}$.
-
-\subsection{Dependence of parameter uncertainty on encounter parameters}
+The spin data at perigee is informative and shows non-trivial behaviour.
+After perigee, the asteroid population tumbles according to torque-free precession with different oscillation periods.
+This dramatically increases the spread of angular velocities within the distribution and allows for more precise refinement of the density moments.
+The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) can be used to constrain $K_{22}$ and $K_{20}$, while the phase is set by the asteroid dynamics near perigee and therefore constrains the higher-order terms.
+
+\subsection{Dependence of parameter uncertainty on encounter properties}
 \label{sec:fit-uncertainty}
-Parameter precision of 1$\sigma$ is defined such that 68.27\% of the PPD lies within 1$\sigma$ of the mean of the PPD.
-2$\sigma$ is defined likewise for 95.45\% of the PPD.
-The PPDs are usually roughly Gaussian, so that the upper and lower error bars are usually roughly equal and 1$\sigma$ is approximately the standard deviation of the PPD.
+
+In this section, we discuss how the precision of the best-fitting density moments is affected by various encounter properties.
+We call this precision ``posterior uncertainty,'' or $\sigma(K_{\ell m})$, defining 1$\sigma$  posterior uncertainty as the range containing 68.27\% of the PPD centred on the median.
+2$\sigma$ posterior uncertainty is defined likewise for 95.45\% of the PPD.
+These are roughly equivalent to 1 or 2 times standard deviation of the PPD respectively.
 In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-
-\subsubsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-The orbit can be rotated to the $\unit X \unit Y$-plane, as mandated by our coordinate definitions, by changing the density moments of the central body.
-Since $J_{00}$ is unchanged by this rotation and $J_{1m}=0$, the orbit orientation is irrelevant until the $J_{2m}$ terms of equation \ref{eqn:tidal-torque}, and we do not investigate them here.
-
-We parametrize the shape of the orbit by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ confidence intervals are displayed in figures \ref{fig:scan-vex} for $v_\infty$ and \ref{fig:scan-perigee} for $r_p$.
-
-Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also smaller-scale oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee, so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.
-This effect explains why these small-scale oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
-
-Figure \ref{fig:scan-perigee} shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the reference 0.01 limit.
-At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
-Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
-The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
-
-Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
-These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
-The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
-These slope values express how much each parameter is dependent on $r_p$.
-It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
-The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
-
-\begin{table}
-  \centering
-  \begin{tabular}{l|c}
-    \hline
-    Parameter & $\alpha$ \\ \hline
-    $\gamma_0$ & $2.05$ \\
-    $K_{22}$ & $5.47$ \\
-    $K_{20}$ & $5.47$ \\ \hline
-    $\Re K_{33}$ & $3.35$ \\
-    $\Im K_{33}$ & $3.37$ \\
-    $\Re K_{32}$ & $3.05$ \\
-    $\Im K_{32}$ & $3.27$ \\
-    $\Re K_{31}$ & $3.53$ \\
-    $\Im K_{31}$ & $4.02$ \\
-    $K_{30}$ & $5.75$ \\ \hline
-  \end{tabular}
-  \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
-  \label{tab:scan-perigee-alpha}
-\end{table}
-
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of large $m$ corresponding to low uncertainty is a general trend and will be seen in the following sections as well.
-
-The very strong dependence of $\sigma$ on $r_p$ makes this analysis only to extract second-order moments on close encounters.
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
-The first-order moments can still be extracted at much larger perigee distances in our model.
 
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/scan-all.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
-The vertical dashed line indicates the reference asteroid values of the parameters.
+    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+The vertical dashed line indicates the reference asteroid values.
 The red vertical lines indicate when $\sigma =0.01$.}
@@
     \centering
-    \includegraphics[width=\linewidth]{figs/scan-all.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of various encounter parameters (\textit{columns}).
-The vertical dashed line indicates the reference asteroid values of the parameters.
+    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, rotational period, observational cadence, and data gap at perigee.
+The vertical dashed line indicates the reference asteroid values.
 The red vertical lines indicate when $\sigma =0.01$.}
@@
     \label{fig:scan-period}
-    \label{fig:scan-gap}
+    \label{fig:observation-gap}
     \end{figure}
@@
 
+There is no clear threshold above which posterior uncertainty is ``too high.'' However, most asteroid distributions tested in this paper have $K_{\ell m} \lesssim 0.01$.
+We therefore call $\sigma(K_{\ell m}) \approx 0.01$ the ``posterior uncertainty threshold,'' beyond which $K_{\ell m}$ are unresolved.
+This should be understood as a rule of thumb and not a precise statement.
+
+\subsubsection{Orbital elements}
+\label{sec:scan-orbit}
+A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
+They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
+We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
+Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ posterior uncertainties are displayed in figure \ref{fig:scan-vex}.
+
+Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$.
+This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
+There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
+(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) This effect explains why these small-scale oscillations have the same period for all parameters.
+Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
+
+The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
+For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the 0.01 threshold.
+At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
+Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
+The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
+
+%Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
+These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
+The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
+These slope values express how much each parameter is dependent on $r_p$.
+It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
+The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
+The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
+
+% \begin{table}
+%   \centering
+%   \begin{tabular}{l|c}
+%     \hline
+%     Parameter & $\alpha$ \\ \hline
+%     $\gamma_0$ & $2.05$ \\
+%     $K_{22}$ & $5.47$ \\
+%     $K_{20}$ & $5.47$ \\ \hline
+%     $\Re K_{33}$ & $3.35$ \\
+%     $\Im K_{33}$ & $3.37$ \\
+%     $\Re K_{32}$ & $3.05$ \\
+%     $\Im K_{32}$ & $3.27$ \\
+%     $\Re K_{31}$ & $3.53$ \\
+%     $\Im K_{31}$ & $4.02$ \\
+%     $K_{30}$ & $5.75$ \\ \hline
+%   \end{tabular}
+%   \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
+%   \label{tab:scan-perigee-alpha}
+% \end{table}
+
+The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
+Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
+This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend and will be seen in the following sections as well.
+
+The very strong dependence of $\sigma$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters (5-20 Earth radii).
+Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
+The first-order moments can still be extracted at much larger perigee distances in our model.
+
 \subsubsection{Observational Uncertainty}
 \label{sec:scan-uncertainty}
-There are two parameters, $\sigma_\theta$ and $\sigma_\rho$, which govern the observational uncertainty of the data set (defined in section \ref{sec:uncertainty}).
-Rather than explore the full space spanned by these two values, we measure how parameter uncertainties depend on the product of uncertainties $\sigma_\theta\sigma_\rho$ (with the radio fixed), and the ratio $\sigma_\rho / \sigma_\theta$ (with the product fixed).
-
-We choose these metrics because we generally expect that the parameter uncertainty $\sigma$ be proportional to the observational uncertainty, but whether the dependence is stronger on $\sigma_\theta$ or $\sigma_\rho$ is not immediately clear.
-We get around this problem by varying $\sigma_\theta$ and $\sigma_\rho$ together and fixing their ratio, and measuring the posterior uncertainty $\sigma$, with $\sigma/\sigma_\theta$ shown in figure \ref{fig:scan-product}.
-Indeed, we find that $\sigma \propto \sigma_\theta$ almost exactly, and since $\sigma_\rho / \sigma_\theta$ is fixed, we also have $\sigma \propto \sigma_\rho$.
-For large $\sigma_\theta \sigma_\rho$, the proportionality fails, but this is because $\sigma(K_{30}) \approx 1$ which fills the prior.
-Uncertainty cannot increase beyond this value.
-
-We also investigate the dependence of posterior uncertainty on $\sigma_\rho / \sigma_\theta$ with $\sigma_\theta \sigma_\rho$ fixed in figure \ref{fig:scan-ratio}.
-If we simply had $\sigma \propto \sigma_\theta \sigma_\rho$, then $\sigma$ would have no dependence on $\sigma_\rho / \sigma_\theta$.
-Any deviation from constant $\sigma$ shown in the figure therefore reveals some additional dependence in the model on one of the observational uncertainties.
-
-Indeed, figure  \ref{fig:scan-ratio} shows increased uncertainty when $\sigma_\rho/\sigma_\theta$ is large, so that $\sigma$ depends more on $\sigma_\rho$ than on $\sigma_\theta$.
-We summarize this pattern by stating that, if the observer had to choose between better precision on the period or on the spin pole of the data, they should choose period.
-This is fortunate for observers since, \jtd{I want to say that precision on the period is better constrained by light curve analysis, but I do not know enough about light curve analysis to be sure.}
-
-Another conclusion that can be drawn from figure \ref{fig:scan-ratio} is that $\sigma(\sigma_\rho/\sigma_\theta)$ is proportional for all $K_{\ell m}$.
-The proportionality constant shows the same dependence on $\ell$ and $m$ mentioned previously.
-The proportionality is broken near $\sigma \approx \pm 1$, where $\sigma$ fills the prior.
-
-The location of the $\sigma > 0.01$ limit demonstrates the great influence of observational precision on fit uncertainty; increasing $\sigma_\theta \sigma_\rho$ or $\sigma_\rho / \sigma_\theta$ by even a small amount raises $\sigma(K_{3m}) > 0.01$ in most cases.
+Two parameters, $\sigma_\theta$ and $\sigma_\rho$, govern the observational uncertainty of the data set.
+These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
+Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole ($\sigma_\theta$) or uncertainty in period ($\sigma_\rho$) more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
+This dependence is displayed in figure \ref{fig:scan-theta}.
+
+For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
+The $K_{30}$ parameter reaches the $\sigma(K_{30})\approx 0.01$ threshold at $\sigma_\theta = 0.032\ \text{radians} \approx 2^\circ$ when $\sigma_\rho$ is held fixed, whereas the other parameters reach the threshold between $8^\circ$ and $45^\circ$.
+The $K_{2m}$ parameters are never reach the $\sigma(K_{\ell m})$ threshold, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
+
+If $\sigma_\rho$ is allowed to vary, then $K_{30}$ reaches the threshold at $\sigma_\rho \approx \num{2.8e-7}$, and the other parameters reach the threshold at $\sigma_\rho \approx 1.2-\num{8.6e-6}$.
+These correspond to uncertainty in period of roughly milliseconds to seconds.
+At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
+Otherwise, posterior uncertainty is proportional to $\sigma_\rho$.
+
+These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period $\sigma_\rho$ in our analysis.
+To accurately measure density moments, very accurate rotational period estimates would have to be made every cadence.
+However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different rotational velocity measurements.
+If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
 
@@
 
-The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the uncertainties in extracted density moments $\sigma$.
-Here, we only investigate the sensitivity of $\sigma$ to the first-order parameters and $a_\mathcal{A}$.
-The $K_{2m}$ moments can therefore also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
-
-In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ confidence intervals as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
+The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the posterior uncertainties.
+Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
+The $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
+
+In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
 We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
@@
 The latter is expected due to the $1/c$ dependence.
-As for the former, this correlation could likely be removed by an alternate parametrization, reducing uncertainties in the shape parameters.
 
@@
 On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
-The vertical axis is shown in log space, meaning that the average of the upper and lower error bars of $\sigma$ is shown instead of showing both as is done in other figures.
-
-As was mentioned in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
+As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
 The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
@@
 This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
-(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma$.
+(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma(K_{\ell m})$.
 It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is very unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
 
-For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius, which was mentioned in section \ref{sec:moments} and explicitly shown in equation \ref{eqn:ellipsoid-axes}.
+For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius.
 In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
@@
 
-We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is slightly exceeded).
+%We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
+
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is exceeded).
 However, shorter cadence almost always leads to lower uncertainties.
@@
 That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
-However, $K_{3m}$ are not extractable from precession data alone.
-We are therefore curious as to how our posterior uncertainties change due to lack of data during the encounter perigee.
+However, $K_{3m}$ does not affect the precession periods (though they do affect the phase).
+We are therefore curious as to how our posterior uncertainties change due to lack of perigee data.
 
@@
 To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
-We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma$ in figure \ref{fig:observation-gap}.
+We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
 
@@
 
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma$ on cadence $\Delta t$.
+Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma(K_{\ell m})$ on cadence $\Delta t$.
 They also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
-This suggests that the factors that govern uncertainty due to cadence (appendix \ref{app:cadence-tests}) also may govern sensitivity to lack of data at perigee in a similar way.
+This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
 
@@
 
-In figure \ref{fig:scan-spin}, we display 1$\sigma$ uncertainties for all parameters as a function of the direction of $\bm \Omega_0$, mapped onto the unit sphere in the inertial frame.
+In figure \ref{fig:scan-spin}, we display 1$\sigma$ posterior uncertainties as a function of the direction of $\bm \Omega_0$ mapped onto the unit sphere in the inertial frame.
 Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
 To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
-The average is weighted such that the uncertainty map for each parameter contributes an equal amount
-(the weight of each map is set to one-tenth of the map's mean). This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-`'
+The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each map is set to one-tenth of the map's mean).
+This average map is presented in two different projections to allow data at $\unit Z$ to be read.
+
 \begin{figure*}
@@
 We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
-Then, since $\bm \omega_0 \parallel \unit z$ in the body-fixed frame as an initial condition (section \ref{sec:sim}), we have that $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
+Then $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
 
@@
 Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
-Also, $\tau_z$ affected by fewer parameters than $\tau_x$ or $\tau_y$.
-Both of these are reasons why $\bm \tau \parallel \unit z$ might inhibit precise fits to spin data.
-If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma$.
+If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.
 
 It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma ~0.01$ benchmark.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma$ (figure \ref{fig:scan-spin-avg}).
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{\ell m}) \approx 0.01$ threshold.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
 
@@
 
-We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma$.
-The dynamical time scales $r_p/v_\infty$ and $\mu_\mathcal{B} / (r_p v_\infty)$ have already been mentioned in the context of the cadence cut-off (section \ref{sec:scan-cadence}), and the ratio between them and $P_\omega$ in principal may affect $\sigma$.
-In figure \ref{fig:scan-period}, we show $\sigma$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-
-Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
+We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma(K_{\ell m})$.
+In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$ for a range of periods typical of NEOs.
+Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
 But a large-scale trend is also visible in many parameters.
@@
 
-The most severe effect of period on $\sigma$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
+The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
 The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids still have better uncertainty.
+It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids have better uncertainty.
 
@@
 The effect of central body oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have little effect on the asteroid.
+We expect these parameters to have small, but noticeable effect on the asteroid.
 
@@
 For simplicity, we use this equatorial orbit case.
-If the orbit is non-equatorial, the other $J_{2m}$ terms will be non-zero.
 Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
 The next order of precision after this oblateness approximation is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and  non-ellipsoid corrections to the central body shape.
-
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for $\sigma(\epsilon)$.
+We do not consider these extra factors.
 
@@
 
-The figure demonstrates a small dependence of $\sigma$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
+The figure demonstrates a small dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
 Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
-The best-fitting lines match the uncertainties well, and they have slope of $(\Delta \sigma / \sigma_{\epsilon=0}) / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
-The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them here.
+The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
 
 Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the precision of the fit parameters (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+These two parameters also affect the posterior uncertainty (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
 
@@
 Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass.
-Since $J_{20}$ is a second moment, this effect is magnified for large distances of the mass from the central body centre of mass (though the effect is not quite quadratic because $a_\mathcal{B}$ also increases for large distances, and $J_{20}$ is divided by $a_\mathcal{B}^2$).
-This process is only valid when the asteroid never passes inside the moon's orbit.
-
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
 As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
-Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about one quarter.
+Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about two.
 
@@
 The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
+The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in section \ref{sec:scan-orbit}, so we keep it at the reference value.
+% We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
 The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
 The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
-
-Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
+%Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
 We therefore do not distinguish between the two cases further.
@@
     \hline 
-    $K_{\ell m}$ & $\sigma_\text{Jupiter}/\sigma_\text{Earth}$\\ \hline 
+    $K_{\ell m}$ & $\sigma(K_{\ell m})_\text{Jupiter}/\sigma(K_{\ell m})_\text{Earth}$\\ \hline 
     $\gamma_0$ & 1.6 \\
@@
 
-The $K_{\ell 0}$ components differ in that $\sigma_\text{Jupiter}/\sigma_\text{Earth}$ is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
+The $K_{\ell 0}$ components differ in that the posterior uncertainty increase for a Jupiter encounter over an Earth encounter is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
 In fact, $K_{30}$ essentially fills the prior.
-The special properties of $K_{\ell 0}$ have been analysed noted before, in that they are always more uncertain than other moments and are particularly uncertain in regimes where the asteroid does not tumble after the perigee.
+In section \ref{sec:scan-spin}, we noted that $K_{\ell 0}$ is particularly uncertain when the asteroid does not tumble after the perigee.
 In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
@@
 It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
-Other effects, such as a change in the physical properties of the encountering asteroids, may also affect the fit uncertainties.
-
-Table \ref{tab:jupiter-uncertainty} shows that an encounter with Jupiter yields less precise posteriors than an encounter with Earth, all else being equal.
-However, these selection biases will cause more large-$a_\mathcal{A}$ and small-$r_p$ asteroids to encounter Jupiter, and therefore yield increased precision.
-Which of these contradicting effects dominates is not immediately clear, and depends on the specific asteroid population near Jupiter.
-
-\subsection{Comparisons between density models}
+Other effects, such as a change in the physical properties of the encountering asteroids or decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
+Which of these contradicting effects dominates is not immediately clear, and depends on the asteroid population near Jupiter and the observation method.
+
+\subsection{Comparisons between density distribution models}
 \label{sec:density-compare}
 
-To test the properties of the three density models defined in section \ref{sec:specific-density}, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
-Density moments are extracted via our fit process and density distributions extracted by the three above methods.
-Below, we compare the resulting distributions to understand the performance of the extraction methods.
-
-\subsubsection{Uniform density test asteroids}
+To test the properties of the three density models defined in section \ref{sec:specific-density} to extract density distributions from density moments, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
+In all cases, the density moments are extracted via our fit process.
+Below, we compare the resulting distributions to understand the performance of the density distribution models.
+
+\subsubsection{Uniform density asteroids}
 
@@
   \centering
+  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
+
   \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
@@
   \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
 
@@
   \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The asteroid shapes are, from top to bottom, the reference symmetric asteroid, the dumbbell model, and a tetrahedron.
+The asteroid shapes are, from top to bottom, a dumbbell, the symmetric reference asteroid, and a tetrahedron.
 Density is normalized so that mean density is one.
@@
 
-From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions.
-This is generally true for uniform density asteroids, which have harmonic density distributions.
+From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
 Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
-This similarity lends confidence that the models produced are truly representative of the asteroid since they are produced via two independent methods.
-
-The dumbbell asteroid, like the asymmetric asteroid of figure \ref{fig:uniform-density-results}, produces distributions whose non-uniformity is limited to a factor of 2 or less for the harmonic and likelihood models.
-This non-uniformity is driven by error in the estimates of the density moments.
-Note that most of the asteroid has density close to one in both cases, with the factor of two reached only by small regions.
-The lumpy model yields a much more uniform distribution, because it is designed to produce uniform lumps.
-Note that its uncertainty $\Delta K_{\ell m}$ is usually large, both because the model is severely overdetermined (it has 2 degrees of freedom) and because the lump found extends outside the asteroid, violating the assumptions of the model.
-This is a sign that the lump found does not really exist inside the asteroid.
+Also like section \ref{sec:asym-density}, the dumbbell asteroid produces largely uniform distributions except in a few small regions, and the lumpy model generates clearly incorrect results indicating that no lump is present.
 
@@
 In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the small and ill-constrained $K_{3m}$ components.
+To avoid negative density distributions, the likelihood model could be adjusted to use, for example, a multivariate log-normal distribution.
+However, the model would no longer be linear.
 
@@
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
-
-From these examples, we may draw the conclusions that all three models produce density distributions generally consistent with uniform for uniform asteroids.
-The most likely distributions (i.e., the ones shown in the figures) are themselves mostly uniform, but can still produce non-uniformities as large as a factor of 2 in certain regions due to uncertainty in $K_{\ell m}$.
-Asymmetric asteroids such as the dumbbell and the asymmetric reference asteroids yield the best results because they have $K_{22} \neq 0$ and therefore do not suffer from degeneracy in initial orientation.
-Finally, the lumpy model can generally be ruled out in these cases because it produces unphysical results.
+\jtd{Confirm}
 
@@
 
-\subsubsection{Spherical shape test}
+\subsubsection{Spherical asteroids}
 \label{sec:spherical-density}
-We test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by obtaining density moments from an ellipsoidal asteroid encounter and extracting density distributions assuming a spherical shape.
-We do this for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
+In this section, we test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by assuming a spherical shape for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
 
@@
 Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
-However, now they both produce negative density distributions for both asteroid shapes.
-(In the previous section, only the symmetric model did.) This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
+However, now even the asymmetric asteroid (with low uncertainty in $K_{\ell m}$) produces negative densities.
+This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
 In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top and bottom of the figure).
 The density is large at large $|y|$ (front right and back left in the figure).
-Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
+Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density-results} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
 In other words, the shape can be corrected by extending it where density is large and retracting it where density is low.
@@
 
-In short, severely incorrect shape estimates can be caught for all three models by negative predicted densities or by the failure of the density distribution model to match the extracted density moments.
-The shape can be corrected by extending it where the density distribution is high and retracting it where the density distribution is low.
-
-\subsubsection{Nonuniformity test}
+\subsubsection{Nonuniform asteroids}
 \label{sec:non-uniform-density}
@@
 For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models do give similar results.
-Comparing the centre-weighted asteroid and the edge-weighted asteroid distributions, one can see that the centre-weighted case indeed places more mass in the centre of the asteroid shape for the harmonic and likelihood models, while the edge-weighted asteroid places mass at the edges.
-
-Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the precise density distributions are inaccurate because they predict negative densities.
-This might be addressed for the likelihood model by selecting a likelihood that strongly disfavours negative densities, such as a log-normal distribution.
-A log-normal likelihood however would no longer yield a linear model, so we do not use one here.
+However, the two models do give qualitatively similar results.
+Furthermore, the centre-weighted density distribution indeed contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models, while the edge-weighted asteroid contains mass at the edges.
+Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
 
 Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative estimate of the density distribution of the asteroid which is useful for interpreting the other two models.
+Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
 This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
 
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ if (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
+The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ when the density moments are redundant with the asteroid shape; specifically, when (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
 (1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
@@
 
-\subsubsection{Lump test}
-
-Finally, we test an asteroid with a discrete change in density distribution (for example, a boulder), of the kind that the lumpy model is designed to detect.
-We place a spherical mass of density six times the density of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
-The rest of the asteroid we set to uniform density.
-The density distributions found by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
+\subsubsection{Lumpy asteroids}
+
+Finally, we test an asteroid with a discrete change in density distribution (for example, a rock of high density), of the kind that the lumpy model is designed to detect.
+We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
+Both the mass and the medium have uniform density.
+The distributions extracted by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
 
@@
 
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail completely to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
-
-The failure of these models to find lumps is expected, since $K_{\ell m}$ is most sensitive to non-uniformities of characteristic size $\pi/(\ell + 1)$ radians in the polar direction, and $2\pi / (|m|+1)$ in the azimuthal direction by the definition of $Y_{\ell m}$.
-This lump is too small to be resolvable by $K_{3m}$, so we do not expect most models to find it.
-
+We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump.
+There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect.
+Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
+
+The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edge of the lump.
 However, the lumpy model computes the location and density of the mass very well.
 Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
-This in turn causes a 70 m inaccuracy in the lump's radius.
-Nevertheless, the accuracy is still good compared to other models, and we conclude that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned in the previous section for distributions with $K_{\ell m}$ proportional to the asteroid shape's moments).
-But the ability of the lumpy model to place a lump does not guarantee the lump to actually exist, as was seen in the other asteroid distributions analysed here.
+This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
+Nevertheless, it seems that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned above when the density moment data is redundant with the asteroid shape).
+But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in the above sections.
 
 \section{Conclusions}
-
-We assess the feasibility of extracting density moments and density distributions for a general asteroid encounters, and ask what encounter properties are necessary to obtain the most information about asteroid density.
 
@@
 The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
-
-We built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
+We then built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
 We observe the following general properties of the moments:
 \begin{enumerate}
-  \item The second-order moments $K_{3m}$ are generally a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is the asteroid radius and $r_p$ is the perigee distance.
+  \item Extracted density moments are generally more precise when the asteroid leaves the encounter tumbling.
+  \item The second-order moments $K_{3m}$ are roughly a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is proportional to the asteroid radius and $r_p$ is the perigee distance.
 For our reference asteroid, this fraction was about $10^{-5}$.
-  \item Of the seven second-order moments, those that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
+  \item The second-order moments that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
 It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
-  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates, but a non-zero oblateness does not greatly increase the precision of the extracted moments except perhaps when a moon is present.
+  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates.
 \end{enumerate}
 
-We assessed the posterior uncertainty generated by the fit process by adjusting eleven parameters of an asteroid on an Earth encounter. The main conclusions are listed below.
+We assessed the posterior uncertainty generated by the fit process by adjusting various properties of an asteroid on an Earth encounter. The main conclusions are listed below.
 
 \begin{enumerate}
-  \item Highly precise rotational velocity data is required to produce precise second-order moments.
-Especially the uncertainty on the asteroid rotational period must be small compared to the uncertainty on asteroid spin pole.
+  \item Highly precise rotational period data is required to produce precise second-order moments.
   \item Large $a_\mathcal{A}$ is required for $K_{3m}$ resolution, though the size of $a_\mathcal{A}$ has no effect on $K_{2m}$.
@@
   \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
-  \item If the asteroid rotational period is too small, the asteroid will not tumble after perigee.
-This inhibits the precise determination of $K_{2m}$, though $K_{3m}$ are largely unaffected.
-For the reference asteroid, the threshold was about 4 hours (although $K_{30}$ will become unresolved at for periods smaller than 8 hours).
-For similar reasons, initial rotational velocities orthogonal to the orbital plane or in the plane and perpendicular to the perigee vector will yield poor-quality fits, though the spin pole effect is smaller than the effect of rotational period.
-  \item The cadence of observation should be shorter than about 30 minutes (except $K_{30}$ will become unresolved for cadence longer than 10 minutes).
-Gaps of data can appear, specifically at perigee, but only for a little over an hour given 2 minute cadence before the posterior uncertainty greatly increases.
+  \item If the asteroid rotational period is too small, or if the initial rotational velocity points in an inconvenient direction, the density moments will be poorly constrained.
+  \item The cadence of observation should generally be shorter than about 30 minutes for the reference asteroid case. Gaps of data can appear, even at perigee, but not for more than about an hour.
 \end{enumerate}
@@
 
-Finally, we present three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid as obtained by light-curve analysis.
-The extracted density distributions largely are consistent with the true distributions in all cases we tested.
+Finally, we presented three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid The extracted density distributions are largely consistent with the true distributions in all cases we tested.
 Slight adjustments to $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
@@
 
-In the appendices, we answer more specific questions that might arise about the behaviour of the tidal torque system and the fit process.
-
 \section*{Acknowledgements}
 
-We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work, and pointing out possible future directions to take it.
-JTD would like to thank the Massachusetts Institute of Technology Undergraduate Research Opportunities Program (MIT UROP) office for funding his work for many semesters, and their flexibility in funding students from departments other than the source of funding.
-Much of the computation behind this paper was executed on MIT Supercloud's facilities.
+We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work and pointing out possible future initiatives.
+JTD also thanks the MIT UROP office for funding his work for many semesters.
+This paper made substantial use of MIT Supercloud's facilities.
 
@@
 
-The code used to generate data, fit density moments to it, and extract density distributions from the moments is available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}, or by contacting JTD.
+The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}.
 
@@
 
-%\include{appendices}
+\input{appendices}
 

### 2022-04-21 data/oblateness-differ/compile.py

@@ -113,9 +113,9 @@ for i in range(N_DIM):
 custom_lines = [Line2D([0], [0], color='k', lw=4, alpha=0.3),
                 Line2D([0], [0], color='k', lw=4, alpha=0.6),
                 Line2D([0], [0], color='k', lw=1, linestyle='dashed')]
-fig.legend(custom_lines, ['95\%', '68\%', '50\%'], ncol=3, framealpha=1, loc="lower center", prop={'size': LEGEND_SIZE})
+#fig.legend(custom_lines, ['95\%', '68\%', '50\%'], ncol=3, framealpha=1, loc="lower center", prop={'size': LEGEND_SIZE})
 fig.tight_layout()
-fig.subplots_adjust(bottom=0.15)
+#fig.subplots_adjust(bottom=0.15)
 plt.savefig("oblateness-differ.pdf")
 plt.savefig("oblateness-differ.png")
 plt.show()

### 2022-04-21 data/probe-s-theta/compile.py

@@ -88,6 +88,7 @@ for plot_index in range(N_DIM):
 
     thresh = s_theta[(np.abs(param_data[2]-param_data[0]) > 0.01) | np.abs((param_data[-2]-param_data[0]) > 0.01)]
     if len(thresh) > 0:
+        #print("Threshold", thresh[0])
         ax.axvline(x=thresh[0], color='r', linewidth=1)
 
 

### 2022-04-21 data/pull-summary.py

@@ -1,7 +1,7 @@
 import os, sys
 from shutil import copyfile
 
-PATH = "probe-s-theta"
+PATH = "probe-s-rho"
 FORBIDDEN_NAMES = []
 
 I_LIMIT = -1

### 2022-04-25 old-papers/draft2/appendices.tex
Response to Julien's comments on draft 2

--- 2022-04-21 paper/appendices.tex
@@
 Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}) and write the equations of motion for the system (section \ref{sec:eom}).
+We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
 
@@
 
-Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with periapse $r_p$ and excess velocity $v_\infty$.
-We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
-
 We make use of two frames of reference to model this system.
-One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass and each axis aligned with an asteroid principal axis.
-$\unit{X}$ points from the central body to the asteroid periapse and $\unit{Z}$ points parallel to the orbit angular momentum.
-We will assume that the mass distribution of the central body is known in this inertial frame.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass.
+$\unit{X}$ points from the central body to the asteroid periapse, and $\unit{Z}$ points parallel to the orbit angular momentum.
+We assume that the mass distribution of the central body is known in this inertial frame.
 
 Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
-This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI.
+Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal moment of inertia.
 In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
@@
     \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
-    \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
+    \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {};
     \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
@@
 In the next section, it will be shown that only certain parameters of the asteroid density distribution affect tidal torque called ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
-The regular and irregular spherical harmonics then defined as:
+The regular and irregular spherical harmonics then defined as
 \begin{equation}
@@
 \end{equation}
-These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which derives spherical harmonic identities useful for quantum mechanics.
+These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
 
@@
 Note that these are complex.
-Here, $\mathcal{A}$ indicates the volume of the asteroid, $\mu_\mathcal{A}$ is the mass of the asteroid, $\rho_\mathcal{A}(\bm r)$ is the density distribution, and $a_\mathcal{A}$ is a real length scale defined in equation \ref{eqn:am}.
-This length can be thought of as akin to the radius of the asteroid (although a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
-Both equations \ref{eqn:am} and \ref{eqn:klm} should be computed in the body-fixed axes.
+The length defined in equation \ref{eqn:am} can be thought of as akin to the radius of the asteroid (a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
+Both equations \ref{eqn:am} and \ref{eqn:klm} should be computed in the body-fixed frame.
 
@@
 \end{equation}
-which should be computed in the inertial axes.
+which should be computed in the inertial frame.
 
@@
 In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
-For the rest of this paper, we therefore treat an uncertainty on $|K_{3m}|$ of $0.01$ or less as a practical limit on observability, in that uncertainty greater than 0.01 means $K_{3m}$ are effectively unknown.
-This is only a rough estimate, however.
 
@@
 This equation is given explicitly as equation \ref{eqn:tidal-torque}.
-Some $K_{\ell m}$ terms are included in this equation with $|m|>\ell$; these should all be taken to be zero.
+Some $K_{\ell m}$ terms are written in this equation with $|m|>\ell$; these should all be taken to be zero.
 
@@
 Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
-For our analysis, we remove $\ell' > 3$ and we usually keep only $\ell=0$.
+For our analysis, we removed $\ell' > 3$ and we usually keep only $\ell=0$.
 Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
@@
   \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho / \sigma_\theta = 10^{-5}$.
-  \item A rotational period of 9 hours, with the rotational velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
+  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
   \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
@@
 
-Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form a set of $n+1$ constraints, where $n$ is the number of density moments known.
-That is, $n=(\ell_\text{max}+1)^2+1$, where $\ell_\text{max}$ is the maximum degree of $K_{\ell m}$ known.
-By setting the same maximum degree on $C_{\ell m}$, we also have $n$ variables plus one for $\rho_0$.
-The system is therefore well-determined and will yield finitely many solutions.
-These solutions can be further refined by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
-We do not attempt to model uncertainty on the shape.
+Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form $(\ell_\text{max} + 1)^2 + 1$ constraints, where $\ell_\text{max}$ is the maximum degree of $C_{\ell m}$.
+By setting the same maximum degree as for the known $K_{\ell m}$, the system is well-determined and will yield finitely many solutions.
+These solutions can be filtered by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
 
-To test the model, this process was run for an asteroid with $K_{1m}=K_{2m'}=0$, but randomly chosen $K_{3m}$.
+To test the model, this process was run for an asteroid with $K_{1m}=K_{2m'}=0$, but randomly chosen $K_{3m}$ in the range 0.01 to -0.01.
 The resulting surface is shown in figure \ref{fig:surface-density}.
@@
 Where the likelihood model yields high density, the surface model extends.
-Thus, the connection made in section \ref{sec:spherical-density} between non-uniformities in the densities of the likelihood and harmonic models at the asteroid surface and inaccuracies in the surface is more firmly represented.
+Thus, the connection made in section \ref{sec:spherical-density} between non-uniformities in extracted densities at the asteroid surface and inaccuracies in the surface shape is more firmly represented.
 
@@
 Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
-We only suggest this as a possibility, however, since light-curve analysis is beyond the scope of this paper.
+However, light-curve analysis is beyond the scope of this paper.

### 2022-04-25 old-papers/draft2/main.tex
Response to Julien's comments on draft 2

--- 2022-04-21 paper/main.tex
@@
 However, most asteroid observational techniques are not sensitive to interior structure.
-We investigate the degree to which interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
+We investigate the degree to which interior density distributions can be extracted from angular velocity data gathered during a close encounter.
+We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
 Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
@@
 Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
-Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
-More encounter candidates are likely to be discovered in the future by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) or the Las Cumbres Observatory (LCO).
-Light curve analysis has been performed on many of these new asteroids to study their surface properties, but observations that are sensitive to the interior structure of the asteroid are rarer.
+Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to closely encounter Earth or other planets in the near future.
+More encounter candidates are likely to be discovered by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) or the Las Cumbres Observatory (LCO).
+Light curve analysis has been performed on many asteroids to study their surface properties, but observations that are sensitive to the interior asteroid structure are rarer.
 
@@
 
-The upcoming encounter of Apophis is of particular interest and much theoretical work has been devoted to accurate estimates of its orbital and physical properties, and predictions of how its angular velocity will be affected by tidal torque \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis, souchay2014rotational, souchay2018changes}.
-This research builds on a larger body of theoretical work showing that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
-This two-body generalized system has been studied to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-One success of this work was the recent extraction of moment of inertia ratios for Duende \cite{MOSKOVITZ2020113519}.
+The upcoming 2029 encounter of 99942 Apophis is of particular interest and much theoretical work has been devoted to accurate estimates of its orbital and physical properties and predictions of how its angular velocity will be affected by tidal torque \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis, souchay2014rotational, souchay2018changes}.
+This research builds on a larger body of theoretical work.
+The gravitational two-body system has been studied in the context of tidal torque to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
 However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
@@
 
-In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system which is quickly computable and valid to arbitrary order.
+In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system which is quick to compute and valid to arbitrary order.
 In section \ref{sec:methods}, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts physical characteristics of the asteroid (specifically, density moments) from the fit data.
 We then describe three methods to generate full density distributions from the density moments.
-Section \ref{sec:results} demonstrates the efficacy of this spin-data-to-density-distribution pipeline and explores the key properties.
+Section \ref{sec:results} demonstrates the efficacy of this spin-data-to-density-distribution pipeline and explores its key properties.
 Finally, in section \ref{sec:discussion}, we measure the uncertainties of the best-fitting parameter estimates as a function of various encounter properties to determine which properties most inhibit accurate extraction of density distributions.
+We also test the density distribution extraction methods on several sample asteroids.
 
@@
 both of which are constant and only need to be computed once to generate data.
-Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see the appendix for details).
+Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
 They produce a tidal torque of
@@
 \end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$ and $J_{\ell m}$ are the mass and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$, $a_\mathcal{A}$, and $J_{\ell m}$ are the mass, length, and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
 Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
-Throughout the paper, we also refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also discussed in appendix \ref{app:eom}.
+Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also defined in appendix \ref{app:eom}.
 
@@
 We further assume that the asteroid is initially not tumbling.
-Thus, the rotational velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia).
+Thus, the angular velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia).
 This sets $\beta = 0$ and we can further choose $\alpha = 0$.
@@
 We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-This width is related to the more physical uncertainty in asteroid period $\sigma_P$ by $\sigma_P=P \sigma_\rho$ for small $\sigma_\rho$.
+This width is related to the uncertainty in asteroid period $\sigma_P$ by $\sigma_P=P \sigma_\rho$ for small $\sigma_\rho$.
 Explicitly, the probability density function (PDF) of $\rho$ is
@@
 Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
-Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ since this is equivalent to re-labeling $\unit y$ as $\unit x$ and $\unit x$ as $-\unit y$.
+Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ because both of these align the asteroid principal axes with the body-fixed axes.
 The other bounds were $|K_{3m}| < 1$.
@@
 
-We further improved the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$.
-In practice, $f=2$ often led to likelihood minima successfully found.
+To further ensure convergence, we minimized with respect to data truncated after perigee at double the perigee distance.
+This cut-off was manually chosen.
 The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
 
-\subsection{Extracting density distributions from density moments: general model design}
+\subsection{Extracting density distributions from moments: general model design}
 \label{sec:general-density}
@@
 However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
-Here, we outline three different assumptions which constitute three models for extracting density distributions from density moments.
-All three of them are (partially) linear to facilitate computational ease and uncertainty propagation.
+We outline three different assumptions which constitute three models for extracting density distributions from density moments.
+All are (partially) linear to facilitate computational ease and uncertainty propagation.
 One of them can be chosen, or another created, depending on what features are desired to be represented in the density distribution.
@@
 The models then produce a density distribution $\rho_\mathcal{A}(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho_\mathcal{A}$.
-In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
+If the asteroid shape is not known, a fourth model defined in appendix \ref{app:find-surface} can be used to extract it assuming uniform density.
+In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
 However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
@@
 If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
-Likewise, if the asteroid shape is not known with certainty, a fourth model described in appendix \ref{app:find-surface} can be used to extract asteroid shape assuming constant density.
-
-Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
-Only the differences in $\rho$ across the body are measurable.
+
+Since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense. Only the differences in $\rho$ across the body are measurable.
 
@@
 The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame and the body-fixed frame aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (equal in all frames).
-
-The density moments defined in equation \ref{eqn:klm} are not linear in $\rho(\bm r)$, but we may fix $a_\mathcal{A}$ at the value assumed during the fit and set $\mu_\mathcal{A}$ equal to an arbitrary constant since the system is independent of the total asteroid mass.
-Thus, equations \ref{eqn:am} and \ref{eqn:klm} guarantees that $K_{\ell m}$ and $a_\mathcal{A}^2$ are linear in $\rho(\bm r)$.
+We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (the same in both frames).
+
+We fix $a_\mathcal{A}$ at the value assumed during the fit and set $\mu_\mathcal{A}$ equal to an arbitrary constant since the system is independent of the total asteroid mass.
+Thus, $K_{\ell m}$ and $a_\mathcal{A}^2$ are linear in $\rho(\bm r)$ by equations \ref{eqn:am} and \ref{eqn:klm}.
 Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
@@
 \begin{equation}
-  \rho(\bm r, \bm \Theta) = \bm B(\bm r) \cdot \bm \Theta
+  \rho(\bm r, \bm \Theta) = \bm B(\bm r)^\dagger \bm \Theta
   \label{eqn:density-distro}
 \end{equation}
-for a $m$-dimensional vector $\bm B(\bm r)$.
+for a $m$-dimensional vector $\bm B(\bm r)$ with adjoint $\bm B(\bm r)^\dagger$.
 ($\bm B$ need not be linear in $\bm r$.) Thus, $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
@@
 \end{equation}
-where $A^\dagger$ is the adjoint of $A$.
-
-The role of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional constant matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-model} and \ref{eqn:density-distro} are true.
+
+The role of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-distro} and \ref{eqn:density-model} are true.
 Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
@@
 
-\subsection{Model implementations for extracting density distributions from density moments}
+\subsection{Extracting density distributions from moments: specific models}
 \label{sec:specific-density}
@@
 
-A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes likelihood and exactly reproduces $\bm K$.
-We call this method the ``likelihood'' model.
+A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes $\mathcal{L}$ and exactly reproduces $\bm K$.
+We call this the ``likelihood'' model.
 This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
@@
 
-Note that this model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+This model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
 
@@
 We  call this  the ``harmonic'' model.
-The expansion of a harmonic function in spherical coordinates is given by
+Any harmonic function can be expanded as
 \begin{equation}
@@
 
-Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:am} and \ref{eqn:klm}, we get 
+Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:am} and \ref{eqn:klm},
 \begin{equation}
@@
 \begin{equation}
-  A=M^+ = (M^\dagger M)^{-1} M^\dagger 
+  A=M^+ = (M^\dagger M)^{-1} M^\dagger .
   \label{eqn:mpi-overdetermined}
@@
 A non-spherical perturbation will introduce small, off-diagonal entries of $M$.
-This diagonal represents another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
+This suggests another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
 
@@
 The total number of degrees of freedom are displayed in table \ref{tab:lump-dof}.
-They should be compared to the number of known asteroid parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, which is $(\ell_\text{max}+1)^2+1$, which is 17 when the second-order density moments are known and 10 when only $K_{2m}$ are known.
-We assume that the degrees of freedom of this lumpy model are always fewer than the number of $\bm K$, so that the model is overdetermined.
+They should be compared to the number of known asteroid parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, which is $(\ell_\text{max}+1)^2+1$: 17 when the second-order density moments are known and 10 when only $K_{2m}$ are known.
+We assume that the degrees of freedom of this lumpy model are fewer than the number of $\bm K$, so that the model is overdetermined.
 
@@
 
-The net $K_{\ell m}$ components of such an ensemble obey
+The net $K_{\ell m}$ components of such an ensemble are
 \begin{equation}
@@
   \begin{split}
-  & K_{\ell m}'^i = \sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
+  & K_{\ell m}'^i = \frac{1}{a_\mathcal{A}^{\ell - \ell'}}\sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
   & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
@@
 \begin{equation}
-  \mu_0 \bm x_0 + \sum_{i=1}^N \bm x_i \mu_i = 0 \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}
+  \mu_0 \bm x_0 + \sum_{i=1}^N \mu_i \bm x_i = 0, \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}.
   \label{eqn:lump-constraints}
 \end{equation}
-There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-Combining both constraints in equation \ref{eqn:lump-constraints}, we can fix $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid, which can be enforced manually.
+Combining both constraints in equation \ref{eqn:lump-constraints}, we can eliminate $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
 
@@
   \includegraphics[width=0.6\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best fit results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. Uncertainty bands are also shown.}
+  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. Uncertainty bands are also shown.}
   \label{fig:example-residuals}
@@
 
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted PPD, marginalized to functions of one or two variables.
+Figure \ref{fig:example-corner} shows a corner plot of the ten fitted PPDs, marginalized to functions of one (histograms) or two (contours) variables.
 The true parameters are shown as lines.
@@
 \label{sec:asym-density}
-To demonstrate the success of our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
+To demonstrate our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
 These distributions were made given the density moment PPDs extracted above, with $a_\mathcal{A}$ fixed.
@@
 
-The size of uncertainty is such that the density distribution is consistent with uniform at most points for the harmonic and likelihood models (within 1.5$\sigma$).
+The size of uncertainty is such that the density distribution is consistent with uniform for the harmonic and likelihood models (within 1.5$\sigma$).
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
@@
 These are roughly equivalent to 1 or 2 times standard deviation of the PPD respectively.
-In all cases, we use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
+We use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
 
@@
 The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma =0.01$.}
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
     \label{fig:scan-perigee}
@@
 The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma =0.01$.}
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
     \label{fig:scan-am}
@@
 
-There is no clear threshold above which posterior uncertainty is ``too high.'' However, most asteroid distributions tested in this paper have $K_{\ell m} \lesssim 0.01$.
-We therefore call $\sigma(K_{\ell m}) \approx 0.01$ the ``posterior uncertainty threshold,'' beyond which $K_{\ell m}$ are unresolved.
-This should be understood as a rule of thumb and not a precise statement.
+There is no clear threshold above which posterior uncertainty is ``too high.'' However, most asteroid distributions tested in this paper have $K_{3 m} \lesssim 0.01$.
+We therefore call $\sigma(K_{3 m}) \approx 0.01$ the ``posterior uncertainty threshold,'' beyond which $K_{3 m}$ are unresolved.
+This should be understood as a rule of thumb, not a precise statement.
 
@@
 
-Figure \ref{fig:scan-vex} demonstrates that parameter precision does not depend strongly on excess velocity, aside from a slight trend especially in the higher order parameters for uncertainty to increase with $v_\infty$.
+Figure \ref{fig:scan-vex} demonstrates that posterior uncertainty follows a slight trend for uncertainty to increase with $v_\infty$.
 This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
 There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) This effect explains why these small-scale oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma > 0.01$, shown by the red vertical line.
+(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) This explains why the oscillations have the same period for all parameters.
+Note that these oscillations are sometimes large enough to raise $\sigma(K_{3m}) > 0.01$, shown by the red vertical line.
 
@@
 At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
-Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma$ curve there.
-The location of these limits will change if different encounter properties are used, but this is still an illustrative example.
+Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
+The exact location of these limits will change if different encounter properties are used.
 
@@
 
-The very strong dependence of $\sigma$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters (5-20 Earth radii).
+The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters (5-20 Earth radii).
 Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
@@
 
-\subsubsection{Observational Uncertainty}
+\subsubsection{Observational uncertainty}
 \label{sec:scan-uncertainty}
@@
 These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
-Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole ($\sigma_\theta$) or uncertainty in period ($\sigma_\rho$) more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
+Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
 This dependence is displayed in figure \ref{fig:scan-theta}.
@@
 For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
-The $K_{30}$ parameter reaches the $\sigma(K_{30})\approx 0.01$ threshold at $\sigma_\theta = 0.032\ \text{radians} \approx 2^\circ$ when $\sigma_\rho$ is held fixed, whereas the other parameters reach the threshold between $8^\circ$ and $45^\circ$.
-The $K_{2m}$ parameters are never reach the $\sigma(K_{\ell m})$ threshold, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
+The $K_{30}$ parameter reaches the $\sigma(K_{30})\approx 0.01$ threshold at $\sigma_\theta = 0.032\ \text{radians} \approx 2^\circ$, whereas the other parameters reach the threshold between $8^\circ$ and $45^\circ$.
+The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
 
@@
 
-These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period $\sigma_\rho$ in our analysis.
-To accurately measure density moments, very accurate rotational period estimates would have to be made every cadence.
-However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different rotational velocity measurements.
+These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
+To precisely measure density moments, very accurate rotational period estimates would have to be made every cadence.
+However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
 If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
@@
 
-The true values of $K_{\ell m}$, $\gamma_0$, and $a_\mathcal{A}$ affect the posterior uncertainties.
+THe true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
 Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
-The $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
+These $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
 
@@
 The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The data then have no physical dependence on $\gamma_0$ when $K_{22}=0$.
+The system then has no dependence on $\gamma_0$ when $K_{22}=0$.
 This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
@@
 
-  \caption{1$\sigma$ confidence interval for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
+  \caption{1$\sigma$ posterior uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
   \label{fig:scan-space-sigma}
@@
 
-Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters for reference.
+Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters.
 They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
@@
 
-  \caption{Correlations between PPDs for fit parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes; the symmetric case is marked with a red circle and the asymmetric with a black triangle.}
+  \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
   \label{fig:scan-space-corr}
@@
 
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation (except the large $K_{22}$ corner).
+Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation.
 It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
@@
 On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$, defined in equation \ref{eqn:am}.
-As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) is canceled by the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
-The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that uncertainty is strongly dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
+As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
+The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
 At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
 The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
-This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 1$.
-(In figure \ref{fig:scan-am}, the best fitting values are $p < 0.1$.) This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma(K_{\ell m})$.
-It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is very unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
+This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 0.1$.
+This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma(K_{\ell m})$.
+It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
 
@@
 The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
 
@@
 
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal (except for $K_{30}$ where the $\sigma<0.01$ limit is exceeded).
-However, shorter cadence almost always leads to lower uncertainties.
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
 
@@
 To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same length of data before and after the perigee.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same size.
 We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
@@
 Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-On the other hand, none of the uncertainties increase noticeably for $T < 30$ min.
+On the other hand, none of the uncertainties increase noticeably for $T \lesssim 1$ hr.
 Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
 
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T$ as \ref{fig:scan-cadence} showed for $\sigma(K_{\ell m})$ on cadence $\Delta t$.
-They also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
+Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
 This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
@@
 The orange star indicates the reference spin pole.
-The red contours enclose regions where $\sigma \geq 0.01$.}
+The red contours enclose regions where $\sigma(K_{3m}) \geq 0.01$.}
   \label{fig:scan-spin}
@@
 
-It is important to note, however, that uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{\ell m}) \approx 0.01$ threshold.
+However, uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{3 m}) \approx 0.01$ threshold.
 The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
@@
 We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ and reveal that each rotation has zero average first-order torque.
-Since the first-order torque over each rotational period cancels out, there is no secular torque to force the asteroid to tumble.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular, first-order torque to force the asteroid to tumble.
 However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
@@
 The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids have better uncertainty.
+It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids yield smaller uncertainty.
 
@@
 By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
-The effect of central body oblateness, then, is limited to the $J_{2m}$ terms, and therefore damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have small, but noticeable effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_M^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_M$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
+The effect of central body non-sphericity, then, is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
+We expect these parameters to have small effect on the asteroid.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
 
 $J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -2J_{20}$ and $J_{22} = 0$.
-(Some sources such as Ref.~\cite{paterLissauer2015} take $\epsilon=J_{20}$ as their definition of $J_{20}$).
+However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
 For simplicity, we use this equatorial orbit case.
 Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
-The next order of precision after this oblateness approximation is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and  non-ellipsoid corrections to the central body shape.
+The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
 We do not consider these extra factors.
@@
   \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
-Linear best-fitting lines to $\sigma$ (black, dotted) are plotted.
+Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
 \textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
@@
 These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
-The figure demonstrates a small dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, but the effect is far from important compared to the other factors studied above.
-Most Solar System bodies do not reach the oblateness necessary to significantly increase precision on the first-order parameters.
-The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.26$ for $\gamma_0$, $-0.94$ for $K_{22}$, and $-1.2$ for $K_{20}$.
+The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
+The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.06$ for $\gamma_0$, $-0.2$ for $K_{22}$, and $-0.3$ for $K_{20}$.
 The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
@@
 Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the posterior uncertainty (appendix \ref{app:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+These two parameters also affect the posterior uncertainty (section \ref{sec:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
 
@@
 Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Moon-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $10^{-2}$ between the true and fit parameters for large oblateness.
+The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
 Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
@@
 
-Note that $J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
+$J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
 If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
-As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined $J_{20} = 0.25$.
-Extrapolating posterior uncertainty by the slopes of the best fit lines given earlier, this represents a decrease in $\sigma(K_{2m})$ by a factor of about two.
+As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
+Extrapolating posterior uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
+Furthermore, $J_{22}$ is non-zero for this case, which likely decreases posterior uncertainty even more.
 
@@
 \subsection{Comparison of Jupiter and Earth encounters}
-\label{app:jupiter-earth}
+\label{sec:jupiter-earth}
 
 If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
-In this appendix, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
+In this section, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
 
@@
 For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
-The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perigee distance is
+The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perijove distance is
 \begin{equation}
@@
 \end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower periapse.
+It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower perijove.
 Other effects, such as a change in the physical properties of the encountering asteroids or decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
@@
 This was already done in section \ref{sec:asym-density} for the asymmetric reference asteroid.
-Here, we perform the same process for the symmetric reference asteroid, a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), and a tetrahedron.
-We use these shapes as rough approximations of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron), but also to demonstrate the density models' efficacy on sharp corners.
+Here, we perform the same process for a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), the symmetric reference asteroid, and a tetrahedron.
+We use these shapes as examples of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron) and to demonstrate the density models' efficacy on very different shapes.
 The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
@@
 Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is consistent with uniform at most points for all models(within 1-2$\sigma$), with a small number of low-uncertainty regions that are less consistent with uniform.
+The size of uncertainty is such that the density distribution is very consistent with uniform at most points for the (asymmetric) dumbbell model (within $\sim 1\sigma$), while the symmetric reference and tetrahedral asteroids were generally within $\sim 2 \sigma$ of uniform.
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
-\jtd{Confirm}
 
@@
 The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
-The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|$ for the original asteroids, making it clearly a poor model.
+The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|^2$ for the original asteroids, making it clearly a poor model.
 
@@
 
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).Density is normalized so that mean density is one.
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).
+Density is normalized so that mean density is one.
 The same distance scale is used in all figures.}
@@
 
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and the fact that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models do give qualitatively similar results.
-Furthermore, the centre-weighted density distribution indeed contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models, while the edge-weighted asteroid contains mass at the edges.
+For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
+However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
 Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
+The difference of the model output from the true distribution is generally less than $2\sigma$, but can rise to $3\sigma$ in some regions.
 
@@
 An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape, rather than an a distribution that conforms to the asteroid shape.
+This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape rather than a distribution that conforms to the asteroid shape.
 
@@
 
-The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edge of the lump.
+The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edges of the lump.
 However, the lumpy model computes the location and density of the mass very well.
@@
 We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the rotational velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
+The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the angular velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
 We then built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
@@
 \begin{enumerate}
-  \item Extracted density moments are generally more precise when the asteroid leaves the encounter tumbling.
   \item The second-order moments $K_{3m}$ are roughly a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is proportional to the asteroid radius and $r_p$ is the perigee distance.
@@
 It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
+  \item Extracted density moments are generally more precise when the asteroid leaves the encounter tumbling.
   \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates.
@@
 The threshold on $a_\mathcal{A}$ for the reference asteroid was $\sim$700 m for $K_{30}$ and $\sim$50 m for $K_{33}$.
-  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters, extending to about a third of a Lunar distance for the reference asteroid.
+  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters.
   \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
-  \item If the asteroid rotational period is too small, or if the initial rotational velocity points in an inconvenient direction, the density moments will be poorly constrained.
+  \item If the asteroid rotational period is too small, or if the initial angular velocity points in an inconvenient direction, the density moments will be poorly constrained.
   \item The cadence of observation should generally be shorter than about 30 minutes for the reference asteroid case. Gaps of data can appear, even at perigee, but not for more than about an hour.
@@
 Large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
-Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.
+Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.`'
 
@@
 We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work and pointing out possible future initiatives.
-JTD also thanks the MIT UROP office for funding his work for many semesters.
+JTD also thanks the MIT UROP office for funding his work.
 This paper made substantial use of MIT Supercloud's facilities.

### 2022-04-25 paper/main.tex
Response to Julien's comments on draft 2

@@
 \begin{abstract}
-  Knowledge of the interior distribution of an asteroid can reveal its composition and constrain its evolutionary history.
-However, most asteroid observational techniques are not sensitive to interior structure.
-We investigate the degree to which interior density distributions can be extracted from rotational velocity data gathered during a close encounter.
-We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic rotational velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
-Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the planet being encountered, the quantity of near-pericentre data, and the central body oblateness.
-Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
+  Knowledge of the interior density distribution of an asteroid can reveal its composition and constrain its evolutionary history.
+However, most asteroid observational techniques are not sensitive to interior properties.
+We investigate here the interior constraints accessible through monitoring variations in angular velocity during a close encounter.
+We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
+Using Markov Chain Monte Carlo fits, we perform injection-retrieval \jtd{tests} on these synthetic data to gain insights into the extent to which interior properties can be constrained.
+We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., moment of inertia and initial spin pole direction), observational set up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
+\jtd{We find that high precision in period estimates (order of milliseconds to seconds) are necessary for each cadence, and that large asteroids ($> 100$ m radius) with low perigees ($<20$ Earth radii) are necessary to resolve beyond-leading-order density moments}.
 \end{abstract}
@@
 Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
-Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to encounter Earth or other planets closely in the near future.
-More encounter candidates are likely to be discovered in the future by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) or the Las Cumbres Observatory (LCO).
-Light curve analysis has been performed on many of these new asteroids to study their surface properties, but observations that are sensitive to the interior structure of the asteroid are rarer.
-
-However, tidal torque acting on an asteroid and perturbing its angular velocity during an encounter presents an opportunity to constrain the interior mass distribution.
-Such angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus respectively.
-Altered rotational states altered by Solar tidal torque have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
-
-The upcoming encounter of Apophis is of particular interest and much theoretical work has been devoted to accurate estimates of its orbital and physical properties, and predictions of how its angular velocity will be affected by tidal torque \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis, souchay2014rotational, souchay2018changes}.
-This research builds on a larger body of theoretical work showing that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
-This two-body generalized system has been studied to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-One success of this work was the recent extraction of moment of inertia ratios for Duende \cite{MOSKOVITZ2020113519}.
+Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to closely encounter Earth or other planets in the near future.
+More encounter candidates are likely to be discovered by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) \cite{tyson2002large}.
+Their encounters can then be monitored by global ground-based networks such as the Las Cumbres Observatory (LCO) \cite{brown2013cumbres}.
+Such ground-based monitoring is typically used to derive the rotation period of an asteroid and its surface properties \cite{}\jtd{Ask for reference from Artem}.
+
+Since the tidal torque acting on an asteroid during an encounter depends on the interior mass distribution, the careful monitoring of angular velocity variations during an encounter also presents a window into the interior properties of asteroids.
+The gravitational two-body system has
+been studied in the context of tidal torque to different orders
+and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
 However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
-More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
-
-In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system which is quickly computable and valid to arbitrary order.
-In section \ref{sec:methods}, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts physical characteristics of the asteroid (specifically, density moments) from the fit data.
+More research is needed to study in what cases these effects are observable, and what
+factors generally inhibit observation of these new features.
+
+Angular velocity perturbations have been observed and
+used to extract asteroid properties in several cases, including
+for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid
+binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
+Orbital and physical properties, including moment of inertia ratios have also been extracted for 99942 Apophis, which will closely encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
+It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity \cite{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
+
+We address this community need by developing a methodology to translate (1) time series of angular velocity data into constraints on density moments and (2) constraints on density moments into constraints on an asteroid's density distribution.
+In section \ref{sec:methods}, we introduce the analytical and numerical fundamentals of this methodology.
+There, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts density moments from the fit data.
+We note that these equations fo motion for an asteroid equation are novel and designed to be computationally efficient and valid to arbitrary order.
 We then describe three methods to generate full density distributions from the density moments.
-Section \ref{sec:results} demonstrates the efficacy of this spin-data-to-density-distribution pipeline and explores the key properties.
-Finally, in section \ref{sec:discussion}, we measure the uncertainties of the best-fitting parameter estimates as a function of various encounter properties to determine which properties most inhibit accurate extraction of density distributions.
+In section \ref{sec:results}, we present the results of a series of injection-retrieval \jtd{tests} demonstrating the extent to which the properties of an asteroid chosen to generate synthetic spin data can be retrieved via our methodology.
+Finally, in section \ref{sec:discussion}, we assess the sensitivity of these constraints to various physical, observational, and methodological parameters to provide guidance for monitoring upcoming close encounters.
+We also test the density distribution extraction methods on several sample asteroids.
 
@@
 \end{equation}
-both of which are constant and only need to be computed once to generate data.
-Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see the appendix for details).
+both of which are constant and only need to be computed once to generate data assuming no asteroid deformation.
+Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
 They produce a tidal torque of
@@
 \end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$ and $J_{\ell m}$ are the mass and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$, $a_\mathcal{A}$, and $J_{\ell m}$ are the mass, length, and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
 Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
-Throughout the paper, we also refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also discussed in appendix \ref{app:eom}.
+Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also defined in appendix \ref{app:eom}.
 
 In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion.
-In section \ref{sec:uncertainty}, we define the uncertainty model used to add noise to the data, and we describe how posterior probability distributions (PPDs) for density moments were extracted from spin-pole data in section \ref{sec:fit}.
-Finally, we outline a general model to extract density distributions from density moments in section \ref{sec:general-density} and define specific model implementations in section \ref{sec:specific-density}.
+In section \ref{sec:uncertainty}, we define the uncertainty model used to add realistic noise to the data, and we describe how posterior probability distributions (PPDs) for density moments were extracted from spin-pole data in section \ref{sec:fit}.
+Finally, we describe models to translate constraints on the density moments into constraints on the density distribution in section \ref{sec:density-distro}.
 
@@
 
-We built a publicly accessible, custom simulation in C++ to produce angular velocity data as a function of time.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+We built a publicly accessible, custom simulation in C++ to produce time series of angular velocity data during a close encounter with a more massive astronomical object.
+This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$ (see equation \ref{eqn:am}); and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
@@
 The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low-quality to resolve the parameters.
-$\sim 10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
+The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data quality was low, leading to degeneracies between the second order parameters ($K_{3 m}$).
+This degeneracy could be removed by only fitting $K_{2m}$ instead.
+About $10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
 
@@
 
-We further improved the minimization process by first minimizing with respect to data truncated at the point after perigee where $D=fr_p$ for some manually-set fraction $f$.
-In practice, $f=2$ often led to likelihood minima successfully found.
+To further ensure convergence, we minimized with respect to data truncated after perigee at double the perigee distance.
+This cut-off was manually chosen.
 The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
 
-\subsection{Extracting density distributions from density moments: general model design}
-\label{sec:general-density}
+\subsection{Translating constraints on density moments into constraints on the density distributon}
+\label{sec:density-distro}
 
@@
 However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
-Here, we outline three different assumptions which constitute three models for extracting density distributions from density moments.
-All three of them are (partially) linear to facilitate computational ease and uncertainty propagation.
-One of them can be chosen, or another created, depending on what features are desired to be represented in the density distribution.
-
+We outline three different assumptions which constitute three models for extracting density distributions from density moments.
+Our goal in investigating different families of models to translate constraints on the density moments into constraints on the density distribution is to reveal the major features in the density distribution that are consistently present, independent of the family of mapping model used, despite the problem underdetermination (in a similar fashion to \cite{de2012towards}).
+
+All are (partially) linear to facilitate computational ease and uncertainty propagation.
 All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
-Uncertainty on this shape estimate is assumed to be small.
+Uncertainty on this shape estimate is assumed to be negligible compared to the density moment uncertainty and their contributions to to the density distribution.
 The models then produce a density distribution $\rho_\mathcal{A}(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho_\mathcal{A}$.
-In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling the $K_{3m}$ components.
-However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
+If the asteroid shape is not known, a fourth model defined in appendix \ref{app:find-surface} can be used to extract it assuming uniform density.
+In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
+\jtd{Move this: However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
 It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
-Likewise, if the asteroid shape is not known with certainty, a fourth model described in appendix \ref{app:find-surface} can be used to extract asteroid shape assuming constant density.
-
-Note that, since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense.
-Only the differences in $\rho$ across the body are measurable.
+If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.}
+
+Since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense. Only the differences in $\rho$ across the body are measurable.
 
@@
 
-\subsection{Model implementations for extracting density distributions from density moments}
-\label{sec:specific-density}
-
 \subsubsection{The ``likelihood'' model}
@@
 
-We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
+We now explore a model that seeks to restrict the space of allowed density distributions in a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
 We  call this  the ``harmonic'' model.
-The expansion of a harmonic function in spherical coordinates is given by
+Any harmonic function can be expanded as
 \begin{equation}
@@
 The above two simple models produce smooth density distributions.
-In this section, we define a more complicated model which identifies discrete regions differing from the overall density.
+In this section, we define a model which identifies discrete regions differing from the overall density.
 We call this model the ``lumpy'' model.
@@
 
-We use a non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described in section \ref{sec:general-density}.
+We use the following non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described above.
 We must incorporate the centre-of-mass and total-mass constraints
 \begin{equation}
-  \mu_0 \bm x_0 + \sum_{i=1}^N \bm x_i \mu_i = 0 \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}
+  \mu_0 \bm x_0 + \sum_{i=1}^N \mu_i \bm x_i = 0, \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}.
   \label{eqn:lump-constraints}
 \end{equation}
-There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid which can be enforced manually.
-Combining both constraints in equation \ref{eqn:lump-constraints}, we can fix $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
+There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid, which can be enforced manually.
+Combining both constraints in equation \ref{eqn:lump-constraints}, we can eliminate $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
 
@@
 
-\subsection{Density moment extraction}
+To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the asymmetric reference asteroid.
+We first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
+For both level of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
+
+\subsection{Density moments}
 \label{sec:example-fit}
-To demonstrate our fit process, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
-The fit results were consistent with the true density moments, and produced consistent data.
-
 \begin{figure*}
@@
 
-Figure \ref{fig:example-residuals} shows the spin data with noise added.
-The best-fitting model is overlaid in the top pane and residuals are shown the bottom pane.
-Specifically, we show the model whose parameters are the means of the PPDs.
+Figure \ref{fig:example-residuals} shows the synthetic spin data.
+The best-fitting model is overlaid in the top panel and residuals are shown the bottom panel.
 Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
@@
 
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted PPD, marginalized to functions of one or two variables.
+Figure \ref{fig:example-corner} shows a corner plot of the PPDs of the ten parameters (namely $\gamma_0$ and $K_{\ell m}$ for $\ell \leq 3$), marginalized to functions of one (histograms) or two (contours) variables.
 The true parameters are shown as lines.
@@
 
-\subsection{Density distribution extraction}
+\subsection{Density distribution}
 \label{sec:asym-density}
-To demonstrate the success of our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
+Figure \ref{fig:uniform-density-results} shows the density distributions and uncertainties extracted for the asymmetric reference asteroid.
 These distributions were made given the density moment PPDs extracted above, with $a_\mathcal{A}$ fixed.
@@
 
-To test the properties of the three density models defined in section \ref{sec:specific-density} to extract density distributions from density moments, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
+To test the properties of the three density models defined in section \ref{sec:density-distro} to extract density distributions from density moments, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
 In all cases, the density moments are extracted via our fit process.

### 2022-04-25 paper/appendices.tex
Cited Kaasalainen 2001

@@
 
-Throughout this paper, we assume that the asteroid under study is on a hyperbolic encounter with periapse $r_p$ and excess velocity $v_\infty$.
-We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
-
 We make use of two frames of reference to model this system.
-One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass and each axis aligned with an asteroid principal axis.
-$\unit{X}$ points from the central body to the asteroid periapse and $\unit{Z}$ points parallel to the orbit angular momentum.
-We will assume that the mass distribution of the central body is known in this inertial frame.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass.
+$\unit{X}$ points from the central body to the asteroid periapse, and $\unit{Z}$ points parallel to the orbit angular momentum.
+We assume that the mass distribution of the central body is known in this inertial frame.
 
 Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
-This frame is fixed with respect to the asteroid's principal axes and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-We will solve for the asteroid's mass distribution with reference to the body-fixed frame.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI.
+Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal moment of inertia (this is the short axis mode, to use the vocabulary of Ref.~\cite{kaasalainen2001interpretation}).
 In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.

### 2022-04-26 paper/main.tex
Ready for repull of density figures

@@
 One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
+\jtd{The choice of $a_\mathcal{A}$ can be adjusted after the fit to assess the dependence of the density distributions on $a_\mathcal{A}$}
 
@@
 See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model.
+\jtd{A log normal distribution is chosen such that $\rho > 0$, but since $\sigma_\rho \ll 1$ typically in our analysis, $P(\rho)$ is approximately Gaussian.}
 
@@
 In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
-\jtd{Move this: However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
-It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.}
+\jtd{When extracting density distributions, multiple $a_\mathcal{A}$ values may be tested and the multiple produced density distributions can be compared to highlight common features.}
 
@@
 To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
+In our work, we use $m \sim 10^{6}$.
 This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
@@
 
-This model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the number of finite elements $m$.
+This model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the large number of finite elements $m$.
 
@@
 
+  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
+  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
   \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
   \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
+  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-ratio-likelihood.pdf}\hfill
+  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-ratio-harmonic.pdf}\hfill\hspace{0.3\textwidth}
 

### 2022-04-26 code/density/display.py

@@ -5,6 +5,8 @@ from multiprocessing import Pool
 
 #plt.style.use("jcap")
 
+FONT_SIZE = 20
+
 import matplotlib as mpl
 mpl.rcParams["font.family"] = "serif"
 mpl.rcParams["font.monospace"] = "Roboto mono"
@@ -13,7 +15,7 @@ mpl.rcParams["figure.figsize"] = (6.5, 4.00)
 mpl.rcParams["legend.framealpha"] = 0.5
 mpl.rcParams["lines.linewidth"] = 2
 mpl.rcParams["lines.markersize"] = 4
-mpl.rcParams["font.size"] = 16
+mpl.rcParams["font.size"] = FONT_SIZE
 mpl.rcParams["legend.fontsize"] = 10
 
 VERY_SMALL = 1
@@ -64,7 +66,7 @@ def make_frame(densities, pos_array, axis_name, cmap, percentile, balance, z_ind
         vmin=want_min,
         vmax=want_max,
         cmap=cmap)
-    plt.colorbar(c, label=axis_name)
+    plt.colorbar(c).set_label(axis_name)
     plt.axis('equal')
     plt.xlabel("$y$ (m)")
     plt.ylabel("$x$ (m)")
@@ -149,7 +151,7 @@ def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percenti
     ax.set_ylabel("$y$")
     ax.set_zlabel("$z$")
 
-    ax.set_title(f"$\\Delta K_{{\\ell m}}={latexify(klm_error)}$", y=0.1, fontdict={'fontsize': 16})
+    ax.set_title(f"$\\Delta K_{{\\ell m}}^2={latexify(klm_error)}$", y=0.1, fontdict={'fontsize': FONT_SIZE})
 
     c = fig.colorbar(contour_handle, ax=ax)
     c.set_label(axis_name)

### 2022-04-26 paper/main.tex
Updated paper

@@
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
+
+To test the ability of the asteroid to identify discrete changes in density distribution of the kind that the lumpy model is designed to detect, we show one more example extraction.
+We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
+Both the mass and the medium have uniform density.
+The density moments are extracted via  a fit similarly to section \ref{sec:example-fit} and the distributions extracted by the three models for this asteroid are shown in figure \ref{fig:blob-density}.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
+
+  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
+  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
+  %\includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}
+
+  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
+  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
+  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-likelihood.pdf}\hfill
+  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
+Density is normalized so that mean density is one.
+The same distance scale is used in all figures.}
+  \label{fig:blob-density}
+\end{figure*}
+
+We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump.
+There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect.
+Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
+
+The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edges of the lump.
+However, the lumpy model computes the location and density of the mass very well.
+Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
+This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
+Nevertheless, it seems that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned above when the density moment data is redundant with the asteroid shape).
+But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in the above sections.
+
+\jtd{I will also add a discussion of uncertainties once the plots are generated.}
 
@@
 
-\subsubsection{Lumpy asteroids}
-
-Finally, we test an asteroid with a discrete change in density distribution (for example, a rock of high density), of the kind that the lumpy model is designed to detect.
-We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
-Both the mass and the medium have uniform density.
-The distributions extracted by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:blob-density}
-\end{figure*}
-
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect.
-Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
-
-The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edges of the lump.
-However, the lumpy model computes the location and density of the mass very well.
-Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
-This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
-Nevertheless, it seems that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned above when the density moment data is redundant with the asteroid shape).
-But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in the above sections.
-
 \section{Conclusions}

### 2022-04-28 paper/appendices.tex
Pulled speed contour plots

@@
 
-% \section{The cadence cut-off}
-% \label{app:cadence-tests}
+\section{The cadence cut-off}
+\label{app:cadence-tests}
 
-% In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-We mentioned that this cadence cut-off is likely a function both of the rotational period of the asteroid and the time spent near perigee.
-We study this cut-off in closer detail in this appendix.
+In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
+In the left panel of figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} \ t_\text{orbit}$ (right panel).
+Both panels show the sudden increase in posterior uncertainty we named $T_\text{cad}$.
+Now $T_\text{cad}$ is visible as a function of frequency and relative orbit speed.
 
-% We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
-Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference $P_\omega=9$ hr.
-The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ (i.e., those studied in section \ref{sec:scan-period}), are removed; they are irrelevant here.
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.49\textwidth]{figs/cad-period.pdf}\hfill
+  \includegraphics[width=0.49\textwidth]{figs/cad-speed.pdf}
+  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).}
+  \label{fig:cad-contour}
+\end{figure*}
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-%   \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-%   \label{fig:cad-period}
-% \end{figure}
+The relative orbit speed $t_\text{spin} \ t_\text{orbit}$ was determined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
+The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
+With this unphysical process, we isolate the effect of the amount of time spent near perigee on posterior uncertainty, without inheriting additional affects that would have been caused by the orbit changing shape.
 
-% We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
-Instead, we (un-physically) manipulate the speed at which the asteroid moves through the orbit.
-In one instance, the asteroid's path is artificially slowed by a factor of 2, which we denote as $t_\text{spin}/t_\text{orbit}=0.5$; in the other instance, $t_\text{spin}/t_\text{orbit}=2$, meaning that the orbit is sped up.
-This approach of changing the speed of the orbit is meant to approximate changes to $T_p$ defined in equation \ref{eqn:tp}.
-The posterior uncertainties for these two cases and the original case are shown as a function of $\Delta t$ in figure \ref{fig:cad-speed}.
-Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
-The $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-%   \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
-See text for the definition of $t_\text{spin}/t_\text{orbit}$.
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-%   \label{fig:cad-speed}
-% \end{figure}
-
-% Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
-Those that show no cut-off (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cut-off $T_\text{cad} > 60$ min, which is off the plot.
-By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dashed lines often (but not always) reach the cadence cut-off at lower $\Delta t$ than the solid line.
-For example, in figure \ref{fig:cad-period}, this effect is especially clear for $K_{22}$, $K_{33}$, $\Im K_{22}$, and $\Re K_{31}$, but the opposite appears for $\Re K_{32}$.
-The dashed curves are significant in both figures because they represent larger $\sigma$ cases ($P_\omega=5$ hours, or $t_\text{spin}/t_\text{orbit}=2$); section \ref{sec:scan-period} reveals that fast rotators lead to larger $\sigma$, and $t_\text{spin}/t_\text{orbit} > 1$ leads to larger $\sigma$ because of the presence of less perigee data.
-It therefore appears that small $P_\omega$ and small times spent at perigee move the cadence cut-off to smaller $T_\text{cad}$.
-
-% The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
-However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-vex} is) to study these regimes.
-Computation time and random variation in $\sigma$ also limits us.
-We therefore do not attempt to explore the dependence between $T_\text{cad}$ and the encounter parameters further.
-If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence} to yield more information.
+Figure \ref{fig:cad-contour} demonstrates that ...
 
@@
 
-In section \ref{sec:general-density}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
+In section \ref{sec:density-distro}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
 We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.

### 2022-04-28 paper/main.tex
Pulled speed contour plots

@@
 Their encounters can then be monitored by global ground-based networks such as the Las Cumbres Observatory (LCO) \cite{brown2013cumbres}.
-Such ground-based monitoring is typically used to derive the rotation period of an asteroid and its surface properties \cite{}\jtd{Ask for reference from Artem}.
+Such ground-based monitoring is typically used to derive the rotation period of an asteroid and its surface properties (see e.g.
+\cite{10.1093/mnras/stab1252}).
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
-  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-ratio-likelihood.pdf}\hfill
-  % \includegraphics[width=0.3\textwidth]{figs/asym-ell-ratio-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
-
-  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
-  % \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
-  %\includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}
-
-  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
-  % \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-likelihood.pdf}\hfill
-  % \includegraphics[width=0.3\textwidth]{figs/blob-ratio-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-diff-lumpy.pdf}
+
+  \includegraphics[width=0.33\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+
+  \includegraphics[width=0.33\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}
 
@@
 
-We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the time spent near perigee $T_p$.
-The latter can be estimated by
-\begin{equation}
-  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
-  \label{eqn:tp}
-\end{equation}
-which is the ratio of the perigee radius to velocity at perigee.
+We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
+How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
+% \begin{equation}
+%   T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
+%   \label{eqn:tp}
+% \end{equation}
+% which is the ratio of the perigee radius to velocity at perigee.
 The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
 For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
-
-%We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
 

### 2022-04-28 code/density/display.py

@@ -62,11 +62,19 @@ def make_frame(densities, pos_array, axis_name, cmap, percentile, balance, z_ind
     if balance:
         want_max = max(want_max, -want_min)
         want_min = -want_max
+
+    densities = np.clip(densities, want_min, want_max)
+
+    # Does the colorbar have an arrow?
+    extend = 'neither'
+    if percentile < 95:
+        extend = 'max'
+
     c = plt.pcolormesh(pos_array, pos_array, csection.transpose()   , shading='auto',
         vmin=want_min,
         vmax=want_max,
         cmap=cmap)
-    plt.colorbar(c).set_label(axis_name)
+    plt.colorbar(c, extend=extend).set_label(axis_name)
     plt.axis('equal')
     plt.xlabel("$y$ (m)")
     plt.ylabel("$x$ (m)")
@@ -80,12 +88,21 @@ def make_frame(densities, pos_array, axis_name, cmap, percentile, balance, z_ind
 
 def show_cross_section(densities, pos_array, axis_name, cmap, fname, percentile=99, balance=False):
     plt.figure()
+    want_min = np.nanpercentile(densities, 1)
+    want_max = np.nanpercentile(densities, percentile)
+    densities = np.clip(densities, want_min, want_max)
     csection = densities[:,:,densities.shape[-1]//2]
+
+    # Does the colorbar have an arrow?
+    extend = 'neither'
+    if percentile < 95:
+        extend = 'max'
+
     plt.pcolormesh(pos_array, pos_array, csection.transpose(), shading='auto',
-        vmin= np.nanpercentile(densities, 1),
-        vmax= np.nanpercentile(densities, percentile),
+        vmin= want_min,
+        vmax= want_max,
         cmap=cmap)
-    c = plt.colorbar()
+    c = plt.colorbar(extend=extend)
     plt.axis('equal')
     plt.xlabel("$x$ (m)")
     plt.ylabel("$y$ (m)")
@@ -109,6 +126,12 @@ def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percenti
         want_min = np.nanmin(densities)
         want_min = 0
 
+    densities = np.clip(densities, want_min, want_max)
+
+    # Does the colorbar have an arrow?
+    extend = 'neither'
+    if percentile < 95:
+        extend = 'max'
 
     if balance:
         want_max = min(want_max, -want_min)
[…]

### 2022-04-28 code/density/run.py

@@ -5,7 +5,7 @@ from lumpy import Lumpy, LUMPY_D, LUMPY_N
 from core import Asteroid, Indicator, TrueShape
 import matplotlib.pyplot as plt
 
-DIVISION = 9
+DIVISION = 99
 MAX_RADIUS = 2000
 RELOAD = False
 
@@ -46,8 +46,8 @@ asteroids = {
 }
 
 methods = {
-    #"likelihood": Likelihood,
-    #"harmonic": Harmonic, 
+    "likelihood": Likelihood,
+    "harmonic": Harmonic, 
     "lumpy": Lumpy, 
 }
 

### 2022-04-28 data/cad-period-sync-contour/compile.py

@@ -1,9 +1,10 @@
 # Goal: spawn a bunch of runs that cover the parameter space.
 from matplotlib import pyplot as plt
 import numpy as np
-from matplotlib.colors import Colormap
+import matplotlib as mpl
 
 plt.style.use("jcap")
+mpl.rcParams['font.size'] = 14
 
 param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
 
@@ -86,11 +87,13 @@ for plot_index in range(N_DIM):
 
     cbar = fig.colorbar(p, ax=ax)
     if plot_index < 3:
-        cbar.set_label(f"${param_names[plot_index]}\ (\\times 10^{{5}})$")
+        cbar.set_label(f"$\sigma({param_names[plot_index]})\ (\\times 10^{{5}})$")
     else:
-        cbar.set_label(f"${param_names[plot_index]}\ (\\times 10^{{2}})$")
+        cbar.set_label(f"$\sigma({param_names[plot_index]})\ (\\times 10^{{2}})$")
 
     ax.set_ylabel(f"$P_\omega$ (hr)")
+
+    ax.axhline(y=9, color='k', linestyle='dashed', linewidth=1)
 
     #axs[plot_index].set_xscale('log')
     #axs[plot_index].set_yscale('log')

### 2022-04-28 data/cad-speed-contour/extract-percentiles.py

@@ -1,0 +1,52 @@
+# Goal: spawn a bunch of runs that cover the parameter space.
+from matplotlib import pyplot as plt
+import numpy as np
+import os
+
+TRUE_THETA = np.array([0.39269908169, 0.05200629, -0.2021978, 0, 0, 0, 0, 0, 0, 0])
+DIST_DIMENSION = 1
+
+plt.style.use("jcap")
+
+file_names = os.listdir()
+file_names.sort()
+
+pf = open("percentiles.dat", 'w')
+
+for bare in file_names:
+    if not os.path.isdir(bare):
+        continue
+
+    min_dist = None
+    min_text = None
+    for file in os.listdir(bare):
+        if not file[-11:] == "samples.npy": continue
+        with open("{}/{}".format(bare, file), 'rb') as f:
+            array = np.load(f)
+        
+        flat_samples = array.reshape(-1, array.shape[-1])
+
+        # Get means
+        means = np.mean(flat_samples, axis=0)
+        dist = (means - TRUE_THETA)[DIST_DIMENSION]
+        if min_dist is None or dist < min_dist:
+            data = []
+            for i in range(flat_samples.shape[1]):
+                data.append(", ".join([
+                    str(np.mean(flat_samples[:,i])),
+                    str(np.percentile(flat_samples[:,i], 50 + 95.45 / 2)),
+                    str(np.percentile(flat_samples[:,i], 50 + 68.27 / 2)),
+                    str(np.percentile(flat_samples[:,i], 50)),
+                    str(np.percentile(flat_samples[:,i], 50 - 68.27 / 2)),
+                    str(np.percentile(flat_samples[:,i], 50 - 95.45 / 2)),
+                ]))
+
+            min_text = file + ": " +  ": ".join(data)+"\n"
+            min_dist = dist
+
+    if min_text is None:
+        continue
+    pf.write(min_text)
+    print(bare, min_dist)
+
+pf.close()

### 2022-04-28 paper/appendices.tex
Added cadence appendix to paper

@@
 In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-In the left panel of figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} \ t_\text{orbit}$ (right panel).
+In the left panel of figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
 Both panels show the sudden increase in posterior uncertainty we named $T_\text{cad}$.
 Now $T_\text{cad}$ is visible as a function of frequency and relative orbit speed.
+In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
 
@@
   \includegraphics[width=0.49\textwidth]{figs/cad-speed.pdf}
-  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).}
+  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
+The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
+The line }
   \label{fig:cad-contour}
@@
 
-The relative orbit speed $t_\text{spin} \ t_\text{orbit}$ was determined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
+The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was determined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
 The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
@@
 
-Figure \ref{fig:cad-contour} demonstrates that ...
+Figure \ref{fig:cad-contour} demonstrates that, near the reference values of $P_\text{omega}$ and $t_\text{spin} / t_\text{orbit}$, $T_\text{cad}$ depends on both time scales $P_\omega$ and $t_\text{spin} / t_\text{orbit}$.
+Specifically, high rotational period and slow orbits are optimal for large $T_\text{cad}$.
+The dependence on $P_\omega$ agrees with the fact that large rotational periods for fixed cadence lead to better posterior uncertainty, discussed in section \ref{sec:scan-period}.
+The figure also demonstrates that for large $P_\omega$, $T_\text{cad}$ depends less strongly on $P_\text{omega}$ and may even reverse its dependence such that increasing $P_\text{omega}$ decreases $T_\text{omega}$.
+In all cases except $\Re K_{33}$, at least constant-$\sigma(K_{\ell m})$ contour is seen to curve back such that $\Delta t$ decreases as a function of $P_\text{omega}$ for large $P_\text{omega}$.
+However, in these regions the cadence cut-off also dulls, as shown by the spreading of the constant-$\sigma(K_{\ell m})$ contours in this region.
+
+The right panel of figure \ref{fig:cad-contour} shows a slightly stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
+It appears that slightly slower orbits sharply increases $T_\text{cad}$.
+Similar in the $P_\omega$ case, for increasingly fast orbits, $T_\text{cad}$ depends less on $t_\text{spin}/ t_\text{orbit}$.
+\jtd{I wanted to talk to Julien about the interpretation of this panel. Because $t_\text{spin} / t_\text{orbit}$, I find it hard to interpret. Maybe a different type of scan is better.}
+
+Figure \ref{fig:cad-contour} demonstrates that, for large period, the cadence cut-off $T_\text{cad}$ reduces in prominence and rises to above one hour, meaning that large gaps of time between observations can still lead to well-constrained parameters in these cases.
+Faster orbits also lead to $T_\text{cad} > 1$ hr for for as small a decrease as $t_\text{spin} / t_\text{orbit}  \approx 75$\%.
 

### 2022-04-28 paper/main.tex
Added cadence appendix to paper

@@
 
-  \caption{Density distributions (\textit{top}) and uncertainties (\textit{bottom}) extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density, asymmetric reference asteroid.
+  \caption{Based on density moments extracted from synthetic data of the uniform-density asymmetric reference asteroid encounter, the following are shown.
+From top to bottom, the density distributions, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
+The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
 Density is normalized so that mean density is one.}
@@
 
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
+  \caption{Based on density moments extracted from synthetic data of the asymmetric reference asteroid encounter with an off-center lump, the following are shown.
+From top to bottom, the density distributions, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
+The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
+Density is normalized so that mean density is one.}
   \label{fig:blob-density}

### 2022-04-28 data/cad-speed-contour/compile.py

@@ -82,7 +82,8 @@ for plot_index in range(N_DIM):
 
     #p = ax.pcolormesh(cadences, time_ratios, param_data.transpose() * scale, vmin=0, cmap="Oranges_r")
     levels = np.linspace(0, np.percentile(param_data * scale, 90), 12)
-    p = ax.contourf(cadences, time_ratios, param_data.transpose() * scale, cmap="Oranges_r", levels=levels, extend='max')
+    p = ax.contourf(cadences, time_ratios, param_data.transpose() * scale, cmap="PuBu_r", levels=levels, extend='max')
+    ax.contour(cadences, time_ratios, param_data.transpose(), colors=['r'], levels=[0.01])
 
     cbar = fig.colorbar(p, ax=ax)
     if plot_index < 3:
@@ -91,6 +92,7 @@ for plot_index in range(N_DIM):
         cbar.set_label(f"$\sigma({param_names[plot_index]})\ (\\times 10^{{2}})$")
 
     ax.set_ylabel(f"$t_\\mathrm{{spin}}/t_\\mathrm{{orbit}}$")
+
 
     #axs[plot_index].set_xscale('log')
     #axs[plot_index].set_yscale('log')

### 2022-04-29 paper/appendices.tex
Responded to Julien's comments

@@
 The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
-The line }
+The red line represents the $\sigma(K_{\ell m})$ threshold.
+Cadence cutoff depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
   \label{fig:cad-contour}
@@
 \textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
-The same length scale is used in both figures.}
+The same length scale is used in both figures.
+This new shape model successfully estimates an asteroid shape which is qualitatively consistent with the distributions extracted via models from the main text.}
   \label{fig:surface-density}

### 2022-04-29 paper/main.tex
Responded to Julien's comments

@@
 We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we perform injection-retrieval \jtd{tests} on these synthetic data to gain insights into the extent to which interior properties can be constrained.
+Using Markov Chain Monte Carlo fits, we perform injection-retrieval tests on these synthetic data to gain insights into the extent to which interior properties can be constrained.
 We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., moment of inertia and initial spin pole direction), observational set up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
-\jtd{We find that high precision in period estimates (order of milliseconds to seconds) are necessary for each cadence, and that large asteroids ($> 100$ m radius) with low perigees ($<20$ Earth radii) are necessary to resolve beyond-leading-order density moments}.
+We find that high precision in rotational period estimates (order of milliseconds to seconds) are necessary for each cadence, and that large asteroids ($> 100$ m radius) with low perigees ($<20$ Earth radii) are necessary to resolve second-order density moments.
 \end{abstract}
@@
 We then describe three methods to generate full density distributions from the density moments.
-In section \ref{sec:results}, we present the results of a series of injection-retrieval \jtd{tests} demonstrating the extent to which the properties of an asteroid chosen to generate synthetic spin data can be retrieved via our methodology.
+In section \ref{sec:results}, we present the results of a series of injection-retrieval tests demonstrating the extent to which the properties of an asteroid chosen to generate synthetic spin data can be retrieved via our methodology.
 Finally, in section \ref{sec:discussion}, we assess the sensitivity of these constraints to various physical, observational, and methodological parameters to provide guidance for monitoring upcoming close encounters.
@@
 One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
-\jtd{The choice of $a_\mathcal{A}$ can be adjusted after the fit to assess the dependence of the density distributions on $a_\mathcal{A}$}
+The choice of $a_\mathcal{A}$ can be adjusted after the fit to assess the dependence of the density distributions on $a_\mathcal{A}$
 
@@
 See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model.
-\jtd{A log normal distribution is chosen such that $\rho > 0$, but since $\sigma_\rho \ll 1$ typically in our analysis, $P(\rho)$ is approximately Gaussian.}
+A log normal distribution is chosen such that $\rho > 0$, but since $\sigma_\rho \ll 1$ typically in our analysis, $P(\rho)$ is approximately Gaussian.
 
@@
 In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
-\jtd{When extracting density distributions, multiple $a_\mathcal{A}$ values may be tested and the multiple produced density distributions can be compared to highlight common features.}
+When extracting density distributions, multiple $a_\mathcal{A}$ values may be tested and the multiple produced density distributions can be compared to highlight common features.
 
@@
   \includegraphics[width=0.6\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. Uncertainty bands are also shown.}
+  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
+Uncertainty bands are also shown.
+The best fit results appear consistent with the data.}
   \label{fig:example-residuals}
@@
 Samples from the MCMC fit are shown as individual points, and the contours enclose 1, 2, and 3$\sigma$ confidence regions.
-True values are shown as blue lines.}
+True values are shown as blue lines.
+PPDs are Gaussian and show no degeneracies.}
   \label{fig:example-corner}
@@
   \caption{Based on density moments extracted from synthetic data of the uniform-density asymmetric reference asteroid encounter, the following are shown.
-From top to bottom, the density distributions, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
+From top to bottom, the density distributions extracted by the methods of section \ref{sec:density-distro}, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
 The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
-Density is normalized so that mean density is one.}
+Density is normalized so that mean density is one.
+Density is consistent with uniform in all cases ($\lesssim 1 \sigma$ deviation), and typically differs from uniform by little more than 40\%.}
   \label{fig:uniform-density-results}
@@
 
-Also in each pane of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
+Also in each panel of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}^2$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
 This difference is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
@@
 This is generally true for uniform density asteroids, which have harmonic density distributions.
-Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
+Consequentially, $\Delta K_{\ell m}^2$ is low for the harmonic model.
 This similarity lends confidence to both models, because if one were unexpectedly biased towards certain distributions, the other would have to be equally biased in the same way in this case to produce the same distribution, which appears unlikely given that the models share little in common.
@@
 The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
-However, it does not produce a density distribution consistent with the moments extracted from spin data (i.e., $\Delta K_{\ell m}$ is large).
+However, it does not produce a density distribution consistent with the moments extracted from spin data (i.e., $\Delta K_{\ell m}^2$ is large).
 This is because the lump found extends outside the asteroid, violating the assumptions of the model.
@@
 The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
-Density is normalized so that mean density is one.}
+Density is normalized so that mean density is one.
+\jtd{Explanatory sentence}}
   \label{fig:blob-density}
@@
 
-\subsection{Spin evolution}
-\label{sec:spin-evolution}
-In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
+% \subsection{Spin evolution}
+% \label{sec:spin-evolution}
+% In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
 A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter.
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/nominal-data-sym.pdf}
-  \includegraphics[width=\linewidth]{figs/nominal-data-asym.pdf}
-  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=\linewidth]{figs/nominal-data-sym.pdf}
+%   \includegraphics[width=\linewidth]{figs/nominal-data-asym.pdf}
+%   \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
 The true angular velocity evolution is shown as a black line.
 Also plotted is the deviation of the data for PPD-distributed perturbations to the asteroid shape (bands).
-Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
-  \label{fig:example-data}
-\end{figure}
-
-The initial values of $\gamma_0$, $K_{20}$, and $K_{22}$ were distributed proportional to the PPDs extracted via the MCMC fit shown in section \ref{sec:example-fit}.
+Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.
+The spread of the bands after perigee indicates that angular velocity data is perturbed by tidal interactions at perigee, in a manner sensitive to the density distribution of the asteroid.}
+%   \label{fig:example-data}
+% \end{figure}
+
+% The initial values of $\gamma_0$, $K_{20}$, and $K_{22}$ were distributed proportional to the PPDs extracted via the MCMC fit shown in section \ref{sec:example-fit}.
 The PPDs were widened by a factor of 1000 to make the band widths visible.
@@
 
-The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
+% The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
 The spin data at perigee is informative and shows non-trivial behaviour.
@@
 We use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
+
+\jtd{Add table}
 
@@
     \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, rotational period, observational cadence, and data gap at perigee.
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
 The vertical dashed line indicates the reference asteroid values.
@@
 These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
-To precisely measure density moments, very accurate rotational period estimates would have to be made every cadence.
+To precisely measure density moments, very accurate rotational period estimates would have to be made for every angular velocity data point.
 However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
@@
 
-THe true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
+The true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
 Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
@@
   \caption{1$\sigma$ posterior uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
+Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
+Symmetric asteroids ($K_{22}=0$ or $a/c=b/c$) show increased posterior uncertainty, but otherwise posterior uncertainty is roughly constant.}
   \label{fig:scan-space-sigma}
@@
   \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
+Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
+The first order parameters $K_{22}$ and $K_{20}$ are correlated, as are initial orientation $\gamma_0$ and $K_{22}$.}
   \label{fig:scan-space-corr}
 \end{figure*}
+
+\jtd{More info}
 
@@
 We name this rough cadence limit $T_\text{cad}$.
-
-We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
+$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
+
+We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
 How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
@@
 
-To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same size.
-We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
-
-Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
-We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
+To test this, we mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T_\text{gap}$, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
+We then fit the same asteroid model to the cut data for all $T_\text{gap}$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
+
+Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T_\text{gap}$, which is seen in figure \ref{fig:observation-gap}.
+We also see that the first-order parameters are not as sensitive to $T_\text{gap}$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
 
@@
 
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
+Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T_\text{gap}$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T_\text{gap}$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T_\text{gap}$.
 This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
@@
 The orange star indicates the reference spin pole.
-The red contours enclose regions where $\sigma(K_{3m}) \geq 0.01$.}
+The red contours enclose regions where $\sigma(K_{3m}) \geq 0.01$.
+Posterior uncertainty depends similarly on initial spin pole direction for all parameters}
   \label{fig:scan-spin}
@@
 Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the south pole, or $-\unit Z$.}
+The polar projection is centred at the south pole, or $-\unit Z$.
+Posterior uncertainty is large near $\pm \unit Z$ and $\pm \unit Y$, but roughly constant elsewhere.}
   \label{fig:scan-spin-avg}
@@
 \textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.}
+Also shown in both figures are the oblatenesses of reference Solar System bodies.
+Posterior uncertainty depends little on oblateness, but the best-fitting parameter estimates are affected enough by oblateness that oblateness must still be modelled.}
   \label{fig:scan-oblateness}
@@
 Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
+These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
 The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
@@
 Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
+However, the bottom panel of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
 This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
@@
   \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
+  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.
+Observational uncertainty and cadence are assumed to be equivalent for the Jupiter and Earth encounters.
+Without taking the frequencies of close encounters into account, massive planets such as Jupiter yield less precise density moment estimates.}
   \label{tab:jupiter-uncertainty}
@@
 Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
+The same distance scale is used in all figures.
+The likelihood and harmonic models generally recover accurate density distributions for asymmetric, uniform density asteroids, though symmetric asteroids yield much worse precision.}
   \label{fig:uniform-density}
@@
 From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
-Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
+Consequentially, $\Delta K_{\ell m}^2$ is low for the harmonic model.
 Also like section \ref{sec:asym-density}, the dumbbell asteroid produces largely uniform distributions except in a few small regions, and the lumpy model generates clearly incorrect results indicating that no lump is present.
@@
 Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
+The same distance scale is used in all figures.
+Density distributions show clear pathologies when the incorrect shape is used.}
   \label{fig:sphere-density}
@@
 
-Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
+Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}^2$ is low, and they produce similar distributions as in the previous section.
 However, now even the asymmetric asteroid (with low uncertainty in $K_{\ell m}$) produces negative densities.
@@
 The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
-The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|^2$ for the original asteroids, making it clearly a poor model.
+The error in density moments $\Delta K_{\ell m}^2$ is therefore very large, equal to the sum of $|K_{\ell m}|^2$ for the original asteroids, making it clearly a poor model.
 
@@
 Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
+The same distance scale is used in all figures.
+The extracted distributions agree qualitatively with the true distributions.}
   \label{fig:non-uniform-density}
@@
 
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
+For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
 However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
@@
 Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
+Greater error is incurred in $\Delta K_{\ell m}^2$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
 This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.

### 2022-04-29 paper/appendices.tex
Pulled apophis data

@@
 Similar in the $P_\omega$ case, for increasingly fast orbits, $T_\text{cad}$ depends less on $t_\text{spin}/ t_\text{orbit}$.
-\jtd{I wanted to talk to Julien about the interpretation of this panel. Because $t_\text{spin} / t_\text{orbit}$, I find it hard to interpret. Maybe a different type of scan is better.}
+\jtd{I wanted to talk to Julien about the interpretation of this panel.
+Because $t_\text{spin} / t_\text{orbit}$, I find it hard to interpret because it's unphysical.
+Maybe a different type of scan is better?
+Or I could just stop here and not interpret further.}
 

### 2022-04-29 paper/main.tex
Pulled apophis data

@@
 
-\subsubsection{Uniform density asteroids}
-
-We simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
+% \subsubsection{Uniform density asteroids}
+
+% We simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
 This was already done in section \ref{sec:asym-density} for the asymmetric reference asteroid.
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
+
+%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
+
+%   \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
+%   \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
+%   \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
 The asteroid shapes are, from top to bottom, a dumbbell, the symmetric reference asteroid, and a tetrahedron.
@@
 The likelihood and harmonic models generally recover accurate density distributions for asymmetric, uniform density asteroids, though symmetric asteroids yield much worse precision.}
-  \label{fig:uniform-density}
-\end{figure*}
-
-From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
+%   \label{fig:uniform-density}
+% \end{figure*}
+
+% From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
 Consequentially, $\Delta K_{\ell m}^2$ is low for the harmonic model.
@@
 
-The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
+% The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
 In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
@@
 
-Uncertainty in each distribution was calculated but not shown.
+% Uncertainty in each distribution was calculated but not shown.
 The size of uncertainty is such that the density distribution is very consistent with uniform at most points for the (asymmetric) dumbbell model (within $\sim 1\sigma$), while the symmetric reference and tetrahedral asteroids were generally within $\sim 2 \sigma$ of uniform.
@@
 
-If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
+% If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
 However, doing so ignores the observational insight we gain from our fits to $K_{3m}$, so it is only valid when $K_{3m}$ are too poorly constrained to be used.

### 2022-04-29 apophis/code/generate/display.py

@@ -25,6 +25,9 @@ time = np.arange(0, len(perfect_xs), 1) * 120/3600
 plt.plot(time, perfect_xs, label=f'x perfect')
 plt.plot(time, perfect_ys, label=f'y perfect')
 plt.plot(time, perfect_zs, label=f'z perfect')
+plt.scatter(time, perfect_xs, label=f'x perfect', s=2)
+plt.scatter(time, perfect_ys, label=f'y perfect', s=2)
+plt.scatter(time, perfect_zs, label=f'z perfect', s=2)
 plt.title(file_name)
 
 f = open(f"{file_name}-resolved.dat", 'r')

### 2022-04-29 apophis/code/sim/backend.hpp

@@ -18,7 +18,7 @@
 #define MAX_DT 20.0
 #define POSITION_DT 1.0
 
-#define INTEGRAL_LIMIT_FRAC_START 1,0e-3 // 1.0e-12
+#define INTEGRAL_LIMIT_FRAC_START 1.0e-3 // 1.0e-12
 #define INTEGRAL_LIMIT_FRAC_END 1.0e-3
 
 //#define TEXT_DEBUG

### 2022-04-30 paper/main.tex
Fixed staged

@@
 The same distance scale is used in all figures.
-Density distributions show clear pathologies when the incorrect shape is used.}
+Density distributions show clear pathologies when the incorrect shape is used.
+\jtd{Add uncertainty plots}}
   \label{fig:sphere-density}
@@
 The same distance scale is used in all figures.
-The extracted distributions agree qualitatively with the true distributions.}
+The extracted distributions agree qualitatively with the true distributions.
+\jtd{Add uncertainty plots}}
   \label{fig:non-uniform-density}

### 2022-05-01 paper/main.tex
Fit less to test degeneracy

@@
 \usepackage{bm}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 
-Figure \ref{fig:example-residuals} shows the synthetic spin data.
+Figure \ref{fig:example-residuals} shows our synthetic spin data.
 The best-fitting model is overlaid in the top panel and residuals are shown the bottom panel.
@@
 From top to bottom, the density distributions extracted by the methods of section \ref{sec:density-distro}, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
+For the bottom three rows, color map range is chosen to include 95\% of the asteroid to suppress outliers.
 The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
@@
 
-Also in each panel of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}^2$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
+Also in each panel of figure \ref{fig:uniform-density-results} is $\chi^2_r$, or reduced chi squared value, defined as the average of the squared differences between the fitted density moments and the density moments of the final distribution divided by the fit uncertainties.
+This fit metric is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
 The harmonic and lumpy models have no such guarantee, however.
@@
 This is generally true for uniform density asteroids, which have harmonic density distributions.
-Consequentially, $\Delta K_{\ell m}^2$ is low for the harmonic model.
+Consequentially, $\chi^2_r$ is relatively low for the harmonic model.
 This similarity lends confidence to both models, because if one were unexpectedly biased towards certain distributions, the other would have to be equally biased in the same way in this case to produce the same distribution, which appears unlikely given that the models share little in common.
@@
 The distributions are non-uniform for the harmonic and likelihood models (driven by error in the estimates of $K_{3m}$), but the non-uniformity is limited.
-Note that most of the asteroid has density close to the mean density (one) in both cases, with densities of 40\% or 160\% of the mean attained only in small regions.
+The second row of figures indicates that 95\% of the asteroid lies within 39\% of the true density distribution for the likelihood and harmonic models.
 The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
-However, it does not produce a density distribution consistent with the moments extracted from spin data (i.e., $\Delta K_{\ell m}^2$ is large).
-This is because the lump found extends outside the asteroid, violating the assumptions of the model.
-This is a sign that the lump found does not really exist inside the asteroid.
-
-The size of uncertainty is such that the density distribution is consistent with uniform for the harmonic and likelihood models (within 1.5$\sigma$).
+However, it produces a density distribution less consistent with the moments extracted from spin data than the previous two models (i.e., $\chi^2_r$ is large).
+This is because the lump found extends outside the asteroid, violating the assumptions of the model, which is a sign that the lump found does not really exist inside the asteroid.
+
+The third row of figures indicates that density distribution uncertainty  can extend to 78\% of the local density, but most of the asteroid is well below this value.
 Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
-
-To test the ability of the asteroid to identify discrete changes in density distribution of the kind that the lumpy model is designed to detect, we show one more example extraction.
+The fourth row indicates that for 95\% of the asteroid, the density distribution is within 1$\sigma$ of the true, uniform distribution.
+Uncertainty plots are not generated for the lumpy model because the distribution is not continuous; each point in the asteroid can only take one of two density values, depending on whether it is inside the asteroid or outside it.
+
+To test the ability of our methodology to identify discrete changes in density distribution of the kind that the lumpy model is designed to detect, we show another example extraction.
 We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
 Both the mass and the medium have uniform density.
-The density moments are extracted via  a fit similarly to section \ref{sec:example-fit} and the distributions extracted by the three models for this asteroid are shown in figure \ref{fig:blob-density}.
+The density moments are extracted and density distributions made via the three models and are shown in figure \ref{fig:blob-density}.
 
@@
 
-  \caption{Based on density moments extracted from synthetic data of the asymmetric reference asteroid encounter with an off-center lump, the following are shown.
-From top to bottom, the density distributions, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
-The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
-Density is normalized so that mean density is one.
-\jtd{Explanatory sentence}}
+  \caption{Density distributions and uncertainties for the asymmetric reference asteroid encounter with an off-center lump.
+See figure \ref{fig:uniform-density-results} for a description of each panel.}
   \label{fig:blob-density}
@@
 
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect.
-Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
-
-The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edges of the lump.
+We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump, in that the top row shows a smoothly varying distribution while the second row shows that the distribution is too low by a factor of half the mean density in the region of the lump.
+In the case of the likelihood model, the density is also twice the mean just outside the lump boundary, indicating that the model has identified the general location of the lump but cannot refine its radius and resolve the lump's edge.
+Unlike the previous example, the harmonic and likelihood models do not agree exactly, and $\chi^2_r$ is large for the harmonic model.
+These two facts arise from the fact that the true distribution is not harmonic.
+
+The uncertainty plots (lower two rows) of figure \ref{fig:blob-density}  show consistency with the true distribution (within 1.2 $\sigma$ for 95\% of the asteroid), although uncertainties are larger for this non-uniform case than they were for figure \ref{fig:uniform-density-results}.
+The uncertainty rises to as much as 85\% of the local density as opposed to 78\% in the former case.
+
+The failure of the harmonic and likelihood models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities.
 However, the lumpy model computes the location and density of the mass very well.
@@
 This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
-Nevertheless, it seems that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned above when the density moment data is redundant with the asteroid shape).
-But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in the above sections.
-
-\jtd{I will also add a discussion of uncertainties once the plots are generated.}
+There is therefore a 70 m-thick shell surrounding the lump produced by the lumpy model which has been inaccurately estimated, but this shell contains less than 5\% of the asteroid.
+The scale of figure \ref{fig:blob-density} shows that, for the rest of the asteroid, the density is estimated accurately to about two parts in one thousand.
+This model produces a $\chi^2_r$ lower than the harmonic model, indicative of its accuracy.
+
+It seems that the lumpy model is capable of recreating the location of lumps.
+But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in figure \ref{fig:uniform-density-results}.
+
+\jtd{Note for Julien: the cutoffs on the color bars (95\% of the asteroid) are kind of arbitrary.
+I could make histograms showing, on the vertical axis, $\Delta \sigma$ or $\sigma_\rho/\rho$ or $\Delta \rho$ (i.e.,  the metrics which are plotted in these figures).
+On the vertical axis, I would plot what fraction of the asteroid has these values.
+So you would expect to see that most of the asteroid has $\Delta \rho$ small, and then there's a cutoff beyond which only a small fraction of the asteroid has larger $\Delta \rho$.
+Do you think this plot is worth the space?}
 
@@
 
-\jtd{Add table}
-
 \afterpage{
@@
 
-There is no clear threshold above which posterior uncertainty is ``too high.'' However, most asteroid distributions tested in this paper have $K_{3 m} \lesssim 0.01$.
-We therefore call $\sigma(K_{3 m}) \approx 0.01$ the ``posterior uncertainty threshold,'' beyond which $K_{3 m}$ are unresolved.
-This should be understood as a rule of thumb, not a precise statement.
+It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
+There are many possible definitions of posterior uncertainty, but we explore one in this paper which is outlined in appendix \ref{app:sigma-threshold}.
+This leads to cut-offs of the encounter properties which lead to posterior uncertainty less than the threshold.
+These critical values are shown in table \ref{tab:threshold-summary} as a summary, and are discussed in detail in the following sections.
+
+\begin{table}
+  \centering
+  \begin{tabular}{lll} \hline
+    Encounter property & Strong & Weak \\ \hline
+    Excess velocity ($v_\infty$) & & \\
+    Perigee ($r_p$) & & \\
+    Spin pole uncertainty ($\sigma_\theta$) & & \\
+    Spin period uncertainty ($P_\omega \sigma_\rho$) & & \\
+    Asteroid length ($a_\mathcal{A}$) & & \\
+    Cadence ($\Delta t$) & & \\
+    Data gap ($T_\text{gap}$) & & \\
+    Rotational period ($P_\omega$) & & \\ \hline
+  \end{tabular}
+  \caption{For each encounter property discussed in section \ref{sec:discussion}, the cut-offs (i.e., the values which leads to $\sigma(K_{3 m})$ at the threshold value) are given.
+Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cutoff have at least one $\sigma(K_{3m})$ under the threshold value.
+The reference asymmetric asteroid is used.
+\jtd{summary}}
+  \label{tab:threshold-summary}
+\end{table}
 
@@
 
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids.
-In both cases, the density distributions have been extracted assuming a spherical shape.
+  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
+  \hspace{0.33\textwidth}
+
+  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asymmetric asteroid.
+The density distributions have been extracted assuming a spherical shape.
+The extracted density distributions are shown in the top row with uncertainties in the bottom row.
 Density is normalized so that mean density is one.
@@
 Density distributions show clear pathologies when the incorrect shape is used.
-\jtd{Add uncertainty plots}}
+}
   \label{fig:sphere-density}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/in-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/in-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/in-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/out-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/out-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/out-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).
+\jtd{The failure of this model (which is not yet reflected in the text well) makes me think we really should only do the finite element analysis. Though it is slow.}
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+      \begin{subfigure}{0.49\linewidth}
+        \centering
+        \includegraphics[width=0.33\linewidth]{figs/in-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-harmonic.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-lumpy.pdf}
+
+        \includegraphics[width=0.33\linewidth]{figs/in-diff-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-diff-harmonic.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-diff-lumpy.pdf}
+
+        \includegraphics[width=0.33\linewidth]{figs/in-unc-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-unc-harmonic.pdf}\hfill
+        \hspace{0.33\linewidth}
+
+        \includegraphics[width=0.33\linewidth]{figs/in-rat-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/in-rat-harmonic.pdf}\hfill
+        \hspace{0.33\linewidth}
+      \end{subfigure}\hfill
+      \begin{subfigure}{0.49\linewidth}
+        \centering
+        \includegraphics[width=0.33\linewidth]{figs/out-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-harmonic.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-lumpy.pdf}
+
+        \includegraphics[width=0.33\linewidth]{figs/out-diff-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-diff-harmonic.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-diff-lumpy.pdf}
+
+        \includegraphics[width=0.33\linewidth]{figs/out-unc-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-unc-harmonic.pdf}\hfill
+        \hspace{0.33\linewidth}
+
+        \includegraphics[width=0.33\linewidth]{figs/out-rat-likelihood.pdf}\hfill
+        \includegraphics[width=0.33\linewidth]{figs/out-rat-harmonic.pdf}\hfill
+        \hspace{0.33\linewidth}
+      \end{subfigure}
+    \caption{Density distributions extracted for non-uniform-density asteroids with mass concentrated in the middle (\textit{left}) and the edges (\textit{right}).
+Within each half-figure, the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models are used.
 Density is normalized so that mean density is one.
@@
 The extracted distributions agree qualitatively with the true distributions.
-\jtd{Add uncertainty plots}}
+\jtd{Summarizing sentence}}
     \label{fig:non-uniform-density}
-\end{figure*}
+  \end{figure}
+  \end{landscape}
+}
 

### 2022-05-01 code/density/core.py

@@ -141,6 +141,8 @@ class Method:
         nonzero_cov = self.asteroid.sigma_data[uncertain_params,:][:,uncertain_params]
         self.klm_error = abs(deltas.transpose().conj() @ pinv(nonzero_cov) @ deltas / dof)
 
+        print("Ratios", deltas / np.sqrt(np.diagonal(nonzero_cov)))
+
         for i, r in enumerate(calc_rlms):
             l = int(np.sqrt(i))
             m = i - l**2 - l
@@ -177,8 +179,8 @@ class Method:
                 make_slices(ratios, self.asteroid.grid_line, "$\\Delta\\sigma$", 'coolwarm', f"{fname}-r", self.klm_error, percentile=95, balance=True)
                 make_gif(ratios, self.asteroid.grid_line, "$\\Delta\\sigma$", 'coolwarm', f"{fname}-r.gif", duration=duration, percentile=95, balance=True)
 
-                for p in 10 * np.arange(11):
-                    print(f"Ratio percentile {p} = {np.nanpercentile(ratios, p)}")
+                # for p in 10 * np.arange(11):
+                #     print(f"Ratio percentile {p} = {np.nanpercentile(ratios, p)}")
             difference = (true_densities - display_densities) / true_densities
 
         print("Plotting density")

### 2022-05-06 paper/main.tex
Apophis cadence staged

@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-diff-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
-
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}
 
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-diff-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.33\textwidth}
-
-  \includegraphics[width=0.33\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.33\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
+
+  \includegraphics[width=0.3\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}
 
@@
 We use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-perigee}
-    \label{fig:scan-vex}
-    \label{fig:scan-theta}
-    \label{fig:scan-rho}
-    \end{figure}
-  \end{landscape}
-}
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-am}
-    \label{fig:scan-cadence}
-    \label{fig:scan-period}
-    \label{fig:observation-gap}
-    \end{figure}
-  \end{landscape}
-}
 
@@
 
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+    \label{fig:scan-perigee}
+    \label{fig:scan-vex}
+    \label{fig:scan-theta}
+    \label{fig:scan-rho}
+    \end{figure}
+  \end{landscape}
+}
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+    \label{fig:scan-am}
+    \label{fig:scan-cadence}
+    \label{fig:scan-period}
+    \label{fig:observation-gap}
+    \end{figure}
+  \end{landscape}
+}
+
 \subsubsection{Observational uncertainty}
@@
 In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
+We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$.
+\jtd{The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
+The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.}
+
 The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
@@
 
-\jtd{More info}
+\jtd{The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
+If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated.
+This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.}
 
@@
   \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
-  \hspace{0.33\textwidth}
+  \includegraphics[width=0.3\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-sph-lumpy.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
+  \hspace{0.3\textwidth}
 
@@
 
-\jtd{The failure of this model (which is not yet reflected in the text well) makes me think we really should only do the finite element analysis. Though it is slow.}
+\jtd{The failure of this model makes me think we really should only do the finite element analysis. Though it is slow.}
+
+For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\chi_r^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
+However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
+Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
+The difference of the model output from the true distribution is generally less than $1-1.5\sigma$ for 95\% of the asteroid.
+However, there are regions with very large uncertainty (as much as 14 times the local density).
+This leads to deviations from the local density by factors of a much as 4.
+The locations of these high-uncertainty regions correspond to low-density, in that they occur at the edge of the edge-weighted asteroid and at the center of the center-weighted asteroid.
+
+Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
+Greater error is incurred in $\chi^2_r$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
+This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
+
+The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ when the density moments are redundant with the asteroid shape; specifically, when (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
+(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
+The lump radius will then be set to zero because the fitted density moments are already matched.
+This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
+The lump model will therefore fail to recognize the lump in the true density distribution.
+
+An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
+This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape rather than a distribution that conforms to the asteroid shape.
 
@@
 The same distance scale is used in all figures.
-The extracted distributions agree qualitatively with the true distributions.
-\jtd{Summarizing sentence}}
+The extracted distributions agree qualitatively with the true distributions, but are highly uncertain and can misestimate the local density by factors of almost 4.}
     \label{fig:non-uniform-density}
@@
 }
-
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
-Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
-The difference of the model output from the true distribution is generally less than $2\sigma$, but can rise to $3\sigma$ in some regions.
-
-Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}^2$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
-This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
-
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ when the density moments are redundant with the asteroid shape; specifically, when (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
-(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
-The lump radius will then be set to zero because the fitted density moments are already matched.
-This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
-The lump model will therefore fail to recognize the lump in the true density distribution.
-
-An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape rather than a distribution that conforms to the asteroid shape.
 

### 2022-05-11 paper/main.tex
Thresholds added

@@
 
+\jtd{This Klm uncertainty threshold language is still in the paper, although the numbers in the above table reflect the method I used for the conference, which is asking what encounter properties yield density distributions with uncertainty 100 or 20\% of the local density.
+The caveat to the latter, density-distribution based, uncertainty threshold is that it changes based on which models you use and how many Klms you choose to fit due to the fact that the density distribution is underdetermined.
+A constraint on the density moments is more general, but harder to define.
+My feeling is that we should use this distribution-based constraint, and mention the caveats here.
+I'll write up all this if Julien agrees.}
+
 \begin{table}
@@
   \begin{tabular}{lll} \hline
-    Encounter property & Strong & Weak \\ \hline
-    Excess velocity ($v_\infty$) & & \\
-    Perigee ($r_p$) & & \\
-    Spin pole uncertainty ($\sigma_\theta$) & & \\
-    Spin period uncertainty ($P_\omega \sigma_\rho$) & & \\
-    Asteroid length ($a_\mathcal{A}$) & & \\
-    Cadence ($\Delta t$) & & \\
-    Data gap ($T_\text{gap}$) & & \\
-    Rotational period ($P_\omega$) & & \\ \hline
+    Encounter property & $\sigma_\rho / \rho = 100\%$ & $\sigma_\rho / \rho = 20\%$ \\ \hline
+    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
+    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
+    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
+    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
+    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
+    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\
+    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
   \end{tabular}
   \caption{For each encounter property discussed in section \ref{sec:discussion}, the cut-offs (i.e., the values which leads to $\sigma(K_{3 m})$ at the threshold value) are given.
-Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cutoff have at least one $\sigma(K_{3m})$ under the threshold value.
+Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cut-off have at least one $\sigma(K_{3m})$ under the threshold value.
 The reference asymmetric asteroid is used.
@@
 
-\jtd{The failure of this model makes me think we really should only do the finite element analysis. Though it is slow.}
+\jtd{The failure of this model makes me think we really should only do the finite element analysis, though I think uncertainty will only improve if we average over multiple grids.
+That's based on my messing around so far.}
 

### 2022-05-11 code/density/finite_element.py

@@ -1,0 +1,104 @@
+import numpy as np
+from core import Method
+from scipy.linalg import inv
+
+NUM_DRAWS = 10
+SHIFT_FRACTION = 1
+
+class FiniteElement(Method):
+    def __init__(self, asteroid):
+        print("Finite element model")
+        super().__init__(asteroid, False)
+
+        if self.asteroid.max_l is not None:
+            self.num_grids = (self.asteroid.max_l + 1)**2 + 1
+        self.points, self.grids = self.get_grids_centroid(self.num_grids)
+
+    def get_grids_centroid(self, num_grids):
+        # Shift each point to its cell's centroid and iterate
+        points = self.get_rand_points(num_grids)
+        x,y,z = np.meshgrid(self.asteroid.grid_line, self.asteroid.grid_line, self.asteroid.grid_line)
+        grids = None
+        for i in range(NUM_DRAWS):
+            grids = self.get_grids_voronoi(points)
+            for grid_index, grid in enumerate(grids):
+                centroid = np.array([np.sum(grid * x), np.sum(grid * y), np.sum(grid * z)]) / np.sum(grid)
+                points[grid_index] = points[grid_index] + (centroid - points[grid_index]) * SHIFT_FRACTION
+            print(np.sort(np.sum(grids, axis=(1,2,3))))
+            #print(np.sum(grids, axis=(1,2,3)))
+        grids = self.get_grids_voronoi(points)
+        return points, grids
+
+    def get_grids_weights(self, num_grids):
+        # Weight the points with small volumes stronger and iterate
+        points = self.get_rand_points(num_grids)
+        weights = np.ones(num_grids)
+        grids = None
+        equal_vol = np.sum(self.asteroid.indicator_map) / num_grids
+        for i in range(NUM_DRAWS):
+            grids = self.get_grids_weight(points, weights)
+            vols = np.sum(grids, axis=(1,2,3)) / equal_vol
+            weights = (1 / vols)**0.3
+            print(vols)
+        grids = self.get_grids_weight(points, weights)
+        return points, grids
+
+    def get_rand_points(self, num_grids):
+        points = []
+        while len(points) < num_grids:
+            p = np.random.uniform(low=np.min(self.asteroid.grid_line), high=np.max(self.asteroid.grid_line), size=3)
+            if self.asteroid.indicator(p[0], p[1], p[2]):
+                points.append(p)
[…]

### 2022-05-11 code/density/old/display.py

@@ -1,115 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from setup import *
-from PIL import Image
-from multiprocessing import Pool
-
-plt.style.use("jcap")
-
-VERY_SMALL = 1
-NUM_SLICES = 6
-EXPAND_X=1.15 # Scale along x and y so that spheres look circular
-AXIS_LIMIT = 1000
-
-
-def make_gif(densities, fname, duration):
-    imgs = []
-    mins = np.min(np.where(~np.isnan(densities)), axis=1)
-    maxes = np.max(np.where(~np.isnan(densities)), axis=1)
-    num_frames = maxes[2] - mins[2]
-    for i in range(num_frames):
-        fig = make_frame(densities, i + mins[2])
-        fig.canvas.draw()
-        imgs.append(Image.frombytes('RGB',
-            fig.canvas.get_width_height(),fig.canvas.tostring_rgb()))
-        plt.close()
-    imgs[0].save(fp=fname, format='GIF', append_images=imgs,
-                save_all=True, duration= int(duration * 1000 / num_frames), loop=0)
-
-def make_frame(densities, z_index):
-    # Save imports until here for supercomputer run
-    fig = plt.figure()
-    csection = densities[:,:,z_index] / np.nanmean(densities)
-    c = plt.pcolormesh(pos_array, pos_array, csection.transpose()   , shading='auto',
-        vmin=np.nanmin(densities / np.nanmean(densities)),
-        vmax=np.nanmax(densities / np.nanmean(densities)),
-        cmap='plasma')
-    plt.colorbar(c, label="$\\eta / \overline{\\eta}$")
-    plt.axis('equal')
-    plt.xlabel("$x$ (m)")
-    plt.ylabel("$y$ (m)")
-    mins = np.min(np.where(~np.isnan(densities)), axis=1)
-    maxes = np.max(np.where(~np.isnan(densities)), axis=1)
-    plt.xlim(pos_array[mins[0]], pos_array[maxes[0]])
-    plt.ylim(pos_array[mins[1]], pos_array[maxes[1]])
-    plt.title("$z$ = {} m".format(str(pos_array[z_index])[:5]))
-    fig.tight_layout()
-    return fig
-
-def show_cross_section(densities, fname):
[…]

### 2022-05-11 code/density/old/surface.py

@@ -1,198 +1,0 @@
-import numpy as np
-from scipy.special import lpmv, factorial
-from scipy.optimize import root
-from multiprocessing import Pool
-from setup import *
-#from functools import lru_cache
-
-INTEGRAL_WIDTH = 1000
-NUM_THREADS = 48
-EPSILON = 1e-10
-
-realized_hlms = []
-for l in range(MAX_L+1):
-    for m in range(0, l+1):
-        realized_hlms.append(complex_hlms[get_index(l, m)].real)
-        if m != 0:
-            realized_hlms.append(complex_hlms[get_index(l, m)].imag)
-data = np.append(realized_hlms[1:], A_M**2)
-
-def surface_integrate(theta_func, phi_func):
-    integral_theta = 0
-    integral_phi = 0
-    for theta in np.linspace(0, np.pi, INTEGRAL_WIDTH):
-        integral_theta += theta_func(theta) * np.sin(theta) * np.pi / INTEGRAL_WIDTH
-    for phi in np.linspace(0, 2 * np.pi, 2 * INTEGRAL_WIDTH):
-        integral_phi += phi_func(phi) * np.pi / INTEGRAL_WIDTH
-    return integral_theta * integral_phi
-
-def get_hlm_coeff(args):
-    l, m, quantity_list = args
-    assert(np.sum(quantity_list) == 3 + l)
-    theta_func, phi_func = get_r_coeff(quantity_list)
-    return 1 / (3 + l) * surface_integrate(
-        lambda theta: theta_func(theta) * lpmv(m, l, np.cos(theta)) / factorial(l + m),
-        lambda phi: phi_func(phi) * np.exp(1j * m * phi))
-
-def get_radius_coeff(quantity_list):
-    assert(np.sum(quantity_list) == 5)
-    theta_func, phi_func = get_r_coeff(quantity_list)
-    return 1 / 5 * surface_integrate(theta_func, phi_func )
-
-def ylms_theta(index):
-    l, m = lm_from_index(index)
-    return lambda theta: lpmv(m, l, np.cos(theta))
-
-def ylms_phi(index):
-    l, m = lm_from_index(index)
-    return lambda phi: np.exp(-1j * m * phi)
-
-def get_pascal_coeff(quantity_list):
-    return factorial(np.sum(quantity_list)) / factorial(np.sum(quantity_list) - np.sum(quantity_list!=0) + 1)
-
-#@lru_cache(maxsize=None)
-def make_quantity_lists(level):
[…]

### 2022-05-11 code/density/run.py

@@ -1,11 +1,12 @@
 import sys, os
 from likelihood import Likelihood
+from finite_element import FiniteElement
 from harmonic import Harmonic
 from lumpy import Lumpy, LUMPY_D, LUMPY_N
 from core import Asteroid, Indicator, TrueShape
 import matplotlib.pyplot as plt
 
-DIVISION = 9
+DIVISION = 29
 MAX_RADIUS = 2000
 RELOAD = False
 
@@ -50,6 +51,7 @@ methods = {
     "likelihood": Likelihood,
     "harmonic": Harmonic, 
     "lumpy": Lumpy, 
+    "fe": FiniteElement, 
 }
 
 def make_asteroid(args):

### 2022-05-11 code/generate/tests/view-nutation.py

@@ -1,24 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-dots = []
-
-start = False
-
-f = open("nutation.txt", 'r')
-for line in f.readlines():
-    if line == '' or line[0] == "S" or line[0] == 'M':
-        continue
-    if line == '\n':
-        start = True
-        continue
-    if start:
-        dots.append(float(line))
-
-plt.xlabel("Time step")
-plt.ylabel("$\\L \\cdot \\omega")
-plot_x = np.arange(len(dots))
-plt.plot(plot_x, dots, label="x")
-
-plt.savefig("img-nutation.png")
-plt.show()

### 2022-05-11 code/thresholds/compute-uncs.py

@@ -1,0 +1,156 @@
+# PROBLEM: this data doesn't have K3m.
+
+import sys, os
+import numpy as np
+sys.path.append("../density")
+from likelihood import Likelihood as Model
+#from harmonic import Harmonic as Model
+#from finite_element import FiniteElement as Model
+from core import Asteroid, Indicator
+
+DIVISION = 29
+FILE_PATH = "../../data/"
+
+NAMES = [
+    #"scan-perigee", 
+    #"probe-s-theta", 
+    #"probe-s-rho", 
+    #"scan-cadence",
+    #"scan-period", 
+    #"scan-am", 
+    #"scan-vex", 
+    #"observation-gap"
+    "scan-spin-pole",
+    ]
+
+from contextlib import contextmanager
+import sys, os
+
+@contextmanager
+def suppress_stdout():
+    with open(os.devnull, "w") as devnull:
+        old_stdout = sys.stdout
+        sys.stdout = devnull
+        try:  
+            yield
+        finally:
+            sys.stdout = old_stdout
+
+def scan_directory(directory):
+    if not os.path.exists(directory):
+        raise Exception(f"Directory {directory} does not exist")
+
+    max_index = 0
+    for dname in os.listdir(directory):
+        if os.path.isdir(directory+'/'+dname):
+            max_index = max(max_index, int(dname[-2:]))
+            
+    uncs = np.ones(max_index + 1) * np.nan
+
+    for dname in os.listdir(directory):
+        if not os.path.isdir(directory+'/'+dname):
+            continue
+        for fname in os.listdir(directory+'/'+dname):
+            if not fname.endswith("-0-samples.npy"):
+                continue
+            unc = get_unc_for_file(directory+'/'+dname, directory+'/'+dname+'/'+fname)
+            index = int(dname[-2:])
+            uncs[index] = unc
+    return uncs
+
+
+def get_unc_for_file(dname, fname):
+    with open(fname, 'rb') as f:
+        array = np.load(f)
+        if len(array) == 0: return np.nan
+    
+        # flat_samples = array.reshape(-1, array.shape[-1])
+
+        # median = np.percentile(flat_samples, 50, axis=0)
+        # up_sigma = np.percentile(flat_samples, 50 + 68.27 / 2, axis=0)
+        # down_sigma = np.percentile(flat_samples, 50 - 68.27 / 2, axis=0)
+        # original_sigma = ((up_sigma - median) - (down_sigma - median))/2
+
[…]

### 2022-05-17 paper/appendices.tex
Fit less to test degeneracy
Updated paper

--- 2022-04-29 paper/appendices.tex
@@
 In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-In the left panel of figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
-Both panels show the sudden increase in posterior uncertainty we named $T_\text{cad}$.
-Now $T_\text{cad}$ is visible as a function of frequency and relative orbit speed.
+In this appendix, we discuss the location of this cadence cut-off as a function of the physical parameters of the asteroid.
+
+In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
+Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, now visible as a function of frequency and relative orbit speed.
 In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{figs/cad-period.pdf}\hfill
-  \includegraphics[width=0.49\textwidth]{figs/cad-speed.pdf}
-  \caption{Contour plots showing posterior uncertainties in the first- and second-order fit parameters as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
+  \includegraphics[width=0.48\textwidth]{figs/cad-period.pdf}\hfill
+  \includegraphics[width=0.48\textwidth]{figs/cad-speed.pdf}
+  \caption{Contour plots showing posterior uncertainties as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
 The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
-The red line represents the $\sigma(K_{\ell m})$ threshold.
+The red line represents the uncertainty threshold.
 Cadence cutoff depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
@@
 
-The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was determined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
-The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
-With this unphysical process, we isolate the effect of the amount of time spent near perigee on posterior uncertainty, without inheriting additional affects that would have been caused by the orbit changing shape.
-
-Figure \ref{fig:cad-contour} demonstrates that, near the reference values of $P_\text{omega}$ and $t_\text{spin} / t_\text{orbit}$, $T_\text{cad}$ depends on both time scales $P_\omega$ and $t_\text{spin} / t_\text{orbit}$.
-Specifically, high rotational period and slow orbits are optimal for large $T_\text{cad}$.
+Figure \ref{fig:cad-contour} demonstrates that large rotational period produces high $T_\text{cad}$.
 The dependence on $P_\omega$ agrees with the fact that large rotational periods for fixed cadence lead to better posterior uncertainty, discussed in section \ref{sec:scan-period}.
@@
 In all cases except $\Re K_{33}$, at least constant-$\sigma(K_{\ell m})$ contour is seen to curve back such that $\Delta t$ decreases as a function of $P_\text{omega}$ for large $P_\text{omega}$.
-However, in these regions the cadence cut-off also dulls, as shown by the spreading of the constant-$\sigma(K_{\ell m})$ contours in this region.
+In these regions the cadence cut-off also dulls, as shown by the spreading of the constant-$\sigma(K_{\ell m})$ contours in this region.
 
-The right panel of figure \ref{fig:cad-contour} shows a slightly stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
-It appears that slightly slower orbits sharply increases $T_\text{cad}$.
-Similar in the $P_\omega$ case, for increasingly fast orbits, $T_\text{cad}$ depends less on $t_\text{spin}/ t_\text{orbit}$.
-\jtd{I wanted to talk to Julien about the interpretation of this panel. Because $t_\text{spin} / t_\text{orbit}$, I find it hard to interpret. Maybe a different type of scan is better.}
+ The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was defined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
+The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
+$t_\text{spin} / t_\text{orbit} > 1$ corresponds to a faster orbit, and $t_\text{spin} / t_\text{orbit} < 1$ corresponds to a slower orbit.
+With this unphysical process, we isolate the effect of the amount of time spent near perigee on posterior uncertainty, without inheriting additional affects that would have been caused by the orbit changing shape.
 
-Figure \ref{fig:cad-contour} demonstrates that, for large period, the cadence cut-off $T_\text{cad}$ reduces in prominence and rises to above one hour, meaning that large gaps of time between observations can still lead to well-constrained parameters in these cases.
-Faster orbits also lead to $T_\text{cad} > 1$ hr for for as small a decrease as $t_\text{spin} / t_\text{orbit}  \approx 75$\%.
+The right panel of figure \ref{fig:cad-contour} shows a stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
+It appears that even slightly slower orbits sharply increases $T_\text{cad}$.
+This effect is both due to the asteroid spending greater time in the high-torque, near-perigee region, and the larger data set that can be collected for slow orbits.
+However, if the orbit speed is changed by adjusting its parameters ($v_\infty$, $r_p$) or the central body mass $\mu_\mathcal{B}$, then the orbit shape will also change.
+This induces other effects studied in the main text and will complicate the trend observed here.
+Unlike the $P_\omega$ case, the cadence cut-off does not visibly broaden as a function of $t_\text{spin} / t_\text{orbit}$.
+It appears that the increased orbit speed merely shifts $T_\text{cad}$ rather than changing its sharpness.
 

### 2022-05-17 paper/main.tex
Updated paper

--- 2022-05-06 paper/main.tex
@@
 
-It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
-There are many possible definitions of posterior uncertainty, but we explore one in this paper which is outlined in appendix \ref{app:sigma-threshold}.
-This leads to cut-offs of the encounter properties which lead to posterior uncertainty less than the threshold.
-These critical values are shown in table \ref{tab:threshold-summary} as a summary, and are discussed in detail in the following sections.
+\jtd{It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
+We define this posterior uncertainty threshold as the point at which the median of the ratio between the the local density uncertainty and local density  ($\rho_\sigma / \rho$) is equal to a fraction $f$.
+For this analysis, we investigate both $f=100\%$ (corresponding to an essentially unconstrained density distribution) and $f=20\%$.}
+
+\jtd{We use this threshold because it has clear physical meaning, unlike the density moments.
+But the value of $\rho_\sigma / \rho$ depends on the model used.
+In this analysis, we use the likelihood model, but choosing a different model with constraints added would reduce density uncertainty, and lead to less restrictive thresholds.}
 
@@
   \begin{tabular}{lll} \hline
-    Encounter property & Strong & Weak \\ \hline
-    Excess velocity ($v_\infty$) & & \\
-    Perigee ($r_p$) & & \\
-    Spin pole uncertainty ($\sigma_\theta$) & & \\
-    Spin period uncertainty ($P_\omega \sigma_\rho$) & & \\
-    Asteroid length ($a_\mathcal{A}$) & & \\
-    Cadence ($\Delta t$) & & \\
-    Data gap ($T_\text{gap}$) & & \\
-    Rotational period ($P_\omega$) & & \\ \hline
+    Encounter property & $\sigma_\rho / \rho = 100\%$ & $20\%$ \\ \hline
+    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
+    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
+    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
+    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
+    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
+    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\
+    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
   \end{tabular}
-  \caption{For each encounter property discussed in section \ref{sec:discussion}, the cut-offs (i.e., the values which leads to $\sigma(K_{3 m})$ at the threshold value) are given.
-Properties inside the strong cut-off have all $\sigma(K_{3m})$ under the threshold value, while properties inside the weak cutoff have at least one $\sigma(K_{3m})$ under the threshold value.
+  \caption{For each encounter property discussed in section \ref{sec:discussion}, the properties that lead to density uncertainty equal to 100\% (20\%) of the local density are shown in the middle (right) columns.
 The reference asymmetric asteroid is used.
-\jtd{summary}}
+The 20\% threshold is very restrictive, but the 100\% threshold is more achievable and demonstrates the thresholds in the right column are not hard cut-offs.}
   \label{tab:threshold-summary}

### 2022-05-17 paper/appendices.tex
Corrected threshold line in cadence n cadence appendix

@@
 In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
-Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, now visible as a function of frequency and relative orbit speed.
+Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
 In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
@@
 The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
-The red line represents the uncertainty threshold.
-Cadence cutoff depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
+The solid (dotted) red line represents the $\sigma_\rho / \rho = 100\%$ (20\%) threshold.
+Cadence cut-off depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
   \label{fig:cad-contour}

### 2022-05-17 paper/main.tex
Corrected threshold line in cadence n cadence appendix

@@
 
-\jtd{It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
+It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
 We define this posterior uncertainty threshold as the point at which the median of the ratio between the the local density uncertainty and local density  ($\rho_\sigma / \rho$) is equal to a fraction $f$.
-For this analysis, we investigate both $f=100\%$ (corresponding to an essentially unconstrained density distribution) and $f=20\%$.}
-
-\jtd{We use this threshold because it has clear physical meaning, unlike the density moments.
-But the value of $\rho_\sigma / \rho$ depends on the model used.
-In this analysis, we use the likelihood model, but choosing a different model with constraints added would reduce density uncertainty, and lead to less restrictive thresholds.}
+For this analysis, we investigate both $f=100\%$ (corresponding to an essentially unconstrained density distribution) and $f=20\%$.
+
+We use this threshold because it has clear physical meaning, unlike the density moments.
+But the value of $\rho_\sigma / \rho$ depends on the model used, unlike $\sigma(K_{\ell m})$.
+In this analysis, we use the likelihood model, but choosing a different model with constraints added would reduce density uncertainty, and lead to less restrictive thresholds.
 
@@
 There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) This explains why the oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma(K_{3m}) > 0.01$, shown by the red vertical line.
+(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
+The dependence of posterior uncertainty on $v_\infty$ is weak enough so that $\sigma_\rho/\rho$ never reaches 100\% for the $v_\infty$ investigated.
 
 The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the 0.01 threshold.
-At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
-Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
-The exact location of these limits will change if different encounter properties are used.
+For $r_p =7.9$ Earth radii, $\sigma_\rho/\rho$ reaches the 100\% threshold.
+The 20\% threshold is reached at lower 4.7 Earth radii.
+Much of this uncertainty is dominated by uncertainty in $K_{30}$, which is the parameter least constrained by tidal torque analysis.
+At $r_p \approx 10$ Earth radii, $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
 
@@
 
-The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters (5-20 Earth radii).
+The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters.
 Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
@@
 For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
-The $K_{30}$ parameter reaches the $\sigma(K_{30})\approx 0.01$ threshold at $\sigma_\theta = 0.032\ \text{radians} \approx 2^\circ$, whereas the other parameters reach the threshold between $8^\circ$ and $45^\circ$.
+The uncertainty threshold is reached at $\sigma_\theta = 2.8^\circ$ (0.5$^\circ$) for $\sigma_\rho / \rho=$100\% (20\%).
 The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
 
-If $\sigma_\rho$ is allowed to vary, then $K_{30}$ reaches the threshold at $\sigma_\rho \approx \num{2.8e-7}$, and the other parameters reach the threshold at $\sigma_\rho \approx 1.2-\num{8.6e-6}$.
-These correspond to uncertainty in period of roughly milliseconds to seconds.
+If $\sigma_\rho$ is allowed to vary instead, then $K_{30}$ reaches the 100\% and 20\% thresholds at $\sigma_\rho$ which correspond to period uncertainty of several milliseconds.
 At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
@@
 We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$.
-\jtd{The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
-The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.}
+The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
+The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.
 
@@
 
-\jtd{The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
+The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
 If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated.
-This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.}
+This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.
 
@@
 The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
-At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
-The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
-This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 0.1$.
-This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma(K_{\ell m})$.
-It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
+At $a_\mathcal{A} \leq 1100$ m, $\sigma_\rho/\rho \approx 100\%$.
+However, the 20\% cut-off is much lower, at $a_\mathcal{A} \leq 180$.
+Figure \ref{fig:scan-am} demonstrates why these cut-offs are so distant; for large $a_\mathcal{A}$, uncertainty decreases slowly with length.
+Only for small lengths is the uncertainty very large.
+This behaviour indicates that the uncertainty threshold is unlikely to fall much below 180 m even if other properties of the encounter are adjusted.
 
@@
 The orange star indicates the reference spin pole.
-The red contours enclose regions where $\sigma(K_{3m}) \geq 0.01$.
+The red contours enclose regions the 20\% (dotted) and 100\% (solid) $\sigma_\rho / \rho$ cut-off.
 Posterior uncertainty depends similarly on initial spin pole direction for all parameters}
@@
 Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the south pole, or $-\unit Z$.
+The polar projection is centred at the north pole, or $\unit Z$.
 Posterior uncertainty is large near $\pm \unit Z$ and $\pm \unit Y$, but roughly constant elsewhere.}
@@
 
-The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
+The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega < 4.3$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
 The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
@@
 
-We assessed the posterior uncertainty generated by the fit process by adjusting various properties of an asteroid on an Earth encounter. The main conclusions are listed below.
-
-\begin{enumerate}
-  \item Highly precise rotational period data is required to produce precise second-order moments.
-  \item Large $a_\mathcal{A}$ is required for $K_{3m}$ resolution, though the size of $a_\mathcal{A}$ has no effect on $K_{2m}$.
-The threshold on $a_\mathcal{A}$ for the reference asteroid was $\sim$700 m for $K_{30}$ and $\sim$50 m for $K_{33}$.
-  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters.
-  \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
-  \item If the asteroid rotational period is too small, or if the initial angular velocity points in an inconvenient direction, the density moments will be poorly constrained.
-  \item The cadence of observation should generally be shorter than about 30 minutes for the reference asteroid case. Gaps of data can appear, even at perigee, but not for more than about an hour.
-\end{enumerate}
-
-If some of these conditions are not met, the first-order $K_{2m}$ moments may still be resolvable.
+We assessed the posterior uncertainty generated by the fit process by adjusting various properties of an asteroid on an Earth encounter.
+The precise thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit are the most difficult requirements to meet, with perigee $\lesssim 6$ Earth radii, spin pole uncertainty $\lesssim 1^\circ$, and period uncertainty $\lesssim 10$ ms.
+However, these thresholds depend on the model used to extract a density distribution, and useful information may be able to be extracted when they are not achieved by using a different model.
 

### 2022-05-23 paper/main.tex
Finite element model finished

@@
 and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
+Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
 However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
@@
 
-We address this community need by developing a methodology to translate (1) time series of angular velocity data into constraints on density moments and (2) constraints on density moments into constraints on an asteroid's density distribution.
+We address this community need by developing a methodology to translate (1) time series of asteroid angular velocity data into constraints on density moments and (2) constraints on density moments into constraints on an asteroid's density distribution.
+Other techniques, such as measurement of tidal distortion \cite{RICHARDSON199847}, impact or seismometry experiments \cite{RICHARDSON2005325}, or gradiometry \cite{carroll2018tidal}, may additionally constrain the density distribution.
 In section \ref{sec:methods}, we introduce the analytical and numerical fundamentals of this methodology.

### 2022-05-23 code/density/core.py

@@ -22,6 +22,7 @@ class Method:
         self.asteroid = asteroid
         self.unc = None
         self.d = None
+        self.is_linear = True
         self.densities = None
         self.density_uncs = None
         self.finite_element = finite_element
@@ -41,6 +42,12 @@ class Method:
         # Return number for finite_element, vector otherwise
         raise NotImplementedError
 
+    def get_nonlinear_d(self):
+        raise NotImplementedError
+
+    def get_nonlinear_unc(self):
+        raise NotImplementedError
+
     def get_c(self):
         # Default value.
         return np.zeros_like(self.asteroid.data)
@@ -50,14 +57,24 @@ class Method:
 
     def solve(self):
         if self.unc is None:
-            a = self.get_a()
-            self.d = a @ (self.asteroid.data - self.get_c())
+            if self.is_linear:
+                a = self.get_a()
+                self.d = a @ (self.asteroid.data - self.get_c())
 
-            if self.asteroid.sigma_data is not None:
-                if self.finite_element:
-                    self.unc = np.einsum('ij,jk,ki->i', a, self.asteroid.sigma_data, a.transpose().conjugate())# Diagonal entries
-                else:
-                    self.unc = a @ self.asteroid.sigma_data @ a.transpose().conjugate()
+                if self.asteroid.sigma_data is not None:
+                    if self.finite_element:
+                        self.unc = np.einsum('ij,jk,ki->i', a, self.asteroid.sigma_data, a.transpose().conjugate())# Diagonal entries
+                    else:
+                        self.unc = a @ self.asteroid.sigma_data @ a.transpose().conjugate()
+            else:
+                self.get_nonlinear_d()
+
+                if self.asteroid.sigma_data is not None:
+                    if self.finite_element:
+                        self.unc = self.get_nonlinear_unc()
+                    else:
+                        raise NotImplementedError
+
 
     def get_density(self, x,y,z):
         if self.finite_element:
@@ -120,9 +137,11 @@ class Method:
         densities = self.map_density()
         for l in range(0, self.asteroid.max_l + 1):
             for m in range(-l, l+1):
-                calc_rlms[index] = np.sum(rlms_field[index] * densities) / self.asteroid.am ** l * self.asteroid.division**3
+                calc_rlms[index] = np.sum(rlms_field[index] * densities) / self.asteroid.surface_am ** (l - 2) * self.asteroid.division**3
                 index += 1
[…]

### 2022-05-23 code/density/finite-element/main.py

@@ -1,31 +1,33 @@
-import emcee, corner, sys, lmfit, random, os, time
+import emcee, corner, sys, lmfit, random, os, warnings
 import numpy as np
 from scipy.linalg import pinvh, inv
 from matplotlib import pyplot as plt
 from multiprocessing import Pool, Lock
 from grids import get_grids_centroid
 sys.path.append("..")
-from core import Asteroid, Indicator
+from core import Asteroid, Indicator, TrueShape
 from scipy.optimize import minimize
 from threading import Thread
-from numdifftools import Hessian
+from display import make_gif, make_slices
 
 N_WALKERS = 32
 MAX_L = 3
 N_ALL_DIM = (MAX_L + 1)**2
 N_FREE_DIM = N_ALL_DIM - 7
 MAX_N_STEPS = 100_000
-DIVISION = 49
+DIVISION = 29
 RLM_EPSILON = 1e-20
 MAX_RADIUS = 2000
 SMALL_SIGMA = 1e-5
 CERTAIN_INDICES = [0, 1, 2, 3, 5, 7, -1]
 MAX_DENSITY = 10
 MIN_DENSITY = 0
-UNCERTAINTY_RATIO = 0.005
-AM = 1000
-VERY_LARGE_SLOPE = 1e30
+UNCERTAINTY_RATIO = 0.25
+VERY_LARGE_SLOPE = 1e30 # Can be infinite for mcmc
 NUM_THREADS = os.cpu_count()
+MIN_LOG_LIKE = 1000# 100
+
+np.random.seed(23678)
 
 def get_cov(path):
     with open(path, 'rb') as f:
@@ -34,72 +36,72 @@ def get_cov(path):
     data = np.mean(flat_samples, axis=0)
     return data, cov
 
-def get_theta_long(theta_short):
+def get_theta_long(theta_short, info):
     # Get the densities consistent with making the mass 1 and com 0 and rotation
-    return np.append(theta_short, rlm_fixed_inv[:,-1] - rlm_prod @ theta_short)
+    return np.append(theta_short, info.rlm_fixed_inv[:,-1] - info.rlm_prod @ theta_short)
 
-def get_klms(theta_long):
-    unscaled_klms = rlm_mat @ theta_long
-    radius_sqr = radius_vec @ theta_long
+def get_klms(theta_long, info):
+    unscaled_klms = info.rlm_mat @ theta_long
+    radius_sqr = info.radius_vec @ theta_long
+    #radius_sqr = 1000**2
[…]

### 2022-06-15 paper/main.tex
Worked on Julien's comments
Updated paper with new moments

@@
 However, most asteroid observational techniques are not sensitive to interior properties.
-We investigate here the interior constraints accessible through monitoring variations in angular velocity during a close encounter.
+We investigate the interior constraints accessible through monitoring variations in angular velocity during a close encounter.
 We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
 Using Markov Chain Monte Carlo fits, we perform injection-retrieval tests on these synthetic data to gain insights into the extent to which interior properties can be constrained.
-We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., moment of inertia and initial spin pole direction), observational set up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
+We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., moment of inertia and initial spin pole direction), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
 We find that high precision in rotational period estimates (order of milliseconds to seconds) are necessary for each cadence, and that large asteroids ($> 100$ m radius) with low perigees ($<20$ Earth radii) are necessary to resolve second-order density moments.
@@
 
-Only some aspects of an asteroid's density distribution affect tidal torque interactions. These are the asteroid ``length'' 
+The only properties of an asteroid's density moments that affect tidal torque interactions are its ``density moments,'' defined here as
 \begin{equation}
-  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2
+  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\text{bulk}^2 a_\text{surf}^{\ell - 2}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
+  \label{eqn:klm}
+\end{equation}
+These are complex, unitless quantities.
+$\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
+The integral is computed over the entire asteroid mass, denoted $\mathcal{A}$.
+The two length scales $a_\text{surf}$ and $a_\text{bulk}$ are defined as
+\begin{equation}
+  a_\text{bulk}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2 \qquad
+  a_\text{surf}^2 = \frac{1}{V_\mathcal{A}} \int_\mathcal{A} d^3 r r^2
   \label{eqn:am}
 \end{equation}
-and (complex) ``density moments''
-\begin{equation}
-  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r),
-  \label{eqn:klm}
-\end{equation}
-both of which are constant and only need to be computed once to generate data assuming no asteroid deformation.
-Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
-They produce a tidal torque of
+where $V_\mathcal{A}$ is the asteroid volume.
+We highlight two crucial details of these length scales: (1) that they are equal when $\rho_\mathcal{A}$ is uniform across the asteroid, and (2) that $a_\text{surf}$ is a function only of the boundary of $\mathcal{A}$ whereas $a_\text{bulk}$ is a function of the internal density distribution.
+
+The tidal torque experienced by an asteroid is 
 \begin{equation}
   \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[a_\text{bulk}^2 \sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\text{surf}^{\ell' - 2}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
   \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
@@
 \end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$, $a_\mathcal{A}$, and $J_{\ell m}$ are the mass, length, and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body, with the $a_\text{bulk}$ and $a_\text{surf}$ of equation \ref{eqn:klm} replaced by $a_\mathcal{B}$.
 Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
+
+Since it is the angular acceleration of the asteroid that is observable, rather than the torque applied, we also compute the moment of inertia of the asteroid around the principal axes: 
+\begin{equation}
+  \begin{split}
+    I_x &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{K_{20} - 6 K_{22} + 1}\\
+    I_y &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{K_{20} + 6 K_{22} + 1}\\
+    I_z &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{-2K_{20} + 1}.
+  \end{split}
+  \label{eqn:moi}
+\end{equation}
+
+The angular acceleration of the asteroid is proportional to $\bm \tau / I$ (equation \ref{eqn:omega-eom}), such that the $a_\text{bulk}^2$ factor of equation \ref{eqn:tidal-torque} is canceled out.
+Thus, the observables do not depend explicitly on $a_\text{bulk}$.
+
 Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also defined in appendix \ref{app:eom}.
-
-In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion.
-In section \ref{sec:uncertainty}, we define the uncertainty model used to add realistic noise to the data, and we describe how posterior probability distributions (PPDs) for density moments were extracted from spin-pole data in section \ref{sec:fit}.
-Finally, we describe models to translate constraints on the density moments into constraints on the density distribution in section \ref{sec:density-distro}.
 
@@
 
-We built a publicly accessible, custom simulation in C++ to produce time series of angular velocity data during a close encounter with a more massive astronomical object.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$ (see equation \ref{eqn:am}); and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+We built a publicly accessible, custom simulation in C++ to produce time series of angular velocity data during a close encounter with a central body.
+This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\text{surf}$ and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
-One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
-The choice of $a_\mathcal{A}$ can be adjusted after the fit to assess the dependence of the density distributions on $a_\mathcal{A}$
-
-We further assume that the asteroid is initially not tumbling.
-Thus, the angular velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia).
+For example, $\bm \Omega_0$ could be extracted from pre-encounter light-curve data and $a_\text{surf}$ from a model for the asteroid's surface using radar.
+
+We assume for simplicity that the asteroid is initially not tumbling, though this assumption can be relaxed.
+We assume a short-axis rotation mode such that energy of the asteroid's rotation is minimized.
 This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Thus, only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
+Only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
 
@@
 The asteroid density distribution $\rho_\mathcal{A}(\bm r)$ is not uniquely constrained via tidal torque interactions because only the density moments $K_{\ell m}$ contribute to equation \ref{eqn:tidal-torque}.
-However, by making sufficient assumptions about the density distribution, we can nevertheless estimate $\rho(\bm r)$ from $K_{\ell m}$.
-We outline three different assumptions which constitute three models for extracting density distributions from density moments.
-Our goal in investigating different families of models to translate constraints on the density moments into constraints on the density distribution is to reveal the major features in the density distribution that are consistently present, independent of the family of mapping model used, despite the problem underdetermination (in a similar fashion to \cite{de2012towards}).
-
-All are (partially) linear to facilitate computational ease and uncertainty propagation.
-All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
-Uncertainty on this shape estimate is assumed to be negligible compared to the density moment uncertainty and their contributions to to the density distribution.
-The models then produce a density distribution $\rho_\mathcal{A}(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho_\mathcal{A}$.
-If the asteroid shape is not known, a fourth model defined in appendix \ref{app:find-surface} can be used to extract it assuming uniform density.
-In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
-When extracting density distributions, multiple $a_\mathcal{A}$ values may be tested and the multiple produced density distributions can be compared to highlight common features.
-
-Since the overall mass of the asteroid is not observable from tidal torque, we do not expect to measure $\rho$ in an absolute sense. Only the differences in $\rho$ across the body are measurable.
-
-To set the shape of the asteroid, we assume that an indicator function $\mathds{1}(\bm r)$ has been determined such that $\mathds{1}(\bm r) = 1$ inside the asteroid and 0 outside, where $\mathds{1}(\bm r)$ is defined in some frame whose orientation with respect to Earth is known.
-Since the asteroid rotates around its centre of mass during observations, we assume that the location of the centre of mass is also known in this frame, so that we can set it to be the origin.
-
-We define a new coordinate system, the ``hybrid frame,'' which coincides exactly with body-fixed frame at the initial orientation of the asteroid assuming that the fit result for $\gamma_0$ is perfectly accurate.
-The orientation of the hybrid frame with respect to the inertial frame is therefore exactly known, so that $\mathds{1}$ is also exact in the hybrid frame and the body-fixed frame aligns with the hybrid frame up to uncertainty in $\gamma_0$.
-We will solve for $\rho(\bm r)$ in the hybrid frame given fit results $K_{\ell m}$ (known in the body-fixed frame) and the fixed $a_\mathcal{A}$ (the same in both frames).
-
-We fix $a_\mathcal{A}$ at the value assumed during the fit and set $\mu_\mathcal{A}$ equal to an arbitrary constant since the system is independent of the total asteroid mass.
-Thus, $K_{\ell m}$ and $a_\mathcal{A}^2$ are linear in $\rho(\bm r)$ by equations \ref{eqn:am} and \ref{eqn:klm}.
-Equation \ref{eqn:am} and the $K_{00}=1$ component of equation \ref{eqn:klm} can each be applied as constraints to enforce these choices of $a_\mathcal{A}^2$ and $\mu_\mathcal{A}$.
-
-Suppose that we restrict the number of degrees of freedom of $\rho(\bm r)$ from infinity to $m$ by explicitly defining some function $\rho(\bm r, \bm \Theta)$ for an $m$-dimensional vector $\bm \Theta$ which contains the free parameters of $\rho$.
-We will leave the explicit definition of $\rho(\bm r, \bm \Theta)$ to the model descriptions below, but for now we assume that $\rho$ is linear in $\bm \Theta$; i.e.,
+For example, since the mass of the asteroid is unconstrained, $\rho_\mathcal{A}(\bm r)$ cannot be determined on an absolute scale.
+However, by making sufficient assumptions about the density distribution, we can nevertheless extract fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
+
+We assume that the asteroid's surface is known in the inertial frame from radar data.
+Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is extracted.
+However, the density moments which are extracted from flyby data are known in the body-fixed frame.
+
+We rotate the known surface of the asteroid to a new frame called the ``hybrid frame'' by translating such that the known center of mass is at the origin, then rotating such that $\Omega_0$ points in the $+\unit z_\text{hybrid}$ direction and $\unit Y$ points in the $\unit Y_\text{hybrid}$ direction.
+Since $\Omega_0$ is exact, the surface in this hybrid frame is known exactly.
+The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}$ of $\gamma_0$.
+Such rotations affect density moments via
 \begin{equation}
-  \rho(\bm r, \bm \Theta) = \bm B(\bm r)^\dagger \bm \Theta
-  \label{eqn:density-distro}
-\end{equation}
-for a $m$-dimensional vector $\bm B(\bm r)$ with adjoint $\bm B(\bm r)^\dagger$.
-($\bm B$ need not be linear in $\bm r$.) Thus, $a_\mathcal{A}^2$ and $K_{\ell m}$ are linear in $\bm \Theta$.
-We further assume that the model describes a way to reverse the relationship between $K_{\ell m}$ or $a_\mathcal{A}^2$ and $\bm \Theta$ so that
-\begin{equation}
-  \bm \Theta = A \bm K
-  \label{eqn:density-model}
-\end{equation}
-where $A$ is a matrix.
-Here, we have arranged $a_\mathcal{A}^2$ and $K_{\ell m}$ into a vector $K$ which we say has $n$ dimensions.
-The order of this arrangement is irrelevant as long as it is kept consistent.
-
-To propagate uncertainties from $\bm K$ to $\bm \Theta$ to $\rho(\bm r)$, we need the covariance matrix $\Sigma_K$ for $\bm K$.
-Suppose that the hybrid frame is offset from the body-fixed frame by some small angle $\Delta \gamma$, which results from uncertainty in $\gamma_0$.
-Then
-\begin{equation}
-  K_{\ell m}^\mathrm{hybrid} = e^{-im\Delta \gamma}K_{\ell m}^\mathrm{body-fixed}.
+  K_{\ell m}^\mathrm{hybrid} = e^{-im\gamma_0}K_{\ell m}^\mathrm{body-fixed}.
   \label{eqn:body-fixed-to-hybrid}
@@
 by equation \ref{eqn:ylm-rotation}.
-Since $K_{\ell m}^\mathrm{body-fixed}$ was obtained by an MCMC fit, a large set of PPD-distributed samples is available for $\Delta \gamma$ and $K_{\ell m}^\mathrm{body-fixed}$, and the covariance matrix $\Sigma_K$ can be computed statistically in the hybrid frame by applying equation \ref{eqn:body-fixed-to-hybrid} to the samples.
-Then, propagation of uncertainty guarantees that the covariance matrix of $\bm \Theta$ is $\Sigma_\Theta = A \Sigma_K A^\dagger$ and the density distribution and uncertainty on density distribution are equal to
-\begin{equation}
-  \rho(\bm r) = \bm B(\bm r)^\dagger A\bm K \qquad \sigma^2_\rho(\bm r) = \bm B(\bm r)^\dagger A \Sigma_K A^\dagger \bm B(\bm r).
-  \label{eqn:unc-rho}
-\end{equation}
-
-The role of a model is therefore to restrict the space of valid density distributions by defining the $m\times n$-dimensional matrix $A$ and the $m$-dimensional vector $\bm B(\bm r)$ such that equations \ref{eqn:density-distro} and \ref{eqn:density-model} are true.
-Then the density distribution and its uncertainty are given by equation \ref{eqn:unc-rho}.
-Three examples of possible models are given below.
-
-\subsubsection{The ``likelihood'' model}
-\label{sec:likelihood}
-
-A natural way to restrict the degrees of freedom of $\rho(\bm r)$ is by defining a likelihood function $\mathcal{L}$ on the density distribution and choosing the one distribution which maximizes $\mathcal{L}$ and exactly reproduces $\bm K$.
-We call this the ``likelihood'' model.
-This likelihood should not be confused with the likelihood of equation \ref{eqn:log-likelihood}, which was a function of the spin data, not the density distribution.
-The choice of $\mathcal{L}$ is arbitrary, but a Gaussian likelihood will produce a linear model.
-
-To employ this likelihood method, we divide the asteroid into a square grid of $m \gg n$ elements, each of which is assumed to have uniform density $\rho_0+\Theta_i$, where $\rho_0$ is constant across the asteroid and $\Theta_i$ is a local deviation.
-In our work, we use $m \sim 10^{6}$.
-This defines the model function $\bm B(\bm r)$, which is zeroed in all components except for the $i$th, where $i$ is the index of the grid element that contains $\bm r$.
-
-We use a likelihood of 
-\begin{equation}
-  \mathcal{L}(\bm \Theta) = \prod_{i=1}^m \frac{1}{\sqrt{2\pi \sigma^2}} \exp\parens{-\frac{\Theta_i^2}{2 \sigma^2}}
-\end{equation}
-with free parameters $\mu$ and $\sigma$.
-These parameters do not affect the location of the maximum, so we do not define them.
-Given this likelihood, the log likelihood is proportional to $-|\bm \Theta|^2$.
-Minimizing the norm of $\bm \Theta$ is therefore equivalent to finding the maximum likelihood.
-
-Putting aside the problem of minimizing the norm, we use the linearity of equations \ref{eqn:am} and \ref{eqn:klm} to write $\bm K = M \bm \Theta$, where the $i$th entry of every row of the $n\times m$ matrix $M$ is the integral presented in equation \ref{eqn:am} or \ref{eqn:klm}, evaluated over the $i$th finite element.
-We want to solve $\bm K = M \bm \Theta$ for $\bm \Theta$ to match equation \ref{eqn:density-model}, which we do via the Moore-Penrose inverse.
-Since $m>n$, the Moore-Penrose inverse of $M$ is
-\begin{equation}
-  A=M^+ = M^\dagger(MM^\dagger)^{-1}.
-  \label{eqn:mpi-underdetermined}
-\end{equation}
-The vector $\bm \Theta=M^+\bm K$ is guaranteed to solve $\bm K = M \bm \Theta$, and by the properties of the Moore-Penrose inverse, this $\bm \Theta$ also happens to minimize the norm of all possible $\bm \Theta$ that satisfy the equation.
-Thus, defining $A=M^+$ also minimizes $\mathcal{L}$ and fully defines the model.
-
-This model is fast to compute; assuming fast matrix multiplication, the matrix inversion of equation \ref{eqn:mpi-underdetermined} is fast because $MM^\dagger$ is an $n$-dimensional square matrix, which is very small compared to the large number of finite elements $m$.
-
-\subsubsection{The ``harmonic'' model}
-\label{sec:harmonic}
-
-We now explore a model that seeks to restrict the space of allowed density distributions in a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
-We  call this  the ``harmonic'' model.
-Any harmonic function can be expanded as
-\begin{equation}
-  \rho(\bm r) = \sum_{\ell m} \Theta_{\ell m}\frac{R_{\ell m}^*(\bm r)}{a_\mathcal{A}^\ell} 
-  \label{eqn:harmonic-rho}
-\end{equation}
-where the terms which lead to $\rho \rightarrow \infty$ at the origin have been removed and $\Theta_{\ell m}$ are free (complex) parameters.
-Since $\rho$ is real, we have $\Theta_{\ell m}=(-1)^m \Theta_{\ell,-m}^*$.
-By setting a maximum on $\ell$, we restrict the number of degrees of freedom to $(\ell_\mathrm{max}+ 1)^2$.
-Choosing the same maximum $\ell$ as the maximum $\ell$ for the $K_{\ell m}$ moments, we have $m=n-1$ coefficients $\Theta_{\ell m}$ which can be stacked into an $m$-dimensional vector $\bm \Theta$.
-
-Inserting equation \ref{eqn:harmonic-rho} into equations \ref{eqn:am} and \ref{eqn:klm},
-\begin{equation}
-  K_{\ell' m'} = \sum_{\ell m} \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^{\ell'} a_\mathcal{A}^\ell} \Theta_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}^*(\bm r) R_{\ell' m'}(\bm r).
-  \label{eqn:harmonic-mat}
-\end{equation}
-This is an over-determined matrix equation $\bm K = M \bm \Theta$, where $M$ is an $n \times m$ matrix.
-The Moore-Penrose inverse can therefore be used again to find an inverse $A=M^+$ which yields approximately correct $\bm \Theta$ (approximate in that the norm of the error vector between $\bm K$ and $M \bm \Theta$ is minimized).
-However, the form of the inverse changes due to the equation being overdetermined:
-\begin{equation}
-  A=M^+ = (M^\dagger M)^{-1} M^\dagger .
-  \label{eqn:mpi-overdetermined}
-\end{equation}
-
-In the special case where the asteroid is a sphere of radius $R$, the matrix defined by equation \ref{eqn:harmonic-mat} is diagonal. %, with entries 
-% \begin{equation}
-%   M_{\ell m; \ell' m'} = \frac{4\pi R^3}{\mu_\mathcal{A}} \frac{R^{2\ell}}{a_\mathcal{A}^{2\ell}} \frac{\delta_{\ell \ell'} \delta_{m m'}}{(4\ell^2 + 8\ell + 3)(\ell - m)!(\ell+m)!}.
-%\end{equation}
-A non-spherical perturbation will introduce small, off-diagonal entries of $M$.
-This suggests another interpretation of the physical meaning of $K_{\ell m}$; they are directly proportional through this form of $M$ and the matrix equation $\bm K = M \bm \Theta$ to the coefficients of the spherical harmonic expansion of the asteroid density in the case of a spherical asteroid.
-
-\subsubsection{The ``lumpy'' model}
-\label{sec:lumpy}
-
-The above two simple models produce smooth density distributions.
-In this section, we define a model which identifies discrete regions differing from the overall density.
-We call this model the ``lumpy'' model.
-
-Suppose the asteroid contains $N$ ``lumps'' of uniform mass $\mu_i$ displaced by distance $\bm x_i$ from the asteroid centre of mass and superimposed on a constant-density overall asteroid ``medium'' with known shape given by $\mathds{1}(\bm r)$.
-For simplicity, we assume that all $N$ regions are ellipsoids with $d$ independent axis lengths.
-For example, $d=3$ corresponds to an asymmetric ellipsoid, $d=2$ corresponds to a symmetric ellipsoid, and $d=1$ corresponds to a sphere.
-The model therefore has $3N$ positional degrees of freedom, along with $N$ degrees of freedom for $\mu_i$, $Nd$ shape degrees of freedom, and 0, $2N$, or $3N$ rotational degrees of freedom for $d=1$, 2, or 3 respectively.
-The medium adds one additional degree of freedom for its mass, but its position is determined by knowledge of the surface $\mathds{1}(\bm r)$.
-The total number of degrees of freedom are displayed in table \ref{tab:lump-dof}.
-They should be compared to the number of known asteroid parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, which is $(\ell_\text{max}+1)^2+1$: 17 when the second-order density moments are known and 10 when only $K_{2m}$ are known.
-We assume that the degrees of freedom of this lumpy model are fewer than the number of $\bm K$, so that the model is overdetermined.
-
-%Recall that $\mathds{1}(\bm r)$ is known in the hybrid frame where the origin is the centre of mass of the asteroid.
-The displacement of the shape's centroid from the centre of mass, called $\bm x_0$, is therefore observable from light curve analysis and therefore constrains $\bm x_i$ so that the asteroid centre of mass lies on the origin.
-
-\begin{table}
-  \centering
-  \begin{tabular}{cc|ccc}
-    \hline \hline
-        &  & & $N$ &  \\
-        &  & 1  & 2  & 3  \\ \hline 
-        & 1& \cellcolor{black}\color{white} 6 & \cellcolor{gray}\color{white} 11 & \cellcolor{gray}\color{white} 16\\
-    $d$ & 2& \cellcolor{black}\color{white} 9 & \cellcolor{gray}\color{white} 17 & 25 \\
-        & 3& \cellcolor{gray}\color{white}  11 &  21 &  31 \\
-    \hline \hline
-  \end{tabular}
-  \caption{Total degrees of freedom $D$ as a function of $N$, the number of lumps modelled, and $d$, the number of independent axis lengths considered for each lump.
-The configurations with $D \leq$ the 10 known parameters not including $K_{3m}$ are coloured black, and with $D \leq$ the 17 parameters including $K_{3m}$ parameters are coloured gray.}
-  \label{tab:lump-dof}
-\end{table}
-
-The net $K_{\ell m}$ components of such an ensemble are
-\begin{equation}
-  K_{\ell m} = K_{\ell m}'^0 + \sum_{i=1}^N K_{\ell m}'^i \qquad a_\mathcal{A}^2 = a_0'^2 + \sum_{i=1}^N a_i'^2
-  \label{eqn:klm-stack}
-\end{equation}
-where $K_{\ell m}^i$ and $a_i^2$ obey the same definition as $K_{\ell m}$ in equation \ref{eqn:klm} and $a_\mathcal{A}$ in equation \ref{eqn:am} respectively integrated over the $i$th lump, but we set the normalizing factors $1/(\mu_\mathcal{A} a_\mathcal{A}^\ell)$ and $1/\mu_\mathcal{A}$ equal to the values for the entire asteroid, not their counterparts for each lump.
-The zero-indexed parameters indicate the moments of the medium.
-The prime in equation \ref{eqn:klm-stack} denotes that the moments are calculated in the hybrid frame, with its origin at the asteroid centre of mass.
-
-We can relate the primed moments to the moments calculated relative to each lump's centre of mass via the translation rules for solid spherical harmonics:
-\begin{equation}
-  \begin{split}
-  & K_{\ell m}'^i = \frac{1}{a_\mathcal{A}^{\ell - \ell'}}\sum_{\ell' m'} (-1)^{\ell - \ell'} R_{\ell - \ell', m - m'}(\bm x_i) K_{\ell' m'}^i\\
-  & a_i'^2 = a_i^2 + x_i^2 \frac{\mu_i}{\mu_\mathcal{A}}
-  \end{split}
-  \label{eqn:translate-klm}
-\end{equation}
-from Ref.~\cite{Gelderen1998TheSO}.
-The dummy indices $\ell', m'$ should only be summed over values in which $\ell-\ell' \geq 0$ and $|m-m'| \leq \ell - \ell'$.
-Here, $\mu_i$ is the added mass of lump $i$, while $K_{1m}=0$ and $K_{2m}$ incorporate the lump's orientation and moment of inertia ratios.
-Its volume is constrained by $a_i^2$.
-These values map onto an ellipsoid shape via equations \ref{eqn:ellipsoid-axes}, so that if $K_{\ell m}^i$, $a_i^2$, $\mu_i$, and $x_i$ are known, then the density distribution of the asteroid is known.
-
-Fixing $\bm x_i$, equation \ref{eqn:translate-klm} is linear in $K_{\ell m}^i$ and $a_i^2$.
-Therefore, if we define $\bm \Theta$ to contain $K_{2m}^i$ and $a_i^2$ for all $i$ in some order, then equations \ref{eqn:translate-klm} and \ref{eqn:klm-stack} define a matrix equation $\bm K = \bm C + M \bm \Theta$ which can be solved by setting $A$ equal to the Moore-Penrose inverse of $M$ (equation \ref{eqn:mpi-overdetermined}, since $\bm \Theta$ is overdetermined).
-The $\bm C$ term of this equation came from the expansion of $K_{\ell m}'^0$ and $a_0^2$, which is written in terms of the already-known displacement of the asteroid surface from its centre of mass and the surface shape.
-
-We use the following non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described above.
-We must incorporate the centre-of-mass and total-mass constraints
-\begin{equation}
-  \mu_0 \bm x_0 + \sum_{i=1}^N \mu_i \bm x_i = 0, \qquad \mu_0 + \sum_{i=1}^N \mu_i = \mu_\mathcal{A}.
-  \label{eqn:lump-constraints}
-\end{equation}
-There are also additional constraints, such as that $\bm x_i$ should lie inside the asteroid, which can be enforced manually.
-Combining both constraints in equation \ref{eqn:lump-constraints}, we can eliminate $\mu_0$ and vary only $\mu_i$ and $\bm x_i$ for $i \geq 1$.
-
-The matrix equation defining $M$ is overdetermined, but we would like it to have a solution nevertheless.
-We therefore solve for $\bm x_i$ and $\mu_i$ by minimizing the difference between the known density moments and the output of the model.
-This is done by minimizing
-\begin{equation}
-  |(M(\bm x_i, \mu_i) M^+(\bm x_i, \mu_i) - \mathds{1}) (\bm K - \bm C)|^2.\
-  \label{eqn:lump-minimize}
-\end{equation}
-where $\mathds{1}$ is the identity matrix.
-We cannot define $\bm B(\bm r)$ such that $\rho(\bm r)$ is linear in $\bm B$, but uncertainty on $K_{\ell m}^i$ can still be evaluated as $\Sigma_\Theta$ and these can be converted into uncertainties in the dimensions and orientations of the lumps.
-If the resulting density distribution is somehow excluded (it predicts negative density distributions or the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
+Thus, uncertainty on $K_{\ell m}^\mathrm{body-fixed}$ (obtained from the encounter data) can be translated to uncertainty in $K_{\ell m}^\mathrm{hybrid}$.
+From now on, we will operate only in the hybrid frame and suppress the label.
+
+To extract a density distribution for the asteroid, we divide the asteroid into $N$ finite elements of uniform density.
+When the $K_{3m}$ are extracted, 16 moments are known.
+However, one of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely.
+Six more are redundant with the position and orientation of the coordinate axes, such that only nine finite elements are free.
+On all the $N$ densities, we place constraints that $0.25 < \rho < 3$, in units where the average density of the asteroid is one (i.e., the mass of the asteroid is set equal to the volume).
+
+\jtd{Continue description}
 
@@
 But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in figure \ref{fig:uniform-density-results}.
-
-\jtd{Note for Julien: the cutoffs on the color bars (95\% of the asteroid) are kind of arbitrary.
-I could make histograms showing, on the vertical axis, $\Delta \sigma$ or $\sigma_\rho/\rho$ or $\Delta \rho$ (i.e.,  the metrics which are plotted in these figures).
-On the vertical axis, I would plot what fraction of the asteroid has these values.
-So you would expect to see that most of the asteroid has $\Delta \rho$ small, and then there's a cutoff beyond which only a small fraction of the asteroid has larger $\Delta \rho$.
-Do you think this plot is worth the space?}
 
@@
 
-\jtd{The failure of this model makes me think we really should only do the finite element analysis, though I think uncertainty will only improve if we average over multiple grids.
-That's based on my messing around so far.}
-
 For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\chi_r^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).

### 2022-06-15 paper/main.tex
Added hybrid frame into computations

@@
 However, one of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely.
-Six more are redundant with the position and orientation of the coordinate axes, such that only nine finite elements are free.
-On all the $N$ densities, we place constraints that $0.25 < \rho < 3$, in units where the average density of the asteroid is one (i.e., the mass of the asteroid is set equal to the volume).
+We set the asteroid mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.Three more are redundant with the center of mass, such that only twelve finite elements are free.
+In cases where $\gamma_0$ is known very accurately such that the correction imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable not to impose this equation on $K_{2m}$.
+In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom.
+On all the $N$ densities, we place additional constraints that $0.25 < \rho < 3$.
 

### 2022-06-15 code/density/finite-element/main.py

@@ -32,11 +32,35 @@ MINIMIZATION_ATTEMPTS = 500
 
 def get_cov(path):
     with open(path, 'rb') as f:
-        flat_samples = np.load(f).reshape(-1, N_FITTED_MOMENTS + 1)[:, 1:]
+        data = np.load(f).reshape(-1, N_FITTED_MOMENTS + 1)
+        initial_rolls = data[:, 0]
+        flat_samples = data[:, 1:]
     if flat_samples.shape[0] == 0:
         return None, None
-    cov = np.cov(flat_samples.transpose())
-    data = np.mean(flat_samples, axis=0)
+    complex_samples = np.zeros((len(flat_samples), 6), dtype=np.complex)
+    complex_samples[:, 0] = flat_samples[:, 0] # K22
+    complex_samples[:, 1] = flat_samples[:, 1] # K20
+    complex_samples[:, 2] = flat_samples[:, 2] + 1j * flat_samples[:, 3] # K33
+    complex_samples[:, 3] = flat_samples[:, 4] + 1j * flat_samples[:, 5] # K32
+    complex_samples[:, 4] = flat_samples[:, 6] + 1j * flat_samples[:, 7] # K31
+    complex_samples[:, 5] = flat_samples[:, 8] # K30
+    ms = np.array([
+        0, # I chose not to apply to K22 because the correction is so small
+        0, 3, 2, 1, 0])
+    exponents = -1j * np.outer(initial_rolls - np.mean(initial_rolls), ms)
+    complex_hybrid_samples = complex_samples * np.exp(exponents)
+    real_hybrid_samples = np.zeros_like(flat_samples)
+    real_hybrid_samples[:, 0]  = complex_hybrid_samples[:, 0].real # K22
+    real_hybrid_samples[:, 1]  = complex_hybrid_samples[:, 1].real # K20
+    real_hybrid_samples[:, 2]  = complex_hybrid_samples[:, 2].real # R K33
+    real_hybrid_samples[:, 3]  = complex_hybrid_samples[:, 2].imag # I K33
+    real_hybrid_samples[:, 4]  = complex_hybrid_samples[:, 3].real # R K32
+    real_hybrid_samples[:, 5]  = complex_hybrid_samples[:, 3].imag # I K32
+    real_hybrid_samples[:, 6]  = complex_hybrid_samples[:, 4].real # R K31
+    real_hybrid_samples[:, 7]  = complex_hybrid_samples[:, 4].imag # I K31
[…]

### 2022-06-17 paper/main.tex
Updated paper

@@
 Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
-However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
+However, density distribution features beyond the moment of inertia (MOI) ratios have not yet been extracted for any asteroid encounters.
 More research is needed to study in what cases these effects are observable, and what
@@
 binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
-Orbital and physical properties, including moment of inertia ratios have also been extracted for 99942 Apophis, which will closely encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
+Orbital and physical properties, including MOI ratios have also been extracted for 99942 Apophis, which will closely encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
 It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity \cite{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
@@
 \begin{equation}
-  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\text{bulk}^2 a_\text{surf}^{\ell - 2}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
+  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r).
   \label{eqn:klm}
@@
 These are complex, unitless quantities.
-$\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
+$\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
 The integral is computed over the entire asteroid mass, denoted $\mathcal{A}$.
-The two length scales $a_\text{surf}$ and $a_\text{bulk}$ are defined as
+$I_\mathcal{A}$ denotes a MOI scale defined as
 \begin{equation}
-  a_\text{bulk}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2 \qquad
-  a_\text{surf}^2 = \frac{1}{V_\mathcal{A}} \int_\mathcal{A} d^3 r r^2
-  \label{eqn:am}
+  I_\mathcal{A} = \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2
+  \label{eqn:ia}
+\end{equation}
+while $a_\mathcal{A}$ is the length scale
+\begin{equation}
+  a_\mathcal{A}^2 = \frac{1}{V_\mathcal{A}} \int_\mathcal{A} d^3 r r^2
+  \label{eqn:aa}
 \end{equation}
 where $V_\mathcal{A}$ is the asteroid volume.
-We highlight two crucial details of these length scales: (1) that they are equal when $\rho_\mathcal{A}$ is uniform across the asteroid, and (2) that $a_\text{surf}$ is a function only of the boundary of $\mathcal{A}$ whereas $a_\text{bulk}$ is a function of the internal density distribution.
+We call these MOI and length scales in part because they obey $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$ where $\mu_\mathcal{A}$ is the mass of the asteroid for uniform asteroids.
+Note that $a_\mathcal{A}$ is a function only of the surface of the asteroid, so that $a_\mathcal{A}$ is known if the surface is observed.
 
@@
   \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[a_\text{bulk}^2 \sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\text{surf}^{\ell' - 2}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \bm \tau = & G\frac{\mu_\mathcal{B}}{2}\left[I_\mathcal{A} \sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\text{surf}^{\ell' - 2}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
   \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
@@
 
-Since it is the angular acceleration of the asteroid that is observable, rather than the torque applied, we also compute the moment of inertia of the asteroid around the principal axes: 
+Since it is the angular acceleration of the asteroid that is observable, rather than the torque applied, we also compute the MOI of the asteroid around the principal axes: 
 \begin{equation}
   \begin{split}
-    I_x &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{K_{20} - 6 K_{22} + 1}\\
-    I_y &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{K_{20} + 6 K_{22} + 1}\\
-    I_z &= \frac{2}{3}\mu_\mathcal{A} a_\text{bulk}^2 \parens{-2K_{20} + 1}.
+    I_x &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} - 6 K_{22} + 1}\\
+    I_y &= \frac{2}{3} I_\mathcal{A} \parens{K_{20} + 6 K_{22} + 1}\\
+    I_z &= \frac{2}{3} I_\mathcal{A} \parens{-2K_{20} + 1}.
   \end{split}
@@
 
-The angular acceleration of the asteroid is proportional to $\bm \tau / I$ (equation \ref{eqn:omega-eom}), such that the $a_\text{bulk}^2$ factor of equation \ref{eqn:tidal-torque} is canceled out.
-Thus, the observables do not depend explicitly on $a_\text{bulk}$.
+The angular acceleration of the asteroid is proportional to $\bm \tau / I$ (equation \ref{eqn:omega-eom}), such that the $I_\mathcal{A}$ factor of equation \ref{eqn:tidal-torque} is canceled out.
+Thus, the observables do not depend explicitly on $I_\mathcal{A}$, nor on the asteroid mass.
 
@@
 We built a publicly accessible, custom simulation in C++ to produce time series of angular velocity data during a close encounter with a central body.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\text{surf}$ and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
+This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$ and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
 All parameters except (6) are assumed to be known to high accuracy.
@@
 Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-This width is related to the uncertainty in asteroid period $\sigma_P$ by $\sigma_P=P \sigma_\rho$ for small $\sigma_\rho$.
+We also draw the ratio $\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_P / P$, where $P = 2\pi \Omega$ is the period of the asteroid.
 Explicitly, the probability density function (PDF) of $\rho$ is
 \begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi (\sigma_P / P)^2}} \exp\parens{-\frac{\ln^2\rho}{2(\sigma_P / P)^2}}.
 \end{equation}
@@
   \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
-  &+\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
+  &+\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{(\sigma_P / P)^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
   \end{split}
@@
 This model was chosen because it separates spin pole and period uncertainty.
-Therefore, if one is more precisely determined by measurement, $\sigma_\theta$ and $\sigma_\rho$ can be adjusted separately in accordance.
+Therefore, if one is more precisely determined by measurement, $\sigma_\theta$ and $\sigma_P / P$ can be adjusted separately in accordance.
 
@@
 
-\subsection{Translating constraints on density moments into constraints on the density distributon}
+\section{Density distributon constraints}
 \label{sec:density-distro}
@@
 Thus, uncertainty on $K_{\ell m}^\mathrm{body-fixed}$ (obtained from the encounter data) can be translated to uncertainty in $K_{\ell m}^\mathrm{hybrid}$.
-From now on, we will operate only in the hybrid frame and suppress the label.
-
-To extract a density distribution for the asteroid, we divide the asteroid into $N$ finite elements of uniform density.
+Henceforth, we will operate only in the hybrid frame and suppress the label.
+
 When the $K_{3m}$ are extracted, 16 moments are known.
-However, one of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely.
-We set the asteroid mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.Three more are redundant with the center of mass, such that only twelve finite elements are free.
+However, $K_{00}$ of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely.
+It is convenient to set the asteroid mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
+Three more moments are redundant with the center of mass, such that only twelve finite elements are free.
 In cases where $\gamma_0$ is known very accurately such that the correction imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable not to impose this equation on $K_{2m}$.
 In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom.
-On all the $N$ densities, we place additional constraints that $0.25 < \rho < 3$.
-
-\jtd{Continue description}
+We also place additional constraints that $0.25 < \rho < 3$ to ensure realistic densities.
+
+To extract a density distribution, we use another MCMC given one of the two parametrizations of density distributions discussed below.
+The prior is set to be flat and nonzero for all configurations that obey the $0.25 < \rho < 3$ constraint.
+The likelihood used is set equal to the multivariate-Gaussian approximation of the posterior distribution for $K_{\ell m}$, extracted from flyby data.
+Otherwise, the MCMC parameters chosen were identical to those discussed in section \ref{sec:fit}.
+
+\subsection{Finite element model}
+
+Given values of $K_{\ell m}^\mathrm{body-fixed}$ and their uncertainties extracted from encounter data, there are many ways to extract a density distribution.
+Here, we outline a method termed the ``finite element'' model.
+We divide the asteroid into $N$ finite elements of uniform density and use the density $\rho_i$ of each as parameters.
+The four constraints imposed by the known mass and center of mass of the asteroid (seven with $K_{21}$ and $\Im K_{22}$ are also fixed) are used to constrain some of these $\rho_i$.
+The constrained densities are easily computed since the asteroid mass $\mu_\mathcal{A}$ and the product $I_\mathcal{A}K_{\ell m}$ are both linear functions of $\rho_i$.
+Because $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, computing the constrained densities is simply a matrix inversion.
+
+The size and location of the elements must be chosen before extracting their densities.
+Best results generally require elements of equal size to be chosen.
+To remove the dependence on this choice, density distributions for many distinct element layouts can be extracted and the density of each point in the asteroid can be randomly sampled from any of these solutions to yield estimates for the mean density and uncertainty in density at each point.
+
+The value of $N$ must be carefully chosen, since it embodies a balance between the precision and accuracy of the resulting distribution.
+If $N$ is set equal to the number of data points, an accurate solution is  guaranteed, but uncertainties are inflated.
+If $N$ is chosen lower, the choice of element layout might exclude a distribution that exactly matches $K_{\ell m}$, but uncertainties are diminished due to less redundancy in the model.
+To select our value of $N$, we extract density distributions for moments extracted from simulated flyby data of the reference asteroid.
+We assume an ellipsoidal shape consistent with uniform asteroid density and extract 5 density distributions for it using this finite element model.
+We do this for multiple values of observational precision on the rotational period of the asteroid.
+Figure \ref{fig:dof-scan} displays the resulting average uncertainty on $\rho_i$ for each of the five extractions ($\sigma_\rho / \rho$), as well as the average deviation from the truth  ($\Delta \rho / \rho$), and displays the maximum and mean significance of these deviations ($\Delta_\rho / \sigma_\rho$).
+s\begin{figure}
+  \centering
+  \caption{Uncertainty in density, deviations from the true density, and maximum and mean significance of these deviations are plotted as a function of the observational precision of the flyby data.
+Five density distributions are computed for each value of observational precision (light dots) and their average is displayed (solid dots and lines).
+Each line represents a different choice in the number of free parameters used, with nine being maximal.
+Results show that few free parameters yield precise but inaccurate results, and that more yield imprecise but accurate results.}
+  \label{fig:dof-scan}
+\end{figure}
+The figure demonstrates that model accuracy is not a significant effect until the number of degrees of freedom is $\lesssim 3$, at which point $\Delta_\rho / \sigma_\rho$ rises greatly.
+Uncertainty, however, is lower for 7 or 5 degrees of freedom than it is for 9.
+To balance accuracy and precision, we choose to use this lumpy model with 5 degrees of freedom henceforth, meaning we choose $N=12$ finite elements (using the $K_{21} = \Im K_{21} = 0$ constraint).
+
+\subsection{Lumpy model}
+
+A drawback of the finite element model is that the generated density distribution might not be representative of the asteroid if the elements are not optimally placed.
+We therefore describe an alternate model, which includes the positions of the elements as parameters at the cost of larger elements and therefore lower resolution.
+We call this model the ``lumpy'' model.
+
+Suppose the asteroid is formed of $N$ constant-density, possibly overlapping ``lumps,'' enclosed within a constant-density substrate whose surface is visible to observers.
+The lumps and the substrate are described by the mass added to the substrate by a lump $\mu_i$, the position of its center of mass $\bm r_i$ (relative to the asteroid's center of mass), its density moments $K_{\ell m}^{(i)}$, and its length scale $a_i$.
+Here, $i$ denotes the index of the lump where the substrate is $i=0$.
+We do not need to include $I_i$ as a free parameter because these lumps have constant density, so that $I_i = \mu_i a_i^2$.
+Furthermore, by requiring that a lump's density moments be computed relative to the center of mass of the lump, we have $K_{1m} = 0$.
+
+The translation rules of spherical harmonics give that the asteroid properties in the hybrid frame are
+\begin{equation}
+  \begin{aligned}
+    K_{\ell m} = &\brackets{\sum_{i=0}^N \frac{a_i^2 + r_i^2}
+    {a_\mathcal{A}^2}\mu_i}^{-1} \\
+    &\brackets{\sum_{i=0}^N \sum_{\ell' m'}\mu_i
+    \frac{a_i^{\ell'}}{a_\mathcal{A}^\ell}
+    R_{\ell - \ell', m - m'}(\bm r_i)K_{\ell' m'}^{(i)}} \\
+  \end{aligned}
+\end{equation}
+where the sum limits are $0 \leq l' \leq l$ and $-\ell' \leq m' \leq \ell'$. We also have total mass and center of mass constraints:
+\begin{equation}
+  \mu_\mathcal{A} = \sum_{i=0}^N \mu_i,  \qquad 0 = \sum_{i=0}^N \mu_i \bm r_i.
+\end{equation}
+Additional constraints can be imposed on $K_{\ell m}^{(i)}$ if desired.
+For example, we can require that the lumps be ellipsoids, so that $K_{3 m}^{(i)} = 0$.
+Additional rotational symmetries also constrain $K$, with the most extreme case being that spherical lumps have $K_{\ell m} = 0$ for $\ell > 0$.
+However, $K_{00}=1$ is guaranteed by definition, meaning that each spherical lump has only five degrees of freedom ($a_i$, $\mu_i$, and $\bm r_i$).
+The substrate has one degree of freedom, since only $\mu_0$ is unknown.
+Thus, this lumpy model has $5N - 3$ total degrees of freedom.
 
@@
 Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
-As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
+As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the MOI (equation \ref{eqn:moi}).
 The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
@@
 Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-There, the angular velocity evolution is dominated by torque-free precession dictated by the moment of inertia components.
+There, the angular velocity evolution is dominated by torque-free precession dictated by the MOI components.
 That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
@@
 This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
+Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern MOI ratios from zero-torque precession after the encounter.
 If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.

### 2022-06-22 old-papers/draft3/old-models.tex
Added to paper and converted to using many samples rather than an average density distribution

--- 2022-04-25 old-papers/draft2/main.tex
@@
-\documentclass[fleqn,usenatbib]{mnras}
-
-\usepackage[T1]{fontenc}
-
-\DeclareRobustCommand{\VAN}[3]{#2}
-\let\VANthebibliography\thebibliography
-\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
-
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{xcolor}
-\usepackage{tikz}
-\usepackage{colortbl}
-\usepackage{dsfont}
-\usepackage{siunitx}
-\usepackage{bm}
-
-% For the sideways figure
-\usepackage{pdflscape}
-\usepackage{afterpage}
-
-\usetikzlibrary{arrows.meta}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\newcommand{\jtd}[1]{ {\bf{\color{red} JTD: #1}} }
-\newcommand{\unit}[1]{\bm{\hat{#1}}}
-
-\newcommand{\parens}[1]{\left( #1 \right)}
-\newcommand{\brackets}[1]{\left[ #1 \right]}
-\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
-
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-\title[Flyby Constraints on Asteroids Interiors]{Constraining the Interiors of Asteroids Through Close Encounters}
-
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
-\author[Jack T. Dinsmore, Julien de Wit]{
-Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
-Julien de Wit$^{2}$
-\\
-% List of institutions
-$^{1}$Department of Physics, Massachusetts Institute of Technology\\
-$^{2}$Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-% Enter the current year, for the copyright statements etc.
-\pubyear{2022}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-
-% Abstract of the paper
-\begin{abstract}
-  Knowledge of the interior distribution of an asteroid can reveal its composition and constrain its evolutionary history.
-However, most asteroid observational techniques are not sensitive to interior structure.
-We investigate the degree to which interior density distributions can be extracted from angular velocity data gathered during a close encounter.
-We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we re-extract the density moments of the asteroid in a wide range of scenarios to measure the degree to which best-fitting parameter precision is affected.
-Specifically, we use many injection-retrieval tests to study fit precision's dependence on the asteroid's moment of inertia, observational precision and cadence, orbital parameters, and initial spin pole direction as well as the planet being encountered, the quantity of near-pericentre data, and the central body oblateness.
-Finally, we discuss the degeneracy between the density moments and the actual density distribution and propose three models to construct a representative density distribution from fit results.
-\end{abstract}
-
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
-\begin{keywords}
-  minor planets, asteroids: general -- methods: data analysis
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Over the past twenty years, the increase in quantity and quality of sensitive all-sky surveys has prompted the discovery of numerous asteroids.
-Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
-Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to closely encounter Earth or other planets in the near future.
-More encounter candidates are likely to be discovered by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) or the Las Cumbres Observatory (LCO).
-Light curve analysis has been performed on many asteroids to study their surface properties, but observations that are sensitive to the interior asteroid structure are rarer.
-
-However, tidal torque acting on an asteroid and perturbing its angular velocity during an encounter presents an opportunity to constrain the interior mass distribution.
-Such angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus respectively.
-Altered rotational states altered by Solar tidal torque have been excluded for 1I/2017 U1 `Oumuamua \cite{KWIECINSKI2018170}.
-
-The upcoming 2029 encounter of 99942 Apophis is of particular interest and much theoretical work has been devoted to accurate estimates of its orbital and physical properties and predictions of how its angular velocity will be affected by tidal torque \cite{yu2014numerical, hirabayashi2021finite,valvano2022apophis, Lee2022Apophis, souchay2014rotational, souchay2018changes}.
-This research builds on a larger body of theoretical work.
-The gravitational two-body system has been studied in the context of tidal torque to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, RICHARDSON199847, scheeres2004evolution}.
-However, density distribution features beyond the moment of inertia ratios have not yet been extracted for any asteroid encounters.
-More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
-
-In this paper, we address this question by deriving a new equation of motion for an asteroid encounter system which is quick to compute and valid to arbitrary order.
-In section \ref{sec:methods}, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts physical characteristics of the asteroid (specifically, density moments) from the fit data.
-We then describe three methods to generate full density distributions from the density moments.
-Section \ref{sec:results} demonstrates the efficacy of this spin-data-to-density-distribution pipeline and explores its key properties.
-Finally, in section \ref{sec:discussion}, we measure the uncertainties of the best-fitting parameter estimates as a function of various encounter properties to determine which properties most inhibit accurate extraction of density distributions.
-We also test the density distribution extraction methods on several sample asteroids.
-
-\section{Methods}
-\label{sec:methods}
-
-Only some aspects of an asteroid's density distribution affect tidal torque interactions. These are the asteroid ``length'' 
-\begin{equation}
-  a_\mathcal{A}^2 = \frac{1}{\mu_\mathcal{A}} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) r^2
-  \label{eqn:am}
-\end{equation}
-and (complex) ``density moments''
-\begin{equation}
-  K_{\ell m} = \frac{1}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \int_\mathcal{A} d^3 r \rho_\mathcal{A}(\bm r) R_{\ell m}(\bm r),
-  \label{eqn:klm}
-\end{equation}
-both of which are constant and only need to be computed once to generate data.
-Here, $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution, $\mu_\mathcal{A}$ is the asteroid mass, and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
-They produce a tidal torque of
-\begin{equation}
-  \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{A}\mu_\mathcal{B}}{2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
-  \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
-  \times & \Big((i\unit x - \unit y)(\ell'-m''+1)K_{\ell',m''-1} \\
-  & +(i\unit x+\unit y)(\ell'+m''+1)K_{\ell',m''+1}+2im''\unit z K_{\ell'm''}\Big) \Bigg],
-  \end{split}
-  \label{eqn:tidal-torque}
-\end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $\mu_\mathcal{B}$, $a_\mathcal{A}$, and $J_{\ell m}$ are the mass, length, and density moments of the central body respectively; and $S_{\ell m}$ are the irregular solid spherical harmonics.
-Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
-Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also defined in appendix \ref{app:eom}.
-
-In section \ref{sec:sim}, we describe the simulation used to integrate the equations of motion.
-In section \ref{sec:uncertainty}, we define the uncertainty model used to add noise to the data, and we describe how posterior probability distributions (PPDs) for density moments were extracted from spin-pole data in section \ref{sec:fit}.
-Finally, we outline a general model to extract density distributions from density moments in section \ref{sec:general-density} and define specific model implementations in section \ref{sec:specific-density}.
-
-\subsection{Simulation design}
-\label{sec:sim}
-
-We built a publicly accessible, custom simulation in C++ to produce angular velocity data as a function of time.
-This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$; and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
-All parameters except (6) are assumed to be known to high accuracy.
-One can imagine that $a_\mathcal{A}$ is approximated by light-curve analysis, but if not, it is still necessary to fix $a_\mathcal{A}$ or else the values of $K_{\ell m}$ are degenerate with $a_\mathcal{A}$.
-
-We further assume that the asteroid is initially not tumbling.
-Thus, the angular velocity is aligned with a principal axis (assumed to be $\unit z$, which maximizes moment of inertia).
-This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Thus, only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
-
-We begin our simulation at $D = 10 r_p$, with velocity predicted by Kepler's laws given by the orbital parameters.
-Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
-Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
-
-With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step
-\begin{equation}
-  dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
-\end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
-The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
-
-\subsection{Uncertainty model}
-\label{sec:uncertainty}
-
-To add noise to data generated via the above simulation, we use the following uncertainty model.
-Each asteroid spin vector $\bm \Omega$ is assumed to be uncorrelated with other spin vectors, and we model uncertainty in the orientation and in the period as also uncorrelated.
-Consider a true spin vector $\bm \Omega^*$.
-For the sake of description, we work in coordinates in which $\bm \Omega^* \parallel \unit z$.
-Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\rho=\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_\rho$.
-This width is related to the uncertainty in asteroid period $\sigma_P$ by $\sigma_P=P \sigma_\rho$ for small $\sigma_\rho$.
-Explicitly, the probability density function (PDF) of $\rho$ is
-\begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi \sigma_\rho^2}} \exp\parens{-\frac{\ln^2\rho}{2\sigma_\rho^2}}.
-\end{equation}
-See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model.
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit X$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (1, -1.5) node[anchor=west] {$\unit Y$};
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
-
-  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
-  \draw[dashed] (-3, -2) -- (-3, 3);
-  \draw[dashed] (-3, -2) -- (0, 0);
-
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
-  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
-  \draw (-3, 3) arc (110:93:6);
-  \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-0.5, 2.5) node[anchor=center] {$\rho \Omega^*$};
-
-  \end{tikzpicture}
-  \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
-The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
-  \label{fig:uncertainty-model}
-\end{figure}
-
-The log likelihood resulting from this uncertainty model is (excluding additive constants)
-\begin{equation}
-  \begin{split}
-  \ln \mathcal{L} = -\frac{1}{2}\sum_{i = 0}\Bigg[&\frac{\cos^{-1} (\bm \Omega_i^* \cdot \bm \Omega_i/(\Omega_i^* \Omega_i))^2}{\sigma_\theta^2}\\
-  &+\frac{\ln \parens{\Omega_i /\Omega_i^*}^2}{\sigma_\rho^2} + 2\ln\frac{\Omega_i}{\Omega_i^*}\Bigg].
-  \end{split}
-  \label{eqn:log-likelihood}
-\end{equation}
-where $\Omega_i$ is the $i$th spin vector in the data set.
-
-This model was chosen because it separates spin pole and period uncertainty.
-Therefore, if one is more precisely determined by measurement, $\sigma_\theta$ and $\sigma_\rho$ can be adjusted separately in accordance.
-
-\subsection{Extracting density moments from spin data}
-\label{sec:fit}
-Given synthetic data, an Affine Invariant MCMC Ensemble sampler was used to generate PPDs from flat priors.
-We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
-Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
-Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ because both of these align the asteroid principal axes with the body-fixed axes.
-The other bounds were $|K_{3m}| < 1$.
-In general, spin data is most sensitive to $\gamma_0$ and $K_{2m}$, which we call the ``first-order parameters.'' We call $K_{3m}$ the ``second-order parameters.''
-
-The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data was too low-quality to resolve the parameters.
-$\sim 10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
-
-Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
-Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
-Ensemble walkers were initialized near this local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
-Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
-Therefore, a simpler simulation without the $K_{3m}$ terms of equation \ref{eqn:tidal-torque} was first used to minimize likelihood as a function of the first-order parameters $\gamma_0$ and $K_{2m}$, and then the full simulation was used to find the second-order parameters $K_{3m}$ with the first-order parameters fixed.
-
-To further ensure convergence, we minimized with respect to data truncated after perigee at double the perigee distance.
-This cut-off was manually chosen.
-The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
-
-\subsection{Extracting density distributions from moments: general model design}
-\label{sec:general-density}
+\subsection{Translating constraints on density moments into constraints on the density distributon}
+\label{sec:density-distro}
 
@@
 We outline three different assumptions which constitute three models for extracting density distributions from density moments.
+Our goal in investigating different families of models to translate constraints on the density moments into constraints on the density distribution is to reveal the major features in the density distribution that are consistently present, independent of the family of mapping model used, despite the problem underdetermination (in a similar fashion to \cite{de2012towards}).
+
 All are (partially) linear to facilitate computational ease and uncertainty propagation.
-One of them can be chosen, or another created, depending on what features are desired to be represented in the density distribution.
-
 All three of these models assume that $a_\mathcal{A}$ and the asteroid shape is known (for example, by light curve or radar data).
-Uncertainty on this shape estimate is assumed to be small.
+Uncertainty on this shape estimate is assumed to be negligible compared to the density moment uncertainty and their contributions to to the density distribution.
 The models then produce a density distribution $\rho_\mathcal{A}(\bm r)$ with uncertainty from $K_{\ell m}$ propagated to uncertainty in $\rho_\mathcal{A}$.
@@
 In section \ref{sec:results}, we were forced to fix $a_\mathcal{A}$ rather than fit for it because $a_\mathcal{A}$ is degenerate with scaling $K_{3m}$.
-However, $a_\mathcal{A}$ contains information about the density distribution as shown by its definition in equation \ref{eqn:am}.
-It might therefore be unreasonable to assume that it is exactly determined by light-curve or radar analysis.
-If $a_\mathcal{A}$ is too uncertain to be used as a known quantity when extracting density distributions from the moments, then the following models are flexible enough that the $a_\mathcal{A}$ constraint can be removed.
+When extracting density distributions, multiple $a_\mathcal{A}$ values may be tested and the multiple produced density distributions can be compared to highlight common features.
 
@@
 
-\subsection{Extracting density distributions from moments: specific models}
-\label{sec:specific-density}
-
 \subsubsection{The ``likelihood'' model}
@@
 
-We now explore a model that seeks to restrict the space of allowed density distributions a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
+We now explore a model that seeks to restrict the space of allowed density distributions in a different way: we allow only the density distributions with $\nabla^2 \rho = 0$ inside the asteroid (the harmonic distributions).
 We  call this  the ``harmonic'' model.
@@
 
-We use a non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described in section \ref{sec:general-density}.
+We use the following non-linear process to choose $\bm x_i$ and $\mu_i$ so that $K_{\ell m}^i$ and $a_i$ can then be extracted via the linear process described above.
 We must incorporate the centre-of-mass and total-mass constraints
@@
 If the resulting density distribution is somehow excluded (it predicts negative density distributions or the lumps extend outside the asteroid, etc.), then another minimum of equation \ref{eqn:lump-minimize} can be used, or another combination of $N$ and $d$ listed in table \ref{tab:lump-dof}.
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Density moment extraction}
-\label{sec:example-fit}
-To demonstrate our fit process, we present example results of the MCMC fit described in section \ref{sec:fit}, applied to encounter data of the asymmetric reference asteroid.
-The fit results were consistent with the true density moments, and produced consistent data.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.6\textwidth]{figs/example-residuals.pdf}
-  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid. Uncertainty bands are also shown.}
-  \label{fig:example-residuals}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.85\textwidth]{figs/example-corner.png}
-  \caption{PPDs extracted from synthetic encounter data for the asymmetric reference asteroid.
-Samples from the MCMC fit are shown as individual points, and the contours enclose 1, 2, and 3$\sigma$ confidence regions.
-True values are shown as blue lines.}
-  \label{fig:example-corner}
-\end{figure*}
-
-Figure \ref{fig:example-residuals} shows the spin data with noise added.
-The best-fitting model is overlaid in the top pane and residuals are shown the bottom pane.
-Specifically, we show the model whose parameters are the means of the PPDs.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
-The fit results are clearly consistent with the data.
-
-Figure \ref{fig:example-corner} shows a corner plot of the ten fitted PPDs, marginalized to functions of one (histograms) or two (contours) variables.
-The true parameters are shown as lines.
-Note that the true parameters usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-The PPDs are generally Gaussian and sometimes show correlation between parameters, but no continuous degeneracy occurs.
-We performed 48 independent minimizations of the likelihood before the MCMC fit began, each with an initial point chosen randomly in the parameter space.
-All converged to the same minimum, demonstrating that the model lacks discrete degeneracy as well.
-
-\subsection{Density distribution extraction}
-\label{sec:asym-density}
-To demonstrate our three density distribution extraction models, we show density distributions and uncertainties extracted for the asymmetric reference asteroid in figure \ref{fig:uniform-density-results}.
-These distributions were made given the density moment PPDs extracted above, with $a_\mathcal{A}$ fixed.
-The surface is fixed as a triaxial ellipsoid with semi-axis lengths such that the true values of $K_{\ell m}$ are consistent with uniform density (equation \ref{eqn:ellipsoid-axes}).
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \caption{Density distributions (\textit{top}) and uncertainties (\textit{bottom}) extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density, asymmetric reference asteroid.
-Density is normalized so that mean density is one.}
-  \label{fig:uniform-density-results}
-\end{figure*}
-
-Also in each pane of figure \ref{fig:uniform-density-results} is $\Delta K_{\ell m}$, the squared magnitude of difference between the fitted density moments and the density moments of the final distribution.
-This difference is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
-The harmonic and lumpy models have no such guarantee, however.
-
-The likelihood and harmonic models produce nearly identical density distributions.
-This is generally true for uniform density asteroids, which have harmonic density distributions.
-Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
-This similarity lends confidence to both models, because if one were unexpectedly biased towards certain distributions, the other would have to be equally biased in the same way in this case to produce the same distribution, which appears unlikely given that the models share little in common.
-
-The distributions are non-uniform for the harmonic and likelihood models (driven by error in the estimates of $K_{3m}$), but the non-uniformity is limited.
-Note that most of the asteroid has density close to the mean density (one) in both cases, with densities of 40\% or 160\% of the mean attained only in small regions.
-The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
-However, it does not produce a density distribution consistent with the moments extracted from spin data (i.e., $\Delta K_{\ell m}$ is large).
-This is because the lump found extends outside the asteroid, violating the assumptions of the model.
-This is a sign that the lump found does not really exist inside the asteroid.
-
-The size of uncertainty is such that the density distribution is consistent with uniform for the harmonic and likelihood models (within 1.5$\sigma$).
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Spin evolution}
-\label{sec:spin-evolution}
-In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
-A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter.
-The exact parameters used were the symmetric and asymmetric cases described in appendix \ref{app:reference-configs}.
-Bands containing 68.3\%, 95.5\%, and 99.7\% of the population's spin are shown, as is the spin of the reference asteroids in black.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\linewidth]{figs/nominal-data-sym.pdf}
-  \includegraphics[width=\linewidth]{figs/nominal-data-asym.pdf}
-  \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
-The true angular velocity evolution is shown as a black line.
-Also plotted is the deviation of the data for PPD-distributed perturbations to the asteroid shape (bands).
-Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.}
-  \label{fig:example-data}
-\end{figure}
-
-The initial values of $\gamma_0$, $K_{20}$, and $K_{22}$ were distributed proportional to the PPDs extracted via the MCMC fit shown in section \ref{sec:example-fit}.
-The PPDs were widened by a factor of 1000 to make the band widths visible.
-Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
-
-The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
-The spin data at perigee is informative and shows non-trivial behaviour.
-After perigee, the asteroid population tumbles according to torque-free precession with different oscillation periods.
-This dramatically increases the spread of angular velocities within the distribution and allows for more precise refinement of the density moments.
-The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) can be used to constrain $K_{22}$ and $K_{20}$, while the phase is set by the asteroid dynamics near perigee and therefore constrains the higher-order terms.
-
-\subsection{Dependence of parameter uncertainty on encounter properties}
-\label{sec:fit-uncertainty}
-
-In this section, we discuss how the precision of the best-fitting density moments is affected by various encounter properties.
-We call this precision ``posterior uncertainty,'' or $\sigma(K_{\ell m})$, defining 1$\sigma$  posterior uncertainty as the range containing 68.27\% of the PPD centred on the median.
-2$\sigma$ posterior uncertainty is defined likewise for 95.45\% of the PPD.
-These are roughly equivalent to 1 or 2 times standard deviation of the PPD respectively.
-We use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-perigee}
-    \label{fig:scan-vex}
-    \label{fig:scan-theta}
-    \label{fig:scan-rho}
-    \end{figure}
-  \end{landscape}
-}
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, rotational period, observational cadence, and data gap at perigee.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-am}
-    \label{fig:scan-cadence}
-    \label{fig:scan-period}
-    \label{fig:observation-gap}
-    \end{figure}
-  \end{landscape}
-}
-
-There is no clear threshold above which posterior uncertainty is ``too high.'' However, most asteroid distributions tested in this paper have $K_{3 m} \lesssim 0.01$.
-We therefore call $\sigma(K_{3 m}) \approx 0.01$ the ``posterior uncertainty threshold,'' beyond which $K_{3 m}$ are unresolved.
-This should be understood as a rule of thumb, not a precise statement.
-
-\subsubsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
-We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ posterior uncertainties are displayed in figure \ref{fig:scan-vex}.
-
-Figure \ref{fig:scan-vex} demonstrates that posterior uncertainty follows a slight trend for uncertainty to increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) This explains why the oscillations have the same period for all parameters.
-Note that these oscillations are sometimes large enough to raise $\sigma(K_{3m}) > 0.01$, shown by the red vertical line.
-
-The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p \approx 6$ or 7 Earth radii, $\sigma(K_{30})$ reaches the 0.01 threshold.
-At slightly higher $r_p$, $K_{31}$ and $K_{32}$ become similarly unresolved, and at $r_p \approx 20$ Earth radii, $K_{33}$, the last second-order component, becomes unresolved.
-Even before this, at $r_p \approx 10$ Earth radii, the most uncertain parameter $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
-The exact location of these limits will change if different encounter properties are used.
-
-%Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
-These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
-The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
-These slope values express how much each parameter is dependent on $r_p$.
-It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
-The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
-
-% \begin{table}
-%   \centering
-%   \begin{tabular}{l|c}
-%     \hline
-%     Parameter & $\alpha$ \\ \hline
-%     $\gamma_0$ & $2.05$ \\
-%     $K_{22}$ & $5.47$ \\
-%     $K_{20}$ & $5.47$ \\ \hline
-%     $\Re K_{33}$ & $3.35$ \\
-%     $\Im K_{33}$ & $3.37$ \\
-%     $\Re K_{32}$ & $3.05$ \\
-%     $\Im K_{32}$ & $3.27$ \\
-%     $\Re K_{31}$ & $3.53$ \\
-%     $\Im K_{31}$ & $4.02$ \\
-%     $K_{30}$ & $5.75$ \\ \hline
-%   \end{tabular}
-%   \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
-%   \label{tab:scan-perigee-alpha}
-% \end{table}
-
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend and will be seen in the following sections as well.
-
-The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters (5-20 Earth radii).
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
-The first-order moments can still be extracted at much larger perigee distances in our model.
-
-\subsubsection{Observational uncertainty}
-\label{sec:scan-uncertainty}
-Two parameters, $\sigma_\theta$ and $\sigma_\rho$, govern the observational uncertainty of the data set.
-These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
-Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
-This dependence is displayed in figure \ref{fig:scan-theta}.
-
-For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
-The $K_{30}$ parameter reaches the $\sigma(K_{30})\approx 0.01$ threshold at $\sigma_\theta = 0.032\ \text{radians} \approx 2^\circ$, whereas the other parameters reach the threshold between $8^\circ$ and $45^\circ$.
-The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
-
-If $\sigma_\rho$ is allowed to vary, then $K_{30}$ reaches the threshold at $\sigma_\rho \approx \num{2.8e-7}$, and the other parameters reach the threshold at $\sigma_\rho \approx 1.2-\num{8.6e-6}$.
-These correspond to uncertainty in period of roughly milliseconds to seconds.
-At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
-Otherwise, posterior uncertainty is proportional to $\sigma_\rho$.
-
-These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
-To precisely measure density moments, very accurate rotational period estimates would have to be made every cadence.
-However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
-If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
-
-\subsubsection{Asteroid shape}
-\label{sec:scan-shape}
-
-THe true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
-Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
-These $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
-
-In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ to remove the $a_\mathcal{A}$ dependence of equation \ref{eqn:ellipsoid-axes}.
-The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The system then has no dependence on $\gamma_0$ when $K_{22}=0$.
-This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
-
-\begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-3-sigma.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-b-sigma.pdf}
-
-  \caption{1$\sigma$ posterior uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
-  \label{fig:scan-space-sigma}
-\end{figure*}
-
-To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
-For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
-This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
-
-Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
-
-Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters.
-They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
-This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
-They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
-The latter is expected due to the $1/c$ dependence.
-
-\begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}
-
-  \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).}
-  \label{fig:scan-space-corr}
-\end{figure*}
-
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation.
-It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
-The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
-
-On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
-As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the moment of inertia (equation \ref{eqn:moi}).
-The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
-At $a_\mathcal{A} \lesssim 700$ m, $K_{30}$ becomes unresolved.
-The other parameters become unresolved for $a_\mathcal{A} \lesssim 300$ m, with the cut-off for $K_{33}$ being less than 100 meters.
-This $a_\mathcal{A}$ cut-off is quite sharp; figure \ref{fig:scan-am} shows steep decrease in $\sigma(a_\mathcal{A})$ for low $a_\mathcal{A}$, with an approximate functional form of $\sigma(a_\mathcal{A}) \sim e^{(a_\mathcal{A}/C)^p}$ for a scaling constant $C$ and some power $p < 0.1$.
-This sharpness indicates that the cut-off value of $a_\mathcal{A}$ is unlikely to change significantly if other parameters of the flyby are altered in a way that slightly increases or decreases $\sigma(K_{\ell m})$.
-It therefore appears that extracting precise $K_{30}$ from asteroids with $a_\mathcal{A} \lesssim 700$ m is unlikely with this analysis, and for $a_\mathcal{A} \lesssim 50$ m, all $K_{3m}$ will likely be unresolved.
-
-For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius.
-In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
-
-\subsubsection{Cadence}
-\label{sec:scan-cadence}
-
-The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
-We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-We name this rough cadence limit $T_\text{cad}$.
-
-We expect $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the time spent near perigee $T_p$.
-The latter can be estimated by
-\begin{equation}
-  T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
-  \label{eqn:tp}
-\end{equation}
-which is the ratio of the perigee radius to velocity at perigee.
-The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
-For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
-
-%We further study the effect of $P_\omega$ and $T_p$ on $T_\text{cad}$ in appendix \ref{app:cadence-tests}, and find that both affect $T_\text{cad}$ by roughly the same amount.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
-
-\subsubsection{Perigee gap}
-\label{sec:scan-gap}
-In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
-The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
-Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-There, the angular velocity evolution is dominated by torque-free precession dictated by the moment of inertia components.
-That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
-However, $K_{3m}$ does not affect the precession periods (though they do affect the phase).
-We are therefore curious as to how our posterior uncertainties change due to lack of perigee data.
-
-To test this, we mask the perigee of the counter by removing a duration $T$ of data centred on the perigee, where $T$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T$, we always cut 3 hr$-T$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T$ has the same size.
-We then fit the same asteroid model to the cut data for all $T$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
-
-Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T$, which is seen in figure \ref{fig:observation-gap}.
-We also see that the first-order parameters are not as sensitive to $T$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
-
-Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-On the other hand, none of the uncertainties increase noticeably for $T \lesssim 1$ hr.
-Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
-
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T$.
-This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
-
-\subsubsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:scan-spin}, we display 1$\sigma$ posterior uncertainties as a function of the direction of $\bm \Omega_0$ mapped onto the unit sphere in the inertial frame.
-Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
-To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
-The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each map is set to one-tenth of the map's mean).
-This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/spin-pole.png}
-  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection.
-The orange star indicates the reference spin pole.
-The red contours enclose regions where $\sigma(K_{3m}) \geq 0.01$.}
-  \label{fig:scan-spin}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.png}
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.png}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
-See text for a description of how the average was computed.
-Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the south pole, or $-\unit Z$.}
-  \label{fig:scan-spin-avg}
-\end{figure*}
-
-Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
-For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
-Then $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
-
-Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
-This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern moment of inertia ratios from zero-torque precession after the encounter.
-If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.
-
-However, uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{3 m}) \approx 0.01$ threshold.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
-
-\subsubsection{Rotational period}
-\label{sec:scan-period}
-
-We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma(K_{\ell m})$.
-In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
-But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
-This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
-
-We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular, first-order torque to force the asteroid to tumble.
-However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
-This is most visible in the figure for $K_{30}$.
-The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
-
-The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega \lesssim 5$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
-The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids yield smaller uncertainty.
-
-\subsubsection{Central body oblateness}
-\label{sec:scan-oblateness}
-
-In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
-The effect of central body non-sphericity, then, is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have small effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
-
-$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
-For simplicity, we use this equatorial orbit case.
-Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
-The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
-We do not consider these extra factors.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
-  \vfill
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
-Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
-\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.}
-  \label{fig:scan-oblateness}
-\end{figure}
-
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top pane of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
-The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
-The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.06$ for $\gamma_0$, $-0.2$ for $K_{22}$, and $-0.3$ for $K_{20}$.
-The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
-
-Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the posterior uncertainty (section \ref{sec:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
-
-Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom pane of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
-The difference between the PPD means and true parameters are shown.
-Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
-Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
-For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
-
-$J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
-As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
-Extrapolating posterior uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
-Furthermore, $J_{22}$ is non-zero for this case, which likely decreases posterior uncertainty even more.
-
-This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
-Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
-However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
-
-\subsection{Comparison of Jupiter and Earth encounters}
-\label{sec:jupiter-earth}
-
-If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
-In this section, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
-
-The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
-The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in section \ref{sec:scan-orbit}, so we keep it at the reference value.
-% We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
-The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
-The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
-%Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
-We therefore do not distinguish between the two cases further.
-The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
-In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
-
-\begin{table}
-  \centering
-  \begin{tabular}{c|cc}
-    \hline 
-    $K_{\ell m}$ & $\sigma(K_{\ell m})_\text{Jupiter}/\sigma(K_{\ell m})_\text{Earth}$\\ \hline 
-    $\gamma_0$ & 1.6 \\
-    $K_{22}$ & 2.3 \\
-    $K_{20}$ & 11 \\
-    $\Re K_{33}$ & 18 \\
-    $\Im K_{33}$ & 18 \\
-    $\Re K_{32}$ & 18 \\
-    $\Im K_{32}$ & 18 \\
-    $\Re K_{31}$ & 25 \\
-    $\Im K_{31}$ & 10 \\
-    $K_{30}$ & 53 \\ \hline
-  \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.}
-  \label{tab:jupiter-uncertainty}
-\end{table}
-
-These uncertainty ratios can be understood as follows.
-The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
-If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
-Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
-
-The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
-Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
-
-The $K_{\ell 0}$ components differ in that the posterior uncertainty increase for a Jupiter encounter over an Earth encounter is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
-In fact, $K_{30}$ essentially fills the prior.
-In section \ref{sec:scan-spin}, we noted that $K_{\ell 0}$ is particularly uncertain when the asteroid does not tumble after the perigee.
-In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
-
-There are additional effects of central body mass which are not captured in this analysis.
-For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
-The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perijove distance is
-\begin{equation}
-  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
-\end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower perijove.
-Other effects, such as a change in the physical properties of the encountering asteroids or decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
-Which of these contradicting effects dominates is not immediately clear, and depends on the asteroid population near Jupiter and the observation method.
-
-\subsection{Comparisons between density distribution models}
-\label{sec:density-compare}
-
-To test the properties of the three density models defined in section \ref{sec:specific-density} to extract density distributions from density moments, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
-In all cases, the density moments are extracted via our fit process.
-Below, we compare the resulting distributions to understand the performance of the density distribution models.
-
-\subsubsection{Uniform density asteroids}
-
-We simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
-This was already done in section \ref{sec:asym-density} for the asymmetric reference asteroid.
-Here, we perform the same process for a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), the symmetric reference asteroid, and a tetrahedron.
-We use these shapes as examples of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron) and to demonstrate the density models' efficacy on very different shapes.
-The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The asteroid shapes are, from top to bottom, a dumbbell, the symmetric reference asteroid, and a tetrahedron.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:uniform-density}
-\end{figure*}
-
-From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
-Consequentially, $\Delta K_{\ell m}$ is low for the harmonic model.
-Also like section \ref{sec:asym-density}, the dumbbell asteroid produces largely uniform distributions except in a few small regions, and the lumpy model generates clearly incorrect results indicating that no lump is present.
-
-The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
-In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
-This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy in $\gamma_0$ and inflated uncertainty in the density moments.
-In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the small and ill-constrained $K_{3m}$ components.
-To avoid negative density distributions, the likelihood model could be adjusted to use, for example, a multivariate log-normal distribution.
-However, the model would no longer be linear.
-
-Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is very consistent with uniform at most points for the (asymmetric) dumbbell model (within $\sim 1\sigma$), while the symmetric reference and tetrahedral asteroids were generally within $\sim 2 \sigma$ of uniform.
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
-
-If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
-However, doing so ignores the observational insight we gain from our fits to $K_{3m}$, so it is only valid when $K_{3m}$ are too poorly constrained to be used.
-
-\subsubsection{Spherical asteroids}
-\label{sec:spherical-density}
-In this section, we test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by assuming a spherical shape for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/asym-sph-lumpy.pdf}
-
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.33\textwidth]{figs/sym-sph-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The original asteroid shapes were the reference asymmetric (\textit{top}) and symmetric (\textit{bottom}) ellipsoids.
-In both cases, the density distributions have been extracted assuming a spherical shape.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:sphere-density}
-\end{figure*}
-
-Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}$ is low, and they produce similar distributions as in the previous section.
-However, now even the asymmetric asteroid (with low uncertainty in $K_{\ell m}$) produces negative densities.
-This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
-In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top and bottom of the figure).
-The density is large at large $|y|$ (front right and back left in the figure).
-Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density-results} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
-In other words, the shape can be corrected by extending it where density is large and retracting it where density is low.
-
-A similar statement is true for the symmetric ellipsoid case in that density is low near the poles, but this time the regions with large density are evenly distributed around the equator, indicating the symmetry of the original asteroid.
-
-The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
-The error in density moments $\Delta K_{\ell m}$ is therefore very large, equal to the sum of $|K_{\ell m}|^2$ for the original asteroids, making it clearly a poor model.
-
-\subsubsection{Nonuniform asteroids}
-\label{sec:non-uniform-density}
-
-We also test several non-uniform density asteroids and compare the generated density distributions for all three models to see if the non-uniformities are recovered.
-We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated around the edges.
-(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_\mathcal{A}^2}$).
-To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
-The extracted density distributions are shown in figure \ref{fig:non-uniform-density}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/in-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/in-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/in-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/out-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/out-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/out-lumpy.pdf}\
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for non-uniform-density asteroids with mass concentrated in the middle (\textit{top}) and the edges (\textit{bottom}).
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:non-uniform-density}
-\end{figure*}
-
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\Delta K_{\ell m}$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
-Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
-The difference of the model output from the true distribution is generally less than $2\sigma$, but can rise to $3\sigma$ in some regions.
-
-Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\Delta K_{\ell m}$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
-This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
-
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ when the density moments are redundant with the asteroid shape; specifically, when (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
-(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
-The lump radius will then be set to zero because the fitted density moments are already matched.
-This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
-The lump model will therefore fail to recognize the lump in the true density distribution.
-
-An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape rather than a distribution that conforms to the asteroid shape.
-
-\subsubsection{Lumpy asteroids}
-
-Finally, we test an asteroid with a discrete change in density distribution (for example, a rock of high density), of the kind that the lumpy model is designed to detect.
-We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
-Both the mass and the medium have uniform density.
-The distributions extracted by the three model for this asteroid are shown in figure \ref{fig:blob-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for an asteroid with an off-centre lump.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.}
-  \label{fig:blob-density}
-\end{figure*}
-
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump.
-There appears to be a slight increase in density at roughly the correct location for both models, but this is a small effect.
-Like figure \ref{fig:non-uniform-density}, we see that the harmonic and likelihood models do not agree exactly, and the failure of the harmonic model to exactly reproduce $K_{\ell m}$ suggests that the true distribution is not harmonic.
-
-The failure of these models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities in the density and cannot exactly resolve the edges of the lump.
-However, the lumpy model computes the location and density of the mass very well.
-Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
-This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
-Nevertheless, it seems that the lumpy model is capable of recreating the location of lumps (except for the caveat mentioned above when the density moment data is redundant with the asteroid shape).
-But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in the above sections.
-
-\section{Conclusions}
-
-We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the angular velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
-We then built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
-We observe the following general properties of the moments:
-\begin{enumerate}
-  \item The second-order moments $K_{3m}$ are roughly a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is proportional to the asteroid radius and $r_p$ is the perigee distance.
-For our reference asteroid, this fraction was about $10^{-5}$.
-  \item The second-order moments that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
-It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
-  \item Extracted density moments are generally more precise when the asteroid leaves the encounter tumbling.
-  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates.
-\end{enumerate}
-
-We assessed the posterior uncertainty generated by the fit process by adjusting various properties of an asteroid on an Earth encounter. The main conclusions are listed below.
-
-\begin{enumerate}
-  \item Highly precise rotational period data is required to produce precise second-order moments.
-  \item Large $a_\mathcal{A}$ is required for $K_{3m}$ resolution, though the size of $a_\mathcal{A}$ has no effect on $K_{2m}$.
-The threshold on $a_\mathcal{A}$ for the reference asteroid was $\sim$700 m for $K_{30}$ and $\sim$50 m for $K_{33}$.
-  \item A close encounter is vital for accurate second-order moment extraction, though some of the second-order moments can still be required for more distant encounters.
-  \item This model will yield inflated uncertainties if the asteroid is rotationally symmetric around its rotating spin axis. In this case, a different parametrization should be used. 
-  \item If the asteroid rotational period is too small, or if the initial angular velocity points in an inconvenient direction, the density moments will be poorly constrained.
-  \item The cadence of observation should generally be shorter than about 30 minutes for the reference asteroid case. Gaps of data can appear, even at perigee, but not for more than about an hour.
-\end{enumerate}
-
-If some of these conditions are not met, the first-order $K_{2m}$ moments may still be resolvable.
-
-Finally, we presented three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid The extracted density distributions are largely consistent with the true distributions in all cases we tested.
-Slight adjustments to $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
-Indeed, the models sometimes predict negative density (though more complicated models could be made not to).
-Errors in the shape estimate of the asteroid also distort the density distribution, but the resulting distributions provide hints as to exactly where the shape is incorrect.
-Large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
-Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.`'
-
-\section*{Acknowledgements}
-
-We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work and pointing out possible future initiatives.
-JTD also thanks the MIT UROP office for funding his work.
-This paper made substantial use of MIT Supercloud's facilities.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Data Availability}
-
-The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
-
-\bibliographystyle{mnras}
-\bibliography{asteroids.bib}
-
-\input{appendices}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bsp	% typesetting comment
-\label{lastpage}
-\end{document}

### 2022-06-22 paper/appendices.tex
Added to paper and converted to using many samples rather than an average density distribution

@@
 Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$ and the same for $m<0$.
-The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by
-\begin{equation}
-  \begin{split}
-    I_x &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} - 6 K_{22} + 1}\\
-    I_y &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{K_{20} + 6 K_{22} + 1}\\
-    I_z &= \frac{2}{3}\mu_\mathcal{A} a_\mathcal{A}^2 \parens{-2K_{20} + 1}.
-  \end{split}
-  \label{eqn:moi}
-\end{equation}
+The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by equation \ref{eqn:moi}.
 Incidentally, the definition of $a_\mathcal{A}$ was chosen to satisfy equation \ref{eqn:moi}.
@@
 
+\section{Additional density distribution models}
+
+A finite element model was defined in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
+However, other models are possible.
+Here, we outline three models that can be explored to further understand the underdetermined density distribution of the asteroid: the likelihood model, the harmonic model, and the lumpy model.
+The first two produce smooth distributions, unlike the discrete transitions that occur for the finite element model across the boundaries of the elements.
+The lumpy model produces discrete distributions like the finite element model, but the locations of the elements are included as free parameters.
+
+\jtd{Describe these}
+
 \section{The cadence cut-off}

### 2022-06-22 paper/main.tex
Added to paper and converted to using many samples rather than an average density distribution

@@
 
-\section{Density distributon constraints}
+\subsection{Density distributon constraints}
 \label{sec:density-distro}
@@
 However, by making sufficient assumptions about the density distribution, we can nevertheless extract fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
+To best understand the potential density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
+To this end, we throughly outline two possible models and discuss two more in appendix \ref{app:other-models}.
 
@@
 Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is extracted.
-However, the density moments which are extracted from flyby data are known in the body-fixed frame.
+However, the density moments which are extracted from flyby data are known instead in the body-fixed frame.
 
@@
 
-\subsection{Finite element model}
+\subsubsection{Finite element model}
 
@@
 
-\subsection{Lumpy model}
+\subsubsection{Lumpy model}
 
@@
 \label{sec:asym-density}
-Figure \ref{fig:uniform-density-results} shows the density distributions and uncertainties extracted for the asymmetric reference asteroid.
-These distributions were made given the density moment PPDs extracted above, with $a_\mathcal{A}$ fixed.
-The surface is fixed as a triaxial ellipsoid with semi-axis lengths such that the true values of $K_{\ell m}$ are consistent with uniform density (equation \ref{eqn:ellipsoid-axes}).
-
+
+Density moments of the kind described above were extracted for the asymmetric and symmetric reference asteroids.
+The finite element model was then used to extract density distributions from these moments, and propagate uncertainties.
+Five degrees of freedom were used rather than the maximum possible number of nine, and 20 different finite element layouts were used to generate sample density distributions to avoid dependence on the manually-chosen layout.
+The resulting density distributions and uncertainties are displayed in figure \ref{fig:uniform}.
 \begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-diff-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-ell-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \caption{Based on density moments extracted from synthetic data of the uniform-density asymmetric reference asteroid encounter, the following are shown.
-From top to bottom, the density distributions extracted by the methods of section \ref{sec:density-distro}, their deviations from the true distributions, uncertainties, and the ratio of deviations to uncertainty.
-For the bottom three rows, color map range is chosen to include 95\% of the asteroid to suppress outliers.
-The models used are likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}).
-Density is normalized so that mean density is one.
-Density is consistent with uniform in all cases ($\lesssim 1 \sigma$ deviation), and typically differs from uniform by little more than 40\%.}
-  \label{fig:uniform-density-results}
+  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top}) and symmetric (\textit{bottom}) reference asteroids.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.}
+  \label{fig:uniform}
 \end{figure*}
 
-Also in each panel of figure \ref{fig:uniform-density-results} is $\chi^2_r$, or reduced chi squared value, defined as the average of the squared differences between the fitted density moments and the density moments of the final distribution divided by the fit uncertainties.
-This fit metric is non-zero due to numerical error in the likelihood model case, which is guaranteed to exactly reproduce $K_{\ell m}$.
-The harmonic and lumpy models have no such guarantee, however.
-
-The likelihood and harmonic models produce nearly identical density distributions.
-This is generally true for uniform density asteroids, which have harmonic density distributions.
-Consequentially, $\chi^2_r$ is relatively low for the harmonic model.
-This similarity lends confidence to both models, because if one were unexpectedly biased towards certain distributions, the other would have to be equally biased in the same way in this case to produce the same distribution, which appears unlikely given that the models share little in common.
-
-The distributions are non-uniform for the harmonic and likelihood models (driven by error in the estimates of $K_{3m}$), but the non-uniformity is limited.
-The second row of figures indicates that 95\% of the asteroid lies within 39\% of the true density distribution for the likelihood and harmonic models.
-The lumpy model yields a much more uniform distribution because it is designed to produce uniform lumps.
-However, it produces a density distribution less consistent with the moments extracted from spin data than the previous two models (i.e., $\chi^2_r$ is large).
-This is because the lump found extends outside the asteroid, violating the assumptions of the model, which is a sign that the lump found does not really exist inside the asteroid.
-
-The third row of figures indicates that density distribution uncertainty  can extend to 78\% of the local density, but most of the asteroid is well below this value.
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown later.
-The fourth row indicates that for 95\% of the asteroid, the density distribution is within 1$\sigma$ of the true, uniform distribution.
-Uncertainty plots are not generated for the lumpy model because the distribution is not continuous; each point in the asteroid can only take one of two density values, depending on whether it is inside the asteroid or outside it.
-
-To test the ability of our methodology to identify discrete changes in density distribution of the kind that the lumpy model is designed to detect, we show another example extraction.
-We place a spherical mass of density six times that of the surrounding medium inside the asymmetric reference asteroid, slightly displaced along $\unit y$.
-Both the mass and the medium have uniform density.
-The density moments are extracted and density distributions made via the three models and are shown in figure \ref{fig:blob-density}.
-
+The figure demonstrates that the finite element model successfully extracts a uniform density distribution.
+This property of the model was observed to be robust even for asteroids of different shapes.
+For the reference asteroid observational set-up, the uncertainty on observations is such that the density distribution is constrained to about \jtd{number}.
+The dependence of this constraint on the observational set-up is discussed in section \ref{sec:fit-uncertainty}.
+
+The lumpy model, however, fails for a uniform asteroid.
+This is because the data is consistent with a massless lump placed anywhere in the asteroid, such that the model is underdetermined even when only one lump is attempted to be extracted.
+This failure of the lumpy model can be interpreted as evidence that the true density of the asteroid is close to uniform.
+
+We also analyze asteroids of non-uniform density to assess the features our density-extraction models are most sensitive to.
+We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario.
+But we place a solid core of radius $\SI{500}{\meter}$ and density three times the surrounding density at the center of the asteroid, which changes the asteroid density moments.
+New density moments are extracted via the process described in section \ref{sec:fit} and the finite-element and lumpy models are used to extract density distributions shown in figure \ref{fig:center-core}.
 \begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/blob-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/blob-diff-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-diff-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-diff-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/blob-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-unc-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \includegraphics[width=0.3\textwidth]{figs/blob-rat-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/blob-rat-harmonic.pdf}\hfill\hspace{0.3\textwidth}
-
-  \caption{Density distributions and uncertainties for the asymmetric reference asteroid encounter with an off-center lump.
-See figure \ref{fig:uniform-density-results} for a description of each panel.}
-  \label{fig:blob-density}
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centered core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.}
+  \label{fig:center-core}
 \end{figure*}
 
-We see from figure \ref{fig:blob-density} that the harmonic and likelihood model fail to recover the presence or location of the lump, in that the top row shows a smoothly varying distribution while the second row shows that the distribution is too low by a factor of half the mean density in the region of the lump.
-In the case of the likelihood model, the density is also twice the mean just outside the lump boundary, indicating that the model has identified the general location of the lump but cannot refine its radius and resolve the lump's edge.
-Unlike the previous example, the harmonic and likelihood models do not agree exactly, and $\chi^2_r$ is large for the harmonic model.
-These two facts arise from the fact that the true distribution is not harmonic.
-
-The uncertainty plots (lower two rows) of figure \ref{fig:blob-density}  show consistency with the true distribution (within 1.2 $\sigma$ for 95\% of the asteroid), although uncertainties are larger for this non-uniform case than they were for figure \ref{fig:uniform-density-results}.
-The uncertainty rises to as much as 85\% of the local density as opposed to 78\% in the former case.
-
-The failure of the harmonic and likelihood models to find lumps is expected, since $K_{2 m}$ and $K_{3 m}$ are only sensitive to large-scale non-uniformities.
-However, the lumpy model computes the location and density of the mass very well.
-Some inaccuracies are induced by the uncertainty in $K_{3m}$, which changes the minimum of equation \ref{eqn:lump-minimize} such that the lump is displaced by 9 m along $\unit y$ from where it should be.
-This in turn causes a 70 m difference between the extracted lump's radius and the true radius.
-There is therefore a 70 m-thick shell surrounding the lump produced by the lumpy model which has been inaccurately estimated, but this shell contains less than 5\% of the asteroid.
-The scale of figure \ref{fig:blob-density} shows that, for the rest of the asteroid, the density is estimated accurately to about two parts in one thousand.
-This model produces a $\chi^2_r$ lower than the harmonic model, indicative of its accuracy.
-
-It seems that the lumpy model is capable of recreating the location of lumps.
-But the ability of the lumpy model to place a lump does not guarantee the lump to exist, as was seen in figure \ref{fig:uniform-density-results}.
+Figure \ref{fig:center-core} demonstrates disagreement between the models caused by their different assumptions.
+The finite element model produces a density distribution with a more massive center, but the density of the core has been spread throughout the asteroid such that the density at the center is much less than three times the surrounding density.
+However, the lumpy model is designed to detect discrete changes in density distribution, and identifies the boundary of the core very accurately.
+The same density moments can be achieved via a smoothed density distribution, similar to the one produced by the finite element model.
+Therefore, neither model is more correct in the general case, but they can be used to explore different scenarios.
 
@@
 
-% \subsection{Spin evolution}
-% \label{sec:spin-evolution}
-% In figure \ref{fig:example-data}, we present example spin data generated via our simulation.
-A population of one thousand asteroids with identical initial conditions except for $\gamma_0$, $K_{20}$, and $K_{22}$ were simulated on a close Earth encounter.
-The exact parameters used were the symmetric and asymmetric cases described in appendix \ref{app:reference-configs}.
-Bands containing 68.3\%, 95.5\%, and 99.7\% of the population's spin are shown, as is the spin of the reference asteroids in black.
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=\linewidth]{figs/nominal-data-sym.pdf}
-%   \includegraphics[width=\linewidth]{figs/nominal-data-asym.pdf}
-%   \caption{Angular velocity data simulated for the symmetric (above) and asymmetric (below) reference asteroids.
-The true angular velocity evolution is shown as a black line.
-Also plotted is the deviation of the data for PPD-distributed perturbations to the asteroid shape (bands).
-Bands contain 68.3\%, 95.5\%, and 99.7\% of the 1000 simulations run.
-The spread of the bands after perigee indicates that angular velocity data is perturbed by tidal interactions at perigee, in a manner sensitive to the density distribution of the asteroid.}
-%   \label{fig:example-data}
-% \end{figure}
-
-% The initial values of $\gamma_0$, $K_{20}$, and $K_{22}$ were distributed proportional to the PPDs extracted via the MCMC fit shown in section \ref{sec:example-fit}.
-The PPDs were widened by a factor of 1000 to make the band widths visible.
-Therefore, the scale of the bands in figure \ref{fig:example-data} have little meaning in an absolute sense, but they are meaningful when comparing two bands or two times in the same band.
-
-% The figure illustrates the sensitivity of spin data to asteroid density moments and $\gamma_0$; Before perigee, all asteroids had similar angular velocities, but after perigee the angular velocities of the population diverged.
-The spin data at perigee is informative and shows non-trivial behaviour.
-After perigee, the asteroid population tumbles according to torque-free precession with different oscillation periods.
-This dramatically increases the spread of angular velocities within the distribution and allows for more precise refinement of the density moments.
-The oscillation periods observable during the torque-free precession phase of the spin data (about 5 hours after perigee) can be used to constrain $K_{22}$ and $K_{20}$, while the phase is set by the asteroid dynamics near perigee and therefore constrains the higher-order terms.
-
-\subsection{Dependence of parameter uncertainty on encounter properties}
+In this section, we discuss the sensitivity of our results to the properties of the asteroid encounter system.
+We start with the encounter properties that are required to adequately constrain the asteroid's density moments and distribution, and further discuss the properties of Jupiter encounters compared to Earth encounters.
+Finally, we discuss in greater detail which features of an asteroid density distribution can be extracted by our models and which cannot be.
+
+\subsection{Dependence of uncertainty on encounter properties}
 \label{sec:fit-uncertainty}
@@
 
-To test the properties of the three density models defined in section \ref{sec:density-distro} to extract density distributions from density moments, we simulate several asteroids with different shapes and density distributions on a close Earth encounter with the reference asteroid orbital and observational parameters.
-In all cases, the density moments are extracted via our fit process.
-Below, we compare the resulting distributions to understand the performance of the density distribution models.
-
-% \subsubsection{Uniform density asteroids}
-
-% We simulate several asteroids with uniform density distributions and ask whether a uniform distribution is recovered.
-This was already done in section \ref{sec:asym-density} for the asymmetric reference asteroid.
-Here, we perform the same process for a ``dumbbell'' (two spheres of equal radius conjoined such that the surface of one intersects the centre of the other), the symmetric reference asteroid, and a tetrahedron.
-We use these shapes as examples of potential shape types (i.e., a contact binary for the dumbbell, a polyhedron for the tetrahedron) and to demonstrate the density models' efficacy on very different shapes.
-The extracted distributions for all three models are shown in figure \ref{fig:uniform-density}.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.3\textwidth]{figs/db-likelihood.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/db-harmonic.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/db-lumpy.pdf}
-
-%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-likelihood.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-harmonic.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/sym-ell-lumpy.pdf}
-
-%   \includegraphics[width=0.3\textwidth]{figs/tet-likelihood.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/tet-harmonic.pdf}\hfill
-%   \includegraphics[width=0.3\textwidth]{figs/tet-lumpy.pdf}
-%   \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asteroid.
-The asteroid shapes are, from top to bottom, a dumbbell, the symmetric reference asteroid, and a tetrahedron.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.
-The likelihood and harmonic models generally recover accurate density distributions for asymmetric, uniform density asteroids, though symmetric asteroids yield much worse precision.}
-%   \label{fig:uniform-density}
-% \end{figure*}
-
-% From figure \ref{fig:uniform-density}, it can be seen that the likelihood and harmonic models produce mostly the same density distributions like in the case of section \ref{sec:asym-density}.
-Consequentially, $\Delta K_{\ell m}^2$ is low for the harmonic model.
-Also like section \ref{sec:asym-density}, the dumbbell asteroid produces largely uniform distributions except in a few small regions, and the lumpy model generates clearly incorrect results indicating that no lump is present.
-
-% The symmetric and tetrahedral asteroids are less-well represented by the density distribution model results.
-In both cases, the likelihood and harmonic models produce sometimes-negative distributions, and non-uniformity is especially large in the tetrahedral case.
-This is not the fault of the density models, but rather because both of these asteroids have $K_{22} = 0$ and (as discussed in section \ref{sec:scan-shape}), this leads to degeneracy in $\gamma_0$ and inflated uncertainty in the density moments.
-In the tetrahedral case, the problem is worsened because $K_{20}=0$ as well, so that torque is dominated by the small and ill-constrained $K_{3m}$ components.
-To avoid negative density distributions, the likelihood model could be adjusted to use, for example, a multivariate log-normal distribution.
-However, the model would no longer be linear.
-
-% Uncertainty in each distribution was calculated but not shown.
-The size of uncertainty is such that the density distribution is very consistent with uniform at most points for the (asymmetric) dumbbell model (within $\sim 1\sigma$), while the symmetric reference and tetrahedral asteroids were generally within $\sim 2 \sigma$ of uniform.
-Uncertainty is generally larger towards the edges of the distribution, both for these shapes and for the shapes shown in the following sections.
-
-% If desired, the parameters of the models can be reduced to only fit the $K_{2m}$ density moments; this will produce exactly uniform distributions, since it is equivalent to assuming $K_{3m}=0$.
-However, doing so ignores the observational insight we gain from our fits to $K_{3m}$, so it is only valid when $K_{3m}$ are too poorly constrained to be used.
-
-\subsubsection{Spherical asteroids}
-\label{sec:spherical-density}
-In this section, we test the sensitivity of the density distributions to incorrect estimates for the shape of the asteroid by assuming a spherical shape for the asymmetric and symmetric reference asteroids, with density distributions shown in figure \ref{fig:sphere-density}.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/asym-sph-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-sph-harmonic.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-sph-lumpy.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-likelihood.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/asym-sph-unc-harmonic.pdf}\hfill
-  \hspace{0.3\textwidth}
-
-  \caption{Density distributions extracted by the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models from data generated for a uniform-density asymmetric asteroid.
-The density distributions have been extracted assuming a spherical shape.
-The extracted density distributions are shown in the top row with uncertainties in the bottom row.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.
-Density distributions show clear pathologies when the incorrect shape is used.
-}
-  \label{fig:sphere-density}
-\end{figure*}
-
-Both the likelihood and harmonic models are accurate in that $\Delta K_{\ell m}^2$ is low, and they produce similar distributions as in the previous section.
-However, now even the asymmetric asteroid (with low uncertainty in $K_{\ell m}$) produces negative densities.
-This is a signal that the shape model is incorrect, and indeed the density distribution allows us to determine exactly how the shape model is wrong.
-In the asymmetric ellipsoid case, the density distribution is small (even negative) at large $|z|$ (top and bottom of the figure).
-The density is large at large $|y|$ (front right and back left in the figure).
-Comparison with the asymmetric reference asteroid depicted in figure \ref{fig:uniform-density-results} shows that the low-density region is outside the true asteroid shape, and the high-density region is inside.
-In other words, the shape can be corrected by extending it where density is large and retracting it where density is low.
-
-A similar statement is true for the symmetric ellipsoid case in that density is low near the poles, but this time the regions with large density are evenly distributed around the equator, indicating the symmetry of the original asteroid.
-
-The lumpy model produces lumps so large that they dominate the asteroid, predicting uniform distribution with $K_{\ell m} = 0$ for $\ell \geq 1$.
-The error in density moments $\Delta K_{\ell m}^2$ is therefore very large, equal to the sum of $|K_{\ell m}|^2$ for the original asteroids, making it clearly a poor model.
-
-\subsubsection{Nonuniform asteroids}
-\label{sec:non-uniform-density}
-
-We also test several non-uniform density asteroids and compare the generated density distributions for all three models to see if the non-uniformities are recovered.
-We consider two asteroids, one with mass concentrated in the middle, and one with mass concentrated around the edges.
-(Specifically, the mass distribution follows a spherically symmetric exponential $\rho(r) \propto e^{\pm r^2/a_\mathcal{A}^2}$).
-To prevent the problems seen in previous sections when a symmetric asteroid is simulated, we set the shape of the asteroids to the asymmetric reference asteroid.
-The extracted density distributions are shown in figure \ref{fig:non-uniform-density}
-
-For these non-uniform asteroids, the likelihood and harmonic model do not coincide, as can be seen by comparing the density distributions and that $\chi_r^2$ is much larger for the harmonic distribution (indicating that the true density distribution is not harmonic).
-However, the two models give qualitatively similar results in that the centre-weighted density distribution contains more mass in the centre of the asteroid shape for both the harmonic and likelihood models while the edge-weighted asteroid contains mass at the edges.
-Though these general trends in mass placement arrived at by both the likelihood and harmonic models are accurate, the actual density distributions are inaccurate because they predict negative densities.
-The difference of the model output from the true distribution is generally less than $1-1.5\sigma$ for 95\% of the asteroid.
-However, there are regions with very large uncertainty (as much as 14 times the local density).
-This leads to deviations from the local density by factors of a much as 4.
-The locations of these high-uncertainty regions correspond to low-density, in that they occur at the edge of the edge-weighted asteroid and at the center of the center-weighted asteroid.
-
-Figure \ref{fig:non-uniform-density} shows that the lumpy model places one large lump of greater density than the surrounding medium for the centre-weighted asteroid and less density for the edge-weighted asteroid, as expected.
-Greater error is incurred in $\chi^2_r$ in this lumpy model than for the harmonic and likelihood models due to the lumpy model's crudeness, but the lump gives a good qualitative description of the density distribution of the asteroid which is useful for interpreting the other two models.
-This fact demonstrates that it can be illustrative to run the models with reduced degrees of freedom for the sake of simplicity, even if doing so yields less accurate distributions.
-
-The lumpy model has one caveat that has not yet been mentioned, which applies for $N=d=1$ when the density moments are redundant with the asteroid shape; specifically, when (1) the centre of mass of the asteroid is the centroid of the asteroid shape and (2) the density moments of the asteroid shape are proportional to the fitted density moments.
-(1) guarantees that the lump will be placed at the origin and therefore will not contribute to $K_{\ell m}$ for $\ell \geq 1$, and (2) guarantees that the mass of the asteroid shape will be chosen such that the shape density moments exactly match the fitted density moments.
-The lump radius will then be set to zero because the fitted density moments are already matched.
-This zero-radius-lump result will occur even if the true density distribution has a large-radius lump at the origin.
-The lump model will therefore fail to recognize the lump in the true density distribution.
-
-An example of this caveat applied is an elliptical lump inside an elliptical asteroid similar to the ones above.
-This is why, in the centre-weighted and edge-weighted density distributions, we specifically chose a spherically symmetric density distribution for our ellipsoidal asteroid shape rather than a distribution that conforms to the asteroid shape.
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-      \begin{subfigure}{0.49\linewidth}
-        \centering
-        \includegraphics[width=0.33\linewidth]{figs/in-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-harmonic.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-lumpy.pdf}
-
-        \includegraphics[width=0.33\linewidth]{figs/in-diff-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-diff-harmonic.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-diff-lumpy.pdf}
-
-        \includegraphics[width=0.33\linewidth]{figs/in-unc-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-unc-harmonic.pdf}\hfill
-        \hspace{0.33\linewidth}
-
-        \includegraphics[width=0.33\linewidth]{figs/in-rat-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/in-rat-harmonic.pdf}\hfill
-        \hspace{0.33\linewidth}
-      \end{subfigure}\hfill
-      \begin{subfigure}{0.49\linewidth}
-        \centering
-        \includegraphics[width=0.33\linewidth]{figs/out-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-harmonic.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-lumpy.pdf}
-
-        \includegraphics[width=0.33\linewidth]{figs/out-diff-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-diff-harmonic.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-diff-lumpy.pdf}
-
-        \includegraphics[width=0.33\linewidth]{figs/out-unc-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-unc-harmonic.pdf}\hfill
-        \hspace{0.33\linewidth}
-
-        \includegraphics[width=0.33\linewidth]{figs/out-rat-likelihood.pdf}\hfill
-        \includegraphics[width=0.33\linewidth]{figs/out-rat-harmonic.pdf}\hfill
-        \hspace{0.33\linewidth}
-      \end{subfigure}
-    \caption{Density distributions extracted for non-uniform-density asteroids with mass concentrated in the middle (\textit{left}) and the edges (\textit{right}).
-Within each half-figure, the likelihood (\textit{left}), harmonic (\textit{middle}), and lumpy with $d=N=1$ (\textit{right}) models are used.
-Density is normalized so that mean density is one.
-The same distance scale is used in all figures.
-The extracted distributions agree qualitatively with the true distributions, but are highly uncertain and can misestimate the local density by factors of almost 4.}
-    \label{fig:non-uniform-density}
-  \end{figure}
-  \end{landscape}
-}
+In section \ref{sec:asym-density}, we displayed density distributions extracted via the lumpy model with $N=1$ lumps.
+When $N=1$, the model has two degrees of freedom, meaning that the density distribution can be determined only via the fit results for $K_{2m}$, rather than the relatively poorly constrained $K_{3m}$.
+Therefore, we also explore a density distribution with $N=2$ lumps, which has seven degrees of freedom.
+
+\jtd{Continue}
 

### 2022-06-22 paper/main.tex
Ready for double-lump and new gens

@@
 
-In this section, we discuss how the precision of the best-fitting density moments is affected by various encounter properties.
-We call this precision ``posterior uncertainty,'' or $\sigma(K_{\ell m})$, defining 1$\sigma$  posterior uncertainty as the range containing 68.27\% of the PPD centred on the median.
+Density density moment uncertainty is determined by the quality of the data set, but its physical relevance is not obvious.
+Uncertainty on the density distribution is much more physically motivated, but its value depends on the choice of model used.
+We therefore investigate the dependence of both uncertainties on encounter properties in this section.
+
+For the density moments, we define their $1\sigma$ uncertainty as the range containing 68.27\% of the PPD centred on the median.
 2$\sigma$ posterior uncertainty is defined likewise for 95.45\% of the PPD.
-These are roughly equivalent to 1 or 2 times standard deviation of the PPD respectively.
-We use the configuration of the asymmetric reference asteroid (appendix \ref{app:reference-configs}) unless otherwise stated.
+For the density distribution, we produce an uncertainty map which is the standard deviation of the densities produced by 1000 samples each from five different finite element extractions with different element layouts.
+We report the average uncertainty computed over this uncertainty map.
 
-It will be useful to have a rule-of-thumb ``posterior uncertainty threshold,'' above which we say that posterior uncertainty $\sigma(K_{\ell m})$ is too large to yield meaningful estimates of density distribution.
-We define this posterior uncertainty threshold as the point at which the median of the ratio between the the local density uncertainty and local density  ($\rho_\sigma / \rho$) is equal to a fraction $f$.
-For this analysis, we investigate both $f=100\%$ (corresponding to an essentially unconstrained density distribution) and $f=20\%$.
+The encounter parameters we discuss are a mix of properties of the observational campaign (i.e., the cadence of observations, gaps in data, and uncertainty in the spin pole and period of the asteroid), and the physical properties of the asteroid (i.e., the true density moments, rotational period, perigee, excess velocity, initial spin pole direction, and length).
+As a rule-of-thumb, we say that a parameter becomes too large (or small) to allow for useful constraints on asteroid density when the uncertainty on the density $\sigma_\rho$ becomes greater than some threshold value.
+We use both threshold values of $\sigma_\rho / \rho = 20\%$ and 100\%, and the resulting limits on the various encounter properties are displayed in table \ref{tab:threshold-summary}.
 
-We use this threshold because it has clear physical meaning, unlike the density moments.
-But the value of $\rho_\sigma / \rho$ depends on the model used, unlike $\sigma(K_{\ell m})$.
-In this analysis, we use the likelihood model, but choosing a different model with constraints added would reduce density uncertainty, and lead to less restrictive thresholds.
+\jtd{Discuss conclusions}. Each of these parameters is discussed in greater detail for the rest of this section.
 
@@
 At $r_p \approx 10$ Earth radii, $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
-
-%Fitted to each of the curves in figure \ref{fig:scan-perigee} are power law uncertainties $\sigma \propto r_p^\alpha$.
-These fits were performed via the method of least squares, and all data with $\sigma > 0.7$ was removed due to its sensitivity to the arbitrarily-chosen boundary of the prior.
-The values of $\alpha$ are shown in table \ref{tab:scan-perigee-alpha}.
-These slope values express how much each parameter is dependent on $r_p$.
-It is observed that $\gamma_0$ is least dependent on $r_p$, with $\sigma(\gamma_0) \sim r_p^2$.
-The other two first-order parameters are much more strongly dependent, with $\sigma \sim r_p^{5.5}$.
-The second-order parameters have milder slopes between 3 and 4 (except for $K_{30}$) which is fortunate from the perspective of making precise observations, since lower $\alpha$ renders larger values of $r_p$ accessible to measuring $K_{3m}$.
-
-% \begin{table}
-%   \centering
-%   \begin{tabular}{l|c}
-%     \hline
-%     Parameter & $\alpha$ \\ \hline
-%     $\gamma_0$ & $2.05$ \\
-%     $K_{22}$ & $5.47$ \\
-%     $K_{20}$ & $5.47$ \\ \hline
-%     $\Re K_{33}$ & $3.35$ \\
-%     $\Im K_{33}$ & $3.37$ \\
-%     $\Re K_{32}$ & $3.05$ \\
-%     $\Im K_{32}$ & $3.27$ \\
-%     $\Re K_{31}$ & $3.53$ \\
-%     $\Im K_{31}$ & $4.02$ \\
-%     $K_{30}$ & $5.75$ \\ \hline
-%   \end{tabular}
-%   \caption{Power law slope values for the dependence of parameter uncertainty on perigee distance $r_p$. Slope is defined by $\sigma \propto r_p^\alpha$.}
-%   \label{tab:scan-perigee-alpha}
-% \end{table}
 
@@
 How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
-% \begin{equation}
-%   T_p \sim \frac{r_p}{v_\infty}\brackets{2\frac{\mu_\mathcal{B}}{r_pv_\infty^2}+1}^{-\frac{1}{2}}
-%   \label{eqn:tp}
-% \end{equation}
-% which is the ratio of the perigee radius to velocity at perigee.
-The exact choice of the formula of $T_p$ not obvious, and alternatives to equation \ref{eqn:tp} are possible.
-For the simulated asteroid, $P_\omega = 9$ hr and $T_p = 42$ min by this definition.
 
@@
 The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in section \ref{sec:scan-orbit}, so we keep it at the reference value.
-% We perform two fits, each with a different value of $v_\infty$: in one case we keep the Earth-encounter value of $v_\infty = 6$ km s$^{-1}$, and in the other case we increase the velocity such that the eccentricity (and therefore the angle between the orbits' hyperbolic asymptotes) are the same for both encounters.
-The latter requires $v_\infty = \sqrt{G\mu_\mathcal{B}/r_p (e-1)}=32$ km s$^{-1}$.
-The rationale for these excess velocity values is that, for $v_\infty = 6$ km s$^{-1}$, we keep a physically typical encounter excess velocity at the expense of changing the orbit shape, whereas for $v_\infty =32$ km s$^{-1}$ the orbit shape is unchanged, although the asteroid speed is dramatically increased.
-%Section \ref{sec:scan-orbit} found that $v_\infty$ does not affect the posterior uncertainties, and indeed we find very little difference between the two $v_\infty$ cases.
-We therefore do not distinguish between the two cases further.
 The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
@@
 
+\jtd{Possibly discuss moved core}
+
 \section{Conclusions}

### 2022-06-22 code/density/mcmc/core-scan/gen-cores.sh

@@ -8,7 +8,9 @@ source /etc/profile
 
 module load anaconda/2022a
 
-python gen-cores.py sph-3 $SLURM_ARRAY_TASK_ID
-python gen-cores.py sph-1.5 $SLURM_ARRAY_TASK_ID
-python gen-cores.py move-3 $SLURM_ARRAY_TASK_ID
-python gen-cores.py move-1.5 $SLURM_ARRAY_TASK_ID
+python gen-cores.py sym $SLURM_ARRAY_TASK_ID
+python gen-cores.py asym $SLURM_ARRAY_TASK_ID
+#python gen-cores.py sph-3 $SLURM_ARRAY_TASK_ID
+#python gen-cores.py sph-1.5 $SLURM_ARRAY_TASK_ID
+#python gen-cores.py move-3 $SLURM_ARRAY_TASK_ID
+#python gen-cores.py move-1.5 $SLURM_ARRAY_TASK_ID

### 2022-06-22 code/density/mcmc/tests/tests.py

@@ -58,6 +58,7 @@ TRUE_SHAPES = {
     "sph-1.5": TrueShape.core_sph(1.5, 500),
     "move-3": TrueShape.core_shift(3, 500, core_displacement),
     "move-1.5": TrueShape.core_shift(1.5, 500, core_displacement),
+    "double": TrueShape.two_core(3, blob_rad, core_one, 3, blob_rad, core_two),
 }
 TRUE_MOMENTS = { # Moments of the known shape
     "asym-ell": TrueMoments.ell(),
@@ -65,6 +66,7 @@ TRUE_MOMENTS = { # Moments of the known shape
     "sph-1.5": TrueMoments.ell(),
     "move-3": TrueMoments.move_3(),
     "move-1.5": TrueMoments.move_1_5(),
+    "double": TrueMoments.ell(),
 }
 INDICATORS = {
     "asym-ell": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
@@ -72,6 +74,7 @@ INDICATORS = {
     "sph-1.5": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
     "move-3": Indicator.ell_y_shift(ELLIPSOID_AM, k22a, k20a, -core_shift_high),
     "move-1.5": Indicator.ell_y_shift(ELLIPSOID_AM, k22a, k20a, -core_shift_low),
+    "double": Indicator.ell_3_shift(ELLIPSOID_AM, k22a, k20a, -core_shift_two),
 }
 SAMPLE_NAMES = {
     "asym-ell": "den-asym",
@@ -79,6 +82,7 @@ SAMPLE_NAMES = {
     "sph-1.5": "den-core-sph-1.5",
     "move-3": "den-core-move-3",
     "move-1.5": "den-core-move-1.5",
+    "double": "den-core-double",
 }
 
 

### 2022-06-23 paper/appendices.tex
Worked on paper

@@
 
-A finite element model was defined in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
-However, other models are possible.
-Here, we outline three models that can be explored to further understand the underdetermined density distribution of the asteroid: the likelihood model, the harmonic model, and the lumpy model.
-The first two produce smooth distributions, unlike the discrete transitions that occur for the finite element model across the boundaries of the elements.
-The lumpy model produces discrete distributions like the finite element model, but the locations of the elements are included as free parameters.
+Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
+Here we outline two additional models, the prior and the harmonic models, which are less conventional but still useable for extracting density distribution properties.
+Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.
+They also rely on a known surface for the asteroid.
 
-\jtd{Describe these}
+\subsection{Prior model}
+In the likelihood model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f(\rho(\bm r))$, which can be chosen manually.
+Any prior distribution can be chosen, but a Gaussian prior preferring uniform distributions is both interesting and numerically efficient.
+
+\subsection{Harmonic model}
+For the harmonic model, we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
+We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.
+
+A harmonic density distribution can be expanded in terms of the spherical harmonics as $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*$ where $C_{\ell m}$ are complex, free parameters.
+This series can be truncated at some maximum $\ell$.
+The density moments can then be explicitly computed as a function of $C_{\ell m}$:
+\begin{equation}
+  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r).
+  \label{eqn:harmonic-klm}
+\end{equation}
+\begin{equation}
+  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2.
+  \label{eqn:harmonic-ia}
+\end{equation}
+These integrals can be pre-computed given a known asteroid shape $\mathcal{A}$, so that computing $C_{\ell m}$ to match a given $K_{\ell m}$ is fast.
+Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions.
+In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is nonzero only when $\ell' = \ell$ and $m'=m$.
+Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$.
+The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics weighted by $K_{\ell m}$.
+When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to break this picture.
+
+Imposing constraints on these moments is also necessary. The asteroid mass is given by
+\begin{equation}
+  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*
+  \label{eqn:harmonic-mass}
+\end{equation}
+and these integrals can again be precomputed such that $C_{\ell m}$ can be constrained by fixing the asteroid mass.
+We impose bounds on $\rho(\bm r)$ by defining an indicator function $\mathds{1}(\bm r) = \mathds{1}(\rho(\bm r))$ which is zero when $\rho(\bm r)$ lies within the bounds and one otherwise.
+Then the integral of $\mathds{1}$ over the asteroid is
+\begin{equation}
+  \langle\mathds{1}\rangle = \int_\mathcal{A} d^3 r \mathds{1}\parens{\sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*}.
+\end{equation}
+Except where $\rho(\bm r)$ is at the edge of its bounds, $\mathds{1}(\bm r)$ is flat and therefore harmonic. We can write it as 
+\begin{equation}
+  \mathds{1}(\bm r) = \sum_{\ell m} A_{\ell m} R_{\ell m}(\bm r) + B_{\ell m} S_{\ell m}(\bm r)
+\end{equation}
+in these regions, where the complex-valued constants $A_{\ell m}$ and $B_{\ell m}$ are evaluated by the fact that
 
@@
 However, light-curve analysis is beyond the scope of this paper.
+
+\section{Uncertainty dependence on encounter properties}
+\label{app:uncertainty-dependence}
+
+In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
+
+\subsection{Orbital elements}
+\label{sec:scan-orbit}
+A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
+They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
+We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
+Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ posterior uncertainties are displayed in figure \ref{fig:scan-vex}.
+
+Figure \ref{fig:scan-vex} demonstrates that posterior uncertainty follows a slight trend for uncertainty to increase with $v_\infty$.
+This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
+There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
+(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
+The dependence of posterior uncertainty on $v_\infty$ is weak enough so that $\sigma_\rho/\rho$ never reaches 100\% for the $v_\infty$ investigated.
+
+The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
+For $r_p =7.9$ Earth radii, $\sigma_\rho/\rho$ reaches the 100\% threshold.
+The 20\% threshold is reached at lower 4.7 Earth radii.
+Much of this uncertainty is dominated by uncertainty in $K_{30}$, which is the parameter least constrained by tidal torque analysis.
+At $r_p \approx 10$ Earth radii, $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
+
+The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
+Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
+This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend and will be seen in the following sections as well.
+
+The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters.
+Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
+The first-order moments can still be extracted at much larger perigee distances in our model.
+
+\subsection{Observational uncertainty}
+\label{sec:scan-uncertainty}
+Two parameters, $\sigma_\theta$ and $\sigma_\rho$, govern the observational uncertainty of the data set.
+These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
+Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
+This dependence is displayed in figure \ref{fig:scan-theta}.
+
+For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
+The uncertainty threshold is reached at $\sigma_\theta = 2.8^\circ$ (0.5$^\circ$) for $\sigma_\rho / \rho=$100\% (20\%).
+The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
+
+If $\sigma_\rho$ is allowed to vary instead, then $K_{30}$ reaches the 100\% and 20\% thresholds at $\sigma_\rho$ which correspond to period uncertainty of several milliseconds.
+At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
+Otherwise, posterior uncertainty is proportional to $\sigma_\rho$.
+
+These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
+To precisely measure density moments, very accurate rotational period estimates would have to be made for every angular velocity data point.
+However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
+If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
+
+\subsection{Asteroid shape}
+\label{sec:scan-shape}
+
+The true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
+Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
+These $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
+
+In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
+We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$.
+The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
+The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.
+
+The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
+The system then has no dependence on $\gamma_0$ when $K_{22}=0$.
+This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
+
+To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
+For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
+This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
+
+Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
+Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
+
+Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters.
+They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
+This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
+They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
+The latter is expected due to the $1/c$ dependence.
+
+\begin{figure*}
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}
+
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}
+
+  \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
+The first order parameters $K_{22}$ and $K_{20}$ are correlated, as are initial orientation $\gamma_0$ and $K_{22}$.}
+  \label{fig:scan-space-corr}
+\end{figure*}
+
+The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
+If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated.
+This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.
+
+Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation.
+It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
+The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
+
+On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
+Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
+As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the MOI (equation \ref{eqn:moi}).
+The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
+At $a_\mathcal{A} \leq 1100$ m, $\sigma_\rho/\rho \approx 100\%$.
+However, the 20\% cut-off is much lower, at $a_\mathcal{A} \leq 180$.
+Figure \ref{fig:scan-am} demonstrates why these cut-offs are so distant; for large $a_\mathcal{A}$, uncertainty decreases slowly with length.
+Only for small lengths is the uncertainty very large.
+This behaviour indicates that the uncertainty threshold is unlikely to fall much below 180 m even if other properties of the encounter are adjusted.
+
+For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius.
+In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
+
+\subsection{Cadence}
+\label{sec:scan-cadence}
+
+The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
+We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+
+Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
+We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
+We name this rough cadence limit $T_\text{cad}$.
+$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
+
+We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
+How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
+
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
+
+\subsection{Perigee gap}
+\label{sec:scan-gap}
+In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
+The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
+Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
+There, the angular velocity evolution is dominated by torque-free precession dictated by the MOI components.
+That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
+However, $K_{3m}$ does not affect the precession periods (though they do affect the phase).
+We are therefore curious as to how our posterior uncertainties change due to lack of perigee data.
+
+To test this, we mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
+To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T_\text{gap}$, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
+We then fit the same asteroid model to the cut data for all $T_\text{gap}$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
+
+Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T_\text{gap}$, which is seen in figure \ref{fig:observation-gap}.
+We also see that the first-order parameters are not as sensitive to $T_\text{gap}$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
+
+Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
+On the other hand, none of the uncertainties increase noticeably for $T \lesssim 1$ hr.
+Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
+
+Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T_\text{gap}$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T_\text{gap}$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T_\text{gap}$.
+This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
+
+\subsection{Initial spin pole}
+\label{sec:scan-spin}
+
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+
+In figure \ref{fig:scan-spin}, we display 1$\sigma$ posterior uncertainties as a function of the direction of $\bm \Omega_0$ mapped onto the unit sphere in the inertial frame.
+Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
+To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
+The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each map is set to one-tenth of the map's mean).
+This average map is presented in two different projections to allow data at $\unit Z$ to be read.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.png}
+  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.png}
+  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
+See text for a description of how the average was computed.
+Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
+The polar projection is centred at the north pole, or $\unit Z$.
+Posterior uncertainty is large near $\pm \unit Z$ and $\pm \unit Y$, but roughly constant elsewhere.}
+  \label{fig:scan-spin-avg}
+\end{figure*}
+
+Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
+For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
+We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
+Then $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
+
+Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
+This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
+Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern MOI ratios from zero-torque precession after the encounter.
+If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.
+
+However, uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
+Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{3 m}) \approx 0.01$ threshold.
+The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
+
+\subsection{Rotational period}
+\label{sec:scan-period}
+
+We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma(K_{\ell m})$.
+In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$ for a range of periods typical of NEOs.
+Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
+But a large-scale trend is also visible in many parameters.
+$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
+This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
+
+We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular, first-order torque to force the asteroid to tumble.
+However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
+
+Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
+This is most visible in the figure for $K_{30}$.
+The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
+We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
+
+The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega < 4.3$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
+The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
+It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids yield smaller uncertainty.
+
+\subsection{Central body oblateness}
+\label{sec:scan-oblateness}
+
+In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
+By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
+The effect of central body non-sphericity, then, is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
+We expect these parameters to have small effect on the asteroid.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
+
+$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
+However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
+For simplicity, we use this equatorial orbit case.
+Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
+The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
+We do not consider these extra factors.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
+  \vfill
+  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
+Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
+\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies.
+Posterior uncertainty depends little on oblateness, but the best-fitting parameter estimates are affected enough by oblateness that oblateness must still be modelled.}
+  \label{fig:scan-oblateness}
+\end{figure}
+
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
+The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
+The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.06$ for $\gamma_0$, $-0.2$ for $K_{22}$, and $-0.3$ for $K_{20}$.
+The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
+
+Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
+These two parameters also affect the posterior uncertainty (section \ref{sec:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
+
+Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
+However, the bottom panel of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
+The difference between the PPD means and true parameters are shown.
+Posterior uncertainties are also shown as bands.
+The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
+Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
+For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
+
+$J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
+As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
+Extrapolating posterior uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
+Furthermore, $J_{22}$ is non-zero for this case, which likely decreases posterior uncertainty even more.
+
+This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
+Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
+However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.

### 2022-06-23 paper/main.tex
Worked on paper

@@
 
-When the $K_{3m}$ are extracted, 16 moments are known.
-However, $K_{00}$ of these is redundant with the mass of the asteroid, which must be fixed since density cannot be determined absolutely.
-It is convenient to set the asteroid mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
+When the $K_{3m}$ are extracted, 15 moments are known (excluding $K_{00}$).
+Since the asteroid mass cannot be determiend by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
 Three more moments are redundant with the center of mass, such that only twelve finite elements are free.
 In cases where $\gamma_0$ is known very accurately such that the correction imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable not to impose this equation on $K_{2m}$.
-In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom.
+In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom (DOF).
+Since $\gamma_0$ is precisely known for all cases studied in this paper, we will always study this case.
 We also place additional constraints that $0.25 < \rho < 3$ to ensure realistic densities.
@@
 \end{figure}
-The figure demonstrates that model accuracy is not a significant effect until the number of degrees of freedom is $\lesssim 3$, at which point $\Delta_\rho / \sigma_\rho$ rises greatly.
-Uncertainty, however, is lower for 7 or 5 degrees of freedom than it is for 9.
-To balance accuracy and precision, we choose to use this lumpy model with 5 degrees of freedom henceforth, meaning we choose $N=12$ finite elements (using the $K_{21} = \Im K_{21} = 0$ constraint).
+The figure demonstrates that model accuracy is not a significant effect until the number of DOF is $\lesssim 3$, at which point $\Delta_\rho / \sigma_\rho$ rises greatly.
+Uncertainty, however, is lower for 7 or 5 DOF than it is for 9.
+To balance accuracy and precision, we choose to use this lumpy model with 5 DOF henceforth, meaning we choose $N=12$ finite elements (using the $K_{21} = \Im K_{21} = 0$ constraint).
 
@@
 Additional rotational symmetries also constrain $K$, with the most extreme case being that spherical lumps have $K_{\ell m} = 0$ for $\ell > 0$.
-However, $K_{00}=1$ is guaranteed by definition, meaning that each spherical lump has only five degrees of freedom ($a_i$, $\mu_i$, and $\bm r_i$).
+However, $K_{00}=1$ is guaranteed by definition, meaning that each spherical lump has only five DOF ($a_i$, $\mu_i$, and $\bm r_i$).
 The substrate has one degree of freedom, since only $\mu_0$ is unknown.
-Thus, this lumpy model has $5N - 3$ total degrees of freedom.
+Thus, this lumpy model has $5N - 3$ total DOF.
 
@@
 The finite element model was then used to extract density distributions from these moments, and propagate uncertainties.
-Five degrees of freedom were used rather than the maximum possible number of nine, and 20 different finite element layouts were used to generate sample density distributions to avoid dependence on the manually-chosen layout.
+Five DOF were used rather than the maximum possible number of nine, and 20 different finite element layouts were used to generate sample density distributions to avoid dependence on the manually-chosen layout.
 The resulting density distributions and uncertainties are displayed in figure \ref{fig:uniform}.
@@
 
-\jtd{Discuss conclusions}. Each of these parameters is discussed in greater detail for the rest of this section.
-
 \begin{table}
@@
 
-\subsubsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
-We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ posterior uncertainties are displayed in figure \ref{fig:scan-vex}.
+\jtd{Discuss conclusions}.
 
-Figure \ref{fig:scan-vex} demonstrates that posterior uncertainty follows a slight trend for uncertainty to increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
-The dependence of posterior uncertainty on $v_\infty$ is weak enough so that $\sigma_\rho/\rho$ never reaches 100\% for the $v_\infty$ investigated.
+Uncertainties on the density moments, which do not depend on models used, are displayed as a function of encounter properties in figures \ref{fig:scan-perigee} and \ref{fig:scan-am}.
+The properties corresponding to the 20\% and 100\% density uncertainty thresholds are indicated with red lines, and a dotted black line indicates the properties of the reference asteroid.
+The initial spin pole direction and the asteroid shape are also shown in figures \ref{fig:scan-spin} and \ref{fig:scan-space-sigma} respectively.
 
-The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p =7.9$ Earth radii, $\sigma_\rho/\rho$ reaches the 100\% threshold.
-The 20\% threshold is reached at lower 4.7 Earth radii.
-Much of this uncertainty is dominated by uncertainty in $K_{30}$, which is the parameter least constrained by tidal torque analysis.
-At $r_p \approx 10$ Earth radii, $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
+\jtd{Discuss conclusions}.
 
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend and will be seen in the following sections as well.
-
-The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters.
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
-The first-order moments can still be extracted at much larger perigee distances in our model.
+Additional data and analysis and description for this relationship between encounter parameters and uncertainties are given in appendix \ref{app:uncertainty-dependence}
 
@@
 
-\subsubsection{Observational uncertainty}
-\label{sec:scan-uncertainty}
-Two parameters, $\sigma_\theta$ and $\sigma_\rho$, govern the observational uncertainty of the data set.
-These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
-Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
-This dependence is displayed in figure \ref{fig:scan-theta}.
-
-For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
-The uncertainty threshold is reached at $\sigma_\theta = 2.8^\circ$ (0.5$^\circ$) for $\sigma_\rho / \rho=$100\% (20\%).
-The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
-
-If $\sigma_\rho$ is allowed to vary instead, then $K_{30}$ reaches the 100\% and 20\% thresholds at $\sigma_\rho$ which correspond to period uncertainty of several milliseconds.
-At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
-Otherwise, posterior uncertainty is proportional to $\sigma_\rho$.
-
-These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
-To precisely measure density moments, very accurate rotational period estimates would have to be made for every angular velocity data point.
-However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
-If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
-
-\subsubsection{Asteroid shape}
-\label{sec:scan-shape}
-
-The true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
-Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
-These $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
-
-In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$.
-The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
-The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.
-
-The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The system then has no dependence on $\gamma_0$ when $K_{22}=0$.
-This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
-
 \begin{figure*}
@@
 
-To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
-For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
-This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
-
-Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
-
-Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters.
-They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
-This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
-They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
-The latter is expected due to the $1/c$ dependence.
-
-\begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}
-
-  \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
-The first order parameters $K_{22}$ and $K_{20}$ are correlated, as are initial orientation $\gamma_0$ and $K_{22}$.}
-  \label{fig:scan-space-corr}
-\end{figure*}
-
-The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
-If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated.
-This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.
-
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation.
-It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
-The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
-
-On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
-As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the MOI (equation \ref{eqn:moi}).
-The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
-At $a_\mathcal{A} \leq 1100$ m, $\sigma_\rho/\rho \approx 100\%$.
-However, the 20\% cut-off is much lower, at $a_\mathcal{A} \leq 180$.
-Figure \ref{fig:scan-am} demonstrates why these cut-offs are so distant; for large $a_\mathcal{A}$, uncertainty decreases slowly with length.
-Only for small lengths is the uncertainty very large.
-This behaviour indicates that the uncertainty threshold is unlikely to fall much below 180 m even if other properties of the encounter are adjusted.
-
-For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius.
-In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
-
-\subsubsection{Cadence}
-\label{sec:scan-cadence}
-
-The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
-We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-We name this rough cadence limit $T_\text{cad}$.
-$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
-
-We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
-How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
-
-\subsubsection{Perigee gap}
-\label{sec:scan-gap}
-In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
-The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
-Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-There, the angular velocity evolution is dominated by torque-free precession dictated by the MOI components.
-That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
-However, $K_{3m}$ does not affect the precession periods (though they do affect the phase).
-We are therefore curious as to how our posterior uncertainties change due to lack of perigee data.
-
-To test this, we mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T_\text{gap}$, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
-We then fit the same asteroid model to the cut data for all $T_\text{gap}$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
-
-Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T_\text{gap}$, which is seen in figure \ref{fig:observation-gap}.
-We also see that the first-order parameters are not as sensitive to $T_\text{gap}$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
-
-Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-On the other hand, none of the uncertainties increase noticeably for $T \lesssim 1$ hr.
-Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
-
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T_\text{gap}$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T_\text{gap}$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T_\text{gap}$.
-This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
-
-\subsubsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:scan-spin}, we display 1$\sigma$ posterior uncertainties as a function of the direction of $\bm \Omega_0$ mapped onto the unit sphere in the inertial frame.
-Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
-To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
-The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each map is set to one-tenth of the map's mean).
-This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-
 \begin{figure*}
@@
 \end{figure*}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.png}
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.png}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
-See text for a description of how the average was computed.
-Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the north pole, or $\unit Z$.
-Posterior uncertainty is large near $\pm \unit Z$ and $\pm \unit Y$, but roughly constant elsewhere.}
-  \label{fig:scan-spin-avg}
-\end{figure*}
-
-Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
-For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
-Then $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
-
-Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
-This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern MOI ratios from zero-torque precession after the encounter.
-If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.
-
-However, uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{3 m}) \approx 0.01$ threshold.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
-
-\subsubsection{Rotational period}
-\label{sec:scan-period}
-
-We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma(K_{\ell m})$.
-In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
-But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
-This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
-
-We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular, first-order torque to force the asteroid to tumble.
-However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
-This is most visible in the figure for $K_{30}$.
-The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
-
-The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega < 4.3$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
-The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids yield smaller uncertainty.
-
-\subsubsection{Central body oblateness}
-\label{sec:scan-oblateness}
-
-In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
-The effect of central body non-sphericity, then, is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have small effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
-
-$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
-For simplicity, we use this equatorial orbit case.
-Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
-The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
-We do not consider these extra factors.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
-  \vfill
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
-Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
-\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.
-Posterior uncertainty depends little on oblateness, but the best-fitting parameter estimates are affected enough by oblateness that oblateness must still be modelled.}
-  \label{fig:scan-oblateness}
-\end{figure}
-
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
-The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
-The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.06$ for $\gamma_0$, $-0.2$ for $K_{22}$, and $-0.3$ for $K_{20}$.
-The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
-
-Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the posterior uncertainty (section \ref{sec:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
-
-Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom panel of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
-The difference between the PPD means and true parameters are shown.
-Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
-Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
-For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
-
-$J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
-As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
-Extrapolating posterior uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
-Furthermore, $J_{22}$ is non-zero for this case, which likely decreases posterior uncertainty even more.
-
-This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
-Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
-However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
 
@@
 
+\subsection{Finite element model DOF}
+The number of elements $N$ used for the finite element model can be freely chosen.
+As discussed in section \ref{sec:finite-element}, seven of these are fixed by various constraints on the asteroid density distribution.
+There are 16 density moments with $\ell \leq 3$, so $N=16$ with nine DOF is the largest number of parameters the model can support.
+However, maximizing the DOF adds model-induced uncertainty to our results.
+This uncertainty can be reduced by reducing $N$, but with $N < 16$, a solution perfectly matching the extracted moments is not guaranteed.
+There is therefore a trade-off between the average density uncertainty $\sigma_\rho$ and the accuracy, which can be represented as the deviation of the density distribution from the true distribution $\Delta \rho$.
+
+We investigate this trade-off by extracting five density distributions with five different finite-element layouts from moments extracted from synthetic data of the asymmetric reference asteroid.
+For each point in the asteroid, 1000 samples are drawn from each of the five density distributions.
+We use the standard deviation of the 5000 samples as the uncertainty at that point, and the mean of the samples as the density.
+We then compute $\sigma_\rho$ and $\Delta \rho$ by averaging over every point in the asteroid.
+We do this for 9 (maximal), 7, 5, 3, and 2 DOF.
+Additionally, we vary the precision $\sigma_P$ of the data set used to extract the density moments, and plot $\sigma_\rho$ and $\Delta \rho$ as a function of $\sigma_P$.
+The result is shown in figure \ref{fig:dof-scan}
+
+\begin{figure}
+  \caption{The average uncertainty $\sigma_\rho$ and deviation from the truth $\Delta \rho$ of density distributions extracted by the finite element model with varying degrees of freedom.
+5 DOF appears to optimize the trade-off between the model-induced uncertainty caused by too many DOF and the inaccuracy caused by too few.}
+  \label{fig:dof-scan}
+\end{figure}
+
+The figure demonstrates the expected behaviour that the uncertainty of the result increases with additional degrees of freedom, and its accuracy decreases.
+\jtd{Comment}.
+For these reasons, we use 5 DOF which corresponds to $N=12$ throughout this paper.
+
+Figure \ref{fig:dof-scan} also demonstrates that $\sigma_\rho$ reaches a plateau for large $\sigma_P$.
+For data this uncertain, the prior constraints that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data quality.
+\jtd{Further comment}.
+
 \subsection{Comparisons between density distribution models}
@@
 In section \ref{sec:asym-density}, we displayed density distributions extracted via the lumpy model with $N=1$ lumps.
-When $N=1$, the model has two degrees of freedom, meaning that the density distribution can be determined only via the fit results for $K_{2m}$, rather than the relatively poorly constrained $K_{3m}$.
-Therefore, we also explore a density distribution with $N=2$ lumps, which has seven degrees of freedom.
+When $N=1$, the model has two DOF, meaning that the density distribution can be determined only via the fit results for $K_{2m}$, rather than the relatively poorly constrained $K_{3m}$.
+Therefore, we also explore a density distribution with $N=2$ lumps, which has seven DOF.
 

### 2022-06-23 code/density/mcmc/core-scan/average.py

@@ -9,9 +9,9 @@ from fe import FiniteElement
 from display import make_gif, make_slices
 from core import TrueShape, Indicator
 
-RUN_NAME = "asym"
-PULL = False
-GENERATE = False
+RUN_NAME = "sym"
+PULL = True
+GENERATE = True
 
 NUM_DRAWS = 20
 NUM_CHOOSE = 1000

### 2022-06-23 paper/appendices.tex
Worked on paper

@@
 Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
-Here we outline two additional models, the prior and the harmonic models, which are less conventional but still useable for extracting density distribution properties.
+Here we outline two additional models, the nearly-uniform and the harmonic models, which are less conventional but still useable for extracting density distribution properties.
 Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.
@@
 
-\subsection{Prior model}
-In the likelihood model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f(\rho(\bm r))$, which can be chosen manually.
-Any prior distribution can be chosen, but a Gaussian prior preferring uniform distributions is both interesting and numerically efficient.
+\subsection{Nearly-uniform model}
+In this nearly-uniform model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$, which can be chosen manually.
+Any prior distribution can be chosen, but the following prior is both interesting and numerically efficient.
+
+As part of our prior, we require that the asteroid density distribution satisfy $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$.
+This constraint is desirable as it encourages nearly uniform density distributions; recall that a perfectly uniform asteroid always satisfies this constraint.
+To define the prior, we divide the asteroid into $n \gg 1$ small regions of volume $V$, each with position $\bm r_i$ and density $\rho_i = \delta_i + 1$.
+Setting the mass of the asteroid equal to its volume, the average density is 1, so $\delta_i$ is the difference between the average and local density.
+We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$ centred on zero to minimize non-uniformity, i.e.
+\begin{equation}
+  f[\rho(\bm r)] \propto \prod_i \frac{\delta_i^2}{2\sigma^2}
+\end{equation}
+where $\sigma$ is an irrelevant constant. The The density moments, MOI scale, and mass are 
+\begin{equation}
+  K_{\ell m} = \frac{V}{\mu_\mathcal{A}a_\mathcal{A}^{\ell}} \sum_i (\delta_i + 1) R_{\ell m}(\bm r_i)
+  \label{eqn:nu-klm}
+\end{equation}
+\begin{equation}
+  I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2 = V \sum_i (\delta_i + 1) r_i^2
+  \label{eqn:nu-ia}
+\end{equation}
+\begin{equation}
+  \mu_\mathcal{A} = V\sum_i (\delta_i + 1) \implies 0 = \sum_i \delta_i.
+  \label{eqn:nu-mass}
+\end{equation}
+Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$ and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations.
+Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as $\bm K = M \bm \delta + \bm C$, where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions.
+Some of the components of $\bm K$, such as $I_\mathcal{A}$, $\mu_\mathcal{A}$, and $K_{1m}$, are constraints.
+We treat the other components as parameters of the model.
+The task is then to find $\bm \delta$ that satisfies this matrix equation and minimizes $f(\bm \delta) \propto |\bm \delta|^2$.
+The Moore-Penrose inverse satisfies these properties:
+\begin{equation}
+  \bm \delta = M^+ (\bm K - \bm C); \qquad M^+ = M^\dagger(M M^\dagger)^{-1}
+  \label{eqn:nu-delta}
+\end{equation}
+where $M^\dagger$ is the adjoint of $M$.
+
+The probability distribution of $\bm K$ is given by the output of the fit described in section \ref{sec:fit}.
+The parameters of this model, $\bm K$, might differ from this distribution due to the additional constraint that the density fall in realistic values.
+This can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
 
@@
 This series can be truncated at some maximum $\ell$.
-The density moments can then be explicitly computed as a function of $C_{\ell m}$:
+The density moments, MOI scale, and mass can then be explicitly computed as a function of $C_{\ell m}$:
 \begin{equation}
-  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r).
+  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r)
   \label{eqn:harmonic-klm}
@@
 \begin{equation}
-  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2.
+  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2
   \label{eqn:harmonic-ia}
+\end{equation}
+\begin{equation}
+  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*.
+  \label{eqn:harmonic-mass}
 \end{equation}
@@
 
-Imposing constraints on these moments is also necessary. The asteroid mass is given by
-\begin{equation}
-  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*
-  \label{eqn:harmonic-mass}
-\end{equation}
-and these integrals can again be precomputed such that $C_{\ell m}$ can be constrained by fixing the asteroid mass.
-We impose bounds on $\rho(\bm r)$ by defining an indicator function $\mathds{1}(\bm r) = \mathds{1}(\rho(\bm r))$ which is zero when $\rho(\bm r)$ lies within the bounds and one otherwise.
-Then the integral of $\mathds{1}$ over the asteroid is
-\begin{equation}
-  \langle\mathds{1}\rangle = \int_\mathcal{A} d^3 r \mathds{1}\parens{\sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*}.
-\end{equation}
-Except where $\rho(\bm r)$ is at the edge of its bounds, $\mathds{1}(\bm r)$ is flat and therefore harmonic. We can write it as 
-\begin{equation}
-  \mathds{1}(\bm r) = \sum_{\ell m} A_{\ell m} R_{\ell m}(\bm r) + B_{\ell m} S_{\ell m}(\bm r)
-\end{equation}
-in these regions, where the complex-valued constants $A_{\ell m}$ and $B_{\ell m}$ are evaluated by the fact that
+Imposing constraints on these moments is also necessary.
+The choice of mass is enforced merely by enforcing equation \ref{eqn:harmonic-mass}.
+We impose bounds on $\rho(\bm r)$ by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid.
+This can be done by parametrizing the asteroid surface as a function of two variables and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
 
@@
 It appears that the increased orbit speed merely shifts $T_\text{cad}$ rather than changing its sharpness.
-
-\section{Computing asteroid shape from density moments}
-\label{app:find-surface}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.45\textwidth]{figs/high-surface.pdf}\hfill
-  \includegraphics[width=0.45\textwidth]{figs/high-likelihood.pdf}
-  \caption{\textit{Left}: the surface of a near-spherical asteroid with uniform density distribution extracted via the surface model.
-\textit{Right}: the density distribution extracted via the likelihood model for the same density moments but a spherical surface.
-The same length scale is used in both figures.
-This new shape model successfully estimates an asteroid shape which is qualitatively consistent with the distributions extracted via models from the main text.}
-  \label{fig:surface-density}
-\end{figure*}
-
-In section \ref{sec:density-distro}, we mention that the shape of the asteroid can be computed from observations of the density moments and $a_\mathcal{A}$ if a uniform density distribution is assumed.
-We did not further describe the model in the main text because it is unlike the other three models in the nature of its assumptions, and in the fact that it is non-linear.
-However, it may be a useful technique so it is mentioned here; we call it the ``surface'' model.
-A similar model was also studied in Ref.~\cite{BAXANSKY2007756}.
-
-Suppose our asteroid has constant density $\rho_0$ and known parameters $K_{\ell m}$ and $a_\mathcal{A}^2$, and that the asteroid is ``star shaped'' in that every ray originating from the centre of mass of the asteroid (the origin of the body-fixed frame) passes through the surface of the asteroid exactly once, at distance $r(\theta, \phi)$ written in spherical coordinates.
-By the divergence theorem, we write
-\begin{equation}
-  K_{\ell m} = \frac{\rho_0}{\mu_\mathcal{A} a_\mathcal{A}^\ell} \oint_{\partial \mathcal{A}} d^2 \bm r \cdot \bm v (\bm r)
-\end{equation}
-where $\bm v (\bm r) = \unit r R_{\ell m} (\bm r) r / (3+\ell) $ so that $\nabla \cdot \bm v(\bm r) = R_{\ell m}(\bm r)$.
-The integral is carried out over the surface of the asteroid.
-We know the area element satisfies $d^2 \bm r = (\partial \bm r / \partial \theta \times \partial \bm r / \partial \phi) d\theta d\phi$ in our coordinates, and when dotted with $\bm v \parallel \unit r$, this gives
-\begin{equation}
-  K_{\ell m} = \frac{\rho_0 }{\mu_\mathcal{A} a_\mathcal{A}^\ell (3 + \ell)} \int d\Omega r(\theta, \phi)^3 R_{\ell m}(r(\theta, \phi), \theta, \phi).
-  \label{eqn:surface-klm}
-\end{equation}
-where the integral is carried out over the unit sphere. Note that the integrand of each $K_{\ell m}$ is proportional to $r(\theta, \phi)^{(3+\ell)}$ times constants and a spherical harmonic.
-
-We write 
-\begin{equation}
-  r(\theta, \phi) = \sum_{\ell m} Y_{\ell m}^* C_{\ell m}
-\end{equation}
-without loss of generality.
-To keep $r(\theta, \phi) \in \mathds{R}$, we require $C_{\ell m}^* = (-1)^m C_{l,-m} (\ell-m)!/(\ell+m)$.
-With this definition, equation \ref{eqn:surface-klm} becomes a polynomial of degree $3+\ell$ in terms of $C_{\ell m}$ and integrals of products of spherical harmonics.
-These integrals can be pre-computed so that equation \ref{eqn:surface-klm} can then be numerically solved via standard polynomial solution methods to find $C_{\ell m}$.
-A similar equation to equation \ref{eqn:surface-klm} can be written for $a_\mathcal{A}$
-\begin{equation}
-  a_\mathcal{A}^2 = \frac{\rho_0}{5\mu_\mathcal{A}}\int d\Omega r(\theta, \phi)^5
-  \label{eqn:surface-am}
-\end{equation}
-which can also be solved via polynomial methods.
-
-Equations \ref{eqn:surface-klm} and \ref{eqn:surface-am} form $(\ell_\text{max} + 1)^2 + 1$ constraints, where $\ell_\text{max}$ is the maximum degree of $C_{\ell m}$.
-By setting the same maximum degree as for the known $K_{\ell m}$, the system is well-determined and will yield finitely many solutions.
-These solutions can be filtered by removing those that produce $r(\theta, \phi) < 0$ for any $\theta, \phi$, which is unphysical.
-
-To test the model, this process was run for an asteroid with $K_{1m}=K_{2m'}=0$, but randomly chosen $K_{3m}$ in the range 0.01 to -0.01.
-The resulting surface is shown in figure \ref{fig:surface-density}.
-The figure shows a near-spherical asteroid, which is expected for $K_{\ell m} = 0$ for $\ell > 0$.
-However, the additional $K_{3m}$ components clearly induce non-sphericity in the asteroid which is captured by the surface model.
-
-To give an alternate view of the non-sphericities found via this new surface model, figure \ref{fig:surface-density} also displays the density distribution extracted via the likelihood model assuming a spherical asteroid shape, but with the same density moments.
-(Uncertainty in the moments is not modelled in this figure, to better compare the two.) Where the likelihood model displays low density, the surface model clearly retracts into the asteroid.
-Where the likelihood model yields high density, the surface model extends.
-Thus, the connection made in section \ref{sec:spherical-density} between non-uniformities in extracted densities at the asteroid surface and inaccuracies in the surface shape is more firmly represented.
-
-This surface model could, in principle, be used to improve estimates of the surface of an asteroid made by light curve analysis, since it connects rotational data to the asteroid surface which reflects the light we observe.
-Thus, uncertainties either in the density moments or the asteroid surface (or both), could be reduced.
-However, light-curve analysis is beyond the scope of this paper.
 

### 2022-06-24 paper/main.tex
Worked on paper
Further changes to display

@@
     {a_\mathcal{A}^2}\mu_i}^{-1} \\
-    &\brackets{\sum_{i=0}^N \sum_{\ell' m'}\mu_i
+    &\times \brackets{\sum_{i=0}^N \sum_{\ell' m'}\mu_i
     \frac{a_i^{\ell'}}{a_\mathcal{A}^\ell}
@@
 \begin{figure*}
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-r}
+
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-r}
+
   \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top}) and symmetric (\textit{bottom}) reference asteroids.
@@
 \begin{figure*}
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centered core.
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-r}
+
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.}
@@
 
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+% \afterpage{
+%   \begin{landscape}
+%     \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
+%     \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
 The vertical dashed line indicates the reference asteroid values.
 The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-perigee}
-    \label{fig:scan-vex}
-    \label{fig:scan-theta}
-    \label{fig:scan-rho}
-    \end{figure}
-  \end{landscape}
-}
+%     \label{fig:scan-perigee}
+%     \label{fig:scan-vex}
+%     \label{fig:scan-theta}
+%     \label{fig:scan-rho}
+%     \end{figure}
+%   \end{landscape}
+% }
 
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
+% \afterpage{
+%   \begin{landscape}
+%     \begin{figure}
+%     \centering
+%     \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+%     \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
 The vertical dashed line indicates the reference asteroid values.
 The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-am}
-    \label{fig:scan-cadence}
-    \label{fig:scan-period}
-    \label{fig:observation-gap}
-    \end{figure}
-  \end{landscape}
-}
+%     \label{fig:scan-am}
+%     \label{fig:scan-cadence}
+%     \label{fig:scan-period}
+%     \label{fig:observation-gap}
+%     \end{figure}
+%   \end{landscape}
+% }
 

### 2022-06-24 code/density/display.py

@@ -1,17 +1,17 @@
 import numpy as np
 import matplotlib.pyplot as plt
 from PIL import Image
-from multiprocessing import Pool
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
 
 #plt.style.use("jcap")
 
-FONT_SIZE = 20
+FONT_SIZE = 16
 
 import matplotlib as mpl
 mpl.rcParams["font.family"] = "serif"
 mpl.rcParams["font.monospace"] = "Roboto mono"
 mpl.rcParams["text.usetex"] = "true"
-mpl.rcParams["figure.figsize"] = (6.5, 4.00)
+mpl.rcParams["figure.figsize"] = (4.25, 4)
 mpl.rcParams["legend.framealpha"] = 0.5
 mpl.rcParams["lines.linewidth"] = 2
 mpl.rcParams["lines.markersize"] = 4
@@ -23,6 +23,7 @@ NUM_SLICES = 6
 EXPAND_X=1.15 # Scale along x and y so that spheres look circular
 AXIS_LIMIT = 1000
 EPSILON = 0.00000001
+NUM_CONTOURS = 6
 
 
 def latexify(number):
@@ -89,7 +90,7 @@ def make_frame(densities, pos_array, axis_name, cmap, percentile, balance, z_ind
     return fig
 
 def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percentile=99, balance=False):
-    fig = plt.figure(figsize=(6.5,5))
+    fig = plt.figure()
     ax = fig.gca(projection='3d')
     ax.set_axis_off()
     ax.grid(False)
@@ -118,9 +119,9 @@ def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percenti
 
 
     if want_min != want_max:
-        levels = np.linspace(want_min, want_max, 10)
+        levels = np.linspace(want_min, want_max, NUM_CONTOURS + 1)
     else:
-        levels = np.linspace(0.99, 1.01, 10)
+        levels = np.linspace(0.99, 1.01, NUM_CONTOURS + 1)
 
     mins = np.min(np.where(~np.isnan(densities)), axis=1)
     maxes = np.max(np.where(~np.isnan(densities)), axis=1)
@@ -153,10 +154,20 @@ def make_slices(densities, pos_array, axis_name, cmap, name, klm_error, percenti
     ax.set_ylabel("$y$")
     ax.set_zlabel("$z$")
 
[…]

### 2022-06-24 paper/figs/get-figs.py

@@ -1,22 +1,0 @@
-import os, shutil
-
-ROOT = "/home/jtdinsmo/Dropbox (MIT)/12.420 project/"
-
-f = open(ROOT + "paper/figs/fig-sources.txt", 'r')
-for line in f.readlines():
-    if line == '':
-        continue
-    if line.startswith('#'):
-        continue
-    args = line[:-1].split(' ')
-    if len(args) != 2:
-        continue
-    name, path = args
-    if not os.path.isfile(ROOT + path):
-        print("Could not find " + path)
-        continue
-    if path[-4:] not in [".eps", ".pdf"]:
-        print("WARNING: .eps or .pdf file formats are preferred")
-    shutil.copyfile(ROOT+path, ROOT + "paper/figs/"+name)
-
-f.close()

### 2022-06-27 paper/main.tex
Added to paper

--- 2022-06-23 paper/main.tex
@@
 If $N$ is chosen lower, the choice of element layout might exclude a distribution that exactly matches $K_{\ell m}$, but uncertainties are diminished due to less redundancy in the model.
-To select our value of $N$, we extract density distributions for moments extracted from simulated flyby data of the reference asteroid.
-We assume an ellipsoidal shape consistent with uniform asteroid density and extract 5 density distributions for it using this finite element model.
-We do this for multiple values of observational precision on the rotational period of the asteroid.
-Figure \ref{fig:dof-scan} displays the resulting average uncertainty on $\rho_i$ for each of the five extractions ($\sigma_\rho / \rho$), as well as the average deviation from the truth  ($\Delta \rho / \rho$), and displays the maximum and mean significance of these deviations ($\Delta_\rho / \sigma_\rho$).
-s\begin{figure}
-  \centering
-  \caption{Uncertainty in density, deviations from the true density, and maximum and mean significance of these deviations are plotted as a function of the observational precision of the flyby data.
-Five density distributions are computed for each value of observational precision (light dots) and their average is displayed (solid dots and lines).
-Each line represents a different choice in the number of free parameters used, with nine being maximal.
-Results show that few free parameters yield precise but inaccurate results, and that more yield imprecise but accurate results.}
-  \label{fig:dof-scan}
-\end{figure}
-The figure demonstrates that model accuracy is not a significant effect until the number of DOF is $\lesssim 3$, at which point $\Delta_\rho / \sigma_\rho$ rises greatly.
-Uncertainty, however, is lower for 7 or 5 DOF than it is for 9.
-To balance accuracy and precision, we choose to use this lumpy model with 5 DOF henceforth, meaning we choose $N=12$ finite elements (using the $K_{21} = \Im K_{21} = 0$ constraint).
+An analysis of which value of $N$ is appropriate for our purposes is given in section \ref{sec:dof-scan}.
 
@@
 Thus, this lumpy model has $5N - 3$ total DOF.
+Again, the choice of $N$ affects the accuracy and uncertainty of the model results, which is discussed in section \ref{sec:density-compare}.
 
@@
 \label{sec:example-fit}
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=0.6\textwidth]{figs/example-residuals.pdf}
+  \includegraphics[width=\linewidth]{figs/example-residuals.pdf}
   \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
@@
   \label{fig:example-residuals}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure*}
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-fe-r}
+
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-fe-r}
+
   \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top}) and symmetric (\textit{bottom}) reference asteroids.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.}
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Extracted densities are generally within 10\% of the truth.}
   \label{fig:uniform}
@@
 
-The figure demonstrates that the finite element model successfully extracts a uniform density distribution.
-This property of the model was observed to be robust even for asteroids of different shapes.
-For the reference asteroid observational set-up, the uncertainty on observations is such that the density distribution is constrained to about \jtd{number}.
+The figure demonstrates that the finite element model successfully extracts density distributions consistent with the extracted density moments, as shown by the $\chi^2$ value per degree of freedom, $\chi^2_r$, depicted in the figure.
+These express the agreement of the density moments of the shown distributions with the posterior distributions for the density moments, produced by the MCMC described in section \ref{sec:fit}.
+$\chi^2_r = 0$ indicates that the moments of the shown distributions are exactly equal to the means of the moment posterior extracted by the MCMC.
+The accuracy of this model is robust for additional shapes, including non-ellipsoidal shapes.
+
+Furthermore, these density distributions are consistent with uniform, which is the true density distribution of the asteroid.
+For the reference asteroid observational set-up, the uncertainty on observations is such that the density distribution is generally within 10\% of the true density (second column) while the density uncertainty is generally less than 40-50\% of the density value at any point in the asteroid (third column).
 The dependence of this constraint on the observational set-up is discussed in section \ref{sec:fit-uncertainty}.
+In no place is the significance of these deviations from the true distribution greater than $0.3 \sigma$ (last column).
 
-The lumpy model, however, fails for a uniform asteroid.
+The lumpy model (not shown) fails for a uniform asteroid.
 This is because the data is consistent with a massless lump placed anywhere in the asteroid, such that the model is underdetermined even when only one lump is attempted to be extracted.
 This failure of the lumpy model can be interpreted as evidence that the true density of the asteroid is close to uniform.
-
-We also analyze asteroids of non-uniform density to assess the features our density-extraction models are most sensitive to.
-We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario.
-But we place a solid core of radius $\SI{500}{\meter}$ and density three times the surrounding density at the center of the asteroid, which changes the asteroid density moments.
+Therefore, we also analyze asteroids of non-uniform density.
+We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario, but we place a solid core of radius $\SI{500}{\meter}$ and density three times the surrounding density at the center of the asteroid.
+This changes the asteroid density moments.
 New density moments are extracted via the process described in section \ref{sec:fit} and the finite-element and lumpy models are used to extract density distributions shown in figure \ref{fig:center-core}.
 \begin{figure*}
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centered core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.}
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-r}
+
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+The core is successfully extracted in all cases.}
   \label{fig:center-core}
@@
 
-Figure \ref{fig:center-core} demonstrates disagreement between the models caused by their different assumptions.
-The finite element model produces a density distribution with a more massive center, but the density of the core has been spread throughout the asteroid such that the density at the center is much less than three times the surrounding density.
+Once again, figure \ref{fig:center-core} shows that the model results are successful in that they reproduce the extracted density moments ($\chi^2_r$ is low).
+However, the density distributions extracted by the finite model match the true distributions less well.
+The deviation the true density extends to as much as 35\% in some locations, leading to a maximum significance of $0.86\sigma$.
+The distributions are consistent with the true distribution, but the finite element model has distributed the core into the rest of the asteroid so that the peak density is lowered.
+
 However, the lumpy model is designed to detect discrete changes in density distribution, and identifies the boundary of the core very accurately.
-The same density moments can be achieved via a smoothed density distribution, similar to the one produced by the finite element model.
-Therefore, neither model is more correct in the general case, but they can be used to explore different scenarios.
+Deviations from the truth are less than 0.2\%, with uncertainties about 10\% of the local density at maximum and usually much lower.
+THe significance of the deviations is around 20\%, as it was in figure \ref{fig:uniform} where the extracted distribution again matched the truth.
+The low uncertainty is caused by the small number of degrees of freedom (2) of the lumpy model.
+A consequence is that if the core had been non-spherical, the lumpy model would be inaccurate, with significant deviations from the truth.
+Therefore, neither model is more correct in the general case, but each can be used to explore different scenarios.
 
@@
 \label{sec:fit-uncertainty}
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+    \label{fig:scan-perigee}
+    \label{fig:scan-vex}
+    \label{fig:scan-theta}
+    \label{fig:scan-rho}
+    \end{figure}
+  \end{landscape}
+}
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+    \label{fig:scan-am}
+    \label{fig:scan-cadence}
+    \label{fig:scan-period}
+    \label{fig:observation-gap}
+    \end{figure}
+  \end{landscape}
+}
 
@@
 Additional data and analysis and description for this relationship between encounter parameters and uncertainties are given in appendix \ref{app:uncertainty-dependence}
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-perigee}
-    \label{fig:scan-vex}
-    \label{fig:scan-theta}
-    \label{fig:scan-rho}
-    \end{figure}
-  \end{landscape}
-}
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-am}
-    \label{fig:scan-cadence}
-    \label{fig:scan-period}
-    \label{fig:observation-gap}
-    \end{figure}
-  \end{landscape}
-}
 
@@
 \subsection{Finite element model DOF}
+\label{sec:dof-scan}
 The number of elements $N$ used for the finite element model can be freely chosen.
@@
 For each point in the asteroid, 1000 samples are drawn from each of the five density distributions.
-We use the standard deviation of the 5000 samples as the uncertainty at that point, and the mean of the samples as the density.
-We then compute $\sigma_\rho$ and $\Delta \rho$ by averaging over every point in the asteroid.
+We use the standard deviation of the 5000 samples as the uncertainty $\sigma_\rho$ at that point, and the mean of the samples as the density $\rho$.
+Modelling the asteroid as having a uniform true density, we compute the deviation of the density from the truth $\Delta \rho$ over the asteroid.
 We do this for 9 (maximal), 7, 5, 3, and 2 DOF.
 Additionally, we vary the precision $\sigma_P$ of the data set used to extract the density moments, and plot $\sigma_\rho$ and $\Delta \rho$ as a function of $\sigma_P$.
-The result is shown in figure \ref{fig:dof-scan}
+Figure \ref{fig:dof-scan} displays the distribution of $\sigma_\rho$, $\Delta \rho$, and the significance of the deviations from the truth ($\Delta \rho / \sigma_\rho$) over the asteroid.
 
 \begin{figure}
+  \includegraphics[width=\linewidth]{figs/dof-scan.pdf}
   \caption{The average uncertainty $\sigma_\rho$ and deviation from the truth $\Delta \rho$ of density distributions extracted by the finite element model with varying degrees of freedom.
@@
 
-The figure demonstrates the expected behaviour that the uncertainty of the result increases with additional degrees of freedom, and its accuracy decreases.
-\jtd{Comment}.
-For these reasons, we use 5 DOF which corresponds to $N=12$ throughout this paper.
+The figure demonstrates the expected behaviour that few degrees of freedom results in low uncertainty but large $\Delta \rho / \sigma$, wile many degrees of freedom is more accurate but also more uncertain.
+The trend of uncertainty, deviation, and significance as a function of $\sigma_P$ is also discontinuous for few DOF, because in these cases the properties of the output distribution are strongly dependent on the initial choice of uncertainty of the initial choice of grids, and more than five grids are necessary to remove that dependence.
+This discontinuity is most noticeable for 3 and 2 DOFs, which also produce deviations from the true density distribution of the highest significance.
+We use 5 DOFs throughout this paper, produce the most precise results while still accurately reproducing the asteroid density distribution.
+5 DOFs corresponds to $N=12$ finite elements.
 
-Figure \ref{fig:dof-scan} also demonstrates that $\sigma_\rho$ reaches a plateau for large $\sigma_P$.
-For data this uncertain, the prior constraints that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data quality.
-\jtd{Further comment}.
+The top panel of \ref{fig:dof-scan} also demonstrates that $\sigma_\rho$ reaches a plateau for large $\sigma_P$.
+In that regime, the prior constraints that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data quality.
+This is a further example of how the extracted asteroid density distribution is strongly dependent on the choice of model, and one of the reasons why we display the uncertainties of density moments in section \ref{sec:fit-uncertainty} rather than density distribution uncertainty.
+This moment uncertainty is not prone to the same model-dependent plateau.
 

### 2022-06-27 code/fit_resolved/display.py

@@ -302,7 +302,7 @@ class Display:
         mean_res = np.array(mean_res)
         uncertainties = np.array([2 * np.sqrt(np.diagonal(pinvh(a))) for a in self.true_uncs])
 
-        fig, (ax1, ax2) = plt.subplots(2, 1, gridspec_kw={'height_ratios': [3, 1]}, figsize=(12, 6), sharex=True)
+        fig, (ax1, ax2) = plt.subplots(2, 1, gridspec_kw={'height_ratios': [3, 1]}, figsize=(9, 6), sharex=True)
 
         x_display = np.arange(len(self.true_results)) * self.cadence / 3600.0
         ax1.scatter(x_display, self.true_results[:,0] * 3600, label = 'true x', alpha=0.5, color='C0', s=1)

### 2022-06-27 paper/appendices.tex
Reweighted lumpy moments

@@
 \begin{equation}
-  f[\rho(\bm r)] \propto \prod_i \frac{\delta_i^2}{2\sigma^2}
+  f[\rho(\bm r)] \propto \prod_i \exp\parens{-\frac{\delta_i^2}{2\sigma^2}} \implies \ln f[\rho(\bm r)] \simeq -\sum_i \delta_i^2
+  \label{eqn:nu-f}
 \end{equation}
-where $\sigma$ is an irrelevant constant. The The density moments, MOI scale, and mass are 
+where $\sigma$ is an irrelevant constant. The density moments, MOI scale, and mass are 
 \begin{equation}
@@
 We treat the other components as parameters of the model.
-The task is then to find $\bm \delta$ that satisfies this matrix equation and minimizes $f(\bm \delta) \propto |\bm \delta|^2$.
-The Moore-Penrose inverse satisfies these properties:
+The task is then to find $\bm \delta$ that satisfies this matrix equation and maximizes $f(\bm \delta)$.
+But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (and the maximum of $f$) is the minimum of $|\bm \delta|^2$.
+The value of $\bm \delta$ that obeys the constraints and minimizes its norm is given by the Moore-Penrose inverse:
 \begin{equation}

### 2022-06-28 paper/main.tex
Updated paper

@@
 The fit results are clearly consistent with the data.
+This figure is also instructing in revealing which points in the data set are most informative.
+The at-perigee data is irregular and reveals information about the density moments, and the post-perigee data shows torque-free tumbling behaviour which constrains $K_{2m}$ via the moment of inertia ratios, and also indirectly sheds light on the at-perigee data by constraining the rotational velocity the asteroid must have had when leaving the perigee.
 
@@
 
+  \includegraphics[width=0.24\linewidth]{figs/asym-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/asym-l-r}
+
   \includegraphics[width=0.24\linewidth]{figs/sym-fe-d}\hfill
@@
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top}) and symmetric (\textit{bottom}) reference asteroids.
+  \includegraphics[width=0.24\linewidth]{figs/sym-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sym-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{first and thrid row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
+The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
@@
 
-Furthermore, these density distributions are consistent with uniform, which is the true density distribution of the asteroid.
+Furthermore, the finite element density distributions are consistent with uniform, which is the true density distribution of the asteroid.
 For the reference asteroid observational set-up, the uncertainty on observations is such that the density distribution is generally within 10\% of the true density (second column) while the density uncertainty is generally less than 40-50\% of the density value at any point in the asteroid (third column).
@@
 
-The lumpy model (not shown) fails for a uniform asteroid.
-This is because the data is consistent with a massless lump placed anywhere in the asteroid, such that the model is underdetermined even when only one lump is attempted to be extracted.
-This failure of the lumpy model can be interpreted as evidence that the true density of the asteroid is close to uniform.
-Therefore, we also analyze asteroids of non-uniform density.
+The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform (the $\chi^2_r$ values are large due to numerical error and correspond to deviations in $K_{2m}$ only on the order of \jtd{number}).
+These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of \jtd{number}) due to its few degrees of freedom.
+With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius.
+Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more apt to be contained inside a lump.
+In order for the lumpy model to converge given the unconstrained lump radius, we use the mass-weighted $\mu_i a_i \rightarrow 0$ as a model parameter rather than the lump length $a_i$.
+
+We also explore model behaviour in non-uniform density asteroids.
 We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario, but we place a solid core of radius $\SI{500}{\meter}$ and density three times the surrounding density at the center of the asteroid.
@@
 
-In this section, we discuss the sensitivity of our results to the properties of the asteroid encounter system.
+% In this section, we discuss the sensitivity of our results to the properties of the asteroid encounter system.
 We start with the encounter properties that are required to adequately constrain the asteroid's density moments and distribution, and further discuss the properties of Jupiter encounters compared to Earth encounters.
@@
 
+The question of which encounters are most suited to this analysis is of great interest.
+We investigate a mix of encounter parameters, from observational parameters (e.g., the cadence of observations, gaps in data, and uncertainty in the spin pole and period of the asteroid) and physical asteroid properties (e.g., the true density moments, rotational period, perigee, excess velocity, initial spin pole direction, and length), and discuss their effect on the uncertainty of this methodology's results.
+
+Specifically, we highlight both the uncertainties on the density moments and uncertainty on density distribution.
+Moment uncertainty is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
+Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined.
+However, its physical relevance is not obvious.
+The density distribution uncertainty is presented as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
+The average uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid.
+This measure of uncertainty is more physically relevant than moment uncertainty, but it is affected by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
+
+We therefore investigate both the moment uncertainty and the density distribution uncertainty.
+Figure \ref{fig:scan-physical} displays the dependence of moment uncertainty on four asteroid physical parameters and and \ref{fig:scan-observational} displays dependence on observational parameters.
+Additionally, figures \ref{fig:scan-space-sigma} and \ref{fig:scan-spin} display dependence on asteroid shape and initial spin direction.
+These are useful as a sensitive and model-independent measure of the relationship between the encounter properties and the methodology uncertainty.
+
+In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
+These are collected by \jtd{Explain}.
+Their values are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
+These thresholds are more physically relevant, but they should be understood as moveable, since making different model choices can drastically change their locations.
+
+Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and its length.
+\jtd{Further discuss}.
+Figure \ref{fig:scan-physical} demonstrates that the asteroid length cut-off is particularly sharp, since the density moment uncertainty $\sigma_{K_{3m}}$ is very steep there.
+However, precision on the moment of inertia ratios of the asteroid $K_{2m}$ are not affected by asteroid length; these may still be collected even for small asteroids.
+
+\begin{table}
+  \centering
+  \begin{tabular}{lll} \hline
+    Encounter property & $\sigma_\rho / \rho = 100\%$ & $20\%$ \\ \hline
+    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
+    Excess velocity ($v_\infty$) & - & - \\
+    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
+    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
+    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
+    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
+    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
+    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\ 
+    \hline
+  \end{tabular}
+  \caption{The physical / observational encounter property thresholds (\textit{top} / \textit{bottom} consistent with useable density distribution uncertainty. \jtd{Summarizing sentence}.}
+  \label{tab:threshold-summary}
+\end{table}
+
+The excess velocity and rotational period of the asteroid do not drastically affect the moment uncertainty and therefore do not impose strict thresholds, except for a dramatic increase in $\sigma(K_{2m})$ visible in figure \ref{fig:scan-physical} for rotational period $P_\omega \approx 4$ hr.
+The location of this threshold is likely dependent on other dynamical time scales of the system such as the cadence of observations and possibly the orbital time scales of $v_\infty / r_p$ and $\mu_\mathcal{A} / (v_\infty^2 r_p)$.
+
+\afterpage{
+  \begin{landscape}
+    \begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+    \label{fig:scan-rho}
+    \label{fig:scan-theta}
+    \label{fig:scan-cadence}
+    \label{fig:observation-gap}
+    \label{fig:scan-observational}
+  \end{figure}
+  \end{landscape}
+}
 \afterpage{
@@
     \label{fig:scan-vex}
-    \label{fig:scan-theta}
-    \label{fig:scan-rho}
+    \label{fig:scan-am}
+    \label{fig:scan-period}
+    \label{fig:scan-physical}
   \end{figure}
@@
 }
-
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-am}
-    \label{fig:scan-cadence}
-    \label{fig:scan-period}
-    \label{fig:observation-gap}
-    \end{figure}
-  \end{landscape}
-}
-
-Density density moment uncertainty is determined by the quality of the data set, but its physical relevance is not obvious.
-Uncertainty on the density distribution is much more physically motivated, but its value depends on the choice of model used.
-We therefore investigate the dependence of both uncertainties on encounter properties in this section.
-
-For the density moments, we define their $1\sigma$ uncertainty as the range containing 68.27\% of the PPD centred on the median.
-2$\sigma$ posterior uncertainty is defined likewise for 95.45\% of the PPD.
-For the density distribution, we produce an uncertainty map which is the standard deviation of the densities produced by 1000 samples each from five different finite element extractions with different element layouts.
-We report the average uncertainty computed over this uncertainty map.
-
-The encounter parameters we discuss are a mix of properties of the observational campaign (i.e., the cadence of observations, gaps in data, and uncertainty in the spin pole and period of the asteroid), and the physical properties of the asteroid (i.e., the true density moments, rotational period, perigee, excess velocity, initial spin pole direction, and length).
-As a rule-of-thumb, we say that a parameter becomes too large (or small) to allow for useful constraints on asteroid density when the uncertainty on the density $\sigma_\rho$ becomes greater than some threshold value.
-We use both threshold values of $\sigma_\rho / \rho = 20\%$ and 100\%, and the resulting limits on the various encounter properties are displayed in table \ref{tab:threshold-summary}.
-
-\begin{table}
-  \centering
-  \begin{tabular}{lll} \hline
-    Encounter property & $\sigma_\rho / \rho = 100\%$ & $20\%$ \\ \hline
-    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
-    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
-    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
-    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
-    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
-    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\
-    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
-  \end{tabular}
-  \caption{For each encounter property discussed in section \ref{sec:discussion}, the properties that lead to density uncertainty equal to 100\% (20\%) of the local density are shown in the middle (right) columns.
-The reference asymmetric asteroid is used.
-The 20\% threshold is very restrictive, but the 100\% threshold is more achievable and demonstrates the thresholds in the right column are not hard cut-offs.}
-  \label{tab:threshold-summary}
-\end{table}
-
-\jtd{Discuss conclusions}.
-
-Uncertainties on the density moments, which do not depend on models used, are displayed as a function of encounter properties in figures \ref{fig:scan-perigee} and \ref{fig:scan-am}.
-The properties corresponding to the 20\% and 100\% density uncertainty thresholds are indicated with red lines, and a dotted black line indicates the properties of the reference asteroid.
-The initial spin pole direction and the asteroid shape are also shown in figures \ref{fig:scan-spin} and \ref{fig:scan-space-sigma} respectively.
-
-\jtd{Discuss conclusions}.
-
-Additional data and analysis and description for this relationship between encounter parameters and uncertainties are given in appendix \ref{app:uncertainty-dependence}
 
@@
 \end{figure*}
+
+Physical parameters not studied here include the possibility of an initially tumbling asteroid and the presence of a third perturbing body, such as the Moon.
+Both are likely to increase precision but they are not within the scope of this paper.
+
+The observational parameters also impose strict thresholds, most of all the uncertainty of the data set $\sigma_P / P$ and $\sigma_\rho$.
+Instantaneous rotational period uncertainty of less than one part in one million is required to resolve precise details of the asteroid density distribution.
+This could be accomplished by multiple, precise period measurements, increasing the time between observations to maximize the change in period between observations, increasing the data set to include more post-flyby tumbling data, or if necessary by increasing precision in the other observational parameters to relieve the burden on asteroid period.
+The instantaneous spin pole direction of the asteroid must also be known with precision on the order of degrees.
+However, the cadence of observations and the possibility of missing data points does not strongly affect results.
+Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence) due to the asteroid passing in front of the sun, for example.
+
+Two other properties important that affect moment uncertainty are the asteroid shape (as parametrized by the values of $K_{2m}$ or the axis lengths of the corresponding ellipsoid) and initial spin pole direction.
+The asteroid shape does not strongly affect density moment uncertainty, except that this model is not well-equipped to handle rotationally-symmetric asteroids with $K_{22} = 0$.
+For such asteroids, the principal axes can be selected to lie anywhere in the $xy$-plane, so that $\gamma_0$ is unconstrained.
+This inflates the moment uncertainties, although the density uncertainties are not badly affected as seen for the symmetric density distribution shown in figure \ref{fig:uniform}.
+A reparametrization of $\gamma_0$ would aid in decreasing moment uncertainty.
+
+The initial spin pole of the asteroid also does not strongly affect the moment uncertainties, except when the initial spin pole happens to point perpendicular to the orbital plane, or in the plane and perpendicular to the major axis of the encounter.
+Both of these regions tend to result in less tidal torque, but even within these regions, the moment uncertainty generally is only double or triple that of other regions.
+
+Additional analysis of the data shown in this section, descriptions of how they were collected, and some supplementary figures are given in appendix \ref{app:uncertainty-dependence}.
 

### 2022-06-28 code/fit_resolved/display.py

@@ -305,6 +305,7 @@ class Display:
         fig, (ax1, ax2) = plt.subplots(2, 1, gridspec_kw={'height_ratios': [3, 1]}, figsize=(9, 6), sharex=True)
 
         x_display = np.arange(len(self.true_results)) * self.cadence / 3600.0
+        x_display -= np.median(x_display)
         ax1.scatter(x_display, self.true_results[:,0] * 3600, label = 'true x', alpha=0.5, color='C0', s=1)
         ax1.scatter(x_display, self.true_results[:,1] * 3600, label = 'true y', alpha=0.5, color='C1', s=1)
         ax1.scatter(x_display, self.true_results[:,2] * 3600, label = 'true z', alpha=0.5, color='C2', s=1)
@@ -332,7 +333,7 @@ class Display:
             ax2.fill_between(x_display, uncertainties[:,2] * 3600, -uncertainties[:,2] * 3600, color="C2", alpha=0.2)
 
         ax2.set_ylabel("Residuals (rad/hr)")
-        ax2.set_xlabel("Time (hours)")
+        ax2.set_xlabel("Time to perigee (hours)")
         plt.tight_layout()
 
         plt.savefig(self.h5_name+"-compare.png")

### 2022-06-28 paper/main.tex
Changed example data plot

@@
 However, the cadence of observations and the possibility of missing data points does not strongly affect results.
-Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence) due to the asteroid passing in front of the sun, for example.
+Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence), even during the high-torque perigee.
+The latter could be caused by the asteroid passing in front of the sun, for example.
 

### 2022-06-28 paper/appendices.tex
Refactored paper

@@
 These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
-
-We define the density moments of an asteroid in equation \ref{eqn:klm}.
-Note that these are complex.
-The length defined in equation \ref{eqn:am} can be thought of as akin to the radius of the asteroid (a spherical, uniform-density asteroid has radius $a_\mathcal{A}\sqrt{5/3} $).
-Both equations \ref{eqn:am} and \ref{eqn:klm} should be computed in the body-fixed frame.
-
-Equations \ref{eqn:am} and \ref{eqn:klm} can be extended to the central body:
+They were used to define the density moments in equation \ref{eqn:klm}, which can be extended to the central body:
 \begin{equation}
   \begin{split}
-    &J_{\ell m} = \frac{1}{\mu_\mathcal{B} a_\mathcal{B}^\ell} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) R_{\ell m}(\bm r)\\
-    &a_\mathcal{B}^2 = \frac{1}{\mu_\mathcal{B}} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) r^2.
+    &J_{\ell m} = \frac{a_\mathcal{B}^{2-\ell}}{I_\mathcal{B}} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) R_{\ell m}(\bm r)\\
   \end{split}
@@
 \end{equation}
-which should be computed in the inertial frame.
+By contrast, $J_{\ell m}$ should be computed in the inertial frame.
+The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations \ref{eqn:aa} and \ref{eqn:ia}, but they could also be set to any other scales of the proper units, e.g.
+$a_\mathcal{B}$ equal to the central body radius and $I_\mathcal{B} = \mu_\mathcal{B}a_\mathcal{B}^2$, where $\mu_\mathcal{B}$ is the central body mass.
 
@@
 Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ contains $\ell_\text{max}^2$ degrees of freedom.
-However, some of these degrees of freedom are redundant with the choice of coordinates as we discuss next.
-
-By definition, $K_{00}=1$.
-Furthermore, $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid centre of mass.
-Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$ and the same for $m<0$.
-The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$ and $K_{20}$, which are related to the moment of inertia around each principal axis by equation \ref{eqn:moi}.
-Incidentally, the definition of $a_\mathcal{A}$ was chosen to satisfy equation \ref{eqn:moi}.
+However, some of these degrees of freedom are redundant with the choice of coordinates: $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid centre of mass.
+Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$.
+The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$, $K_{20}$, and $K_{00}$.
+The first two are related to the moment of inertia around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in \ref{eqn:tidal-torque}.
 
@@
 \end{equation}
-
-The physical meaning of the higher-order moments $K_{3m}$ can be aided by assessing their symmetry properties.
+The higher-order moments $K_{3m}$ can be thought of loosely as measuring the large-scale asymmetries of the asteroid.
 An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_\mathcal{A}(x,y,z)=\rho_\mathcal{A}(-x,y,z)$) necessarily sets certain density moments to zero.
 Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}.
-Note that, while no mirror symmetries set $K_{00}$, $K_{20}$, or $K_{22}$ equal to zero, mirror symmetries exist which zero all the other moments, including $K_{3m}$.
-$\Re K_{32}$, $K_{31}$, and $K_{30}$ are the only $K_{3m}$ components zeroed by only one axis.
-This will not affect our fit results for $K_{3m}$, but when we compute density moments for sample distributions, we find that most $K_{3m}=0$.
+All $K_{3m}$ are zeroed by at least one mirror symmetry.
 
@@
 \end{equation}
-In practice, we also observe that $|K_{3m}| < 1$; often, $|K_{3m}| < 0.01$ even.
+An analytical constraint on $K_{3m}$ based on this property is more difficult to derive, but in practice, we also observe that $|K_{3m}| < 0.01$.
 
@@
 
-Here, we present a novel derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
+Here, we present a new derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
 These density moments can be pre-computed and do not have to be re-evaluated every time-step.
@@
 We also assume no third-body perturbations from other Solar System objects.
-(Actually, third-body perturbing objects are allowed if they are closer to the central body's centre of mass than the asteroid perigee distance.
-Then, their density moments can be included in the density moments of the central body and this derivation can still be used.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body's rotation is marginal compared to the timescale of the encounter).
+(More accurately, we assume that all third-body perturbing objects lie closer to the central body's centre of mass than the asteroid perigee distance so that their density moments can be included in the density moments of the central body.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body's rotation is marginal compared to the timescale of the encounter).
 
@@
 \end{equation}
-tidal torque can now be expressed as a function only of $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A}$, $a_\mathcal{B}$, and the asteroid orientation and position.
-This equation is given explicitly as equation \ref{eqn:tidal-torque}.
+tidal torque can now be expressed as a function only of the constants $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A/B}$, $I_\mathcal{A/B}$, and the asteroid orientation and position (equation \ref{eqn:tidal-torque}).
 Some $K_{\ell m}$ terms are written in this equation with $|m|>\ell$; these should all be taken to be zero.
 
-Equation \ref{eqn:tidal-torque} possesses a few explicit properties which we discuss before writing the asteroid equations of motion.
-Firstly, $K_{00}$ does not appear, so that $\bm \tau$ is independent of asteroid mass.
+Equation \ref{eqn:tidal-torque} possesses a few explicit properties.
+Firstly, $\bm \tau$ is independent of asteroid mass.
 The mean density of the asteroid is therefore not constrained by tidal torque analysis.
@@
 Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
+$J_{2m}$ measures the oblaneness and its effects are studied in appendix \ref{app:uncertainty-dependence}.
 
@@
 
-The equations of motion of the asteroid position $\bm D$ are given by Newton's law of gravitation:
+The equations of motion of the asteroid position $\bm D$ are given by Newton's law of gravitation
 \begin{equation}
@@
 \end{equation}
+where $\bm V$ is the asteroid velocity in the inertial frame.
 Rather than derive equations of motion for the Euler angles (which suffer from gimbal lock), we instead represent the orientation of the asteroid with a quaternion $\quat q$ which can be converted into Euler angles to compute $\mathcal{D}(\alpha, \beta, \gamma)$.
@@
 \end{equation}
-Equations \ref{eqn:tidal-torque} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
-They are expressed in terms of the constant physical parameters $\mu_{M/m}$, $a_{M/m}$, $J_{\ell m}$ and $K_{\ell m}$ given the density moment-moment of inertia relations given by equation \ref{eqn:moi}.
+Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, and \ref{eqn:pos-eom} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
+They are expressed in terms of the constant physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$.
 
@@
 Except when otherwise mentioned, we use the following asteroid encounter parameters.
-Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our uncertainties have room to grow; if the reference asteroid has low uncertainty, we would not be able to measure uncertainty increases as well when the encounter parameters are adjusted.
+Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our analysis is most sensitive to the affect changing these parameters to the methodology's output.
 
@@
 The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
-It therefore is not entirely comparable to our analysis.
+Further work must therefore be done to apply this analysis to Apophis.
   \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_\rho / \sigma_\theta = 10^{-5}$.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_P / P = 10^{-7}$.
   \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
@@
 
-We use the asymmetric ellipsoid in nearly all runs, due to the degeneracy induced in our model when $K_{22} = 0$.
-
 \section{Additional density distribution models}
+\label{app:more-models}
 
@@
 
+\jtd{Remove this section or included it in the following section.}
+
 In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
@@
 
+\jtd{Review after thresholds.}
+
 In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
@@
 (The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
-The dependence of posterior uncertainty on $v_\infty$ is weak enough so that $\sigma_\rho/\rho$ never reaches 100\% for the $v_\infty$ investigated.
 

### 2022-06-28 paper/main.tex
Refactored paper

@@
 \usepackage{subcaption}
-
-% For the sideways figure
-\usepackage{pdflscape}
-\usepackage{afterpage}
 
@@
   \begin{split}
-  \bm \tau = & G\frac{\mu_\mathcal{B}}{2}\left[I_\mathcal{A} \sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\text{surf}^{\ell' - 2}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \bm \tau = & G\frac{I_\mathcal{A}I_\mathcal{B}}{2 a_\mathcal{A}^2a_\mathcal{B}^2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
   \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
@@
 where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body, with the $a_\text{bulk}$ and $a_\text{surf}$ of equation \ref{eqn:klm} replaced by $a_\mathcal{B}$.
-Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no third-body perturbations.
+Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no distant third-body perturbations.
 
@@
 
-Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed), which are also defined in appendix \ref{app:eom}.
+Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed and in which $K_{\ell m}$, $I_\mathcal{A}$, and $a_\mathcal{A}$ are computed), which are also defined in appendix \ref{app:eom}.
 
@@
 Otherwise, the MCMC parameters chosen were identical to those discussed in section \ref{sec:fit}.
+We also present two further models in appendix \ref{app:more-models} which are viable substitutes for the following two models but are not used in the main text.
 
@@
 
-In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
-These are collected by \jtd{Explain}.
-Their values are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
-These thresholds are more physically relevant, but they should be understood as moveable, since making different model choices can drastically change their locations.
-
-Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and its length.
-\jtd{Further discuss}.
-Figure \ref{fig:scan-physical} demonstrates that the asteroid length cut-off is particularly sharp, since the density moment uncertainty $\sigma_{K_{3m}}$ is very steep there.
-However, precision on the moment of inertia ratios of the asteroid $K_{2m}$ are not affected by asteroid length; these may still be collected even for small asteroids.
-
 \begin{table}
@@
 
-The excess velocity and rotational period of the asteroid do not drastically affect the moment uncertainty and therefore do not impose strict thresholds, except for a dramatic increase in $\sigma(K_{2m})$ visible in figure \ref{fig:scan-physical} for rotational period $P_\omega \approx 4$ hr.
-The location of this threshold is likely dependent on other dynamical time scales of the system such as the cadence of observations and possibly the orbital time scales of $v_\infty / r_p$ and $\mu_\mathcal{A} / (v_\infty^2 r_p)$.
+In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
+These are collected by \jtd{Explain}.
+Their values are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
+These thresholds are more physically relevant, but they should be understood as moveable, since making different model choices can drastically change their locations.
 
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
+\begin{figure*}
+  \newpage
   \centering
-    \includegraphics[width=\linewidth]{figs/scan-all2.pdf}
+  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all1.pdf}
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+The vertical dashed line indicates the reference asteroid values.
+The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+  \label{fig:scan-perigee}
+  \label{fig:scan-vex}
+  \label{fig:scan-am}
+  \label{fig:scan-period}
+  \label{fig:scan-physical}
+\end{figure*}
+
+\begin{figure*}
+  \newpage
+  \centering
+  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all2.pdf}
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
@@
     \label{fig:scan-observational}
-  \end{figure}
-  \end{landscape}
-}
-\afterpage{
-  \begin{landscape}
-    \begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{figs/scan-all1.pdf}
-    \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
-    \label{fig:scan-perigee}
-    \label{fig:scan-vex}
-    \label{fig:scan-am}
-    \label{fig:scan-period}
-    \label{fig:scan-physical}
-  \end{figure}
-  \end{landscape}
-}
+\end{figure*}
 
@@
 \end{figure*}
+
+Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and its length.
+\jtd{Further discuss}.
+Figure \ref{fig:scan-physical} demonstrates that the asteroid length cut-off is particularly sharp, since the density moment uncertainty $\sigma_{K_{3m}}$ is very steep there.
+However, precision on the moment of inertia ratios of the asteroid $K_{2m}$ are not affected by asteroid length; these may still be collected even for small asteroids.
+
+The excess velocity and rotational period of the asteroid do not drastically affect the moment uncertainty and therefore do not impose strict thresholds, except for a dramatic increase in $\sigma(K_{2m})$ visible in figure \ref{fig:scan-physical} for rotational period $P_\omega \approx 4$ hr.
+The location of this threshold is likely dependent on other dynamical time scales of the system such as the cadence of observations and possibly the orbital time scales of $v_\infty / r_p$ and $\mu_\mathcal{A} / (v_\infty^2 r_p)$.
 

### 2022-06-29 paper/main.tex
New threshold plots and lumpy double model

@@
 
-The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform (the $\chi^2_r$ values are large due to numerical error and correspond to deviations in $K_{2m}$ only on the order of \jtd{number}).
+The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform.
 These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of \jtd{number}) due to its few degrees of freedom.

### 2022-06-29 code/density/mcmc/tests/tests.py

@@ -30,7 +30,7 @@ if METHOD_NAME == "lumpy":
         lumpy.MODEL_N = 2
         lumpy.SLOW_PRIOR = True
         dof = 7
-        mcmc_core.NUM_SUCCESSES = 48
+        mcmc_core.NUM_SUCCESSES = 8
 elif METHOD_NAME == "fe":
     cut_k2m = False
     DIVISION = 49

### 2022-06-30 paper/main.tex
Hessian spread on mcmc points

@@
 The density distribution uncertainty is presented as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
-The average uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid.
+The median uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid.
 This measure of uncertainty is more physically relevant than moment uncertainty, but it is affected by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
+
+\begin{table}
+  \centering
+  \begin{tabular}{lll} \hline
+    Encounter property & Weak &Strong \\ \hline
+    Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
+    Excess velocity ($v_\infty$) & - & - \\
+    Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
+    Period ($P_\omega$, hr) & $>$7.6 & - \\ \hline
+    Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\
+    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$1.9 & $<$35 \\
+    Cadence ($\Delta t$, min) & $<$15 & - \\
+    Data gap ($T_\text{gap}$, hr) & - & - \\ 
+    \hline
+  \end{tabular}
+  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty.
+Perigee and observational uncertainty are the most constraining properties, followed by asteroid length, rotational period, and observational cadence.}
+  \label{tab:threshold-summary}
+\end{table}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
+  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution as a function of various encounter properties.
+Density distributions from both the lumpy and finite element models are used.
+The benchmark uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
+The figures illustrate the marked difference in density distributions that results from using different models.}
+  \label{fig:net-uncertainty}
+\end{figure*}
 
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{lll} \hline
-    Encounter property & $\sigma_\rho / \rho = 100\%$ & $20\%$ \\ \hline
-    Perigee ($r_p$, Earth radii) & $<$7.9 & $<$4.7 \\
-    Excess velocity ($v_\infty$) & - & - \\
-    Asteroid length ($a_\mathcal{A}$, m) & $>$180 & $>$1100 \\
-    Period ($P_\omega$, hr) & $>$4.3 & $>$9.5\\ \hline
-    Spin period uncertainty ($P_\omega \sigma_\rho$, ms) & $<$15 & $<$3.1\\
-    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$2.8 & $<$0.5 \\
-    Cadence ($\Delta t$, min) & $<$38 & $<$2 \\
-    Data gap ($T_\text{gap}$, hr) & $<$1.8 & $<$0 \\ 
-    \hline
-  \end{tabular}
-  \caption{The physical / observational encounter property thresholds (\textit{top} / \textit{bottom} consistent with useable density distribution uncertainty. \jtd{Summarizing sentence}.}
-  \label{tab:threshold-summary}
-\end{table}
-
-In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
-These are collected by \jtd{Explain}.
-Their values are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
-These thresholds are more physically relevant, but they should be understood as moveable, since making different model choices can drastically change their locations.
-
 \begin{figure*}
-  \newpage
   \centering
@@
 \begin{figure*}
-  \newpage
   \centering
@@
 \end{figure*}
+
+In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
+These are collected by evaluating the median uncertainty ratio of the asteroid density distribution extracted by the lumpy model as a function of each encounter property and identifying when it exceeds $\sigma_\rho / \rho = 10^{-4}$ (the weak threshold) and $\sigma_\rho / \rho = 10^{-3}$ (the strong threshold).
+These thresholds are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
+The values of $\sigma_\rho / \rho$ are plotted as a function of encounter properties in figure \ref{fig:net-uncertainty}, similarly to figures \ref{fig:scan-physical} and \ref{fig:scan-observational}.
 

### 2022-06-30 code/density/mcmc/fe.py

@@ -93,7 +93,7 @@ class FiniteElement(MCMCMethod):
             unc_ratios[~asteroid.indicator_map] = np.nan
             return densities, unc_ratios
 
-    def scatter_walkers(self, theta_start, n_walkers):
+    def scatter_walkers(self, theta_start, n_walkers, data_storage):
         pos = np.zeros((n_walkers, self.n_free))
         for i in range(self.n_free):
             pos[:,i] = np.random.randn(n_walkers) * UNCERTAINTY_RATIO * self.mean_density + theta_start[i]

### 2022-06-30 paper/appendices.tex
Double lumpy model

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/spin-pole.png}
+  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
+All maps are made in the Mollweide projection.
+The orange star indicates the reference spin pole.
+The red contours enclose regions the 20\% (dotted) and 100\% (solid) $\sigma_\rho / \rho$ cut-off.
+Posterior uncertainty depends similarly on initial spin pole direction for all parameters}
+  \label{fig:scan-spin}
+\end{figure*}
+
 In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
@@
 However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
+
+\section{Animated density distributions}
+
+This figure contains animations to better display the density distributions shown in the main text.
+Each frame represents a cross section perpendicular to the $\unit z$-axis, starting with negative $z$ and ending with positive $z$.
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{}{}
+
+  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{first and thrid row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
+The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-uniform}.}
+  \label{fig:animated-uniform}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-sph}.}
+  \label{fig:animated-sph}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-move}.}
+  \label{fig:animated-move}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-double}.}
+  \label{fig:animated-double}
+\end{figure*}

### 2022-06-30 paper/main.tex
Double lumpy model

@@
 \usepackage{subcaption}
-
+\usepackage{animate}
 \usetikzlibrary{arrows.meta}
@@
 \author[Jack T. Dinsmore, Julien de Wit]{
-Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtdinsmo@mit.edu}
+Jack T. Dinsmore,$^{1}$\thanks{E-mail: jtd@stanford.edu}
 Julien de Wit$^{2}$
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Extracted densities are generally within 10\% of the truth.}
-  \label{fig:uniform}
+These figures are available in animated form in appendix figure \ref{fig:animated-uniform}.Extracted densities are generally within 10\% of the truth.}
+  \label{fig:den-uniform}
 \end{figure*}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+These figures are available in animated form in appendix figure \ref{fig:animated-den-sph}.
 The core is successfully extracted in all cases.}
-  \label{fig:center-core}
+  \label{fig:den-sph}
 \end{figure*}
@@
 
-The question of which encounters are most suited to this analysis is of great interest.
-We investigate a mix of encounter parameters, from observational parameters (e.g., the cadence of observations, gaps in data, and uncertainty in the spin pole and period of the asteroid) and physical asteroid properties (e.g., the true density moments, rotational period, perigee, excess velocity, initial spin pole direction, and length), and discuss their effect on the uncertainty of this methodology's results.
+The question of which encounters are most suited to this methodology is of great interest, as is the question of how observational campaigns can be designed to best take advantage of an asteroid to maximize the success of this methodology.
+We investigate a mix of encounter parameters, from observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage) and physical asteroid properties (the encounter's orbital properties, the asteroid's true shape, and its initial rotational velocity), and discuss their effect on the uncertainty of this methodology's results.
 
-Specifically, we highlight both the uncertainties on the density moments and uncertainty on density distribution.
-Moment uncertainty is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
+We study both the uncertainties on the density moments and uncertainty on density distribution.
+Moment uncertainty $\sigma (K_{\ell m})$ is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
 Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined.
 However, its physical relevance is not obvious.
-The density distribution uncertainty is presented as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
-The median uncertainty over this map, divided by the local density, is taken as the uncertainty in density distribution of the asteroid.
-This measure of uncertainty is more physically relevant than moment uncertainty, but it is affected by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
+The density distribution uncertainty $\sigma_\rho / \rho$ is defined as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
+The median uncertainty over this map, divided by the local density, is taken to represent the density distribution uncertainty.
+This measure of uncertainty is more physically relevant than moment uncertainty, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
+We therefore investigate both the moment uncertainty and the density distribution uncertainty.
 
@@
   \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty.
-Perigee and observational uncertainty are the most constraining properties, followed by asteroid length, rotational period, and observational cadence.}
+Perigee and observational uncertainty are the most constraining properties, followed by rotational period, asteroid length, and observational cadence.}
   \label{tab:threshold-summary}
@@
   \centering
+  % \includegraphics[width=0.5\linewidth]{figs/spin-unc.pdf}
+  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction.
+The benchmark uncertainty thresholds (\textit{red lines}) are shown, as is the reference spin pole direction (\textit{\jtd{What symbol?}}).
+\jtd{Summary}}
+  \label{fig:spin-uncertainty}
+\end{figure*}
+
+\begin{figure*}
+  \centering
   \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
-  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution as a function of various encounter properties.
+  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution as a function of physical / observational encounter properties (\textit{top / bottom}).
 Density distributions from both the lumpy and finite element models are used.
 The benchmark uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
+Te vertical black dotted lines are the property values of the reference asteroid.
 The figures illustrate the marked difference in density distributions that results from using different models.}
@@
 
-We therefore investigate both the moment uncertainty and the density distribution uncertainty.
-Figure \ref{fig:scan-physical} displays the dependence of moment uncertainty on four asteroid physical parameters and and \ref{fig:scan-observational} displays dependence on observational parameters.
-Additionally, figures \ref{fig:scan-space-sigma} and \ref{fig:scan-spin} display dependence on asteroid shape and initial spin direction.
-These are useful as a sensitive and model-independent measure of the relationship between the encounter properties and the methodology uncertainty.
+Table \ref{tab:threshold-summary} displays the encounter properties which beyond which the density distribution uncertainty rises above two sample values we term the ``weak'' and ``strong'' thresholds.
+These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
+These thresholds are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
+Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the encounter properties.
+Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines.
+Bands contain 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.
+
+Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and period.
+Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only effective for $a_\mathcal{A} \sim 15$ m.
+By contrast, the radius of asteroid 99942 Apophis is
+$\sim 300$ m and Apophis will encounter Earth in 2029.
+Apophis's perigee of 5--6 Earth radii also obeys the weak and strong constraints.
+In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} also shows a threshold on spin pole direction.
+\jtd{Describe}.
+
+Table \ref{tab:threshold-summary} also demonstrates the strong affect of properties of the observational campaign on the final density uncertainty.
+Most vital are the uncertainty on the instantaneous asteroid rotational period $\sigma_P / P$ and its direction $\sigma_\theta$, which require precision on the order of tens to hundreds of milliseconds and degrees every cadence, respectively.
+This could be accomplished by multiple, precise angular velocity measurements from multiple telescopes, or by increasing the time between observations to maximize the change in period between observations.
+Increasing the data set size to include more post-flyby tumbling data would also relieve the burden on each data point for uncertainty to be so low.
+On the other hand, the cadence of observations $\Delta t$ and the presence of gaps in the data $T_\text{gap}$ do not affect results as strongly.
+Observations can be as much as 15 minutes apart to obey the weak threshold, with no constraint required to meet the strong threshold in our data set (which contains $\Delta t < 1$ hr).
+Likewise, there is no constraint on our data set of $T_\text{gap} < 3$ hr.
+This gap was simulated to occur in one contiguous unit centred on the encounter perigee, where torque is highest.
+If the gap occurred elsewhere in the data set or was subdivided into multiple gaps, it would likely affect density uncertainty even less.
+All of these thresholds are liable to change if the encounter properties are adjusted, since they are all interdependent.
+
+Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\sigma_\rho / \rho$) for the encounter perigee $r_p$and observational precision $\sigma_P$ and $\sigma_\theta$.
+These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are much more volatile.
+The figure also displays the stark difference between density uncertainty as computed by the lumpy model and the finite element model.
+This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model).
+The model assumptions also affect this uncertainty; the lumpy model must place the asteroid lump at the center of the asteroid since placing it elsewhere would move the asteroid's center of mass away from its observed position.
+Therefore, uncertainty on the edge of the asteroid where the lump is unlikely to be located, is very low for the lumpy model.
+The same reasoning does not apply to the finite element model, which has no bias towards the asteroid center.
+This model-dependence of $\sigma_\rho / \rho$ is another reason to take the thresholds of table \ref{tab:threshold-summary} as estimates rather than strict limits on encounter properties.
 
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/spin-pole.png}
-  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection.
-The orange star indicates the reference spin pole.
-The red contours enclose regions the 20\% (dotted) and 100\% (solid) $\sigma_\rho / \rho$ cut-off.
-Posterior uncertainty depends similarly on initial spin pole direction for all parameters}
-  \label{fig:scan-spin}
-\end{figure*}
+To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate moment uncertainty as well.
+Figures \ref{scan-physical} and \ref{scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ on physical and observational encounter properties respectively.
+The thresholds of table \ref{tab:threshold-summary} are depicted as red lines.
+Also shown is moment uncertainty as a function of $K_{2m}$ in figure \ref{fig:scan-space-sigma}.
 
-In table \ref{tab:threshold-summary}, we present the property ``thresholds'' required in order to obtain meaningful information about the asteroid density distribution.
-These are collected by evaluating the median uncertainty ratio of the asteroid density distribution extracted by the lumpy model as a function of each encounter property and identifying when it exceeds $\sigma_\rho / \rho = 10^{-4}$ (the weak threshold) and $\sigma_\rho / \rho = 10^{-3}$ (the strong threshold).
-These thresholds are also shown in figures \ref{fig:scan-physical} to \ref{fig:scan-observational} as vertical red lines.
-The values of $\sigma_\rho / \rho$ are plotted as a function of encounter properties in figure \ref{fig:net-uncertainty}, similarly to figures \ref{fig:scan-physical} and \ref{fig:scan-observational}.
+Figure \ref{scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $K_{3m}$.
+For instance, $\sigma(K_{2m})$ is constant as $a_\mathcal{A}$ is varied despite a dramatic increase in $\sigma(K_{3m})$ for low $a_\mathcal{A}$.
+The resulting $\sigma_\rho / \rho$ is mostly constant.
+However, the roles are reversed for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and here $\sigma_\rho /\rho$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
+This fact has several consequences.
+First of all, if more post-flyby tumbling data is collected, this will place stronger constraints on $K_{2m}$ and not $K_{3m}$.
+If so much data is available that $K_{2m}$ have essentially no uncertainty, then uncertainty on $K_{3m}$ will be dominant and the most constraining parameters will change.
+Rotational period $P_\omega$ will cease to be a vital parameter but asteroid length $a_\mathcal{A}$ will be because $\sigma(K_{3m})$ are much more dependent on $a_\mathcal{A}$ than $P_\omega$.
 
-Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and its length.
-\jtd{Further discuss}.
-Figure \ref{fig:scan-physical} demonstrates that the asteroid length cut-off is particularly sharp, since the density moment uncertainty $\sigma_{K_{3m}}$ is very steep there.
-However, precision on the moment of inertia ratios of the asteroid $K_{2m}$ are not affected by asteroid length; these may still be collected even for small asteroids.
+Figure \ref{fig:scan-physical} also demonstrates exponentially increasing $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
+(Figure \ref{fig:net-uncertainty} also indicated this, since $\sigma_\rho / \rho$ falls for low perigee in both the lumpy and the finite element model).
+Dependence of moment uncertainty on data precision $\sigma_P$ and $\sigma_\theta$ is similarly exponential as shown by figure \ref{fig:scan-observational}.
+However, moment uncertainty on cadence $\Delta t$ and gaps in data $T_\text{gap}$ are less exponential.
+These tend to increase in uncertainty at some characteristic time scale of $\Delta t \sim 15 -40$ min for cadence and $1-2$ hr for $T_\text{gap}$.
+As long as $\Delta t$ and $T_\text{gap}$ are below these time scales, uncertainty is not strongly dependent on them.
 
-The excess velocity and rotational period of the asteroid do not drastically affect the moment uncertainty and therefore do not impose strict thresholds, except for a dramatic increase in $\sigma(K_{2m})$ visible in figure \ref{fig:scan-physical} for rotational period $P_\omega \approx 4$ hr.
-The location of this threshold is likely dependent on other dynamical time scales of the system such as the cadence of observations and possibly the orbital time scales of $v_\infty / r_p$ and $\mu_\mathcal{A} / (v_\infty^2 r_p)$.
-
-Physical parameters not studied here include the possibility of an initially tumbling asteroid and the presence of a third perturbing body, such as the Moon.
-Both are likely to increase precision but they are not within the scope of this paper.
-
-The observational parameters also impose strict thresholds, most of all the uncertainty of the data set $\sigma_P / P$ and $\sigma_\rho$.
-Instantaneous rotational period uncertainty of less than one part in one million is required to resolve precise details of the asteroid density distribution.
-This could be accomplished by multiple, precise period measurements, increasing the time between observations to maximize the change in period between observations, increasing the data set to include more post-flyby tumbling data, or if necessary by increasing precision in the other observational parameters to relieve the burden on asteroid period.
-The instantaneous spin pole direction of the asteroid must also be known with precision on the order of degrees.
-However, the cadence of observations and the possibility of missing data points does not strongly affect results.
-Observations can be as much as 30 minutes apart and as much as 1.5 hr can be left out of the data set (equivalent to 45 missing data points for the reference 2 minute cadence), even during the high-torque perigee.
-The latter could be caused by the asteroid passing in front of the sun, for example.
-
-Two other properties important that affect moment uncertainty are the asteroid shape (as parametrized by the values of $K_{2m}$ or the axis lengths of the corresponding ellipsoid) and initial spin pole direction.
-The asteroid shape does not strongly affect density moment uncertainty, except that this model is not well-equipped to handle rotationally-symmetric asteroids with $K_{22} = 0$.
-For such asteroids, the principal axes can be selected to lie anywhere in the $xy$-plane, so that $\gamma_0$ is unconstrained.
-This inflates the moment uncertainties, although the density uncertainties are not badly affected as seen for the symmetric density distribution shown in figure \ref{fig:uniform}.
-A reparametrization of $\gamma_0$ would aid in decreasing moment uncertainty.
-
-The initial spin pole of the asteroid also does not strongly affect the moment uncertainties, except when the initial spin pole happens to point perpendicular to the orbital plane, or in the plane and perpendicular to the major axis of the encounter.
-Both of these regions tend to result in less tidal torque, but even within these regions, the moment uncertainty generally is only double or triple that of other regions.
-
-Additional analysis of the data shown in this section, descriptions of how they were collected, and some supplementary figures are given in appendix \ref{app:uncertainty-dependence}.
+Finally, figure \ref{fig:scan-space-sigma} depicts moment uncertainty $\sigma(K_{2m})$ as a function of $K_{2m}$ and $\gamma_0$.
+$K_{2m}$ can be interpreted as moment inertia ratios or the dimensions of the uniform-density ellipsoid with the same $K_{\ell m}$.
+Therefore, moment uncertainty is depicted both as a function of $K_{2m}$ and these ratios $a/c$ and $b/c$.
+The figure shows a dramatic increase in moment uncertainty for $K_{22} = 0$, which corresponds to $a=b$, or a rotationally symmetric ellipsoid.
+This uncertainty is caused by degeneracy in the model; if the asteroid is rotationally symmetric, then two principal axes can lie anywhere in the $xy$-plane, so that the definition of $\gamma_0$ becomes meaningless.
+$\gamma_0$ is therefore poorly constrained as $K_{22} \rightarrow 0$.
+Figure \ref{fig:uniform} revealed that density distributions can still be extracted for symmetric asteroids, but to reduce uncertainty, the moments must be re-parametrized to remove this degeneracy if this methodology is to be run on nearly symmetric asteroids.
+Beyond this dependence on $K_{2m}$, almost no moment uncertainty variation is visible, indicating that this methodology will give similar results given many asteroid shapes distinct from the reference asteroid.
 
@@
 
-In section \ref{sec:asym-density}, we displayed density distributions extracted via the lumpy model with $N=1$ lumps.
-When $N=1$, the model has two DOF, meaning that the density distribution can be determined only via the fit results for $K_{2m}$, rather than the relatively poorly constrained $K_{3m}$.
-Therefore, we also explore a density distribution with $N=2$ lumps, which has seven DOF.
+In section \ref{sec:asym-density}, we displayed uniform and non-uniform density distributions extracted via the finite element and single-lump lumpy model.
+Here we highlight the success of the model in two other scenarios.
 
-\jtd{Continue}
+\begin{figure*}
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-r}
 
-\jtd{Possibly discuss moved core}
+  \includegraphics[width=0.24\linewidth]{figs/move-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+These figures are available in animated form in appendix figure \ref{fig:animated-move}.
+The core is successfully extracted in all cases.}
+  \label{fig:den-move}
+\end{figure*}
+
+Figure \ref{fig:den-move} shows density distributions extracted via the finite element model and the lumpy model for an off-center core.
+Results are similar to the centred core shown in \ref{fig:den-sph} in that the moments of the resulting density distribution are consistent with those extracted from the encounter data (i.e., $\chi^2_r$ is low).
+Again, the finite element model does not isolate the lump, instead spreading the excess mass over the right side of the asteroid.
+The ability of the lumpy model to isolate the core is rooted in the fact that the shape of the asteroid is offset from the center of mass by a fixed amount with no uncertainty attached.
+The position of the lump is therefore set to balance the offset of the surrounding asteroid medium; the only free parameter is the lump's mass, which determines this offset.
+The assumption that the asteroid's center of mass is precisely known is rooted stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
+If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain.
+
+To assess the lumpy model when the positions of the lump are not as certain as in this off-center case, we consider an asteroid with two lumps of radius 300 m and density three times the surrounding density.
+Each lump is located 500 meters from the center of the asteroid, so that they counterbalance and the asteroid's observed center of mass is its surface's centroid.
+The lumpy model with $N=2$ lumps then inherits three additional DOF corresponding to one lump's position (the other lump is fixed to counterbalance it) as well as two more from the additional lump's radius and mass.
+The model thus has seven DOF, in contrast to the 5 DOF of the finite element model.
+Both models are run on this asteroid and the resulting distributions are shown in figure \ref{fig:den-double}.
+
+\begin{figure*}
+  \includegraphics[width=0.24\linewidth]{figs/double-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-fe-r}
+
+  \includegraphics[width=0.24\linewidth]{figs/double-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/double-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+These figures are available in animated form in appendix figure \ref{fig:animated-double}.
+The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
+  \label{fig:den-double}
+\end{figure*}
+
+Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased asteroid near the center.
+On the other hand, the lumpy model detects that the two lumps are opposite each other, and of roughly the same radius and mass.
+These radius and mass values are also close to the true values.
+The model places the lumps correctly in the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in very high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
+Note that $\chi^2_r$ remains low despite the lumpy model's misplacement of the lumps.
+This is because the lumpy model gains its information on the placement of the lumps from the $K_{3m}$ density moments, which figures \ref{fig:scan-physical} and \ref{fig:scan-observational} suggest are not as well constrained as the $K_{2m}$ density moments.
+The moments estimated by the MCMC fit to encounter data are not perfectly correct, resulting in a deviation of a few hundred meters in lump location.
+Overall, the figures show that even the poorly constrained $K_{3m}$ moments can be used to determine features of the asteroid density, given a well-chosen model.
 
@@
 We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque equation (equation \ref{eqn:tidal-torque}) revealed that the angular velocity of the asteroid over time depends strongly on $K_{\ell m}$ and the initial orientation.
-We then built a fast simulation for an asteroid encounter, truncating the equation at second-order, and used the simulation to extract first- and second-order density moments from synthetic spin pole data via a Markov Chain Monte Carlo fit.
-We observe the following general properties of the moments:
-\begin{enumerate}
-  \item The second-order moments $K_{3m}$ are roughly a factor of $~\frac{a_\mathcal{A}}{r_p}$ more uncertain than the first-order moments, where $a_\mathcal{A}$ is proportional to the asteroid radius and $r_p$ is the perigee distance.
-For our reference asteroid, this fraction was about $10^{-5}$.
-  \item The second-order moments that measure small-scale variations in density (i.e., $|m|$ is large) are generally less uncertain.
-It is often possible to measure $K_{3|m|}$ for large $m$ even when $K_{30}$ is not resolved.
-  \item Extracted density moments are generally more precise when the asteroid leaves the encounter tumbling.
-  \item The oblateness of the central body cannot be ignored without generating incorrect density moment estimates.
-\end{enumerate}
+The tidal torque (equation \ref{eqn:tidal-torque}) revealed that the angular velocity of the asteroid over time depends strongly on the asteroid's density moments and the initial orientation.
+We then built a fast simulation for an asteroid encounter and designed an MCMC to extract density moments from simulated data.
+We also created two models --- the finite element model and the lumpy model --- to translate these density moments back into density distributions.
+Since this problem is underdetermined, the models give different results and were contrasted.
+Nevertheless, we find that the models always produce results consistent with the data set.
+The entire pipeline was run starting from simulated encounter data and ending with density distribution predictions and was shown to be robust.
 
-We assessed the posterior uncertainty generated by the fit process by adjusting various properties of an asteroid on an Earth encounter.
-The precise thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit are the most difficult requirements to meet, with perigee $\lesssim 6$ Earth radii, spin pole uncertainty $\lesssim 1^\circ$, and period uncertainty $\lesssim 10$ ms.
-However, these thresholds depend on the model used to extract a density distribution, and useful information may be able to be extracted when they are not achieved by using a different model.
+We assessed the uncertainty of the pipeline's results by adjusting various properties of the asteroid and its Earth encounter.
+The precise thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
+We also discussed how these thresholds could be eased by changes in observational behaviour such as lengthening the data set, or by physical asteroid properties such as a closer encounter or an initially tumbling state.
+If the thresholds were eased enough, then the asteroid length would become an important threshold as well.
 
-Finally, we presented three fast, linear methods for extracting density distributions (together with uncertainties) from the density moments and the shape of the asteroid The extracted density distributions are largely consistent with the true distributions in all cases we tested.
-Slight adjustments to $K_{3m}$ dramatically change the overall distribution, so that they are not very precise.
-Indeed, the models sometimes predict negative density (though more complicated models could be made not to).
-Errors in the shape estimate of the asteroid also distort the density distribution, but the resulting distributions provide hints as to exactly where the shape is incorrect.
-Large-scale properties of the asteroid's true distribution, such as whether the mass is located in the middle or on the edges, are often observable.
-Two of the models presented (the harmonic and lumpy models) are flexible in their number of parameters, so that if only these large-scale properties are necessary, a small set of parameters can be chosen to prevent over-fitting.`'
+Finally, we highlighted that the properties of the final density distribution are strongly dependent.
+The uncertainties on density distribution of the two models were drastically different, and also depended on the number of degrees of freedom used in the model.
+For asteroids of non-uniform distributions, the distributions themselves also differed.
+The lumpy model, designed to look for specific types of features, was much more sensitive to these features than the generic finite element model.
+To efficiently use encounter data, it is therefore important to investigate multiple models and choose different models to answer different questions.
 
@@
 
-The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}.
+The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}. Please contact JTD with questions.
 

### 2022-06-30 data/scan-spin-pole/compile.py

@@ -24,9 +24,9 @@ N_PERCENTILES = None
 PULL = True
 
 if PULL:
-    os.sysmem("scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/code/thresholds/lumpy/scan-spin-pole.npy .")
+    os.system("scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/code/thresholds/lumpy/scan-spin-pole.npy .")
 
-with open("../../code/thresholds/scan-spin-pole.npy", 'rb') as f:
+with open("scan-spin-pole.npy", 'rb') as f:
     uncs = np.load(f)
 
 def show_true_point(ax, flip=False):
@@ -104,17 +104,25 @@ for plot_index in range(N_DIM+1):
         param_data[:,name_index[f]] = percentiles[f][i]
 
     interp = LinearNDInterpolator(xyzs, data[i])
+    interp_unc = LinearNDInterpolator(xyzs, uncs)
 
     cart_array = []
+    cart_array_unc = []
     for pi, lat in enumerate(lats):
         cart_line = []
+        cart_line_unc = []
         for pj, lon in enumerate(lons):
             p = projected_vecs[pi][pj]
             cart_line.append(interp(p[0], p[1], p[2]))
+            cart_line_unc.append(interp_unc(p[0], p[1], p[2]))
         cart_array.append(cart_line)
+        cart_array_unc.append(np.array(cart_line_unc))
 
     vmax = np.percentile(cart_array, 95)
     im = axs[plot_index].pcolormesh(Lon, Lat, cart_array, vmin=np.min(cart_array), vmax=vmax, cmap='Blues_r')
+
+    axs[plot_index].contour(Lon, Lat, np.array(cart_array_unc), levels=[1e-3], colors=['r'], linewidths=[1])
+    axs[plot_index].contour(Lon, Lat, np.array(cart_array_unc), levels=[1e-4], colors=['r'], linewidths=[1], linestyles=['dotted'])
     
     cbar = fig.colorbar(im, ax=axs[plot_index], extend='max')
     if i < 3:

### 2022-06-30 data/scan-spin-pole/net-unc-map.py

@@ -1,0 +1,85 @@
+from matplotlib import pyplot as plt
+import numpy as np
+from scipy.interpolate import LinearNDInterpolator
+from scipy.linalg import norm
+import os
+
+plt.style.use("jcap")
+
+xyzs = []
+theta_phis = []
+
+PULL = True
+
+if PULL:
+    os.system("scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/code/thresholds/lumpy/scan-spin-pole.npy .")
+
+with open("scan-spin-pole.npy", 'rb') as f:
+    uncs = np.load(f)
+
+def show_true_point(ax, flip=False):
+    spin = [0.00006464182, 0.00012928364, -0.00012928364]
+    theta, phi = np.pi / 2 - np.arccos(spin[2] / norm(spin)), np.arctan2(spin[1], spin[0])
+    if flip:
+        theta *= -1
+    ax.scatter(phi, theta, color='tab:orange', marker='*', s=32)
+
+for i in range(len(uncs)):
+    dir_name = f"pole-{i}"
+    with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
+        max_j, max_l = f.readline().split(", ")
+        max_j, max_l = (int(max_j), int(max_l))
+        cadence = int(f.readline())
+        perigee = int(f.readline())
+        radius = float(f.readline())
+        speed = float(f.readline())
+        spin = [float(x) for x in f.readline().split(',')]
+        jlms = [float(x) for x in f.readline().split(',')]
+        theta_true = [float(x) for x in f.readline().split(',')]
+        theta_high = [float(x) for x in f.readline().split(',')]
+        theta_low = [float(x) for x in f.readline().split(',')]
+        sigma = [float(d) for d in f.readline().split(',')]
+    sigma_theta = sigma[0]
+    theta, phi = np.pi / 2 - np.arccos(spin[2] / norm(spin)), np.arctan2(spin[1], spin[0])
+    theta_phis.append((theta, phi))
+    xyzs.append(np.array(spin) / norm(spin))
+
+theta_phis = np.array(theta_phis)
+lons = np.linspace(-np.pi, np.pi, 180)
+lats = np.linspace(-np.pi/2, np.pi/2, 90)
[…]

### 2022-06-30 paper/gifs/get-figs.py

@@ -1,0 +1,22 @@
+import os, shutil
+
+ROOT = "/home/jtdinsmo/Dropbox (MIT)/12.420 project/"
+
+f = open(ROOT + "paper/gifs/fig-sources.txt", 'r')
+for line in f.readlines():
+    if line == '':
+        continue
+    if line.startswith('#'):
+        continue
+    args = line[:-1].split(' ')
+    if len(args) != 2:
+        continue
+    name, path = args
+    if not os.path.isfile(ROOT + path):
+        print("Could not find " + path)
+        continue
+    if path[-4:] not in [".eps", ".pdf"]:
+        print("WARNING: .eps or .pdf file formats are preferred")
+    shutil.copyfile(ROOT+path, ROOT + "paper/gifs/"+name)
+
+f.close()

### 2022-06-30 paper/appendices.tex
Added animated figure links

@@
 
-  \href{}{}
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-d}{FE asymmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-s}{FE asymmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-u}{FE asymmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-r}{FE asymmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-d}{FE symmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-s}{FE symmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-u}{FE symmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-r}{FE symmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-d}{Lumpy asymmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-s}{Lumpy asymmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-u}{Lumpy asymmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-r}{Lumpy asymmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-d}{Lumpy symmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-s}{Lumpy symmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-u}{Lumpy symmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-r}{Lumpy symmetric significance}
 
@@
 \begin{figure*}
-  \textbf{Please see the published version of the paper for these animations}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-d.gif}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-s.gif}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-u.gif}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-r.gif}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-d.gif}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-s.gif}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-u.gif}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-r.gif}{Lumpy significance}
 
@@
 \begin{figure*}
-  \textbf{Please see the published version of the paper for these animations}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.gif}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.gif}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.gif}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.gif}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.gif}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.gif}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.gif}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.gif}{Lumpy significance}
 
@@
 \begin{figure*}
-  \textbf{Please see the published version of the paper for these animations}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-d.gif}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-s.gif}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-u.gif}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-r.gif}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-d.gif}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-s.gif}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-u.gif}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-r.gif}{Lumpy significance}
 

### 2022-07-01 paper/appendices.tex
Paper draft complete

@@
 Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal moment of inertia (this is the short axis mode, to use the vocabulary of Ref.~\cite{kaasalainen2001interpretation}).
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI (this is the short axis mode, to use the vocabulary of Ref.~\cite{kaasalainen2001interpretation}).
 In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
@@
 The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$, $K_{20}$, and $K_{00}$.
-The first two are related to the moment of inertia around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in \ref{eqn:tidal-torque}.
+The first two are related to the MOI around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in \ref{eqn:tidal-torque}.
 
@@
 
-Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the moment of inertia of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
-A simple, first-order derivation is also easily computable in terms of the asteroid moment of inertia in the inertial frame.
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.
 
@@
 Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
-$J_{2m}$ measures the oblaneness and its effects are studied in appendix \ref{app:uncertainty-dependence}.
+$J_{2m}$ measures the oblateness and its effects are studied in appendix \ref{app:uncertainty-dependence}.
 
@@
 Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions.
-In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is nonzero only when $\ell' = \ell$ and $m'=m$.
+In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is non-zero only when $\ell' = \ell$ and $m'=m$.
 Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$.
@@
 
-\section{The cadence cut-off}
-\label{app:cadence-tests}
+% \section{The cadence cut-off}
+% \label{app:cadence-tests}
 
-\jtd{Remove this section or included it in the following section.}
+% \jtd{Remove this section or included it in the following section.}
 
-In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
+% In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
 In this appendix, we discuss the location of this cadence cut-off as a function of the physical parameters of the asteroid.
 
-In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
+% In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
 Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.48\textwidth]{figs/cad-period.pdf}\hfill
-  \includegraphics[width=0.48\textwidth]{figs/cad-speed.pdf}
-  \caption{Contour plots showing posterior uncertainties as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=0.48\textwidth]{figs/cad-period.pdf}\hfill
+%   \includegraphics[width=0.48\textwidth]{figs/cad-speed.pdf}
+%   \caption{Contour plots showing posterior uncertainties as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
 The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
@@
 Cadence cut-off depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
-  \label{fig:cad-contour}
-\end{figure*}
+%   \label{fig:cad-contour}
+% \end{figure*}
 
-Figure \ref{fig:cad-contour} demonstrates that large rotational period produces high $T_\text{cad}$.
+% Figure \ref{fig:cad-contour} demonstrates that large rotational period produces high $T_\text{cad}$.
 The dependence on $P_\omega$ agrees with the fact that large rotational periods for fixed cadence lead to better posterior uncertainty, discussed in section \ref{sec:scan-period}.
@@
 
- The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was defined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
+%  The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was defined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
 The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
@@
 
-The right panel of figure \ref{fig:cad-contour} shows a stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
+% The right panel of figure \ref{fig:cad-contour} shows a stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
 It appears that even slightly slower orbits sharply increases $T_\text{cad}$.
@@
 
-\jtd{Review after thresholds.}
+In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
+
+\subsection{Orbital elements}
+\label{sec:scan-orbit}
+A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
+They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
+We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$, for which the moment and density distribution uncertainties are shown in figures \ref{fig:scan-perigee} and \ref{fig:net-uncertainty}.
+
+Figure \ref{fig:scan-perigee} shows a very strong dependence on perigee as mentioned in the main text --- so strong that for large perigee, $\sigma(K_{3m})$ is constrained by the prior boundaries of $\pm 1$ for $m < 3$.
+This occurs as low as $r_p = 10$ Earth radii for $K_{30}$, though the fact that density distributions can still be extracted for $r_p > 10$ Earth radii indicates that precise constraints on $K_{30}$ are not crucial.
+This strong dependence is expected from equation \ref{eqn:tidal-torque}; it is caused by the $(a_\mathcal{A}/D)^{\ell'}$ dependence of the tidal torque on distance $D$.
+
+By contrast, density moment uncertainty shows only a slight increase with $v_\infty$.
+This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
+There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
+(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
+These oscillations are large enough that the density uncertainty of figure \ref{fig:net-uncertainty} exceeds the weak threshold, but we do not treat this on a limit of $v_\infty$ since it is more directly related to the value of $\gamma$ at perigee.
+
+The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
+Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
+This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend across the parameters.
+
+\subsection{Rotational period}
+\label{sec:scan-period}
+
+In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$.
+Like the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, moment uncertainty varies periodically with $P_\omega$ due to the fact that the value of $\gamma$ at perigee depends on $P_\omega$.
+A large-scale trend is also visible in many parameters.
+$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast rotators tumble very little after perigee.
+This increases uncertainty on the $K_{2m}$ parameters, which are largely constrained by post-encounter tumbling.
+
+We expect that fast rotators would not tumble post-encounter because, for small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular first-order torque to force the asteroid to tumble.
+However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
+
+Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
+This is most visible in the figure for $K_{30}$.
+The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
+We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is $\tau_z$.
+Asymmetry is therefore more measurable than symmetry for these fast rotators.
+
+\subsection{Observational uncertainty}
+\label{sec:scan-uncertainty}
+Two parameters, $\sigma_\theta$ and $\sigma_P$, govern the observational uncertainty of the data set.
+These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_P$ represents the standard deviation of the rotational period.
+Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects uncertainty.
+This dependence is displayed in figure \ref{fig:scan-theta}.
+More precisely, we can ask if some error $\bm {\delta}_\omega$ is added to angular velocity $\omega$, does it affect results more strongly if it is parallel to $\omega$ (affects the period) or perpendicular (affects the spin pole direction)?
+
+Let $\delta = |\bm{\delta}_\omega| / |\bm \omega|$ and $\delta \ll 1$.
+Then if $\bm {\delta}_\omega \parallel \bm \omega$, it decreases the period $P_\omega$ by $P_\omega \delta$.
+This is a fractional change in period of $\delta$.
+If $\bm {\delta}_\omega \perp \bm \omega$, then the spin pole angle changes by $\delta$ radians.
+
+Comparing the $\sigma_P / P$ (fractional change in period) and $\sigma_\theta$ (spin pole angle) columns of figure \ref{fig:scan-observational}, one can see that a given value of $\sigma_\theta$ contributes a much smaller moment uncertainty than the same value of $\sigma_P/ P$.
+This is also visible in figure \ref{fig:net-uncertainty} for the lumpy model.
+In other words, if $\bm {\delta}_\omega \perp \bm \omega$ using the symbols defined above, then $\delta$ can be large.
+But if $\delta = |\bm{\delta}_\omega| / |\bm \omega|$, then $\delta$ must be very small.
+Period precision is therefore more vital than spin pole direction precision when it comes to decreasing density distribution uncertainties.
+
+% \subsection{Cadence}
+% \label{sec:scan-cadence}
+
+% The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
+We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+
+% Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
+We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
+We name this rough cadence limit $T_\text{cad}$.
+$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
+
+% We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
+How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
+
+% Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
+
+\subsection{Perigee gap}
+\label{sec:scan-gap}
+In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
+The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
+The resulting gap in data is intended to be captured by the $T_\text{gap}$ parameter of figure \ref{fig:scan-observational}, which deserves to be more fully defined.
+
+We mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
+To prevent lack of precision induced by lower amounts of data when $T_\text{gap}$ is large, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
+We cut around the perigee because tidal torque is the greatest at perigee, and we expect that part of the data set to be most valuable.
+Indeed, figure \ref{fig:scan-observational} shows that $K_{3m}$ especially are more uncertain for $T_\text{gap} \gtrsim 1.5$ hr.
+However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the thresholds, indicating that large amounts of data can be cut without compromising the methodology.
+
+\subsection{Initial spin pole}
+\label{sec:scan-spin}
+
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+
+In figure \ref{fig:spin-uncertainty}, we displayed density uncertainty as a function of initial spin pole direction, which showed large uncertainty for $\bm \Omega \parallel \unit Z$; i.e., initial spin pole perpendicular to the orbital plane.
+The density moment $1\sigma$ uncertainties $\sigma(K_{\ell m})$ as a function of spin pole direction are shown in figure \ref{fig:scan-spin}.
+These uncertainties are computed for 64 samples laid out on a Fibonacci sphere (green dots on lower-most panel) to ensure roughly even spacing.
 
@@
 The orange star indicates the reference spin pole.
-The red contours enclose regions the 20\% (dotted) and 100\% (solid) $\sigma_\rho / \rho$ cut-off.
-Posterior uncertainty depends similarly on initial spin pole direction for all parameters}
+Green dots are the sampled spin pole directions.
+The red contours enclose regions above the weak uncertainty threshold on $\sigma_\rho / \rho$.
+The strong threshold is never exceeded.
+Beyond the $\pm \unit Z$ increase in uncertainty, there is also increased moment uncertainty for $\pm \unit Y$.}
   \label{fig:scan-spin}
@@
 
-In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
+Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, as did the density uncertainty discussed in the main text.
+$\sigma(K_{20})$ especially exhibits this increase.
+However, many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
+This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
+By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
+$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
+In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
+As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling will result in greater uncertainty as observed.
 
-\subsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
-We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
-Fits of the type described in section \ref{sec:fit} were run for many values of $r_p$ and $v_\infty$ and the 1 and 2$\sigma$ posterior uncertainties are displayed in figure \ref{fig:scan-vex}.
-
-Figure \ref{fig:scan-vex} demonstrates that posterior uncertainty follows a slight trend for uncertainty to increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
-
-The figure shows much stronger dependence of parameter uncertainty on perigee distance, as expected by the factor of $(a_\mathcal{A}/D)^{\ell'}$ present in equation \ref{eqn:tidal-torque} and mentioned in section \ref{sec:tidal-torque}.
-For $r_p =7.9$ Earth radii, $\sigma_\rho/\rho$ reaches the 100\% threshold.
-The 20\% threshold is reached at lower 4.7 Earth radii.
-Much of this uncertainty is dominated by uncertainty in $K_{30}$, which is the parameter least constrained by tidal torque analysis.
-At $r_p \approx 10$ Earth radii, $K_{30}$ fills the prior distribution with uncertainty ranging from -1 to 1, visible by the sudden cut-off in uncertainty increase and the discontinuity of the $\sigma(K_{\ell m})$ curve there.
-
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend and will be seen in the following sections as well.
-
-The very strong dependence of $\sigma(K_{\ell m})$ on $r_p$ makes this analysis most useful to extract second-order moments on close encounters.
-Fortunately, in the case of Earth, these encounters are also likely to have the best associated observational uncertainty when above the horizon due to their proximity.
-The first-order moments can still be extracted at much larger perigee distances in our model.
-
-\subsection{Observational uncertainty}
-\label{sec:scan-uncertainty}
-Two parameters, $\sigma_\theta$ and $\sigma_\rho$, govern the observational uncertainty of the data set.
-These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_\rho$ represents the standard deviation of the ratio between the observed and true rotational velocities.
-Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects posterior uncertainty $\sigma(K_{\ell m})$.
-This dependence is displayed in figure \ref{fig:scan-theta}.
-
-For the case in which $\sigma_\rho$ is held fixed and $\sigma_\theta$ is varied, the figure shows that the dependence of $\sigma(K_{\ell m})$ on $\sigma_\theta$ is linear.
-The uncertainty threshold is reached at $\sigma_\theta = 2.8^\circ$ (0.5$^\circ$) for $\sigma_\rho / \rho=$100\% (20\%).
-The $K_{2m}$ uncertainties remain low, even for $\sigma_\theta \approx 1$, which is large enough that the spin pole has non-negligible probability to be observed in any direction.
-
-If $\sigma_\rho$ is allowed to vary instead, then $K_{30}$ reaches the 100\% and 20\% thresholds at $\sigma_\rho$ which correspond to period uncertainty of several milliseconds.
-At large period uncertainty, the PPDs begin to fill the prior and the posterior uncertainty $\sigma(K_{\ell m}$) is no longer linear with $\sigma_\rho$ (this is especially visible in the $K_{30}$) case.
-Otherwise, posterior uncertainty is proportional to $\sigma_\rho$.
-
-These data show that posterior uncertainty is extremely sensitive to observational uncertainty in period in our analysis.
-To precisely measure density moments, very accurate rotational period estimates would have to be made for every angular velocity data point.
-However this analysis does not study the effect of collecting more data after the encounter, or the correlations between different angular velocity measurements.
-If these correlations were taken into account, or a more accurate uncertainty model used which took into account the asteroid's location in the sky or its distance to Earth, then the precision limit we find here will be affected.
-
-\subsection{Asteroid shape}
-\label{sec:scan-shape}
-
-The true values of $K_{\ell m}$ and $a_\mathcal{A}$, which quantify the asteroid's physical properties, affect the posterior uncertainties.
-Here, we only investigate the sensitivity of $\sigma(K_{\ell m})$ to the first-order parameters and $a_\mathcal{A}$.
-These $K_{2m}$ moments can also be viewed as the axes of a uniform density triaxial ellipsoid (equation \ref{eqn:ellipsoid-axes}).
-
-In figure \ref{fig:scan-space-sigma}, we show the 1$\sigma$ posterior uncertainties as a function of $K_{20}$ and $K_{22}$, or alternatively $a/c$ and $b/c$.
-We use axis ratios rather than the values of $a$, $b$, and $c$ because axis ratios are independent of $a_\mathcal{A}$.
-The large $|K_{22}|$ sides of the $K_{2m}$-space plots correspond to asymmetric ellipsoids, as do the points far from the $a/c=b/c$ diagonal of the axis-ratio-space plots.
-The point corresponding to a sphere, which experiences no tidal torque and no tumbling, is at $K_{2m}=0$ and $a/c=b/c=1$.
-
-The figure shows large uncertainty in $\gamma_0$ for $K_{22}=0$, or $a/c=b/c$, because $K_{20}$ is rotationally symmetric around $\unit z$, and $\gamma_0$ is the initial orientation with respect to the $\unit z$ axis.
-The system then has no dependence on $\gamma_0$ when $K_{22}=0$.
-This induces degeneracy in the model which inflates uncertainties, not only in $\gamma_0$ but also the other components.
-
-To remove the inflated uncertainty, one could assume a rotationally symmetric asteroid, remove $\gamma_0$ as a parameter, and run a fit.
-For a nearly rotationally symmetric asteroid however, a new parametrization is necessary which does not contain the ill-constrained $\gamma_0$ parameter.
-This task is beyond the scope of this paper, so we mostly consider asymmetric asteroids throughout.
-
-Figure \ref{fig:scan-space-sigma} also shows low uncertainty for highly asymmetric asteroids, where $b/c$ and $a/c$ are very different (i.e., when $|K_{22}|$ is large).
-Additionally, $\sigma(K_{20})$ and $\sigma(K_{22})$ decrease for large $|K_{20}|$, which corresponds to large axis ratios in the ellipsoid case.
-
-Figure \ref{fig:scan-space-corr} displays the correlation between the first-order parameters.
-They show that $\gamma_0$ and $K_{22}$ are often correlated for asymmetric asteroids, while $\gamma_0$ and $K_{20}$ are usually not.
-This is expected as $K_{22}$ is dependent on the orientation of the asteroid and $K_{20}$ is not.
-They also show that $K_{22}$ and $K_{20}$ are usually correlated, and that $a/c$ and $b/c$ are highly correlated.
-The latter is expected due to the $1/c$ dependence.
-
-\begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr12.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr13.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-corr23.pdf}
-
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1b.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1a.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-ab.pdf}
-
-  \caption{Correlations between PPDs for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
-The first order parameters $K_{22}$ and $K_{20}$ are correlated, as are initial orientation $\gamma_0$ and $K_{22}$.}
-  \label{fig:scan-space-corr}
-\end{figure*}
-
-The fact that $K_{\ell m}$ are correlated indicates that, in order to correctly propagate density moment uncertainties to a density distribution, a full PPD is necessary.
-If only 1$\sigma$ uncertainty intervals for each parameter were used, density distribution uncertainty would be overestimated.
-This full PPD is produced by our fit process, but only the 1$\sigma$ uncertainties are displayed in this paper in most cases.
-
-Overall, the variation in the uncertainties on $K_{20}$ and $K_{22}$ (the first-order density moments) is present but largely smooth across their allowed parameter space, as is their correlation.
-It therefore seems reasonable to use the asymmetric asteroid shape as a stand-in for an unknown's asteroid shape when simulating an encounter, as we do in this paper.
-The uncertainty then can be expected to differ across other shapes by a factor of about two or less, as long as the degenerate, symmetric asteroid regime is avoided.
-
-On the other hand, the posterior uncertainty of $K_{3m}$ is much more strongly dependent on asteroid length $a_\mathcal{A}$.
-Figure \ref{fig:scan-am} displays posterior uncertainty $\sigma(K_{\ell m})$ as a function of $a_\mathcal{A}$.
-As was mention in section \ref{sec:tidal-torque}, the $K_{2m}$ parameters are insensitive to $a_\mathcal{A}$ since the $a_\mathcal{A}^2$ term in $\bm \tau$ (equation \ref{eqn:tidal-torque}) cancels the $a_\mathcal{A}^2$ in the MOI (equation \ref{eqn:moi}).
-The $K_{3m}$ uncertainty is strongly dependent on $a_\mathcal{A}$ for the same reason that it is dependent on $r_p$: the $(a_\mathcal{A}/D)^{\ell'}$ dependence of equation \ref{eqn:tidal-torque}.
-At $a_\mathcal{A} \leq 1100$ m, $\sigma_\rho/\rho \approx 100\%$.
-However, the 20\% cut-off is much lower, at $a_\mathcal{A} \leq 180$.
-Figure \ref{fig:scan-am} demonstrates why these cut-offs are so distant; for large $a_\mathcal{A}$, uncertainty decreases slowly with length.
-Only for small lengths is the uncertainty very large.
-This behaviour indicates that the uncertainty threshold is unlikely to fall much below 180 m even if other properties of the encounter are adjusted.
-
-For uniform density asteroids, large $a_\mathcal{A}$ is equivalent to large asteroid radius.
-In non-uniform density asteroids, large $a_\mathcal{A}$ can also be achieved by distributing the mass of the asteroid near the surface, because the $r^2$ term in the integrand of the definition of $a_\mathcal{A}$ causes the density of regions distant from the asteroid centre of mass to dominate $a_\mathcal{A}$.
-
-\subsection{Cadence}
-\label{sec:scan-cadence}
-
-The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
-We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-We name this rough cadence limit $T_\text{cad}$.
-$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
-
-We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
-How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
-
-Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
-
-\subsection{Perigee gap}
-\label{sec:scan-gap}
-In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
-The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
-Generally, angular velocity data can be collected when the asteroid is distant from the central body, where torque is low.
-There, the angular velocity evolution is dominated by torque-free precession dictated by the MOI components.
-That zero-torque data can still be used to fix $K_{20}$ and $K_{22}$ as in \cite{MOSKOVITZ2020113519}.
-However, $K_{3m}$ does not affect the precession periods (though they do affect the phase).
-We are therefore curious as to how our posterior uncertainties change due to lack of perigee data.
-
-To test this, we mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
-To prevent lack of precision on $K_{\ell m}$ induced by lower amounts of data for high $T_\text{gap}$, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
-We then fit the same asteroid model to the cut data for all $T_\text{gap}$ and plot posterior uncertainties $\sigma(K_{\ell m})$ in figure \ref{fig:observation-gap}.
-
-Since torque is greatest at perigee, we expect that region of the data to contain the most information about $K_{\ell m}$, and therefore uncertainty should increase monotonically with $T_\text{gap}$, which is seen in figure \ref{fig:observation-gap}.
-We also see that the first-order parameters are not as sensitive to $T_\text{gap}$ as the second-order parameters, because $K_{2m}$ are additionally constrained by torque-free precession after perigee.
-
-Most parameters show dramatically increased uncertainty in the $T \sim 1-2$ hr range.
-On the other hand, none of the uncertainties increase noticeably for $T \lesssim 1$ hr.
-Thirty minutes of dropped data is equivalent to fifteen dropped points for the simulated cadence of $\Delta t = 2$ minutes, showing that many data points can dropped from the data set at perigee before the uncertainty starts to increase.
-
-Qualitatively, \ref{fig:observation-gap} shows similar dependence of $\sigma(K_{\ell m})$ on $T_\text{gap}$ as on cadence $\Delta t$; they also both have cut-offs where uncertainty markedly increases, and both the $T_\text{gap}$ and $\Delta t$ cut-offs have qualitatively similar shapes although they occur at different values of $\Delta t$ and $T_\text{gap}$.
-This suggests that the factors that govern uncertainty due to cadence also may govern sensitivity to lack of data at perigee in a similar way.
-
-\subsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:scan-spin}, we display 1$\sigma$ posterior uncertainties as a function of the direction of $\bm \Omega_0$ mapped onto the unit sphere in the inertial frame.
-Our samples for $\bm \Omega_0$ were laid out on a Fibonacci sphere to ensure they were roughly evenly spaced (marked in figure \ref{fig:scan-spin-avg}).
-To highlight common features across the parameters, we also display the average 1$\sigma$ sensitivity in figure \ref{fig:scan-spin-avg}.
-The average is weighted such that the uncertainty map for each parameter contributes an equal amount (the weight of each map is set to one-tenth of the map's mean).
-This average map is presented in two different projections to allow data at $\unit Z$ to be read.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-mollweide.png}
-  \includegraphics[width=0.3\textwidth]{figs/spin-pole-avg-polar.png}
-  \caption{The weighted average of the uncertainties shown in figure \ref{fig:scan-spin}, in Mollweide (\textit{left}) and polar (\textit{right}) projections in the inertial frame.
-See text for a description of how the average was computed.
-Black dots indicate the Fibonacci-sphere-distributed locations of sample spin poles, and the orange star indicates the reference spin pole.
-The polar projection is centred at the north pole, or $\unit Z$.
-Posterior uncertainty is large near $\pm \unit Z$ and $\pm \unit Y$, but roughly constant elsewhere.}
-  \label{fig:scan-spin-avg}
-\end{figure*}
-
-Certain alignments of the body-fixed frame to the inertial frame lead to special conditions on torque, as discussed in section \ref{sec:tidal-torque}.
-For example, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \parallel \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-We relate this to the initial direction of $\bm \Omega_0$, via the approximation that $\bm \tau$ is small until perigee.
-Then $\bm \Omega_0 \parallel \unit Y$ and $\bm \Omega_0 \parallel \unit Z$ both lead to $\bm \tau \parallel \unit z$, and $\bm \Omega_0 \parallel \unit X$ leads to $\bm \tau = 0$.
-
-Figure \ref{fig:scan-spin-avg} shows area of increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, but not the $\unit X$ case.
-This indicates that $\bm \tau \parallel \unit z$ causes increased uncertainty.
-Physically, $\bm \tau \parallel \unit z$ only changes an asteroid's rotational period and does not cause it to tumble, eliminating the ability to discern MOI ratios from zero-torque precession after the encounter.
-If $\bm \tau = 0$ to first-order, then second-order $\bm \tau$ and non-perigee $\bm \tau$ will dominate, which may increase precision to these usually non-dominant parameters and therefore not have the same increasing effect on $\sigma(K_{\ell m})$.
-
-However, uncertainty does not vary by much more than a factor of two outside the imprecise regions of $\bm \Omega_0 \parallel \unit Z$ and $\bm \Omega_0 \parallel \unit Y$, though these regions are wide for some parameters.
-Within the imprecise regions, uncertainty can grow up to four times or more the uncertainty at other $\bm \Omega_0$ values, and can exceed the $\sigma(K_{3 m}) \approx 0.01$ threshold.
-The trends for are roughly consistent across parameters (figure \ref{fig:scan-spin}), leading to clearly visible imprecise regions in the average $\sigma(K_{\ell m})$ (figure \ref{fig:scan-spin-avg}).
-
-\subsection{Rotational period}
-\label{sec:scan-period}
-
-We also study the effect of the initial rotational period of the asteroid $P_\omega$ on posterior uncertainty $\sigma(K_{\ell m})$.
-In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$ for a range of periods typical of NEOs.
-Like figure \ref{fig:scan-vex}, depicting the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, figure \ref{fig:scan-period} shows small-scale variation in uncertainty due to the fact that varying the initial period changes the value of $\gamma$ at perigee, which affects uncertainty to a factor of about two.
-But a large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast-rotators tumble very little after perigee.
-This increases uncertainty on the $K_{2m}$ parameters, which are constrained by tumbling.
-
-We expect that quickly rotating asteroids would not tumble because, for small $P_\omega$, the dynamical variables $\bm D$, $\bm \omega$, $\alpha$, and $\beta$ vary much smaller than $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular, first-order torque to force the asteroid to tumble.
-However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
-This is most visible in the figure for $K_{30}$.
-The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is therefore $\tau_z$, which $K_{\ell 0}$ do not affect.
-
-The most severe effect of period on $\sigma(K_{\ell m})$ is in the low-period regime ($P_\omega < 4.3$ hr), but in this case, the most strongly affected parameters are $K_{2m}$, which are generally known better than $K_{3m}$.
-The effect on the imprecise parameters $K_{3m}$ is small, except for $K_{30}$.
-It therefore seems as though small-period asteroids are still candidates for observation, although high-period asteroids yield smaller uncertainty.
-
-\subsection{Central body oblateness}
-\label{sec:scan-oblateness}
-
-In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
-By assumption that $\mu_\mathcal{B} \gg \mu_\mathcal{A}$ (so that the asteroid orbit's focus is the centre of mass of the central body), we have $J_{1m} = 0$.
-The effect of central body non-sphericity, then, is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
-We expect these parameters to have small effect on the asteroid.
-
-Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
-$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:jlm}).
-
-$J_{\ell m}$ is defined in equation \ref{eqn:jlm} with respect to the asteroid orbit, not the principal axes of the central body.
-However, for an equatorial orbit, the central body principal axes coincide with the asteroid orbit frame and we may express $\epsilon$ simply in terms of $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
-For simplicity, we use this equatorial orbit case.
-Since an oblate ellipsoid is mirror-symmetric around all three axes, table \ref{tab:klm-symmetries} indicates that $J_{3m}$ are all zero.
-The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
-We do not consider these extra factors.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness.pdf}
-  \vfill
-  \includegraphics[width=0.88\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
-Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
-\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
-Also shown in both figures are the oblatenesses of reference Solar System bodies.
-Posterior uncertainty depends little on oblateness, but the best-fitting parameter estimates are affected enough by oblateness that oblateness must still be modelled.}
-  \label{fig:scan-oblateness}
-\end{figure}
-
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze posterior uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves.
-The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although posterior uncertainty does measurably decrease for oblate central bodies.
-The best-fitting lines match the uncertainties well, and they have slope of $[\Delta \sigma(K_{\ell m}) / \sigma(K_{\ell m})_{\epsilon=0}] / \Delta \epsilon = -0.06$ for $\gamma_0$, $-0.2$ for $K_{22}$, and $-0.3$ for $K_{20}$.
-The second-order parameters $K_{3m}$ likely depend on oblateness similarly, but fitting these parameters is computationally more expensive and we do not study them.
-
-Note that if an encounter is executed around one of the non-Earth objects noted in figure \ref{fig:scan-oblateness}, $a_\mathcal{B}$ and $\mu_\mathcal{B}$ will change in addition to $\epsilon$.
-These two parameters also affect the posterior uncertainty (section \ref{sec:jupiter-earth}), so the figure does not show that encounters with other bodies have the same precision as encounters with Earth; only that the difference in oblateness between the two bodies is of little concern.
-
-Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
-However, the bottom panel of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
-This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
-The difference between the PPD means and true parameters are shown.
-Posterior uncertainties are also shown as bands.
-The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
-This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
-Therefore, accurately modelling central-body oblateness to high precision is essential for accurate estimation of fit parameters.
-For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
-
-$J_{20}$, the parameter studied in this section, has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
-As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
-Extrapolating posterior uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
-Furthermore, $J_{22}$ is non-zero for this case, which likely decreases posterior uncertainty even more.
-
-This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect is beyond the scope of this paper.
-Without a moon to inflate the oblateness of the central body, planetary oblateness does not significantly improve posterior uncertainty.
-However, correct representation of oblateness is essential to accurately estimate $K_{\ell m}$.
+We may understand the cases of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\Omega$ is unchanged.
+Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
+Note that $\sigma(K_{20})$ in particular is not higher for $\bm \Omega_0 \parallel \unit Y$.
+This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque effects are dominated by non-perigee effects.
+This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
 
@@
 
-This figure contains animations to better display the density distributions shown in the main text.
+This appendix contains animations to better display the density distributions shown in the main text.
 Each frame represents a cross section perpendicular to the $\unit z$-axis, starting with negative $z$ and ending with positive $z$.
@@
 
-  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{first and thrid row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
+  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{first and third row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
 The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
@@
   \label{fig:animated-uniform}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.gif}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.gif}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.gif}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.gif}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.gif}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.gif}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.gif}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.gif}{Lumpy significance}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-move}.}
+  \label{fig:animated-move}
 \end{figure*}
@@
 
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.gif}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.gif}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.gif}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.gif}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.gif}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.gif}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.gif}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.gif}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-move}.}
-  \label{fig:animated-move}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
   \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-d.gif}{FE density} \hfill

### 2022-07-01 paper/main.tex
Added animated figure links
Paper draft complete

@@
 Using Markov Chain Monte Carlo fits, we perform injection-retrieval tests on these synthetic data to gain insights into the extent to which interior properties can be constrained.
-We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., moment of inertia and initial spin pole direction), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
-We find that high precision in rotational period estimates (order of milliseconds to seconds) are necessary for each cadence, and that large asteroids ($> 100$ m radius) with low perigees ($<20$ Earth radii) are necessary to resolve second-order density moments.
+We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
+We find that high precision in rotational period estimates (order of tens of milliseconds to seconds) are necessary for each cadence, and that low perigees ($\lesssim 18$ Earth radii) are necessary to resolve density distributions.
 \end{abstract}
@@
 There, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts density moments from the fit data.
-We note that these equations fo motion for an asteroid equation are novel and designed to be computationally efficient and valid to arbitrary order.
-We then describe three methods to generate full density distributions from the density moments.
+We note that these equations of motion for an asteroid equation are novel and designed to be computationally efficient and valid to arbitrary order.
+We then describe two methods to generate full density distributions from the density moments.
 In section \ref{sec:results}, we present the results of a series of injection-retrieval tests demonstrating the extent to which the properties of an asteroid chosen to generate synthetic spin data can be retrieved via our methodology.
 Finally, in section \ref{sec:discussion}, we assess the sensitivity of these constraints to various physical, observational, and methodological parameters to provide guidance for monitoring upcoming close encounters.
-We also test the density distribution extraction methods on several sample asteroids.
 
@@
 where $V_\mathcal{A}$ is the asteroid volume.
-We call these MOI and length scales in part because they obey $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$ where $\mu_\mathcal{A}$ is the mass of the asteroid for uniform asteroids.
+We call these MOI and length scales in part because they obey $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$ for uniform asteroids where $\mu_\mathcal{A}$ is the mass of the asteroid.
 Note that $a_\mathcal{A}$ is a function only of the surface of the asteroid, so that $a_\mathcal{A}$ is known if the surface is observed.
@@
 \end{equation}
-where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body, with the $a_\text{bulk}$ and $a_\text{surf}$ of equation \ref{eqn:klm} replaced by $a_\mathcal{B}$.
+where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body.
 Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no distant third-body perturbations.
@@
 The angular acceleration of the asteroid is proportional to $\bm \tau / I$ (equation \ref{eqn:omega-eom}), such that the $I_\mathcal{A}$ factor of equation \ref{eqn:tidal-torque} is canceled out.
-Thus, the observables do not depend explicitly on $I_\mathcal{A}$, nor on the asteroid mass.
+Thus, the observables do not depend explicitly on $I_\mathcal{A}$.
 
@@
 All parameters except (6) are assumed to be known to high accuracy.
-For example, $\bm \Omega_0$ could be extracted from pre-encounter light-curve data and $a_\text{surf}$ from a model for the asteroid's surface using radar.
+For example, $\bm \Omega_0$ could be extracted from pre-encounter light-curve data and $a_\mathcal{A}$ from a model for the asteroid's surface using radar.
 
@@
 We assume a short-axis rotation mode such that energy of the asteroid's rotation is minimized.
-This sets $\beta = 0$ and we can further choose $\alpha = 0$.
-Only the Euler angle $\gamma_0$ is necessary to provide initial data for the simulation.
+This sets two of the Euler angles equal to zer initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
 
-We begin our simulation at $D = 10 r_p$, with velocity predicted by Kepler's laws given by the orbital parameters.
+We begin our simulation at $D = 10 r_p$.
 Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
@@
 
-With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step
-\begin{equation}
-  dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
-\end{equation}
-The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
+With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, chosen to limit integration error to only ~100 times the floating point numerical error.
+% \begin{equation}
+%   dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
+% \end{equation}
+% The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
 The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
@@
 Then, expressing the observed spin vector $\bm \Omega$ in spherical coordinates, we draw the polar angle from a normal distribution with standard deviation $\sigma_\theta$ centred on zero and the azimuthal angle from a uniform distribution.
-We also draw the ratio $\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_P / P$, where $P = 2\pi \Omega$ is the period of the asteroid.
-Explicitly, the probability density function (PDF) of $\rho$ is
+We also draw the ratio $\Omega/\Omega^*$ from a log-normal distribution centred on one, with width $\sigma_P / P_\omega$, where $P_\omega = 2\pi / \Omega$ is the period of the asteroid.
+Explicitly, the probability density function (PDF) of $P_\omega$ is
 \begin{equation}
-  P(\rho) = \frac{1}{\rho\sqrt{2\pi (\sigma_P / P)^2}} \exp\parens{-\frac{\ln^2\rho}{2(\sigma_P / P)^2}}.
+  P(\rho) = \frac{1}{\rho\sqrt{2\pi (\sigma_P / P_\omega)^2}} \exp\parens{-\frac{\ln^2(\sigma_P / P_\omega)}{2(\sigma_P / P_\omega)^2}}.
 \end{equation}
 See figure \ref{fig:uncertainty-model} for an illustration of the uncertainty model.
-A log normal distribution is chosen such that $\rho > 0$, but since $\sigma_\rho \ll 1$ typically in our analysis, $P(\rho)$ is approximately Gaussian.
+A log normal distribution is chosen such that $P_\omega > 0$, but since $\sigma_P/P_\omega \ll 1$ typically in our analysis, the probability distribution is essentially Gaussian.
 
@@
   \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
-The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_\rho$.}
+The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_P/P$.}
   \label{fig:uncertainty-model}
@@
 Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
-Note that $\gamma_0$ is degenerate with $\gamma_0 + \pi/2$ because both of these align the asteroid principal axes with the body-fixed axes.
 The other bounds were $|K_{3m}| < 1$.
@@
 The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits in which the data quality was low, leading to degeneracies between the second order parameters ($K_{3 m}$).
+The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits computed for asteroid encounters in which degeneracies were present.
 This degeneracy could be removed by only fitting $K_{2m}$ instead.
@@
 Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
-Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused multiple values of $\gamma_0$ to be degenerate.
+Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused all values of $\gamma_0$ to be degenerate.
 Ensemble walkers were initialized near this local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
@@
 
-\subsection{Density distributon constraints}
+\subsection{Density distribution constraints}
 \label{sec:density-distro}
@@
 To best understand the potential density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
-To this end, we throughly outline two possible models and discuss two more in appendix \ref{app:other-models}.
+To this end, we thoroughly outline two possible models and discuss two more in appendix \ref{app:other-models}.
 
@@
 
-We rotate the known surface of the asteroid to a new frame called the ``hybrid frame'' by translating such that the known center of mass is at the origin, then rotating such that $\Omega_0$ points in the $+\unit z_\text{hybrid}$ direction and $\unit Y$ points in the $\unit Y_\text{hybrid}$ direction.
-Since $\Omega_0$ is exact, the surface in this hybrid frame is known exactly.
-The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}$ of $\gamma_0$.
+We rotate the known surface of the asteroid to a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame.
+(It has $\bm \Omega_0 \parallel \unit z_\text{hybrid}$ with third Euler angle $\gamma = 0$.) The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
 Such rotations affect density moments via
@@
 by equation \ref{eqn:ylm-rotation}.
-Thus, uncertainty on $K_{\ell m}^\mathrm{body-fixed}$ (obtained from the encounter data) can be translated to uncertainty in $K_{\ell m}^\mathrm{hybrid}$.
+Thus, uncertainties on $K_{\ell m}^\mathrm{body-fixed}$ and $\gamma_0$ (obtained from the encounter data) can be translated to uncertainty in $K_{\ell m}^\mathrm{hybrid}$.
 Henceforth, we will operate only in the hybrid frame and suppress the label.
@@
 When the $K_{3m}$ are extracted, 15 moments are known (excluding $K_{00}$).
-Since the asteroid mass cannot be determiend by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
+Since the asteroid mass cannot be determined by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
 Three more moments are redundant with the center of mass, such that only twelve finite elements are free.
@@
 To extract a density distribution, we use another MCMC given one of the two parametrizations of density distributions discussed below.
-The prior is set to be flat and nonzero for all configurations that obey the $0.25 < \rho < 3$ constraint.
+The prior is set to be flat and non-zero for all configurations that obey the $0.25 < \rho < 3$ constraint.
 The likelihood used is set equal to the multivariate-Gaussian approximation of the posterior distribution for $K_{\ell m}$, extracted from flyby data.
@@
 The constrained densities are easily computed since the asteroid mass $\mu_\mathcal{A}$ and the product $I_\mathcal{A}K_{\ell m}$ are both linear functions of $\rho_i$.
-Because $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, computing the constrained densities is simply a matrix inversion.
+Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, $I_\mathcal{A} K_{\ell m}$ is known for all the constrained moments, computing the corresponding constrained densities is simply a matrix inversion.
 
@@
 Suppose the asteroid is formed of $N$ constant-density, possibly overlapping ``lumps,'' enclosed within a constant-density substrate whose surface is visible to observers.
-The lumps and the substrate are described by the mass added to the substrate by a lump $\mu_i$, the position of its center of mass $\bm r_i$ (relative to the asteroid's center of mass), its density moments $K_{\ell m}^{(i)}$, and its length scale $a_i$.
+The substrate mass and added mass of the lumps are denoted by $\mu_i$, each with position $\bm r_i$ (relative to the asteroid's center of mass), density moments $K_{\ell m}^{(i)}$, and length $a_i$.
 Here, $i$ denotes the index of the lump where the substrate is $i=0$.
@@
 
-The translation rules of spherical harmonics give that the asteroid properties in the hybrid frame are
+The translation rules of spherical harmonics \cite{Gelderen1998TheSO} give that the asteroid properties in the hybrid frame are
 \begin{equation}
@@
 \end{equation}
-where the sum limits are $0 \leq l' \leq l$ and $-\ell' \leq m' \leq \ell'$. We also have total mass and center of mass constraints:
+where the unmarked sum limits are $0 \leq l' \leq l$ and $-\ell' \leq m' \leq \ell'$. We also have total mass and center of mass constraints:
 \begin{equation}
@@
 Additional rotational symmetries also constrain $K$, with the most extreme case being that spherical lumps have $K_{\ell m} = 0$ for $\ell > 0$.
-However, $K_{00}=1$ is guaranteed by definition, meaning that each spherical lump has only five DOF ($a_i$, $\mu_i$, and $\bm r_i$).
+$K_{00}=1$ is also guaranteed by definition, meaning that each spherical lump has only five DOF ($a_i$, $\mu_i$, and $\bm r_i$).
 The substrate has one degree of freedom, since only $\mu_0$ is unknown.
@@
 
-To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the asymmetric reference asteroid.
+To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the asymmetric reference asteroid (defined in appendix \ref{app:reference-configs}).
 We first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
-For both level of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
+For both stages of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
 
@@
 Uncertainty bands are also shown.
-The best fit results appear consistent with the data.}
+The best fit results are consistent with the data.}
   \label{fig:example-residuals}
@@
 The fit results are clearly consistent with the data.
-This figure is also instructing in revealing which points in the data set are most informative.
-The at-perigee data is irregular and reveals information about the density moments, and the post-perigee data shows torque-free tumbling behaviour which constrains $K_{2m}$ via the moment of inertia ratios, and also indirectly sheds light on the at-perigee data by constraining the rotational velocity the asteroid must have had when leaving the perigee.
+This figure also reveals which points in the data set are most informative.
+The at-perigee data is irregular and reveals information about the density moments, and the post-perigee data shows torque-free tumbling behaviour which constrains $K_{2m}$ via the MOI ratios as in Ref.~\cite{MOSKOVITZ2020113519}.
+The post-encounter periods and phase also indirectly sheds light on the at-perigee data by constraining the rotational velocity the asteroid must have had when leaving the perigee.
 
@@
 Note that the true parameters usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
-The PPDs are generally Gaussian and sometimes show correlation between parameters, but no continuous degeneracy occurs.
+The PPDs are generally Gaussian and sometimes show strong correlation between parameters, but no continuous degeneracy occurs.
 We performed 48 independent minimizations of the likelihood before the MCMC fit began, each with an initial point chosen randomly in the parameter space.
@@
 Five DOF were used rather than the maximum possible number of nine, and 20 different finite element layouts were used to generate sample density distributions to avoid dependence on the manually-chosen layout.
-The resulting density distributions and uncertainties are displayed in figure \ref{fig:uniform}.
+The resulting density distributions and uncertainties are displayed in figure \ref{fig:den-uniform}.
 \begin{figure*}
@@
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{first and thrid row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
+  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{first and third row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
 The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted.
 These figures are available in animated form in appendix figure \ref{fig:animated-uniform}.Extracted densities are generally within 10\% of the truth.}
@@
 
-The figure demonstrates that the finite element model successfully extracts density distributions consistent with the extracted density moments, as shown by the $\chi^2$ value per degree of freedom, $\chi^2_r$, depicted in the figure.
+The figure demonstrates that the finite element model successfully extracts density distributions consistent with the input density moments, as shown by the $\chi^2$ value per degree of freedom, $\chi^2_r$, depicted in the figure.
 These express the agreement of the density moments of the shown distributions with the posterior distributions for the density moments, produced by the MCMC described in section \ref{sec:fit}.
 $\chi^2_r = 0$ indicates that the moments of the shown distributions are exactly equal to the means of the moment posterior extracted by the MCMC.
-The accuracy of this model is robust for additional shapes, including non-ellipsoidal shapes.
+The accuracy of this model is robust for other shapes, including non-ellipsoidal shapes.
 
@@
 The dependence of this constraint on the observational set-up is discussed in section \ref{sec:fit-uncertainty}.
-In no place is the significance of these deviations from the true distribution greater than $0.3 \sigma$ (last column).
+In no place is the significance of these deviations from the true distribution greater than $1 \sigma$ (last column).
 
 The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform.
-These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of \jtd{number}) due to its few degrees of freedom.
+These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom.
 With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius.
 Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more apt to be contained inside a lump.
-In order for the lumpy model to converge given the unconstrained lump radius, we use the mass-weighted $\mu_i a_i \rightarrow 0$ as a model parameter rather than the lump length $a_i$.
 
 We also explore model behaviour in non-uniform density asteroids.
-We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario, but we place a solid core of radius $\SI{500}{\meter}$ and density three times the surrounding density at the center of the asteroid.
+We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario, but we place a solid core of radius $\SI{300}{\meter}$ and density 50\% greater than the surrounding density, 500 m away from the center of the asteroid.
 This changes the asteroid density moments.
-New density moments are extracted via the process described in section \ref{sec:fit} and the finite-element and lumpy models are used to extract density distributions shown in figure \ref{fig:center-core}.
+New density moments are extracted via the process described in section \ref{sec:fit} and the finite-element and lumpy models are used to extract density distributions shown in figure \ref{fig:den-move}.
+
 \begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-r}
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-fe-r}
 
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-r}
+  \includegraphics[width=0.24\linewidth]{figs/move-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/move-l-r}
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-den-sph}.
-The core is successfully extracted in all cases.}
-  \label{fig:den-sph}
+These figures are available in animated form in appendix figure \ref{fig:animated-move}.
+The core is successfully extracted.}
+  \label{fig:den-move}
 \end{figure*}
 
-Once again, figure \ref{fig:center-core} shows that the model results are successful in that they reproduce the extracted density moments ($\chi^2_r$ is low).
-However, the density distributions extracted by the finite model match the true distributions less well.
-The deviation the true density extends to as much as 35\% in some locations, leading to a maximum significance of $0.86\sigma$.
+Once again, figure \ref{fig:den-move} shows that the model results are successful in that they reproduce the extracted density moments ($\chi^2_r$ is low).
+However, the density distributions extracted by the finite model matches the true distributions less well.
+The deviation the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
 The distributions are consistent with the true distribution, but the finite element model has distributed the core into the rest of the asteroid so that the peak density is lowered.
 
-However, the lumpy model is designed to detect discrete changes in density distribution, and identifies the boundary of the core very accurately.
-Deviations from the truth are less than 0.2\%, with uncertainties about 10\% of the local density at maximum and usually much lower.
-THe significance of the deviations is around 20\%, as it was in figure \ref{fig:uniform} where the extracted distribution again matched the truth.
+On the other hand, the lumpy model is designed to detect discrete changes in density distribution, and identifies the boundary of the core very accurately.
+Deviations from the truth are around $10^{-5}$ of the local density, with uncertainties about 1\% of the local density at maximum and usually much lower.
+The significance of the deviations is around 30\%, as it was in figure \ref{fig:den-uniform} where the extracted distribution again matched the truth.
 The low uncertainty is caused by the small number of degrees of freedom (2) of the lumpy model.
@@
 The question of which encounters are most suited to this methodology is of great interest, as is the question of how observational campaigns can be designed to best take advantage of an asteroid to maximize the success of this methodology.
-We investigate a mix of encounter parameters, from observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage) and physical asteroid properties (the encounter's orbital properties, the asteroid's true shape, and its initial rotational velocity), and discuss their effect on the uncertainty of this methodology's results.
+We investigate physical asteroid properties (the encounter's orbital properties, the asteroid's true shape, and its initial rotational velocity) and observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage), and discuss their effect on the uncertainty of this methodology's results.
 
@@
 However, its physical relevance is not obvious.
-The density distribution uncertainty $\sigma_\rho / \rho$ is defined as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each made using a different sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
-The median uncertainty over this map, divided by the local density, is taken to represent the density distribution uncertainty.
+The density distribution uncertainty $\sigma_\rho / \rho$ is defined as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each corresponding to a random sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
+The median of the uncertainty divided by the local density over this map is taken to represent the density distribution uncertainty.
 This measure of uncertainty is more physically relevant than moment uncertainty, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
-We therefore investigate both the moment uncertainty and the density distribution uncertainty.
+We therefore investigate both measures of uncertainty.
 
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
-  % \includegraphics[width=0.5\linewidth]{figs/spin-unc.pdf}
+  \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
   \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction.
-The benchmark uncertainty thresholds (\textit{red lines}) are shown, as is the reference spin pole direction (\textit{\jtd{What symbol?}}).
-\jtd{Summary}}
+The weak uncertainty thresholds (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
+Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
   \label{fig:spin-uncertainty}
-\end{figure*}
+\end{figure}
 
@@
 Density distributions from both the lumpy and finite element models are used.
-The benchmark uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
+The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
 Te vertical black dotted lines are the property values of the reference asteroid.
@@
 
-Table \ref{tab:threshold-summary} displays the encounter properties which beyond which the density distribution uncertainty rises above two sample values we term the ``weak'' and ``strong'' thresholds.
+Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds.
 These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
@@
 $\sim 300$ m and Apophis will encounter Earth in 2029.
-Apophis's perigee of 5--6 Earth radii also obeys the weak and strong constraints.
-In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} also shows a threshold on spin pole direction.
-\jtd{Describe}.
+Apophis's perigee of 5--6 Earth radii also obeys the weak and strong constraints \cite{giorgini2008predicting}.
+In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} also shows a threshold on initial spin pole direction.
+The poles (i.e., angular velocities perpendicular to the orbital plane) lead to greater uncertainty and this is the only region which rises above the weak uncertainty threshold.
 
@@
 This could be accomplished by multiple, precise angular velocity measurements from multiple telescopes, or by increasing the time between observations to maximize the change in period between observations.
-Increasing the data set size to include more post-flyby tumbling data would also relieve the burden on each data point for uncertainty to be so low.
+Acknowledging and correcting for correlations in uncertainty between data points could also reduce uncertainty.
+Increasing the data set size to include more post-flyby tumbling data would also increase precision on some parameters, especially $K_{2m}$, without requiring such high period uncertainty.
+
 On the other hand, the cadence of observations $\Delta t$ and the presence of gaps in the data $T_\text{gap}$ do not affect results as strongly.
@@
 
-Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\sigma_\rho / \rho$) for the encounter perigee $r_p$and observational precision $\sigma_P$ and $\sigma_\theta$.
-These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are much more volatile.
+Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\sigma_\rho / \rho$) for the encounter perigee $r_p$ and observational precision $\sigma_P$ and $\sigma_\theta$.
+These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are more volatile.
 The figure also displays the stark difference between density uncertainty as computed by the lumpy model and the finite element model.
@@
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+The vertical dotted line indicates the reference asteroid values.
+The red vertical lines indicate the uncertainty thresholds.}
   \label{fig:scan-perigee}
@@
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
-The vertical dashed line indicates the reference asteroid values.
-The red vertical lines indicate when $\sigma(K_{3m}) =0.01$.}
+The vertical dotted line indicates the reference asteroid values.
+The red vertical lines indicate the uncertainty thresholds.}
     \label{fig:scan-rho}
@@
 
-  \caption{1$\sigma$ posterior uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as black points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
-Symmetric asteroids ($K_{22}=0$ or $a/c=b/c$) show increased posterior uncertainty, but otherwise posterior uncertainty is roughly constant.}
+  \caption{1$\sigma$ moment uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
+Also shown as points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
+Symmetric asteroids ($K_{22}=0$ or $a/c=b/c$) show increased moment uncertainty, but otherwise moment uncertainty is roughly constant.}
   \label{fig:scan-space-sigma}
@@
 To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate moment uncertainty as well.
-Figures \ref{scan-physical} and \ref{scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ on physical and observational encounter properties respectively.
+Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ on physical and observational encounter properties respectively.
 The thresholds of table \ref{tab:threshold-summary} are depicted as red lines.
@@
 
-Figure \ref{scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $K_{3m}$.
+Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $K_{3m}$.
 For instance, $\sigma(K_{2m})$ is constant as $a_\mathcal{A}$ is varied despite a dramatic increase in $\sigma(K_{3m})$ for low $a_\mathcal{A}$.
@@
 However, the roles are reversed for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and here $\sigma_\rho /\rho$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
-This fact has several consequences.
-First of all, if more post-flyby tumbling data is collected, this will place stronger constraints on $K_{2m}$ and not $K_{3m}$.
-If so much data is available that $K_{2m}$ have essentially no uncertainty, then uncertainty on $K_{3m}$ will be dominant and the most constraining parameters will change.
+It follows that if more post-flyby tumbling data is collected, placing stronger constraints on $K_{2m}$ rather than $K_{3m}$, then $K_{2m}$ at some point might have essentially no uncertainty.
+In this case, uncertainty on $K_{3m}$ will be dominant and the most constraining parameters will change.
 Rotational period $P_\omega$ will cease to be a vital parameter but asteroid length $a_\mathcal{A}$ will be because $\sigma(K_{3m})$ are much more dependent on $a_\mathcal{A}$ than $P_\omega$.
 
-Figure \ref{fig:scan-physical} also demonstrates exponentially increasing $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
+Figure \ref{fig:scan-physical} also demonstrates an accelerating increase of $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
 (Figure \ref{fig:net-uncertainty} also indicated this, since $\sigma_\rho / \rho$ falls for low perigee in both the lumpy and the finite element model).
-Dependence of moment uncertainty on data precision $\sigma_P$ and $\sigma_\theta$ is similarly exponential as shown by figure \ref{fig:scan-observational}.
-However, moment uncertainty on cadence $\Delta t$ and gaps in data $T_\text{gap}$ are less exponential.
+Dependence of moment uncertainty on data precision $\sigma_P$ and $\sigma_\theta$ is linear as shown by figure \ref{fig:scan-observational}.
+However, moment uncertainty on cadence $\Delta t$ and gaps in data $T_\text{gap}$ does not increase so quickly.
 These tend to increase in uncertainty at some characteristic time scale of $\Delta t \sim 15 -40$ min for cadence and $1-2$ hr for $T_\text{gap}$.
 As long as $\Delta t$ and $T_\text{gap}$ are below these time scales, uncertainty is not strongly dependent on them.
+The time scales might be a function of the period of the asteroid or the orbital time scales $r_p / v_\infty$ and $\mu_\mathcal{B} / v_\infty^3$.
 
@@
 $\gamma_0$ is therefore poorly constrained as $K_{22} \rightarrow 0$.
-Figure \ref{fig:uniform} revealed that density distributions can still be extracted for symmetric asteroids, but to reduce uncertainty, the moments must be re-parametrized to remove this degeneracy if this methodology is to be run on nearly symmetric asteroids.
+Figure \ref{fig:den-uniform} revealed that density distributions can still be extracted for symmetric asteroids, but to reduce uncertainty, the moments must be re-parametrized to remove this degeneracy if this methodology is to be run on nearly symmetric asteroids.
 Beyond this dependence on $K_{2m}$, almost no moment uncertainty variation is visible, indicating that this methodology will give similar results given many asteroid shapes distinct from the reference asteroid.
+
+These figures are more thoroughly interpreted in appendix \ref{app:uncertainty-dependence}, which also describes how the data was collected.
+
+\subsection{Central body oblateness}
+\label{sec:scan-oblateness}
+
+In all the above studies, we assumed a spherical planet ($J_{\ell m} = 0$ for $\ell \geq 1$).
+$J_{1m} = 0$ is enforced by the coordinate definitions, so the effect of central body non-sphericity is limited to the $J_{2m}$ terms and damped by a factor of $(a_\mathcal{B} / D)^2$.
+We expect these parameters to have small effect on the asteroid behaviour.
+
+Here, we define oblateness as $\epsilon = (I_z - I_x)/(\mu_\mathcal{B} R_\mathcal{B}^2)$, where $I_{x,y,z}$ are the central body moments of inertia along the principal axes, and $I_x = I_y$.
+$R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:aa}).
+For an equatorial orbit, $\epsilon$ and the central body density moments (equation \ref{eqn:jlm}) are related by $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
+Since an oblate ellipsoid is mirror-symmetric around all three axes, $J_{3m}$ are all zero.
+The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
+We do not consider these extra factors.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\columnwidth]{figs/oblateness.pdf}
+  \vfill
+  \includegraphics[width=0.7\columnwidth]{figs/oblateness-differ.pdf}
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
+Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
+\textit{Bottom}: The difference between PPD means extracted from a zero-oblateness model and the true parameters given data with true oblateness $\epsilon_\text{true} \neq 0$.
+Also shown in both figures are the oblatenesses of reference Solar System bodies.
+Moment uncertainty depends little on oblateness, but the best-fitting parameter estimates are affected enough by oblateness that oblateness must still be modelled.}
+  \label{fig:scan-oblateness}
+\end{figure}
+
+Given this conversion between $\epsilon$ and $J_{20}$, we analyze moment uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for moment uncertainty as a function of oblateness.
+The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although moment uncertainty does measurably decrease for oblate central bodies.
+
+Given the small effect of $\epsilon$ on $K_{\ell m}$, it might be tempting to neglect the planetary oblateness when fitting $K_{\ell m}$ to data.
+However, the bottom panel of figure \ref{fig:scan-oblateness} demonstrates that doing so is invalid.
+This figure displays $K_{\ell m}$ as extracted by a fit assuming $\epsilon = 0$, but run on data generated with non-zero $\epsilon$.
+The difference between the PPD means and true parameters are shown.
+Moment uncertainties are also shown as bands.
+The figure shows that even for low (Earth-scale) oblateness, the fit results are inconsistent with the true $K_{\ell m}$ values, since $\Delta K_{\ell m} = 0$ is not contained in the 2$\sigma$ band.
+This effect is much worse for large oblateness, growing to a difference on the order of $\mathcal{O}(100)\sigma$ for Jupiter's oblateness.
+Therefore, accurately modelling central body oblateness to high precision is essential for the accurate estimation of fit parameters.
+For non-equatorial orbits, with $J_{22} \neq 0$, we also expect $J_{22}$ to affect the accuracy of the fit results to a similar degree, with the additional requirement of using the correct asteroid orbital plane.
+
+$J_{20}$ has a slightly more general definition than oblateness.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
+As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
+Extrapolating moment uncertainties via the slopes of the best fit lines given earlier yields a reduction in $\sigma(K_{2m})$ by about 25\%.
+Furthermore, $J_{22}$ is non-zero for this case, which likely decreases moment uncertainty even more.
+
+This analysis suggests that large moons such as ours can improve fit quality, but further study of this effect (e.g., investigating an encounter that approaches both the Earth and the Moon closely) is beyond the scope of this paper.
 
@@
 The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
-The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in section \ref{sec:scan-orbit}, so we keep it at the reference value.
-The ratio between the posterior uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
-In all cases, the Jupiter posteriors are more uncertain than Earth posteriors.
+The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in figure \ref{fig:scan-physical}, so we keep it at the reference value.
+The ratio between the moment uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
+In all cases, the Jupiter-encounter moments are more uncertain than Earth-encounter moments.
 
@@
   \end{tabular}
-  \caption{Ratio of posterior uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.
+  \caption{Ratio of moment uncertainty for all density moments $K_{\ell m}$ between an Earth encounter and a Jupiter encounter with identical properties except for an increased perigee.
 Observational uncertainty and cadence are assumed to be equivalent for the Jupiter and Earth encounters.
@@
 The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
-If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant (as in this case, where $r_p/a_\mathcal{B}=5$), then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
+If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant as in this case, then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
 Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
@@
 
-The $K_{\ell 0}$ components differ in that the posterior uncertainty increase for a Jupiter encounter over an Earth encounter is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
+The $K_{\ell 0}$ components differ in that the moment uncertainty increase for a Jupiter encounter over an Earth encounter is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
 In fact, $K_{30}$ essentially fills the prior.
-In section \ref{sec:scan-spin}, we noted that $K_{\ell 0}$ is particularly uncertain when the asteroid does not tumble after the perigee.
+In section \ref{sec:scan-spin}, we note that $K_{\ell 0}$ is particularly uncertain when the asteroid does not tumble after the perigee.
 In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
@@
 There are additional effects of central body mass which are not captured in this analysis.
-For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (large $a_\mathcal{A}$, small $r_p$, etc.).
-The distribution of $r_p$ in this encounter sample will also change; the ratio of the orbit impact parameter (the distance between the orbit asymptotes and the central body) to perijove distance is
+For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (small $r_p$, large $a_\mathcal{A}$, etc.).
+This can be seen via the following equation for the area of the keyhole through which the asteroid must fly to have a perijove $r_p$ low enough to meet the uncertainty threshold:
 \begin{equation}
-  \frac{b}{r_p} = \sqrt{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
+  A = 2 \pi r_p^2 \parens{1+2\frac{G\mu_\mathcal{B}}{r_p v_\infty^2}}.
+  \label{eqn:impact-parameter}
 \end{equation}
-It was mentioned above that the observable perigee distance $r_p$ increases with $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, so that $\frac{b}{r_p}$ is larger for more massive planets and therefore the same impact parameter leads to lower perijove.
+Table \ref{tab:jupiter-uncertainty} suggested that moment uncertainty is roughly $\sigma(K_{\ell m}) \propto a_\mathcal{B}^{\ell - 1} / r_p$, so that constant uncertainty roughly implies $r_p \propto a_\mathcal{B}^{1-2}$.
+Since $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, equation \ref{eqn:impact-parameter} dictates that $b/r_p$ will increase faster than $a_\mathcal{B}$ as $\mu_B$ is increased.
+It follows that the number of encounters that meet the uncertainty threshold will grow substantially.
 Other effects, such as a change in the physical properties of the encountering asteroids or decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
-Which of these contradicting effects dominates is not immediately clear, and depends on the asteroid population near Jupiter and the observation method.
+Which of these contradicting effects dominates depends on the asteroid population near Jupiter and the observation method.
 
@@
 The number of elements $N$ used for the finite element model can be freely chosen.
-As discussed in section \ref{sec:finite-element}, seven of these are fixed by various constraints on the asteroid density distribution.
+As discussed in section \ref{sec:density-distro}, seven of these are fixed by various constraints on the asteroid density distribution.
 There are 16 density moments with $\ell \leq 3$, so $N=16$ with nine DOF is the largest number of parameters the model can support.
@@
 Figure \ref{fig:dof-scan} displays the distribution of $\sigma_\rho$, $\Delta \rho$, and the significance of the deviations from the truth ($\Delta \rho / \sigma_\rho$) over the asteroid.
+Median values of these three measures are shown, as well as bands that enclose the values for 68\% of the asteroid.
 
@@
   \includegraphics[width=\linewidth]{figs/dof-scan.pdf}
-  \caption{The average uncertainty $\sigma_\rho$ and deviation from the truth $\Delta \rho$ of density distributions extracted by the finite element model with varying degrees of freedom.
+  \caption{The average uncertainty divided by local density $\sigma_\rho / \rho$ and deviation from the truth divided by local density $\Delta \rho / \rho$ of density distributions extracted by the finite element model with varying degrees of freedom.
 5 DOF appears to optimize the trade-off between the model-induced uncertainty caused by too many DOF and the inaccuracy caused by too few.}
@@
 The trend of uncertainty, deviation, and significance as a function of $\sigma_P$ is also discontinuous for few DOF, because in these cases the properties of the output distribution are strongly dependent on the initial choice of uncertainty of the initial choice of grids, and more than five grids are necessary to remove that dependence.
-This discontinuity is most noticeable for 3 and 2 DOFs, which also produce deviations from the true density distribution of the highest significance.
-We use 5 DOFs throughout this paper, produce the most precise results while still accurately reproducing the asteroid density distribution.
+This discontinuity is most noticeable for 3 and 2 DOFs.
+We use 5 DOFs throughout this paper, because it produces the most precise results in this test while still accurately reproducing the asteroid density distribution.
 5 DOFs corresponds to $N=12$ finite elements.
@@
 This is a further example of how the extracted asteroid density distribution is strongly dependent on the choice of model, and one of the reasons why we display the uncertainties of density moments in section \ref{sec:fit-uncertainty} rather than density distribution uncertainty.
-This moment uncertainty is not prone to the same model-dependent plateau.
+Moment uncertainty is not prone to the same model-dependent plateau.
 
@@
 In section \ref{sec:asym-density}, we displayed uniform and non-uniform density distributions extracted via the finite element and single-lump lumpy model.
-Here we highlight the success of the model in two other scenarios.
+Here we highlight the properties of the model in two other scenarios.
 
 \begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-r}
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-r}
 
-  \includegraphics[width=0.24\linewidth]{figs/move-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-r}
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-d}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-s}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-u}\hfill
+  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-r}
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-move}.
-The core is successfully extracted in all cases.}
-  \label{fig:den-move}
+These figures are available in animated form in appendix figure \ref{fig:animated-sph}.
+The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
+  \label{fig:den-sph}
 \end{figure*}
 
-Figure \ref{fig:den-move} shows density distributions extracted via the finite element model and the lumpy model for an off-center core.
-Results are similar to the centred core shown in \ref{fig:den-sph} in that the moments of the resulting density distribution are consistent with those extracted from the encounter data (i.e., $\chi^2_r$ is low).
+Figure \ref{fig:den-sph} shows density distributions extracted via the finite element model and the lumpy model for a centred core of density three times the surrounding density.
+Results are similar to the off-center core shown in \ref{fig:den-move} in that the moments of the resulting density distribution are consistent with those extracted from the encounter data (i.e., $\chi^2_r$ is low).
 Again, the finite element model does not isolate the lump, instead spreading the excess mass over the right side of the asteroid.
-The ability of the lumpy model to isolate the core is rooted in the fact that the shape of the asteroid is offset from the center of mass by a fixed amount with no uncertainty attached.
-The position of the lump is therefore set to balance the offset of the surrounding asteroid medium; the only free parameter is the lump's mass, which determines this offset.
-The assumption that the asteroid's center of mass is precisely known is rooted stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
-If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain.
+Unlike the off-center core example, the lumpy model is not able to recover the true distribution either.
+It produces deviations from the true density distribution of roughly the same size as the finite element model, with large significance.
+This is because, for centred, spherical cores, the core mass is degenerate with the core's radius.
+Uncertainty is therefore larger for the centred core than for the off-center core and the maximum density deviation over the asteroid is larger.
 
-To assess the lumpy model when the positions of the lump are not as certain as in this off-center case, we consider an asteroid with two lumps of radius 300 m and density three times the surrounding density.
+The success of the model in the off-center case was due to the fact that the shape of the asteroid was offset from the center of mass by a corresponding amount, assumed to be known to great precision.
+The position of the lump was therefore observed up to one free parameter: the lump's mass.
+The assumption that the asteroid's center of mass is so precisely known is rooted stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
+If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain for the off-center case.
+
+To assess the lumpy model when the positions of the lump are not as certain as in the off-center case, we consider an asteroid with two lumps of radii 300 m and density three times the surrounding density.
 Each lump is located 500 meters from the center of the asteroid, so that they counterbalance and the asteroid's observed center of mass is its surface's centroid.
-The lumpy model with $N=2$ lumps then inherits three additional DOF corresponding to one lump's position (the other lump is fixed to counterbalance it) as well as two more from the additional lump's radius and mass.
-The model thus has seven DOF, in contrast to the 5 DOF of the finite element model.
+This model has seven DOF, in contrast to the 5 DOF of the finite element model.
 Both models are run on this asteroid and the resulting distributions are shown in figure \ref{fig:den-double}.
@@
 These radius and mass values are also close to the true values.
-The model places the lumps correctly in the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in very high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
+The model places the lumps correctly in the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
 Note that $\chi^2_r$ remains low despite the lumpy model's misplacement of the lumps.
@@
 The moments estimated by the MCMC fit to encounter data are not perfectly correct, resulting in a deviation of a few hundred meters in lump location.
-Overall, the figures show that even the poorly constrained $K_{3m}$ moments can be used to determine features of the asteroid density, given a well-chosen model.
 
@@
 We also created two models --- the finite element model and the lumpy model --- to translate these density moments back into density distributions.
+Uncertainties are propagated throughout the pipeline.
 Since this problem is underdetermined, the models give different results and were contrasted.
@@
 The precise thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
-We also discussed how these thresholds could be eased by changes in observational behaviour such as lengthening the data set, or by physical asteroid properties such as a closer encounter or an initially tumbling state.
+The properties that do not affect density uncertainty as much, such as the central body oblateness, must still be accurately represented in simulations to avoid errors in the pipeline results.
+We also discussed how these thresholds could be eased by changes in observational behaviour such as lengthening the data set, or by physical asteroid properties such as a closer encounter, an initially tumbling state, or the presence of a massive moon such as Earth's.
 If the thresholds were eased enough, then the asteroid length would become an important threshold as well.

### 2022-07-01 code/thresholds/thresholds.py

@@ -31,7 +31,7 @@ INCREASING = {
 LABELS = {
     "scan-perigee": "$r_p$ (Earth radii)",
     "probe-s-theta": "$\sigma_\\theta$",
-    "probe-s-rho": "$\sigma_P / P$",
+    "probe-s-rho": "$\sigma_P / P_\omega$",
     "scan-cadence": "$\Delta t$ (min)",
     "scan-period": "$P_\omega$ (hr)",
     "scan-am": "$a_\\mathcal{A}$ (m)",
@@ -67,7 +67,7 @@ EXCLUDE = ["scan-vex"]
 PULL = False
 DIRECTORIES = ["lumpy", "fe"]
 
-THRESHOLDS = ((1e-4, "gray"),(1e-3, "k"),)
+THRESHOLDS = ((1e-4, "dashed"),(1e-3, "solid"),)
 
 if PULL:
     for directory in DIRECTORIES:
@@ -103,8 +103,8 @@ for directory in DIRECTORIES:
         axs[i].fill_between(xs, uncs[:,1], uncs[:,3], alpha=0.3, color=COLORS[directory], label='foo')
 
         if directory == "lumpy":
-            for threshold, color in THRESHOLDS:
-                axs[i].axhline(y=threshold, c='r', linewidth=1)
+            for threshold, style in THRESHOLDS:
+                axs[i].axhline(y=threshold, c='r', linewidth=1, linestyle=style)
                 if name in EXCLUDE:
                     continue
 

### 2022-07-01 data/all-fig/compile.py

@@ -13,7 +13,7 @@ param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re
 axis_names = {
     "scan-perigee": "$r_p$ (Earth radii)",
     "probe-s-theta": "$\sigma_\\theta$",
-    "probe-s-rho": "$\sigma_P / P$",
+    "probe-s-rho": "$\sigma_P / P_\omega$",
     "scan-cadence": "$\Delta t$ (min)",
     "scan-period": "$P_\omega$ (hr)",
     "scan-am": "$a_\\mathcal{A}$ (m)",

### 2022-07-01 paper/gifs/get-figs.py

@@ -15,8 +15,8 @@ for line in f.readlines():
     if not os.path.isfile(ROOT + path):
         print("Could not find " + path)
         continue
-    if path[-4:] not in [".eps", ".pdf"]:
-        print("WARNING: .eps or .pdf file formats are preferred")
+    if path[-4:] not in [".gif"]:
+        print("WARNING: .gif file formats are preferred")
     shutil.copyfile(ROOT+path, ROOT + "paper/gifs/"+name)
 
 f.close()

### 2022-07-05 paper/appendices.tex
MNRAS submission

@@
 In this appendix, we derive the equations of motion used to simulate the asteroid angular velocity during the encounter.
-In particular, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its ``density moments'' (section \ref{sec:moments}).
+In particular, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its density moments (section \ref{sec:moments}).
 Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}) and write the equations of motion for the system (section \ref{sec:eom}).
@@
     \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid.
-Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold and uppercase).
+Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold lines and uppercase).
 The origins are co-located for demonstration purposes.}
@@
 
-In the next section, it will be shown that only certain parameters of the asteroid density distribution affect tidal torque called ``density moments.'' First, we define the un-normalized spherical harmonics $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
-The regular and irregular spherical harmonics then defined as
+The un-normalized spherical harmonics are defined as $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
+The regular and irregular spherical harmonics are further defined as
 \begin{equation}
@@
 By contrast, $J_{\ell m}$ should be computed in the inertial frame.
-The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations \ref{eqn:aa} and \ref{eqn:ia}, but they could also be set to any other scales of the proper units, e.g.
+The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations \ref{eqn:aa} and \ref{eqn:ia}, but they could also be set to any other scales of the same units, e.g.
 $a_\mathcal{B}$ equal to the central body radius and $I_\mathcal{B} = \mu_\mathcal{B}a_\mathcal{B}^2$, where $\mu_\mathcal{B}$ is the central body mass.
@@
 We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
-The gravitational potential field of the asteroid can be written entirely in terms of $K_{\ell m}$ and $a_\mathcal{A}$, so we expect not to need any information about the density distribution of the asteroid beyond these parameters to compute tidal torque.
 
@@
 The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$, $K_{20}$, and $K_{00}$.
-The first two are related to the MOI around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in \ref{eqn:tidal-torque}.
+The first two are related to the MOI around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in equation \ref{eqn:tidal-torque}.
 
@@
 Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first-order.
-Also, the component $\tau_z$ oscillates, so that for certain values of $\alpha$ and $\gamma$, $\bm \tau = 0.$ This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
+This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
 
@@
 One is for $\alpha = \phi$ (or $\alpha = \pi + \phi$), where $\phi$ is the angle between the asteroid and the perigee.
-In this case, $\tau = 0$ to first-order.
-The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$ and $\tau_z$ oscillates.
+In this case, $\bm \tau = 0$ to first-order.
+The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$.
 At perigee ($\phi=0$), these conditions are equivalent to $\unit z \parallel \unit X$ and $\unit z \parallel \unit Y$ respectively.
@@
 
-Note that equation \ref{eqn:omega-eom} is independent of $a_\mathcal{A}$ to first-order in $\bm \tau$, because $I_{j} \propto a_\mathcal{A}^2$ for all $j$ and $\bm \tau \propto a_\mathcal{A}^2$.
-Therefore, scaling $a_\mathcal{A}$ merely scales the value of the sub-leading-order contributions to $\bm \tau$.
-
-\section{Reference asteroid configurations}
-\label{app:reference-configs}
-
-Except when otherwise mentioned, we use the following asteroid encounter parameters.
-Many of the parameter choices are made to maximize the quality of observations (a close orbit, large asteroid, etc.) This is so that our analysis is most sensitive to the affect changing these parameters to the methodology's output.
-
-\begin{enumerate}
-  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
-This orbit was chosen to roughly match that of 99942 Apophis \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, discovered on June 19, 2004 by R.
-A.
-Tucker, D.
-J.
-Tholen, and F.
-Bernardi.
-These orbital parameters correspond to an eccentricity of 3.88.
-The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
-Further work must therefore be done to apply this analysis to Apophis.
-  \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 0.01$ and $\sigma_P / P = 10^{-7}$.
-  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
-  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
-For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
-The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
-The second case and its reflection are called the asymmetric cases.
-Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
-If not specified, we use the $a < b$ case.
-Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
-\end{enumerate}
-
-The surface of a spherical asteroid with this rotational period and $a_\mathcal{A}$ rotates at $\SI{25}{\centi\meter\per\second}$ at the equator.
-The asymmetric and symmetric ellipsoids have maximum equatorial velocities of $\SI{36}{\centi\meter\per\second}$ and $\SI{27}{\centi\meter\per\second}$ respectively.
-
 \section{Additional density distribution models}
@@
 \subsection{Nearly-uniform model}
-In this nearly-uniform model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$, which can be chosen manually.
+In this ``nearly-uniform'' model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$, which can be chosen manually.
 Any prior distribution can be chosen, but the following prior is both interesting and numerically efficient.
@@
 As part of our prior, we require that the asteroid density distribution satisfy $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$.
-This constraint is desirable as it encourages nearly uniform density distributions; recall that a perfectly uniform asteroid always satisfies this constraint.
+This constraint is desirable as it is obeyed for uniform density distributions.
 To define the prior, we divide the asteroid into $n \gg 1$ small regions of volume $V$, each with position $\bm r_i$ and density $\rho_i = \delta_i + 1$.
 Setting the mass of the asteroid equal to its volume, the average density is 1, so $\delta_i$ is the difference between the average and local density.
-We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$ centred on zero to minimize non-uniformity, i.e.
+We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$, centred on zero to minimize non-uniformity, i.e.
 \begin{equation}
@@
 \end{equation}
-Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$ and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations.
-Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as $\bm K = M \bm \delta + \bm C$, where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions.
+Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$, and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations.
+Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as
+\begin{equation}
+  \bm K = M \bm \delta + \bm C,
+  \label{eqn:nu-matrix}
+\end{equation}
+where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions.
 Some of the components of $\bm K$, such as $I_\mathcal{A}$, $\mu_\mathcal{A}$, and $K_{1m}$, are constraints.
 We treat the other components as parameters of the model.
-The task is then to find $\bm \delta$ that satisfies this matrix equation and maximizes $f(\bm \delta)$.
-But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (and the maximum of $f$) is the minimum of $|\bm \delta|^2$.
-The value of $\bm \delta$ that obeys the constraints and minimizes its norm is given by the Moore-Penrose inverse:
+The task is then to find $\bm \delta$ that satisfies equation \ref{eqn:nu-matrix} and maximizes $f(\bm \delta)$.
+But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (also the maximum of $f$) is the minimum of $|\bm \delta|^2$.
+This shortest value of $\bm \delta$ that obeys equation \ref{eqn:nu-matrix} is given by the Moore-Penrose inverse:
 \begin{equation}
@@
 
-The probability distribution of $\bm K$ is given by the output of the fit described in section \ref{sec:fit}.
-The parameters of this model, $\bm K$, might differ from this distribution due to the additional constraint that the density fall in realistic values.
-This can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
+The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
+ can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
 
 \subsection{Harmonic model}
-For the harmonic model, we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
+This the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
 We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.
@@
 Imposing constraints on these moments is also necessary.
-The choice of mass is enforced merely by enforcing equation \ref{eqn:harmonic-mass}.
+The choice of mass is enforced via equation \ref{eqn:harmonic-mass}.
 We impose bounds on $\rho(\bm r)$ by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid.
-This can be done by parametrizing the asteroid surface as a function of two variables and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
+This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
+
+\section{Reference asteroid configurations}
+\label{app:reference-configs}
+
+Except when otherwise mentioned, we use the following asteroid encounter parameters.
+Many of the parameter choices are made to increase the precision of observations (a close orbit, large asteroid, etc.) This is so that our methodology's output is most sensitive to changes in these parameters.
+
+\begin{enumerate}
+  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
+This orbit was chosen to roughly match that of Apophis.
+These orbital parameters correspond to an eccentricity of 3.88.
+  \item An initial roll of $\gamma_0=\pi/8$.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 10^{-2}$ and $\sigma_P / P = 10^{-7}$.
+  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
+  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
+The second case and its reflection are called the asymmetric cases.
+Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
+If not specified, we use the $a < b$ case.
+Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
+\end{enumerate}
+
+The surface of a spherical asteroid with this rotational period and $a_\mathcal{A}$ rotates at $\SI{25}{\centi\meter\per\second}$ at the equator.
+The asymmetric and symmetric ellipsoids have maximum equatorial velocities of $\SI{36}{\centi\meter\per\second}$ and $\SI{27}{\centi\meter\per\second}$ respectively.
 
@@
 
+\section{Animated density distributions}
+
+This appendix contains animations to better display the density distributions shown in the main text.
+Each frame represents a cross section perpendicular to the $\unit z$-axis, starting with negative $z$ and ending with positive $z$.
+All densities are divided by the mean asteroid density.
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-d.mp4}{FE asymmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-s.mp4}{FE asymmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-u.mp4}{FE asymmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-r.mp4}{FE asymmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-d.mp4}{Lumpy asymmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-s.mp4}{Lumpy asymmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-u.mp4}{Lumpy asymmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-r.mp4}{Lumpy asymmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-d.mp4}{FE symmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-s.mp4}{FE symmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-u.mp4}{FE symmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-r.mp4}{FE symmetric significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-d.mp4}{Lumpy symmetric density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-s.mp4}{Lumpy symmetric deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-u.mp4}{Lumpy symmetric uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-r.mp4}{Lumpy symmetric significance}
+
+  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) reference asteroids.
+The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-uniform}.}
+  \label{fig:animated-uniform}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.mp4}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.mp4}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.mp4}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.mp4}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.mp4}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.mp4}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.mp4}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.mp4}{Lumpy significance}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-move}.}
+  \label{fig:animated-move}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-d.mp4}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-s.mp4}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-u.mp4}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-r.mp4}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-d.mp4}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-s.mp4}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-u.mp4}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-r.mp4}{Lumpy significance}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-sph}.}
+  \label{fig:animated-sph}
+\end{figure*}
+
+\begin{figure*}
+  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-d.mp4}{FE density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-s.mp4}{FE deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-u.mp4}{FE uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-r.mp4}{FE significance}
+
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-d.mp4}{Lumpy density} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-s.mp4}{Lumpy deviation} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-u.mp4}{Lumpy uncertainty} \hfill
+  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-r.mp4}{Lumpy significance}
+
+  \caption{Density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+Animated form of figure \ref{fig:den-double}.}
+  \label{fig:animated-double}
+\end{figure*}
+
 \section{Uncertainty dependence on encounter properties}
@@
 (The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
-These oscillations are large enough that the density uncertainty of figure \ref{fig:net-uncertainty} exceeds the weak threshold, but we do not treat this on a limit of $v_\infty$ since it is more directly related to the value of $\gamma$ at perigee.
+These oscillations are large enough that the density uncertainty of figure \ref{fig:net-uncertainty} exceeds the strong threshold, but we do not treat this on a limit of $v_\infty$ since it is more directly related to the value of $\gamma$ at perigee.
 
@@
 We expect that fast rotators would not tumble post-encounter because, for small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, we can integrate the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$, which gives no secular first-order torque to force the asteroid to tumble.
+Approximating each variable as constant over one full rotation of $\gamma$, the integral of the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ gives no secular first-order torque to force the asteroid to tumble.
 However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
@@
 Asymmetry is therefore more measurable than symmetry for these fast rotators.
+
+\subsection{Initial spin pole}
+\label{sec:scan-spin}
+
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+
+In figure \ref{fig:spin-uncertainty}, we displayed density uncertainty as a function of initial spin pole direction, which showed large uncertainty for $\bm \Omega \parallel \unit Z$; i.e., initial spin pole perpendicular to the orbital plane.
+The density moment $1\sigma$ uncertainties $\sigma(K_{\ell m})$ as a function of spin pole direction are shown in figure \ref{fig:scan-spin}.
+These uncertainties are computed for 64 samples laid out on a Fibonacci sphere (green dots on lower-most panel) to ensure roughly even spacing.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/spin-pole}
+  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
+All maps are made in the Mollweide projection.
+The orange star indicates the reference spin pole.
+Green dots are the sampled spin pole directions.
+The red contours enclose regions above the strong uncertainty threshold on $\sigma_\rho / \rho$.
+The weak threshold is never exceeded.
+Beyond the $\pm \unit Z$ increase in uncertainty, there is also increased moment uncertainty for $\pm \unit Y$.}
+  \label{fig:scan-spin}
+\end{figure*}
+
+Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, as did the density uncertainty discussed in the main text.
+$\sigma(K_{20})$ especially exhibits this increase.
+However, many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
+This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
+By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
+$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
+In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel \unit Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
+As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling results in greater uncertainty.
+
+We may understand the case of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\bm \Omega$ is unchanged.
+Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
+This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque is dominated by non-perigee effects.
+This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
 
@@
 However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the thresholds, indicating that large amounts of data can be cut without compromising the methodology.
-
-\subsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:spin-uncertainty}, we displayed density uncertainty as a function of initial spin pole direction, which showed large uncertainty for $\bm \Omega \parallel \unit Z$; i.e., initial spin pole perpendicular to the orbital plane.
-The density moment $1\sigma$ uncertainties $\sigma(K_{\ell m})$ as a function of spin pole direction are shown in figure \ref{fig:scan-spin}.
-These uncertainties are computed for 64 samples laid out on a Fibonacci sphere (green dots on lower-most panel) to ensure roughly even spacing.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/spin-pole.png}
-  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection.
-The orange star indicates the reference spin pole.
-Green dots are the sampled spin pole directions.
-The red contours enclose regions above the weak uncertainty threshold on $\sigma_\rho / \rho$.
-The strong threshold is never exceeded.
-Beyond the $\pm \unit Z$ increase in uncertainty, there is also increased moment uncertainty for $\pm \unit Y$.}
-  \label{fig:scan-spin}
-\end{figure*}
-
-Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, as did the density uncertainty discussed in the main text.
-$\sigma(K_{20})$ especially exhibits this increase.
-However, many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
-This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
-By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
-In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
-As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling will result in greater uncertainty as observed.
-
-We may understand the cases of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\Omega$ is unchanged.
-Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
-Note that $\sigma(K_{20})$ in particular is not higher for $\bm \Omega_0 \parallel \unit Y$.
-This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque effects are dominated by non-perigee effects.
-This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
-
-\section{Animated density distributions}
-
-This appendix contains animations to better display the density distributions shown in the main text.
-Each frame represents a cross section perpendicular to the $\unit z$-axis, starting with negative $z$ and ending with positive $z$.
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-d}{FE asymmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-s}{FE asymmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-u}{FE asymmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-r}{FE asymmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-d}{FE symmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-s}{FE symmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-u}{FE symmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-r}{FE symmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-d}{Lumpy asymmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-s}{Lumpy asymmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-u}{Lumpy asymmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-r}{Lumpy asymmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-d}{Lumpy symmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-s}{Lumpy symmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-u}{Lumpy symmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-r}{Lumpy symmetric significance}
-
-  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{first and third row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
-The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-uniform}.}
-  \label{fig:animated-uniform}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.gif}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.gif}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.gif}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.gif}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.gif}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.gif}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.gif}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.gif}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-move}.}
-  \label{fig:animated-move}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-d.gif}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-s.gif}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-u.gif}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-r.gif}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-d.gif}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-s.gif}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-u.gif}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-r.gif}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-sph}.}
-  \label{fig:animated-sph}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-d.gif}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-s.gif}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-u.gif}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-r.gif}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-d.gif}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-s.gif}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-u.gif}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-r.gif}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-double}.}
-  \label{fig:animated-double}
-\end{figure*}

### 2022-07-05 code/thresholds/thresholds.py

@@ -110,6 +110,7 @@ for directory in DIRECTORIES:
 
                 locs = np.where(use_uncs > threshold)[0]
                 if len(locs) == 0:
+                    print(f"\t-\t\t", end="")
                     continue
                 if INCREASING[name]:
                     index = np.min(locs)

### 2022-07-05 data/probe-space/compile-abc.py

@@ -164,6 +164,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/corrab.pdf")
+    plt.savefig("compile-figs/corrab.png")
 
     corr01_max = max(np.nanmax(corr01_data), -np.nanmin(corr01_data))
     plt.figure(figsize=FIG_SIZE)
@@ -177,6 +178,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/corr1a.pdf")
+    plt.savefig("compile-figs/corr1a.png")
 
     corr02_max = max(np.nanmax(corr02_data), -np.nanmin(corr02_data))
     plt.figure(figsize=FIG_SIZE)
@@ -190,6 +192,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/corr1b.pdf")
+    plt.savefig("compile-figs/corr1b.png")
 
     plt.figure(figsize=FIG_SIZE)
     flat_sig_0 = np.array(sigma0_data).reshape(-1) * 1e6
@@ -203,6 +206,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/theta-1-ab-sigma.pdf")
+    plt.savefig("compile-figs/theta-1-ab-sigma.png")
 
     plt.figure(figsize=FIG_SIZE)
     c = plt.contourf(X, Y, np.array(sigma1_data) * 10**6, levels=20, cmap="Purples_r")
@@ -215,6 +219,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/theta-a-sigma.pdf")
+    plt.savefig("compile-figs/theta-a-sigma.png")
 
     plt.figure(figsize=FIG_SIZE)
     c = plt.contourf(X, Y, np.array(sigma2_data) * 10**6, levels=20, cmap="Purples_r")
@@ -227,6 +232,7 @@ def covariance():
     plt.ylim(1, 6.7)
     plt.tight_layout()
     plt.savefig("compile-figs/theta-b-sigma.pdf")
+    plt.savefig("compile-figs/theta-b-sigma.png")
 
 
 if __name__ == "__main__":

### 2022-07-05 data/probe-space/compile.py

@@ -103,6 +103,7 @@ def plot_pdf(index):
         #    ax.set_xticklabels([])
 
     fig.savefig("theta-{}-hists.pdf".format(index))
+    fig.savefig("theta-{}-hists.png".format(index))
 
 def covariance():
     side_length = int(-0.5 + np.sqrt(1 + 8 * len(names)) / 2)
@@ -208,6 +209,7 @@ def covariance():
     plt.ylabel("$K_{20}$")
     plt.tight_layout()
     plt.savefig("compile-figs/corr23.pdf")
+    plt.savefig("compile-figs/corr23.png")
 
     corr01_max = max(np.nanmax(corr01_data), -np.nanmin(corr01_data))
     plt.figure(figsize=FIG_SIZE)
@@ -221,6 +223,7 @@ def covariance():
     plt.ylabel("$K_{20}$")
     plt.tight_layout()
     plt.savefig("compile-figs/corr12.pdf")
+    plt.savefig("compile-figs/corr12.png")
 
     corr02_max = max(np.nanmax(corr02_data), -np.nanmin(corr02_data))
     plt.figure(figsize=FIG_SIZE)
@@ -234,6 +237,7 @@ def covariance():
     plt.ylabel("$K_{20}$")
     plt.tight_layout()
     plt.savefig("compile-figs/corr13.pdf")
+    plt.savefig("compile-figs/corr13.png")
 
     plt.figure(figsize=FIG_SIZE)
     flat_sig_0 = np.array(sigma0_data).reshape(-1) * 1e6
@@ -247,6 +251,7 @@ def covariance():
     plt.ylabel("$K_{20}$")
     plt.tight_layout()
     plt.savefig("compile-figs/theta-1-sigma.pdf")
+    plt.savefig("compile-figs/theta-1-sigma.png")
 
     plt.figure(figsize=FIG_SIZE)
     c = plt.contourf(X, Y, np.array(sigma1_data) * 1e6, levels=np.linspace(0, np.nanmax(sigma1_data) * 1e6, NUM_LEVELS), cmap='Purples_r')
@@ -259,6 +264,7 @@ def covariance():
     plt.ylabel("$K_{20}$")
     plt.tight_layout()
     plt.savefig("compile-figs/theta-2-sigma.pdf")
+    plt.savefig("compile-figs/theta-2-sigma.png")
 
     plt.figure(figsize=FIG_SIZE)
[…]

### 2022-07-29 old-papers/draft3/appendices.tex
Redownload and new runs adjusted for gamma_0

--- 2022-04-25 old-papers/draft2/appendices.tex
@@
 Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal moment of inertia.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal moment of inertia (this is the short axis mode, to use the vocabulary of Ref.~\cite{kaasalainen2001interpretation}).
 In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
@@
 
-% \section{The cadence cut-off}
-% \label{app:cadence-tests}
+\section{Additional density moments}
 
-% In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-We mentioned that this cadence cut-off is likely a function both of the rotational period of the asteroid and the time spent near perigee.
-We study this cut-off in closer detail in this appendix.
+A finite element model was defined in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
+However, other models are possible.
+Here, we outline three models that can be explored to further understand the underdetermined density distribution of the asteroid: the likelihood model, the harmonic model, and the lumpy model.
+The first two produce smooth distributions, unlike the discrete transitions that occur for the finite element model across the boundaries of the elements.
+The lumpy model produces discrete distributions like the finite element model, but the locations of the elements are included as free parameters.
 
-% We measure the dependence of the cadence cut-off on rotational period by varying the period $P_\omega$ and reproducing figure \ref{fig:scan-cadence}; i.e., we run many simulations of the changed $P_\omega$ with different cadences and plot the posterior fit uncertainty $\sigma$ as a function of cadence $\Delta t$.
-Specifically, we use $P_\omega = 5$ hr and 20 hr, roughly double and half of the reference $P_\omega=9$ hr.
-The resulting curves of $\sigma(\Delta t)$ are shown in figure \ref{fig:cad-period}, with each normalized so that their maximum values is 1 so that changes to $\sigma$ induced by the change in $P_\omega$ that are not a function of $\Delta t$ (i.e., those studied in section \ref{sec:scan-period}), are removed; they are irrelevant here.
+\jtd{Describe these}
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[height=0.89\textheight]{figs/cad-period.pdf}
-%   \caption{1$\sigma$ confidence intervals plotted as a function of cadence $\Delta t$ for periods of 9 hr (the reference asteroid, solid coloured lines), and 5 hours (dotted lines), and 20 hours (dashed lines).
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-%   \label{fig:cad-period}
-% \end{figure}
+\section{The cadence cut-off}
+\label{app:cadence-tests}
 
-% We also wish to capture dependence on the time spent by the asteroid near perigee, but we do not wish to change the orbit shape or central body, because this may induce other effects that could also affect the cadence plot.
-Instead, we (un-physically) manipulate the speed at which the asteroid moves through the orbit.
-In one instance, the asteroid's path is artificially slowed by a factor of 2, which we denote as $t_\text{spin}/t_\text{orbit}=0.5$; in the other instance, $t_\text{spin}/t_\text{orbit}=2$, meaning that the orbit is sped up.
-This approach of changing the speed of the orbit is meant to approximate changes to $T_p$ defined in equation \ref{eqn:tp}.
-The posterior uncertainties for these two cases and the original case are shown as a function of $\Delta t$ in figure \ref{fig:cad-speed}.
-Again, $\sigma$ is normalized so that $\Delta t$-independent variations are removed.
-The $t_\text{spin}/t_\text{orbit}=2$ uncertainties begin to fill the prior distribution for large $\Delta t$ for some parameters, which can be seen by discontinuous variation in the dotted line of figure \ref{fig:cad-speed}.
+In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
+In this appendix, we discuss the location of this cadence cut-off as a function of the physical parameters of the asteroid.
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[height=0.89\textheight]{figs/cad-speed.pdf}
-%   \caption{1$\sigma$ confidence intervals plotted as a function of the orbit time scaling $t_\text{spin}/t_\text{orbit}$ for no scaling (the reference asteroid, solid coloured lines), time doubling (dotted lines), and halving (dashed lines).
-See text for the definition of $t_\text{spin}/t_\text{orbit}$.
-Confidence intervals have been normalized for the sake of comparison, so that the maximum for each curve is 1.}
-%   \label{fig:cad-speed}
-% \end{figure}
+In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
+Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
+In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
 
-% Many of the curves in figures \ref{fig:cad-period} and \ref{fig:cad-speed} show a cadence cut-off at $T_\text{cad} \sim 30-60$ min.
-Those that show no cut-off (i.e., they merely smoothly increase over $\Delta t$) may in fact exhibit a cut-off $T_\text{cad} > 60$ min, which is off the plot.
-By comparing $\sigma(\Delta t)$ for a specific parameter, we see that the dashed lines often (but not always) reach the cadence cut-off at lower $\Delta t$ than the solid line.
-For example, in figure \ref{fig:cad-period}, this effect is especially clear for $K_{22}$, $K_{33}$, $\Im K_{22}$, and $\Re K_{31}$, but the opposite appears for $\Re K_{32}$.
-The dashed curves are significant in both figures because they represent larger $\sigma$ cases ($P_\omega=5$ hours, or $t_\text{spin}/t_\text{orbit}=2$); section \ref{sec:scan-period} reveals that fast rotators lead to larger $\sigma$, and $t_\text{spin}/t_\text{orbit} > 1$ leads to larger $\sigma$ because of the presence of less perigee data.
-It therefore appears that small $P_\omega$ and small times spent at perigee move the cadence cut-off to smaller $T_\text{cad}$.
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.48\textwidth]{figs/cad-period.pdf}\hfill
+  \includegraphics[width=0.48\textwidth]{figs/cad-speed.pdf}
+  \caption{Contour plots showing posterior uncertainties as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
+The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
+The solid (dotted) red line represents the $\sigma_\rho / \rho = 100\%$ (20\%) threshold.
+Cadence cut-off depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
+  \label{fig:cad-contour}
+\end{figure*}
 
-% The dependence of the exact location of the cadence cut-off is likely more complicated than the above analysis indicates.
-However, large uncertainties induced by small $P_\omega$ or large $t_\text{spin}/t_\text{orbit}$ makes it difficult to produce data which are not affected by the finite size of the prior (as figure \ref{fig:scan-vex} is) to study these regimes.
-Computation time and random variation in $\sigma$ also limits us.
-We therefore do not attempt to explore the dependence between $T_\text{cad}$ and the encounter parameters further.
-If a future analysis does require a detailed understanding of how cadence affects uncertainty for a specific encounter, our simulation and fit process can be run given the parameters of the encounter in question in a similar manner to section \ref{sec:scan-cadence} to yield more information.
+Figure \ref{fig:cad-contour} demonstrates that large rotational period produces high $T_\text{cad}$.
+The dependence on $P_\omega$ agrees with the fact that large rotational periods for fixed cadence lead to better posterior uncertainty, discussed in section \ref{sec:scan-period}.
+The figure also demonstrates that for large $P_\omega$, $T_\text{cad}$ depends less strongly on $P_\text{omega}$ and may even reverse its dependence such that increasing $P_\text{omega}$ decreases $T_\text{omega}$.
+In all cases except $\Re K_{33}$, at least constant-$\sigma(K_{\ell m})$ contour is seen to curve back such that $\Delta t$ decreases as a function of $P_\text{omega}$ for large $P_\text{omega}$.
+In these regions the cadence cut-off also dulls, as shown by the spreading of the constant-$\sigma(K_{\ell m})$ contours in this region.
+
+ The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was defined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
+The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
+$t_\text{spin} / t_\text{orbit} > 1$ corresponds to a faster orbit, and $t_\text{spin} / t_\text{orbit} < 1$ corresponds to a slower orbit.
+With this unphysical process, we isolate the effect of the amount of time spent near perigee on posterior uncertainty, without inheriting additional affects that would have been caused by the orbit changing shape.
+
+The right panel of figure \ref{fig:cad-contour} shows a stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
+It appears that even slightly slower orbits sharply increases $T_\text{cad}$.
+This effect is both due to the asteroid spending greater time in the high-torque, near-perigee region, and the larger data set that can be collected for slow orbits.
+However, if the orbit speed is changed by adjusting its parameters ($v_\infty$, $r_p$) or the central body mass $\mu_\mathcal{B}$, then the orbit shape will also change.
+This induces other effects studied in the main text and will complicate the trend observed here.
+Unlike the $P_\omega$ case, the cadence cut-off does not visibly broaden as a function of $t_\text{spin} / t_\text{orbit}$.
+It appears that the increased orbit speed merely shifts $T_\text{cad}$ rather than changing its sharpness.
 

### 2022-07-29 paper/main.tex
Redownload and new runs adjusted for gamma_0

@@
 \begin{keywords}
-  minor planets, asteroids: general -- methods: data analysis
+  minor planets, asteroids: general -- methods: data analysis -- planets and satellites: interiors
 \end{keywords}
@@
 Since the tidal torque acting on an asteroid during an encounter depends on the interior mass distribution, the careful monitoring of angular velocity variations during an encounter also presents a window into the interior properties of asteroids.
-The gravitational two-body system has
-been studied in the context of tidal torque to different orders
-and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-Further studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
+The gravitational two-body system has been studied in the context of tidal torque to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+Further theoretical studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
+
+Angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
+Orbital and physical properties, including MOI ratios have also been extracted for asteroid 99942 Apophis, discovered on June 19, 2004 by R.
+A.
+Tucker, D.
+J.
+Tholen, and F.
+Bernardi \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, and on target to encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
 However, density distribution features beyond the moment of inertia (MOI) ratios have not yet been extracted for any asteroid encounters.
-More research is needed to study in what cases these effects are observable, and what
-factors generally inhibit observation of these new features.
-
-Angular velocity perturbations have been observed and
-used to extract asteroid properties in several cases, including
-for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid
-binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
-Orbital and physical properties, including MOI ratios have also been extracted for 99942 Apophis, which will closely encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
-It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity \cite{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
+More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
+It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity in particular \cite{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
 
@@
 There, we describe a simulation used to integrate the equations of motion and produce synthetic data of angular velocity over time, followed by a Markov Chain Monte Carlo (MCMC) fit process which  extracts density moments from the fit data.
-We note that these equations of motion for an asteroid equation are novel and designed to be computationally efficient and valid to arbitrary order.
 We then describe two methods to generate full density distributions from the density moments.
@@
 Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no distant third-body perturbations.
+This is a novel derivation and accurate to arbitrary order in $D$.
 
@@
 
-The angular acceleration of the asteroid is proportional to $\bm \tau / I$ (equation \ref{eqn:omega-eom}), such that the $I_\mathcal{A}$ factor of equation \ref{eqn:tidal-torque} is canceled out.
+The angular acceleration of the asteroid is proportional to $\bm \tau / I$ such that the $I_\mathcal{A}$ factor of equation \ref{eqn:tidal-torque} is canceled out.
 Thus, the observables do not depend explicitly on $I_\mathcal{A}$.
@@
 We assume a short-axis rotation mode such that energy of the asteroid's rotation is minimized.
-This sets two of the Euler angles equal to zer initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
+This sets two of the Euler angles equal to zer0 initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
 
@@
   \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-0.5, 2.5) node[anchor=center] {$\rho \Omega^*$};
+  \draw (-0.5, 2.5) node[anchor=center] {$|\bm \Omega|$};
 
@@
   \caption{Diagram in the inertial frame of the uncertainty model used to define the probability that the true spin vector $\bm \Omega^*$ should be observed as $\bm \Omega$.
-The parameter $\theta$ is drawn from a Gaussian with width $\sigma_\theta$, and $\rho$ is drawn from a log normal distribution with width $\sigma_P/P$.}
+The angular uncertainty on $\theta$ and period uncertainty on $|\bm \Omega|$ are treated separately.}
   \label{fig:uncertainty-model}
@@
 \label{sec:fit}
-Given synthetic data, an Affine Invariant MCMC Ensemble sampler was used to generate PPDs from flat priors.
+Given synthetic data, an Affine Invariant MCMC Ensemble sampler was used to generate Posterior Probability Distributions (PPDs) from flat priors.
 We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
-Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), and were bounded by $|\gamma_0| < \pi/4$, and bounds on $K_{2 m}$ given in equation \ref{eqn:parameter-bounds}.
-The other bounds were $|K_{3m}| < 1$.
+Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in equation \ref{eqn:parameter-bounds}.
+We also use $|K_{3m}| < 1$.
 In general, spin data is most sensitive to $\gamma_0$ and $K_{2m}$, which we call the ``first-order parameters.'' We call $K_{3m}$ the ``second-order parameters.''
 
-The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations computed so far was more than 100 times the autocorrelation time.
+The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations already computed was more than 100 times the autocorrelation time.
 The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits computed for asteroid encounters in which degeneracies were present.
 This degeneracy could be removed by only fitting $K_{2m}$ instead.
-About $10^4$ iterations was often sufficient, which generally consumed about 7 hours of computation time on a super computer running 16 threads on 8 cores.
+About $10^4$ iterations was often sufficient.
 
@@
 
-To further ensure convergence, we minimized with respect to data truncated after perigee at double the perigee distance.
-This cut-off was manually chosen.
-The minimum was then further refined by minimizing based on the full data, with the previous minimum as the initial estimate.
+To further ensure convergence, we first minimized with respect to data truncated soon after perigee.
+After convergence, we refined the minimum by minimizing based on the full data, with the previous minimum as the initial estimate.
 
@@
 The asteroid density distribution $\rho_\mathcal{A}(\bm r)$ is not uniquely constrained via tidal torque interactions because only the density moments $K_{\ell m}$ contribute to equation \ref{eqn:tidal-torque}.
-For example, since the mass of the asteroid is unconstrained, $\rho_\mathcal{A}(\bm r)$ cannot be determined on an absolute scale.
-However, by making sufficient assumptions about the density distribution, we can nevertheless extract fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
+For example, the mass of the asteroid is unconstrained so $\rho_\mathcal{A}(\bm r)$ cannot be determined on an absolute scale.
+However, by making sufficient assumptions about the density distribution, we can nevertheless measure fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
 To best understand the potential density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
-To this end, we thoroughly outline two possible models and discuss two more in appendix \ref{app:other-models}.
+To this end, we thoroughly outline two possible models and discuss two more in appendix \ref{app:more-models}.
 
 We assume that the asteroid's surface is known in the inertial frame from radar data.
-Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is extracted.
-However, the density moments which are extracted from flyby data are known instead in the body-fixed frame.
+Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is extracted in the inertial frame.
+The density moments are extracted from flyby data, but these are known instead in the body-fixed frame.
 
@@
 by equation \ref{eqn:ylm-rotation}.
-Thus, uncertainties on $K_{\ell m}^\mathrm{body-fixed}$ and $\gamma_0$ (obtained from the encounter data) can be translated to uncertainty in $K_{\ell m}^\mathrm{hybrid}$.
+Thus, values and  uncertainties on $K_{\ell m}^\mathrm{body-fixed}$ and $\gamma_0$ (obtained from the encounter data) can be translated into values and uncertainties on $K_{\ell m}^\mathrm{hybrid}$.
 Henceforth, we will operate only in the hybrid frame and suppress the label.
 
-When the $K_{3m}$ are extracted, 15 moments are known (excluding $K_{00}$).
-Since the asteroid mass cannot be determined by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is one and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
-Three more moments are redundant with the center of mass, such that only twelve finite elements are free.
-In cases where $\gamma_0$ is known very accurately such that the correction imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable not to impose this equation on $K_{2m}$.
-In this case, the three orientation constraints that set $K_{21}=\Im K_{22} = 0$ carry over to the hybrid frame so that there are nine degrees of freedom (DOF).
+When the $K_{3m}$ are extracted, 15 moments are constrained (excluding $K_{00}$).
+Since the asteroid mass cannot be determined by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is $\rho_\text{avg}=1$ and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
+Three of the moments are redundant with the center of mass, such that only twelve finite elements are free.
+In cases where $\gamma_0$ is known very accurately such that the uncertainty increase imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable to treat $K_{2m}$ as fixed, just as $\Im K_{22}^\text{body-fixed}$ and $K_{21}^\text{body-fixed}$ are fixed.
+In this case, there are nine degrees of freedom (DOF).
 Since $\gamma_0$ is precisely known for all cases studied in this paper, we will always study this case.
@@
 To extract a density distribution, we use another MCMC given one of the two parametrizations of density distributions discussed below.
+We also present two further models in appendix \ref{app:more-models} which are viable substitutes for the following two models but are not used in the main text.
 The prior is set to be flat and non-zero for all configurations that obey the $0.25 < \rho < 3$ constraint.
 The likelihood used is set equal to the multivariate-Gaussian approximation of the posterior distribution for $K_{\ell m}$, extracted from flyby data.
-Otherwise, the MCMC parameters chosen were identical to those discussed in section \ref{sec:fit}.
-We also present two further models in appendix \ref{app:more-models} which are viable substitutes for the following two models but are not used in the main text.
 
@@
 
-Given values of $K_{\ell m}^\mathrm{body-fixed}$ and their uncertainties extracted from encounter data, there are many ways to extract a density distribution.
-Here, we outline a method termed the ``finite element'' model.
-We divide the asteroid into $N$ finite elements of uniform density and use the density $\rho_i$ of each as parameters.
-The four constraints imposed by the known mass and center of mass of the asteroid (seven with $K_{21}$ and $\Im K_{22}$ are also fixed) are used to constrain some of these $\rho_i$.
-The constrained densities are easily computed since the asteroid mass $\mu_\mathcal{A}$ and the product $I_\mathcal{A}K_{\ell m}$ are both linear functions of $\rho_i$.
-Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, $I_\mathcal{A} K_{\ell m}$ is known for all the constrained moments, computing the corresponding constrained densities is simply a matrix inversion.
+To define the ``finite element'' model, we divide the asteroid into $N$ finite elements of uniform density and use the density $\rho_i$ of each as parameters.
+The four constraints imposed by the known mass and center of mass of the asteroid (seven with $K_{21}$ and $\Im K_{22}$ are also fixed) are used to fix some of the $\rho_i$.
+These constrained densities are easily computed since the asteroid mass $\mu_\mathcal{A}$ and the product $I_\mathcal{A}K_{\ell m}$ are both linear functions of $\rho_i$.
+Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, $I_\mathcal{A} K_{\ell m}$ is known for all the fixed moments, and computing the corresponding constrained densities is simply a matrix inversion.
 
@@
 A drawback of the finite element model is that the generated density distribution might not be representative of the asteroid if the elements are not optimally placed.
-We therefore describe an alternate model, which includes the positions of the elements as parameters at the cost of larger elements and therefore lower resolution.
-We call this model the ``lumpy'' model.
+We therefore describe an alternate model which includes the positions of the elements as parameters at the cost of resolution.
+We call this the ``lumpy'' model.
 
@@
 We do not need to include $I_i$ as a free parameter because these lumps have constant density, so that $I_i = \mu_i a_i^2$.
-Furthermore, by requiring that a lump's density moments be computed relative to the center of mass of the lump, we have $K_{1m} = 0$.
+Furthermore, by requiring that a lump's density moments be computed relative to the center of mass of the lump, we have $K_{1m}^{(i)} = 0$.
 
-The translation rules of spherical harmonics \cite{Gelderen1998TheSO} give that the asteroid properties in the hybrid frame are
+The translation rules of spherical harmonics \cite{Gelderen1998TheSO} give that the density moments in the hybrid frame are
 \begin{equation}
@@
 For example, we can require that the lumps be ellipsoids, so that $K_{3 m}^{(i)} = 0$.
-Additional rotational symmetries also constrain $K$, with the most extreme case being that spherical lumps have $K_{\ell m} = 0$ for $\ell > 0$.
+The most extreme case is that spherical lumps, which have $K_{\ell m} = 0$ for $\ell > 0$.
 $K_{00}=1$ is also guaranteed by definition, meaning that each spherical lump has only five DOF ($a_i$, $\mu_i$, and $\bm r_i$).
 The substrate has one degree of freedom, since only $\mu_0$ is unknown.
-Thus, this lumpy model has $5N - 3$ total DOF.
+Thus, this spherical lumpy model has $5N - 3$ total DOF.
 Again, the choice of $N$ affects the accuracy and uncertainty of the model results, which is discussed in section \ref{sec:density-compare}.
@@
 
-To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the asymmetric reference asteroid (defined in appendix \ref{app:reference-configs}).
+To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the reference asteroids (defined in appendix \ref{app:reference-configs}).
 We first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
@@
 
-Figure \ref{fig:example-residuals} shows our synthetic spin data.
+Figure \ref{fig:example-residuals} shows our synthetic spin data for the asymmetric reference asteroid.
 The best-fitting model is overlaid in the top panel and residuals are shown the bottom panel.
 Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
-The fit results are clearly consistent with the data.
-This figure also reveals which points in the data set are most informative.
-The at-perigee data is irregular and reveals information about the density moments, and the post-perigee data shows torque-free tumbling behaviour which constrains $K_{2m}$ via the MOI ratios as in Ref.~\cite{MOSKOVITZ2020113519}.
+The fit results are consistent with the data.
+This figure also reveals which data points are most informative.
+The at-perigee data is irregular and reveals information about the density moments, and the post-perigee data shows torque-free tumbling behaviour which constrains $K_{2m}$ via the MOI ratios as in \cite{MOSKOVITZ2020113519}.
 The post-encounter periods and phase also indirectly sheds light on the at-perigee data by constraining the rotational velocity the asteroid must have had when leaving the perigee.
@@
 Figure \ref{fig:example-corner} shows a corner plot of the PPDs of the ten parameters (namely $\gamma_0$ and $K_{\ell m}$ for $\ell \leq 3$), marginalized to functions of one (histograms) or two (contours) variables.
-The true parameters are shown as lines.
-Note that the true parameters usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+The true parameters are shown and usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
 The PPDs are generally Gaussian and sometimes show strong correlation between parameters, but no continuous degeneracy occurs.
@@
 
-Density moments of the kind described above were extracted for the asymmetric and symmetric reference asteroids.
-The finite element model was then used to extract density distributions from these moments, and propagate uncertainties.
-Five DOF were used rather than the maximum possible number of nine, and 20 different finite element layouts were used to generate sample density distributions to avoid dependence on the manually-chosen layout.
-The resulting density distributions and uncertainties are displayed in figure \ref{fig:den-uniform}.
 \begin{figure*}
@@
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{first and third row}) and symmetric (\textit{second and fourth rows}) reference asteroids.
-The finite element model (\textit{top two rows}) and the lumpy model (\textit{bottom two rows}) are employed.
+  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) reference asteroids.
+The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed.
 From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-uniform}.Extracted densities are generally within 10\% of the truth.}
+These figures are available in animated form in appendix figure \ref{fig:animated-uniform}.
+Extracted densities are generally within 10\% of the truth.}
   \label{fig:den-uniform}
@@
 
+Figure \ref{fig:den-uniform} displays density distributions extracted by both the finite element and lumpy models for the reference asteroids.
+For the finite element model, five DOF and 20 different element layouts were used.
 The figure demonstrates that the finite element model successfully extracts density distributions consistent with the input density moments, as shown by the $\chi^2$ value per degree of freedom, $\chi^2_r$, depicted in the figure.
@@
 With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius.
-Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more apt to be contained inside a lump.
+Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more likely to be contained inside a lump.
 
@@
 These figures are available in animated form in appendix figure \ref{fig:animated-move}.
-The core is successfully extracted.}
+The lumpy model successfully extracts the core.}
   \label{fig:den-move}
@@
 However, the density distributions extracted by the finite model matches the true distributions less well.
-The deviation the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
-The distributions are consistent with the true distribution, but the finite element model has distributed the core into the rest of the asteroid so that the peak density is lowered.
+The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
+Uncertainties are large enough that the distributions are consistent with the true distribution, but the finite element model has distributed the core into the rest of the asteroid so that the peak density is lowered.
 
@@
 The significance of the deviations is around 30\%, as it was in figure \ref{fig:den-uniform} where the extracted distribution again matched the truth.
-The low uncertainty is caused by the small number of degrees of freedom (2) of the lumpy model.
+Again, the low uncertainty is caused by the small number of degrees of freedom of the lumpy model.
 A consequence is that if the core had been non-spherical, the lumpy model would be inaccurate, with significant deviations from the truth.
@@
 
-The question of which encounters are most suited to this methodology is of great interest, as is the question of how observational campaigns can be designed to best take advantage of an asteroid to maximize the success of this methodology.
+The question of which encounters are most suited to this methodology is of great interest, as is the question of how observational campaigns can be designed to best take advantage of an asteroid and maximize the success of this methodology.
 We investigate physical asteroid properties (the encounter's orbital properties, the asteroid's true shape, and its initial rotational velocity) and observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage), and discuss their effect on the uncertainty of this methodology's results.
@@
 The density distribution uncertainty $\sigma_\rho / \rho$ is defined as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each corresponding to a random sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
-The median of the uncertainty divided by the local density over this map is taken to represent the density distribution uncertainty.
+The median of this uncertainty divided by the local density over this map is taken to represent the density distribution uncertainty.
 This measure of uncertainty is more physically relevant than moment uncertainty, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
@@
   \begin{tabular}{lll} \hline
-    Encounter property & Weak &Strong \\ \hline
+    Encounter property & Strong & Weak \\ \hline
     Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
@@
   \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction.
-The weak uncertainty thresholds (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
+The strong uncertainty thresholds (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
 Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
@@
 Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds.
-These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
-These thresholds are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
+These values are $\sigma_\rho / \rho = 10^{-3}$ (weak) and $10^{-4}$ (strong), for density distributions extracted via the lumpy model.
+They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
 Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the encounter properties.
 Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines.
-Bands contain 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.
+Bands containing 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.
 
@@
 Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only effective for $a_\mathcal{A} \sim 15$ m.
-By contrast, the radius of asteroid 99942 Apophis is
-$\sim 300$ m and Apophis will encounter Earth in 2029.
-Apophis's perigee of 5--6 Earth radii also obeys the weak and strong constraints \cite{giorgini2008predicting}.
-In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} also shows a threshold on initial spin pole direction.
+By contrast, the radius of Apophis is
+$\sim 300$ m and its perigee and rotational period also obey the strong constraints \cite{giorgini2008predicting}.
+The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
+Further work must therefore be done to apply this analysis to Apophis.
+
+In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} shows a threshold on initial spin pole direction.
 The poles (i.e., angular velocities perpendicular to the orbital plane) lead to greater uncertainty and this is the only region which rises above the weak uncertainty threshold.
@@
 These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are more volatile.
-The figure also displays the stark difference between density uncertainty as computed by the lumpy model and the finite element model.
-This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model).
-The model assumptions also affect this uncertainty; the lumpy model must place the asteroid lump at the center of the asteroid since placing it elsewhere would move the asteroid's center of mass away from its observed position.
-Therefore, uncertainty on the edge of the asteroid where the lump is unlikely to be located, is very low for the lumpy model.
-The same reasoning does not apply to the finite element model, which has no bias towards the asteroid center.
+The figure also displays the stark difference between density uncertainty computed by the lumpy model and the finite element model.
+This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model), and to the assumptions of the model; the lumpy model is more biased towards uniform asteroids such as these, since it is comprised of a small number of uniform density regions.
 This model-dependence of $\sigma_\rho / \rho$ is another reason to take the thresholds of table \ref{tab:threshold-summary} as estimates rather than strict limits on encounter properties.
@@
   \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all1.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, spin pole uncertainty, and period uncertainty.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, asteroid length, and rotational period.
 The vertical dotted line indicates the reference asteroid values.
-The red vertical lines indicate the uncertainty thresholds.}
+The red solid/dashed lines indicate the weak/strong uncertainty thresholds.}
   \label{fig:scan-perigee}
@@
   \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all2.pdf}
-  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) asteroid length, observational cadence, data gap at perigee, and rotational period.
+  \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) period and spin pole uncertainty, observational cadence, and length of gaps in the data.
 The vertical dotted line indicates the reference asteroid values.
-The red vertical lines indicate the uncertainty thresholds.}
+The red solid/dashed lines indicate the weak/strong uncertainty thresholds.}
     \label{fig:scan-rho}
@@
 \begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-2-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-3-sigma.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-1-sigma.png}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-2-sigma.png}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-3-sigma.png}
 
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-a-sigma.pdf}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-b-sigma.pdf}
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1-sigma.png}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-a-sigma.png}\hfill
+  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-b-sigma.png}
 
@@
 
-To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate moment uncertainty as well.
-Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ on physical and observational encounter properties respectively.
+To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate the model-independent moment uncertainty as well.
+Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ as a function of physical and observational encounter properties respectively.
 The thresholds of table \ref{tab:threshold-summary} are depicted as red lines.
@@
 
-Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $K_{3m}$.
+Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $\sigma(K_{3m})$.
 For instance, $\sigma(K_{2m})$ is constant as $a_\mathcal{A}$ is varied despite a dramatic increase in $\sigma(K_{3m})$ for low $a_\mathcal{A}$.
 The resulting $\sigma_\rho / \rho$ is mostly constant.
-However, the roles are reversed for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and here $\sigma_\rho /\rho$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
-It follows that if more post-flyby tumbling data is collected, placing stronger constraints on $K_{2m}$ rather than $K_{3m}$, then $K_{2m}$ at some point might have essentially no uncertainty.
+The opposite is true for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and $\sigma_\rho /\rho$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
+A consequence is that if more post-flyby tumbling data is collected, placing stronger constraints on $K_{2m}$ rather than $K_{3m}$, then $K_{2m}$ at some point might have essentially no uncertainty.
 In this case, uncertainty on $K_{3m}$ will be dominant and the most constraining parameters will change.
@@
 (Figure \ref{fig:net-uncertainty} also indicated this, since $\sigma_\rho / \rho$ falls for low perigee in both the lumpy and the finite element model).
+
 Dependence of moment uncertainty on data precision $\sigma_P$ and $\sigma_\theta$ is linear as shown by figure \ref{fig:scan-observational}.
@@
 Figure \ref{fig:den-uniform} revealed that density distributions can still be extracted for symmetric asteroids, but to reduce uncertainty, the moments must be re-parametrized to remove this degeneracy if this methodology is to be run on nearly symmetric asteroids.
-Beyond this dependence on $K_{2m}$, almost no moment uncertainty variation is visible, indicating that this methodology will give similar results given many asteroid shapes distinct from the reference asteroid.
+Beyond this dependence on $K_{2m}$, almost no moment uncertainty variation is visible, indicating that this methodology gives similarly successful results for many asteroid shapes distinct from the reference asteroid.
 
-These figures are more thoroughly interpreted in appendix \ref{app:uncertainty-dependence}, which also describes how the data was collected.
+These figures are more thoroughly interpreted in appendix \ref{app:uncertainty-dependence}, which also describes how the data was collected and presents additional data.
 
@@
 
-Given this conversion between $\epsilon$ and $J_{20}$, we analyze moment uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
-These uncertainties are shown in the top panel of figure \ref{fig:scan-oblateness}, together with linear best-fitting curves for moment uncertainty as a function of oblateness.
-The figure demonstrates almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$, although moment uncertainty does measurably decrease for oblate central bodies.
+Figure \ref{fig:scan-oblateness} displays moment uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+It also shows linear best-fitting curves for moment uncertainty as a function of oblateness.
+Almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$ is apparent, although moment uncertainty does measurably decrease for oblate central bodies.
 
@@
 Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
-Since Jupiter is less dense than Earth, we expect that uncertainty in the first-order parameters $\gamma_0$ and $K_{2m}$ would be slightly worse than in the case of Earth, which is seen in table \ref{tab:jupiter-uncertainty}.
-
 The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
@@
 For example, encounters with massive planets are more plentiful, so that observation for a fixed period of time will lead to a larger number of observed encounters conducive to low-uncertainty moment extraction (small $r_p$, large $a_\mathcal{A}$, etc.).
-This can be seen via the following equation for the area of the keyhole through which the asteroid must fly to have a perijove $r_p$ low enough to meet the uncertainty threshold:
+This can be seen via the following equation for the area of the keyhole through which the asteroid must fly to have a perijove $r_p$ or lower:
 \begin{equation}
@@
 \end{equation}
-Table \ref{tab:jupiter-uncertainty} suggested that moment uncertainty is roughly $\sigma(K_{\ell m}) \propto a_\mathcal{B}^{\ell - 1} / r_p$, so that constant uncertainty roughly implies $r_p \propto a_\mathcal{B}^{1-2}$.
+Table \ref{tab:jupiter-uncertainty} suggested that moment uncertainty is roughly $\sigma(K_{\ell m}) \propto a_\mathcal{B}^{\ell - 1} / r_p$, so that constant uncertainty roughly implies $r_p \propto a_\mathcal{B}^{1\ \text{to} \ 2}$.
 Since $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, equation \ref{eqn:impact-parameter} dictates that $b/r_p$ will increase faster than $a_\mathcal{B}$ as $\mu_B$ is increased.
@@
 We do this for 9 (maximal), 7, 5, 3, and 2 DOF.
-Additionally, we vary the precision $\sigma_P$ of the data set used to extract the density moments, and plot $\sigma_\rho$ and $\Delta \rho$ as a function of $\sigma_P$.
+Additionally, we vary the precision $\sigma_P$ of the data set used to extract the density moments and plot $\sigma_\rho$ and $\Delta \rho$ as a function of $\sigma_P$.
 Figure \ref{fig:dof-scan} displays the distribution of $\sigma_\rho$, $\Delta \rho$, and the significance of the deviations from the truth ($\Delta \rho / \sigma_\rho$) over the asteroid.
@@
   \includegraphics[width=\linewidth]{figs/dof-scan.pdf}
-  \caption{The average uncertainty divided by local density $\sigma_\rho / \rho$ and deviation from the truth divided by local density $\Delta \rho / \rho$ of density distributions extracted by the finite element model with varying degrees of freedom.
+  \caption{The average uncertainty divided by local density $\sigma_\rho / \rho$,deviation from the truth divided by local density $\Delta \rho / \rho$, and the significance of deviations $\Delta \rho / \sigma_\rho$ extracted by the finite element model with varying degrees of freedom.
 5 DOF appears to optimize the trade-off between the model-induced uncertainty caused by too many DOF and the inaccuracy caused by too few.}
@@
 
-The figure demonstrates the expected behaviour that few degrees of freedom results in low uncertainty but large $\Delta \rho / \sigma$, wile many degrees of freedom is more accurate but also more uncertain.
-The trend of uncertainty, deviation, and significance as a function of $\sigma_P$ is also discontinuous for few DOF, because in these cases the properties of the output distribution are strongly dependent on the initial choice of uncertainty of the initial choice of grids, and more than five grids are necessary to remove that dependence.
+The figure demonstrates the expected behaviour that few degrees of freedom results in low uncertainty but large $\Delta \rho / \sigma_\rho$, wile many degrees of freedom is more accurate but also more uncertain.
+The trend of uncertainty, deviation, and significance as a function of $\sigma_P$ is also discontinuous for few DOF because in these cases the properties of the output distribution are strongly dependent on the initial choice of element layout, and more than five trials are necessary to remove that dependence.
 This discontinuity is most noticeable for 3 and 2 DOFs.
@@
 The top panel of \ref{fig:dof-scan} also demonstrates that $\sigma_\rho$ reaches a plateau for large $\sigma_P$.
-In that regime, the prior constraints that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data quality.
+In that regime, the prior constraint that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data precision.
 This is a further example of how the extracted asteroid density distribution is strongly dependent on the choice of model, and one of the reasons why we display the uncertainties of density moments in section \ref{sec:fit-uncertainty} rather than density distribution uncertainty.
@@
 Results are similar to the off-center core shown in \ref{fig:den-move} in that the moments of the resulting density distribution are consistent with those extracted from the encounter data (i.e., $\chi^2_r$ is low).
-Again, the finite element model does not isolate the lump, instead spreading the excess mass over the right side of the asteroid.
+Again, the finite element model does not isolate the lump, instead spreading the excess mass over the asteroid.
 Unlike the off-center core example, the lumpy model is not able to recover the true distribution either.
@@
 This is because, for centred, spherical cores, the core mass is degenerate with the core's radius.
-Uncertainty is therefore larger for the centred core than for the off-center core and the maximum density deviation over the asteroid is larger.
 
-The success of the model in the off-center case was due to the fact that the shape of the asteroid was offset from the center of mass by a corresponding amount, assumed to be known to great precision.
+The success of the model in the off-center case was due to the fact that the shape of the asteroid was offset from the center of mass by a corresponding amount, assumed to be known precisely.
 The position of the lump was therefore observed up to one free parameter: the lump's mass.
-The assumption that the asteroid's center of mass is so precisely known is rooted stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
+The assumption that the asteroid's center of mass is so precisely known stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
 If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain for the off-center case.
@@
 Each lump is located 500 meters from the center of the asteroid, so that they counterbalance and the asteroid's observed center of mass is its surface's centroid.
-This model has seven DOF, in contrast to the 5 DOF of the finite element model.
+The corresponding two-lump lumpy model has seven DOF, in contrast to the 5 DOF of the finite element model.
 Both models are run on this asteroid and the resulting distributions are shown in figure \ref{fig:den-double}.
@@
 
-Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased asteroid near the center.
-On the other hand, the lumpy model detects that the two lumps are opposite each other, and of roughly the same radius and mass.
+Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center.
+On the other hand, the lumpy model detects that the two lumps are opposite each other,and of roughly the same radius and mass.
 These radius and mass values are also close to the true values.
 The model places the lumps correctly in the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
+Uncertainty is also high, due to the extra DOF.
 Note that $\chi^2_r$ remains low despite the lumpy model's misplacement of the lumps.
 This is because the lumpy model gains its information on the placement of the lumps from the $K_{3m}$ density moments, which figures \ref{fig:scan-physical} and \ref{fig:scan-observational} suggest are not as well constrained as the $K_{2m}$ density moments.
-The moments estimated by the MCMC fit to encounter data are not perfectly correct, resulting in a deviation of a few hundred meters in lump location.
+The high uncertainty results in a deviation of a few hundred meters in lump location for the reference encounter properties.
 
@@
 Uncertainties are propagated throughout the pipeline.
-Since this problem is underdetermined, the models give different results and were contrasted.
-Nevertheless, we find that the models always produce results consistent with the data set.
-The entire pipeline was run starting from simulated encounter data and ending with density distribution predictions and was shown to be robust.
+Since the density distribution inverse problem is underdetermined, the models give different results and were contrasted.
+Nevertheless, we find that the models always produce results consistent with the data set and usually consistent with the true distribution.
 
 We assessed the uncertainty of the pipeline's results by adjusting various properties of the asteroid and its Earth encounter.
-The precise thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
+The thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
 The properties that do not affect density uncertainty as much, such as the central body oblateness, must still be accurately represented in simulations to avoid errors in the pipeline results.
@@
 
-Finally, we highlighted that the properties of the final density distribution are strongly dependent.
+Finally, we highlighted that the properties of the final density distribution are strongly model-dependent.
 The uncertainties on density distribution of the two models were drastically different, and also depended on the number of degrees of freedom used in the model.
 For asteroids of non-uniform distributions, the distributions themselves also differed.
-The lumpy model, designed to look for specific types of features, was much more sensitive to these features than the generic finite element model.
-To efficiently use encounter data, it is therefore important to investigate multiple models and choose different models to answer different questions.
+To efficiently use encounter data, it is therefore important to investigate multiple models and choose different models to answer different questions, such as the lumpy model to look for discrete regions of increased density.
 

### 2022-07-29 summaries/21-11/21-11.tex
Redownload and new runs adjusted for gamma_0

@@
     \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {$\unit n$};
-    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
-    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
-    \draw[thick,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
     \draw[->] (0.5, -0.75) arc (290:302:2.5);

### 2022-07-29 summaries/urop/main.tex
Redownload and new runs adjusted for gamma_0

\documentclass[11pt]{article}

\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[backend=bibtex, style=numeric, sorting=none,
  doi=false, isbn=false, url=false]{biblatex}
\usepackage[colorlinks=true, citecolor=magenta]{hyperref}
\addbibresource{asteroids.bib}

\title{Constraining the Interiors of Asteroids Through Close Encounters\\ 
{\Large Spring 2022 UROP proposal}}

\author{Jack Dinsmore}

\begin{document}
\maketitle

\begin{abstract}
  This UROP will be conducted with Prof. Julien de Wit of the Earth, Atmospheric, and Planetary Sciences Department (office: 54-1726) during the Spring of 2022. It will be a theoretical UROP, so no room number is applicable. I am applying for 20 hours per week of direct funding.
\end{abstract}

\section{Overview}
Asteroids provide vital information about the properties and evolution of the early Solar System. Many asteroids are preserved fragments of the planetesimals that made up the Sun's protoplanetary disk and are some of the only remnants from this era which are not bound in planets or stars and altered beyond recognition. Much research has therefore been devoted to studying asteroids in recent years, including many observational initiatives such as the NEOWISE mission and asteroid sample return missions Hayabusa and OSIRIS-REx. In total, hundreds of thousands of asteroids have been discovered.

However, it is difficult to determine the properties of many of these asteroids. For nearby or large asteroids, the surface topography and composition can be constrained given data of the total amount of sunlight reflected off the rotating asteroid as a function of time (light curve analysis). In general, however, it is very difficult to constrain the interior distribution of an asteroid without sending an expensive spacecraft to the body itself.

One way of constraining the interior properties of an asteroid is to observe its gravitational interactions. This has been done in general, from a theoretical perspective \cite{ashenberg07, paul88, BOUE2009750}, in the context of observing an asteroid binary system \cite{Naidu_2015, DESCAMPS2020113726}, and for asteroid encounters with a planet \cite{BENSON2020113518, MOSKOVITZ2020113519, SCHEERES2005281}. But only a small set of the parameters capable of being observed by this gravitational analysis have actually been constrained to this point.

In this project, we derive new equations of motion for an asteroid encounter with a planet to arbitrary order and build a simulation for the asteroid encounter system. We use Markov Chain Monte Carlo fit algorithm to perform many injection-retrieval tests, extracting parameters constraining the density distribution of the asteroid. We sudy both parameters which have previously been extracted, and parameters which have not yet been observed. By studying many different flyby settings, we determine what system parameters lead to poor constraints on the asteroid parameters. We then discuss four methods to extract density distributions from these parameters under different assumptions, and conclude with a discussion of what technology and flyby types are required to observe the hitherto undetected asteroid parameters.

To keep the scope of this project appropriate, we make several physical assumptions about the asteroid encounter system. Specifically, we assume that (1) the system contains two bodies (perturbations from the Sun and moons are neglected), (2) the asteroid remains rigid throughout the flyby, and (3) the asteroid is initially not tumbling. We also make several assumptions about the encounter data available, namely (1) that the angular velocity of the asteroid can be extracted as a function of time, and (2) that the uncertainty on the angular velocity follows our uncertainty model. To apply the model to specific flybys in which these assumptions do not hold would require a modification to the asteroid model. However, these assumptions are data-motivated, designed to be characteristic of many asteroid flybys. By making them, we intend to increase the generality of our findings.

\section{Work Plan \& Goals}
I have been working on this research project since last summer and have made significant progress. The project is nearly complete insofar as it is currently scoped. This semester, I will write up my work into a paper which will be submitted for publication in \textit{The Astrophysical Journal}, and I will present my work to several faculty in the EAPS department. I anticipate making several modifications to respond to suggestions made by the faculty members, which is why I require 20 hours of funding this semester. Examples of additional work that may be required are (1) performing a flyby fit to actual data rather than synthetic data and (2) a more careful review of assumptions.

My personal goal for this project initially was to continue with a project I had enjoyed from a class. I viewed it as a good way to increase my research skills, especially simulation design and statistics knowledge. As the project has expanded, my perception of the project has switched from one of personal improvement to an actual paper that would be submitted. My primary goal now is one of aiding scientific research on asteroids. My research shows that we may be able to constrain the interior distribution of asteroids better than is currently done, and I'm excited to help in that effort.

\section{Personal Statement}
When I started this project, I was considering not going to grad school and moving to industry instead. My experience in doing self-directed research in this project, and enjoying it, helped me make the decision to apply to grad school. It also convinced me to apply for astrophysics programs; I had previously been considering condensed matter and other fields.

Now that I've been accepted to grad school, I'm interested in branching out into other research areas. Specifically, research areas that are not purely classical. Compact body physics, for instance. However, this research project will still be extremely useful to me as a full-fledged example of a theoretical, classical physics research project, and I will use it to help guide myself towards my eventual field of specialization, regardless of whether I continue with asteroid research specifically.

\printbibliography

\end{document}

### 2022-07-29 paper/appendices.tex
Ready to push new runs to SC & responded to some revisions

@@
 This dependence is displayed in figure \ref{fig:scan-theta}.
-More precisely, we can ask if some error $\bm {\delta}_\omega$ is added to angular velocity $\omega$, does it affect results more strongly if it is parallel to $\omega$ (affects the period) or perpendicular (affects the spin pole direction)?
+More precisely, we can ask if some error $\bm {\delta}_\omega$ is added to angular velocity $\bm \omega$, does it affect results more strongly if it is parallel to $\bm \omega$ (affects the period) or perpendicular (affects the spin pole direction)?
 
@@
 In other words, if $\bm {\delta}_\omega \perp \bm \omega$ using the symbols defined above, then $\delta$ can be large.
-But if $\delta = |\bm{\delta}_\omega| / |\bm \omega|$, then $\delta$ must be very small.
+But if $\bm{\delta}_\omega  \parallel \bm \omega$, then $\delta$ must be very small.
 Period precision is therefore more vital than spin pole direction precision when it comes to decreasing density distribution uncertainties.

### 2022-07-29 paper/main.tex
Ready to push new runs to SC & responded to some revisions

@@
 \newcommand{\jtd}[1]{ {\bf{\color{red} JTD: #1}} }
-\newcommand{\unit}[1]{\bm{\hat{#1}}}
+\renewcommand{\unit}[1]{\bm{\hat{#1}}}
 
@@
 Angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
-Orbital and physical properties, including MOI ratios have also been extracted for asteroid 99942 Apophis, discovered on June 19, 2004 by R.
+Orbital and physical properties, including moment of inertia (MOI) ratios have also been extracted for asteroid 99942 Apophis, discovered on June 19, 2004 by R.
 A.
@@
 Bernardi \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, and on target to encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
-However, density distribution features beyond the moment of inertia (MOI) ratios have not yet been extracted for any asteroid encounters.
+However, density distribution features beyond the MOI ratios have not yet been extracted for any asteroid encounters.
 More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
@@
 $\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
-The integral is computed over the entire asteroid mass, denoted $\mathcal{A}$.
+The integral is computed over the entire asteroid mass, denoted $\mathcal{A}$, and $d^3 r$ indicates the three-dimensional volume element throughout the paper.
 $I_\mathcal{A}$ denotes a MOI scale defined as
@@
 \end{equation}
-
-The angular acceleration of the asteroid is proportional to $\bm \tau / I$ such that the $I_\mathcal{A}$ factor of equation \ref{eqn:tidal-torque} is canceled out.
+Note that all moments of inertia are proportional to $I_\mathcal{A}$.
+Equation \ref{eqn:tidal-torque} indicated that tidal torque was also proportional to $I_\mathcal{A}$.
+The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is independent $I_\mathcal{A}$.
 Thus, the observables do not depend explicitly on $I_\mathcal{A}$.
@@
 We assume a short-axis rotation mode such that energy of the asteroid's rotation is minimized.
-This sets two of the Euler angles equal to zer0 initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
+This sets two of the Euler angles equal to zero initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
 
@@
 Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in equation \ref{eqn:parameter-bounds}.
-We also use $|K_{3m}| < 1$.
+Computing $K_{3m}$ for many positive density distributions revealed a $|K_{3m}| \lesssim 0.01$, so we use more conservative bounds on $K_{3 m}$ of $|K_{3 m}| < 1$.
 In general, spin data is most sensitive to $\gamma_0$ and $K_{2m}$, which we call the ``first-order parameters.'' We call $K_{3m}$ the ``second-order parameters.''
@@
 The MCMC was determined to converge when the fractional change in autocorrelation time (computed every 100 iterations) was one percent, and the number of iterations already computed was more than 100 times the autocorrelation time.
-The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits computed for asteroid encounters in which degeneracies were present.
-This degeneracy could be removed by only fitting $K_{2m}$ instead.
+The MCMC fit also was set to terminate if more than $10^5$ iterations were run, but this only occurred for fits computed for asteroid encounters in which degeneracies were present, for example when the asteroid has rotational symmetry.
 About $10^4$ iterations was often sufficient.
@@
 
-We rotate the known surface of the asteroid to a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame.
+To compare the asteroid surface and extracted density moments in the same coordinate system, we define a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame.
 (It has $\bm \Omega_0 \parallel \unit z_\text{hybrid}$ with third Euler angle $\gamma = 0$.) The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
@@
 
-  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) reference asteroids.
+  \caption{Cross-sectional slices of the density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) uniform-density reference asteroids.
 The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed.
@@
 These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom.
-With only one lump, the location of the known center of mass requires that the lump lie at the centroid of the asteroid center with mass close to zero and unconstrained radius.
-Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more likely to be contained inside a lump.
+With only one lump and with asteroids where the surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the lump must lie at the centroid with mass close to zero and unconstrained radius.
+Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have more density uncertainty.
 
@@
 The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
-Te vertical black dotted lines are the property values of the reference asteroid.
+The vertical black dotted lines are the property values of the reference asteroid.
 The figures illustrate the marked difference in density distributions that results from using different models.}
@@
   \includegraphics[width=0.7\columnwidth]{figs/oblateness-differ.pdf}
-  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$ .
+  \caption{\textit{Top}: 1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs as a function of oblateness $\epsilon$.
+All other parameters, including the central body radius, are kept constant.
 Linear best-fitting lines to $\sigma(K_{2m})$ (black, dotted) are plotted.
@@
 It also shows linear best-fitting curves for moment uncertainty as a function of oblateness.
+All other parameters, include $I_\mathcal{B}$ which parametrizes the central body radius, are kept constant.
 Almost no dependence of $\sigma(K_{\ell m})$ on oblateness $\epsilon$ is apparent, although moment uncertainty does measurably decrease for oblate central bodies.

### 2022-07-29 data/scan-gamma/scatter.py

@@ -1,0 +1,35 @@
+# Goal: spawn a bunch of runs that cover the parameter space.
+from matplotlib import pyplot as plt
+import numpy as np
+
+LOW_ORDER_INDEX = 1
+BASE_NAME = f"gamma"
+LOW_GAMMA_0= 0
+HIGH_GAMMA_0 = 2 * np.pi
+NUM_DIVISIONS = 48 # Run with 12 cores per process.
+LOW_ORDER = [(0.39269908169, 0, -0.09766608), (0.39269908169, 0.05200629, -0.2021978)][LOW_ORDER_INDEX]
+HIGH_ORDER = [0, 0, 0, 0, 0, 0, 0]
+PERIGEE_GAMMA = -2.58971954411
+MU = 3.986004418e14
+
+def get_text(gamma_0):
+    quartile = int((gamma_0 + np.pi / 4) / (np.pi / 2))
+    high_lim = np.pi / 4 + quartile * np.pi / 2
+    low_lim = - np.pi / 4 + quartile * np.pi / 2
+    return """0, 3
+120
+5
+1000
+6000
+0.00006464182, 0.00012928364, -0.00012928364
+1.0
+{}, {}, {}, {}, {}, {}, {}, {}, {}, {}
+{}, 0.125, 0, 1, 1, 1, 1, 1, 1, 1
+{}, -0.125, -0.25, -1, -1, -1, -1, -1, -1, -1
+1e-2, 1e-5""".format(gamma_0, LOW_ORDER[1], LOW_ORDER[2], HIGH_ORDER[0], HIGH_ORDER[1],
+    HIGH_ORDER[2], HIGH_ORDER[3], HIGH_ORDER[4], HIGH_ORDER[5], HIGH_ORDER[6], high_lim, low_lim)
+
+for ratio_index, perigee in enumerate(np.linspace(LOW_GAMMA_0, HIGH_GAMMA_0, NUM_DIVISIONS)):
+    f = open("../../staged/{}-{:02}.txt".format(BASE_NAME, ratio_index), 'w')
+    f.write(get_text(perigee))
+    f.close()

### 2022-08-01 paper/appendices.tex
Paper update

--- 2022-07-05 paper/appendices.tex
@@
 
-\section{Reference asteroid configurations}
-\label{app:reference-configs}
-
-Except when otherwise mentioned, we use the following asteroid encounter parameters.
-Many of the parameter choices are made to increase the precision of observations (a close orbit, large asteroid, etc.) This is so that our methodology's output is most sensitive to changes in these parameters.
-
-\begin{enumerate}
-  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
-This orbit was chosen to roughly match that of Apophis.
-These orbital parameters correspond to an eccentricity of 3.88.
-  \item An initial roll of $\gamma_0=\pi/8$.
-  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 10^{-2}$ and $\sigma_P / P = 10^{-7}$.
-  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
-  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
-For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
-The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
-The second case and its reflection are called the asymmetric cases.
-Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
-If not specified, we use the $a < b$ case.
-Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
-\end{enumerate}
-
-The surface of a spherical asteroid with this rotational period and $a_\mathcal{A}$ rotates at $\SI{25}{\centi\meter\per\second}$ at the equator.
-The asymmetric and symmetric ellipsoids have maximum equatorial velocities of $\SI{36}{\centi\meter\per\second}$ and $\SI{27}{\centi\meter\per\second}$ respectively.
-
 % \section{The cadence cut-off}
@@
 \end{figure*}
-
-\section{Uncertainty dependence on encounter properties}
-\label{app:uncertainty-dependence}
-
-In this section, we investigate in greater detail the data presented in section \ref{sec:fit-uncertainty} of the main text.
-
-\subsection{Orbital elements}
-\label{sec:scan-orbit}
-A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
-They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
-We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$, for which the moment and density distribution uncertainties are shown in figures \ref{fig:scan-perigee} and \ref{fig:net-uncertainty}.
-
-Figure \ref{fig:scan-perigee} shows a very strong dependence on perigee as mentioned in the main text --- so strong that for large perigee, $\sigma(K_{3m})$ is constrained by the prior boundaries of $\pm 1$ for $m < 3$.
-This occurs as low as $r_p = 10$ Earth radii for $K_{30}$, though the fact that density distributions can still be extracted for $r_p > 10$ Earth radii indicates that precise constraints on $K_{30}$ are not crucial.
-This strong dependence is expected from equation \ref{eqn:tidal-torque}; it is caused by the $(a_\mathcal{A}/D)^{\ell'}$ dependence of the tidal torque on distance $D$.
-
-By contrast, density moment uncertainty shows only a slight increase with $v_\infty$.
-This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-There are also comparatively large oscillations in the uncertainty, due to the orientation of the asteroid at perigee varying.
-(The asteroid is always simulated to start at the same orientation, but increasing $v_\infty$ decreases the time to perigee so that the asteroid enters this region of high torque at different orientations depending on $v_\infty$.) Hence, the oscillations have the same period for all parameters.
-These oscillations are large enough that the density uncertainty of figure \ref{fig:net-uncertainty} exceeds the strong threshold, but we do not treat this on a limit of $v_\infty$ since it is more directly related to the value of $\gamma$ at perigee.
-
-The axes of figure \ref{fig:scan-perigee} show that parameters with large $m$ are more precisely determined than parameters with small $m$, as can be seen by comparing $K_{22}$ to $K_{20}$ and comparing $K_{33}$ to other $K_{3m}$ values.
-Large $m$ moments correspond to moments that control higher frequency fluctuations in density at the asteroid equator.
-This pattern of $\sigma(K_{\ell m})$ smaller for large $m$ is a general trend across the parameters.
-
-\subsection{Rotational period}
-\label{sec:scan-period}
-
-In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of $P_\omega$.
-Like the dependence of $\sigma(K_{\ell m})$ on $v_\infty$, moment uncertainty varies periodically with $P_\omega$ due to the fact that the value of $\gamma$ at perigee depends on $P_\omega$.
-A large-scale trend is also visible in many parameters.
-$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast rotators tumble very little after perigee.
-This increases uncertainty on the $K_{2m}$ parameters, which are largely constrained by post-encounter tumbling.
-
-We expect that fast rotators would not tumble post-encounter because, for small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
-Approximating each variable as constant over one full rotation of $\gamma$, the integral of the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ gives no secular first-order torque to force the asteroid to tumble.
-However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters.
-This is most visible in the figure for $K_{30}$.
-The cause is likely that $K_{\ell 0}$ cannot contribute to $\tau_z$ as shown in equation \ref{eqn:tidal-torque}.
-We already discussed that asteroids with small $P_\omega$ do not tumble, and since $\tau_x$ and $\tau_y$ are what induces tumbling, the most observable component of torque is $\tau_z$.
-Asymmetry is therefore more measurable than symmetry for these fast rotators.
-
-\subsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
-
-In figure \ref{fig:spin-uncertainty}, we displayed density uncertainty as a function of initial spin pole direction, which showed large uncertainty for $\bm \Omega \parallel \unit Z$; i.e., initial spin pole perpendicular to the orbital plane.
-The density moment $1\sigma$ uncertainties $\sigma(K_{\ell m})$ as a function of spin pole direction are shown in figure \ref{fig:scan-spin}.
-These uncertainties are computed for 64 samples laid out on a Fibonacci sphere (green dots on lower-most panel) to ensure roughly even spacing.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{figs/spin-pole}
-  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
-All maps are made in the Mollweide projection.
-The orange star indicates the reference spin pole.
-Green dots are the sampled spin pole directions.
-The red contours enclose regions above the strong uncertainty threshold on $\sigma_\rho / \rho$.
-The weak threshold is never exceeded.
-Beyond the $\pm \unit Z$ increase in uncertainty, there is also increased moment uncertainty for $\pm \unit Y$.}
-  \label{fig:scan-spin}
-\end{figure*}
-
-Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, as did the density uncertainty discussed in the main text.
-$\sigma(K_{20})$ especially exhibits this increase.
-However, many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
-This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
-By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
-In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel \unit Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
-As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling results in greater uncertainty.
-
-We may understand the case of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\bm \Omega$ is unchanged.
-Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
-This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque is dominated by non-perigee effects.
-This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
-
-\subsection{Observational uncertainty}
-\label{sec:scan-uncertainty}
-Two parameters, $\sigma_\theta$ and $\sigma_P$, govern the observational uncertainty of the data set.
-These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_P$ represents the standard deviation of the rotational period.
-Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects uncertainty.
-This dependence is displayed in figure \ref{fig:scan-theta}.
-More precisely, we can ask if some error $\bm {\delta}_\omega$ is added to angular velocity $\omega$, does it affect results more strongly if it is parallel to $\omega$ (affects the period) or perpendicular (affects the spin pole direction)?
-
-Let $\delta = |\bm{\delta}_\omega| / |\bm \omega|$ and $\delta \ll 1$.
-Then if $\bm {\delta}_\omega \parallel \bm \omega$, it decreases the period $P_\omega$ by $P_\omega \delta$.
-This is a fractional change in period of $\delta$.
-If $\bm {\delta}_\omega \perp \bm \omega$, then the spin pole angle changes by $\delta$ radians.
-
-Comparing the $\sigma_P / P$ (fractional change in period) and $\sigma_\theta$ (spin pole angle) columns of figure \ref{fig:scan-observational}, one can see that a given value of $\sigma_\theta$ contributes a much smaller moment uncertainty than the same value of $\sigma_P/ P$.
-This is also visible in figure \ref{fig:net-uncertainty} for the lumpy model.
-In other words, if $\bm {\delta}_\omega \perp \bm \omega$ using the symbols defined above, then $\delta$ can be large.
-But if $\delta = |\bm{\delta}_\omega| / |\bm \omega|$, then $\delta$ must be very small.
-Period precision is therefore more vital than spin pole direction precision when it comes to decreasing density distribution uncertainties.
-
-% \subsection{Cadence}
-% \label{sec:scan-cadence}
-
-% The time between observations of asteroid angular velocity, or cadence, may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
-
-% Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
-We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-We name this rough cadence limit $T_\text{cad}$.
-$T_\text{cad}$ is also the location at which the $\sigma(K_{3m}$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
-
-% We expect this $T_\text{cad}$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time and may be relevant).
-How these time scales affect $T_\text{cad}$ is discussed in appendix \ref{app:cadence-tests}.
-
-% Figure \ref{fig:scan-cadence} shows that as long as $\Delta t < T_\text{cad}$ is achieved, the influence of cadence on $\sigma$ is minimal, but shorter cadence leads to lower uncertainties.
-
-\subsection{Perigee gap}
-\label{sec:scan-gap}
-In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
-The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
-The resulting gap in data is intended to be captured by the $T_\text{gap}$ parameter of figure \ref{fig:scan-observational}, which deserves to be more fully defined.
-
-We mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
-To prevent lack of precision induced by lower amounts of data when $T_\text{gap}$ is large, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
-We cut around the perigee because tidal torque is the greatest at perigee, and we expect that part of the data set to be most valuable.
-Indeed, figure \ref{fig:scan-observational} shows that $K_{3m}$ especially are more uncertain for $T_\text{gap} \gtrsim 1.5$ hr.
-However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the thresholds, indicating that large amounts of data can be cut without compromising the methodology.

### 2022-08-01 paper/main.tex
Paper update

@@
 % The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
-The data used to choose this $dt$ was obtained using the reference asteroid configuration, described in appendix \ref{app:reference-configs}.
+The data used to choose this $dt$ was obtained using the reference asteroid configuration.
 
@@
 If $N$ is chosen lower, the choice of element layout might exclude a distribution that exactly matches $K_{\ell m}$, but uncertainties are diminished due to less redundancy in the model.
-An analysis of which value of $N$ is appropriate for our purposes is given in section \ref{sec:dof-scan}.
+For the rest of this paper, we use $N=12$ finite elements, which corresponds to 7 constrained elements and 5 DOF.
+
+To arrive at this choice of 5 DOF, we extracted five density distributions with uncertainties from five random grids for the asymmetric asteroid.
+We calculated the mean density uncertainty over the asteroid for all five grids $\sigma_\rho$, as well as the average deviation from the true density distribution $\Delta \rho$ and the significance of that deviation $\Delta \rho / \sigma_\rho$.
+We did this for different levels of observational precision and with either 9, 7, 5, 3, or 2 DOF.
+Our data revealed that 5 DOF appeared to show the lowest density uncertainty while still producing low significance of deviations from the true density distribution.
 
@@
 Thus, this spherical lumpy model has $5N - 3$ total DOF.
-Again, the choice of $N$ affects the accuracy and uncertainty of the model results, which is discussed in section \ref{sec:density-compare}.
+Again, the choice of $N$ affects the accuracy and uncertainty of the model results.
+For the rest of this paper, we use $N=1$ lump for simplicity, corresponding to 2 DOF.
+In section \ref{sec:density-compare}, we also use $N=2$ lumps which possesses 7 DOF.
 
@@
 
-To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for the reference asteroids (defined in appendix \ref{app:reference-configs}).
-We first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
+To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for two ``reference asteroids,'' which correspond to the following encounter parameter choices.
+
+\begin{enumerate}
+  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
+This orbit was chosen to roughly match that of Apophis.
+These orbital parameters correspond to an eccentricity of 3.88.
+  \item An initial roll of $\gamma_0=\pi/8$.
+  \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 10^{-2}$ and $\sigma_P / P = 10^{-7}$.
+  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
+  \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
+For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
+The second case and its reflection are called the asymmetric cases.
+Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
+If not specified, we use the $a < b$ case.
+Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
+\end{enumerate}
+
+In the following sections, we first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
 For both stages of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
 
-\subsection{Density moments}
+\subsection{Density moment retrieval}
 \label{sec:example-fit}
@@
 
-\subsection{Density distribution}
+\subsection{Density distribution retrieval}
 \label{sec:asym-density}
@@
   \centering
-  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all1.pdf}
+  \includegraphics[angle=90, origin=c, width=0.99\linewidth]{figs/scan-all1.pdf}
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, asteroid length, and rotational period.
@@
   \centering
-  \includegraphics[angle=90, origin=c, width=\linewidth]{figs/scan-all2.pdf}
+  \includegraphics[angle=90, origin=c, width=0.99\linewidth]{figs/scan-all2.pdf}
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) period and spin pole uncertainty, observational cadence, and length of gaps in the data.
@@
 
-\begin{figure*}
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-1-sigma.png}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-2-sigma.png}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-theta-3-sigma.png}
-
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-1-sigma.png}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-a-sigma.png}\hfill
-  \includegraphics[width=0.3\textwidth]{figs/probe-space-ab-b-sigma.png}
-
-  \caption{1$\sigma$ moment uncertainty for first-order parameters $\gamma_0$, $K_{22}$, and $K_{20}$ (\textit{top row}) and $\gamma_0$, $a/c$, and $b/c$ (\textit{bottom row}).
-Also shown as points are the reference asteroid shapes: symmetric (red circle) and asymmetric (black triangle).
-Symmetric asteroids ($K_{22}=0$ or $a/c=b/c$) show increased moment uncertainty, but otherwise moment uncertainty is roughly constant.}
-  \label{fig:scan-space-sigma}
-\end{figure*}
-
 To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate the model-independent moment uncertainty as well.
 Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ as a function of physical and observational encounter properties respectively.
+Figure \ref{fig:scan-spin} additionally depicts moment uncertainty as a function of initial spin pole.
 The thresholds of table \ref{tab:threshold-summary} are depicted as red lines.
-Also shown is moment uncertainty as a function of $K_{2m}$ in figure \ref{fig:scan-space-sigma}.
 
@@
 
-Figure \ref{fig:scan-physical} also demonstrates an accelerating increase of $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
+In the following sections, we study each panel of figures  \ref{fig:scan-physical} and \ref{fig:scan-observational} individually and discuss their implications.
+
+% Figure \ref{fig:scan-physical} also demonstrates an accelerating increase of $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
 (Figure \ref{fig:net-uncertainty} also indicated this, since $\sigma_\rho / \rho$ falls for low perigee in both the lumpy and the finite element model).
 
-Dependence of moment uncertainty on data precision $\sigma_P$ and $\sigma_\theta$ is linear as shown by figure \ref{fig:scan-observational}.
-However, moment uncertainty on cadence $\Delta t$ and gaps in data $T_\text{gap}$ does not increase so quickly.
-These tend to increase in uncertainty at some characteristic time scale of $\Delta t \sim 15 -40$ min for cadence and $1-2$ hr for $T_\text{gap}$.
-As long as $\Delta t$ and $T_\text{gap}$ are below these time scales, uncertainty is not strongly dependent on them.
-The time scales might be a function of the period of the asteroid or the orbital time scales $r_p / v_\infty$ and $\mu_\mathcal{B} / v_\infty^3$.
+\subsubsection{Orbital elements}
+\label{sec:scan-orbit}
+A Keplerian orbit is completely described by five parameters, but three describe the orbit's orientation with respect to the central body.
+They are therefore redundant with the orientation of the inertial frame and we do not investigate them here.
+We parametrize the remaining two parameters by the perigee distance $r_p$ and excess velocity $v_\infty$.
 
-Finally, figure \ref{fig:scan-space-sigma} depicts moment uncertainty $\sigma(K_{2m})$ as a function of $K_{2m}$ and $\gamma_0$.
-$K_{2m}$ can be interpreted as moment inertia ratios or the dimensions of the uniform-density ellipsoid with the same $K_{\ell m}$.
-Therefore, moment uncertainty is depicted both as a function of $K_{2m}$ and these ratios $a/c$ and $b/c$.
-The figure shows a dramatic increase in moment uncertainty for $K_{22} = 0$, which corresponds to $a=b$, or a rotationally symmetric ellipsoid.
-This uncertainty is caused by degeneracy in the model; if the asteroid is rotationally symmetric, then two principal axes can lie anywhere in the $xy$-plane, so that the definition of $\gamma_0$ becomes meaningless.
-$\gamma_0$ is therefore poorly constrained as $K_{22} \rightarrow 0$.
-Figure \ref{fig:den-uniform} revealed that density distributions can still be extracted for symmetric asteroids, but to reduce uncertainty, the moments must be re-parametrized to remove this degeneracy if this methodology is to be run on nearly symmetric asteroids.
-Beyond this dependence on $K_{2m}$, almost no moment uncertainty variation is visible, indicating that this methodology gives similarly successful results for many asteroid shapes distinct from the reference asteroid.
+Figure \ref{fig:scan-perigee} shows a very strong dependence on perigee as mentioned in the main text --- so strong that for large perigee, $\sigma(K_{3m})$ is constrained by the prior boundaries of $\pm 1$ for $m < 3$.
+This occurs as low as $r_p = 10$ Earth radii for $K_{30}$, though the fact that density distributions can still be extracted at this perigee value shows that resolution of $K_{30}$ is not essential to extract density distributions.
+Figure \ref{fig:net-uncertainty} also demonstrates that low perigee yield more certain density distributions as extracted by both the lumpy and the finite element models.
+Such a strong strong dependence is expected from equation \ref{eqn:tidal-torque}; it is caused by the $(a_\mathcal{A}/D)^{\ell'}$ dependence of the tidal torque on distance $D$.
 
-These figures are more thoroughly interpreted in appendix \ref{app:uncertainty-dependence}, which also describes how the data was collected and presents additional data.
+By contrast, density moment uncertainty shows only a slight increase with $v_\infty$.
+This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
+This change in encounter timing also adjusts the orientation of the asteroid at perigee, which has a separate effect on moment uncertainty.
+We control for this undesired orientation dependence by adjusting $\gamma_0$ so that, if no tidal torque is present, the orientation of the asteroid at perigee is constant for all $v_\infty$.
+The effect of tidal torque then causes orientations to be \textit{roughly} the same at perigee where tidal torque is highest.
+This effectively removes the orientation dependence.
+
+\subsubsection{Rotational period}
+\label{sec:scan-period}
+
+In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of rotational period $P_\omega$.
+As in the above section, the value of $\gamma_0$ was corrected to ensure roughly constant orientation at perigee.
+$K_{20}$ and $K_{22}$ show very large uncertainty for $P_\omega \lesssim 4$ hr because these fast rotators tumble very little after perigee.
+This increases uncertainty on the $K_{2m}$ parameters, which are largely constrained by post-encounter tumbling.
+
+We expect that fast rotators would not tumble post-encounter because, for small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
+Approximating each variable as constant over one full rotation of $\gamma$, the integral of the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ gives no secular first-order torque to force the asteroid to tumble.
+However, this effect does not apply to the second-order parameters, since the integral over the second-order term of $\bm \tau$ does not vanish, as seen in the figure.
+An asteroid with large $K_{3m}$ moments might therefore be yield better uncertainties at these low rotational periods (e.g., a non-uniform or non-elliptical asteroid).
+
+Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters (most visible for $K_{30}$).
+The explanation is likely the following: Tidal torque components $\tau_x$ and $\tau_y$ induce tumbling, and since fast rotators exhibit reduced tumbling post-encounter, these components likely have little effect on moment uncertainty.
+The most observable component of torque is then $\tau_z$, but equation \ref{eqn:tidal-torque} shows that $K_{\ell 0}$ does not contribute to $\tau_z$.
+Asymmetry is therefore more measurable than symmetry for these fast rotators.
+
+\subsubsection{Initial spin pole}
+\label{sec:scan-spin}
+
+The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{figs/spin-pole}
+  \caption{$1\sigma$ uncertainties for the first-order parameters (\textit{top}) and second-order (\textit{bottom}) as a function of the initial direction of spin in the inertial frame.
+All maps are made in the Mollweide projection.
+The orange star indicates the reference spin pole.
+Green dots are the sampled spin pole directions.
+The red contours enclose regions above the strong uncertainty threshold on $\sigma_\rho / \rho$.
+The weak threshold is never exceeded.
+Beyond the $\pm \unit Z$ increase in uncertainty, there is also increased moment uncertainty for $\pm \unit Y$.}
+  \label{fig:scan-spin}
+\end{figure*}
+
+Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, just as \ref{fig:spin-uncertainty} depicts increased density distribution uncertainty.
+Many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
+This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
+By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
+$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
+In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel \unit Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
+As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling results in greater uncertainty.
+
+We may understand the case of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\bm \Omega$ is unchanged.
+Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
+This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque is dominated by non-perigee effects.
+This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
+
+\subsubsection{Observational uncertainty}
+\label{sec:scan-uncertainty}
+Two parameters, $\sigma_\theta$ and $\sigma_P$, govern the observational uncertainty of the data set.
+These parameters are defined in section \ref{sec:uncertainty}; $\sigma_\theta$ represents the standard deviation of the angle between the true spin pole and the observed spin pole, while $\sigma_P$ represents the standard deviation of the rotational period.
+Rather than explore the full space spanned by these two values, we fix one and allow the other to vary to better assess whether uncertainty in spin pole or uncertainty in period more strongly affects uncertainty.
+This dependence is displayed in figure \ref{fig:scan-theta}.
+Moment uncertainty ($\sigma(K_{\ell m})$) grows linearly with observational uncertainty ($\sigma_\theta$ or $\sigma_P$).
+
+In particular, we might ask if some error $\bm {\delta}_\omega$ is added to angular velocity $\bm \omega$, does it affect results more strongly if it is parallel to $\bm \omega$ (affects the period) or perpendicular (affects the spin pole direction)?
+
+Let $\delta = |\bm{\delta}_\omega| / |\bm \omega|$ and $\delta \ll 1$.
+Then if $\bm {\delta}_\omega \parallel \bm \omega$, it decreases the period $P_\omega$ by $P_\omega \delta$.
+This is a fractional change in period of $\delta$.
+If $\bm {\delta}_\omega \perp \bm \omega$, then the spin pole angle changes by $\delta$ radians.
+Comparing the $\sigma_P / P$ (fractional change in period) and $\sigma_\theta$ (spin pole angle) columns of figure \ref{fig:scan-observational}, one can see that a given value of $\sigma_\theta$ contributes a much smaller moment uncertainty than the same value of $\sigma_P/ P$.
+This is also visible in figure \ref{fig:net-uncertainty} for the lumpy model.
+In other words, if $\bm {\delta}_\omega \perp \bm \omega$ using the symbols defined above, then $|\bm {\delta}_\omega|$ can be large.
+But if $\bm{\delta}_\omega  \parallel \bm \omega$, then $|\bm {\delta}_\omega|$ must be very small.
+Period precision is therefore more vital than spin pole direction precision when it comes to decreasing uncertainties.
+
+\subsubsection{Cadence}
+\label{sec:scan-cadence}
+
+The time between observations of asteroid angular velocity, (cadence, $\Delta t$), may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
+We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+
+Figure \ref{fig:scan-cadence} displays little dependence of uncertainty on cadence $\Delta t$ for $\Delta t \lesssim 40$ min.
+We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
+This increase is generally where the $\sigma(K_{3m})$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
+
+We expect this threshold value of $\Delta t$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time).
+\jtd{How these time scales affect the $\Delta t$ threshold is discussed in appendix \ref{app:cadence-tests}.}
+
+Figure \ref{fig:scan-cadence} shows that as long as $\Delta t$ is less than this threshold, the influence of cadence on $\sigma$ is small, but shorter cadence leads to lower uncertainties.
+
+\subsubsection{Data gaps}
+\label{sec:scan-gap}
+In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
+The asteroid might dip below the horizon, or it might pass too close to the sun to be observed.
+The resulting gap in data is intended to be captured by the $T_\text{gap}$ parameter of figure \ref{fig:scan-observational}, which deserves to be more fully defined.
+
+We mask the perigee of the counter by removing a duration $T_\text{gap}$ of data centred on the perigee, where $T_\text{gap}$ ranges from 0 to 3 hours.
+To prevent lack of precision induced by lower amounts of data when $T_\text{gap}$ is large, we always cut 3 hr$-T_\text{gap}$ from the data set, half from the beginning and half from the end, so that each data set produced for all $T_\text{gap}$ has the same size.
+We cut around the perigee because tidal torque is the greatest at perigee, and we expect that part of the data set to be most valuable.
+Indeed, figure \ref{fig:scan-observational} shows that $K_{3m}$ especially are more uncertain for $T_\text{gap} \gtrsim 1.5$ hr.
+However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the thresholds, indicating that large amounts of data can be cut without compromising the methodology.
+As with the threshold for cadence discussed above, this 1.5 hr cut-off may depend on the asteroid rotational period or the orbital time scales.
+It likely also depends on the observational cadence used.
+
+\subsubsection{Other parameters}
+
+We also study the dependence of moment uncertainty on the asteroid MOI and on the asteroid's initial orientation, but these relationships are simple enough that they are not included in figures \ref{fig:scan-physical} and \ref{fig:scan-observational}.
+Moment uncertainty is generally unrelated to the asteroid shape, except when the asteroid is rotationally symmetric (e.g., for the symmetric reference asteroid).
+In this case the initial orientation of the asteroid $\gamma_0$ is undefined, creating degeneracy and inflating density moment uncertainty.
+For symmetric or near-symmetric asteroids, this issue could be resolved by re-parametrizing the MCMC to remove this degeneracy.
+
+Moment uncertainty is also affected by $\gamma_0$, which was corrected for in section \ref{sec:scan-orbit}.
+We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant.
+Moment uncertainties varied by factors of \jtd{25-100\%}, generally exhibiting roughly sinusoidal behaviour.
+The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape.
 
@@
 
-The physical parameters of the asteroid body are kept the same as the Earth encounter case (listed in appendix \ref{app:reference-configs}), as are the observational uncertainty and cadence.
+The physical parameters of the asteroid body are kept the same as the Earth encounter case, as are the observational uncertainty and cadence.
 The orbit is adjusted for the Jupiter case by setting a perijove distance of $r_p=5$ Jupiter radii (compared to perigee radius $r_p=5$ Earth radii for the Earth encounter).
@@
 Which of these contradicting effects dominates depends on the asteroid population near Jupiter and the observation method.
-
-\subsection{Finite element model DOF}
-\label{sec:dof-scan}
-The number of elements $N$ used for the finite element model can be freely chosen.
-As discussed in section \ref{sec:density-distro}, seven of these are fixed by various constraints on the asteroid density distribution.
-There are 16 density moments with $\ell \leq 3$, so $N=16$ with nine DOF is the largest number of parameters the model can support.
-However, maximizing the DOF adds model-induced uncertainty to our results.
-This uncertainty can be reduced by reducing $N$, but with $N < 16$, a solution perfectly matching the extracted moments is not guaranteed.
-There is therefore a trade-off between the average density uncertainty $\sigma_\rho$ and the accuracy, which can be represented as the deviation of the density distribution from the true distribution $\Delta \rho$.
-
-We investigate this trade-off by extracting five density distributions with five different finite-element layouts from moments extracted from synthetic data of the asymmetric reference asteroid.
-For each point in the asteroid, 1000 samples are drawn from each of the five density distributions.
-We use the standard deviation of the 5000 samples as the uncertainty $\sigma_\rho$ at that point, and the mean of the samples as the density $\rho$.
-Modelling the asteroid as having a uniform true density, we compute the deviation of the density from the truth $\Delta \rho$ over the asteroid.
-We do this for 9 (maximal), 7, 5, 3, and 2 DOF.
-Additionally, we vary the precision $\sigma_P$ of the data set used to extract the density moments and plot $\sigma_\rho$ and $\Delta \rho$ as a function of $\sigma_P$.
-Figure \ref{fig:dof-scan} displays the distribution of $\sigma_\rho$, $\Delta \rho$, and the significance of the deviations from the truth ($\Delta \rho / \sigma_\rho$) over the asteroid.
-Median values of these three measures are shown, as well as bands that enclose the values for 68\% of the asteroid.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{figs/dof-scan.pdf}
-  \caption{The average uncertainty divided by local density $\sigma_\rho / \rho$,deviation from the truth divided by local density $\Delta \rho / \rho$, and the significance of deviations $\Delta \rho / \sigma_\rho$ extracted by the finite element model with varying degrees of freedom.
-5 DOF appears to optimize the trade-off between the model-induced uncertainty caused by too many DOF and the inaccuracy caused by too few.}
-  \label{fig:dof-scan}
-\end{figure}
-
-The figure demonstrates the expected behaviour that few degrees of freedom results in low uncertainty but large $\Delta \rho / \sigma_\rho$, wile many degrees of freedom is more accurate but also more uncertain.
-The trend of uncertainty, deviation, and significance as a function of $\sigma_P$ is also discontinuous for few DOF because in these cases the properties of the output distribution are strongly dependent on the initial choice of element layout, and more than five trials are necessary to remove that dependence.
-This discontinuity is most noticeable for 3 and 2 DOFs.
-We use 5 DOFs throughout this paper, because it produces the most precise results in this test while still accurately reproducing the asteroid density distribution.
-5 DOFs corresponds to $N=12$ finite elements.
-
-The top panel of \ref{fig:dof-scan} also demonstrates that $\sigma_\rho$ reaches a plateau for large $\sigma_P$.
-In that regime, the prior constraint that the density of the asteroid take on physically meaningful values are more constraining than the actual data, leading to less dependence on the data precision.
-This is a further example of how the extracted asteroid density distribution is strongly dependent on the choice of model, and one of the reasons why we display the uncertainties of density moments in section \ref{sec:fit-uncertainty} rather than density distribution uncertainty.
-Moment uncertainty is not prone to the same model-dependent plateau.
 

### 2022-08-01 core-data/scan-spin-pole/compile.py

@@ -1,208 +1,0 @@
-# Goal: spawn a bunch of runs that cover the parameter space.
-from matplotlib import pyplot as plt
-import numpy as np
-from matplotlib.lines import Line2D
-import matplotlib as mpl
-from scipy.interpolate import LinearNDInterpolator
-from scipy.linalg import norm
-import os
-
-plt.style.use("jcap")
-mpl.rcParams["font.size"] = 14
-
-param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
-
-percentiles = {}
-name_index = {}
-xyzs = []
-theta_phis = []
-
-N_DIM = None
-N_PERCENTILES = None
-PULL = False
-DRAW_AVG_PLOTS = False
-
-if PULL:
-    os.system("scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/code/thresholds/lumpy/scan-spin-pole.npy .")
-
-with open("scan-spin-pole.npy", 'rb') as f:
-    uncs = np.load(f)[:,2]
-
-def show_true_point(ax, flip=False):
-    spin = [0.00006464182, 0.00012928364, -0.00012928364]
-    theta, phi = np.pi / 2 - np.arccos(spin[2] / norm(spin)), np.arctan2(spin[1], spin[0])
-    if flip:
-        theta *= -1
-    ax.scatter(phi, theta, color='tab:orange', marker='*', s=32)
-
-# Get percentiles
-with open("percentiles.dat", 'r') as f:
-    for line in f.readlines():
-        if line == '': continue
-        elements = line.split(':')
-        name = elements[0]
-        perc_array = []
-        for percs in elements[1:]:
-            perc_array.append([float(x) for x in percs.split(',')])
-        perc_array = np.array(perc_array)
-        N_DIM = perc_array.shape[0]
-        N_PERCENTILES = perc_array.shape[1]
-        percentiles[name] = perc_array
-
-index = 0
-for name in percentiles.keys():
-    dir_name = name[:7]
-    with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
-        max_j, max_l = f.readline().split(", ")
-        max_j, max_l = (int(max_j), int(max_l))
[…]

### 2022-08-01 paper/appendices.tex
Further edits to the paper and updated the documentation

@@
 Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}) and write the equations of motion for the system (section \ref{sec:eom}).
-We do not consider any third-body perturbations, and we assume that the body being encountered (the central body, e.g.~a planet) is much more massive than the asteroid.
 
@@
 
-Throughout this paper, we assume that the asteroid remains rigid throughout the encounter.
-We also assume no third-body perturbations from other Solar System objects.
-(More accurately, we assume that all third-body perturbing objects lie closer to the central body's centre of mass than the asteroid perigee distance so that their density moments can be included in the density moments of the central body.) For the sake of simplicity, we also assume that the density moments of the central body are known and do not evolve with time (i.e., the central body's rotation is marginal compared to the timescale of the encounter).
-
 The gravitational potential energy of the central body is, in its most general form,
@@
 where the sum is shorthand for $\sum_{\ell, m} = \sum_{\ell = 0}^\infty \sum_{m=-\ell}^\ell$.
+
+Incidentally, it is the $|\bm R| < |\bm R'|$ assumption that inspires the assumption that there are ``no \textit{distant} perturbing objects'' (section \ref{sec:methods}).
+If a perturbing object such as a moon is not distant (i.e., it is closer to the system center of mass than the asteroid perigee so that $|\bm R| < |\bm R'|$ always), then it can be absorbed into $J_{\ell m}$ by equation \ref{eqn:jlm} and the assumptions of this derivation are not violated.
+
 We are interested in translating the potential energy of equation \ref{eqn:first-pe} to the body-fixed frame.

### 2022-08-01 paper/main.tex
Further edits to the paper and updated the documentation

@@
 \label{sec:methods}
+
+In the following mathematical model for the influence of tidal torque on asteroid encounters, we assume for simplicity that (1) that the central body is much more massive than the asteroid, (2) that both are rigid, (3) that there are no distant perturbing objects and (4) that the asteroid is in a short-axis, non-tumbling rotational state before the encounter.
+All of these assumptions except 2 can be relaxed without drastic changes to the model.
 
@@
   \begin{split}
-  \bm \tau = & G\frac{I_\mathcal{A}I_\mathcal{B}}{2 a_\mathcal{A}^2a_\mathcal{B}^2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S^*_{\ell+\ell', m + m'} (\bm D) (-1)^{\ell'}\right.\\
+  \bm \tau = & G\frac{I_\mathcal{A}I_\mathcal{B}}{2 a_\mathcal{A}^2a_\mathcal{B}^2}\left[\sum_{\ell m} a_\mathcal{B}^\ell J_{\ell m} \sum_{\ell' m'}a_\mathcal{A}^{\ell'}S_{\ell+\ell', m + m'} (\bm D)^* (-1)^{\ell'}\right.\\
   \times & \left.\sum_{m''=-\ell'}^{\ell'} \sqrt{\frac{(\ell'-m'')!(\ell'+m'')!}{(\ell'-m')!(\ell'+m')!}}  \mathcal{D}^{\ell'}_{m'm''}(\alpha, \beta, \gamma)^* \right. \\
@@
 For example, $\bm \Omega_0$ could be extracted from pre-encounter light-curve data and $a_\mathcal{A}$ from a model for the asteroid's surface using radar.
-
-We assume for simplicity that the asteroid is initially not tumbling, though this assumption can be relaxed.
-We assume a short-axis rotation mode such that energy of the asteroid's rotation is minimized.
-This sets two of the Euler angles equal to zero initially, so that only $\gamma_0$ is necessary to provide initial data for the simulation.
+The other two initial Euler angles $\alpha_0$ and $\beta_0$ are required to be zero by the assumption of no initial tumbling.
 
@@
 \begin{enumerate}
-  \item An orbit around a spherical, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
-This orbit was chosen to roughly match that of Apophis.
-These orbital parameters correspond to an eccentricity of 3.88.
+  \item An orbit around a spherical, non-rotating, Moonless Earth with $6$ km s$^{-1}$ excess velocity and perigee at 5 Earth radii.
+This orbit was chosen to roughly match that of Apophis and corresponds to an eccentricity of 3.88.
   \item An initial roll of $\gamma_0=\pi/8$.
@@
 These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom.
-With only one lump and with asteroids where the surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the lump must lie at the centroid with mass close to zero and unconstrained radius.
-Hence, the uncertainty of regions far from the asteroid is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have more density uncertainty.
+With the one-lump-model and with asteroids whose surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the single lump must lie at the centroid with mass close to zero and unconstrained radius.
+The uncertainty of regions far from the asteroid center, where the lump is unlikely to extend, is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have greater density uncertainty.
 

### 2022-08-03 paper/appendices.tex
Orientation uncertainty model

@@
 \end{figure*}
+
+\section{Comparing orientation and angular velocity data}
+
+To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
+It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
+In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
+
+\subsection{Uncertainty model}
+We will use the same tools to extract data from the orientation data set as we did in the main text for the angular velocity data set.
+The only item that requires redefinition is the likelihood used by the MCMC (equation \ref{eqn:log-likelihood}), which depends on a model for the uncertainty of orientation observations.
+
+For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
+Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
+\begin{equation}
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\brackets{(\quat q_i (\quat q_i^*)^{-1})_r}}^2
+  \label{eqn:orientation-like}
+\end{equation}
+where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
+
+\subsection{Moment uncertainty comparison}
+With the likelihood defined, density moments can be extracted from the orientation data via the fit process described in the main text and compared to those extracted from the angular velocity data.
+We generate data of both types for the reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets.
+
+Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
+One could not tell if one data set yields more precise moments because the observational precision of that data set is better or because that data type affords better estimation of density moments.
+However, the relative uncertainty of moments can be compared between the two data sets.
+
+We generate moment uncertainty for the orientation data using a test value of $\sigma_\phi = 0.1$ and compute the mean uncertainty.
+We then scale the moment uncertainties attained from the angular velocity data set with the reference observational uncertainty parameters so that the mean uncertainty of all the moments is equal to that of the orientation data set.
+This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
+We then compute the ratio between $\sigma(K_{\ell m})$ for the observational data set and the angular velocity data set and show the result as a function of $\ell$ and $m$ in figure \ref{fig:observational-moment-uncertainty}.
+\begin{figure}
+  \centering
+  % \includegraphics{figs/observational-moment-uncertainty}
+  \caption{\jtd{Write}}
+  \label{fig:observational-moment-uncertainty}
+\end{figure}
+
+\subsection{Density uncertainty comparison}

### 2022-08-03 paper/appendices.tex
Orientation data set fit process

@@
 
+We may expect some differences in the resolving power of orientation and angular velocity data, but not a large difference, due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid position.
+The initial position is defined up to $\gamma_0$ by the assumption of no initial tumbling, and figures \ref{fig:scan-physical} and \ref{fig:scan-observational} reveal that $\gamma_0$ is typically also constrained to high precision even by angular velocity data.
+Thus, we expect the only differences between moment uncertainty as obtained from angular velocity data or from orientation data to be due to the uncertainty of the data itself.
+
 \subsection{Uncertainty model}
-We will use the same tools to extract data from the orientation data set as we did in the main text for the angular velocity data set.
-The only item that requires redefinition is the likelihood used by the MCMC (equation \ref{eqn:log-likelihood}), which depends on a model for the uncertainty of orientation observations.
+The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
+This requires a new model for the uncertainty of orientation observations.
 

### 2022-08-03 orientation/fit_resolved/collect.py

@@ -1,0 +1,94 @@
+import os, sys
+import numpy as np
+from PIL import Image, ImageFont, ImageDraw
+
+RUNS = 0
+CORNER = 1
+PARAMS = 2
+REDCHI = 3
+font = ImageFont.truetype("cmunrm.ttf", 20)
+
+def collect(d, bare):
+    try:
+        images = [Image.open(d+x) for x in ['-compare.png', '-corner.png', '-params.png', '-redchi.png']]
+    except:
+        print("Could not find files for {}".format(d))
+        return False
+
+    widths, heights = zip(*(i.size for i in images))
+
+    bi_height = max(heights[PARAMS], heights[REDCHI])
+    bi_width = widths[PARAMS] + widths[REDCHI]
+
+    im_width = widths[CORNER] + max(widths[RUNS], bi_width)
+    im_height = max(heights[CORNER], heights[RUNS] + bi_height)
+
+    new_im = Image.new('RGB', (im_width, im_height), color=(255, 255, 255))
+
+    new_im.paste(images[CORNER], (0, int((im_height - heights[CORNER]) / 2)))
+    new_im.paste(images[RUNS],
+        (widths[CORNER] + int((im_width - widths[CORNER] - widths[RUNS]) / 2),
+        int((im_height - heights[RUNS] - bi_height) / 2)))
+    new_im.paste(images[PARAMS],
+        (widths[CORNER] + int((im_width - widths[CORNER] - bi_width) / 2),
+        heights[RUNS] + int((im_height - heights[RUNS] - bi_height) / 2)))
+    new_im.paste(images[REDCHI],
+        (widths[PARAMS] + widths[CORNER] + int((im_width - widths[CORNER] - bi_width) / 2),
+        heights[RUNS] + int((im_height - heights[RUNS] - bi_height) / 2)))
+
+    f = open("../../staged/"+bare+".txt", 'r')
+    max_j, max_l = f.readline().split(", ")
+    max_j, max_l = (int(max_j), int(max_l))
+    cadence = int(float(f.readline()))
+    impact_parameter = float(f.readline())
+    radius = float(f.readline())
+    speed = float(f.readline())
+    spin = [float(x) for x in f.readline().split(',')]
+    jlms = [float(x) for x in f.readline().split(',')]
+    theta_true = [float(x) for x in f.readline().split(',')]
+    theta_high = [float(x) for x in f.readline().split(',')]
+    theta_low = [float(x) for x in f.readline().split(',')]
[…]

### 2022-08-03 orientation/fit_resolved/fit.py

@@ -1,0 +1,602 @@
+TEST = False
+
+import numpy as np
+import quaternion
+import emcee, time, sys, logging
+if not TEST:
+    import asteroids_0_2, asteroids_0_3, asteroids_2_2, asteroids_2_3, asteroids_3_2, asteroids_3_3
+if TEST:
+    import test_loglike as asteroids_0_2
+    import test_loglike as asteroids_0_3
+    import test_loglike as asteroids_2_2
+    import test_loglike as asteroids_2_3
+    import test_loglike as asteroids_3_2
+    import test_loglike as asteroids_3_3
+from multiprocessing import Pool
+import random_vector, random
+from scipy import optimize
+from scipy.linalg import pinvh
+from mpmath import mp
+import plotille
+
+import numdifftools as nd
+
+try:
+    import coloredlogs
+    coloredlogs.install()
+except:
+    pass
+
+logging.basicConfig(level=logging.INFO)
+
+PLOT_POSES = True
+NUM_MINIMIZE_POINTS_PER = 4 # Used to be 4
+NUM_L3_MINIMIZATIONS = 1# Changed to 1 to decrease time.
+DISTANCE_RATIO_CUTS = [
+    [2.0, None],
+    [-2.0, None]
+]
+THRESHOLD_LIKE_RAT = 2
+
+ASTEROIDS_MAX_J = 0
+ASTEROIDS_MAX_K = 3
+
+GM = 3.986004418e14 # Earth
+
+EARTH_RADIUS = 6_370_000
+UNCERTAINTY_MODEL = random_vector.UNIFORM_ANGLE
+INTEGRAL_LIMIT_FRAC = 1.0e-3
+
+N_WALKERS = 32
+MAX_N_STEPS = 100_000
+MIN_THETA_DIST = 1e-4
+LARGE_NUMBER = 1e100
+MIN_SPACING = np.array([1.0e-6, 1.0e-6, 1.0e-6,
+    1.0e-1, 1.0e-1, 1.0e-1, 1.0e-1, 1.0e-1, 1.0e-1, 1.0e-1])# Comes in blocks corresponding to the block diagonals
+MAX_SPACING = np.array([0.0003, 0.0003, 0.0003,
+    LARGE_NUMBER, LARGE_NUMBER, LARGE_NUMBER, LARGE_NUMBER, LARGE_NUMBER, LARGE_NUMBER, LARGE_NUMBER])
+DEFAULT_THIN = 10
[…]

### 2022-08-03 orientation/fit_resolved/main.cpp

@@ -1,0 +1,90 @@
+#include <pybind11/pybind11.h>
+#include <pybind11/stl.h>
+#include <vector>
+
+#include "../sim/backend.hpp"
+#include "../sim/algebra.hpp"
+
+std::vector<double> simulate(double cadence, const std::vector<double> jlms_raw,
+    const std::vector<double> parameters,  double radius, double spinx, double spiny, double spinz,
+    double perigee, double speed, double central_mu, double central_radius,
+    double distance_ratio_cut=0, double enforce_drc=false,
+    double velocity_mul=1) {
+
+    std::vector<cdouble> halfjlms;
+    auto jlm_raw_iter = jlms_raw.begin();
+    for (int l = 0; l <= ASTEROIDS_MAX_J; l++){
+        if (l != 0) {
+            for (int m = 1; m <= l; m++) {
+                halfjlms.push_back({*jlm_raw_iter++, *jlm_raw_iter++});
+            }
+        }
+        halfjlms.push_back({*jlm_raw_iter++, 0});
+    }
+
+    std::vector<cdouble> halfklms;
+    auto klm_raw_iter = parameters.begin();
+    const double initial_roll = *klm_raw_iter++;
+    halfklms.push_back({1, 0}); // K00
+    halfklms.push_back({0, 0}); // K11
+    halfklms.push_back({0, 0}); // K10
+    halfklms.push_back({*klm_raw_iter++, 0}); // K22
+    halfklms.push_back({0, 0}); // K20
+    halfklms.push_back({*klm_raw_iter++, 0}); // K20
+    for (int l = 3; l <= ASTEROIDS_MAX_K; l++){
+        for (int m = 1; m <= l; m++) {
+            halfklms.push_back({*klm_raw_iter++, *klm_raw_iter++});
+        }
+        halfklms.push_back({*klm_raw_iter++, 0});
+    }
+
+
+    // Make full jlms
+    cdouble jlms[(ASTEROIDS_MAX_J+1) * (ASTEROIDS_MAX_J+1)];
+    cdouble klms[(ASTEROIDS_MAX_K+1) * (ASTEROIDS_MAX_K+1)];
+    uint j = 0;
+    for (uint l = 0; l <= ASTEROIDS_MAX_J; l++) {
+        for (int m = -l; m <= (int)l; m++) {
+            assert(j < (ASTEROIDS_MAX_J+1) * (ASTEROIDS_MAX_J+1));
[…]

### 2022-08-04 paper/main.tex
Pulled cad-speed data, redid vex and period data.
Pushed some remaining files and decided not to include cadence dependence appendix

@@
   \draw (-2, 3.5) node[anchor=center] {$\theta$};
-  \draw (-0.5, 2.5) node[anchor=center] {$|\bm \Omega|$};
 
@@
   \begin{tabular}{lll} \hline
-    Encounter property & Strong & Weak \\ \hline
+    Encounter property & Weak & Strong \\ \hline
     Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
@@
   \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction.
-The strong uncertainty thresholds (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
+The weak uncertainty cut-off (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
+The strong cut-off is never exceeded and thus does not appear.
 Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
@@
 Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds.
-These values are $\sigma_\rho / \rho = 10^{-3}$ (weak) and $10^{-4}$ (strong), for density distributions extracted via the lumpy model.
+These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
 They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
@@
 The time between observations of asteroid angular velocity, (cadence, $\Delta t$), may vary depending on the observational schedule of the observing telescopes and the path of the asteroid through the sky.
-We measure how the posterior uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
+We measure how the moment uncertainty $\sigma(K_{\ell m})$ varies with cadence ranging from two minutes to one hour in figure \ref{fig:scan-cadence}.
 
@@
 We also see flaring of uncertainty for very large cadence, largely driven by the paucity of data points.
-However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which is likely characteristic of the asteroid system.
-This increase is generally where the $\sigma(K_{3m})$ threshold is crossed for all second-order moments except $K_{30}$, which exceeds the uncertainty threshold at $\Delta t \approx 5$ min.
-
-We expect this threshold value of $\Delta t$ to be a function of two dynamical time scales of the system: the rotational period of the asteroid $P_\omega$ and the dynamical time scale of the orbit (the latter can be estimated in multiple ways, since both $r_p / v_\infty$ and $v_\infty r_p^2 / \mu_\mathcal{B}$ have units of time).
-\jtd{How these time scales affect the $\Delta t$ threshold is discussed in appendix \ref{app:cadence-tests}.}
+However, uncertainty dramatically increases for many parameters at about $\Delta t = 30-40$ min, a time scale which depends both on the asteroid rotational period $P_\omega$ and the time scales of its orbit.
 

### 2022-08-04 code/thresholds/compile-period.py

@@ -8,10 +8,10 @@ mpl.rcParams["font.size"] = 14
 
 percentiles = {}
 cadences = []
-time_ratios = []
+periods = []
 
 def get_indices_from_name(name):
-    return int(name[7:9]), int(name[10:12])
+    return int(name[8:10]), int(name[11:13])
 
 with open("cad-period-sync-contour.npy", 'rb') as f:
    uncs = np.load(f)[:,:,2] # Use median
@@ -29,7 +29,7 @@ with open("../../data/cad-period-sync-contour/percentiles.dat", 'r') as f:
         percentiles[name] = perc_array
 
 for name in percentiles.keys():
-    dir_name = name[:12]
+    dir_name = name[:13]
     with open(f"../../data/cad-period-sync-contour/{dir_name}/{dir_name}.txt", 'r') as f:
         max_j, max_l = f.readline().split(", ")
         max_j, max_l = (int(max_j), int(max_l))
@@ -43,20 +43,22 @@ for name in percentiles.keys():
         theta_high = [float(x) for x in f.readline().split(',')]
         theta_low = [float(x) for x in f.readline().split(',')]
         sigma = [float(d) for d in f.readline().split(',')]
-        time_ratio = float(f.readline())
     cadence_index, period_index = get_indices_from_name(name)
     if period_index == 1:
         cadences.append(cadence / 60)
     if cadence_index == 1:
-        time_ratios.append(time_ratio)
+        period = 2 * np.pi / np.linalg.norm(spin) / 3600.0
+        periods.append(period)
 
 cadences = np.sort(cadences)
-time_ratios = np.sort(time_ratios)
+periods = np.sort(periods)
+print(cadences),
+print(periods)
 
 fig = plt.figure(figsize=(6.6, 4))
-p = plt.contourf(cadences, time_ratios, uncs, levels=10)
+p = plt.contourf(cadences, periods, uncs, levels=10)
 cbar = plt.colorbar(p)
-plt.ylabel(f"$t_\\mathrm{{spin}}/t_\\mathrm{{orbit}}$")
+plt.ylabel(f"$P_\omega$ (hr)")
 plt.xlabel(f"$\Delta t$ (min)")
 plt.savefig("cad-period-contour-net.pdf", bbox_inches="tight")
 plt.savefig("cad-period-contour-net.png", bbox_inches="tight")

### 2022-08-04 data/cad-period-sync-contour/compile.py

@@ -25,7 +25,7 @@ def get_indices_from_name(name):
     return int(name[8:10]), int(name[11:13])
 
 with open("../../code/thresholds/cad-period-sync-contour.npy", 'rb') as f:
-    uncs = np.load(f)
+    uncs = np.load(f)[:,:,2] # Use median
 
 # Adjust uncs so that everything after the first large unc is large
 def adjust(a):
@@ -99,7 +99,7 @@ for plot_index in range(N_DIM):
     #p = ax.pcolormesh(cadences, periods, param_data.transpose() * scale, vmin=0, cmap="Oranges_r")
     levels = np.linspace(0, np.percentile(param_data * scale, 90), 12)
     p = ax.contourf(cadences, periods, param_data.transpose() * scale, cmap="PuBu_r", levels=levels, extend='max')
-    ax.contour(cadences, periods, uncs, colors='r', levels=[0.2, 1], linestyles=["dashed", "solid"])
+    ax.contour(cadences, periods, uncs, colors='r', levels=[1e-4, 1e-3], linestyles=["dashed", "solid"])
 
     cbar = fig.colorbar(p, ax=ax)
     if plot_index < 3:

### 2022-08-04 paper/appendices.tex
Pushed some remaining files and decided not to include cadence dependence appendix
Staged perigee as well

@@
 
-Equation \ref{eqn:tidal-torque} possesses a few explicit properties.
-Firstly, $\bm \tau$ is independent of asteroid mass.
-The mean density of the asteroid is therefore not constrained by tidal torque analysis.
-Secondly, torque is largest when $D$ is small (as expected), with the leading order of $\bm \tau$ proportional to $D^{-3}$.
-Thirdly, each $J_{\ell m}K_{\ell' m'}$ term is multiplied by $(a_\mathcal{B}/D)^\ell (a_\mathcal{A}/D)^{\ell'}$, the latter of which especially is small in most cases.
-Equation \ref{eqn:tidal-torque} can therefore be computed approximately by removing terms of large $\ell$ and $\ell'$.
-For our analysis, we removed $\ell' > 3$ and we usually keep only $\ell=0$.
-Note that $\ell=1$ contributes nothing since $J_{1m}=0$.
-$J_{2m}$ measures the oblateness and its effects are studied in appendix \ref{app:uncertainty-dependence}.
-
-Further insight can be gained by remarking the value of the first-order of $\bm \tau$ for particular Euler angle cases.
-Setting $\beta = 0$ produces diagonal Wigner-$D$ matrices, and hence $\bm \tau \parallel \unit z$ to first-order.
-This $\beta=0$ condition is equivalent to $\unit z \parallel \unit Z$ (see figure \ref{fig:euler-angles}).
-
-For $\beta = \pi/2$, there are two interesting cases.
-One is for $\alpha = \phi$ (or $\alpha = \pi + \phi$), where $\phi$ is the angle between the asteroid and the perigee.
-In this case, $\bm \tau = 0$ to first-order.
-The second case is $\alpha = \phi \pm \pi/2$, when again $\bm \tau \parallel \unit z$.
-At perigee ($\phi=0$), these conditions are equivalent to $\unit z \parallel \unit X$ and $\unit z \parallel \unit Y$ respectively.
-
-The $\bm \tau \parallel \unit z$ cases are interesting because they do not induce tumbling.
-If velocity is $\bm \omega \parallel \unit z$ (a non-tumbling state, since $\unit z$ is a principal axis), then $\bm \omega \parallel \bm L$ and $\bm \tau = \dot{\bm L} \parallel \dot{\bm \omega}$ so that $\bm \omega$ remains parallel to $\unit z$ and non-tumbling.
-These cases of torque are additionally significant because not as many terms contribute to $\tau_z$ as to $\tau_x$ and $\tau_y$.
-
 \subsection{Equations of motion}
@@
   \begin{split}
-    I_x \dot \omega_1 - \omega_y \omega_z (I_y - I_z) &= \tau_x\\
-    I_y \dot \omega_2 - \omega_z \omega_x (I_z - I_x) &= \tau_y\\
-    I_z \dot \omega_3 - \omega_x \omega_y (I_x - I_y) &= \tau_z.
+    I_x \dot \omega_x - \omega_y \omega_z (I_y - I_z) &= \tau_x\\
+    I_y \dot \omega_y - \omega_z \omega_x (I_z - I_x) &= \tau_y\\
+    I_z \dot \omega_z - \omega_x \omega_y (I_x - I_y) &= \tau_z.
   \end{split}
@@
 Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, and \ref{eqn:pos-eom} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
-They are expressed in terms of the constant physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$.
+They are expressed in terms of the physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$ which are constant if the asteroid is rigid and the central body does not rotate.
 
@@
 
-% \section{The cadence cut-off}
+\section{Comparing orientation and angular velocity data}
+
+To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
+It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
+In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
+
+We may expect some differences in the resolving power of orientation and angular velocity data, but not a large difference, due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid position.
+The initial position is defined up to $\gamma_0$ by the assumption of no initial tumbling, and figures \ref{fig:scan-physical} and \ref{fig:scan-observational} reveal that $\gamma_0$ is typically also constrained to high precision even by angular velocity data.
+Thus, we expect the only differences between moment uncertainty as obtained from angular velocity data or from orientation data to be due to the uncertainty of the data itself.
+
+\subsection{Uncertainty model}
+The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
+This requires a new model for the uncertainty of orientation observations.
+
+For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
+Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
+\begin{equation}
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\brackets{(\quat q_i (\quat q_i^*)^{-1})_r}}^2
+  \label{eqn:orientation-like}
+\end{equation}
+where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
+
+\subsection{Moment uncertainty comparison}
+With the likelihood defined, density moments can be extracted from the orientation data via the fit process described in the main text and compared to those extracted from the angular velocity data.
+We generate data of both types for the reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets.
+
+Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
+One could not tell if one data set yields more precise moments because the observational precision of that data set is better or because that data type affords better estimation of density moments.
+However, the relative uncertainty of moments can be compared between the two data sets.
+
+We generate moment uncertainty for the orientation data using a test value of $\sigma_\phi = 0.1$ and compute the mean uncertainty.
+We then scale the moment uncertainties attained from the angular velocity data set with the reference observational uncertainty parameters so that the mean uncertainty of all the moments is equal to that of the orientation data set.
+This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
+We then compute the ratio between $\sigma(K_{\ell m})$ for the observational data set and the angular velocity data set and show the result as a function of $\ell$ and $m$ in figure \ref{fig:observational-moment-uncertainty}.
+\begin{figure}
+  \centering
+  % \includegraphics{figs/observational-moment-uncertainty}
+  \caption{\jtd{Write}}
+  \label{fig:observational-moment-uncertainty}
+\end{figure}
+
+\subsection{Density uncertainty comparison}
+
+% \section{Dependence of the cadence cut-off on time scales}
 % \label{app:cadence-tests}
 
-% \jtd{Remove this section or included it in the following section.}
+% In section \ref{sec:scan-cadence}, we noted that moment uncertainty as a function of observation cadence $\Delta t$ increases suddenly near $\Delta t_\text{cut-off} \approx 30-40$ min.
+By dimensional analysis, $\Delta t_\text{cut-off}$ depends both on the asteroid period $P_\omega$ and the orbital time scales.
+In this appendix, we assess the relationship between $\Delta t_\text{cut-off}$ and these time scales by measuring moment uncertainty as a function of cadence at different values of these time scales.
+However, changing the time scales also affects the moment uncertainty directly, obscuring the cadence dependence of the moment uncertainty.
+Figure \ref{fig:scan-period} indicates that $P_\omega$ only slightly affects moment uncertainty as long as $P_\omega$ is not too small, so we neglect this obscuring effect in the case of $P_\omega$.
+To assess the dependence of $\Delta t$ on the orbital time scales, we fix the orbit shape and simulate the asteroid as following the orbit at different speeds.
+This process is unphysical, but it has the advantage of keeping all encounter parameters fixed except for the time the asteroid spends in the orbit, thereby isolating the orbital time scale.
+We parametrize this change $v_\text{orbit} / v_\text{physical}$, which is large for an artificially fast encounter, low for an artificially slow encounter, and 1 for a physical encounter.
 
-% In section \ref{sec:scan-cadence}, we noted that posterior uncertainty as a function of observation cadence $\Delta t$ appears to increase suddenly near $\Delta t \sim T_\text{cad}=30-40$ min.
-In this appendix, we discuss the location of this cadence cut-off as a function of the physical parameters of the asteroid.
-
-% In figure \ref{fig:cad-contour}, we display contour plots of posterior uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ (left panel) or the relative orbit speed $t_\text{spin} / t_\text{orbit}$ (right panel).
-Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
+% In figure \ref{fig:cad-contour}, we display contour plots of moment uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ and the relative orbit speed $v_\text{orbit} / v_\text{physical}$.
+Superimposed is the weak Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
 In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
@@
 \end{figure*}
-
-\section{Comparing orientation and angular velocity data}
-
-To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
-It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
-In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
-
-We may expect some differences in the resolving power of orientation and angular velocity data, but not a large difference, due to the following argument.
-If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
-Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid position.
-The initial position is defined up to $\gamma_0$ by the assumption of no initial tumbling, and figures \ref{fig:scan-physical} and \ref{fig:scan-observational} reveal that $\gamma_0$ is typically also constrained to high precision even by angular velocity data.
-Thus, we expect the only differences between moment uncertainty as obtained from angular velocity data or from orientation data to be due to the uncertainty of the data itself.
-
-\subsection{Uncertainty model}
-The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
-This requires a new model for the uncertainty of orientation observations.
-
-For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
-Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
-\begin{equation}
-  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\brackets{(\quat q_i (\quat q_i^*)^{-1})_r}}^2
-  \label{eqn:orientation-like}
-\end{equation}
-where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
-
-\subsection{Moment uncertainty comparison}
-With the likelihood defined, density moments can be extracted from the orientation data via the fit process described in the main text and compared to those extracted from the angular velocity data.
-We generate data of both types for the reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets.
-
-Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
-One could not tell if one data set yields more precise moments because the observational precision of that data set is better or because that data type affords better estimation of density moments.
-However, the relative uncertainty of moments can be compared between the two data sets.
-
-We generate moment uncertainty for the orientation data using a test value of $\sigma_\phi = 0.1$ and compute the mean uncertainty.
-We then scale the moment uncertainties attained from the angular velocity data set with the reference observational uncertainty parameters so that the mean uncertainty of all the moments is equal to that of the orientation data set.
-This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
-We then compute the ratio between $\sigma(K_{\ell m})$ for the observational data set and the angular velocity data set and show the result as a function of $\ell$ and $m$ in figure \ref{fig:observational-moment-uncertainty}.
-\begin{figure}
-  \centering
-  % \includegraphics{figs/observational-moment-uncertainty}
-  \caption{\jtd{Write}}
-  \label{fig:observational-moment-uncertainty}
-\end{figure}
-
-\subsection{Density uncertainty comparison}

### 2022-08-04 data/scan-perigee-sync/compile.py

@@ -1,0 +1,146 @@
+# Goal: spawn a bunch of runs that cover the parameter space.
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib.lines import Line2D
+import lmfit
+
+plt.style.use("jcap")
+
+param_names = ["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"]
+
+percentiles = {}
+name_index = {}
+true_sigma = None
+perigees = []
+
+AXIS_SIZE = 12
+LEGEND_SIZE = 12
+
+N_DIM = None
+N_PERCENTILES = None
+
+SCALE_Y = 1.1
+
+# Get percentiles
+with open("percentiles.dat", 'r') as f:
+    for line in f.readlines():
+        if line == '': continue
+        elements = line.split(':')
+        name = elements[0]
+        perc_array = []
+        for percs in elements[1:]:
+            perc_array.append([float(x) for x in percs.split(',')])
+        perc_array = np.array(perc_array)
+        N_DIM = perc_array.shape[0]
+        N_PERCENTILES = perc_array.shape[1]
+        percentiles[name] = perc_array
+
+# Get true sigmas
+index = 0
+for name in percentiles.keys():
+    dir_name = name[:7]
+    with open(f"{dir_name}/{dir_name}.txt", 'r') as f:
+        max_j, max_l = f.readline().split(", ")
+        max_j, max_l = (int(max_j), int(max_l))
+        cadence = int(f.readline())
+        perigee = float(f.readline())
+        radius = float(f.readline())
+        speed = float(f.readline())
+        spin = [float(x) for x in f.readline().split(',')]
+        jlms = [float(x) for x in f.readline().split(',')]
+        theta_true = [float(x) for x in f.readline().split(',')]
+        theta_high = [float(x) for x in f.readline().split(',')]
+        theta_low = [float(x) for x in f.readline().split(',')]
+        sigma = [float(d) for d in f.readline().split(',')]
+    name_index[name] = index
+    index += 1
+    true_sigma = sigma[0]
+    perigees.append(perigee)
+
+perigees = np.array(perigees)
+
+fig = plt.figure(figsize=(6.6, 19))
+
[…]

### 2022-08-08 paper/appendices.tex
Updated orientation
Orientation moments finished

@@
 
-We may expect some differences in the resolving power of orientation and angular velocity data, but not a large difference, due to the following argument.
-If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
-Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid position.
-The initial position is defined up to $\gamma_0$ by the assumption of no initial tumbling, and figures \ref{fig:scan-physical} and \ref{fig:scan-observational} reveal that $\gamma_0$ is typically also constrained to high precision even by angular velocity data.
-Thus, we expect the only differences between moment uncertainty as obtained from angular velocity data or from orientation data to be due to the uncertainty of the data itself.
-
 \subsection{Uncertainty model}
@@
 \begin{equation}
-  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\brackets{(\quat q_i (\quat q_i^*)^{-1})_r}}^2
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
   \label{eqn:orientation-like}
@@
 \subsection{Moment uncertainty comparison}
-With the likelihood defined, density moments can be extracted from the orientation data via the fit process described in the main text and compared to those extracted from the angular velocity data.
-We generate data of both types for the reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets.
-
+With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets via the fit method defined in the main text.
 Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
-One could not tell if one data set yields more precise moments because the observational precision of that data set is better or because that data type affords better estimation of density moments.
+If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
 However, the relative uncertainty of moments can be compared between the two data sets.
 
-We generate moment uncertainty for the orientation data using a test value of $\sigma_\phi = 0.1$ and compute the mean uncertainty.
-We then scale the moment uncertainties attained from the angular velocity data set with the reference observational uncertainty parameters so that the mean uncertainty of all the moments is equal to that of the orientation data set.
+To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets and also compute the mean value of $\sigma(K_{\ell m})$ over all fit parameters.
+We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
 This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
-We then compute the ratio between $\sigma(K_{\ell m})$ for the observational data set and the angular velocity data set and show the result as a function of $\ell$ and $m$ in figure \ref{fig:observational-moment-uncertainty}.
-\begin{figure}
+The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
+
+\begin{figure*}
   \centering
-  % \includegraphics{figs/observational-moment-uncertainty}
-  \caption{\jtd{Write}}
-  \label{fig:observational-moment-uncertainty}
-\end{figure}
+  \includegraphics[width=0.75\linewidth]{figs/orientation-unc}
+  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
+First order parameters are shown in the left panel and second-order parameters in the right.
+Mean values are also shown as horizontal lines.
+Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
+  \label{fig:orientation-unc}
+\end{figure*}
+
+The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$.
+This is expected due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
+This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly.
+A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
 

### 2022-08-08 code/density/mcmc/core-scan/gen-cores.py

@@ -18,6 +18,8 @@ ELLIPSOID_AM = 1000
 SURFACE_AMS = {
     "sym": 1000,
     "asym": 1000,
+    "ori": 1000,
+    "vel": 1000,
     "sph-3": 1000,
     "sph-1.5": 1000,
     "move-3": 1002.0081758422925,
@@ -28,6 +30,8 @@ SURFACE_AMS = {
 BULK_AMS = {
     "sym": 1000,
     "asym": 1000,
+    "ori": 1000,
+    "vel": 1000,
     "sph-3": 922.9234884822591,
     "sph-1.5": 978.4541044108308,
     "move-3": 933.1648422811957,
@@ -54,6 +58,8 @@ core_two = np.array([0, -500, 0])
 TRUE_SHAPES = {
     "sym": TrueShape.uniform(),
     "asym": TrueShape.uniform(),
+    "ori": TrueShape.uniform(),
+    "vel": TrueShape.uniform(),
     "sph-3": TrueShape.core_sph(3, 500),
     "sph-1.5": TrueShape.core_sph(1.5, 500),
     "move-3": TrueShape.core_shift(3, 500, core_displacement),
@@ -63,6 +69,8 @@ TRUE_SHAPES = {
 INDICATORS = {
     "sym": Indicator.ell(ELLIPSOID_AM, k22s, k20s),
     "asym": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
+    "ori": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
+    "vel": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
     "sph-3": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
     "sph-1.5": Indicator.ell(ELLIPSOID_AM, k22a, k20a),
     "move-3": Indicator.ell_y_shift(ELLIPSOID_AM, k22a, k20a, -core_shift_high),
@@ -72,6 +80,8 @@ INDICATORS = {
 SAMPLE_NAME = {
     "sym": "den-sym",
     "asym": "den-asym",
+    "ori": "ori-e-5",
+    "vel": "scale-vel",
     "sph-3": "den-core-sph-3",
     "sph-1.5": "den-core-sph-1.5",
     "move-3": "den-core-move-3",

### 2022-08-08 code/density/mcmc/core-scan/gen-cores.sh

@@ -8,8 +8,10 @@ source /etc/profile
 
 module load anaconda/2022a
 
-python gen-cores.py sym $SLURM_ARRAY_TASK_ID
-python gen-cores.py double $SLURM_ARRAY_TASK_ID
+python gen-cores.py ori $SLURM_ARRAY_TASK_ID
+python gen-cores.py vel $SLURM_ARRAY_TASK_ID
+#python gen-cores.py sym $SLURM_ARRAY_TASK_ID
+#python gen-cores.py double $SLURM_ARRAY_TASK_ID
 #python gen-cores.py asym $SLURM_ARRAY_TASK_ID
 #python gen-cores.py sph-3 $SLURM_ARRAY_TASK_ID
 #python gen-cores.py sph-1.5 $SLURM_ARRAY_TASK_ID

### 2022-08-09 paper/appendices.tex
Finished orientation appendix

@@
 
+\section{Comparing orientation and angular velocity data}
+
+To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
+It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
+In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
+
+\subsection{Uncertainty model}
+The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
+This requires a new model for the uncertainty of orientation observations.
+
+For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
+Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
+\begin{equation}
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
+  \label{eqn:orientation-like}
+\end{equation}
+where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
+
+\subsection{Moment uncertainty comparison}
+With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets via the fit method defined in the main text.
+Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
+If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
+However, the relative uncertainty of moments can be compared between the two data sets.
+
+To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets and also compute the mean value of $\sigma(K_{\ell m})$ over all fit parameters.
+We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
+This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
+The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{figs/orientation-unc}
+  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
+First order parameters are shown in the top panel and second-order parameters in the bottom.
+Mean values are also shown as vertical lines.
+Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
+  \label{fig:orientation-unc}
+\end{figure}
+
+The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$.
+This is expected due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
+This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly.
+
+A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$, which will alter the density uncertainty discussed in the next section.
+However, this has little effect on the density distributions extracted by the finite element model from the two PPDs shown in the figure.
+The average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the distribution of density and density uncertainty extracted.
+
 \section{Additional density distribution models}
@@
 This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
-
-\section{Comparing orientation and angular velocity data}
-
-To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
-It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
-In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
-
-\subsection{Uncertainty model}
-The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
-This requires a new model for the uncertainty of orientation observations.
-
-For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
-Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
-\begin{equation}
-  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
-  \label{eqn:orientation-like}
-\end{equation}
-where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
-
-\subsection{Moment uncertainty comparison}
-With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets via the fit method defined in the main text.
-Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
-If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
-However, the relative uncertainty of moments can be compared between the two data sets.
-
-To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets and also compute the mean value of $\sigma(K_{\ell m})$ over all fit parameters.
-We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
-This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
-The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.75\linewidth]{figs/orientation-unc}
-  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
-First order parameters are shown in the left panel and second-order parameters in the right.
-Mean values are also shown as horizontal lines.
-Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
-  \label{fig:orientation-unc}
-\end{figure*}
-
-The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$.
-This is expected due to the following argument.
-If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
-Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
-This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly.
-A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
-
-\subsection{Density uncertainty comparison}
 

### 2022-08-09 orientation/moments/compile.py

@@ -1,0 +1,115 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import corner
+import os
+
+PULL = False
+ORI_NAME = "ori-e-5"
+SIGMA_DISPLAY = 3
+N_BINS = 30
+TRUES = np.array([0.39269908169, 0.05200629, -0.2021978, 0, 0, 0, 0, 0, 0, 0])
+
+plt.style.use('jcap')
+
+param_names = np.array(["\\gamma_0", "K_{22}", "K_{20}", "\Re K_{33}", "\Im K_{33}", "\Re K_{32}", "\Im K_{32}", "\Re K_{31}", "\Im K_{31}", "K_{30}"])
+
+if PULL:
+    os.system(f"scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/orientation/fit_resolved/{ORI_NAME}-0-samples.npy .")
+    os.system("scp jdinsmore@txe1-login.mit.edu:asteroid-tidal-torque/code/fit_resolved/scan-cadence/cad-00-0-samples.npy .")
+
+with open("cad-00-0-samples.npy", 'rb') as f:
+    vel_moments = np.load(f).reshape(-1, 10)
+
+with open(f"{ORI_NAME}-0-samples.npy", 'rb') as f:
+    o_moments = np.load(f).reshape(-1, 10)
+
+num_select = min(vel_moments.shape[0], o_moments.shape[0])
+vel_moments = vel_moments[np.random.choice(np.arange(0, vel_moments.shape[0]), num_select, replace=False)]
+o_moments = o_moments[np.random.choice(np.arange(0, o_moments.shape[0]), num_select, replace=False)]
+
+vel_resids = vel_moments - np.mean(vel_moments, axis=0)
+o_resids = o_moments - np.mean(o_moments, axis=0)
+ratio = np.mean(np.std(vel_resids, axis=0)) / np.mean(np.std(o_resids, axis=0))
+print(f"Ratio {ratio}")
+vel_resids /= ratio
+vel_moments = vel_resids + np.mean(vel_moments, axis=0)
+
+## Save new moments
+
+for name, moments in zip(["scale-vel", "scale-ori"], [vel_moments, o_moments]):
+    new_moments = np.zeros_like(moments)
+    # Rotate so that K22 -> -K22 
+    new_moments[:,0] = moments[:,0] # gamma_0
+    new_moments[:,1] = -moments[:,1] # K22
+    new_moments[:,2] = moments[:,2] # K20
[…]

### 2022-08-09 paper/appendices.tex
Edits to paper

--- 2022-08-08 paper/appendices.tex
@@
 
+\section{Comparing orientation and angular velocity data}
+
+To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
+It is possible that the orientation of the asteroid may be more readily available as a data set.
+In this appendix, we generate an orientation data set for the reference asteroid flyby, extract density moments from it, and compare the results to moments extracted from angular velocity data.
+
+\subsection{Uncertainty model}
+To use an asteroid orientation data set rather than angular velocity, we must create an uncertainty model for orientation observations and produce a likelihood to be used by the MCMC (replacing equation \ref{eqn:log-likelihood}).
+
+For the sake of this appendix, we will assume that all observations of orientation $\quat q$ differ from the true orientation $\quat q^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
+As in the rest of the paper, orientation is expressed as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$.
+The angle $\phi$ can be extracted from these quaternion components to yield a likelihood of
+\begin{equation}
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
+  \label{eqn:orientation-like}
+\end{equation}
+where a subscript $i$ denotes the $i$th element of the data set. It is assumed that both quaternions have norm one.
+
+\subsection{Moment uncertainty comparison}
+With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract density moment PPDs for both data sets via the fit method defined in the main text.
+Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the amount of moment uncertainty for both data sets.
+If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
+However, the relative uncertainty of moments can be compared between the two data sets.
+
+To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets.
+We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
+This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same average precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
+The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{figs/orientation-unc}
+  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
+First order parameters are shown in the top panel and second-order parameters in the bottom.
+Mean values are also shown as vertical lines.
+Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
+  \label{fig:orientation-unc}
+\end{figure}
+
+The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$, which is much more precisely constrained by orientation data than by angular velocity data.
+This result is expected due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
+That initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so we expect the angular velocity data set to yield increased uncertainties in $\gamma_0$ only, relative to the observational data, to a first approximation.
+
+A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
+However, this has little effect on the density distributions extracted by the finite element model; the average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
+
 \section{Additional density distribution models}
@@
 Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
-Here we outline two additional models, the nearly-uniform and the harmonic models, which are less conventional but still useable for extracting density distribution properties.
+Here we outline two additional models --- the nearly-uniform and the harmonic models --- which are less conventional but still useable for extracting density distribution properties.
 Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.
-They also rely on a known surface for the asteroid.
 
@@
 \end{equation}
-where $M^\dagger$ is the adjoint of $M$.
+where $M^\dagger$ is the hermitian conjugate of $M$.
 
 The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
- can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
 
 \subsection{Harmonic model}
-This the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
+In the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
 We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.
@@
 \end{equation}
-These integrals can be pre-computed given a known asteroid shape $\mathcal{A}$, so that computing $C_{\ell m}$ to match a given $K_{\ell m}$ is fast.
+Since the integrals are independent of the parameters, they can be computed before solving for $C_{\ell m}$.
 Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions.
@@
 Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$.
-The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics weighted by $K_{\ell m}$.
-When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to break this picture.
+The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics $R_{\ell m}$ weighted by $K_{\ell m}$.
+When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to alter this picture.
 
-Imposing constraints on these moments is also necessary.
-The choice of mass is enforced via equation \ref{eqn:harmonic-mass}.
-We impose bounds on $\rho(\bm r)$ by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid.
+$C_{\ell m}$ can be treated as parameters for a fitting method (such as an MCMC) that enforces our bounds on $\rho(\bm r)$.
+With the integrals pre-computed, obtaining $K_{\ell m}$ from $C_{\ell m}$ is fast.
+We impose these bounds by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid.
 This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
-
-\section{Comparing orientation and angular velocity data}
-
-To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
-It is possible that the orientation of the asteroid may be better constrained by observations than angular velocity.
-In this appendix, we generate an orientation data set for the reference asteroid flyby, extract a density distribution from it, and compare the results to distributions extracted from angular velocity data.
-
-\subsection{Uncertainty model}
-The likelihood used by the MCMC (equation \ref{eqn:log-likelihood}) requires redefinition in order to extract density moments from orientation data.
-This requires a new model for the uncertainty of orientation observations.
-
-For the sake of this appendix, we will assume that all observations of orientation $O$ differ from the true orientation $O^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
-Expressing orientation as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$, $\phi$ can be extracted and the likelihood written as
-\begin{equation}
-  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i=0}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
-  \label{eqn:orientation-like}
-\end{equation}
-where $\quat q_i$ is the $i$th quaternion in the data set measured in the inertial frame, and $\quat q_i^*$ is the true quaternion. It is assumed that both quaternions have norm one.
-
-\subsection{Moment uncertainty comparison}
-With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract $K_{\ell m}$ means and uncertainties for both data sets via the fit method defined in the main text.
-Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the sizes of moment uncertainty for both data sets.
-If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
-However, the relative uncertainty of moments can be compared between the two data sets.
-
-To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets and also compute the mean value of $\sigma(K_{\ell m})$ over all fit parameters.
-We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
-This is equivalent to simply choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
-The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.75\linewidth]{figs/orientation-unc}
-  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
-First order parameters are shown in the left panel and second-order parameters in the right.
-Mean values are also shown as horizontal lines.
-Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
-  \label{fig:orientation-unc}
-\end{figure*}
-
-The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$.
-This is expected due to the following argument.
-If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
-Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
-This initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so that the orientation data set will affect $\sigma(\gamma_0)$ most strongly.
-A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
-
-\subsection{Density uncertainty comparison}
 

### 2022-08-09 paper/main.tex
Done with gamma
Edits to paper

@@
 
-In the following mathematical model for the influence of tidal torque on asteroid encounters, we assume for simplicity that (1) that the central body is much more massive than the asteroid, (2) that both are rigid, (3) that there are no distant perturbing objects and (4) that the asteroid is in a short-axis, non-tumbling rotational state before the encounter.
+In the following mathematical model for the influence of tidal torque on asteroid encounters, we assume for simplicity that (1) the central body is much more massive than the asteroid, (2) both are rigid, (3) there are no distant perturbing objects, and (4) the asteroid is in a short-axis, non-tumbling rotational state before the encounter.
 All of these assumptions except 2 can be relaxed without drastic changes to the model.
@@
 Equation \ref{eqn:tidal-torque} indicated that tidal torque was also proportional to $I_\mathcal{A}$.
-The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is independent $I_\mathcal{A}$.
+The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is therefore independent $I_\mathcal{A}$.
 Thus, the observables do not depend explicitly on $I_\mathcal{A}$.
@@
 We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant.
-Moment uncertainties varied by factors of \jtd{25-100\%}, generally exhibiting roughly sinusoidal behaviour.
+Moment uncertainties generally varied by factors of two or less, exhibiting roughly sinusoidal behaviour.
 The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape.

### 2022-08-12 paper/main.tex
Review of new perigee data

@@
     Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
-    Period ($P_\omega$, hr) & $>$7.6 & - \\ \hline
+    Period ($P_\omega$, hr) & $>$5.3 & - \\ \hline
     Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\

### 2022-08-16 paper/appendices.tex
Revised paper

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%
-
 \appendix
@@
 
-In this appendix, we derive the equations of motion used to simulate the asteroid angular velocity during the encounter.
+In this appendix, we derive the equations of motion used to simulate the asteroid encounter.
 In particular, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its density moments (section \ref{sec:moments}).
@@
 \end{equation}
-Here, $R_i(\theta)$ is a rotation around the unit vector $i$ by $\theta$ (figure \ref{fig:euler-angles}).
+Here, $R_i(\theta)$ is a rotation around the unit vector $i$ by angle $\theta$ (figure \ref{fig:euler-angles}).
 
@@
     \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit Z$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (4, 0) node[anchor=west] {$\unit Y$};
-    %\draw[-{Latex[length=3mm]}] (0, 0) -- (-2, -2) node[anchor=east] {$\unit X$};
     \end{tikzpicture}
@@
 Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless.
-We call them ``moments'' because the $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
+We call them ``moments'' because $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
 
@@
 \begin{equation}
-  -\frac{1}{4} \leq K_{20} \leq 0, \qquad |K_{22}| \leq -\frac{K_{20}}{2}.
+  -\frac{1}{4} \leq K_{20} \leq 0, \qquad |K_{22}| \leq \frac{|K_{20}|}{2}.
   \label{eqn:parameter-bounds}
 \end{equation}
-An analytical constraint on $K_{3m}$ based on this property is more difficult to derive, but in practice, we also observe that $|K_{3m}| < 0.01$.
+An analytical constraint on $K_{3m}$ based on this property is more difficult to derive, but in practice, we observe that $|K_{3m}| < 0.01$.
 
@@
 \begin{equation}
-V(\bm R') = -G\int_\mathcal{B} d^3 R \rho_\mathcal{B}(\bm R) \frac{1}{|\bm{R}-\bm{R'}|}.
+V(\bm R') = -G\int_\mathcal{B} d^3 R \frac{\rho_\mathcal{B}(\bm R)}{|\bm{R}-\bm{R'}|}.
 \label{eqn:first-pe}
@@
 \end{equation}
-Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, and \ref{eqn:pos-eom} to \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
+Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, \ref{eqn:pos-eom}, and \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
 They are expressed in terms of the physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$ which are constant if the asteroid is rigid and the central body does not rotate.
@@
 \section{Comparing orientation and angular velocity data}
+\label{app:orientation}
 
@@
 Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the amount of moment uncertainty for both data sets.
-If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.
-However, the relative uncertainty of moments can be compared between the two data sets.
+(If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.) However, the relative uncertainty of moments can be compared.
 
@@
 We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
-This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same average precision as the observational data set, because figure \ref{fig:scan-observational} shows that density moment uncertainty $\sigma(K_{\ell m})$ is proportional to observational uncertainty.
-The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc}, as well as their mean values relative to the true values.
+This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same average precision as the observational data set.
+The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc} relative to the true values.
 
@@
 Mean values are also shown as vertical lines.
-Both data produce similar constraints on parameters, except in the case of $\gamma_0$.}
+Both data sets produce similar constraints on parameters, except in the case of $\gamma_0$.}
   \label{fig:orientation-unc}
@@
 A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
-However, this has little effect on the density distributions extracted by the finite element model; the average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
+However, this has little effect on the density distributions extracted by the finite element model (not shown); the average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
 
@@
 This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
-
-% \section{Dependence of the cadence cut-off on time scales}
-% \label{app:cadence-tests}
-
-% In section \ref{sec:scan-cadence}, we noted that moment uncertainty as a function of observation cadence $\Delta t$ increases suddenly near $\Delta t_\text{cut-off} \approx 30-40$ min.
-By dimensional analysis, $\Delta t_\text{cut-off}$ depends both on the asteroid period $P_\omega$ and the orbital time scales.
-In this appendix, we assess the relationship between $\Delta t_\text{cut-off}$ and these time scales by measuring moment uncertainty as a function of cadence at different values of these time scales.
-However, changing the time scales also affects the moment uncertainty directly, obscuring the cadence dependence of the moment uncertainty.
-Figure \ref{fig:scan-period} indicates that $P_\omega$ only slightly affects moment uncertainty as long as $P_\omega$ is not too small, so we neglect this obscuring effect in the case of $P_\omega$.
-To assess the dependence of $\Delta t$ on the orbital time scales, we fix the orbit shape and simulate the asteroid as following the orbit at different speeds.
-This process is unphysical, but it has the advantage of keeping all encounter parameters fixed except for the time the asteroid spends in the orbit, thereby isolating the orbital time scale.
-We parametrize this change $v_\text{orbit} / v_\text{physical}$, which is large for an artificially fast encounter, low for an artificially slow encounter, and 1 for a physical encounter.
-
-% In figure \ref{fig:cad-contour}, we display contour plots of moment uncertainty $\sigma(K_{\ell m})$ of the fit parameters as a function of both cadence $\Delta t$ and $P_\omega$ and the relative orbit speed $v_\text{orbit} / v_\text{physical}$.
-Superimposed is the weak Both panels show the same sudden increase in posterior uncertainty we named $T_\text{cad}$, located around the region where $\sigma_\rho / \rho = 100\%$ and now visible as a function of frequency and relative orbit speed.
-In all cases, the value of $\gamma_0$ was set so that all data points achieve the same value of $\gamma$ at perigee.
-
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=0.48\textwidth]{figs/cad-period.pdf}\hfill
-%   \includegraphics[width=0.48\textwidth]{figs/cad-speed.pdf}
-%   \caption{Contour plots showing posterior uncertainties as a function of cadence $\Delta t$ and dynamical time scales for the encounter: rotational period $P_\omega$ (\textit{left}) and the relative speed of the orbit (\textit{right}; see text for a definition).
-The reference values of $P_\omega=9$ hr and $t_\text{spin}/t_\text{orbit}=1$ are shown as dotted lines.
-The solid (dotted) red line represents the $\sigma_\rho / \rho = 100\%$ (20\%) threshold.
-Cadence cut-off depends strongly on both $P_\text{omega}$ and $t_\text{spin}/t_\text{orbit}=1$.}
-%   \label{fig:cad-contour}
-% \end{figure*}
-
-% Figure \ref{fig:cad-contour} demonstrates that large rotational period produces high $T_\text{cad}$.
-The dependence on $P_\omega$ agrees with the fact that large rotational periods for fixed cadence lead to better posterior uncertainty, discussed in section \ref{sec:scan-period}.
-The figure also demonstrates that for large $P_\omega$, $T_\text{cad}$ depends less strongly on $P_\text{omega}$ and may even reverse its dependence such that increasing $P_\text{omega}$ decreases $T_\text{omega}$.
-In all cases except $\Re K_{33}$, at least constant-$\sigma(K_{\ell m})$ contour is seen to curve back such that $\Delta t$ decreases as a function of $P_\text{omega}$ for large $P_\text{omega}$.
-In these regions the cadence cut-off also dulls, as shown by the spreading of the constant-$\sigma(K_{\ell m})$ contours in this region.
-
-%  The relative orbit speed $t_\text{spin} / t_\text{orbit}$ was defined by un-physically increasing or decreasing the time at which the asteroid moved through the orbit determined by the equations of motion (but leaving the orbit shape unchanged).
-The equations of motion affecting the orientation and spin of the asteroid however were unaffected.
-$t_\text{spin} / t_\text{orbit} > 1$ corresponds to a faster orbit, and $t_\text{spin} / t_\text{orbit} < 1$ corresponds to a slower orbit.
-With this unphysical process, we isolate the effect of the amount of time spent near perigee on posterior uncertainty, without inheriting additional affects that would have been caused by the orbit changing shape.
-
-% The right panel of figure \ref{fig:cad-contour} shows a stronger and more monotonic dependence of $T_\text{cad}$ on $t_\text{spin} / t_\text{orbit}$.
-It appears that even slightly slower orbits sharply increases $T_\text{cad}$.
-This effect is both due to the asteroid spending greater time in the high-torque, near-perigee region, and the larger data set that can be collected for slow orbits.
-However, if the orbit speed is changed by adjusting its parameters ($v_\infty$, $r_p$) or the central body mass $\mu_\mathcal{B}$, then the orbit shape will also change.
-This induces other effects studied in the main text and will complicate the trend observed here.
-Unlike the $P_\omega$ case, the cadence cut-off does not visibly broaden as a function of $t_\text{spin} / t_\text{orbit}$.
-It appears that the increased orbit speed merely shifts $T_\text{cad}$ rather than changing its sharpness.
 

### 2022-08-16 paper/main.tex
Revised paper

@@
 
-%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
-
-% Only include extra packages if you really need them. Common packages are:
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{xcolor}
@@
 \usepackage{subcaption}
-\usepackage{animate}
 \usetikzlibrary{arrows.meta}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
-\newcommand{\jtd}[1]{ {\bf{\color{red} JTD: #1}} }
 \renewcommand{\unit}[1]{\bm{\hat{#1}}}
-
 \newcommand{\parens}[1]{\left( #1 \right)}
@@
 
-% Please keep new commands to a minimum, and use \newcommand not \def to avoid
-% overwriting existing commands. Example:
-%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
 \title[Flyby Constraints on Asteroids Interiors]{Constraining the Interiors of Asteroids Through Close Encounters}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
 \author[Jack T. Dinsmore, Julien de Wit]{
@@
 \\
-% List of institutions
 $^{1}$Department of Physics, Massachusetts Institute of Technology\\
@@
 
-% These dates will be filled out by the publisher
 \date{Accepted XXX. Received YYY; in original form ZZZ}
 
-% Enter the current year, for the copyright statements etc.
 \pubyear{2022}
 
-% Don't change these lines
 \begin{document}
@@
 
-% Abstract of the paper
 \begin{abstract}
@@
 
-% Select between one and six entries from the list of approved keywords.
-% Don't make up new ones.
 \begin{keywords}
@@
 \end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
 
@@
 where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body.
-Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom}, assuming a rigid asteroid and no distant third-body perturbations.
-This is a novel derivation and accurate to arbitrary order in $D$.
+Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom} via a novel derivation and is accurate to arbitrary order in $D$.
 
@@
 
-We built a publicly accessible, custom simulation in C++ to produce time series of angular velocity data during a close encounter with a central body.
+We built a publicly accessible, custom simulation in C++ of an asteroid's rotational state during a close encounter with a central body.
 This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$ and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
@@
 We begin our simulation at $D = 10 r_p$.
-Since the leading order of the equations of motion is $\ell' = 2, \ell = 0$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
+Since the leading order of equation \ref{eqn:tidal-torque} yields $\tau \propto D^{-3}$, this corresponds roughly to a torque of $10^{-3}$ times the maximum torque at perigee.
 Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
+With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, manually chosen to limit integration error to only \~100 times the floating point numerical error.
 
-With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, chosen to limit integration error to only ~100 times the floating point numerical error.
-% \begin{equation}
-%   dt = dt_\text{min} + 10^{-3}(dt_\text{max} - dt_\text{min}) \brackets{\parens{\frac{D}{r_p}}^3 - 1}.
-% \end{equation}
-% The parameters $dt_\text{max}$ and $dt_\text{min}$ (20 and 10 seconds respectively) were chosen such that the numerical integration error was $\sim$100 times the floating point error, and that neighbouring values of $K_{\ell m}$ yielded significantly different spin pole data compared to floating point error.
-The data used to choose this $dt$ was obtained using the reference asteroid configuration.
+We extract angular velocity from this simulation assuming that angular velocity is observable.
+If orientation data is more readily available instead, the same simulation may be used to generate orientation data.
+Appendix \ref{app:orientation} describes the consequences of this change, which are relatively small.
 
@@
 
-  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 3) node[anchor=south] {$\bm \Omega^*$};
-  \draw[dashed] (-3, -2) -- (-3, 3);
-  \draw[dashed] (-3, -2) -- (0, 0);
+  \draw[line width=0.5mm, -{Latex[length=3mm]}] (0, 0) -- (-3, 2.5) node[anchor=east] {$\bm \Omega^*$};
+  \draw[dashed] (-3, -1.5) -- (-3, 2.5);
+  \draw[dashed] (-3, -1.5) -- (0, 0);
 
-  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.25, 3.35) node[anchor=south west] {$\bm \Omega$};
-  \draw[rotate around={-50:(-3,3)}] (-3,3) ellipse (1.4 and 2);
-  \draw (-3, 3) arc (110:93:6);
-  \draw (-2, 3.5) node[anchor=center] {$\theta$};
+  \draw[-{Latex[length=3mm]}] (0, 0) -- (-1.9, 3.35) node[anchor=south west] {$\bm \Omega$};
+  \draw[rotate around={-35:(-3,2.5)}] (-3,2.5) ellipse (0.9 and 1.5);
+  \draw (-3, 2.5) arc (145:113:2.5);
+  \draw (-2.68, 3.22) node[anchor=center] {$\theta$};
 
@@
 Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in equation \ref{eqn:parameter-bounds}.
-Computing $K_{3m}$ for many positive density distributions revealed a $|K_{3m}| \lesssim 0.01$, so we use more conservative bounds on $K_{3 m}$ of $|K_{3 m}| < 1$.
+Computing $K_{3m}$ for many positive density distributions revealed a $|K_{3m}| \lesssim 0.01$ typically, so we use more conservative bounds on $K_{3 m}$ of $|K_{3 m}| < 1$.
 In general, spin data is most sensitive to $\gamma_0$ and $K_{2m}$, which we call the ``first-order parameters.'' We call $K_{3m}$ the ``second-order parameters.''
@@
 Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused all values of $\gamma_0$ to be degenerate.
-Ensemble walkers were initialized near this local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
+Ensemble walkers were initialized near the local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
 Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
@@
 
-The asteroid density distribution $\rho_\mathcal{A}(\bm r)$ is not uniquely constrained via tidal torque interactions because only the density moments $K_{\ell m}$ contribute to equation \ref{eqn:tidal-torque}.
+The asteroid density distribution $\rho_\mathcal{A}(\bm r)$ is not uniquely determined via the density moments.
 For example, the mass of the asteroid is unconstrained so $\rho_\mathcal{A}(\bm r)$ cannot be determined on an absolute scale.
 However, by making sufficient assumptions about the density distribution, we can nevertheless measure fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
-To best understand the potential density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
-To this end, we thoroughly outline two possible models and discuss two more in appendix \ref{app:more-models}.
+To best understand the density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
+To this end, we outline two possible models here and discuss two more in appendix \ref{app:more-models}.
 
@@
 
-To compare the asteroid surface and extracted density moments in the same coordinate system, we define a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame.
-(It has $\bm \Omega_0 \parallel \unit z_\text{hybrid}$ with third Euler angle $\gamma = 0$.) The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
+To compare the asteroid surface and extracted density moments in the same coordinate system, we define a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame; it has $\bm \Omega_0 \parallel \unit z_\text{hybrid}$ with third Euler angle $\gamma = 0$.
+The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
 Such rotations affect density moments via
@@
 Thus, values and  uncertainties on $K_{\ell m}^\mathrm{body-fixed}$ and $\gamma_0$ (obtained from the encounter data) can be translated into values and uncertainties on $K_{\ell m}^\mathrm{hybrid}$.
+The surface model can be rotated from the inertial frame to the hybrid frame so that both the surface and $K_{\ell m}$ are now in the same frame and are comparable.
 Henceforth, we will operate only in the hybrid frame and suppress the label.
 
-When the $K_{3m}$ are extracted, 15 moments are constrained (excluding $K_{00}$).
+When $K_{3m}$ are extracted, 12 moments are constrained (excluding the trivial $K_{00}$ and $K_{1m}$, which govern the center of mass).
+In cases where $\gamma_0$ is known very accurately such that the uncertainty increase imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable to treat $\Im K_{22}$ and $K_{21}$ as fixed, just as $\Im K_{22}^\text{body-fixed}$ and $K_{21}^\text{body-fixed}$ are fixed.
+In this case, there are nine constrained moments.
+Since $\gamma_0$ is precisely known for all cases studied in this paper, we will always study this case.
+
 Since the asteroid mass cannot be determined by this analysis, it is convenient to additionally set the mass equal to its volume, so that the average density is $\rho_\text{avg}=1$ and thus the extracted densities can be interpreted as ratios of $\rho / \rho_\text{avg}$.
-Three of the moments are redundant with the center of mass, such that only twelve finite elements are free.
-In cases where $\gamma_0$ is known very accurately such that the uncertainty increase imposed by equation \ref{eqn:body-fixed-to-hybrid} is very small, it is numerically favourable to treat $K_{2m}$ as fixed, just as $\Im K_{22}^\text{body-fixed}$ and $K_{21}^\text{body-fixed}$ are fixed.
-In this case, there are nine degrees of freedom (DOF).
-Since $\gamma_0$ is precisely known for all cases studied in this paper, we will always study this case.
-We also place additional constraints that $0.25 < \rho < 3$ to ensure realistic densities.
-
-To extract a density distribution, we use another MCMC given one of the two parametrizations of density distributions discussed below.
-We also present two further models in appendix \ref{app:more-models} which are viable substitutes for the following two models but are not used in the main text.
-The prior is set to be flat and non-zero for all configurations that obey the $0.25 < \rho < 3$ constraint.
-The likelihood used is set equal to the multivariate-Gaussian approximation of the posterior distribution for $K_{\ell m}$, extracted from flyby data.
+We then place additional constraints that $0.25 < \rho < 3$ to ensure realistic densities.
+Using this constraint as a prior, we design another MCMC given one of the two density distribution models discussed below.
+The likelihood used is the multivariate-Gaussian approximation of the posterior distribution for $K_{\ell m}$, extracted from flyby data.
 
@@
 Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, $I_\mathcal{A} K_{\ell m}$ is known for all the fixed moments, and computing the corresponding constrained densities is simply a matrix inversion.
-
-The size and location of the elements must be chosen before extracting their densities.
-Best results generally require elements of equal size to be chosen.
-To remove the dependence on this choice, density distributions for many distinct element layouts can be extracted and the density of each point in the asteroid can be randomly sampled from any of these solutions to yield estimates for the mean density and uncertainty in density at each point.
+The size and location of each finite element must be chosen before extracting its density.
 
@@
 If $N$ is chosen lower, the choice of element layout might exclude a distribution that exactly matches $K_{\ell m}$, but uncertainties are diminished due to less redundancy in the model.
-For the rest of this paper, we use $N=12$ finite elements, which corresponds to 7 constrained elements and 5 DOF.
+For the rest of this paper, we use $N=12$ finite elements, which corresponds to 7 constrained elements and 5 degrees of freedom (DOF).
 
@@
 \begin{equation}
-  \mu_\mathcal{A} = \sum_{i=0}^N \mu_i,  \qquad 0 = \sum_{i=0}^N \mu_i \bm r_i.
+  \mu_\mathcal{A} = \sum_{i=0}^N \mu_i;  \qquad 0 = \sum_{i=0}^N \mu_i \bm r_i.
 \end{equation}
@@
 For example, we can require that the lumps be ellipsoids, so that $K_{3 m}^{(i)} = 0$.
-The most extreme case is that spherical lumps, which have $K_{\ell m} = 0$ for $\ell > 0$.
+The most extreme case is spherical lumps, which have $K_{\ell m} = 0$ for $\ell > 0$.
 $K_{00}=1$ is also guaranteed by definition, meaning that each spherical lump has only five DOF ($a_i$, $\mu_i$, and $\bm r_i$).
@@
 Again, the choice of $N$ affects the accuracy and uncertainty of the model results.
-For the rest of this paper, we use $N=1$ lump for simplicity, corresponding to 2 DOF.
-In section \ref{sec:density-compare}, we also use $N=2$ lumps which possesses 7 DOF.
+For the rest of this paper, we use $N=1$ spherical lump for simplicity, corresponding to 2 DOF.
+In section \ref{sec:density-compare}, we also use $N=2$ spherical lumps which possesses 7 DOF.
+
+\subsubsection{Density distribution uncertainties}
+\label{sec:density-uncertainty}
+
+Once the parameters of the density distribution models have been extracted, each MCMC sample corresponds to its own density distribution.
+To generate an average distribution, we randomly choose 1,000 of these samples and define the density distribution $\rho$ at each point to be the mean of the densities at that point across the 1,000 samples, and take the standard deviation of the sample densities as the density uncertainty $\sigma_\rho$.
+In the case of the finite element model, we run the MCMC twenty times and select 1,000 parameter samples from each to reduce dependence on the initial choice of finite element locations.
 
@@
   \item A cadence of 2 minutes and observational uncertainty of $\sigma_\theta = 10^{-2}$ and $\sigma_P / P = 10^{-7}$.
-  \item A rotational period of 9 hours, with the angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
+  \item A rotational period of 9 hours, with the initial angular velocity vector distributed between the $\unit X$, $\unit Y$, and $\unit Z$ axes in a $1:2:-2$ ratio.
   \item An asteroid with radius $a_\mathcal{A} = 1$ km and $K_{3m}=0$.
 For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$, these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$ (a 90$^\circ$ rotation), these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
 The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
@@
 Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
-If not specified, we use the $a < b$ case.
 Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
@@
 The best-fitting model is overlaid in the top panel and residuals are shown the bottom panel.
-Uncertainties are plotted on the residuals corresponding to the square root of the diagonal entries of the covariance matrix (correlations not included).
+Uncertainties are plotted on the residuals with correlations between the vector components.
 The fit results are consistent with the data.
@@
 
-Figure \ref{fig:den-uniform} displays density distributions extracted by both the finite element and lumpy models for the reference asteroids.
-For the finite element model, five DOF and 20 different element layouts were used.
-The figure demonstrates that the finite element model successfully extracts density distributions consistent with the input density moments, as shown by the $\chi^2$ value per degree of freedom, $\chi^2_r$, depicted in the figure.
-These express the agreement of the density moments of the shown distributions with the posterior distributions for the density moments, produced by the MCMC described in section \ref{sec:fit}.
-$\chi^2_r = 0$ indicates that the moments of the shown distributions are exactly equal to the means of the moment posterior extracted by the MCMC.
-The accuracy of this model is robust for other shapes, including non-ellipsoidal shapes.
+Figure \ref{fig:den-uniform} displays density distributions and uncertainties extracted by both the finite element and lumpy models for the reference asteroids, as well as the $\chi^2$ value per DOF ($\chi^2_r$) of the extracted distribution's density moments compared to the density moment PPDs produced by the MCMC described in section \ref{sec:fit}.
+$\chi^2_r = 0$ indicates that the moments of the distribution are exactly the means of the moment PPD extracted by the MCMC.
+The fact that $\chi^2_r$ is generally low indicates that the extracted density distributions are consistent with the data.
+This remains true even for non-ellipsoidal asteroid shapes (not shown).
 
-Furthermore, the finite element density distributions are consistent with uniform, which is the true density distribution of the asteroid.
-For the reference asteroid observational set-up, the uncertainty on observations is such that the density distribution is generally within 10\% of the true density (second column) while the density uncertainty is generally less than 40-50\% of the density value at any point in the asteroid (third column).
-The dependence of this constraint on the observational set-up is discussed in section \ref{sec:fit-uncertainty}.
+For the finite element model with the reference observational set-up, the uncertainty on observations is such that the density distribution is generally within 10\% of the true uniform density (second column) while the density uncertainty is generally less than 40-50\% of the density value at any point in the asteroid (third column).
 In no place is the significance of these deviations from the true distribution greater than $1 \sigma$ (last column).
-
-The lumpy model also yields distributions which are consistent with the extracted moments and consistent with uniform.
-These distributions have much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom.
-With the one-lump-model and with asteroids whose surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the single lump must lie at the centroid with mass close to zero and unconstrained radius.
+The lumpy model yields distributions with much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom; with the one-lump-model and with asteroids whose surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the single lump must lie at the centroid with mass close to zero and with unconstrained radius.
 The uncertainty of regions far from the asteroid center, where the lump is unlikely to extend, is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have greater density uncertainty.
@@
 
-Once again, figure \ref{fig:den-move} shows that the model results are successful in that they reproduce the extracted density moments ($\chi^2_r$ is low).
-However, the density distributions extracted by the finite model matches the true distributions less well.
+The distributions of figure \ref{fig:den-move} reproduce the extracted density moments ($\chi^2_r$ is low); nevertheless the distributions extracted by the finite model match the true distributions less well.
 The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
-Uncertainties are large enough that the distributions are consistent with the true distribution, but the finite element model has distributed the core into the rest of the asteroid so that the peak density is lowered.
+Visually the finite element model has spread the high-density core into the rest of the asteroid.
 
@@
 
-% In this section, we discuss the sensitivity of our results to the properties of the asteroid encounter system.
-We start with the encounter properties that are required to adequately constrain the asteroid's density moments and distribution, and further discuss the properties of Jupiter encounters compared to Earth encounters.
-Finally, we discuss in greater detail which features of an asteroid density distribution can be extracted by our models and which cannot be.
-
 \subsection{Dependence of uncertainty on encounter properties}
@@
 
-The question of which encounters are most suited to this methodology is of great interest, as is the question of how observational campaigns can be designed to best take advantage of an asteroid and maximize the success of this methodology.
-We investigate physical asteroid properties (the encounter's orbital properties, the asteroid's true shape, and its initial rotational velocity) and observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage), and discuss their effect on the uncertainty of this methodology's results.
+The question of which encounters are most suited to this methodology is of great interest, as is the related question of how observational campaigns can be designed to best take advantage of an encounter and maximize the success of this methodology.
+We investigate physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage), and discuss their effect on the uncertainty of this methodology's results.
 
-We study both the uncertainties on the density moments and uncertainty on density distribution.
+We measure both the uncertainties on the density moments and average density distribution uncertainty.
+Density distribution uncertainty $\sigma_\rho / \rho$ is the median value of density uncertainty divided by local density over the whole asteroid.
+This measure of uncertainty physically relevant, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, noise, and other effects unrelated to the encounter properties.
 Moment uncertainty $\sigma (K_{\ell m})$ is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
-Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined.
-However, its physical relevance is not obvious.
-The density distribution uncertainty $\sigma_\rho / \rho$ is defined as a map of uncertainty over the asteroid, made by taking the standard deviation of density at each point over 5000 maps of asteroid density, each corresponding to a random sample of the output of the density distribution MCMC described in section \ref{sec:density-distro}.
-The median of this uncertainty divided by the local density over this map is taken to represent the density distribution uncertainty.
-This measure of uncertainty is more physically relevant than moment uncertainty, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, and other effects unrelated to the encounter properties.
-We therefore investigate both measures of uncertainty.
+Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined and less noise-prone, though its physical relevance is not as obvious as that of the density distribution uncertainty.
 
@@
     Encounter property & Weak & Strong \\ \hline
-    Perigee ($r_p$, Earth radii) & $<$6.0 & $<$18\\
+    Perigee ($r_p$, Earth radii) & $<$6.3 & $<$18\\
     Excess velocity ($v_\infty$) & - & - \\
@@
   \end{tabular}
-  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) consistent with useable density distribution uncertainty.
+  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) that meet certain density distribution thresholds (see text).
 Perigee and observational uncertainty are the most constraining properties, followed by rotational period, asteroid length, and observational cadence.}
@@
   \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
-  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution via the lumpy model as a function of initial spin pole direction.
+  \caption{Density uncertainty computed via the lumpy model as a function of initial spin pole direction.
 The weak uncertainty cut-off (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
-The strong cut-off is never exceeded and thus does not appear.
+The strong cut-off is never exceeded and does not appear.
 Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
@@
   \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
-  \caption{Median ratio of density uncertainty to density computed over the reference asteroid density distribution as a function of physical / observational encounter properties (\textit{top / bottom}).
-Density distributions from both the lumpy and finite element models are used.
+  \caption{Density uncertainty as a function of physical / observational encounter properties (\textit{top / bottom}).
+Both the lumpy and finite element models are used.
 The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
@@
 They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
-Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the encounter properties.
+Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the other encounter properties.
 Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines.
@@
 
-In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} shows a threshold on initial spin pole direction.
+In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} shows a threshold on initial spin direction.
 The poles (i.e., angular velocities perpendicular to the orbital plane) lead to greater uncertainty and this is the only region which rises above the weak uncertainty threshold.
+Compared to other physical parameters, initial spin direction is not very constraining.
 
@@
 If the gap occurred elsewhere in the data set or was subdivided into multiple gaps, it would likely affect density uncertainty even less.
-All of these thresholds are liable to change if the encounter properties are adjusted, since they are all interdependent.
 
@@
 These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are more volatile.
+
 The figure also displays the stark difference between density uncertainty computed by the lumpy model and the finite element model.
-This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model), and to the assumptions of the model; the lumpy model is more biased towards uniform asteroids such as these, since it is comprised of a small number of uniform density regions.
+This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model), and to the assumptions of the model; the lumpy model is more biased towards uniform asteroids such as these, since it assumes that the asteroid is comprised of a small number of uniform density regions.
 This model-dependence of $\sigma_\rho / \rho$ is another reason to take the thresholds of table \ref{tab:threshold-summary} as estimates rather than strict limits on encounter properties.
@@
   \centering
-  \includegraphics[angle=90, origin=c, width=0.99\linewidth]{figs/scan-all1.pdf}
+  \includegraphics[angle=90, origin=c, width=0.98\linewidth]{figs/scan-all1.pdf}
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) perigee, excess velocity, asteroid length, and rotational period.
 The vertical dotted line indicates the reference asteroid values.
-The red solid/dashed lines indicate the weak/strong uncertainty thresholds.}
+The red dashed/solid lines indicate the weak/strong uncertainty thresholds.}
   \label{fig:scan-perigee}
@@
   \centering
-  \includegraphics[angle=90, origin=c, width=0.99\linewidth]{figs/scan-all2.pdf}
+  \includegraphics[angle=90, origin=c, width=0.98\linewidth]{figs/scan-all2.pdf}
   \caption{1 and 2$\sigma$ confidence intervals for the first-order parameter PPDs (\textit{top}) and second-order parameters (\textit{bottom}) as a function of (left to right) period and spin pole uncertainty, observational cadence, and length of gaps in the data.
 The vertical dotted line indicates the reference asteroid values.
-The red solid/dashed lines indicate the weak/strong uncertainty thresholds.}
+The red dashed/solid lines indicate the weak/strong uncertainty thresholds.}
     \label{fig:scan-rho}
@@
 
-Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ is more sensitive to $\sigma (K_{2m})$ than to $\sigma(K_{3m})$.
+Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ from figure \ref{fig:net-uncertainty} is more sensitive to $\sigma (K_{2m})$ than to $\sigma(K_{3m})$.
 For instance, $\sigma(K_{2m})$ is constant as $a_\mathcal{A}$ is varied despite a dramatic increase in $\sigma(K_{3m})$ for low $a_\mathcal{A}$.
@@
 
-In the following sections, we study each panel of figures  \ref{fig:scan-physical} and \ref{fig:scan-observational} individually and discuss their implications.
-
-% Figure \ref{fig:scan-physical} also demonstrates an accelerating increase of $\sigma(K_{\ell m})$ as a function of perigee $r_p$, indicating that the constraint on $r_p$ noted in table \ref{tab:threshold-summary} is not entirely a feature of the density model.
-(Figure \ref{fig:net-uncertainty} also indicated this, since $\sigma_\rho / \rho$ falls for low perigee in both the lumpy and the finite element model).
+Since figures \ref{fig:scan-physical} and \ref{fig:scan-observational} show such clear uncertainty dependence on encounter properties, we discuss the implication of each panel individually in the following sections.
 
@@
 
-Figure \ref{fig:scan-perigee} shows a very strong dependence on perigee as mentioned in the main text --- so strong that for large perigee, $\sigma(K_{3m})$ is constrained by the prior boundaries of $\pm 1$ for $m < 3$.
-This occurs as low as $r_p = 10$ Earth radii for $K_{30}$, though the fact that density distributions can still be extracted at this perigee value shows that resolution of $K_{30}$ is not essential to extract density distributions.
+Figure \ref{fig:scan-perigee} shows that moment uncertainty depends so strongly on perigee that for $r_p > 10$ Earth radii, $\sigma(K_{3m})$ is constrained by the prior boundaries of $\pm 1$ for $m \leq 2$.
 Figure \ref{fig:net-uncertainty} also demonstrates that low perigee yield more certain density distributions as extracted by both the lumpy and the finite element models.
-Such a strong strong dependence is expected from equation \ref{eqn:tidal-torque}; it is caused by the $(a_\mathcal{A}/D)^{\ell'}$ dependence of the tidal torque on distance $D$.
+Such a strong strong dependence is expected from equation \ref{eqn:tidal-torque}; it is caused by the $D^{-\ell'}$ factor contained in $S_{\ell' m}(\bm D)$.
 
@@
 This is likely due to the fact that larger $v_\infty$ leads to a faster and flatter orbit with less time spent close to the planet, where tidal torque is strongest.
-This change in encounter timing also adjusts the orientation of the asteroid at perigee, which has a separate effect on moment uncertainty.
-We control for this undesired orientation dependence by adjusting $\gamma_0$ so that, if no tidal torque is present, the orientation of the asteroid at perigee is constant for all $v_\infty$.
-The effect of tidal torque then causes orientations to be \textit{roughly} the same at perigee where tidal torque is highest.
-This effectively removes the orientation dependence.
+The change in encounter timing also adjusts the orientation of the asteroid at perigee, which has a separate effect on moment uncertainty.
+We control for this undesired orientation dependence by adjusting $\gamma_0$ so that, if no tidal torque is present, the orientation of the asteroid at perigee is constant for all orbits.
+The effect of tidal torque then causes orientations to be roughly the same at perigee where tidal torque is highest.
+This effectively removes the orientation-induced uncertainty.
 
@@
 
-We expect that fast rotators would not tumble post-encounter because, for small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
+We expect that fast rotators would not tumble post-encounter for the following reason, For small $P_\omega$, all the dynamical variables vary much more slowly than the orientation $\gamma$.
 Approximating each variable as constant over one full rotation of $\gamma$, the integral of the first-order contribution of $\bm \tau$ over $\gamma \in (0, 2\pi)$ gives no secular first-order torque to force the asteroid to tumble.
@@
 An asteroid with large $K_{3m}$ moments might therefore be yield better uncertainties at these low rotational periods (e.g., a non-uniform or non-elliptical asteroid).
-
-Another feature of figure \ref{fig:scan-period} is that $K_{\ell 0}$ is more uncertain at low $P_\omega$ than the other parameters (most visible for $K_{30}$).
-The explanation is likely the following: Tidal torque components $\tau_x$ and $\tau_y$ induce tumbling, and since fast rotators exhibit reduced tumbling post-encounter, these components likely have little effect on moment uncertainty.
-The most observable component of torque is then $\tau_z$, but equation \ref{eqn:tidal-torque} shows that $K_{\ell 0}$ does not contribute to $\tau_z$.
-Asymmetry is therefore more measurable than symmetry for these fast rotators.
 
@@
 
-Figure \ref{fig:scan-spin} depicts increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, just as \ref{fig:spin-uncertainty} depicts increased density distribution uncertainty.
+Figure \ref{fig:scan-spin} shows increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, just as \ref{fig:spin-uncertainty} shows increased density distribution uncertainty.
 Many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
@@
 We also study the dependence of moment uncertainty on the asteroid MOI and on the asteroid's initial orientation, but these relationships are simple enough that they are not included in figures \ref{fig:scan-physical} and \ref{fig:scan-observational}.
-Moment uncertainty is generally unrelated to the asteroid shape, except when the asteroid is rotationally symmetric (e.g., for the symmetric reference asteroid).
+Moment uncertainty is generally unrelated to the MOI ratios, except when the asteroid is rotationally symmetric (e.g., for the symmetric reference asteroid).
 In this case the initial orientation of the asteroid $\gamma_0$ is undefined, creating degeneracy and inflating density moment uncertainty.
@@
 
-Moment uncertainty is also affected by $\gamma_0$, which was corrected for in section \ref{sec:scan-orbit}.
+Moment uncertainty does depend on the asteroid length, which sets not MOI ratios but the MOI itself, as shown in figure  \ref{fig:scan-physical}.
+This dependence is relatively simple; high-order moments are damped by factors of $a_{\mathcal{A}} / D$, so that reducing asteroid size without reducing perigee yields poor constraints on $K_{3m}$
+
+Moment uncertainty is also affected by $\gamma_0$.
 We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant.
@@
 If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant as in this case, then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
-Therefore, little advantage is to be gained by looking for encounters of a massive planet in this sense.
+Therefore, tidal torque is not increased around massive planets when we keep $r_p \propto a_\mathcal{B}$.
 The second-order terms are damped by an additional factor of $a_\mathcal{A}/D$, which decreases if a massive central body is used.
 Since Jupiter is about 10 times larger in radius than Earth, we expect that the $K_{3m}$ terms are about ten times more uncertain than the $K_{2m}$ components, which is the case.
-
-The $K_{\ell 0}$ components differ in that the moment uncertainty increase for a Jupiter encounter over an Earth encounter is about five times greater for $K_{\ell 0}$ than other moments of the same $\ell$.
-In fact, $K_{30}$ essentially fills the prior.
-In section \ref{sec:scan-spin}, we note that $K_{\ell 0}$ is particularly uncertain when the asteroid does not tumble after the perigee.
-In this case, the Jupiter encounter resulted in less tumbling than the Earth encounter, so the larger increase in uncertainty in $K_{\ell 0}$ shown in table \ref{tab:jupiter-uncertainty} is expected.
+Furthermore, since the orbit size is increased without a decrease in asteroid rotational velocity, the asteroid tends to tumble less for the same reasons as described in section \ref{sec:scan-period}.
+This also increases moment uncertainty.
 
@@
 \end{equation}
-Table \ref{tab:jupiter-uncertainty} suggested that moment uncertainty is roughly $\sigma(K_{\ell m}) \propto a_\mathcal{B}^{\ell - 1} / r_p$, so that constant uncertainty roughly implies $r_p \propto a_\mathcal{B}^{1\ \text{to} \ 2}$.
-Since $a_\mathcal{B} \sim \mu_\mathcal{B}^{1/3}$, equation \ref{eqn:impact-parameter} dictates that $b/r_p$ will increase faster than $a_\mathcal{B}$ as $\mu_B$ is increased.
-It follows that the number of encounters that meet the uncertainty threshold will grow substantially.
-Other effects, such as a change in the physical properties of the encountering asteroids or decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
-Which of these contradicting effects dominates depends on the asteroid population near Jupiter and the observation method.
+It is true that $\sigma(K_{\ell m})$ decreases with central body radius, but $A$ increases so fast that the number of encounters that meet the uncertainty threshold will still grow, assuming that the flux of asteroids through keyholes of equal area is the same for Earth and Jupiter.
+Other effects, such as a change in the physical properties of the encountering asteroids, changes in asteroid rarity, and decreased observational uncertainty due to the distance between Jupiter and Earth-based telescopes, may also affect the fit uncertainties.
+These effects contradict, and which dominates depends on the asteroid population near Jupiter and the observation method.
 
@@
 
-In section \ref{sec:asym-density}, we displayed uniform and non-uniform density distributions extracted via the finite element and single-lump lumpy model.
-Here we highlight the properties of the model in two other scenarios.
+Section \ref{sec:asym-density} briefly explored the density distributions produced for non-uniform asteroids, Here, we evaluate this case more thoroughly by considering two more example distributions.
 
@@
 It produces deviations from the true density distribution of roughly the same size as the finite element model, with large significance.
-This is because, for centred, spherical cores, the core mass is degenerate with the core's radius.
+This is because the core mass is degenerate with the core's radius for centred, spherical cores.
 
@@
 Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center.
-On the other hand, the lumpy model detects that the two lumps are opposite each other,and of roughly the same radius and mass.
+On the other hand, the lumpy model detects that the two lumps are opposite each other and of roughly the same radius and mass.
 These radius and mass values are also close to the true values.
-The model places the lumps correctly in the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
+The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
 Uncertainty is also high, due to the extra DOF.
 Note that $\chi^2_r$ remains low despite the lumpy model's misplacement of the lumps.
-This is because the lumpy model gains its information on the placement of the lumps from the $K_{3m}$ density moments, which figures \ref{fig:scan-physical} and \ref{fig:scan-observational} suggest are not as well constrained as the $K_{2m}$ density moments.
-The high uncertainty results in a deviation of a few hundred meters in lump location for the reference encounter properties.
+This is because the misplacement of the lumps affects only the $K_{3m}$ density moments, which are not as well constrained as the $K_{2m}$ density moments.
+The result is a deviation of a few hundred meters in lump location for the reference encounter properties.
 
@@
 We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque (equation \ref{eqn:tidal-torque}) revealed that the angular velocity of the asteroid over time depends strongly on the asteroid's density moments and the initial orientation.
+The tidal torque revealed that the rotational behaviour of the asteroid over time depends strongly on the asteroid's density moments and the initial orientation.
 We then built a fast simulation for an asteroid encounter and designed an MCMC to extract density moments from simulated data.
-We also created two models --- the finite element model and the lumpy model --- to translate these density moments back into density distributions.
+We also created two models --- the finite element model and the lumpy model --- to translate these density moments into density distributions.
 Uncertainties are propagated throughout the pipeline.
-Since the density distribution inverse problem is underdetermined, the models give different results and were contrasted.
-Nevertheless, we find that the models always produce results consistent with the data set and usually consistent with the true distribution.
+The pipeline was executed for several synthetic encounters and found to yield both density moments and distributions consistent with the true values.
 
@@
 The thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
-The properties that do not affect density uncertainty as much, such as the central body oblateness, must still be accurately represented in simulations to avoid errors in the pipeline results.
+The properties that do not affect density uncertainty as much, such as the central body oblateness, must still be accurately modelled to avoid errors in the pipeline results.
 We also discussed how these thresholds could be eased by changes in observational behaviour such as lengthening the data set, or by physical asteroid properties such as a closer encounter, an initially tumbling state, or the presence of a massive moon such as Earth's.
@@
 Finally, we highlighted that the properties of the final density distribution are strongly model-dependent.
+Each model was able to resolve some density distribution features and not others depending on the model design.
 The uncertainties on density distribution of the two models were drastically different, and also depended on the number of degrees of freedom used in the model.
-For asteroids of non-uniform distributions, the distributions themselves also differed.
-To efficiently use encounter data, it is therefore important to investigate multiple models and choose different models to answer different questions, such as the lumpy model to look for discrete regions of increased density.
+To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Data Availability}
@@
 The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}. Please contact JTD with questions.
-
-%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bsp	% typesetting comment
+\bsp
 \label{lastpage}

### 2022-08-16 summaries/21-11/asteroids/interpret.py

@@ -1,49 +1,0 @@
-# https://ssd-api.jpl.nasa.gov/doc/cad.html
-
-import pandas as pd
-import numpy as np
-import json
-
-DIAM_LIMIT = 100
-DIST_LIMIT = 1# Lunar distances
-YEAR_LIM = 2032
-
-data = pd.read_csv("cneos_closeapproach_data.csv")
-print(data.columns)
-diameter_mask = np.full(len(data), False)
-print(len(data))
-for i in range(len(data)):
-    if str(data["Diameter"][i]) == "nan":
-        continue
-    space_index = data["Diameter"][i].index(' ')
-    unit = data["Diameter"][i][space_index+1:space_index+3]
-    try:
-        space_index = min(space_index, data["Diameter"][i].index('±'))
-    except Exception:
-        pass
-    diam = float(data["Diameter"][i][:space_index])
-    if unit == "km":
-        diam *= 1000
-    diameter_mask[i] = diam > DIAM_LIMIT
-
-dist_mask = np.full(len(data), False)
-for i in range(len(data)):
-    line = data["CA Distance Minimum (LD | au)"][i]
-    ld, au = line.split(" | ")
-    dist_mask[i] = float(ld) < DIST_LIMIT
-
-year_mask = np.full(len(data), False)
-for i in range(len(data)):
-    line = data["Close-Approach (CA) Date"][i]
-    hyphen_index = line.index('-')
-    year = line[:hyphen_index]
-    year_mask[i] = float(year) <= YEAR_LIM
-
-
-        
-    
-print(np.sum(diameter_mask))
-print(np.sum(dist_mask))
-print(np.sum(year_mask))
-print(np.sum(diameter_mask & dist_mask & year_mask))
-print(data[diameter_mask & dist_mask & year_mask])

### 2022-08-19 paper/main.tex
Responding to Julien's comments

@@
 \usepackage{subcaption}
+\usepackage{graphbox}
 \usetikzlibrary{arrows.meta}
@@
 A drawback of the finite element model is that the generated density distribution might not be representative of the asteroid if the elements are not optimally placed.
-We therefore describe an alternate model which includes the positions of the elements as parameters at the cost of resolution.
+We therefore describe an alternate model which includes the positions of the elements as parameters at the cost of resolution similarly to \cite{dewit2012}.
 We call this the ``lumpy'' model.
@@
 \subsubsection{Density distribution uncertainties}
-\label{sec:density-uncertainty}
+\label{sec:density-uncertainty-model}
 
@@
 
+%% Julien asks that I use mean and max values in each plot instead of chisq.
+
 \subsection{Density distribution retrieval}
@@
 \begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/asym-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-fe-r}
+  Asymmetric reference asteroid
 
-  \includegraphics[width=0.24\linewidth]{figs/asym-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/asym-l-r}
+  \rotatebox[origin=c]{90}{Finite element model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-fe-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-fe-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-fe-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-fe-r}
 
-  \includegraphics[width=0.24\linewidth]{figs/sym-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-fe-r}
+  \rotatebox[origin=c]{90}{Lumpy model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-l-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-l-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-l-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/asym-l-r}
 
-  \includegraphics[width=0.24\linewidth]{figs/sym-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sym-l-r}
+  \vspace{2em}
+  Symmetric reference asteroid
+
+  \rotatebox[origin=c]{90}{Finite element model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-fe-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-fe-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-fe-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-fe-r}
+
+  \rotatebox[origin=c]{90}{Lumpy model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-l-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-l-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-l-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sym-l-r}
 
@@
 
-Figure \ref{fig:den-uniform} displays density distributions and uncertainties extracted by both the finite element and lumpy models for the reference asteroids, as well as the $\chi^2$ value per DOF ($\chi^2_r$) of the extracted distribution's density moments compared to the density moment PPDs produced by the MCMC described in section \ref{sec:fit}.
-$\chi^2_r = 0$ indicates that the moments of the distribution are exactly the means of the moment PPD extracted by the MCMC.
-The fact that $\chi^2_r$ is generally low indicates that the extracted density distributions are consistent with the data.
-This remains true even for non-ellipsoidal asteroid shapes (not shown).
+Figure \ref{fig:den-uniform} displays density distributions and uncertainties extracted by both the finite element and lumpy models for the reference asteroids.
+They are consistent with the moments extracted by the MCMC in section \ref{sec:fit}, even for non-ellipsoidal asteroid shapes (not shown).
 
@@
 The uncertainty of regions far from the asteroid center, where the lump is unlikely to extend, is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have greater density uncertainty.
+This uncertainty is entirely model-driven and can be discarded.
 
@@
 
+%% Working on cutting down the uncertainties in the large-uncertainty regions
+
 \begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-fe-r}
+  \rotatebox[origin=c]{90}{Finite element model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-fe-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-fe-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-fe-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-fe-r}
 
-  \includegraphics[width=0.24\linewidth]{figs/move-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/move-l-r}
+  \rotatebox[origin=c]{90}{Lumpy model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-l-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-l-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-l-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/move-l-r}
 
@@
 
-The distributions of figure \ref{fig:den-move} reproduce the extracted density moments ($\chi^2_r$ is low); nevertheless the distributions extracted by the finite model match the true distributions less well.
+The distributions of figure \ref{fig:den-move} reproduce the extracted density moments; nevertheless the distributions extracted by the finite model match the true distributions less well.
 The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
-Visually the finite element model has spread the high-density core into the rest of the asteroid.
+Visually the finite element model has spread the high-density core into the rest of the asteroid, but this deviation from the true density distribution does not have high significance due to the similarly large model-driven uncertainty of the finite element model.
+
+%% Julien wants a side by side figure to display how well the core is extracted
+
+%% Julien also mentioned adding a method to detect deviations.
 
@@
 \label{sec:discussion}
+In the previous section, we saw that the uncertainty in density over the asteroid is strongly model-dependent.
+In section \ref{sec:density-compare} below, we further study the model outputs by considering two more sample asteroid extractions.
 
-\subsection{Dependence of uncertainty on encounter properties}
-\label{sec:fit-uncertainty}
+Given this understanding of our density extraction models, we answer the important questions of which encounters can be successfully studied by this methodology, and how observational campaigns can be designed to best take advantage of an encounter.
+To quantify the methodology's success, we use the median of a density uncertainty distribution $\langle \sigma_\rho / \rho \rangle$ in section \ref{sec:density-uncertainty}.
+But since this median is so model-dependent, we also analyze the success of the method via the density moment uncertainty $\sigma (K_{\ell m})$ (which is not moment dependent) in section \ref{sec:moment-uncertainty}.
+In section \ref{sec:central-body}, we study the methodology's dependence on the properties of the central body.
 
-The question of which encounters are most suited to this methodology is of great interest, as is the related question of how observational campaigns can be designed to best take advantage of an encounter and maximize the success of this methodology.
-We investigate physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational parameters (the data uncertainty, the cadence of observations, and gaps in data coverage), and discuss their effect on the uncertainty of this methodology's results.
+\subsection{Density distribution model caveats}
+\label{sec:density-compare}
+We will consider two example scenarios which lead to inflated density distribution uncertainties independent of the actual asteroid properties or the data quality.
+Specifically, we consider the lumpy model's degeneracy for a centred core and the two-core lumpy model.
+This highlights the model dependence of the density distributions extracted from density moments.
 
-We measure both the uncertainties on the density moments and average density distribution uncertainty.
-Density distribution uncertainty $\sigma_\rho / \rho$ is the median value of density uncertainty divided by local density over the whole asteroid.
-This measure of uncertainty physically relevant, but it is strongly dependent by choices of the density distribution model, degrees of freedom, prior constraints, noise, and other effects unrelated to the encounter properties.
-Moment uncertainty $\sigma (K_{\ell m})$ is defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
-Since there is no degeneracy between moments and the actual encounter data, this uncertainty is well-defined and less noise-prone, though its physical relevance is not as obvious as that of the density distribution uncertainty.
+\begin{figure*}
+  \rotatebox[origin=c]{90}{Finite element model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-fe-r}
+
+  \rotatebox[origin=c]{90}{Lumpy model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-l-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-l-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-l-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/sph-3-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+These figures are available in animated form in appendix figure \ref{fig:animated-sph}.
+The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
+  \label{fig:den-sph}
+\end{figure*}
+
+Figure \ref{fig:den-sph} shows density distributions extracted via the finite element model and the lumpy model for a centred core of density three times the surrounding density.
+Results are similar to the off-center core shown in \ref{fig:den-move} in that the finite element model does not isolate the lump, instead spreading the excess mass over the asteroid.
+Unlike the off-center core example, the lumpy model is not able to recover the true distribution either.
+It produces deviations from the true density distribution of roughly the same size as the finite element model, with large significance.
+
+The success of the model in the off-center case was due to the fact that the shape of the asteroid was offset from the center of mass by a corresponding amount, assumed to be known precisely.
+The position of the lump was therefore observed up to one free parameter: the lump's mass.
+In the centred core case, the core mass does not affect the asteroid center of mass so it is unconstrained, leading to large uncertainty.
+The underlying assumption that the asteroid's center of mass is so precisely known stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
+If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain for the off-center case.
+
+We also consider an asteroid with two lumps of radii 300 m and density three times the surrounding density.
+Each lump is located 500 meters from the center of the asteroid, so that they counterbalance and the asteroid's observed center of mass is its surface's centroid.
+The corresponding two-lump lumpy model has 7 DOF, in contrast to the 5 DOF of the finite element model or the 2 DOF of the one-lump lumpy model.
+Both models are run on this asteroid and the resulting distributions are shown in figure \ref{fig:den-double}.
+
+\begin{figure*}
+  \rotatebox[origin=c]{90}{Finite element model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-fe-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-fe-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-fe-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-fe-r}
+
+  \rotatebox[origin=c]{90}{Lumpy model}
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-l-d}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-l-s}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-l-u}\hfill
+  \includegraphics[align=c, width=0.24\linewidth]{figs/double-l-r}
+
+  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
+From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
+These figures are available in animated form in appendix figure \ref{fig:animated-double}.
+The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
+  \label{fig:den-double}
+\end{figure*}
+
+Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center.
+On the other hand, the lumpy model detects that the two lumps are opposite each other and of roughly the same radius and mass.
+These radius and mass values are also close to the true values.
+The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
+Uncertainty is also high, due to the extra DOF, however the distribution is in agreement with the extracted density moments because the misplacement of the lumps affects only the $K_{3m}$ density moments, which are not as well constrained as the $K_{2m}$ density moments.
+The result is a deviation of a few hundred meters in lump location for the reference encounter properties.
+
+\subsection{Probing density sensitivity to encounter properties}
+\label{sec:density-uncertainty}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
+  \caption{Density uncertainty as a function of physical / observational encounter properties (\textit{top / bottom}).
+Both the lumpy and finite element models are used, though the finite element model uncertainty is model-dominated and not very sensitive to encounter properties.
+The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
+The vertical black dotted lines are the property values of the reference asteroid.
+The figures illustrate the marked difference in density distributions that results from using different models.}
+  \label{fig:net-uncertainty}
+\end{figure*}
+
+Here, we investigate how density uncertainty $\langle \sigma_\rho / \rho \rangle$, extracted by both the finite element and lumpy models, depends on physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational properties (the data uncertainty, the cadence of observations, and gaps in data coverage).
+
+%% Why do we have two thresholds?
+
+Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
+We define two density distribution uncertainty thresholds termed the ``weak'' and ``strong'' thresholds.
+These values are $\langle \sigma_\rho / \rho \rangle = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
+They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
+They are shown as red lines in figures \ref{fig:net-uncertainty} and \ref{fig:spin-uncertainty}, and the encounter properties which exceed these thresholds are listed in table \ref{tab:threshold-summary} for reference.
+
+The thresholds are applied to the lumpy model distribution because the large, model-induced uncertainty of the finite element model makes its density distributions only slightly dependent on encounter parameters.
+This is a further example of model-induced uncertainty in density distributions.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
+  \caption{Density uncertainty computed via the lumpy model as a function of initial spin pole direction.
+The weak uncertainty cut-off (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
+The strong cut-off is never exceeded and does not appear.
+Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
+  \label{fig:spin-uncertainty}
+\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.9\linewidth]{figs/spin-unc.pdf}
-  \caption{Density uncertainty computed via the lumpy model as a function of initial spin pole direction.
-The weak uncertainty cut-off (\textit{red line}) is shown, as is the reference spin pole direction (\textit{orange star}).
-The strong cut-off is never exceeded and does not appear.
-Initial angular velocities perpendicular to the orbital plane lead to greatest uncertainty.}
-  \label{fig:spin-uncertainty}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=\linewidth]{figs/unc-scan.pdf}
-  \caption{Density uncertainty as a function of physical / observational encounter properties (\textit{top / bottom}).
-Both the lumpy and finite element models are used.
-The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
-The vertical black dotted lines are the property values of the reference asteroid.
-The figures illustrate the marked difference in density distributions that results from using different models.}
-  \label{fig:net-uncertainty}
-\end{figure*}
-
-Table \ref{tab:threshold-summary} displays the encounter properties corresponding to density distribution uncertainty equal to two sample values we term the ``weak'' and ``strong'' thresholds.
-These values are $\sigma_\rho / \rho = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
-They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
-Figure \ref{fig:spin-uncertainty} depicts the same $\sigma_\rho / \rho$ as a function of initial spin pole direction, while figure \ref{fig:net-uncertainty} depicts $\sigma_\rho / \rho$ as a function of the other encounter properties.
-Both highlight the threshold values of table \ref{tab:threshold-summary} with red lines.
-Bands containing 68\% (light) and 95\% (dark) of the density uncertainty over the asteroid are shown for figure \ref{fig:net-uncertainty}.
-
-Table \ref{tab:threshold-summary} reveals that the most limiting physical properties of the asteroid are its perigee and period.
+Figure \ref{fig:net-uncertainty} reveals that the most limiting physical properties of the asteroid are its perigee and period.
 Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only effective for $a_\mathcal{A} \sim 15$ m.
 By contrast, the radius of Apophis is
-$\sim 300$ m and its perigee and rotational period also obey the strong constraints \cite{giorgini2008predicting}.
-The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \cite{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \cite{yu2014numerical,hirabayashi2021finite}.
+$\sim 300$ m and its perigee and rotational period also obey the strong constraints \citep{giorgini2008predicting}.
+The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \citep{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \citep{yu2014numerical,hirabayashi2021finite}.
 Further work must therefore be done to apply this analysis to Apophis.
@@
 
-Table \ref{tab:threshold-summary} also demonstrates the strong affect of properties of the observational campaign on the final density uncertainty.
-Most vital are the uncertainty on the instantaneous asteroid rotational period $\sigma_P / P$ and its direction $\sigma_\theta$, which require precision on the order of tens to hundreds of milliseconds and degrees every cadence, respectively.
-This could be accomplished by multiple, precise angular velocity measurements from multiple telescopes, or by increasing the time between observations to maximize the change in period between observations.
-Acknowledging and correcting for correlations in uncertainty between data points could also reduce uncertainty.
-Increasing the data set size to include more post-flyby tumbling data would also increase precision on some parameters, especially $K_{2m}$, without requiring such high period uncertainty.
+Figure \ref{fig:net-uncertainty} also demonstrates the strong affect of properties of the observational campaign on the density uncertainty.
+Most vital are the uncertainties on the asteroid's instantaneous rotational period $\sigma_P / P$ and direction $\sigma_\theta$, which require precision on the order of tens to hundreds of milliseconds and degrees every cadence, respectively (table \ref{tab:threshold-summary}).
+This could be accomplished by multiple precise angular velocity measurements from multiple telescopes or by increasing the time between observations to maximize the change in period between observations.
+Acknowledging and correcting for correlations in uncertainty between data points could also reduce uncertainty without requiring such high period uncertainty, as would increasing the data set size to include more post-flyby tumbling data.
+
+%% Rephrase this to handle one threshold.
 
 On the other hand, the cadence of observations $\Delta t$ and the presence of gaps in the data $T_\text{gap}$ do not affect results as strongly.
-Observations can be as much as 15 minutes apart to obey the weak threshold, with no constraint required to meet the strong threshold in our data set (which contains $\Delta t < 1$ hr).
+Table \ref{tab:threshold-summary} indicates that observations can be as much as 15 minutes apart to obey the weak threshold, with no constraint required to meet the strong threshold in our data set (which contains $\Delta t < 1$ hr).
 Likewise, there is no constraint on our data set of $T_\text{gap} < 3$ hr.
@@
 
-Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\sigma_\rho / \rho$) for the encounter perigee $r_p$ and observational precision $\sigma_P$ and $\sigma_\theta$.
+Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\langle \sigma_\rho / \rho \rangle$) for the encounter perigee $r_p$ and observational precision $\sigma_P$ and $\sigma_\theta$.
 These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are more volatile.
-
-The figure also displays the stark difference between density uncertainty computed by the lumpy model and the finite element model.
-This is partially due to different choices in the number of DOF (5 for the finite element model and 2 for the lumpy model), and to the assumptions of the model; the lumpy model is more biased towards uniform asteroids such as these, since it assumes that the asteroid is comprised of a small number of uniform density regions.
-This model-dependence of $\sigma_\rho / \rho$ is another reason to take the thresholds of table \ref{tab:threshold-summary} as estimates rather than strict limits on encounter properties.
 
@@
 
-To address the dependence of $\sigma_\rho / \rho$ on the choice of model, we investigate the model-independent moment uncertainty as well.
-Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty $\sigma(K_{\ell m})$ as a function of physical and observational encounter properties respectively.
+\subsection{Moment sensitivity to encounter properties}
+\label{sec:moment-uncertainty}
+
+To address the dependence of $\langle \sigma_\rho / \rho \rangle$ on the choice of model, we also investigate the model-independent moment uncertainty $\sigma(K_{\ell m})$ as well, defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
+Since there is no degeneracy between moments and the actual encounter data, $\sigma(K_{\ell m})$ is well-defined and less noise-prone than $\langle \sigma_\rho / \rho \rangle$, though its physical relevance is not as obvious.
+
+Figures \ref{fig:scan-physical} and \ref{fig:scan-observational} display moment uncertainty as a function of physical and observational encounter properties respectively.
 Figure \ref{fig:scan-spin} additionally depicts moment uncertainty as a function of initial spin pole.
 The thresholds of table \ref{tab:threshold-summary} are depicted as red lines.
+Each panel of each figure is generated by creating about 50 synthetic data sets with different encounter parameters and extracting the density moments from each.
 
-Figure \ref{fig:scan-physical} reveals that $\sigma_\rho / \rho$ from figure \ref{fig:net-uncertainty} is more sensitive to $\sigma (K_{2m})$ than to $\sigma(K_{3m})$.
+Figure \ref{fig:scan-physical} reveals that $\langle \sigma_\rho / \rho \rangle$ from figure \ref{fig:net-uncertainty} is more sensitive to $\sigma (K_{2m})$ than to $\sigma(K_{3m})$.
 For instance, $\sigma(K_{2m})$ is constant as $a_\mathcal{A}$ is varied despite a dramatic increase in $\sigma(K_{3m})$ for low $a_\mathcal{A}$.
-The resulting $\sigma_\rho / \rho$ is mostly constant.
-The opposite is true for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and $\sigma_\rho /\rho$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
+The resulting $\langle \sigma_\rho / \rho \rangle$ is mostly constant.
+The opposite is true for $P_\omega$, where $\sigma(K_{3m})$ (except for $m=0$) are mostly constant, and $\langle \sigma_\rho / \rho \rangle$ follows the trend of $\sigma(K_{2m})$ and increases for low rotational period.
 A consequence is that if more post-flyby tumbling data is collected, placing stronger constraints on $K_{2m}$ rather than $K_{3m}$, then $K_{2m}$ at some point might have essentially no uncertainty.
@@
 Green dots are the sampled spin pole directions.
-The red contours enclose regions above the strong uncertainty threshold on $\sigma_\rho / \rho$.
+The red contours enclose regions above the strong uncertainty threshold on $\langle \sigma_\rho / \rho \rangle$.
 The weak threshold is never exceeded.
@@
 
-\subsection{Central body oblateness}
-\label{sec:scan-oblateness}
+\subsection{Sensitivity to central body properties}
+\label{sec:central-body}
 
@@
 
-\subsection{Comparison of Jupiter and Earth encounters}
-\label{sec:jupiter-earth}
-
-If sufficiently accurate spin pole data can be detected for non-Earth encounters, it may be possible to extract density moments for encounters with larger planets.
-In this section, we run our reference asteroid through a Jupiter encounter to analyze the differences in uncertainty.
-
+Aside from oblateness, central body mass may also affect the success of this methodology.
+To address this possibility, we run our reference asteroid through a Jupiter encounter to analyze the differences in moment uncertainty $\sigma(K_{\ell m})$ compared to an Earth encounter.
 The physical parameters of the asteroid body are kept the same as the Earth encounter case, as are the observational uncertainty and cadence.
@@
 The excess velocity does not strongly affect $\sigma(K_{\ell m})$ as shown in figure \ref{fig:scan-physical}, so we keep it at the reference value.
-The ratio between the moment uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
-In all cases, the Jupiter-encounter moments are more uncertain than Earth-encounter moments.
-
 \begin{table}
@@
 
+The ratio between the moment uncertainties in the Jupiter and the Earth encounters are shown in table \ref{tab:jupiter-uncertainty}.
+In all cases, the Jupiter-encounter moments are more uncertain than Earth-encounter moments.
 These uncertainty ratios can be understood as follows.
@@
 
-\subsection{Comparisons between density distribution models}
-\label{sec:density-compare}
-
-Section \ref{sec:asym-density} briefly explored the density distributions produced for non-uniform asteroids, Here, we evaluate this case more thoroughly by considering two more example distributions.
-
-\begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-fe-r}
-
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/sph-3-l-r}
-
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-sph}.
-The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
-  \label{fig:den-sph}
-\end{figure*}
-
-Figure \ref{fig:den-sph} shows density distributions extracted via the finite element model and the lumpy model for a centred core of density three times the surrounding density.
-Results are similar to the off-center core shown in \ref{fig:den-move} in that the moments of the resulting density distribution are consistent with those extracted from the encounter data (i.e., $\chi^2_r$ is low).
-Again, the finite element model does not isolate the lump, instead spreading the excess mass over the asteroid.
-Unlike the off-center core example, the lumpy model is not able to recover the true distribution either.
-It produces deviations from the true density distribution of roughly the same size as the finite element model, with large significance.
-This is because the core mass is degenerate with the core's radius for centred, spherical cores.
-
-The success of the model in the off-center case was due to the fact that the shape of the asteroid was offset from the center of mass by a corresponding amount, assumed to be known precisely.
-The position of the lump was therefore observed up to one free parameter: the lump's mass.
-The assumption that the asteroid's center of mass is so precisely known stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
-If observations do not allow the center of mass to be determined in this way, then the lump's position will be more uncertain for the off-center case.
-
-To assess the lumpy model when the positions of the lump are not as certain as in the off-center case, we consider an asteroid with two lumps of radii 300 m and density three times the surrounding density.
-Each lump is located 500 meters from the center of the asteroid, so that they counterbalance and the asteroid's observed center of mass is its surface's centroid.
-The corresponding two-lump lumpy model has seven DOF, in contrast to the 5 DOF of the finite element model.
-Both models are run on this asteroid and the resulting distributions are shown in figure \ref{fig:den-double}.
-
-\begin{figure*}
-  \includegraphics[width=0.24\linewidth]{figs/double-fe-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-fe-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-fe-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-fe-r}
-
-  \includegraphics[width=0.24\linewidth]{figs/double-l-d}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-l-s}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-l-u}\hfill
-  \includegraphics[width=0.24\linewidth]{figs/double-l-r}
-
-  \caption{Cross-sectional slices of the density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-double}.
-The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
-  \label{fig:den-double}
-\end{figure*}
-
-Figure \ref{fig:den-double} again shows that the finite element model is unable to isolate the lumps except to predict generally increased density near the center.
-On the other hand, the lumpy model detects that the two lumps are opposite each other and of roughly the same radius and mass.
-These radius and mass values are also close to the true values.
-The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
-Uncertainty is also high, due to the extra DOF.
-Note that $\chi^2_r$ remains low despite the lumpy model's misplacement of the lumps.
-This is because the misplacement of the lumps affects only the $K_{3m}$ density moments, which are not as well constrained as the $K_{2m}$ density moments.
-The result is a deviation of a few hundred meters in lump location for the reference encounter properties.
-
 \section{Conclusions}
 
-We derived a novel, arbitrary-order equation for the tidal torque experienced by an asteroid during an encounter with a planet of arbitrary shape and mass distribution.
-The tidal torque revealed that the rotational behaviour of the asteroid over time depends strongly on the asteroid's density moments and the initial orientation.
-We then built a fast simulation for an asteroid encounter and designed an MCMC to extract density moments from simulated data.
-We also created two models --- the finite element model and the lumpy model --- to translate these density moments into density distributions.
-Uncertainties are propagated throughout the pipeline.
-The pipeline was executed for several synthetic encounters and found to yield both density moments and distributions consistent with the true values.
+We develop and demonstrate a pipeline which precisely constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
+We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 18$ Earth radii and the period be $\gtrsim 5.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
+Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.
+Due to the sensitivity of the system, we find that it is also necessary to correctly model effects that influence the system very little, such as the oblateness of the central body, in order for accurate density distributions to be extracted.
 
-We assessed the uncertainty of the pipeline's results by adjusting various properties of the asteroid and its Earth encounter.
-The thresholds we measure (table \ref{tab:threshold-summary}) show that the observational uncertainty and perigee of the asteroid orbit have the strongest effect on the density distribution uncertainty and they are the most important thresholds to meet in order to extract a precise distribution.
-The properties that do not affect density uncertainty as much, such as the central body oblateness, must still be accurately modelled to avoid errors in the pipeline results.
-We also discussed how these thresholds could be eased by changes in observational behaviour such as lengthening the data set, or by physical asteroid properties such as a closer encounter, an initially tumbling state, or the presence of a massive moon such as Earth's.
-If the thresholds were eased enough, then the asteroid length would become an important threshold as well.
+We also find that these inferences can be dominated by model uncertainties which occur when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
+Models which are specialized to fit for certain features (such as the lumpy model) can produce less uncertain results than generalized models (such as the finite element model).
+To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
 
-Finally, we highlighted that the properties of the final density distribution are strongly model-dependent.
-Each model was able to resolve some density distribution features and not others depending on the model design.
-The uncertainties on density distribution of the two models were drastically different, and also depended on the number of degrees of freedom used in the model.
-To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
+In order to further take advantage of close asteroid encounters, improvements to our pipeline may lead to increased precision of the output.
+Specifically, the angular velocity data set may be lengthened to include more post-encounter data, correlations between observational uncertainties could be incorporated into the uncertainty model, and previous knowledge of some of the asteroid properties (such as moment of inertia) could be used to adjust priors on the density moments.
+The presence of Earth's moon or pre-encounter tumbling of the asteroid may also increase the precision of our pipeline's density distribution estimates.
 
@@
 We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work and pointing out possible future initiatives.
-JTD also thanks the MIT UROP office for funding his work.
+We also thank the anonymous reviewer for their careful reading of our paper.
+JTD thanks the MIT UROP office for funding his work.
 This paper made substantial use of MIT Supercloud's facilities.

### 2022-08-19 code/density/mcmc/core-scan/average.py

@@ -9,8 +9,8 @@ from display import make_gif, make_slices
 from core import TrueShape, Indicator
 
 RUN_NAME = sys.argv[1]
-PULL = True
-GENERATE = True
+PULL = False
+GENERATE = False
 
 NUM_DRAWS = 20
 NUM_CHOOSE = 1000

### 2022-08-19 code/density/mcmc/mcmc_core.py

@@ -409,6 +409,7 @@ class MCMCAsteroid:
         densities /= np.nanmean(densities)
 
         PERCENTILE = 99.5# 95
+        UNC_PERCENTILE=95
 
         if true_densities is not None:
             true_densities /= np.nanmean(true_densities)
@@ -422,8 +423,8 @@ class MCMCAsteroid:
         make_gif(densities, self.asteroid.grid_line, "$\\rho$", 'plasma', f"{FIG_DIRECTORY}{self.name}/fe-d.gif", duration)
         
         print("Plotting uncertainty")
-        make_slices(uncertainty_ratios, self.asteroid.grid_line, "$\\sigma_\\rho / \\rho$", 'Greys_r', f"{FIG_DIRECTORY}{self.name}/fe-u", error, PERCENTILE)
-        make_gif(uncertainty_ratios, self.asteroid.grid_line, "$\\sigma_\\rho / \\rho$", 'Greys_r', f"{FIG_DIRECTORY}{self.name}/fe-u.gif", duration, PERCENTILE)
+        make_slices(uncertainty_ratios, self.asteroid.grid_line, "$\\sigma_\\rho / \\rho$", 'Greys_r', f"{FIG_DIRECTORY}{self.name}/fe-u", error, UNC_PERCENTILE)
+        make_gif(uncertainty_ratios, self.asteroid.grid_line, "$\\sigma_\\rho / \\rho$", 'Greys_r', f"{FIG_DIRECTORY}{self.name}/fe-u.gif", duration, UNC_PERCENTILE)
 
         if true_densities is not None:
             print("Plotting differences")

### 2022-08-19 paper/appendices.tex
Responding to Julien's comments
Revised paper

@@
 To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
-It is possible that the orientation of the asteroid may be more readily available as a data set.
+It is possible that the orientation of the asteroid may be more readily available as a data set, notably if a large collection of radar antenna fail to follow the encounter sufficiently.
 In this appendix, we generate an orientation data set for the reference asteroid flyby, extract density moments from it, and compare the results to moments extracted from angular velocity data.
@@
 Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
-Here we outline two additional models --- the nearly-uniform and the harmonic models --- which are less conventional but still useable for extracting density distribution properties.
+Here we outline two additional models which are less conventional but still useable for extracting density distribution properties.
 Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.
@@
 \subsection{Nearly-uniform model}
-In this ``nearly-uniform'' model, we seek to pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$, which can be chosen manually.
+In this ``nearly-uniform'' model, we pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$.
 Any prior distribution can be chosen, but the following prior is both interesting and numerically efficient.
@@
 This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
-
-\section{Animated density distributions}
-
-This appendix contains animations to better display the density distributions shown in the main text.
-Each frame represents a cross section perpendicular to the $\unit z$-axis, starting with negative $z$ and ending with positive $z$.
-All densities are divided by the mean asteroid density.
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-d.mp4}{FE asymmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-s.mp4}{FE asymmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-u.mp4}{FE asymmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-fe-r.mp4}{FE asymmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-d.mp4}{Lumpy asymmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-s.mp4}{Lumpy asymmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-u.mp4}{Lumpy asymmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/asym-l-r.mp4}{Lumpy asymmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-d.mp4}{FE symmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-s.mp4}{FE symmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-u.mp4}{FE symmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-fe-r.mp4}{FE symmetric significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-d.mp4}{Lumpy symmetric density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-s.mp4}{Lumpy symmetric deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-u.mp4}{Lumpy symmetric uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sym-l-r.mp4}{Lumpy symmetric significance}
-
-  \caption{Density distributions extracted via the finite element model for the asymmetric (\textit{top two rows}) and symmetric (\textit{bottom two rows}) reference asteroids.
-The finite element model (\textit{first and third rows}) and the lumpy model (\textit{second and fourth rows}) are employed.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-uniform}.}
-  \label{fig:animated-uniform}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-d.mp4}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-s.mp4}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-u.mp4}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-fe-r.mp4}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-d.mp4}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-s.mp4}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-u.mp4}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/move-l-r.mp4}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with an off-center core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-move}.}
-  \label{fig:animated-move}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-d.mp4}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-s.mp4}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-u.mp4}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-fe-r.mp4}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-d.mp4}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-s.mp4}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-u.mp4}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/sph-3-l-r.mp4}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and lumpy (\textit{bottom}) models for an asteroid with a centred core.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-sph}.}
-  \label{fig:animated-sph}
-\end{figure*}
-
-\begin{figure*}
-  \textbf{Please see the published version of the paper for these animations, or find them online at the following links.}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-d.mp4}{FE density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-s.mp4}{FE deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-u.mp4}{FE uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-fe-r.mp4}{FE significance}
-
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-d.mp4}{Lumpy density} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-s.mp4}{Lumpy deviation} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-u.mp4}{Lumpy uncertainty} \hfill
-  \href{https://github.com/jack-dinsmore/asteroid-tidal-torque/tree/main/paper/gifs/double-l-r.mp4}{Lumpy significance}
-
-  \caption{Density distributions extracted via the finite-element (\textit{top}) and the two-lump lumpy (\textit{bottom}) models for an asteroid with two counterbalancing cores.
-From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-Animated form of figure \ref{fig:den-double}.}
-  \label{fig:animated-double}
-\end{figure*}

### 2022-08-19 paper/main.tex
Revised paper

@@
 Over the past twenty years, the increase in quantity and quality of sensitive all-sky surveys has prompted the discovery of numerous asteroids.
-Such advances have been made via ground-based surveys such as the Catalina Sky Survey \cite{larson1998catalina}, Pan-STARRS \cite{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \cite{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \cite{wright2010wide}.
+Such advances have been made via ground-based surveys such as the Catalina Sky Survey \citep{larson1998catalina}, Pan-STARRS \citep{kaiser2002pan}, and the Lincoln Near-Earth Asteroid Research project (LINEAR) \citep{stokes2000lincoln}, as well as space-based instruments such as the Wide-field Infrared Survey Explorer (WISE) mission \citep{wright2010wide}.
 Many of these asteroids are relatively small, but some are kilometre-sized and a few are predicted to closely encounter Earth or other planets in the near future.
-More encounter candidates are likely to be discovered by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) \cite{tyson2002large}.
-Their encounters can then be monitored by global ground-based networks such as the Las Cumbres Observatory (LCO) \cite{brown2013cumbres}.
+More encounter candidates are likely to be discovered by new efforts such as the Large-aperture Synoptic Survey Telescope (LSST) \citep{tyson2002large}.
+Their encounters can then be monitored by global ground-based networks such as the Las Cumbres Observatory (LCO) \citep{brown2013cumbres}.
 Such ground-based monitoring is typically used to derive the rotation period of an asteroid and its surface properties (see e.g.
@@
 Since the tidal torque acting on an asteroid during an encounter depends on the interior mass distribution, the careful monitoring of angular velocity variations during an encounter also presents a window into the interior properties of asteroids.
-The gravitational two-body system has been studied in the context of tidal torque to different orders and with several different methods \cite{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
-Further theoretical studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \cite{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
+The gravitational two-body system has been studied in the context of tidal torque to different orders and with several different methods \citep{paul88, SCHEERES2000106, ashenberg07, BOUE2009750, HouMar2017}.
+Further theoretical studies showed that the tidal torque, observed through angular velocity perturbations, is sensitive to asteroid interior density distribution \citep{Naidu_2015, Makarov2022ChaosOO, scheeres2004evolution}.
 
-Angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \cite{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus \cite{DESCAMPS2020113726, BERTHIER2020113990}.
+Angular velocity perturbations have been observed and used to extract asteroid properties in several cases, including for the 2013 encounter of (367943) Duende with Earth \citep{MOSKOVITZ2020113519, benson2020spin}, and asteroid binaries (3905) Doppler and (617) Patroclus \citep{DESCAMPS2020113726, BERTHIER2020113990}.
 Orbital and physical properties, including moment of inertia (MOI) ratios have also been extracted for asteroid 99942 Apophis, discovered on June 19, 2004 by R.
@@
 Tholen, and F.
-Bernardi \cite{giorgini2005recent, giorgini2008predicting, smalley20052004}, and on target to encounter Earth in 2029 \cite{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
+Bernardi \citep{giorgini2005recent, giorgini2008predicting, smalley20052004}, and on target to encounter Earth in 2029 \citep{yu2014numerical, hirabayashi2021finite, valvano2022apophis, Lee2022Apophis}.
 However, density distribution features beyond the MOI ratios have not yet been extracted for any asteroid encounters.
 More research is needed to study in what cases these effects are observable, and what factors generally inhibit observation of these new features.
-It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity in particular \cite{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
+It seems pivotal to augment previous work on the affect of tidal torque on Apophis' angular velocity in particular \citep{souchay2014rotational, souchay2018changes} so that upcoming observations may constrain these properties and thus improve our predictions.
 
 We address this community need by developing a methodology to translate (1) time series of asteroid angular velocity data into constraints on density moments and (2) constraints on density moments into constraints on an asteroid's density distribution.
-Other techniques, such as measurement of tidal distortion \cite{RICHARDSON199847}, impact or seismometry experiments \cite{RICHARDSON2005325}, or gradiometry \cite{carroll2018tidal}, may additionally constrain the density distribution.
+Other techniques, such as measurement of tidal distortion \citep{RICHARDSON199847}, impact or seismometry experiments \citep{RICHARDSON2005325}, or gradiometry \citep{carroll2018tidal}, may additionally constrain the density distribution.
 In section \ref{sec:methods}, we introduce the analytical and numerical fundamentals of this methodology.
@@
 Given synthetic data, an Affine Invariant MCMC Ensemble sampler was used to generate Posterior Probability Distributions (PPDs) from flat priors.
-We use the Python implementation \texttt{emcee} \cite{foreman2013emcee}.
+We use the Python implementation \texttt{emcee} \citep{foreman2013emcee}.
 Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in equation \ref{eqn:parameter-bounds}.
@@
 
-Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \cite{Gao2012}.
+Before the MCMC was run, local minima in the likelihood were found via the Nelder-Mead algorithm implemented in \texttt{scipy} \citep{Gao2012}.
 Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused all values of $\gamma_0$ to be degenerate.
@@
 
-The translation rules of spherical harmonics \cite{Gelderen1998TheSO} give that the density moments in the hybrid frame are
+The translation rules of spherical harmonics \citep{Gelderen1998TheSO} give that the density moments in the hybrid frame are
 \begin{equation}
@@
 From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-uniform}.
+These figures are available in animated form in the Supplemental Data.
 Extracted densities are generally within 10\% of the truth.}
@@
 
-%% Working on cutting down the uncertainties in the large-uncertainty regions
-
 \begin{figure*}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-move}.
+These figures are available in animated form in the Supplemental Data.
 The lumpy model successfully extracts the core.}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-sph}.
+These figures are available in animated form in the Supplemental Data.
 The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in appendix figure \ref{fig:animated-double}.
+These figures are available in animated form in the Supplemental Data.
 The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
@@
 
-Figure \ref{fig:scan-oblateness} displays moment uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \cite{paterLissauer2015}.
+Figure \ref{fig:scan-oblateness} displays moment uncertainty $\sigma(K_{2 m})$ of the first-order parameters as a function of $\epsilon$ across a reasonable range of central body oblatenesses based on those of Solar System planets \citep{paterLissauer2015}.
 It also shows linear best-fitting curves for moment uncertainty as a function of oblateness.

### 2022-08-22 paper/main.tex
Ready to run trifecta

@@
 The model places the lumps correctly near the $xy$-plane of the asteroid but does not perfectly align them with the $y$ axis, resulting in high $\Delta \rho$ where the true lumps and predicted lumps do not intersect.
-Uncertainty is also high, due to the extra DOF, however the distribution is in agreement with the extracted density moments because the misplacement of the lumps affects only the $K_{3m}$ density moments, which are not as well constrained as the $K_{2m}$ density moments.
-The result is a deviation of a few hundred meters in lump location for the reference encounter properties.
+Uncertainty is also high, due to the extra DOF.
+The difference between the predicted distribution and the true distribution is due entirely to the uncertainty in the moments computed by the fit to flyby data.
+The density distribution model reproduces those moments perfectly, misplacing the lumps by a few hundred meters because that offset is determined only by the $K_{3m}$ density moments, which are not as well constrained as $K_{2m}$.
 

### 2022-08-22 code/density/mcmc/mcmc_core.py

@@ -24,6 +24,8 @@ EPSILON = 1e-10
 MINIMUM_LIKELIHOOD = -1000
 NUM_SUCCESSES = 1
 
+TRIFECTA = True
+
 class MCMCMethod:
     def __init__(self, asteroid, mean_density, n_free, n_all, generate):
         self.mean_density = mean_density
@@ -238,7 +240,10 @@ class MCMCAsteroid:
 
             error = error_part if cut_k2m else error_full
 
-            self.display(densities, true_densities, uncertainty_ratios, error)
+            if not TRIFECTA:
+                self.display(densities, true_densities, uncertainty_ratios, error)
+            else:
+                self.display(densities, true_densities, uncertainty_ratios)
 
         return unc_tracker
 
@@ -430,6 +435,35 @@ class MCMCAsteroid:
             print("Plotting differences")
             make_slices(difference, self.asteroid.grid_line, "$\\Delta\\rho / \\rho$", 'PuOr_r', f"{FIG_DIRECTORY}{self.name}/fe-s", error, PERCENTILE, balance=True)
             make_gif(difference, self.asteroid.grid_line, "$\\Delta\\rho / \\rho$", 'PuOr_r', f"{FIG_DIRECTORY}{self.name}/fe-s.gif", duration, PERCENTILE, balance=True)
+
+        warnings.filterwarnings("default")
+
+    def display_trifecta(self, densities, true_densities, uncertainty_ratios, duration=5):
+
+        FIG_DIRECTORY = "../../figs/"
+        PERCENTILE = 99.5# 95
+        UNC_PERCENTILE=95
+
+        if not os.path.isdir(f"{FIG_DIRECTORY}trifecta"):
+            os.mkdir(f"{FIG_DIRECTORY}trifecta")
+        warnings.filterwarnings("ignore")
+
+        densities /= np.nanmean(densities)
+        assert true_densities is not None
+
+        true_densities /= np.nanmean(true_densities)
+
+        print("Plotting density")
+        make_slices(densities, self.asteroid.grid_line, "$\\rho_\mathrm{fit}$", 'plasma', f"{FIG_DIRECTORY}trifecta/fe-d", None)
[…]

### 2022-08-23 paper/main.tex
Revised paper

@@
 We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
-We find that high precision in rotational period estimates (order of tens of milliseconds to seconds) are necessary for each cadence, and that low perigees ($\lesssim 18$ Earth radii) are necessary to resolve density distributions.
+We find that high precision in rotational period estimates (order of fifty milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
 \end{abstract}
@@
 
-In the following sections, we first introduce the retrieval capabilities regarding density moments, then we turn to the constraints that can be derived reliably on the density distribution.
+In the following sections, we first introduce the retrieval capabilities regarding density moments, then we turn to an example of a retrieval of the density distribution from the moments.
 For both stages of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
@@
 \subsection{Density moment retrieval}
-\label{sec:example-fit}
+\label{sec:results-moment}
 \begin{figure}
@@
 \subsection{Density distribution retrieval}
-\label{sec:asym-density}
+\label{sec:results-distro}
+
+To provide an example of a density distribution extraction, we consider an asteroid with a core and ask whether our methodology can resolve the location, mass, and size of the core.
+Specifically, we use a spherical core of radius 300 m, placed 500 m from the center and with density 50\% greater that of the surrounding asteroid.
+We use the lumpy model to extract a distribution in this section because it is designed to look for cores.
+
+Synthetic data was generated for the new asteroid and moments were extracted via the process described above.
+These moments were consistent with the true moments, with a $\chi^2$ per DOF of $\chi^2_r = 1.1$, and inconsistent with the moments of a nearly-uniform asteroid of the same shape ($\chi^2_r = 2.7 \times 10^8$).
+The inconsistency comes almost entirely from the MOI-constraining $K_{2m}$ moments, which are sensitive to large mass distribution changes such as the presence of a core.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\linewidth]{figs/side-by-side-d}\hfill
+  \includegraphics[width=0.49\linewidth]{figs/side-by-side-t}
+
+  \includegraphics[width=0.49\linewidth]{figs/side-by-side-u}
+  \caption{The extracted distribution (\textit{left}) and true distribution (\textit{right}) of the asymmetric reference asteroid.
+The density distribution was created via the lumpy model.
+Uncertainty in the distribution is shown below.
+The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth.}
+  \label{fig:den-side-by-side}
+\end{figure}
+
+A density distribution was then extracted, shown in figure \ref{fig:den-side-by-side} next to the true distribution.
+Visually, the extracted distribution is virtually identical to the true distribution, which is emphasized by the low uncertainties of $\sigma_\rho / \rho = \mathcal{O}(10^{-3})$ throughout the asteroid.
+Despite the low uncertainty, the density distribution is still consistent with the truth, with $\chi^2_r = 1.46$ using uncertainties calculated via section \ref{sec:density-uncertainty-model}.
+The number of asteroid points at which this uncertainty was calculated was about 6 million, making $\chi^2_r = 1.46$ actually quite high, due to the fact that our density uncertainty model does not take the correlation between density at different points into account.
+By comparison, the difference between the extracted distribution and a nearly-uniform distribution is $\chi^2_r = 6.4 \times 10^{6}$.
+The lumpy model's successful identification of a core is thus very statistically significant.
+
+\section{Discussion}
+\label{sec:discussion}
+In section \ref{sec:density-compare} below, we discuss the differences between the two density distribution models for many asteroids and find that the distributions and uncertainties they generate are strongly model-dependent.
+
+Given this understanding of our density extraction models, we answer the important questions of which encounters can be successfully studied by this methodology, and how observational campaigns can be designed to best take advantage of an encounter.
+To quantify the methodology's success, we use the median of a density uncertainty distribution $\langle \sigma_\rho / \rho \rangle$ in section \ref{sec:density-uncertainty}.
+But since this median is so model-dependent, we also analyze the success of the method via the density moment uncertainty $\sigma (K_{\ell m})$ (which is not moment dependent) in section \ref{sec:moment-uncertainty}.
+In section \ref{sec:central-body}, we study the methodology's dependence on the properties of the central body.
+
+\subsection{Density distribution model caveats}
+\label{sec:density-compare}
+
+To study the output of the density distributions, we start with executing them on synthetic data generated for the two reference asteroids.
+The result is shown in figure \ref{fig:den-uniform} displays density distributions and uncertainties.
+These distributions are consistent with the moments extracted by the MCMC in section \ref{sec:fit} --- indeed all the distributions we show have moments consistent with the data, even for non-ellipsoidal asteroids (not shown).
 
@@
 
-Figure \ref{fig:den-uniform} displays density distributions and uncertainties extracted by both the finite element and lumpy models for the reference asteroids.
-They are consistent with the moments extracted by the MCMC in section \ref{sec:fit}, even for non-ellipsoidal asteroid shapes (not shown).
-
 For the finite element model with the reference observational set-up, the uncertainty on observations is such that the density distribution is generally within 10\% of the true uniform density (second column) while the density uncertainty is generally less than 40-50\% of the density value at any point in the asteroid (third column).
 In no place is the significance of these deviations from the true distribution greater than $1 \sigma$ (last column).
-The lumpy model yields distributions with much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom; with the one-lump-model and with asteroids whose surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the single lump must lie at the centroid with mass close to zero and with unconstrained radius.
+The lumpy model yields distributions with much lower uncertainty than the finite element distributions (maximum uncertainty on the order of 1\% of the local density or less) due to its few degrees of freedom and its particular design; with the one-lump-model and with asteroids whose surface's centroid is the asteroid's center of mass (such as these uniform asteroids), the single lump must lie at the centroid with mass close to zero and with unconstrained radius.
 The uncertainty of regions far from the asteroid center, where the lump is unlikely to extend, is typically very small, while regions close to the center are more likely to be contained inside a lump and hence have greater density uncertainty.
@@
 We also explore model behaviour in non-uniform density asteroids.
-We employ an asteroid of the same shape as the asymmetric asteroid, and in the same flyby scenario, but we place a solid core of radius $\SI{300}{\meter}$ and density 50\% greater than the surrounding density, 500 m away from the center of the asteroid.
-This changes the asteroid density moments.
-New density moments are extracted via the process described in section \ref{sec:fit} and the finite-element and lumpy models are used to extract density distributions shown in figure \ref{fig:den-move}.
+First we consider again the off-center core asteroid used in section \ref{sec:results-distro}; distributions are shown in figure \ref{fig:den-move}.
+As remarked before, the lumpy model fit is successful.
+However, the finite element model does not reproduce the core.The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
+Visually the finite element model has spread the high-density core into the rest of the asteroid.
+
+This ``spreading out'' of the density distribution is not necessarily a failure of the finite element model; the last column of figure \ref{fig:den-move} shows that the deviation from the true density distribution does not have high significance.
+In effect, the finite element model is acknowledging many possible distributions that could all have the same moments as the true distribution, while the lumpy model picks one.
+In our case the lumpy model was correct, but for asteroids without a discrete, spherical core like this, it may not be.
 
@@
 
-The distributions of figure \ref{fig:den-move} reproduce the extracted density moments; nevertheless the distributions extracted by the finite model match the true distributions less well.
-The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
-Visually the finite element model has spread the high-density core into the rest of the asteroid, but this deviation from the true density distribution does not have high significance due to the similarly large model-driven uncertainty of the finite element model.
-
-%% Julien wants a side by side figure to display how well the core is extracted
-
-%% Julien also mentioned adding a method to detect deviations.
-
-On the other hand, the lumpy model is designed to detect discrete changes in density distribution, and identifies the boundary of the core very accurately.
-Deviations from the truth are around $10^{-5}$ of the local density, with uncertainties about 1\% of the local density at maximum and usually much lower.
-The significance of the deviations is around 30\%, as it was in figure \ref{fig:den-uniform} where the extracted distribution again matched the truth.
-Again, the low uncertainty is caused by the small number of degrees of freedom of the lumpy model.
-A consequence is that if the core had been non-spherical, the lumpy model would be inaccurate, with significant deviations from the truth.
-Therefore, neither model is more correct in the general case, but each can be used to explore different scenarios.
-
-\section{Discussion}
-\label{sec:discussion}
-In the previous section, we saw that the uncertainty in density over the asteroid is strongly model-dependent.
-In section \ref{sec:density-compare} below, we further study the model outputs by considering two more sample asteroid extractions.
-
-Given this understanding of our density extraction models, we answer the important questions of which encounters can be successfully studied by this methodology, and how observational campaigns can be designed to best take advantage of an encounter.
-To quantify the methodology's success, we use the median of a density uncertainty distribution $\langle \sigma_\rho / \rho \rangle$ in section \ref{sec:density-uncertainty}.
-But since this median is so model-dependent, we also analyze the success of the method via the density moment uncertainty $\sigma (K_{\ell m})$ (which is not moment dependent) in section \ref{sec:moment-uncertainty}.
-In section \ref{sec:central-body}, we study the methodology's dependence on the properties of the central body.
-
-\subsection{Density distribution model caveats}
-\label{sec:density-compare}
-We will consider two example scenarios which lead to inflated density distribution uncertainties independent of the actual asteroid properties or the data quality.
-Specifically, we consider the lumpy model's degeneracy for a centred core and the two-core lumpy model.
-This highlights the model dependence of the density distributions extracted from density moments.
+To further highlight the model-dependence of the extracted density distributions, we consider two final asteroids which lead to inflated density distribution uncertainties independent of the data quality.
+Specifically, we will highlight the lumpy model's degeneracy for a centred core and the two-core lumpy model.
 
@@
 
+Here, we investigate how density uncertainty $\langle \sigma_\rho / \rho \rangle$, extracted by both the finite element and lumpy models, depends on physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational properties (the data uncertainty, the cadence of observations, and gaps in data coverage).
+
 \begin{figure*}
@@
 Both the lumpy and finite element models are used, though the finite element model uncertainty is model-dominated and not very sensitive to encounter properties.
-The uncertainty thresholds (\textit{red lines}) are shown and the properties that exceed these thresholds are shaded.
+The uncertainty threshold (\textit{red line}) is shown and the properties that exceed this threshold are shaded.
 The vertical black dotted lines are the property values of the reference asteroid.
@@
 
-Here, we investigate how density uncertainty $\langle \sigma_\rho / \rho \rangle$, extracted by both the finite element and lumpy models, depends on physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational properties (the data uncertainty, the cadence of observations, and gaps in data coverage).
+Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
+We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
+For the most part, we consider the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
 
-%% Why do we have two thresholds?
-
-Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
-We define two density distribution uncertainty thresholds termed the ``weak'' and ``strong'' thresholds.
-These values are $\langle \sigma_\rho / \rho \rangle = 10^{-4}$ (weak) and $10^{-3}$ (strong), for density distributions extracted via the lumpy model.
-They are manually chosen, and adjustments to them or to the lumpy model will affect the data of table \ref{tab:threshold-summary}.
-They are shown as red lines in figures \ref{fig:net-uncertainty} and \ref{fig:spin-uncertainty}, and the encounter properties which exceed these thresholds are listed in table \ref{tab:threshold-summary} for reference.
-
-The thresholds are applied to the lumpy model distribution because the large, model-induced uncertainty of the finite element model makes its density distributions only slightly dependent on encounter parameters.
-This is a further example of model-induced uncertainty in density distributions.
+Figure \ref{fig:net-uncertainty} reveals that the most limiting physical properties of the asteroid are its perigee and period.
+Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only important for $a_\mathcal{A}\sim $tens of meters.
+By contrast, the radius of Apophis is  $\sim 300$ m and its perigee and rotational period also obey the strong constraints \citep{giorgini2008predicting}.
+The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \citep{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \citep{yu2014numerical,hirabayashi2021finite}.
+Further work must therefore be done to apply this analysis to Apophis.
 
@@
 
+In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} shows an uncertainty dependence on initial spin direction.
+The poles (i.e., angular velocities perpendicular to the orbital plane) lead to greater uncertainty, potentially by as much as a factor of ten over to the orbital plane.
+Compared to other physical parameters, initial spin direction is not very constraining.
+
+Figure \ref{fig:net-uncertainty} also demonstrates the strong affect of properties of the observational campaign on the density uncertainty.
+Most vital are the uncertainties on the asteroid's instantaneous rotational period $\sigma_P / P$ and direction $\sigma_\theta$, which require precision on the order of tens to hundreds of milliseconds and degrees every cadence, respectively.
+This could be accomplished by multiple precise angular velocity measurements from multiple telescopes or by increasing the time between observations to maximize the change in period between observations.
+Acknowledging and correcting for correlations in uncertainty between data points could also reduce uncertainty without requiring such high period uncertainty, as would increasing the data set size to include more post-flyby tumbling data.
+
+On the other hand, the cadence of observations $\Delta t$ and the presence of gaps in the data $T_\text{gap}$ do not affect results as strongly.
+Short cadence appears preferable, though as much as 20--40 min between observations is still not as detrimental to data quality as other properties.
+Likewise gaps appearing with size $T_\text{gap}$, even hours in length, do not greatly increase density uncertainty.
+
+To quantify the information contained in \ref{fig:net-uncertainty}, we define a ``threshold'' on each encounter property beyond which we say the data quality is too low to extract meaningful information concerning the density distribution of the asteroid.
+The value of this threshold for perigee is set at the point when the finite element model produces $\langle \sigma_\rho / \rho \rangle = 30\%$, since this is about the maximum uncertainty that the lumpy model can produce.
+We cannot use this process to define the threshold for the other properties because the finite element model does not depend strongly enough on other properties, so we instead transfer the threshold definition to the value of $\langle \sigma_\rho / \rho \rangle$ produced by the lumpy model at that perigee ($5\times 10^{-4}$).
+This threshold is marked as a horizontal red line in figure \ref{fig:net-uncertainty}, and the values at which the encounter parameters exceed the threshold are shown in table \ref{tab:threshold-summary}.
+
 \begin{table}
   \centering
-  \begin{tabular}{lll} \hline
-    Encounter property & Weak & Strong \\ \hline
-    Perigee ($r_p$, Earth radii) & $<$6.3 & $<$18\\
-    Excess velocity ($v_\infty$) & - & - \\
-    Asteroid length ($a_\mathcal{A}$, m) & $>$15 & - \\
-    Period ($P_\omega$, hr) & $>$5.3 & - \\ \hline
-    Spin period uncertainty ($\sigma_P$, ms) & $<$12 & $<$270\\
-    Spin pole uncertainty ($\sigma_\theta$, $^\circ$) & $<$1.9 & $<$35 \\
-    Cadence ($\Delta t$, min) & $<$15 & - \\
-    Data gap ($T_\text{gap}$, hr) & - & - \\ 
+  \begin{tabular}{ll} \hline
+    Encounter property & Threshold \\ \hline
+    Perigee ($r_p$) & $<10$ Earth radii\\
+    Period ($P_\omega$) & $>3.3$ hr \\ \hline
+    Spin period uncertainty ($\sigma_P$) & $<55$ ms\\
+    Spin pole uncertainty ($\sigma_\theta$) & $< 9.1^\circ$ \\
     \hline
   \end{tabular}
-  \caption{The weak and strong thresholds on physical / observational properties (\textit{top} / \textit{bottom}) that meet certain density distribution thresholds (see text).
-Perigee and observational uncertainty are the most constraining properties, followed by rotational period, asteroid length, and observational cadence.}
+  \caption{Thresholds on physical / observational properties (\textit{top} / \textit{bottom}) necessary to obtain density distributions with useable uncertainty.
+Perigee and observational uncertainty are the most constraining properties.}
   \label{tab:threshold-summary}
@@
 
-Figure \ref{fig:net-uncertainty} reveals that the most limiting physical properties of the asteroid are its perigee and period.
-Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only effective for $a_\mathcal{A} \sim 15$ m.
-By contrast, the radius of Apophis is
-$\sim 300$ m and its perigee and rotational period also obey the strong constraints \citep{giorgini2008predicting}.
-The comparison to Apophis is complicated by the fact that Apophis is smaller than our $a_\mathcal{A}$ value, is tumbling \citep{PRAVEC201448}, and may change slightly in physical properties due to tidal interaction during the encounter \citep{yu2014numerical,hirabayashi2021finite}.
-Further work must therefore be done to apply this analysis to Apophis.
+Table \ref{tab:threshold-summary} is consistent with the conclusions we drew for figure \ref{fig:net-uncertainty}.
+Apophis' 2029 encounter is consistent with the thresholds, and the perigee, period, and observational uncertainties are indeed the most constraining.
+The values of the thresholds are interdependent and may change if the encounter conditions are changed, so they should not be taken to be precise values.
 
-In addition to the period constraint shown in this table, figure \ref{fig:spin-uncertainty} shows a threshold on initial spin direction.
-The poles (i.e., angular velocities perpendicular to the orbital plane) lead to greater uncertainty and this is the only region which rises above the weak uncertainty threshold.
-Compared to other physical parameters, initial spin direction is not very constraining.
-
-Figure \ref{fig:net-uncertainty} also demonstrates the strong affect of properties of the observational campaign on the density uncertainty.
-Most vital are the uncertainties on the asteroid's instantaneous rotational period $\sigma_P / P$ and direction $\sigma_\theta$, which require precision on the order of tens to hundreds of milliseconds and degrees every cadence, respectively (table \ref{tab:threshold-summary}).
-This could be accomplished by multiple precise angular velocity measurements from multiple telescopes or by increasing the time between observations to maximize the change in period between observations.
-Acknowledging and correcting for correlations in uncertainty between data points could also reduce uncertainty without requiring such high period uncertainty, as would increasing the data set size to include more post-flyby tumbling data.
-
-%% Rephrase this to handle one threshold.
-
-On the other hand, the cadence of observations $\Delta t$ and the presence of gaps in the data $T_\text{gap}$ do not affect results as strongly.
-Table \ref{tab:threshold-summary} indicates that observations can be as much as 15 minutes apart to obey the weak threshold, with no constraint required to meet the strong threshold in our data set (which contains $\Delta t < 1$ hr).
-Likewise, there is no constraint on our data set of $T_\text{gap} < 3$ hr.
-This gap was simulated to occur in one contiguous unit centred on the encounter perigee, where torque is highest.
-If the gap occurred elsewhere in the data set or was subdivided into multiple gaps, it would likely affect density uncertainty even less.
-
-Figure \ref{fig:net-uncertainty} reveals that the thresholds presented in table \ref{tab:threshold-summary} are particularly sharp (a steep slope of $\langle \sigma_\rho / \rho \rangle$) for the encounter perigee $r_p$ and observational precision $\sigma_P$ and $\sigma_\theta$.
-These thresholds are therefore less likely to change if the asteroid properties are altered, whereas the thresholds on period $P_\omega$, length $a_\mathcal{A}$, and cadence $\Delta t$ are more volatile.
+\subsection{Moment sensitivity to encounter properties}
+\label{sec:moment-uncertainty}
 
@@
 The vertical dotted line indicates the reference asteroid values.
-The red dashed/solid lines indicate the weak/strong uncertainty thresholds.}
+The red line indicates the uncertainty threshold.}
   \label{fig:scan-perigee}
@@
 The vertical dotted line indicates the reference asteroid values.
-The red dashed/solid lines indicate the weak/strong uncertainty thresholds.}
+The red line indicates the uncertainty threshold.}
     \label{fig:scan-rho}
@@
 \end{figure*}
-
-\subsection{Moment sensitivity to encounter properties}
-\label{sec:moment-uncertainty}
 
@@
 Indeed, figure \ref{fig:scan-observational} shows that $K_{3m}$ especially are more uncertain for $T_\text{gap} \gtrsim 1.5$ hr.
-However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the thresholds, indicating that large amounts of data can be cut without compromising the methodology.
+However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the threshold, indicating that large amounts of data can be cut without compromising the methodology.
 As with the threshold for cadence discussed above, this 1.5 hr cut-off may depend on the asteroid rotational period or the orbital time scales.
@@
 We develop and demonstrate a pipeline which precisely constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
-We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 18$ Earth radii and the period be $\gtrsim 5.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
+We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 10$ Earth radii and the period be $\gtrsim 3.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
 Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.

### 2022-08-26 paper/appendices.tex
Edited paper

@@
 Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
-For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI (this is the short axis mode, to use the vocabulary of Ref.~\cite{kaasalainen2001interpretation}).
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI (this is the short axis mode, to use the vocabulary of \cite{kaasalainen2001interpretation}).
 In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
@@
 \end{equation}
-These spherical harmonics obey many useful identities summarized in Ref.~\cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
+These spherical harmonics obey many useful identities summarized in \cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
 They were used to define the density moments in equation \ref{eqn:klm}, which can be extended to the central body:
@@
 
-Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \citep{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
 A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.
@@
 All vectors here are written in the inertial frame.
-Given $|\bm{R}| < |\bm{R'}|$, Ref.~\cite{Gelderen1998TheSO} gives the identity
+Given $|\bm{R}| < |\bm{R'}|$, \cite{Gelderen1998TheSO} gives the identity
 \begin{equation}
@@
 \end{equation}  
-provided by Ref.~\cite{Gelderen1998TheSO}, and from $\bm U$ to $\bm u$ is given by
+provided by \cite{Gelderen1998TheSO}, and from $\bm U$ to $\bm u$ is given by
 \begin{equation}
@@
 To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets.
-We then scale the moment uncertainties attained from the angular velocity data set so that the mean uncertainty of its parameters is equal to that of the orientation data set.
-This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same average precision as the observational data set.
+We then scale the moment uncertainties attained from the angular velocity data set so that the average $\sigma(K_{\ell m})$ value is equal to that of the orientation data set.
+This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set.
 The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc} relative to the true values.
@@
 A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
-However, this has little effect on the density distributions extracted by the finite element model (not shown); the average density uncertainty $\sigma_\rho / \rho$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
+However, this has little effect on the density distributions extracted by the finite element model (not shown); the average density uncertainty $\langle \sigma_\rho / \rho \rangle$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
 

### 2022-08-26 paper/main.tex
Edited paper

@@
 We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
-We find that high precision in rotational period estimates (order of fifty milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
+We find that high precision in rotational period estimates ($\lesssim 50$ milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
 \end{abstract}
@@
 Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
-With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, manually chosen to limit integration error to only \~100 times the floating point numerical error.
+With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, manually chosen to limit integration error to only $\sim 100$ times the floating point numerical error.
 
@@
 Generally, only one local minimum existed, except when $K_{22}=0$ in which case rotational symmetry caused all values of $\gamma_0$ to be degenerate.
-Ensemble walkers were initialized near the local minimum, distributed by a Gaussian approximation of the likelihood, as determined via the Hessian of the likelihood at the minimum.
+Ensemble walkers were initialized near the local minimum, distributed by a Gaussian approximation of the likelihood as determined via the Hessian of the likelihood at the minimum.
 Due to the high sensitivity of the angular velocity data to density moments, the minimization procedure sometimes failed to isolate the minimum likelihood.
@@
 We assume that the asteroid's surface is known in the inertial frame from radar data.
-Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is extracted in the inertial frame.
+Since the asteroid tumbles during the encounter, we also assume that the center of mass of the asteroid is known in the inertial frame.
 The density moments are extracted from flyby data, but these are known instead in the body-fixed frame.
@@
 To compare the asteroid surface and extracted density moments in the same coordinate system, we define a new frame called the ``hybrid frame.'' The hybrid frame is co-located with the body-fixed frame, but its orientation is known with respect to the inertial frame; it has $\bm \Omega_0 \parallel \unit z_\text{hybrid}$ with third Euler angle $\gamma = 0$.
-The hybrid frame differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
+The hybrid frame initially differs from the body-fixed frame only by a rotation around $\unit z_\text{hybrid}=\unit z_\text{body-fixed}$ of $\gamma_0$.
 Such rotations affect density moments via
@@
 These constrained densities are easily computed since the asteroid mass $\mu_\mathcal{A}$ and the product $I_\mathcal{A}K_{\ell m}$ are both linear functions of $\rho_i$.
-Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and $K_{\ell m} = 0$ implies that $I_\mathcal{A}K_{\ell m} = 0$, $I_\mathcal{A} K_{\ell m}$ is known for all the fixed moments, and computing the corresponding constrained densities is simply a matrix inversion.
+Because $I_\mathcal{A}K_{00} = a_\mathcal{A}^2\mu_\mathcal{A}$ by definition (which is known), and the other fixed moments are zero, $I_\mathcal{A} K_{\ell m}$ is known for all the fixed moments, and computing the corresponding constrained densities is simply a matrix inversion.
 The size and location of each finite element must be chosen before extracting its density.
@@
 
-The translation rules of spherical harmonics \citep{Gelderen1998TheSO} give that the density moments in the hybrid frame are
+The translation rules of spherical harmonics \citep{Gelderen1998TheSO} give that the asteroid density moments in the hybrid frame are
 \begin{equation}
@@
 \end{equation}
-Additional constraints can be imposed on $K_{\ell m}^{(i)}$ if desired.
+Additional assumptions can be imposed on $K_{\ell m}^{(i)}$.
 For example, we can require that the lumps be ellipsoids, so that $K_{3 m}^{(i)} = 0$.
@@
 Once the parameters of the density distribution models have been extracted, each MCMC sample corresponds to its own density distribution.
-To generate an average distribution, we randomly choose 1,000 of these samples and define the density distribution $\rho$ at each point to be the mean of the densities at that point across the 1,000 samples, and take the standard deviation of the sample densities as the density uncertainty $\sigma_\rho$.
+To generate an average distribution, we randomly choose 1,000 of these samples and define the density distribution $\rho$ at each point to be the mean of the densities at that point across the 1,000 samples, and take the standard deviation of the sample densities as the (uncorrelated) density uncertainty $\sigma_\rho$.
 In the case of the finite element model, we run the MCMC twenty times and select 1,000 parameter samples from each to reduce dependence on the initial choice of finite element locations.
@@
 The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
-The second case and its reflection are called the asymmetric cases.
-Values of $(0.052, -0.202)$ have $a < b$ in the ellipsoid model, and the reflected value has $a > b$.
-Specifically, the asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
+The second case is called the asymmetric case.
+The asymmetric case has $a=1140$ m, $b=1839$ m, and $c=565$ m, while the symmetric case has $a=b=1411$ m and $c=1008$ m.
 \end{enumerate}
@@
 In the following sections, we first introduce the retrieval capabilities regarding density moments, then we turn to an example of a retrieval of the density distribution from the moments.
-For both stages of information retrieval, we find that the results are consistent with the properties used to generate the synthetic data.
+For both stages of information retrieval, we find that the results are consistent with the synthetic data and the true asteroid interior.
 
@@
   \includegraphics[width=\linewidth]{figs/example-residuals.pdf}
-  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for an asymmetric reference asteroid.
+  \caption{Data, best-fitting results, and residuals for a fit to synthetic data simulated for the asymmetric reference asteroid.
 Uncertainty bands are also shown.
@@
 Figure \ref{fig:example-corner} shows a corner plot of the PPDs of the ten parameters (namely $\gamma_0$ and $K_{\ell m}$ for $\ell \leq 3$), marginalized to functions of one (histograms) or two (contours) variables.
-The true parameters are shown and usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the posterior $K_{\ell m}$ and the true $K_{\ell m}$.
+The true parameters are shown and usually lie within 1 or 2$\sigma$ of the $\Delta K_{\ell m} = 0$, where $\Delta K_{\ell m}$ is the difference between the mean posterior $K_{\ell m}$ and the true $K_{\ell m}$.
 The PPDs are generally Gaussian and sometimes show strong correlation between parameters, but no continuous degeneracy occurs.
@@
 To provide an example of a density distribution extraction, we consider an asteroid with a core and ask whether our methodology can resolve the location, mass, and size of the core.
-Specifically, we use a spherical core of radius 300 m, placed 500 m from the center and with density 50\% greater that of the surrounding asteroid.
+Specifically, we use a spherical core of radius 300 m, placed 500 m from the center and with density 50\% greater than that of the surrounding asteroid.
 We use the lumpy model to extract a distribution in this section because it is designed to look for cores.
@@
 Synthetic data was generated for the new asteroid and moments were extracted via the process described above.
-These moments were consistent with the true moments, with a $\chi^2$ per DOF of $\chi^2_r = 1.1$, and inconsistent with the moments of a nearly-uniform asteroid of the same shape ($\chi^2_r = 2.7 \times 10^8$).
+These moments were again consistent with the true moments, with a $\chi^2$ per DOF of $\chi^2_r = 1.1$, and inconsistent with the moments of a nearly-uniform asteroid of the same shape ($\chi^2_r = 2.7 \times 10^8$).
 The inconsistency comes almost entirely from the MOI-constraining $K_{2m}$ moments, which are sensitive to large mass distribution changes such as the presence of a core.
@@
   \includegraphics[width=0.49\linewidth]{figs/side-by-side-u}
-  \caption{The extracted distribution (\textit{left}) and true distribution (\textit{right}) of the asymmetric reference asteroid.
+  \caption{Cross-sectional slices of the extracted distribution (\textit{left}) and true distribution (\textit{right}) of the asymmetric reference asteroid.
 The density distribution was created via the lumpy model.
@@
 Despite the low uncertainty, the density distribution is still consistent with the truth, with $\chi^2_r = 1.46$ using uncertainties calculated via section \ref{sec:density-uncertainty-model}.
-The number of asteroid points at which this uncertainty was calculated was about 6 million, making $\chi^2_r = 1.46$ actually quite high, due to the fact that our density uncertainty model does not take the correlation between density at different points into account.
+The number of asteroid points at which the $\chi^2$ was evaluated was about 6 million, making $\chi^2_r = 1.46$ actually quite high.
+This is due to the fact that our density uncertainty model does not take the correlation between density at different points into account.
 By comparison, the difference between the extracted distribution and a nearly-uniform distribution is $\chi^2_r = 6.4 \times 10^{6}$.
-The lumpy model's successful identification of a core is thus very statistically significant.
+The lumpy model's successful identification of a core is thus statistically significant.
 
@@
 
-To study the output of the density distributions, we start with executing them on synthetic data generated for the two reference asteroids.
-The result is shown in figure \ref{fig:den-uniform} displays density distributions and uncertainties.
+To study the output of the density distribution models, we begin by executing them on synthetic data generated for the two reference asteroids.
+The resulting density distributions and uncertainties are shown in figure \ref{fig:den-uniform}.
 These distributions are consistent with the moments extracted by the MCMC in section \ref{sec:fit} --- indeed all the distributions we show have moments consistent with the data, even for non-ellipsoidal asteroids (not shown).
@@
 As remarked before, the lumpy model fit is successful.
-However, the finite element model does not reproduce the core.The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
+However, the finite element model does not reproduce the core.
+The deviation from the true density extends to as much as 17\% in some locations, leading to a maximum significance of $0.52\sigma$.
 Visually the finite element model has spread the high-density core into the rest of the asteroid.
@@
 The position of the lump was therefore observed up to one free parameter: the lump's mass.
-In the centred core case, the core mass does not affect the asteroid center of mass so it is unconstrained, leading to large uncertainty.
+In the centred core case, the core mass does not affect the asteroid center of mass so the mass is unconstrained and uncertain.
 The underlying assumption that the asteroid's center of mass is so precisely known stems from the fact that the shape of the asteroid is observed to rotate around its center of mass.
@@
 The vertical black dotted lines are the property values of the reference asteroid.
-The figures illustrate the marked difference in density distributions that results from using different models.}
+Perigee, rotational period, and observational uncertainty most strongly affect density uncertainty.}
   \label{fig:net-uncertainty}
@@
 We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
-For the most part, we consider the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
+We focus on the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
 
 Figure \ref{fig:net-uncertainty} reveals that the most limiting physical properties of the asteroid are its perigee and period.
-Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only important for $a_\mathcal{A}\sim $tens of meters.
+Excess velocity does not greatly affect the uncertainty of the density distribution, and asteroid length is only important for $a_\mathcal{A}\sim$ tens of meters.
 By contrast, the radius of Apophis is  $\sim 300$ m and its perigee and rotational period also obey the strong constraints \citep{giorgini2008predicting}.
@@
 Short cadence appears preferable, though as much as 20--40 min between observations is still not as detrimental to data quality as other properties.
-Likewise gaps appearing with size $T_\text{gap}$, even hours in length, do not greatly increase density uncertainty.
+Likewise, gaps appearing with size $T_\text{gap}$, even hours in length, do not greatly increase density uncertainty.
 
-To quantify the information contained in \ref{fig:net-uncertainty}, we define a ``threshold'' on each encounter property beyond which we say the data quality is too low to extract meaningful information concerning the density distribution of the asteroid.
-The value of this threshold for perigee is set at the point when the finite element model produces $\langle \sigma_\rho / \rho \rangle = 30\%$, since this is about the maximum uncertainty that the lumpy model can produce.
-We cannot use this process to define the threshold for the other properties because the finite element model does not depend strongly enough on other properties, so we instead transfer the threshold definition to the value of $\langle \sigma_\rho / \rho \rangle$ produced by the lumpy model at that perigee ($5\times 10^{-4}$).
+To summarize the information contained in \ref{fig:net-uncertainty}, we define a ``threshold'' on each encounter property beyond which we say the data quality is too low to extract meaningful information concerning the density distribution of the asteroid.
+The value of this threshold for perigee is set at the point when the finite element model produces $\langle \sigma_\rho / \rho \rangle = 30\%$, since this is just under the maximum uncertainty that the lumpy model produces.
+We cannot use this process to define the threshold for the other properties because the finite element model does not depend strongly enough on other properties, so we instead transfer the threshold definition to the value of $\langle \sigma_\rho / \rho \rangle$ produced by the lumpy model at that perigee value ($\langle \sigma_\rho / \rho \rangle = 5\times 10^{-4}$).
 This threshold is marked as a horizontal red line in figure \ref{fig:net-uncertainty}, and the values at which the encounter parameters exceed the threshold are shown in table \ref{tab:threshold-summary}.
@@
 
-To address the dependence of $\langle \sigma_\rho / \rho \rangle$ on the choice of model, we also investigate the model-independent moment uncertainty $\sigma(K_{\ell m})$ as well, defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD for each $\ell$ and $m$.
+To address the dependence of $\langle \sigma_\rho / \rho \rangle$ on the choice of model, we also investigate the model-independent moment uncertainty $\sigma(K_{\ell m})$ as well, defined as the range of $K_{\ell m}$ values that contains 68.27\% of the marginal PPD.
 Since there is no degeneracy between moments and the actual encounter data, $\sigma(K_{\ell m})$ is well-defined and less noise-prone than $\langle \sigma_\rho / \rho \rangle$, though its physical relevance is not as obvious.
@@
 The change in encounter timing also adjusts the orientation of the asteroid at perigee, which has a separate effect on moment uncertainty.
-We control for this undesired orientation dependence by adjusting $\gamma_0$ so that, if no tidal torque is present, the orientation of the asteroid at perigee is constant for all orbits.
-The effect of tidal torque then causes orientations to be roughly the same at perigee where tidal torque is highest.
-This effectively removes the orientation-induced uncertainty.
+We correct this undesired orientation dependence by adjusting $\gamma_0$ so that $\gamma$ is roughly the same value at perigee (where torque is highest) for all points in the data set.
 
-\subsubsection{Rotational period}
+\subsubsection{Initial angular velocity}
 \label{sec:scan-period}
 
-In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of rotational period $P_\omega$.
+In figure \ref{fig:scan-period}, we show $\sigma(K_{\ell m})$ as a function of initial rotational period $P_\omega$.
 As in the above section, the value of $\gamma_0$ was corrected to ensure roughly constant orientation at perigee.
@@
 
-\subsubsection{Initial spin pole}
-\label{sec:scan-spin}
-
-The tidal torque experienced by the asteroid is affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+The tidal torque experienced by the asteroid is also affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
 
@@
 Figure \ref{fig:scan-spin} shows increased moment uncertainty for initial spin pole $\bm \Omega_0 \parallel \unit Z$, just as \ref{fig:spin-uncertainty} shows increased density distribution uncertainty.
-Many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \pm \unit Y$.
+Many other moments also exhibit increased uncertainty for $\bm \Omega_0 \parallel \unit Y$.
 This pattern is explained by the tidal torque equation (equation \ref{eqn:tidal-torque}).
 By plugging in values for the Euler angles, $\bm z \parallel \unit Z$ and $\bm z \parallel \unit Y$ at perigee lead to $\bm \tau \propto K_{22} \unit z$ to first-order, and $\bm \tau \parallel \unit X$ at perigee leads to $\bm \tau = 0$ to first-order.
-$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction.
-In the case of $\bm \Omega_0 \parallel \unit Z$, we therefore expect $\bm \Omega \parallel \unit Z$ throughout the encounter so that the asteroid does not tumble after the flyby.
-As discussed in the main text, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling results in greater uncertainty.
+$\bm \tau \parallel \unit z$ implies that only the period of the asteroid is changed, not its spin pole direction, implying that the asteroid tumbles less after the flyby.
+As discussed above, tumbling allows precise constraints on $K_{2m}$, so that reduced tumbling results in greater uncertainty.
 
-We may understand the case of $\bm \Omega_0 \parallel \unit Y$ by the approximation that $\bm \tau$ is small until perigee, so that the direction of $\bm \Omega$ is unchanged.
-Insofar as this assumption is accurate, the behaviour of $\bm \Omega_0 \parallel \unit Y$ will be similar to that of $\bm \Omega_0 \parallel \unit Z$, explaining the increased moment uncertainty in this region.
-This argument breaks down for $\bm \Omega_0 \parallel \unit X$, because here $\bm \tau = 0$, and torque is dominated by non-perigee effects.
-This may explain why there is no increased uncertainty near $\bm \Omega \parallel \unit X$.
+Since $\Omega_0 \parallel \unit z$ at the start of the simulation, high uncertainty for $\unit z \parallel \unit Y$ at perigee means high uncertainty for $\bm \Omega_0 \parallel \unit Y$ assuming that the perigee torque effects are dominant.
+Since $\bm \tau = 0$ at perigee for $\unit z \parallel \unit X$, the encounter may be dominated by non-perigee effects in that case.
+This may explain the increased uncertainty for $\bm \Omega_0 \parallel \unit Z$ and $\unit Y$ but not $\unit X$.
 
@@
 This dependence is displayed in figure \ref{fig:scan-theta}.
-Moment uncertainty ($\sigma(K_{\ell m})$) grows linearly with observational uncertainty ($\sigma_\theta$ or $\sigma_P$).
+Moment uncertainty $\sigma(K_{\ell m})$ grows linearly with observational uncertainty ($\sigma_\theta$ or $\sigma_P$).
 
@@
 
-\subsubsection{Cadence}
+\subsubsection{Cadence and data gaps}
 \label{sec:scan-cadence}
@@
 
-\subsubsection{Data gaps}
-\label{sec:scan-gap}
 In certain circumstances, spin data might not be able to be captured for a close encounter at perigee.
@@
 
-Moment uncertainty does depend on the asteroid length, which sets not MOI ratios but the MOI itself, as shown in figure  \ref{fig:scan-physical}.
-This dependence is relatively simple; high-order moments are damped by factors of $a_{\mathcal{A}} / D$, so that reducing asteroid size without reducing perigee yields poor constraints on $K_{3m}$
+Moment uncertainty does depend on the asteroid length, which sets the MOI itself, as shown in figure  \ref{fig:scan-physical}.
+This dependence is relatively simple; moments are damped by factors of $a_{\mathcal{A}} / D$, so that reducing asteroid size without reducing perigee yields poor constraints on $K_{3m}$
 
@@
 We measured the moment uncertainty as a function of $\gamma_0$ for the asymmetric reference asteroid, keeping all other parameters constant.
-Moment uncertainties generally varied by factors of two or less, exhibiting roughly sinusoidal behaviour.
-The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape.
+Moment uncertainties generally varied by factors of two or less.
+The details of this dependence are strongly dependent on the initial spin pole and the asteroid shape, so the data are not shown.
 
@@
 The next order of tidal torque is therefore $J_{4m}$, damped by an additional $(a_\mathcal{B}/D)^2$ factor, and non-ellipsoid corrections to the central body shape.
-We do not consider these extra factors.
+We do not consider these extra terms.
 
@@
 $J_{20}$ has a slightly more general definition than oblateness.
-If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:jlm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
+If the planet has a moon, the integral defining $J_{20}$ (equation \ref{eqn:klm}) can be extended to include this extra mass, though this can only be done when the asteroid never passes inside the moon's orbit.
 As an order-of-magnitude estimate for this effect, two spherical objects with masses and radii of Earth and the Moon, separated by one Lunar distance, and both lying in the orbital plane has a combined oblateness of $\epsilon = 0.82$.
@@
 These uncertainty ratios can be understood as follows.
-The leading order of tidal torque is proportional to $\mu_\mathcal{A} / D^3$.
-If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant as in this case, then $\mu_\mathcal{A} / D^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
+The leading order of tidal torque is proportional to $\mu_\mathcal{B} / D^3$.
+If $D/a_\mathcal{B}$ (the ratio of the encounter distance to the central body radius) is roughly constant as in this case, then $\mu_\mathcal{B} / D^3 \propto \mu_\mathcal{B} / a_\mathcal{B}^3 \propto \rho_\mathcal{B}$ where $\rho_\mathcal{B}$ is the density of the central body.
 Therefore, tidal torque is not increased around massive planets when we keep $r_p \propto a_\mathcal{B}$.
@@
 
-We develop and demonstrate a pipeline which precisely constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
+We develop and demonstrate a pipeline which constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
 We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 10$ Earth radii and the period be $\gtrsim 3.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
+Asteroids that tumble strongly after the encounter are also better constrained by our methodology.
 Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.
@@
 
-We also find that these inferences can be dominated by model uncertainties which occur when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
-Models which are specialized to fit for certain features (such as the lumpy model) can produce less uncertain results than generalized models (such as the finite element model).
+We also find that the exact density distributions inferred are model-dependent, and their uncertainties can be dominated by model uncertainties when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
+Models which are specialized to fit for certain features (such as the lumpy model) produce less uncertain results than generalized models (such as the finite element model).
 To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
@@
 We warmly thank Emmanuel Jehin, Maxime Devogele, and Marin Ferrais for meeting with the authors to discuss this work and pointing out possible future initiatives.
-We also thank the anonymous reviewer for their careful reading of our paper.
+We also thank the anonymous reviewer for their careful reading of our paper and their comments.
 JTD thanks the MIT UROP office for funding his work.

### 2022-08-26 paper/main.tex
Started supplemental material

@@
 \usepackage{amssymb}
-\usepackage{xcolor}
+% \usepackage{xcolor}
 \usepackage{tikz}
-\usepackage{colortbl}
-\usepackage{dsfont}
-\usepackage{siunitx}
 \usepackage{bm}
 \usepackage{caption}
-\usepackage{subcaption}
+% \usepackage{subcaption}
 \usepackage{graphbox}
@@
 
-\renewcommand{\unit}[1]{\bm{\hat{#1}}}
+\newcommand{\unit}[1]{\bm{\hat{#1}}}
 \newcommand{\parens}[1]{\left( #1 \right)}
@@
 From left to right, the densities (divided by the average density), deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in the Supplemental Data.
+These figures are available in animated form in the Supplementary Material.
 Extracted densities are generally within 10\% of the truth.}
@@
 
-The asteroid simulation, fit process, and density moment extraction code are available on \href{https://github.com/jack-dinsmore/asteroid-tidal-torque}{GitHub}. Please contact JTD with questions.
+The asteroid simulation, fit process, and density moment extraction code are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/asteroid-interior-constraints}}.
+Please contact JTD with questions.
 

### 2022-08-26 paper/supplement.tex
Started supplemental material

--- 2022-08-26 paper/appendices.tex
@@
-\appendix
+\documentclass[9pt,twocolumn]{article}
+
+\usepackage[T1]{fontenc}
+
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{extsizes}
+\usepackage{tikz}
+\usepackage{titlesec}
+\usepackage{bm}
+\usepackage[font=small,labelfont=bf]{caption}
+\usepackage{graphbox}
+\usepackage{authblk}
+\usepackage[backend=bibtex, style=authoryear]{biblatex}
+\usepackage[top=0.75in,bottom=0.75in,left=0.6in,right=0.6in]{geometry}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+\usetikzlibrary{arrows.meta}
+
+\newcommand{\unit}[1]{\bm{\hat{#1}}}
+\newcommand{\parens}[1]{\left( #1 \right)}
+\newcommand{\brackets}[1]{\left[ #1 \right]}
+\newcommand{\quat}[1]{\widetilde{\bm{#1}}}
+\setlength{\columnsep}{2em}
+\renewcommand\floatpagefraction{.55}
+
+\titleformat{\section}
+  {\normalsize\bfseries}
+  {\thesection}
+  {.5em}
+  {\MakeUppercase}
+\titleformat*{\subsection}{\normalsize\bfseries}
+
+\title{Constraining the Interiors of Asteroids Through Close Encounters: Appendices}
+
+\author[1]{Jack T. Dinsmore}
+\author[2]{Julien de Wit}
+\affil[1]{Department of Physics, Massachusetts Institute of Technology}
+\affil[2]{Department of Earth, Atmospheric, and Planetary Science, Massachusetts Institute of Technology}
+
+\bibliography{asteroids}
+
+\begin{document}
+
+\maketitle
 
@@
 One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass.
-$\unit{X}$ points from the central body to the asteroid periapse, and $\unit{Z}$ points parallel to the orbit angular momentum.
+$\unit{X}$ points from the central body to the asteroid perigee, and $\unit{Z}$ points parallel to the orbit angular momentum.
 We assume that the mass distribution of the central body is known in this inertial frame.
@@
   \centering
+  \small
   \begin{tabular}{c|ccccccc}
@@
 
-Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \citep{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
 A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.
@@
 This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
+
+\printbibliography
+
+\end{document}

### 2022-08-26 paper/main.tex
Added AIME

@@
 \usepackage{amssymb}
-% \usepackage{xcolor}
 \usepackage{tikz}
@@
 \usepackage{caption}
-% \usepackage{subcaption}
 \usepackage{graphbox}
@@
 We derive the equations of motion for a rigid asteroid's orientation and angular velocity to arbitrary order and use them to generate synthetic angular velocity data for a representative asteroid on a close Earth encounter.
-Using Markov Chain Monte Carlo fits, we perform injection-retrieval tests on these synthetic data to gain insights into the extent to which interior properties can be constrained.
-We also perform a sensitivity analysis of such an inversion technique to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and mapping models to convert constraints on the density moments to density distributions.
+We develop a toolkit AIME (Asteroid Interior Mapping from Encounters) which reconstructs asteroid density distribution from these data, and we perform injection-retrieval tests on these synthetic data to assess AIME's accuracy and precision.
+We also perform a sensitivity analysis to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and the mapping models used.
 We find that high precision in rotational period estimates ($\lesssim 50$ milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
@@
 
-We built a publicly accessible, custom simulation in C++ of an asteroid's rotational state during a close encounter with a central body.
+We built a simulation of an asteroid's rotational state during a close encounter with a central body.
 This simulation requires as initial data (1) the orbital parameters of the asteroid $r_p$ (perigee distance) and $v_\infty$ (hyperbolic excess velocity); (2) the cadence of angular velocity observation $\Delta t$; (3) the central body moments $J_{\ell m}$, mass $\mu_\mathcal{B}$, and radius $a_\mathcal{B}$; (4) the initial asteroid angular velocity in the inertial frame $\bm \Omega_0$; (5) the asteroid length $a_\mathcal{A}$ and (6) the asteroid's density moments $K_{\ell m}$ and initial Euler angle $\gamma_0$.
@@
 
-To demonstrate our interior-probing methodology, we provide a full density distribution retrieval applied to synthetic data for two ``reference asteroids,'' which correspond to the following encounter parameter choices.
+The techniques described above were implemented in a publicly available toolset called AIME (Asteroid Interior Mapping from Encounters).
+To demonstrate, we provide a full density distribution retrieval applied to synthetic data for two ``reference asteroids,'' which correspond to the following encounter parameter choices.
 
@@
 
-To provide an example of a density distribution extraction, we consider an asteroid with a core and ask whether our methodology can resolve the location, mass, and size of the core.
+To provide an example of a density distribution extraction, we consider an asteroid with a core and ask whether AIME can resolve the location, mass, and size of the core.
 Specifically, we use a spherical core of radius 300 m, placed 500 m from the center and with density 50\% greater than that of the surrounding asteroid.
@@
 
-Given this understanding of our density extraction models, we answer the important questions of which encounters can be successfully studied by this methodology, and how observational campaigns can be designed to best take advantage of an encounter.
-To quantify the methodology's success, we use the median of a density uncertainty distribution $\langle \sigma_\rho / \rho \rangle$ in section \ref{sec:density-uncertainty}.
+Given this understanding of our density extraction models, we answer the important questions of which encounters can be successfully studied using AIME, and how observational campaigns can be designed to best take advantage of an encounter.
+To quantify AIME's success, we use the median of a density uncertainty distribution $\langle \sigma_\rho / \rho \rangle$ in section \ref{sec:density-uncertainty}.
 But since this median is so model-dependent, we also analyze the success of the method via the density moment uncertainty $\sigma (K_{\ell m})$ (which is not moment dependent) in section \ref{sec:moment-uncertainty}.
-In section \ref{sec:central-body}, we study the methodology's dependence on the properties of the central body.
+In section \ref{sec:central-body}, we study AIME's dependence on the properties of the central body.
 
@@
 Indeed, figure \ref{fig:scan-observational} shows that $K_{3m}$ especially are more uncertain for $T_\text{gap} \gtrsim 1.5$ hr.
-However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the threshold, indicating that large amounts of data can be cut without compromising the methodology.
+However, figure \ref{fig:net-uncertainty} shows that $T_\text{gap}$ never increases density uncertainty above the threshold, indicating that large amounts of data can be cut without compromising AIME.
 As with the threshold for cadence discussed above, this 1.5 hr cut-off may depend on the asteroid rotational period or the orbital time scales.
@@
 
-Aside from oblateness, central body mass may also affect the success of this methodology.
+Aside from oblateness, central body mass may also affect the success of AIME.
 To address this possibility, we run our reference asteroid through a Jupiter encounter to analyze the differences in moment uncertainty $\sigma(K_{\ell m})$ compared to an Earth encounter.
@@
 
-We develop and demonstrate a pipeline which constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
+We develop and demonstrate a methodology, AIME, which constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
 We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 10$ Earth radii and the period be $\gtrsim 3.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
-Asteroids that tumble strongly after the encounter are also better constrained by our methodology.
+Asteroids that tumble strongly after the encounter are also better constrained by AIME.
 Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.
@@
 
-In order to further take advantage of close asteroid encounters, improvements to our pipeline may lead to increased precision of the output.
+In order to further take advantage of close asteroid encounters, improvements to AIME may lead to increased precision of the output.
 Specifically, the angular velocity data set may be lengthened to include more post-encounter data, correlations between observational uncertainties could be incorporated into the uncertainty model, and previous knowledge of some of the asteroid properties (such as moment of inertia) could be used to adjust priors on the density moments.
-The presence of Earth's moon or pre-encounter tumbling of the asteroid may also increase the precision of our pipeline's density distribution estimates.
+The presence of Earth's moon or pre-encounter tumbling of the asteroid may also increase the precision of AIME's density distribution estimates.
 
@@
 
-The asteroid simulation, fit process, and density moment extraction code are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/asteroid-interior-constraints}}.
+All the code used in this paper --- namely, AIME --- are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/aime}}.
+The data showcased here was generated from that code.
 Please contact JTD with questions.

### 2022-08-26 paper/arxiv/appendices.tex
Updated mnras version

--- 2022-08-26 paper/appendices.tex
@@
 
-\section{Comparing orientation and angular velocity data}
+\section{Comparing orientation \& angular velocity data}
 \label{app:orientation}

### 2022-08-26 paper/arxiv/main.tex
Updated mnras version

--- 2022-08-26 paper/main.tex
@@
 
-%% Julien asks that I use mean and max values in each plot instead of chisq.
-
 \subsection{Density distribution retrieval}
@@
 Uncertainty in the distribution is shown below.
-The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth.}
+The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth.
+These figures are available in animated form in the Supplementary Material.}
   \label{fig:den-side-by-side}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in the Supplemental Data.
+These figures are available in animated form in the Supplementary Material.
 The lumpy model successfully extracts the core.}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in the Supplemental Data.
+These figures are available in animated form in the Supplementary Material.
 The resulting density distribution is consistent with the density moments but does not represent the true distribution due to degeneracy.}
@@
 From left to right, the densities, deviations from the true density, uncertainties, and significance of the deviations are plotted.
-These figures are available in animated form in the Supplemental Data.
+These figures are available in animated form in the Supplementary Material.
 The additional lump greatly increases uncertainty, but the resulting distribution is close to accurate.}
@@
 
-All the code used in this paper --- namely, AIME --- are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/aime}}.
+All the code used in this paper --- namely, AIME --- are available on GitHub\footnote{\url{https://github.com/disruptiveplanets/AIME}}.
 The data showcased here was generated from that code.
@@
 
-\input{appendices}
+% \input{appendices}
 

### 2022-10-14 paper/arxiv/main.tex
Updated paper references

@@
 
-\date{Accepted XXX. Received YYY; in original form ZZZ}
+\date{Accepted 2022 September 26. Received 2022 August 29; in original form 2022 July 5}
 
@@
 We also perform a sensitivity analysis to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and the mapping models used.
-We find that high precision in rotational period estimates ($\lesssim 50$ milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
+We find that high precision in rotational period estimates ($\lesssim 0.27$ seconds) are necessary for each cadence, and that low perigees ($\lesssim 18$ Earth radii) are necessary to resolve large-scale density non-uniformities to uncertainties $\sim 0.1\%$ of the local density under some models.
 \end{abstract}
@@
 However, by making sufficient assumptions about the density distribution, we can nevertheless measure fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
-To best understand the density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
+To best understand the density distribution of an asteroid, an ensemble of models with differing assumptions is desired so that common traits across the models can be identified.
 To this end, we outline two possible models here and discuss two more in appendix \ref{app:more-models}.
@@
 Synthetic data was generated for the new asteroid and moments were extracted via the process described above.
-These moments were again consistent with the true moments, with a $\chi^2$ per DOF of $\chi^2_r = 1.1$, and inconsistent with the moments of a nearly-uniform asteroid of the same shape ($\chi^2_r = 2.7 \times 10^8$).
-The inconsistency comes almost entirely from the MOI-constraining $K_{2m}$ moments, which are sensitive to large mass distribution changes such as the presence of a core.
+The true density moments were within the confidence intervals of the extracted moments.
+A density distribution was then extracted and shown in figure \ref{fig:den-side-by-side} next to the true distribution.
+Visually, the extracted distribution is virtually identical to the true distribution, which is emphasized by the low uncertainties of $\langle \sigma_\rho / \rho \rangle = \mathcal{O}(10^{-3})$ throughout the asteroid.
+Again, the extracted density distribution is consistent with the truth despite the low density uncertainties.
+Both the density moments and the extracted density distribution are inconsistent with a uniform distribution; i.e., the deviation from uniform shown in figure \ref{fig:den-side-by-side} is statistically significant.
 
@@
 
+  \includegraphics[width=0.49\linewidth]{figs/side-by-side-s} \hfill
   \includegraphics[width=0.49\linewidth]{figs/side-by-side-u}
@@
 The density distribution was created via the lumpy model.
-Uncertainty in the distribution is shown below.
+The difference between the extracted and the true distributions and density uncertainty are also shown (\textit{bottom left / right}).
 The extracted distribution is nearly identical to the true distribution and is statistically consistent with the truth.
@@
 \end{figure}
-
-A density distribution was then extracted, shown in figure \ref{fig:den-side-by-side} next to the true distribution.
-Visually, the extracted distribution is virtually identical to the true distribution, which is emphasized by the low uncertainties of $\sigma_\rho / \rho = \mathcal{O}(10^{-3})$ throughout the asteroid.
-Despite the low uncertainty, the density distribution is still consistent with the truth, with $\chi^2_r = 1.46$ using uncertainties calculated via section \ref{sec:density-uncertainty-model}.
-The number of asteroid points at which the $\chi^2$ was evaluated was about 6 million, making $\chi^2_r = 1.46$ actually quite high.
-This is due to the fact that our density uncertainty model does not take the correlation between density at different points into account.
-By comparison, the difference between the extracted distribution and a nearly-uniform distribution is $\chi^2_r = 6.4 \times 10^{6}$.
-The lumpy model's successful identification of a core is thus statistically significant.
 
@@
 Here, we investigate how density uncertainty $\langle \sigma_\rho / \rho \rangle$, extracted by both the finite element and lumpy models, depends on physical asteroid properties (the encounter's orbit, the asteroid's true shape, and its initial rotational velocity) and observational properties (the data uncertainty, the cadence of observations, and gaps in data coverage).
+
+Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
+We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
+We focus on the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
 
@@
 
-Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
-We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
-We focus on the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
-
 Figure \ref{fig:net-uncertainty} reveals that the most limiting physical properties of the asteroid are its perigee and period.
@@
 To summarize the information contained in \ref{fig:net-uncertainty}, we define a ``threshold'' on each encounter property beyond which we say the data quality is too low to extract meaningful information concerning the density distribution of the asteroid.
-The value of this threshold for perigee is set at the point when the finite element model produces $\langle \sigma_\rho / \rho \rangle = 30\%$, since this is just under the maximum uncertainty that the lumpy model produces.
-We cannot use this process to define the threshold for the other properties because the finite element model does not depend strongly enough on other properties, so we instead transfer the threshold definition to the value of $\langle \sigma_\rho / \rho \rangle$ produced by the lumpy model at that perigee value ($\langle \sigma_\rho / \rho \rangle = 5\times 10^{-4}$).
+The value of this threshold is set at the point when the lumpy model produces $\langle \sigma_\rho / \rho \rangle = 0.1\%$, since this is just under the maximum uncertainty that the lumpy model produces.
 This threshold is marked as a horizontal red line in figure \ref{fig:net-uncertainty}, and the values at which the encounter parameters exceed the threshold are shown in table \ref{tab:threshold-summary}.
@@
     Encounter property & Threshold \\ \hline
-    Perigee ($r_p$) & $<10$ Earth radii\\
-    Period ($P_\omega$) & $>3.3$ hr \\ \hline
-    Spin period uncertainty ($\sigma_P$) & $<55$ ms\\
-    Spin pole uncertainty ($\sigma_\theta$) & $< 9.1^\circ$ \\
+    Perigee ($r_p$) & $<18$ Earth radii\\ \hline
+    Spin period uncertainty ($\sigma_P$) & $<0.27$ s\\
+    Spin pole uncertainty ($\sigma_\theta$) & $< 35^\circ$ \\
     \hline
@@
 Table \ref{tab:threshold-summary} is consistent with the conclusions we drew for figure \ref{fig:net-uncertainty}.
-Apophis' 2029 encounter is consistent with the thresholds, and the perigee, period, and observational uncertainties are indeed the most constraining.
-The values of the thresholds are interdependent and may change if the encounter conditions are changed, so they should not be taken to be precise values.
+The physical properties of Apophis' 2029 encounter are consistent with the thresholds, with the perigee and observational uncertainties posing the greatest challenge to successful density distribution extraction.
+The values of these thresholds are interdependent and may change if the encounter conditions are changed, so they should not be taken to be precise values.
 
@@
 We develop and demonstrate a methodology, AIME, which constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
-We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 10$ Earth radii and the period be $\gtrsim 3.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
+We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 18$ Earth radii, though this threshold depends on a number of properties of the asteroid and the observational campaign.
 Asteroids that tumble strongly after the encounter are also better constrained by AIME.
 Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.
-Due to the sensitivity of the system, we find that it is also necessary to correctly model effects that influence the system very little, such as the oblateness of the central body, in order for accurate density distributions to be extracted.
-
-We also find that the exact density distributions inferred are model-dependent, and their uncertainties can be dominated by model uncertainties when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
+Nevertheless, for the reference asteroid and observational campaign used in this paper, we were able to extract large-scale density non-uniformities accurately and precisely, achieving density uncertainties $\sim 0.1\%$ of the density and excluding uniform distributions for non-uniform asteroids.
+
+We also find that the density distributions inferred are model-dependent, and their uncertainties can be dominated by model-driven uncertainties when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
 Models which are specialized to fit for certain features (such as the lumpy model) produce less uncertain results than generalized models (such as the finite element model).
 To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
-
-In order to further take advantage of close asteroid encounters, improvements to AIME may lead to increased precision of the output.
-Specifically, the angular velocity data set may be lengthened to include more post-encounter data, correlations between observational uncertainties could be incorporated into the uncertainty model, and previous knowledge of some of the asteroid properties (such as moment of inertia) could be used to adjust priors on the density moments.
-The presence of Earth's moon or pre-encounter tumbling of the asteroid may also increase the precision of AIME's density distribution estimates.
 
@@
 
-% \input{appendices}
+\appendix
+
+\section{Tidal torque \& Equations of motion}
+\label{app:eom}
+
+In this appendix, we derive the equations of motion used to simulate the asteroid encounter.
+In particular, we describe our coordinates (section \ref{sec:coordinates}) for an encountering asteroid's position and orientation, and we parametrize its density distribution via its density moments (section \ref{sec:moments}).
+Then we derive an arbitrary-order equation for tidal torque (section \ref{sec:tidal-torque}) and write the equations of motion for the system (section \ref{sec:eom}).
+
+\subsection{Coordinates}
+\label{sec:coordinates}
+
+We make use of two frames of reference to model this system.
+One is the ``inertial frame,'' with axes denoted by $\unit{X}$, $\unit{Y}$, $\unit{Z}$ and origin placed at the central body's centre of mass.
+$\unit{X}$ points from the central body to the asteroid perigee, and $\unit{Z}$ points parallel to the orbit angular momentum.
+We assume that the mass distribution of the central body is known in this inertial frame.
+
+Our second frame is the ``body-fixed'' frame, denoted by $\unit{x}, \unit{y}, \unit{z}$.
+Each axis in this frame is aligned with a principal axis and rotates with the asteroid, with its origin at the asteroid's centre of mass.
+For definiteness, we define $\unit{z}$ to be the principal axis with maximal MOI (this is the short axis mode, to use the vocabulary of \cite{kaasalainen2001interpretation}).
+In general, we use capital letters to denote vectors in the inertial frame and lowercase vectors to denote vectors in the body-fixed frame.
+
+The difference between the origins of the body-fixed and inertial frames is the position of the asteroid.
+We represent the relative orientations by $z-y-z$ Euler angles $\alpha$, $\beta$, and $\gamma$, such that a matrix $M$ rotating from the body-fixed to the inertial frame ($M\bm{r} = \bm{R}$) is given by
+\begin{equation}
+M = R_z(\alpha) R_y(\beta) R_z(\gamma).
+\label{eqn:euler-angles}
+\end{equation}
+Here, $R_i(\theta)$ is a rotation around the unit vector $i$ by angle $\theta$ (figure \ref{fig:euler-angles}).
+
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+    \draw[-{Latex[length=3mm]}] (0, 0) -- (-4, 0) node[anchor=east] {$\unit x$};
+    \draw[-{Latex[length=3mm]}] (0, 0) -- (2, -3) node[anchor=west] {$\unit y$};
+    \draw[-{Latex[length=3mm]}] (0, 0) -- (0, 4) node[anchor=south] {$\unit z$};
+    \draw[dashed, -{Latex[length=3mm]}] (0, 0) -- (3.7, -2) node[anchor=north] {};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-0.5, -3) node[anchor=north] {$\unit X$};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (4, 1) node[anchor=south] {$\unit Y$};
+    \draw[line width=0.5mm,-{Latex[length=3mm]}] (0, 0) -- (-1.6, 2.7) node[anchor=south] {$\unit Z$};
+    \draw[->] (0.5, -0.75) arc (290:302:2.5);
+    \draw (0.9, -0.9) node[anchor=center] {$\alpha$};
+    \draw[->] (0, 1.2) arc (130:161:1.3);
+    \draw (-0.3, 1.3) node[anchor=center] {$\beta$};
+    \draw[->] (0.97, -0.52) arc (330:368:1.3);
+    \draw (1.4, -0.25) node[anchor=center] {$\gamma$};
+    \end{tikzpicture}
+    \caption{$z-y-z$ Euler angles used in this work to express the orientation of the asteroid.
+Orientation is expressed as a rotation from the body-fixed axes (lowercase) to the inertial axes (bold lines and uppercase).
+The origins are co-located for demonstration purposes.}
+    \label{fig:euler-angles}
+\end{figure}
+
+\subsection{Density moments}
+\label{sec:moments}
+
+The un-normalized spherical harmonics are defined as $Y_{\ell m}(\theta, \phi) = P_{\ell m}(\cos \theta)e^{im\phi}$, where $P_{\ell m}$ are the associated Legendre Polynomials without the Condon-Shortley phase.
+The regular and irregular spherical harmonics are further defined as
+\begin{equation}
+  \begin{split}
+    S_{\ell m}(\bm r) &= (-1)^m (\ell - m)! \frac{Y_{\ell m}(\unit r)}{r^{\ell+1}} \\
+    R_{\ell m} (\bm r) &= (-1)^m \frac{r^\ell}{(\ell + m)!} Y_{\ell m}(\unit r).
+  \end{split}
+\end{equation}
+These spherical harmonics obey many useful identities summarized in \cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
+They were used to define the density moments in equation \ref{eqn:klm}, which can be extended to the central body:
+\begin{equation}
+  \begin{split}
+    &J_{\ell m} = \frac{a_\mathcal{B}^{2-\ell}}{I_\mathcal{B}} \int_\mathcal{B} d^3 r \rho_\mathcal{B}(\bm r) R_{\ell m}(\bm r)\\
+  \end{split}
+  \label{eqn:jlm}
+\end{equation}
+By contrast, $J_{\ell m}$ should be computed in the inertial frame.
+The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations \ref{eqn:aa} and \ref{eqn:ia}, but they could also be set to any other scales of the same units, e.g.
+$a_\mathcal{B}$ equal to the central body radius and $I_\mathcal{B} = \mu_\mathcal{B}a_\mathcal{B}^2$, where $\mu_\mathcal{B}$ is the central body mass.
+
+Note that both $J_{\ell m}$ and $K_{\ell m}$ are unitless.
+We call them ``moments'' because $R_{\ell m}(\bm r)$ contains an $r^\ell$ dependence so that $K_{\ell m}$ is the $\ell$th density moment of the asteroid.
+
+These moments share several key properties which we discuss before continuing.
+Firstly, for real mass density, properties of the spherical harmonics imply that $K_{\ell m} = (-1)^m K_{\ell, -m}^*$.
+Therefore, the set of $K_{\ell m}$ for $\ell < \ell_\text{max}$ contains $\ell_\text{max}^2$ degrees of freedom.
+However, some of these degrees of freedom are redundant with the choice of coordinates: $K_{1m} = 0$ since the body-fixed frame is centred on the asteroid centre of mass.
+Further calculation reveals that the alignment of the body-fixed frame with the asteroid principal axes also forces $K_{21}= 0$ and $\Im K_{22}=0$.
+The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$, $K_{20}$, and $K_{00}$.
+The first two are related to the MOI around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in equation \ref{eqn:tidal-torque}.
+
+The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the semi-axis lengths and can be compared to those found in equation \ref{eqn:moi}.
+This yields semi-axis lengths of
+\begin{equation}
+  \begin{split}
+  a &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}+12K_{22}}\\
+  b &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1-2K_{20}-12K_{22}}\\
+  c &= \sqrt{\frac{5}{3}}a_\mathcal{A}\sqrt{1+4K_{20}}.
+  \label{eqn:ellipsoid-axes}
+  \end{split}
+\end{equation}
+The higher-order moments $K_{3m}$ can be thought of loosely as measuring the large-scale asymmetries of the asteroid.
+An asteroid that is mirror-symmetric along the $\unit{x}$ axis (meaning $\rho_\mathcal{A}(x,y,z)=\rho_\mathcal{A}(-x,y,z)$) necessarily sets certain density moments to zero.
+Which density moments are zeroed by which mirror symmetries is outlined in table \ref{tab:klm-symmetries}.
+All $K_{3m}$ are zeroed by at least one mirror symmetry.
+
+\begin{table}
+  \centering
+  \begin{tabular}{c|ccccccc}
+    \hline
+    $\ell$ & $\Re K_{\ell 3}$ & $\Im K_{\ell 3}$ & $\Re K_{\ell 2}$ & $\Im K_{\ell 2}$ & $\Re K_{\ell 1}$ & $\Im K_{\ell 1}$ & $K_{\ell 0}$ \\ \hline
+    0 &  &  &  &  &  &  & -\\ 
+    1 &  &  &  &  & x & y & z\\ 
+    2 &  &  & - & x,y & y,z & x,z & -\\ 
+    3 & x,z & y,z & z & x,y,z & x & y & z\\ \hline
+  \end{tabular}
+  \caption{Axes of mirror symmetry that imply zeroed density moments.
+For example, for mirror symmetries along $\unit y$ or $\unit z$, $\Im K_{32}=0$.
+Mirror symmetry along $\unit x$ means $\rho_\mathcal{A}(x, y, z) = \rho_\mathcal{A}(-x, y, z)$.
+Dashes indicate that none of the mirror symmetries zero the moment in question.
+Since $r^2>0$ for $r\neq 0$, no symmetries set $a_\mathcal{A}=0$ either.}
+  \label{tab:klm-symmetries}
+\end{table}
+
+Finally, the requirement that $\rho_\mathcal{A}(\bm r) \geq 0$ everywhere restricts $K_{\ell m}$.
+In the case of $K_{2m}$, this fact and the constraint that $I_z$ is larger than $I_x$ or $I_y$ requires $K_{20}$ and $K_{22}$ to fall in the triangle
+\begin{equation}
+  -\frac{1}{4} \leq K_{20} \leq 0, \qquad |K_{22}| \leq \frac{|K_{20}|}{2}.
+  \label{eqn:parameter-bounds}
+\end{equation}
+An analytical constraint on $K_{3m}$ based on this property is more difficult to derive, but in practice, we observe that $|K_{3m}| < 0.01$.
+
+\subsection{Tidal torque}
+\label{sec:tidal-torque}
+
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \citep{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.
+
+Here, we present a new derivation of the tidal torque to arbitrary orders in terms of the density moments of an asteroid defined in section \ref{sec:moments}.
+These density moments can be pre-computed and do not have to be re-evaluated every time-step.
+
+The gravitational potential energy of the central body is, in its most general form,
+\begin{equation}
+V(\bm R') = -G\int_\mathcal{B} d^3 R \frac{\rho_\mathcal{B}(\bm R)}{|\bm{R}-\bm{R'}|}.
+\label{eqn:first-pe}
+\end{equation}
+where $\rho_\mathcal{B}$ is the density distribution of the central body and $\mathcal{B}$ indicates the central body's volume.
+All vectors here are written in the inertial frame.
+Given $|\bm{R}| < |\bm{R'}|$, \cite{Gelderen1998TheSO} gives the identity
+\begin{equation}
+  \frac{1}{|\bm R - \bm R'|} = \sum_{\ell, m} R_{\ell m}(\bm R) S_{\ell m}^*(\bm R'),
+  \label{eqn:ylm-expansion}
+\end{equation}
+where the sum is shorthand for $\sum_{\ell, m} = \sum_{\ell = 0}^\infty \sum_{m=-\ell}^\ell$.
+
+Incidentally, it is the $|\bm R| < |\bm R'|$ assumption that inspires the assumption that there are ``no \textit{distant} perturbing objects'' (section \ref{sec:methods}).
+If a perturbing object such as a moon is not distant (i.e., it is closer to the system center of mass than the asteroid perigee so that $|\bm R| < |\bm R'|$ always), then it can be absorbed into $J_{\ell m}$ by equation \ref{eqn:jlm} and the assumptions of this derivation are not violated.
+
+We are interested in translating the potential energy of equation \ref{eqn:first-pe} to the body-fixed frame.
+To do this, we let $\bm{R'} = \bm D + \bm U$, where $\bm D$ is the location of the asteroid in the inertial frame.
+We further define $\bm U = M\bm u$, where $\bm u$ is in the body-fixed frame and $M$ is the rotation matrix given by the Euler angles $\alpha$, $\beta$, and $\gamma$ (see section \ref{sec:coordinates}).
+The translation from $\bm {R'}$ to $\bm U$ is then attained by the identity
+\begin{equation}
+  S_{\ell m}(\bm R') = \sum_{\ell', m'} (-1)^{\ell'}R^*_{\ell' m'}(\bm U)S_{\ell+\ell', m + m'} (\bm D),
+  \label{eqn:ylm-translation}
+\end{equation}  
+provided by \cite{Gelderen1998TheSO}, and from $\bm U$ to $\bm u$ is given by
+\begin{equation}
+  \begin{split}
+    Y_{\ell m}(M\bm u) = \sum_{m'=-\ell}^\ell & (-1)^{m+m'}\sqrt{\frac{(\ell-m')!(\ell+m)!}{(\ell+m')!(\ell-m)!}} \\
+    & \times \mathcal{D}^\ell_{mm'}(M)^* Y_{\ell m'}(\bm u).\\
+  \end{split}
+  \label{eqn:ylm-rotation}
+\end{equation}
+Here, $\mathcal{D}^\ell_{mm'}(M)$ are the Wigner-$D$ matrices, which are determined by the Euler angles $\alpha$, $\beta$, and $\gamma$ of $M$.
+
+Equations \ref{eqn:first-pe} to \ref{eqn:ylm-rotation} then provide formula for $V(\bm u)$ expressed as a sum of integrals over $\mathcal{B}$ of the central body density $\rho_\mathcal{B}(\bm R)$ times $R_{\ell m}(\bm R)$.
+These are expressed via equation \ref{eqn:jlm} as $J_{\ell m}$.
+
+The tidal torque experienced by the asteroid (in the body-fixed frame) is given by
+\begin{equation}
+  \bm{\tau}(\bm u) = \int_\mathcal{A} d^3 u \rho_\mathcal{A}(\bm u) (\bm u \times (-\nabla_{\bm u} V(\bm u)))
+\end{equation}
+where $\rho_\mathcal{A}$ is the density distribution of the asteroid and $\mathcal{A}$ indicates the volume of the asteroid.
+Making use of one more identity concerning the derivatives of spherical harmonics:
+\begin{equation}
+  \begin{split}
+  \bm u \times \nabla R_{\ell m}(\bm u)=&\frac{1}{2}\Big[(i\unit x - \unit y)(\ell-m+1)R_{\ell,m-1}(\bm u)\\
+  &+(i\unit x+\unit y)(\ell+m+1)R_{\ell,m+1}(\bm u)\\
+  & +2im\unit z R_{\ell m}(\bm u)\Big],
+  \end{split}
+\end{equation}
+tidal torque can now be expressed as a function only of the constants $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A/B}$, $I_\mathcal{A/B}$, and the asteroid orientation and position (equation \ref{eqn:tidal-torque}).
+Some $K_{\ell m}$ terms are written in this equation with $|m|>\ell$; these should all be taken to be zero.
+
+\subsection{Equations of motion}
+\label{sec:eom}
+
+The equations of motion of the asteroid position $\bm D$ are given by Newton's law of gravitation
+\begin{equation}
+  \dot{\bm V} = -\frac{G \mu_\mathcal{B}}{D^3} \bm D \qquad \dot{\bm D} = \bm V
+  \label{eqn:pos-eom}
+\end{equation}
+where $\bm V$ is the asteroid velocity in the inertial frame.
+Rather than derive equations of motion for the Euler angles (which suffer from gimbal lock), we instead represent the orientation of the asteroid with a quaternion $\quat q$ which can be converted into Euler angles to compute $\mathcal{D}(\alpha, \beta, \gamma)$.
+This quaternion evolves as
+\begin{equation}
+  \dot{\quat q} = \frac{1}{2}\quat q\quat \omega.
+  \label{eqn:quat-eom}
+\end{equation}
+for angular velocity $\bm \omega$ given in the body-fixed frame. The equations of motion of $\bm \omega$ in turn are given by
+\begin{equation}
+  \begin{split}
+    I_x \dot \omega_x - \omega_y \omega_z (I_y - I_z) &= \tau_x\\
+    I_y \dot \omega_y - \omega_z \omega_x (I_z - I_x) &= \tau_y\\
+    I_z \dot \omega_z - \omega_x \omega_y (I_x - I_y) &= \tau_z.
+  \end{split}
+  \label{eqn:omega-eom}
+\end{equation}
+Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, \ref{eqn:pos-eom}, and \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
+They are expressed in terms of the physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$ which are constant if the asteroid is rigid and the central body does not rotate.
+
+\section{Comparing orientation \& angular velocity data}
+\label{app:orientation}
+
+To extract the density distribution of an asteroid, the main text assumes that the angular velocity data of the asteroid is observable.
+It is possible that the orientation of the asteroid may be more readily available as a data set, notably if a large collection of radar antenna fail to follow the encounter sufficiently.
+In this appendix, we generate an orientation data set for the reference asteroid flyby, extract density moments from it, and compare the results to moments extracted from angular velocity data.
+
+\subsection{Uncertainty model}
+To use an asteroid orientation data set rather than angular velocity, we must create an uncertainty model for orientation observations and produce a likelihood to be used by the MCMC (replacing equation \ref{eqn:log-likelihood}).
+
+For the sake of this appendix, we will assume that all observations of orientation $\quat q$ differ from the true orientation $\quat q^*$ by a rotation by some angle $\phi$ around an axis drawn from a uniform distribution on the unit sphere, where $\phi$ is drawn from a normal distribution with mean zero and standard deviation $\sigma_\phi$.
+As in the rest of the paper, orientation is expressed as a quaternion $\quat q = q_r + q_i \bm i + q_j \bm j + q_k \bm k$.
+The angle $\phi$ can be extracted from these quaternion components to yield a likelihood of
+\begin{equation}
+  \ln \mathcal{L} = -\frac{2}{\sigma_\phi^2}\sum_{i}\parens{\cos^{-1}\left|\brackets{\quat q_i (\quat q_i^*)^{-1}}_r\right|}^2
+  \label{eqn:orientation-like}
+\end{equation}
+where a subscript $i$ denotes the $i$th element of the data set. It is assumed that both quaternions have norm one.
+
+\subsection{Moment uncertainty comparison}
+With the likelihood defined, we generate both angular velocity and orientation data for the asymmetric reference asteroid configuration and extract density moment PPDs for both data sets via the fit method defined in the main text.
+Due to the different uncertainty models used for the orientation and angular velocity data sets, this set-up does not allow direct comparison between the amount of moment uncertainty for both data sets.
+(If one data set yields more precise moments than the other, one could not determine whether the effect is due to increased observational precision in the data set or the use of a data type that better constrains density moments.) However, the relative uncertainty of moments can be compared.
+
+To make this comparison, we compute moment uncertainties $\sigma(K_{\ell m})$ for both data sets.
+We then scale the moment uncertainties attained from the angular velocity data set so that the average $\sigma(K_{\ell m})$ value is equal to that of the orientation data set.
+This is equivalent to choosing observational uncertainties for the angular velocity data set which yield density moments to the same precision as the observational data set.
+The resulting PPDs for the density moments of both data sets are displayed in figure \ref{fig:orientation-unc} relative to the true values.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\linewidth]{figs/orientation-unc}
+  \caption{PPDs for each parameter as extracted from angular velocity (blue) and orientation (orange) data.
+First order parameters are shown in the top panel and second-order parameters in the bottom.
+Mean values are also shown as vertical lines.
+Both data sets produce similar constraints on parameters, except in the case of $\gamma_0$.}
+  \label{fig:orientation-unc}
+\end{figure}
+
+The figure demonstrates that using orientation data rather than angular velocity data does not greatly affect the relative uncertainties of density moments, except in the case of $\gamma_0$, which is much more precisely constrained by orientation data than by angular velocity data.
+This result is expected due to the following argument.
+If the initial orientation of the asteroid is known, then the orientation of the next data point can be determined by knowledge of the asteroid's angular velocity at that moment.
+Thus, an orientation data set can be produced from an angular velocity data set and vice versa given an initial asteroid orientation.
+That initial orientation is defined up to $\gamma_0$ by the assumption of no initial tumbling, so we expect the angular velocity data set to yield increased uncertainties in $\gamma_0$ only, relative to the observational data, to a first approximation.
+
+A smaller effect observed in figure \ref{fig:orientation-unc} is that the orientation data set yields similar uncertainties for all density moments of fixed $\ell$, whereas the angular velocity data set tends to yield larger uncertainties for small $|m|$.
+However, this has little effect on the density distributions extracted by the finite element model (not shown); the average density uncertainty $\langle \sigma_\rho / \rho \rangle$ are essentially equivalent between the two data sets, as is the extracted distribution of density and density uncertainty.
+
+\section{Additional density distribution models}
+\label{app:more-models}
+
+Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
+Here we outline two additional models which are less conventional but still useable for extracting density distribution properties.
+Unlike the finite element and lumpy models discussed in the main text, these models will yield smooth distributions with no discrete transitions.
+
+\subsection{Nearly-uniform model}
+In this ``nearly-uniform'' model, we pick one density distribution from the many distributions consistent with the data by maximizing a prior distribution $f[\rho(\bm r)]$.
+Any prior distribution can be chosen, but the following prior is both interesting and numerically efficient.
+
+As part of our prior, we require that the asteroid density distribution satisfy $I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2$.
+This constraint is desirable as it is obeyed for uniform density distributions.
+To define the prior, we divide the asteroid into $n \gg 1$ small regions of volume $V$, each with position $\bm r_i$ and density $\rho_i = \delta_i + 1$.
+Setting the mass of the asteroid equal to its volume, the average density is 1, so $\delta_i$ is the difference between the average and local density.
+We set $f[\rho(\bm r)]$ to be a multivariate-Gaussian distribution on $\delta_i$, centred on zero to minimize non-uniformity, i.e.
+\begin{equation}
+  f[\rho(\bm r)] \propto \prod_i \exp\parens{-\frac{\delta_i^2}{2\sigma^2}} \implies \ln f[\rho(\bm r)] \simeq -\sum_i \delta_i^2
+  \label{eqn:nu-f}
+\end{equation}
+where $\sigma$ is an irrelevant constant. The density moments, MOI scale, and mass are 
+\begin{equation}
+  K_{\ell m} = \frac{V}{\mu_\mathcal{A}a_\mathcal{A}^{\ell}} \sum_i (\delta_i + 1) R_{\ell m}(\bm r_i)
+  \label{eqn:nu-klm}
+\end{equation}
+\begin{equation}
+  I_\mathcal{A} = \mu_\mathcal{A} a_\mathcal{A}^2 = V \sum_i (\delta_i + 1) r_i^2
+  \label{eqn:nu-ia}
+\end{equation}
+\begin{equation}
+  \mu_\mathcal{A} = V\sum_i (\delta_i + 1) \implies 0 = \sum_i \delta_i.
+  \label{eqn:nu-mass}
+\end{equation}
+Writing $\delta_i$ as an $n$-dimensional vector $\bm \delta$, equation \ref{eqn:nu-klm} is a matrix equation for $K_{\ell m}$, and equations \ref{eqn:nu-ia} and \ref{eqn:nu-mass} are vector dot product equations.
+Combining $K_{\ell m}$, $I_\mathcal{A}$, and $0$ into a single vector $\bm K$, these equations can be written as a single underdetermined matrix equation we denote as
+\begin{equation}
+  \bm K = M \bm \delta + \bm C,
+  \label{eqn:nu-matrix}
+\end{equation}
+where the components of constant matrix $M$ and constant vector $\bm C$ are known given a fixed layout of the $n$ regions.
+Some of the components of $\bm K$, such as $I_\mathcal{A}$, $\mu_\mathcal{A}$, and $K_{1m}$, are constraints.
+We treat the other components as parameters of the model.
+The task is then to find $\bm \delta$ that satisfies equation \ref{eqn:nu-matrix} and maximizes $f(\bm \delta)$.
+But the form of equation \ref{eqn:nu-f} shows that the maximum of $\ln f$ (also the maximum of $f$) is the minimum of $|\bm \delta|^2$.
+This shortest value of $\bm \delta$ that obeys equation \ref{eqn:nu-matrix} is given by the Moore-Penrose inverse:
+\begin{equation}
+  \bm \delta = M^+ (\bm K - \bm C); \qquad M^+ = M^\dagger(M M^\dagger)^{-1}
+  \label{eqn:nu-delta}
+\end{equation}
+where $M^\dagger$ is the hermitian conjugate of $M$.
+
+The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
+
+\subsection{Harmonic model}
+In the ``harmonic model'', we limit ourselves to density distributions that are harmonic; i.e., they satisfy $\nabla^2 \rho(\bm r) = 0$.
+We have no physical justification for why this assumption should be true, but it is useful as a simplification to gain qualitative insight into the properties of the asteroid density distribution.
+
+A harmonic density distribution can be expanded in terms of the spherical harmonics as $\rho(\bm r) = \sum_{\ell m} C_{\ell m} R_{\ell m}(\bm r)^*$ where $C_{\ell m}$ are complex, free parameters.
+This series can be truncated at some maximum $\ell$.
+The density moments, MOI scale, and mass can then be explicitly computed as a function of $C_{\ell m}$:
+\begin{equation}
+  K_{\ell m} = \frac{a_\mathcal{A}^{2-\ell}}{I_\mathcal{A}} \sum_{\ell m} C_{\ell' m'} \int_\mathcal{A} d^3 r R_{\ell' m'}(\bm r)^* R_{\ell m}(\bm r)
+  \label{eqn:harmonic-klm}
+\end{equation}
+\begin{equation}
+  I_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^* r^2
+  \label{eqn:harmonic-ia}
+\end{equation}
+\begin{equation}
+  \mu_\mathcal{A} = \sum_{\ell m} C_{\ell m} \int_\mathcal{A} d^3 r R_{\ell m}(\bm r)^*.
+  \label{eqn:harmonic-mass}
+\end{equation}
+Since the integrals are independent of the parameters, they can be computed before solving for $C_{\ell m}$.
+Furthermore, their values when $\mathcal{A}$ is spherical gives us insight into the influence of $K_{\ell m}$ on density distributions.
+In this case, $I_\mathcal{A} \propto C_{00}$ and the integral of equation \ref{eqn:harmonic-klm} is non-zero only when $\ell' = \ell$ and $m'=m$.
+Therefore, $C_{\ell m}$ is proportional to $K_{\ell m}$.
+The density distribution can be immediately visualized given the density moments as a sum of the solid spherical harmonics $R_{\ell m}$ weighted by $K_{\ell m}$.
+When the asteroid is non-spherical, the shape itself contributes to $K_{\ell m}$ so as to alter this picture.
+
+$C_{\ell m}$ can be treated as parameters for a fitting method (such as an MCMC) that enforces our bounds on $\rho(\bm r)$.
+With the integrals pre-computed, obtaining $K_{\ell m}$ from $C_{\ell m}$ is fast.
+We impose these bounds by acknowledging that harmonic functions such as $\rho(\bm r)$ in a region such as $\mathcal{A}$ attain their maxima on the boundary of the region, so that it is only necessary to ensure that $\rho$ lies within the allowed range on the asteroid boundary rather than within the entire asteroid.
+This can be done by parametrizing the asteroid surface as a function of two variables (e.g., latitude and longitude) and minimizing and maximizing $\rho$ with respect to those variables, ensuring these minima and maxima are within the allowed range.
 

### 2022-10-14 paper/mnras/main.tex
Updated paper references

--- 2022-08-26 paper/arxiv/main.tex
@@
 We also perform a sensitivity analysis to asteroid parameters (e.g., asteroid shape and orbital elements), observational set-up (e.g., measurement precision and cadence), and the mapping models used.
-We find that high precision in rotational period estimates ($\lesssim 50$ milliseconds) are necessary for each cadence, and that low perigees ($\lesssim 10$ Earth radii) are necessary to resolve density distributions.
+We find that high precision in rotational period estimates ($\lesssim 0.27$ seconds) are necessary for each cadence, and that low perigees ($\lesssim 18$ Earth radii) are necessary to resolve large-scale density non-uniformities with uncertainties of $\sim 0.1\%$ of the local density under some models.
 \end{abstract}
@@
 These are complex, unitless quantities.
-$\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution and $R_{\ell m}$ are the regular solid spherical harmonics (see appendix \ref{app:eom} for details).
+$\rho_\mathcal{A}(\bm r)$ is the asteroid density distribution and $R_{\ell m}$ are the regular solid spherical harmonics (see Supplementary Material A.2 for details).
 The integral is computed over the entire asteroid mass, denoted $\mathcal{A}$, and $d^3 r$ indicates the three-dimensional volume element throughout the paper.
@@
 where $\bm D$ is the position of the asteroid; $\alpha$, $\beta$, and $\gamma$ are $z-y-z$ Euler angles expressing the orientation of the asteroid; $S_{\ell m}$ are the irregular solid spherical harmonics; and $\mu_\mathcal{B}$ and $a_\mathcal{B}$ are the mass and radius of the central body while $J_{\ell m}$ are the density moments of the central body.
-Equation \ref{eqn:tidal-torque} is derived in appendix \ref{app:eom} via a novel derivation and is accurate to arbitrary order in $D$.
+Equation \ref{eqn:tidal-torque} is derived in Supplementary Material A.4 via a novel derivation and is accurate to arbitrary order in $D$.
 
@@
 Equation \ref{eqn:tidal-torque} indicated that tidal torque was also proportional to $I_\mathcal{A}$.
-The Euler equations, giving angular acceleration in terms of moment of inertia and torque (equation \ref{eqn:omega-eom}), show that the angular acceleration of the asteroid is therefore independent $I_\mathcal{A}$.
+The Euler equations, giving angular acceleration in terms of moment of inertia and torque (Supplementary Material equation A.14), show that the angular acceleration of the asteroid is therefore independent $I_\mathcal{A}$.
 Thus, the observables do not depend explicitly on $I_\mathcal{A}$.
 
-Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed and in which $K_{\ell m}$, $I_\mathcal{A}$, and $a_\mathcal{A}$ are computed), which are also defined in appendix \ref{app:eom}.
+Throughout the paper, we refer to the ``inertial frame'' (the frame in which the orbit is fixed) and the ``body-fixed frame'' (the frame in which the asteroid is fixed and in which $K_{\ell m}$, $I_\mathcal{A}$, and $a_\mathcal{A}$ are computed), which are also defined in Supplementary Material A.1.
 
@@
 Unless otherwise indicated, the simulation is terminated at $D=10 r_p$ as well.
-With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method, with a variable time step, manually chosen to limit integration error to only $\sim 100$ times the floating point numerical error.
+With the simulation inputs specified, the equations of motion are integrated via the Runge-Kutta fourth order method with a variable time step, manually chosen to limit integration error to only $\sim 100$ times the floating point numerical error.
 
@@
 If orientation data is more readily available instead, the same simulation may be used to generate orientation data.
-Appendix \ref{app:orientation} describes the consequences of this change, which are relatively small.
+Supplementary Material C describes the consequences of this change, which are relatively small.
 
@@
 We use the Python implementation \texttt{emcee} \citep{foreman2013emcee}.
-Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in equation \ref{eqn:parameter-bounds}.
+Our parameters were $\gamma_0$, $K_{20}$, $K_{22}$, and $K_{3m}$ (10 in total), bounded by $|\gamma_0| < \pi/4$, and the $K_{2 m}$ bounds given in Supplementary Material equation A.5.
 Computing $K_{3m}$ for many positive density distributions revealed a $|K_{3m}| \lesssim 0.01$ typically, so we use more conservative bounds on $K_{3 m}$ of $|K_{3 m}| < 1$.
@@
 However, by making sufficient assumptions about the density distribution, we can nevertheless measure fluctuations in $\rho_\mathcal{A}(\bm r)$ across the asteroid from $K_{\ell m}$.
-To best understand the density distribution of an asteroid, an ensemble of models with differing assumptions is desired, so that common traits across the models can be identified.
-To this end, we outline two possible models here and discuss two more in appendix \ref{app:more-models}.
+To best understand the density distribution of an asteroid, an ensemble of models with differing assumptions is desired so that common traits across the models can be identified.
+To this end, we outline two possible models here and discuss two more in Supplementary Material C.
 
@@
 \end{equation}
-by equation \ref{eqn:ylm-rotation}.
 Thus, values and  uncertainties on $K_{\ell m}^\mathrm{body-fixed}$ and $\gamma_0$ (obtained from the encounter data) can be translated into values and uncertainties on $K_{\ell m}^\mathrm{hybrid}$.
@@
 Once the parameters of the density distribution models have been extracted, each MCMC sample corresponds to its own density distribution.
-To generate an average distribution, we randomly choose 1,000 of these samples and define the density distribution $\rho$ at each point to be the mean of the densities at that point across the 1,000 samples, and take the standard deviation of the sample densities as the (uncorrelated) density uncertainty $\sigma_\rho$.
+To generate an average distribution, we randomly choose 1,000 of these samples and define the density distribution $\rho$ at each point to be the mean of the densities at that point across the 1,000 samples and take the standard deviation of the sample densities as the (uncorrelated) density uncertainty $\sigma_\rho$.
 In the case of the finite element model, we run the MCMC twenty times and select 1,000 parameter samples from each to reduce dependence on the initial choice of finite element locations.
@@
 For $K_{22}$ and $K_{20}$, we use two standard values: one with $(K_{22}, K_{20}) = (0, -0.097)$ and one with $(0.052, -0.202)$.
-Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$ (a 90$^\circ$ rotation), these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (equation \ref{eqn:parameter-bounds}) and these reference values.
+Including the third point obtained by reflection $K_{22}\rightarrow -K_{22}$ (a 90$^\circ$ rotation), these are the three points that minimize the mean distance between an arbitrary point in the allowed parameter space (Supplementary Material equation A.5) and these reference values.
 The first point is called the symmetric case because the corresponding uniform-density-ellipsoid model is rotationally symmetric around $\unit z$.
@@
 
+Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
+We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
+We focus on the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
+
 \begin{figure*}
@@
 \end{figure*}
-
-Figure \ref{fig:net-uncertainty} depicts $\langle \sigma_\rho / \rho \rangle$ as a function of these other encounter properties, except for the dependence of $\langle \sigma_\rho / \rho \rangle$ on initial spin direction which is better shown as a map in figure \ref{fig:spin-uncertainty}.
-We immediately see that the two density distribution models produce very different density uncertainties, due to the strong model-dependence of their output.
-We focus on the lumpy model's output because it is more sensitive to the encounter properties than the finite element model.
 
@@
 
-The tidal torque experienced by the asteroid is also affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (equation \ref{eqn:omega-eom}).
+The tidal torque experienced by the asteroid is also affected by the initial direction of asteroid spin $\bm \Omega_0$ both because spin sets the initial asteroid orientation up to $\gamma_0$ and because of the spin-dependence of the rotational equations of motion (Supplementary Material equation A.14).
 
@@
 $R_\mathcal{B}$ is the true radius of the body (not $a_\mathcal{B}$ from equation \ref{eqn:aa}).
-For an equatorial orbit, $\epsilon$ and the central body density moments (equation \ref{eqn:jlm}) are related by $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
+For an equatorial orbit, $\epsilon$ and the central body density moments (Supplementary Material equation A.3) are related by $J_{\ell m}$ as $\epsilon = -10J_{20}/3$ and $J_{22} = 0$.
 Since an oblate ellipsoid is mirror-symmetric around all three axes, $J_{3m}$ are all zero.
@@
 We develop and demonstrate a methodology, AIME, which constrains density fluctuations in an asteroid from angular velocity changes occurring during a close encounter.
-We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 10$ Earth radii and the period be $\gtrsim 3.3$ hours (though these thresholds depend on a number of properties of the asteroid and the observational campaign used).
+We find that this inversion process is most sensitive to asteroid perigee and period, specifically requiring that the encounter perigee be $\lesssim 18$ Earth radii, though this threshold depends on a number of properties of the asteroid and the observational campaign.
 Asteroids that tumble strongly after the encounter are also better constrained by AIME.
 Highly precise data, especially in the instantaneous rotational asteroid period, is also required in order to extract precise constraints.
-Due to the sensitivity of the system, we find that it is also necessary to correctly model effects that influence the system very little, such as the oblateness of the central body, in order for accurate density distributions to be extracted.
+Nevertheless, for the reference asteroid and observational campaign used in this paper, we were able to extract large-scale density non-uniformities accurately and precisely, achieving density uncertainties $\sim 0.1\%$ of the density and excluding uniform distributions for non-uniform asteroids.
 
-We also find that the exact density distributions inferred are model-dependent, and their uncertainties can be dominated by model uncertainties when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
+We also find that the density distributions inferred are model-dependent, and their uncertainties can be dominated by model-driven uncertainties when the degrees of freedom available to the model exceeds the number of density moments that can be precisely extracted from the data.
 Models which are specialized to fit for certain features (such as the lumpy model) produce less uncertain results than generalized models (such as the finite element model).
 To efficiently use encounter data, it is therefore important to investigate multiple models and compare results.
-
-In order to further take advantage of close asteroid encounters, improvements to AIME may lead to increased precision of the output.
-Specifically, the angular velocity data set may be lengthened to include more post-encounter data, correlations between observational uncertainties could be incorporated into the uncertainty model, and previous knowledge of some of the asteroid properties (such as moment of inertia) could be used to adjust priors on the density moments.
-The presence of Earth's moon or pre-encounter tumbling of the asteroid may also increase the precision of AIME's density distribution estimates.
 
@@
 
-% \input{appendices}
-
 \bsp

### 2022-10-14 paper/mnras/supplement.tex
Updated paper references

--- 2022-08-26 paper/supplement.tex
@@
 \newcommand{\quat}[1]{\widetilde{\bm{#1}}}
-\setlength{\columnsep}{2em}
+\setlength{\columnsep}{2.3em}
 \renewcommand\floatpagefraction{.55}
 
-\titleformat{\section}
+\counterwithin{figure}{section}
+\counterwithin{table}{section}
+\renewcommand{\thesection}{\Alph{section}}
+\numberwithin{equation}{section}
+
+\titleformat{\section}[block]
   {\normalsize\bfseries}
-  {\thesection}
+  {APPENDIX \thesection:}
   {.5em}
   {\MakeUppercase}
+
 \titleformat*{\subsection}{\normalsize\bfseries}
 
-\title{Constraining the Interiors of Asteroids Through Close Encounters: Appendices}
+\title{\Huge Constraining the Interiors of Asteroids Through Close Encounters: Appendices}
 
@@
 These spherical harmonics obey many useful identities summarized in \cite{Gelderen1998TheSO}, which are also useful for quantum mechanics.
-They were used to define the density moments in equation \ref{eqn:klm}, which can be extended to the central body:
+They were used to define the density moments in equation 1, which can be extended to the central body:
 \begin{equation}
@@
 By contrast, $J_{\ell m}$ should be computed in the inertial frame.
-The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations \ref{eqn:aa} and \ref{eqn:ia}, but they could also be set to any other scales of the same units, e.g.
+The length scale $a_\mathcal{B}$ and MOI scale $I_\mathcal{B}$ can be defined similarly to $a_\mathcal{A}$ and $a_\mathcal{B}$ in equations 3 and 2, but they could also be set to any other scales of the same units, e.g.
 $a_\mathcal{B}$ equal to the central body radius and $I_\mathcal{B} = \mu_\mathcal{B}a_\mathcal{B}^2$, where $\mu_\mathcal{B}$ is the central body mass.
@@
 The only physical density moments for $\ell \leq 2$ are therefore $K_{22}$, $K_{20}$, and $K_{00}$.
-The first two are related to the MOI around each principal axis by equation \ref{eqn:moi}, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in equation \ref{eqn:tidal-torque}.
+The first two are related to the MOI around each principal axis by equation 5, while $K_{00} = \mu_\mathcal{A} a_\mathcal{A}^2 / I_\mathcal{A}$ will not be relevant to this study as it does not appear in equation 4.
 
-The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the semi-axis lengths and can be compared to those found in equation \ref{eqn:moi}.
+The physical meaning of $K_{22}$ and $K_{20}$ can also be interpreted via a special case: if the asteroid is a uniform-density triaxial ellipsoid, the moments of inertia are simple to compute in terms of the semi-axis lengths and can be compared to those found in equation 5.
 This yields semi-axis lengths of
@@
 
-Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies \cite{paul88,HouMar2017,BOUE2009750, ashenberg07}, often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
+Derivations for the tidal torque experienced by a rigid body in the gravitational field of a larger mass have been computed by several previous studies (\cite{paul88,HouMar2017,BOUE2009750, ashenberg07}), often in terms of the MOI of the rigid body (or higher order moments of inertia), and to varying degrees of precision.
 A simple, first-order derivation is also easily computable in terms of the asteroid MOI in the inertial frame.
@@
 
-Incidentally, it is the $|\bm R| < |\bm R'|$ assumption that inspires the assumption that there are ``no \textit{distant} perturbing objects'' (section \ref{sec:methods}).
+Incidentally, it is the $|\bm R| < |\bm R'|$ assumption that inspires the assumption that there are ``no \textit{distant} perturbing objects'' (section 2).
 If a perturbing object such as a moon is not distant (i.e., it is closer to the system center of mass than the asteroid perigee so that $|\bm R| < |\bm R'|$ always), then it can be absorbed into $J_{\ell m}$ by equation \ref{eqn:jlm} and the assumptions of this derivation are not violated.
@@
 \end{equation}
-tidal torque can now be expressed as a function only of the constants $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A/B}$, $I_\mathcal{A/B}$, and the asteroid orientation and position (equation \ref{eqn:tidal-torque}).
+tidal torque can now be expressed as a function only of the constants $J_{\ell m}$, $K_{\ell m}$, $a_\mathcal{A/B}$, $I_\mathcal{A/B}$, and the asteroid orientation and position (equation 4).
 Some $K_{\ell m}$ terms are written in this equation with $|m|>\ell$; these should all be taken to be zero.
@@
 \end{equation}
-Equations \ref{eqn:tidal-torque}, \ref{eqn:moi}, \ref{eqn:pos-eom}, and \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
+Equations 4, 5, \ref{eqn:pos-eom}, and \ref{eqn:omega-eom} form a set of non-linear, first-order coupled differential equations in which can be numerically integrated.
 They are expressed in terms of the physical parameters $I_\mathcal{A/B}$, $a_\mathcal{A/B}$, $J_{\ell m}$, and $K_{\ell m}$ which are constant if the asteroid is rigid and the central body does not rotate.
 
-\section{Comparing orientation and angular velocity data}
+\section{Comparing orientation \& angular velocity data}
 \label{app:orientation}
@@
 \subsection{Uncertainty model}
-To use an asteroid orientation data set rather than angular velocity, we must create an uncertainty model for orientation observations and produce a likelihood to be used by the MCMC (replacing equation \ref{eqn:log-likelihood}).
+To use an asteroid orientation data set rather than angular velocity, we must create an uncertainty model for orientation observations and produce a likelihood to be used by the MCMC (replacing equation 7).
 
@@
 
-Two models were discussed in section \ref{sec:density-distro} to translate density moment constraints into density distribution constraints.
+Two models were discussed in section 2.4 to translate density moment constraints into density distribution constraints.
 Here we outline two additional models which are less conventional but still useable for extracting density distribution properties.
@@
 
-The prior distribution on $\rho(\bm r)$ discussed in section \ref{sec:fit} can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
+The prior distribution on $\rho(\bm r)$ discussed in section 2.3 can be implemented by individually checking the components $\bm \delta$ computed by equation \ref{eqn:nu-delta} and confirming that $1 + \delta_i$ lies within the acceptable range of densities.
 
@@
 
-\printbibliography
+% \printbibliography
 

### 2022-10-14 code/thresholds/thresholds.py

@@ -70,7 +70,7 @@ DIRECTORIES = [
     "lumpy",
 ]
 
-THRESHOLDS = ((0.0005369031978644279, "solid", "threshold"),)
+THRESHOLDS = ((0.001, "solid", "threshold"),)
 
 if PULL:
     for directory in DIRECTORIES:
@@ -182,7 +182,7 @@ for directory in DIRECTORIES:
             axs[i].set_xticks(perigee_tick_poses)
             axs[i].set_xticklabels([str(p) for p in perigee_tick_poses])
         if i % 4 == 0:
-            axs[i].set_ylabel("$\sigma_\\rho / \\rho$")
+            axs[i].set_ylabel("$\\langle \sigma_\\rho / \\rho \\rangle$")
 
 fig.legend([handles["lumpy"], handles["fe"], handles["threshold"]], ["Lumpy", "Finite element", "Threshold"], loc="upper center", ncol=3, bbox_to_anchor=(0.5,1.1))
 axs[7].annotate('', xy=(0.9, 0.9), xycoords='axes fraction', xytext=(0.9, 0.4), 

### 2022-10-14 data/all-fig/compile.py

@@ -60,14 +60,14 @@ specialized_y_labels = {
 }
 
 thresholds = {
-    "scan-perigee-sync": (10.05645830142579,),
-    "probe-s-theta": (0.15813979997110503,),
+    "scan-perigee-sync": (17.64784118356001,),
+    "probe-s-theta": (0.6113839751941476,),
     "scan-cadence":	(None,),
-    "scan-period-sync": (3.342475232084257,),
+    "scan-period-sync": (None),
     "scan-am": (None,),
     "scan-vex-sync": (None,),
     "observation-gap": (None,),
-    "probe-s-rho": (1.708724170502394e-06,),
+    "probe-s-rho": (8.228524489683316e-06,),
 }
 
 
